### 2020-09-08 RR_manuscript/Draft_RR.Rmd
first (incomplete) draft of RR

---
title             : "Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech."
shorttitle        : "Many analysts - one speech data set"

author: 
  - name          : "First Author"
    affiliation   : "#"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Second Author"
    affiliation   : "#"
    role:
      - Writing - Review & Editing
  - name          : "..."
    affiliation   : "#"
    role:
      - Writing - Review & Editing    
  - name          : "Last Author"
    affiliation   : "#"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "#"
  - id            : "..."
    institution   : "..."

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust. In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al. 2018, REF) leading to what is now referred to as the *replication crisis*. Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS). The latter situation has been referred to as the *inference crisis* (Rotello, Heit & Dubé 2015, Starns et al. 2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, & Simonsohn, 2011, Gelman & Loken 2013). Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data. Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation. These researcher degrees of freedom are a blessing and a curse at the same time.

There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g. Box 1976, Tukey 1977, de Groot 2014). They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al. 2011). Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020). These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables. Human behavior is complex and offers many ways to be translated into numbers. This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data. In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it. This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.

In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data. We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. Specifically we report the impact of analytic pipeline on research results obtained by ## teams that gained access to the same raw data set to answer the same research question.

## Researcher degrees of freedom
Data analysis comes with many decisions like how to operationalize  a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. This can be problematic because to err is human.

We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975). In connection with an academic incentive system that rewards certain discovery process more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few. This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019). Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to an vast plurality of analytic approaches.

Consequently - if methodologists are correct (e.g. Simmons et al. 2011, Gelman & Loken 2013) - there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies. These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analysed differently. However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. Critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).

While this issue has been widely discussed both from a conceptual point of view (Simmons et al. 2011, Wagenmakers et al. 2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g. Wichert et al. 2015, Charles et al. 2019, Roettger 2019), there is still little known about the extend of analytical plurality in practice. Recent collaborative attempts have started to shed light on how different analyst tackle the same data set and revealed, not surprisingly, a large amount of variability.

## Crowdsourcing alternative analyses
In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research question. Analytic approaches and consequently the results varied widely between teams. 69% of the teams found support for the hypothesis, and 31% did not. Out of the 29 analysis strategies, there were 21 unique combinations of covariates. Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias. Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

Neuroscience
Cognitive Modelling
Clinical
Predictive models

While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling. In these studies the data tables were fixed and data collection or extraction could not be changed. However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question. In social sciences, the raw observations correspond to recorded human behavior. In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporal extended exhibits a complex structure. Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. To understand how analytical flexibility manifests itself in a scenario where complex signals need to be operationalized, the present paper looks at an experimentally elicited speech data set

## Operationalizing speech 
*(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)*

RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.

In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings. Speech offers a considerable number of perspectives and decisions along the data analysis pipeline.

IMAGE SHOWING A WAVE FORM WITH DIFFERENT DOMAINS (temporal) AND STRUCTURAL CUES (e.g. f0, dur, int) MAPPING ONTO FUNCTIONAL CONTRASTS

When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization the relevant behavior, i.e. how to measure the phenomenon of interest. For example, how do we measure whether two sounds are acoustically identical (e.g. "bear" vs. "pear"), whether one word is more prominent than others ("He told YOU to be quite"), or whether two discourse functions are produced differently ("It's raining." vs. "It's raining?")? In other words, how do we quantitatively capture relevant features of speech?

This is not trivial. Speech categories are inherently multidimensional and vary through time. The acoustic parameters for one category are usually asynchronous, i.e. appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g. Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014). For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic (Lisker, 1977). Even temporally dislocated acoustic parameters correlate with this lexical contrast. For example, in the English words "led" versus "let", voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins & Nguyen, 2004).

The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. Studies investigating acoustic correlates of word stress (i.e. the difference between "insight" and "incite"), for example, have been using many different measurements including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g. Gordon & Roettger, 2017).

Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). All of these phonetic parameters are potential manifestations of underlying functional contrasts like speaker's intentions, levels of arousal or identity.

When testing hypotheses on speech production data, researchers need to make many decisions. The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. These decisions are usually made prior to any statistical analysis, but can possible be revised in interaction with downstream analysis steps. To probe the variability in data analysis pipelines across researchers, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.

## The data set - The prosody of redundant modifiers
Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g. “a blue banana” vs. “a yellow banana”)?

Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in the language science. It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana. The context within which an entity occurs (other non-fruits, other fruits, other bananas) plays a large part in determining the choice of referential expression. Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975) and are therefore expected to only use for example a modifier if it is necessary for disambiguation (e.g. the adjective "yellow" when there is a yellow and a less ripe green banana).

Despite this coherent idea of rational and efficient speakers, there is much evidence that speakers are often overinformative: Speaker use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al. 2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al. 2011, Paraboni et al. 2007, Rubio-Fernandez 2016). Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object. For example, Degen et al. (2020) showed that modifiers that are less typical for a given referent (e.g. a blue banana) are more likely to be used in an overinformative scenario (e.g. there is just one banana).

This account, however, has mainly focused on content selection (Gatt et al. 2013), i.e. whether a certain referential expression is chosen or not. However, speech communication is so much richer. Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g. Ladd 2008). Most prominently, languages use intonation to signal discourse relationships between referents (among other functions). Intonation marks discourse-relevant referents for being new or given information to guide listeners’ interpretation of incoming messages. In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse. Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse. Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on ‘banana’ to indicate the contrastive nature of the *noun.* In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on ‘yellow’ to indicate the contrastive nature of the *modifier.* In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e. segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

INFORMATION ABOUT THE DATA SET AND EXP DESIGN

## Research questions

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-09-08 RR_manuscript/Draft_RR.tex
first (incomplete) draft of RR

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.},
  pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
  pdflang={en-EN},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Many analysts - one speech data set}
\keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.}
\author{First Author\textsuperscript{\#}, Second Author\textsuperscript{\#}, \ldots{}\textsuperscript{\#}, \& Last Author\textsuperscript{\#}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Second Author: Writing - Review \& Editing; \ldots{}: Writing - Review \& Editing; Last Author: Writing - Review \& Editing.

Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} \#\\\textsuperscript{\ldots{}} \ldots{}}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust. In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al.~2018, REF) leading to what is now referred to as the \emph{replication crisis}. Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS). The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013). Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data. Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation. These researcher degrees of freedom are a blessing and a curse at the same time.

There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014). They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al.~2011). Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020). These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables. Human behavior is complex and offers many ways to be translated into numbers. This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data. In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it. This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.

In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data. We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. Specifically we report the impact of analytic pipeline on research results obtained by \#\# teams that gained access to the same raw data set to answer the same research question.

\hypertarget{researcher-degrees-of-freedom}{%
\subsection{Researcher degrees of freedom}\label{researcher-degrees-of-freedom}}

Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. This can be problematic because to err is human.

We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975). In connection with an academic incentive system that rewards certain discovery process more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few. This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019). Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to an vast plurality of analytic approaches.

Consequently - if methodologists are correct (e.g.~Simmons et al.~2011, Gelman \& Loken 2013) - there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies. These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analysed differently. However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. Critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).

While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there is still little known about the extend of analytical plurality in practice. Recent collaborative attempts have started to shed light on how different analyst tackle the same data set and revealed, not surprisingly, a large amount of variability.

\hypertarget{crowdsourcing-alternative-analyses}{%
\subsection{Crowdsourcing alternative analyses}\label{crowdsourcing-alternative-analyses}}

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research question. Analytic approaches and consequently the results varied widely between teams. 69\% of the teams found support for the hypothesis, and 31\% did not. Out of the 29 analysis strategies, there were 21 unique combinations of covariates. Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias. Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

Neuroscience
Cognitive Modelling
Clinical
Predictive models

While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling. In these studies the data tables were fixed and data collection or extraction could not be changed. However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question. In social sciences, the raw observations correspond to recorded human behavior. In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporal extended exhibits a complex structure. Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. To understand how analytical flexibility manifests itself in a scenario where complex signals need to be operationalized, the present paper looks at an experimentally elicited speech data set

\hypertarget{operationalizing-speech}{%
\subsection{Operationalizing speech}\label{operationalizing-speech}}

\emph{(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)}
RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.

In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings. Speech offers a considerable number of perspectives and decisions along the data analysis pipeline.

IMAGE SHOWING A WAVE FORM WITH DIFFERENT DOMAINS (temporal) AND STRUCTURAL CUES (e.g.~f0, dur, int) MAPPING ONTO FUNCTIONAL CONTRASTS

When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization the relevant behavior, i.e.~how to measure the phenomenon of interest. For example, how do we measure whether two sounds are acoustically identical (e.g.~\enquote{bear} vs.~\enquote{pear}), whether one word is more prominent than others (\enquote{He told YOU to be quite}), or whether two discourse functions are produced differently (\enquote{It's raining.} vs.~\enquote{It's raining?})? In other words, how do we quantitatively capture relevant features of speech?

This is not trivial. Speech categories are inherently multidimensional and vary through time. The acoustic parameters for one category are usually asynchronous, i.e.~appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014). For example, the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \enquote{bear} vs.~\enquote{pear}) can be manifested by many different acoustic (Lisker, 1977). Even temporally dislocated acoustic parameters correlate with this lexical contrast. For example, in the English words \enquote{led} versus \enquote{let}, voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins \& Nguyen, 2004).

The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. Studies investigating acoustic correlates of word stress (i.e.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).

Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g.~Niebuhr et al., 2011). They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005). All of these phonetic parameters are potential manifestations of underlying functional contrasts like speaker's intentions, levels of arousal or identity.

When testing hypotheses on speech production data, researchers need to make many decisions. The larger the functional domain (e.g.~are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. These decisions are usually made prior to any statistical analysis, but can possible be revised in interaction with downstream analysis steps. To probe the variability in data analysis pipelines across researchers, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.

\hypertarget{the-data-set---the-prosody-of-redundant-modifiers}{%
\subsection{The data set - The prosody of redundant modifiers}\label{the-data-set---the-prosody-of-redundant-modifiers}}

Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g.~\enquote{a blue banana} vs.~\enquote{a yellow banana})?

Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in the language science. It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana. The context within which an entity occurs (other non-fruits, other fruits, other bananas) plays a large part in determining the choice of referential expression. Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975) and are therefore expected to only use for example a modifier if it is necessary for disambiguation (e.g.~the adjective \enquote{yellow} when there is a yellow and a less ripe green banana).

Despite this coherent idea of rational and efficient speakers, there is much evidence that speakers are often overinformative: Speaker use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016). Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object. For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an overinformative scenario (e.g.~there is just one banana).

This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not. However, speech communication is so much richer. Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008). Most prominently, languages use intonation to signal discourse relationships between referents (among other functions). Intonation marks discourse-relevant referents for being new or given information to guide listeners' interpretation of incoming messages. In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse. Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse. Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun.} In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier.} In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.

INFORMATION ABOUT THE DATA SET

\hypertarget{research-questions}{%
\subsection{Research questions}\label{research-questions}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.0.2; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2020-09-17 docs/ExperimentalDetails/Experimental_details.Rmd
Experimental Details

---
title: "Methodological Details - Blue Bananas"
author: ""
date: "9/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)

```

## 1. Research Questions
Do speakers modify the speech signal to indicate the typicality of the modifier of the noun?

## 2. Participants
Participants were paid for participation. Participants were 30 native German speakers (who grew up in a monolingual environment) recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.

## 3. Procedure
In this production study, subjects had to verbally instruct the experimenter to select a certain object from sets of alternatives. The alternatives differ with respect to their colour, their identity, or both. Objects are referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g. yellow banana). These noun phrases differ with respect to the typicality of their combination, as discussed in the stimuli section.

Participants were seated in front of a computer screen. The experimenter sat at the opposite side of the table in front of another computer screen. Participants and experiment could not see each other.

In a familiarization phase, participants saw one object per trial. In order to advance to the next trial, participants had to read the corresponding noun phrase out (e.g. red cucumber). During this phase, Participants had to name all atypical colour-object targets that we used in the critical period of the experiment as well as their typical counterparts. For example, if red cucumber (atypical) was an experimental target, participants were presented with both the red cucumber (atypical) and the green cucumber (typical). The familiarization phase thus exposes participants to the full range of typicality preceding the critical trials in order for subjects to perceive (a)typicality in relative terms. After the familiarization phase, the experiment moved on to the training and the test phase. Training and test phase differed only in the choice of stimuli. In the training phase, only objects that do not occur as targets and competitors in the test phase were used.

On each trial in the test phase, participants first see four coloured objects in the top left, top right, bottom left, and bottom right of the screen, respectively. One of the object, served as the target, another served as a competitor, and the remaining two served as unrelated distractors. The position of the visual stimuli was randomized for each trial. In the center of the picture, a black cube was displayed which could be moved by the experimenter. The participants were asked to instruct the experimenter to move the cube onto one of the four pictures.

After 1500 ms, a ‘trigger’ sentence containing the competitor was orthographically presented below the cube:

“Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”
engl. “You have to put the cube on top of the green sunglasses.”

The trigger sentence was supposed to set a discourse context, such that the colour and the competitor referent were introduced as background information (here: green and sunglasses). The competitor referent was visually indicated by an arrow. The trial proceeds when the experimenter has moved the cube onto the respective referent. Subsequently, the sentence and the arrow disappeared and participants were presented with a new sentence containing the target referent:

“Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”
“And now, you have to put the cube on top of the green avocado.”

Again, the target referent is visually indicated by an arrow. The sentence is orthographically displayed in the middle of the screen. When the experimenter completed the move of the cube to the respective referent, the trial was completed and the next trial initiated. There was a 3000 ms inter stimulus interval (grey screen) between trials. In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they see the arrow and the target sentence.

Using the trigger sentence to set up the discourse context enabled us to manipulate the focus structure of the target sentence. If the colour of the competitor and the target are of the same object type but differed in colour, the colour adjective was in focus (henceforth the Adjective Focus (AF) condition). If the objects differed but not their colour, the noun was in focus (henceforth the Noun Focus (NF) condition). If both the colour and the object differed, the whole noun phrase was in focus (henceforth the Adjective Noun Focus (ANF) condition).

While we included all three focus conditions, the study was originally planned to only look at Noun focus. AF and ANF serve as filler trials. There are 15 NF trials, and 10 AF and ANF trials each. Each trial occurs two times, yielding a total of 70 trials.

The code of the experiment is available [here](https://github.com/SBRitter/fruits-production)

```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen at the beginning of a trials. The discourse setting trigger sentence is displayed in the middle below the cube. The participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow)."}

knitr::include_graphics("sample_experiment_screen_competitor.png")

```

```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen after the trigger sentence. The target sentence is displayed in the middle of the screen. Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow)."}

knitr::include_graphics("sample_experiment_screen_target.png")

```

## 4. Stimuli

### 4.1 Norming study

Images of colored referents serve as visual stimuli. The selection of stimuli was based on a norming study, as described in the following.

We selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs). Selection criteria were mainly informed by visual discriminability and phonemic composition, such that referential expressions were supposed to contain many voiced segments. We created different visual versions of each individual referent. Each version was created by manipulating a photograph of the object in the image editor [gimp](http://www.gimp.org). The photographs were collected from internet databases containing copyright-free high-resolution images (e.g. [Pixabay](https://pixabay.com)). During the manipulation process, the background of the pictures was replaced by a white background. In order to change the colour of the objects, a layer in the respective colour was created and overlaid on top of the original graphics using “Colour” as the layer mode. The hexadecimal colour codes for the colours used are listed here:

Blue: #29429f
Green: #3f8535
Red: #9d1c1c
Purple: #6d1b79
Brown: #2a1d11
Yellow: #e3c917
Orange: #ff8400
Orange (potatoes): #ff6600
Black: #000000
Grey: #FFFFFF

The same colour code was used across referents to achieve a particular colour, except for orange, which had to be adjusted for potatoes to be more distinct from the original colour brown. To achieve grey colouring, a white layer was used – the interaction between the original layer and a white overlay actually resulted in a grey colour on the object. To achieve a darker black on certain fruits, the colour spectrum of the original picture had to be manipulated using Gimp’s Colour Curves tool. This tool allowed us to darken or brighten certain colour channels of the picture. Parts of the fruits that did not have the body colour of the fruit (e.g. like stalks and leaves) were left in their original colour. All pictures with natural and manipulated colors are available [here](https://osf.io/rdtx5/).

The colours for the twenty FOODs were chosen as to be perceived as having different degrees of typicality for each respective object, e.g. a banana is typically yellow, a less typical banana would be brown or green and an atypical exemplar could be blue. Every FOOD was presented in four of nine manipulated colours alongside its original colour. We assumed that the four NON-FOODs did not have a prototypical colour. We thus expected different colours to be comparably typical for these objects. The German nouns for all objects were either feminine singular or they occur in their plural form (e.g. grapes).

We used the following colours: black, blue, brown, green, grey, orange, purple, red, yellow.

We used the following FOODs: apricot, avocado, banana, beans, carrot, cherry, cucumber, eggplant, grapes, lemon, mandarine, pear, pepper, pineapple, potatoes, strawberry, tomato, walnut, zucchini.

We used the following NON-FOODs: clothespin, paper clip, socks, sunglasses.

100 German native speakers participated in the norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac). We presented all objects in different colours to our subjects. FOODs came in 5 colours per object, NON-FOODs came in all nine colours. Subjects were instructed to rate how typical they think the colour for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design [here]](https://github.com/stelaseldano/colour-typicality-norming).

### 4.2 Selection of experimental stimuli

The norming ratings were subsequently used to choose appropriate stimuli for the production study, using the following procedure. The results of the norming study can be retrieved [here](https://osf.io/znpg5/).

First, we chose five colours from the norming data set: yellow, green, red, orange, and brown. Those were the most frequent colours in the superset and their norming ratings varied strongly as a function of the referent.

Second, we sorted the FOODs according to their typicality ratings and binned them into typical, atypical, and medium typical. Typical FOODs are defined by norming ratings above 90. Atypical FOODs are defined by norming ratings below 25. Mediocre typical FOODs are defined by norming ratings in between 25 and 90. For each colour and typicality, we selected one FOOD. Each cell was occupied by a different FOOD.

For the critical focus condition (NF) we thus had 15 target FOODs (5 colours x 3 typicality categories), as given below:

atypical:
Yellow cherry (Gelbe Kirsche)
Green carrot (Grüne Möhre)
Red cucumber (Rote Gurke)
Orange grapes (Oangene Trauben)
Brown pepper (Braune Paprika)

medium:
Yellow peas (Gelbe Erbsen)
Green tomato (Grüne Tomate)
Red apricot (Rote Aprikose)
Orange potatoes (Orangene Kartoffeln)
Brown banana (Braune Banane)

typical:
Yellow lemon (Gelbe Zitrone)
Green green beans (Grüne Bohnen)
Red strawberry (Rote Erdbeere)
Orange mandarine (Orangene Mandarine)
Brown walnut (Braune Walnuss)

The set of 15 competitors from the NON-FOOD subset is chosen such that there are as many distinct competitors in each colour as there are targets. The set consists of:

Yellow sunglasses (Gelbe Sonnenbrille)
Yellow socks (Gelbe Socken)
Yellow clothes peg (Gelbe Wäscheklammer)
Green sunglasses (Grüne Sonnenbrille)
Green socks (Grüne Socken)
Green Paper clip (Grüne Büroklammer)
Red socks (Rote Socken)
Red paper clip (Rote Büroklammer)
Red clothes peg (Rote Wäscheklammer)
Orange socks (Orangene Socken)
Orange paper clip (Orangene Büroklammer)
Orange clothes peg (Orangene Wäscheklammer)
Brown sunglasses (Braune Sonnenbrille)
Brown paper clip (Braune Büroklammer)
Brown clothes peg (Braune Wäscheklammer)

The pairing of targets and competitors was randomized for each subject, with the only constraint that the competitor was of the same colour as the target referent but a different object (e.g. if blue banana was the target, blue grapes was the competitor) (see randomization section below for more detail).

For the filler focus conditions (AF + NAF), we distributed FOODs and NON-FOODs, such that over the whole experiment (a) the frequency of target FOODs is counterbalanced (3 times each) and (b) the frequency of target colour is counterbalanced (14 times each).

For all three conditions, a subset of visual distractors was chosen out of our superset from the norming study: Distractors are FOODS that are not used as targets or competitors (avocado, egg plant, pear, zucchini) and all NON-FOODs. They could have any of the five colours. Within each given trial, the distractors did neither share colour or object identity with the target or the competitor.

Overall, the sets of target, competitors and distractors are chosen such that all five colours occur equally often throughout the experiment, i.e. 28 times.

## 4.3 Randomization
For each trial, targets, competitors, and distractors are chosen in a randomized fashion, fulfilling the following requirements:

- NF-Condition:
Colour of Target = Colour of Competitor
Object of Target != Object of Competitor

- AF-Condition:
Colour of Target != Colour of Competitor
Object of Target = Object of Competitor

- ANF-Condition:
Colour of Target != Colour of Competitor
Object of Target != Object of Competitor

- All conditions:
Both distractors have to be different in colour and object from target and competitor.

The competitor and distractors are matched iteratively to a target. One competitor can only be used twice or a third time if all other competitors that are still left have been considered and prove inappropriate.

The quadruples for the three conditions are formed separately. After the three lists have been compiled, they are merged. The sequence of quadruples is randomized such that the following requirements are met:

- The target colour of one quadruple must not equal the competitor colour of the next to avoid a contrastive focus on the next competitor noun
- The target object of one quadruple must not equal the competitor object of the next to avoid a contrastive focus on the next competitor adjective
- The list can have the same experimental condition in adjacent trials only in 12% of cases at the maximum

One randomised list for each subject is produced and doubled, so that each unique trial occurs twice during a recording session. In case the doubling of the list leads to violation of the above criteria, the first trial of the repetition list is moved until the criteria are met.

The python code for the randomization is available [here](https://github.com/SBRitter/fruits-randomization).

### 2020-09-17 scripts/r/00_libs.R
add scripts directories and gantt fig scripts

@@ -1,0 +1,11 @@
+# Packages --------------------------------------------------------------------
+
+library("here")
+library("purrr")
+library("dplyr")
+library("tidyr")
+library("glue")
+library("ggplot2")
+library("ganttrify")
+
+# -----------------------------------------------------------------------------

### 2020-09-17 scripts/r/00_plot_gantt.R

@@ -1,0 +1,70 @@
+# GANTT chart for RR ----------------------------------------------------------
+#
+# Last update: 20200917
+# About: This script produces a gantt chart of our project timeline
+#
+# -----------------------------------------------------------------------------
+
+
+
+# Source libs -----------------------------------------------------------------
+
+source(here::here("scripts", "r", "00_libs.R"))
+
+# -----------------------------------------------------------------------------
+
+
+
+
+# Create timeline df ----------------------------------------------------------
+
+# This is proof of concept, will change
+time_line_df <- tribble(
+  ~'wp',                ~'activity',          ~'start_date',  ~'end_date',
+  "Investigative team", "Registered report",  "2020-09-16",   "2020-12-15",
+  "Investigative team", "Materials prep.",    "2020-09-16",   "2020-10-20",
+  "Investigative team", "Recruting",          "2020-12-15",   "2021-02-15",
+  "Investigative team", "Analyses",           "2021-06-16",   "2021-08-15",
+  "Investigative team", "Registered report",  "2021-08-16",   "2021-09-15",
+  "Data teams",         "Data processing",    "2021-02-15",   "2021-03-14",
+  "Data teams",         "Reporting",          "2021-05-14",   "2021-06-16"
+)
+
+# "Spots" can be used to mark when things actually occur on expected timeline
+# Not used for now ("X" implies something is finished)
+time_line_spots <- tribble(
+  ~'activity',           ~'spot_type', ~'spot_date', 
+  "Data visualisation",  "X",         "2020-10-30", 
+  "Writing",             "X",         "2020-10-31"
+)
+
+# -----------------------------------------------------------------------------
+
+
+
+
+
+
+
+
+# Generate and save plot ------------------------------------------------------
+
+p_project_timeline <- ganttrify(
+  project = time_line_df,
+  #spots = time_line_spots,
+  by_date = TRUE,
+  exact_date = TRUE,
+  size_text_relative = 1.2,
+  month_number = FALSE,
+  font_family = "Times"
+)
+
+
+devices        <- c('pdf', 'png')
+path_gantt     <- file.path(here("figs"), "project_timeline.")
+
+walk(devices, ~ ggsave(filename = glue(path_gantt, .x), 
+                       plot = p_project_timeline, device = .x, 
+                       height = 5, width = 9, units = "in"))
+
+# -----------------------------------------------------------------------------

### 2020-09-17 scripts/r/00_plot_gantt.R
incldue source comments re ganttrify

@@ -2,6 +2,8 @@
 #
 # Last update: 20200917
 # About: This script produces a gantt chart of our project timeline
+#        The plot is produced using ganttrify: 
+#        https://github.com/giocomai/ganttrify
 #
 # -----------------------------------------------------------------------------
 

### 2020-10-15 docs/ExperimentalDetails/Experimental_details.Rmd
make reading experience more smooth

@@
 ## 1. Research Questions
-Do speakers modify the speech signal to indicate the typicality of the modifier of the noun?
+This study investigates whether speakers modify the speech signal to signal atypical referents?
+Concretely, we ask whether the suprasegmental profile of an utterance with an atypical referent like "blue banana" is different from one with a typical referent such as "yellow banana".
 
 ## 2. Participants
-Participants were paid for participation.
-Participants were 30 native German speakers (who grew up in a monolingual environment) recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
+30 native German speakers participated in this study.
+All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
+Participants were paid for their participation.
 
 ## 3. Procedure
-In this production study, subjects had to verbally instruct the experimenter to select a certain object from sets of alternatives.
-The alternatives differ with respect to their colour, their identity, or both.
-Objects are referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g.
-yellow banana).
-These noun phrases differ with respect to the typicality of their combination, as discussed in the stimuli section.
+In this production study, participants interacted with the experimenter.
+Participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
+The non-target objects differed from the target with respect to their colour, their identity, or both.
+Objects were referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g.
+yellow banana, blue banana).
+These adjective-noun combinations differed with respect to the typicality of their combination.
+The adjective-noun combinations were either typical, medium typical, or atypical (as established in a norming study, see additional materials).
+Some combinations were typical such as yellow banana, red tomato, or yellow apricot; some were atypical such as red banana, purple tomato, or blue apricot; and some were somewhat in the middle like brown banana, green tomato, and red apricot (see )
+
+```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}
+
+knitr::include_graphics("typicality_examples.png")
+
+```
 
@@
 The experimenter sat at the opposite side of the table in front of another computer screen.
-Participants and experiment could not see each other.
+Participants and experimenter could see neither each other nor each others' screens.
+The experiment consisted of two phases.
+A familiarization phase and a test phase.
 
 In a familiarization phase, participants saw one object per trial.
-In order to advance to the next trial, participants had to read the corresponding noun phrase out (e.g.
-red cucumber).
-During this phase, Participants had to name all atypical colour-object targets that we used in the critical period of the experiment as well as their typical counterparts.
-For example, if red cucumber (atypical) was an experimental target, participants were presented with both the red cucumber (atypical) and the green cucumber (typical).
-The familiarization phase thus exposes participants to the full range of typicality preceding the critical trials in order for subjects to perceive (a)typicality in relative terms.
-After the familiarization phase, the experiment moved on to the training and the test phase.
-Training and test phase differed only in the choice of stimuli.
-In the training phase, only objects that do not occur as targets and competitors in the test phase were used.
+In order to advance to the next trial, participants had to read out loud the corresponding noun phrase (e.g.
+blue banana).
+During this phase, participants had to name all atypical colour-object targets that we used in the test phase of the experiment alongside their typical counterparts.
+For example, if red banana (atypical) was an experimental target, participants were presented with both the red banana (atypical) and the yellow banana (typical).
+We included this familiarization phase in order to expose participants to the full range of typicality for each object.
 
-On each trial in the test phase, participants first see four coloured objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
-One of the object, served as the target, another served as a competitor, and the remaining two served as unrelated distractors.
-The position of the visual stimuli was randomized for each trial.
-In the center of the picture, a black cube was displayed which could be moved by the experimenter.
+After the familiarization phase, participants entered the test phase.
+On each trial in the test phase, participants first saw four coloured objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
+One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
+The position of the visual stimuli was randomized for each trial and each participant.
+In the center of the screen, a black cube was displayed which could be moved by the experimenter.
 The participants were asked to instruct the experimenter to move the cube onto one of the four pictures.

### 2020-10-15 docs/ExperimentalDetails/Experimental_details.Rmd
a little better hopefully

@@
 These adjective-noun combinations differed with respect to the typicality of their combination.
-The adjective-noun combinations were either typical, medium typical, or atypical (as established in a norming study, see additional materials).
-Some combinations were typical such as yellow banana, red tomato, or yellow apricot; some were atypical such as red banana, purple tomato, or blue apricot; and some were somewhat in the middle like brown banana, green tomato, and red apricot (see )
+The adjective-noun combinations were either typical, medium typical, or atypical (as established in a norming study, see [additional materials](#adds)).
+Some combinations were typical such as yellow banana, red tomato, or yellow apricot; some were atypical such as red banana, purple tomato, or blue apricot; and some were somewhat in the middle like brown banana, green tomato, and red apricot.
 
@@
 For example, if red banana (atypical) was an experimental target, participants were presented with both the red banana (atypical) and the yellow banana (typical).
-We included this familiarization phase in order to expose participants to the full range of typicality for each object.
+This familiarization phase was included in order to ensure that participants can relate typical and atypical colour-object combinations to each other.
 
@@
 
-After 1500 ms, a ‘trigger’ sentence containing the competitor was orthographically presented below the cube:
+Each test trial consisted of two parts.
+The 'trigger' instruction and the 'test' instruction.
+After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a ‘trigger’ instruction was orthographically presented below the cube (see Figure #):
 
 “Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”
-engl. “You have to put the cube on top of the green sunglasses.”
 
-The trigger sentence was supposed to set a discourse context, such that the colour and the competitor referent were introduced as background information (here: green and sunglasses).
-The competitor referent was visually indicated by an arrow.
-The trial proceeds when the experimenter has moved the cube onto the respective referent.
-Subsequently, the sentence and the arrow disappeared and participants were presented with a new sentence containing the target referent:
-
-“Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”
-“And now, you have to put the cube on top of the green avocado.”
-
-Again, the target referent is visually indicated by an arrow.
-The sentence is orthographically displayed in the middle of the screen.
-When the experimenter completed the move of the cube to the respective referent, the trial was completed and the next trial initiated.
-There was a 3000 ms inter stimulus interval (grey screen) between trials.
-In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they see the arrow and the target sentence.
-
-Using the trigger sentence to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
-If the colour of the competitor and the target are of the same object type but differed in colour, the colour adjective was in focus (henceforth the Adjective Focus (AF) condition).
-If the objects differed but not their colour, the noun was in focus (henceforth the Noun Focus (NF) condition).
-If both the colour and the object differed, the whole noun phrase was in focus (henceforth the Adjective Noun Focus (ANF) condition).
-
-While we included all three focus conditions, the study was originally planned to only look at Noun focus.
-AF and ANF serve as filler trials.
-There are 15 NF trials, and 10 AF and ANF trials each.
-Each trial occurs two times, yielding a total of 70 trials.
-
-The code of the experiment is available [here](https://github.com/SBRitter/fruits-production)
+*engl. 'You have to put the cube on top of the green sunglasses.'*
 
@@
 
+The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (here: green and sunglasses).
+The trial proceeded when the experimenter has moved the cube onto the respective referent.
+The sentence and the arrow disappeared.
+Subsequently, the target object was visually highlighted by an arrow and the test instruction was presented containing the target object (see Figure #):
+
+“Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”
+
+*engl. 'And now, you have to put the cube on top of the green avocado.'*
+
 ```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen after the trigger sentence.
@@
 
-## 4. Stimuli
+The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
+There was a 3000 ms inter stimulus interval between trials (grey screen).
+In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
 
-### 4.1 Norming study
+Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
+If the color of the competitor and the target are of the same object type but differed in color (e.g.
+yellow banana --> blue banana), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
+If the objects differed but not their color (e.g.
+yellow banana --> yellow tomato), the noun was in focus (henceforth the Noun Focus (NF) condition).
+If both the color and the object differed (e.g.
+yellow banana --> blue tomato), the whole noun phrase was in focus (henceforth the Double Focus (DF) condition).
 
-Images of colored referents serve as visual stimuli. The selection of stimuli was based on a norming study, as described in the following.
+We are interested in the Noun Focus condition, only.
+AF and DF served as filler trials.
+There were 15 NF trials, 10 AF and 10 DF trials each.
+Each trial occurred two times per participants, yielding a total of 70 trials per participant.
 
-We selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
-Selection criteria were mainly informed by visual discriminability and phonemic composition, such that referential expressions were supposed to contain many voiced segments.
-We created different visual versions of each individual referent.
-Each version was created by manipulating a photograph of the object in the image editor [gimp](http://www.gimp.org).
-The photographs were collected from internet databases containing copyright-free high-resolution images (e.g.
+The experimental program (implemented as a browser-based application) is available [here](https://github.com/SBRitter/fruits-production).
+
+## Additional Information {#adds}
+Here we specify in detail, how stimuli were selected for the above described production study.
+
+### A.1 Selection of stimuli superset
+The selection of stimuli was informed by a norming study for which we selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
+Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain few voiceless segments.
+
+For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using [gimp](http://www.gimp.org).
+Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g.
 [Pixabay](https://pixabay.com)).
 During the manipulation process, the background of the pictures was replaced by a white background.
-In order to change the colour of the objects, a layer in the respective colour was created and overlaid on top of the original graphics using “Colour” as the layer mode.
-The hexadecimal colour codes for the colours used are listed here:
+In order to change the color of the objects, a layer in the respective color was created and overlaid on top of the original image using “Color” as the layer mode.
+The hexadecimal color codes for the colors that we used are listed below:
 
@@
 
-The same colour code was used across referents to achieve a particular colour, except for orange, which had to be adjusted for potatoes to be more distinct from the original colour brown.
-To achieve grey colouring, a white layer was used – the interaction between the original layer and a white overlay actually resulted in a grey colour on the object.
-To achieve a darker black on certain fruits, the colour spectrum of the original picture had to be manipulated using Gimp’s Colour Curves tool.
-This tool allowed us to darken or brighten certain colour channels of the picture.
-Parts of the fruits that did not have the body colour of the fruit (e.g.
-like stalks and leaves) were left in their original colour.
 All pictures with natural and manipulated colors are available [here](https://osf.io/rdtx5/).
 
-The colours for the twenty FOODs were chosen as to be perceived as having different degrees of typicality for each respective object, e.g.
-a banana is typically yellow, a less typical banana would be brown or green and an atypical exemplar could be blue.
-Every FOOD was presented in four of nine manipulated colours alongside its original colour.
-We assumed that the four NON-FOODs did not have a prototypical colour.
-We thus expected different colours to be comparably typical for these objects.
-The German nouns for all objects were either feminine singular or they occur in their plural form (e.g.
-grapes).
-
-We used the following colours: black, blue, brown, green, grey, orange, purple, red, yellow.
+The colors for the twenty FOODs were subjectively selected to reflect a range of compatibilities with the respective objects, e.g.
+a typical banana is yellow; a less typical banana could be brown (too ripe) or green (not yet ripe); and an atypical banana could be blue.
+Every FOOD was presented in four of nine manipulated colors alongside its original image.
+The four NON-FOODs were subjectively selected to represent color agnostic objects which can and do come in a variety of colors.
+All objects were chosen such that their respective German nouns were either feminine singular (e.g.
+"die Banana" 'the banana') or plural (e.g.
+"die Trauben" 'the grapes').
 
@@
 
-100 German native speakers participated in the norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac).
-We presented all objects in different colours to our subjects.
-FOODs came in 5 colours per object, NON-FOODs came in all nine colours.
-Subjects were instructed to rate how typical they think the colour for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design [here]](https://github.com/stelaseldano/colour-typicality-norming).
-
-### 4.2 Selection of experimental stimuli
-
-The norming ratings were subsequently used to choose appropriate stimuli for the production study, using the following procedure.
+### A.2 The norming study
+100 German native speakers participated in a norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac).
+We presented all objects in different colors to our participants.
+FOODs came in 5 colors per object, NON-FOODs came in all nine colors.
+Participants were instructed to rate how typical they think the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design [here]](https://github.com/stelaseldano/colour-typicality-norming).
 The results of the norming study can be retrieved [here](https://osf.io/znpg5/).
 
-First, we chose five colours from the norming data set: yellow, green, red, orange, and brown.
-Those were the most frequent colours in the superset and their norming ratings varied strongly as a function of the referent.
+### A.3 Selection of experimental stimuli
+The norming ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
 
-Second, we sorted the FOODs according to their typicality ratings and binned them into typical, atypical, and medium typical.
-Typical FOODs are defined by norming ratings above 90.
-Atypical FOODs are defined by norming ratings below 25.
-Mediocre typical FOODs are defined by norming ratings in between 25 and 90.
-For each colour and typicality, we selected one FOOD.
+First, we chose five colors from the norming data set: yellow, green, red, orange, and brown.
+Those were the most frequent colors in the superset and their norming results varied strongly as a function of the object.
+
+Second, we sorted the FOODs according to their typicality ratings and binned them into typical, medium, and atypical.
+Typical FOODs were defined by norming ratings above 90.
+Atypical FOODs were defined by norming ratings below 25.
+Medium typical FOODs were defined by norming ratings in between 25 and 90.
+For each color and typicality, we selected one FOOD object.
 Each cell was occupied by a different FOOD.
 
-For the critical focus condition (NF) we thus had 15 target FOODs (5 colours x 3 typicality categories), as given below:
+For the critical focus condition (NF) this selection procedure resulted in 15 target FOODs (5 colors x 3 typicality categories):
 
@@
 
-The set of 15 competitors from the NON-FOOD subset is chosen such that there are as many distinct competitors in each colour as there are targets. The set consists of:
+The set of 15 competitors from the NON-FOOD subset was selected to ensure that there are as many distinct competitors for each color as there are target objects.
+The set consisted of the following objects:
 
@@
 
-The pairing of targets and competitors was randomized for each subject, with the only constraint that the competitor was of the same colour as the target referent but a different object (e.g.
-if blue banana was the target, blue grapes was the competitor) (see randomization section below for more detail).
+The pairing of targets and competitors was randomized for each subject, with the only constraint that the competitor had the same color as the target object (e.g.
+if blue banana was the target, blue grapes is a possible competitor) (see randomization section below for more details).
 
-For the filler focus conditions (AF + NAF), we distributed FOODs and NON-FOODs, such that over the whole experiment (a) the frequency of target FOODs is counterbalanced (3 times each) and (b) the frequency of target colour is counterbalanced (14 times each).
+For the filler focus conditions (AF + DF), we distributed FOODs and NON-FOODs to fulfil the following constraints: (a) each target FOOD appeared 3 times and (b) each color appeared as a traget color 14 times.
 
-For all three conditions, a subset of visual distractors was chosen out of our superset from the norming study: Distractors are FOODS that are not used as targets or competitors (avocado, egg plant, pear, zucchini) and all NON-FOODs.
-They could have any of the five colours.
-Within each given trial, the distractors did neither share colour or object identity with the target or the competitor.
+For all three focus conditions, a subset of distractors was selected from the initial superset: Distractors were either FOODS that were neither used as targets nor as competitors (avocado, egg plant, pear, zucchini) or NON-FOODs.
+Within each given trial, the distractors did neither share color nor object identity with neither the target nor the competitor.
 
-Overall, the sets of target, competitors and distractors are chosen such that all five colours occur equally often throughout the experiment, i.e. 28 times.
+Overall, the sets of target, competitors and distractors are combined such that all five colors occurred equally often throughout the experiment (= 28 times).
 
-## 4.3 Randomization
-For each trial, targets, competitors, and distractors are chosen in a randomized fashion, fulfilling the following requirements:
+## A.4 Randomization
+For each trial, targets, competitors, and distractors are chosen in a randomized way, fulfilling the following requirements:
 
 - NF-Condition:
-Colour of Target = Colour of Competitor
+Color of Target = Color of Competitor
 Object of Target != Object of Competitor
@@
 - AF-Condition:
-Colour of Target != Colour of Competitor
+Color of Target != Color of Competitor
 Object of Target = Object of Competitor
 
-- ANF-Condition:
-Colour of Target != Colour of Competitor
+- DF-Condition:
+Color of Target != Color of Competitor
 Object of Target != Object of Competitor
@@
 - All conditions:
-Both distractors have to be different in colour and object from target and competitor.
+Both distractors have to differ in color and object identity from both target and competitor.
 
 The competitor and distractors are matched iteratively to a target.
-One competitor can only be used twice or a third time if all other competitors that are still left have been considered and prove inappropriate.
+One competitor could only be used twice or a third time if all other competitors that were left had been considered and prove inappropriate.
 
-The quadruples for the three conditions are formed separately.
-After the three lists have been compiled, they are merged.
-The sequence of quadruples is randomized such that the following requirements are met:
+The set of four objects (quadruple) was formed separately for each condition.
+After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following requirements were met:
 
-- The target colour of one quadruple must not equal the competitor colour of the next to avoid a contrastive focus on the next competitor noun
-- The target object of one quadruple must not equal the competitor object of the next to avoid a contrastive focus on the next competitor adjective
-- The list can have the same experimental condition in adjacent trials only in 12% of cases at the maximum
+- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
+- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
+- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
 
-One randomised list for each subject is produced and doubled, so that each unique trial occurs twice during a recording session.
-In case the doubling of the list leads to violation of the above criteria, the first trial of the repetition list is moved until the criteria are met.
+Following these criteria, one randomized list for each subject was produced.
+The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
+In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
 

### 2020-10-19 RR_manuscript/Draft_RR.tex
Light edits, fixed some typos, put each sentence on its own line, added bib file for refs

@@
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al.~2018, REF) leading to what is now referred to as the \emph{replication crisis}.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
 Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS).
@@
 Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling.
-Specifically we report the impact of analytic pipeline on research results obtained by \#\# teams that gained access to the same raw data set to answer the same research question.
+Specifically we report the impact of analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
 
@@
 
-Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
+Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
 This can be problematic because to err is human.
@@
 Analytic approaches and consequently the results varied widely between teams.
-69\% of the teams found support for the hypothesis, and 31\% did not.
+Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
 Out of the 29 analysis strategies, there were 21 unique combinations of covariates.
@@
 
-Neuroscience
-Cognitive Modelling
-Clinical
+Neuroscience\\
+Cognitive Modelling\\
+Clinical\\
 Predictive models
@@
 \emph{(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)}
+
 RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.
@@
 Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun.} In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier.} In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
+Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun}.
+In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier}.
+In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
 
-INFORMATION ABOUT THE DATA SET
+INFORMATION ABOUT THE DATA SET AND EXP DESIGN
 
@@
 
-We used R (Version 4.0.2; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.
+We used R (Version 4.0.3; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.
 
@@
 
+\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
+Camerer, C.
+F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} others.
+(2018).
+Evaluating the replicability of social science experiments in nature and science between 2010 and 2015.
+\emph{Nature Human Behaviour}, \emph{2}(9), 637--644.
+\url{https://doi.org/10.1038/s41562-018-0399-z}
+
+\leavevmode\hypertarget{ref-open2015estimating}{}%
+Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
 \leavevmode\hypertarget{ref-R-base}{}%

### 2020-10-30 RR_manuscript/Draft_RR.Rmd

@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : 
+  - "r-references.bib"
+  - "other_refs.bib"
 
@@
 # Introduction
+
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust. 
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al.
-2018, REF) leading to what is now referred to as the *replication crisis*.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
 Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS).
@@
 2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not only restricted to statistical inference of data tables. 
 Human behavior is complex and offers many ways to be translated into numbers. 
@@
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. 
-Specifically we report the impact of analytic pipeline on research results obtained by ## teams that gained access to the same raw data set to answer the same research question.
+Specifically we report the impact of analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
 
 ## Researcher degrees of freedom
-Data analysis comes with many decisions like how to operationalize  a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
+
+Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
 This can be problematic because to err is human.
@@
 ## Crowdsourcing alternative analyses
-In a collaborative effort, Silberzahn et al.
-(2018) let twenty-nine independent analysis teams address the same research question.
+
+In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research question. 
 Analytic approaches and consequently the results varied widely between teams. 
-69% of the teams found support for the hypothesis, and 31% did not.
+Sixty-nine percent of the teams found support for the hypothesis, and 31% did not. 
 Out of the 29 analysis strategies, there were 21 unique combinations of covariates. 
@@
 ## Operationalizing speech
+
 *(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)*
@@
 Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
-For example, the distinction between voiced and voiceless stops in English (i.e.
-/b/ and /p/ in "bear" vs.
-"pear") can be manifested by many different acoustic (Lisker, 1977).
+For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic (Lisker, 1977). 
 Even temporally dislocated acoustic parameters correlate with this lexical contrast. 
@@
 Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
-Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g.
-Niebuhr et al., 2011).
-They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.
-van Heuven & van Zanten 2005).
+Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). 
+They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
 All of these phonetic parameters are potential manifestations of underlying functional contrasts like speaker's intentions, levels of arousal or identity.
@@
 When testing hypotheses on speech production data, researchers need to make many decisions. 
-The larger the functional domain (e.g.
-are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations.
+The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. 
 These decisions are usually made prior to any statistical analysis, but can possible be revised in interaction with downstream analysis steps. 
@@
 ## The data set - The prosody of redundant modifiers
+
 Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g.
@@
 
-This account, however, has mainly focused on content selection (Gatt et al.
-2013), i.e.
-whether a certain referential expression is chosen or not.
+This account, however, has mainly focused on content selection (Gatt et al. 2013), i.e. whether a certain referential expression is chosen or not. 
 However, speech communication is so much richer. 
@@
 Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse. 
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on ‘banana’ to indicate the contrastive nature of the *noun.* In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on ‘yellow’ to indicate the contrastive nature of the *modifier.* In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.
+Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on ‘banana’ to indicate the contrastive nature of the *noun*.
+In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on ‘yellow’ to indicate the contrastive nature of the *modifier*.
+In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.
 segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
@@
 # Methods
+
 We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
@@
 ## Data analysis
+
 We used `r cite_r("r-references.bib")` for all our analyses.

### 2020-10-30 docs/ExperimentalDetails/Experimental_details.Rmd

@@
 ## 1. Research Questions
+
 This study investigates whether speakers modify the speech signal to signal atypical referents? 
@@
 ## 2. Participants
-30 native German speakers participated in this study.
+
+Thirty native German speakers participated in this study. 
 All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing. 
@@
 ## 3. Procedure
+
 In this production study, participants interacted with the experimenter. 
@@
 The non-target objects differed from the target with respect to their colour, their identity, or both. 
-Objects were referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g.
-yellow banana, blue banana).
+Objects were referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g. yellow banana, blue banana). 
 These adjective-noun combinations differed with respect to the typicality of their combination. 
@@
 The experimenter sat at the opposite side of the table in front of another computer screen. 
-Participants and experimenter could see neither each other nor each others' screens.
-The experiment consisted of two phases.
-A familiarization phase and a test phase.
+The participants and the experimenter could see neither each other nor each others' screens. 
+The experiment consisted of two phases: a familiarization phase and a test phase.
 
 In a familiarization phase, participants saw one object per trial. 
-In order to advance to the next trial, participants had to read out loud the corresponding noun phrase (e.g.
-blue banana).
+In order to advance to the next trial, participants had to read out loud the corresponding noun phrase (e.g. blue banana). 
 During this phase, participants had to name all atypical colour-object targets that we used in the test phase of the experiment alongside their typical counterparts. 
@@
 
-“Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”
-
-*engl. 'You have to put the cube on top of the green sunglasses.'*
+\noindent “Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”  
+\noindent *engl. 'You have to put the cube on top of the green sunglasses.'*
 
@@
 
-“Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”
-
-*engl. 'And now, you have to put the cube on top of the green avocado.'*
+\noindent “Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”  
+\noindent *engl. 'And now, you have to put the cube on top of the green avocado.'*
 
@@
 yellow banana --> blue banana), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
-If the objects differed but not their color (e.g.
-yellow banana --> yellow tomato), the noun was in focus (henceforth the Noun Focus (NF) condition).
-If both the color and the object differed (e.g.
-yellow banana --> blue tomato), the whole noun phrase was in focus (henceforth the Double Focus (DF) condition).
+If the objects differed but not their color (e.g. yellow banana --> yellow tomato), the noun was in focus (henceforth the Noun Focus (NF) condition). 
+If both the color and the object differed (e.g. yellow banana --> blue tomato), the whole noun phrase was in focus (henceforth the Double Focus (DF) condition).
 
@@
 
-The experimental program (implemented as a browser-based application) is available [here](https://github.com/SBRitter/fruits-production).
+The experimental program (implemented as a browser-based application) is available here: [https://github.com/SBRitter/fruits-production](https://github.com/SBRitter/fruits-production).
 
 ## Additional Information {#adds}
+
 Here we specify in detail, how stimuli were selected for the above described production study.
@@
 ### A.1 Selection of stimuli superset
+
 The selection of stimuli was informed by a norming study for which we selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs). 
@@
 For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using [gimp](http://www.gimp.org). 
-Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g.
-[Pixabay](https://pixabay.com)).
+Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g. [Pixabay](https://pixabay.com)). 
 During the manipulation process, the background of the pictures was replaced by a white background. 
@@
 
-Blue: #29429f
-Green: #3f8535
-Red: #9d1c1c
-Purple: #6d1b79
-Brown: #2a1d11
-Yellow: #e3c917
-Orange: #ff8400
-Orange (potatoes): #ff6600
-Black: #000000
-Grey: #FFFFFF
+\noindent Blue: #29429f  
+\noindent Green: #3f8535  
+\noindent Red: #9d1c1c  
+\noindent Purple: #6d1b79  
+\noindent Brown: #2a1d11  
+\noindent Yellow: #e3c917  
+\noindent Orange: #ff8400  
+\noindent Orange (potatoes): #ff6600  
+\noindent Black: #000000  
+\noindent Grey: #FFFFFF
 
-All pictures with natural and manipulated colors are available [here](https://osf.io/rdtx5/).
+All pictures with natural and manipulated colors are available here: [https://osf.io/rdtx5/](https://osf.io/rdtx5/).
 
@@
 The four NON-FOODs were subjectively selected to represent color agnostic objects which can and do come in a variety of colors. 
-All objects were chosen such that their respective German nouns were either feminine singular (e.g.
-"die Banana" 'the banana') or plural (e.g.
-"die Trauben" 'the grapes').
+All objects were chosen such that their respective German nouns were either feminine singular (e.g. "die Banana" 'the banana') or plural (e.g. "die Trauben" 'the grapes').
 
@@
 ### A.2 The norming study
-100 German native speakers participated in a norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac).
+
+One-hundred German native speakers participated in a norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac). 
 We presented all objects in different colors to our participants. 
 FOODs came in 5 colors per object, NON-FOODs came in all nine colors. 
-Participants were instructed to rate how typical they think the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design [here]](https://github.com/stelaseldano/colour-typicality-norming).
-The results of the norming study can be retrieved [here](https://osf.io/znpg5/).
+Participants were instructed to rate how typical they think the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design here: [https://github.com/stelaseldano/colour-typicality-norming](https://github.com/stelaseldano/colour-typicality-norming).
+The results of the norming study can be retrieved here: [https://osf.io/znpg5/](https://osf.io/znpg5/).
 
 ### A.3 Selection of experimental stimuli
+
 The norming ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
@@
 
-atypical:
-Yellow cherry (Gelbe Kirsche)
-Green carrot (Grüne Möhre)
-Red cucumber (Rote Gurke)
-Orange grapes (Oangene Trauben)
-Brown pepper (Braune Paprika)
+\noindent atypical:  
+\noindent Yellow cherry (Gelbe Kirsche)  
+\noindent Green carrot (Grüne Möhre)  
+\noindent Red cucumber (Rote Gurke)  
+\noindent Orange grapes (Oangene Trauben)  
+\noindent Brown pepper (Braune Paprika)
 
-medium:
-Yellow peas (Gelbe Erbsen)
-Green tomato (Grüne Tomate)
-Red apricot (Rote Aprikose)
-Orange potatoes (Orangene Kartoffeln)
-Brown banana (Braune Banane)
+\noindent medium:  
+\noindent Yellow peas (Gelbe Erbsen)  
+\noindent Green tomato (Grüne Tomate)  
+\noindent Red apricot (Rote Aprikose)  
+\noindent Orange potatoes (Orangene Kartoffeln)  
+\noindent Brown banana (Braune Banane)
 
-typical:
-Yellow lemon (Gelbe Zitrone)
-Green green beans (Grüne Bohnen)
-Red strawberry (Rote Erdbeere)
-Orange mandarine (Orangene Mandarine)
-Brown walnut (Braune Walnuss)
+\noindent typical:  
+\noindent Yellow lemon (Gelbe Zitrone)  
+\noindent Green green beans (Grüne Bohnen)  
+\noindent Red strawberry (Rote Erdbeere)  
+\noindent Orange mandarine (Orangene Mandarine)  
+\noindent Brown walnut (Braune Walnuss)
 
@@
 
-Yellow sunglasses (Gelbe Sonnenbrille)
-Yellow socks (Gelbe Socken)
-Yellow clothes peg (Gelbe Wäscheklammer)
-Green sunglasses (Grüne Sonnenbrille)
-Green socks (Grüne Socken)
-Green Paper clip (Grüne Büroklammer)
-Red socks (Rote Socken)
-Red paper clip (Rote Büroklammer)
-Red clothes peg (Rote Wäscheklammer)
-Orange socks (Orangene Socken)
-Orange paper clip (Orangene Büroklammer)
-Orange clothes peg (Orangene Wäscheklammer)
-Brown sunglasses (Braune Sonnenbrille)
-Brown paper clip (Braune Büroklammer)
-Brown clothes peg (Braune Wäscheklammer)
+\noindent Yellow sunglasses (Gelbe Sonnenbrille)  
+\noindent Yellow socks (Gelbe Socken)  
+\noindent Yellow clothes peg (Gelbe Wäscheklammer)  
+\noindent Green sunglasses (Grüne Sonnenbrille)  
+\noindent Green socks (Grüne Socken)  
+\noindent Green Paper clip (Grüne Büroklammer)  
+\noindent Red socks (Rote Socken)  
+\noindent Red paper clip (Rote Büroklammer)  
+\noindent Red clothes peg (Rote Wäscheklammer)  
+\noindent Orange socks (Orangene Socken)  
+\noindent Orange paper clip (Orangene Büroklammer)  
+\noindent Orange clothes peg (Orangene Wäscheklammer)  
+\noindent Brown sunglasses (Braune Sonnenbrille)  
+\noindent Brown paper clip (Braune Büroklammer)  
+\noindent Brown clothes peg (Braune Wäscheklammer)
 
@@
 ## A.4 Randomization
+
 For each trial, targets, competitors, and distractors are chosen in a randomized way, fulfilling the following requirements:
@@
 
-The python code for the randomization is available [here](https://github.com/SBRitter/fruits-randomization).
+The python code for the randomization is available here: [https://github.com/SBRitter/fruits-randomization](https://github.com/SBRitter/fruits-randomization).

### 2020-10-31 RR_manuscript/Draft_RR.Rmd
added method section

--- 2020-09-08 RR_manuscript/Draft_RR.Rmd
@@
 
-# Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+# Methods (mostly copy-paste from Evo-RR)
+This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript.
+We estimate that this process, from the time of an in-principle acceptance of this stage 1 Registered Report, will take XX months (Table X).
+The factor most likely to delay our timeline is the rate of completion of the original set of analyses by independent groups of scientists.
 
-## Participants
+## Step 1: Recruitment and Initial Survey of Analysts
+Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK).
+The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
+The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
+Researchers can choose to work independently or in a small team.
+For the sake of simplicity, we refer to single researcher or small teams as ‘analysis teams’.
 
-## Material
+Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
+Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
+If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
+All analysts will sign a consent (ethics) document (LINK).
 
-## Procedure
+## Step 2: Primary Data Analyses
+Analysis teams will register and answer a demographic and expertise survey (LINK).
+We will then provide them with the acoustic data set and request that they answer the following research question: RESEARCH QUESTION HERE.
+Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code [if applicable], and a detailed journal-ready statistical methods section.
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+## Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
+Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR).
+The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
+Balancing the order in which reviewers see the analyses controls for order effects, e.g.
+a reviewer might be less critical of the first methods section they read than the last.
+
+The process for a single reviewer will be as follows.
+First, the reviewer will receive a description of the methods of a single analysis.
+This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
+The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts:
+
+“Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+
+100. A perfect analysis with no conceivable improvements from the reviewer
+ 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
+ 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
+ 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
+ 0.
+A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
+
+*Please note that these values are meant to calibrate your ratings. We welcome ratings of any number between 0 and 100."
+
+After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: “Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?” The reviewer will then be provided with a series of text boxes and the following prompts:
+“Please explain your ratings of this analysis.
+Please evaluate the selection of acoustic features.
+Please evaluate the operationalization of acoustic features.
+Please evaluate the choice of statistical analysis type.
+Please evaluate the process of choosing variables for and structuring the statistical model.
+Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
+Please evaluate the suitability of the structure of the statistical model.
+Please evaluate choices to exclude or not exclude subsets of the data.
+Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).”
+
+After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
+This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
+After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+The invitation to revise the original ratings will be as follows: “If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.” The text box will be prefaced with this prompt: “Please explain your choice to revise (or not to revise) your ratings.”
+
+## Step 4: Evaluate Variation
+Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+We will describe the variation in model specification in several ways.
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of variables per model included as fixed effects, the nature and number of interaction terms, the nature and number of random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.
+
+We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
+We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
+
+ADD FORMULA
+
+SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.
+
+TR:TRUE?
+
+First, we will derive standardized effect sizes from each individual analysis.
+Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
+In multi-level models the variance components are partitioned into multiple sources of variation (e.g.
+varying intercept of speakers and items, varying by-predictor slopes, etc.).
+We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where the t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components like so:
+
+$$\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}$$
+Where $_i$ refers to the individual variance components.
+
+CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
+
+Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure.
+Hypothetically, two analyst teams can arrive at two different effect sizes, even if they have made the exact same measurement, processed the data in the exact same way, and used the same predictor combination, but, crucially, differ in their random effect structure (e.g.
+one team assumes random intercepts only, the other team uses random slopes).
+Thus, additionally, we will run all analyses with a prespecified maximal random effect structure for all predictors.
+
+TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS
+
+WRITE ABOUT HOW TO HANDLE GAMS
+
+...
+
+## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
+Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
 

### 2020-11-11 RR_manuscript/Draft_RR.Rmd
add intro/method edits

@@
 # Introduction
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration 2015, Camerer et al.
-2018, REF) leading to what is now referred to as the *replication crisis*.
-Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS).
+
+In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data. 
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
 The latter situation has been referred to as the *inference crisis* (Rotello, Heit & Dubé 2015, Starns et al.
 2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, & Simonsohn, 2011, Gelman & Loken 2013).
-Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data.
-Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation.
-These researcher degrees of freedom are a blessing and a curse at the same time.
+Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few. 
+Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data. 
+These researcher degrees of freedom are both a blessing and a curse at the same time.
 
-There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g.
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.
 Box 1976, Tukey 1977, de Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al.
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.
 2011).
-Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.
+<!-- taken for granted?
+-->
+Recent projects have shown that the variability between different data analysts is immense and can often lead independent researchers to draw vastly different conclusions about the same dataset (e.g.
 Silberzahn et al.
@@
 2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extend to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets. 
 Human behavior is complex and offers many ways to be translated into numbers. 
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data. 
-In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it. 
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
-Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.
+Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the raw data.
 
@@
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. 
-Specifically we report the impact of analytic pipeline on research results obtained by ## teams that gained access to the same raw data set to answer the same research question.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
 
 ## Researcher degrees of freedom
-Data analysis comes with many decisions like how to operationalize  a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
+
+Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
 This can be problematic because to err is human.
+<!-- I'd probably drop this.
+When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)...
+in other words it might not all be error...
+the issue is that we won't know the difference -->
 
 We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975).
-In connection with an academic incentive system that rewards certain discovery process more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+<!-- If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
+In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
 This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019). 
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to an vast plurality of analytic approaches.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
 
-Consequently - if methodologists are correct (e.g.
+Consequently, if methodologists are correct (e.g.
 Simmons et al.
-2011, Gelman & Loken 2013) - there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
-These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analysed differently.
+2011, Gelman & Loken 2013), there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
+These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
+<!-- RE analysed, if I'm not mistaken the rest of the manuscript is in American English, right?
+-->
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
 Critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
+<!-- aside from adding recent ref, consider adding counter point.
+Something to the effect of "despite recent efforts to improve transparency and reproducibility, i.e., OSF, IRIS.
+-->
 
@@
 2015, Charles et al.
-2019, Roettger 2019), there is still little known about the extend of analytical plurality in practice.
-Recent collaborative attempts have started to shed light on how different analyst tackle the same data set and revealed, not surprisingly, a large amount of variability.
+2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed, not surprisingly, a large amount of variability.
 
 ## Crowdsourcing alternative analyses
-In a collaborative effort, Silberzahn et al.
-(2018) let twenty-nine independent analysis teams address the same research question.
+
+In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research question. 
 Analytic approaches and consequently the results varied widely between teams. 
-69% of the teams found support for the hypothesis, and 31% did not.
-Out of the 29 analysis strategies, there were 21 unique combinations of covariates.
+Sixty-nine percent of the teams found support for the hypothesis, and 31% did not. 
+Out of the 29 analytical strategies, there were 21 unique combinations of covariates. 
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
@@
 While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling. 
-In these studies the data tables were fixed and data collection or extraction could not be changed.
+In these studies the datasets were fixed and data collection or extraction could not be changed. <!-- any particular reason to favor data table over dataset? -->
 However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question. 
 In social sciences, the raw observations correspond to recorded human behavior. 
-In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporal extended exhibits a complex structure.
+In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporally extended and exhibits a complex structure.
+<!-- I had trouble parsing "temporal extended exhibits" -->
 Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
@@
 
-When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization the relevant behavior, i.e.
+When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.
 how to measure the phenomenon of interest.
@@
 Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
-For example, the distinction between voiced and voiceless stops in English (i.e.
-/b/ and /p/ in "bear" vs.
-"pear") can be manifested by many different acoustic (Lisker, 1977).
+For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic measures (Lisker, 1977). 
 Even temporally dislocated acoustic parameters correlate with this lexical contrast. 
@@
 Studies investigating acoustic correlates of word stress (i.e.
-the difference between "insight" and "incite"), for example, have been using many different measurements including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
+the difference between "insight" and "incite"), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
 Gordon & Roettger, 2017).
@@
 Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
-Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g.
-Niebuhr et al., 2011).
-They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.
-van Heuven & van Zanten 2005).
-All of these phonetic parameters are potential manifestations of underlying functional contrasts like speaker's intentions, levels of arousal or identity.
+Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). 
+They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
+All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or identity.
 
 When testing hypotheses on speech production data, researchers need to make many decisions. 
-The larger the functional domain (e.g.
-are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations.
-These decisions are usually made prior to any statistical analysis, but can possible be revised in interaction with downstream analysis steps.
-To probe the variability in data analysis pipelines across researchers, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
+The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. 
+These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions. 
+To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
 
 ## The data set - The prosody of redundant modifiers
+
 Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g.
@@
 
-Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in the language science.
+Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science. 
 It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana. 
-The context within which an entity occurs (other non-fruits, other fruits, other bananas) plays a large part in determining the choice of referential expression.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975) and are therefore expected to only use for example a modifier if it is necessary for disambiguation (e.g.
-the adjective "yellow" when there is a yellow and a less ripe green banana).
+The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression. 
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975). 
+Thus one would expect the use of a modifier, for example, if it is necessary for disambiguation. 
+For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available.
 
-Despite this coherent idea of rational and efficient speakers, there is much evidence that speakers are often overinformative: Speaker use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often overinformative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
 2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
@@
 a blue banana) are more likely to be used in an overinformative scenario (e.g.
-there is just one banana).
+when there is just one banana).
 
-This account, however, has mainly focused on content selection (Gatt et al.
-2013), i.e.
-whether a certain referential expression is chosen or not.
+This account, however, has mainly focused on content selection (Gatt et al. 2013), i.e. whether a certain referential expression is chosen or not. 
 However, speech communication is so much richer. 
@@
 # Methods (mostly copy-paste from Evo-RR)
+
 This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript.
@@
 ## Step 1: Recruitment and Initial Survey of Analysts
+
 Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK).
@@
 ## Step 2: Primary Data Analyses
+
 Analysis teams will register and answer a demographic and expertise survey (LINK). 
@@
 ## Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)
+
+<!-- I believe we were still going to do this -->
+
 At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
@@
 For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
-Balancing the order in which reviewers see the analyses controls for order effects, e.g.
-a reviewer might be less critical of the first methods section they read than the last.
+Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
 
@@
 
-100. A perfect analysis with no conceivable improvements from the reviewer
- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
- 0.
+- 100. A perfect analysis with no conceivable improvements from the reviewer
+- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
+- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
+- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
+- 0.
 A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
 
-*Please note that these values are meant to calibrate your ratings. We welcome ratings of any number between 0 and 100."
+\*Please note that these values are meant to calibrate your ratings. 
+We welcome ratings of any number between 0 and 100."
 
-After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: “Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?” The reviewer will then be provided with a series of text boxes and the following prompts:
-“Please explain your ratings of this analysis.
-Please evaluate the selection of acoustic features.
-Please evaluate the operationalization of acoustic features.
-Please evaluate the choice of statistical analysis type.
-Please evaluate the process of choosing variables for and structuring the statistical model.
-Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
-Please evaluate the suitability of the structure of the statistical model.
-Please evaluate choices to exclude or not exclude subsets of the data.
-Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).”
+After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: “Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?”
+The reviewer will then be provided with a series of text boxes and the following prompts:
+
+\noindent “Please explain your ratings of this analysis.  
+\noindent Please evaluate the selection of acoustic features.  
+\noindent Please evaluate the operationalization of acoustic features.  
+\noindent Please evaluate the choice of statistical analysis type.  
+\noindent Please evaluate the process of choosing variables for and structuring the statistical model.  
+\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.  
+\noindent Please evaluate the suitability of the structure of the statistical model.  
+\noindent Please evaluate choices to exclude or not exclude subsets of the data.  
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).”
 
@@
 After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: “If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.” The text box will be prefaced with this prompt: “Please explain your choice to revise (or not to revise) your ratings.”
+The invitation to revise the original ratings will be as follows: “If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.”
+The text box will be prefaced with this prompt: “Please explain your choice to revise (or not to revise) your ratings.”
 
 ## Step 4: Evaluate Variation
+
 Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
@@
 
+JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models.
+
 TR:TRUE?
@@
 Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate. 
-In multi-level models the variance components are partitioned into multiple sources of variation (e.g.
-varying intercept of speakers and items, varying by-predictor slopes, etc.).
-We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where the t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components like so:
+In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.). 
+We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
 
@@
 CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
+RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/
+
+I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
+
+$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$
 
@@
 
-...
+## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
 
-## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
 Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
+
+## Data analysis
+
+We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2020-11-11 RR_manuscript/Draft_RR.tex
add intro/method edits

@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be recreated by using the same methods and (ii) arrive at conclusions about data that are robust.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low succes rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
-Beyond difficulties replicating scientific findings, more and more evidence suggests that the theoretical conclusions drawn from data are surprisingly variable even if researchers have access to reliable data (REFS).
+In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
 The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
-Data analysis involves many different steps including inspecting, organizing, transforming, and modeling the data.
-Along the way, different methodological and analytical choices need to be made, all of which might change its final interpretation.
-These researcher degrees of freedom are a blessing and a curse at the same time.
+Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
+Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
+These researcher degrees of freedom are both a blessing and a curse at the same time.
 
-There are a blessing, because they allow us to look at nature from many different angles allowing us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretation which find their way into the publication record where they are taken for granted (Simmons et al.~2011).
-Recent projects have shown that the variability between different data analysts is immense and leads researchers to draw vastly different conclusions about one and the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not only restricted to statistical inference of data tables.
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
+Recent projects have shown that the variability between different data analysts is immense and can often lead independent researchers to draw vastly different conclusions about the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets.
 Human behavior is complex and offers many ways to be translated into numbers.
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data.
-In fields working on human speech production for example, researchers need to make many decisions about what to measure and how to measure it.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
-Decisions about operationalizing the raw data might not only influence downstream decisions about statistical modelling but statistical results might lead researchers to go back and revise earlier decisions about the raw data.
+Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the raw data.
 
@@
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling.
-Specifically we report the impact of analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
 
@@
 We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
-In connection with an academic incentive system that rewards certain discovery process more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
 This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019).
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to an vast plurality of analytic approaches.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
 
-Consequently - if methodologists are correct (e.g.~Simmons et al.~2011, Gelman \& Loken 2013) - there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
-These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analysed differently.
+Consequently, if methodologists are correct (e.g.~Simmons et al.~2011, Gelman \& Loken 2013), there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
+These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
@@
 
-While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there is still little known about the extend of analytical plurality in practice.
-Recent collaborative attempts have started to shed light on how different analyst tackle the same data set and revealed, not surprisingly, a large amount of variability.
+While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed, not surprisingly, a large amount of variability.
 
@@
 Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
-Out of the 29 analysis strategies, there were 21 unique combinations of covariates.
+Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
@@
 While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling.
-In these studies the data tables were fixed and data collection or extraction could not be changed.
+In these studies the datasets were fixed and data collection or extraction could not be changed.
 However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question.
 In social sciences, the raw observations correspond to recorded human behavior.
-In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporal extended exhibits a complex structure.
+In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporally extended and exhibits a complex structure.
 Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
@@
 
-When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization the relevant behavior, i.e.~how to measure the phenomenon of interest.
+When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.~how to measure the phenomenon of interest.
 For example, how do we measure whether two sounds are acoustically identical (e.g.~\enquote{bear} vs.~\enquote{pear}), whether one word is more prominent than others (\enquote{He told YOU to be quite}), or whether two discourse functions are produced differently (\enquote{It's raining.} vs.~\enquote{It's raining?})?
@@
 The acoustic parameters for one category are usually asynchronous, i.e.~appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
-For example, the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \enquote{bear} vs.~\enquote{pear}) can be manifested by many different acoustic (Lisker, 1977).
+For example, the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \enquote{bear} vs.~\enquote{pear}) can be manifested by many different acoustic measures (Lisker, 1977).
 Even temporally dislocated acoustic parameters correlate with this lexical contrast.
@@
 The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (i.e.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+Studies investigating acoustic correlates of word stress (i.e.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
@@
 They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-All of these phonetic parameters are potential manifestations of underlying functional contrasts like speaker's intentions, levels of arousal or identity.
+All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or identity.
 
@@
 The larger the functional domain (e.g.~are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations.
-These decisions are usually made prior to any statistical analysis, but can possible be revised in interaction with downstream analysis steps.
-To probe the variability in data analysis pipelines across researchers, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
+These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions.
+To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
 
@@
 
-Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in the language science.
+Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
 It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana.
-The context within which an entity occurs (other non-fruits, other fruits, other bananas) plays a large part in determining the choice of referential expression.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975) and are therefore expected to only use for example a modifier if it is necessary for disambiguation (e.g.~the adjective \enquote{yellow} when there is a yellow and a less ripe green banana).
+The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression.
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975).
+Thus one would expect the use of a modifier, for example, if it is necessary for disambiguation.
+For instance, one might use the adjective \enquote{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available.
 
-Despite this coherent idea of rational and efficient speakers, there is much evidence that speakers are often overinformative: Speaker use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often overinformative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an overinformative scenario (e.g.~there is just one banana).
+For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an overinformative scenario (e.g.~when there is just one banana).
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\hypertarget{methods-mostly-copy-paste-from-evo-rr}{%
+\section{Methods (mostly copy-paste from Evo-RR)}\label{methods-mostly-copy-paste-from-evo-rr}}
 
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
+This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript.
+We estimate that this process, from the time of an in-principle acceptance of this stage 1 Registered Report, will take XX months (Table X).
+The factor most likely to delay our timeline is the rate of completion of the original set of analyses by independent groups of scientists.
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
+\hypertarget{step-1-recruitment-and-initial-survey-of-analysts}{%
+\subsection{Step 1: Recruitment and Initial Survey of Analysts}\label{step-1-recruitment-and-initial-survey-of-analysts}}
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK).
+The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
+The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
+Researchers can choose to work independently or in a small team.
+For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
+Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
+If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
+All analysts will sign a consent (ethics) document (LINK).
+
+\hypertarget{step-2-primary-data-analyses}{%
+\subsection{Step 2: Primary Data Analyses}\label{step-2-primary-data-analyses}}
+
+Analysis teams will register and answer a demographic and expertise survey (LINK).
+We will then provide them with the acoustic data set and request that they answer the following research question: RESEARCH QUESTION HERE.
+Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code {[}if applicable{]}, and a detailed journal-ready statistical methods section.
+
+\hypertarget{step-3-peer-reviews-of-analyses-do-we-still-do-this-cant-remember}{%
+\subsection{Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)}\label{step-3-peer-reviews-of-analyses-do-we-still-do-this-cant-remember}}
+
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
+Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR).
+The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
+Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.
+
+The process for a single reviewer will be as follows.
+First, the reviewer will receive a description of the methods of a single analysis.
+This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code, and the data set.
+The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts:
+
+``Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+
+\begin{itemize}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{99}
+  \tightlist
+  \item
+    A perfect analysis with no conceivable improvements from the reviewer
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{74}
+  \tightlist
+  \item
+    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{49}
+  \tightlist
+  \item
+    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{24}
+  \tightlist
+  \item
+    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
+  \end{enumerate}
+\item
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \setcounter{enumi}{-1}
+  \tightlist
+  \item
+    A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
+  \end{enumerate}
+\end{itemize}
+
+*Please note that these values are meant to calibrate your ratings.
+We welcome ratings of any number between 0 and 100."
+
+After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: \enquote{Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?}
+The reviewer will then be provided with a series of text boxes and the following prompts:
+
+\noindent \enquote{Please explain your ratings of this analysis.\\
+\noindent Please evaluate the selection of acoustic features.\\
+\noindent Please evaluate the operationalization of acoustic features.\\
+\noindent Please evaluate the choice of statistical analysis type.\\
+\noindent Please evaluate the process of choosing variables for and structuring the statistical model.\\
+\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.\\
+\noindent Please evaluate the suitability of the structure of the statistical model.\\
+\noindent Please evaluate choices to exclude or not exclude subsets of the data.\\
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).}
+
+After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
+This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
+After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+The invitation to revise the original ratings will be as follows: \enquote{If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.}
+The text box will be prefaced with this prompt: \enquote{Please explain your choice to revise (or not to revise) your ratings.}
+
+\hypertarget{step-4-evaluate-variation}{%
+\subsection{Step 4: Evaluate Variation}\label{step-4-evaluate-variation}}
+
+Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+We will describe the variation in model specification in several ways.
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of variables per model included as fixed effects, the nature and number of interaction terms, the nature and number of random effects {[}if applicable{]}, as well as the mean, standard deviation and range of effect sizes reported.
+
+We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
+We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
+
+ADD FORMULA
+
+SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.
+
+JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models.
+
+TR:TRUE?
+
+First, we will derive standardized effect sizes from each individual analysis.
+Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
+In multi-level models the variance components are partitioned into multiple sources of variation (e.g.~varying intercept of speakers and items, varying by-predictor slopes, etc.).
+We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index \(\delta_t\) (where t stands for \enquote{total} variance), which is calculated by the estimated difference between group means (\(\beta\)), divided by the square root of the sum of all variance components as formulated below:
+
+\[\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}\]
+Where \(_i\) refers to the individual variance components.
+
+CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN\ldots{}
+RELEVANT: \url{https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/}
+
+I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
+
+\[\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}\]
+
+Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure.
+Hypothetically, two analyst teams can arrive at two different effect sizes, even if they have made the exact same measurement, processed the data in the exact same way, and used the same predictor combination, but, crucially, differ in their random effect structure (e.g.~one team assumes random intercepts only, the other team uses random slopes).
+Thus, additionally, we will run all analyses with a prespecified maximal random effect structure for all predictors.
+
+TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS
+
+WRITE ABOUT HOW TO HANDLE GAMS
+
+\hypertarget{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}{%
+\subsection{Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript}\label{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}}
+
+Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
 
@@
 
-We used R (Version 4.0.3; R Core Team, 2020) and the R-package \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020) for all our analyses.
+We used R (Version 4.0.3; R Core Team, 2020) and the R-packages \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.1.0; Barth, 2020) for all our analyses.
 
@@
 Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-R-tinylabels}{}%
+Barth, M. (2020). \emph{Tinylabels: Lightweight variable labels}. Retrieved from \url{https://CRAN.R-project.org/package=tinylabels}
 

### 2020-11-11 RR_manuscript/refs_to_add.R
add file with list of refs to add to .bib file

@@ -1,0 +1,51 @@
+Rotello, Heit & Dubé 2015, 
+Starns et al. 2019
+Simmons, Nelson, & Simonsohn, 2011, 
+Gelman & Loken 2013
+Box 1976, 
+Tukey 1977, 
+de Groot 2014
+Simmons et al. 2011
+Silberzahn et al. 2018, 
+Starns et al. 2019, 
+Botvinik-Nezer et al., 2020
+Silberzahn et al. 2018, 
+Starns et al. 2019, 
+Botvinik-Nezer et al., 2020
+Tversky and Kahneman 1974
+Brugger 2001
+Nickerson 1998
+Fischhoff 1975
+Sterling 1959, 
+Koole & Lakens 2012
+Roettger 2019
+Simmons et al. 2011, 
+Gelman & Loken 2013
+Wicherts, Borsboom, Kats, & Molenaar, 2006
+Simmons et al. 2011, 
+Wagenmakers et al. 2012, 
+Nosek and Lakens 2014
+Wichert et al. 2015, 
+Charles et al. 2019, 
+Roettger 2019
+Silberzahn et al. (2018)
+Jongman et al., 2000; 
+Lisker, 1986; 
+Summerfield, 1984; 
+Winter, 2014
+Lisker, 1977
+Hawkins & Nguyen, 2004
+Gordon & Roettger, 2017
+Niebuhr et al., 2011
+van Heuven & van Zanten 2005
+Grice 1975
+Sedivy 2003, 
+Westerbeek et al. 2015, 
+Rubio-Fernandez 2016
+Arts et al. 2011, 
+Paraboni et al. 2007, 
+Degen et al. (2020)
+Gatt et al. 2013
+Ladd 2008
+Hedges, 2007
+

### 2020-11-11 scripts/r/00_simulate.R
very basic sim for now

@@ -1,0 +1,152 @@
+### Info # ---------------------------------------------------------------------
+#
+## Author:  Timo Roettger (timo.b.roettger @ gmail.com)
+#
+## Project: Many speech analyses
+#
+## Description: simulate hypothetical data for hypothesis testing analysis
+#
+## Version: 11/11/2020
+# ------------------------------------------------------------------------------
+
+## libraries--------------------------------------------------------------------
+library(tidyverse)
+library(truncnorm)
+library(lme4)
+
+## set parameters---------------------------------------------------------------
+
+# number of observations
+nobs = 1
+
+# probability of peer verdict
+prob_peer_verdict = c(0.2, 0.6, 0.15, 0.05)
+
+# lambda for fixed effect
+fixed_lambda = 3
+
+# lambda for random effect
+random_lambda = 3
+
+# probability of posthoc changes
+post_prob = 0.2
+
+# lambda for models run
+models_lambda = 3
+
+# number of team
+nteams = 16
+
+# number of reviewers
+nrevs  = 8
+
+# number of reviews per reviewer
+nreviews  = nteams / nrevs
+
+# random fluctuation between reviewers for rating
+rand_revs = 0.5
+
+## loop and create data frame for teams-----------------------------------------
+
+# create empty vectors
+team_c = c()
+reviewer_c = c()
+dv_c = c()
+peer_rating_c = c()
+peer_verdict_c = c()
+fixed_c = c()
+random_c = c()
+posthoc_c = c()
+nmodels_c = c()
+
+
+for (i in 1:nteams) { 
+  # print progress
+  print(paste0("random sample # ", i))
+  
+  team_c = c(team_c, 
+             paste0("team_", i))
+
+  ## generate parameters
+
+  # generate DV (divergence from meta-analytic estimate)
+  dv_c <- c(dv_c,
+            rnorm(n = nobs, mean = 0, sd = 1))
+  
+  # generate predictors
+  
+  # number of fixed effect parameters (poisson distributed)
+  fixed_c <- c(fixed_c,
+               rpois(n = nobs, lambda = fixed_lambda))
+
+  # number of random effect parameters (poisson distributed)
+  random_c <- c(random_c,
+                rpois(n = nobs, lambda = random_lambda))
+
+  # post hoc changes to analysis (yes vs. no)
+  posthoc_c <- c(posthoc_c,
+                 rbinom(n = nobs, size = 1, prob = post_prob))
+
+  # number of models run before converging on final model
+  nmodels_c <- c(nmodels_c,
[…]

### 2020-11-12 RR_manuscript/Draft_RR.Rmd
edited the document

@@
 The latter situation has been referred to as the *inference crisis* (Rotello, Heit & Dubé 2015, Starns et al.
-2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, & Simonsohn, 2011, Gelman & Loken 2013).
+2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, & Simonsohn, 2011, Gelman & Loken 2013).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few. 
@@
 -->
-Recent projects have shown that the variability between different data analysts is immense and can often lead independent researchers to draw vastly different conclusions about the same dataset (e.g.
-Silberzahn et al.
-2018, Starns et al.
-2019, Botvinik-Nezer et al., 2020).
+Recent projects have shown that the variability between different data analysts is vast.
+This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020). 
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets. 
@@
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
-Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the raw data.
+Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the processing of the raw data.
 
-In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data. 
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data. 
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. 
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same set of acoustic recordings to answer the same research question.
 
@@
 We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975).
-<!-- If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
+<!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
+<!-- TR: Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased. --> 
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019). 
+This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019). 
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
@@
 These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
-<!-- RE analysed, if I'm not mistaken the rest of the manuscript is in American English, right?
--->
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
-Critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
-<!-- aside from adding recent ref, consider adding counter point.
-Something to the effect of "despite recent efforts to improve transparency and reproducibility, i.e., OSF, IRIS.
--->
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
 
@@
 
-In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research question. 
+In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis 
 Analytic approaches and consequently the results varied widely between teams. 
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
-Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias. 
+The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias. 
 Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
 
+SUM UP:
 Neuroscience  
@@
 
-While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling. 
-In these studies the datasets were fixed and data collection or extraction could not be changed. <!-- any particular reason to favor data table over dataset? -->
+While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling. 
+In these studies the datasets were fixed and data collection or extraction could not be changed.
+<!-- JC: any particular reason to favor data table over dataset?
+--> <!-- TR: I think my reasoning was dataset can be data table or raw data.
+Data table is the numerical derivation of the raw data.
+Maybe not a useful distinction-->
+
 However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question. 
@@
 Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
-To understand how analytical flexibility manifests itself in a scenario where complex signals need to be operationalized, the present paper looks at an experimentally elicited speech data set
+To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
 
@@
 
-*(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)*
+<!-- TR:(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)-->
 
@@
 In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings.
-Speech offers a considerable number of perspectives and decisions along the data analysis pipeline.
+Take for example the sentence: "The president refused to concede".
+This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds.
+Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline.
 
@@
 how to measure the phenomenon of interest.
-For example, how do we measure whether two sounds are acoustically identical (e.g.
+For example, how do we measure whether two sounds are acoustically identical or not (e.g.
 "bear" vs.
-"pear"), whether one word is more prominent than others ("He told YOU to be quite"), or whether two discourse functions are produced differently ("It's raining." vs.
-"It's raining?")?
+"pear"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs.
+"The president refuses to concede?")?
 In other words, how do we quantitatively capture relevant features of speech?
@@
 The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. 
-Studies investigating acoustic correlates of word stress (i.e.
+Studies investigating acoustic correlates of word stress (e.g.
 the difference between "insight" and "incite"), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
@@
 They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
-All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or identity.
+All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity.
 
@@
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g.
+Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
+(e.g.
 “a blue banana” vs.
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression. 
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975). 
-Thus one would expect the use of a modifier, for example, if it is necessary for disambiguation. 
-For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available.
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource efficient in that they avoid redundancy (Grice 1975). 
+Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation. 
+For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
 
@@
 
-This account, however, has mainly focused on content selection (Gatt et al. 2013), i.e. whether a certain referential expression is chosen or not. 
-However, speech communication is so much richer. 
-Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.
+This account, however, has mainly focused on content selection (Gatt et al.
+2013), i.e.
+whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+Even looking at morphosyntactically identical expressions, speakers can modulate these expressions via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.
 Ladd 2008).
@@
 
-This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript.
-We estimate that this process, from the time of an in-principle acceptance of this stage 1 Registered Report, will take XX months (Table X). 
-The factor most likely to delay our timeline is the rate of completion of the original set of analyses by independent groups of scientists.
+We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted).
+
+This project involves a series of steps (X-X) that begins with recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation among the different analyses, and producing the final manuscript.
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X). 
+The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.
 
@@
 Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+<!-- TR: Big to-do point.
+We need to only justify a minimum sample size-->
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels. 
@@
 Analysis teams will register and answer a demographic and expertise survey (LINK). 
-We will then provide them with the acoustic data set and request that they answer the following research question: RESEARCH QUESTION HERE. 
+We will then provide them with the acoustic data set and request that they answer the following research question:
+
+Do speakers acoustically modify utterances to signal atypical word combinations?
+
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
@@
 
-## Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)
+## Step 3: Peer Reviews of Analyses 
+<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats?
+if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
 
-<!-- I believe we were still going to do this -->
-
-At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts. 
@@
 Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
-
 The process for a single reviewer will be as follows. 
@@
 This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set. 
-The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts:
+The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->
 
@@
 \noindent Please evaluate the selection of acoustic features.  
-\noindent Please evaluate the operationalization of acoustic features.  
+\noindent Please evaluate the measurement of acoustic features.  
 \noindent Please evaluate the choice of statistical analysis type.  
@@
 Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
-We will describe the variation in model specification in several ways. 
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of variables per model included as fixed effects, the nature and number of interaction terms, the nature and number of random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.
+We will describe the variation in model specification in several ways:
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.
 
@@
 
+We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
+Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses. 
+We will also archive copies of our survey instruments from analysts and peer reviewers.
+
+Our rules for excluding data from our study are as follows.
+We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
+We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+
+ADD GAM EXCLUSION
+
 ## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript

### 2020-11-12 RR_manuscript/Draft_RR.Rmd
commented out comments

@@
 
-SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.
+<!-- TR: SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW. -->
 
-JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models.
-
-TR:TRUE?
+<!-- JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models. -->
 
@@
 
-CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
-RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/
+<!-- TR: CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
+RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/ -->
 
-I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
+<!-- JC:I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
 
-$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$
+$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$-->
 
@@
 
-TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS
+<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS-->
 

### 2020-11-12 scripts/r/00_simulate.R
added es and se

@@ -69,9 +69,14 @@ for (i in 1:nteams) {
 
   ## generate parameters
 
-  # generate DV (divergence from meta-analytic estimate)
+  # generate effect size 
   dv_c <- c(dv_c,
+            rnorm(n = nobs, mean = 1, sd = 1))
+  
+  # generate standard error
+  se_c <- c(se_c,
             rnorm(n = nobs, mean = 0, sd = 1))
+  
   
   # generate predictors
   
@@ -96,7 +101,7 @@ for (i in 1:nteams) {
 
 ## make data frame
 df <- data.frame(team = team_c,
-                 dv = dv_c,
+                 es = dv_c,
                  fixed = fixed_c,
                  random = random_c,
                  posthoc = posthoc_c,

### 2020-11-12 scripts/r/00_simulate.R
some betapart shenanigans

@@ -13,11 +13,20 @@
 library(tidyverse)
 library(truncnorm)
 library(lme4)
+library(rstudioapi)
+library(betapart)
+
+# get path
+current_path = rstudioapi::getActiveDocumentContext()$path 
+setwd(dirname(current_path))
 
 ## set parameters---------------------------------------------------------------
 
 # number of observations
 nobs = 1
+
+# overall effect
+meta_effect = 1
 
 # probability of peer verdict
 prob_peer_verdict = c(0.2, 0.6, 0.15, 0.05)
@@ -52,6 +61,7 @@ rand_revs = 0.5
 team_c = c()
 reviewer_c = c()
 dv_c = c()
+se_c = c()
 peer_rating_c = c()
 peer_verdict_c = c()
 fixed_c = c()
@@ -71,7 +81,7 @@ for (i in 1:nteams) {
 
   # generate effect size 
   dv_c <- c(dv_c,
-            rnorm(n = nobs, mean = 1, sd = 1))
+            rnorm(n = nobs, mean = meta_effect, sd = 1))
   
   # generate standard error
   se_c <- c(se_c,
@@ -102,6 +112,7 @@ for (i in 1:nteams) {
 ## make data frame
 df <- data.frame(team = team_c,
                  es = dv_c,
+                 se = se_c,
                  fixed = fixed_c,
                  random = random_c,
                  posthoc = posthoc_c,
@@ -147,11 +158,65 @@ for (j in 1:nrow(df2)) {
 } #endfor_j
 
 ## store------------------------------------------------------------------------
-write_csv(df2, "/scripts/simulated_df")
+write_csv(df2, "simulated_df.csv")
 
 
-## model------------------------------------------------------------------------
-xmdl <- lmer(dv ~ peer_rating + fixed + random + posthoc + nmodels +
+## betapart shenanigans---------------------------------------------------------
+
+# add some random columns
+df2$variable1 = ""
+df2$variable2 = ""
+df2$variable3 = ""
+df2$variable4 = ""
+df2$variable5 = ""
+
+# loop through df an fill columns
+for (k in 1:nrow(df2)) { 
+  # print progress
+  print(paste0("random sample # ", k))
+  
+  # add variable with probability proportional to df2$fixed
+  df2$variable1[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
[…]

### 2020-11-15 scripts/r/00_sim_data.R
add data and models directories, create new scripts for simulations (data, ma, similarity)

@@ -10,11 +10,9 @@
 # ------------------------------------------------------------------------------
 
 ## libraries--------------------------------------------------------------------
-library(tidyverse)
-library(truncnorm)
-library(lme4)
-library(rstudioapi)
-library(betapart)
+source(here::here("scripts", "r", "00_libs.R"))
+
+
 
 # get path
 current_path = rstudioapi::getActiveDocumentContext()$path 
@@ -83,9 +81,10 @@ for (i in 1:nteams) {
   dv_c <- c(dv_c,
             rnorm(n = nobs, mean = meta_effect, sd = 1))
   
-  # generate standard error
+  # generate standard error (NOTE: in our model SE is equivalent to SD which 
+  # by def. must be non-negative)
   se_c <- c(se_c,
-            rnorm(n = nobs, mean = 0, sd = 1))
+            rnorm(n = nobs, mean = 1, sd = 0.35))
   
   
   # generate predictors
@@ -158,65 +157,5 @@ for (j in 1:nrow(df2)) {
 } #endfor_j
 
 ## store------------------------------------------------------------------------
-write_csv(df2, "simulated_df.csv")
-
-
-## betapart shenanigans---------------------------------------------------------
-
-# add some random columns
-df2$variable1 = ""
-df2$variable2 = ""
-df2$variable3 = ""
-df2$variable4 = ""
-df2$variable5 = ""
-
-# loop through df an fill columns
-for (k in 1:nrow(df2)) { 
-  # print progress
-  print(paste0("random sample # ", k))
-  
-  # add variable with probability proportional to df2$fixed
-  df2$variable1[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
-  df2$variable2[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
-  df2$variable3[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
-  df2$variable4[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
-  df2$variable5[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
-  
-} #endfor_k
-
-# bring into betapart shape
-df3 <- df2 %>% 
-  select(variable1,
-         variable2,
-         variable3,
-         variable4,
-         variable5)
-
-# get betapart objects
-df.core <- betapart.core(df3)
-
-# get pairwise distance
[…]

### 2020-11-15 scripts/r/00_sim_similarity.R

@@ -1,0 +1,117 @@
+
+## betapart shenanigans---------------------------------------------------------
+
+# add some random columns
+df2$variable1 = ""
+df2$variable2 = ""
+df2$variable3 = ""
+df2$variable4 = ""
+df2$variable5 = ""
+
+# loop through df an fill columns
+for (k in 1:nrow(df2)) { 
+  # print progress
+  print(paste0("random sample # ", k))
+  
+  # add variable with probability proportional to df2$fixed
+  df2$variable1[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
+  df2$variable2[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
+  df2$variable3[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
+  df2$variable4[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
+  df2$variable5[k] <- rbinom(n = nobs, size = 1, prob = df2$fixed / 10)
+  
+} #endfor_k
+
+# bring into betapart shape
+df3 <- df2 %>% 
+  select(variable1,
+         variable2,
+         variable3,
+         variable4,
+         variable5)
+
+# get betapart objects
+df.core <- betapart.core(df3)
+
+# get pairwise distance
+df.pair <- beta.pair(df.core, index.family = "sorensen")
+
+# which one is it? beta.sim / beta.sne / beta.sor?
+# if beta.sor then
+
+df.pair.sor <- broom::tidy(df.pair$beta.sor) %>% 
+  rename(team = item1) %>% 
+  mutate(team = paste0("team_",team)) %>% 
+  group_by(team) %>% 
+  summarise(distance_mean = mean(distance))
+
+# NaN are based on teams without any filled columns basically, but even if I
+# force fill one column, I get NaNs. Dunno
+  
+# add to df2
+df4 <- full_join(df2, df.pair.sor)
+
+## meta analysis----------------------------------------------------------------
+
+
+## hypothesis testing analysis--------------------------------------------------
+xmdl <- lmer(dv ~ peer_rating + distance_mean + posthoc + nmodels +
+               (1 | reviewer), data = df2)
+
+
+
+
+
+data(ceram.s)
+data(ceram.n)
+
[…]

### 2020-11-15 scripts/r/00_libs.R
add data and models directories, create new scripts for simulations (data, ma, similarity)

@@ -7,5 +7,11 @@ library("tidyr")
 library("glue")
 library("ggplot2")
 library("ganttrify")
+library("truncnorm")
+library("lme4")
+library("brms")
+library("rstudioapi")
+library("betapart")
+library("tidybayes")
 
 # -----------------------------------------------------------------------------

### 2020-11-15 scripts/r/00_sim_ma.R

@@ -1,0 +1,125 @@
+# Source libs -----------------------------------------------------------------
+
+source(here::here("scripts", "r", "00_libs.R"))
+
+
+
+# Load data -------------------------------------------------------------------
+
+sim_df <- read_csv(here("data", "sim", "simulated_df.csv"))
+
+
+
+
+
+
+
+# Bayesian meta analysis ------------------------------------------------------
+
+# Set priors
+priors <- c(prior(normal(0, 1), class = Intercept),
+            prior(cauchy(0, 1), class = sd))
+
+# Fit model
+ma_sim_m0 <- brm(
+  formula = es | se(se) ~ 1 + (1 | team), 
+  family = gaussian, 
+  data = sim_df,
+  prior = priors,
+  iter = 4000, warmup = 2000, cores = 4, chains = 4, 
+  file = here::here("models", "sim", "ma_sim_m0")
+)
+
+# Add pooling method
+m1_brm <- brm(
+  formula = es | se(se) ~ 1 + (1 | study) + (1 | stops), 
+  family = gaussian, 
+  data = madata,
+  prior = priors,
+  iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
+  control = list(adapt_delta = 0.9999, max_treedepth = 15), 
+  file = here::here("models", "meta_analysis_mod_1")
+)
+
+# Fit between variable model (add stress)
+m2_brm <- brm(
+  formula = es | se(se) ~ 0 + Intercept + is_stressed + (1 | study) + (1 | stops), 
+  family = gaussian, 
+  data = madata,
+  prior = c(prior(normal(0, 1), class = b),
+            prior(cauchy(0, 1), class = sd)),
+  iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
+  control = list(adapt_delta = 0.9999), 
+  file = here::here("models", "meta_analysis_mod_2")
+)
+
+# Add analytic strategy
+m3_brm <- brm(
+  formula = es | se(se) ~ 0 + Intercept + is_stressed + analytic_str_dev + 
+    (1 | study) + (1 | stops), 
+  family = gaussian, 
+  data = madata,
+  prior = c(prior(normal(0, 1), class = b),
+            prior(cauchy(0, 1), class = sd)),
+  iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
+  control = list(adapt_delta = 0.9999), 
[…]

### 2020-11-24 scripts/r/00_sim_similarity.R
edits on plots

@@ -92,8 +92,8 @@ fe_re <- ggplot(sim_df_new,
                    segment.color = 'grey50') +
   labs(title = "Sørensen distance for fixed & random effect parameters",
        #subtitle = "",
-       x = "\n Distance values for random effects",
-       y = "Distance values for fixed effects\n ") +
+       x = "\nDistance values for random effects",
+       y = "Distance values for fixed effects\n") +
   theme_minimal()
 
 es_fe <- left_join(sim_df_new, 
@@ -112,10 +112,14 @@ es_fe <- left_join(sim_df_new,
                      fill = "white",
                      color = "black",
                      segment.color = 'grey50') + 
+    scale_fill_viridis_c(option = "D", end = 1) +
+    scale_color_viridis_c(option = "D", end = 1) +
     labs(title = "Effect size and Sørensen distance for fixed effects",
        #subtitle = "",
-       y = "\nES (posterior median)",
-       x = "Distance values for fixed effects\n ") +
+       y = "ES (posterior median)\n",
+       x = "\n Distance values for fixed effects",
+       fill = "# fixed effects",
+       color = "# fixed effects") +
     theme_minimal()
 
 es_re <- left_join(sim_df_new, 
@@ -134,10 +138,14 @@ es_re <- left_join(sim_df_new,
                    fill = "white",
                    color = "black",
                    segment.color = 'grey50') + 
+    scale_fill_viridis_c(option = "D", end = 1) +
+    scale_color_viridis_c(option = "D", end = 1) +
     labs(title = "Effect size and Sørensen distance for random effects",
        #subtitle = "",
-       y = "\nES (posterior median)",
-       x = "Distance values for random effects\n ") +
+       y = "ES (posterior median)\n",
+       x = "\nDistance values for random effects",
+       fill = "# fixed effects",
+       color = "# fixed effects") +
     theme_minimal()
 
 # TR: the patchwork of all three doesn't work for me, no idea why

### 2020-11-24 scripts/r/00_sim_ma.R
tidied, ran new models, changed sims slightly

@@ -8,7 +8,7 @@
 
 # Source libs and load simulated data -----------------------------------------
 source(here::here("scripts", "r", "00_libs.R"))
-sim_df <- read_csv(here("data", "sim", "simulated_df.csv"))
+sim_df <- read_csv(here("data", "sim", "simulated_df_distances.csv"))
 
 # -----------------------------------------------------------------------------
 
@@ -28,6 +28,7 @@ ma_sim_m0 <- brm(
   data = sim_df,
   prior = priors,
   iter = 4000, warmup = 2000, cores = 4, chains = 4, 
+  control = list(adapt_delta = 0.99, max_treedepth = 15),
   file = here("models", "sim", "ma_sim_m0")
 )
 
@@ -38,7 +39,7 @@ ma_sim_m1 <- brm(
   data = sim_df,
   prior = priors,
   iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.9999), 
+  control = list(adapt_delta = 0.9999, max_treedepth = 15), 
   file = here("models", "sim", "ma_sim_m1")
 )
 
@@ -51,7 +52,7 @@ ma_sim_m2 <- brm(
   prior = c(prior(normal(0, 1), class = b),
             prior(cauchy(0, 1), class = sd)),
   iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.9999), 
+  control = list(adapt_delta = 0.9999, max_treedepth = 15), 
   file = here("models", "sim", "ma_sim_m2")
 )
 
@@ -64,15 +65,45 @@ ma_sim_m3 <- brm(
   prior = c(prior(normal(0, 1), class = b),
             prior(cauchy(0, 1), class = sd)),
   iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.9999), 
+  control = list(adapt_delta = 0.9999, max_treedepth = 15), 
   file = here("models", "sim", "ma_sim_m3")
 )
+
+# Add fixed_similarity
+ma_sim_m4 <- brm(
+  formula = es | se(se) ~ 0 + Intercept + posthoc + nmodels + fixed_similarity +
+    (1 | team) + (1 | reviewer), 
+  family = gaussian, 
+  data = sim_df,
+  prior = c(prior(normal(0, 1), class = b),
+            prior(cauchy(0, 1), class = sd)),
[…]

### 2020-11-24 scripts/r/00_sim_similarity.R

@@ -17,7 +17,8 @@ cat3_col = "#1b9e77"
 
 # bring into betapart shape
 fixed_df <- sim_df %>% 
-  column_to_rownames(var = "team") %>% 
+  mutate(team_reviewer = paste0(team, "_", reviewer)) %>% 
+  column_to_rownames(var = "team_reviewer") %>% 
   select(fixed_1,
          fixed_2,
          fixed_3,
@@ -25,7 +26,8 @@ fixed_df <- sim_df %>%
          fixed_5)
 
 random_df <- sim_df %>% 
-  column_to_rownames(var = "team") %>% 
+  mutate(team_reviewer = paste0(team, "_", reviewer)) %>% 
+  column_to_rownames(var = "team_reviewer") %>% 
   select(random_1,
          random_2,
          random_3,

### 2020-11-24 RR_manuscript/Draft_RR.Rmd
added info about sorensen distance

@@
 
-Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK).
+Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
 The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
@@
 Analysis teams will register and answer a demographic and expertise survey (LINK).
-We will then provide them with the acoustic data set and request that they answer the following research question:
+The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
+We will then provide teams with the acoustic data set and request that they answer the following research question:
 
@@
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code [if applicable], and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
@@
 
-After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: “Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?”
-The reviewer will then be provided with a series of text boxes and the following prompts:
+After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:
 
@@
 ## Step 4: Evaluate Variation
-
 Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
@@
 First, we will derive standardized effect sizes from each individual analysis. 
-Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate. 
+Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate. 
 In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.). 
@@
 
-## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
+DESCRIBE META-NALYSIS
+
+We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:
+
+The peer ratings (1-100) of each analysis, a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).
+
+The uniqueness of model parameters will be assessed using the Sorensen’s Similarity Index (an index typically used to compare species composition across sites).
+Here we treat model parameters as species and individual analyses as sites.
+To generate an individual Sorensen’s value for each analysis requires calculating the pairwise Sorensen’s value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen’s values for each analysis.
+We will calculate the Sorensen’s index values using the betapart package (Baselga et al.
+2018) in R:
+
+$$\beta_{Sorensen} = \frac{b+c}{2_a + b + c}$$
+
+where $$a$$ is the number of variables common to both models, $$b$$ is the number of variables that occur in the first model but not in the second and $$c$$ is the number of variables that occur in the second model but not in the first.
+
+The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.
+
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).
+
+## Step 6: Collaborative Write-Up of Manuscript
 
 Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
-
-## Data analysis
-
-We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2020-11-24 RR_manuscript/Draft_RR.tex
rr updates

@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis, often referred to as researcher degrees of freedom (Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
-Recent projects have shown that the variability between different data analysts is immense and can often lead independent researchers to draw vastly different conclusions about the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+Recent projects have shown that the variability between different data analysts is vast.
+This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets.
@@
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the raw data.
+Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the processing of the raw data.
 
-In this article, we investigate the diversity in analytic choices when many analyst teams analyze the same speech production data.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data.
 We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling.
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same raw data set to answer the same research question.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same set of acoustic recordings to answer the same research question.
 
@@
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to flexible operationalizations (Roettger 2019).
+This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
 
@@
 
-In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research question.
+In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis
 Analytic approaches and consequently the results varied widely between teams.
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-Their results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
+The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
 Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
 
+SUM UP:
 Neuroscience\\
@@
 
-While these papers show a large degree of analytical flexibility with impactful consequences, these studies dealt with flexibility in inferential or computational modelling.
+While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
 In these studies the datasets were fixed and data collection or extraction could not be changed.
+
 However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question.
@@
 
-\emph{(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)}
-
 RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.
@@
 In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings.
-Speech offers a considerable number of perspectives and decisions along the data analysis pipeline.
+Take for example the sentence: \enquote{The president refused to concede}.
+This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds.
+Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline.
 
@@
 When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.~how to measure the phenomenon of interest.
-For example, how do we measure whether two sounds are acoustically identical (e.g.~\enquote{bear} vs.~\enquote{pear}), whether one word is more prominent than others (\enquote{He told YOU to be quite}), or whether two discourse functions are produced differently (\enquote{It's raining.} vs.~\enquote{It's raining?})?
+For example, how do we measure whether two sounds are acoustically identical or not (e.g.~\enquote{bear} vs.~\enquote{pear}), whether one word is more prominent than others (\enquote{The president REFUSES to concede}), or whether two discourse functions are produced differently (\enquote{The president refuses to concede.} vs.~\enquote{The president refuses to concede?})?
 In other words, how do we quantitatively capture relevant features of speech?
@@
 The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (i.e.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+Studies investigating acoustic correlates of word stress (e.g.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
@@
 They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or identity.
+All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity.
 
@@
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify a referring expression as a function of the typicality of the modifier of the noun (e.g.~\enquote{a blue banana} vs.~\enquote{a yellow banana})?
+Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
+(e.g.~\enquote{a blue banana} vs.~\enquote{a yellow banana})?
 
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object (Grice 1975).
-Thus one would expect the use of a modifier, for example, if it is necessary for disambiguation.
-For instance, one might use the adjective \enquote{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available.
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource efficient in that they avoid redundancy (Grice 1975).
+Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
+For instance, one might use the adjective \enquote{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
 
@@
 
-This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not.
-However, speech communication is so much richer.
-Even looking at morphosyntactically identical expressions, speakers can modulate this expression via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
+This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+Even looking at morphosyntactically identical expressions, speakers can modulate these expressions via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
@@
 
-This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript.
-We estimate that this process, from the time of an in-principle acceptance of this stage 1 Registered Report, will take XX months (Table X).
-The factor most likely to delay our timeline is the rate of completion of the original set of analyses by independent groups of scientists.
+We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted).
+
+This project involves a series of steps (X-X) that begins with recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation among the different analyses, and producing the final manuscript.
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
+The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.
 
@@
 
+We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity (\(\tau^2\)) with a 95\% confidence interval that does not encompass zero.
+This minimum sample size is invariant regardless of \(\tau^2\).
+This is because the same t-statistic value will be obtained by the same sample size regardless of variance (\(\tau^2\)).
+We see this by first examining the formula for the standard error, SE for variance, (\(\tau^2\)) or SE(\(\tau^2\)) assuming normality in an underlying distribution of effect sizes (Knight 2000):
+
+\[SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}\]
+
+and then rearranging the above formula to show how the t-statistic is independent of \(\tau^2\), as seen below.
+
+\[t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}\]
+
+We then find a minimum n = 12 according to this formula.
+
 \hypertarget{step-2-primary-data-analyses}{%
@@
 Analysis teams will register and answer a demographic and expertise survey (LINK).
-We will then provide them with the acoustic data set and request that they answer the following research question: RESEARCH QUESTION HERE.
+We will then provide them with the acoustic data set and request that they answer the following research question:
+
+Do speakers acoustically modify utterances to signal atypical word combinations?
+
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
@@
 
-\hypertarget{step-3-peer-reviews-of-analyses-do-we-still-do-this-cant-remember}{%
-\subsection{Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)}\label{step-3-peer-reviews-of-analyses-do-we-still-do-this-cant-remember}}
+\hypertarget{step-3-peer-reviews-of-analyses}{%
+\subsection{Step 3: Peer Reviews of Analyses}\label{step-3-peer-reviews-of-analyses}}
 
-At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
@@
 Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.
-
 The process for a single reviewer will be as follows.
@@
 \noindent Please evaluate the selection of acoustic features.\\
-\noindent Please evaluate the operationalization of acoustic features.\\
+\noindent Please evaluate the measurement of acoustic features.\\
 \noindent Please evaluate the choice of statistical analysis type.\\
@@
 Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
-We will describe the variation in model specification in several ways.
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of variables per model included as fixed effects, the nature and number of interaction terms, the nature and number of random effects {[}if applicable{]}, as well as the mean, standard deviation and range of effect sizes reported.
+We will describe the variation in model specification in several ways:
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, as well as the mean, standard deviation and range of effect sizes reported.
 
@@
 ADD FORMULA
-
-SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.
-
-JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models.
-
-TR:TRUE?
 
@@
 
-CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN\ldots{}
-RELEVANT: \url{https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/}
-
-I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
-
-\[\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}\]
-
 Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure.
@@
 
-TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS
+Upon calculating a standardized effect size and standard error for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+
+\[
+\begin{aligned}
+\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
+\theta_i     & \sim \text{Normal} (\mu, \tau) \\
+\mu          & \sim \text{Normal} (0, 1) \\
+\tau         & \sim \text{HalfCauchy} (0, 1)
+\end{aligned}
+\]
+
+Effect size (\(\delta_{t}\)) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects).
+The likelihood of the outcome variable is assumed to be normally distributed.
+Analysis teams and reviewers will be included as group-level effects (i.e., random effects).
+For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+A cauchy prior set at 0 with scale 1 will be used for \(\tau\).
+We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
+The analysis will be conducted in R (R core team, 2020) and fit using \texttt{stan} (Stan, 2019) via the R package \texttt{brms} (Bürkner, 2019).
+
+The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other.
+Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis.
+We will use Sorensen's Similarity Index (SSI) to derive a \enquote{uniqueness} score.
+The SSI is an index typically used in ecology research to compare species composition across sites.
+For our purposes, we will treat variables as species and individual analyses as sites.
+In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al.~2018) in R.
+We achieve this using the following formula:
+
+\[\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}\]
+
+where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first.
+We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R (R\_Core\_Team 2019):
 
 WRITE ABOUT HOW TO HANDLE GAMS
+
+We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
+Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
+We will also archive copies of our survey instruments from analysts and peer reviewers.
+
+Our rules for excluding data from our study are as follows.
+We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
+We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+
+ADD GAM EXCLUSION
 
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+SAMPLE SIZE
 
-We used R (Version 4.0.3; R Core Team, 2020) and the R-packages \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), and \emph{tinylabels} (Version 0.1.0; Barth, 2020) for all our analyses.
+META ANALYSIS
+
+SOreenson analysis
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
-Barth, M. (2020). \emph{Tinylabels: Lightweight variable labels}. Retrieved from \url{https://CRAN.R-project.org/package=tinylabels}
-
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
@@
 
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
 \endgroup

### 2020-11-24 RR_manuscript/Draft_RR.Rmd
rr updates

--- 2020-11-12 RR_manuscript/Draft_RR.Rmd
@@
 <!-- TR: Big to-do point.
-We need to only justify a minimum sample size-->
+We need to only justify a minimum sample size JC: added description (word for word) from ecology RR.
+Need to figure out what it means still and then put into our own words.
+-->
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels. 
@@
 All analysts will sign a consent (ethics) document (LINK).
+
+<!-- sample size info from Ecology RR -->
+We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity ($\tau^2$) with a 95% confidence interval that does not encompass zero.
+This minimum sample size is invariant regardless of $\tau^2$. 
+This is because the same t-statistic value will be obtained by the same sample size regardless of variance ($\tau^2$). 
+We see this by first examining the formula for the standard error, SE for variance, ($\tau^2$) or SE($\tau^2$) assuming normality in an underlying distribution of effect sizes (Knight 2000):
+
+$$SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}$$
+
+and then rearranging the above formula to show how the t-statistic is independent of $\tau^2$, as seen below.
+
+$$t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}$$
+
+We then find a minimum n = 12 according to this formula. 
+<!-- We need to decide if we use this (I still don't understand it) -->
 
@@
 ## Step 3: Peer Reviews of Analyses
+
 <!-- TR: So I am still unclear on how this will look like, do they only evaluate stats?
@@
 
-<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS-->
+<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS ... ARE WE STILL DOING THIS? -->
+
+<!-- description of meta-analysis starts here -->
+
+Upon calculating a standardized effect size and standard error for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+
+$$
+\begin{aligned}
+\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
+\theta_i     & \sim \text{Normal} (\mu, \tau) \\
+\mu          & \sim \text{Normal} (0, 1) \\
+\tau         & \sim \text{HalfCauchy} (0, 1)
+\end{aligned}
+$$
+
+Effect size ($\delta_{t}$) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects). 
+The likelihood of the outcome variable is assumed to be normally distributed.
+Analysis teams and reviewers will be included as group-level effects (i.e., random effects). 
+For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1. 
+A cauchy prior set at 0 with scale 1 will be used for $\tau$. 
+We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
+The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019).
+
+<!-- Sorensen analysis starts here -->
+
+The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other. 
+Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis. 
+We will use Sorensen's Similarity Index (SSI) to derive a 'uniqueness' score. 
+The SSI is an index typically used in ecology research to compare species composition across sites. 
+For our purposes, we will treat variables as species and individual analyses as sites.
+In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R. 
+We achieve this using the following formula:
+
+$$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$
+
+where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first.
+We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R  (R_Core_Team 2019):
+<!-- are we going to do this last part? -->
 
@@
 
-## Data analysis
+SAMPLE SIZE
 
-We used `r cite_r("r-references.bib")` for all our analyses.
+META ANALYSIS
+
+SOreenson analysis
 

### 2020-11-24 RR_manuscript/Draft_RR.Rmd
cleanup merge mess

@@
 
-## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
+DESCRIBE META-NALYSIS
+
+We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:
+
+The peer ratings (1-100) of each analysis, a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).
+
+The uniqueness of model parameters will be assessed using the Sorensen’s Similarity Index (an index typically used to compare species composition across sites).
+Here we treat model parameters as species and individual analyses as sites.
+To generate an individual Sorensen’s value for each analysis requires calculating the pairwise Sorensen’s value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen’s values for each analysis.
+We will calculate the Sorensen’s index values using the betapart package (Baselga et al.
+2018) in R:
+
+$$\beta_{Sorensen} = \frac{b+c}{2_a + b + c}$$
+
+where $a$ is the number of variables common to both models, $b$ is the number of variables that occur in the first model but not in the second and $c$ is the number of variables that occur in the second model but not in the first.
+
+The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.
+
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).
+
+## Step 6: Collaborative Write-Up of Manuscript
 
 Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
-
-SAMPLE SIZE
-
-META ANALYSIS
-
-SOreenson analysis
 

### 2020-11-24 RR_manuscript/Draft_RR.tex
cleanup merge mess

@@
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code {[}if applicable{]}, and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
@@
 
-After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: \enquote{Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?}
-The reviewer will then be provided with a series of text boxes and the following prompts:
+After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:
 
@@
 First, we will derive standardized effect sizes from each individual analysis.
-Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
+Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
 In multi-level models the variance components are partitioned into multiple sources of variation (e.g.~varying intercept of speakers and items, varying by-predictor slopes, etc.).
@@
 
-\hypertarget{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}{%
-\subsection{Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript}\label{step-6-facilitated-discussion-and-collaborative-write-up-of-manuscript}}
+DESCRIBE META-NALYSIS
+
+We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:
+
+The peer ratings (1-100) of each analysis, a measurement of the \enquote{uniqueness} of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).
+
+The uniqueness of model parameters will be assessed using the Sorensen's Similarity Index (an index typically used to compare species composition across sites).
+Here we treat model parameters as species and individual analyses as sites.
+To generate an individual Sorensen's value for each analysis requires calculating the pairwise Sorensen's value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen's values for each analysis.
+We will calculate the Sorensen's index values using the betapart package (Baselga et al.~2018) in R:
+
+\[\beta_{Sorensen} = \frac{b+c}{2_a + b + c}\]
+
+where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.
+
+The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.
+
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).
+
+\hypertarget{step-6-collaborative-write-up-of-manuscript}{%
+\subsection{Step 6: Collaborative Write-Up of Manuscript}\label{step-6-collaborative-write-up-of-manuscript}}
 
 Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
-
-SAMPLE SIZE
-
-META ANALYSIS
-
-SOreenson analysis
 

### 2020-11-24 scripts/r/00_sim_ma.R
update models to ma5

@@ -113,7 +113,7 @@ ma_sim_m5 <- brm(
 # Plots -----------------------------------------------------------------------
 
 # Pooled effect and SE
-posterior_samples(ma_sim_m1, c("^b", "^sd")) %>% 
+posterior_samples(ma_sim_m5, c("^b", "^sd")) %>% 
   rename(smd = b_Intercept, tau = sd_team__Intercept) %>% 
   ggplot(., aes(x = smd, y = tau)) + 
   stat_density_2d(aes(fill = after_stat(level)), geom = "polygon") +
@@ -170,11 +170,11 @@ posterior_samples(ma_sim_m5) %>%
 
 # Forrest plot of teams
 # Get draws for each study
-team_draws <- spread_draws(ma_sim_m3, r_team[Team,], b_Intercept) %>% 
+team_draws <- spread_draws(ma_sim_m5, r_team[Team,], b_Intercept) %>% 
   mutate(b_Intercept = r_team + b_Intercept)
 
 # Get draws for pooled effect
-pooled_effect_draws <- spread_draws(ma_sim_m3, b_Intercept) %>% 
+pooled_effect_draws <- spread_draws(ma_sim_m5, b_Intercept) %>% 
   mutate(Team = "Pooled Effect")
 
 # Combine it and clean up
@@ -214,7 +214,7 @@ forest_data %>%
                 ymin = -Inf, ymax = Inf), 
             fill = "#4A978A",
             alpha = 0.3) +
-  geom_vline(xintercept = fixef(ma_sim_m3)[1, 1], 
+  geom_vline(xintercept = fixef(ma_sim_m5)[1, 1], 
              color = "#40758B", size = 0.7, 
              lty = "dashed") +
   geom_pointinterval(data = forest_data_summary %>% 

### 2020-11-24 scripts/r/00_sim_similarity.R
update models to ma5

@@ -5,7 +5,7 @@
 
 source(here::here("scripts", "r", "00_libs.R"))
 sim_df <- read_csv(here("data", "sim", "simulated_df.csv"))
-ma_sim_m3 <- readRDS(here("models", "sim", "ma_sim_m3.rds"))
+ma_sim_m5 <- readRDS(here("models", "sim", "ma_sim_m5.rds"))
 
 # global color scheme / non-optimized
 cat1_col = "#d95f02"
@@ -99,7 +99,7 @@ fe_re <- ggplot(sim_df_new,
   theme_minimal()
 
 es_fe <- left_join(sim_df_new, 
-  spread_draws(ma_sim_m3, r_team[Team,], b_Intercept) %>% 
+  spread_draws(ma_sim_m5, r_team[Team,], b_Intercept) %>% 
     mutate(team = Team, b_Intercept = r_team + b_Intercept) %>% 
     group_by(team) %>% 
     summarize(posterior_median = median(b_Intercept), .groups = "drop"), 
@@ -125,7 +125,7 @@ es_fe <- left_join(sim_df_new,
     theme_minimal()
 
 es_re <- left_join(sim_df_new, 
-  spread_draws(ma_sim_m3, r_team[Team,], b_Intercept) %>% 
+  spread_draws(ma_sim_m5, r_team[Team,], b_Intercept) %>% 
     mutate(team = Team, b_Intercept = r_team + b_Intercept) %>% 
     group_by(team) %>% 
     summarize(posterior_median = median(b_Intercept), .groups = "drop"), 

### 2020-11-24 scripts/r/00_sim_ma.R
center predictors and add slopes for peer_rating

@@ -8,7 +8,12 @@
 
 # Source libs and load simulated data -----------------------------------------
 source(here::here("scripts", "r", "00_libs.R"))
-sim_df <- read_csv(here("data", "sim", "simulated_df_distances.csv"))
+sim_df <- read_csv(here("data", "sim", "simulated_df_distances.csv")) %>% 
+  mutate(posthoc_sum = if_else(posthoc == 0, -1, 1), 
+         nmodels_std = (nmodels - mean(nmodels)) / sd(nmodels), 
+         fixed_sim_std = (fixed_similarity - mean(fixed_similarity)) / sd(fixed_similarity), 
+         random_sim_std = (random_similarity - mean(random_similarity)) / sd(random_similarity), 
+         peer_rating_std = (peer_rating - mean(peer_rating)) / sd(peer_rating))
 
 # -----------------------------------------------------------------------------
 
@@ -28,7 +33,7 @@ ma_sim_m0 <- brm(
   data = sim_df,
   prior = priors,
   iter = 4000, warmup = 2000, cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.99, max_treedepth = 15),
+  #control = list(adapt_delta = 0.99, max_treedepth = 15),
   file = here("models", "sim", "ma_sim_m0")
 )
 
@@ -45,7 +50,7 @@ ma_sim_m1 <- brm(
 
 # Fit between variable model (add posthoc)
 ma_sim_m2 <- brm(
-  formula = es | se(se) ~ 0 + Intercept + posthoc + 
+  formula = es | se(se) ~ 0 + Intercept + posthoc_sum + 
     (1 | team) + (1 | reviewer), 
   family = gaussian, 
   data = sim_df,
@@ -58,7 +63,7 @@ ma_sim_m2 <- brm(
 
 # Add nmodels
 ma_sim_m3 <- brm(
-  formula = es | se(se) ~ 0 + Intercept + posthoc + nmodels + 
+  formula = es | se(se) ~ 0 + Intercept + posthoc_sum + nmodels_std + 
     (1 | team) + (1 | reviewer), 
   family = gaussian, 
   data = sim_df,
@@ -71,7 +76,8 @@ ma_sim_m3 <- brm(
 
 # Add fixed_similarity
 ma_sim_m4 <- brm(
-  formula = es | se(se) ~ 0 + Intercept + posthoc + nmodels + fixed_similarity +
[…]

### 2020-11-30 RR_manuscript/Draft_RR.Rmd
fixed sim

@@
 Human behavior is complex and offers many ways to be translated into numbers. 
-This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data. 
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it. 
+This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data. 
+In fields working on human speech production, for example, researchers need to make numerous decisions about what how to measure it. 
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
-Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the processing of the raw data.
+Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the measuring process.
 
@@
 
-Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019). 
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
 
-Consequently, if methodologists are correct (e.g.
-Simmons et al.
-2011, Gelman & Loken 2013), there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
-These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013). 
+These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
@@
 2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
-Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed, not surprisingly, a large amount of variability.
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
 
 ## Crowdsourcing alternative analyses
-
 In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis 
@@
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling. 
-In these studies the datasets were fixed and data collection or extraction could not be changed.
+In these studies the datasets were fixed and data collection or measurement could not be changed.
 <!-- JC: any particular reason to favor data table over dataset?
@@
 
-However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question. 
-In social sciences, the raw observations correspond to recorded human behavior. 
-In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporally extended and exhibits a complex structure.
-<!-- I had trouble parsing "temporal extended exhibits" -->
-Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question. 
+In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual and/or acoustic signal.
+Decisions about how to measure a theoretically construct of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. 
 To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
@@
 Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline.
-
-IMAGE SHOWING A WAVE FORM WITH DIFFERENT DOMAINS (temporal) AND STRUCTURAL CUES (e.g. f0, dur, int) MAPPING ONTO FUNCTIONAL CONTRASTS
-
 When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.
@@
 For example, how do we measure whether two sounds are acoustically identical or not (e.g.
-"bear" vs.
-"pear"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs.
+"concede" vs.
+"conceal"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs.
 "The president refuses to concede?")?
-In other words, how do we quantitatively capture relevant features of speech?
-
+In other words, how do we quantitatively capture relevant features of speech that correspond to the target behavior?
 This is not trivial. 
@@
 For example, in the English words "led" versus "let", voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins & Nguyen, 2004).
-
 The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. 
@@
 Gordon & Roettger, 2017).
-
 Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
@@
 All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity. 
-
 When testing hypotheses on speech production data, researchers need to make many decisions. 
@@
 “a yellow banana”)?
-
+We are interested in the acoustic profile of referring expression. 
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science. 
@@
 For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
-
 Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often overinformative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
@@
 when there is just one banana).
-
 This account, however, has mainly focused on content selection (Gatt et al.

### 2020-11-30 scripts/r/00_sim_data.R

@@ -82,9 +82,7 @@ for (i in 1:nteams) {
 
   # generate effect size 
   dv_c <- c(dv_c,
-            rnorm(n = nobs, mean = meta_effect, sd = rnorm(n = 1,
-                                                           mean = 1,
-                                                           sd = 1)))
+            rnorm(n = nobs, mean = meta_effect, sd = 1))
   
   # generate standard error (NOTE: in our model SE is equivalent to SD which 
   # by def. must be non-negative)

### 2020-12-01 scripts/r/00_sim_ma.R
update models with non NA df

@@ -33,7 +33,7 @@ ma_sim_m0 <- brm(
   data = sim_df,
   prior = priors,
   iter = 4000, warmup = 2000, cores = 4, chains = 4, 
-  #control = list(adapt_delta = 0.99, max_treedepth = 15),
+  control = list(adapt_delta = 0.99, max_treedepth = 15),
   file = here("models", "sim", "ma_sim_m0")
 )
 
@@ -77,7 +77,7 @@ ma_sim_m3 <- brm(
 # Add fixed_similarity
 ma_sim_m4 <- brm(
   formula = es | se(se) ~ 0 + Intercept + posthoc_sum + nmodels_std + 
-    fixed_similarity_std +
+    fixed_sim_std +
     (1 | team) + (1 | reviewer), 
   family = gaussian, 
   data = sim_df,
@@ -91,7 +91,7 @@ ma_sim_m4 <- brm(
 # Add random_similarity
 ma_sim_m5 <- brm(
   formula = es | se(se) ~ 0 + Intercept + posthoc_sum + nmodels_std + 
-    fixed_similarity_std + random_similarity_std +
+    fixed_sim_std + random_sim_std +
     (1 | team) + (1 | reviewer), 
   family = gaussian, 
   data = sim_df,
@@ -105,7 +105,7 @@ ma_sim_m5 <- brm(
 # Add peer rating and slopes
 ma_sim_m6 <- brm(
   formula = es | se(se) ~ 0 + Intercept + posthoc_sum + nmodels_std + 
-    fixed_similarity_std +  random_similarity_std + peer_rating_std +
+    fixed_sim_std +  random_sim_std + peer_rating_std +
     (1 + peer_rating_std | team) + (1 + peer_rating_std | reviewer), 
   family = gaussian, 
   data = sim_df,
@@ -124,6 +124,7 @@ ma_sim_m6 <- brm(
 # pp_check(ma_sim_m3, nsamples = 200)
 # pp_check(ma_sim_m4, nsamples = 200)
 # pp_check(ma_sim_m5, nsamples = 200)
+# pp_check(ma_sim_m6, nsamples = 200)
 
 # -----------------------------------------------------------------------------
 
@@ -133,11 +134,11 @@ ma_sim_m6 <- brm(
 # Plots -----------------------------------------------------------------------
 
 # Pooled effect and SE
-posterior_samples(ma_sim_m5, c("^b", "^sd")) %>% 
[…]

### 2020-12-02 RR_manuscript/Draft_RR.Rmd
merged meta analysis write up

@@
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data. 
-In fields working on human speech production, for example, researchers need to make numerous decisions about what how to measure it. 
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it. 
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition. 
-Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the measuring process.
+Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data. 
-We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling. 
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same set of acoustic recordings to answer the same research question.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
 
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes. 
@@
 the issue is that we won't know the difference -->
+<!-- TR: But isn't the human bias the major issue in statistical misinterpretation? (It also leads naturally to the next paragraph.) -->
 
@@
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019). 
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019). 
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
-
 Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013). 
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record. 
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
 
@@
 Data table is the numerical derivation of the raw data.
-Maybe not a useful distinction-->
+Maybe not a useful distinction?-->
 
 However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question. 
-In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual and/or acoustic signal.
-Decisions about how to measure a theoretically construct of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse. 
+In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
+Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+<!-- TR:maybe give a concrete example, how such an interactionn would look like for speech data?-->
+
 To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
@@
 These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions. 
-To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
+To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional construct that might be manifested across the whole utterance.
 
@@
 ## Research questions
+The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
+We are further interested in which factors  affect researchers' final results.
 
 # Methods (mostly copy-paste from Evo-RR)
-
 We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted).
 
-This project involves a series of steps (X-X) that begins with recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation among the different analyses, and producing the final manuscript.
+This project involves a series of steps (X-X): 
+First, we recruite independent groups of researchers to analyze the data.
+Second, We give researchers access to the speech corpus and let them analyze the data as they see fit. 
+Third, we generate peer review ratings of the analyses (based on methods, not results).
+Forth, we evaluate the variation among the different analyses.
+And finally, we collaboratively produce the final manuscript. 
 We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X). 
@@
 ## Step 1: Recruitment and Initial Survey of Analysts
-
 Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
@@
 if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
-
 At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts. 
-Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR). 
+Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors. 
 The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer. 
@@
 
-- 100. A perfect analysis with no conceivable improvements from the reviewer
+- 100. A perfect analysis with no conceivable improvements from the reviewer.
 - 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
@@
 ## Step 4: Evaluate Variation
-Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
+Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
 We will describe the variation in model specification in several ways:
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments, as well as the mean, standard deviation and range of effect sizes reported.
 
@@
 Where $_i$ refers to the individual variance components.
+
+<!-- TR: Do we still need standardized effect sizes? to compare shit or are we just going to compare their estimates? -->
 
@@
 
-Effect size ($\delta_{t}$) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects). 
+Effect size ($\delta_{t}$) will be the outcome variable.
 The likelihood of the outcome variable is assumed to be normally distributed.
@@
 
-<!-- Sorensen analysis starts here -->
-
-The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other. 
-Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis. 
-We will use Sorensen's Similarity Index (SSI) to derive a 'uniqueness' score. 
+We will assess the extent to which the meta-analytic estimate is modulated by the following predictors:
+The peer ratings of each analysis (numeric, 1-100), a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below, numeric), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teamsm, numeric).
+The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
 The SSI is an index typically used in ecology research to compare species composition across sites.
@@
 
+<!--TR: question: do we just want to look if the meta analytical estimate is modulated by our preidctors or do we want to look at the individuals teams deviations from the meta estimate are modulated by our predictors?-->
+
+<!--old :The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other.-->
+
 $$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$
 
-where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first.
-We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R  (R_Core_Team 2019):
-<!-- are we going to do this last part? -->
+where $a$ is the number of variables common to both models, $b$ is the number of variables that occur in the first model but not in the second and $c$ is the number of variables that occur in the second model but not in the first.
 
 WRITE ABOUT HOW TO HANDLE GAMS
+<!--TR: maybe don't mention? -->
 
@@
 We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
-
-ADD GAM EXCLUSION
-
-DESCRIBE META-NALYSIS
-
-We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:
-
-The peer ratings (1-100) of each analysis, a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).
-
-The uniqueness of model parameters will be assessed using the Sorensen’s Similarity Index (an index typically used to compare species composition across sites).
-Here we treat model parameters as species and individual analyses as sites.
-To generate an individual Sorensen’s value for each analysis requires calculating the pairwise Sorensen’s value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen’s values for each analysis.
-We will calculate the Sorensen’s index values using the betapart package (Baselga et al.
-2018) in R:
-
-$$\beta_{Sorensen} = \frac{b+c}{2_a + b + c}$$
-
-where $a$ is the number of variables common to both models, $b$ is the number of variables that occur in the first model but not in the second and $c$ is the number of variables that occur in the second model but not in the first.
-
-The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.
 

### 2020-12-07 scripts/r/00_sim_raw.R
added three simple scenarios

@@ -1,0 +1,81 @@
+### Info # ---------------------------------------------------------------------
+#
+## Author:  Timo Roettger (timo.b.roettger @ gmail.com)
+#
+## Project: Many speech analyses
+#
+## Description: simulate hypothetical analyses for hypothesis testing analysis
+#
+## Version: 11/11/2020
+# ------------------------------------------------------------------------------
+
+## libraries--------------------------------------------------------------------
+source(here::here("scripts", "r", "00_libs.R"))
+
+# load in original data
+fruits <- read_csv(here("data", "dataset", "processed_fruits.csv"))
+
+## come up with three options to answer research question:
+# Option#1 centered predictor typicality, 
+# random intercepts for speakers-only
+
+fruits$mean_typicality_s <- scale(fruits$mean_typicality, scale = F)
+
+xmdl1 <- lmer(duration ~  mean_typicality_s +
+                  (1| speaker),
+                data = fruits)
+# TR: This is rather straightforward
+
+# Option#2 uncentered predictor typicality interacting with color, 
+# random intercepts for speakers and objects
+xmdl2 <- lmer(duration ~  mean_typicality * colour +
+                (1| speaker) +
+                (1 | object),
+              data = fruits)
+
+# TR: This is complicated immediately: colour is not contrast-coded, 
+# So the estimate for mean_typicality will be the estimate for the colour reference
+# level. Additionally, is the interaction term relevant for the research question? 
+# or just the main effect?
+# Solution: Different coding and standardization of typicality. Decision as to
+# what coefficient answers the question.
+
+# Option#3 uncentered predictor typicality with additional predictor colour,
+# colour is dummy coded, 
+# random intercepts for speakers and objects + by-speaker random slopes for mean_typicality
+
+xmdl3 <- lmer(duration ~  mean_typicality + colour +
+                (mean_typicality || speaker) +
+                (1 | object),
+              data = fruits)
+
+# TR: Same situation as above
+
+# extract stuff
+m1 <- tidy(xmdl1) %>% 
+  select(effect, term, estimate, std.error) %>% 
+  filter(effect == "fixed",
+         term == "mean_typicality_s") %>% 
+  mutate(model = "model1")
+
+m2 <- tidy(xmdl2) %>% 
+  select(effect, term, estimate, std.error) %>% 
+  filter(effect == "fixed",
+         term %in% c("mean_typicality",
[…]

### 2020-12-09 scripts/r/00_libs.R
Add missing package.

@@ -17,5 +17,6 @@ library("rstudioapi")
 library("betapart")
 library("tidybayes")
 library("patchwork")
+library("broom.mixed")
 
 # -----------------------------------------------------------------------------

### 2020-12-10 RR_manuscript/Draft_RR.Rmd
edited RR according to our conversation

@@
 # Methods (mostly copy-paste from Evo-RR)
-We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted).
+We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted) in terms of data collection. The analysis will substantially diverge from their approach (see §#.#)
 
 This project involves a series of steps (X-X): 
-First, we recruite independent groups of researchers to analyze the data.
+First, we recruit independent groups of researchers to analyze the data.
 Second, We give researchers access to the speech corpus and let them analyze the data as they see fit. 
@@
 Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. 
-We will describe the variation in model specification in several ways:
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments, as well as the mean, standard deviation and range of effect sizes reported.
+We will describe the variation in model specifications in several ways:
 
-We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques. 
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.
+f0 or duration), the operationalization and the temporal domain of measurement (e.g.
+mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments (e.g.
+dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
 We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
@@
 
-<!-- TR: SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW. -->
+Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).
 
-<!-- JC: I believe we can use their ES in our model to get a prob dist. of the pooled estimate. I don't think we need to transform their models. -->
-
+We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques. 
 First, we will derive standardized effect sizes from each individual analysis. 
 Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate. 
-In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.). 
+Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.
+critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).
+
+<!-- In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.). 
 We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
@@
 
-Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure. 
-Hypothetically, two analyst teams can arrive at two different effect sizes, even if they have made the exact same measurement, processed the data in the exact same way, and used the same predictor combination, but, crucially, differ in their random effect structure (e.g.
-one team assumes random intercepts only, the other team uses random slopes).
-Thus, additionally, we will run all analyses with a prespecified maximal random effect structure for all predictors.
+Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
 
-<!-- TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS ... ARE WE STILL DOING THIS? -->
-
-<!-- description of meta-analysis starts here -->
-
-Upon calculating a standardized effect size and standard error for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+<!-- TR: need to change according to new process (not delta t anymore) -->
 
@@
 The likelihood of the outcome variable is assumed to be normally distributed.
-Analysis teams and reviewers will be included as group-level effects (i.e., random effects). 
+Analysis teams will be included as a group-level effect (i.e., random effect). 
 For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+
+<!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
+
 A cauchy prior set at 0 with scale 1 will be used for $\tau$. 
 We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019).
+The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019). The code for the model can be found here: INSERT LINK. 
+We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) ... to be filled.
 
-We will assess the extent to which the meta-analytic estimate is modulated by the following predictors:
-The peer ratings of each analysis (numeric, 1-100), a measurement of the ‘uniqueness’ of the set of model parameters included in each analysis (see below, numeric), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teamsm, numeric).
+As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the
+
+<!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.
+We will use the Box-Cox transformation on the absolute values of deviation scores to achieve an approximately normal distribution (c.f.
+Fanelli and Ioannidis 2013, Fanelli et al.
+2017: supplement).
+-->
+
+<!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
+That gives you both the distance to the meta analytical estimate and the direction of that difference -->
+
+These analyses are secondary to our estimation of variation in effect sizes described above.
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+
+The following predictors will be used:
+
+First, we include a measure of the ‘uniqueness’ of individual analyses for
+- the set of predictor parameters,
+- the set of random effect parameters,
+- the acoustic measurement.
+
 The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
@@
 
-<!--TR: question: do we just want to look if the meta analytical estimate is modulated by our preidctors or do we want to look at the individuals teams deviations from the meta estimate are modulated by our predictors?-->
-
-<!--old :The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other.-->
-
 $$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$
@@
 
-WRITE ABOUT HOW TO HANDLE GAMS
-<!--TR: maybe don't mention? -->
+Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.
+
+Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.
+
+Forth, we include the major acoustic dimension that has been measured to answer the research question.
+We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties
+
+<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
+
+Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.
+
+Sixth, we include the following demographic factors about both the analysis teams:
+- ...
+
+DESCRIBE HOW WE WILL LOOK AT THESE THINGS
 

### 2020-12-21 RR_manuscript/Draft_RR.Rmd
remove trailing spaces
rephrase ~Operationalizing speech~

@@
 <!-- TR:(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)-->
+<!-- SC: Edited and rephrased -->
 
-RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.
+<!-- TODO: RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc. -->
 
-In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings.
-Take for example the sentence: "The president refused to concede".
-This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds.
-Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline.
-When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.
-how to measure the phenomenon of interest.
-For example, how do we measure whether two sounds are acoustically identical or not (e.g.
-"concede" vs.
-"conceal"), whether one word is more prominent than others ("The president REFUSES to concede"), or whether two discourse functions are produced differently ("The president refuses to concede." vs.
-"The president refuses to concede?")?
-In other words, how do we quantitatively capture relevant features of speech that correspond to the target behavior?
-This is not trivial. 
-Speech categories are inherently multidimensional and vary through time. 
-The acoustic parameters for one category are usually asynchronous, i.e.
-appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g.
+One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e. how to operationalize it.
+Take for example the following sentence: "Sheila says Pat is clever".
+Now, imagine we are interested in measuring the difference between that sentence and the sentence "Sheila says *Mat* is clever".
+How can we obtain a measure of dissimilarity between the first sound in *Pat* and the first sound in *Mat*?
+If we want to compare "Sheila says PAT is clever" to "Sheila says Pat is CLEVER", how do we quantify the difference between the two utterances?
+What if we are interested in how the argumentative nature of "Sheila says Pat is clever" and the expression of surprise in "Sheila says Pat is clever?!" are conveyed in speech?
+How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
+<!-- TODO: mention speech domains -->
+Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
+Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
+The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.
+
+Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
+The acoustic signatures of one category are usually asynchronous, i.e.
+they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.
 Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
-For example, the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in "bear" vs. "pear") can be manifested by many different acoustic measures (Lisker, 1977). 
-Even temporally dislocated acoustic parameters correlate with this lexical contrast. 
-For example, in the English words "led" versus "let", voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins & Nguyen, 2004).
-The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech. 
+A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
+This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
+Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
+The initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) (Hawkins & Nguyen, 2004).
+The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
 Studies investigating acoustic correlates of word stress (e.g.
-the difference between "insight" and "incite"), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
+the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
 Gordon & Roettger, 2017).
-Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance. 
-Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g. Niebuhr et al., 2011). 
-They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005). 
-All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity. 
-When testing hypotheses on speech production data, researchers need to make many decisions. 
-The larger the functional domain (e.g. are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations. 
-These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions. 
-To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional construct that might be manifested across the whole utterance.
+
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
+The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.
+
+When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
+Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
+These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.
+after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often overinformative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
 2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
@@
 (2020) showed that modifiers that are less typical for a given referent (e.g.
-a blue banana) are more likely to be used in an overinformative scenario (e.g.
+a blue banana) are more likely to be used in an over-informative scenario (e.g.
 when there is just one banana).

### 2020-12-21 RR_manuscript/Draft_RR.tex
rephrase ~Operationalizing speech~

@@
   man]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
-
 % \usepackage{etoolbox}
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
@@
 Human behavior is complex and offers many ways to be translated into numbers.
-This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like speech or video data.
+This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
 In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about operationalizing the raw data influence downstream decisions about statistical modelling, but statistical results can also lead researchers to go back and revise earlier decisions about the processing of the raw data.
+Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data.
-We explore the interaction between analytic choices at the stage of the operationalization of raw data and subsequent statistical modelling.
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams that gained access to the same set of acoustic recordings to answer the same research question.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
+Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
 
@@
 
-Data analysis comes with many decisions like how to operationalize a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
@@
 
-We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
+We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (``I knew it,'' Nickerson 1998), and perceiving events as being plausible in hindsight (``I knew it all along,'' Fischhoff 1975).
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to flexible measurement (Roettger 2019).
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across fields and subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches.
-
-Consequently, if methodologists are correct (e.g.~Simmons et al.~2011, Gelman \& Loken 2013), there are many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies.
-These interpretation are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
+These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are uncommon because data sharing is still rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
 
 While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
-Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed, not surprisingly, a large amount of variability.
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
 
@@
 SUM UP:
-Neuroscience\\
-Cognitive Modelling\\
-Clinical\\
+Neuroscience
+Cognitive Modelling
+Clinical
 Predictive models
@@
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
-In these studies the datasets were fixed and data collection or extraction could not be changed.
+In these studies the datasets were fixed and data collection or measurement could not be changed.
 
-However, in many fields the primary raw data is a complex signal that needs to be operationalized according to the research question.
-In social sciences, the raw observations correspond to recorded human behavior.
-In many cases, the behavior is recorded and stored as a complex visual and/or acoustic signal that is temporally extended and exhibits a complex structure.
-Decisions about how to operationalize a theoretically relevant aspect of that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
+In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
+Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+
 To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
@@
 
-RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc.
+One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e.~how to operationalize it.
+Take for example the following sentence: ``Sheila says Pat is clever.''
+Now, imagine we are interested in measuring the difference between that sentence and the sentence ``Sheila says \emph{Mat} is clever.''
+How can we obtain a measure of dissimilarity between the first sound in \emph{Pat} and the first sound in \emph{Mat}?
+If we want to compare ``Sheila says PAT is clever'' to ``Sheila says Pat is CLEVER,'' how do we quantify the difference between the two utterances?
+What if we are interested in how the argumentative nature of ``Sheila says Pat is clever'' and the expression of surprise in ``Sheila says Pat is clever?!'' are conveyed in speech?
+How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
+Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
+Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
+The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.
 
-In order to understand speech, listeners have to map a continuous, transient signal onto discrete meanings.
-Take for example the sentence: \enquote{The president refused to concede}.
-This sentence stretches over hundreds of milliseconds and contains several layers of linguistically relevant units such as words, syllables and individual sounds.
-Thus, it offers a considerable number of perspectives and decisions along the data analysis pipeline.
+Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
+The acoustic signatures of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
+A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
+This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
+Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
+The initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
+The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
+Studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
-IMAGE SHOWING A WAVE FORM WITH DIFFERENT DOMAINS (temporal) AND STRUCTURAL CUES (e.g.~f0, dur, int) MAPPING ONTO FUNCTIONAL CONTRASTS
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
+The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.
 
-When conducting a study on speech production, the first important analytic decision to test a hypothesis relates to operationalization of the relevant behavior, i.e.~how to measure the phenomenon of interest.
-For example, how do we measure whether two sounds are acoustically identical or not (e.g.~\enquote{bear} vs.~\enquote{pear}), whether one word is more prominent than others (\enquote{The president REFUSES to concede}), or whether two discourse functions are produced differently (\enquote{The president refuses to concede.} vs.~\enquote{The president refuses to concede?})?
-In other words, how do we quantitatively capture relevant features of speech?
-
-This is not trivial.
-Speech categories are inherently multidimensional and vary through time.
-The acoustic parameters for one category are usually asynchronous, i.e.~appear at different points of time in the unfolding signal and overlap with parameters for other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
-For example, the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \enquote{bear} vs.~\enquote{pear}) can be manifested by many different acoustic measures (Lisker, 1977).
-Even temporally dislocated acoustic parameters correlate with this lexical contrast.
-For example, in the English words \enquote{led} versus \enquote{let}, voicing correlates can be found in the acoustic manifestation of the initial /l/ of the word (Hawkins \& Nguyen, 2004).
-
-The apparent multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (e.g.~the difference between \enquote{insight} and \enquote{incite}), for example, have been using many different measurements, including temporal characteristics (duration of certain segments or subphonemic intervals), spectral characteristics (intensity measures, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
-
-Looking at even larger domains, the expression of pragmatic functions can be expressed by a variety of structurally different acoustic cues which can be distributed throughout the entire utterance.
-Discourse functions are systematically expressed by multiple local pitch modulations differing in their position, shape, and alignment (e.g.~Niebuhr et al., 2011).
-They can also be expressed by global or local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-All of these phonetic parameters are potential manifestations of underlying functional contrasts, like speaker's intentions, levels of arousal or social identity.
-
-When testing hypotheses on speech production data, researchers need to make many decisions.
-The larger the functional domain (e.g.~are we interested in lexical items or in whole utterances), the higher the number of possible operationalizations.
-These decisions are usually made prior to any statistical analysis, but can possibly be revised a posteriori in light of downstream analytic decisions.
-To probe the variability in data analysis pipelines across independent analytic teams, we provided researchers with an experimentally elicited speech corpus that looked at a functional contrast that is potentially manifested across the whole utterance.
+When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
+Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
+These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
-(e.g.~\enquote{a blue banana} vs.~\enquote{a yellow banana})?
-
+(e.g.~``a blue banana'' vs.~``a yellow banana'')?
+We are interested in the acoustic profile of referring expression.
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective \enquote{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
-
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often overinformative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
+For instance, one might use the adjective ``yellow'' to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an overinformative scenario (e.g.~when there is just one banana).
-
+For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
 This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
@@
 Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \enquote{banana} to indicate the contrastive nature of the \emph{noun}.
-In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \enquote{yellow} to indicate the contrastive nature of the \emph{modifier}.
+Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on `banana' to indicate the contrastive nature of the \emph{noun}.
+In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on `yellow' to indicate the contrastive nature of the \emph{modifier}.
 In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
@@
 
+The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
+We are further interested in which factors affect researchers' final results.
+
 \hypertarget{methods-mostly-copy-paste-from-evo-rr}{%
@@
 
-We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted).
+We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection. The analysis will substantially diverge from their approach (see §\#.\#)
 
-This project involves a series of steps (X-X) that begins with recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation among the different analyses, and producing the final manuscript.
+This project involves a series of steps (X-X):
+First, we recruit independent groups of researchers to analyze the data.
+Second, We give researchers access to the speech corpus and let them analyze the data as they see fit.
+Third, we generate peer review ratings of the analyses (based on methods, not results).
+Forth, we evaluate the variation among the different analyses.
+And finally, we collaboratively produce the final manuscript.
 We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.
+For the sake of simplicity, we refer to single researcher or small teams as `analysis teams.'
 
@@
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
-Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR).
+Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
 The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
@@
   \item
-    A perfect analysis with no conceivable improvements from the reviewer
+    A perfect analysis with no conceivable improvements from the reviewer.
   \end{enumerate}
@@
 
-\noindent \enquote{Please explain your ratings of this analysis.\\
-\noindent Please evaluate the selection of acoustic features.\\
-\noindent Please evaluate the measurement of acoustic features.\\
-\noindent Please evaluate the choice of statistical analysis type.\\
-\noindent Please evaluate the process of choosing variables for and structuring the statistical model.\\
-\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.\\
-\noindent Please evaluate the suitability of the structure of the statistical model.\\
-\noindent Please evaluate choices to exclude or not exclude subsets of the data.\\
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).}
+\noindent ``Please explain your ratings of this analysis.
+\noindent Please evaluate the selection of acoustic features.
+\noindent Please evaluate the measurement of acoustic features.
+\noindent Please evaluate the choice of statistical analysis type.
+\noindent Please evaluate the process of choosing variables for and structuring the statistical model.
+\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
+\noindent Please evaluate the suitability of the structure of the statistical model.
+\noindent Please evaluate choices to exclude or not exclude subsets of the data.
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''
 
@@
 After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: \enquote{If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.}
-The text box will be prefaced with this prompt: \enquote{Please explain your choice to revise (or not to revise) your ratings.}
+The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
+The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''
 
@@
 
-Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
-We will describe the variation in model specification in several ways:
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, as well as the mean, standard deviation and range of effect sizes reported.
+Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+We will describe the variation in model specifications in several ways:
 
-We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature an reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
 We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
@@
 
+Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).
+
+We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
 First, we will derive standardized effect sizes from each individual analysis.
 Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
-In multi-level models the variance components are partitioned into multiple sources of variation (e.g.~varying intercept of speakers and items, varying by-predictor slopes, etc.).
-We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index \(\delta_t\) (where t stands for \enquote{total} variance), which is calculated by the estimated difference between group means (\(\beta\)), divided by the square root of the sum of all variance components as formulated below:
+Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.~critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).
 
-\[\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}\]
-Where \(_i\) refers to the individual variance components.
-
-Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure.
-Hypothetically, two analyst teams can arrive at two different effect sizes, even if they have made the exact same measurement, processed the data in the exact same way, and used the same predictor combination, but, crucially, differ in their random effect structure (e.g.~one team assumes random intercepts only, the other team uses random slopes).
-Thus, additionally, we will run all analyses with a prespecified maximal random effect structure for all predictors.
-
-Upon calculating a standardized effect size and standard error for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
 
@@
 
-Effect size (\(\delta_{t}\)) is the outcome variable and the number of post-hoc changes and the number of models fit will be included as population-level effects (i.e., fixed effects).
+Effect size (\(\delta_{t}\)) will be the outcome variable.
 The likelihood of the outcome variable is assumed to be normally distributed.
-Analysis teams and reviewers will be included as group-level effects (i.e., random effects).
+Analysis teams will be included as a group-level effect (i.e., random effect).
 For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+
 A cauchy prior set at 0 with scale 1 will be used for \(\tau\).
 We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using \texttt{stan} (Stan, 2019) via the R package \texttt{brms} (Bürkner, 2019).
+The analysis will be conducted in R (R core team, 2020) and fit using \texttt{stan} (Stan, 2019) via the R package \texttt{brms} (Bürkner, 2019). The code for the model can be found here: INSERT LINK.
+We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) \ldots{} to be filled.
 
-The pooled estimate of the meta-analytic model will be used in a series of descriptive analyses that serve the purpose of describing how individual teams vary from each other.
-Specifically, we will explain how team effect sizes deviate from the pooled estimate based on a measure of the uniqueness of the set of variables included in each analysis.
-We will use Sorensen's Similarity Index (SSI) to derive a \enquote{uniqueness} score.
+As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the
+
+These analyses are secondary to our estimation of variation in effect sizes described above.
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+
+The following predictors will be used:
+
+First, we include a measure of the `uniqueness' of individual analyses for
+- the set of predictor parameters,
+- the set of random effect parameters,
+- the acoustic measurement.
+
+The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
 The SSI is an index typically used in ecology research to compare species composition across sites.
@@
 
-where, given a pair of models, a is the number of variables common to both, b is the number of variables that occur in the first model but not in the second, and c is the number of variables that occur in the second model but not in the first.
-We then will use the per-model average Sorensen's index value as an independent variable to predict the deviation score in a general linear model, with no random effect since each analysis is included only once, in the stats package in R (R\_Core\_Team 2019):
+where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.
 
-WRITE ABOUT HOW TO HANDLE GAMS
+Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.
+
+Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.
+
+Forth, we include the major acoustic dimension that has been measured to answer the research question.
+We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties
+
+Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.
+
+Sixth, we include the following demographic factors about both the analysis teams:
+- \ldots{}
+
+DESCRIBE HOW WE WILL LOOK AT THESE THINGS
 
@@
 We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
-
-ADD GAM EXCLUSION
-
-DESCRIBE META-NALYSIS
-
-We will assess the extent to which deviations from the meta-analytic mean by individual effect sizes can be explained by the following predictors:
-
-The peer ratings (1-100) of each analysis, a measurement of the \enquote{uniqueness} of the set of model parameters included in each analysis (see below), whether or not analysis teams have changed their analyses in a post hoc fashion (EXPLAIN ABOVE, binary), the number of analyses performed before the final model was performed (as self-estimated by the teams).
-
-The uniqueness of model parameters will be assessed using the Sorensen's Similarity Index (an index typically used to compare species composition across sites).
-Here we treat model parameters as species and individual analyses as sites.
-To generate an individual Sorensen's value for each analysis requires calculating the pairwise Sorensen's value for all pairs of analyses (of the same data set), and then taking the average across these Sorensen's values for each analysis.
-We will calculate the Sorensen's index values using the betapart package (Baselga et al.~2018) in R:
-
-\[\beta_{Sorensen} = \frac{b+c}{2_a + b + c}\]
-
-where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.
-
-The individual posterior mean for each analysis of each team serves as the dependent variable in these analyses.
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
@@
 
+\end{CSLReferences}
+
 \endgroup

### 2020-12-22 RR_manuscript/Draft_RR.Rmd
lingering edits
edits and comments

@@
 
-One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e. how to operationalize it.
-Take for example the following sentence: "Sheila says Pat is clever".
-Now, imagine we are interested in measuring the difference between that sentence and the sentence "Sheila says *Mat* is clever".
-How can we obtain a measure of dissimilarity between the first sound in *Pat* and the first sound in *Mat*?
-If we want to compare "Sheila says PAT is clever" to "Sheila says Pat is CLEVER", how do we quantify the difference between the two utterances?
-What if we are interested in how the argumentative nature of "Sheila says Pat is clever" and the expression of surprise in "Sheila says Pat is clever?!" are conveyed in speech?
-How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
+<!-- TR: I added a transition sentence -->
+Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains. 
+Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:
+
+<!-- TR: I'd suggest an easier example (Sheila and Pat are both uncommon names, internationally speaking) and possibly a more relateable (possibly timely) example.
+Something about zoom meetings or sth maybe?
+Examples are super important to relate to the reader and lure them in.
+Here is my suggestion-->
+
+"I hope Liz does not go to the grocery store tomorrow".
+
+Depending on the speaker's intention, this sentence can be said in different ways. 
+If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow. 
+If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
+
+<!-- Now, imagine we are interested in measuring the difference between that sentence and the sentence "Sheila says *Mat* is clever".
+How can we obtain a measure of dissimilarity between the first sound in *Pat* and the first sound in *Mat*? -->
+
+<!-- TR: Keep in mind that the research question is not about segmental phenomena. To relate to the question later, I'd suggest a prosodic measure, e.g.  -->
+
+If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
 <!-- TODO: mention speech domains -->
-Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
+Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (e.g.
+For example, studies investigating acoustic correlates of word stress (e.g.
 the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
@@
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).
 
@@
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
-Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.
+Wicherts et al.).
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
+The present paper probes this garden of forking path in speech analysis.
 To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

### 2020-12-22 RR_manuscript/Draft_RR.Rmd
fix some typos + minor rephrasing + add some refs; up to The data set section

@@
 ---
-title             : "Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech."
+title             : "Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
 shorttitle        : "Many analysts - one speech data set"
@@
 In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
+<!-- TODO: add refs for variable conclusions -->
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
@@
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets.
+This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020).
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
+Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
+<!-- TODO: include number of teams when known -->
 Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
-This can be problematic because to err is human.
+This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 <!-- I'd probably drop this.
@@
 <!-- TR: But isn't the human bias the major issue in statistical misinterpretation? (It also leads naturally to the next paragraph.) -->
+<!-- SC: Rephrased the sentence to underline that the presence of cognitive biases is what creates the problem, rather than just not specifying decisions before hand. -->
 
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
 Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013).
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
+<!-- TODO: add various references about transparency and repro -->
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
 
@@
 ## Crowdsourcing alternative analyses
-In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis
-Analytic approaches and consequently the results varied widely between teams.
+
+In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
+Analytical approaches and consequently the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
@@
 
+<!-- TODO: sum up crowd-sourced studies from different disciplines -->
 SUM UP:
 Neuroscience
-Cognitive Modelling
+Cognitive modeling
 Clinical
@@
 
-While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
-In these studies the datasets were fixed and data collection or measurement could not be changed.
-<!-- JC: any particular reason to favor data table over dataset?
---> <!-- TR: I think my reasoning was dataset can be data table or raw data.
+While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
+In these studies the data sets were fixed and data collection or measurement could not be changed.
+<!-- JC: any particular reason to favor data table over data set?
+--> <!-- TR: I think my reasoning was data set can be data table or raw data.
 Data table is the numerical derivation of the raw data.
 Maybe not a useful distinction?-->
+<!-- SC: I like the distinction between data/data sets and data table. -->
 
@@
 In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa [@flake2019].
 <!-- TR:maybe give a concrete example, how such an interactionn would look like for speech data?-->
+<!-- SC: Added example from speech. Is it any good? -->
+For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
+In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.
 
-To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
+To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
 
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow. 
-If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
+If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word *tomorrow*.
+If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the words *grocery store*.
 
@@
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@ogden2004; @foulkes2006; @white2009].
 
@@
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.
-Wicherts et al.).
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al.).
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
-The present paper probes this garden of forking path in speech analysis.
-To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+The present paper probes this garden of forking paths in the analysis of speech.
+To assess the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 
-Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
 <!-- TR: Big to-do point.

### 2020-12-22 RR_manuscript/Draft_RR.tex

@@
 \hypersetup{
-  pdftitle={Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.},
+  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
   pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
@@
 
-\title{Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.}
+\title{Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
 \author{First Author\textsuperscript{\#}, Second Author\textsuperscript{\#}, \ldots{}\textsuperscript{\#}, \& Last Author\textsuperscript{\#}}
@@
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw vastly different conclusions about the same dataset (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of datasets.
+This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
+Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
 Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modelling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
-This can be problematic because to err is human.
+This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
 Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical reanalyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
 
@@
 
-In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis
-Analytic approaches and consequently the results varied widely between teams.
+In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis.
+Analytical approaches and consequently the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
@@
 Neuroscience
-Cognitive Modelling
+Cognitive modeling
 Clinical
@@
 
-While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
-In these studies the datasets were fixed and data collection or measurement could not be changed.
+While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
+In these studies the data sets were fixed and data collection or measurement could not be changed.
 
@@
 In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
+For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
+In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.
 
-To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
+To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
 
@@
 
-One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e.~how to operationalize it.
-Take for example the following sentence: ``Sheila says Pat is clever.''
-Now, imagine we are interested in measuring the difference between that sentence and the sentence ``Sheila says \emph{Mat} is clever.''
-How can we obtain a measure of dissimilarity between the first sound in \emph{Pat} and the first sound in \emph{Mat}?
-If we want to compare ``Sheila says PAT is clever'' to ``Sheila says Pat is CLEVER,'' how do we quantify the difference between the two utterances?
-What if we are interested in how the argumentative nature of ``Sheila says Pat is clever'' and the expression of surprise in ``Sheila says Pat is clever?!'' are conveyed in speech?
-How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
-Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
+Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
+Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:
+
+``I hope Liz does not go to the grocery store tomorrow.''
+
+Depending on the speaker's intention, this sentence can be said in different ways.
+If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word \emph{tomorrow}.
+If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the words \emph{grocery store}.
+
+If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
+Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
 
@@
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
+The present paper probes this garden of forking paths in the analysis of speech.
+To assess the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 
-Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 
+\leavevmode\hypertarget{ref-flake2019}{}%
+Flake, J. K., \& Fried, E. I. (2019). Measurement schmeasurement: Questionable measurement practices and how to avoid them. Pre-print available at PsyArXiv.
+
+\leavevmode\hypertarget{ref-foulkes2006}{}%
+Foulkes, P., \& Docherty, G. (2006). The social life of phonetics and phonology. \emph{Journal of Phonetics}, \emph{34}(4), 409--438.
+
+\leavevmode\hypertarget{ref-ogden2004}{}%
+Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
+
 \leavevmode\hypertarget{ref-open2015estimating}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-white2009}{}%
+White, L., Payne, E., \& Mattys, S.
+L.
+(2009).
+Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian.
+In M.
+Vigario, S.
+Frota, \& M.
+J.
+Freitas (Eds.), \emph{Phonetics and phonology: Interactions and interrelations} (pp.
+137--158).
+Amsterdam: John Benjamins.
 

### 2020-12-22 RR_manuscript/Draft_RR.tex
fix typos, expand parts of methods; up to Step 4

--- 2020-12-21 RR_manuscript/Draft_RR.tex
@@
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
-In these studies the datasets were fixed and data collection or measurement could not be changed.
+In these studies the data sets were fixed and data collection or measurement could not be changed.
 
@@
 In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
+\textless\textless\textless\textless\textless\textless\textless{} HEAD
 Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+=======
+Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
+\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{} 4860d0ed0c2fc204883e1c150efb5749b4ef1669
 
@@
 
-One of the earliest analytical decisions a researcher has to make when conducting a study on speech production is choosing how to measure the phenomenon of interest, i.e.~how to operationalize it.
-Take for example the following sentence: ``Sheila says Pat is clever.''
-Now, imagine we are interested in measuring the difference between that sentence and the sentence ``Sheila says \emph{Mat} is clever.''
-How can we obtain a measure of dissimilarity between the first sound in \emph{Pat} and the first sound in \emph{Mat}?
-If we want to compare ``Sheila says PAT is clever'' to ``Sheila says Pat is CLEVER,'' how do we quantify the difference between the two utterances?
-What if we are interested in how the argumentative nature of ``Sheila says Pat is clever'' and the expression of surprise in ``Sheila says Pat is clever?!'' are conveyed in speech?
-How do we choose what to measure and how to measure it so that we can answer our research question and test our hypotheses?
-Given the continuous and transient nature of speech, identifying which speech features should be selected within which domain becomes a non-trivial task.
+Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
+Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:
+
+``I hope Liz does not go to the grocery store tomorrow.''
+
+Depending on the speaker's intention, this sentence can be said in different ways.
+If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow.
+If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
+
+If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
+Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
-Studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, the relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole sentences.
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm.
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).
 
@@
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-Moreover, even the analysis of a single measure can be approached via an ever-increasing range of different statistical models, which further multiply the combinations of possible analytical choices.
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
+The present paper probes this garden of forking path in speech analysis.
 To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
@@
 Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
-(e.g.~``a blue banana'' vs.~``a yellow banana'')?
-We are interested in the acoustic profile of referring expression.
+(e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
+We are interested in the acoustic profile of referring expressions.
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
-It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana.
-The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource efficient in that they avoid redundancy (Grice 1975).
+It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
+The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective ``yellow'' to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+
 Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
@@
 This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
-Even looking at morphosyntactically identical expressions, speakers can modulate these expressions via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
+
+Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
-Intonation marks discourse-relevant referents for being new or given information to guide listeners' interpretation of incoming messages.
+Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
 In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
 Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on `banana' to indicate the contrastive nature of the \emph{noun}.
-In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on `yellow' to indicate the contrastive nature of the \emph{modifier}.
+Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
+In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
 In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
-
-INFORMATION ABOUT THE DATA SET AND EXP DESIGN
 
@@
 The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
-We are further interested in which factors affect researchers' final results.
+We are further interested in which factors affect the researchers' final results.
 
@@
 
-We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection. The analysis will substantially diverge from their approach (see §\#.\#)
+We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection.
+However, the analysis will substantially diverge from their approach (see §\#.\#)
 
 This project involves a series of steps (X-X):
-First, we recruit independent groups of researchers to analyze the data.
-Second, We give researchers access to the speech corpus and let them analyze the data as they see fit.
-Third, we generate peer review ratings of the analyses (based on methods, not results).
-Forth, we evaluate the variation among the different analyses.
-And finally, we collaboratively produce the final manuscript.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  We will recruit independent groups of researchers to analyze the data.
+\item
+  We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+\item
+  We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
+\item
+  We will evaluate the variation among the different analyses.
+\item
+  Lastly, we will collaboratively produce the final manuscript.
+\end{enumerate}
+
 We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
@@
 
-Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
+The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
 The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as `analysis teams.'
+For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''
 
-Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below).
+Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 
-We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity (\(\tau^2\)) with a 95\% confidence interval that does not encompass zero.
-This minimum sample size is invariant regardless of \(\tau^2\).
-This is because the same t-statistic value will be obtained by the same sample size regardless of variance (\(\tau^2\)).
-We see this by first examining the formula for the standard error, SE for variance, (\(\tau^2\)) or SE(\(\tau^2\)) assuming normality in an underlying distribution of effect sizes (Knight 2000):
+To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
+The aim of the meta-analysis is to obtain an estimate of heterogeneity (\(\tau^2\)) of the effect sizes reported by the analysis teams.
+Ideally, the 95\% credible interval of \(\tau^2\) should not include 0 (i.e.~we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a \emph{t}-statistic that would correspond to a \emph{p}-value smaller than 0.05).
+Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:
 
@@
 
-and then rearranging the above formula to show how the t-statistic is independent of \(\tau^2\), as seen below.
+Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that \emph{t} will be the same regardless of \(\tau^2\):
 
-\[t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}\]
+\[t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}\]
 
-We then find a minimum n = 12 according to this formula.
+In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
+When \(n = 12\) then \(t_{12-1} = t_{11} = 2.3452\) and \(p = 0.0388\).
+A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.
 
@@
 
-Analysis teams will register and answer a demographic and expertise survey (LINK).
+The analysis teams will register and answer a demographic and expertise survey (LINK).
 The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
@@
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
@@
 
-``Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
 
@@
   \item
-    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
+    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
   \end{enumerate}
@@
   \item
-    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
+    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
   \end{enumerate}
@@
   \item
-    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
+    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
   \end{enumerate}
@@
 
-After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:
+After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:
 
@@
 \noindent Please evaluate the choice of statistical analysis type.
-\noindent Please evaluate the process of choosing variables for and structuring the statistical model.
+\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
 \noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
@@
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
 The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''

### 2020-12-22 RR_manuscript/Draft_RR.Rmd
fix merge conflicts :sparkles:

@@
 In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-<!-- TODO: add refs for variable conclusions -->
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
@@
 In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
-<!-- TODO: include number of teams when known -->
 Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
@@
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
-This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 <!-- I'd probably drop this.
@@
 <!-- TR: But isn't the human bias the major issue in statistical misinterpretation? (It also leads naturally to the next paragraph.) -->
-<!-- SC: Rephrased the sentence to underline that the presence of cognitive biases is what creates the problem, rather than just not specifying decisions before hand. -->
+This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 
-We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (“I knew it”, Nickerson 1998), and perceiving events as being plausible in hindsight (“I knew it all along”, Fischhoff 1975).
+We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations ("I knew it", Nickerson 1998), and perceiving events as being plausible in hindsight ("I knew it all along", Fischhoff 1975).
 <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-<!-- TODO: add various references about transparency and repro -->
 Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
@@
 
-<!-- TODO: sum up crowd-sourced studies from different disciplines -->
 SUM UP:
@@
 Maybe not a useful distinction?-->
-<!-- SC: I like the distinction between data/data sets and data table. -->
 
@@
 Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa [@flake2019].
-<!-- TR:maybe give a concrete example, how such an interactionn would look like for speech data?-->
-<!-- SC: Added example from speech. Is it any good? -->
+<!-- TR:maybe give a concrete example, how such an interaction would look like for speech data?-->
 For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
@@
 
-To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
+To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
 
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word *tomorrow*.
-If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the words *grocery store*.
+If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow.
+If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
 
@@
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@ogden2004; @foulkes2006; @white2009].
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@foulkes2006; @ogden2009; @white2009].
 
@@
 (e.g.
-“a blue banana” vs.
-“a yellow banana”)?
-We are interested in the acoustic profile of referring expression.
+*a blue banana* vs *a yellow banana*)?
+We are interested in the acoustic profile of referring expressions.
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
-It is an open question how speakers choose a referential expression when they want to refer to a specific entity like a banana.
-The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referential expression.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource efficient in that they avoid redundancy (Grice 1975).
+It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
+The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective "yellow" to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+
 Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
@@
 whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
-Even looking at morphosyntactically identical expressions, speakers can modulate these expressions via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.
+
+Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.
 Ladd 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
-Intonation marks discourse-relevant referents for being new or given information to guide listeners’ interpretation of incoming messages.
+Intonation marks discourse-relevant referents for being new or given information to guide the listeners’ interpretation of incoming messages.
 In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
 Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on ‘banana’ to indicate the contrastive nature of the *noun*.
-In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on ‘yellow’ to indicate the contrastive nature of the *modifier*.
+Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on *banana* to indicate the contrastive nature of the noun.
+In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on *yellow* to indicate the contrastive nature of the modifier.
 In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.
@@
 
-INFORMATION ABOUT THE DATA SET AND EXP DESIGN
+<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN -->
 
 ## Research questions
+
 The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
-We are further interested in which factors  affect researchers' final results.
+We are further interested in which factors affect the researchers' final results.
 
 # Methods (mostly copy-paste from Evo-RR)
-We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted) in terms of data collection. The analysis will substantially diverge from their approach (see §#.#)
+
+We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted) in terms of data collection.
+However, the analysis will substantially diverge from their approach (see §#.#)
 
 This project involves a series of steps (X-X):
-First, we recruit independent groups of researchers to analyze the data.
-Second, We give researchers access to the speech corpus and let them analyze the data as they see fit.
-Third, we generate peer review ratings of the analyses (based on methods, not results).
-Forth, we evaluate the variation among the different analyses.
-And finally, we collaboratively produce the final manuscript.
+
+1. We will recruit independent groups of researchers to analyze the data.
+2. We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+3. We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
+4. We will evaluate the variation among the different analyses.
+5. Lastly, we will collaboratively produce the final manuscript.
+
 We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
@@
 ## Step 1: Recruitment and Initial Survey of Analysts
-Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accesibilty to potential analysts (LINK).
+
+<!-- TODO: include materials link and mailing lists -->
+The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
 The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as ‘analysis teams’.
+For the sake of simplicity, we refer to single researcher or small teams as "analysis teams".
 
@@
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
+<!-- TODO: add link to informed consent form -->
 All analysts will sign a consent (ethics) document (LINK).
@@
 <!-- sample size info from Ecology RR -->
-We identified our minimum number of analyses per data set by considering the number of effects needed in a meta-analysis to generate an estimate of heterogeneity ($\tau^2$) with a 95% confidence interval that does not encompass zero.
-This minimum sample size is invariant regardless of $\tau^2$.
-This is because the same t-statistic value will be obtained by the same sample size regardless of variance ($\tau^2$).
-We see this by first examining the formula for the standard error, SE for variance, ($\tau^2$) or SE($\tau^2$) assuming normality in an underlying distribution of effect sizes (Knight 2000):
+<!-- SC: rephrased and expanded -->
+To identify the minimal sample size, we followed the method in [ECO RR].
+The aim of the meta-analysis is to obtain an estimate of heterogeneity ($\tau^2$) of the effect sizes reported by the analysis teams.
+Ideally, the 95% credible interval of $\tau^2$ should not include 0 (i.e.
+we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a *t*-statistic that would correspond to a *p*-value smaller than 0.05).
+Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of $\tau^2$ can be calculated with the formula:
 
@@
 
-and then rearranging the above formula to show how the t-statistic is independent of $\tau^2$, as seen below.
+Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that *t* will be the same regardless of $\tau^2$:
 
-$$t = \frac{\tau^2}{SE(\tau^2)} = \sqrt{\frac{(n-1)}{2}}$$
+$$t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}$$
 
-We then find a minimum n = 12 according to this formula.
-<!-- We need to decide if we use this (I still don't understand it) -->
+In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
+When $n = 12$ then $t_{12-1} = t_{11} = 2.3452$ and $p = 0.0388$.
+A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.
+
+```{r t, eval=FALSE, include=FALSE}
+n = 12
+df = n - 1
+t <- sqrt((df)/2)
+pt(t, df, lower.tail = F) * 2
+```
 
@@
 
-Analysis teams will register and answer a demographic and expertise survey (LINK).
+<!-- TODO: add link to demo survey -->
+The analysis teams will register and answer a demographic and expertise survey (LINK).
 The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
@@
 
+<!-- TODO: add link to analytical survey -->
 Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
@@
 This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
+<!-- TODO: add link to peer review survey -->
 The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->
 
-“Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
 
 - 100. A perfect analysis with no conceivable improvements from the reviewer.
-- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
-- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
-- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
+- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
+- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
+- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
 - 0.
@@
 
-After providing this rating, the reviewer will then be provided with a series of text boxes and the following prompts:
+After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:
 
-\noindent “Please explain your ratings of this analysis.
+\noindent "Please explain your ratings of this analysis.
 \noindent Please evaluate the selection of acoustic features.
@@
 \noindent Please evaluate choices to exclude or not exclude subsets of the data.
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).”
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice)."
 
@@
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: “If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.”
-The text box will be prefaced with this prompt: “Please explain your choice to revise (or not to revise) your ratings.”
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
+The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings."
 
 ## Step 4: Evaluate Variation
+
 Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
@@
 <!-- In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.).
-We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
+We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for "total" variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
 

### 2020-12-28 RR_manuscript/Draft_RR.Rmd
edit RR Step 4

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output:
+  papaja::apa6_pdf:
+    number_sections: true
 ---
@@
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@foulkes2006; @ogden2009; @white2009].
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@foulkes2006; @ogden2004; @white2009].
 
@@
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+To assess the variability in data analysis pipelines across independent researchers, we provided the analysis teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
-We will describe the variation in model specifications in several ways:
 
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.
+### Descriptive statistics
+
+We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.
 f0 or duration), the operationalization and the temporal domain of measurement (e.g.
-mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments (e.g.
+mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature and reasoning behind inferential assessments (e.g.
 dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
@@
 
-ADD FORMULA
+<!-- TODO: ADD FORMULA of linear regression model -->
+FORMULA
 
-Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).
+### Meta-analytical estimation
 
-We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
-First, we will derive standardized effect sizes from each individual analysis.
-Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
-Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.
-critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).
+Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
+We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
+<!-- SC: it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
+-->
+Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.
+*z*-scores) using a Bayesian multilevel model.
+The standardized effect size ($\eta_i$) of each analysis will be the estimated coefficient of the critical predictor (i.e.
+critical according to the analysis teams' self-reported inferential criteria).
+If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
+Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size ($\text{se}_i$).
+This will enable us to fit a so-called "measurement-error" model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
 
-<!-- In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.).
-We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for "total" variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
-
-$$\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}$$
-Where $_i$ refers to the individual variance components.
-
-<!-- TR: Do we still need standardized effect sizes? to compare shit or are we just going to compare their estimates? -->
-
-<!-- TR: CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
-RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/ -->
-
-<!-- JC:I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
-
-$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$-->
-
-Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+After the extraction of the standardized effect sizes $\eta_i$ and related standard error $\text{se}_i$ for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
 
 <!-- TR: need to change according to new process (not delta t anymore) -->
+<!-- SC: done! -->
 
@@
 \begin{aligned}
-\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
-\theta_i     & \sim \text{Normal} (\mu, \tau) \\
-\mu          & \sim \text{Normal} (0, 1) \\
-\tau         & \sim \text{HalfCauchy} (0, 1)
+\eta_i   & \sim \text{Normal}(\mu_i, \sigma_i) \\
+\mu_i     & = \alpha + \alpha_{\text{team}[i]} + \beta_n\\
+\alpha  & \sim \text{Normal}(0, 1) \\
+\beta_n & \sim \text{Normal}(0, 1) \\
+\sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
+\sigma_i  & = \text{se}_i
 \end{aligned}
@@
 
-Effect size ($\delta_{t}$) will be the outcome variable.
-The likelihood of the outcome variable is assumed to be normally distributed.
-Analysis teams will be included as a group-level effect (i.e., random effect).
-For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+The outcome variable will be the set of standardized effect sizes.
+The respective standard errors $\text{se}_i$ will be included to fit a measurement-error model.
+The likelihood of $\eta_i$ is assumed to be normally distributed (Knight 2000).
+The analysis teams will be included as a group-level effect (i.e., random effect).
+For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+<!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
+<!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
+We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
+The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+<!-- TODO: add link to code of the meta-analytical model -->
+The code for the model can be found here: INSERT LINK.
 
-<!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
+<!-- TODO: list predictors in meta-analytical model -->
+We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
 
-A cauchy prior set at 0 with scale 1 will be used for $\tau$.
-We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019). The code for the model can be found here: INSERT LINK.
-We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) ... to be filled.
+* The peer ratings of each analysis (numeric, 1-100).
+* ...
 
-As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the
+<!-- From ?brms:brmsformula -->
+<!-- For families gaussian, student and skew_normal, it is possible to
+specify standard errors of the observations, thus allowing to perform
+meta-analysis. Suppose that the variable yi contains the effect sizes
+from the studies and sei the corresponding standard errors. Then,
+fixed and random effects meta-analyses can be conducted using the
+formulas yi | se(sei) ~ 1 and yi | se(sei) ~ 1 + (1|study),
+respectively, where study is a variable uniquely identifying every
+study. If desired, meta-regression can be performed via yi | se(sei) ~
+1 + mod1 + mod2 + (1|study) or  yi | se(sei) ~ 1 + mod1 + mod2 + (1 +
+mod1 + mod2|study), where mod1 and mod2 represent moderator variables.
+By default, the standard errors replace the parameter sigma. To model
+sigma in addition to the known standard errors, set argument sigma in
+function se to TRUE, for instance, yi | se(sei, sigma = TRUE) ~ 1. -->
 
+### Exploratory road map
+<!-- SC: change heading to your liking -->
+
+As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference ($\delta_i$) between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
 <!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.
@@
 -->
-
 <!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
 That gives you both the distance to the meta analytical estimate and the direction of that difference -->
+<!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
+These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+We will model the effect of the following predictors:
 
-These analyses are secondary to our estimation of variation in effect sizes described above.
-We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+- *Measure of uniqueness* of individual analyses for the set of predictors in each model.
+- *Measure of conservativeness* of the model specification.
+- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out.
+- *Number of models* the teams will report to have run.
+- *Major dimension* that has been measured to answer the research question.
+- *Temporal window* that the measurement is taken over.
+- *Demographic factors* of analysis teams and analysts.
 
-The following predictors will be used:
+The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
+The SDI is an index typically used in ecology research to compare species composition across sites.
+For our purposes, we will treat predictors as species and individual analyses as sites.
+The SDI for a pair of analyses $(X, Y)$ can be obtained using the following formula:
 
-First, we include a measure of the ‘uniqueness’ of individual analyses for
-- the set of predictor parameters,
-- the set of random effect parameters,
-- the acoustic measurement.
+<!-- SC: refactored the formula so it is closer to the original source -->
 
-The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
-The SSI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat variables as species and individual analyses as sites.
-In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R.
-We achieve this using the following formula:
+$$\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}$$
 
-$$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$
+where $|X \cap Y|$ is the number of variables common to both models, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
 
-where $a$ is the number of variables common to both models, $b$ is the number of variables that occur in the first model but not in the second and $c$ is the number of variables that occur in the second model but not in the first.
+```{r sdi, eval=FALSE, include=FALSE}
+x <- c("a", "b", "c", "d")
+y <- c("b", "d", "e", "f")
+(2 * length(intersect(x,y))) / (length(x) + length(y))
+```
 
-Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package (Baselga et al.
+2018).
+The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.
+frequency center of gravity, harmonics difference, etc.), other measures (e.g.
+principal components, vowel dispersion, etc.)
+<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
+<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
+The temporal window that the measurement is taken over is defined by the target linguistic unit.
+We assume the following relevant linguistic units: segment, syllable, word, phrase.
 
-Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.
+We will include the following demographic factors about both the analysis teams:
 
-Forth, we include the major acoustic dimension that has been measured to answer the research question.
-We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties
-
-<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
-
-Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.
-
-Sixth, we include the following demographic factors about both the analysis teams:
 - ...
 
-DESCRIBE HOW WE WILL LOOK AT THESE THINGS
+<!-- TODO: DESCRIBE HOW WE WILL LOOK AT demographics -->
 
-We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
+We will publicly archive all relevant data, code, and materials on the Open Science Framework (<https://osf.io/3bmcp/>).
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2020-12-28 RR_manuscript/Draft_RR.tex
edit RR Step 4

@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 
-While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
+While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
 In these studies the data sets were fixed and data collection or measurement could not be changed.
@@
 In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-\textless\textless\textless\textless\textless\textless\textless{} HEAD
-Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
-=======
-Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
-\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{} 4860d0ed0c2fc204883e1c150efb5749b4ef1669
+Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
+For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
+In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.
 
-To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set
+To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
 
@@
 The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).
+Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
 
@@
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
-The present paper probes this garden of forking path in speech analysis.
-To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+The present paper probes this garden of forking paths in the analysis of speech.
+To assess the variability in data analysis pipelines across independent researchers, we provided the analysis teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
-We will describe the variation in model specifications in several ways:
 
-First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature an reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
+\hypertarget{descriptive-statistics}{%
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
+
+We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
 We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
 
-ADD FORMULA
+FORMULA
 
-Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).
+\hypertarget{meta-analytical-estimation}{%
+\subsubsection{Meta-analytical estimation}\label{meta-analytical-estimation}}
 
-We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
-First, we will derive standardized effect sizes from each individual analysis.
-Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
-Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.~critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).
+Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
+We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
+Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.~\emph{z}-scores) using a Bayesian multilevel model.
+The standardized effect size (\(\eta_i\)) of each analysis will be the estimated coefficient of the critical predictor (i.e.~critical according to the analysis teams' self-reported inferential criteria).
+If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
+Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size (\(\text{se}_i\)).
+This will enable us to fit a so-called ``measurement-error'' model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
 
-Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
+After the extraction of the standardized effect sizes \(\eta_i\) and related standard error \(\text{se}_i\) for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
 
@@
 
-Effect size (\(\delta_{t}\)) will be the outcome variable.
-The likelihood of the outcome variable is assumed to be normally distributed.
-Analysis teams will be included as a group-level effect (i.e., random effect).
-For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+The outcome variable will be the set of standardized effect sizes.
+The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
+The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight 2000).
+The analysis teams will be included as a group-level effect (i.e., random effect).
+For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
+The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+The code for the model can be found here: INSERT LINK.
 
-A cauchy prior set at 0 with scale 1 will be used for \(\tau\).
-We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using \texttt{stan} (Stan, 2019) via the R package \texttt{brms} (Bürkner, 2019). The code for the model can be found here: INSERT LINK.
-We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) \ldots{} to be filled.
+We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
 
-As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the
+\begin{itemize}
+\tightlist
+\item
+  The peer ratings of each analysis (numeric, 1-100).
+\item
+  \ldots{}
+\end{itemize}
 
-These analyses are secondary to our estimation of variation in effect sizes described above.
+\hypertarget{exploratory-road-map}{%
+\subsubsection{Exploratory road map}\label{exploratory-road-map}}
+
+As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference (\(\delta_i\)) between the meta-analytical mean (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
+These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
 We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+We will model the effect of the following predictors:
 
-The following predictors will be used:
+\begin{itemize}
+\tightlist
+\item
+  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
+\item
+  \emph{Measure of conservativeness} of the model specification.
+\item
+  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
+\item
+  \emph{Number of models} the teams will report to have run.
+\item
+  \emph{Major dimension} that has been measured to answer the research question.
+\item
+  \emph{Temporal window} that the measurement is taken over.
+\item
+  \emph{Demographic factors} of analysis teams and analysts.
+\end{itemize}
 
-First, we include a measure of the `uniqueness' of individual analyses for
-- the set of predictor parameters,
-- the set of random effect parameters,
-- the acoustic measurement.
+The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
+The SDI is an index typically used in ecology research to compare species composition across sites.
+For our purposes, we will treat predictors as species and individual analyses as sites.
+The SDI for a pair of analyses \((X, Y)\) can be obtained using the following formula:
 
-The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
-The SSI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat variables as species and individual analyses as sites.
-In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al.~2018) in R.
-We achieve this using the following formula:
+\[\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}\]
 
-\[\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}\]
+where \(|X \cap Y|\) is the number of variables common to both models, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
 
-where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).
+The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
+The temporal window that the measurement is taken over is defined by the target linguistic unit.
+We assume the following relevant linguistic units: segment, syllable, word, phrase.
 
-Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.
+We will include the following demographic factors about both the analysis teams:
 
-Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.
+\begin{itemize}
+\tightlist
+\item
+  \ldots{}
+\end{itemize}
 
-Forth, we include the major acoustic dimension that has been measured to answer the research question.
-We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties
-
-Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.
-
-Sixth, we include the following demographic factors about both the analysis teams:
-- \ldots{}
-
-DESCRIBE HOW WE WILL LOOK AT THESE THINGS
-
-We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
+We will publicly archive all relevant data, code, and materials on the Open Science Framework (\url{https://osf.io/3bmcp/}).
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
@@
 
+\leavevmode\hypertarget{ref-dice1945}{}%
+Dice, L. R. (1945). Measures of the amount of ecologic association between species. \emph{Ecology}, \emph{26}(3), 297--302.
+
+\leavevmode\hypertarget{ref-flake2019}{}%
+Flake, J. K., \& Fried, E. I. (2019). Measurement schmeasurement: Questionable measurement practices and how to avoid them. Pre-print available at PsyArXiv.
+
+\leavevmode\hypertarget{ref-foulkes2006}{}%
+Foulkes, P., \& Docherty, G. (2006). The social life of phonetics and phonology. \emph{Journal of Phonetics}, \emph{34}(4), 409--438.
+
+\leavevmode\hypertarget{ref-ogden2004}{}%
+Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
+
 \leavevmode\hypertarget{ref-open2015estimating}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-sorensen1948}{}%
+Sørensen, T.
+(1948).
+A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on {D}anish commons.
+\emph{Kongelige Danske Videnskabernes Selskab}, \emph{5}(4), 1--34.
+
+\leavevmode\hypertarget{ref-white2009}{}%
+White, L., Payne, E., \& Mattys, S.
+L.
+(2009).
+Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian.
+In M.
+Vigario, S.
+Frota, \& M.
+J.
+Freitas (Eds.), \emph{Phonetics and phonology: Interactions and interrelations} (pp.
+137--158).
+Amsterdam: John Benjamins.
 

### 2020-12-29 RR_manuscript/Draft_RR.Rmd
use package cleveref
update sample size justification

@@
     number_sections: true
+header-includes:
+  - \usepackage{cleveref}
 ---
@@
 <!-- SC: rephrased and expanded -->
+<!-- TODO: include citation to ECO RR -->
 To identify the minimal sample size, we followed the method in [ECO RR].
-The aim of the meta-analysis is to obtain an estimate of heterogeneity ($\tau^2$) of the effect sizes reported by the analysis teams.
-Ideally, the 95% credible interval of $\tau^2$ should not include 0 (i.e.
-we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a *t*-statistic that would correspond to a *p*-value smaller than 0.05).
+The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
+the variance $\sigma^2_{\alpha_{\text{team}}}$, see \Cref{s:meta-est}).
+Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
+The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:
+
+$$t = \frac{\tau^2}{SE(\tau^2)}$$
+
 Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of $\tau^2$ can be calculated with the formula:
@@
 
-Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that *t* will be the same regardless of $\tau^2$:
+where $n$ is the sample size.
+Since we know $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
+Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
 
@@
 
-In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
-When $n = 12$ then $t_{12-1} = t_{11} = 2.3452$ and $p = 0.0388$.
-A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.
+In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CrI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
+When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which is below the 0.05 threshold, as required.
+In sum, a minimal sample of 12 effect sizes (i.e. of 12 analysis teams) would thus be sufficient to exclude 0 from the 95% CrI of $\tau^2$.
 
@@
 
-### Meta-analytical estimation
+### Meta-analytical estimation {#s:meta-est}
 

### 2020-12-29 RR_manuscript/Draft_RR.tex
update sample size justification

@@
 \usepackage{csquotes}
+\usepackage{cleveref}
 \ifxetex
@@
 To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
-The aim of the meta-analysis is to obtain an estimate of heterogeneity (\(\tau^2\)) of the effect sizes reported by the analysis teams.
-Ideally, the 95\% credible interval of \(\tau^2\) should not include 0 (i.e.~we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a \emph{t}-statistic that would correspond to a \emph{p}-value smaller than 0.05).
+The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{team}}}\), see \Cref{s:meta-est}).
+Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
+The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:
+
+\[t = \frac{\tau^2}{SE(\tau^2)}\]
+
 Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:
@@
 
-Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that \emph{t} will be the same regardless of \(\tau^2\):
+where \(n\) is the sample size.
+Since we know \(p\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
+Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that, when \(n\) is fixed, \emph{t} (and hence \(p\)) will be the same regardless of \(\tau^2\):
 
@@
 
-In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
-When \(n = 12\) then \(t_{12-1} = t_{11} = 2.3452\) and \(p = 0.0388\).
-A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.
+In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CrI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
+When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which is below the 0.05 threshold, as required.
+In sum, a minimal sample of 12 effect sizes (i.e.~of 12 analysis teams) would thus be sufficient to exclude 0 from the 95\% CrI of \(\tau^2\).
 
@@
 
-\hypertarget{meta-analytical-estimation}{%
-\subsubsection{Meta-analytical estimation}\label{meta-analytical-estimation}}
+\hypertarget{s:meta-est}{%
+\subsubsection{Meta-analytical estimation}\label{s:meta-est}}
 

### 2020-12-30 osf/comps/dataset/README.Rmd
use osfr to manage the OSF repo

---
title: "Dataset & Materials"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

# Overview

This directory contains 3 subdirectories: `Materials/`, `Raw data/`, and `TextGrids/`.
See the `README.md` files of each individual directory for more information about the contents.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp) %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2020-12-30 osf/comps/dataset/raw/README.Rmd
use osfr to manage the OSF repo

--- 2020-12-30 osf/comps/dataset/README.Rmd
@@
 ---
-title: "Dataset & Materials"
+title: "Raw data"
 output:
@@
 
-This directory contains 3 subdirectories: `Materials/`, `Raw data/`, and `TextGrids/`.
-See the `README.md` files of each individual directory for more information about the contents.
+This directory contains `.wav` files of the participants’ production from the experiment.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp) %>%
+osf_ls_files(data_comp, "Raw data") %>%
   select(name) %>%

### 2020-12-30 osf/comps/dataset/textgrids/README.Rmd
use osfr to manage the OSF repo

--- 2020-12-30 osf/comps/dataset/raw/README.Rmd
@@
 ---
-title: "Raw data"
+title: "TextGrids"
 output:
@@
 
-This directory contains `.wav` files of the participants’ production from the experiment.
+This directory contains Praat's `.TextGrid` files corresponding to the `.wav` files in `Raw data/`.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Raw data") %>%
+osf_ls_files(data_comp, "TextGrids") %>%
   select(name) %>%

### 2020-12-30 osf/manage-osf.Rmd
use osfr to manage the OSF repo

---
title: "OSF management"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

# Manage OSF with osfr

This document contains the code used to manage the OSF repo with the [osfr](https://docs.ropensci.org/osfr/) package.

# Retrieve OSF repo and components

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
```

# List data_comp files

```{r data_files}
osf_ls_files(data_comp)
```

# Knit readme files

We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting) by running `osf/knit-all.R`.

------
**NOTE**

For some reason I can't get this file to knit the other Rmd files when knitted (I get an error).
So for now we need to manually run the `osf/knit-all.R` script before uploading files to OSF.
I asked on StackOverflow how to fix this: <https://stackoverflow.com/q/65505119/2804314>.

------

# Upload files to the OFS repo

```{r readmes}
# A loop would be better
osf_upload(data_comp, path = "./osf/comps/dataset/README.md", conflicts = "overwrite", verbose = T)

data_comp_files <- osf_ls_files(data_comp)

materials <- data_comp_files %>% filter(name == "Materials")
osf_upload(materials, path = "./osf/comps/dataset/materials/README.md", conflicts = "overwrite", verbose = T)

raw <- data_comp_files %>% filter(name == "Raw data")
osf_upload(raw, path = "./osf/comps/dataset/raw/README.md", conflicts = "overwrite", verbose = T)

tgs <- data_comp_files %>% filter(name == "TextGrids")
osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)
```

### 2020-12-30 osf/knit-all.R

@@ -1,0 +1,3 @@
+files <- list.files("./osf/comps", pattern = "[.]Rmd$", recursive = T, full.names = T)
+for (f in files) rmarkdown::render(f, knit_root_dir = here::here(), output_format = "github_document", envir = new.env())
+

### 2020-12-31 osf/manage-osf.Rmd
:bug: - use xfun::Rscript_call() to knit all READMEs

@@
 
-We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting) by running `osf/knit-all.R`.
+We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting).
 
-------
-**NOTE**
+```{r knit-all, message=FALSE, warning=FALSE}
+files <- list.files("./osf/comps", pattern = "[.]Rmd$", recursive = T, full.names = T)
 
-For some reason I can't get this file to knit the other Rmd files when knitted (I get an error).
-So for now we need to manually run the `osf/knit-all.R` script before uploading files to OSF.
-I asked on StackOverflow how to fix this: <https://stackoverflow.com/q/65505119/2804314>.
-
-------
+for (f in files) {
+  xfun::Rscript_call(rmarkdown::render, list(f))
+}
+```
 
@@
 osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)
+
+osf_rm(osf_ls_files(data_comp, "Materials/Norming results", pattern = "README.md"), check = FALSE)
+osf_upload(osf_ls_files(data_comp, "Materials", type = "folder", pattern = "Norm"), path = "./osf/comps/dataset/materials/norming-results/README.md", conflicts = "overwrite", verbose = T)
+
+osf_rm(osf_ls_files(data_comp, "Materials/Trial lists", pattern = "README.md"), check = FALSE)
+osf_upload(osf_ls_files(data_comp, "Materials", type = "folder", pattern = "Trial lists"), path = "./osf/comps/dataset/materials/trials/README.md", conflicts = "overwrite", verbose = T)
 ```

### 2021-01-04 RR_manuscript/Draft_RR.Rmd
remove spurious sentence from ## Step 5
expand exploration variables list (closes #15)

@@
 - *Temporal window* that the measurement is taken over.
+- *Data exclusion*, whether data has been excluded or not.
 - *Demographic factors* of analysis teams and analysts.
@@
 2018).
+
 The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.
@@
 
-- ...
+- *Research experience* as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
+- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
 
@@
 We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
-
-We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions (such as statistical significance).
 

### 2021-01-04 RR_manuscript/Draft_RR.Rmd
some edits on introduction

--- 2020-12-28 RR_manuscript/Draft_RR.Rmd
@@
 classoption       : "man"
-output:
-  papaja::apa6_pdf:
-    number_sections: true
+output            : papaja::apa6_pdf
 ---
@@
 Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
-These researcher degrees of freedom are both a blessing and a curse at the same time.
+These researcher degrees of freedom are both a blessing and a curse.
 
@@
 2011).
-<!-- taken for granted?
--->
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g. Silberzahn et al. 2018, Starns et al. 2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.
+Silberzahn et al.
+2018, Starns et al.
+2019, Botvinik-Nezer et al., 2020).
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-
-We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations ("I knew it", Nickerson 1998), and perceiving events as being plausible in hindsight ("I knew it all along", Fischhoff 1975).
+Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ("I knew it", Nickerson 1998), and perceiving events as being plausible in hindsight ("I knew it all along", Fischhoff 1975).
 <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
@@
 Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa [@flake2019].
-<!-- TR:maybe give a concrete example, how such an interaction would look like for speech data?-->
-For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
-In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.
-
 To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
@@
 
-<!-- TR:(copy pasted from RDF paper and slightly shortened by myself. I think its a good point of departure. Maybe one of your can try to rephrase it in your own words?)-->
-<!-- SC: Edited and rephrased -->
+Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
+One major challenge in the speech sciences is the mapping between communicative intentions and their physical manifestation.
 
-<!-- TODO: RELEVANCE OF SPEECH PRODUCTION RESEARCH FOR COGSCI, AI, etc. -->
-
-<!-- TR: I added a transition sentence -->
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1:
 
@@
 
-"I hope Liz does not go to the grocery store tomorrow".
+(1) "I hope Liz does not go to the grocery store tomorrow".
 
@@
 <!-- TODO: mention speech domains -->
-Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
+Given the continuous and transient nature of speech, identifying  speech parameters and temporal domain becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
-The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.
+The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
 
-Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
-The acoustic signatures of one category are usually asynchronous, i.e.
-they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.
+<!-- TR: I changed features to parameters. Features is too close to phonological theory and will confuse some linguists, I believe. -->
+
+Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
+The acoustic parameters of one category are usually asynchronous, i.e.
+they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.
 Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
@@
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-The initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) (Hawkins & Nguyen, 2004).
-The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
+For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) (Hawkins & Nguyen, 2004).
+The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.
@@
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.
+Ladd 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation [@foulkes2006; @ogden2004; @white2009].
+The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2009; @white2009].
 
@@
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations. 
+For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on *tomorrow* and one of which emphasizes *grocery store*.
+
+(2a) "I hope Liz does not go to the grocery store TOMORROW".
+(2b) "I hope Liz does not go to the GROCERY STORE tomorrow"
+
+Do we only compare the word *tomorrow* in 2a and 2b or also the word *grocery store* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable? 
+Do we measure average the domain or do we measure a specific point in time?
+Do we measure fundamental frequency or intensity?
+When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes (see Figure x)
+
+<!-- TR: How about a plot like Figure 2 in my RDF paper: https://www.journal-labphon.org/articles/10.5334/labphon.147/ -->
+
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.
@@
 These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al.).
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided the analysis teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 
-<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN -->
+<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN + TRANSITION -->
 
@@
 Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+We will describe the variation in model specifications in several ways:
 
-### Descriptive statistics
-
-We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.
+First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.
 f0 or duration), the operationalization and the temporal domain of measurement (e.g.
-mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature and reasoning behind inferential assessments (e.g.
+mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature an reasoning behind inferential assessments (e.g.
 dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
@@
 
-<!-- TODO: ADD FORMULA of linear regression model -->
-FORMULA
+ADD FORMULA
 
-### Meta-analytical estimation
+Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).
 
-Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
-We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
-<!-- SC: it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
--->
-Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.
-*z*-scores) using a Bayesian multilevel model.
-The standardized effect size ($\eta_i$) of each analysis will be the estimated coefficient of the critical predictor (i.e.
-critical according to the analysis teams' self-reported inferential criteria).
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
-Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size ($\text{se}_i$).
-This will enable us to fit a so-called "measurement-error" model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
+We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
+First, we will derive standardized effect sizes from each individual analysis.
+Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
+Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.
+critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).
 
-After the extraction of the standardized effect sizes $\eta_i$ and related standard error $\text{se}_i$ for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
+<!-- In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.).
+We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where t stands for "total" variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components as formulated below:
+
+$$\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}$$
+Where $_i$ refers to the individual variance components.
+
+<!-- TR: Do we still need standardized effect sizes? to compare shit or are we just going to compare their estimates? -->
+
+<!-- TR: CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...
+RELEVANT: https://www.reddit.com/r/statistics/comments/fouwp9/q_effect_size_calculation_for_brms_delta_t/ -->
+
+<!-- JC:I THINK IT LOOKS GOOD (MAKES SENSE), THOUGH THIS IS ALSO A POSSIBILITY:
+
+$$\delta_t = \frac{\beta}{\sqrt{\sigma^2_{i} + ... \sigma^2_{k}}}$$-->
+
+Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:
 
 <!-- TR: need to change according to new process (not delta t anymore) -->
-<!-- SC: done! -->
 
@@
 \begin{aligned}
-\eta_i   & \sim \text{Normal}(\mu_i, \sigma_i) \\
-\mu_i     & = \alpha + \alpha_{\text{team}[i]} + \beta_n\\
-\alpha  & \sim \text{Normal}(0, 1) \\
-\beta_n & \sim \text{Normal}(0, 1) \\
-\sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
-\sigma_i  & = \text{se}_i
+\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
+\theta_i     & \sim \text{Normal} (\mu, \tau) \\
+\mu          & \sim \text{Normal} (0, 1) \\
+\tau         & \sim \text{HalfCauchy} (0, 1)
 \end{aligned}
@@
 
-The outcome variable will be the set of standardized effect sizes.
-The respective standard errors $\text{se}_i$ will be included to fit a measurement-error model.
-The likelihood of $\eta_i$ is assumed to be normally distributed (Knight 2000).
-The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+Effect size ($\delta_{t}$) will be the outcome variable.
+The likelihood of the outcome variable is assumed to be normally distributed.
+Analysis teams will be included as a group-level effect (i.e., random effect).
+For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+
 <!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
-<!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
+
+A cauchy prior set at 0 with scale 1 will be used for $\tau$.
 We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
-<!-- TODO: add link to code of the meta-analytical model -->
-The code for the model can be found here: INSERT LINK.
+The analysis will be conducted in R (R core team, 2020) and fit using `stan` (Stan, 2019) via the R package `brms` (Bürkner, 2019). The code for the model can be found here: INSERT LINK.
+We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) ... to be filled.
 
-<!-- TODO: list predictors in meta-analytical model -->
-We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
+As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the
 
-* The peer ratings of each analysis (numeric, 1-100).
-* ...
-
-<!-- From ?brms:brmsformula -->
-<!-- For families gaussian, student and skew_normal, it is possible to
-specify standard errors of the observations, thus allowing to perform
-meta-analysis. Suppose that the variable yi contains the effect sizes
-from the studies and sei the corresponding standard errors. Then,
-fixed and random effects meta-analyses can be conducted using the
-formulas yi | se(sei) ~ 1 and yi | se(sei) ~ 1 + (1|study),
-respectively, where study is a variable uniquely identifying every
-study. If desired, meta-regression can be performed via yi | se(sei) ~
-1 + mod1 + mod2 + (1|study) or  yi | se(sei) ~ 1 + mod1 + mod2 + (1 +
-mod1 + mod2|study), where mod1 and mod2 represent moderator variables.
-By default, the standard errors replace the parameter sigma. To model
-sigma in addition to the known standard errors, set argument sigma in
-function se to TRUE, for instance, yi | se(sei, sigma = TRUE) ~ 1. -->
-
-### Exploratory road map
-<!-- SC: change heading to your liking -->
-
-As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference ($\delta_i$) between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
 <!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.
@@
 -->
+
 <!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
 That gives you both the distance to the meta analytical estimate and the direction of that difference -->
-<!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
-These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
+
+These analyses are secondary to our estimation of variation in effect sizes described above.
 We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
-We will model the effect of the following predictors:
 
-- *Measure of uniqueness* of individual analyses for the set of predictors in each model.
-- *Measure of conservativeness* of the model specification.
-- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out.
-- *Number of models* the teams will report to have run.
-- *Major dimension* that has been measured to answer the research question.
-- *Temporal window* that the measurement is taken over.
-- *Demographic factors* of analysis teams and analysts.
+The following predictors will be used:
 
-The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
-The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat predictors as species and individual analyses as sites.
-The SDI for a pair of analyses $(X, Y)$ can be obtained using the following formula:
+First, we include a measure of the ‘uniqueness’ of individual analyses for
+- the set of predictor parameters,
+- the set of random effect parameters,
+- the acoustic measurement.
 
-<!-- SC: refactored the formula so it is closer to the original source -->
+The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI).
+The SSI is an index typically used in ecology research to compare species composition across sites.
+For our purposes, we will treat variables as species and individual analyses as sites.
+In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al. 2018) in R.
+We achieve this using the following formula:
 
-$$\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}$$
+$$\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}$$
 
-where $|X \cap Y|$ is the number of variables common to both models, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
+where $a$ is the number of variables common to both models, $b$ is the number of variables that occur in the first model but not in the second and $c$ is the number of variables that occur in the second model but not in the first.
 
-```{r sdi, eval=FALSE, include=FALSE}
-x <- c("a", "b", "c", "d")
-y <- c("b", "d", "e", "f")
-(2 * length(intersect(x,y))) / (length(x) + length(y))
-```
+Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package (Baselga et al.
-2018).
-The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.
-frequency center of gravity, harmonics difference, etc.), other measures (e.g.
-principal components, vowel dispersion, etc.)
+Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.
+
+Forth, we include the major acoustic dimension that has been measured to answer the research question.
+We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties
+
 <!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
-<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
-The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: segment, syllable, word, phrase.
 
-We will include the following demographic factors about both the analysis teams:
+Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.
 
+Sixth, we include the following demographic factors about both the analysis teams:
 - ...
 
-<!-- TODO: DESCRIBE HOW WE WILL LOOK AT demographics -->
+DESCRIBE HOW WE WILL LOOK AT THESE THINGS
 
-We will publicly archive all relevant data, code, and materials on the Open Science Framework (<https://osf.io/3bmcp/>).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
+We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2021-01-04 RR_manuscript/Draft_RR.tex
include paragraph on funnel plots in section 2.4.2

@@
 
-\hypertarget{methods-mostly-copy-paste-from-evo-rr}{%
-\section{Methods (mostly copy-paste from Evo-RR)}\label{methods-mostly-copy-paste-from-evo-rr}}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
+Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
+This will be achieved through inspection of funnel plots (Light \& Pillemer, 1984; for a review see Egger, Smith, Schneider, \& Minder, 1997; and Sterne, Becker, \& Egger, 2005; for a critique Lau, Ioannidis, Terrin, Schmid, \& Olkin, 2006).
+In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the \emph{x}-axis and estimated error (i.e.~standard deviation) on \emph{y}-axis.
+In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \ref{fig:funnel-plot}).
+A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.
+
+\begin{figure}
+\centering
+\includegraphics{Draft_RR_files/figure-latex/funnel-plot-1.pdf}
+\caption{\label{fig:funnel-plot}Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
+The vertical dashed line represents the meta-analitical mean.}
+\end{figure}
+
 \hypertarget{exploratory-road-map}{%
@@
 \item
+  \emph{Data exclusion}, whether data has been excluded or not.
+\item
   \emph{Demographic factors} of analysis teams and analysts.
@@
 In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).
+
 The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
@@
 \item
-  \ldots{}
+  \emph{Research experience} as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
+\item
+  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-egger1997}{}%
+Egger, M., Smith, G. D., Schneider, M., \& Minder, C. (1997). Bias in meta-analysis detected by a simple, graphical test. \emph{British Medical Journal}, \emph{315}, 629--634.
+
 \leavevmode\hypertarget{ref-flake2019}{}%
@@
 
+\leavevmode\hypertarget{ref-lau2006}{}%
+Lau, J., Ioannidis, J. P. A., Terrin, N., Schmid, C. H., \& Olkin, I. (2006). The case of the misleading funnel plot. \emph{British Medical Journal}, \emph{333}(7568), 597--600.
+
+\leavevmode\hypertarget{ref-light1984}{}%
+Light, R. J., \& Pillemer, D. B. (1984). \emph{Summing up; the science of reviewing research}. Cambridge, MA (USA) Harvard Univ. Press.
+
 \leavevmode\hypertarget{ref-ogden2004}{}%
@@
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-sterne2005}{}%
+Sterne, J.
+A.
+C., Becker, B.
+J., \& Egger, M.
+(2005).
+The funnel plot.
+In H.
+R.
+Rothstein, A.
+J.
+Sutton, \& M.
+Borenstein (Eds.), \emph{Publication bias in meta-analysis: Prevention, assessment and adjustments} (pp.
+75--98).
+Wiley Online Library.
 

### 2021-01-04 RR_manuscript/Draft_RR.Rmd
include paragraph on funnel plots in section 2.4.2

--- 2021-01-04 RR_manuscript/Draft_RR.Rmd
@@
 r_refs("r-references.bib")
+library(tidyverse)
+library(patchwork)
 ```
@@
 
-# Methods (mostly copy-paste from Evo-RR)
+# Methods
 
@@
 
+Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
+This will be achieved through inspection of funnel plots [@light1984; for a review see @egger1997; and @sterne2005; for a critique @lau2006].
+In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the *x*-axis and estimated error (i.e. standard deviation) on *y*-axis.
+In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \@ref(fig:funnel-plot)).
+A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.
+
+```{r funnel-plot, include=TRUE, fig.cap="Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
+The vertical dashed line represents the meta-analitical mean.", fig.dim = c(6, 2)}
+meta_est <- 0
+
+datasets <- map(
+  c(0, 0.1, -0.1),
+  function(.x) {
+    set.seed(101)
+    sd <- runif(100, min = 1, max = 10)
+    est <- rnorm(length(sd), mean = meta_est, sd = 0.1*sd) + .x * sd
+    tibble(est, sd)
+  }
+)
+
+plots <- map(
+  datasets,
+  function(.x) {
+    ggplot(.x, aes(est, sd)) +
+      geom_vline(aes(xintercept = meta_est), linetype = "dashed") +
+      geom_point(colour = "black", size = 1, alpha = 0.5) +
+      scale_y_reverse() +
+      labs(est = element_blank(), sd = element_blank())  +
+      xlim(-3, 3) +
+      theme_minimal()
+  }
+)
+
+plots[[1]] + labs(title = "(a) no bias") +
+  plots[[2]] + labs(title = "(b) positive bias") +
+  plots[[3]] + labs(title = "(c) negative bias")
+```
+
+```{r funnel-calc, include=FALSE, eval=FALSE}
+# meta_bm is the meta-analytical Bayesian regression model
+meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"
+meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
+meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]
+
+# estimated_tbl contains the standardized effect sizes
+se_range <- seq(0, max(estimated_tbl$Est.Error), by = 0.001)
+
+ci <- tibble(
+  x_seq = se_range,
+  ci_lo = meta_ln_bm_est - 1.96 * se_range,
+  ci_up = meta_ln_bm_est + 1.96 * se_range
+)
+
+estimated_tbl %>%
+  ggplot(aes(Estimate, Est.Error)) +
+  geom_line(aes(y = x_seq, x = ci_up), data = ci) +
+  geom_line(aes(y = x_seq, x = ci_lo), data = ci) +
+  geom_vline(aes(xintercept = 0), colour = "grey") +
+  geom_vline(aes(xintercept = meta_ln_bm_est)) +
+  annotate(
+    "rect",
+    ymin = -Inf, ymax = Inf,
+    xmin = meta_bm_q2.5, xmax = meta_bm_q97.5,
+    alpha = 0.5, fill = "#a6cee3") +
+  geom_point(size = 3) +
+  scale_y_reverse()
+```
+
 ### Exploratory road map

### 2021-01-05 RR_manuscript/Draft_RR.Rmd
update todos; remove trailing ws

@@
 
-SUM UP:
-Neuroscience
-Cognitive modeling
-Clinical
-Predictive models
+<!-- TODO: SUMUP neuroscience, cognitive modeling, clinical, predictive models -->
 
@@
 If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
-<!-- TODO: mention speech domains -->
-Given the continuous and transient nature of speech, identifying  speech parameters and temporal domain becomes a non-trivial task.
+Given the continuous and transient nature of speech, identifying speech parameters and temporal domains becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 
-<!-- TODO: include materials link and mailing lists -->
+<!-- TODO: add materials link and mailing lists -->
 The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
@@
 <!-- SC: rephrased and expanded -->
-<!-- TODO: include citation to ECO RR -->
+<!-- TODO: add citation to ECO RR -->
 To identify the minimal sample size, we followed the method in [ECO RR].
@@
 
-<!-- TODO: ADD FORMULA of linear regression model -->
+<!-- TODO: ADD FORMULA of linear regression model to express majority of analysis -->
 FORMULA
@@
 
-<!-- TODO: DESCRIBE HOW WE WILL LOOK AT demographics -->
-
 We will publicly archive all relevant data, code, and materials on the Open Science Framework (<https://osf.io/3bmcp/>).

### 2021-01-05 RR_manuscript/Draft_RR.Rmd
update notes

@@
 We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
-<!-- SC: it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
+<!-- NOTE: (SC) it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
 -->

### 2021-01-05 osf/knit-all.R
update renv packages; delete unused R file

@@ -1,3 +1,0 @@
-files <- list.files("./osf/comps", pattern = "[.]Rmd$", recursive = T, full.names = T)
-for (f in files) rmarkdown::render(f, knit_root_dir = here::here(), output_format = "github_document", envir = new.env())
-

### 2021-01-05 osf/comps/data/exp-materials/README.Rmd
restructure osf/comps folder to reflect changes in OSF repo

--- 2020-12-30 osf/comps/dataset/raw/README.Rmd
@@
 ---
-title: "Raw data"
+title: "Materials"
 output:
@@
 
-This directory contains `.wav` files of the participants’ production from the experiment.
+This directory contains the images, trial lists, and the results from the norming study.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Raw data") %>%
+osf_ls_files(data_comp, "Materials") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
restructure osf/comps folder to reflect changes in OSF repo

--- 2020-12-30 osf/comps/dataset/raw/README.Rmd
@@
 ---
-title: "Raw data"
+title: "Norming results"
 output:
@@
 
-This directory contains `.wav` files of the participants’ production from the experiment.
+This directory contains the results from the norming study.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Raw data") %>%
+osf_ls_files(data_comp, "Materials/Norming results") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/exp-materials/norming/README.Rmd
restructure osf/comps folder to reflect changes in OSF repo

--- 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
@@
 ---
-title: "Norming results"
+title: "Trial lists"
 output:
@@
 
-This directory contains the results from the norming study.
+This directory contains `.csv` files of the trial lists from the norming study.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Materials/Norming results") %>%
+osf_ls_files(data_comp, "Materials/Trial lists") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/data/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

---
title: "Data"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

# Overview

This directory contains the files from the production experiment:

- `.wav` files with the participants' recordings (one file per participant).
- `.TextGrid` (Praat) files with time-aligned annotation of the recordings (one file per participant, same names as `.wav`).

<!-- TODO: ADD more info on annotation -->

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=FALSE}
osf_ls_files(data_comp, "data") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/comps/data/exp-materials/norming/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

--- 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
@@
 ---
-title: "Norming results"
+title: "Norming study"
 output:
@@
 
-This directory contains the results from the norming study.
+This directory contains the `images/` used in the norming study and the `results/` of the study (i.e. the typicality ratings for each image/object for each participant).
 
@@
 # Dataset & Materials component
-data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
+data_comp <- osf_comps %>% filter(name == "Data")
 ```
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Materials/Norming results") %>%
+osf_ls_files(data_comp, "exp-materials/norming") %>%
   select(name) %>%

### 2021-01-05 osf/manage-osf.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

--- 2020-12-30 osf/manage-osf.Rmd
@@
 
-We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting) by running `osf/knit-all.R`.
+We can knit the readme files (they are GitHub documents, i.e. `.Rmd` files that are converted to `.md` files upon knitting).
 
-------
-**NOTE**
+```{r knit-all, message=FALSE, warning=FALSE}
+files <- list.files("./osf/comps/data", pattern = "[.]Rmd$", recursive = T, full.names = T)
 
-For some reason I can't get this file to knit the other Rmd files when knitted (I get an error).
-So for now we need to manually run the `osf/knit-all.R` script before uploading files to OSF.
-I asked on StackOverflow how to fix this: <https://stackoverflow.com/q/65505119/2804314>.
-
-------
+for (f in files) {
+  xfun::Rscript_call(rmarkdown::render, list(f))
+}
+```
 
@@
 # A loop would be better
-osf_upload(data_comp, path = "./osf/comps/dataset/README.md", conflicts = "overwrite", verbose = T)
+osf_upload(data_comp, path = "./osf/comps/data/README.md", conflicts = "overwrite", verbose = T)
 
@@
 
-materials <- data_comp_files %>% filter(name == "Materials")
-osf_upload(materials, path = "./osf/comps/dataset/materials/README.md", conflicts = "overwrite", verbose = T)
+# data/data
+raw <- data_comp_files %>% filter(name == "data")
 
-raw <- data_comp_files %>% filter(name == "Raw data")
-osf_upload(raw, path = "./osf/comps/dataset/raw/README.md", conflicts = "overwrite", verbose = T)
+osf_rm(osf_ls_files(data_comp, "data", pattern = "README.md"), check = FALSE)
+osf_upload(raw, path = "./osf/comps/data/data/README.md", conflicts = "overwrite", verbose = T)
 
-tgs <- data_comp_files %>% filter(name == "TextGrids")
-osf_upload(tgs, path = "./osf/comps/dataset/textgrids/README.md", conflicts = "overwrite", verbose = T)
+# data/exp-materials
+materials <- data_comp_files %>% filter(name == "exp-materials")
+
+osf_rm(osf_ls_files(data_comp, "exp-materials", pattern = "README.md"), check = FALSE)
+osf_upload(materials, path = "./osf/comps/data/exp-materials/README.md", conflicts = "overwrite", verbose = T)
+
+# data/exp-materials/norming
+osf_rm(osf_ls_files(data_comp, "exp-materials/norming", pattern = "README.md"), check = FALSE)
+osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "norming"), path = "./osf/comps/data/exp-materials/norming/README.md", conflicts = "overwrite", verbose = T)
+
+# data/exp-materials/experiment
+osf_rm(osf_ls_files(data_comp, "exp-materials/experiment", pattern = "README.md"), check = FALSE)
+osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "experiment"), path = "./osf/comps/data/exp-materials/experiment/README.md", conflicts = "overwrite", verbose = T)
 ```

### 2021-01-05 osf/comps/data/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

--- 2020-12-30 osf/comps/dataset/README.Rmd
@@
 
-This directory contains 3 subdirectories: `Materials/`, `Raw data/`, and `TextGrids/`.
+This directory contains 2 subdirectories: `exp-materials/` and `data/`.
+
+Files and results of the norming study are in `exp-materials/`
+The `data` directory hosts the `.wav` and `.TextGrid` files from the production experiment.
 See the `README.md` files of each individual directory for more information about the contents.

### 2021-01-05 osf/comps/data/exp-materials/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

--- 2020-12-30 osf/comps/dataset/raw/README.Rmd
@@
 ---
-title: "Raw data"
+title: "Experiment materials"
 output:
@@
 
-This directory contains `.wav` files of the participants’ production from the experiment.
+This directory contains the files used for the norming study and for the production experiment:
+
+- The `norming/` directory hosts the images of the objects with modified color used in the norming study and the results (ratings) of the study.
+- The `experiment/` directory contains the randomization lists for each participant in the production study.
 
@@
 ```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Raw data") %>%
+osf_ls_files(data_comp, "exp-materials") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo

@@
 ---
-title: "Norming results"
+title: "Production experiment"
 output:
@@
 
-This directory contains the results from the norming study.
+This directory contains one `.csv` file per participant from the production experiment with information about the trials (one row per trial).
+
+The files include the following columns:
+
+- `condition`: The condition of the trial (`NF` = noun focus, `AF` = adjective focus, `ANF` = adjective/noun focus).
+- `target_name`: Name of the target object.
+- `target_colour`: Color of the target object.
+- `competitor_name`: Name of the competitor object.
+- `competitor_colour`: Color of the competitor object.
+- `distractor1_name`: Name of the distractor 1.
+- `distractor1_colour`: Color of the distractor 1.
+- `distractor2_name`: Name of the distractor 2.
+- `distractor2_colour`: Color of the distractor 2.
 
@@
 # Dataset & Materials component
-data_comp <- osf_comps %>% filter(name == "Dataset & Materials")
+data_comp <- osf_comps %>% filter(name == "Data")
 ```
 
-```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "Materials/Norming results") %>%
+```{r data_files, include=FALSE}
+osf_ls_files(data_comp, "exp-materials/experiment") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/norming/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

---
title: "Norming study"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

# Overview

This directory contains the files of the norming study, designed to obtain typicality ratings of re-colored images of everyday objects.

There are 2 subdirectories:

- The `images/` directory contains the re-colored images used in the norming study.
- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.

The `tipicality.csv` file has the following columns:

- `prolific id`: The participant/trial id.
- `object`: The name of the object represented in the image.
- `typicality`: The typicality rating (numeric, `1-100`, `1` = most atypical, `100` = most typical).
- `colour`: The color of the object in the image.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "norming") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

### 2021-01-05 osf/comps/data/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

@@
 ---
-title: "Dataset & Materials"
+title: "Data component"
 output:
@@
 
-This directory contains 2 subdirectories: `exp-materials/` and `data/`.
+This component hosts the data of the *Many Speech Analyses* project.
+For an overview, see the [wiki](https://osf.io/rdtx5/wiki/home/).
 
-Files and results of the norming study are in `exp-materials/`
-The `data` directory hosts the `.wav` and `.TextGrid` files from the production experiment.
+There are 2 subdirectories:
+
+- The `norming/` directory holds the files of the norming study.
+- The `production/` directory contains the `.wav` and `.TextGrid` files from the production experiment.
+
 See the `README.md` files of each individual directory for more information about the contents.

### 2021-01-05 osf/comps/data/production/audio/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

--- 2021-01-05 osf/comps/data/data/README.Rmd
@@
 ---
-title: "Data"
+title: "Audio and annotation files of the production study"
 output:
@@
 
-This directory contains the files from the production experiment:
+This directory contains the files from the production study:
 
@@
 ```{r data_files, include=FALSE}
-osf_ls_files(data_comp, "data") %>%
+osf_ls_files(data_comp, "production/audio") %>%
   select(name) %>%

### 2021-01-05 osf/comps/data/production/trial-lists/README.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

--- 2021-01-05 osf/comps/data/exp-materials/experiment/README.Rmd
@@
 ---
-title: "Production experiment"
+title: "Trial lists of the production study"
 output:
@@
 ```{r data_files, include=FALSE}
-osf_ls_files(data_comp, "exp-materials/experiment") %>%
+osf_ls_files(data_comp, "production/trial-lists") %>%
   select(name) %>%

### 2021-01-05 osf/manage-osf.Rmd
update osf/manage-osf.Rmd to reflect restructuring in OSF repo: take 2

@@
 
-# data/data
-raw <- data_comp_files %>% filter(name == "data")
+# data/norming/
+raw <- data_comp_files %>% filter(name == "norming")
 
-osf_rm(osf_ls_files(data_comp, "data", pattern = "README.md"), check = FALSE)
-osf_upload(raw, path = "./osf/comps/data/data/README.md", conflicts = "overwrite", verbose = T)
+#### delete old readme ("overwrite" option fails)
+old_readme <- osf_ls_files(data_comp, "norming", pattern = "README.md")
+osf_rm(old_readme, check = FALSE)
 
-# data/exp-materials
-materials <- data_comp_files %>% filter(name == "exp-materials")
+#### upload new readme
+osf_upload(
+  raw,
+  path = "./osf/comps/data/norming/README.md",
+  conflicts = "overwrite", verbose = T)
 
-osf_rm(osf_ls_files(data_comp, "exp-materials", pattern = "README.md"), check = FALSE)
-osf_upload(materials, path = "./osf/comps/data/exp-materials/README.md", conflicts = "overwrite", verbose = T)
+# data/production/audio/
+#### delete old readme
+old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
+osf_rm(old_readme, check = FALSE)
 
-# data/exp-materials/norming
-osf_rm(osf_ls_files(data_comp, "exp-materials/norming", pattern = "README.md"), check = FALSE)
-osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "norming"), path = "./osf/comps/data/exp-materials/norming/README.md", conflicts = "overwrite", verbose = T)
+#### upload new readme
+audio <- osf_ls_files(data_comp, "production", pattern = "audio")
+osf_upload(
+  audio,
+  path = "./osf/comps/data/production/audio/README.md",
+  conflicts = "overwrite", verbose = T)
 
-# data/exp-materials/experiment
-osf_rm(osf_ls_files(data_comp, "exp-materials/experiment", pattern = "README.md"), check = FALSE)
-osf_upload(osf_ls_files(data_comp, "exp-materials", pattern = "experiment"), path = "./osf/comps/data/exp-materials/experiment/README.md", conflicts = "overwrite", verbose = T)
+# data/production/trial-lists
+#### delete old readme
+old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
+osf_rm(old_readme, check = FALSE)
+
+#### upload new readme
+trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
+osf_upload(
+  trials,
+  path = "./osf/comps/data/production/trial-lists/README.md",
+  conflicts = "overwrite", verbose = T)
 ```

### 2021-01-08 RR_manuscript/Draft_RR.Rmd
changed example

@@
 
-(1) "I hope Liz does not go to the grocery store tomorrow".
+(1) "I can't bear another meeting on zoom."
 
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow.
-If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word "another" or "meeting".
+If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word "zoom".
 
@@
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on *tomorrow* and one of which emphasizes *grocery store*.
+For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.
 
-(2a) "I hope Liz does not go to the grocery store TOMORROW".
-(2b) "I hope Liz does not go to the GROCERY STORE tomorrow"
+(2a) "I can't bear ANOTHER meeting on zoom."
+(2b) "I can't bear another meeting on ZOOM."
 
-Do we only compare the word *tomorrow* in 2a and 2b or also the word *grocery store* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
+Do we only compare the word *another* in 2a and 2b or also the word *zoom* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
 Do we measure average the domain or do we measure a specific point in time?

### 2021-01-12 RR_manuscript/Draft_RR.Rmd
:memo: - update description of the meta-analytical model plus minor edits

@@
 
-floatsintext      : no
+floatsintext      : yes
 figurelist        : no
@@
     number_sections: true
+    latex_engine: xelatex
 header-includes:
@@
 ```{r setup, include = FALSE}
+knitr::opts_knit$set(root.dir = here::here())
 library("papaja")
@@
 
+In text ref to Figure \@ref(fig:forkingPaths)
+
+(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
+(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
+
+```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
+
+knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
+
+```
+
+<!-- TR: Insertion does not work yet, gotta dash. Also the following paragraph is just a draft for now -->
+
 Do we only compare the word *another* in 2a and 2b or also the word *zoom* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
-Do we measure average the domain or do we measure a specific point in time?
+Do we average the domain or do we measure a specific point in time?
 Do we measure fundamental frequency or intensity?
-When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes (see Figure x)
-
-<!-- TR: How about a plot like Figure 2 in my RDF paper: https://www.journal-labphon.org/articles/10.5334/labphon.147/ -->
+When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
+This plurality of analytical paths is illustrated in figure X.
+When comparing two utterance such as 2a and 2b, there are many things to consider.
+Even if we know that we want to compare fundamental frequency of only the word *another* across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
+Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+And the garden of forking paths does not stop here.
+In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
+Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
 
@@
 
-We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.
-f0 or duration), the operationalization and the temporal domain of measurement (e.g.
-mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects [if applicable], the nature and reasoning behind inferential assessments (e.g.
-dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
-We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
-
-<!-- TODO: ADD FORMULA of linear regression model to express majority of analysis -->
-FORMULA
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.
+f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.
+mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects [if applicable], (d) the nature and reasoning behind inferential assessments (e.g.
+dichotomous decision based on *p*-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
 
@@
 
-Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
-We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
 <!-- NOTE: (SC) it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
 -->
-Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.
-*z*-scores) using a Bayesian multilevel model.
-The standardized effect size ($\eta_i$) of each analysis will be the estimated coefficient of the critical predictor (i.e.
-critical according to the analysis teams' self-reported inferential criteria).
+<!-- NOTE: (SC) shouldn't we standardise all variables? -->
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables [???].
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017] in R [@r-core-team2020].
+For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
+If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
+
+The estimated coefficients of the critical predictors (i.e.
+critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
-Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size ($\text{se}_i$).
-This will enable us to fit a so-called "measurement-error" model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
+This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the the meta-analytical model.
+As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
 
-After the extraction of the standardized effect sizes $\eta_i$ and related standard error $\text{se}_i$ for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
-
-<!-- TR: need to change according to new process (not delta t anymore) -->
-<!-- SC: done! -->
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel regression model:
 
@@
 \eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
-\mu_i     & = \alpha + \alpha_{\text{team}[i]} + \beta_n\\
+\mu_i       & = \alpha + \alpha_{\text{team}[i]} \\
 \alpha      & \sim \text{Normal}(0, 1) \\
-\beta_n & \sim \text{Normal}(0, 1) \\
 \sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
@@
 
-The outcome variable will be the set of standardized effect sizes.
-The respective standard errors $\text{se}_i$ will be included to fit a measurement-error model.
-The likelihood of $\eta_i$ is assumed to be normally distributed (Knight 2000).
-The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+The outcome variable will be the set of standardized effect sizes $\eta_i$.
+The likelihood of $\eta_i$ is assumed to correspond to a normal distribution (Knight 2000).
+The analysis teams will constitute the group-level effect (i.e., random effect, `(1 | team)`).
+The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
+We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{team}[i]}$ ($HalfCauchy(0, 1)$).
 <!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
 <!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
-We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+<!-- NOTE: (SC) we might not include pop-level parameters. -->
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling of the posterior distribution and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+The analysis will be conducted in R [@r-core-team2020] and fit using Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017].
 <!-- TODO: add link to code of the meta-analytical model -->
-The code for the model can be found here: INSERT LINK.
-
-<!-- TODO: list predictors in meta-analytical model -->
-We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
-
-* The peer ratings of each analysis (numeric, 1-100).
-* ...
+The code used to run the model can be found here: INSERT LINK.
 
@@
 function se to TRUE, for instance, yi | se(sei, sigma = TRUE) ~ 1. -->
+
+<!-- TODO: explain how the MA model will be interpreted. -->
 
@@
 
-### Exploratory road map
-<!-- SC: change heading to your liking -->
+### Analytical factors affecting effect sizes
 
-As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference ($\delta_i$) between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
+As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below).
+The deviation score $\delta_i$, which serves as the dependent variable in this analysis, will be the difference between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
 <!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.

### 2021-01-14 RR_manuscript/Draft_RR.Rmd
inserted graph (needs fixing)

--- 2021-01-08 RR_manuscript/Draft_RR.Rmd
@@
 
+```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses.
+(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}
+
+knitr::include_graphics("/RR_manuscript/Draft_RR_files/figure-latex/ForkingPaths.png")
+
+```
+
+<!-- TR: Insertion does not work yet, gotta dash. Also the following paragraph is just a draft for now -->
+
 Do we only compare the word *another* in 2a and 2b or also the word *zoom* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
-Do we measure average the domain or do we measure a specific point in time?
+Do we average the domain or do we measure a specific point in time?
 Do we measure fundamental frequency or intensity?
-When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes (see Figure x)
-
-<!-- TR: How about a plot like Figure 2 in my RDF paper: https://www.journal-labphon.org/articles/10.5334/labphon.147/ -->
+When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
+This plurality of analytical paths is illustrated in figure X.
+When comparing two utterance such as 2a and 2b, there are many things to consider.
+Even if we know that we want to compare fundamental frequency of only the word *another* across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
+Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+And the garden of forking paths does not stop here.
+In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
+Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
 

### 2021-01-16 RR_manuscript/Draft_RR.Rmd
:construction: - begin fixing error from figure (WIP)

@@
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}
+The words \"another is highlighted by the green box\"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}
 
-knitr::include_graphics("/RR_manuscript/Draft_RR_files/figure-latex/ForkingPaths.png")
+knitr::include_graphics("./RR_manuscript/img/ForkingPaths.png")
 

### 2021-01-16 RR_manuscript/Draft_RR.Rmd
:construction: - move figure to figs/ (WIP)
update fig error

@@
 
-```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses.
+In text ref to Figure \@ref(fig:forkingPaths)
+
+(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words \"another is highlighted by the green box\"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}
+The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
 
-knitr::include_graphics("./RR_manuscript/img/ForkingPaths.png")
+```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
+
+knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
 

### 2021-01-16 RR_manuscript/Draft_RR.tex
update fig error

@@
   english,
-  man]{apa6}
-\usepackage{amsmath,amssymb}
+  man,floatsintext]{apa6}
 \usepackage{lmodern}
+\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
 \usepackage{lineno}
@@
 \else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
+  \usepackage[shorthands=off,main=english]{babel}
 \fi
-\ifluatex
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration, 2015; Camerer et al., 2018) leading to what is now referred to as the \emph{replication crisis}.
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
@@
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, what models to use or what inferential decision procedure to apply.
+Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
 However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-
-We have evolved to filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing ourselves of the validity of prior expectations (``I knew it,'' Nickerson 1998), and perceiving events as being plausible in hindsight (``I knew it all along,'' Fischhoff 1975).
+Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 
-SUM UP:
-Neuroscience
-Cognitive modeling
-Clinical
-Predictive models
-
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
@@
 Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
-For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
-In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.
-
 To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
@@
 
+Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
+One major challenge in the speech sciences is the mapping between communicative intentions and their physical manifestation.
+
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure the phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence:
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1:
 
-``I hope Liz does not go to the grocery store tomorrow.''
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\tightlist
+\item
+  \enquote{I can't bear another meeting on zoom.}
+\end{enumerate}
 
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is worried about Liz mistakenly going to the grocery store tomorrow instead of today, the speaker might acoustically highlight the word tomorrow.
-If, on the other hand, the speaker is worried that Liz goes to a crowded place like the supermarket, they might acoustically highlight the word grocery store.
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \enquote{another} or \enquote{meeting}.
+If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word \enquote{zoom}.
 
 If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
-Given the continuous and transient nature of speech, identifying which speech features should be selected within which temporal domain becomes a non-trivial task.
+Given the continuous and transient nature of speech, identifying speech parameters and temporal domains becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
-The researcher is thus confronted with a considerable number of features and combinations thereof to choose from.
+The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
 
-Speech categories are inherently multidimensional and dynamic: they consist of a cluster of features that are modulated over time.
-The acoustic signatures of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with the signatures of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
+Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-The initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
-The multiplicity of phonetic cues grows exponentially if we look at larger temporal windows as is the case for suprasegmental aspects of speech.
+For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
+The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.~Ladd 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
+The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch ({\textbf{???}}; Foulkes \& Docherty, 2006; White, Payne, \& Mattys, 2009).
 
@@
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
+For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{zoom}.
+
+(2a) \enquote{I can't bear ANOTHER meeting on zoom.}
+(2b) \enquote{I can't bear another meeting on ZOOM.}
+
+In text ref to Figure \ref{fig:forkingPaths}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/casillas/academia/research/in_progress/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
+(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
+\end{figure}
+
+Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
+Do we average the domain or do we measure a specific point in time?
+Do we measure fundamental frequency or intensity?
+When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
+This plurality of analytical paths is illustrated in figure X.
+When comparing two utterance such as 2a and 2b, there are many things to consider.
+Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
+Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+And the garden of forking paths does not stop here.
+In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
+Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
+
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
 These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided the analysis teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
 
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''
+For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.
 
@@
 
-\noindent ``Please explain your ratings of this analysis.
+\noindent \enquote{Please explain your ratings of this analysis.
 \noindent Please evaluate the selection of acoustic features.
@@
 \noindent Please evaluate choices to exclude or not exclude subsets of the data.
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).}
 
@@
 After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
-The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''
+The invitation to revise the original ratings will be as follows: \enquote{If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.}
+The text box will be prefaced with this prompt: \enquote{Please explain your choice to revise (or not to revise) your ratings.}
 
@@
 Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size (\(\text{se}_i\)).
-This will enable us to fit a so-called ``measurement-error'' model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
+This will enable us to fit a so-called \enquote{measurement-error} model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
@@
 
-\leavevmode\hypertarget{ref-ogden2004}{}%
-Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
-
 \leavevmode\hypertarget{ref-open2015estimating}{}%
@@
 (1948).
-A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on {D}anish commons.
+A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on Danish commons.
 \emph{Kongelige Danske Videnskabernes Selskab}, \emph{5}(4), 1--34.
@@
 (2009).
-Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian.
+Rhythmic and prosodic contrast in Venetan and Sicilian Italian.
 In M.
@@
 
-\end{CSLReferences}
-
 \endgroup

### 2021-01-18 RR_manuscript/Draft_RR.Rmd
:memo: edit step 4 section
I have updated info on brms related settings, added a description of how we will interpret the meta-analytical posteriors, made edits in the section about the analytical and demo factors analysis.

@@
   - \usepackage{cleveref}
+  - \usepackage{changes}
+  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
+  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
+  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 ---
@@
 
-Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
-We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
 <!-- NOTE: (SC) it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
 -->
-Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.
-*z*-scores) using a Bayesian multilevel model.
-The standardized effect size ($\eta_i$) of each analysis will be the estimated coefficient of the critical predictor (i.e.
-critical according to the analysis teams' self-reported inferential criteria).
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017] in R [@r-core-team2020].
+For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
+If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
+
+The estimated coefficients of the critical predictors (i.e.
+critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
-Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size ($\text{se}_i$).
-This will enable us to fit a so-called "measurement-error" model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
+This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the the meta-analytical model.
+As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
 
-After the extraction of the standardized effect sizes $\eta_i$ and related standard error $\text{se}_i$ for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
-
-<!-- TR: need to change according to new process (not delta t anymore) -->
-<!-- SC: done! -->
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
 
@@
 
-The outcome variable will be the set of standardized effect sizes.
-The respective standard errors $\text{se}_i$ will be included to fit a measurement-error model.
-The likelihood of $\eta_i$ is assumed to be normally distributed (Knight 2000).
-The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+The outcome variable will be the set of standardized effect sizes $\eta_i$.
+The likelihood of $\eta_i$ is assumed to correspond to a normal distribution (Knight 2000).
+The analysis teams will constitute the group-level effect (i.e., random effect, `(1 | team)`).
+The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
+We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{team}[i]}$ ($HalfCauchy(0, 1)$).
 <!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
 <!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
-We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there are no divergent transitions.
+The analysis will be conducted in R [@r-core-team2020] and fit using Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017].
 <!-- TODO: add link to code of the meta-analytical model -->
-The code for the model can be found here: INSERT LINK.
-
-<!-- TODO: list predictors in meta-analytical model -->
-We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
-
-* The peer ratings of each analysis (numeric, 1-100).
-* ...
+The code used to run the model can be found here: INSERT LINK.
 
@@
 function se to TRUE, for instance, yi | se(sei, sigma = TRUE) ~ 1. -->
+
+The posterior probability of the population-level intercept $\alpha$ will give us an estimate of the range of probable values of the standardized effect size $\hat{\eta}$.
+This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \@ref(ana-factors).
+Crucially, the posterior probability of $\sigma_{\alpha_{\text{team}}}$ (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 
-### Exploratory road map
-<!-- SC: change heading to your liking -->
+### Analytical and demographic factors affecting effect sizes {#ana-factors}
 
-As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference ($\delta_i$) between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
-<!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.
-We will use the Box-Cox transformation on the absolute values of deviation scores to achieve an approximately normal distribution (c.f.
-Fanelli and Ioannidis 2013, Fanelli et al.
-2017: supplement).
--->
+As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
+The deviation score $\delta_i$, which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
+See minutes.}]{difference between the meta-analytical mean} ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
 <!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
@@
 <!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
-These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
-We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
-We will model the effect of the following predictors:
+We will fit a single Bayesian regression model with $\delta_i$ as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
+<!-- TODO: add brm info on factors analysis model -->
+
+**Analytical factors**. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
 - *Data exclusion*, whether data has been excluded or not.
-- *Demographic factors* of analysis teams and analysts.
 
@@
 
-We will include the following demographic factors about both the analysis teams:
+<!-- TODO: explain how the demographic factors will be entered in the factors analysis -->
+
+**Demographic factors**.
+We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
 

### 2021-01-18 RR_manuscript/Draft_RR.tex
:memo: edit step 4 section
I have updated info on brms related settings, added a description of how we will interpret the meta-analytical posteriors, made edits in the section about the analytical and demo factors analysis.

@@
   man,floatsintext]{apa6}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
 \usepackage{ifxetex,ifluatex}
@@
 \usepackage{cleveref}
+\usepackage{changes}
+\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
+\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
+\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 \ifxetex
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
+Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (``I knew it,'' Nickerson 1998), and perceiving events as being plausible in hindsight (``I knew it all along,'' Fischhoff 1975).
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 \item
-  \enquote{I can't bear another meeting on zoom.}
+  ``I can't bear another meeting on zoom.''
 \end{enumerate}
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \enquote{another} or \enquote{meeting}.
-If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word \enquote{zoom}.
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word ``another'' or ``meeting.''
+If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word ``zoom.''
 
@@
 The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch ({\textbf{???}}; Foulkes \& Docherty, 2006; White, Payne, \& Mattys, 2009).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2009; White, Payne, \& Mattys, 2009).
 
@@
 
-(2a) \enquote{I can't bear ANOTHER meeting on zoom.}
-(2b) \enquote{I can't bear another meeting on ZOOM.}
+(2a) ``I can't bear ANOTHER meeting on zoom.''
+(2b) ``I can't bear another meeting on ZOOM.''
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/casillas/academia/research/in_progress/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/stefano/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
+The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
 \end{figure}
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as \enquote{analysis teams}.
+For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''
 
@@
 
-\noindent \enquote{Please explain your ratings of this analysis.
+\noindent ``Please explain your ratings of this analysis.
 \noindent Please evaluate the selection of acoustic features.
@@
 \noindent Please evaluate choices to exclude or not exclude subsets of the data.
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).}
+\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''
 
@@
 After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: \enquote{If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.}
-The text box will be prefaced with this prompt: \enquote{Please explain your choice to revise (or not to revise) your ratings.}
+The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
+The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''
 
@@
 
-We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
-We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.
-
-FORMULA
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
 
@@
 
-Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
-We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
-Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.~\emph{z}-scores) using a Bayesian multilevel model.
-The standardized effect size (\(\eta_i\)) of each analysis will be the estimated coefficient of the critical predictor (i.e.~critical according to the analysis teams' self-reported inferential criteria).
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017) in R (R Core Team, 2020).
+For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
+If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
+
+The estimated coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size (\(\eta_i\)) of each reported model.
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
-Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size (\(\text{se}_i\)).
-This will enable us to fit a so-called \enquote{measurement-error} model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error (\(\text{se}_i\)) of the effect size.
+This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the the meta-analytical model.
+As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
 
-After the extraction of the standardized effect sizes \(\eta_i\) and related standard error \(\text{se}_i\) for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
 
@@
 
-The outcome variable will be the set of standardized effect sizes.
-The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
-The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight 2000).
-The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
-We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
-The code for the model can be found here: INSERT LINK.
+The outcome variable will be the set of standardized effect sizes \(\eta_i\).
+The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
+The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
+The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
+We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
+The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017).
+The code used to run the model can be found here: INSERT LINK.
 
-We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:
-
-\begin{itemize}
-\tightlist
-\item
-  The peer ratings of each analysis (numeric, 1-100).
-\item
-  \ldots{}
-\end{itemize}
+The posterior probability of the population-level intercept \(\alpha\) will give us an estimate of the range of probable values of the standardized effect size \(\hat{\eta}\).
+This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
+Crucially, the posterior probability of \(\sigma_{\alpha_{\text{team}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 
-\hypertarget{exploratory-road-map}{%
-\subsubsection{Exploratory road map}\label{exploratory-road-map}}
+\hypertarget{ana-factors}{%
+\subsubsection{Analytical and demographic factors affecting effect sizes}\label{ana-factors}}
 
-As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference (\(\delta_i\)) between the meta-analytical mean (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
-These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
-We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
-We will model the effect of the following predictors:
+As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
+The deviation score \(\delta_i\), which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
+See minutes.}]{difference between the meta-analytical mean} (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
+We will fit a single Bayesian regression model with \(\delta_i\) as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
+
+\textbf{Analytical factors}. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
   \emph{Data exclusion}, whether data has been excluded or not.
-\item
-  \emph{Demographic factors} of analysis teams and analysts.
 \end{itemize}
@@
 
-We will include the following demographic factors about both the analysis teams:
+\textbf{Demographic factors}.
+We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
 
@@
 \hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-burkner2017}{}%
+Bürkner, P.-C. (2017). Brms: An {R} package for {B}ayesian multilevel models using {S}tan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.
+
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
@@
 
+\leavevmode\hypertarget{ref-ogden2009}{}%
+Ogden, R. (2009). \emph{An introduction to {E}nglish phonetics}. Edinburgh University Press.
+
 \leavevmode\hypertarget{ref-open2015estimating}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-r-core-team2020}{}%
+R Core Team. (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
+
+\leavevmode\hypertarget{ref-stan-development-team2020a}{}%
+Stan Development Team. (2020a). RStan: The r interface to stan. R package version 2.21.2.
+
+\leavevmode\hypertarget{ref-stan-development-team2020}{}%
+Stan Development Team. (2020b). Stan modeling language users guide and reference manual, 2.25.
 
@@
 (1948).
-A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on Danish commons.
+A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on {D}anish commons.
 \emph{Kongelige Danske Videnskabernes Selskab}, \emph{5}(4), 1--34.
@@
 (2009).
-Rhythmic and prosodic contrast in Venetan and Sicilian Italian.
+Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian.
 In M.

### 2021-01-18 docs/ExperimentalDetails/Experimental_details.tex
use expex

--- 2020-10-30 docs/ExperimentalDetails/Experimental_details.Rmd
@@
----
-title: "Methodological Details - Blue Bananas"
-author: ""
-date: "9/17/2020"
-output: pdf_document
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Methodological Details - Blue Bananas},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{5}
+\usepackage{expex}
+\lingset{everygla=,everyglpreamble=\it}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-options(tinytex.verbose = TRUE)
+\title{Methodological Details - Blue Bananas}
+\author{}
+\date{\vspace{-2.5em}9/17/2020}
 
-```
+\begin{document}
+\maketitle
 
-## 1. Research Questions
+\hypertarget{research-questions}{%
+\section{Research Questions}\label{research-questions}}
 
-This study investigates whether speakers modify the speech signal to signal atypical referents? 
-Concretely, we ask whether the suprasegmental profile of an utterance with an atypical referent like "blue banana" is different from one with a typical referent such as "yellow banana".
+This study investigates whether speakers modify the speech signal to
+signal atypical referents? Concretely, we ask whether the suprasegmental
+profile of an utterance with an atypical referent like ``blue banana''
+is different from one with a typical referent such as ``yellow banana''.
 
-## 2. Participants
+\hypertarget{participants}{%
+\section{Participants}\label{participants}}
 
-Thirty native German speakers participated in this study. 
-All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing. 
-Participants were paid for their participation.
+Thirty native German speakers participated in this study. All
+participants grew up in a monolingual environment and were recruited
+from the population living in the broad Cologne area with normal or
+corrected-to-normal vision and normal hearing. Participants were paid
+for their participation.
 
-## 3. Procedure
+\hypertarget{procedure}{%
+\section{Procedure}\label{procedure}}
 
 In this production study, participants interacted with the experimenter.
-Participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects. 
-The non-target objects differed from the target with respect to their colour, their identity, or both. 
-Objects were referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g. yellow banana, blue banana). 
-These adjective-noun combinations differed with respect to the typicality of their combination. 
-The adjective-noun combinations were either typical, medium typical, or atypical (as established in a norming study, see [additional materials](#adds)). 
-Some combinations were typical such as yellow banana, red tomato, or yellow apricot; some were atypical such as red banana, purple tomato, or blue apricot; and some were somewhat in the middle like brown banana, green tomato, and red apricot.
+Participants had to verbally instruct the experimenter to select a
+specified target object out of four visually presented objects. The
+non-target objects differed from the target with respect to their
+colour, their identity, or both. Objects were referred to using noun
+phrases that consist of a modifier denoting colour and a modified object
+(e.g.~yellow banana, blue banana). These adjective-noun combinations
+differed with respect to the typicality of their combination. The
+adjective-noun combinations were either typical, medium typical, or
+atypical (as established in a norming study, see
+\protect\hyperlink{adds}{additional materials}). Some combinations were
+typical such as yellow banana, red tomato, or yellow apricot; some were
+atypical such as red banana, purple tomato, or blue apricot; and some
+were somewhat in the middle like brown banana, green tomato, and red
+apricot.
 
-```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}
+\begin{figure}[tbp]
 
-knitr::include_graphics("typicality_examples.png")
+{\centering \includegraphics[width=0.6\linewidth]{typicality_examples}
 
-```
+}
 
-Participants were seated in front of a computer screen. 
-The experimenter sat at the opposite side of the table in front of another computer screen. 
-The participants and the experimenter could see neither each other nor each others' screens. 
-The experiment consisted of two phases: a familiarization phase and a test phase.
+\caption{Three examples for typical, medium typical and atypical combinations of colour and object.}\label{fig:image0}
+\end{figure}
 
-In a familiarization phase, participants saw one object per trial. 
-In order to advance to the next trial, participants had to read out loud the corresponding noun phrase (e.g. blue banana). 
-During this phase, participants had to name all atypical colour-object targets that we used in the test phase of the experiment alongside their typical counterparts. 
-For example, if red banana (atypical) was an experimental target, participants were presented with both the red banana (atypical) and the yellow banana (typical). 
-This familiarization phase was included in order to ensure that participants can relate typical and atypical colour-object combinations to each other.
+Participants were seated in front of a computer screen. The experimenter
+sat at the opposite side of the table in front of another computer
+screen. The participants and the experimenter could see neither each
+other nor each others' screens. The experiment consisted of two phases:
+a familiarization phase and a test phase.
 
-After the familiarization phase, participants entered the test phase. 
-On each trial in the test phase, participants first saw four coloured objects in the top left, top right, bottom left, and bottom right of the screen, respectively. 
-One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors. 
-The position of the visual stimuli was randomized for each trial and each participant. 
-In the center of the screen, a black cube was displayed which could be moved by the experimenter. 
-The participants were asked to instruct the experimenter to move the cube onto one of the four pictures.
+In a familiarization phase, participants saw one object per trial. In
+order to advance to the next trial, participants had to read out loud
+the corresponding noun phrase (e.g.~blue banana). During this phase,
+participants had to name all atypical colour-object targets that we used
+in the test phase of the experiment alongside their typical
+counterparts. For example, if red banana (atypical) was an experimental
+target, participants were presented with both the red banana (atypical)
+and the yellow banana (typical). This familiarization phase was included
+in order to ensure that participants can relate typical and atypical
+colour-object combinations to each other.
 
-Each test trial consisted of two parts. 
-The 'trigger' instruction and the 'test' instruction. 
-After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a ‘trigger’ instruction was orthographically presented below the cube (see Figure #):
+After the familiarization phase, participants entered the test phase. On
+each trial in the test phase, participants first saw four coloured
+objects in the top left, top right, bottom left, and bottom right of the
+screen, respectively. One of the object served as the target; another
+served as the competitor; and the remaining two served as unrelated
+distractors. The position of the visual stimuli was randomized for each
+trial and each participant. In the center of the screen, a black cube
+was displayed which could be moved by the experimenter. The participants
+were asked to instruct the experimenter to move the cube onto one of the
+four pictures.
 
-\noindent “Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”  
-\noindent *engl. 'You have to put the cube on top of the green sunglasses.'*
+Each test trial consisted of two parts. The `trigger' instruction and
+the `test' instruction. After the preview of all images was displayed
+for 1500 ms, the competitor object was visually highlighted by an arrow,
+and a `trigger' instruction was orthographically presented below the
+cube (see Figure \#):
 
-```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen at the beginning of a trials.
+\ex \begingl
+\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
+\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
+\glb you have.to the cube on the green sunglasses put//
+\glft `You have to put the cube on top of the green sunglasses.'//
+\endgl \xe
+
+\begin{figure}[tbp]
+
+{\centering \includegraphics[width=0.6\linewidth]{sample_experiment_screen_competitor}
+
+}
+
+\caption{Example screen at the beginning of a trials.
 The discourse setting trigger sentence is displayed in the middle below the cube.
-The participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow)."}
+The participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).}\label{fig:image1}
+\end{figure}
 
-knitr::include_graphics("sample_experiment_screen_competitor.png")
+The trigger instruction was supposed to create a discourse context, such
+that both the color and the competitor object were introduced as
+background information into the discourse (here: green and sunglasses).
+The trial proceeded when the experimenter has moved the cube onto the
+respective referent. The sentence and the arrow disappeared.
+Subsequently, the target object was visually highlighted by an arrow and
+the test instruction was presented containing the target object (see
+Figure \#):
 
-```
+\ex \begingl
+\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
+\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
+\glb and now have.to you the cube on the green avocado put//
+\glft `And now, you have to put the cube on top of the green avocado.'//
+\endgl \xe
 
-The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (here: green and sunglasses).
-The trial proceeded when the experimenter has moved the cube onto the respective referent. 
-The sentence and the arrow disappeared. 
-Subsequently, the target object was visually highlighted by an arrow and the test instruction was presented containing the target object (see Figure #):
+\begin{figure}[tbp]
 
-\noindent “Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”  
-\noindent *engl. 'And now, you have to put the cube on top of the green avocado.'*
+{\centering \includegraphics[width=0.6\linewidth]{sample_experiment_screen_target}
 
-```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen after the trigger sentence.
+}
+
+\caption{Example screen after the trigger sentence.
 The target sentence is displayed in the middle of the screen.
-Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow)."}
+Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).}\label{fig:image2}
+\end{figure}
 
-knitr::include_graphics("sample_experiment_screen_target.png")
+The trial was completed and the next trial initiated as soon as the
+experimenter had moved the cube to the target referent. There was a 3000
+ms inter stimulus interval between trials (grey screen). In both
+competitor and target sub sequences, the arrow was displayed with a lag
+of 1000 ms and the target sentence with a lag of 1500 ms in order to
+give participants sufficient time to glance at all referents before they
+were able to identify the relevant object and the instructions.
 
-```
+Using the trigger instruction to set up the discourse context enabled us
+to manipulate the focus structure of the target sentence. If the color
+of the competitor and the target are of the same object type but
+differed in color (e.g.~yellow banana --\textgreater{} blue banana), the
+color adjective was discourse-pragmatically focused (henceforth the
+Adjective Focus (AF) condition). If the objects differed but not their
+color (e.g.~yellow banana --\textgreater{} yellow tomato), the noun was
+in focus (henceforth the Noun Focus (NF) condition). If both the color
+and the object differed (e.g.~yellow banana --\textgreater{} blue
+tomato), the whole noun phrase was in focus (henceforth the Double Focus
+(DF) condition).
 
-The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent. 
-There was a 3000 ms inter stimulus interval between trials (grey screen). 
-In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
+We are interested in the Noun Focus condition, only. AF and DF served as
+filler trials. There were 15 NF trials, 10 AF and 10 DF trials each.
+Each trial occurred two times per participants, yielding a total of 70
+trials per participant.
 
-Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence. 
-If the color of the competitor and the target are of the same object type but differed in color (e.g.
-yellow banana --> blue banana), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
-If the objects differed but not their color (e.g. yellow banana --> yellow tomato), the noun was in focus (henceforth the Noun Focus (NF) condition). 
-If both the color and the object differed (e.g. yellow banana --> blue tomato), the whole noun phrase was in focus (henceforth the Double Focus (DF) condition).
+The experimental program (implemented as a browser-based application) is
+available here: \url{https://github.com/SBRitter/fruits-production}.
 
-We are interested in the Noun Focus condition, only. 
-AF and DF served as filler trials. 
-There were 15 NF trials, 10 AF and 10 DF trials each. 
-Each trial occurred two times per participants, yielding a total of 70 trials per participant.
+\appendix
 
-The experimental program (implemented as a browser-based application) is available here: [https://github.com/SBRitter/fruits-production](https://github.com/SBRitter/fruits-production).
+\hypertarget{adds}{%
+\section{Additional Information}\label{adds}}
 
-## Additional Information {#adds}
+Here we specify in detail, how stimuli were selected for the above
+described production study.
 
-Here we specify in detail, how stimuli were selected for the above described production study.
+\hypertarget{selection-of-stimuli-superset}{%
+\subsection{Selection of stimuli
+superset}\label{selection-of-stimuli-superset}}
 
-### A.1 Selection of stimuli superset
+The selection of stimuli was informed by a norming study for which we
+selected twenty fruits or vegetables (henceforth: FOODs) and four other
+referents (henceforth: NON-FOODs). Selection criteria were mainly
+informed by visual discriminability and phonemic composition, such that
+nouns denoting our objects were supposed to contain few voiceless
+segments.
 
-The selection of stimuli was informed by a norming study for which we selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs). 
-Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain few voiceless segments.
+For each of the FOODs and NON-FOODs, we created colored versions by
+image manipulation using \href{http://www.gimp.org}{gimp}. Images of all
+individual objects were collected from internet databases containing
+copyright-free high-resolution images
+(e.g.~\href{https://pixabay.com}{Pixabay}). During the manipulation
+process, the background of the pictures was replaced by a white
+background. In order to change the color of the objects, a layer in the
+respective color was created and overlaid on top of the original image
+using ``Color'' as the layer mode. The hexadecimal color codes for the
+colors that we used are listed below:
 
-For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using [gimp](http://www.gimp.org). 
-Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g. [Pixabay](https://pixabay.com)). 
-During the manipulation process, the background of the pictures was replaced by a white background. 
-In order to change the color of the objects, a layer in the respective color was created and overlaid on top of the original image using “Color” as the layer mode. 
-The hexadecimal color codes for the colors that we used are listed below:
+\noindent Blue: \#29429f\\
+\noindent Green: \#3f8535\\
+\noindent Red: \#9d1c1c\\
+\noindent Purple: \#6d1b79\\
+\noindent Brown: \#2a1d11\\
+\noindent Yellow: \#e3c917\\
+\noindent Orange: \#ff8400\\
+\noindent Orange (potatoes): \#ff6600\\
+\noindent Black: \#000000\\
+\noindent Grey: \#FFFFFF
 
-\noindent Blue: #29429f  
-\noindent Green: #3f8535  
-\noindent Red: #9d1c1c  
-\noindent Purple: #6d1b79  
-\noindent Brown: #2a1d11  
-\noindent Yellow: #e3c917  
-\noindent Orange: #ff8400  
-\noindent Orange (potatoes): #ff6600  
-\noindent Black: #000000  
-\noindent Grey: #FFFFFF
+All pictures with natural and manipulated colors are available here:
+\url{https://osf.io/rdtx5/}.
 
-All pictures with natural and manipulated colors are available here: [https://osf.io/rdtx5/](https://osf.io/rdtx5/).
+The colors for the twenty FOODs were subjectively selected to reflect a
+range of compatibilities with the respective objects, e.g.~a typical
+banana is yellow; a less typical banana could be brown (too ripe) or
+green (not yet ripe); and an atypical banana could be blue. Every FOOD
+was presented in four of nine manipulated colors alongside its original
+image. The four NON-FOODs were subjectively selected to represent color
+agnostic objects which can and do come in a variety of colors. All
+objects were chosen such that their respective German nouns were either
+feminine singular (e.g.~``die Banana'' `the banana') or plural
+(e.g.~``die Trauben'' `the grapes').
 
-The colors for the twenty FOODs were subjectively selected to reflect a range of compatibilities with the respective objects, e.g.
-a typical banana is yellow; a less typical banana could be brown (too ripe) or green (not yet ripe); and an atypical banana could be blue.
-Every FOOD was presented in four of nine manipulated colors alongside its original image. 
-The four NON-FOODs were subjectively selected to represent color agnostic objects which can and do come in a variety of colors. 
-All objects were chosen such that their respective German nouns were either feminine singular (e.g. "die Banana" 'the banana') or plural (e.g. "die Trauben" 'the grapes').
+We used the following FOODs: apricot, avocado, banana, beans, carrot,
+cherry, cucumber, eggplant, grapes, lemon, mandarine, pear, pepper,
+pineapple, potatoes, strawberry, tomato, walnut, zucchini.
 
-We used the following FOODs: apricot, avocado, banana, beans, carrot, cherry, cucumber, eggplant, grapes, lemon, mandarine, pear, pepper, pineapple, potatoes, strawberry, tomato, walnut, zucchini.
+We used the following NON-FOODs: clothespin, paper clip, socks,
+sunglasses.
 
-We used the following NON-FOODs: clothespin, paper clip, socks, sunglasses.
+\hypertarget{the-norming-study}{%
+\subsection{The norming study}\label{the-norming-study}}
 
-### A.2 The norming study
+One-hundred German native speakers participated in a norming study using
+the crowd sourcing platform
+{[}Prolific{]}{]}(\url{https://www.prolific.ac}). We presented all
+objects in different colors to our participants. FOODs came in 5 colors
+per object, NON-FOODs came in all nine colors. Participants were
+instructed to rate how typical they think the color for each object was,
+using a smooth slider ranging from 1 to 100 (see javascript for the
+experimental design here:
+\url{https://github.com/stelaseldano/colour-typicality-norming}. The
+results of the norming study can be retrieved here:
+\url{https://osf.io/znpg5/}.
 
-One-hundred German native speakers participated in a norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac). 
-We presented all objects in different colors to our participants. 
-FOODs came in 5 colors per object, NON-FOODs came in all nine colors. 
-Participants were instructed to rate how typical they think the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design here: [https://github.com/stelaseldano/colour-typicality-norming](https://github.com/stelaseldano/colour-typicality-norming).
-The results of the norming study can be retrieved here: [https://osf.io/znpg5/](https://osf.io/znpg5/).
+\hypertarget{selection-of-experimental-stimuli}{%
+\subsection{Selection of experimental
+stimuli}\label{selection-of-experimental-stimuli}}
 
-### A.3 Selection of experimental stimuli
+The norming ratings were subsequently used to select appropriate stimuli
+for the production study according to the following procedure:
 
-The norming ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
+First, we chose five colors from the norming data set: yellow, green,
+red, orange, and brown. Those were the most frequent colors in the
+superset and their norming results varied strongly as a function of the
+object.
 
-First, we chose five colors from the norming data set: yellow, green, red, orange, and brown. 
-Those were the most frequent colors in the superset and their norming results varied strongly as a function of the object.
+Second, we sorted the FOODs according to their typicality ratings and
+binned them into typical, medium, and atypical. Typical FOODs were
+defined by norming ratings above 90. Atypical FOODs were defined by
+norming ratings below 25. Medium typical FOODs were defined by norming
+ratings in between 25 and 90. For each color and typicality, we selected
+one FOOD object. Each cell was occupied by a different FOOD.
 
-Second, we sorted the FOODs according to their typicality ratings and binned them into typical, medium, and atypical. 
-Typical FOODs were defined by norming ratings above 90. 
-Atypical FOODs were defined by norming ratings below 25. 
-Medium typical FOODs were defined by norming ratings in between 25 and 90. 
-For each color and typicality, we selected one FOOD object. 
-Each cell was occupied by a different FOOD.
+For the critical focus condition (NF) this selection procedure resulted
+in 15 target FOODs (5 colors x 3 typicality categories):
 
-For the critical focus condition (NF) this selection procedure resulted in 15 target FOODs (5 colors x 3 typicality categories):
-
-\noindent atypical:  
-\noindent Yellow cherry (Gelbe Kirsche)  
-\noindent Green carrot (Grüne Möhre)  
-\noindent Red cucumber (Rote Gurke)  
-\noindent Orange grapes (Oangene Trauben)  
+\noindent atypical:\\
+\noindent Yellow cherry (Gelbe Kirsche)\\
+\noindent Green carrot (Grüne Möhre)\\
+\noindent Red cucumber (Rote Gurke)\\
+\noindent Orange grapes (Oangene Trauben)\\
 \noindent Brown pepper (Braune Paprika)
 
-\noindent medium:  
-\noindent Yellow peas (Gelbe Erbsen)  
-\noindent Green tomato (Grüne Tomate)  
-\noindent Red apricot (Rote Aprikose)  
-\noindent Orange potatoes (Orangene Kartoffeln)  
+\noindent medium:\\
+\noindent Yellow peas (Gelbe Erbsen)\\
+\noindent Green tomato (Grüne Tomate)\\
+\noindent Red apricot (Rote Aprikose)\\
+\noindent Orange potatoes (Orangene Kartoffeln)\\
 \noindent Brown banana (Braune Banane)
 
-\noindent typical:  
-\noindent Yellow lemon (Gelbe Zitrone)  
-\noindent Green green beans (Grüne Bohnen)  
-\noindent Red strawberry (Rote Erdbeere)  
-\noindent Orange mandarine (Orangene Mandarine)  
+\noindent typical:\\
+\noindent Yellow lemon (Gelbe Zitrone)\\
+\noindent Green green beans (Grüne Bohnen)\\
+\noindent Red strawberry (Rote Erdbeere)\\
+\noindent Orange mandarine (Orangene Mandarine)\\
 \noindent Brown walnut (Braune Walnuss)
 
-The set of 15 competitors from the NON-FOOD subset was selected to ensure that there are as many distinct competitors for each color as there are target objects. 
-The set consisted of the following objects:
+The set of 15 competitors from the NON-FOOD subset was selected to
+ensure that there are as many distinct competitors for each color as
+there are target objects. The set consisted of the following objects:
 
-\noindent Yellow sunglasses (Gelbe Sonnenbrille)  
-\noindent Yellow socks (Gelbe Socken)  
-\noindent Yellow clothes peg (Gelbe Wäscheklammer)  
-\noindent Green sunglasses (Grüne Sonnenbrille)  
-\noindent Green socks (Grüne Socken)  
-\noindent Green Paper clip (Grüne Büroklammer)  
-\noindent Red socks (Rote Socken)  
-\noindent Red paper clip (Rote Büroklammer)  
-\noindent Red clothes peg (Rote Wäscheklammer)  
-\noindent Orange socks (Orangene Socken)  
-\noindent Orange paper clip (Orangene Büroklammer)  
-\noindent Orange clothes peg (Orangene Wäscheklammer)  
-\noindent Brown sunglasses (Braune Sonnenbrille)  
-\noindent Brown paper clip (Braune Büroklammer)  
+\noindent Yellow sunglasses (Gelbe Sonnenbrille)\\
+\noindent Yellow socks (Gelbe Socken)\\
+\noindent Yellow clothes peg (Gelbe Wäscheklammer)\\
+\noindent Green sunglasses (Grüne Sonnenbrille)\\
+\noindent Green socks (Grüne Socken)\\
+\noindent Green Paper clip (Grüne Büroklammer)\\
+\noindent Red socks (Rote Socken)\\
+\noindent Red paper clip (Rote Büroklammer)\\
+\noindent Red clothes peg (Rote Wäscheklammer)\\
+\noindent Orange socks (Orangene Socken)\\
+\noindent Orange paper clip (Orangene Büroklammer)\\
+\noindent Orange clothes peg (Orangene Wäscheklammer)\\
+\noindent Brown sunglasses (Braune Sonnenbrille)\\
+\noindent Brown paper clip (Braune Büroklammer)\\
 \noindent Brown clothes peg (Braune Wäscheklammer)
 
-The pairing of targets and competitors was randomized for each subject, with the only constraint that the competitor had the same color as the target object (e.g.
-if blue banana was the target, blue grapes is a possible competitor) (see randomization section below for more details).
+The pairing of targets and competitors was randomized for each subject,
+with the only constraint that the competitor had the same color as the
+target object (e.g.~if blue banana was the target, blue grapes is a
+possible competitor) (see randomization section below for more details).
 
-For the filler focus conditions (AF + DF), we distributed FOODs and NON-FOODs to fulfil the following constraints: (a) each target FOOD appeared 3 times and (b) each color appeared as a traget color 14 times.
+For the filler focus conditions (AF + DF), we distributed FOODs and
+NON-FOODs to fulfil the following constraints: (a) each target FOOD
+appeared 3 times and (b) each color appeared as a traget color 14 times.
 
-For all three focus conditions, a subset of distractors was selected from the initial superset: Distractors were either FOODS that were neither used as targets nor as competitors (avocado, egg plant, pear, zucchini) or NON-FOODs.
-Within each given trial, the distractors did neither share color nor object identity with neither the target nor the competitor.
+For all three focus conditions, a subset of distractors was selected
+from the initial superset: Distractors were either FOODS that were
+neither used as targets nor as competitors (avocado, egg plant, pear,
+zucchini) or NON-FOODs. Within each given trial, the distractors did
+neither share color nor object identity with neither the target nor the
+competitor.
 
-Overall, the sets of target, competitors and distractors are combined such that all five colors occurred equally often throughout the experiment (= 28 times).
+Overall, the sets of target, competitors and distractors are combined
+such that all five colors occurred equally often throughout the
+experiment (= 28 times).
 
-## A.4 Randomization
+\hypertarget{randomization}{%
+\section{Randomization}\label{randomization}}
 
-For each trial, targets, competitors, and distractors are chosen in a randomized way, fulfilling the following requirements:
+For each trial, targets, competitors, and distractors are chosen in a
+randomized way, fulfilling the following requirements:
 
-- NF-Condition:  
-Color of Target = Color of Competitor  
+\begin{itemize}
+\item
+  NF-Condition:\\
+  Color of Target = Color of Competitor\\
   Object of Target != Object of Competitor
+\item
+  AF-Condition:\\
+  Color of Target != Color of Competitor\\
+  Object of Target = Object of Competitor
+\item
+  DF-Condition:\\
+  Color of Target != Color of Competitor\\
+  Object of Target != Object of Competitor
+\item
+  All conditions:\\
+  Both distractors have to differ in color and object identity from both
+  target and competitor.
+\end{itemize}
 
-- AF-Condition:  
-Color of Target != Color of Competitor  
-Object of Target = Object of Competitor
+The competitor and distractors are matched iteratively to a target. One
+competitor could only be used twice or a third time if all other
+competitors that were left had been considered and prove inappropriate.
 
-- DF-Condition:  
-Color of Target != Color of Competitor  
-Object of Target != Object of Competitor
+The set of four objects (quadruple) was formed separately for each
+condition. After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following
+requirements were met:
 
-- All conditions:  
-Both distractors have to differ in color and object identity from both target and competitor.
+\begin{itemize}
+\tightlist
+\item
+  The target color of one quadruple must not be equal to the competitor
+  color of the following quadruple in order to avoid a contrastive focus
+  on the next competitor noun.
+\item
+  The target object of one quadruple must not be equal to the competitor
+  object of the following quadruple to avoid a contrastive focus on the
+  next competitor adjective.
+\item
+  The list can have the same experimental condition in adjacent trials
+  only in maximally 12\% of all cases.
+\end{itemize}
 
-The competitor and distractors are matched iteratively to a target. 
-One competitor could only be used twice or a third time if all other competitors that were left had been considered and prove inappropriate.
+Following these criteria, one randomized list for each subject was
+produced. The list was then copied and merged with the first list in
+order to ensure that each unique trial occurs twice during one recording
+session. In case the copy-and-merge procedure led to violation of any of
+the criteria described above, the first trial of the repetition list was
+shuffled until the criteria were met.
 
-The set of four objects (quadruple) was formed separately for each condition. 
-After the three lists had been compiled, they were merged. 
-The sequence of quadruples was randomized such that the following requirements were met:
+The python code for the randomization is available here:
+\url{https://github.com/SBRitter/fruits-randomization}.
 
-- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
-- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
-- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
-
-Following these criteria, one randomized list for each subject was produced. 
-The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session. 
-In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
-
-The python code for the randomization is available here: [https://github.com/SBRitter/fruits-randomization](https://github.com/SBRitter/fruits-randomization).
+\end{document}

### 2021-01-18 docs/ExperimentalDetails/Experimental_details.Rmd
:art: - use numbered sections + appendix
use expex

@@
 date: "9/17/2020"
-output: pdf_document
+output:
+  pdf_document:
+    number_sections: true
+    keep_tex: true
+header-includes:
+  - \usepackage{expex}
+  - \lingset{everygla=,everyglpreamble=\it}
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, fig.pos = "tbp")
 options(tinytex.verbose = TRUE)
-
 ```
 
-## 1. Research Questions
+# Research Questions
 
@@
 
-## 2. Participants
+# Participants
 
@@
 
-## 3. Procedure
+# Procedure
 
@@
 
-\noindent “Du sollst den Würfel auf der grünen Sonnenbrille ablegen.”  
-\noindent *engl. 'You have to put the cube on top of the green sunglasses.'*
+```{=latex}
+\ex \begingl
+\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
+\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
+\glb you have.to the cube on the green sunglasses put//
+\glft `You have to put the cube on top of the green sunglasses.'//
+\endgl \xe
+```
 
@@
 
-\noindent “Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.”  
-\noindent *engl. 'And now, you have to put the cube on top of the green avocado.'*
+```{=latex}
+\ex \begingl
+\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
+\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
+\glb and now have.to you the cube on the green avocado put//
+\glft `And now, you have to put the cube on top of the green avocado.'//
+\endgl \xe
+```
 
@@
 
-## Additional Information {#adds}
+\appendix
+
+# Additional Information {#adds}
 
@@
 
-### A.1 Selection of stimuli superset
+## Selection of stimuli superset
 
@@
 
-### A.2 The norming study
+## The norming study
 
@@
 
-### A.3 Selection of experimental stimuli
+## Selection of experimental stimuli
 
@@
 
-## A.4 Randomization
+# Randomization
 

### 2021-01-19 docs/ExperimentalDetails/Experimental_details.tex
:memo: - edit ExperimentalDetails

@@
 \hypersetup{
-  pdftitle={Methodological Details - Blue Bananas},
+  pdftitle={Production study: Methodological details},
   hidelinks,
@@
 \usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \lingset{everygla=,everyglpreamble=\it}
+\usepackage[export]{adjustbox}
 \ifluatex
@@
 
-\title{Methodological Details - Blue Bananas}
+\title{Production study: Methodological details}
 \author{}
@@
 
-\hypertarget{research-questions}{%
-\section{Research Questions}\label{research-questions}}
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
+}
+\hypertarget{overview}{%
+\section{Overview}\label{overview}}
 
-This study investigates whether speakers modify the speech signal to
-signal atypical referents? Concretely, we ask whether the suprasegmental
-profile of an utterance with an atypical referent like ``blue banana''
-is different from one with a typical referent such as ``yellow banana''.
+This document describes the methodological details of the production study, which generated the data your team will analyze for the \emph{Many Speech Analyses} project.
+
+Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \ref{norming} for context.
+
+\hypertarget{research-question}{%
+\section{Research question}\label{research-question}}
+
+This study investigated whether speakers modify speech to signal atypical referents.
+Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like \emph{blue banana} is different from one with a typical referent such as \emph{yellow banana}.
 
@@
 
-Thirty native German speakers participated in this study. All
-participants grew up in a monolingual environment and were recruited
-from the population living in the broad Cologne area with normal or
-corrected-to-normal vision and normal hearing. Participants were paid
-for their participation.
+Thirty native German speakers participated in this study.
+All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
+Participants were paid for their participation.
 
@@
 
-In this production study, participants interacted with the experimenter.
-Participants had to verbally instruct the experimenter to select a
-specified target object out of four visually presented objects. The
-non-target objects differed from the target with respect to their
-colour, their identity, or both. Objects were referred to using noun
-phrases that consist of a modifier denoting colour and a modified object
-(e.g.~yellow banana, blue banana). These adjective-noun combinations
-differed with respect to the typicality of their combination. The
-adjective-noun combinations were either typical, medium typical, or
-atypical (as established in a norming study, see
-\protect\hyperlink{adds}{additional materials}). Some combinations were
-typical such as yellow banana, red tomato, or yellow apricot; some were
-atypical such as red banana, purple tomato, or blue apricot; and some
-were somewhat in the middle like brown banana, green tomato, and red
-apricot.
+In this production study, participants interacted with the experimenter in German.
+Participants were seated in front of a computer screen.
+The experimenter sat at the opposite side of the table in front of another computer screen.
+The participants and the experimenter could not see each other nor each others' screens.
+The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
+The non-target objects differed from the target with respect to their color, their identity, or both.
+Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
+These color-object combinations differed with respect to their typicality.
+The color-object combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
+The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \ref{norming} for details).
+Figure \ref{fig:image0} illustrates combination typicality for a banana, a tomato, and an apricot.
 
@@
 
-Participants were seated in front of a computer screen. The experimenter
-sat at the opposite side of the table in front of another computer
-screen. The participants and the experimenter could see neither each
-other nor each others' screens. The experiment consisted of two phases:
-a familiarization phase and a test phase.
+The experiment consisted of two phases: a familiarization phase and a test phase.
 
-In a familiarization phase, participants saw one object per trial. In
-order to advance to the next trial, participants had to read out loud
-the corresponding noun phrase (e.g.~blue banana). During this phase,
-participants had to name all atypical colour-object targets that we used
-in the test phase of the experiment alongside their typical
-counterparts. For example, if red banana (atypical) was an experimental
-target, participants were presented with both the red banana (atypical)
-and the yellow banana (typical). This familiarization phase was included
-in order to ensure that participants can relate typical and atypical
-colour-object combinations to each other.
+In a familiarization phase, participants saw the picture of one object per trial.
+In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
+During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
+For example, one of the experimental targets was a red banana (atypical).
+The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
+This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
 
-After the familiarization phase, participants entered the test phase. On
-each trial in the test phase, participants first saw four coloured
-objects in the top left, top right, bottom left, and bottom right of the
-screen, respectively. One of the object served as the target; another
-served as the competitor; and the remaining two served as unrelated
-distractors. The position of the visual stimuli was randomized for each
-trial and each participant. In the center of the screen, a black cube
-was displayed which could be moved by the experimenter. The participants
-were asked to instruct the experimenter to move the cube onto one of the
-four pictures.
+After the familiarization phase, the participants entered the test phase.
+On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
+One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
+The position of the visual stimuli was randomized for each trial and each participant (see Appendix \ref{random}).
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
 
-Each test trial consisted of two parts. The `trigger' instruction and
-the `test' instruction. After the preview of all images was displayed
-for 1500 ms, the competitor object was visually highlighted by an arrow,
-and a `trigger' instruction was orthographically presented below the
-cube (see Figure \#):
+\begin{figure}[tbp]
+
+{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_competitor}
+
+}
+
+\caption{Test trial: Example screen of a trigger instruction.
+The trigger instruction is displayed in the middle below the cube.
+Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).}\label{fig:image1}
+\end{figure}
+
+Each test trial consisted of two parts.
+The trigger instruction and the test instruction.
+After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \ref{fig:image1}).
+The trigger instruction was constituted by the frame sentence \emph{Du sollst den Würfel auf X ablegen}.
+\emph{X} was one of the adjective-noun combinations.
+
+For example, the subjects saw the following sentence:
 
@@
 
-\begin{figure}[tbp]
+The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: \emph{green} and \emph{sunglasses}).
+The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
 
-{\centering \includegraphics[width=0.6\linewidth]{sample_experiment_screen_competitor}
-
-}
-
-\caption{Example screen at the beginning of a trials.
-The discourse setting trigger sentence is displayed in the middle below the cube.
-The participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).}\label{fig:image1}
-\end{figure}
-
-The trigger instruction was supposed to create a discourse context, such
-that both the color and the competitor object were introduced as
-background information into the discourse (here: green and sunglasses).
-The trial proceeded when the experimenter has moved the cube onto the
-respective referent. The sentence and the arrow disappeared.
-Subsequently, the target object was visually highlighted by an arrow and
-the test instruction was presented containing the target object (see
-Figure \#):
+Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \ref{fig:image2}).
+This time the frame sentence was \emph{Und jetzt sollst du den Würfel auf X ablegen}, where \emph{X} was again an adjective-noun combination.
+To continue the example above, the subject would see the following test instruction:
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth]{sample_experiment_screen_target}
+{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_target}
 
@@
 
-\caption{Example screen after the trigger sentence.
+\caption{Test trial: Example screen of the test instruction.
 The target sentence is displayed in the middle of the screen.
@@
 
-The trial was completed and the next trial initiated as soon as the
-experimenter had moved the cube to the target referent. There was a 3000
-ms inter stimulus interval between trials (grey screen). In both
-competitor and target sub sequences, the arrow was displayed with a lag
-of 1000 ms and the target sentence with a lag of 1500 ms in order to
-give participants sufficient time to glance at all referents before they
-were able to identify the relevant object and the instructions.
+The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
+There was a 3000 ms inter stimulus interval between trials (grey screen).
+In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
 
-Using the trigger instruction to set up the discourse context enabled us
-to manipulate the focus structure of the target sentence. If the color
-of the competitor and the target are of the same object type but
-differed in color (e.g.~yellow banana --\textgreater{} blue banana), the
-color adjective was discourse-pragmatically focused (henceforth the
-Adjective Focus (AF) condition). If the objects differed but not their
-color (e.g.~yellow banana --\textgreater{} yellow tomato), the noun was
-in focus (henceforth the Noun Focus (NF) condition). If both the color
-and the object differed (e.g.~yellow banana --\textgreater{} blue
-tomato), the whole noun phrase was in focus (henceforth the Double Focus
-(DF) condition).
+Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
+If the color of the competitor and the target are of the same object type but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
+If the objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (henceforth the Noun Focus (NF) condition).
+If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
 
-We are interested in the Noun Focus condition, only. AF and DF served as
-filler trials. There were 15 NF trials, 10 AF and 10 DF trials each.
-Each trial occurred two times per participants, yielding a total of 70
-trials per participant.
+There were 15 NF trials, 10 AF and 10 ANF trials each.
+Each trial occurred two times per participants, yielding a total of 70 trials per participant.
 
-The experimental program (implemented as a browser-based application) is
-available here: \url{https://github.com/SBRitter/fruits-production}.
+The program (implemented as a browser-based application) used for the experiment is available at the following link: \url{https://github.com/SBRitter/fruits-production}.
 
@@
 
-\hypertarget{adds}{%
-\section{Additional Information}\label{adds}}
+\hypertarget{random}{%
+\section{Randomization}\label{random}}
 
-Here we specify in detail, how stimuli were selected for the above
-described production study.
-
-\hypertarget{selection-of-stimuli-superset}{%
-\subsection{Selection of stimuli
-superset}\label{selection-of-stimuli-superset}}
-
-The selection of stimuli was informed by a norming study for which we
-selected twenty fruits or vegetables (henceforth: FOODs) and four other
-referents (henceforth: NON-FOODs). Selection criteria were mainly
-informed by visual discriminability and phonemic composition, such that
-nouns denoting our objects were supposed to contain few voiceless
-segments.
-
-For each of the FOODs and NON-FOODs, we created colored versions by
-image manipulation using \href{http://www.gimp.org}{gimp}. Images of all
-individual objects were collected from internet databases containing
-copyright-free high-resolution images
-(e.g.~\href{https://pixabay.com}{Pixabay}). During the manipulation
-process, the background of the pictures was replaced by a white
-background. In order to change the color of the objects, a layer in the
-respective color was created and overlaid on top of the original image
-using ``Color'' as the layer mode. The hexadecimal color codes for the
-colors that we used are listed below:
-
-\noindent Blue: \#29429f\\
-\noindent Green: \#3f8535\\
-\noindent Red: \#9d1c1c\\
-\noindent Purple: \#6d1b79\\
-\noindent Brown: \#2a1d11\\
-\noindent Yellow: \#e3c917\\
-\noindent Orange: \#ff8400\\
-\noindent Orange (potatoes): \#ff6600\\
-\noindent Black: \#000000\\
-\noindent Grey: \#FFFFFF
-
-All pictures with natural and manipulated colors are available here:
-\url{https://osf.io/rdtx5/}.
-
-The colors for the twenty FOODs were subjectively selected to reflect a
-range of compatibilities with the respective objects, e.g.~a typical
-banana is yellow; a less typical banana could be brown (too ripe) or
-green (not yet ripe); and an atypical banana could be blue. Every FOOD
-was presented in four of nine manipulated colors alongside its original
-image. The four NON-FOODs were subjectively selected to represent color
-agnostic objects which can and do come in a variety of colors. All
-objects were chosen such that their respective German nouns were either
-feminine singular (e.g.~``die Banana'' `the banana') or plural
-(e.g.~``die Trauben'' `the grapes').
-
-We used the following FOODs: apricot, avocado, banana, beans, carrot,
-cherry, cucumber, eggplant, grapes, lemon, mandarine, pear, pepper,
-pineapple, potatoes, strawberry, tomato, walnut, zucchini.
-
-We used the following NON-FOODs: clothespin, paper clip, socks,
-sunglasses.
-
-\hypertarget{the-norming-study}{%
-\subsection{The norming study}\label{the-norming-study}}
-
-One-hundred German native speakers participated in a norming study using
-the crowd sourcing platform
-{[}Prolific{]}{]}(\url{https://www.prolific.ac}). We presented all
-objects in different colors to our participants. FOODs came in 5 colors
-per object, NON-FOODs came in all nine colors. Participants were
-instructed to rate how typical they think the color for each object was,
-using a smooth slider ranging from 1 to 100 (see javascript for the
-experimental design here:
-\url{https://github.com/stelaseldano/colour-typicality-norming}. The
-results of the norming study can be retrieved here:
-\url{https://osf.io/znpg5/}.
-
-\hypertarget{selection-of-experimental-stimuli}{%
-\subsection{Selection of experimental
-stimuli}\label{selection-of-experimental-stimuli}}
-
-The norming ratings were subsequently used to select appropriate stimuli
-for the production study according to the following procedure:
-
-First, we chose five colors from the norming data set: yellow, green,
-red, orange, and brown. Those were the most frequent colors in the
-superset and their norming results varied strongly as a function of the
-object.
-
-Second, we sorted the FOODs according to their typicality ratings and
-binned them into typical, medium, and atypical. Typical FOODs were
-defined by norming ratings above 90. Atypical FOODs were defined by
-norming ratings below 25. Medium typical FOODs were defined by norming
-ratings in between 25 and 90. For each color and typicality, we selected
-one FOOD object. Each cell was occupied by a different FOOD.
-
-For the critical focus condition (NF) this selection procedure resulted
-in 15 target FOODs (5 colors x 3 typicality categories):
-
-\noindent atypical:\\
-\noindent Yellow cherry (Gelbe Kirsche)\\
-\noindent Green carrot (Grüne Möhre)\\
-\noindent Red cucumber (Rote Gurke)\\
-\noindent Orange grapes (Oangene Trauben)\\
-\noindent Brown pepper (Braune Paprika)
-
-\noindent medium:\\
-\noindent Yellow peas (Gelbe Erbsen)\\
-\noindent Green tomato (Grüne Tomate)\\
-\noindent Red apricot (Rote Aprikose)\\
-\noindent Orange potatoes (Orangene Kartoffeln)\\
-\noindent Brown banana (Braune Banane)
-
-\noindent typical:\\
-\noindent Yellow lemon (Gelbe Zitrone)\\
-\noindent Green green beans (Grüne Bohnen)\\
-\noindent Red strawberry (Rote Erdbeere)\\
-\noindent Orange mandarine (Orangene Mandarine)\\
-\noindent Brown walnut (Braune Walnuss)
-
-The set of 15 competitors from the NON-FOOD subset was selected to
-ensure that there are as many distinct competitors for each color as
-there are target objects. The set consisted of the following objects:
-
-\noindent Yellow sunglasses (Gelbe Sonnenbrille)\\
-\noindent Yellow socks (Gelbe Socken)\\
-\noindent Yellow clothes peg (Gelbe Wäscheklammer)\\
-\noindent Green sunglasses (Grüne Sonnenbrille)\\
-\noindent Green socks (Grüne Socken)\\
-\noindent Green Paper clip (Grüne Büroklammer)\\
-\noindent Red socks (Rote Socken)\\
-\noindent Red paper clip (Rote Büroklammer)\\
-\noindent Red clothes peg (Rote Wäscheklammer)\\
-\noindent Orange socks (Orangene Socken)\\
-\noindent Orange paper clip (Orangene Büroklammer)\\
-\noindent Orange clothes peg (Orangene Wäscheklammer)\\
-\noindent Brown sunglasses (Braune Sonnenbrille)\\
-\noindent Brown paper clip (Braune Büroklammer)\\
-\noindent Brown clothes peg (Braune Wäscheklammer)
-
-The pairing of targets and competitors was randomized for each subject,
-with the only constraint that the competitor had the same color as the
-target object (e.g.~if blue banana was the target, blue grapes is a
-possible competitor) (see randomization section below for more details).
-
-For the filler focus conditions (AF + DF), we distributed FOODs and
-NON-FOODs to fulfil the following constraints: (a) each target FOOD
-appeared 3 times and (b) each color appeared as a traget color 14 times.
-
-For all three focus conditions, a subset of distractors was selected
-from the initial superset: Distractors were either FOODS that were
-neither used as targets nor as competitors (avocado, egg plant, pear,
-zucchini) or NON-FOODs. Within each given trial, the distractors did
-neither share color nor object identity with neither the target nor the
-competitor.
-
-Overall, the sets of target, competitors and distractors are combined
-such that all five colors occurred equally often throughout the
-experiment (= 28 times).
-
-\hypertarget{randomization}{%
-\section{Randomization}\label{randomization}}
-
-For each trial, targets, competitors, and distractors are chosen in a
-randomized way, fulfilling the following requirements:
-
-\begin{itemize}
-\item
-  NF-Condition:\\
-  Color of Target = Color of Competitor\\
-  Object of Target != Object of Competitor
-\item
-  AF-Condition:\\
-  Color of Target != Color of Competitor\\
-  Object of Target = Object of Competitor
-\item
-  DF-Condition:\\
-  Color of Target != Color of Competitor\\
-  Object of Target != Object of Competitor
-\item
-  All conditions:\\
-  Both distractors have to differ in color and object identity from both
-  target and competitor.
-\end{itemize}
-
-The competitor and distractors are matched iteratively to a target. One
-competitor could only be used twice or a third time if all other
-competitors that were left had been considered and prove inappropriate.
-
-The set of four objects (quadruple) was formed separately for each
-condition. After the three lists had been compiled, they were merged.
-The sequence of quadruples was randomized such that the following
-requirements were met:
+In the production study, the combination of target/competitor/distractors were randomized in each trial.
+Randomization was restricted to satisfy the following criteria, depending on the condition.
 
@@
 \item
-  The target color of one quadruple must not be equal to the competitor
-  color of the following quadruple in order to avoid a contrastive focus
-  on the next competitor noun.
+  NF-Condition:
+
+  \begin{itemize}
+  \tightlist
   \item
-  The target object of one quadruple must not be equal to the competitor
-  object of the following quadruple to avoid a contrastive focus on the
-  next competitor adjective.
+    Color of Target = Color of Competitor.
   \item
-  The list can have the same experimental condition in adjacent trials
-  only in maximally 12\% of all cases.
+    Object of Target != Object of Competitor.
+  \end{itemize}
+\item
+  AF-Condition:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Color of Target != Color of Competitor.
+  \item
+    Object of Target = Object of Competitor.
+  \end{itemize}
+\item
+  DF-Condition:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Color of Target != Color of Competitor.
+  \item
+    Object of Target != Object of Competitor.
+  \end{itemize}
+\item
+  Distractors, all conditions:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Both distractors have to differ in color and object identity from both target and competitor.
+  \end{itemize}
 \end{itemize}
 
-Following these criteria, one randomized list for each subject was
-produced. The list was then copied and merged with the first list in
-order to ensure that each unique trial occurs twice during one recording
-session. In case the copy-and-merge procedure led to violation of any of
-the criteria described above, the first trial of the repetition list was
-shuffled until the criteria were met.
+The competitor and distractors were matched iteratively to a target.
+One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
 
-The python code for the randomization is available here:
-\url{https://github.com/SBRitter/fruits-randomization}.
+The set of four objects (quadruple) was formed separately for each of the three focus conditions.
+After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following requirements were met:
+
+\begin{itemize}
+\tightlist
+\item
+  The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
+\item
+  The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
+\item
+  The list can have the same experimental condition in adjacent trials only in maximally 12\% of all cases.
+\end{itemize}
+
+Following these criteria, one randomized list for each subject was produced.
+The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
+In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
+
+The python code for the randomization is available at the following link: \url{https://github.com/SBRitter/fruits-randomization}.
+
+\hypertarget{norming}{%
+\section{Norming study}\label{norming}}
+
+Here we specify in detail the selection of the stimuli for the production study.
+
+\hypertarget{selection-of-stimuli-superset}{%
+\subsection{Selection of stimuli superset}\label{selection-of-stimuli-superset}}
+
+The selection of stimuli was informed by a norming study for which we have chosen twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
+Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain as few voiceless segments as possible.
+
+For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using \href{http://www.gimp.org}{Gimp}.
+Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g.~\href{https://pixabay.com}{Pixabay}).
+During the manipulation process, the background of the pictures was replaced with a white background.
+In order to change the color of the objects, a layer in the respective color was created and overlaid on top of the original image using \texttt{Color} as the layer mode.
+The hexadecimal color codes for the colors that we used are listed below:
+
+\begin{itemize}
+\tightlist
+\item
+  Blue: \#29429f
+\item
+  Green: \#3f8535
+\item
+  Red: \#9d1c1c
+\item
+  Purple: \#6d1b79
+\item
+  Brown: \#2a1d11
+\item
+  Yellow: \#e3c917
+\item
+  Orange: \#ff8400
+\item
+  Orange (potatoes): \#ff6600
+\item
+  Black: \#000
+\item
+  Grey: \#fff
+\end{itemize}
+
+All pictures with natural and manipulated colors are available here: \url{https://osf.io/rdtx5/}.
+
+The colors for the twenty FOODs were subjectively selected to reflect a range of compatibilities with the respective objects, e.g.~a typical banana is yellow; a less typical banana could be brown (too ripe) or green (not yet ripe); and an atypical banana could be blue.
+Every FOOD was presented in four of nine manipulated colors alongside its original image.
+The four NON-FOODs were subjectively selected to represent color agnostic objects which can and do come in a variety of colors.
+All objects were chosen such that their respective German nouns were either feminine singular (e.g.~\emph{die Banana} `the banana') or plural (e.g.~\emph{die Trauben} `the grapes').
+
+We used the following FOODs: apricot, avocado, banana, beans, carrot, cherry, cucumber, eggplant, grapes, lemon, mandarine, pear, pepper, pineapple, potatoes, strawberry, tomato, walnut, zucchini.
+
+We used the following NON-FOODs: clothespin, paper clip, socks, sunglasses.
+
+\hypertarget{participants-and-procedures}{%
+\subsection{Participants and procedures}\label{participants-and-procedures}}
+
+A hundred German native speakers participated in a norming study using the crowd sourcing platform \href{https://www.prolific.ac}{Prolific}.
+We presented all objects in different colors to our participants.
+FOODs came in 5 colors per object, NON-FOODs came in all nine colors.
+Participants were instructed to rate how typical they thought the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design here: \url{https://github.com/stelaseldano/colour-typicality-norming}).
+The results of the norming study can be retrieved here: \url{https://osf.io/znpg5/}.
+
+\hypertarget{selection-of-experimental-stimuli-for-the-production-study}{%
+\subsection{Selection of experimental stimuli for the production study}\label{selection-of-experimental-stimuli-for-the-production-study}}
+
+The typicality ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
+
+First, we chose five colors from the norming data set: yellow, green, red, orange, and brown.
+Those were the most frequent colors in the superset and their norming results varied strongly as a function of the object.
+
+Second, we sorted the FOODs according to their typicality ratings and binned them into typical, medium, and atypical.
+Typical FOODs were defined by norming ratings above 90.
+Atypical FOODs were defined by norming ratings below 25.
+Medium typical FOODs were defined by norming ratings in between 25 and 90.
+For each color and typicality, we selected one FOOD object.
+Each cell was occupied by a different FOOD.
+
+For the noun focus condition (NF) this selection procedure resulted in 15 target FOODs (5 colors x 3 typicality categories):
+
+\begin{itemize}
+\tightlist
+\item
+  Atypical:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Yellow cherry (\emph{Gelbe Kirsche}).
+  \item
+    Green carrot (\emph{Grüne Möhre}).
+  \item
+    Red cucumber (\emph{Rote Gurke}).
+  \item
+    Orange grapes (\emph{Oangene Trauben}).
+  \item
+    Brown pepper (\emph{Braune Paprika}).
+  \end{itemize}
+\item
+  Medium:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Yellow peas (\emph{Gelbe Erbsen}).
+  \item
+    Green tomato (\emph{Grüne Tomate}).
+  \item
+    Red apricot (\emph{Rote Aprikose}).
+  \item
+    Orange potatoes (\emph{Orangene Kartoffeln}).
+  \item
+    Brown banana (\emph{Braune Banane}).
+  \end{itemize}
+\item
+  Typical:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Yellow lemon (\emph{Gelbe Zitrone}).
+  \item
+    Green green beans (\emph{Grüne Bohnen}).
+  \item
+    Red strawberry (\emph{Rote Erdbeere}).
+  \item
+    Orange mandarine (\emph{Orangene Mandarine}).
+  \item
+    Brown walnut (\emph{Braune Walnuss}).
+  \end{itemize}
+\end{itemize}
+
+The set of 15 competitors from the NON-FOOD subset was selected to ensure that there are as many distinct competitors for each color as there are target objects.
+The set consisted of the following objects:
+
+\begin{itemize}
+\tightlist
+\item
+  Yellow sunglasses (\emph{Gelbe Sonnenbrille}).
+\item
+  Yellow socks (\emph{Gelbe Socken}).
+\item
+  Yellow clothes peg (\emph{Gelbe Wäscheklammer}).
+\item
+  Green sunglasses (\emph{Grüne Sonnenbrille}).
+\item
+  Green socks (\emph{Grüne Socken}).
+\item
+  Green Paper clip (\emph{Grüne Büroklammer}).
+\item
+  Red socks (\emph{Rote Socken}).
+\item
+  Red paper clip (\emph{Rote Büroklammer}).
+\item
+  Red clothes peg (\emph{Rote Wäscheklammer}).
+\item
+  Orange socks (\emph{Orangene Socken}).
+\item
+  Orange paper clip (\emph{Orangene Büroklammer})
+\item
+  Orange clothes peg (\emph{Orangene Wäscheklammer}).
+\item
+  Brown sunglasses (\emph{Braune Sonnenbrille}).
+\item
+  Brown paper clip (\emph{Braune Büroklammer}).
+\item
+  Brown clothes peg (\emph{Braune Wäscheklammer}).
+\end{itemize}
+
+For the Adjective and Adjective/Noun conditions (AF + ANF), we distributed FOODs and NON-FOODs to fulfill the following constraints: (a) each target FOOD appeared 3 times and (b) each color appeared as a target color 14 times.
+
+For all three focus conditions, a subset of distractors was selected from the initial superset.
+The distractors were either FOODS that were neither used as targets nor as competitors (avocado, egg plant, pear, zucchini) or NON-FOODs.
+Within each given trial, the distractors did not share color nor object identity with neither the target nor the competitor.
+
+Overall, the sets of target, competitors and distractors were combined such that all five colors occurred equally often throughout the experiment (i.e.~28 times).
 

### 2021-01-19 docs/ExperimentalDetails/Experimental_details.Rmd
:memo: - edit ExperimentalDetails

@@
 ---
-title: "Methodological Details - Blue Bananas"
+title: "Production study: Methodological details"
 author: ""
@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
     number_sections: true
@@
   - \lingset{everygla=,everyglpreamble=\it}
+  - \usepackage[export]{adjustbox}
 ---
@@
 
-# Research Questions
+# Overview
 
-This study investigates whether speakers modify the speech signal to signal atypical referents? 
-Concretely, we ask whether the suprasegmental profile of an utterance with an atypical referent like "blue banana" is different from one with a typical referent such as "yellow banana".
+This document describes the methodological details of the production study, which generated the data your team will analyze for the *Many Speech Analyses* project.
+
+<!-- TODO: link to OSF wiki for overview of the norming and production studies -->
+Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \@ref(norming) for context.
+
+# Research question
+
+This study investigated whether speakers modify speech to signal atypical referents.
+Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like *blue banana* is different from one with a typical referent such as *yellow banana*.
 
@@
 
-In this production study, participants interacted with the experimenter. 
-Participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects. 
-The non-target objects differed from the target with respect to their colour, their identity, or both. 
-Objects were referred to using noun phrases that consist of a modifier denoting colour and a modified object (e.g. yellow banana, blue banana). 
-These adjective-noun combinations differed with respect to the typicality of their combination. 
-The adjective-noun combinations were either typical, medium typical, or atypical (as established in a norming study, see [additional materials](#adds)). 
-Some combinations were typical such as yellow banana, red tomato, or yellow apricot; some were atypical such as red banana, purple tomato, or blue apricot; and some were somewhat in the middle like brown banana, green tomato, and red apricot.
+In this production study, participants interacted with the experimenter in German.
+Participants were seated in front of a computer screen.
+The experimenter sat at the opposite side of the table in front of another computer screen.
+The participants and the experimenter could not see each other nor each others' screens.
+The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
+The non-target objects differed from the target with respect to their color, their identity, or both.
+Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.
+*Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
+These color-object combinations differed with respect to their typicality.
+The color-object combinations were either typical (e.g.
+*Orangene Mandarine* 'orange mandarin'), medium typical (e.g.
+*Grüne Tomate* 'green tomato'), or atypical (e.g.
+*Gelbe Kirsche* 'yellow cherry').
+The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \@ref(norming) for details).
+Figure \@ref(fig:image0) illustrates combination typicality for a banana, a tomato, and an apricot.
 
@@
 
-Participants were seated in front of a computer screen. 
-The experimenter sat at the opposite side of the table in front of another computer screen. 
-The participants and the experimenter could see neither each other nor each others' screens. 
 The experiment consisted of two phases: a familiarization phase and a test phase.
 
-In a familiarization phase, participants saw one object per trial. 
-In order to advance to the next trial, participants had to read out loud the corresponding noun phrase (e.g. blue banana). 
-During this phase, participants had to name all atypical colour-object targets that we used in the test phase of the experiment alongside their typical counterparts. 
-For example, if red banana (atypical) was an experimental target, participants were presented with both the red banana (atypical) and the yellow banana (typical). 
-This familiarization phase was included in order to ensure that participants can relate typical and atypical colour-object combinations to each other.
+In a familiarization phase, participants saw the picture of one object per trial.
+In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
+During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
+For example, one of the experimental targets was a red banana (atypical).
+The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
+This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
 
-After the familiarization phase, participants entered the test phase. 
-On each trial in the test phase, participants first saw four coloured objects in the top left, top right, bottom left, and bottom right of the screen, respectively. 
+After the familiarization phase, the participants entered the test phase.
+On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
 One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
-The position of the visual stimuli was randomized for each trial and each participant. 
-In the center of the screen, a black cube was displayed which could be moved by the experimenter. 
-The participants were asked to instruct the experimenter to move the cube onto one of the four pictures.
+The position of the visual stimuli was randomized for each trial and each participant (see Appendix \@ref(random)).
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
+
+```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of a trigger instruction.
+The trigger instruction is displayed in the middle below the cube.
+Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).", out.extra="frame"}
+
+knitr::include_graphics("sample_experiment_screen_competitor.png")
+
+```
 
 Each test trial consisted of two parts.
-The 'trigger' instruction and the 'test' instruction. 
-After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a ‘trigger’ instruction was orthographically presented below the cube (see Figure #):
+The trigger instruction and the test instruction.
+After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \@ref(fig:image1)).
+The trigger instruction was constituted by the frame sentence *Du sollst den Würfel auf X ablegen*.
+*X* was one of the adjective-noun combinations.
+
+For example, the subjects saw the following sentence:
 
@@
 
-```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen at the beginning of a trials.
-The discourse setting trigger sentence is displayed in the middle below the cube.
-The participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow)."}
+The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: *green* and *sunglasses*).
+The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
 
-knitr::include_graphics("sample_experiment_screen_competitor.png")
-
-```
-
-The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (here: green and sunglasses).
-The trial proceeded when the experimenter has moved the cube onto the respective referent. 
-The sentence and the arrow disappeared. 
-Subsequently, the target object was visually highlighted by an arrow and the test instruction was presented containing the target object (see Figure #):
+Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \@ref(fig:image2)).
+This time the frame sentence was *Und jetzt sollst du den Würfel auf X ablegen*, where *X* was again an adjective-noun combination.
+To continue the example above, the subject would see the following test instruction:
 
@@
 
-```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Example screen after the trigger sentence.
+```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of the test instruction.
 The target sentence is displayed in the middle of the screen.
-Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow)."}
+Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).", out.extra="frame"}
 
@@
 If the color of the competitor and the target are of the same object type but differed in color (e.g.
-yellow banana --> blue banana), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
-If the objects differed but not their color (e.g. yellow banana --> yellow tomato), the noun was in focus (henceforth the Noun Focus (NF) condition). 
-If both the color and the object differed (e.g. yellow banana --> blue tomato), the whole noun phrase was in focus (henceforth the Double Focus (DF) condition).
+*yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
+If the objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (henceforth the Noun Focus (NF) condition).
+If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
 
-We are interested in the Noun Focus condition, only. 
-AF and DF served as filler trials. 
-There were 15 NF trials, 10 AF and 10 DF trials each. 
+There were 15 NF trials, 10 AF and 10 ANF trials each.
 Each trial occurred two times per participants, yielding a total of 70 trials per participant.
 
-The experimental program (implemented as a browser-based application) is available here: [https://github.com/SBRitter/fruits-production](https://github.com/SBRitter/fruits-production).
+The program (implemented as a browser-based application) used for the experiment is available at the following link: <https://github.com/SBRitter/fruits-production>.
 
@@
 
-# Additional Information {#adds}
+# Randomization {#random}
 
-Here we specify in detail, how stimuli were selected for the above described production study.
+In the production study, the combination of target/competitor/distractors were randomized in each trial.
+Randomization was restricted to satisfy the following criteria, depending on the condition.
+
+- NF-Condition:
+  - Color of Target = Color of Competitor.
+  - Object of Target != Object of Competitor.
+
+- AF-Condition:
+  - Color of Target != Color of Competitor.
+  - Object of Target = Object of Competitor.
+
+- DF-Condition:
+  - Color of Target != Color of Competitor.
+  - Object of Target != Object of Competitor.
+
+- Distractors, all conditions:
+  - Both distractors have to differ in color and object identity from both target and competitor.
+
+The competitor and distractors were matched iteratively to a target.
+One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
+<!-- NOTE: (SC) I don't understand this bit. Need clarification. -->
+
+The set of four objects (quadruple) was formed separately for each of the three focus conditions.
+After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following requirements were met:
+
+- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
+- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
+- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
+
+Following these criteria, one randomized list for each subject was produced.
+The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
+<!-- NOTE: (SC) Which first list? -->
+In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
+
+The python code for the randomization is available at the following link: <https://github.com/SBRitter/fruits-randomization>.
+
+# Norming study {#norming}
+
+Here we specify in detail the selection of the stimuli for the production study.
 
@@
 
-The selection of stimuli was informed by a norming study for which we selected twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs). 
-Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain few voiceless segments.
+The selection of stimuli was informed by a norming study for which we have chosen twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
+Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain as few voiceless segments as possible.
 
-For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using [gimp](http://www.gimp.org). 
+For each of the FOODs and NON-FOODs, we created colored versions by image manipulation using [Gimp](http://www.gimp.org).
 Images of all individual objects were collected from internet databases containing copyright-free high-resolution images (e.g. [Pixabay](https://pixabay.com)).
-During the manipulation process, the background of the pictures was replaced by a white background. 
-In order to change the color of the objects, a layer in the respective color was created and overlaid on top of the original image using “Color” as the layer mode. 
+During the manipulation process, the background of the pictures was replaced with a white background.
+In order to change the color of the objects, a layer in the respective color was created and overlaid on top of the original image using `Color` as the layer mode.
 The hexadecimal color codes for the colors that we used are listed below:
 
-\noindent Blue: #29429f  
-\noindent Green: #3f8535  
-\noindent Red: #9d1c1c  
-\noindent Purple: #6d1b79  
-\noindent Brown: #2a1d11  
-\noindent Yellow: #e3c917  
-\noindent Orange: #ff8400  
-\noindent Orange (potatoes): #ff6600  
-\noindent Black: #000000  
-\noindent Grey: #FFFFFF
+- Blue: #29429f
+- Green: #3f8535
+- Red: #9d1c1c
+- Purple: #6d1b79
+- Brown: #2a1d11
+- Yellow: #e3c917
+- Orange: #ff8400
+- Orange (potatoes): #ff6600
+- Black: #000
+- Grey: #fff
 
-All pictures with natural and manipulated colors are available here: [https://osf.io/rdtx5/](https://osf.io/rdtx5/).
+All pictures with natural and manipulated colors are available here: <https://osf.io/rdtx5/>.
 
@@
 The four NON-FOODs were subjectively selected to represent color agnostic objects which can and do come in a variety of colors.
-All objects were chosen such that their respective German nouns were either feminine singular (e.g. "die Banana" 'the banana') or plural (e.g. "die Trauben" 'the grapes').
+All objects were chosen such that their respective German nouns were either feminine singular (e.g. *die Banana* 'the banana') or plural (e.g. *die Trauben* 'the grapes').
 
@@
 
-## The norming study
+## Participants and procedures
 
-One-hundred German native speakers participated in a norming study using the crowd sourcing platform [Prolific]](https://www.prolific.ac). 
+A hundred German native speakers participated in a norming study using the crowd sourcing platform [Prolific](https://www.prolific.ac).
 We presented all objects in different colors to our participants.
 FOODs came in 5 colors per object, NON-FOODs came in all nine colors.
-Participants were instructed to rate how typical they think the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design here: [https://github.com/stelaseldano/colour-typicality-norming](https://github.com/stelaseldano/colour-typicality-norming).
-The results of the norming study can be retrieved here: [https://osf.io/znpg5/](https://osf.io/znpg5/).
+Participants were instructed to rate how typical they thought the color for each object was, using a smooth slider ranging from 1 to 100 (see javascript for the experimental design here: <https://github.com/stelaseldano/colour-typicality-norming>).
+<!-- TODO: fix link to typicality results csv -->
+The results of the norming study can be retrieved here: <https://osf.io/znpg5/>.
 
-## Selection of experimental stimuli
+## Selection of experimental stimuli for the production study
 
-The norming ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
+The typicality ratings were subsequently used to select appropriate stimuli for the production study according to the following procedure:
 
@@
 
-For the critical focus condition (NF) this selection procedure resulted in 15 target FOODs (5 colors x 3 typicality categories):
+For the noun focus condition (NF) this selection procedure resulted in 15 target FOODs (5 colors x 3 typicality categories):
 
-\noindent atypical:  
-\noindent Yellow cherry (Gelbe Kirsche)  
-\noindent Green carrot (Grüne Möhre)  
-\noindent Red cucumber (Rote Gurke)  
-\noindent Orange grapes (Oangene Trauben)  
-\noindent Brown pepper (Braune Paprika)
-
-\noindent medium:  
-\noindent Yellow peas (Gelbe Erbsen)  
-\noindent Green tomato (Grüne Tomate)  
-\noindent Red apricot (Rote Aprikose)  
-\noindent Orange potatoes (Orangene Kartoffeln)  
-\noindent Brown banana (Braune Banane)
-
-\noindent typical:  
-\noindent Yellow lemon (Gelbe Zitrone)  
-\noindent Green green beans (Grüne Bohnen)  
-\noindent Red strawberry (Rote Erdbeere)  
-\noindent Orange mandarine (Orangene Mandarine)  
-\noindent Brown walnut (Braune Walnuss)
+- Atypical:
+  - Yellow cherry (*Gelbe Kirsche*).
+  - Green carrot (*Grüne Möhre*).
+  - Red cucumber (*Rote Gurke*).
+  - Orange grapes (*Oangene Trauben*).
+  - Brown pepper (*Braune Paprika*).
+- Medium:
+  - Yellow peas (*Gelbe Erbsen*).
+  - Green tomato (*Grüne Tomate*).
+  - Red apricot (*Rote Aprikose*).
+  - Orange potatoes (*Orangene Kartoffeln*).
+  - Brown banana (*Braune Banane*).
+- Typical:
+  - Yellow lemon (*Gelbe Zitrone*).
+  - Green green beans (*Grüne Bohnen*).
+  - Red strawberry (*Rote Erdbeere*).
+  - Orange mandarine (*Orangene Mandarine*).
+  - Brown walnut (*Braune Walnuss*).
 
@@
 
-\noindent Yellow sunglasses (Gelbe Sonnenbrille)  
-\noindent Yellow socks (Gelbe Socken)  
-\noindent Yellow clothes peg (Gelbe Wäscheklammer)  
-\noindent Green sunglasses (Grüne Sonnenbrille)  
-\noindent Green socks (Grüne Socken)  
-\noindent Green Paper clip (Grüne Büroklammer)  
-\noindent Red socks (Rote Socken)  
-\noindent Red paper clip (Rote Büroklammer)  
-\noindent Red clothes peg (Rote Wäscheklammer)  
-\noindent Orange socks (Orangene Socken)  
-\noindent Orange paper clip (Orangene Büroklammer)  
-\noindent Orange clothes peg (Orangene Wäscheklammer)  
-\noindent Brown sunglasses (Braune Sonnenbrille)  
-\noindent Brown paper clip (Braune Büroklammer)  
-\noindent Brown clothes peg (Braune Wäscheklammer)
+- Yellow sunglasses (*Gelbe Sonnenbrille*).
+- Yellow socks (*Gelbe Socken*).
+- Yellow clothes peg (*Gelbe Wäscheklammer*).
+- Green sunglasses (*Grüne Sonnenbrille*).
+- Green socks (*Grüne Socken*).
+- Green Paper clip (*Grüne Büroklammer*).
+- Red socks (*Rote Socken*).
+- Red paper clip (*Rote Büroklammer*).
+- Red clothes peg (*Rote Wäscheklammer*).
+- Orange socks (*Orangene Socken*).
+- Orange paper clip (*Orangene Büroklammer*)
+- Orange clothes peg (*Orangene Wäscheklammer*).
+- Brown sunglasses (*Braune Sonnenbrille*).
+- Brown paper clip (*Braune Büroklammer*).
+- Brown clothes peg (*Braune Wäscheklammer*).
 
-The pairing of targets and competitors was randomized for each subject, with the only constraint that the competitor had the same color as the target object (e.g.
-if blue banana was the target, blue grapes is a possible competitor) (see randomization section below for more details).
+For the Adjective and Adjective/Noun conditions (AF + ANF), we distributed FOODs and NON-FOODs to fulfill the following constraints: (a) each target FOOD appeared 3 times and (b) each color appeared as a target color 14 times.
 
-For the filler focus conditions (AF + DF), we distributed FOODs and NON-FOODs to fulfil the following constraints: (a) each target FOOD appeared 3 times and (b) each color appeared as a traget color 14 times.
+For all three focus conditions, a subset of distractors was selected from the initial superset.
+The distractors were either FOODS that were neither used as targets nor as competitors (avocado, egg plant, pear, zucchini) or NON-FOODs.
+Within each given trial, the distractors did not share color nor object identity with neither the target nor the competitor.
 
-For all three focus conditions, a subset of distractors was selected from the initial superset: Distractors were either FOODS that were neither used as targets nor as competitors (avocado, egg plant, pear, zucchini) or NON-FOODs.
-Within each given trial, the distractors did neither share color nor object identity with neither the target nor the competitor.
-
-Overall, the sets of target, competitors and distractors are combined such that all five colors occurred equally often throughout the experiment (= 28 times).
-
-# Randomization
-
-For each trial, targets, competitors, and distractors are chosen in a randomized way, fulfilling the following requirements:
-
-- NF-Condition:  
-Color of Target = Color of Competitor  
-Object of Target != Object of Competitor
-
-- AF-Condition:  
-Color of Target != Color of Competitor  
-Object of Target = Object of Competitor
-
-- DF-Condition:  
-Color of Target != Color of Competitor  
-Object of Target != Object of Competitor
-
-- All conditions:  
-Both distractors have to differ in color and object identity from both target and competitor.
-
-The competitor and distractors are matched iteratively to a target. 
-One competitor could only be used twice or a third time if all other competitors that were left had been considered and prove inappropriate.
-
-The set of four objects (quadruple) was formed separately for each condition. 
-After the three lists had been compiled, they were merged. 
-The sequence of quadruples was randomized such that the following requirements were met:
-
-- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
-- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
-- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
-
-Following these criteria, one randomized list for each subject was produced. 
-The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session. 
-In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
-
-The python code for the randomization is available here: [https://github.com/SBRitter/fruits-randomization](https://github.com/SBRitter/fruits-randomization).
+Overall, the sets of target, competitors and distractors were combined such that all five colors occurred equally often throughout the experiment (i.e. 28 times).

### 2021-01-20 RR_manuscript/Draft_RR.tex

--- 2021-01-16 RR_manuscript/Draft_RR.tex
@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011; Gelman \& Loken, 2014).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al., 2011).
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al., 2018; Botvinik-Nezer et al., 2020; Starns et al., 2019).
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (\enquote{I knew it}, Nickerson 1998), and perceiving events as being plausible in hindsight (\enquote{I knew it all along}, Fischhoff 1975).
-In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
+Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (``I knew it'', Nickerson, 1998), and perceiving events as being plausible in hindsight (``I knew it all along'', Fischhoff, 1975).
+In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g., Simmons et al., 2011; Gelman \& Loken, 2014).
 These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).
 
-While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons et al., 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 
-In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis.
+In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
 Analytical approaches and consequently the results varied widely between teams.
@@
 Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g., Jongman, Wayland, \& Wong, 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.~Ladd 2008).
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch ({\textbf{???}}; Foulkes \& Docherty, 2006; White, Payne, \& Mattys, 2009).
+The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
 
@@
 
-(2a) \enquote{I can't bear ANOTHER meeting on zoom.}
+(2a) \enquote{I can't bear ANOTHER meeting on zoom.}\\
 (2b) \enquote{I can't bear another meeting on ZOOM.}
@@
 Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
-Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
+For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
 We could also measure the value or time of the minimum or maximum f0 value.
@@
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.~????).
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice, 1975).
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
@@
 
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.~2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.~2011, Paraboni et al.~2007, Rubio-Fernandez 2016).
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Rubio-Fernández, 2016; Sedivy, 2003; Westerbeek, Koolen, \& Maes, 2015), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts, Maes, Noordman, \& Jansen, 2011; Paraboni, Van Deemter, \& Masthoff, 2007; Rubio-Fernández, 2016).
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen et al.~(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection (Gatt et al.~2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+For example, Degen, Hawkins, Graf, Kreiss, and Goodman (2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
+This account, however, has mainly focused on content selection (Gatt, Gompel, Deemter, \& Krahmer, 2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.~Ladd 2008).
+Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd, 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
@@
 
-Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:
+Assuming that the underlying distribution of effect sizes is normal (Knight, 2000), the standard error of \(\tau^2\) can be calculated with the formula:
 
@@
 The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
-The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight 2000).
+The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight, 2000).
 The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, Simpson, \& Betancourt, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
 We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2018).
 The code for the model can be found here: INSERT LINK.
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-arts2011overspecification}{}%
+Arts, A., Maes, A., Noordman, L. G., \& Jansen, C. (2011). Overspecification in written instruction. \emph{Linguistics}, \emph{49}(3), 555--574.
+
+\leavevmode\hypertarget{ref-botvinik2020variability}{}%
+Botvinik-Nezer, R., Holzmeister, F., Camerer, C.
+F., Dreber, A., Huber, J., Johannesson, M., \ldots{} others.
+(2020).
+Variability in the analysis of a single neuroimaging dataset by many teams.
+\emph{Nature}, 1--7.
+
+\leavevmode\hypertarget{ref-box1976science}{}%
+Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.
+
+\leavevmode\hypertarget{ref-brms}{}%
+Bürkner, P.-C. (2018). Advanced Bayesian multilevel modeling with the R package brms. \emph{The R Journal}, \emph{10}(1), 395--411. \url{https://doi.org/10.32614/RJ-2018-017}
+
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
@@
 
+\leavevmode\hypertarget{ref-degen2020redundancy}{}%
+Degen, J., Hawkins, R. D., Graf, C., Kreiss, E., \& Goodman, N. D. (2020). When redundancy is useful: A bayesian approach to ``overinformative'' referring expressions. \emph{Psychological Review}.
+
+\leavevmode\hypertarget{ref-de2014thought}{}%
+De Groot, A. D. (2014). \emph{Thought and choice in chess} (Vol. 4). Walter de Gruyter GmbH \& Co KG.
+
 \leavevmode\hypertarget{ref-dice1945}{}%
@@
 Egger, M., Smith, G. D., Schneider, M., \& Minder, C. (1997). Bias in meta-analysis detected by a simple, graphical test. \emph{British Medical Journal}, \emph{315}, 629--634.
+
+\leavevmode\hypertarget{ref-fischhoff1975hindsight}{}%
+Fischhoff, B.
+(1975).
+Hindsight is not equal to foresight: The effect of outcome knowledge on judgment under uncertainty.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{1}(3), 288.
 
@@
 
+\leavevmode\hypertarget{ref-gatt2013we}{}%
+Gatt, A., Gompel, R. P. van, Deemter, K. van, \& Krahmer, E. (2013). Are we bayesian referring expression generators. In. Cognitive Science Society.
+
+\leavevmode\hypertarget{ref-gelman2014statistical}{}%
+Gelman, A., \& Loken, E.
+(2014).
+The statistical crisis in science: Data-dependent analysis--a" garden of forking paths"--explains why many statistically significant comparisons don't hold up.
+\emph{American Scientist}, \emph{102}(6), 460--466.
+
+\leavevmode\hypertarget{ref-Gelman_2017}{}%
+Gelman, A., Simpson, D., \& Betancourt, M.
+(2017).
+The prior can often only be understood in the context of the likelihood.
+\emph{Entropy}, \emph{19}(10), 1--13.
+\url{https://doi.org/10.3390/e19100555}
+
+\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
+Gordon, M., \& Roettger, T. (2017). Acoustic correlates of word stress: A cross-linguistic survey. \emph{Linguistics Vanguard}, \emph{3}(1), 1--11.
+
+\leavevmode\hypertarget{ref-grice1975logic}{}%
+Grice, H. P. (1975). Logic and conversation. In \emph{Speech acts} (pp. 41--58). Brill.
+
+\leavevmode\hypertarget{ref-hawkins2004influence}{}%
+Hawkins, S., \& Nguyen, N. (2004). Influence of syllable-coda voicing on the acoustic properties of syllable-onset /l/ in English. \emph{Journal of Phonetics}, \emph{32}(2), 199--231.
+
+\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
+Jongman, A., Wayland, R., \& Wong, S. (2000). Acoustic characteristics of english fricatives. \emph{The Journal of the Acoustical Society of America}, \emph{108}(3), 1252--1263.
+
+\leavevmode\hypertarget{ref-knight2000}{}%
+Knight, K. (2000). \emph{Mathematical statistics}. Chapman; Hall, New York.
+
+\leavevmode\hypertarget{ref-koole2012rewarding}{}%
+Koole, S. L., \& Lakens, D. (2012). Rewarding replications: A sure and simple way to improve psychological science. \emph{Perspectives on Psychological Science}, \emph{7}(6), 608--614.
+
+\leavevmode\hypertarget{ref-ladd2008intonational}{}%
+Ladd, D. R. (2008). \emph{Intonational phonology}. Cambridge University Press.
+
 \leavevmode\hypertarget{ref-lau2006}{}%
@@
 
+\leavevmode\hypertarget{ref-lisker1977rapid}{}%
+Lisker, L. (1977). Rapid versus rabid: A catalogue of acoustic features that may cue the distinction. \emph{The Journal of the Acoustical Society of America}, \emph{62}(S1), S77--S78.
+
+\leavevmode\hypertarget{ref-lisker1986voicing}{}%
+Lisker, L. (1986). ``Voicing'' in English: A catalogue of acoustic features signaling /b/ versus /p/ in trochees. \emph{Language and Speech}, \emph{29}(1), 3--11.
+
+\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
+Nickerson, R. S. (1998). Confirmation bias: A ubiquitous phenomenon in many guises. \emph{Review of General Psychology}, \emph{2}(2), 175--220.
+
+\leavevmode\hypertarget{ref-nosek2014method}{}%
+Nosek, B. A., \& Lakens, D. (2014). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141.
+
+\leavevmode\hypertarget{ref-ogden2004}{}%
+Ogden, R. (2004). Non-modal voice quality and turn-taking in Finnish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
+
 \leavevmode\hypertarget{ref-open2015estimating}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+
+\leavevmode\hypertarget{ref-paraboni2007generating}{}%
+Paraboni, I., Van Deemter, K., \& Masthoff, J. (2007). Generating referring expressions: Making referents easy to identify. \emph{Computational Linguistics}, \emph{33}(2), 229--254.
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-roettger2019researcher}{}%
+Roettger, T. B. (2019). Researcher degrees of freedom in phonetic research. \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology}, \emph{10}(1).
+
+\leavevmode\hypertarget{ref-rotello2015more}{}%
+Rotello, C.
+M., Heit, E., \& Dubé, C.
+(2015).
+When more data steer us wrong: Replications with the wrong dependent measure perpetuate erroneous conclusions.
+\emph{Psychonomic Bulletin \& Review}, \emph{22}(4), 944--954.
+
+\leavevmode\hypertarget{ref-rubio2016redundant}{}%
+Rubio-Fernández, P. (2016). How redundant are redundant color adjectives? An efficiency-based analysis of color overspecification. \emph{Frontiers in Psychology}, \emph{7}, 153.
+
+\leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
+Sedivy, J.
+C.
+(2003).
+Pragmatic versus form-based accounts of referential contrast: Evidence for effects of informativity expectations.
+\emph{Journal of Psycholinguistic Research}, \emph{32}(1), 3--23.
+
+\leavevmode\hypertarget{ref-silberzahn2018many}{}%
+Silberzahn, R., Uhlmann, E.
+L., Martin, D.
+P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others.
+(2018).
+Many analysts, one data set: Making transparent how variations in analytic choices affect results.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337--356.
+
+\leavevmode\hypertarget{ref-simmons2011false}{}%
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2011).
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+
+\leavevmode\hypertarget{ref-stan}{}%
+Stan Development Team. (2019). Stan modeling language users guide and reference manual (Version 2.18.0). Stan Development Team. Retrieved from \url{http://mc-stan.org}
+
+\leavevmode\hypertarget{ref-starns2019assessing}{}%
+Starns, J.
+J., Cataldo, A.
+M., Rotello, C.
+M., Annis, J., Aschenbrenner, A., Bröder, A., \ldots{} Wilson, J.
+(2019).
+Assessing theoretical conclusions with blinded inference to investigate a potential inference crisis.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 335--349.
+
+\leavevmode\hypertarget{ref-sterling1959publication}{}%
+Sterling, T.
+D.
+(1959).
+Publication decisions and their possible effects on inferences drawn from tests of significance---or vice versa.
+\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
 
@@
 
+\leavevmode\hypertarget{ref-tukey1977exploratory}{}%
+Tukey, J. W. (1977). \emph{Exploratory data analysis} (Vol. 2). Reading, MA.
+
+\leavevmode\hypertarget{ref-tversky1974judgment}{}%
+Tversky, A., \& Kahneman, D. (1974). Judgment under uncertainty: Heuristics and biases. \emph{Science}, \emph{185}(4157), 1124--1131.
+
+\leavevmode\hypertarget{ref-van2005speech}{}%
+Van Heuven, V. J., \& Van Zanten, E. (2005). Speech rate as a secondary prosodic characteristic of polarity questions in three languages. \emph{Speech Communication}, \emph{47}(1-2), 87--99.
+
+\leavevmode\hypertarget{ref-wagenmakers2012agenda}{}%
+Wagenmakers, E.-J., Wetzels, R., Borsboom, D., Maas, H.
+L.
+van der, \& Kievit, R.
+A.
+(2012).
+An agenda for purely confirmatory research.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 632--638.
+
+\leavevmode\hypertarget{ref-westerbeek2015stored}{}%
+Westerbeek, H., Koolen, R., \& Maes, A. (2015). Stored object knowledge and the production of referring expressions: The case of color typicality. \emph{Frontiers in Psychology}, \emph{6}, 935.
+
 \leavevmode\hypertarget{ref-white2009}{}%
@@
 
+\leavevmode\hypertarget{ref-wicherts2006poor}{}%
+Wicherts, J. M., Borsboom, D., Kats, J., \& Molenaar, D. (2006). The poor availability of psychological research data for reanalysis. \emph{American Psychologist}, \emph{61}(7), 726.
+
+\leavevmode\hypertarget{ref-winter2014spoken}{}%
+Winter, B. (2014). Spoken language achieves robustness and evolvability by exploiting degeneracy and neutrality. \emph{BioEssays}, \emph{36}(10), 960--967.
+
 \endgroup

### 2021-01-20 RR_manuscript/Draft_RR.Rmd

--- 2021-01-16 RR_manuscript/Draft_RR.Rmd
@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the *inference crisis* (Rotello, Heit & Dubé 2015, Starns et al.
-2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, & Simonsohn, 2011, Gelman & Loken 2013).
+The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.
-Box 1976, Tukey 1977, de Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.
-2011).
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.
-Silberzahn et al.
-2018, Starns et al.
-2019, Botvinik-Nezer et al., 2020).
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ("I knew it", Nickerson 1998), and perceiving events as being plausible in hindsight ("I knew it all along", Fischhoff 1975).
+Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
 <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
 <!-- TR: Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased. -->
-In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole & Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
+In connection with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure [@roettger2019researcher].
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g. Simmons et al. 2011, Gelman & Loken 2013).
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
 These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, & Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare [@wicherts2006poor].
 
-While this issue has been widely discussed both from a conceptual point of view (Simmons et al.
-2011, Wagenmakers et al.
-2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.
+While this issue has been widely discussed both from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and its application in individual scientific fields [e.g.
 Wichert et al.
 2015, Charles et al.
-2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+2019, @roettger2019researcher], there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 
-In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
+In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
 Analytical approaches and consequently the results varied widely between teams.
@@
 The acoustic parameters of one category are usually asynchronous, i.e.
-they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.
-Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
+they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g., @jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
 A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
-This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
+This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) (Hawkins & Nguyen, 2004).
+For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.
-the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.
-Gordon & Roettger, 2017).
+the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.
-Ladd 2008).
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g. van Heuven & van Zanten 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2009; @white2009].
+The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
 
@@
 Even if we know that we want to compare fundamental frequency of only the word *another* across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified. 
-Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
+For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint. 
 We could also measure the value or time of the minimum or maximum f0 value. 
@@
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al.).
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. ????). <!-- year needed -->
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
@@
 
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003, Westerbeek et al.
-2015, Rubio-Fernandez 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
-2011, Paraboni et al.
-2007, Rubio-Fernandez 2016).
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen et al.
-(2020) showed that modifiers that are less typical for a given referent (e.g.
+For example, @degen2020redundancy showed that modifiers that are less typical for a given referent (e.g.
 a blue banana) are more likely to be used in an over-informative scenario (e.g.
 when there is just one banana).
-This account, however, has mainly focused on content selection (Gatt et al.
-2013), i.e.
+This account, however, has mainly focused on content selection [@gatt2013we], i.e.
 whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g.
-Ladd 2008).
+Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
@@
 
-Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of $\tau^2$ can be calculated with the formula:
+Assuming that the underlying distribution of effect sizes is normal [@knight2000], the standard error of $\tau^2$ can be calculated with the formula:
 
@@
 The respective standard errors $\text{se}_i$ will be included to fit a measurement-error model.
-The likelihood of $\eta_i$ is assumed to be normally distributed (Knight 2000).
+The likelihood of $\eta_i$ is assumed to be normally distributed [@knight2000].
 The analysis teams will be included as a group-level effect (i.e., random effect).
-For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
+For each population-level parameter $\beta_n$ (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors [@Gelman_2017], which are normally distributed and centered at 0 with a standard deviation of 1.
 <!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
@@
 We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
-The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
+The analysis will be conducted in R [@R-base] and fit using Stan [@stan] via the R package brms [@brms].
 <!-- TODO: add link to code of the meta-analytical model -->

### 2021-01-20 RR_manuscript/Draft_RR.Rmd

--- 2021-01-18 RR_manuscript/Draft_RR.Rmd
@@
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
-The likelihood of $\eta_i$ is assumed to correspond to a normal distribution (Knight 2000).
+The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
 The analysis teams will constitute the group-level effect (i.e., random effect, `(1 | team)`).

### 2021-01-25 RR_manuscript/Draft_RR.Rmd

--- 2021-01-18 RR_manuscript/Draft_RR.Rmd
@@
 
-floatsintext      : yes
+floatsintext      : no
 figurelist        : no
@@
     number_sections: true
-    latex_engine: xelatex
 header-includes:
   - \usepackage{cleveref}
-  - \usepackage{changes}
-  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
-  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
-  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 ---
@@
 ```{r setup, include = FALSE}
-knitr::opts_knit$set(root.dir = here::here())
 library("papaja")
@@
 
-In text ref to Figure \@ref(fig:forkingPaths)
+```{r forkingPaths, echo=FALSE, fig.cap="Illustrations of the analytical flexibility associated with acoustic analyses.
+(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch", fig.dim = c(6, 2)}
 
-(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
-
-```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
-
-knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
+knitr::include_graphics("/RR_manuscript/Draft_RR_files/figure-latex/ForkingPaths.png")
 
@@
 -->
+<!-- NOTE: (SC) shouldn't we standardise all variables? -->
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
-the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
+the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables [???].
 Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017] in R [@r-core-team2020].
@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel regression model:
 
@@
 <!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there are no divergent transitions.
+<!-- NOTE: (SC) we might not include pop-level parameters. -->
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling of the posterior distribution and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 The analysis will be conducted in R [@r-core-team2020] and fit using Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017].
@@
 
-The posterior probability of the population-level intercept $\alpha$ will give us an estimate of the range of probable values of the standardized effect size $\hat{\eta}$.
-This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \@ref(ana-factors).
-Crucially, the posterior probability of $\sigma_{\alpha_{\text{team}}}$ (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+<!-- TODO: explain how the MA model will be interpreted. -->
 
@@
 
-### Analytical and demographic factors affecting effect sizes {#ana-factors}
+### Analytical factors affecting effect sizes
 
-As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-The deviation score $\delta_i$, which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
-See minutes.}]{difference between the meta-analytical mean} ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
+As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below).
+The deviation score $\delta_i$, which serves as the dependent variable in this analysis, will be the difference between the meta-analytical mean ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
+<!--ecoRR: absolute value of the difference between the meta-analytic mean Zr (or y) and the individual Zr (or y) estimate for each analysis.
+We will use the Box-Cox transformation on the absolute values of deviation scores to achieve an approximately normal distribution (c.f.
+Fanelli and Ioannidis 2013, Fanelli et al.
+2017: supplement).
+-->
 <!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
@@
 <!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
-We will fit a single Bayesian regression model with $\delta_i$ as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
-<!-- TODO: add brm info on factors analysis model -->
-
-**Analytical factors**. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
+These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+We will model the effect of the following predictors:
 
@@
 - *Data exclusion*, whether data has been excluded or not.
+- *Demographic factors* of analysis teams and analysts.
 
@@
 
-<!-- TODO: explain how the demographic factors will be entered in the factors analysis -->
-
-**Demographic factors**.
-We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
+We will include the following demographic factors about both the analysis teams:
 

### 2021-01-25 RR_manuscript/Draft_RR.tex

--- 2021-01-18 RR_manuscript/Draft_RR.tex
@@
   english,
-  man,floatsintext]{apa6}
+  man]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis\newline\indent Word count: X}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
 \usepackage{lineno}
@@
 \usepackage{cleveref}
-\usepackage{changes}
-\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
-\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
-\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 \ifxetex
@@
 
-In text ref to Figure \ref{fig:forkingPaths}
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{/Users/stefano/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
-\end{figure}
-
 Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
-Do we average the domain or do we measure a specific point in time?
+Do we measure average the domain or do we measure a specific point in time?
 Do we measure fundamental frequency or intensity?
-When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
-This plurality of analytical paths is illustrated in figure X.
-When comparing two utterance such as 2a and 2b, there are many things to consider.
-Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
-Fopr example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
-And the garden of forking paths does not stop here.
-In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
-Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
+When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes (see Figure x)
 
@@
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables {[}???{]}.
 Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017) in R (R Core Team, 2020).
@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel regression model:
 
@@
 We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling of the posterior distribution and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017).
 The code used to run the model can be found here: INSERT LINK.
-
-The posterior probability of the population-level intercept \(\alpha\) will give us an estimate of the range of probable values of the standardized effect size \(\hat{\eta}\).
-This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
-Crucially, the posterior probability of \(\sigma_{\alpha_{\text{team}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 
-\hypertarget{ana-factors}{%
-\subsubsection{Analytical and demographic factors affecting effect sizes}\label{ana-factors}}
+\hypertarget{analytical-factors-affecting-effect-sizes}{%
+\subsubsection{Analytical factors affecting effect sizes}\label{analytical-factors-affecting-effect-sizes}}
 
-As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-The deviation score \(\delta_i\), which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
-See minutes.}]{difference between the meta-analytical mean} (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
-We will fit a single Bayesian regression model with \(\delta_i\) as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
-
-\textbf{Analytical factors}. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
+As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below).
+The deviation score \(\delta_i\), which serves as the dependent variable in this analysis, will be the difference between the meta-analytical mean (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
+These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
+We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
+We will model the effect of the following predictors:
 
@@
   \emph{Data exclusion}, whether data has been excluded or not.
+\item
+  \emph{Demographic factors} of analysis teams and analysts.
 \end{itemize}
@@
 
-\textbf{Demographic factors}.
-We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
+We will include the following demographic factors about both the analysis teams:
 

### 2021-01-25 RR_manuscript/Draft_RR.Rmd
added summary

@@
 In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
-Analytical approaches and consequently the results varied widely between teams.
+Analytical approaches and scientific conclusions varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
@@
 The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
-Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
-
-<!-- TODO: SUMUP neuroscience, cognitive modeling, clinical, predictive models -->
+Similar crowd-sourced studies recruiting independent analyst teams showed similar results: 
+Both Dulith et al. (2019) ad Starns et al. (2019) investigated analysts choices when inferring theoretical constructs based on the same data set using computational models.
+Both studies reveal vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.
+(accepted) on analytical flexibility in ecology and Botvinik-Nezer et al.
+(2020) on neuroimaging data).
+Bastiaansen et al. (2019) crowdsourced clinical recommendations based on data analysis of an individual patient. 
+Results suggests that analysis team differed substantially regarding decisions related to both the statistical analysis of the data set and the theoretical rationale behind interpreting the statistical results, indicating that there are multiple layers for degrees of freedom that interact with each other.
 
@@
 In these studies the data sets were fixed and data collection or measurement could not be changed. 
-<!-- JC: any particular reason to favor data table over data set?
---> <!-- TR: I think my reasoning was data set can be data table or raw data.
-Data table is the numerical derivation of the raw data.
-Maybe not a useful distinction?-->
-
 However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
@@
 Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa [@flake2019].
-To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
+
+To add to our understanding of how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
 

### 2021-01-26 RR_manuscript/Draft_RR.Rmd
:memo: - add sim code to RR

--- 2021-01-20 RR_manuscript/Draft_RR.Rmd
@@
 library(patchwork)
+library(brms)
+library(extraDistr)
 ```
@@
 ```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+my_seed <- 115116106
 ```
@@
 
+```{r meta-bm}
+set.seed(my_seed)
+n <- 12
+eta <- rnorm(n, 1, 0.5)
+se <- rhcauchy(n, 0.1)
+team <- letters[1:n]
+
+eta_tbl <- tibble(
+  eta,
+  se,
+  team
+)
+
+priors <- c(
+  prior(normal(0, 1), class = Intercept),
+  prior(cauchy(0, 1), class = sd)
+)
+
+meta_bm <- brm(
+  eta | se(se) ~
+    (1 | team),
+  data = eta_tbl,
+  prior = priors,
+  chain = 1,
+  seed = my_seed,
+  file = here::here("RR_manuscript", "cache", "meta_bm")
+)
+```
+
 Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).

### 2021-01-26 RR_manuscript/Draft_RR.tex
:memo: - render RR with plots and bib

--- 2021-01-18 RR_manuscript/Draft_RR.tex
@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit \& Dubé 2015, Starns et al.~2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011, Gelman \& Loken 2013).
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (Gelman \& Loken, 2014; often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, \& Simonsohn, 2011).
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (Botvinik-Nezer et al., 2020; e.g., Silberzahn et al., 2018; Starns et al., 2019).
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations (``I knew it,'' Nickerson 1998), and perceiving events as being plausible in hindsight (``I knew it all along,'' Fischhoff 1975).
-In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959, Koole \& Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
+Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
+In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g.~Simmons et al.~2011, Gelman \& Loken 2013).
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
 These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006, RECENT REF).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).
 
-While this issue has been widely discussed both from a conceptual point of view (Simmons et al.~2011, Wagenmakers et al.~2012, Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons, Nelson, \& Simonsohn, 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.~Jongman et al., 2000; Lisker, 1986; Summerfield, 1984; Winter, 2014).
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories {[}e.g., Jongman, Wayland, and Wong (2000); Lisker (1986); Summerfield, 1984; Winter (2014){]}.
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g.~Gordon \& Roettger, 2017).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g.~Ladd 2008).
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2009; White, Payne, \& Mattys, 2009).
+The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
 
@@
 
-(2a) ``I can't bear ANOTHER meeting on zoom.''
+(2a) ``I can't bear ANOTHER meeting on zoom.''\\
 (2b) ``I can't bear another meeting on ZOOM.''
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/stefano/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
@@
 \highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017) in R (R Core Team, 2020).
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}) in R (\textbf{r-core-team2020?}).
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
-The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
+The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight, 2000).
 The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
@@
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
-The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2020b), RStan (Stan Development Team, 2020a), and brms (Bürkner, 2017).
+The analysis will be conducted in R (\textbf{r-core-team2020?}) and fit using Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}).
 The code used to run the model can be found here: INSERT LINK.
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-burkner2017}{}%
-Bürkner, P.-C. (2017). Brms: An {R} package for {B}ayesian multilevel models using {S}tan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28.
+\leavevmode\hypertarget{ref-arts2011overspecification}{}%
+Arts, A., Maes, A., Noordman, L. G., \& Jansen, C. (2011). Overspecification in written instruction. \emph{Linguistics}, \emph{49}(3), 555--574.
+
+\leavevmode\hypertarget{ref-botvinik2020variability}{}%
+Botvinik-Nezer, R., Holzmeister, F., Camerer, C.
+F., Dreber, A., Huber, J., Johannesson, M., \ldots{} others.
+(2020).
+Variability in the analysis of a single neuroimaging dataset by many teams.
+\emph{Nature}, 1--7.
+
+\leavevmode\hypertarget{ref-box1976science}{}%
+Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.
 
@@
 
+\leavevmode\hypertarget{ref-de2014thought}{}%
+De Groot, A. D. (2014). \emph{Thought and choice in chess} (Vol. 4). Walter de Gruyter GmbH \& Co KG.
+
+\leavevmode\hypertarget{ref-degen2020redundancy}{}%
+Degen, J., Hawkins, R. D., Graf, C., Kreiss, E., \& Goodman, N. D. (2020). When redundancy is useful: A bayesian approach to {``overinformative''} referring expressions. \emph{Psychological Review}.
+
 \leavevmode\hypertarget{ref-dice1945}{}%
@@
 
+\leavevmode\hypertarget{ref-gatt2013we}{}%
+Gatt, A., Gompel, R. P. van, Deemter, K. van, \& Krahmer, E. (2013). Are we bayesian referring expression generators. Cognitive Science Society.
+
+\leavevmode\hypertarget{ref-gelman2014statistical}{}%
+Gelman, A., \& Loken, E.
+(2014).
+The statistical crisis in science: Data-dependent analysis--a" garden of forking paths"--explains why many statistically significant comparisons don't hold up.
+\emph{American Scientist}, \emph{102}(6), 460--466.
+
+\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
+Gordon, M., \& Roettger, T. (2017). Acoustic correlates of word stress: A cross-linguistic survey. \emph{Linguistics Vanguard}, \emph{3}(1), 1--11.
+
+\leavevmode\hypertarget{ref-grice1975logic}{}%
+Grice, H. P. (1975). Logic and conversation. In \emph{Speech acts} (pp. 41--58). Brill.
+
+\leavevmode\hypertarget{ref-hawkins2004influence}{}%
+Hawkins, S., \& Nguyen, N. (2004). Influence of syllable-coda voicing on the acoustic properties of syllable-onset /l/ in {E}nglish. \emph{Journal of Phonetics}, \emph{32}(2), 199--231.
+
+\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
+Jongman, A., Wayland, R., \& Wong, S. (2000). Acoustic characteristics of english fricatives. \emph{The Journal of the Acoustical Society of America}, \emph{108}(3), 1252--1263.
+
+\leavevmode\hypertarget{ref-knight2000}{}%
+Knight, K. (2000). \emph{Mathematical statistics}. Chapman; Hall, New York.
+
+\leavevmode\hypertarget{ref-koole2012rewarding}{}%
+Koole, S. L., \& Lakens, D. (2012). Rewarding replications: A sure and simple way to improve psychological science. \emph{Perspectives on Psychological Science}, \emph{7}(6), 608--614.
+
+\leavevmode\hypertarget{ref-ladd2008intonational}{}%
+Ladd, D. R. (2008). \emph{Intonational phonology}. Cambridge University Press.
+
 \leavevmode\hypertarget{ref-lau2006}{}%
@@
 
-\leavevmode\hypertarget{ref-ogden2009}{}%
-Ogden, R. (2009). \emph{An introduction to {E}nglish phonetics}. Edinburgh University Press.
+\leavevmode\hypertarget{ref-lisker1977rapid}{}%
+Lisker, L. (1977). Rapid versus rabid: A catalogue of acoustic features that may cue the distinction. \emph{The Journal of the Acoustical Society of America}, \emph{62}(S1), S77--S78.
+
+\leavevmode\hypertarget{ref-lisker1986voicing}{}%
+Lisker, L. (1986). {``Voicing''} in {E}nglish: A catalogue of acoustic features signaling /b/ versus /p/ in trochees. \emph{Language and Speech}, \emph{29}(1), 3--11.
+
+\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
+Nickerson, R. S. (1998). Confirmation bias: A ubiquitous phenomenon in many guises. \emph{Review of General Psychology}, \emph{2}(2), 175--220.
+
+\leavevmode\hypertarget{ref-nosek2014method}{}%
+Nosek, B. A., \& Lakens, D. (2014). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141.
+
+\leavevmode\hypertarget{ref-ogden2004}{}%
+Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
 
@@
 
-\leavevmode\hypertarget{ref-r-core-team2020}{}%
-R Core Team. (2020). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria.
+\leavevmode\hypertarget{ref-paraboni2007generating}{}%
+Paraboni, I., Van Deemter, K., \& Masthoff, J. (2007). Generating referring expressions: Making referents easy to identify. \emph{Computational Linguistics}, \emph{33}(2), 229--254.
 
-\leavevmode\hypertarget{ref-stan-development-team2020a}{}%
-Stan Development Team. (2020a). RStan: The r interface to stan. R package version 2.21.2.
+\leavevmode\hypertarget{ref-roettger2019researcher}{}%
+Roettger, T. B. (2019). Researcher degrees of freedom in phonetic research. \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology}, \emph{10}(1).
 
-\leavevmode\hypertarget{ref-stan-development-team2020}{}%
-Stan Development Team. (2020b). Stan modeling language users guide and reference manual, 2.25.
+\leavevmode\hypertarget{ref-rotello2015more}{}%
+Rotello, C.
+M., Heit, E., \& Dubé, C.
+(2015).
+When more data steer us wrong: {R}eplications with the wrong dependent measure perpetuate erroneous conclusions.
+\emph{Psychonomic Bulletin \& Review}, \emph{22}(4), 944--954.
+
+\leavevmode\hypertarget{ref-rubio2016redundant}{}%
+Rubio-Fernández, P. (2016). How redundant are redundant color adjectives? An efficiency-based analysis of color overspecification. \emph{Frontiers in Psychology}, \emph{7}, 153.
+
+\leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
+Sedivy, J.
+C.
+(2003).
+Pragmatic versus form-based accounts of referential contrast: Evidence for effects of informativity expectations.
+\emph{Journal of Psycholinguistic Research}, \emph{32}(1), 3--23.
+
+\leavevmode\hypertarget{ref-silberzahn2018many}{}%
+Silberzahn, R., Uhlmann, E.
+L., Martin, D.
+P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others.
+(2018).
+Many analysts, one data set: Making transparent how variations in analytic choices affect results.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337--356.
+
+\leavevmode\hypertarget{ref-simmons2011false}{}%
+Simmons, J.
+P., Nelson, L.
+D., \& Simonsohn, U.
+(2011).
+False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
+\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+
+\leavevmode\hypertarget{ref-starns2019assessing}{}%
+Starns, J.
+J., Cataldo, A.
+M., Rotello, C.
+M., Annis, J., Aschenbrenner, A., Bröder, A., \ldots{} Wilson, J.
+(2019).
+Assessing theoretical conclusions with blinded inference to investigate a potential inference crisis.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 335--349.
+
+\leavevmode\hypertarget{ref-sterling1959publication}{}%
+Sterling, T.
+D.
+(1959).
+Publication decisions and their possible effects on inferences drawn from tests of significance---or vice versa.
+\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
 
@@
 
+\leavevmode\hypertarget{ref-wicherts2006poor}{}%
+Wicherts, J. M., Borsboom, D., Kats, J., \& Molenaar, D. (2006). The poor availability of psychological research data for reanalysis. \emph{American Psychologist}, \emph{61}(7), 726.
+
+\leavevmode\hypertarget{ref-winter2014spoken}{}%
+Winter, B. (2014). Spoken language achieves robustness and evolvability by exploiting degeneracy and neutrality. \emph{BioEssays}, \emph{36}(10), 960--967.
+
 \end{CSLReferences}

### 2021-01-27 RR_manuscript/Draft_RR.Rmd
:memo: - edit RR section on factor analysis

@@
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
+The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
 
@@
 The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
-the variance $\sigma^2_{\alpha_{\text{team}}}$, see \Cref{s:meta-est}).
+the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
 Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
@@
 \eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
-\mu_i       & = \alpha + \alpha_{\text{team}[i]} \\
+\mu_i       & = \alpha + \alpha_{\text{t}[i]} \\
 \alpha      & \sim \text{Normal}(0, 1) \\
-\sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
+\sigma_{\alpha_{\text{t}}} & \sim \text{HalfCauchy}(0, 1) \\
 \sigma_i    & = \text{se}_i
@@
 The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{team}[i]}$ ($HalfCauchy(0, 1)$).
+We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
 <!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
@@
 This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \@ref(ana-factors).
-Crucially, the posterior probability of $\sigma_{\alpha_{\text{team}}}$ (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+Crucially, the posterior probability of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-The deviation score $\delta_i$, which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
-See minutes.}]{difference between the meta-analytical mean} ($\hat{\eta}$) and the individual standardized effect size of each analysis ($\eta_i$).
+We will fit a single Bayesian regression model with each team's group-level coefficient $\alpha_{\text{t}[i]}$ as the outcome variable, and the analytical and demographic factors described below as predictors.
+The coefficient $\alpha_{\text{t}[i]}$ can be interpreted as the deviation score of the team's $\eta_i$ from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
+Since each $\alpha_{\text{t}[i]}$ comes with uncertainty, quantified by its standard deviation $\sigma_{\alpha_{\text{t}[i]}}$, we will fit a measurement-error model, as we did in the meta-analytical model above.
+The formula of the model is the following (see the description of the predictors below for the meaning of acronyms):
+
+$$
+\begin{aligned}
+\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
+\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
+ & \qquad\qquad +\upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
+\iota      & \sim \text{Normal}(0, 1) \\
+\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
+resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
+belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
+\sigma_i    & = \sigma_{\alpha_{t[i]}}
+\end{aligned}
+$$
+
+The likelihood of $\alpha_{t[i]}$ is a normal distribution.
+The mean is based on the overall intercept $i$ and on the $\upsilon$ coefficient of each predictor.
+The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
+As the prior for $i$ and $\upsilon$ we will use a normal distribution with mean 0 and standard deviation 1.
+<!-- TODO: add explanation of me() predictors resp and belf -->
+
 <!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
@@
 <!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
-We will fit a single Bayesian regression model with $\delta_i$ as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
+
 <!-- TODO: add brm info on factors analysis model -->
@@
 
-- *Measure of uniqueness* of individual analyses for the set of predictors in each model.
-- *Measure of conservativeness* of the model specification.
-- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out.
-- *Number of models* the teams will report to have run.
-- *Major dimension* that has been measured to answer the research question.
-- *Temporal window* that the measurement is taken over.
-- *Data exclusion*, whether data has been excluded or not.
+- *Measure of uniqueness* [numeric] of individual analyses for the set of predictors in each model ($uniq_i$).
+- *Measure of conservativeness* [numeric] of the model specification, as the number of random/group-level effects included ($cons_i$).
+- *Number of post-hoc changes to the acoustic measurements* [numeric] the teams will report to have carried out ($phoc_i$).
+- *Number of models* [numeric] the teams will report to have run ($modn_i$).
+- *Major dimension* [categorical] that has been measured to answer the research question ($mdim_i$).
+- *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
+- *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).
 
@@
 For our purposes, we will treat predictors as species and individual analyses as sites.
-The SDI for a pair of analyses $(X, Y)$ can be obtained using the following formula:
+For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:
 
@@
 
-where $|X \cap Y|$ is the number of variables common to both models, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
+where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
 
@@
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package (Baselga et al.
-2018).
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.
-frequency center of gravity, harmonics difference, etc.), other measures (e.g.
+The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g.
+frequency center of gravity, harmonics difference, etc.), *other measures* (e.g.
 principal components, vowel dispersion, etc.)
@@
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: segment, syllable, word, phrase.
+We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*.
 
@@
 
-**Demographic factors**.
-We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
+**Demographic factors**. We will include the following demographic factors about the teams:
 
-- *Research experience* as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
-- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
+- *Research experience* [numeric] as the elapsed time from PhD award. Negative values will indicate that the person is a student or graduate studens ($rexp_i$).
+- *Initial belief* [numeric] in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire ($belf_i$).
 

### 2021-01-27 RR_manuscript/Draft_RR.tex
:memo: - render RR + bib updates

@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
+Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger, 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
 In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
+The latter can also be expressed by global vs local pitch modulations (Van Heuven, Haan, Gussenhoven, \& Warner, 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
 Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
@@
 
-(2a) ``I can't bear ANOTHER meeting on zoom.''\\
+(2a) ``I can't bear ANOTHER meeting on zoom.''
 (2b) ``I can't bear another meeting on ZOOM.''
@@
 (A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box'\,'; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
+The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
 \end{figure}
@@
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.~????).
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis {[}e.g.~wicherts2016{]}.
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
@@
 To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
-The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{team}}}\), see \Cref{s:meta-est}).
+The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
 Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
@@
 \highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}) in R (\textbf{r-core-team2020?}).
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017) in R (R Core Team, 2020).
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{team}[i]}\) (\(HalfCauchy(0, 1)\)).
+We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{t}[i]}\) (\(HalfCauchy(0, 1)\)).
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
-The analysis will be conducted in R (\textbf{r-core-team2020?}) and fit using Stan (\textbf{stan-development-team2020?}), RStan (\textbf{stan-development-team2020a?}), and brms (\textbf{burkner2017?}).
+The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017).
 The code used to run the model can be found here: INSERT LINK.
@@
 This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
-Crucially, the posterior probability of \(\sigma_{\alpha_{\text{team}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+Crucially, the posterior probability of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-The deviation score \(\delta_i\), which serves as the dependent variable in this analysis, will be the \highlight[id=SC, comment = {We might wanna fit a me model.
-See minutes.}]{difference between the meta-analytical mean} (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
-We will fit a single Bayesian regression model with \(\delta_i\) as the outcome variable, and the analytical and demographic factors described in the following paragraphs as predictors.
+We will fit a single Bayesian regression model with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
+The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
+Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytical model above.
+The formula of the model is the following (see the description of the predictors below for the meaning of acronyms):
+
+\[
+\begin{aligned}
+\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
+\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
+ & \qquad\qquad +\upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
+\iota      & \sim \text{Normal}(0, 1) \\
+\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
+resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
+belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
+\sigma_i    & = \sigma_{\alpha_{t[i]}}
+\end{aligned}
+\]
+
+The likelihood of \(\alpha_{t[i]}\) is a normal distribution.
+The mean is based on the overall intercept \(i\) and on the \(\upsilon\) coefficient of each predictor.
+The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
+As the prior for \(i\) and \(\upsilon\) we will use a normal distribution with mean 0 and standard deviation 1.
 
@@
 \item
-  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
+  \emph{Measure of uniqueness} {[}numeric{]} of individual analyses for the set of predictors in each model (\(uniq_i\)).
 \item
-  \emph{Measure of conservativeness} of the model specification.
+  \emph{Measure of conservativeness} {[}numeric{]} of the model specification, as the number of random/group-level effects included (\(cons_i\)).
 \item
-  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
+  \emph{Number of post-hoc changes to the acoustic measurements} {[}numeric{]} the teams will report to have carried out (\(phoc_i\)).
 \item
-  \emph{Number of models} the teams will report to have run.
+  \emph{Number of models} {[}numeric{]} the teams will report to have run (\(modn_i\)).
 \item
-  \emph{Major dimension} that has been measured to answer the research question.
+  \emph{Major dimension} {[}categorical{]} that has been measured to answer the research question (\(mdim_i\)).
 \item
-  \emph{Temporal window} that the measurement is taken over.
+  \emph{Temporal window} {[}categorical{]} that the measurement is taken over (\(twin_i\)).
 \item
-  \emph{Data exclusion}, whether data has been excluded or not.
+  \emph{Data exclusion}, {[}categorical{]} whether data has been excluded or not (\(excl_i\)).
 \end{itemize}
@@
 For our purposes, we will treat predictors as species and individual analyses as sites.
-The SDI for a pair of analyses \((X, Y)\) can be obtained using the following formula:
+For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
 
@@
 
-where \(|X \cap Y|\) is the number of variables common to both models, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
+where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al., 2020).
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
+The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.)
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: segment, syllable, word, phrase.
+We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}.
 
-\textbf{Demographic factors}.
-We will include the following demographic factors about the \highlight[id=SC, comment = {How do we do this, since we will have a score per individual rather than per team?}]{analysis} teams:
+\textbf{Demographic factors}. We will include the following demographic factors about the teams:
 
@@
 \item
-  \emph{Research experience} as the elapsed time from PhD award (negative values will indicate that the person is a student or graduate student).
+  \emph{Research experience} {[}numeric{]} as the elapsed time from PhD award. Negative values will indicate that the person is a student or graduate studens (\(rexp_i\)).
 \item
-  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire.
+  \emph{Initial belief} {[}numeric{]} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire (\(belf_i\)).
 \end{itemize}
@@
 
+\leavevmode\hypertarget{ref-baselga2020}{}%
+Baselga, A., Orme, D., Villeger, S., De Bortoli, J., Leprieur, F., \& Logez, M.
+(2020).
+{b}etapart: Partitioning beta diversity into turnover and nestedness components.
+Retrieved from \url{https://CRAN.R-project.org/package=betapart}
+
 \leavevmode\hypertarget{ref-botvinik2020variability}{}%
@@
 Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.
+
+\leavevmode\hypertarget{ref-brugger2001}{}%
+Brugger, P.
+(2001).
+From haunted brain to haunted science: A cognitive neuroscience view of paranormal and pseudoscientific thought.
+\emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, 195--213.
+
+\leavevmode\hypertarget{ref-burkner2017}{}%
+Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
 \leavevmode\hypertarget{ref-roettger2019researcher}{}%
@@
 \emph{Psychological Science}, \emph{22}(11), 1359--1366.
+
+\leavevmode\hypertarget{ref-stan2020a}{}%
+Stan Development Team. (2020). {RStan}: The {R} interface to {Stan}. Retrieved from \url{http://mc-stan.org/}
+
+\leavevmode\hypertarget{ref-stan2021}{}%
+Stan Development Team. (2021). Stan modeling language users guide and reference manual, v2.26.0. Retrieved from \url{http://mc-stan.org/}
 
@@
 
+\leavevmode\hypertarget{ref-heuven2002}{}%
+Van Heuven, V.
+J., Haan, J., Gussenhoven, C., \& Warner, N.
+(2002).
+Temporal distribution of interrogativity markers in {D}utch: A perceptual study.
+In \emph{Laboratory phonology 7} (Vol.
+4, p.
+61).
+Walter de Gruyter.
+
 \leavevmode\hypertarget{ref-van2005speech}{}%

### 2021-01-27 RR_manuscript/Draft_RR.Rmd
:memo: - render RR + bib updates

@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
+Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
 <!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
@@
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Haan 2002), as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
+The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
 Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
@@
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. ????). <!-- year needed -->
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis [e.g. wicherts2016].
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
@@
 \highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017] in R [@r-core-team2020].
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there are no divergent transitions.
-The analysis will be conducted in R [@r-core-team2020] and fit using Stan [@stan-development-team2020], RStan [@stan-development-team2020a], and brms [@burkner2017].
+The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
 <!-- TODO: add link to code of the meta-analytical model -->

### 2021-01-31 osf/data/README.Rmd
:bento: - upload TextGrids and READMEs to osf

--- 2021-01-05 osf/comps/data/README.Rmd
@@
 - The `norming/` directory holds the files of the norming study.
-- The `production/` directory contains the `.wav` and `.TextGrid` files from the production experiment.
+- The `production/` directory contains two subdirectories:
+  - `audio/`: with `.wav` and `.TextGrid` files from the production experiment.
+  - `trial-lists/`: with `.csv` files with info on the trials from the production experiment.
 
@@
 osf_comps <- osf_ls_nodes(osf_repo)
-# Dataset & Materials component
+# Data component
 data_comp <- osf_comps %>% filter(name == "Data")

### 2021-01-31 osf/data/norming/ratings/README.Rmd
:bento: - upload TextGrids and READMEs to osf

--- 2021-01-05 osf/comps/data/norming/README.Rmd
@@
 ---
-title: "Norming study"
+title: "Typicality ratings of the norming study"
 output:
@@
 
-This directory contains the files of the norming study, designed to obtain typicality ratings of re-colored images of everyday objects.
-
-There are 2 subdirectories:
-
-- The `images/` directory contains the re-colored images used in the norming study.
-- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.
+Here you can find an aggregated dataset with the typicality judgement for each of the images in `norming/images/`, for each participant.
 
@@
 - `colour`: The color of the object in the image.
-
-```{r retrieve}
-# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
-osf_repo <- osf_retrieve_node("3bmcp")
-# Repo components
-osf_comps <- osf_ls_nodes(osf_repo)
-# Dataset & Materials component
-data_comp <- osf_comps %>% filter(name == "Data")
-```
-
-```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "norming") %>%
-  select(name) %>%
-  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
-  arrange(name)
-```

### 2021-01-31 osf/manage-osf.Rmd
:bento: - upload TextGrids and READMEs to osf

@@
 
-# Knit readme files
+# Readme files
+
+## Knit Readmes
 
@@
 ```{r knit-all, message=FALSE, warning=FALSE}
-files <- list.files("./osf/comps/data", pattern = "[.]Rmd$", recursive = T, full.names = T)
+files <- list.files("./osf/data", pattern = "[.]Rmd$", recursive = T, full.names = T)
 
@@
 
-# Upload files to the OFS repo
+## Upload Readmes to the OFS repo
 
@@
 # A loop would be better
-osf_upload(data_comp, path = "./osf/comps/data/README.md", conflicts = "overwrite", verbose = T)
+
+# data/ ----
+osf_upload(data_comp, path = "./osf/data/README.md", conflicts = "overwrite", verbose = T)
 
@@
 
-# data/norming/
+# data/norming/ ----
 raw <- data_comp_files %>% filter(name == "norming")
@@
   raw,
-  path = "./osf/comps/data/norming/README.md",
+  path = "./osf/data/norming/README.md",
   conflicts = "overwrite", verbose = T)
 
-# data/production/audio/
+# data/norming/images/ ----
 #### delete old readme
-old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
+old_readme <- osf_ls_files(data_comp, "norming/images/", pattern = "README.md")
 osf_rm(old_readme, check = FALSE)
@@
 #### upload new readme
-audio <- osf_ls_files(data_comp, "production", pattern = "audio")
+audio <- osf_ls_files(data_comp, "norming", pattern = "images")
 osf_upload(
   audio,
-  path = "./osf/comps/data/production/audio/README.md",
+  path = "./osf/data/norming/images/README.md",
   conflicts = "overwrite", verbose = T)
 
-# data/production/trial-lists
+# data/production/audio/ ----
 #### delete old readme
-old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
-osf_rm(old_readme, check = FALSE)
+# old_readme <- osf_ls_files(data_comp, "production/audio", pattern = "README.md")
+# osf_rm(old_readme, check = FALSE)
+# 
+# #### upload new readme
+# audio <- osf_ls_files(data_comp, "production", pattern = "audio")
+# osf_upload(
+#   audio,
+#   path = "./osf/data/production/audio/README.md",
+#   conflicts = "overwrite", verbose = T)
 
-#### upload new readme
-trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
+# data/production/trial-lists ----
+#### delete old readme
+# old_readme <- osf_ls_files(data_comp, "production/trial-lists", pattern = "README.md")
+# osf_rm(old_readme, check = FALSE)
+# 
+# #### upload new readme
+# trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
+# osf_upload(
+#   trials,
+#   path = "./osf/data/production/trial-lists/README.md",
+#   conflicts = "overwrite", verbose = T)
+```
+
+# TextGrids
+
+```{r textgrids, eval=FALSE}
+audio <- osf_ls_files(data_comp, "production", pattern = "audio")
+
+# delete old tgs
+old_tgs <- osf_ls_files(audio, pattern = ".TextGrid", n_max = Inf)
+
+for (file in 2:nrow(old_tgs)) {
+  osf_rm(old_tgs[file,], check = FALSE)
+}
+
+# upload new tgs
+new_tgs <- list.files("./osf/data/production/audio/", ".TextGrid", full.names = TRUE)
+
+for (tg in new_tgs) {
   osf_upload(
-  trials,
-  path = "./osf/comps/data/production/trial-lists/README.md",
-  conflicts = "overwrite", verbose = T)
+    audio,
+    path = tg,
+    conflicts = "overwrite", verbose = T
+  )
+}
 ```

### 2021-02-01 osf/manage-osf.Rmd
:bento: - update trial lists for osf

@@
 
-for (file in 2:nrow(old_tgs)) {
+for (file in 1:nrow(old_tgs)) {
   osf_rm(old_tgs[file,], check = FALSE)
@@
 ```
+
+# Trial lists
+
+```{r tlists}
+tlists <- list.files("./data/trial-lists", ".csv", full.names = TRUE)
+typ <- read_csv("./data/dataset/typicality.csv")
+
+for (tlist in tlists) {
+  speaker <- str_sub(tlist, 20, 21)
+  tbl <- read_csv(tlist) %>%
+    mutate(
+      speaker = speaker,
+      trial = row_number()
+    ) %>%
+    left_join(y = typ) %>%
+    select(speaker, trial, condition, typicality, everything())
+
+  write_csv(tbl, file = paste0("./osf/data/production/trial-lists/", speaker, ".csv"))
+}
+```
+
+```{r tlists-upload}
+trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")
+
+# delete old trials
+old_trials <- osf_ls_files(trials, pattern = ".csv", n_max = Inf)
+
+for (file in 1:nrow(old_trials)) {
+  osf_rm(old_trials[file,], check = FALSE)
+}
+
+# upload new trials
+new_trials <- list.files("./osf/data/production/trial-lists/", ".csv", full.names = TRUE)
+
+for (trial in new_trials) {
+  osf_upload(
+    trials,
+    path = trial,
+    conflicts = "overwrite", verbose = T
+  )
+}
+```

### 2021-02-03 RR_manuscript/Draft_RR.Rmd
:bug: - fix bug on RR code

@@
 # meta_bm is the meta-analytical Bayesian regression model
-meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"
+meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
 meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]

### 2021-02-03 RR_manuscript/Draft_RR.Rmd
:memo: - minor edits to RR

@@
 
-As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-We will fit a single Bayesian regression model with each team's group-level coefficient $\alpha_{\text{t}[i]}$ as the outcome variable, and the analytical and demographic factors described below as predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytical mean by the individual standardized effect sizes relate to those same predictors.
+We will fit two Bayesian regression models, one for (a) and one for (b).
+<!-- TODO: check if stand. effect sizes and deviations are equivalent. -->
+with each team's group-level coefficient $\alpha_{\text{t}[i]}$ as the outcome variable, and the analytical and demographic factors described below as predictors.
 The coefficient $\alpha_{\text{t}[i]}$ can be interpreted as the deviation score of the team's $\eta_i$ from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
@@
 \alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
-\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
- & \qquad\qquad +\upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
+\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
+ & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
+ & \qquad + \upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
 \iota      & \sim \text{Normal}(0, 1) \\

### 2021-02-05 scripts/simulations/simulations.Rmd
:construction: - start rmd of RR simulations
You can have a look at the html output to get an idea of what it looks like.

---
title: "Perspective simulation"
date: "`r Sys.Date()`"
output:
  rmdformats::downcute:
    toc_depth: 3
    number_sections: yes
    use_bookdown: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(rmdformats)
library(tidyverse)
library(patchwork)
library(brms)
library(extraDistr)
my_seed <- 115116106
```

# Meta-analysis

## Simulate data set

We first simulate a dataset (`eta_tbl`) of standardised effect sizes.
Each team ($n = 12$) contributes a standardized effect size $\eta_i$, with respective standard error $\text{se}_i$.
The $\eta_i$ is randomly sampled from a $Normal(1, 0.5)$ distribution, while $\text{se}_i$ from a $HalfCauchy(0, 0.1)$.

```{r eta-tbl}
set.seed(my_seed)

# Number of teams, each team contributes one effect size
n <- 12
# standardized effect size
eta <- rnorm(n, 1, 0.5)
# standard error of the standardised effect size
se <- rhcauchy(n, 0.1)
# label each team
team <- letters[1:n]

# put together in a tibble
eta_tbl <- tibble(
  eta,
  se,
  team
)
```

## Model priors

In the meta-analytical model, we will use the following priors:

<!-- TODO: need to discuss prior for sd -->

- A $Normal(0, 1)$ distribution for the prior of the intercept.
- A $HalfCauchy(0, 0.01)$ distribution for the prior of the intercept standard deviation.

```{r meta-priors}
priors <- c(
  prior(normal(0, 1), class = Intercept),
  prior(cauchy(0, 0.01), class = sd)
)
```

### Prior predictive checks

```{r prior-predictive}
meta_bm_ppred <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  sample_prior = "only",
  chain = 1,
  seed = my_seed,
  file = "./models/sim/meta_bm_ppred"
)
```

```{r ppred-samples}
ppred_samples <- posterior_samples(meta_bm_ppred)
glimpse(ppred_samples)
```

## Meta-analytical model

```{r meta-bm}
meta_bm <- brm(
  eta | se(se) ~
    (1 | team),
  data = eta_tbl,
  prior = priors,
  chain = 1,
  seed = my_seed,
  file = "./models/sim/meta_bm"
)
```

```{r meta-bm-summary}
meta_bm
```

```{r plot-meta-bm}
plot(meta_bm)
```

### 2021-02-09 scripts/simulations/simulations.Rmd
:sparkles: - add analytical and demographic features

@@
 library(extraDistr)
+library(betapart)
+library(summarytools)
 my_seed <- 115116106
@@
 
-## Simulate data set
+## Simulate data
 
@@
 Each team ($n = 12$) contributes a standardized effect size $\eta_i$, with respective standard error $\text{se}_i$.
+
+### Helper functions
+
+```{r helpers}
+at_least <- function(x) {
+  if (1 %in% x) {x} else {sample(c(1, 0, 0, 0, 0))}
+}
+
+sdi_mean <- function(preds) {
+  bpair <- tibble::tibble(preds) %>% tidyr::unnest_wider(preds, names_sep = ".") %>%
+    as.matrix() %>%
+    betapart::beta.pair(.)
+  sdim <- as.matrix(bpair$beta.sor)
+  diag(sdim) <- NA
+  rowSums(sdim, na.rm = T) / length(preds)
+}
+```
+
+### Tibble
+
 The $\eta_i$ is randomly sampled from a $Normal(1, 0.5)$ distribution, while $\text{se}_i$ from a $HalfCauchy(0, 0.1)$.
 
-```{r eta-tbl}
+```{r sim-data}
 set.seed(my_seed)
@@
 
+# pop-level predictors
+pop_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
+# group-level predictors
+group_pred <- lapply(replicate(n, list(rbinom(5, 1, 0.5))), at_least)
+# number of post-hoc changes to the measures
+phoc_n <- rpois(n, 1)
+# number of models run
+mod_n <- sample(1:5, n, replace = T)
+# major dimension
+mdim <- sample(c("duration", "amplitude", "f0", "spectral", "other"), n, TRUE)
+# temporal window
+twin <- sample(c("segment", "syllable", "word", "phrase"), n, T)
+# was data excluded?
+excl <- rbinom(n, 1, 0.5)
+
+# research experience as years from PhD
+exp <- replicate(n, sample(-3:20, sample(1:10, 1), replace = T))
+# prior belief in the research hypothesis
+belf <- lapply(lengths(exp), function(.x) rbinom(.x, 1, 0.5))
+```
+
+```{r eta-tbl}
 # put together in a tibble
@@
   se,
-  team
+  team,
+  pop_pred,
+  pop_n = map(pop_pred, sum),
+  group_pred,
+  group_n = map(group_pred, sum),
+  pop_sdi = sdi_mean(pop_pred),
+  group_sdi = sdi_mean(group_pred),
+  phoc_n,
+  mod_n,
+  mdim,
+  twin,
+  excl,
+  exp,
+  belf
 )
@@
 ```
+
+# Simulated data summary
+
+```{r dfsummary}
+# seems dfSummary() does not support list columns
+dfSummary(eta_tbl %>% select(-where(is.list)))
+```

### 2021-02-11 scripts/r/simulations/simulations.Rmd
:sparkles: - use proper prior for sd

--- 2021-02-09 scripts/simulations/simulations.Rmd
@@
 library(tidyverse)
+theme_set(theme_light())
 library(patchwork)
@@
 library(extraDistr)
+library(HDInterval)
 library(betapart)
@@
 
-# Meta-analysis
-
-## Simulate data
+# Simulate data
 
@@
 
-The $\eta_i$ is randomly sampled from a $Normal(1, 0.5)$ distribution, while $\text{se}_i$ from a $HalfCauchy(0, 0.1)$.
+The $\eta_i$ is randomly sampled from a $Normal(1, 0.5)$ distribution, while $\text{se}_i$ from a $HalfCauchy(0, 0.15)$.
 
@@
 # standard error of the standardised effect size
-se <- rhcauchy(n, 0.1)
+se <- rhcauchy(n, 0.15)
 # label each team
@@
 
+# Meta-analytical model
+
+## Model formula
+
+$$
+\begin{aligned}
+\eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
+\mu_i       & = \alpha + \alpha_{\text{t}[i]} \\
+\alpha      & \sim \text{Normal}(0, 1) \\
+\sigma_{\alpha_{\text{t}}} & \sim \text{HalfCauchy}(0, 1) \\
+\sigma_i    & = \text{se}_i
+\end{aligned}
+$$
+
 ## Model priors
@@
 
-<!-- TODO: need to discuss prior for sd -->
+- A $Normal(0, 1)$ distribution for the prior of the intercept.
+- A $HalfCauchy(0, 1)$ distribution for the prior of the teams' intercept standard deviation.
 
-- A $Normal(0, 1)$ distribution for the prior of the intercept.
-- A $HalfCauchy(0, 0.01)$ distribution for the prior of the intercept standard deviation.
+```{r sd-prior}
+tibble(
+  x = seq(0, 10, by = 0.05),
+  density = dhcauchy(x, 1)
+) %>%
+  ggplot(aes(x, density)) +
+  geom_area(fill = "#325756", alpha = 0.9) +
+  labs(
+    title = "HalfCauchy(0, 1)",
+    x = "teams' intercept standard deviation"
+  )
+```
 
@@
   prior(normal(0, 1), class = Intercept),
-  prior(cauchy(0, 0.01), class = sd)
+  prior(cauchy(0, 1), class = sd)
 )
@@
   sample_prior = "only",
-  chain = 1,
+  chain = 4,
   seed = my_seed,
@@
 )
+
+ppred_samples <- posterior_samples(meta_bm_ppred) %>%
+  rename(intercept = b_Intercept, `group-level SD` = sd_team__Intercept)
 ```
 
-```{r ppred-samples}
-ppred_samples <- posterior_samples(meta_bm_ppred)
-glimpse(ppred_samples)
+```{r ppred-posts}
+ppred_samples %>%
+  pivot_longer(intercept:`group-level SD`, names_to = "term") %>%
+  mutate(term = factor(term, levels = c("intercept", "group-level SD"))) %>%
+  ggplot(aes(value)) +
+  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 0.4) +
+  facet_wrap(~ term, scales = "free")
+```
+
+```{r ppred-joint-post}
+ppred_samples %>%
+  select(intercept, `r_team[a,Intercept]`:`r_team[l,Intercept]`) %>%
+  pivot_longer(-intercept, names_to = "team") %>%
+  mutate(eta = intercept + value) %>%
+  ggplot(aes(eta)) +
+  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 0.4) +
+  xlim(-7, 7)
 ```
@@
   prior = priors,
-  chain = 1,
+  chain = 4,
   seed = my_seed,
@@
 ```
-
-# Simulated data summary
-
-```{r dfsummary}
-# seems dfSummary() does not support list columns
-dfSummary(eta_tbl %>% select(-where(is.list)))
-```

### 2021-02-18 RR_manuscript/Draft_RR.Rmd
:memo: - add reviewer ratings in factor analysis

@@
 <!-- TODO: add link to peer review survey -->
-The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts: <!-- TR:Need flow chart here-->
+The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria: <!-- TR:Need flow chart here-->
 
@@
 - *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).
+- *Average peer-review rating* [numeric], as the mean of the peer-review ratings for each analysis.
 
@@
 We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*.
+Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
+These will be entered in the model formula with a measurement-error term (`me(mean, sd)` in brms).
 

### 2021-02-18 RR_manuscript/Draft_RR.tex
:memo: - add reviewer ratings in factor analysis

@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code, and the data set.
-The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts:
+The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria:
 
@@
 
-As a second step, we will investigate the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors related to analytical and demographic factors (see below).
-We will fit a single Bayesian regression model with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytical mean by the individual standardized effect sizes relate to those same predictors.
+We will fit two Bayesian regression models, one for (a) and one for (b).
+with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
 The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
@@
   \emph{Data exclusion}, {[}categorical{]} whether data has been excluded or not (\(excl_i\)).
+\item
+  \emph{Average peer-review rating} {[}numeric{]}, as the mean of the peer-review ratings for each analysis.
 \end{itemize}
@@
 We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}.
+Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
+These will be entered in the model formula with a measurement-error term (\texttt{me(mean,\ sd)} in brms).
 

### 2021-02-18 RR_manuscript/Draft_RR.Rmd
:art: - use pdf_document2 for now

@@
 draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
 output:
-  papaja::apa6_pdf:
+  bookdown::pdf_document2:
     number_sections: true
     latex_engine: xelatex
+    keep_tex: true
+geometry: margin=4cm
+fontsize: 12pt
 header-includes:
   - \usepackage{cleveref}
+  - \setlength{\marginparwidth}{2cm}
   - \usepackage{changes}
@@
 
-```{r setup, include = FALSE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 knitr::opts_knit$set(root.dir = here::here())
-library("papaja")
-r_refs("r-references.bib")
+
 library(tidyverse)

### 2021-02-18 RR_manuscript/Draft_RR.tex
:art: - use pdf_document2 for now

@@
 \documentclass[
-  english,
-  man,floatsintext]{apa6}
+  12pt,
+]{article}
 \usepackage{amsmath,amssymb}
@@
   pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
-  pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
-  pdflang={en-EN},
   pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage[margin=4cm]{geometry}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \setcounter{secnumdepth}{5}
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{Many analysts - one speech data set}
-\keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis\newline\indent Word count: X}
-\usepackage{lineno}
-
-\linenumbers
-\usepackage{csquotes}
 \usepackage{cleveref}
+\setlength{\marginparwidth}{2cm}
 \usepackage{changes}
@@
 \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifluatex
@@
 \title{Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
-\author{First Author\textsuperscript{\#}, Second Author\textsuperscript{\#}, \ldots{}\textsuperscript{\#}, \& Last Author\textsuperscript{\#}}
+\author{true \and true \and true \and true}
 \date{}
 
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-The authors made the following contributions.
-First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Second Author: Writing - Review \& Editing; \ldots{}: Writing - Review \& Editing; Last Author: Writing - Review \& Editing.
-
-Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} \#\\\textsuperscript{\ldots{}} \ldots{}}
-
-\abstract{
+\begin{document}
+\maketitle
+\begin{abstract}
 One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
@@
 Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+\end{abstract}
+
+{
+\setcounter{tocdepth}{2}
+\tableofcontents
 }
-
-\begin{document}
-\maketitle
-
 \hypertarget{introduction}{%
@@
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (Camerer et al., 2018; e.g., Open Science Collaboration, 2015) leading to what is now referred to as the \emph{replication crisis}.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration 2015; Camerer et al.
+2018) leading to what is now referred to as the \emph{replication crisis}.
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, \& Dubé, 2015; Starns et al., 2019) and is, among other things, rooted in the inherent flexibility of data analysis (Gelman \& Loken, 2014; often referred to as researcher degrees of freedom: Simmons, Nelson, \& Simonsohn, 2011).
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Starns et al.
+2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box, 1976; De Groot, 2014; Tukey, 1977).
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, \& Simonsohn, 2011).
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box 1976; Tukey 1977; De Groot 2014).
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, and Simonsohn 2011).
 Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (Botvinik-Nezer et al., 2020; e.g., Silberzahn et al., 2018; Starns et al., 2019).
+This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al.
+2018; Starns et al.
+2019; Botvinik-Nezer et al.
+2020).
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky \& Kahneman, 1974), seeing coherent patterns in randomness (Brugger, 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson, 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff, 1975).
-In connection with an academic incentive system that rewards certain discovery processes more than others (Koole \& Lakens, 2012; Sterling, 1959), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger, 2019).
+Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
+In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (Gelman \& Loken, 2014; e.g., Simmons, Nelson, \& Simonsohn, 2011).
+Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g., Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
 These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts, Borsboom, Kats, \& Molenaar, 2006).
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts et al.
+2006).
 
-While this issue has been widely discussed both from a conceptual point of view (Nosek \& Lakens, 2014; Simmons, Nelson, \& Simonsohn, 2011; Wagenmakers, Wetzels, Borsboom, Maas, \& Kievit, 2012) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger, 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+While this issue has been widely discussed both from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
+2012; Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
+Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake and Fried 2019).
 To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
@@
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
-This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker, 1977).
+This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins \& Nguyen, 2004).
+For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon \& Roettger, 2017).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).
 
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd, 2008).
+Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Van Heuven, Haan, Gussenhoven, \& Warner, 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven \& Van Zanten, 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).
+The latter can also be expressed by global vs local pitch modulations (Van Heuven et al.
+2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven and Van Zanten 2005).
+Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes and Docherty 2006; Ogden 2004; White, Payne, and Mattys 2009).
 
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice, 1975).
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
@@
 
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Rubio-Fernández, 2016; Sedivy, 2003; Westerbeek, Koolen, \& Maes, 2015), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts, Maes, Noordman, \& Jansen, 2011; Paraboni, Van Deemter, \& Masthoff, 2007; Rubio-Fernández, 2016).
+Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003; Westerbeek, Koolen, and Maes 2015; Rubio-Fernández 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
+2011; Paraboni, Van Deemter, and Masthoff 2007; Rubio-Fernández 2016).
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen, Hawkins, Graf, Kreiss, and Goodman (2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection (Gatt, Gompel, Deemter, \& Krahmer, 2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+For example, Degen et al.
+(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
+This account, however, has mainly focused on content selection (Gatt et al.
+2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd, 2008).
+Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
@@
 
-Assuming that the underlying distribution of effect sizes is normal (Knight, 2000), the standard error of \(\tau^2\) can be calculated with the formula:
+Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:
 
@@
 \highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017) in R (R Core Team, 2020).
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team 2021), RStan (Stan Development Team 2020), and brms (Bürkner 2017) in R (R Core Team 2020).
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
-The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight, 2000).
+The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
 The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
@@
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
-The analysis will be conducted in R (R Core Team, 2020) and fit using Stan (Stan Development Team, 2021), RStan (Stan Development Team, 2020), and brms (Bürkner, 2017).
+The analysis will be conducted in R (R Core Team 2020) and fit using Stan (Stan Development Team 2021), RStan (Stan Development Team 2020), and brms (Bürkner 2017).
 The code used to run the model can be found here: INSERT LINK.
@@
 Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
-This will be achieved through inspection of funnel plots (Light \& Pillemer, 1984; for a review see Egger, Smith, Schneider, \& Minder, 1997; and Sterne, Becker, \& Egger, 2005; for a critique Lau, Ioannidis, Terrin, Schmid, \& Olkin, 2006).
+This will be achieved through inspection of funnel plots (Light and Pillemer 1984; for a review see Egger et al. 1997; and Sterne, Becker, and Egger 2005; for a critique Lau et al. 2006).
 In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the \emph{x}-axis and estimated error (i.e.~standard deviation) on \emph{y}-axis.
@@
 
-The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
+The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
 The SDI is an index typically used in ecology research to compare species composition across sites.
@@
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al., 2020).
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.
+2020).
 
@@
 \leavevmode\hypertarget{ref-arts2011overspecification}{}%
-Arts, A., Maes, A., Noordman, L. G., \& Jansen, C. (2011). Overspecification in written instruction. \emph{Linguistics}, \emph{49}(3), 555--574.
+Arts, Anja, Alfons Maes, Leo GM Noordman, and Carel Jansen. 2011. {``Overspecification in Written Instruction.''} \emph{Linguistics} 49 (3): 555--74.
 
 \leavevmode\hypertarget{ref-baselga2020}{}%
-Baselga, A., Orme, D., Villeger, S., De Bortoli, J., Leprieur, F., \& Logez, M.
-(2020).
-{b}etapart: Partitioning beta diversity into turnover and nestedness components.
-Retrieved from \url{https://CRAN.R-project.org/package=betapart}
+Baselga, Andres, David Orme, Sebastien Villeger, Julien De Bortoli, Fabien Leprieur, and Maxime Logez.
+2020.
+{``{b}etapart: Partitioning Beta Diversity into Turnover and Nestedness Components.''} \url{https://CRAN.R-project.org/package=betapart}.
 
 \leavevmode\hypertarget{ref-botvinik2020variability}{}%
-Botvinik-Nezer, R., Holzmeister, F., Camerer, C.
-F., Dreber, A., Huber, J., Johannesson, M., \ldots{} others.
-(2020).
-Variability in the analysis of a single neuroimaging dataset by many teams.
-\emph{Nature}, 1--7.
+Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
+2020.
+{``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature}, 1--7.
 
 \leavevmode\hypertarget{ref-box1976science}{}%
-Box, G. E. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799.
+Box, George EP. 1976. {``Science and Statistics.''} \emph{Journal of the American Statistical Association} 71 (356): 791--99.
 
 \leavevmode\hypertarget{ref-brugger2001}{}%
-Brugger, P.
-(2001).
-From haunted brain to haunted science: A cognitive neuroscience view of paranormal and pseudoscientific thought.
-\emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, 195--213.
+Brugger, Peter.
+2001.
+{``From Haunted Brain to Haunted Science: A Cognitive Neuroscience View of Paranormal and Pseudoscientific Thought.''} \emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, January, 195--213.
 
 \leavevmode\hypertarget{ref-burkner2017}{}%
-Bürkner, P.-C. (2017). {brms}: An {R} package for {Bayesian} multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, Paul-Christian.
+2017.
+{``{brms}: An {R} Package for {Bayesian} Multilevel Models Using {Stan}.''} \emph{Journal of Statistical Software} 80 (1): 1--28.
+\url{https://doi.org/10.18637/jss.v080.i01}.
 
 \leavevmode\hypertarget{ref-camerer2018evaluating}{}%
-Camerer, C.
-F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} others.
-(2018).
-Evaluating the replicability of social science experiments in nature and science between 2010 and 2015.
-\emph{Nature Human Behaviour}, \emph{2}(9), 637--644.
-\url{https://doi.org/10.1038/s41562-018-0399-z}
+Camerer, Colin F, Anna Dreber, Felix Holzmeister, Teck-Hua Ho, Jürgen Huber, Magnus Johannesson, Michael Kirchler, et al.
+2018.
+{``Evaluating the Replicability of Social Science Experiments in Nature and Science Between 2010 and 2015.''} \emph{Nature Human Behaviour} 2 (9): 637--44.
+\url{https://doi.org/10.1038/s41562-018-0399-z}.
 
 \leavevmode\hypertarget{ref-de2014thought}{}%
-De Groot, A. D. (2014). \emph{Thought and choice in chess} (Vol. 4). Walter de Gruyter GmbH \& Co KG.
+De Groot, Adriaan D. 2014. \emph{Thought and Choice in Chess}. Vol. 4. Walter de Gruyter GmbH \& Co KG.
 
 \leavevmode\hypertarget{ref-degen2020redundancy}{}%
-Degen, J., Hawkins, R. D., Graf, C., Kreiss, E., \& Goodman, N. D. (2020). When redundancy is useful: A bayesian approach to {``overinformative''} referring expressions. \emph{Psychological Review}.
+Degen, Judith, Robert D Hawkins, Caroline Graf, Elisa Kreiss, and Noah D Goodman.
+2020.
+{``When Redundancy Is Useful: A Bayesian Approach to {`Overinformative'} Referring Expressions.''} \emph{Psychological Review}.
 
 \leavevmode\hypertarget{ref-dice1945}{}%
-Dice, L. R. (1945). Measures of the amount of ecologic association between species. \emph{Ecology}, \emph{26}(3), 297--302.
+Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.
 
 \leavevmode\hypertarget{ref-egger1997}{}%
-Egger, M., Smith, G. D., Schneider, M., \& Minder, C. (1997). Bias in meta-analysis detected by a simple, graphical test. \emph{British Medical Journal}, \emph{315}, 629--634.
+Egger, Matthias, George Davey Smith, Martin Schneider, and Christoph Minder. 1997. {``Bias in Meta-Analysis Detected by a Simple, Graphical Test.''} \emph{British Medical Journal} 315: 629--34.
 
 \leavevmode\hypertarget{ref-fischhoff1975hindsight}{}%
-Fischhoff, B.
-(1975).
-Hindsight is not equal to foresight: The effect of outcome knowledge on judgment under uncertainty.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{1}(3), 288.
+Fischhoff, Baruch.
+1975.
+{``Hindsight Is Not Equal to Foresight: The Effect of Outcome Knowledge on Judgment Under Uncertainty.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 1 (3): 288.
 
 \leavevmode\hypertarget{ref-flake2019}{}%
-Flake, J. K., \& Fried, E. I. (2019). Measurement schmeasurement: Questionable measurement practices and how to avoid them. Pre-print available at PsyArXiv.
+Flake, Jessica Kay, and Eiko I. Fried. 2019. {``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} Pre-print available at PsyArXiv.
 
 \leavevmode\hypertarget{ref-foulkes2006}{}%
-Foulkes, P., \& Docherty, G. (2006). The social life of phonetics and phonology. \emph{Journal of Phonetics}, \emph{34}(4), 409--438.
+Foulkes, Paul, and Gerard Docherty. 2006. {``The Social Life of Phonetics and Phonology.''} \emph{Journal of Phonetics} 34 (4): 409--38.
 
 \leavevmode\hypertarget{ref-gatt2013we}{}%
-Gatt, A., Gompel, R. P. van, Deemter, K. van, \& Krahmer, E. (2013). Are we bayesian referring expression generators. Cognitive Science Society.
+Gatt, Albert, Roger PG van Gompel, Kees van Deemter, and Emiel Krahmer. 2013. {``Are We Bayesian Referring Expression Generators.''} In. Cognitive Science Society.
 
 \leavevmode\hypertarget{ref-gelman2014statistical}{}%
-Gelman, A., \& Loken, E.
-(2014).
-The statistical crisis in science: Data-dependent analysis--a" garden of forking paths"--explains why many statistically significant comparisons don't hold up.
-\emph{American Scientist}, \emph{102}(6), 460--466.
+Gelman, Andrew, and Eric Loken.
+2014.
+{``The Statistical Crisis in Science: Data-Dependent Analysis--a" Garden of Forking Paths"--Explains Why Many Statistically Significant Comparisons Don't Hold Up.''} \emph{American Scientist} 102 (6): 460--66.
 
 \leavevmode\hypertarget{ref-gordon2017acoustic}{}%
-Gordon, M., \& Roettger, T. (2017). Acoustic correlates of word stress: A cross-linguistic survey. \emph{Linguistics Vanguard}, \emph{3}(1), 1--11.
+Gordon, Matthew, and Timo Roettger. 2017. {``Acoustic Correlates of Word Stress: A Cross-Linguistic Survey.''} \emph{Linguistics Vanguard} 3 (1): 1--11.
 
 \leavevmode\hypertarget{ref-grice1975logic}{}%
-Grice, H. P. (1975). Logic and conversation. In \emph{Speech acts} (pp. 41--58). Brill.
+Grice, Herbert P. 1975. {``Logic and Conversation.''} In \emph{Speech Acts}, 41--58. Brill.
 
 \leavevmode\hypertarget{ref-hawkins2004influence}{}%
-Hawkins, S., \& Nguyen, N. (2004). Influence of syllable-coda voicing on the acoustic properties of syllable-onset /l/ in {E}nglish. \emph{Journal of Phonetics}, \emph{32}(2), 199--231.
+Hawkins, Sarah, and Noël Nguyen. 2004. {``Influence of Syllable-Coda Voicing on the Acoustic Properties of Syllable-Onset /l/ in {E}nglish.''} \emph{Journal of Phonetics} 32 (2): 199--231.
 
 \leavevmode\hypertarget{ref-jongman2000acoustic}{}%
-Jongman, A., Wayland, R., \& Wong, S. (2000). Acoustic characteristics of english fricatives. \emph{The Journal of the Acoustical Society of America}, \emph{108}(3), 1252--1263.
+Jongman, Allard, Ratree Wayland, and Serena Wong. 2000. {``Acoustic Characteristics of English Fricatives.''} \emph{The Journal of the Acoustical Society of America} 108 (3): 1252--63.
 
 \leavevmode\hypertarget{ref-knight2000}{}%
-Knight, K. (2000). \emph{Mathematical statistics}. Chapman; Hall, New York.
+Knight, K. 2000. \emph{Mathematical Statistics}. Chapman; Hall, New York.
 
 \leavevmode\hypertarget{ref-koole2012rewarding}{}%
-Koole, S. L., \& Lakens, D. (2012). Rewarding replications: A sure and simple way to improve psychological science. \emph{Perspectives on Psychological Science}, \emph{7}(6), 608--614.
+Koole, Sander L, and Daniël Lakens. 2012. {``Rewarding Replications: A Sure and Simple Way to Improve Psychological Science.''} \emph{Perspectives on Psychological Science} 7 (6): 608--14.
 
 \leavevmode\hypertarget{ref-ladd2008intonational}{}%
-Ladd, D. R. (2008). \emph{Intonational phonology}. Cambridge University Press.
+Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.
 
 \leavevmode\hypertarget{ref-lau2006}{}%
-Lau, J., Ioannidis, J. P. A., Terrin, N., Schmid, C. H., \& Olkin, I. (2006). The case of the misleading funnel plot. \emph{British Medical Journal}, \emph{333}(7568), 597--600.
+Lau, Joseph, John P. A. Ioannidis, Norma Terrin, Christopher H. Schmid, and Ingram Olkin. 2006. {``The Case of the Misleading Funnel Plot.''} \emph{British Medical Journal} 333 (7568): 597--600.
 
 \leavevmode\hypertarget{ref-light1984}{}%
-Light, R. J., \& Pillemer, D. B. (1984). \emph{Summing up; the science of reviewing research}. Cambridge, MA (USA) Harvard Univ. Press.
+Light, Richard J., and David B. Pillemer. 1984. \emph{Summing up; the Science of Reviewing Research}. Cambridge, MA (USA) Harvard Univ. Press.
 
 \leavevmode\hypertarget{ref-lisker1977rapid}{}%
-Lisker, L. (1977). Rapid versus rabid: A catalogue of acoustic features that may cue the distinction. \emph{The Journal of the Acoustical Society of America}, \emph{62}(S1), S77--S78.
+Lisker, Leigh. 1977. {``Rapid Versus Rabid: A Catalogue of Acoustic Features That May Cue the Distinction.''} \emph{The Journal of the Acoustical Society of America} 62 (S1): S77--78.
 
 \leavevmode\hypertarget{ref-lisker1986voicing}{}%
-Lisker, L. (1986). {``Voicing''} in {E}nglish: A catalogue of acoustic features signaling /b/ versus /p/ in trochees. \emph{Language and Speech}, \emph{29}(1), 3--11.
+---------. 1986. {``{`Voicing'} in {E}nglish: A Catalogue of Acoustic Features Signaling /b/ Versus /p/ in Trochees.''} \emph{Language and Speech} 29 (1): 3--11.
 
 \leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
-Nickerson, R. S. (1998). Confirmation bias: A ubiquitous phenomenon in many guises. \emph{Review of General Psychology}, \emph{2}(2), 175--220.
+Nickerson, Raymond S. 1998. {``Confirmation Bias: A Ubiquitous Phenomenon in Many Guises.''} \emph{Review of General Psychology} 2 (2): 175--220.
 
 \leavevmode\hypertarget{ref-nosek2014method}{}%
-Nosek, B. A., \& Lakens, D. (2014). A method to increase the credibility of published results. \emph{Social Psychology}, \emph{45}(3), 137--141.
+Nosek, Brian A, and Daniël Lakens. 2014. {``A Method to Increase the Credibility of Published Results.''} \emph{Social Psychology} 45 (3): 137--41.
 
 \leavevmode\hypertarget{ref-ogden2004}{}%
-Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
+Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
 
 \leavevmode\hypertarget{ref-open2015estimating}{}%
-Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251). \url{https://doi.org/10.1126/science.aac4716}
+Open Science Collaboration. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.
 
 \leavevmode\hypertarget{ref-paraboni2007generating}{}%
-Paraboni, I., Van Deemter, K., \& Masthoff, J. (2007). Generating referring expressions: Making referents easy to identify. \emph{Computational Linguistics}, \emph{33}(2), 229--254.
+Paraboni, Ivandré, Kees Van Deemter, and Judith Masthoff. 2007. {``Generating Referring Expressions: Making Referents Easy to Identify.''} \emph{Computational Linguistics} 33 (2): 229--54.
 
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. 2020. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 
 \leavevmode\hypertarget{ref-roettger2019researcher}{}%
-Roettger, T. B. (2019). Researcher degrees of freedom in phonetic research. \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology}, \emph{10}(1).
+Roettger, Timo B. 2019. {``Researcher Degrees of Freedom in Phonetic Research.''} \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology} 10 (1).
 
 \leavevmode\hypertarget{ref-rotello2015more}{}%
-Rotello, C.
-M., Heit, E., \& Dubé, C.
-(2015).
-When more data steer us wrong: {R}eplications with the wrong dependent measure perpetuate erroneous conclusions.
-\emph{Psychonomic Bulletin \& Review}, \emph{22}(4), 944--954.
+Rotello, Caren M, Evan Heit, and Chad Dubé.
+2015.
+{``When More Data Steer Us Wrong: {R}eplications with the Wrong Dependent Measure Perpetuate Erroneous Conclusions.''} \emph{Psychonomic Bulletin \& Review} 22 (4): 944--54.
 
 \leavevmode\hypertarget{ref-rubio2016redundant}{}%
-Rubio-Fernández, P. (2016). How redundant are redundant color adjectives? An efficiency-based analysis of color overspecification. \emph{Frontiers in Psychology}, \emph{7}, 153.
+Rubio-Fernández, Paula. 2016. {``How Redundant Are Redundant Color Adjectives? An Efficiency-Based Analysis of Color Overspecification.''} \emph{Frontiers in Psychology} 7: 153.
 
 \leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
-Sedivy, J.
-C.
-(2003).
-Pragmatic versus form-based accounts of referential contrast: Evidence for effects of informativity expectations.
-\emph{Journal of Psycholinguistic Research}, \emph{32}(1), 3--23.
+Sedivy, Julie C.
+2003.
+{``Pragmatic Versus Form-Based Accounts of Referential Contrast: Evidence for Effects of Informativity Expectations.''} \emph{Journal of Psycholinguistic Research} 32 (1): 3--23.
 
 \leavevmode\hypertarget{ref-silberzahn2018many}{}%
-Silberzahn, R., Uhlmann, E.
-L., Martin, D.
-P., Anselmi, P., Aust, F., Awtrey, E., \ldots{} others.
-(2018).
-Many analysts, one data set: Making transparent how variations in analytic choices affect results.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(3), 337--356.
+Silberzahn, Raphael, Eric Luis Uhlmann, Daniel P Martin, Pasquale Anselmi, Frederik Aust, Eli Awtrey, Štěpán Bahnı́k, et al.
+2018.
+{``Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results.''} \emph{Advances in Methods and Practices in Psychological Science} 1 (3): 337--56.
 
 \leavevmode\hypertarget{ref-simmons2011false}{}%
-Simmons, J.
-P., Nelson, L.
-D., \& Simonsohn, U.
-(2011).
-False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
-\emph{Psychological Science}, \emph{22}(11), 1359--1366.
+Simmons, Joseph P, Leif D Nelson, and Uri Simonsohn.
+2011.
+{``False-Positive Psychology: Undisclosed Flexibility in Data Collection and Analysis Allows Presenting Anything as Significant.''} \emph{Psychological Science} 22 (11): 1359--66.
 
 \leavevmode\hypertarget{ref-stan2020a}{}%
-Stan Development Team. (2020). {RStan}: The {R} interface to {Stan}. Retrieved from \url{http://mc-stan.org/}
+Stan Development Team. 2020. {``{RStan}: The {R} Interface to {Stan}.''} \url{http://mc-stan.org/}.
 
 \leavevmode\hypertarget{ref-stan2021}{}%
-Stan Development Team. (2021). Stan modeling language users guide and reference manual, v2.26.0. Retrieved from \url{http://mc-stan.org/}
+---------. 2021. {``Stan Modeling Language Users Guide and Reference Manual, V2.26.0.''} \url{http://mc-stan.org/}.
 
 \leavevmode\hypertarget{ref-starns2019assessing}{}%
-Starns, J.
-J., Cataldo, A.
-M., Rotello, C.
-M., Annis, J., Aschenbrenner, A., Bröder, A., \ldots{} Wilson, J.
-(2019).
-Assessing theoretical conclusions with blinded inference to investigate a potential inference crisis.
-\emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 335--349.
+Starns, Jeffrey J, Andrea M Cataldo, Caren M Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
+2019.
+{``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
 
 \leavevmode\hypertarget{ref-sterling1959publication}{}%
-Sterling, T.
-D.
-(1959).
-Publication decisions and their possible effects on inferences drawn from tests of significance---or vice versa.
-\emph{Journal of the American Statistical Association}, \emph{54}(285), 30--34.
+Sterling, Theodore D.
+1959.
+{``Publication Decisions and Their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.''} \emph{Journal of the American Statistical Association} 54 (285): 30--34.
 
 \leavevmode\hypertarget{ref-sterne2005}{}%
-Sterne, J.
-A.
-C., Becker, B.
-J., \& Egger, M.
-(2005).
-The funnel plot.
-In H.
-R.
-Rothstein, A.
-J.
-Sutton, \& M.
-Borenstein (Eds.), \emph{Publication bias in meta-analysis: Prevention, assessment and adjustments} (pp.
-75--98).
+Sterne, Jonathan A.
+C., Betsy Jane Becker, and Matthias Egger.
+2005.
+{``The Funnel Plot.''} In \emph{Publication Bias in Meta-Analysis: Prevention, Assessment and Adjustments}, edited by Hannah R.
+Rothstein, Alexander J.
+Sutton, and Michael Borenstein, 75--98.
 Wiley Online Library.
@@
 \leavevmode\hypertarget{ref-sorensen1948}{}%
-Sørensen, T.
-(1948).
-A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on {D}anish commons.
-\emph{Kongelige Danske Videnskabernes Selskab}, \emph{5}(4), 1--34.
+Sørensen, Thorlvald.
+1948.
+{``A Method of Establishing Groups of Equal Amplitude in Plant Sociology Based on Similarity of Species and Its Application to Analyses of the Vegetation on {D}anish Commons.''} \emph{Kongelige Danske Videnskabernes Selskab} 5 (4): 1--34.
 
 \leavevmode\hypertarget{ref-tukey1977exploratory}{}%
-Tukey, J. W. (1977). \emph{Exploratory data analysis} (Vol. 2). Reading, MA.
+Tukey, John W. 1977. \emph{Exploratory Data Analysis}. Vol. 2. Reading, MA.
 
 \leavevmode\hypertarget{ref-tversky1974judgment}{}%
-Tversky, A., \& Kahneman, D. (1974). Judgment under uncertainty: Heuristics and biases. \emph{Science}, \emph{185}(4157), 1124--1131.
+Tversky, Amos, and Daniel Kahneman. 1974. {``Judgment Under Uncertainty: Heuristics and Biases.''} \emph{Science} 185 (4157): 1124--31.
 
 \leavevmode\hypertarget{ref-heuven2002}{}%
-Van Heuven, V.
-J., Haan, J., Gussenhoven, C., \& Warner, N.
-(2002).
-Temporal distribution of interrogativity markers in {D}utch: A perceptual study.
-In \emph{Laboratory phonology 7} (Vol.
-4, p.
-61).
+Van Heuven, Vincent J, Judith Haan, Carlos Gussenhoven, and Natasha Warner.
+2002.
+{``Temporal Distribution of Interrogativity Markers in {D}utch: A Perceptual Study.''} In \emph{Laboratory Phonology 7}, 4:61.
+1.
 Walter de Gruyter.
@@
 \leavevmode\hypertarget{ref-van2005speech}{}%
-Van Heuven, V. J., \& Van Zanten, E. (2005). Speech rate as a secondary prosodic characteristic of polarity questions in three languages. \emph{Speech Communication}, \emph{47}(1-2), 87--99.
+Van Heuven, Vincent J, and Ellen Van Zanten. 2005. {``Speech Rate as a Secondary Prosodic Characteristic of Polarity Questions in Three Languages.''} \emph{Speech Communication} 47 (1-2): 87--99.
 
 \leavevmode\hypertarget{ref-wagenmakers2012agenda}{}%
-Wagenmakers, E.-J., Wetzels, R., Borsboom, D., Maas, H.
-L.
-van der, \& Kievit, R.
-A.
-(2012).
-An agenda for purely confirmatory research.
-\emph{Perspectives on Psychological Science}, \emph{7}(6), 632--638.
+Wagenmakers, Eric-Jan, Ruud Wetzels, Denny Borsboom, Han LJ van der Maas, and Rogier A Kievit.
+2012.
+{``An Agenda for Purely Confirmatory Research.''} \emph{Perspectives on Psychological Science} 7 (6): 632--38.
 
 \leavevmode\hypertarget{ref-westerbeek2015stored}{}%
-Westerbeek, H., Koolen, R., \& Maes, A. (2015). Stored object knowledge and the production of referring expressions: The case of color typicality. \emph{Frontiers in Psychology}, \emph{6}, 935.
+Westerbeek, Hans, Ruud Koolen, and Alfons Maes. 2015. {``Stored Object Knowledge and the Production of Referring Expressions: The Case of Color Typicality.''} \emph{Frontiers in Psychology} 6: 935.
 
 \leavevmode\hypertarget{ref-white2009}{}%
-White, L., Payne, E., \& Mattys, S.
-L.
-(2009).
-Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian.
-In M.
+White, Laurence, Elinor Payne, and Sven L.
+Mattys.
+2009.
+{``Rhythmic and Prosodic Contrast in {V}enetan and {S}icilian {I}talian.''} In \emph{Phonetics and Phonology: Interactions and Interrelations}, edited by M.
 Vigario, S.
-Frota, \& M.
+Frota, and M.
 J.
-Freitas (Eds.), \emph{Phonetics and phonology: Interactions and interrelations} (pp.
-137--158).
+Freitas, 137--58.
 Amsterdam: John Benjamins.
@@
 \leavevmode\hypertarget{ref-wicherts2006poor}{}%
-Wicherts, J. M., Borsboom, D., Kats, J., \& Molenaar, D. (2006). The poor availability of psychological research data for reanalysis. \emph{American Psychologist}, \emph{61}(7), 726.
+Wicherts, Jelte M, Denny Borsboom, Judith Kats, and Dylan Molenaar. 2006. {``The Poor Availability of Psychological Research Data for Reanalysis.''} \emph{American Psychologist} 61 (7): 726.
 
 \leavevmode\hypertarget{ref-winter2014spoken}{}%
-Winter, B. (2014). Spoken language achieves robustness and evolvability by exploiting degeneracy and neutrality. \emph{BioEssays}, \emph{36}(10), 960--967.
+Winter, Bodo. 2014. {``Spoken Language Achieves Robustness and Evolvability by Exploiting Degeneracy and Neutrality.''} \emph{BioEssays} 36 (10): 960--67.
 

### 2021-02-22 scripts/r/simulations/simulations.Rmd
:memo: - start factors model

@@
 library(betapart)
-library(summarytools)
+# library(summarytools)
 my_seed <- 115116106
@@
 excl <- rbinom(n, 1, 0.5)
+# reviewers' ratings
+rating <- replicate(n, sample(0:100, sample(3:4, 1), replace = T))
 
@@
   excl,
+  rating,
   exp,
-  belf
+  belf,
+  rating_mean = unlist(map(rating, mean)),
+  rating_sd = unlist(map(rating, sd)),
+  exp_mean = unlist(map(exp, mean)),
+  exp_sd = unlist(map(exp, sd)),
+  belf_mean = unlist(map(belf, mean)),
+  belf_sd = unlist(map(belf, sd))
+) %>%
+  mutate(
+  # need the following in cases where score = 0
+  rating_mean = ifelse(rating_mean == 0, 0.01, rating_mean),
+  exp_mean = ifelse(exp_mean == 0, 0.01, exp_mean),
+  belf_mean = ifelse(belf_mean == 0, 0.01, belf_mean),
+  # need the following in cases where there only one person in the team
+  rating_sd = ifelse(is.na(rating_sd) | rating_sd == 0, 0.01, rating_sd),
+  exp_sd = ifelse(is.na(exp_sd) | exp_sd == 0, 0.01, exp_sd),
+  belf_sd = ifelse(is.na(belf_sd) | belf_sd == 0, 0.01, belf_sd)
 )
@@
   seed = my_seed,
+  cores = 4,
   file = "./models/sim/meta_bm"
@@
 ```
+
+# Factors analysis model
+
+```{r factors-priors}
+factors_priors <- c(
+  prior(normal(0, 1), class = Intercept),
+  prior(normal(0, 1), class = b),
+  prior(normal(0, 1), class = meanme),
+  prior(cauchy(0, 1), class = sdme),
+  prior(lkj(2), class = corme)
+)
+```
+
+```{r factors-bm}
+factors_bm <- brm(
+  eta | se(se) ~
+    pop_sdi +
+    phoc_n +
+    mod_n +
+    mdim +
+    twin +
+    excl +
+    me(rating_mean, rating_sd) +
+    me(exp_mean, exp_sd) +
+    me(belf_mean, belf_sd),
+  data = eta_tbl,
+  prior = factors_priors,
+  chain = 4,
+  iter = 4000,
+  control = list(max_treedepth = 15),
+  seed = my_seed,
+  cores = 4,
+  file = "./models/sim/factors_bm"
+)
+```

### 2021-02-22 RR_manuscript/Draft_RR.Rmd
:memo: edit RR

@@
 
-## The data set - The prosody of redundant modifiers
+## The data set: The acoustic properties of redundant modifiers
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
-(e.g.
-*a blue banana* vs *a yellow banana*)?
-We are interested in the acoustic profile of referring expressions.
+Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.
+the atypical *a blue banana* vs the typical *a yellow banana*)?
+More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.

### 2021-02-25 RR_manuscript/Draft_RR.Rmd
:memo: edit reviewing process in RR draft

@@
 fontsize: 12pt
+indent: true
 header-includes:
@@
 <!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN + TRANSITION -->
+To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
+The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
+The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
+The participant and the experimenter could not see each other nor each others' screens.
+After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
+Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.
+*Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
+
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participant would read a sentence prompt out loud (*Du sollst den Würfel auf der <COLOR OBJECT> ablegen* 'You have to put the cube on top of the <COLOR OBJECT>') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
+After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der <COLOR OBJECT> ablegen* 'And now, you have to put the cube on top of the <COLOR OBJECT>') instructing the experimenter to move the cube on top of a different object (the *target*).
+
+The two sentence prompts were used to create a focus contrast between the competitor and the target object.
+If the competitor and target objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (the Noun Focus condition, NF).
+If the the objects were the same object but differed in color (e.g. *yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
+If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
+The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
+The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
+The combinations were either typical (e.g. *Orangene Mandarine* 'orange mandarin'), medium typical (e.g. *Grüne Tomate* 'green tomato'), or atypical (e.g. *Gelbe Kirsche* 'yellow cherry').
+The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
+Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
 
@@
 Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
+
 The process for a single reviewer will be as follows.
 First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set.
+This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code and the data set.
 <!-- TODO: add link to peer review survey -->
-The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria: <!-- TR:Need flow chart here-->
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:
+<!-- TR:Need flow chart here-->
 
-"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+* Overall appropriateness of the acoustic analysis.
+* Overall appropriateness of the statistical analysis.
+* Choice of statistical analysis type.
+* Model variables choice.
+* Model specification.
+* Data exclusion.
+* Data transformation.
 
-- 100. A perfect analysis with no conceivable improvements from the reviewer.
-- 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
-- 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
-- 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
-- 0.
+To help reviewers calibrate their rating, they will be given the following guidelines:
+
+* 100. A perfect analysis with no conceivable improvements from the reviewer.
+* 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
+* 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
+* 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
+* 0.
 A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
 
-\*Please note that these values are meant to calibrate your ratings.
-We welcome ratings of any number between 0 and 100."
+Furthermore, the reviewer will be given the option to include further comments in a text box.
 
-After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:
-
-\noindent "Please explain your ratings of this analysis.
-\noindent Please evaluate the selection of acoustic features.
-\noindent Please evaluate the measurement of acoustic features.
-\noindent Please evaluate the choice of statistical analysis type.
-\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
-\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
-\noindent Please evaluate the suitability of the structure of the statistical model.
-\noindent Please evaluate choices to exclude or not exclude subsets of the data.
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice)."
-
-After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
+After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
-The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings."
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
+<!-- The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
+The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings." -->
 

### 2021-02-25 RR_manuscript/Draft_RR.tex
:memo: edit reviewing process in RR draft

@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
 \usepackage{xcolor}
@@
 
-\hypertarget{the-data-set---the-prosody-of-redundant-modifiers}{%
-\subsection{The data set - The prosody of redundant modifiers}\label{the-data-set---the-prosody-of-redundant-modifiers}}
+\hypertarget{the-data-set-the-acoustic-properties-of-redundant-modifiers}{%
+\subsection{The data set: The acoustic properties of redundant modifiers}\label{the-data-set-the-acoustic-properties-of-redundant-modifiers}}
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations?
-(e.g.~\emph{a blue banana} vs \emph{a yellow banana})?
-We are interested in the acoustic profile of referring expressions.
+Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.~the atypical \emph{a blue banana} vs the typical \emph{a yellow banana})?
+More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
+
+To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
+The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
+The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
+The participant and the experimenter could not see each other nor each others' screens.
+After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
+Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon,' \emph{Rote Gurke} `red cucumber,' \emph{Rote Socken} `red socks').
+
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der ablegen} `You have to put the cube on top of the ') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
+After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der ablegen} `And now, you have to put the cube on top of the ') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
+
+The two sentence prompts were used to create a focus contrast between the competitor and the target object.
+If the competitor and target objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (the Noun Focus condition, NF).
+If the the objects were the same object but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
+If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
+The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
+The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
+The combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
+The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
+Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
 
@@
 Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.
+
 The process for a single reviewer will be as follows.
 First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code, and the data set.
-The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on the following criteria:
+This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:
 
-"Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:
+\begin{itemize}
+\tightlist
+\item
+  Overall appropriateness of the acoustic analysis.
+\item
+  Overall appropriateness of the statistical analysis.
+\item
+  Choice of statistical analysis type.
+\item
+  Model variables choice.
+\item
+  Model specification.
+\item
+  Data exclusion.
+\item
+  Data transformation.
+\end{itemize}
+
+To help reviewers calibrate their rating, they will be given the following guidelines:
 
@@
 
-*Please note that these values are meant to calibrate your ratings.
-We welcome ratings of any number between 0 and 100."
+Furthermore, the reviewer will be given the option to include further comments in a text box.
 
-After providing this rating, the reviewer will then be shown a series of text boxes and the following prompts:
-
-\noindent ``Please explain your ratings of this analysis.
-\noindent Please evaluate the selection of acoustic features.
-\noindent Please evaluate the measurement of acoustic features.
-\noindent Please evaluate the choice of statistical analysis type.
-\noindent Please evaluate the process of choosing variables and structuring of the statistical model.
-\noindent Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
-\noindent Please evaluate the suitability of the structure of the statistical model.
-\noindent Please evaluate choices to exclude or not exclude subsets of the data.
-\noindent Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).''
-
-After submitting this review, a methods section from a second analysis will then be made available to the reviewer.
+After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
-The invitation to revise the original ratings will be as follows: ``If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.''
-The text box will be prefaced with this prompt: ``Please explain your choice to revise (or not to revise) your ratings.''
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
 

### 2021-02-25 RR_manuscript/Draft_RR.Rmd
:fire: - remove RR draft cache (cache is now in models/)

@@
 
-```{r meta-bm}
-set.seed(my_seed)
-n <- 12
-eta <- rnorm(n, 1, 0.5)
-se <- rhcauchy(n, 0.1)
-team <- letters[1:n]
-
-eta_tbl <- tibble(
-  eta,
-  se,
-  team
-)
-
-priors <- c(
-  prior(normal(0, 1), class = Intercept),
-  prior(cauchy(0, 1), class = sd)
-)
-
-meta_bm <- brm(
-  eta | se(se) ~
-    (1 | team),
-  data = eta_tbl,
-  prior = priors,
-  chain = 1,
-  seed = my_seed,
-  file = here::here("RR_manuscript", "cache", "meta_bm")
-)
-```
-
 Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).

### 2021-02-25 docs/Registered_Report_Analysis_Script.R
:fire: - remove unused files in docs/

@@ -1,39 +1,0 @@
-#Transcribe data from Silberzahn et al. 2018. Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results. Advances in Methods and Practices in Psychological Science
-
-#Odds Ratio Results
-MeanOdds<-c(1.18,1.28,1.21,1.21,1.25,1.03,1.34,1.28,1.12,1.39,1.39,1.02,1.31,1.38,1.48,0.96,1.10,1.31,1.38,1.42,1.38,2.88,1.71,0.89,2.93,1.41,1.32,1.4,1.3)
-Lower<-c(.95,.77,.97,1.20,1.05,1.01,1.1,1.04,0.88,1.1,1.17,1,1.09,1.10,1.20,.77,.98,1.1,1.11,1.19,1.12,1.03,1.7,.49,.11,1.13,1.06,1.15,1.08)
-Upper<-c(1.41,2.13,1.46,1.21,1.49,1.05,1.63,1.57,1.43,1.75,1.65,1.03,1.57,1.75,1.84,1.18,1.27,1.56,1.72,1.71,1.71,11.47,1.72,1.60,78.66,1.75,1.63,1.71,1.56)
-Team<-seq(1:29) #note that teams aren't in the order specified in Silberzahn
-Silberzahn<-cbind.data.frame(M,Lower,Upper,Team)
-write.csv(Silberzahn,"./Silberzahn_OR.csv")
-
-#Investigate what the odds ratio data would look like without the two major outliers
-SilberzahnNOutliers<-Silberzahn[-c(22,25),]
-write.csv(SilberzahnNOutliers,"./Silberzahn_OR_nooutliers.csv")
-
-#Analysis Variable Results
-position<-c(1,1,1,0,0,1,0,0,1,1,1,1,1,1,0,0,0,0,1,1,1,1,1,1,0,1,1,1,1)
-height<-c(1,1,0,1,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,1,0,1,1,1,0,0,1,1,0)
-weight<-c(1,1,0,1,0,1,0,0,0,0,0,1,0,1,0,0,0,0,0,0,0,1,1,1,0,0,1,1,0)
[…]

### 2021-02-25 scripts/r/00_libs.R
:fire: - remove unused files in scripts/r/

@@ -1,22 +1,0 @@
-# Packages --------------------------------------------------------------------
-
-library("here")
-library("tidyverse")
-library("readr")
-library("ggrepel")
-library("purrr")
-library("dplyr")
-library("tidyr")
-library("glue")
-library("ggplot2")
-library("ganttrify")
-library("truncnorm")
-library("lme4")
-library("brms")
-library("rstudioapi")
-library("betapart")
-library("tidybayes")
-library("patchwork")
-library("broom.mixed")
-
-# -----------------------------------------------------------------------------

### 2021-02-25 scripts/r/00_plot_gantt.R

@@ -1,77 +1,0 @@
-# GANTT chart for RR ----------------------------------------------------------
-#
-# Last update: 20200917
-# About: This script produces a gantt chart of our project timeline
-#        The plot is produced using ganttrify: 
-#        https://github.com/giocomai/ganttrify
-#
-# -----------------------------------------------------------------------------
-
-
-
-# Source libs -----------------------------------------------------------------
-
-source(here::here("scripts", "r", "00_libs.R"))
-
-# -----------------------------------------------------------------------------
-
-
-
-
-# Create timeline df ----------------------------------------------------------
-
-# This is proof of concept, will change
-time_line_df <- tribble(
-  ~'wp',                ~'activity',          ~'start_date',  ~'end_date',
-  "Initiating authors", "Recruiting",         "2021-02-01",   "2021-04-01",
-  "Analysis teams",     "Survey",             "2021-04-01",   "2021-04-15",
-  "Analysis teams",     "Analysis",           "2021-04-15",   "2021-06-15",
-  "Analysis teams",     "Post-Survey",        "2021-06-15",   "2021-06-30",
-  "Reviewer",           "Review Analyses",    "2021-07-01",   "2021-07-31",
-  "Initiating authors", "Final Analysis",     "2021-08-01",   "2021-08-30",
-  "Initiating authors", "Write-Up",           "2021-09-01",   "2021-10-15",
-  # hacky way of having three rows for all teams doing the write up
-  "Analysis teams",     "Write-Up ",          "2021-09-01",   "2021-10-15",
-  "Reviewer",           "Write-Up  ",         "2021-09-01",   "2021-10-15"
-)
-
-# "Spots" can be used to mark when things actually occur on expected timeline
-# Not used for now ("X" implies something is finished)
-time_line_spots <- tribble(
-  ~'activity',           ~'spot_type', ~'spot_date', 
-  "Data visualisation",  "X",         "2020-10-30", 
-  "Writing",             "X",         "2020-10-31"
-)
-
-# -----------------------------------------------------------------------------
-
-
-
-
-
-
-
-
-# Generate and save plot ------------------------------------------------------
-
-p_project_timeline <- ganttrify(
-  project = time_line_df,
-  #spots = time_line_spots,
-  by_date = TRUE,
-  exact_date = TRUE,
-  colour_palette = c("#FDE624", "#1EA385", "#450D53"),
-  size_text_relative = 1.2,
-  month_number = FALSE,
[…]

### 2021-02-25 scripts/r/00_sim_ma.R

@@ -1,263 +1,0 @@
-# Meta-analysis of simulated data ---------------------------------------------
-#
-# Last update: 20201115
-# About: This script loads simulated data and uses brms to conduct a 
-#        meta-analysis
-#
-# -----------------------------------------------------------------------------
-
-# Source libs and load simulated data -----------------------------------------
-source(here::here("scripts", "r", "00_libs.R"))
-sim_df <- read_csv(here("data", "sim", "simulated_df_distances.csv")) %>% 
-  mutate(posthoc_sum = if_else(posthoc == 0, -1, 1), 
-         nmodels_std = (nmodels - mean(nmodels)) / sd(nmodels), 
-         fixed_sim_std = (fixed_similarity - mean(fixed_similarity)) / sd(fixed_similarity), 
-         random_sim_std = (random_similarity - mean(random_similarity)) / sd(random_similarity), 
-         peer_rating_std = (peer_rating - mean(peer_rating)) / sd(peer_rating))
-
-# -----------------------------------------------------------------------------
-
-
-
-
-# Bayesian meta analysis ------------------------------------------------------
-
-# Set priors
-priors <- c(prior(normal(0, 1), class = Intercept),
-            prior(cauchy(0, 1), class = sd))
-
-# Fit model
-ma_sim_m0 <- brm(
-  formula = es | se(se) ~ 1 + (1 | team), 
-  family = gaussian, 
-  data = sim_df,
-  prior = priors,
-  iter = 4000, warmup = 2000, cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.99, max_treedepth = 15),
-  file = here("models", "sim", "ma_sim_m0")
-)
-
-# Add pooling method
-ma_sim_m1 <- brm(
-  formula = es | se(se) ~ 1 + (1 | team) + (1 | reviewer), 
-  family = gaussian, 
-  data = sim_df,
-  prior = priors,
-  iter = 4000, warmup = 2000,  cores = 4, chains = 4, 
-  control = list(adapt_delta = 0.9999, max_treedepth = 15), 
-  file = here("models", "sim", "ma_sim_m1")
-)
-
-# Fit between variable model (add posthoc)
-ma_sim_m2 <- brm(
-  formula = es | se(se) ~ 0 + Intercept + posthoc_sum + 
[…]

### 2021-02-25 scripts/r/00_sim_data.R
:fire: - remove unused files in scripts/r/

@@ -1,198 +1,0 @@
-### Info # ---------------------------------------------------------------------
-#
-## Author:  Timo Roettger (timo.b.roettger @ gmail.com)
-#
-## Project: Many speech analyses
-#
-## Description: simulate hypothetical data for hypothesis testing analysis
-#
-## Version: 11/11/2020
-# ------------------------------------------------------------------------------
-
-## libraries--------------------------------------------------------------------
-source(here::here("scripts", "r", "00_libs.R"))
-
-## set parameters---------------------------------------------------------------
-
-# number of observations
-nobs = 1
-
-# overall effect
-meta_effect = 1
-
-# probability of peer verdict
-prob_peer_verdict = c(0.2, 0.6, 0.15, 0.05)
-
-# probability for fixed effect
-fixed_prob = 0.3
-
-# probability for random effect
-random_prob = 0.5
-
-# probability of posthoc changes
-post_prob = 0.2
-
-# lambda for models run
-models_lambda = 3
-
-# number of team
-nteams = 16
-
-# number of reviewers
-nrevs  = nteams
-
-# number of reviews per reviewer
-nreviews  = 4
-
-# random fluctuation between reviewers for rating
-rand_revs = 0.5
-
-## loop and create data frame for teams-----------------------------------------
-
-# create empty vectors
-team_c = c()
-reviewer_c = c()
-dv_c = c()
-se_c = c()
-peer_rating_c = c()
-posthoc_c = c()
-nmodels_c = c()
-
-# create logical vectors for different fixed & random parameters
-fixed_1_c = c()
-fixed_2_c = c()
-fixed_3_c = c()
-fixed_4_c = c()
-fixed_5_c = c()
-random_1_c = c()
-random_2_c = c()
-random_3_c = c()
-random_4_c = c()
-random_5_c = c()
-
-
-for (i in 1:nteams) { 
-  # print progress
-  print(paste0("random sample # ", i))
-  
-  team_c = c(team_c, 
-             paste0("team_", i))
-
-  ## generate parameters
-
-  # generate effect size 
-  dv_c <- c(dv_c,
-            rnorm(n = nobs, mean = meta_effect, sd = 1))
-  
-  # generate standard error (NOTE: in our model SE is equivalent to SD which 
-  # by def. must be non-negative)
-  se_c <- c(se_c,
-            rnorm(n = nobs, mean = 1, sd = 0.35))
[…]

### 2021-02-25 scripts/r/00_sim_raw.R

@@ -1,81 +1,0 @@
-### Info # ---------------------------------------------------------------------
-#
-## Author:  Timo Roettger (timo.b.roettger @ gmail.com)
-#
-## Project: Many speech analyses
-#
-## Description: simulate hypothetical analyses for hypothesis testing analysis
-#
-## Version: 11/11/2020
-# ------------------------------------------------------------------------------
-
-## libraries--------------------------------------------------------------------
-source(here::here("scripts", "r", "00_libs.R"))
-
-# load in original data
-fruits <- read_csv(here("data", "dataset", "processed_fruits.csv"))
-
-## come up with three options to answer research question:
-# Option#1 centered predictor typicality, 
-# random intercepts for speakers-only
-
-fruits$mean_typicality_s <- scale(fruits$mean_typicality, scale = F)
-
-xmdl1 <- lmer(duration ~  mean_typicality_s +
-                  (1| speaker),
-                data = fruits)
-# TR: This is rather straightforward
-
-# Option#2 uncentered predictor typicality interacting with color, 
-# random intercepts for speakers and objects
-xmdl2 <- lmer(duration ~  mean_typicality * colour +
-                (1| speaker) +
-                (1 | object),
-              data = fruits)
-
-# TR: This is complicated immediately: colour is not contrast-coded, 
-# So the estimate for mean_typicality will be the estimate for the colour reference
-# level. Additionally, is the interaction term relevant for the research question? 
-# or just the main effect?
-# Solution: Different coding and standardization of typicality. Decision as to
-# what coefficient answers the question.
-
-# Option#3 uncentered predictor typicality with additional predictor colour,
-# colour is dummy coded, 
-# random intercepts for speakers and objects + by-speaker random slopes for mean_typicality
-
-xmdl3 <- lmer(duration ~  mean_typicality + colour +
-                (mean_typicality || speaker) +
-                (1 | object),
-              data = fruits)
-
-# TR: Same situation as above
-
-# extract stuff
-m1 <- tidy(xmdl1) %>% 
-  select(effect, term, estimate, std.error) %>% 
-  filter(effect == "fixed",
-         term == "mean_typicality_s") %>% 
-  mutate(model = "model1")
-
-m2 <- tidy(xmdl2) %>% 
-  select(effect, term, estimate, std.error) %>% 
-  filter(effect == "fixed",
-         term %in% c("mean_typicality",
[…]

### 2021-02-25 scripts/r/00_sim_similarity.R

@@ -1,154 +1,0 @@
-# betapart shenanigans --------------------------------------------------------
-
-
-# Source libs and load simulated data -----------------------------------------
-
-source(here::here("scripts", "r", "00_libs.R"))
-sim_df <- read_csv(here("data", "sim", "simulated_df.csv"))
-ma_sim_m5 <- readRDS(here("models", "sim", "ma_sim_m5.rds"))
-
-# global color scheme / non-optimized
-cat1_col = "#d95f02"
-cat2_col = "#7570b3"
-cat3_col = "#1b9e77"
-
-
-# -----------------------------------------------------------------------------
-
-# bring into betapart shape
-fixed_df <- sim_df %>% 
-  mutate(team_reviewer = paste0(team, "_", reviewer)) %>% 
-  column_to_rownames(var = "team_reviewer") %>% 
-  select(fixed_1,
-         fixed_2,
-         fixed_3,
-         fixed_4,
-         fixed_5)
-
-random_df <- sim_df %>% 
-  mutate(team_reviewer = paste0(team, "_", reviewer)) %>% 
-  column_to_rownames(var = "team_reviewer") %>% 
-  select(random_1,
-         random_2,
-         random_3,
-         random_4,
-         random_5)
-
-# get betapart objects
-df.core.fixed <- betapart.core(fixed_df)
-df.core.random <- betapart.core(random_df)
-
-# get pairwise distance
-df.pair.fixed <- beta.pair(df.core.fixed, index.family = "sorensen")
-df.pair.random <- beta.pair(df.core.random, index.family = "sorensen")
-
-# which one is it? beta.sim / beta.sne / beta.sor?
-# if beta.sor then
-
-df.pair.fixed.sor <- broom::tidy(df.pair.fixed$beta.sor) %>% 
-  rename(team = item1) %>% 
-  group_by(team) %>% 
-  summarise(distance_fixed_mean = mean(distance), .groups = "drop")
-
-df.pair.random.sor <- broom::tidy(df.pair.random$beta.sor) %>% 
-  rename(team = item1) %>% 
-  group_by(team) %>% 
-  summarise(distance_random_mean = mean(distance), .groups = "drop")
-
-# this way we only get values for team1-15 ?
-# this is how ecoRR does it
-
-df.pair.fixed.sor <- as.matrix(beta.pair(df.core.fixed, index.family = "sorensen")$beta.sor)
-fixed_similarity <- colMeans(df.pair.fixed.sor, na.rm = T) 
-
[…]

### 2021-02-25 docs/methods_norm_prod/methods_norm_prod.Rmd
:bento: - upload methods description to the OSF

--- 2021-01-19 docs/ExperimentalDetails/Experimental_details.Rmd
@@
 ---
-title: "Production study: Methodological details"
+title: "Methodological details of the norming and production studies"
 author: ""
@@
     keep_tex: true
+fontsize: 12pt
 header-includes:
+  - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{expex}
@@
 knitr::opts_chunk$set(echo = TRUE, fig.pos = "tbp")
+knitr::opts_knit$set(root.dir = here::here())
+library(here)
 options(tinytex.verbose = TRUE)
@@
 
-This document describes the methodological details of the production study, which generated the data your team will analyze for the *Many Speech Analyses* project.
+This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the *Many Speech Analyses* project.
+
+The norming study was run to obtain ratings on the typicality of color/object combinations used to create the experimental categories manipulated in the production study.
+The production study then investigated whether speakers modify speech to signal the (a)typicality of the color/object combinations.
+Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like *blue banana* is different from one with a typical referent such as *yellow banana*.
 
 <!-- TODO: link to OSF wiki for overview of the norming and production studies -->
-Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \@ref(norming) for context.
 
-# Research question
+# Norming study
 
-This study investigated whether speakers modify speech to signal atypical referents.
-Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like *blue banana* is different from one with a typical referent such as *yellow banana*.
-
-# Participants
-
-Thirty native German speakers participated in this study.
-All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
-Participants were paid for their participation.
-
-# Procedure
-
-In this production study, participants interacted with the experimenter in German.
-Participants were seated in front of a computer screen.
-The experimenter sat at the opposite side of the table in front of another computer screen.
-The participants and the experimenter could not see each other nor each others' screens.
-The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
-The non-target objects differed from the target with respect to their color, their identity, or both.
-Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.
-*Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
-These color-object combinations differed with respect to their typicality.
-The color-object combinations were either typical (e.g.
-*Orangene Mandarine* 'orange mandarin'), medium typical (e.g.
-*Grüne Tomate* 'green tomato'), or atypical (e.g.
-*Gelbe Kirsche* 'yellow cherry').
-The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \@ref(norming) for details).
-Figure \@ref(fig:image0) illustrates combination typicality for a banana, a tomato, and an apricot.
-
-```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}
-
-knitr::include_graphics("typicality_examples.png")
-
-```
-
-The experiment consisted of two phases: a familiarization phase and a test phase.
-
-In a familiarization phase, participants saw the picture of one object per trial.
-In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
-During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
-For example, one of the experimental targets was a red banana (atypical).
-The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
-This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
-
-After the familiarization phase, the participants entered the test phase.
-On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
-One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
-The position of the visual stimuli was randomized for each trial and each participant (see Appendix \@ref(random)).
-In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
-
-```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of a trigger instruction.
-The trigger instruction is displayed in the middle below the cube.
-Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).", out.extra="frame"}
-
-knitr::include_graphics("sample_experiment_screen_competitor.png")
-
-```
-
-Each test trial consisted of two parts.
-The trigger instruction and the test instruction.
-After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \@ref(fig:image1)).
-The trigger instruction was constituted by the frame sentence *Du sollst den Würfel auf X ablegen*.
-*X* was one of the adjective-noun combinations.
-
-For example, the subjects saw the following sentence:
-
-```{=latex}
-\ex \begingl
-\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
-\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
-\glb you have.to the cube on the green sunglasses put//
-\glft `You have to put the cube on top of the green sunglasses.'//
-\endgl \xe
-```
-
-The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: *green* and *sunglasses*).
-The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
-
-Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \@ref(fig:image2)).
-This time the frame sentence was *Und jetzt sollst du den Würfel auf X ablegen*, where *X* was again an adjective-noun combination.
-To continue the example above, the subject would see the following test instruction:
-
-```{=latex}
-\ex \begingl
-\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
-\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
-\glb and now have.to you the cube on the green avocado put//
-\glft `And now, you have to put the cube on top of the green avocado.'//
-\endgl \xe
-```
-
-```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of the test instruction.
-The target sentence is displayed in the middle of the screen.
-Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).", out.extra="frame"}
-
-knitr::include_graphics("sample_experiment_screen_target.png")
-
-```
-
-The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
-There was a 3000 ms inter stimulus interval between trials (grey screen).
-In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
-
-Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
-If the color of the competitor and the target are of the same object type but differed in color (e.g.
-*yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
-If the objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (henceforth the Noun Focus (NF) condition).
-If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
-
-There were 15 NF trials, 10 AF and 10 ANF trials each.
-Each trial occurred two times per participants, yielding a total of 70 trials per participant.
-
-The program (implemented as a browser-based application) used for the experiment is available at the following link: <https://github.com/SBRitter/fruits-production>.
-
-\appendix
-
-# Randomization {#random}
-
-In the production study, the combination of target/competitor/distractors were randomized in each trial.
-Randomization was restricted to satisfy the following criteria, depending on the condition.
-
-- NF-Condition:
-  - Color of Target = Color of Competitor.
-  - Object of Target != Object of Competitor.
-
-- AF-Condition:
-  - Color of Target != Color of Competitor.
-  - Object of Target = Object of Competitor.
-
-- DF-Condition:
-  - Color of Target != Color of Competitor.
-  - Object of Target != Object of Competitor.
-
-- Distractors, all conditions:
-  - Both distractors have to differ in color and object identity from both target and competitor.
-
-The competitor and distractors were matched iteratively to a target.
-One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
-<!-- NOTE: (SC) I don't understand this bit. Need clarification. -->
-
-The set of four objects (quadruple) was formed separately for each of the three focus conditions.
-After the three lists had been compiled, they were merged.
-The sequence of quadruples was randomized such that the following requirements were met:
-
-- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
-- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
-- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
-
-Following these criteria, one randomized list for each subject was produced.
-The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
-<!-- NOTE: (SC) Which first list? -->
-In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
-
-The python code for the randomization is available at the following link: <https://github.com/SBRitter/fruits-randomization>.
-
-# Norming study {#norming}
-
-Here we specify in detail the selection of the stimuli for the production study.
+Here we specify in detail the selection of the stimuli used in the production study.
 
@@
 
-The selection of stimuli was informed by a norming study for which we have chosen twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs).
-Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting our objects were supposed to contain as few voiceless segments as possible.
+The selection of stimuli was informed by a norming study for which twenty fruits or vegetables (henceforth: FOODs) and four other referents (henceforth: NON-FOODs) were chosen.
+Selection criteria were mainly informed by visual discriminability and phonemic composition, such that nouns denoting objects were supposed to contain as few voiceless segments as possible.
 
@@
 Overall, the sets of target, competitors and distractors were combined such that all five colors occurred equally often throughout the experiment (i.e. 28 times).
+
+# Production study
+
+## Participants
+
+Thirty native German speakers participated in this study.
+All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
+Participants were paid for their participation.
+
+## Procedure
+
+In this production study, participants interacted with the experimenter in German.
+Participants were seated in front of a computer screen.
+The experimenter sat at the opposite side of the table in front of another computer screen.
+The participants and the experimenter could not see each other nor each others' screens.
+The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
+The non-target objects differed from the target with respect to their color, their identity, or both.
+Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.
+*Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
+These color-object combinations differed with respect to their typicality.
+The color-object combinations were either typical (e.g.
+*Orangene Mandarine* 'orange mandarin'), medium typical (e.g.
+*Grüne Tomate* 'green tomato'), or atypical (e.g.
+*Gelbe Kirsche* 'yellow cherry').
+Figure \@ref(fig:image0) illustrates combination typicality for a banana, a tomato, and an apricot.
+
+```{r image0, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Three examples for typical, medium typical and atypical combinations of colour and object."}
+knitr::include_graphics(here("figs", "typicality_examples.png"))
+```
+
+The experiment consisted of two phases: a familiarization phase and a test phase.
+
+In a familiarization phase, participants saw the picture of one object per trial.
+In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
+During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
+For example, one of the experimental targets was a red banana (atypical).
+The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
+This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
+
+After the familiarization phase, the participants entered the test phase.
+On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
+One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
+The position of the visual stimuli was randomized for each trial and each participant (see Appendix \@ref(random)).
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
+
+```{r image1, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of a trigger instruction.
+The trigger instruction is displayed in the middle below the cube.
+Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).", out.extra="frame"}
+knitr::include_graphics(here("figs", "sample_experiment_screen_competitor.png"))
+```
+
+Each test trial consisted of two parts.
+The trigger instruction and the test instruction.
+After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \@ref(fig:image1)).
+The trigger instruction was constituted by the frame sentence *Du sollst den Würfel auf X ablegen*.
+*X* was one of the adjective-noun combinations.
+
+For example, the subjects saw the following sentence:
+
+```{=latex}
+\ex \begingl
+\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
+\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
+\glb you have.to the cube on the green sunglasses put//
+\glft `You have to put the cube on top of the green sunglasses.'//
+\endgl \xe
+```
+
+The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: *green* and *sunglasses*).
+The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
+
+Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \@ref(fig:image2)).
+This time the frame sentence was *Und jetzt sollst du den Würfel auf X ablegen*, where *X* was again an adjective-noun combination.
+To continue the example above, the subject would see the following test instruction:
+
+```{=latex}
+\ex \begingl
+\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
+\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
+\glb and now have.to you the cube on the green avocado put//
+\glft `And now, you have to put the cube on top of the green avocado.'//
+\endgl \xe
+```
+
+```{r image2, echo = FALSE, fig.align="center", out.width = "60%", fig.cap = "Test trial: Example screen of the test instruction.
+The target sentence is displayed in the middle of the screen.
+Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).", out.extra="frame"}
+knitr::include_graphics(here("figs", "sample_experiment_screen_target.png"))
+```
+
+The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
+There was a 3000 ms inter stimulus interval between trials (grey screen).
+In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
+
+Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
+If the color of the competitor and the target are of the same object type but differed in color (e.g.
+*yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
+If the objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (henceforth the Noun Focus (NF) condition).
+If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
+
+There were 15 NF trials, 10 AF and 10 ANF trials each.
+Each trial occurred two times per participants, yielding a total of 70 trials per participant.
+
+The program (implemented as a browser-based application) used for the experiment is available at the following link: <https://github.com/SBRitter/fruits-production>.
+
+\appendix
+
+# Randomization {#random}
+
+In the production study, the combination of target/competitor/distractors were randomized in each trial.
+Randomization was restricted to satisfy the following criteria, depending on the condition.
+
+- NF-Condition:
+  - Color of Target = Color of Competitor.
+  - Object of Target != Object of Competitor.
+
+- AF-Condition:
+  - Color of Target != Color of Competitor.
+  - Object of Target = Object of Competitor.
+
+- DF-Condition:
+  - Color of Target != Color of Competitor.
+  - Object of Target != Object of Competitor.
+
+- Distractors, all conditions:
+  - Both distractors have to differ in color and object identity from both target and competitor.
+
+The competitor and distractors were matched iteratively to a target.
+One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
+<!-- NOTE: (SC) I don't understand this bit. Need clarification. -->
+
+The set of four objects (quadruple) was formed separately for each of the three focus conditions.
+After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following requirements were met:
+
+- The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
+- The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
+- The list can have the same experimental condition in adjacent trials only in maximally 12% of all cases.
+
+Following these criteria, one randomized list for each subject was produced.
+The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
+<!-- NOTE: (SC) Which first list? -->
+In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
+
+The python code for the randomization is available at the following link: <https://github.com/SBRitter/fruits-randomization>.

### 2021-02-25 docs/methods_norm_prod/methods_norm_prod.tex
:bento: - upload methods description to the OSF

--- 2021-01-19 docs/ExperimentalDetails/Experimental_details.tex
@@
 \documentclass[
+  12pt,
 ]{article}
@@
 \hypersetup{
-  pdftitle={Production study: Methodological details},
+  pdftitle={Methodological details of the norming and production studies},
   hidelinks,
@@
 \setcounter{secnumdepth}{5}
+\renewcommand{\familydefault}{\sfdefault}
 \usepackage{expex}
@@
 
-\title{Production study: Methodological details}
+\title{Methodological details of the norming and production studies}
 \author{}
@@
 
-This document describes the methodological details of the production study, which generated the data your team will analyze for the \emph{Many Speech Analyses} project.
+This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the \emph{Many Speech Analyses} project.
 
-Although the details of the norming study (run prior to the production study, see OSF Wiki) might not be directly relevant for your analysis, we provide an outline of the norming study methods in Appendix \ref{norming} for context.
-
-\hypertarget{research-question}{%
-\section{Research question}\label{research-question}}
-
-This study investigated whether speakers modify speech to signal atypical referents.
+The norming study was run to obtain ratings on the typicality of color/object combinations used to create the experimental categories manipulated in the production study.
+The production study then investigated whether speakers modify speech to signal the (a)typicality of the color/object combinations.
 Concretely, we asked whether the acoustic profile of an utterance with an atypical referent like \emph{blue banana} is different from one with a typical referent such as \emph{yellow banana}.
 
-\hypertarget{participants}{%
-\section{Participants}\label{participants}}
+\hypertarget{norming-study}{%
+\section{Norming study}\label{norming-study}}
 
-Thirty native German speakers participated in this study.
-All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
-Participants were paid for their participation.
-
-\hypertarget{procedure}{%
-\section{Procedure}\label{procedure}}
-
-In this production study, participants interacted with the experimenter in German.
-Participants were seated in front of a computer screen.
-The experimenter sat at the opposite side of the table in front of another computer screen.
-The participants and the experimenter could not see each other nor each others' screens.
-The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
-The non-target objects differed from the target with respect to their color, their identity, or both.
-Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
-These color-object combinations differed with respect to their typicality.
-The color-object combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
-The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix \ref{norming} for details).
-Figure \ref{fig:image0} illustrates combination typicality for a banana, a tomato, and an apricot.
-
-\begin{figure}[tbp]
-
-{\centering \includegraphics[width=0.6\linewidth]{typicality_examples}
-
-}
-
-\caption{Three examples for typical, medium typical and atypical combinations of colour and object.}\label{fig:image0}
-\end{figure}
-
-The experiment consisted of two phases: a familiarization phase and a test phase.
-
-In a familiarization phase, participants saw the picture of one object per trial.
-In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
-During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
-For example, one of the experimental targets was a red banana (atypical).
-The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
-This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
-
-After the familiarization phase, the participants entered the test phase.
-On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
-One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
-The position of the visual stimuli was randomized for each trial and each participant (see Appendix \ref{random}).
-In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
-
-\begin{figure}[tbp]
-
-{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_competitor}
-
-}
-
-\caption{Test trial: Example screen of a trigger instruction.
-The trigger instruction is displayed in the middle below the cube.
-Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).}\label{fig:image1}
-\end{figure}
-
-Each test trial consisted of two parts.
-The trigger instruction and the test instruction.
-After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \ref{fig:image1}).
-The trigger instruction was constituted by the frame sentence \emph{Du sollst den Würfel auf X ablegen}.
-\emph{X} was one of the adjective-noun combinations.
-
-For example, the subjects saw the following sentence:
-
-\ex \begingl
-\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
-\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
-\glb you have.to the cube on the green sunglasses put//
-\glft `You have to put the cube on top of the green sunglasses.'//
-\endgl \xe
-
-The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: \emph{green} and \emph{sunglasses}).
-The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
-
-Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \ref{fig:image2}).
-This time the frame sentence was \emph{Und jetzt sollst du den Würfel auf X ablegen}, where \emph{X} was again an adjective-noun combination.
-To continue the example above, the subject would see the following test instruction:
-
-\ex \begingl
-\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
-\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
-\glb and now have.to you the cube on the green avocado put//
-\glft `And now, you have to put the cube on top of the green avocado.'//
-\endgl \xe
-
-\begin{figure}[tbp]
-
-{\centering \includegraphics[width=0.6\linewidth,frame]{sample_experiment_screen_target}
-
-}
-
-\caption{Test trial: Example screen of the test instruction.
-The target sentence is displayed in the middle of the screen.
-Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).}\label{fig:image2}
-\end{figure}
-
-The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
-There was a 3000 ms inter stimulus interval between trials (grey screen).
-In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
-
-Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
-If the color of the competitor and the target are of the same object type but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
-If the objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (henceforth the Noun Focus (NF) condition).
-If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
-
-There were 15 NF trials, 10 AF and 10 ANF trials each.
-Each trial occurred two times per participants, yielding a total of 70 trials per participant.
-
-The program (implemented as a browser-based application) used for the experiment is available at the following link: \url{https://github.com/SBRitter/fruits-production}.
-
-\appendix
-
-\hypertarget{random}{%
-\section{Randomization}\label{random}}
-
-In the production study, the combination of target/competitor/distractors were randomized in each trial.
-Randomization was restricted to satisfy the following criteria, depending on the condition.
-
-\begin{itemize}
-\tightlist
-\item
-  NF-Condition:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Color of Target = Color of Competitor.
-  \item
-    Object of Target != Object of Competitor.
-  \end{itemize}
-\item
-  AF-Condition:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Color of Target != Color of Competitor.
-  \item
-    Object of Target = Object of Competitor.
-  \end{itemize}
-\item
-  DF-Condition:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Color of Target != Color of Competitor.
-  \item
-    Object of Target != Object of Competitor.
-  \end{itemize}
-\item
-  Distractors, all conditions:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    Both distractors have to differ in color and object identity from both target and competitor.
-  \end{itemize}
-\end{itemize}
-
-The competitor and distractors were matched iteratively to a target.
-One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
-
-The set of four objects (quadruple) was formed separately for each of the three focus conditions.
-After the three lists had been compiled, they were merged.
-The sequence of quadruples was randomized such that the following requirements were met:
-
-\begin{itemize}
-\tightlist
-\item
-  The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
-\item
-  The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
-\item
-  The list can have the same experimental condition in adjacent trials only in maximally 12\% of all cases.
-\end{itemize}
-
-Following these criteria, one randomized list for each subject was produced.
-The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
-In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
-
-The python code for the randomization is available at the following link: \url{https://github.com/SBRitter/fruits-randomization}.
-
-\hypertarget{norming}{%
-\section{Norming study}\label{norming}}
-
-Here we specify in detail the selection of the stimuli for the production study.
+Here we specify in detail the selection of the stimuli used in the production study.
 
@@
 
+\hypertarget{production-study}{%
+\section{Production study}\label{production-study}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Thirty native German speakers participated in this study.
+All participants grew up in a monolingual environment and were recruited from the population living in the broad Cologne area with normal or corrected-to-normal vision and normal hearing.
+Participants were paid for their participation.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+In this production study, participants interacted with the experimenter in German.
+Participants were seated in front of a computer screen.
+The experimenter sat at the opposite side of the table in front of another computer screen.
+The participants and the experimenter could not see each other nor each others' screens.
+The participants had to verbally instruct the experimenter to select a specified target object out of four visually presented objects.
+The non-target objects differed from the target with respect to their color, their identity, or both.
+Objects were referred to using noun phrases that consist of a modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
+These color-object combinations differed with respect to their typicality.
+The color-object combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
+Figure \ref{fig:image0} illustrates combination typicality for a banana, a tomato, and an apricot.
+
+\begin{figure}[tbp]
+
+{\centering \includegraphics[width=0.6\linewidth]{/Users/ste/repos/many_analyses/figs/typicality_examples}
+
+}
+
+\caption{Three examples for typical, medium typical and atypical combinations of colour and object.}\label{fig:image0}
+\end{figure}
+
+The experiment consisted of two phases: a familiarization phase and a test phase.
+
+In a familiarization phase, participants saw the picture of one object per trial.
+In order to advance to the next trial, participants had to read out loud the corresponding color-object combination.
+During this phase, participants had to name all atypical color-object targets that we used in the test phase of the experiment alongside their typical counterparts.
+For example, one of the experimental targets was a red banana (atypical).
+The participants were presented with the picture of both a red banana (atypical) and a yellow banana (typical).
+This familiarization phase was included in order to ensure that participants could relate typical and atypical color-object combinations to each other.
+
+After the familiarization phase, the participants entered the test phase.
+On each trial in the test phase, the subjects first saw four colored objects in the top left, top right, bottom left, and bottom right of the screen, respectively.
+One of the object served as the target; another served as the competitor; and the remaining two served as unrelated distractors.
+The position of the visual stimuli was randomized for each trial and each participant (see Appendix \ref{random}).
+In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
+The participants were asked to instruct the experimenter to move the cube on top of one of the four depicted object.
+
+\begin{figure}[tbp]
+
+{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_competitor}
+
+}
+
+\caption{Test trial: Example screen of a trigger instruction.
+The trigger instruction is displayed in the middle below the cube.
+Here, the participants have to instruct the experimenter to move the cube on top of the green sunglasses (indicated by an arrow).}\label{fig:image1}
+\end{figure}
+
+Each test trial consisted of two parts.
+The trigger instruction and the test instruction.
+After the preview of all images was displayed for 1500 ms, the competitor object was visually highlighted by an arrow, and a trigger instruction was presented in writing below the cube (see Figure \ref{fig:image1}).
+The trigger instruction was constituted by the frame sentence \emph{Du sollst den Würfel auf X ablegen}.
+\emph{X} was one of the adjective-noun combinations.
+
+For example, the subjects saw the following sentence:
+
+\ex \begingl
+\glpreamble Du sollst den Würfel auf der grünen Sonnenbrille ablegen.//
+\gla du sollst den würfel auf der grünen sonnenbrille ablegen.//
+\glb you have.to the cube on the green sunglasses put//
+\glft `You have to put the cube on top of the green sunglasses.'//
+\endgl \xe
+
+The trigger instruction was supposed to create a discourse context, such that both the color and the competitor object were introduced as background information into the discourse (in this example: \emph{green} and \emph{sunglasses}).
+The trial proceeded when the experimenter has moved the cube onto the respective referent, at which point the sentence and the arrow would disappear.
+
+Subsequently, the target object was visually highlighted by an arrow and the test instruction containing the target object was presented (see Figure \ref{fig:image2}).
+This time the frame sentence was \emph{Und jetzt sollst du den Würfel auf X ablegen}, where \emph{X} was again an adjective-noun combination.
+To continue the example above, the subject would see the following test instruction:
+
+\ex \begingl
+\glpreamble Und jetzt sollst du den Würfel auf der grünen Avokado ablegen.//
+\gla und jetzt sollst du den würfel auf der grünen avokado ablegen//
+\glb and now have.to you the cube on the green avocado put//
+\glft `And now, you have to put the cube on top of the green avocado.'//
+\endgl \xe
+
+\begin{figure}[tbp]
+
+{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_target}
+
+}
+
+\caption{Test trial: Example screen of the test instruction.
+The target sentence is displayed in the middle of the screen.
+Now, participants have to instruct the experimenter to move the cube on top of the green avocado (indicated by an arrow).}\label{fig:image2}
+\end{figure}
+
+The trial was completed and the next trial initiated as soon as the experimenter had moved the cube to the target referent.
+There was a 3000 ms inter stimulus interval between trials (grey screen).
+In both competitor and target sub sequences, the arrow was displayed with a lag of 1000 ms and the target sentence with a lag of 1500 ms in order to give participants sufficient time to glance at all referents before they were able to identify the relevant object and the instructions.
+
+Using the trigger instruction to set up the discourse context enabled us to manipulate the focus structure of the target sentence.
+If the color of the competitor and the target are of the same object type but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (henceforth the Adjective Focus (AF) condition).
+If the objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (henceforth the Noun Focus (NF) condition).
+If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (henceforth the Adjective/Noun Focus (ANF) condition).
+
+There were 15 NF trials, 10 AF and 10 ANF trials each.
+Each trial occurred two times per participants, yielding a total of 70 trials per participant.
+
+The program (implemented as a browser-based application) used for the experiment is available at the following link: \url{https://github.com/SBRitter/fruits-production}.
+
+\appendix
+
+\hypertarget{random}{%
+\section{Randomization}\label{random}}
+
+In the production study, the combination of target/competitor/distractors were randomized in each trial.
+Randomization was restricted to satisfy the following criteria, depending on the condition.
+
+\begin{itemize}
+\tightlist
+\item
+  NF-Condition:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Color of Target = Color of Competitor.
+  \item
+    Object of Target != Object of Competitor.
+  \end{itemize}
+\item
+  AF-Condition:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Color of Target != Color of Competitor.
+  \item
+    Object of Target = Object of Competitor.
+  \end{itemize}
+\item
+  DF-Condition:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Color of Target != Color of Competitor.
+  \item
+    Object of Target != Object of Competitor.
+  \end{itemize}
+\item
+  Distractors, all conditions:
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Both distractors have to differ in color and object identity from both target and competitor.
+  \end{itemize}
+\end{itemize}
+
+The competitor and distractors were matched iteratively to a target.
+One competitor could only be used twice or a third time if all other competitors that were left had been considered and proved inappropriate.
+
+The set of four objects (quadruple) was formed separately for each of the three focus conditions.
+After the three lists had been compiled, they were merged.
+The sequence of quadruples was randomized such that the following requirements were met:
+
+\begin{itemize}
+\tightlist
+\item
+  The target color of one quadruple must not be equal to the competitor color of the following quadruple in order to avoid a contrastive focus on the next competitor noun.
+\item
+  The target object of one quadruple must not be equal to the competitor object of the following quadruple to avoid a contrastive focus on the next competitor adjective.
+\item
+  The list can have the same experimental condition in adjacent trials only in maximally 12\% of all cases.
+\end{itemize}
+
+Following these criteria, one randomized list for each subject was produced.
+The list was then copied and merged with the first list in order to ensure that each unique trial occurs twice during one recording session.
+In case the copy-and-merge procedure led to violation of any of the criteria described above, the first trial of the repetition list was shuffled until the criteria were met.
+
+The python code for the randomization is available at the following link: \url{https://github.com/SBRitter/fruits-randomization}.
+
 \end{document}

### 2021-02-26 RR_manuscript/Draft_RR.Rmd
:memo: - move formulas to simulations supplement

@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
-
-$$
-\begin{aligned}
-\eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
-\mu_i       & = \alpha + \alpha_{\text{t}[i]} \\
-\alpha      & \sim \text{Normal}(0, 1) \\
-\sigma_{\alpha_{\text{t}}} & \sim \text{HalfCauchy}(0, 1) \\
-\sigma_i    & = \text{se}_i
-\end{aligned}
-$$
-
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
 The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
-The analysis teams will constitute the group-level effect (i.e., random effect, `(1 | team)`).
+The analysis teams will be entered as a group-level effect (i.e., random effect, `(1 | team)`).
 The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
@@
 <!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there are no divergent transitions.
@@
 ```{r funnel-plot, include=TRUE, fig.cap="Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analitical mean.", fig.dim = c(6, 2)}
+The vertical dashed line represents the meta-analytical mean.", fig.dim = c(6, 2)}
 meta_est <- 0
@@
 Since each $\alpha_{\text{t}[i]}$ comes with uncertainty, quantified by its standard deviation $\sigma_{\alpha_{\text{t}[i]}}$, we will fit a measurement-error model, as we did in the meta-analytical model above.
-The formula of the model is the following (see the description of the predictors below for the meaning of acronyms):
 
-$$
-\begin{aligned}
-\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
-\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
- & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
- & \qquad + \upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
-\iota      & \sim \text{Normal}(0, 1) \\
-\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
-resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
-belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
-\sigma_i    & = \sigma_{\alpha_{t[i]}}
-\end{aligned}
-$$
-
-The likelihood of $\alpha_{t[i]}$ is a normal distribution.
-The mean is based on the overall intercept $i$ and on the $\upsilon$ coefficient of each predictor.
+A normal distribution will be used as the likelihood of $\alpha_{t[i]}$.
+The mean of $\alpha_{t[i]}$ is modelled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.

### 2021-02-26 scripts/r/simulations/simulations.Rmd
:memo: - move formulas to simulations supplement

@@
 
-## Meta-analytical model
+## Run
 
@@
 
+## Model formula
+
+$$
+\begin{aligned}
+\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
+\mu_{\alpha_{t[i]}}       & = \beta + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
+ & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
+ & \qquad + \upsilon_r\cdot rat_i + \\
+ & \qquad + \upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
+\iota      & \sim \text{Normal}(0, 1) \\
+\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
+rat_i & \sim \text{Normal}(\mu_{rat_i}, \sigma_{rat_i}) \\
+resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
+belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
+\sigma_i    & = \sigma_{\alpha_{t[i]}}
+\end{aligned}
+$$
+
+## Model priors
+
 ```{r factors-priors}
@@
 ```
+
+## Run
 

### 2021-03-03 RR_manuscript/Draft_RR.Rmd
:memo: - Draft_RR edits in Introduction, plus typo fixes

@@
 The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
+
 Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
-
-<!-- TODO: SUMUP neuroscience, cognitive modeling, clinical, predictive models -->
+Both @dutilh2019 ad @starns2019 investigated analysts choices when inferring theoretical constructs based on the same data set using computational models.
+<!-- TODO: Parker et al. bib info -->
+Both studies reveal vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
+(accepted) on analytical flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
+@bastiaansen2020 crowdsourced clinical recommendations based on data analysis of an individual patient.
+Results suggests that analysis team differed substantially regarding decisions related to both the statistical analysis of the data set and the theoretical rationale behind interpreting the statistical results, indicating that there are multiple layers for degrees of freedom that interact with each other.
 
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1:
-
-<!-- TR: I'd suggest an easier example (Sheila and Pat are both uncommon names, internationally speaking) and possibly a more relateable (possibly timely) example.
-Something about zoom meetings or sth maybe?
-Examples are super important to relate to the reader and lure them in.
-Here is my suggestion-->
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1.
 
@@
 
-<!-- Now, imagine we are interested in measuring the difference between that sentence and the sentence "Sheila says *Mat* is clever".
-How can we obtain a measure of dissimilarity between the first sound in *Pat* and the first sound in *Mat*? -->
-
-<!-- TR: Keep in mind that the research question is not about segmental phenomena. To relate to the question later, I'd suggest a prosodic measure, e.g.  -->
-
 If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
@@
 The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
-
-<!-- TR: I changed features to parameters. Features is too close to phonological theory and will confuse some linguists, I believe. -->
 
@@
 (2a) "I can't bear ANOTHER meeting on zoom."
+
 (2b) "I can't bear another meeting on ZOOM."
-
-In text ref to Figure \@ref(fig:forkingPaths)
 
@@
 ```
-
-<!-- TR: Insertion does not work yet, gotta dash. Also the following paragraph is just a draft for now -->
 
@@
 And the garden of forking paths does not stop here.
-In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
+<!-- TODO: add examples of pitch tracking options -->
+In \highlight[id=SC, comment = {The figure text is quite small.
+Probably better to change to a longer rather then wider layout.}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
 Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
@@
 These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis [e.g. wicherts2016].
+<!-- TODO: references to range of statistical models -->
 Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
@@
 
-<!-- TODO: INFORMATION ABOUT THE DATA SET AND EXP DESIGN + TRANSITION -->
 To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
@@
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der <COLOR OBJECT> ablegen* 'And now, you have to put the cube on top of the <COLOR OBJECT>') instructing the experimenter to move the cube on top of a different object (the *target*).
+The audio of this second utterance in the trial was recorded.
 
@@
 The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+
 Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
 Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
+The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.
 
@@
 
-The present project examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
+The present study examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
 We are further interested in which factors affect the researchers' final results.
@@
 
-Furthermore, the reviewer will be given the option to include further comments in a text box.
+Furthermore, the reviewers will be given the option to include further comments in a text box.
 
@@
 After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
-<!-- The invitation to revise the original ratings will be as follows: "If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now."
-The text box will be prefaced with this prompt: "Please explain your choice to revise (or not to revise) your ratings." -->
 
-## Step 4: Evaluate Variation
+## Step 4: Evaluate variation
 

### 2021-03-03 RR_manuscript/Draft_RR.tex
:memo: - Draft_RR edits in Introduction, plus typo fixes

@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Starns et al.
-2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Jeffrey J.
+Starns et al.
+2019b) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al.
-2018; Starns et al.
-2019; Botvinik-Nezer et al.
-2020).
+2018; Jeffrey J.
+Starns et al.
+2019b; Botvinik-Nezer et al.
+2020b).
 These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
+
 Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
+Both Dutilh et al. (2019) ad Jeffrey J. Starns et al. (2019a) investigated analysts choices when inferring theoretical constructs based on the same data set using computational models.
+Both studies reveal vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytical flexibility in ecology and Botvinik-Nezer et al.
+2020a on neuroimaging data).
+Bastiaansen et al. (2020) crowdsourced clinical recommendations based on data analysis of an individual patient.
+Results suggests that analysis team differed substantially regarding decisions related to both the statistical analysis of the data set and the theoretical rationale behind interpreting the statistical results, indicating that there are multiple layers for degrees of freedom that interact with each other.
 
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1:
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1.
 
@@
 (2a) ``I can't bear ANOTHER meeting on zoom.''
+
 (2b) ``I can't bear another meeting on ZOOM.''
-
-In text ref to Figure \ref{fig:forkingPaths}
 
@@
 And the garden of forking paths does not stop here.
-In Figure X, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
+In \highlight[id=SC, comment = {The figure text is quite small.
+Probably better to change to a longer rather then wider layout.}]{Figure} \ref{fig:forkingPaths}, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
 Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
@@
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der ablegen} `And now, you have to put the cube on top of the ') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
+The audio of this second utterance in the trial was recorded.
 
@@
 The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+
 Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
 Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
+The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.
 
@@
 \hypertarget{step-4-evaluate-variation}{%
-\subsection{Step 4: Evaluate Variation}\label{step-4-evaluate-variation}}
+\subsection{Step 4: Evaluate variation}\label{step-4-evaluate-variation}}
 
@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using the following multilevel (intercept-only) regression model:
-
-\[
-\begin{aligned}
-\eta_i      & \sim \text{Normal}(\mu_i, \sigma_i) \\
-\mu_i       & = \alpha + \alpha_{\text{t}[i]} \\
-\alpha      & \sim \text{Normal}(0, 1) \\
-\sigma_{\alpha_{\text{t}}} & \sim \text{HalfCauchy}(0, 1) \\
-\sigma_i    & = \text{se}_i
-\end{aligned}
-\]
-
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
 The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
-The analysis teams will constitute the group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
+The analysis teams will be entered as a group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
 The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
 We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{t}[i]}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan (Stan Development Team 2021), and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 \highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
@@
 \caption{\label{fig:funnel-plot}Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analitical mean.}
+The vertical dashed line represents the meta-analytical mean.}
 \end{figure}
@@
 Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytical model above.
-The formula of the model is the following (see the description of the predictors below for the meaning of acronyms):
 
-\[
-\begin{aligned}
-\alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
-\mu_{\alpha_{t[i]}}       & = \iota + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
- & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
- & \qquad + \upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
-\iota      & \sim \text{Normal}(0, 1) \\
-\upsilon_{[\ldots]} & \sim \text{Normal}(0,1) \\
-resp_i & \sim \text{Normal}(\mu_{resp_i}, \sigma_{resp_i}) \\
-belf_i & \sim \text{Normal}(\mu_{belf_i}, \sigma_{belf_i}) \\
-\sigma_i    & = \sigma_{\alpha_{t[i]}}
-\end{aligned}
-\]
-
-The likelihood of \(\alpha_{t[i]}\) is a normal distribution.
-The mean is based on the overall intercept \(i\) and on the \(\upsilon\) coefficient of each predictor.
+A normal distribution will be used as the likelihood of \(\alpha_{t[i]}\).
+The mean of \(\alpha_{t[i]}\) is modelled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
@@
 
+\leavevmode\hypertarget{ref-bastiaansen2020}{}%
+Bastiaansen, Jojanneke A., Yoram K.
+Kunkels, Frank J.
+Blaauw, Steven M.
+Boker, Eva Ceulemans, Meng Chen, Sy-Miin Chow, et al.
+2020.
+{``Time to Get Personal?
+The Impact of Researchers Choices on the Selection of Treatment Targets Using the Experience Sampling Methodology.''} \emph{Journal of Psychosomatic Research} 137: 110211.
+
+\leavevmode\hypertarget{ref-botvinik-nezer2020}{}%
+Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F.
+Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
+2020a.
+{``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature} 582 (7810): 84--88.
+
 \leavevmode\hypertarget{ref-botvinik2020variability}{}%
 Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
-2020.
+2020b.
 {``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature}, 1--7.
@@
 Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.
+
+\leavevmode\hypertarget{ref-dutilh2019}{}%
+Dutilh, Gilles, Jeffrey Annis, Scott D.
+Brown, Peter Cassey, Nathan J.
+Evans, Raoul Grasman, Guy E.
+Hawkins, et al.
+2019.
+{``The Quality of Response Time Data Inference: A Blinded, Collaborative Assessment of the Validity of Cognitive Models.''} \emph{Psychonomic Bulletin \& Review} 26 (4): 1051--69.
 
@@
 
+\leavevmode\hypertarget{ref-starns2019}{}%
+Starns, Jeffrey J., Andrea M.
+Cataldo, Caren M.
+Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
+2019a.
+{``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
+
 \leavevmode\hypertarget{ref-starns2019assessing}{}%
 Starns, Jeffrey J, Andrea M Cataldo, Caren M Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
-2019.
+2019b.
 {``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
@@
 1959.
-{``Publication Decisions and Their Possible Effects on Inferences Drawn from Tests of Significance---or Vice Versa.''} \emph{Journal of the American Statistical Association} 54 (285): 30--34.
+{``Publication Decisions and Their Possible Effects on Inferences Drawn from Tests of Significance--or Vice Versa.''} \emph{Journal of the American Statistical Association} 54 (285): 30--34.
 

### 2021-03-04 RR_manuscript/Draft_RR.Rmd
:memo: - edits to Draft_RR: introduction, peer-review section

@@
   - \setlength{\marginparwidth}{2cm}
-  - \usepackage{changes}
+  - \usepackage[todonotes={textsize=tiny}]{changes}
   - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
@@
 
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
+In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by the data.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates in replication attempts [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
+<!-- TODO: add refs about variable conclusions from reliable data -->
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (\highlight{REFS}).
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
@@
 In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
-This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
+This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
 Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
@@
 In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
+<!-- TODO: include number of teams when known -->
 Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
@@
 Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
-However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
-<!-- I'd probably drop this.
+\highlight[id=JC, comment = {I'd probably drop this.
 When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)...
 in other words it might not all be error...
-the issue is that we won't know the difference -->
-<!-- TR: But isn't the human bias the major issue in statistical misinterpretation? (It also leads naturally to the next paragraph.) -->
+the issue is that we won't know the difference}]{However, if these decisions} during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.\comment[id=TR]{But isn't the human bias the major issue in statistical misinterpretation?
+(It also leads naturally to the next paragraph.)}
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
-<!-- JC: If helpful we could also give a concrete common example here, like regarding forecasting the weather or something -->
-<!-- TR: Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased. -->
+\comment[id=JC]{If helpful we could also give a concrete common example here, like regarding forecasting the weather or something}
+\comment[id=TR]{Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased.}
 In connection with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
-In these studies the data sets were fixed and data collection or measurement could not be changed.
-<!-- JC: any particular reason to favor data table over data set?
---> <!-- TR: I think my reasoning was data set can be data table or raw data.
+In these studies the data sets were fixed and data collection or measurement could not be changed.\comment[id=JC]{any particular reason to favor data table over data set?}\comment[id=TR]{I think my reasoning was data set can be data table or raw data.
 Data table is the numerical derivation of the raw data.
-Maybe not a useful distinction?-->
+Maybe not a useful distinction?}
 
-However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
-In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa [@flake2019].
-To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
+However, in many fields the primary raw data are complex signals that need to be operationalized in light of the research question.
+This is especially true in the social sciences, where the subject of investigation corresponds to observable and unobservable human behavior.
+Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
+For example, @flake2020 discuss the cascading impact different practices can have on several components of psychometric research.
+The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
+Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.
+
+In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
+This added complexity introduces further fork junctions in the research pipe-line, thus increasing yet again analytical flexibility.
+The present study looks at experimentally elicited speech data to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
 
@@
 Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
-One major challenge in the speech sciences is the mapping between communicative intentions and their physical manifestation.
+One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behaviour).
 
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1.
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision.
+Take for example the following sentence in (1).
 
-(1) "I can't bear another meeting on zoom."
+(1) "I can't bear another meeting on Zoom."
 
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word "another" or "meeting".
-If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word "zoom".
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word *another* or *meeting*.
+If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word *Zoom*.
 
-If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
-Given the continuous and transient nature of speech, identifying speech parameters and temporal domains becomes a non-trivial task.
+If we decide to compare the speech signal associated with these two intentions, how can we quantify the difference between them?
+Given their physical manifestation (speech), what do we measure and how do we measure it?
+Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].
+
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
@@
 the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
-
 Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
@@
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.
+For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.
 
-(2a) "I can't bear ANOTHER meeting on zoom."
+(2a) I can't bear *ANOTHER* meeting on zoom.
 
-(2b) "I can't bear another meeting on ZOOM."
+(2b) I can't bear another meeting on *ZOOM*.
 
+Do we compare only the word *another* in (2a) and (2b), or also the word *zoom*?
+Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
+Do we average across the chosen time domain or do we measure a specific point in time?
+Do we measure fundamental frequency, intensity, something else?
+
+When looking at phrase-level temporal domains, the number of possible analytical pipelines quickly explodes.
+This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
+When comparing two utterance such as (2a) and (2b), there are many things to consider.
+Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
+For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+And the garden of forking paths does not stop here.
+<!-- TODO: add examples of pitch tracking options -->
+In \highlight[id=SC, comment = {The figure text is quite small.
+Probably better to change to a longer rather then wider layout.}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
+Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+
+<!-- FIGURE -->
 (ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
@@
 ```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
-
 knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
-
 ```
-
-Do we only compare the word *another* in 2a and 2b or also the word *zoom* or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
-Do we average the domain or do we measure a specific point in time?
-Do we measure fundamental frequency or intensity?
-When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
-This plurality of analytical paths is illustrated in figure X.
-When comparing two utterance such as 2a and 2b, there are many things to consider.
-Even if we know that we want to compare fundamental frequency of only the word *another* across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
-For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
-And the garden of forking paths does not stop here.
-<!-- TODO: add examples of pitch tracking options -->
-In \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
-Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
+<!-- END:FIGURE -->
 
@@
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis [e.g. wicherts2016].
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
 <!-- TODO: references to range of statistical models -->
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (\highlight{REFs}).
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.\comment[id=SC]{This needs a smother transition.}
 
@@
 Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
-<!-- TR: Big to-do point.
-We need to only justify a minimum sample size JC: added description (word for word) from ecology RR.
-Need to figure out what it means still and then put into our own words.
--->
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 
-<!-- sample size info from Ecology RR -->
-<!-- SC: rephrased and expanded -->
 <!-- TODO: add citation to ECO RR -->
@@
 
-<!-- TR: So I am still unclear on how this will look like, do they only evaluate stats?
-if they evaluate the entire pipeline they need to be phoneticians, do they evaluate acoustic analysis and stats analysis independently?-->
 At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
-<!-- TR: I have a hunch that finding reviewers will potentially be more difficult than finding analysis teams. They had as many reviewers as they had teams.-->
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
@@
 <!-- TODO: add link to peer review survey -->
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100.
 <!-- TR:Need flow chart here-->
-
-* Overall appropriateness of the acoustic analysis.
-* Overall appropriateness of the statistical analysis.
-* Choice of statistical analysis type.
-* Model variables choice.
-* Model specification.
-* Data exclusion.
-* Data transformation.
-
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-Furthermore, the reviewers will be given the option to include further comments in a text box.
+The reviewers will also be given the option to include further comments in text box for each of the three ratings.
 
@@
 
-To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
-<!-- NOTE: (SC) it would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model.
--->
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
@@
 We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
-<!-- TR: isn't an SD of 1 rather conservative. Also small sample size, maybe rather using cauchy for the thick tails? -->
-<!-- SC: For the pop-level params I would stick to the Normal, or if we want to avoid problems with thick tails I'd go with a student-t. -->
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
@@
 
-<!--TR: Question: Do we need to estimate the absolute deviation or is it useful to consider the raw deviation (stretching from negative to positive values).
-That gives you both the distance to the meta analytical estimate and the direction of that difference -->
-<!-- SC: I agree that using the raw deviation has the plus of knowing the sign of the difference. I updated the text above accordingly, but feel free to change it. -->
-
 <!-- TODO: add brm info on factors analysis model -->
@@
 For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:
-
-<!-- SC: refactored the formula so it is closer to the original source -->
+For each pair of analyses $(X, Y)$, the SDI will be obtained using the following \highlight[id=SC, comment={refactored the formula so it is closer to the original source}]{formula}:
 
@@
 frequency center of gravity, harmonics difference, etc.), *other measures* (e.g.
-principal components, vowel dispersion, etc.)
-<!--TR: Stefano, do you think these four will cover possible ways to measure? We might want to define them too? dunno-->
-<!-- SC: I just added a "other measures" category for other things that are not strictly acoustic. -->
+principal components, vowel dispersion, etc.)\comment[id=TR]{Stefano, do you think these four will cover possible ways to measure?
+We might want to define them too?
+dunno}\comment[id=SC]{I just added a "other measures" category for other things that are not strictly acoustic.}
 The temporal window that the measurement is taken over is defined by the target linguistic unit.

### 2021-03-04 RR_manuscript/Draft_RR.tex
:memo: - edits to Draft_RR: introduction, peer-review section

@@
 \setlength{\marginparwidth}{2cm}
-\usepackage{changes}
+\usepackage[todonotes={textsize=tiny}]{changes}
 \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
@@
 
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates for (i) (e.g., Open Science Collaboration 2015; Camerer et al.
+In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by the data.
+In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates in replication attempts (e.g., Open Science Collaboration 2015; Camerer et al.
 2018) leading to what is now referred to as the \emph{replication crisis}.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (REFS).
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (\highlight{REFS}).
 The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Jeffrey J.
@@
 Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
-However, if these decisions during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.
+\highlight[id=JC, comment = {I'd probably drop this.
+When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)...
+in other words it might not all be error...
+the issue is that we won't know the difference}]{However, if these decisions} during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.\comment[id=TR]{But isn't the human bias the major issue in statistical misinterpretation?
+(It also leads naturally to the next paragraph.)}
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
+\comment[id=JC]{If helpful we could also give a concrete common example here, like regarding forecasting the weather or something}
+\comment[id=TR]{Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased.}
 In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Wicherts et al.
+Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Jelte M.
+Wicherts et al.
 2006).
@@
 While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
-In these studies the data sets were fixed and data collection or measurement could not be changed.
+In these studies the data sets were fixed and data collection or measurement could not be changed.\comment[id=JC]{any particular reason to favor data table over data set?}\comment[id=TR]{I think my reasoning was data set can be data table or raw data.
+Data table is the numerical derivation of the raw data.
+Maybe not a useful distinction?}
 
-However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
-In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
-Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake and Fried 2019).
-To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.
+However, in many fields the primary raw data are complex signals that need to be operationalized in light of the research question.
+This is especially true in the social sciences, where the subject of investigation corresponds to observable and unobservable human behavior.
+Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
+For example, Flake and Fried (2020) discuss the cascading impact different practices can have on several components of psychometric research.
+The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
+Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.
+
+In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
+This added complexity introduces further fork junctions in the research pipe-line, thus increasing yet again analytical flexibility.
+The present study looks at experimentally elicited speech data to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
 
@@
 Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
-One major challenge in the speech sciences is the mapping between communicative intentions and their physical manifestation.
+One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behaviour).
 
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision. Take for example the following sentence in 1.
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision.
+Take for example the following sentence in (1).
 
@@
 \item
-  ``I can't bear another meeting on zoom.''
+  ``I can't bear another meeting on Zoom.''
 \end{enumerate}
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word ``another'' or ``meeting.''
-If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word ``zoom.''
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \emph{another} or \emph{meeting}.
+If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word \emph{Zoom}.
 
-If we want to compare the speech signal associated with these two intentions, how do we quantify the difference between them? What do we measure and how do we measure it?
-Given the continuous and transient nature of speech, identifying speech parameters and temporal domains becomes a non-trivial task.
+If we decide to compare the speech signal associated with these two intentions, how can we quantify the difference between them?
+Given their physical manifestation (speech), what do we measure and how do we measure it?
+Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
 Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
@@
 For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).
+
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).
-
 Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
@@
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, when comparing two realization of example (1) (here repeated as 2), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{zoom}.
+For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{zoom}.
 
-(2a) ``I can't bear ANOTHER meeting on zoom.''
+(2a) I can't bear \emph{ANOTHER} meeting on zoom.
 
-(2b) ``I can't bear another meeting on ZOOM.''
+(2b) I can't bear another meeting on \emph{ZOOM}.
+
+Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{zoom}?
+Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
+Do we average across the chosen time domain or do we measure a specific point in time?
+Do we measure fundamental frequency, intensity, something else?
+
+When looking at phrase-level temporal domains, the number of possible analytical pipelines quickly explodes.
+This plurality of analytical paths is illustrated in Figure \ref{fig:forkingPaths}.
+When comparing two utterance such as (2a) and (2b), there are many things to consider.
+Even if we have decided to compare fundamental frequency (f0) of only the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
+For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+And the garden of forking paths does not stop here.
+In \highlight[id=SC, comment = {The figure text is quite small.
+Probably better to change to a longer rather then wider layout.}]{Figure} \ref{fig:forkingPaths}, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
+Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
 
@@
 
-Do we only compare the word \emph{another} in 2a and 2b or also the word \emph{zoom} or do we measure utterance wide acoustic profiles? Do we measure the whole word? Or just the stressed syllable?
-Do we average the domain or do we measure a specific point in time?
-Do we measure fundamental frequency or intensity?
-When looking at phrase-wide temporal domains, the number of possible analytical pipelines quickly explodes.
-This plurality of analytical paths is illustrated in figure X.
-When comparing two utterance such as 2a and 2b, there are many things to consider.
-Even if we know that we want to compare fundamental frequency of only the word \emph{another} across utterances 2a and 2b, there are still many decisions to be made, all of which can be justified.
-For example, we could measure f0 at specific points in time like the onset of the window, the offset, the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
-And the garden of forking paths does not stop here.
-In \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}]{Figure} \ref{fig:forkingPaths}, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.
-Moreover, knowing that theses estimates are somewhat noisy, we could smooth these contours to different degrees, automatically or manually remove estimates that are off, etc.
-
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis {[}e.g.~wicherts2016{]}.
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (REFs).
+These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Jelte M. Wicherts et al. 2016).
+Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (\highlight{REFs}).
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.
+To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.\comment[id=SC]{This needs a smother transition.}
 
@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses on several criteria, using a scale of 0-100:
-
-\begin{itemize}
-\tightlist
-\item
-  Overall appropriateness of the acoustic analysis.
-\item
-  Overall appropriateness of the statistical analysis.
-\item
-  Choice of statistical analysis type.
-\item
-  Model variables choice.
-\item
-  Model specification.
-\item
-  Data exclusion.
-\item
-  Data transformation.
-\end{itemize}
-
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
@@
 For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
+For each pair of analyses \((X, Y)\), the SDI will be obtained using the following \highlight[id=SC, comment={refactored the formula so it is closer to the original source}]{formula}:
 
@@
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.)
+The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.)\comment[id=TR]{Stefano, do you think these four will cover possible ways to measure?
+We might want to define them too?
+dunno}\comment[id=SC]{I just added a "other measures" category for other things that are not strictly acoustic.}
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
@@
 
-\leavevmode\hypertarget{ref-flake2019}{}%
-Flake, Jessica Kay, and Eiko I. Fried. 2019. {``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} Pre-print available at PsyArXiv.
+\leavevmode\hypertarget{ref-flake2020}{}%
+Flake, Jessica Kay, and Eiko I.
+Fried.
+2020.
+{``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (4): 456--65.
+\url{https://doi.org/10.1177/2515245920952393}.
 
@@
 
+\leavevmode\hypertarget{ref-wicherts2016}{}%
+Wicherts, Jelte M., Coosje L.
+S.
+Veldkamp, Hilde E.
+M.
+Augusteijn, Marjan Bakker, Robbie C.
+M.
+van Aert, and Marcel A.
+L.
+M.
+van Assen.
+2016.
+{``Degrees of Freedom in Planning, Running, Analyzing, and Reporting Psychological Studies: A Checklist to Avoid p-Hacking.''} \emph{Frontiers in Psychology} 7.
+\url{https://doi.org/10.3389/fpsyg.2016.01832}.
+
 \leavevmode\hypertarget{ref-wicherts2006poor}{}%

### 2021-03-04 RR_manuscript/Draft_RR.Rmd
:memo: - Draft_RR ready

@@
 
-## Operationalizing speech
+## Operationalizing speech {#s:operspeech}
 
@@
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.
-the atypical *a blue banana* vs the typical *a yellow banana*)?
-More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
+The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as  *a blue banana* (atypical) vs *a yellow banana* (typical).
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
-The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.
+The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
+The teams were asked to answer the same questions as the study that generated the data set: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+\comment[id=SC]{Need transition here.}
 
@@
 
-The present study examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
-We are further interested in which factors affect the researchers' final results.
+The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
+As outlined in Section \@ref(s:operspeech), researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
+Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
+\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
+We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.
 
@@
 
-This project involves a series of steps (X-X):
+This project involves the following five phases:
 
-1. We will recruit independent groups of researchers to analyze the data.
-2. We will give researchers access to the speech corpus and let them analyze the data as they see fit.
-3. We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
-4. We will evaluate the variation among the different analyses.
-5. Lastly, we will collaboratively produce the final manuscript.
+1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
+2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+3. \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
+4. \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
+5. \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
-The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.
+<!-- TODO: project timeline -->
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
+The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
 
-## Step 1: Recruitment and Initial Survey of Analysts
+## Phase 1: Recruitment of analysts and initial survey
 
 <!-- TODO: add materials link and mailing lists -->
-The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
-The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
-The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
+The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as "analysis teams".
+For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
 
-Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 <!-- TODO: add citation to ECO RR -->
-To identify the minimal sample size, we followed the method in [ECO RR].
+To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
 The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
@@
 
-## Step 2: Primary Data Analyses
+## Phase 2: Primary Data Analyses
 
@@
 
-## Step 3: Peer Reviews of Analyses
+## Phase 3: Peer Reviews of Analyses
 
@@
 
-## Step 4: Evaluate variation
+## Phase 4: Evaluate variation
 
@@
 
-## Step 6: Collaborative Write-Up of Manuscript
+## Phase 6: Collaborative Write-Up of Manuscript
 

### 2021-03-04 RR_manuscript/Draft_RR.tex
:memo: - Draft_RR ready

@@
 
-\hypertarget{operationalizing-speech}{%
-\subsection{Operationalizing speech}\label{operationalizing-speech}}
+\hypertarget{s:operspeech}{%
+\subsection{Operationalizing speech}\label{s:operspeech}}
 
@@
 
-Our data set was collected in order to answer the following research question: Do speakers acoustically modify utterances to signal atypical word combinations (e.g.~the atypical \emph{a blue banana} vs the typical \emph{a yellow banana})?
-More specifically, we are interested in the acoustic profile of referring expressions made up of a noun and an adjective modifier.
+The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as \emph{a blue banana} (atypical) vs \emph{a yellow banana} (typical).
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
-The recordings of the second sentence prompt of each trial make up the speech dataset given to the analysis teams.
+The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
+The teams were asked to answer the same questions as the study that generated the data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
+\comment[id=SC]{Need transition here.}
 
@@
 
-The present study examines the extent to which subjective choices by different researchers analyzing a complex speech data set affect the reported results.
-We are further interested in which factors affect the researchers' final results.
+The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
+As outlined in Section \ref{s:operspeech}, researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
+Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
+\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
+We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.
 
@@
 
-This project involves a series of steps (X-X):
+This project involves the following five phases:
 
@@
 \item
-  We will recruit independent groups of researchers to analyze the data.
+  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
 \item
-  We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+  \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
 \item
-  We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
+  \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
 \item
-  We will evaluate the variation among the different analyses.
+  \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
 \item
-  Lastly, we will collaboratively produce the final manuscript.
+  \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
 \end{enumerate}
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report, will take XX months (Table X).
-The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent groups of scientists.
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
+The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
 
-\hypertarget{step-1-recruitment-and-initial-survey-of-analysts}{%
-\subsection{Step 1: Recruitment and Initial Survey of Analysts}\label{step-1-recruitment-and-initial-survey-of-analysts}}
+\hypertarget{phase-1-recruitment-of-analysts-and-initial-survey}{%
+\subsection{Phase 1: Recruitment of analysts and initial survey}\label{phase-1-recruitment-of-analysts-and-initial-survey}}
 
-The initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question in order to increase accessibility to potential analysts (LINK).
-The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth.
-The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline.
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
+The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we refer to single researcher or small teams as ``analysis teams.''
+For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
 
-Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 
-To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
+To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
 The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
@@
 
-\hypertarget{step-2-primary-data-analyses}{%
-\subsection{Step 2: Primary Data Analyses}\label{step-2-primary-data-analyses}}
+\hypertarget{phase-2-primary-data-analyses}{%
+\subsection{Phase 2: Primary Data Analyses}\label{phase-2-primary-data-analyses}}
 
@@
 
-\hypertarget{step-3-peer-reviews-of-analyses}{%
-\subsection{Step 3: Peer Reviews of Analyses}\label{step-3-peer-reviews-of-analyses}}
+\hypertarget{phase-3-peer-reviews-of-analyses}{%
+\subsection{Phase 3: Peer Reviews of Analyses}\label{phase-3-peer-reviews-of-analyses}}
 
@@
 
-\hypertarget{step-4-evaluate-variation}{%
-\subsection{Step 4: Evaluate variation}\label{step-4-evaluate-variation}}
+\hypertarget{phase-4-evaluate-variation}{%
+\subsection{Phase 4: Evaluate variation}\label{phase-4-evaluate-variation}}
 
@@
 
-\hypertarget{step-6-collaborative-write-up-of-manuscript}{%
-\subsection{Step 6: Collaborative Write-Up of Manuscript}\label{step-6-collaborative-write-up-of-manuscript}}
+\hypertarget{phase-6-collaborative-write-up-of-manuscript}{%
+\subsection{Phase 6: Collaborative Write-Up of Manuscript}\label{phase-6-collaborative-write-up-of-manuscript}}
 

### 2021-03-06 RR_manuscript/Draft_RR.Rmd
edited until 2.2 (not done yet)

@@
 
-In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates in replication attempts [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
+In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
+In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
 <!-- TODO: add refs about variable conclusions from reliable data -->
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (\highlight{REFS}).
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
@@
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
-Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
+Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
+These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
+In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
 <!-- TODO: include number of teams when known -->
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
+Specifically, we will report the impact of analytic decision on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
+<!-- TODO: check tense throughout, should be future tense -->
 
@@
 Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
-\highlight[id=JC, comment = {I'd probably drop this.
-When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)...
-in other words it might not all be error...
-the issue is that we won't know the difference}]{However, if these decisions} during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.\comment[id=TR]{But isn't the human bias the major issue in statistical misinterpretation?
-(It also leads naturally to the next paragraph.)}
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
-\comment[id=JC]{If helpful we could also give a concrete common example here, like regarding forecasting the weather or something}
-\comment[id=TR]{Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased.}
 In connection with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare [@wicherts2006poor].
+Despite recent efforts to improve transparency and reproducibility [e.g.
+miguel2014promoting; @klein2018practical] and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare [@wicherts2006poor].
 
-While this issue has been widely discussed both from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and its application in individual scientific fields [e.g.
+While analytical flexibility has been widely discussed both from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and its application in individual scientific fields [e.g.
 Wichert et al.
@@
 2019, @roettger2019researcher], there are still many unknowns regarding the extent of analytical plurality in practice.
+<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019 -->
+
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 
-Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
-Both @dutilh2019 ad @starns2019 investigated analysts choices when inferring theoretical constructs based on the same data set using computational models.
+Several other recent studies corroborated this analytical flexibility across different disciplines.
+Both @dutilh2019 ad @starns2019 investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
 <!-- TODO: Parker et al. bib info -->
-Both studies reveal vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
 (accepted) on analytical flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
-@bastiaansen2020 crowdsourced clinical recommendations based on data analysis of an individual patient.
-Results suggests that analysis team differed substantially regarding decisions related to both the statistical analysis of the data set and the theoretical rationale behind interpreting the statistical results, indicating that there are multiple layers for degrees of freedom that interact with each other.
+@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
+Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
-While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
-In these studies the data sets were fixed and data collection or measurement could not be changed.\comment[id=JC]{any particular reason to favor data table over data set?}\comment[id=TR]{I think my reasoning was data set can be data table or raw data.
-Data table is the numerical derivation of the raw data.
-Maybe not a useful distinction?}
+While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
+In these studies the data sets were fixed and data collection or measurement could not be changed.
 
-However, in many fields the primary raw data are complex signals that need to be operationalized in light of the research question.
-This is especially true in the social sciences, where the subject of investigation corresponds to observable and unobservable human behavior.
+However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
+This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
 Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
-For example, @flake2020 discuss the cascading impact different practices can have on several components of psychometric research.
+For example, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
@@
 In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
-This added complexity introduces further fork junctions in the research pipe-line, thus increasing yet again analytical flexibility.
-The present study looks at experimentally elicited speech data to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
+<!-- TODO: check BE vs. AE -->
+This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
+The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
 
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word *another* or *meeting*.
-If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word *Zoom*.
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word *another* or *meeting* to contrast it with other, more pleasant activities.
+If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word *Zoom*.
 
@@
 Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
-Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
+Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
 The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
 
-Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
+Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
 The acoustic parameters of one category are usually asynchronous, i.e.
-they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g., @jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
+they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g.
+@jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
+<!-- TODO: add summerfield ref-->
 A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
-This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
+This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, something else?
+Do we measure fundamental frequency, intensity, or something else?
 
@@
 We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyse speech data [see @gordon2017acoustic].
 And the garden of forking paths does not stop here.
@@
 In \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
+Probably better to change to a longer rather then wider layout.}][id=TR, comment = {Better now?}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
 Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
@@
 (ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+(A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
 The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
@@
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
-<!-- TODO: references to range of statistical models -->
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (\highlight{REFs}).
+These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
+In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytical flexibility when choosing measures and operationalizing underlying theoretical constructs.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.\comment[id=SC]{This needs a smother transition.}
+To assess the variability in data analysis pipelines across independent researchers, we will provide analytical teams with an experimentally elicited speech production data set.
+The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following, we will shortly introduce the research question of the original study.
 
-## The data set: The acoustic properties of redundant modifiers
-
-The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as  *a blue banana* (atypical) vs *a yellow banana* (typical).
+## The data set: The acoustic properties of atypical modifiers
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
+Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
@@
 
-Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
+Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
 Intonation marks discourse-relevant referents for being new or given information to guide the listeners’ interpretation of incoming messages. 
-In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
-Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on *banana* to indicate the contrastive nature of the noun.
-In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on *yellow* to indicate the contrastive nature of the modifier.
-In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.
-segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
+Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations [e.g.
+dimitrova2008prosodic; dimitrova2009did].
+Referential expressions such as *blue banana* were produced with greater prosodic prominence than more typical referent such as *yellow banana*.
+If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
+However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes. 
+Moreover, the data is not available, and the statistical analysis uses anti-conservative co-variance structures, lending reasonable doubt on the original conclusions.
 
-To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
+<!-- QUESTION: ask people if they have ever heard of these papers? -->
+
+To further illuminate the question of whether speakers modify speech to signal atypical referents, we recorded thirty native German speakers interacting with a confederate (one of the experimenters) in a referential game.
 The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
@@
 After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+
+<!-- TODO: see XXX, what do we refer to here? -->
+
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 
+<!-- QUESTION: add pictures? -->
+
 In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
@@
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der <COLOR OBJECT> ablegen* 'And now, you have to put the cube on top of the <COLOR OBJECT>') instructing the experimenter to move the cube on top of a different object (the *target*).
-The audio of this second utterance in the trial was recorded.
+The second utterance in the trial was the critical trial for analysis.
 
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was in focus (the Noun Focus condition, NF).
-If the the objects were the same object but differed in color (e.g. *yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
-If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was discourse-pragmatically focused (the Noun Focus condition, NF).
+If the objects were the same but differed in color (e.g. *yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
+If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was discourse-pragmatically focused (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
 The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g. *Orangene Mandarine* 'orange mandarin'), medium typical (e.g. *Grüne Tomate* 'green tomato'), or atypical (e.g. *Gelbe Kirsche* 'yellow cherry').
-The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+The combinations were either typical (e.g.
+*orange mandarin*), medium typical (e.g.
+*greem tomato* ), or atypical (e.g.
+*yellow cherry*), as established by a norming study that was conducted prior to the production experiment (see Appendix XXX for details).
 
-Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
-Each trial was repeated twice, yielding a total of 70 trials ($(15 \times 10 \times 10) \times 2$) per participant and a grand-total of 2100 observations ($70 \times 30$ participants), of which 900 ($15 \times 2 \times 30$ participants) were the experimentally relevant trials.
-The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
-The teams were asked to answer the same questions as the study that generated the data set: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+<!-- TODO: Appendix and stuff -->
+
+Each participant responded to 15 critical trials (NF condition).
+Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total 900 ($15 \times 2 \times 30$ participants) spoken utterances.
+All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
 \comment[id=SC]{Need transition here.}
 
-## Research questions
-
-The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
-As outlined in Section \@ref(s:operspeech), researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
-Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
-\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
+# Methods
+As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
+Analyst must identify relevant measurements as well as temporal domain(s) from within which these measures are to be taken, operationalize and possibly transform those measures, before submitting them to statistical models, which have to be chosen alongside inferential criteria.
+The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
 We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.
 
-# Methods
+<!-- QUESTION: wanna meditate over the term demographic-->
 
-We are closely following the methodology proposed by Parker et al. (Stage 1 in-principle accepted) in terms of data collection.
-However, the analysis will substantially diverge from their approach (see §#.#)
-
-This project involves the following five phases:
+We are closely following the data collection procedure proposed by Parker et al. (Stage 1 in-principle accepted).
+The project involves the following five phases:
 
@@
 The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
-The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
@@
 Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+
+<!-- QUESTION: How to frame this sentence. It is not ongoing. Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted.-->
+
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 All analysts will sign a consent (ethics) document (LINK).
+<!-- TODO: add information about what this consent form does -->
 
 <!-- TODO: add citation to ECO RR -->
-To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
+To identify the minimal sample size, we followed the method in Parker et al. \highlight{[ECO RR]}.
 The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
 the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
-Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
+In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity. 
+We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient (i.e.
+the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
+<!-- QUESTION: the sentence in brackets looks wrong, this would be true for confidence intervals right? -->
 The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:
@@
 
-Assuming that the underlying distribution of effect sizes is normal [@knight2000], the standard error of $\tau^2$ can be calculated with the formula:
+Assuming that the underlying distribution of effect sizes is normal [@knight2000], the standard error of $\tau^2$ can be calculated with the following formula:
 
@@
 Since we know $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
-Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
+Inserting $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
 
@@
 In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CrI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
-When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which is below the 0.05 threshold, as required.
-In sum, a minimal sample of 12 effect sizes (i.e. of 12 analysis teams) would thus be sufficient to exclude 0 from the 95% CrI of $\tau^2$.
+When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which we consider sufficiently unlikely.
 
@@
 ```
+
+<!-- QUESTION: Should we double check that with some folks? -->
 

### 2021-03-08 scripts/r/simulations/simulations.Rmd
:memo: - edit simulations.Rmd

@@
 ---
-title: "Perspective simulation"
+title: "Prospective simulation"
 date: "`r Sys.Date()`"
@@
     use_bookdown: yes
+bibliography: "`r here::here('./RR_manuscript/other_refs.bib')`"
+cls: unified-style-sheet-for-linguistics.csl
 ---
@@
 We first simulate a dataset (`eta_tbl`) of standardised effect sizes.
-Each team ($n = 12$) contributes a standardized effect size $\eta_i$, with respective standard error $\text{se}_i$.
+Each team ($n = 12$) contributes one standardized effect size $\eta_i$, with respective standard error $\text{se}_i$.
 
-### Helper functions
+## Helper functions
+
+Let's create helper functions:
+
+* `at_least()` ensures that there is at least a `1` when sampling for predictors (= there must be at least one predictor in the model).
+
+* `sdi_mean()` calculates the mean SDI for the pop-level and group-level predictions.
 
@@
 
-### Tibble
+## Tibble
 
 The $\eta_i$ is randomly sampled from a $Normal(1, 0.5)$ distribution, while $\text{se}_i$ from a $HalfCauchy(0, 0.15)$.
+See comments in code for the other variables.
 
@@
 
+We can now put the tibble together.
+
 ```{r eta-tbl}
@@
     belf_mean = ifelse(belf_mean == 0, 0.01, belf_mean),
-  # need the following in cases where there only one person in the team
+    # need the following in cases where there is only one person in the team
     rating_sd = ifelse(is.na(rating_sd) | rating_sd == 0, 0.01, rating_sd),
@@
 
+**See paper for more details.**
+
+To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical techniques.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+
 ## Model formula
+
+The estimated coefficients of the critical predictors (i.e.
+critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
+If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
+
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
+The outcome variable will be the set of standardized effect sizes $\eta_i$.
+The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
+The analysis teams will be entered as a group-level effect (i.e., random effect, `(1 | team)`).
+The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
+We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
 
@@
 
-In the meta-analytical model, we will use the following priors:
+For the meta-analytical model, we will use the following priors:
 
@@
 
-```{r ppred-joint-post}
+```{r ppred-joint-post, message=FALSE, warning=FALSE}
 ppred_samples %>%
@@
 ```
+
+# References

### 2021-03-08 RR_manuscript/Draft_RR.Rmd
finished editing

@@
 The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
+<!-- QUESTION: should the survey ask for expertise in their acoustic skills? -->
 We will then provide teams with the acoustic data set and request that they answer the following research question:
+<!-- TODO: Link dataset here -->
 
@@
 <!-- TODO: add link to analytical survey -->
-Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanations of their analytical choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
-## Phase 3: Peer Reviews of Analyses
+## Phase 3: Peer Review of Analyses
 
-At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
@@
 The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
-For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
-Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.
 
@@
 <!-- TODO: add link to peer review survey -->
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100.
-<!-- TR:Need flow chart here-->
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-## Phase 4: Evaluate variation
+## Phase 4: Evaluating variation
 
@@
 dichotomous decision based on *p*-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
+<!-- QUESTION: range of the standardized effect sizes, right? -->
 
@@
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Herz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
 \highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
+<!-- TR: don't know what you mean tbh -->
 Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
@@
 Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
-This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the the meta-analytical model.
+This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytical model.
 As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
@@
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there are no divergent transitions.
+In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there we obtain a model fit with no divergent transitions.
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
@@
 
-The posterior probability of the population-level intercept $\alpha$ will give us an estimate of the range of probable values of the standardized effect size $\hat{\eta}$.
-This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \@ref(ana-factors).
-Crucially, the posterior probability of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+The posterior probability of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
+The posterior probability will further allow us to investigate the effect of a set of analytical and demographic predictors, detailed in Section \@ref(ana-factors).
+Crucially, the posterior probability of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
@@
 In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \@ref(fig:funnel-plot)).
+<!-- QUESTION: do we need the plot? Since there is no crisp operationalization of what we call publication bias and what we call unbiased, I wonder whether we could get rid of the plots -->
 A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.
@@
 
-### Analytical and demographic factors affecting effect sizes {#ana-factors}
-
+### Analytical and demographic predictors affecting effect sizes {#ana-factors}
+<!-- TR: I think we should use the term predictors. Factors is really ambiguous -->
 As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytical mean by the individual standardized effect sizes relate to those same predictors.
@@
 
-A normal distribution will be used as the likelihood of $\alpha_{t[i]}$.
+A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
 The mean of $\alpha_{t[i]}$ is modelled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
@@
 
-**Analytical factors**. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
+**Analytical factors**. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
 - *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).
+<!-- QUESTION: this is a little weird to me. Binary for data exclusion or not.-->
 - *Average peer-review rating* [numeric], as the mean of the peer-review ratings for each analysis.
+<!-- QUESTION: Just overall? or do we feed in the scales for stats vs. acoustics?-->
 
-The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
+Following Parker et al. (in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
 The SDI is an index typically used in ecology research to compare species composition across sites.
 For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses $(X, Y)$, the SDI will be obtained using the following \highlight[id=SC, comment={refactored the formula so it is closer to the original source}]{formula}:
+For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:
 
@@
 The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g.
-frequency center of gravity, harmonics difference, etc.), *other measures* (e.g.
-principal components, vowel dispersion, etc.)\comment[id=TR]{Stefano, do you think these four will cover possible ways to measure?
-We might want to define them too?
-dunno}\comment[id=SC]{I just added a "other measures" category for other things that are not strictly acoustic.}
+frequency, center of gravity, harmonics difference, etc.), *other measures* (e.g.
+principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
@@
 Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
-These will be entered in the model formula with a measurement-error term (`me(mean, sd)` in brms).
+These will be entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
 
@@
 **Demographic factors**. We will include the following demographic factors about the teams:
+<!-- QUESTION: Would like to discuss the term demographic here-->
 
-- *Research experience* [numeric] as the elapsed time from PhD award. Negative values will indicate that the person is a student or graduate studens ($rexp_i$).
+- *Research experience* [numeric] as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens ($rexp_i$).
 - *Initial belief* [numeric] in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire ($belf_i$).
 
-We will publicly archive all relevant data, code, and materials on the Open Science Framework (<https://osf.io/3bmcp/>).
+### Data managment {#ana-archive}
+All relevantdata, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
 Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
@@
 
-Our rules for excluding data from our study are as follows.
 We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.

### 2021-03-09 RR_manuscript/Draft_RR.Rmd
jvc edits

@@
 <!-- TODO: include number of teams when known -->
-Specifically, we will report the impact of analytic decision on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
+Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
 <!-- TODO: check tense throughout, should be future tense -->
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
+Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
-In connection with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure [@roettger2019researcher].
+In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+<!-- in connection with = referring to; in conjunction with = together, coupled with.
+I think we want the later, but change if I'm mistaken (JVC) -->
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
@@
 Despite recent efforts to improve transparency and reproducibility [e.g.
-miguel2014promoting; @klein2018practical] and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare [@wicherts2006poor].
+miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].
 
-While analytical flexibility has been widely discussed both from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and its application in individual scientific fields [e.g.
+Analytical flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
 Wichert et al.
 2015, Charles et al.
-2019, @roettger2019researcher], there are still many unknowns regarding the extent of analytical plurality in practice.
-<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019 -->
-
+2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
+<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019... are we certain this isn't @wicherts2016? (JVC) -->
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
+<!-- I think this should be part of the previous paragraph.
+-->
 
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
+The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.
 
@@
 While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
-In these studies the data sets were fixed and data collection or measurement could not be changed.
-
+In these studies the data sets were fixed and neither data collection nor measurement could be changed.
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
@@
 Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
-For example, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
+
+For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
@@
 
-In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
-<!-- TODO: check BE vs. AE -->
+In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
 This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
@@
 Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
-One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behaviour).
+One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).
 
@@
 This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
+<!-- why not "phonological contrast"?
+-->
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 For example, studies investigating acoustic correlates of word stress (e.g.
-the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
+the difference between *ínsight* and *incíte*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
+Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
 The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
+Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
 
-When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
@@
 
-When looking at phrase-level temporal domains, the number of possible analytical pipelines quickly explodes.
+When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially. <!-- this is hyperbole, but seems (possibly) more appropriate than "explodes" -->
 This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
-When comparing two utterance such as (2a) and (2b), there are many things to consider.
+<!-- When comparing two utterances such as (2a) and (2b), there are many things to consider.  (I think we can do without this sentence.) -->
 Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyse speech data [see @gordon2017acoustic].
+We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
 And the garden of forking paths does not stop here.
 <!-- TODO: add examples of pitch tracking options -->
-In \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}][id=TR, comment = {Better now?}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
-Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+Figure \@ref(fig:forkingPaths) \highlight[id=SC, comment = {The figure text is quite small.
+Probably better to change to a longer rather then wider layout.}]\highlight[id=TR, comment = {Better now?}], illustrates a specific option to automatically calculate f0\highlight[id=TR, comment = {add examples of pitch tracking options}.
+Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+<!-- Im having a bit of trouble with this sentence.
+I tried to fix it and now I am realizing I don't quite follow (JVC) -->
 
@@
 ## The data set: The acoustic properties of atypical modifiers
+
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes. 
-Moreover, the data is not available, and the statistical analysis uses anti-conservative co-variance structures, lending reasonable doubt on the original conclusions.
+Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
+<!-- "lending doubt on" sounded a bit weird to me (JVC) -->
 
@@
 The participant and the experimenter could not see each other nor each others' screens.
-After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
 
-<!-- TODO: see XXX, what do we refer to here? -->
+<!-- TODO: see XXX, what do we refer to here? Are we going to include an image? -->
 
@@
 # Methods
+
 As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
-Analyst must identify relevant measurements as well as temporal domain(s) from within which these measures are to be taken, operationalize and possibly transform those measures, before submitting them to statistical models, which have to be chosen alongside inferential criteria.
+Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
-We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
 
-<!-- QUESTION: wanna meditate over the term demographic-->
+<!-- QUESTION: wanna meditate over the term demographic (add analytic vs. analytical too)-->
 
@@
 <!-- TODO: add materials link and mailing lists -->
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project [https://many-speech-analyses.github.io](https://many-speech-analyses.github.io) and a short pre-recorded slide show that summarizes the study and research question (LINK).
+<!-- same as above, or OSF -->
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
@@
 
-Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
 
-<!-- QUESTION: How to frame this sentence. It is not ongoing. Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted.-->
+<!-- QUESTION: How to frame this sentence.
+It is not ongoing.
+Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted.
+(This seems good to me.
+added) -->
 
@@
 <!-- TODO: add citation to ECO RR -->
-To identify the minimal sample size, we followed the method in Parker et al. \highlight{[ECO RR]}.
-The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
+Following Parker et al.
+\highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
 the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
@@
 <!-- QUESTION: the sentence in brackets looks wrong, this would be true for confidence intervals right? -->
-The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:
+The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistic:
 
@@
 where $n$ is the sample size.
-Since we know $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
-Inserting $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
+Given $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
+Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
 
@@
 <!-- TODO: add link to analytical survey -->
-Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanations of their analytical choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code and the data set.
+This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
 <!-- TODO: add link to peer review survey -->
@@
 
-The reviewers will also be given the option to include further comments in text box for each of the three ratings.
+The reviewers will also be given the option to include further comments in a text box for each of the three ratings.
 
@@
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
 
@@
 mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects [if applicable], (d) the nature and reasoning behind inferential assessments (e.g.
-dichotomous decision based on *p*-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
+dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
 <!-- QUESTION: range of the standardized effect sizes, right? -->
@@
 
-To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Herz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+We will summarize the variability in reported effect sizes using Bayesian meta-analytic \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-<!-- TR: don't know what you mean tbh -->
+\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each categorical variable will mirror that of the original analyses.
+<!-- TR: don't know what you mean tbh; JVC: I get what you're saying, essentially we will keep the levels of their categorical variables the same when we refit the models, right?
+I changed it so that it says that.
+Change if wrong.
+-->
 Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
@@
 critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
+If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
 Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
-This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytical model.
-As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
+This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
+As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
@@
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until there we obtain a model fit with no divergent transitions.
+In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
@@
 
-The posterior probability of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
-The posterior probability will further allow us to investigate the effect of a set of analytical and demographic predictors, detailed in Section \@ref(ana-factors).
-Crucially, the posterior probability of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
+The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \@ref(ana-factors).
+Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
-Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
+<!-- I understand "posterior probability" to refer to a point estimate, i.e., the posterior probability that B > 0 = some value between 0 and 1.
+I may be mistaken, but I think you are referring to the posterior distribution in the above paragraph -->
+
+Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportionately greater number of bigger or smaller effect sizes than the meta-analytic point estimate of the pooled effect).
+<!-- in case we want to use the median -->
 This will be achieved through inspection of funnel plots [@light1984; for a review see @egger1997; and @sterne2005; for a critique @lau2006].
 In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the *x*-axis and estimated error (i.e. standard deviation) on *y*-axis.
-In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \@ref(fig:funnel-plot)).
+In absence of bias, the points should be symmetrically distributed around the meta-analytic point estimate of the pooled effect (see Figure \@ref(fig:funnel-plot)).
 <!-- QUESTION: do we need the plot? Since there is no crisp operationalization of what we call publication bias and what we call unbiased, I wonder whether we could get rid of the plots -->
-A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.
+A sign of possible bias is when there are more points which are farther from the meta-analytic point estimate on just one side.
+
+<!-- Note: I keep changing meta-analytical to meta-analytic (the -cal sounds weird to me).
+My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs.
+500k) -->
 
 ```{r funnel-plot, include=TRUE, fig.cap="Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analytical mean.", fig.dim = c(6, 2)}
+The vertical dashed line represents the meta-analytic mean.", fig.dim = c(6, 2)}
 meta_est <- 0
@@
 <!-- TR: I think we should use the term predictors. Factors is really ambiguous -->
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytical mean by the individual standardized effect sizes relate to those same predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.
 We will fit two Bayesian regression models, one for (a) and one for (b).
@@
 with each team's group-level coefficient $\alpha_{\text{t}[i]}$ as the outcome variable, and the analytical and demographic factors described below as predictors.
-The coefficient $\alpha_{\text{t}[i]}$ can be interpreted as the deviation score of the team's $\eta_i$ from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
-Since each $\alpha_{\text{t}[i]}$ comes with uncertainty, quantified by its standard deviation $\sigma_{\alpha_{\text{t}[i]}}$, we will fit a measurement-error model, as we did in the meta-analytical model above.
+The coefficient $\alpha_{\text{t}[i]}$ can be interpreted as the deviation score of the team's $\eta_i$ from the meta-analytic point estimate, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytic mean.
+Since each $\alpha_{\text{t}[i]}$ comes with uncertainty, quantified by its standard deviation $\sigma_{\alpha_{\text{t}[i]}}$, we will fit a measurement-error model, as we did in the meta-analytic model above.
 
 A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
-The mean of $\alpha_{t[i]}$ is modelled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
+The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
@@
 ### Data managment {#ana-archive}
-All relevantdata, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
+
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
 Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.

### 2021-03-10 scripts/r/simulations/simulations.Rmd
:memo: - edit simulation.Rmd with explanations

@@
 
+Prior predictive checks are run to assess the goodness of the prior specification before model fitting.
+
 ```{r prior-predictive}
+# run checks
 meta_bm_ppred <- brm(
@@
 
+# get samples
 ppred_samples <- posterior_samples(meta_bm_ppred) %>%
@@
 
-```{r ppred-posts}
-ppred_samples %>%
+Let's plot the prior probability distributions of the intercept and the standard deviation.
+
+```{r ppred-posts, message=FALSE, warning=FALSE}
+ppred_long <- ppred_samples %>%
   pivot_longer(intercept:`group-level SD`, names_to = "term") %>%
-  mutate(term = factor(term, levels = c("intercept", "group-level SD"))) %>%
+  mutate(term = factor(term, levels = c("intercept", "group-level SD")))
+
+int <- ppred_long %>%
+  filter(term == "intercept") %>%
   ggplot(aes(value)) +
   geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 0.4) +
-  facet_wrap(~ term, scales = "free")
+  labs(title = "Intercept")
+
+sd <- ppred_long %>%
+  filter(term == "group-level SD") %>%
+  ggplot(aes(value)) +
+  geom_density(colour = NA, fill = "#325756", alpha = 0.9, bw = 1) +
+  xlim(0, 25) +
+  labs(title = "Group-level SD")
+
+int + sd
 ```
+
+And the joint prior probability distribution.
 
@@
 ## Run
+
+The following code fits the meta-analytical model to the simulated data.
 

### 2021-03-10 RR_manuscript/Draft_RR.Rmd
:bug: - fix bugs and render pdf

@@
 Despite recent efforts to improve transparency and reproducibility [e.g.
-miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].
+@miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].
 
@@
 Several other recent studies corroborated this analytical flexibility across different disciplines.
-Both @dutilh2019 ad @starns2019 investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
 <!-- TODO: Parker et al. bib info -->
@@
 
+\vspace{1em}
 (1) "I can't bear another meeting on Zoom."
+\vspace{1em}
 
@@
 they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g.
-@jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
+@jongman2000acoustic; @lisker1986voicing; @summerfield1984; @winter2014spoken].
 <!-- TODO: add summerfield ref-->
@@
 
+\vspace{1em}
+
 (2a) I can't bear *ANOTHER* meeting on zoom.
@@
 (2b) I can't bear another meeting on *ZOOM*.
+
+\vspace{1em}
 
@@
 <!-- TODO: add examples of pitch tracking options -->
-Figure \@ref(fig:forkingPaths) \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}]\highlight[id=TR, comment = {Better now?}], illustrates a specific option to automatically calculate f0\highlight[id=TR, comment = {add examples of pitch tracking options}.
+<!-- NOTE: (TR) is the figure better now? -->
+Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
 Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
@@
 
-We will summarize the variability in reported effect sizes using Bayesian meta-analytic \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
+<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model -->
+We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
@@
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each categorical variable will mirror that of the original analyses.
-<!-- TR: don't know what you mean tbh; JVC: I get what you're saying, essentially we will keep the levels of their categorical variables the same when we refit the models, right?
+Factor-level ordering for each categorical variable will mirror that of the original analyses.
+<!-- NOTE: TR: don't know what you mean tbh -->
+<!-- NOTE: JVC: I get what you're saying, essentially we will keep the levels of their categorical variables the same when we refit the models, right?
 I changed it so that it says that.

### 2021-03-10 RR_manuscript/Draft_RR.tex
:bug: - fix bugs and render pdf

@@
 
-In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, the scientific disciplines have uncovered surprisingly low success rates in replication attempts (e.g., Open Science Collaboration 2015; Camerer et al.
+In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
+In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates (e.g., Collaboration 2015; Camerer et al.
 2018) leading to what is now referred to as the \emph{replication crisis}.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data (\highlight{REFS}).
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Jeffrey J.
-Starns et al.
-2019b) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
+The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Starns et al.
+2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, and Simonsohn 2011).
-Recent projects have shown that the variability between different data analysts is vast.
-This variability can lead independent researchers to draw different conclusions about the same data set as demonstrated by several projects crowd-sourcing analysis strategies (e.g., Silberzahn et al.
-2018; Jeffrey J.
-Starns et al.
-2019b; Botvinik-Nezer et al.
+Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set (e.g., Silberzahn et al.
+2018; Starns et al.
+2019; Botvinik-Nezer et al.
 2020b).
-These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
+These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
 Human behavior is complex and offers many ways to be translated into numbers.
@@
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
-Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.
+In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
+Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
 
@@
 
-Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
-\highlight[id=JC, comment = {I'd probably drop this.
-When we make unspecified decisions during data analysis we can stumble upon spurious results (most likely) as well as real results (less likely, still possible)...
-in other words it might not all be error...
-the issue is that we won't know the difference}]{However, if these decisions} during data analysis are not specified in advance, we might stumble upon seemingly meaningful patterns in the data that are merely statistical flukes.\comment[id=TR]{But isn't the human bias the major issue in statistical misinterpretation?
-(It also leads naturally to the next paragraph.)}
+Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
-\comment[id=JC]{If helpful we could also give a concrete common example here, like regarding forecasting the weather or something}
-\comment[id=TR]{Generally a good idea, but I'd say we keep it crisp at that point. The take-home here is: Humans are biased.}
-In connection with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure (Roettger 2019).
+In conjunction with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured (Roettger 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (REFS) and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io, ADD), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare (Jelte M.
-Wicherts et al.
+Despite recent efforts to improve transparency and reproducibility (e.g.
+Miguel et al.
+2014; Klein et al.
+2018) and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare (Wicherts et al.
 2006).
 
-While this issue has been widely discussed both from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
-2012; Nosek and Lakens 2014) and its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), there are still many unknowns regarding the extent of analytical plurality in practice.
+Analytical flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
+2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
+The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.
 
-Similar crowd-sourced studies recruiting independent analyst teams showed similar results.
-Both Dutilh et al. (2019) ad Jeffrey J. Starns et al. (2019a) investigated analysts choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies reveal vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytical flexibility in ecology and Botvinik-Nezer et al.
+Several other recent studies corroborated this analytical flexibility across different disciplines.
+Both Dutilh et al. (2019) ad Starns et al. (2019) investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytical flexibility in ecology and Botvinik-Nezer et al.
 2020a on neuroimaging data).
-Bastiaansen et al. (2020) crowdsourced clinical recommendations based on data analysis of an individual patient.
-Results suggests that analysis team differed substantially regarding decisions related to both the statistical analysis of the data set and the theoretical rationale behind interpreting the statistical results, indicating that there are multiple layers for degrees of freedom that interact with each other.
+Bastiaansen et al. (2020) crowdsourced clinical recommendations based on analyses of an individual patient.
+Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
-While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
-In these studies the data sets were fixed and data collection or measurement could not be changed.\comment[id=JC]{any particular reason to favor data table over data set?}\comment[id=TR]{I think my reasoning was data set can be data table or raw data.
-Data table is the numerical derivation of the raw data.
-Maybe not a useful distinction?}
+While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
+In these studies the data sets were fixed and neither data collection nor measurement could be changed.
+However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
+This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
+Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
 
-However, in many fields the primary raw data are complex signals that need to be operationalized in light of the research question.
-This is especially true in the social sciences, where the subject of investigation corresponds to observable and unobservable human behavior.
-Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
-For example, Flake and Fried (2020) discuss the cascading impact different practices can have on several components of psychometric research.
+For instance, Flake and Fried (2020) discuss the cascading impact that different practices can have on psychometric research.
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
@@
 
-In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
-This added complexity introduces further fork junctions in the research pipe-line, thus increasing yet again analytical flexibility.
-The present study looks at experimentally elicited speech data to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
+In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
+This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
+The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
 
@@
 Take for example the following sentence in (1).
+
+\vspace{1em}
 
@@
   ``I can't bear another meeting on Zoom.''
+  \vspace{1em}
 \end{enumerate}
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \emph{another} or \emph{meeting}.
-If, on the other hand, the speaker is just tired of video conferences, they might acoustically highlight the word \emph{Zoom}.
+If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with other, more pleasant activities.
+If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word \emph{Zoom}.
 
@@
 Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
-Utterances stretch over hundreds of milliseconds and contain several levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
+Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
 The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
 
-Speech categories are inherently multidimensional and dynamic: they consist of a cluster of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories {[}e.g., Jongman, Wayland, and Wong (2000); Lisker (1986); Summerfield, 1984; Winter (2014){]}.
+Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.
+Jongman, Wayland, and Wong 2000; Lisker 1986; \textbf{summerfield1984?}; Winter 2014).
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
-This voiced/voiceless contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
+This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{insíght} and \emph{íncite}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).
-Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).
+Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
@@
 2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven and Van Zanten 2005).
-Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes and Docherty 2006; Ogden 2004; White, Payne, and Mattys 2009).
+Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes and Docherty 2006; Ogden 2004; White, Payne, and Mattys 2009).
 
-When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
 For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{zoom}.
+
+\vspace{1em}
 
@@
 
+\vspace{1em}
+
 Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{zoom}?
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, something else?
+Do we measure fundamental frequency, intensity, or something else?
 
-When looking at phrase-level temporal domains, the number of possible analytical pipelines quickly explodes.
+When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
 This plurality of analytical paths is illustrated in Figure \ref{fig:forkingPaths}.
-When comparing two utterance such as (2a) and (2b), there are many things to consider.
 Even if we have decided to compare fundamental frequency (f0) of only the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 We could also measure the value or time of the minimum or maximum f0 value.
-We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0.
+We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data (see Gordon and Roettger 2017).
 And the garden of forking paths does not stop here.
-In \highlight[id=SC, comment = {The figure text is quite small.
-Probably better to change to a longer rather then wider layout.}]{Figure} \ref{fig:forkingPaths}, we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
-Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+Figure \ref{fig:forkingPaths}, illustrates a specific option to automatically calculate f0.
+Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
 
@@
 \includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing to utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
+(A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
 The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
@@
 These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g. Jelte M. Wicherts et al. 2016).
-Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models (\highlight{REFs}).
+These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. 2016).
+In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytical flexibility when choosing measures and operationalizing underlying theoretical constructs.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided XX analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.\comment[id=SC]{This needs a smother transition.}
+To assess the variability in data analysis pipelines across independent researchers, we will provide analytical teams with an experimentally elicited speech production data set.
+The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following, we will shortly introduce the research question of the original study.
 
-\hypertarget{the-data-set-the-acoustic-properties-of-redundant-modifiers}{%
-\subsection{The data set: The acoustic properties of redundant modifiers}\label{the-data-set-the-acoustic-properties-of-redundant-modifiers}}
+\hypertarget{the-data-set-the-acoustic-properties-of-atypical-modifiers}{%
+\subsection{The data set: The acoustic properties of atypical modifiers}\label{the-data-set-the-acoustic-properties-of-atypical-modifiers}}
 
-The data set given to the analysis teams comes from a study that investigated whether speakers acoustically modify utterances to signal typicality of noun/adjective combinations in referring expressions such as \emph{a blue banana} (atypical) vs \emph{a yellow banana} (typical).
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
@@
 
-Despite this coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003; Westerbeek, Koolen, and Maes 2015; Rubio-Fernández 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
+Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003; Westerbeek, Koolen, and Maes 2015; Rubio-Fernández 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
 2011; Paraboni, Van Deemter, and Masthoff 2007; Rubio-Fernández 2016).
@@
 
-Even looking at morphosyntactically identical expressions, speakers can modulate these via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd 2008).
+Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd 2008).
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
 Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
-In many languages, speakers can use particular pitch movements to signal whether a referent has already been mentioned and is therefore referred back to, or a referent is newly introduced into the discourse.
-Many languages use intonation in order to signal if a referent is contrasting with one or more alternatives that are relevant to the current discourse.
-Content selection aside, in a scenario in which a speaker wants to refer to a banana when there is also a pear on the table, the speaker would most likely produce a high rising pitch accent on \emph{banana} to indicate the contrastive nature of the noun.
-In a scenario in which the speaker wants to refer to a yellow banana when there is also a less ripe green banana on the table, the speaker would most likely produce a high rising pitch accent on \emph{yellow} to indicate the contrastive nature of the modifier.
-In addition to a pitch accent, elements that are new and/or contrastive are often produced with additional suprasegmental prominence, i.e.~segments are hyperarticulated, resulting in longer, louder and more clearly articulated acoustic targets.
+Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations {[}e.g.~dimitrova2008prosodic; dimitrova2009did{]}.
+Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referent such as \emph{yellow banana}.
+If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
+However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes.
+Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
 
-To answer the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded in a speech production study while interacting with a confederate (one of the experimenters).
+To further illuminate the question of whether speakers modify speech to signal atypical referents, we recorded thirty native German speakers interacting with a confederate (one of the experimenters) in a referential game.
 The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
@@
 The participant and the experimenter could not see each other nor each others' screens.
-After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der ablegen} `And now, you have to put the cube on top of the ') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
-The audio of this second utterance in the trial was recorded.
+The second utterance in the trial was the critical trial for analysis.
 
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was in focus (the Noun Focus condition, NF).
-If the the objects were the same object but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
-If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was in focus (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was discourse-pragmatically focused (the Noun Focus condition, NF).
+If the objects were the same but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
+If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was discourse-pragmatically focused (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
 The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{Orangene Mandarine} `orange mandarin'), medium typical (e.g.~\emph{Grüne Tomate} `green tomato'), or atypical (e.g.~\emph{Gelbe Kirsche} `yellow cherry').
-The typicality rating of each color-object combination was established, prior to the production experiment, with a norming study (see Appendix XXX for details).
+The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{greem tomato} ), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment (see Appendix XXX for details).
 
-Each participant went through 15 NF trials, 10 AF and 10 ANF trials.
-Each trial was repeated twice, yielding a total of 70 trials (\((15 \times 10 \times 10) \times 2\)) per participant and a grand-total of 2100 observations (\(70 \times 30\) participants), of which 900 (\(15 \times 2 \times 30\) participants) were the experimentally relevant trials.
-The recordings of the second sentence prompt of each trial make up the speech data set given to the analysis teams.
-The teams were asked to answer the same questions as the study that generated the data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
+Each participant responded to 15 critical trials (NF condition).
+Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total 900 (\(15 \times 2 \times 30\) participants) spoken utterances.
+All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
 \comment[id=SC]{Need transition here.}
-
-\hypertarget{research-questions}{%
-\subsection{Research questions}\label{research-questions}}
-
-The present study examines the extent to which subjective choices by different researchers analyzing the same speech data set affect the reported results.
-As outlined in Section \ref{s:operspeech}, researchers are faced with a large set of analytical choices when investigating a multidimensional signal such as speech.
-Not only must they choose appropriate statistical models and inferential criteria, but also identify relevant measures and their operationalisation and transformation, and the temporal domain(s) from within which these measures are to be taken.
-\highlight[id=SC, comment={I need help completing this sentence...}]{The ... makes up the ideal testing ground for ...}
-We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.
 
@@
 
-We are closely following the methodology proposed by Parker et al.~(Stage 1 in-principle accepted) in terms of data collection.
-However, the analysis will substantially diverge from their approach (see §\#.\#)
+As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
+Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
+The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
 
-This project involves the following five phases:
+We are closely following the data collection procedure proposed by Parker et al.~(Stage 1 in-principle accepted).
+The project involves the following five phases:
 
@@
 
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include \highlight{LIST OF LISTS}, and via word of mouth.
-The target population is active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in a relevant discipline.
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project \url{https://many-speech-analyses.github.io} and a short pre-recorded slide show that summarizes the study and research question (LINK).
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
@@
 
-Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
@@
 
-To identify the minimal sample size, we followed the method in \highlight{[ECO RR]}.
-The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
-Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
-The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:
+Following Parker et al.~\highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
+In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
+We consider a posterior distribution of \(\tau^2\), for which the 95\% credible interval (CrI) does not include 0 as sufficient (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
+The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistic:
 
@@
 
-Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:
+Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the following formula:
 
@@
 where \(n\) is the sample size.
-Since we know \(p\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
-Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that, when \(n\) is fixed, \emph{t} (and hence \(p\)) will be the same regardless of \(\tau^2\):
+Given \(p\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
+Inserting \(SE(\tau^2)\) into the formula for the \emph{t}-statistic shows that, when \(n\) is fixed, \emph{t} (and hence \(p\)) will be the same regardless of \(\tau^2\):
 
@@
 In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CrI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
-When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which is below the 0.05 threshold, as required.
-In sum, a minimal sample of 12 effect sizes (i.e.~of 12 analysis teams) would thus be sufficient to exclude 0 from the 95\% CrI of \(\tau^2\).
+When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which we consider sufficiently unlikely.
 
@@
 
-Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
 
-\hypertarget{phase-3-peer-reviews-of-analyses}{%
-\subsection{Phase 3: Peer Reviews of Analyses}\label{phase-3-peer-reviews-of-analyses}}
+\hypertarget{phase-3-peer-review-of-analyses}{%
+\subsection{Phase 3: Peer Review of Analyses}\label{phase-3-peer-review-of-analyses}}
 
-At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
+At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
 Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
@@
 The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
-For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer.
-Balancing the order in which reviewers see the analyses controls for order effects, e.g.~a reviewer might be less critical of the first methods section they read than the last.
 
@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100.
+The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.
+After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
 
-\hypertarget{phase-4-evaluate-variation}{%
-\subsection{Phase 4: Evaluate variation}\label{phase-4-evaluate-variation}}
+\hypertarget{phase-4-evaluating-variation}{%
+\subsection{Phase 4: Evaluating variation}\label{phase-4-evaluating-variation}}
 
@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
 
@@
 
-To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Stan Development Team 2021), RStan (Stan Development Team 2020), and brms (Bürkner 2017) in R (R Core Team 2020).
+We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+Factor-level ordering for each categorical variable will mirror that of the original analyses.
+Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Team 2021), RStan (Team 2020), and brms (Bürkner 2017) in R (R Core Team 2020).
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 The estimated coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size (\(\eta_i\)) of each reported model.
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
+If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
 Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error (\(\text{se}_i\)) of the effect size.
-This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the the meta-analytical model.
-As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.
+This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
+As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, the initiating authors will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model, as described in the following.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
@@
 We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{t}[i]}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan (Stan Development Team 2021), and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-\highlight[id=SC, comment = {This ok?}]{In case of issues from divergent transitions} in the sampling, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until there are no divergent transitions.
-The analysis will be conducted in R (R Core Team 2020) and fit using Stan (Stan Development Team 2021), RStan (Stan Development Team 2020), and brms (Bürkner 2017).
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan (Team 2021), and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+In case of divergent transitions, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
+The analysis will be conducted in R (R Core Team 2020) and fit using Stan (Team 2021), RStan (Team 2020), and brms (Bürkner 2017).
 The code used to run the model can be found here: INSERT LINK.
 
-The posterior probability of the population-level intercept \(\alpha\) will give us an estimate of the range of probable values of the standardized effect size \(\hat{\eta}\).
-This posterior probability will also form the basis \highlight[id=SC, comment = {A lot of "of"s...}]{of} the investigation of the effect of a set of analytical and demographic factors, detailed in Section \ref{ana-factors}.
-Crucially, the posterior probability of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
+The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \ref{ana-factors}.
+Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
 
-Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportional greater number of bigger or smaller effect sizes than the meta-analytical mean estimate).
+Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportionately greater number of bigger or smaller effect sizes than the meta-analytic point estimate of the pooled effect).
 This will be achieved through inspection of funnel plots (Light and Pillemer 1984; for a review see Egger et al. 1997; and Sterne, Becker, and Egger 2005; for a critique Lau et al. 2006).
 In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the \emph{x}-axis and estimated error (i.e.~standard deviation) on \emph{y}-axis.
-In absence of bias, the points should be symmetrically distributed around the meta-analytical mean (see Figure \ref{fig:funnel-plot}).
-A sign of possible bias is when there are more points which are farther from the meta-analytical mean on just one side.
+In absence of bias, the points should be symmetrically distributed around the meta-analytic point estimate of the pooled effect (see Figure \ref{fig:funnel-plot}).
+A sign of possible bias is when there are more points which are farther from the meta-analytic point estimate on just one side.
 
@@
 \caption{\label{fig:funnel-plot}Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analytical mean.}
+The vertical dashed line represents the meta-analytic mean.}
 \end{figure}
@@
 \hypertarget{ana-factors}{%
-\subsubsection{Analytical and demographic factors affecting effect sizes}\label{ana-factors}}
+\subsubsection{Analytical and demographic predictors affecting effect sizes}\label{ana-factors}}
 
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytical mean by the individual standardized effect sizes relate to those same predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.
 We will fit two Bayesian regression models, one for (a) and one for (b).
 with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
-The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytical mean, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytical mean.
-Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytical model above.
+The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytic point estimate, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytic mean.
+Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytic model above.
 
-A normal distribution will be used as the likelihood of \(\alpha_{t[i]}\).
-The mean of \(\alpha_{t[i]}\) is modelled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
+A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
+The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
@@
 
-\textbf{Analytical factors}. We will model the effect of the following predictors related to the analytical characteristics of each team's reported analysis:
+\textbf{Analytical factors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
 
-The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
+Following Parker et al.~(in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
 The SDI is an index typically used in ecology research to compare species composition across sites.
 For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses \((X, Y)\), the SDI will be obtained using the following \highlight[id=SC, comment={refactored the formula so it is closer to the original source}]{formula}:
+For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
 
@@
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.)\comment[id=TR]{Stefano, do you think these four will cover possible ways to measure?
-We might want to define them too?
-dunno}\comment[id=SC]{I just added a "other measures" category for other things that are not strictly acoustic.}
+The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
@@
 Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
-These will be entered in the model formula with a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
 
@@
 \item
-  \emph{Research experience} {[}numeric{]} as the elapsed time from PhD award. Negative values will indicate that the person is a student or graduate studens (\(rexp_i\)).
+  \emph{Research experience} {[}numeric{]} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens (\(rexp_i\)).
 \item
@@
 
-We will publicly archive all relevant data, code, and materials on the Open Science Framework (\url{https://osf.io/3bmcp/}).
+\hypertarget{ana-archive}{%
+\subsubsection{Data managment}\label{ana-archive}}
+
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
 Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
@@
 
+\leavevmode\hypertarget{ref-open2015estimating}{}%
+Collaboration, Open Science. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.
+
 \leavevmode\hypertarget{ref-de2014thought}{}%
@@
 
+\leavevmode\hypertarget{ref-klein2018practical}{}%
+Klein, Olivier, Tom E Hardwicke, Frederik Aust, Johannes Breuer, Henrik Danielsson, Alicia Hofelich Mohr, Hans IJzerman, et al.
+2018.
+{``A Practical Guide for Transparency in Psychological Science.''} \emph{Collabra: Psychology} 4 (1).
+
 \leavevmode\hypertarget{ref-knight2000}{}%
@@
 
+\leavevmode\hypertarget{ref-miguel2014promoting}{}%
+Miguel, Edward, Colin Camerer, Katherine Casey, Joshua Cohen, Kevin M Esterling, Alan Gerber, Rachel Glennerster, et al.
+2014.
+{``Promoting Transparency in Social Science Research.''} \emph{Science} 343 (6166): 30--31.
+
 \leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
@@
 Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
-
-\leavevmode\hypertarget{ref-open2015estimating}{}%
-Open Science Collaboration. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.
 
@@
 
-\leavevmode\hypertarget{ref-stan2020a}{}%
-Stan Development Team. 2020. {``{RStan}: The {R} Interface to {Stan}.''} \url{http://mc-stan.org/}.
-
-\leavevmode\hypertarget{ref-stan2021}{}%
----------. 2021. {``Stan Modeling Language Users Guide and Reference Manual, V2.26.0.''} \url{http://mc-stan.org/}.
-
-\leavevmode\hypertarget{ref-starns2019}{}%
+\leavevmode\hypertarget{ref-starns2019assessing}{}%
 Starns, Jeffrey J., Andrea M.
@@
 Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
-2019a.
-{``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
-
-\leavevmode\hypertarget{ref-starns2019assessing}{}%
-Starns, Jeffrey J, Andrea M Cataldo, Caren M Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
-2019b.
+2019.
 {``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
@@
 {``A Method of Establishing Groups of Equal Amplitude in Plant Sociology Based on Similarity of Species and Its Application to Analyses of the Vegetation on {D}anish Commons.''} \emph{Kongelige Danske Videnskabernes Selskab} 5 (4): 1--34.
+
+\leavevmode\hypertarget{ref-stan2020a}{}%
+Team, Stan Development. 2020. {``{RStan}: The {R} Interface to {Stan}.''} \url{http://mc-stan.org/}.
+
+\leavevmode\hypertarget{ref-stan2021}{}%
+---------. 2021. {``Stan Modeling Language Users Guide and Reference Manual, V2.26.0.''} \url{http://mc-stan.org/}.
 
@@
 
+\leavevmode\hypertarget{ref-wicherts2006poor}{}%
+Wicherts, Jelte M., Denny Borsboom, Judith Kats, and Dylan Molenaar. 2006. {``The Poor Availability of Psychological Research Data for Reanalysis.''} \emph{American Psychologist} 61 (7): 726.
+
 \leavevmode\hypertarget{ref-wicherts2016}{}%
@@
 
-\leavevmode\hypertarget{ref-wicherts2006poor}{}%
-Wicherts, Jelte M, Denny Borsboom, Judith Kats, and Dylan Molenaar. 2006. {``The Poor Availability of Psychological Research Data for Reanalysis.''} \emph{American Psychologist} 61 (7): 726.
-
 \leavevmode\hypertarget{ref-winter2014spoken}{}%

### 2021-03-10 RR_manuscript/Draft_RR.Rmd
:memo: - add comments

@@
 In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-<!-- in connection with = referring to; in conjunction with = together, coupled with.
-I think we want the later, but change if I'm mistaken (JVC) -->
+<!-- NOTE: (JVC) in connection with = referring to; in conjunction with = together, coupled with. I think we want the later, but change if I'm mistaken -->
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-<!-- I think this should be part of the previous paragraph.
--->
+<!-- NOTE: (?) I think this should be part of the previous paragraph. -->
 
@@
 This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
-<!-- why not "phonological contrast"?
+<!-- NOTE: (?) why not "phonological contrast"?
 -->
@@
 
-When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially. <!-- this is hyperbole, but seems (possibly) more appropriate than "explodes" -->
+When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
+<!-- NOTE: (JVC) this is hyperbole, but seems (possibly) more appropriate than "explodes" -->
 This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
-<!-- When comparing two utterances such as (2a) and (2b), there are many things to consider.  (I think we can do without this sentence.) -->
+<!-- When comparing two utterances such as (2a) and (2b), there are many things to consider.  NOTE: (JVC) (I think we can do without this sentence.) -->
 Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
-<!-- Im having a bit of trouble with this sentence.
+<!-- NOTE: (JVC) Im having a bit of trouble with this sentence.
 I tried to fix it and now I am realizing I don't quite follow (JVC) -->
@@
 Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
-<!-- "lending doubt on" sounded a bit weird to me (JVC) -->
+<!-- NOTE: (JVC) "lending doubt on" sounded a bit weird to me (JVC) -->
 
@@
 The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project [https://many-speech-analyses.github.io](https://many-speech-analyses.github.io) and a short pre-recorded slide show that summarizes the study and research question (LINK).
-<!-- same as above, or OSF -->
+<!-- NOTE: same as above, or OSF -->
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
@@
 
-<!-- I understand "posterior probability" to refer to a point estimate, i.e., the posterior probability that B > 0 = some value between 0 and 1.
+<!-- NOTE: I understand "posterior probability" to refer to a point estimate, i.e., the posterior probability that B > 0 = some value between 0 and 1.
 I may be mistaken, but I think you are referring to the posterior distribution in the above paragraph -->
@@
 
-<!-- Note: I keep changing meta-analytical to meta-analytic (the -cal sounds weird to me).
+<!-- NOTE: I keep changing meta-analytical to meta-analytic (the -cal sounds weird to me).
 My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs.
 500k) -->
+<!-- NOTE: (SC) I tend to use analytical to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent.
+-->
 
@@
 ### Analytical and demographic predictors affecting effect sizes {#ana-factors}
-<!-- TR: I think we should use the term predictors. Factors is really ambiguous -->
+<!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
 As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.

### 2021-03-10 RR_manuscript/Draft_RR.Rmd
:memo: - edit RR draft based on what discussed in meeting

@@
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-<!-- TODO: add refs about variable conclusions from reliable data -->
+<!-- TODO: add REFS about variable conclusions from reliable data -->
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
@@
 In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
-<!-- TODO: include number of teams when known -->
+<!-- TODO: LATER include number of teams when known -->
 Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
@@
 In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
-<!-- NOTE: (JVC) in connection with = referring to; in conjunction with = together, coupled with. I think we want the later, but change if I'm mistaken -->
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
@@
 Analytical flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
-Wichert et al.
-2015, Charles et al.
+@wicherts2016, Charles et al.
 2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
-<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019... are we certain this isn't @wicherts2016? (JVC) -->
+<!-- TODO: add REFS Charles et al. 2019 -->
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-<!-- TODO: Parker et al. bib info -->
+<!-- TODO: Parker et al. (ECO) REFS -->
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
@@
 @jongman2000acoustic; @lisker1986voicing; @summerfield1984; @winter2014spoken].
-<!-- TODO: add summerfield ref-->
+<!-- TODO: add summerfield REFS-->
 A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
@@
 When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
-<!-- NOTE: (JVC) this is hyperbole, but seems (possibly) more appropriate than "explodes" -->
 This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
-<!-- When comparing two utterances such as (2a) and (2b), there are many things to consider.  NOTE: (JVC) (I think we can do without this sentence.) -->
 Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 <!-- TODO: add examples of pitch tracking options -->
-<!-- NOTE: (TR) is the figure better now? -->
 Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
 Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
-<!-- NOTE: (JVC) Im having a bit of trouble with this sentence.
-I tried to fix it and now I am realizing I don't quite follow (JVC) -->
+<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->
 
@@
 If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
-However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes.
+However, the original conclusions of above studies were based on small (N = 10), unjustified sample sizes.
 Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
-<!-- NOTE: (JVC) "lending doubt on" sounded a bit weird to me (JVC) -->
 
-<!-- QUESTION: ask people if they have ever heard of these papers? -->
+<!-- TODO: ask people if they have ever heard of these papers -->
 
@@
 The participant and the experimenter could not see each other nor each others' screens.
+<!-- TODO: add ref to experiment procedure figure in (see XXX) -->
 After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
-
-<!-- TODO: see XXX, what do we refer to here? Are we going to include an image? -->
-
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 
-<!-- QUESTION: add pictures? -->
+<!-- TODO: add experiment procedure figure -->
 
@@
 All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
-\comment[id=SC]{Need transition here.}
 
@@
 We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
-
-<!-- QUESTION: wanna meditate over the term demographic (add analytic vs. analytical too)-->
 
@@
 
-<!-- TODO: add materials link and mailing lists -->
+<!-- TODO: add materials LINK and mailing lists -->
 The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project [https://many-speech-analyses.github.io](https://many-speech-analyses.github.io) and a short pre-recorded slide show that summarizes the study and research question (LINK).
@@
 For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
-
 Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
-
-<!-- QUESTION: How to frame this sentence.
-It is not ongoing.
-Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted.
-(This seems good to me.
-added) -->
 
@@
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-<!-- TODO: add link to informed consent form -->
+<!-- TODO: add LINK to informed consent form -->
 All analysts will sign a consent (ethics) document (LINK).
@@
 
-<!-- TODO: add citation to ECO RR -->
+<!-- TODO: Parker et al. (ECO) REFS -->
 Following Parker et al.
@@
 In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
-We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient (i.e.
-the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
-<!-- QUESTION: the sentence in brackets looks wrong, this would be true for confidence intervals right? -->
-The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistic:
+We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
+The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:
 
@@
 where $n$ is the sample size.
-Given $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
-Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:
+Given $Pr$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
+Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $Pr$) will be the same regardless of $\tau^2$:
 
@@
 
-<!-- QUESTION: Should we double check that with some folks? -->
+<!-- TODO: double check with BN if sample size justification is correct -->
 
@@
 
-<!-- TODO: add link to demo survey -->
+<!-- TODO: add LINK to demo survey -->
 The analysis teams will register and answer a demographic and expertise survey (LINK).
-The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
-<!-- QUESTION: should the survey ask for expertise in their acoustic skills? -->
+The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
 We will then provide teams with the acoustic data set and request that they answer the following research question:
-<!-- TODO: Link dataset here -->
+<!-- TODO: LINK dataset here -->
 
@@
 
-<!-- TODO: add link to analytical survey -->
+<!-- TODO: add LINK to analytical survey -->
 Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
-<!-- TODO: add link to peer review survey -->
+<!-- TODO: add LINK to peer review survey -->
 The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
@@
 f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.
-mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects [if applicable], (d) the nature and reasoning behind inferential assessments (e.g.
-dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
-<!-- QUESTION: range of the standardized effect sizes, right? -->
+mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.
+dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see \@ref(s:meta-est) for the standardization procedure).
 
@@
 Factor-level ordering for each categorical variable will mirror that of the original analyses.
-<!-- NOTE: TR: don't know what you mean tbh -->
-<!-- NOTE: JVC: I get what you're saying, essentially we will keep the levels of their categorical variables the same when we refit the models, right?
-I changed it so that it says that.
-Change if wrong.
--->
 Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
@@
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
-<!-- TODO: add link to code of the meta-analytical model -->
+<!-- TODO: add LINK to code of the meta-analytical model -->
 The code used to run the model can be found here: INSERT LINK.
@@
 
-<!-- NOTE: I understand "posterior probability" to refer to a point estimate, i.e., the posterior probability that B > 0 = some value between 0 and 1.
-I may be mistaken, but I think you are referring to the posterior distribution in the above paragraph -->
-
 Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportionately greater number of bigger or smaller effect sizes than the meta-analytic point estimate of the pooled effect).
@@
 In absence of bias, the points should be symmetrically distributed around the meta-analytic point estimate of the pooled effect (see Figure \@ref(fig:funnel-plot)).
-<!-- QUESTION: do we need the plot? Since there is no crisp operationalization of what we call publication bias and what we call unbiased, I wonder whether we could get rid of the plots -->
 A sign of possible bias is when there are more points which are farther from the meta-analytic point estimate on just one side.
+<!-- NOTE: We are gonna keep the funnel plots at least for Stage 1 review, because it is easier to understand how this works. -->
 
@@
 
+<!-- NOTE: We dropped data exclusion -->
 - *Measure of uniqueness* [numeric] of individual analyses for the set of predictors in each model ($uniq_i$).
@@
 - *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
-- *Data exclusion*, [categorical] whether data has been excluded or not ($excl_i$).
-<!-- QUESTION: this is a little weird to me. Binary for data exclusion or not.-->
 - *Average peer-review rating* [numeric], as the mean of the peer-review ratings for each analysis.
-<!-- QUESTION: Just overall? or do we feed in the scales for stats vs. acoustics?-->
+<!-- NOTE: We decided to use just the overall rating -->
 
@@
 **Demographic factors**. We will include the following demographic factors about the teams:
-<!-- QUESTION: Would like to discuss the term demographic here-->
 

### 2021-03-10 RR_manuscript/Draft_RR.tex
:memo: - edit RR draft based on what discussed in meeting

@@
 Analytical flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
-2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields (e.g.~Wichert et al.~2015, Charles et al.~2019, Roettger 2019), notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
+2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields Roettger (2019), notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
-However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes.
+However, the original conclusions of above studies were based on small (N = 10), unjustified sample sizes.
 Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
@@
 After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
-
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
-\comment[id=SC]{Need transition here.}
 
@@
 For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
-
 Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
@@
 In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
-We consider a posterior distribution of \(\tau^2\), for which the 95\% credible interval (CrI) does not include 0 as sufficient (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
-The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistic:
+We consider a posterior distribution of \(\tau^2\), for which the 95\% credible interval (CrI) does not include 0 as sufficient.
+The probability \(Pr\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistic:
 
@@
 where \(n\) is the sample size.
-Given \(p\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
-Inserting \(SE(\tau^2)\) into the formula for the \emph{t}-statistic shows that, when \(n\) is fixed, \emph{t} (and hence \(p\)) will be the same regardless of \(\tau^2\):
+Given \(Pr\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
+Inserting \(SE(\tau^2)\) into the formula for the \emph{t}-statistic shows that, when \(n\) is fixed, \emph{t} (and hence \(Pr\)) will be the same regardless of \(\tau^2\):
 
@@
 The analysis teams will register and answer a demographic and expertise survey (LINK).
-The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise.
+The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
 We will then provide teams with the acoustic data set and request that they answer the following research question:
@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see \ref{s:meta-est} for the standardization procedure).
 
@@
   \emph{Temporal window} {[}categorical{]} that the measurement is taken over (\(twin_i\)).
-\item
-  \emph{Data exclusion}, {[}categorical{]} whether data has been excluded or not (\(excl_i\)).
 \item

### 2021-03-12 RR_manuscript/Draft_RR.Rmd
some refs

@@
 they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g.
-@jongman2000acoustic; @lisker1986voicing; @summerfield1984; @winter2014spoken].
-<!-- TODO: add summerfield REFS-->
+@jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
 A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).

### 2021-03-15 RR_manuscript/Draft_RR.Rmd
:memo: - edit second model with details about deviation from posterior

@@
 <!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
 We will fit two Bayesian regression models, one for (a) and one for (b).
-<!-- TODO: check if stand. effect sizes and deviations are equivalent. -->
-with each team's group-level coefficient $\alpha_{\text{t}[i]}$ as the outcome variable, and the analytical and demographic factors described below as predictors.
-The coefficient $\alpha_{\text{t}[i]}$ can be interpreted as the deviation score of the team's $\eta_i$ from the meta-analytic point estimate, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytic mean.
-Since each $\alpha_{\text{t}[i]}$ comes with uncertainty, quantified by its standard deviation $\sigma_{\alpha_{\text{t}[i]}}$, we will fit a measurement-error model, as we did in the meta-analytic model above.
-
-A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
-The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
-The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for $i$ and $\upsilon$ we will use a normal distribution with mean 0 and standard deviation 1.
-<!-- TODO: add explanation of me() predictors resp and belf -->
-
-<!-- TODO: add brm info on factors analysis model -->
 
@@
 
-### Data managment {#ana-archive}
+**Models specification**. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
+The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
+The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
+The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance $Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})$.
+
+<!-- TODO: add brm info on factors analysis model -->
+A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
+The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
+The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
+As the prior for $i$ and $\upsilon$ we will use a normal distribution with mean 0 and standard deviation 1.
+<!-- TODO: add explanation of me() predictors resp and belf -->
+
+### Data management {#ana-archive}
 

### 2021-03-15 RR_manuscript/Draft_RR.tex
:memo: - edit second model with details about deviation from posterior

@@
 \usepackage{lmodern}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
@@
 The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.
-Jongman, Wayland, and Wong 2000; Lisker 1986; \textbf{summerfield1984?}; Winter 2014).
+Jongman, Wayland, and Wong 2000; Lisker 1986; Summerfield 1981; Winter 2014).
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.
+As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
 We will fit two Bayesian regression models, one for (a) and one for (b).
-with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
-The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytic point estimate, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytic mean.
-Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytic model above.
-
-A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
-The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
-The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for \(i\) and \(\upsilon\) we will use a normal distribution with mean 0 and standard deviation 1.
 
@@
 
+\textbf{Models specification}. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
+The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
+The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
+The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance \(Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})\).
+
+A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
+The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
+The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
+As the prior for \(i\) and \(\upsilon\) we will use a normal distribution with mean 0 and standard deviation 1.
+
 \hypertarget{ana-archive}{%
-\subsubsection{Data managment}\label{ana-archive}}
+\subsubsection{Data management}\label{ana-archive}}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-arts2011overspecification}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-arts2011overspecification}{}}%
 Arts, Anja, Alfons Maes, Leo GM Noordman, and Carel Jansen. 2011. {``Overspecification in Written Instruction.''} \emph{Linguistics} 49 (3): 555--74.
 
-\leavevmode\hypertarget{ref-baselga2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-baselga2020}{}}%
 Baselga, Andres, David Orme, Sebastien Villeger, Julien De Bortoli, Fabien Leprieur, and Maxime Logez.
@@
 
-\leavevmode\hypertarget{ref-bastiaansen2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bastiaansen2020}{}}%
 Bastiaansen, Jojanneke A., Yoram K.
@@
 
-\leavevmode\hypertarget{ref-botvinik-nezer2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-botvinik-nezer2020}{}}%
 Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F.
@@
 
-\leavevmode\hypertarget{ref-botvinik2020variability}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-botvinik2020variability}{}}%
 Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
@@
 
-\leavevmode\hypertarget{ref-box1976science}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-box1976science}{}}%
 Box, George EP. 1976. {``Science and Statistics.''} \emph{Journal of the American Statistical Association} 71 (356): 791--99.
 
-\leavevmode\hypertarget{ref-brugger2001}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-brugger2001}{}}%
 Brugger, Peter.
@@
 
-\leavevmode\hypertarget{ref-burkner2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
 Bürkner, Paul-Christian.
@@
 
-\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-camerer2018evaluating}{}}%
 Camerer, Colin F, Anna Dreber, Felix Holzmeister, Teck-Hua Ho, Jürgen Huber, Magnus Johannesson, Michael Kirchler, et al.
@@
 
-\leavevmode\hypertarget{ref-open2015estimating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-open2015estimating}{}}%
 Collaboration, Open Science. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.
 
-\leavevmode\hypertarget{ref-de2014thought}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-de2014thought}{}}%
 De Groot, Adriaan D. 2014. \emph{Thought and Choice in Chess}. Vol. 4. Walter de Gruyter GmbH \& Co KG.
 
-\leavevmode\hypertarget{ref-degen2020redundancy}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-degen2020redundancy}{}}%
 Degen, Judith, Robert D Hawkins, Caroline Graf, Elisa Kreiss, and Noah D Goodman.
@@
 
-\leavevmode\hypertarget{ref-dice1945}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-dice1945}{}}%
 Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.
 
-\leavevmode\hypertarget{ref-dutilh2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-dutilh2019}{}}%
 Dutilh, Gilles, Jeffrey Annis, Scott D.
@@
 
-\leavevmode\hypertarget{ref-egger1997}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-egger1997}{}}%
 Egger, Matthias, George Davey Smith, Martin Schneider, and Christoph Minder. 1997. {``Bias in Meta-Analysis Detected by a Simple, Graphical Test.''} \emph{British Medical Journal} 315: 629--34.
 
-\leavevmode\hypertarget{ref-fischhoff1975hindsight}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-fischhoff1975hindsight}{}}%
 Fischhoff, Baruch.
@@
 
-\leavevmode\hypertarget{ref-flake2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
 Flake, Jessica Kay, and Eiko I.
@@
 
-\leavevmode\hypertarget{ref-foulkes2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-foulkes2006}{}}%
 Foulkes, Paul, and Gerard Docherty. 2006. {``The Social Life of Phonetics and Phonology.''} \emph{Journal of Phonetics} 34 (4): 409--38.
 
-\leavevmode\hypertarget{ref-gatt2013we}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gatt2013we}{}}%
 Gatt, Albert, Roger PG van Gompel, Kees van Deemter, and Emiel Krahmer. 2013. {``Are We Bayesian Referring Expression Generators.''} In. Cognitive Science Society.
 
-\leavevmode\hypertarget{ref-gelman2014statistical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gelman2014statistical}{}}%
 Gelman, Andrew, and Eric Loken.
@@
 
-\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-gordon2017acoustic}{}}%
 Gordon, Matthew, and Timo Roettger. 2017. {``Acoustic Correlates of Word Stress: A Cross-Linguistic Survey.''} \emph{Linguistics Vanguard} 3 (1): 1--11.
 
-\leavevmode\hypertarget{ref-grice1975logic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grice1975logic}{}}%
 Grice, Herbert P. 1975. {``Logic and Conversation.''} In \emph{Speech Acts}, 41--58. Brill.
 
-\leavevmode\hypertarget{ref-hawkins2004influence}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hawkins2004influence}{}}%
 Hawkins, Sarah, and Noël Nguyen. 2004. {``Influence of Syllable-Coda Voicing on the Acoustic Properties of Syllable-Onset /l/ in {E}nglish.''} \emph{Journal of Phonetics} 32 (2): 199--231.
 
-\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jongman2000acoustic}{}}%
 Jongman, Allard, Ratree Wayland, and Serena Wong. 2000. {``Acoustic Characteristics of English Fricatives.''} \emph{The Journal of the Acoustical Society of America} 108 (3): 1252--63.
 
-\leavevmode\hypertarget{ref-klein2018practical}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-klein2018practical}{}}%
 Klein, Olivier, Tom E Hardwicke, Frederik Aust, Johannes Breuer, Henrik Danielsson, Alicia Hofelich Mohr, Hans IJzerman, et al.
@@
 
-\leavevmode\hypertarget{ref-knight2000}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-knight2000}{}}%
 Knight, K. 2000. \emph{Mathematical Statistics}. Chapman; Hall, New York.
 
-\leavevmode\hypertarget{ref-koole2012rewarding}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-koole2012rewarding}{}}%
 Koole, Sander L, and Daniël Lakens. 2012. {``Rewarding Replications: A Sure and Simple Way to Improve Psychological Science.''} \emph{Perspectives on Psychological Science} 7 (6): 608--14.
 
-\leavevmode\hypertarget{ref-ladd2008intonational}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ladd2008intonational}{}}%
 Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.
 
-\leavevmode\hypertarget{ref-lau2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lau2006}{}}%
 Lau, Joseph, John P. A. Ioannidis, Norma Terrin, Christopher H. Schmid, and Ingram Olkin. 2006. {``The Case of the Misleading Funnel Plot.''} \emph{British Medical Journal} 333 (7568): 597--600.
 
-\leavevmode\hypertarget{ref-light1984}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-light1984}{}}%
 Light, Richard J., and David B. Pillemer. 1984. \emph{Summing up; the Science of Reviewing Research}. Cambridge, MA (USA) Harvard Univ. Press.
 
-\leavevmode\hypertarget{ref-lisker1977rapid}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lisker1977rapid}{}}%
 Lisker, Leigh. 1977. {``Rapid Versus Rabid: A Catalogue of Acoustic Features That May Cue the Distinction.''} \emph{The Journal of the Acoustical Society of America} 62 (S1): S77--78.
 
-\leavevmode\hypertarget{ref-lisker1986voicing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-lisker1986voicing}{}}%
 ---------. 1986. {``{`Voicing'} in {E}nglish: A Catalogue of Acoustic Features Signaling /b/ Versus /p/ in Trochees.''} \emph{Language and Speech} 29 (1): 3--11.
 
-\leavevmode\hypertarget{ref-miguel2014promoting}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-miguel2014promoting}{}}%
 Miguel, Edward, Colin Camerer, Katherine Casey, Joshua Cohen, Kevin M Esterling, Alan Gerber, Rachel Glennerster, et al.
@@
 
-\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-nickerson1998confirmation}{}}%
 Nickerson, Raymond S. 1998. {``Confirmation Bias: A Ubiquitous Phenomenon in Many Guises.''} \emph{Review of General Psychology} 2 (2): 175--220.
 
-\leavevmode\hypertarget{ref-nosek2014method}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
 Nosek, Brian A, and Daniël Lakens. 2014. {``A Method to Increase the Credibility of Published Results.''} \emph{Social Psychology} 45 (3): 137--41.
 
-\leavevmode\hypertarget{ref-ogden2004}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-ogden2004}{}}%
 Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
 
-\leavevmode\hypertarget{ref-paraboni2007generating}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-paraboni2007generating}{}}%
 Paraboni, Ivandré, Kees Van Deemter, and Judith Masthoff. 2007. {``Generating Referring Expressions: Making Referents Easy to Identify.''} \emph{Computational Linguistics} 33 (2): 229--54.
 
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. 2020. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 
-\leavevmode\hypertarget{ref-roettger2019researcher}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-roettger2019researcher}{}}%
 Roettger, Timo B. 2019. {``Researcher Degrees of Freedom in Phonetic Research.''} \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology} 10 (1).
 
-\leavevmode\hypertarget{ref-rotello2015more}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rotello2015more}{}}%
 Rotello, Caren M, Evan Heit, and Chad Dubé.
@@
 
-\leavevmode\hypertarget{ref-rubio2016redundant}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rubio2016redundant}{}}%
 Rubio-Fernández, Paula. 2016. {``How Redundant Are Redundant Color Adjectives? An Efficiency-Based Analysis of Color Overspecification.''} \emph{Frontiers in Psychology} 7: 153.
 
-\leavevmode\hypertarget{ref-sedivy2003pragmatic}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sedivy2003pragmatic}{}}%
 Sedivy, Julie C.
@@
 
-\leavevmode\hypertarget{ref-silberzahn2018many}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
 Silberzahn, Raphael, Eric Luis Uhlmann, Daniel P Martin, Pasquale Anselmi, Frederik Aust, Eli Awtrey, Štěpán Bahnı́k, et al.
@@
 
-\leavevmode\hypertarget{ref-simmons2011false}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-simmons2011false}{}}%
 Simmons, Joseph P, Leif D Nelson, and Uri Simonsohn.
@@
 
-\leavevmode\hypertarget{ref-starns2019assessing}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-starns2019assessing}{}}%
 Starns, Jeffrey J., Andrea M.
@@
 
-\leavevmode\hypertarget{ref-sterling1959publication}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sterling1959publication}{}}%
 Sterling, Theodore D.
@@
 
-\leavevmode\hypertarget{ref-sterne2005}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sterne2005}{}}%
 Sterne, Jonathan A.
@@
 
-\leavevmode\hypertarget{ref-sorensen1948}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-summerfield1981articulatory}{}}%
+Summerfield, Quentin. 1981. {``Articulatory Rate and Perceptual Constancy in Phonetic Perception.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 7 (5): 1074.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sorensen1948}{}}%
 Sørensen, Thorlvald.
@@
 
-\leavevmode\hypertarget{ref-stan2020a}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-stan2020a}{}}%
 Team, Stan Development. 2020. {``{RStan}: The {R} Interface to {Stan}.''} \url{http://mc-stan.org/}.
 
-\leavevmode\hypertarget{ref-stan2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-stan2021}{}}%
 ---------. 2021. {``Stan Modeling Language Users Guide and Reference Manual, V2.26.0.''} \url{http://mc-stan.org/}.
 
-\leavevmode\hypertarget{ref-tukey1977exploratory}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tukey1977exploratory}{}}%
 Tukey, John W. 1977. \emph{Exploratory Data Analysis}. Vol. 2. Reading, MA.
 
-\leavevmode\hypertarget{ref-tversky1974judgment}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tversky1974judgment}{}}%
 Tversky, Amos, and Daniel Kahneman. 1974. {``Judgment Under Uncertainty: Heuristics and Biases.''} \emph{Science} 185 (4157): 1124--31.
 
-\leavevmode\hypertarget{ref-heuven2002}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-heuven2002}{}}%
 Van Heuven, Vincent J, Judith Haan, Carlos Gussenhoven, and Natasha Warner.
@@
 
-\leavevmode\hypertarget{ref-van2005speech}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-van2005speech}{}}%
 Van Heuven, Vincent J, and Ellen Van Zanten. 2005. {``Speech Rate as a Secondary Prosodic Characteristic of Polarity Questions in Three Languages.''} \emph{Speech Communication} 47 (1-2): 87--99.
 
-\leavevmode\hypertarget{ref-wagenmakers2012agenda}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wagenmakers2012agenda}{}}%
 Wagenmakers, Eric-Jan, Ruud Wetzels, Denny Borsboom, Han LJ van der Maas, and Rogier A Kievit.
@@
 
-\leavevmode\hypertarget{ref-westerbeek2015stored}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-westerbeek2015stored}{}}%
 Westerbeek, Hans, Ruud Koolen, and Alfons Maes. 2015. {``Stored Object Knowledge and the Production of Referring Expressions: The Case of Color Typicality.''} \emph{Frontiers in Psychology} 6: 935.
 
-\leavevmode\hypertarget{ref-white2009}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-white2009}{}}%
 White, Laurence, Elinor Payne, and Sven L.
@@
 
-\leavevmode\hypertarget{ref-wicherts2006poor}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wicherts2006poor}{}}%
 Wicherts, Jelte M., Denny Borsboom, Judith Kats, and Dylan Molenaar. 2006. {``The Poor Availability of Psychological Research Data for Reanalysis.''} \emph{American Psychologist} 61 (7): 726.
 
-\leavevmode\hypertarget{ref-wicherts2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-wicherts2016}{}}%
 Wicherts, Jelte M., Coosje L.
@@
 
-\leavevmode\hypertarget{ref-winter2014spoken}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-winter2014spoken}{}}%
 Winter, Bodo. 2014. {``Spoken Language Achieves Robustness and Evolvability by Exploiting Degeneracy and Neutrality.''} \emph{BioEssays} 36 (10): 960--67.

### 2021-03-18 RR_manuscript/Draft_RR.Rmd
:bug: - remove deviations model

@@
 <!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
-We will fit two Bayesian regression models, one for (a) and one for (b).
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.
 
-**Analytical factors**. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
+**Analytical predictors**. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
 
-**Demographic factors**. We will include the following demographic factors about the teams:
+**Researcher-related factors**. We will include the following predictors about the teams:
 
@@
 
-**Models specification**. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
-The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
-The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
-The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance $Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})$.
+**Model specification**. The model will be fitted as measurement-error models, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model will be the standardized effect sizes.
 

### 2021-03-18 scripts/r/simulations/simulations.Rmd
:arrow_up: - update renv lock
:bug: - remove deviations model

@@
 twin <- sample(c("segment", "syllable", "word", "phrase"), n, T)
-# was data excluded?
-excl <- rbinom(n, 1, 0.5)
 # reviewers' ratings
@@
   twin,
-  excl,
   rating,
@@
 
-# Factors analysis model
+# Analytic and researchers' predictors model
+
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.
 
@@
 \mu_{\alpha_{t[i]}}       & = \beta + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
- & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i + \upsilon_e\cdot excl_i \\
+ & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i \\
  & \qquad + \upsilon_r\cdot rat_i + \\
@@
 
-```{r factors-priors}
-factors_priors <- c(
+```{r preds-priors}
+preds_priors <- c(
   prior(normal(0, 1), class = Intercept),
@@
 
-```{r factors-bm}
-factors_bm <- brm(
+```{r predictors-bm}
+predictors_bm <- brm(
   eta | se(se) ~
@@
   data = eta_tbl,
-  prior = factors_priors,
+  prior = preds_priors,
   chain = 4,
@@
   cores = 4,
-  file = "./models/sim/factors_bm"
+  file = "./models/sim/predictors_bm"
 )

### 2021-03-18 scripts/r/simulations/simulations.Rmd
:bug: - create sim dir
:bug: - use recursive when creating dir
:bug: - remove data excl predictor

@@
 my_seed <- 115116106
+```
+
+```{r include=FALSE}
+dir.create("./models/sim/", F, recursive = T)
 ```
@@
     twin +
-    excl +
     me(rating_mean, rating_sd) +

### 2021-03-18 RR_manuscript/Draft_RR.tex
:memo: - render RR

@@
 
-As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
-We will fit two Bayesian regression models, one for (a) and one for (b).
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.
 
-\textbf{Analytical factors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
+\textbf{Analytical predictors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
 
@@
 
-\textbf{Demographic factors}. We will include the following demographic factors about the teams:
+\textbf{Researcher-related factors}. We will include the following predictors about the teams:
 
@@
 
-\textbf{Models specification}. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
-The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
-The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
-The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance \(Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})\).
+\textbf{Model specification}. The model will be fitted as measurement-error models, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model will be the standardized effect sizes.
 

### 2021-03-19 RR_manuscript/Draft_RR.Rmd
:memo: - analytical > analytic; remove todo tex package

@@
 ---
-title             : "Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
+title             : "Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
 shorttitle        : "Many analysts - one speech data set"
@@
   - \usepackage{cleveref}
-  - \setlength{\marginparwidth}{2cm}
-  - \usepackage[todonotes={textsize=tiny}]{changes}
-  - \definechangesauthor[name={Stefano Coretta}, color=red]{SC}
-  - \definechangesauthor[name={Timo Röttger}, color=blue]{TR}
-  - \definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 ---
@@
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
-Along the way, different methodological and analytical choices need to be made, all of which may influence the final interpretation of the data.
+Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
 These researcher degrees of freedom are both a blessing and a curse.
@@
 Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
-In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
@@
 
-Analytical flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
+Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
 @wicherts2016, Charles et al.
-2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
+2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
 <!-- TODO: add REFS Charles et al. 2019 -->
@@
 In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
-Analytical approaches and consequently the results varied widely between teams.
+Analytic approaches and consequently the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
-Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
+Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
@@
 
-Several other recent studies corroborated this analytical flexibility across different disciplines.
+Several other recent studies corroborated this analytic flexibility across different disciplines.
 Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
@@
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
-(accepted) on analytical flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
+(accepted) on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 
-While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to inferential statistics or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
@@
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
-Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.
+Taken together, these aspects alone exponentially increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
 
 In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
-This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
+This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytic flexibility.
 The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytical decision.
+Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytic decision.
 Take for example the following sentence in (1).
@@
 
-When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
-This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
+When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
+This plurality of analytic paths is illustrated in Figure \@ref(fig:forkingPaths).
 Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 <!-- FIGURE -->
-(ref:forkingPaths) Illustrations of the analytical flexibility associated with acoustic analyses.
+(ref:forkingPaths) Illustrations of the analytic flexibility associated with acoustic analyses.
 (A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
@@
 These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
-In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytical flexibility when choosing measures and operationalizing underlying theoretical constructs.
+In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we will provide analytical teams with an experimentally elicited speech production data set.
+To assess the variability in data analysis pipelines across independent researchers, we will provide analytic teams with an experimentally elicited speech production data set.
 The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
@@
 
-As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
+As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
-The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
+The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
 We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
@@
 <!-- TODO: project timeline -->
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take XX months (Table X).
 The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
@@
 Following Parker et al.
-\highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
+[ECO RR], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
 the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
@@
 
-<!-- TODO: add LINK to analytical survey -->
-Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
+<!-- TODO: add LINK to analytic survey -->
+Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 
-### Meta-analytical estimation {#s:meta-est}
+### Meta-analytic estimation {#s:meta-est}
 
-<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model -->
+<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytic model -->
 We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
@@
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
-<!-- TODO: add LINK to code of the meta-analytical model -->
+<!-- TODO: add LINK to code of the meta-analytic model -->
 The code used to run the model can be found here: INSERT LINK.
@@
 
-<!-- NOTE: I keep changing meta-analytical to meta-analytic (the -cal sounds weird to me).
+<!-- NOTE: I keep changing meta-analytic to meta-analytic (the -cal sounds weird to me).
 My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs.
 500k) -->
-<!-- NOTE: (SC) I tend to use analytical to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent.
+<!-- NOTE: (SC) I tend to use analytic to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent.
 -->
@@
 ```{r funnel-calc, include=FALSE, eval=FALSE}
-# meta_bm is the meta-analytical Bayesian regression model
+# meta_bm is the meta-analytic Bayesian regression model
 meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
@@
 
-### Analytical and demographic predictors affecting effect sizes {#ana-factors}
+### Analytic and demographic predictors affecting effect sizes {#ana-factors}
 <!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.
 
-**Analytical predictors**. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
+**Analytic predictors**. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
 

### 2021-03-19 RR_manuscript/Draft_RR.tex
:memo: - analytical > analytic; remove todo tex package

@@
 \hypersetup{
-  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
+  pdftitle={Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
   pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
@@
 \usepackage{cleveref}
-\setlength{\marginparwidth}{2cm}
-\usepackage[todonotes={textsize=tiny}]{changes}
-\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
-\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
-\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
 \ifLuaTeX
@@
 
-\title{Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
+\title{Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
 \author{true \and true \and true \and true}
@@
 Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
-In conjunction with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
+In conjunction with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured (Roettger 2019).
@@
 
-Analytical flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
-2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields Roettger (2019), notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
+Analytic flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
+2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields Roettger (2019), notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
@@
 In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
-Analytical approaches and consequently the results varied widely between teams.
+Analytic approaches and consequently the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
-Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
+Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
@@
 
-Several other recent studies corroborated this analytical flexibility across different disciplines.
+Several other recent studies corroborated this analytic flexibility across different disciplines.
 Both Dutilh et al. (2019) ad Starns et al. (2019) investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytical flexibility in ecology and Botvinik-Nezer et al.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytic flexibility in ecology and Botvinik-Nezer et al.
 2020a on neuroimaging data).
@@
 
-When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially.
-This plurality of analytical paths is illustrated in Figure \ref{fig:forkingPaths}.
+When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
+This plurality of analytic paths is illustrated in Figure \ref{fig:forkingPaths}.
 Even if we have decided to compare fundamental frequency (f0) of only the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytical flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytic flexibility associated with acoustic analyses.
 (A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
@@
 These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. 2016).
-In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytical flexibility when choosing measures and operationalizing underlying theoretical constructs.
+In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we will provide analytical teams with an experimentally elicited speech production data set.
+To assess the variability in data analysis pipelines across independent researchers, we will provide analytic teams with an experimentally elicited speech production data set.
 The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
@@
 
-As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
+As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
-The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
+The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
 We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
@@
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take \highlight{XX months (Table X).}
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take XX months (Table X).
 The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
@@
 
-Following Parker et al.~\highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
+Following Parker et al.~{[}ECO RR{]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
 In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
@@
 
-Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 \hypertarget{s:meta-est}{%
-\subsubsection{Meta-analytical estimation}\label{s:meta-est}}
+\subsubsection{Meta-analytic estimation}\label{s:meta-est}}
 
@@
 \hypertarget{ana-factors}{%
-\subsubsection{Analytical and demographic predictors affecting effect sizes}\label{ana-factors}}
+\subsubsection{Analytic and demographic predictors affecting effect sizes}\label{ana-factors}}
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.
 
-\textbf{Analytical predictors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:
+\textbf{Analytic predictors}. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
 

### 2021-03-19 RR_manuscript/Draft_RR.Rmd
:memo: edits to RR draft

@@
 In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
+
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
-These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
+Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
+@wicherts2016; @charles2019; @roettger2019researcher].
+This notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
+
+Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
+These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalisability (dependent on the chosen analysis).
+Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
@@
 
-Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
-@wicherts2016, Charles et al.
-2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
-<!-- TODO: add REFS Charles et al. 2019 -->
-Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-<!-- NOTE: (?) I think this should be part of the previous paragraph. -->
-
 ## Crowdsourcing alternative analyses
 
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
 In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
@@
 
-## The data set: The acoustic properties of atypical modifiers
+## The data set: The acoustic properties of atypical modifiers {#s:dataset}
 
@@
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, we recorded thirty native German speakers interacting with a confederate (one of the experimenters) in a referential game.
+To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
 The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
+\Cref{f:procedural-timeline}
 The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
@@
 
-<!-- TODO: add experiment procedure figure -->
+<!-- FIGURE -->
+(ref:procedural) Experimental procedure timeline.
+
+```{r 'procedural', echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
+knitr::include_graphics(here::here("figs", "procedure_plot.png"))
+```
+<!-- END: FIGURE -->
 
@@
 
-<!-- TODO: double check with BN if sample size justification is correct -->
-
 ## Phase 2: Primary Data Analyses
 
-<!-- TODO: add LINK to demo survey -->
+<!-- TODO: add LINK to survey -->
 The analysis teams will register and answer a demographic and expertise survey (LINK).
 The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We will then provide teams with the acoustic data set and request that they answer the following research question:
-<!-- TODO: LINK dataset here -->
-
-Do speakers acoustically modify utterances to signal atypical word combinations?
+We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.^[See <https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe>.
+Due to storage caps on the OSF, we will make the audio files available on <https://eudat.eu/catalogue/B2SHARE> in due course.]
 

### 2021-03-19 RR_manuscript/Draft_RR.tex
:memo: edits to RR draft

@@
 In conjunction with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
+
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured (Roettger 2019).
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies (e.g., Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
-These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
+Analytic flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
+2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields (e.g.
+Wicherts et al.
+2016; Charles et al.
+2019; Roettger 2019).
+This notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
+
+Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies (e.g., Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
+These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalisability (dependent on the chosen analysis).
+Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
@@
 
-Analytic flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
-2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields Roettger (2019), notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
-Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-
 \hypertarget{crowdsourcing-alternative-analyses}{%
@@
 
+Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
 In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
@@
 
-\hypertarget{the-data-set-the-acoustic-properties-of-atypical-modifiers}{%
-\subsection{The data set: The acoustic properties of atypical modifiers}\label{the-data-set-the-acoustic-properties-of-atypical-modifiers}}
+\hypertarget{s:dataset}{%
+\subsection{The data set: The acoustic properties of atypical modifiers}\label{s:dataset}}
 
@@
 Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon,' \emph{Rote Gurke} `red cucumber,' \emph{Rote Socken} `red socks').
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure timeline.}\label{fig:procedural}
+\end{figure}
 
@@
 The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We will then provide teams with the acoustic data set and request that they answer the following research question:
-
-Do speakers acoustically modify utterances to signal atypical word combinations?
+We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{See \url{https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe}.
+Due to storage caps on the OSF, we will make the audio files available on \url{https://eudat.eu/catalogue/B2SHARE} in due course.}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-charles2019}{}}%
+Charles, Sarah J., James E.
+Bartlett, Kyle J.
+Messick, Thomas J.
+Coleman, and Alex Uzdavines.
+2019.
+{``Researcher Degrees of Freedom in the Psychology of Religion.''} \emph{The International Journal for the Psychology of Religion} 29 (4): 230--45.
+
 \leavevmode\vadjust pre{\hypertarget{ref-open2015estimating}{}}%

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
:sparkles: - update links

@@
 
-<!-- TODO: add LINK to survey -->
-The analysis teams will register and answer a demographic and expertise survey (LINK).
-The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+The analysis teams will register and answer a demographic and expertise questionnaire (`intake_form.pdf`).^[PDF versions of all the questionnaires mentioned in this paper are available at <https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires>.]
+The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
 We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
@@
 
-<!-- TODO: add LINK to analytic survey -->
-Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (`analytical_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
-Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts.
+Each peer reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
 Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
-<!-- TODO: add LINK to peer review survey -->
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2021-03-24 RR_manuscript/Draft_RR.tex
:sparkles: - update links

@@
 
-The analysis teams will register and answer a demographic and expertise survey (LINK).
-The survey collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+The analysis teams will register and answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{PDF versions of all the questionnaires mentioned in this paper are available at \url{https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires}.}
+The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
 We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
@@
 
-Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytical\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
+Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
added parker et al. bibtex

@@
 Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-<!-- TODO: Parker et al. (ECO) REFS -->
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al.
-(accepted) on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
+
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 All analysts will sign a consent (ethics) document (LINK).
-<!-- TODO: add information about what this consent form does -->
 
-<!-- TODO: Parker et al. (ECO) REFS -->
 Following Parker et al.
-[ECO RR], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
+[@Parker2020], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
 the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
:bento: - update osf data; edit RR

--- 2021-03-24 RR_manuscript/Draft_RR.Rmd
@@
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-<!-- TODO: add REFS about variable conclusions from reliable data -->
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
@@
 And the garden of forking paths does not stop here.
-<!-- TODO: add examples of pitch tracking options -->
 Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
@@
 
-<!-- TODO: ask people if they have ever heard of these papers -->
-
 To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
@@
 The participant and the experimenter could not see each other nor each others' screens.
-<!-- TODO: add ref to experiment procedure figure in (see XXX) -->
 After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.

### 2021-03-24 osf/data/README.Rmd
:bento: - update osf data; edit RR

@@
 - The `norming/` directory holds the files of the norming study.
+  - `images/`: re-colored images for the norming study.
+  - `ratings/`: rating results of the norming study.
 - The `production/` directory contains two subdirectories:
@@
 
-See the `README.md` files of each individual directory for more information about the contents.
-
-```{r retrieve}
-# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
-osf_repo <- osf_retrieve_node("3bmcp")
-# Repo components
-osf_comps <- osf_ls_nodes(osf_repo)
-# Data component
-data_comp <- osf_comps %>% filter(name == "Data")
-```
-
-```{r data_files, include=TRUE}
-osf_ls_files(data_comp) %>%
-  select(name) %>%
-  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
-  arrange(name)
-```
+See the `README.md` files in each directory for more information about the contents.

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
minor fix

--- 2021-03-24 RR_manuscript/Draft_RR.Rmd
@@
 <!-- FIGURE -->
-(ref:procedural) Experimental procedure timeline.
+(ref:procedural) Experimental procedure - The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
+After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
+Reading the orthographic instructions out loud, the speaker gives the confederate verbal instructions onto which referent they should drag the cube (c).
+The confederate, in turn, drags the black cube onto the target referent (d).
+Both the arrow and the orthographic instruction disappear from the speaker's screen and a new referent is indicated by an arrow on the same display alongside a new orthographic instruction (e).
+The speaker gives the confederate verbal instructions (f) which the confederate follows by dragging the cube onto the next referent (g).
 

### 2021-03-24 osf/data/production/README.Rmd

---
title: "Production study"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

This directory contains the files of the production study, which was designed to elicit spoken utterances that contain referential phrases like *blue banana*.

# Overview

There are 2 subdirectories:

- `audio/` contains `.wav` and `.TextGrid` files from the production experiment.
- `trial-lists/` contains `.csv` files with info on the trials from the production experiment.

# TextGrids

# Trial lists

Trial lists contain the following columns:

- `speaker`: The speaker id.
- `trial`: The position of the trial within the experiment (numeric).
- `condition`: The focus condition (`NF` = noun focus, `AF` = adjective focus, `ANF` = double focus on adjective and noun; `NF`s are the critical conditions).
- `typicality`: Typicality category (`typical`, `medium`, `atypical`; `NA` for AF and ANF).
- `target_object`: Target object.
- `target_colour`: Colour of the target object.
- `competitor_name`: Competitor object.
- `competitor_colour`: Colour of the competitor object.
- `distractror1_name`: Distractor-1 object.
- `distractror1_colour`: Colour of the distractor-1 object.
- `distractror2_name`: Distractor-2 object.
- `distractror2_colour`: Colour of the distractor-2 object.
- `object_en`: The English translation of `target_object`.
- `colour_en`: The English translation of `target_colour`.
- `typ_sd`: The standard deviation of the typicality ratings .
- `typ_median`: The median typicality rating.
- `typ_median`: The median typicality rating.

### 2021-03-25 RR_manuscript/Draft_RR.Rmd
:memo: - edits to RR

@@
 In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
-<!-- TODO: LATER include number of teams when known -->
+<!-- TODOLATER: include number of teams when known -->
 Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
@@
 This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
-<!-- NOTE: (?) why not "phonological contrast"?
--->
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 And the garden of forking paths does not stop here.
-Figure \@ref(fig:forkingPaths), illustrates a specific option to automatically calculate f0.
-Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
-<!-- NOTE: (JVC) Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->
+Figure \@ref(fig:forkingPaths), illustrates one specific procedure to automatically calculate f0.
+However, another options would be to filter the audio signal, to smooth the extracted f0 signal, to remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
 
@@
 
-These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.
+These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
@@
 *greem tomato* ), or atypical (e.g.
-*yellow cherry*), as established by a norming study that was conducted prior to the production experiment (see Appendix XXX for details).
-
-<!-- TODO: Appendix and stuff -->
+*yellow cherry*), as established by a norming study that was conducted prior to the production experiment (see HERE^[Temporary link: <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]).
 
@@
 
-<!-- TODO: project timeline -->
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take XX months (Table X).
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
 The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
@@
 
-<!-- TODO: add materials LINK and mailing lists -->
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project [https://many-speech-analyses.github.io](https://many-speech-analyses.github.io) and a short pre-recorded slide show that summarizes the study and research question (LINK).
-<!-- NOTE: same as above, or OSF -->
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (<https://many-speech-analyses.github.io>).
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
@@
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-<!-- TODO: add LINK to informed consent form -->
-All analysts will sign a consent (ethics) document (LINK).
 
@@
 
-The analysis teams will register and answer a demographic and expertise questionnaire (`intake_form.pdf`).^[PDF versions of all the questionnaires mentioned in this paper are available at <https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires>.]
+The analysis teams will register and answer a demographic and expertise questionnaire (`intake_form.pdf`).
+PDF versions of all the questionnaires used in this study are available at LINK^[Temporary link: <https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8>.].
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.^[See <https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe>.
-Due to storage caps on the OSF, we will make the audio files available on <https://eudat.eu/catalogue/B2SHARE> in due course.]
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK^[Temporary link: <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]).
 
@@
 
-<!-- NOTE: (SC) t would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytic model -->
 We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
@@
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
-<!-- TODO: add LINK to code of the meta-analytic model -->
+<!-- TODO: add LINK to code of the meta-analytic model: add to landing page in non-linked page -->
 The code used to run the model can be found here: INSERT LINK.
@@
 The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
-The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \@ref(ana-factors).
+The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \@ref(anares-preds).
 Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 <!-- NOTE: We are gonna keep the funnel plots at least for Stage 1 review, because it is easier to understand how this works. -->
-
-<!-- NOTE: I keep changing meta-analytic to meta-analytic (the -cal sounds weird to me).
-My unscientific google searching shows that people use both, but meta-analytic is much more common (nearly 4 million hits vs.
-500k) -->
-<!-- NOTE: (SC) I tend to use analytic to mean "related to analysis" and "analytic" in opposition to "synthetic" (from their use in logic and linguistics) but I am flex as long as we are consistent.
--->
 
@@
 
-### Analytic and demographic predictors affecting effect sizes {#ana-factors}
-<!-- NOTE: (TR) I think we should use the term predictors. Factors is really ambiguous -->
+### Analytic and researcher-related predictors affecting effect sizes {#anares-preds}
+
 As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.
@@
 - *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
-- *Average peer-review rating* [numeric], as the mean of the peer-review ratings for each analysis.
-<!-- NOTE: We decided to use just the overall rating -->
+- *Average peer-review rating* [numeric], as the mean of the overall peer-review ratings for each analysis.
 
@@
 
-<!-- TODO: explain how the demographic factors will be entered in the factors analysis -->
-
-**Researcher-related factors**. We will include the following predictors about the teams:
+**Researcher-related factors**. We will also include the following predictors:
 
@@
 
-**Model specification**. The model will be fitted as measurement-error models, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model will be the standardized effect sizes.
+Since we will obtain scores for each member in the analytic teams, we will calculate the team mean and standard deviation for each predictor.
+These will be entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
 
-<!-- TODO: add brm info on factors analysis model -->
+**Model specification**. The model will be fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model will be the standardized effect sizes and related standard deviation.
+
 A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
-The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients $\upsilon_n$ of each predictor.
+The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for $i$ and $\upsilon$ we will use a normal distribution with mean 0 and standard deviation 1.
-<!-- TODO: add explanation of me() predictors resp and belf -->
+As the prior for the intercept and the predictors we will use a normal distribution with mean 0 and standard deviation 1.
+The model will be run with the same settings as with the meta-analytic model.
+<!-- TODO: add LINK to code of the predictors model: add to landing page in non-linked page -->
+The code used to run the model can be found here: INSERT LINK.
 
@@
 
+<!-- TODO: add glossary -->
+
 \newpage

### 2021-03-25 RR_manuscript/Draft_RR.tex
:memo: - edits to RR

@@
 Both Dutilh et al. (2019) ad Starns et al. (2019) investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also Parker et al.~(accepted) on analytic flexibility in ecology and Botvinik-Nezer et al.
-2020a on neuroimaging data).
+
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams Botvinik-Nezer et al. (2020a).
 Bastiaansen et al. (2020) crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 And the garden of forking paths does not stop here.
-Figure \ref{fig:forkingPaths}, illustrates a specific option to automatically calculate f0.
-Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+Figure \ref{fig:forkingPaths}, illustrates one specific procedure to automatically calculate f0.
+However, another options would be to filter the audio signal, to smooth the extracted f0 signal, to remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
 
@@
 
-These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
 These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. 2016).
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure timeline.}\label{fig:procedural}
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure - The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
+After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
+Reading the orthographic instructions out loud, the speaker gives the confederate verbal instructions onto which referent they should drag the cube (c).
+The confederate, in turn, drags the black cube onto the target referent (d).
+Both the arrow and the orthographic instruction disappear from the speaker's screen and a new referent is indicated by an arrow on the same display alongside a new orthographic instruction (e).
+The speaker gives the confederate verbal instructions (f) which the confederate follows by dragging the cube onto the next referent (g).}\label{fig:procedural}
 \end{figure}
@@
 The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{greem tomato} ), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment (see Appendix XXX for details).
+The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{greem tomato} ), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment (see HERE\footnote{Temporary link: \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}).
 
@@
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take XX months (Table X).
+We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
 The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
@@
 
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project \url{https://many-speech-analyses.github.io} and a short pre-recorded slide show that summarizes the study and research question (LINK).
+The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (\url{https://many-speech-analyses.github.io}).
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
@@
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-All analysts will sign a consent (ethics) document (LINK).
 
-Following Parker et al.~{[}ECO RR{]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
+Following Parker et al.
+(Parker et al.
+2020), we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
 In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
@@
 
-The analysis teams will register and answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{PDF versions of all the questionnaires mentioned in this paper are available at \url{https://github.com/many-speech-analyses/many_analyses/tree/master/docs/questionnaires}.}
+The analysis teams will register and answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
+PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8}.}.
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{See \url{https://osf.io/rdtx5/?view_only=66989a3bbe034e188846e23f84913ffe}.
-Due to storage caps on the OSF, we will make the audio files available on \url{https://eudat.eu/catalogue/B2SHARE} in due course.}
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}).
 
@@
 The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
-The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \ref{ana-factors}.
+The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \ref{anares-preds}.
 Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 
-\hypertarget{ana-factors}{%
-\subsubsection{Analytic and demographic predictors affecting effect sizes}\label{ana-factors}}
+\hypertarget{anares-preds}{%
+\subsubsection{Analytic and researcher-related predictors affecting effect sizes}\label{anares-preds}}
 
@@
 \item
-  \emph{Average peer-review rating} {[}numeric{]}, as the mean of the peer-review ratings for each analysis.
+  \emph{Average peer-review rating} {[}numeric{]}, as the mean of the overall peer-review ratings for each analysis.
 \end{itemize}
@@
 
-\textbf{Researcher-related factors}. We will include the following predictors about the teams:
+\textbf{Researcher-related factors}. We will also include the following predictors:
 
@@
 
-\textbf{Model specification}. The model will be fitted as measurement-error models, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model will be the standardized effect sizes.
+Since we will obtain scores for each member in the analytic teams, we will calculate the team mean and standard deviation for each predictor.
+These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+
+\textbf{Model specification}. The model will be fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model will be the standardized effect sizes and related standard deviation.
 
 A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
-The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients \(\upsilon_n\) of each predictor.
+The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
 The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for \(i\) and \(\upsilon\) we will use a normal distribution with mean 0 and standard deviation 1.
+As the prior for the intercept and the predictors we will use a normal distribution with mean 0 and standard deviation 1.
+The model will be run with the same settings as with the meta-analytic model.
+The code used to run the model can be found here: INSERT LINK.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Parker2020}{}}%
+Parker, Timothy, Hannah Fraser, Shinichi Nakagawa, Elise Bethany Gould, Simon Griffith, Peter Vesk, and Fiona Fidler.
+2020.
+{``{Same data, different analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology {[}passed peer review and granted in-principle acceptance March 2020{]}}.''} \emph{BMC Biology}.
+\url{https://doi.org/10.6084/m9.figshare.12034833.v1}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%

### 2021-03-25 RR_manuscript/Draft_RR.Rmd
:memo: - edits to RR

@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.
 
-We are closely following the data collection procedure proposed by Parker et al. (Stage 1 in-principle accepted).
+We are closely following the data collection procedure proposed by @Parker2020.
 The project involves the following five phases:
@@
 For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
-Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project will commence upon receiving in-principle acceptance.
+As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate *per se*.
+Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
+Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
 
@@
 If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-
-Following Parker et al.
-[@Parker2020], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e.
-the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
-In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
-We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
-The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:
-
-$$t = \frac{\tau^2}{SE(\tau^2)}$$
-
-Assuming that the underlying distribution of effect sizes is normal [@knight2000], the standard error of $\tau^2$ can be calculated with the following formula:
-
-$$SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}$$
-
-where $n$ is the sample size.
-Given $Pr$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
-Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $Pr$) will be the same regardless of $\tau^2$:
-
-$$t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}$$
-
-In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CrI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
-When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which we consider sufficiently unlikely.
-
-```{r t, eval=FALSE, include=FALSE}
-n = 12
-df = n - 1
-t <- sqrt((df)/2)
-pt(t, df, lower.tail = F) * 2
-```
+Informed consent will be obtained as part of the intake form.
 
@@
 The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
-The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \@ref(anares-preds).
+The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \@ref(anares-preds).
 Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 
-Following Parker et al. (in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
+Following @Parker2020, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
 The SDI is an index typically used in ecology research to compare species composition across sites.

### 2021-03-25 RR_manuscript/Draft_RR.tex
:memo: - edits to RR

@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.
 
-We are closely following the data collection procedure proposed by Parker et al.~(Stage 1 in-principle accepted).
+We are closely following the data collection procedure proposed by Parker et al. (2020).
 The project involves the following five phases:
@@
 For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
-Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).
+Recruitment for this project will commence upon receiving in-principle acceptance.
+As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate \emph{per se}.
+Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
+Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
 
@@
 If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+
 All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-
-Following Parker et al.
-(Parker et al.
-2020), we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{t}}}\), see \Cref{s:meta-est}).
-In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
-We consider a posterior distribution of \(\tau^2\), for which the 95\% credible interval (CrI) does not include 0 as sufficient.
-The probability \(Pr\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistic:
-
-\[t = \frac{\tau^2}{SE(\tau^2)}\]
-
-Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the following formula:
-
-\[SE(\tau^2) = \sqrt{\frac{2\tau^4}{(n-1)}}\]
-
-where \(n\) is the sample size.
-Given \(Pr\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
-Inserting \(SE(\tau^2)\) into the formula for the \emph{t}-statistic shows that, when \(n\) is fixed, \emph{t} (and hence \(Pr\)) will be the same regardless of \(\tau^2\):
-
-\[t = \frac{\tau^2}{SE(\tau^2)} = \frac{\tau^2}{\sqrt{\frac{2\tau^4}{(n-1)}}} = \sqrt{\frac{(n-1)}{2}}\]
-
-In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CrI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
-When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which we consider sufficiently unlikely.
+Informed consent will be obtained as part of the intake form.
 
@@
 The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
-The posterior distribution will further allow us to investigate the effect of a set of analytic and demographic predictors, detailed in Section \ref{anares-preds}.
+The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \ref{anares-preds}.
 Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 
-Following Parker et al.~(in principle accepted), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
+Following Parker et al. (2020), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
 The SDI is an index typically used in ecology research to compare species composition across sites.

### 2021-03-26 RR_manuscript/Draft_RR.Rmd
:construction: - edit RR and sims (WIP)

@@
 As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate *per se*.
-Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
+Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
 Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
 
-We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
+We will simultaneously recruit volunteers to peer-review the analyses conducted by the analysis teams through the same channels.
 Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
@@
 
-We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
+We will investigate the variability in reported effect sizes using Bayesian meta-analytic techniques.
+As the measure of variability, we will take the estimated group-level standard deviation ($\sigma_{\alpha_{\text{t}}}$ below), where group refers to the analytical teams.
+
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
@@
 The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
+We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
@@
 
-Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportionately greater number of bigger or smaller effect sizes than the meta-analytic point estimate of the pooled effect).
-<!-- in case we want to use the median -->
-This will be achieved through inspection of funnel plots [@light1984; for a review see @egger1997; and @sterne2005; for a critique @lau2006].
-In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the *x*-axis and estimated error (i.e. standard deviation) on *y*-axis.
-In absence of bias, the points should be symmetrically distributed around the meta-analytic point estimate of the pooled effect (see Figure \@ref(fig:funnel-plot)).
-A sign of possible bias is when there are more points which are farther from the meta-analytic point estimate on just one side.
-<!-- NOTE: We are gonna keep the funnel plots at least for Stage 1 review, because it is easier to understand how this works. -->
-
-```{r funnel-plot, include=TRUE, fig.cap="Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analytic mean.", fig.dim = c(6, 2)}
-meta_est <- 0
-
-datasets <- map(
-  c(0, 0.1, -0.1),
-  function(.x) {
-    set.seed(101)
-    sd <- runif(100, min = 1, max = 10)
-    est <- rnorm(length(sd), mean = meta_est, sd = 0.1*sd) + .x * sd
-    tibble(est, sd)
-  }
-)
-
-plots <- map(
-  datasets,
-  function(.x) {
-    ggplot(.x, aes(est, sd)) +
-      geom_vline(aes(xintercept = meta_est), linetype = "dashed") +
-      geom_point(colour = "black", size = 1, alpha = 0.5) +
-      scale_y_reverse() +
-      labs(est = element_blank(), sd = element_blank())  +
-      xlim(-3, 3) +
-      theme_minimal()
-  }
-)
-
-plots[[1]] + labs(title = "(a) no bias") +
-  plots[[2]] + labs(title = "(b) positive bias") +
-  plots[[3]] + labs(title = "(c) negative bias")
-```
-
-```{r funnel-calc, include=FALSE, eval=FALSE}
-# meta_bm is the meta-analytic Bayesian regression model
-meta_bm_est <- fixef(meta_bm)["Intercept","Estimate"]
-meta_bm_q2.5 <- fixef(meta_bm)["Intercept","Q2.5"]
-meta_bm_q97.5 <- fixef(meta_bm)["Intercept","Q97.5"]
-
-# estimated_tbl contains the standardized effect sizes
-se_range <- seq(0, max(estimated_tbl$Est.Error), by = 0.001)
-
-ci <- tibble(
-  x_seq = se_range,
-  ci_lo = meta_ln_bm_est - 1.96 * se_range,
-  ci_up = meta_ln_bm_est + 1.96 * se_range
-)
-
-estimated_tbl %>%
-  ggplot(aes(Estimate, Est.Error)) +
-  geom_line(aes(y = x_seq, x = ci_up), data = ci) +
-  geom_line(aes(y = x_seq, x = ci_lo), data = ci) +
-  geom_vline(aes(xintercept = 0), colour = "grey") +
-  geom_vline(aes(xintercept = meta_ln_bm_est)) +
-  annotate(
-    "rect",
-    ymin = -Inf, ymax = Inf,
-    xmin = meta_bm_q2.5, xmax = meta_bm_q97.5,
-    alpha = 0.5, fill = "#a6cee3") +
-  geom_point(size = 3) +
-  scale_y_reverse()
-```
-
 ### Analytic and researcher-related predictors affecting effect sizes {#anares-preds}
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of analytic and researcher-related predictors.
 

### 2021-03-26 scripts/r/simulations/simulations.Rmd
:construction: - edit RR and sims (WIP)

--- 2021-03-18 scripts/r/simulations/simulations.Rmd
@@
 my_seed <- 115116106
+```
+
+```{r create-dir, include=FALSE}
+dir.create("./models/sim/", F, recursive = T)
 ```
@@
   pop_sdi = sdi_mean(pop_pred),
-  group_sdi = sdi_mean(group_pred),
   phoc_n,
@@
 
-**See paper for more details.**
+**See paper for details.**
 
@@
 The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\alpha_{\text{t}[i]}$ ($HalfCauchy(0, 1)$).
+We will use regularizing weakly-informative priors for the intercept  ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
 
@@
 
-- A $Normal(0, 1)$ distribution for the prior of the intercept.
-- A $HalfCauchy(0, 1)$ distribution for the prior of the teams' intercept standard deviation.
+- A $Normal(0, 1)$ distribution for the prior of the intercept $\alpha$.
+- A $HalfCauchy(0, 1)$ distribution for the prior of the teams' intercept standard deviation $\sigma_{\alpha_{\text{t}}}$.
+
+The following graph illustrates the density function of $HalfCauchy(0, 1)$.
+The long tail ensures that values of $\sigma_{\alpha_{\text{t}}}$ greater than 5 be possible but less probable.
+This is desirable since the effect sizes are standardized (i.e. they should in principle be within a [-3, +3] range).
 
@@
     title = "HalfCauchy(0, 1)",
-    x = "teams' intercept standard deviation"
+    x = "Teams' intercept standard deviation"
   )
@@
 
-Prior predictive checks are run to assess the goodness of the prior specification before model fitting.
+We run prior predictive checks to assess the goodness of the prior specification before model fitting.
 
@@
 
-Let's plot the prior probability distributions of the intercept and the standard deviation.
+We can now inspect the prior probability distributions of the intercept and the standard deviation.
 
@@
 
-```{r meta-bm-summary}
+```{r meta-bm-summary, cache=TRUE}
 meta_bm
@@
 
-# Analytic and researchers' predictors model
+The degree of variability among the team's reported effects is within the range [0.41, 1.14] in SD units at 95% probability.
+
+# Analytic and researcher-related predictors model
 
@@
 \alpha_{\text{t}[i]}      & \sim \text{Normal}(\mu_{\alpha_{t[i]}}, \sigma_i) \\
-\mu_{\alpha_{t[i]}}       & = \beta + \upsilon_u\cdot uniq_i + \upsilon_c\cdot cons_i + \upsilon_p\cdot phoc_i + \upsilon_m\cdot modn_i \\
- & \qquad + \upsilon_d\cdot mdim_i + \upsilon_w\cdot twin_i \\
- & \qquad + \upsilon_r\cdot rat_i + \\
- & \qquad + \upsilon_{xp}\cdot rexp_i + \upsilon_{be}\cdot belf_i  \\
+\mu_{\alpha_{t[i]}}       & = \beta + \upsilon_u\cdot uniqueness_i + \upsilon_c\cdot conservativeness_i \\
+ & \qquad + \upsilon_p\cdot posthoc_i + \upsilon_m\cdot numModels_i \\
+ & \qquad + \upsilon_d\cdot mearuredDimension_i + \upsilon_w\cdot timeWindow_i \\
+ & \qquad + \upsilon_r\cdot PRrating_i + \\
+ & \qquad + \upsilon_{xp}\cdot resExpirience_i + \upsilon_{be}\cdot priorBelief_i  \\
 \iota      & \sim \text{Normal}(0, 1) \\
@@
 ## Model priors
+
+Weakly-informative regularising priors.
 
@@
   chain = 4,
-  iter = 4000,
-  control = list(max_treedepth = 15),
+  iter = 8000,
+  control = list(adapt_delta = 0.9999, max_treedepth = 15),
   seed = my_seed,

### 2021-03-26 RR_manuscript/Draft_RR.tex
:memo: - edits to RR and sims

@@
 As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate \emph{per se}.
-Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, it is not possible for us to establish a well-grounded minimal sample size.
+Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
 Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
 
-We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
+We will simultaneously recruit volunteers to peer-review the analyses conducted by the analysis teams through the same channels.
 Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
@@
 
-We will summarize the variability in reported effect sizes using Bayesian meta-analytic techniques.
+We will investigate the variability in reported effect sizes using Bayesian meta-analytic techniques.
+As the measure of variability, we will take the estimated group-level standard deviation (\(\sigma_{\alpha_{\text{t}}}\) below), where group refers to the analytical teams.
+
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
@@
 The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\alpha_{\text{t}[i]}\) (\(HalfCauchy(0, 1)\)).
+We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
 We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan (Team 2021), and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
@@
 
-Finally, we will assess whether the standardized effect sizes show bias, and, if so, whether the bias is positive or negative (i.e., whether there is a disproportionately greater number of bigger or smaller effect sizes than the meta-analytic point estimate of the pooled effect).
-This will be achieved through inspection of funnel plots (Light and Pillemer 1984; for a review see Egger et al. 1997; and Sterne, Becker, and Egger 2005; for a critique Lau et al. 2006).
-In brief, a funnel plot is a scatter plot of each standardized effect size with effect size on the \emph{x}-axis and estimated error (i.e.~standard deviation) on \emph{y}-axis.
-In absence of bias, the points should be symmetrically distributed around the meta-analytic point estimate of the pooled effect (see Figure \ref{fig:funnel-plot}).
-A sign of possible bias is when there are more points which are farther from the meta-analytic point estimate on just one side.
-
-\begin{figure}
-\centering
-\includegraphics{Draft_RR_files/figure-latex/funnel-plot-1.pdf}
-\caption{\label{fig:funnel-plot}Illustrations of funnel plots showing (a) no bias, (b) positive bias, and (c) negative bias in effect sizes.
-The vertical dashed line represents the meta-analytic mean.}
-\end{figure}
-
 \hypertarget{anares-preds}{%
@@
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytic and researcher-related factors.
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of analytic and researcher-related predictors.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-egger1997}{}}%
-Egger, Matthias, George Davey Smith, Martin Schneider, and Christoph Minder. 1997. {``Bias in Meta-Analysis Detected by a Simple, Graphical Test.''} \emph{British Medical Journal} 315: 629--34.
-
 \leavevmode\vadjust pre{\hypertarget{ref-fischhoff1975hindsight}{}}%
@@
 Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lau2006}{}}%
-Lau, Joseph, John P. A. Ioannidis, Norma Terrin, Christopher H. Schmid, and Ingram Olkin. 2006. {``The Case of the Misleading Funnel Plot.''} \emph{British Medical Journal} 333 (7568): 597--600.
-
-\leavevmode\vadjust pre{\hypertarget{ref-light1984}{}}%
-Light, Richard J., and David B. Pillemer. 1984. \emph{Summing up; the Science of Reviewing Research}. Cambridge, MA (USA) Harvard Univ. Press.
 
@@
 {``Publication Decisions and Their Possible Effects on Inferences Drawn from Tests of Significance--or Vice Versa.''} \emph{Journal of the American Statistical Association} 54 (285): 30--34.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sterne2005}{}}%
-Sterne, Jonathan A.
-C., Betsy Jane Becker, and Matthias Egger.
-2005.
-{``The Funnel Plot.''} In \emph{Publication Bias in Meta-Analysis: Prevention, Assessment and Adjustments}, edited by Hannah R.
-Rothstein, Alexander J.
-Sutton, and Michael Borenstein, 75--98.
-Wiley Online Library.
 

### 2021-03-27 RR_manuscript/Draft_RR.Rmd
:memo: - edit RR draft

@@
 ---
-title             : "Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech."
-shorttitle        : "Many analysts - one speech data set"
-
+title: "Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech"
+runninghead: "Many analysts, one speech data set"
 author:
-  - name          : "First Author"
-    affiliation   : "#"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Second Author"
-    affiliation   : "#"
-    role:
-      - Writing - Review & Editing
-  - name          : "..."
-    affiliation   : "#"
-    role:
-      - Writing - Review & Editing
-  - name          : "Last Author"
-    affiliation   : "#"
-    role:
-      - Writing - Review & Editing
-
-affiliation:
-  - id            : "1"
-    institution   : "#"
-  - id            : "..."
-    institution   : "..."
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
-wordcount         : "X"
-
-bibliography      :
-  - "r-references.bib"
-  - "other_refs.bib"
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+- name: Stefano Coretta*
+  num: 1
+- name: Timo Roettger
+  num: 2
+- name: Joseph V. Casillas
+  num: 3
+address:
+- num: 1
+  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.
+- num: 2
+  org: Department of Applied Things, University B, City B, Country B
+- num: 3
+  org: Very Important Stuff Committee, Institute C, City C, Country C
+corrauth: "Stefano coretta."
+email: "s.coretta@lmu.de"
+abstract: "TBA"
+keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
+classoption:
+  - Review
+  - times
+bibliography: references
+bibliographystyle: sageh
 output:
-  bookdown::pdf_document2:
-    number_sections: true
-    latex_engine: xelatex
-    keep_tex: true
-geometry: margin=4cm
-fontsize: 12pt
-indent: true
-header-includes:
-  - \usepackage{cleveref}
+  bookdown::pdf_book:
+    base_format: rticles::sage_article
+    keep_tex: yes
+    includes:
+      in_header: preamble.tex
 ---
@@
 knitr::opts_knit$set(root.dir = here::here())
-
 library(tidyverse)
@@
 The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
-\Cref{f:procedural-timeline}
+Figure \@ref(fig:procedural) shows the experimental procedure time-line.
 The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
@@
 <!-- FIGURE -->
-(ref:procedural) Experimental procedure - The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
+(ref:procedural) Experimental procedure.
+The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
 After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
@@
 
-As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
+As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".
+For the sake of simplicity, we will refer to single researcher or small teams as \textsc{analysis teams}.
 Recruitment for this project will commence upon receiving in-principle acceptance.
@@
 We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
-To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
+To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
 The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK^[Temporary link: <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]).
@@
 mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.
-dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see \@ref(s:meta-est) for the standardization procedure).
+dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see the next section for the standardization procedure).
 
@@
 
-We will investigate the variability in reported effect sizes using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the estimated group-level standard deviation ($\sigma_{\alpha_{\text{t}}}$ below), where group refers to the analytical teams.
+We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
+As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where group refers to the analytical teams.
 
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
 Factor-level ordering for each categorical variable will mirror that of the original analyses.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
+Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 
-The estimated coefficients of the critical predictors (i.e.
-critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
+The coefficients of the critical predictors (i.e.
+critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models will be used as the \textsc{standardized effect size} ($\eta_i$) of each reported model.
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the \textsc{standardized standard error} ($\text{se}_i$).
 This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
@@
 The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
-The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \@ref(anares-preds).
+The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
 Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of analytic and researcher-related predictors.
+As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
 
@@
 <!-- NOTE: We dropped data exclusion -->
-- *Measure of uniqueness* [numeric] of individual analyses for the set of predictors in each model ($uniq_i$).
-- *Measure of conservativeness* [numeric] of the model specification, as the number of random/group-level effects included ($cons_i$).
-- *Number of post-hoc changes to the acoustic measurements* [numeric] the teams will report to have carried out ($phoc_i$).
-- *Number of models* [numeric] the teams will report to have run ($modn_i$).
-- *Major dimension* [categorical] that has been measured to answer the research question ($mdim_i$).
-- *Temporal window* [categorical] that the measurement is taken over ($twin_i$).
-- *Average peer-review rating* [numeric], as the mean of the overall peer-review ratings for each analysis.
+- *Measure of uniqueness* of individual analyses for the set of predictors in each model [numeric].
+- *Measure of conservativeness* of the model specification, as the number of random/group-level effects included [numeric].
+- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out [numeric].
+- *Number of models* the teams will report to have run [numeric].
+- *Major dimension* that has been measured to answer the research question [categorical].
+- *Temporal window* that the measurement is taken over [categorical].
+- *Average peer-review rating*, as the mean of the overall peer-review ratings for each analysis [numeric].
 
@@
 
-- *Research experience* [numeric] as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens ($rexp_i$).
-- *Initial belief* [numeric] in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire ($belf_i$).
+- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens [numeric].
+- *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].
 
@@
 
-\newpage
+\appendix
 
-# References
+# Glossary
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
-\endgroup
+- **Analysis team**: team of analysts or single analyst.
+- **Reported effect sizes**: effect sizes reported by each analysis team.
+- **Standardized model**: Bayesian refit of the team's model.
+- **Standardized effect sizes**: ($\eta_i$) effect sizes returned by the standardised models.
+- **Standardized standard error**: ($\text{se}_i$) standard deviation of the standardized effect sizes.
+- **Bayesian random-effects meta-analysis** and **meta-analytic model**: multilevel intercept-only regression model for meta-analysis.
+- **Meta-analytic group-level standard deviation**: ($\sigma_{\alpha_{\text{t}}}$) group-level standard deviation returned by the meta-analytic model.
+- **Analytic and researcher-related predictors**: predictors used in model XX.

### 2021-03-27 RR_manuscript/Draft_RR.tex
:memo: - edit RR draft

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  12pt,
-]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
-  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=4cm]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
+\documentclass[Review,times,sageh]{sagej}
+
+\usepackage{moreverb,url,natbib, multirow, tabularx}
+\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
+
+% Pandoc citation processing
+
 \usepackage{cleveref}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.}
-\author{true \and true \and true \and true}
-\date{}
+\providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
 \begin{document}
-\maketitle
+
+\title{Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech}
+
+\runninghead{Many analysts, one speech data set}
+
+\author{Stefano Coretta*\affilnum{1}, Timo Roettger\affilnum{2}, Joseph V. Casillas\affilnum{3}}
+
+\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Applied Things, University B, City B, Country B}\\\affilnum{3}{Very Important Stuff Committee, Institute C, City C, Country C}}
+
+\corrauth{Stefano coretta.}
+
+\email{\href{mailto:s.coretta@lmu.de}{\nolinkurl{s.coretta@lmu.de}}}
+
 \begin{abstract}
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+TBA
 \end{abstract}
 
-{
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
+\keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis}
+
+\maketitle
+
 \hypertarget{introduction}{%
@@
 In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
-In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates (e.g., Collaboration 2015; Camerer et al.
-2018) leading to what is now referred to as the \emph{replication crisis}.
+In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates \citep[e.g.,][]{open2015estimating, camerer2018evaluating} leading to what is now referred to as the \emph{replication crisis}.
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
-The latter situation has been referred to as the \emph{inference crisis} (Rotello, Heit, and Dubé 2015; Starns et al.
-2019) and is, among other things, rooted in the inherent flexibility of data analysis (often referred to as researcher degrees of freedom: Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
+The latter situation has been referred to as the \emph{inference crisis} \citep{rotello2015more, starns2019assessing} and is, among other things, rooted in the inherent flexibility of data analysis \citep[often referred to as researcher degrees of freedom:][]{simmons2011false, gelman2014statistical}.
 Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
@@
 
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g., Box 1976; Tukey 1977; De Groot 2014).
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons, Nelson, and Simonsohn 2011).
-Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set (e.g., Silberzahn et al.
-2018; Starns et al.
-2019; Botvinik-Nezer et al.
-2020b).
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis \citep[e.g.,][]{box1976science, tukey1977exploratory, de2014thought}.
+They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted \citep{simmons2011false}.
+Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set \citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik2020variability}.
 These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways (e.g., Tversky and Kahneman 1974), seeing coherent patterns in randomness (Brugger 2001), convincing themselves of the validity of prior expectations ({``I knew it,''} Nickerson 1998), and perceiving events as being plausible in hindsight ({``I knew it all along,''} Fischhoff 1975).
-In conjunction with an academic incentive system that rewards certain discovery processes more than others (Sterling 1959; Koole and Lakens 2012), we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
+Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, seeing coherent patterns in randomness \citep{brugger2001}, convincing themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceiving events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
+In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
 
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured (Roettger 2019).
+This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured \citep{roettger2019researcher}.
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
-Analytic flexibility has been widely discussed from a conceptual point of view (Simmons, Nelson, and Simonsohn 2011; Wagenmakers et al.
-2012; Nosek and Lakens 2014) and in regard to its application in individual scientific fields (e.g.
-Wicherts et al.
-2016; Charles et al.
-2019; Roettger 2019).
+Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}.
 This notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
 
-Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies (e.g., Simmons, Nelson, and Simonsohn 2011; Gelman and Loken 2014).
+Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
 These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalisability (dependent on the chosen analysis).
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility (e.g.
-Miguel et al.
-2014; Klein et al.
-2018) and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare (Wicherts et al.
-2006).
+Despite recent efforts to improve transparency and reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
 
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a collaborative effort, Silberzahn et al. (2018) let twenty-nine independent analysis teams address the same research hypothesis.
+In a collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
 Analytic approaches and consequently the results varied widely between teams.
@@
 Several other recent studies corroborated this analytic flexibility across different disciplines.
-Both Dutilh et al. (2019) ad Starns et al. (2019) investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+Both \citet{dutilh2019} ad \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
 
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams Botvinik-Nezer et al. (2020a).
-Bastiaansen et al. (2020) crowdsourced clinical recommendations based on analyses of an individual patient.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citep[see also][ on analytic flexibility in ecology and \citet{botvinik-nezer2020} on neuroimaging data]{Parker2020}.
+\citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
 Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
@@
 
-For instance, Flake and Fried (2020) discuss the cascading impact that different practices can have on psychometric research.
+For instance, \citet{flake2020} discuss the cascading impact that different practices can have on psychometric research.
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
@@
 Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g.
-Jongman, Wayland, and Wong 2000; Lisker 1986; Summerfield 1981; Winter 2014).
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
-This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
+This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).
+For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) \citep{hawkins2004influence}.
 
 The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) (e.g., Gordon and Roettger 2017).
-Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances (e.g., Ladd 2008).
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
+Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
-The latter can also be expressed by global vs local pitch modulations (Van Heuven et al.
-2002), as well as acoustic information within the temporal or spectral domain (e.g., Van Heuven and Van Zanten 2005).
-Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch (Foulkes and Docherty 2006; Ogden 2004; White, Payne, and Mattys 2009).
+The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
+Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
 
@@
 We could also measure the value or time of the minimum or maximum f0 value.
-We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data (see Gordon and Roettger 2017).
+We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data \citep[see][]{gordon2017acoustic}.
 And the garden of forking paths does not stop here.
@@
 These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis (e.g. Wicherts et al. 2016).
+These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
 In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
@@
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy (Grice 1975).
+Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy \citep{grice1975logic}.
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
@@
 
-Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent (Sedivy 2003; Westerbeek, Koolen, and Maes 2015; Rubio-Fernández 2016), which has been argued to facilitate object identification and making communication between speakers and listeners more efficient (Arts et al.
-2011; Paraboni, Van Deemter, and Masthoff 2007; Rubio-Fernández 2016).
+Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and making communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, Degen et al.
-(2020) showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection (Gatt et al.
-2013), i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
+This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved (e.g., Ladd 2008).
+Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved \citep[e.g.,][]{ladd2008intonational}.
 Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
@@
 The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
-\Cref{f:procedural-timeline}
+Figure \ref{fig:procedural} shows the experimental procedure time-line.
 The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
@@
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
-Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon,' \emph{Rote Gurke} `red cucumber,' \emph{Rote Socken} `red socks').
+Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure - The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
 After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
@@
 
-As outlined in Section \ref{s:operspeech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
+As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
@@
 
-We are closely following the data collection procedure proposed by Parker et al. (2020).
+We are closely following the data collection procedure proposed by \citet{Parker2020}.
 The project involves the following five phases:
@@
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer to single researcher or small teams as ``analysis teams.''
+For the sake of simplicity, we will refer to single researcher or small teams as \textsc{analysis teams}.
 Recruitment for this project will commence upon receiving in-principle acceptance.
@@
 We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
-To do so, they will be given the data generated by the experiment described in \Cref{s:dataset}.
+To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
 The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}).
@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see \ref{s:meta-est} for the standardization procedure).
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see the next section for the standardization procedure).
 
@@
 
-We will investigate the variability in reported effect sizes using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the estimated group-level standard deviation (\(\sigma_{\alpha_{\text{t}}}\) below), where group refers to the analytical teams.
+We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
+As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where group refers to the analytical teams.
 
 Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
 Factor-level ordering for each categorical variable will mirror that of the original analyses.
-Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan (Team 2021), RStan (Team 2020), and brms (Bürkner 2017) in R (R Core Team 2020).
+Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
@@
 
-The estimated coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size (\(\eta_i\)) of each reported model.
+The coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models will be used as the \textsc{standardized effect size} (\(\eta_i\)) of each reported model.
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error (\(\text{se}_i\)) of the effect size.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the \textsc{standardized standard error} (\(\text{se}_i\)).
 This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, we will fit a Bayesian random-effects meta-analysis using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
-The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution (Knight 2000).
+The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution \citep{knight2000}.
 The analysis teams will be entered as a group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
@@
 We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan (Team 2021), and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
+We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
 In case of divergent transitions, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The analysis will be conducted in R (R Core Team 2020) and fit using Stan (Team 2021), RStan (Team 2020), and brms (Bürkner 2017).
+The analysis will be conducted in R \citep{R-base} and fit using Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017}.
 The code used to run the model can be found here: INSERT LINK.
@@
 The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
-The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in Section \ref{anares-preds}.
+The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
 Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
@@
 \item
-  \emph{Measure of uniqueness} {[}numeric{]} of individual analyses for the set of predictors in each model (\(uniq_i\)).
+  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model {[}numeric{]}.
 \item
-  \emph{Measure of conservativeness} {[}numeric{]} of the model specification, as the number of random/group-level effects included (\(cons_i\)).
+  \emph{Measure of conservativeness} of the model specification, as the number of random/group-level effects included {[}numeric{]}.
 \item
-  \emph{Number of post-hoc changes to the acoustic measurements} {[}numeric{]} the teams will report to have carried out (\(phoc_i\)).
+  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out {[}numeric{]}.
 \item
-  \emph{Number of models} {[}numeric{]} the teams will report to have run (\(modn_i\)).
+  \emph{Number of models} the teams will report to have run {[}numeric{]}.
 \item
-  \emph{Major dimension} {[}categorical{]} that has been measured to answer the research question (\(mdim_i\)).
+  \emph{Major dimension} that has been measured to answer the research question {[}categorical{]}.
 \item
-  \emph{Temporal window} {[}categorical{]} that the measurement is taken over (\(twin_i\)).
+  \emph{Temporal window} that the measurement is taken over {[}categorical{]}.
 \item
-  \emph{Average peer-review rating} {[}numeric{]}, as the mean of the overall peer-review ratings for each analysis.
+  \emph{Average peer-review rating}, as the mean of the overall peer-review ratings for each analysis {[}numeric{]}.
 \end{itemize}
 
-Following Parker et al. (2020), the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice 1945; Sørensen 1948).
+Following \citet{Parker2020}, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index \citep[SDI,][]{dice1945, sorensen1948}.
 The SDI is an index typically used in ecology research to compare species composition across sites.
@@
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.
-2020).
+In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
 
@@
 \item
-  \emph{Research experience} {[}numeric{]} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens (\(rexp_i\)).
+  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens {[}numeric{]}.
 \item
-  \emph{Initial belief} {[}numeric{]} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire (\(belf_i\)).
+  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire {[}numeric{]}.
 \end{itemize}
@@
 
-\newpage
+\appendix
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\hypertarget{glossary}{%
+\section{Glossary}\label{glossary}}
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Analysis team}: team of analysts or single analyst.
+\item
+  \textbf{Reported effect sizes}: effect sizes reported by each analysis team.
+\item
+  \textbf{Standardized model}: Bayesian refit of the team's model.
+\item
+  \textbf{Standardized effect sizes}: (\(\eta_i\)) effect sizes returned by the standardised models.
+\item
+  \textbf{Standardized standard error}: (\(\text{se}_i\)) standard deviation of the standardized effect sizes.
+\item
+  \textbf{Bayesian random-effects meta-analysis} and \textbf{meta-analytic model}: multilevel intercept-only regression model for meta-analysis.
+\item
+  \textbf{Meta-analytic group-level standard deviation}: (\(\sigma_{\alpha_{\text{t}}}\)) group-level standard deviation returned by the meta-analytic model.
+\item
+  \textbf{Analytic and researcher-related predictors}: predictors used in model XX.
+\end{itemize}
 
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-arts2011overspecification}{}}%
-Arts, Anja, Alfons Maes, Leo GM Noordman, and Carel Jansen. 2011. {``Overspecification in Written Instruction.''} \emph{Linguistics} 49 (3): 555--74.
-
-\leavevmode\vadjust pre{\hypertarget{ref-baselga2020}{}}%
-Baselga, Andres, David Orme, Sebastien Villeger, Julien De Bortoli, Fabien Leprieur, and Maxime Logez.
-2020.
-{``{b}etapart: Partitioning Beta Diversity into Turnover and Nestedness Components.''} \url{https://CRAN.R-project.org/package=betapart}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bastiaansen2020}{}}%
-Bastiaansen, Jojanneke A., Yoram K.
-Kunkels, Frank J.
-Blaauw, Steven M.
-Boker, Eva Ceulemans, Meng Chen, Sy-Miin Chow, et al.
-2020.
-{``Time to Get Personal?
-The Impact of Researchers Choices on the Selection of Treatment Targets Using the Experience Sampling Methodology.''} \emph{Journal of Psychosomatic Research} 137: 110211.
-
-\leavevmode\vadjust pre{\hypertarget{ref-botvinik-nezer2020}{}}%
-Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F.
-Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
-2020a.
-{``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature} 582 (7810): 84--88.
-
-\leavevmode\vadjust pre{\hypertarget{ref-botvinik2020variability}{}}%
-Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al.
-2020b.
-{``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature}, 1--7.
-
-\leavevmode\vadjust pre{\hypertarget{ref-box1976science}{}}%
-Box, George EP. 1976. {``Science and Statistics.''} \emph{Journal of the American Statistical Association} 71 (356): 791--99.
-
-\leavevmode\vadjust pre{\hypertarget{ref-brugger2001}{}}%
-Brugger, Peter.
-2001.
-{``From Haunted Brain to Haunted Science: A Cognitive Neuroscience View of Paranormal and Pseudoscientific Thought.''} \emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, January, 195--213.
-
-\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
-Bürkner, Paul-Christian.
-2017.
-{``{brms}: An {R} Package for {Bayesian} Multilevel Models Using {Stan}.''} \emph{Journal of Statistical Software} 80 (1): 1--28.
-\url{https://doi.org/10.18637/jss.v080.i01}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-camerer2018evaluating}{}}%
-Camerer, Colin F, Anna Dreber, Felix Holzmeister, Teck-Hua Ho, Jürgen Huber, Magnus Johannesson, Michael Kirchler, et al.
-2018.
-{``Evaluating the Replicability of Social Science Experiments in Nature and Science Between 2010 and 2015.''} \emph{Nature Human Behaviour} 2 (9): 637--44.
-\url{https://doi.org/10.1038/s41562-018-0399-z}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-charles2019}{}}%
-Charles, Sarah J., James E.
-Bartlett, Kyle J.
-Messick, Thomas J.
-Coleman, and Alex Uzdavines.
-2019.
-{``Researcher Degrees of Freedom in the Psychology of Religion.''} \emph{The International Journal for the Psychology of Religion} 29 (4): 230--45.
-
-\leavevmode\vadjust pre{\hypertarget{ref-open2015estimating}{}}%
-Collaboration, Open Science. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-de2014thought}{}}%
-De Groot, Adriaan D. 2014. \emph{Thought and Choice in Chess}. Vol. 4. Walter de Gruyter GmbH \& Co KG.
-
-\leavevmode\vadjust pre{\hypertarget{ref-degen2020redundancy}{}}%
-Degen, Judith, Robert D Hawkins, Caroline Graf, Elisa Kreiss, and Noah D Goodman.
-2020.
-{``When Redundancy Is Useful: A Bayesian Approach to {`Overinformative'} Referring Expressions.''} \emph{Psychological Review}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dice1945}{}}%
-Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dutilh2019}{}}%
-Dutilh, Gilles, Jeffrey Annis, Scott D.
-Brown, Peter Cassey, Nathan J.
-Evans, Raoul Grasman, Guy E.
-Hawkins, et al.
-2019.
-{``The Quality of Response Time Data Inference: A Blinded, Collaborative Assessment of the Validity of Cognitive Models.''} \emph{Psychonomic Bulletin \& Review} 26 (4): 1051--69.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fischhoff1975hindsight}{}}%
-Fischhoff, Baruch.
-1975.
-{``Hindsight Is Not Equal to Foresight: The Effect of Outcome Knowledge on Judgment Under Uncertainty.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 1 (3): 288.
-
-\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
-Flake, Jessica Kay, and Eiko I.
-Fried.
-2020.
-{``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (4): 456--65.
-\url{https://doi.org/10.1177/2515245920952393}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-foulkes2006}{}}%
-Foulkes, Paul, and Gerard Docherty. 2006. {``The Social Life of Phonetics and Phonology.''} \emph{Journal of Phonetics} 34 (4): 409--38.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gatt2013we}{}}%
-Gatt, Albert, Roger PG van Gompel, Kees van Deemter, and Emiel Krahmer. 2013. {``Are We Bayesian Referring Expression Generators.''} In. Cognitive Science Society.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gelman2014statistical}{}}%
-Gelman, Andrew, and Eric Loken.
-2014.
-{``The Statistical Crisis in Science: Data-Dependent Analysis--a" Garden of Forking Paths"--Explains Why Many Statistically Significant Comparisons Don't Hold Up.''} \emph{American Scientist} 102 (6): 460--66.
-
-\leavevmode\vadjust pre{\hypertarget{ref-gordon2017acoustic}{}}%
-Gordon, Matthew, and Timo Roettger. 2017. {``Acoustic Correlates of Word Stress: A Cross-Linguistic Survey.''} \emph{Linguistics Vanguard} 3 (1): 1--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-grice1975logic}{}}%
-Grice, Herbert P. 1975. {``Logic and Conversation.''} In \emph{Speech Acts}, 41--58. Brill.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hawkins2004influence}{}}%
-Hawkins, Sarah, and Noël Nguyen. 2004. {``Influence of Syllable-Coda Voicing on the Acoustic Properties of Syllable-Onset /l/ in {E}nglish.''} \emph{Journal of Phonetics} 32 (2): 199--231.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jongman2000acoustic}{}}%
-Jongman, Allard, Ratree Wayland, and Serena Wong. 2000. {``Acoustic Characteristics of English Fricatives.''} \emph{The Journal of the Acoustical Society of America} 108 (3): 1252--63.
-
-\leavevmode\vadjust pre{\hypertarget{ref-klein2018practical}{}}%
-Klein, Olivier, Tom E Hardwicke, Frederik Aust, Johannes Breuer, Henrik Danielsson, Alicia Hofelich Mohr, Hans IJzerman, et al.
-2018.
-{``A Practical Guide for Transparency in Psychological Science.''} \emph{Collabra: Psychology} 4 (1).
-
-\leavevmode\vadjust pre{\hypertarget{ref-knight2000}{}}%
-Knight, K. 2000. \emph{Mathematical Statistics}. Chapman; Hall, New York.
-
-\leavevmode\vadjust pre{\hypertarget{ref-koole2012rewarding}{}}%
-Koole, Sander L, and Daniël Lakens. 2012. {``Rewarding Replications: A Sure and Simple Way to Improve Psychological Science.''} \emph{Perspectives on Psychological Science} 7 (6): 608--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ladd2008intonational}{}}%
-Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lisker1977rapid}{}}%
-Lisker, Leigh. 1977. {``Rapid Versus Rabid: A Catalogue of Acoustic Features That May Cue the Distinction.''} \emph{The Journal of the Acoustical Society of America} 62 (S1): S77--78.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lisker1986voicing}{}}%
----------. 1986. {``{`Voicing'} in {E}nglish: A Catalogue of Acoustic Features Signaling /b/ Versus /p/ in Trochees.''} \emph{Language and Speech} 29 (1): 3--11.
-
-\leavevmode\vadjust pre{\hypertarget{ref-miguel2014promoting}{}}%
-Miguel, Edward, Colin Camerer, Katherine Casey, Joshua Cohen, Kevin M Esterling, Alan Gerber, Rachel Glennerster, et al.
-2014.
-{``Promoting Transparency in Social Science Research.''} \emph{Science} 343 (6166): 30--31.
-
-\leavevmode\vadjust pre{\hypertarget{ref-nickerson1998confirmation}{}}%
-Nickerson, Raymond S. 1998. {``Confirmation Bias: A Ubiquitous Phenomenon in Many Guises.''} \emph{Review of General Psychology} 2 (2): 175--220.
-
-\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
-Nosek, Brian A, and Daniël Lakens. 2014. {``A Method to Increase the Credibility of Published Results.''} \emph{Social Psychology} 45 (3): 137--41.
-
-\leavevmode\vadjust pre{\hypertarget{ref-ogden2004}{}}%
-Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.
-
-\leavevmode\vadjust pre{\hypertarget{ref-paraboni2007generating}{}}%
-Paraboni, Ivandré, Kees Van Deemter, and Judith Masthoff. 2007. {``Generating Referring Expressions: Making Referents Easy to Identify.''} \emph{Computational Linguistics} 33 (2): 229--54.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Parker2020}{}}%
-Parker, Timothy, Hannah Fraser, Shinichi Nakagawa, Elise Bethany Gould, Simon Griffith, Peter Vesk, and Fiona Fidler.
-2020.
-{``{Same data, different analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology {[}passed peer review and granted in-principle acceptance March 2020{]}}.''} \emph{BMC Biology}.
-\url{https://doi.org/10.6084/m9.figshare.12034833.v1}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. 2020. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-roettger2019researcher}{}}%
-Roettger, Timo B. 2019. {``Researcher Degrees of Freedom in Phonetic Research.''} \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology} 10 (1).
-
-\leavevmode\vadjust pre{\hypertarget{ref-rotello2015more}{}}%
-Rotello, Caren M, Evan Heit, and Chad Dubé.
-2015.
-{``When More Data Steer Us Wrong: {R}eplications with the Wrong Dependent Measure Perpetuate Erroneous Conclusions.''} \emph{Psychonomic Bulletin \& Review} 22 (4): 944--54.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rubio2016redundant}{}}%
-Rubio-Fernández, Paula. 2016. {``How Redundant Are Redundant Color Adjectives? An Efficiency-Based Analysis of Color Overspecification.''} \emph{Frontiers in Psychology} 7: 153.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sedivy2003pragmatic}{}}%
-Sedivy, Julie C.
-2003.
-{``Pragmatic Versus Form-Based Accounts of Referential Contrast: Evidence for Effects of Informativity Expectations.''} \emph{Journal of Psycholinguistic Research} 32 (1): 3--23.
-
-\leavevmode\vadjust pre{\hypertarget{ref-silberzahn2018many}{}}%
-Silberzahn, Raphael, Eric Luis Uhlmann, Daniel P Martin, Pasquale Anselmi, Frederik Aust, Eli Awtrey, Štěpán Bahnı́k, et al.
-2018.
-{``Many Analysts, One Data Set: Making Transparent How Variations in Analytic Choices Affect Results.''} \emph{Advances in Methods and Practices in Psychological Science} 1 (3): 337--56.
-
-\leavevmode\vadjust pre{\hypertarget{ref-simmons2011false}{}}%
-Simmons, Joseph P, Leif D Nelson, and Uri Simonsohn.
-2011.
-{``False-Positive Psychology: Undisclosed Flexibility in Data Collection and Analysis Allows Presenting Anything as Significant.''} \emph{Psychological Science} 22 (11): 1359--66.
-
-\leavevmode\vadjust pre{\hypertarget{ref-starns2019assessing}{}}%
-Starns, Jeffrey J., Andrea M.
-Cataldo, Caren M.
-Rotello, Jeffrey Annis, Andrew Aschenbrenner, Arndt Bröder, Gregory Cox, et al.
-2019.
-{``Assessing Theoretical Conclusions with Blinded Inference to Investigate a Potential Inference Crisis.''} \emph{Advances in Methods and Practices in Psychological Science} 2 (4): 335--49.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sterling1959publication}{}}%
-Sterling, Theodore D.
-1959.
-{``Publication Decisions and Their Possible Effects on Inferences Drawn from Tests of Significance--or Vice Versa.''} \emph{Journal of the American Statistical Association} 54 (285): 30--34.
-
-\leavevmode\vadjust pre{\hypertarget{ref-summerfield1981articulatory}{}}%
-Summerfield, Quentin. 1981. {``Articulatory Rate and Perceptual Constancy in Phonetic Perception.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 7 (5): 1074.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sorensen1948}{}}%
-Sørensen, Thorlvald.
-1948.
-{``A Method of Establishing Groups of Equal Amplitude in Plant Sociology Based on Similarity of Species and Its Application to Analyses of the Vegetation on {D}anish Commons.''} \emph{Kongelige Danske Videnskabernes Selskab} 5 (4): 1--34.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stan2020a}{}}%
-Team, Stan Development. 2020. {``{RStan}: The {R} Interface to {Stan}.''} \url{http://mc-stan.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-stan2021}{}}%
----------. 2021. {``Stan Modeling Language Users Guide and Reference Manual, V2.26.0.''} \url{http://mc-stan.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tukey1977exploratory}{}}%
-Tukey, John W. 1977. \emph{Exploratory Data Analysis}. Vol. 2. Reading, MA.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tversky1974judgment}{}}%
-Tversky, Amos, and Daniel Kahneman. 1974. {``Judgment Under Uncertainty: Heuristics and Biases.''} \emph{Science} 185 (4157): 1124--31.
-
-\leavevmode\vadjust pre{\hypertarget{ref-heuven2002}{}}%
-Van Heuven, Vincent J, Judith Haan, Carlos Gussenhoven, and Natasha Warner.
-2002.
-{``Temporal Distribution of Interrogativity Markers in {D}utch: A Perceptual Study.''} In \emph{Laboratory Phonology 7}, 4:61.
-1.
-Walter de Gruyter.
-
-\leavevmode\vadjust pre{\hypertarget{ref-van2005speech}{}}%
-Van Heuven, Vincent J, and Ellen Van Zanten. 2005. {``Speech Rate as a Secondary Prosodic Characteristic of Polarity Questions in Three Languages.''} \emph{Speech Communication} 47 (1-2): 87--99.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wagenmakers2012agenda}{}}%
-Wagenmakers, Eric-Jan, Ruud Wetzels, Denny Borsboom, Han LJ van der Maas, and Rogier A Kievit.
-2012.
-{``An Agenda for Purely Confirmatory Research.''} \emph{Perspectives on Psychological Science} 7 (6): 632--38.
-
-\leavevmode\vadjust pre{\hypertarget{ref-westerbeek2015stored}{}}%
-Westerbeek, Hans, Ruud Koolen, and Alfons Maes. 2015. {``Stored Object Knowledge and the Production of Referring Expressions: The Case of Color Typicality.''} \emph{Frontiers in Psychology} 6: 935.
-
-\leavevmode\vadjust pre{\hypertarget{ref-white2009}{}}%
-White, Laurence, Elinor Payne, and Sven L.
-Mattys.
-2009.
-{``Rhythmic and Prosodic Contrast in {V}enetan and {S}icilian {I}talian.''} In \emph{Phonetics and Phonology: Interactions and Interrelations}, edited by M.
-Vigario, S.
-Frota, and M.
-J.
-Freitas, 137--58.
-Amsterdam: John Benjamins.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wicherts2006poor}{}}%
-Wicherts, Jelte M., Denny Borsboom, Judith Kats, and Dylan Molenaar. 2006. {``The Poor Availability of Psychological Research Data for Reanalysis.''} \emph{American Psychologist} 61 (7): 726.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wicherts2016}{}}%
-Wicherts, Jelte M., Coosje L.
-S.
-Veldkamp, Hilde E.
-M.
-Augusteijn, Marjan Bakker, Robbie C.
-M.
-van Aert, and Marcel A.
-L.
-M.
-van Assen.
-2016.
-{``Degrees of Freedom in Planning, Running, Analyzing, and Reporting Psychological Studies: A Checklist to Avoid p-Hacking.''} \emph{Frontiers in Psychology} 7.
-\url{https://doi.org/10.3389/fpsyg.2016.01832}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-winter2014spoken}{}}%
-Winter, Bodo. 2014. {``Spoken Language Achieves Robustness and Evolvability by Exploiting Degeneracy and Neutrality.''} \emph{BioEssays} 36 (10): 960--67.
-
-\end{CSLReferences}
-
-\endgroup
+\bibliographystyle{sageh}
+\bibliography{references}
 

### 2021-03-29 RR_manuscript/Draft_RR.Rmd
:memo: - edits to RR (in progress)

@@
   org: Very Important Stuff Committee, Institute C, City C, Country C
-corrauth: "Stefano coretta."
+corrauth: "Stefano Coretta."
 email: "s.coretta@lmu.de"
@@
 
-In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
 <!-- TODOLATER: include number of teams when known -->
-Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
+Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
 <!-- TODO: check tense throughout, should be future tense -->
@@
 
-Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
+Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
-In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
+In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
 
@@
 Several other recent studies corroborated this analytic flexibility across different disciplines.
-Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
+@dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology; and @botvinik-nezer2020 on neuroimaging data].
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
-Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
 
+Decisions about how to measure a theoretical construct related to human behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
 For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
@@
 
-In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
-This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.
+In those disciplines concerned with communication, human behavior sometimes corresponds to multidimensional visual or acoustic signals.
+The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
+The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved in the operationalization and measuring of complex signals.
 
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important and non-trivial analytic decision.
+Thus, choosing how to measure a phenomenon of interest is an important analytic decision.
 Take for example the following sentence in (1).
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word *another* or *meeting* to contrast it with other, more pleasant activities.
+For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with other, more pleasant activities.
 If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word *Zoom*.
@@
 If we decide to compare the speech signal associated with these two intentions, how can we quantify the difference between them?
-Given their physical manifestation (speech), what do we measure and how do we measure it?
+In other words, given their physical manifestation (speech), what do we measure and how do we measure it?
 Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
@@
 The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
-Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
+Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
 
@@
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.
+For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom*.
 
@@
 
-(2a) I can't bear *ANOTHER* meeting on zoom.
+(2a) I can't bear *ANOTHER* meeting on Zoom.
 
@@
 
-Do we compare only the word *another* in (2a) and (2b), or also the word *zoom*?
+Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
 Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
@@
 
-When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
-This plurality of analytic paths is illustrated in Figure \@ref(fig:forkingPaths).
-Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
-For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
-And the garden of forking paths does not stop here.
-Figure \@ref(fig:forkingPaths), illustrates one specific procedure to automatically calculate f0.
-However, another options would be to filter the audio signal, to smooth the extracted f0 signal, to remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
-
 <!-- FIGURE -->
-(ref:forkingPaths) Illustrations of the analytic flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words "another is highlighted by the green box"; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.
+(ref:forkingPaths) Illustration of the analytic flexibility associated with acoustic analyses.
+(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances *I can't bear ANOTHER meeting on Zoom* and *I can't bear another meeting on ZOOM*.
+The green boxes mark the word *another* in both sentences; (C) Spectrogram and f0 track of the word *another*, exemplifying possible operationalizations of differences in f0.
 
@@
 
+When looking at phrase-level temporal domains, the number of alternative analytic pipelines substantially increases.
+Figure \@ref(fig:forkingPaths)A shows a typical example of a decision tree which speech researcher are often confronted with.
+Each of the four analytic decisions in the example have different possible options.
+Here only one particular path has been taken, and a different one would likely produce quite different results.
+Once we have decided to compare fundamental frequency of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
+As Figures \@ref(fig:forkingPaths)B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data in previous work [see @gordon2017acoustic].
+But the journey in the garden of analytic paths goes on.
+Other important operationalization steps could involve filtering the audio signal, smoothing the extracted f0 track, removing values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+
 These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.
 after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
-In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
+These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
+In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we will provide analytic teams with an experimentally elicited speech production data set.
-The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
-In the following, we will shortly introduce the research question of the original study.
+To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.
 
@@
 
-Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
+Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
@@
 This account, however, has mainly focused on content selection [@gatt2013we], i.e.
-whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+whether a certain referential expression is chosen or not, while not taking into consideration the indexical potential of speech.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
-Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
-Intonation marks discourse-relevant referents for being new or given information to guide the listeners’ interpretation of incoming messages.
+Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications [e.g., @ladd2008intonational].
+Most prominently, languages use intonation to signal discourse relationships between referents, among other functions.
+Intonation marks discourse-relevant referents for being new or given information, to guide the listeners’ interpretation of incoming messages.
 Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations [e.g.
-dimitrova2008prosodic; dimitrova2009did].
-Referential expressions such as *blue banana* were produced with greater prosodic prominence than more typical referent such as *yellow banana*.
-If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
-However, the original conclusions of above studies were based on small (N = 10), unjustified sample sizes.
-Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
+@dimitrova2008prosodic; @dimitrova2009did].
+Referential expressions such as *blue banana* were produced with greater prosodic prominence than more typical referents such as *yellow banana*.
+These results are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension.
+However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalisability of the studies' conclusions.
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
-The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
-Figure \@ref(fig:procedural) shows the experimental procedure time-line.
+To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game.
+The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
 The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
 The participant and the experimenter could not see each other nor each others' screens.
-After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+Figure \@ref(fig:procedural) shows the experimental procedure time-line.
+After a familiarization phase, the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participant would read a sentence prompt out loud (*Du sollst den Würfel auf der <COLOR OBJECT> ablegen* 'You have to put the cube on top of the <COLOR OBJECT>') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
-After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der <COLOR OBJECT> ablegen* 'And now, you have to put the cube on top of the <COLOR OBJECT>') instructing the experimenter to move the cube on top of a different object (the *target*).
+The participant would read a sentence prompt out loud (*Du sollst den Würfel auf der COLOR OBJECT ablegen* 'You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
+After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der COLOR OBJECT ablegen* 'And now, you have to put the cube on top of the COLOR OBJECT') instructing the experimenter to move the cube on top of a different object (the *target*).
 The second utterance in the trial was the critical trial for analysis.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differed but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun was discourse-pragmatically focused (the Noun Focus condition, NF).
-If the objects were the same but differed in color (e.g. *yellow banana* vs *blue banana*), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
-If both the color and the object differed (e.g. *yellow banana* vs *blue tomato*), the whole noun phrase was discourse-pragmatically focused (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the narrow focus is on the noun (the Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
+If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
-The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
+Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
 The combinations were either typical (e.g.
 *orange mandarin*), medium typical (e.g.
-*greem tomato* ), or atypical (e.g.
-*yellow cherry*), as established by a norming study that was conducted prior to the production experiment (see HERE^[Temporary link: <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]).
+*green tomato*), or atypical (e.g.
+*yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming study, with a more in-depth description of this production study can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
+Each subject produced 15 critical trials (NF condition).
+Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 ($15 \times 2 \times 30$ participants) spoken utterances.
 
-Each participant responded to 15 critical trials (NF condition).
-Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total 900 ($15 \times 2 \times 30$ participants) spoken utterances.
-All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+For the present study, N analysis teams were given access to the entire data set generated by the production study and were instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+...
 

### 2021-03-29 RR_manuscript/Draft_RR.tex
:memo: - edits to RR (in progress)

@@
 
-\corrauth{Stefano coretta.}
+\corrauth{Stefano Coretta.}
 
@@
 
-In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
-Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
+In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
+Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
 
@@
 
-Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
+Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
 Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, seeing coherent patterns in randomness \citep{brugger2001}, convincing themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceiving events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
-In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a select few.
+In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
 
@@
 Several other recent studies corroborated this analytic flexibility across different disciplines.
-Both \citet{dutilh2019} ad \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citep[see also][ on analytic flexibility in ecology and \citet{botvinik-nezer2020} on neuroimaging data]{Parker2020}.
+\citet{dutilh2019} ad \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citetext{\citealp[see also][ on analytic flexibility in ecology]{Parker2020}; \citealp[and][ on neuroimaging data]{botvinik-nezer2020}}.
 \citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
-Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
 
+Decisions about how to measure a theoretical construct related to human behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
 For instance, \citet{flake2020} discuss the cascading impact that different practices can have on psychometric research.
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-If, for instance, the speaker is exhausted by all their meetings, the speaker might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with other, more pleasant activities.
+For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with other, more pleasant activities.
 If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word \emph{Zoom}.
@@
 The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
-Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
+Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
 
@@
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{zoom}.
+For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{Zoom}.
 
@@
 
-(2a) I can't bear \emph{ANOTHER} meeting on zoom.
+(2a) I can't bear \emph{ANOTHER} meeting on Zoom.
 
@@
 
-Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{zoom}?
+Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{Zoom}?
 Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
@@
 
-When looking at phrase-level temporal domains, the number of possible analytic pipelines increases exponentially.
-This plurality of analytic paths is illustrated in Figure \ref{fig:forkingPaths}.
-Even if we have decided to compare fundamental frequency (f0) of only the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
-For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data \citep[see][]{gordon2017acoustic}.
-And the garden of forking paths does not stop here.
-Figure \ref{fig:forkingPaths}, illustrates one specific procedure to automatically calculate f0.
-However, another options would be to filter the audio signal, to smooth the extracted f0 signal, to remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
-
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustrations of the analytic flexibility associated with acoustic analyses.
-(A) an example of multiple possible and justifiable decisions when comparing two utterances; (B) waveform and fundamental frequency (f0) track of two instances of utterances 2a and 2b.
-The words ``another is highlighted by the green box''; (C) spectrogram and f0 track of the word another, exemplifying different operationalizations of differences in pitch.}\label{fig:forkingPaths}
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
+The green boxes mark the word \emph{another} in both sentences; (C) Spectrogram and f0 track of the word \emph{another}, exemplifying possible operationalizations of differences in f0.}\label{fig:forkingPaths}
 \end{figure}
 
+When looking at phrase-level temporal domains, the number of alternative analytic pipelines substantially increases.
+Figure \ref{fig:forkingPaths}A shows a typical example of a decision tree which speech researcher are often confronted with.
+Each of the four analytic decisions in the example have different possible options.
+Here only one particular path has been taken, and a different one would likely produce quite different results.
+Once we have decided to compare fundamental frequency of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
+As Figures \ref{fig:forkingPaths}B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
+We could also measure the value or time of the minimum or maximum f0 value.
+We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data in previous work \citep[see][]{gordon2017acoustic}.
+But the journey in the garden of analytic paths goes on.
+Other important operationalization steps could involve filtering the audio signal, smoothing the extracted f0 track, removing values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+
 These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
-These myriads of possible decisions are exponentiated by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
-In sum, speech data are complex physical signals that constitutes an as of yet unappreciated amount of analytic flexibility when choosing measures and operationalizing underlying theoretical constructs.
+These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
+In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we will provide analytic teams with an experimentally elicited speech production data set.
-The study aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
-In the following, we will shortly introduce the research question of the original study.
+To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.
 
@@
 
-Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative: Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and making communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
+Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and making communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
 For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~whether a certain referential expression is chosen or not, ignoring the fact that speech communication is much richer.
+This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~whether a certain referential expression is chosen or not, while not taking into consideration the indexical potential of speech.
 
-Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved \citep[e.g.,][]{ladd2008intonational}.
-Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
-Intonation marks discourse-relevant referents for being new or given information to guide the listeners' interpretation of incoming messages.
-Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations {[}e.g.~dimitrova2008prosodic; dimitrova2009did{]}.
-Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referent such as \emph{yellow banana}.
-If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
-However, the original conclusions of above studies were based on small (N = 10), unjustified sample sizes.
-Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions.
+Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications \citep[e.g.,][]{ladd2008intonational}.
+Most prominently, languages use intonation to signal discourse relationships between referents, among other functions.
+Intonation marks discourse-relevant referents for being new or given information, to guide the listeners' interpretation of incoming messages.
+Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
+Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referents such as \emph{yellow banana}.
+These results are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension.
+However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalisability of the studies' conclusions.
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, thirty native German speakers were recorded while interacting with a confederate (one of the experimenters) in a referential game.
-The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
-Figure \ref{fig:procedural} shows the experimental procedure time-line.
+To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game.
+The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
 The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
 The participant and the experimenter could not see each other nor each others' screens.
-After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
+Figure \ref{fig:procedural} shows the experimental procedure time-line.
+After a familiarization phase, the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
@@
 In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der ablegen} `You have to put the cube on top of the ') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
-After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der ablegen} `And now, you have to put the cube on top of the ') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
+The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der COLOR OBJECT ablegen} `You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
+After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der COLOR OBJECT ablegen} `And now, you have to put the cube on top of the COLOR OBJECT') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
 The second utterance in the trial was the critical trial for analysis.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differed but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun was discourse-pragmatically focused (the Noun Focus condition, NF).
-If the objects were the same but differed in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective was discourse-pragmatically focused (the Adjective Focus condition, AF).
-If both the color and the object differed (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the whole noun phrase was discourse-pragmatically focused (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the narrow focus is on the noun (the Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
+If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
-The color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{greem tomato} ), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment (see HERE\footnote{Temporary link: \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}).
+Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
+The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming study, with a more in-depth description of this production study can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
+Each subject produced 15 critical trials (NF condition).
+Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 (\(15 \times 2 \times 30\) participants) spoken utterances.
 
-Each participant responded to 15 critical trials (NF condition).
-Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total 900 (\(15 \times 2 \times 30\) participants) spoken utterances.
-All analysis teams will be given access to the entire data set and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
+For the present study, N analysis teams were given access to the entire data set generated by the production study and were instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
+\ldots{}
 

### 2021-03-29 docs/methods_norm_prod/methods_norm_prod.Rmd
:memo: - edit RR (in prgoress)

@@
 author: ""
-date: "9/17/2020"
 output:
@@
 
-This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the *Many Speech Analyses* project.
+This document describes the methodological details of the norming and the production studies that generated the data your team will analyze for the *Many Speech Analyses* project.
 

### 2021-03-30 RR_manuscript/Draft_RR.Rmd

@@
 To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
-The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
-In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.
+The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.
 
@@
 *green tomato*), or atypical (e.g.
-*yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming study, with a more in-depth description of this production study can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
+*yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming and production studies from the *Prosodic encoding of redundant referring expressions* project, which was given to the analysts with the data set, can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
 Each subject produced 15 critical trials (NF condition).

### 2021-03-30 RR_manuscript/Draft_RR.tex

@@
 To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
-The unpublished study we took the data from aimed at investigating whether speakers acoustically modify utterances to signal unexpected referring expressions.
-In the following section we introduce the research question and the experimental procedure of said study, and we describe the dataset as it was given to the analysts.
+The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
+In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.
 
@@
 Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming study, with a more in-depth description of this production study can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
+The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming and production studies from the \emph{Prosodic encoding of redundant referring expressions} project, which was given to the analysts with the data set, can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
 Each subject produced 15 critical trials (NF condition).

### 2021-03-30 docs/methods_norm_prod/methods_norm_prod.tex

@@
 \usepackage[export]{adjustbox}
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
@@
 \author{}
-\date{\vspace{-2.5em}9/17/2020}
+\date{\vspace{-2.5em}}
 
@@
 
-This document describes the methodological details of the norming study and the production study that generated the data your team will analyze for the \emph{Many Speech Analyses} project.
+This document describes the methodological details of the norming and the production studies that generated the data your team will analyze for the \emph{Many Speech Analyses} project.
 

### 2021-03-30 RR_manuscript/Draft_RR.Rmd
:tada: - finish RR proof-read

@@
   org: Very Important Stuff Committee, Institute C, City C, Country C
-corrauth: "Stefano Coretta."
+corrauth: "Stefano Coretta"
 email: "s.coretta@lmu.de"
@@
 Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
-<!-- TODO: check tense throughout, should be future tense -->
 
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
 
-We are closely following the data collection procedure proposed by @Parker2020.
+In this study, we are follow the data collection procedure proposed by @Parker2020.
 The project involves the following five phases:
@@
 2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
-3. \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
-4. \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
+3. \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
+4. \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
 5. \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
@@
 We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
-The factor most likely to delay our time line is the rate of completion of the original set of analyses by independent analysis teams.
+The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
 
@@
 
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (<https://many-speech-analyses.github.io>).
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer to single researcher or small teams as \textsc{analysis teams}.
+For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.
 Recruitment for this project will commence upon receiving in-principle acceptance.
-As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate *per se*.
-Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
+As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytic estimate of the investigated effect *per se*.
+Given the scarcity of previous meta-analytic studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
 Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
@@
 We will simultaneously recruit volunteers to peer-review the analyses conducted by the analysis teams through the same channels.
-Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
+Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer-reviewer to review a minimum of four analyses.
 If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
@@
 
-The analysis teams will register and answer a demographic and expertise questionnaire (`intake_form.pdf`).
+The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
 PDF versions of all the questionnaires used in this study are available at LINK^[Temporary link: <https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8>.].
@@
 
-Once their analysis is complete, they will answer a structured questionnaire (`analytical_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 
-At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned to analyses from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited).
-Each peer reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
+At a minimum, each analysis will be evaluated by four different reviewers, and each peer-reviewer will be randomly assigned to analyses from at least four analysis teams (the exact number will depend on the number of analysis teams and peer-reviewers recruited).
+Each peer-reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
 Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
@@
 First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
+This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
 The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
@@
 
-Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
 
@@
 We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where group refers to the analytical teams.
+As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/mixed-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
@@
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the \textsc{standardized standard error} ($\text{se}_i$).
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each standardized effect size as the \textsc{standardized standard error} ($\text{se}_i$).
 This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported analyses, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.
 The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
-The analysis teams will be entered as a group-level effect (i.e., random effect, `(1 | team)`).
-The standard errors $\text{se}_i$ will be included as the standard deviation $\sigma_i$ of $\eta_i$ to fit a measurement-error model, as discussed above.
+The analysis teams will be entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
+The standard errors $\text{se}_i$ will be included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
 We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
@@
 The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
-<!-- TODO: add LINK to code of the meta-analytic model: add to landing page in non-linked page -->
-The code used to run the model can be found here: INSERT LINK.
+The code used to run the model can be found at <https://many-speech-analyses.github.io/suppl/simulations.html>.
 
@@
 The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
-Crucially, the posterior distribution of $\sigma_{\alpha_{\text{t}}}$ (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+Crucially, the posterior distribution of the [group-level standard deviation](.smallcaps) $\sigma_{\alpha_{\text{t}}}$ (i.e.
+the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between the teams' analyses on a standardized scale.
 
@@
 The model will be run with the same settings as with the meta-analytic model.
-<!-- TODO: add LINK to code of the predictors model: add to landing page in non-linked page -->
-The code used to run the model can be found here: INSERT LINK.
+The code used to run the model can be found at <https://many-speech-analyses.github.io/suppl/simulations.html>.
 
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).^[Link for peer-review: <https://osf.io/3bmcp/?view_only=4f00dff704d742d493870f9f3d68e432>.]
+Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
-We will also archive copies of our survey instruments from analysts and peer reviewers.
+We will also archive copies of our survey instruments from analysts and peer-reviewers.
 
@@
 Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
-
-<!-- TODO: add glossary -->
 
@@
 - **Bayesian random-effects meta-analysis** and **meta-analytic model**: multilevel intercept-only regression model for meta-analysis.
-- **Meta-analytic group-level standard deviation**: ($\sigma_{\alpha_{\text{t}}}$) group-level standard deviation returned by the meta-analytic model.
-- **Analytic and researcher-related predictors**: predictors used in model XX.
+- **Meta-analytic group-level standard deviation**: ($\sigma_{\alpha_{\text{t}}}$) standard deviation of the group-level effect of team returned by the meta-analytic model.
+- **Analytic and researcher-related predictors**: predictors used in the model that assess the effect of analytic and researcher-related factors on the standardized effects.

### 2021-03-30 RR_manuscript/Draft_RR.tex
:tada: - finish RR proof-read

@@
 
-\corrauth{Stefano Coretta.}
+\corrauth{Stefano Coretta}
 
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and research-related predictors affect the researchers' final results.
+We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
 
-We are closely following the data collection procedure proposed by \citet{Parker2020}.
+In this study, we are follow the data collection procedure proposed by \citet{Parker2020}.
 The project involves the following five phases:
@@
 \item
-  \textsc{Review}: We will ask reviewers to generate peer review ratings of the analyses based on methods (not results).
+  \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
 \item
-  \textsc{Meta-analysis}: We will evaluate the variation among the different analyses.
+  \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
 \item
@@
 
-The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project and a short pre-recorded slide show that summarizes the study and research question (\url{https://many-speech-analyses.github.io}).
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer to single researcher or small teams as \textsc{analysis teams}.
+For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.
 Recruitment for this project will commence upon receiving in-principle acceptance.
-As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytical estimate \emph{per se}.
-Given the scarcity of previous meta-analytical studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
+As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
+Given the scarcity of previous meta-analytic studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
 Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
@@
 
-The analysis teams will register and answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
+The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
 PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8}.}.
@@
 
-Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytical\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
@@
 First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
+This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
 The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
@@
 We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where group refers to the analytical teams.
+As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/mixed-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
@@
 If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the \textsc{standardized standard error} (\(\text{se}_i\)).
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each standardized effect size as the \textsc{standardized standard error} (\(\text{se}_i\)).
 This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported analyses, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
 The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution \citep{knight2000}.
-The analysis teams will be entered as a group-level effect (i.e., random effect, \texttt{(1\ \textbar{}\ team)}).
-The standard errors \(\text{se}_i\) will be included as the standard deviation \(\sigma_i\) of \(\eta_i\) to fit a measurement-error model, as discussed above.
+The analysis teams will be entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
+The standard errors \(\text{se}_i\) will be included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
 We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
@@
 The analysis will be conducted in R \citep{R-base} and fit using Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017}.
-The code used to run the model can be found here: INSERT LINK.
+The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
 
@@
 The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
-Crucially, the posterior distribution of \(\sigma_{\alpha_{\text{t}}}\) (the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between teams on a standardized scale.
+Crucially, the posterior distribution of the \href{.smallcaps}{group-level standard deviation} \(\sigma_{\alpha_{\text{t}}}\) (i.e.~the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between the teams' analyses on a standardized scale.
 
@@
 The model will be run with the same settings as with the meta-analytic model.
-The code used to run the model can be found here: INSERT LINK.
+The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
 
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
-Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer reviewers.
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=4f00dff704d742d493870f9f3d68e432}.}
+Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
-We will also archive copies of our survey instruments from analysts and peer reviewers.
+We will also archive copies of our survey instruments from analysts and peer-reviewers.
 
@@
 \item
-  \textbf{Meta-analytic group-level standard deviation}: (\(\sigma_{\alpha_{\text{t}}}\)) group-level standard deviation returned by the meta-analytic model.
+  \textbf{Meta-analytic group-level standard deviation}: (\(\sigma_{\alpha_{\text{t}}}\)) standard deviation of the group-level effect of team returned by the meta-analytic model.
 \item
-  \textbf{Analytic and researcher-related predictors}: predictors used in model XX.
+  \textbf{Analytic and researcher-related predictors}: predictors used in the model that assess the effect of analytic and researcher-related factors on the standardized effects.
 \end{itemize}

### 2021-03-30 scripts/r/simulations/simulations.Rmd
:tada: - finish RR proof-read

@@
 ---
-title: "Prospective simulation"
+title: "Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech --- Prospective simulations"
 date: "`r Sys.Date()`"
@@
     use_bookdown: yes
-bibliography: "`r here::here('./RR_manuscript/other_refs.bib')`"
+bibliography: "`r here::here('./RR_manuscript/references.bib')`"
 cls: unified-style-sheet-for-linguistics.csl
@@
 
+- `uniqueness_i`: *Measure of uniqueness* of individual analyses for the set of predictors in each model [numeric].
+- `conservativeness_i`: *Measure of conservativeness* of the model specification, as the number of random/group-level effects included [numeric].
+- `posthoc_i`: *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out [numeric].
+- `numModels_i`: *Number of models* the teams will report to have run [numeric].
+- `majorDimension_i`: *Major dimension* that has been measured to answer the research question [categorical].
+- `timeWindow_i`: *Temporal window* that the measurement is taken over [categorical].
+- `PRrating_i`: *Average peer-review rating*, as the mean of the overall peer-review ratings for each analysis [numeric].
+- `resExpirience_i`: *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens [numeric].
+- `initialBelief_i`: *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].
+
 $$
@@
  & \qquad + \upsilon_p\cdot posthoc_i + \upsilon_m\cdot numModels_i \\
- & \qquad + \upsilon_d\cdot mearuredDimension_i + \upsilon_w\cdot timeWindow_i \\
+ & \qquad + \upsilon_d\cdot majorDimension_i + \upsilon_w\cdot timeWindow_i \\
  & \qquad + \upsilon_r\cdot PRrating_i + \\
- & \qquad + \upsilon_{xp}\cdot resExpirience_i + \upsilon_{be}\cdot priorBelief_i  \\
+ & \qquad + \upsilon_{xp}\cdot resExpirience_i + \upsilon_{be}\cdot initialBelief_i  \\
 \iota      & \sim \text{Normal}(0, 1) \\
@@
 
+```{r preds-summary}
+predictors_bm
+```
+
+```{r plot-preds-bm}
+plot(predictors_bm, ask = FALSE)
+```
+
 # References

### 2021-03-30 RR_manuscript/Draft_RR.Rmd
:memo: - add abstract to RR

@@
   num: 1
+- name: Joseph V. Casillas
+  num: 2
 - name: Timo Roettger
-  num: 2
-- name: Joseph V. Casillas
   num: 3
@@
 email: "s.coretta@lmu.de"
-abstract: "TBA"
+abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates (the replication crisis) and variability in the conclusions drawn by different researchers based on the same data (the inference crisis).
+Theses have highlighted the large degree of analytic flexibility of data analysis (the so-called researcher degrees of freedom).
+Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
+The multidimensional nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches and outcomes that derives not only from aspects of statistical modelling but also from decisions regarding how to quantify a particular phenomenon.
+For this study, we gave the same speech dataset to N teams of researchers and asked them to answer the same research question.
+[Results TBA]"
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"

### 2021-03-30 RR_manuscript/Draft_RR.tex
:memo: - add abstract to RR

@@
 
-\author{Stefano Coretta*\affilnum{1}, Timo Roettger\affilnum{2}, Joseph V. Casillas\affilnum{3}}
+\author{Stefano Coretta*\affilnum{1}, Joseph V. Casillas\affilnum{2}, Timo Roettger\affilnum{3}}
 
@@
 \begin{abstract}
-TBA
+Recent efforts to replicate published findings have uncovered surprisingly low success rates (the replication crisis) and variability in the conclusions drawn by different researchers based on the same data (the inference crisis).
+Theses have highlighted the large degree of analytic flexibility of data analysis (the so-called researcher degrees of freedom).
+Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
+The multidimensional nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches and outcomes that derives not only from aspects of statistical modelling but also from decisions regarding how to quantify a particular phenomenon.
+For this study, we gave the same speech dataset to N teams of researchers and asked them to answer the same research question.
+{[}Results TBA{]}
 \end{abstract}

### 2021-03-30 RR_manuscript/Draft_RR.Rmd
edited abstract

@@
 - num: 3
-  org: Very Important Stuff Committee, Institute C, City C, Country C
+  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
 corrauth: "Stefano Coretta"
 email: "s.coretta@lmu.de"
-abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates (the replication crisis) and variability in the conclusions drawn by different researchers based on the same data (the inference crisis).
-Theses have highlighted the large degree of analytic flexibility of data analysis (the so-called researcher degrees of freedom).
+abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
+Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
+Thus, researchers have expressed their concerns that these researcher degrees of freedom might can facilitate bias and can lead to claims that do not stand the test of time.
 Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches and outcomes that derives not only from aspects of statistical modelling but also from decisions regarding how to quantify a particular phenomenon.
-For this study, we gave the same speech dataset to N teams of researchers and asked them to answer the same research question.
-[Results TBA]"
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
+In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
+Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"

### 2021-03-30 RR_manuscript/Draft_RR.Rmd
edits TR

@@
   num: 2
-- name: Timo Roettger
+- name: Timo B. Roettger
   num: 3
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions [@roettger2019emergent].
 Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
@@
 Several other recent studies corroborated this analytic flexibility across different disciplines.
-@dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+@dutilh2019 and @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology; and @botvinik-nezer2020 on neuroimaging data].
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with other, more pleasant activities.
+For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with more pleasant activities.
 If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word *Zoom*.
@@
 
-The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
+The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.
@@
 Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011there].
 The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
@@
 ```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
-knitr::include_graphics(here::here("figs", "ForkingPaths.png"))
+knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"))
 ```
@@
 
-These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.
-after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.
+after data collection and/or preliminary analyses).
 These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
@@
 The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
-The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
+The subject and confederate were seated at the opposite sides of a table, each facing one of two computer screens.
 The participant and the experimenter could not see each other nor each others' screens.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the narrow focus is on the noun (the Noun Focus condition, NF).
-If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).
+If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 
-For the present study, N analysis teams were given access to the entire data set generated by the production study and were instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
 ...
@@
 
-In this study, we are follow the data collection procedure proposed by @Parker2020.
+In this study, we will follow the data collection procedure proposed by @Parker2020.
 The project involves the following five phases:
 
-1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
+1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review data analyses.
 2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
@@
 4. \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
-5. \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
+5. \textsc{Write-up}: We will collaboratively produce the final manuscript.
 
@@
 Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
 
@@
 
-The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. We will not conduct confirmatory tests of any a priori hypotheses. We consider our analysis exploratory.
 
@@
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/mixed-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
@@
 In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The analysis will be conducted in R [@R-base] and fit using Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017].
 The code used to run the model can be found at <https://many-speech-analyses.github.io/suppl/simulations.html>.
@@
 The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g.
-frequency, center of gravity, harmonics difference, etc.), *other measures* (e.g.
+frequency, center of gravity, harmonics difference, etc.), and *other measures* (e.g.
 principal components, vowel dispersion, etc.).

### 2021-03-31 RR_manuscript/Draft_RR.Rmd
fixed a few typos, added a few comments

@@
 - num: 2
-  org: Department of Applied Things, University B, City B, Country B
+  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
 - num: 3
@@
 Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
+<!-- repetition "data" -->
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
@@
 Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
-These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalisability (dependent on the chosen analysis).
+These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
 Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
@@
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
+<!-- Still not sure why in this example we refer to a lexical contrast when it is clear we are focusing on the segment.
+Does it make sense to say the acoustic features can differ depending on the position of the consonant in the word?
+It wouldn't be the same lexical contrast if the segment was in another position...
+they would be different words and maybe no longer a minimal pair.
+-->
 For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].
@@
 For example, studies investigating acoustic correlates of word stress (e.g.
-the difference between *ínsight* and *incíte*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
+the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
 Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
@@
 
-When looking at phrase-level temporal domains, the number of alternative analytic pipelines substantially increases.
-Figure \@ref(fig:forkingPaths)A shows a typical example of a decision tree which speech researcher are often confronted with.
+When looking at phrase-level temporal domains, the number of alternative analytic pipelines increases substantially.
+Figure \@ref(fig:forkingPaths)A shows a typical example of a decision tree with which speech researchers are often confronted. 
 Each of the four analytic decisions in the example have different possible options.
@@
 For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
-...
+... <!-- what's with the 3 periods? -->
 
@@
 mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.
-dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see the next section for the standardization procedure).
+dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
 
@@
 For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
+<!-- It's a technicality but given that bayesian approximation of the posterior is based on sampling, this statement can't be true.
+I understand you are referring specifically to the MAP and that it would be the same as the MLE point estimate, but this reads as if youre saying the models are equivalent.
+-->
 If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we will conduct a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes $\eta_i$.

### 2021-03-31 RR_manuscript/Draft_RR.Rmd
:bug: - implement suggested edits, add credit tax

@@
 
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
+In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by such data.
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
-<!-- repetition "data" -->
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
@@
 A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
-This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
+This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-<!-- Still not sure why in this example we refer to a lexical contrast when it is clear we are focusing on the segment.
-Does it make sense to say the acoustic features can differ depending on the position of the consonant in the word?
-It wouldn't be the same lexical contrast if the segment was in another position...
-they would be different words and maybe no longer a minimal pair.
--->
 For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].
@@
 For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
-... <!-- what's with the 3 periods? -->
 
@@
 Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
-For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
-<!-- It's a technicality but given that bayesian approximation of the posterior is based on sampling, this statement can't be true.
-I understand you are referring specifically to the MAP and that it would be the same as the MLE point estimate, but this reads as if youre saying the models are equivalent.
--->
+For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e.
+only the distribution of the data determines the posterior distribution).
 If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
@@
 
+# Author contributions
+
+<!-- TODO: add LINK to credit -->
+See image at link: .
+
+# Conflicts of interest
+
+We have no conflicts of interest to disclose.
+
 \appendix

### 2021-03-31 RR_manuscript/Draft_RR.tex
:bug: - implement suggested edits, add credit tax

--- 2021-03-30 RR_manuscript/Draft_RR.tex
@@
 
-\author{Stefano Coretta*\affilnum{1}, Timo Roettger\affilnum{2}, Joseph V. Casillas\affilnum{3}}
+\author{Stefano Coretta*\affilnum{1}, Joseph V. Casillas\affilnum{2}, Timo B. Roettger\affilnum{3}}
 
-\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Applied Things, University B, City B, Country B}\\\affilnum{3}{Very Important Stuff Committee, Institute C, City C, Country C}}
+\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{3}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
 
@@
 \begin{abstract}
-TBA
+Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
+Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
+Thus, researchers have expressed their concerns that these researcher degrees of freedom might can facilitate bias and can lead to claims that do not stand the test of time.
+Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
+In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
+Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
 \end{abstract}
@@
 
-In order to effectively accumulate knowledge, science needs to (i) produce data that can be replicated using the original methods and (ii) arrive at robust conclusions substantiated by the data.
+In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by such data.
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates \citep[e.g.,][]{open2015estimating, camerer2018evaluating} leading to what is now referred to as the \emph{replication crisis}.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the theoretical conclusions drawn from data are often variable even when researchers have access to reliable data.
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
 The latter situation has been referred to as the \emph{inference crisis} \citep{rotello2015more, starns2019assessing} and is, among other things, rooted in the inherent flexibility of data analysis \citep[often referred to as researcher degrees of freedom:][]{simmons2011false, gelman2014statistical}.
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured \citep{roettger2019researcher}.
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions \citep{roettger2019emergent}.
 Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}.
@@
 Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
-These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalisability (dependent on the chosen analysis).
+These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
 Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
@@
 Several other recent studies corroborated this analytic flexibility across different disciplines.
-\citet{dutilh2019} ad \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
+\citet{dutilh2019} and \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citetext{\citealp[see also][ on analytic flexibility in ecology]{Parker2020}; \citealp[and][ on neuroimaging data]{botvinik-nezer2020}}.
@@
 Depending on the speaker's intention, this sentence can be said in different ways.
-For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with other, more pleasant activities.
+For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with more pleasant activities.
 If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word \emph{Zoom}.
@@
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
-This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
+This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 
-The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
+The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
 Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011there}.
 The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
@@
 
-When looking at phrase-level temporal domains, the number of alternative analytic pipelines substantially increases.
-Figure \ref{fig:forkingPaths}A shows a typical example of a decision tree which speech researcher are often confronted with.
+When looking at phrase-level temporal domains, the number of alternative analytic pipelines increases substantially.
+Figure \ref{fig:forkingPaths}A shows a typical example of a decision tree with which speech researchers are often confronted.
 Each of the four analytic decisions in the example have different possible options.
@@
 
-These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
+These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
 These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the narrow focus is on the noun (the Noun Focus condition, NF).
-If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the narrow focus is on the color adjective (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the narrow focus is on the whole noun phrase (the Adjective/Noun Focus condition, ANF).
+If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is in focus (the Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
+If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 
-For the present study, N analysis teams were given access to the entire data set generated by the production study and were instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
-\ldots{}
+For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
 
@@
 
-In this study, we are follow the data collection procedure proposed by \citet{Parker2020}.
+In this study, we will follow the data collection procedure proposed by \citet{Parker2020}.
 The project involves the following five phases:
@@
 \item
-  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data.
+  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review data analyses.
 \item
@@
 \item
-  \textsc{Write-up}: Lastly, we will collaboratively produce the final manuscript.
+  \textsc{Write-up}: We will collaboratively produce the final manuscript.
 \end{enumerate}
@@
 Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.
+They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
 
@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardizes effect sizes (see the next section for the standardization procedure).
+We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
 
@@
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/mixed-effects regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
+Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
@@
 Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
-For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
+For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e.~only the distribution of the data determines the posterior distribution).
 If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we will fit a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we will conduct a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
 The outcome variable will be the set of standardized effect sizes \(\eta_i\).
@@
 In case of divergent transitions, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The analysis will be conducted in R \citep{R-base} and fit using Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017}.
 The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
@@
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
+The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
@@
 
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
+
+See image at link: .
+
+\hypertarget{conflicts-of-interest}{%
+\section{Conflicts of interest}\label{conflicts-of-interest}}
+
+We have no conflicts of interest to disclose.
+
 \appendix

### 2021-03-31 scripts/r/credit-taxonomy.R

@@ -1,0 +1,24 @@
+# CRediT taxonomy
+
+library(tidyverse)
+
+credit <- read_csv(here::here("./data/meta/credit-taxonomy.csv")) %>%
+  pivot_longer(SC:TR, names_to = "author", values_to = "value") %>%
+  mutate(
+    author = factor(author, levels = c("SC", "JVC", "TR")),
+    value = ifelse(is.na(value), 0.2, value)
+  )
+
+credit %>%
+  ggplot(aes(author, Roles)) +
+  geom_point(aes(alpha = value)) +
+  scale_y_discrete(limits = rev) +
+  scale_x_discrete(position = "top") +
+  labs(
+    x = element_blank(), y = element_blank(),
+    caption = "CRediT (Contributor Roles Taxonomy), http://credit.niso.org."
+  ) +
+  theme_light() +
+  theme(legend.position = "none", text = element_text(size = 8))
+
+ggsave(here::here("./figs/credit-taxonomy.png"), width = 3, height = 3)

### 2021-03-31 RR_manuscript/Draft_RR.Rmd
:memo: - edit RR

@@
 Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
-Thus, researchers have expressed their concerns that these researcher degrees of freedom might can facilitate bias and can lead to claims that do not stand the test of time.
+Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time.
 Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
 In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?*
+For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 
@@
 
-- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens [numeric].
+- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students [numeric].
 - *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].

### 2021-03-31 RR_manuscript/Draft_RR.tex
:memo: - edit RR

@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations in referring expressions?}
+For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 
@@
 \item
-  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate studens {[}numeric{]}.
+  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students {[}numeric{]}.
 \item

### 2021-04-01 RR_manuscript/Draft_RR.Rmd
:memo: - various fixes to RR

@@
 ---
-title: "Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech"
-runninghead: "Many analysts, one speech data set"
+title: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses"
+runninghead: "Multidimensional signals and analytic flexibility"
 author:
@@
 Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011there].
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
 The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].

### 2021-04-01 RR_manuscript/Draft_RR.tex
:memo: - various fixes to RR

@@
 
-\title{Analytic choices for analyzing multidimensional behavior: Many analysts test hypotheses about human speech}
+\title{Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses}
 
-\runninghead{Many analysts, one speech data set}
+\runninghead{Multidimensional signals and analytic flexibility}
 
@@
 Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011there}.
+Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
 The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.

### 2021-04-01 RR_manuscript/Draft_RR.Rmd
:memo: - prepare for submission

@@
     keep_tex: yes
+    template: template.tex
     includes:
@@
 These results are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension.
-However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalisability of the studies' conclusions.
+However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalizability of the studies' conclusions.
 
@@
 The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
+The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
 
@@
 
-An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).
+An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts.
+"Join Project" will link to the intake form.]
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
@@
 The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
-PDF versions of all the questionnaires used in this study are available at LINK^[Temporary link: <https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8>.].
+PDF versions of all the questionnaires used in this study are available at LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Questionnaires component.].
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK^[Temporary link: <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]).
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Data component.]).
 
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).^[Link for peer-review: <https://osf.io/3bmcp/?view_only=4f00dff704d742d493870f9f3d68e432>.]
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).^[Link for peer-review: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
@@
 <!-- TODO: add LINK to credit -->
-See image at link: .
+See image at LINK [for peer-review, see figure `credit-taxonomy.png` attached with submission].
 
@@
 - **Standardized model**: Bayesian refit of the team's model.
-- **Standardized effect sizes**: ($\eta_i$) effect sizes returned by the standardised models.
+- **Standardized effect sizes**: ($\eta_i$) effect sizes returned by the standardized models.
 - **Standardized standard error**: ($\text{se}_i$) standard deviation of the standardized effect sizes.

### 2021-04-01 RR_manuscript/Draft_RR.tex
:memo: - prepare for submission

@@
 \usepackage{moreverb,url,natbib, multirow, tabularx}
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
+\usepackage[hidelinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
 
@@
 
-An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).
+An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).\footnote{``Questions'' and ``Join Project'' buttons will be functioning when recruitment starts.
+``Join Project'' will link to the intake form.}
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
@@
 The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
-PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/h6z8w/?view_only=3457f2b01a5f4435b3d917eb7b5134e8}.}.
+PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Questionnaires component.}.
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}).
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Data component.}).
 
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=4f00dff704d742d493870f9f3d68e432}.}
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
@@
 
-See image at link: .
+See image at LINK {[}for peer-review, see figure \texttt{credit-taxonomy.png} attached with submission{]}.
 
@@
 \item
-  \textbf{Standardized effect sizes}: (\(\eta_i\)) effect sizes returned by the standardised models.
+  \textbf{Standardized effect sizes}: (\(\eta_i\)) effect sizes returned by the standardized models.
 \item

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:sparkles: - add sample size simulation

---
title: "Sample size"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(brms)
library(extraDistr)
library(tidybayes)
```

```{r functions}
simulate_data <- function(sd, n) {
  tibble(
    es_mean = rnorm(n, 1, sd),
    # 
    es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

run_brm <- function(data) {
  priors <- c(
    prior(normal(0, 1), class = Intercept),
    prior(cauchy(0, 1), class = sd)
  )

  meta_bm <- brm(
    es_mean | se(es_se) ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = threading(4),
    control = list(adapt_delta = 0.999)
  )

  return(meta_bm)
}

run_simulations <- function(sd, n = 12) {
  data <- simulate_data(sd, n)
  brm_model <- run_brm(data)
  return(brm_model)
}
```

```{r run-sims}
sims <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    run_simulations
  )
)

sims_20 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    ~run_simulations(.x, 20)
  )
)

sims_40 <- tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  model = map(
    team_sd,
    ~run_simulations(.x, 40)
  )
)
```

```{r team-sds}
sds <- map(
  sims$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_20 <- map(
  sims_20$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_40 <- map(
  sims_40$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()
```

```{r plot}
tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds,
  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_12.pdf", width = 7, height = 5)

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_20.pdf", width = 7, height = 5)

tibble(
  team_sd = seq(0.01, 0.9, by = 0.05),
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min
) %>%
  ggplot(aes(team_sd, width)) +
  geom_point(size = 5) +
  geom_segment(aes(xend = team_sd, yend = 0))

ggsave("./figs/sds_40.pdf", width = 7, height = 5)
```

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:bug: - fix missing package in sample-size.Rmd

@@
 library(extraDistr)
+library(HDInterval)
 library(tidybayes)
@@
     backend = "cmdstanr", threads = threading(4),
-    control = list(adapt_delta = 0.999)
+    control = list(adapt_delta = 0.999),
   )
@@
 
+saveRDS(sims, "./models/sim/sims.rds")
+
 sims_20 <- tibble(
@@
 
+saveRDS(sims_20, "./models/sim/sims_20.rds")
+
 sims_40 <- tibble(
@@
 )
+
+saveRDS(sims_40, "./models/sim/sims_40.rds")
 ```

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:art: - update sample size figures (work in progress)

@@
   geom_point(size = 5) +
-  geom_segment(aes(xend = team_sd, yend = 0))
+  geom_segment(aes(xend = team_sd, yend = 0)) +
+  ylim(0, 8)
 

### 2021-04-12 scripts/r/sample-size/sample-size.Rmd
:sparkles: - sample size calculation

--- 2021-04-12 scripts/r/sample-size/sample-size.Rmd
@@
 library(tidyverse)
+theme_set(theme_light())
 library(brms)
@@
 library(tidybayes)
+```
+
+```{r}
+dir.create("./figs/sample-size", FALSE)
 ```
@@
 ```{r run-sims}
+if (file.exists("./models/sim/sims_40.rds")) {
+  sims <- readRDS("./models/sim/sims.rds")
+  sims_20 <- readRDS("./models/sim/sims_20.rds")
+  sims_40 <- readRDS("./models/sim/sims_40.rds")
+} else {
   sims <- tibble(
@@
   saveRDS(sims_40, "./models/sim/sims_40.rds")
+}
 ```
@@
 ```{r plot}
-tibble(
+sd_12 <- tibble(
   team_sd = seq(0.01, 0.9, by = 0.05),
@@
   max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min
-) %>%
-  ggplot(aes(team_sd, width)) +
-  geom_point(size = 5) +
-  geom_segment(aes(xend = team_sd, yend = 0))
+  width = max - min,
+  n = 12
+)
 
-ggsave("./figs/sds_12.pdf", width = 7, height = 5)
-
-tibble(
+sd_20 <- tibble(
   team_sd = seq(0.01, 0.9, by = 0.05),
@@
   max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min
-) %>%
-  ggplot(aes(team_sd, width)) +
-  geom_point(size = 5) +
-  geom_segment(aes(xend = team_sd, yend = 0))
+  width = max - min,
+  n = 20
+)
 
-ggsave("./figs/sds_20.pdf", width = 7, height = 5)
-
-tibble(
+sd_40 <- tibble(
   team_sd = seq(0.01, 0.9, by = 0.05),
@@
   max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min
-) %>%
-  ggplot(aes(team_sd, width)) +
-  geom_point(size = 5) +
-  geom_segment(aes(xend = team_sd, yend = 0))
+  width = max - min,
+  n = 40
+)
 
-ggsave("./figs/sds_40.pdf", width = 7, height = 5)
+bind_rows(sd_12, sd_20, sd_40) %>%
+  ggplot(aes(team_sd, width, colour = as.factor(n))) +
+  geom_line() +
+  geom_point(size = 4) +
+  geom_hline(yintercept = 1) +
+  annotate("text", 0.9, 1.3, label = "1 SD") +
+  geom_hline(yintercept = 2, linetype = "dashed") +
+  annotate("text", 0.9, 2.3, label = "2 SD") +
+  geom_hline(yintercept = 3, linetype = "dotted") +
+  annotate("text", 0.9, 3.3, label = "3 SD") +
+  ylim(0, 8) +
+  scale_color_brewer() +
+  labs(
+    title = "95% CrI width depending on teams' true SD and number of teams",
+    x = "Teams' true standard deviation",
+    y = "95% CrI width (standard units)",
+    colour = "N of teams"
+  )
+
+ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5)
 ```

### 2021-04-15 scripts/r/sample-size/sample-size_TR.Rmd
attempt to alter script

---
title: "Sample size"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
theme_set(theme_light())
library(brms)
library(extraDistr)
library(HDInterval)
library(tidybayes)
```

```{r}
dir.create("./figs/sample-size", FALSE)
```

```{r Silberzahn}

# load in Silberzahn et al. data: https://osf.io/fa743/
silber = read_csv("https://osf.io/fa743/download")

## run model on OR to estimate between teams SD

# set weakly informative priors
# mean OR
round(mean(silber$OR),2)

priors <- c(
  prior(normal(1.39, 1), class = Intercept),
  prior(cauchy(0, 0.5), class = sd)
)

# run simple model
silber_sd <- brm(
  OR ~ (1 | Team),
  data = silber,
  prior = priors,
  chain = 4,
  iter = 4000,
  cores = 4,
  backend = "cmdstanr", threads = threading(4),
  control = list(adapt_delta = 0.99999, max_treedepth = 15),
)

# extract SD estimate and 95 CrI
SD = summary(silber_sd)$random[[1]][1]
lower = summary(silber_sd)$random[[1]][3]
upper = summary(silber_sd)$random[[1]][4]

quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])

```

```{r functions}
simulate_data <- function(sd, n) {
  tibble(
    es_mean = rnorm(n, 0, sd),
    # no measurement error model for the simulation
    # es_se = rhcauchy(n, 0.15),
    team = letters[1:n]
  )
}

run_brm <- function(data) {
  priors <- c(
    prior(normal(0, 1), class = Intercept),
    prior(cauchy(0, 0.15), class = sd)
  )

  meta_bm <- brm(
    es_mean ~
    #es_mean | se(es_se) ~
      (1 | team),
    data = data,
    prior = priors,
    chain = 4,
    cores = 4,
    backend = "cmdstanr", threads = threading(4),
    control = list(adapt_delta = 0.9999, max_treedepth = 15),
  )

  return(meta_bm)
}

run_simulations <- function(sd, n = 10) {
  data <- simulate_data(sd, n)
  brm_model <- run_brm(data)
  return(brm_model)
}
```

```{r run-sims}
if (file.exists("./models/sim/sims_40.rds")) {
  sims_20 <- readRDS("./models/sim/sims_20.rds")
  sims_25 <- readRDS("./models/sim/sims_25.rds")
  sims_30 <- readRDS("./models/sim/sims_30.rds")
  sims_35 <- readRDS("./models/sim/sims_35.rds")
  sims_40 <- readRDS("./models/sim/sims_40.rds")
} else {

  sims_20 <- tibble(
    team_sd = quantiles,
    model = map(
      team_sd,
      run_simulations
    )
  )

  saveRDS(sims_20, "./models/sim/sims_20.rds")

  sims_25 <- tibble(
    team_sd = quantiles,
    model = map(
      team_sd,
      ~run_simulations(.x, 25)
    )
  )

  saveRDS(sims_25, "./models/sim/sims_25.rds")

  sims_30 <- tibble(
    team_sd = quantiles,
    model = map(
      team_sd,
      run_simulations(.x, 30)
    )
  )

  saveRDS(sims_30, "./models/sim/sims_30.rds")

  sims_35 <- tibble(
    team_sd = quantiles,
    model = map(
      team_sd,
      ~run_simulations(.x, 35)
    )
  )

  saveRDS(sims_35, "./models/sim/sims_35.rds")

  sims_40 <- tibble(
    team_sd = quantiles,
    model = map(
      team_sd,
      ~run_simulations(.x, 40)
    )
  )

  saveRDS(sims_40, "./models/sim/sims_40.rds")
}
```

```{r team-sds}
sds_20 <- map(
  sims_20$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_25 <- map(
  sims_25$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_30 <- map(
  sims_30$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_35 <- map(
  sims_35$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()

sds_40 <- map(
  sims_40$model,
  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
) %>%
  unlist()
```

```{r plot}
sd_20 <- tibble(
  team_sd = quantiles,
  sd = sds_20,
  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 20
)

sd_25 <- tibble(
  team_sd = quantiles,
  sd = sds_25,
  min = sapply(sds_25, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_25, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 25
)

sd_30 <- tibble(
  team_sd = quantiles,
  sd = sds_30,
  min = sapply(sds_30, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_30, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 30
)

sd_35 <- tibble(
  team_sd = quantiles,
  sd = sds_35,
  min = sapply(sds_35, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_35, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 35
)

sd_40 <- tibble(
  team_sd = quantiles,
  sd = sds_40,
  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
  width = max - min,
  n = 40
)

bind_rows(sd_20, sd_25,sd_30, sd_35, sd_40) %>%
  ggplot(aes(team_sd, width, colour = as.factor(n))) +
  geom_line() +
  geom_point(size = 4) +
  geom_hline(yintercept = 1) +
  annotate("text", 0.9, 1.3, label = "1 SD") +
  geom_hline(yintercept = 2, linetype = "dashed") +
  annotate("text", 0.9, 2.3, label = "2 SD") +
  geom_hline(yintercept = 3, linetype = "dotted") +
  annotate("text", 0.9, 3.3, label = "3 SD") +
  ylim(0, 8) +
  scale_color_brewer() +
  labs(
    title = "95% CrI width depending on teams' true SD and number of teams",
    x = "Teams' true standard deviation",
    y = "95% CrI width (standard units)",
    colour = "N of teams"
  )

ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5)
```

### 2021-04-15 scripts/r/sample-size/sample-size.Rmd
:construction: - prep new code for sample size simulations

@@
 
-```{r}
+```{r dirs}
+# Create dirs to save files to if they don't exist
+dir.create("./models/sims", FALSE, TRUE)
 dir.create("./figs/sample-size", FALSE)
@@
 
+```{r Silberzahn}
+# load in Silberzahn et al. data: https://osf.io/fa743/
+silber <- read_csv("https://osf.io/fa743/download")
+
+## run model on OR to estimate between teams SD
+
+# set weakly informative priors
+# mean OR
+round(mean(silber$OR), 2)
+
+priors <- c(
+  prior(normal(1, 1), class = Intercept),
+  prior(cauchy(0, 1), class = sd)
+)
+
+# run simple model
+silber_sd <- brm(
+  OR ~ (1 | Team),
+  data = silber,
+  prior = priors,
+  chain = 4,
+  iter = 4000,
+  cores = 4,
+  backend = "cmdstanr", threads = threading(4),
+  control = list(adapt_delta = 0.99999, max_treedepth = 15),
+  file = "./models/sims/silber_sd"
+)
+
+# extract SD estimate and 95 CrI
+SD <- summary(silber_sd)$random[[1]][1]
+lower <- summary(silber_sd)$random[[1]][3]
+upper <- summary(silber_sd)$random[[1]][4]
+
+quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
+quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])
+n_teams <- seq(15, 40, by = 5)
+
+# Get all unique combos of number of teams and quantiles of SD.
+n_ts_qs <- expand_grid(n_teams, quantiles)
+```
+
 ```{r functions}
-simulate_data <- function(sd, n) {
+simulate_data <- function(n, sd) {
   tibble(
-    es_mean = rnorm(n, 1, sd),
-    # 
-    es_se = rhcauchy(n, 0.15),
+    odds = rnorm(n, 1, sd),
+    # no measurement error model for the simulation
+    # es_se = rhcauchy(n, 0.15),
     team = letters[1:n]
@@
   meta_bm <- brm(
-    es_mean | se(es_se) ~
+    odds ~
       (1 | team),
@@
     backend = "cmdstanr", threads = threading(4),
-    control = list(adapt_delta = 0.999),
+    control = list(adapt_delta = 0.9999, max_treedepth = 15),
   )
@@
 
-run_simulations <- function(sd, n = 12) {
-  data <- simulate_data(sd, n)
+run_simulations <- function(n, sd) {
+  data <- simulate_data(n, sd)
   brm_model <- run_brm(data)
@@
 ```{r run-sims}
-if (file.exists("./models/sim/sims_40.rds")) {
-  sims <- readRDS("./models/sim/sims.rds")
-  sims_20 <- readRDS("./models/sim/sims_20.rds")
-  sims_40 <- readRDS("./models/sim/sims_40.rds")
-} else {
-  sims <- tibble(
-    team_sd = seq(0.01, 0.9, by = 0.05),
-    model = map(
-      team_sd,
-      run_simulations
+sample_sims <- tibble(
+  n_teams = n_ts_qs$n_teams,
+  quants = n_ts_qs$quantiles,
+  models = map2(
+    n_teams, quants,
+    ~run_simulations(.x, .y)
   )
 )
-
-  saveRDS(sims, "./models/sim/sims.rds")
-
-  sims_20 <- tibble(
-    team_sd = seq(0.01, 0.9, by = 0.05),
-    model = map(
-      team_sd,
-      ~run_simulations(.x, 20)
-    )
-  )
-
-  saveRDS(sims_20, "./models/sim/sims_20.rds")
-
-  sims_40 <- tibble(
-    team_sd = seq(0.01, 0.9, by = 0.05),
-    model = map(
-      team_sd,
-      ~run_simulations(.x, 40)
-    )
-  )
-
-  saveRDS(sims_40, "./models/sim/sims_40.rds")
-}
 ```
 
-```{r team-sds}
-sds <- map(
-  sims$model,
+```{r team-sds, eval=FALSE, include=FALSE}
+sds_20 <- map(
+  sims_20$model,
   ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
@@
 
-sds_20 <- map(
-  sims_20$model,
+sds_25 <- map(
+  sims_25$model,
+  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
+) %>%
+  unlist()
+
+sds_30 <- map(
+  sims_30$model,
+  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
+) %>%
+  unlist()
+
+sds_35 <- map(
+  sims_35$model,
   ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
@@
 
-```{r plot}
-sd_12 <- tibble(
-  team_sd = seq(0.01, 0.9, by = 0.05),
-  sd = sds,
-  min = sapply(sds, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 12
-)
-
+```{r plot, eval=FALSE, include=FALSE}
 sd_20 <- tibble(
-  team_sd = seq(0.01, 0.9, by = 0.05),
+  team_sd = quantiles,
   sd = sds_20,
@@
 
+sd_25 <- tibble(
+  team_sd = quantiles,
+  sd = sds_25,
+  min = sapply(sds_25, function(.x) inverseCDF(0.025, phcauchy, .x)),
+  max = sapply(sds_25, function(.x) inverseCDF(0.975, phcauchy, .x)),
+  width = max - min,
+  n = 25
+)
+
+sd_30 <- tibble(
+  team_sd = quantiles,
+  sd = sds_30,
+  min = sapply(sds_30, function(.x) inverseCDF(0.025, phcauchy, .x)),
+  max = sapply(sds_30, function(.x) inverseCDF(0.975, phcauchy, .x)),
+  width = max - min,
+  n = 30
+)
+
+sd_35 <- tibble(
+  team_sd = quantiles,
+  sd = sds_35,
+  min = sapply(sds_35, function(.x) inverseCDF(0.025, phcauchy, .x)),
+  max = sapply(sds_35, function(.x) inverseCDF(0.975, phcauchy, .x)),
+  width = max - min,
+  n = 35
+)
+
 sd_40 <- tibble(
-  team_sd = seq(0.01, 0.9, by = 0.05),
+  team_sd = quantiles,
   sd = sds_40,
@@
 
-bind_rows(sd_12, sd_20, sd_40) %>%
+bind_rows(sd_20, sd_25,sd_30, sd_35, sd_40) %>%
   ggplot(aes(team_sd, width, colour = as.factor(n))) +

### 2021-04-15 scripts/r/sample-size/sample-size.Rmd
add save sample_sims

@@
 )
+
+saveRDS(sample_sims, "./models/sims/sample_sims.rds")
 ```

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:recycle: - refactor sample size simulations

@@
 simulate_data <- function(n, sd) {
-  tibble(
+  tibble::tibble(
     odds = rnorm(n, 1, sd),
@@
   priors <- c(
-    prior(normal(0, 1), class = Intercept),
-    prior(cauchy(0, 1), class = sd)
+    brms::prior(normal(0, 1), class = Intercept),
+    brms::prior(cauchy(0, 1), class = sd)
   )
 
-  meta_bm <- brm(
+  meta_bm <- brms::brm(
     odds ~
@@
     cores = 4,
-    backend = "cmdstanr", threads = threading(4),
+    backend = "cmdstanr", threads = brms::threading(4),
     control = list(adapt_delta = 0.9999, max_treedepth = 15),
@@
   brm_model <- run_brm(data)
-  return(brm_model)
+
+  sd_team <- purr::map(
+    brm_model$model,
+    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
+      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
+      dplyr::pull()
+  ) %>%
+  unlist()
+
+  return(sd_team)
 }
@@
 saveRDS(sample_sims, "./models/sims/sample_sims.rds")
-```
-
-```{r team-sds, eval=FALSE, include=FALSE}
-sds_20 <- map(
-  sims_20$model,
-  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
-) %>%
-  unlist()
-
-sds_25 <- map(
-  sims_25$model,
-  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
-) %>%
-  unlist()
-
-sds_30 <- map(
-  sims_30$model,
-  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
-) %>%
-  unlist()
-
-sds_35 <- map(
-  sims_35$model,
-  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
-) %>%
-  unlist()
-
-sds_40 <- map(
-  sims_40$model,
-  ~spread_draws(.x, sd_team__Intercept) %>% summarise(sd = sd(sd_team__Intercept)) %>% pull
-) %>%
-  unlist()
 ```

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - fix package namespace

@@
 
-  sd_team <- purr::map(
+  sd_team <- purrr::map(
     brm_model$model,

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - return sd

--- 2021-04-16 scripts/r/sample-size/sample-size.Rmd
@@
 
-  sd_team <- purr::map(
-    brm_model$model,
-    ~tidybayes::spread_draws(.x, sd_team__Intercept) %>%
-      dplyr::summarise(sd = sd(sd_team__Intercept)) %>%
-      dplyr::pull()
-  ) %>%
-  unlist()
+  sd_team <- as_tibble(summary(brm_model)$team)
 
@@
   quants = n_ts_qs$quantiles,
-  models = map2(
+  sd_team = map2(
     n_teams, quants,

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:sparkles: - transform OR to z-scores for sample size simulations

@@
 # load in Silberzahn et al. data: https://osf.io/fa743/
-silber <- read_csv("https://osf.io/fa743/download")
+silber <- read_csv("https://osf.io/fa743/download") %>%
+  mutate(
+    z_score = log(OR) / ((log(OR) - log(OR_lo)) / 1.96)
+  ) %>%
+  filter(z_score < 6)
 
@@
 # mean OR
-round(mean(silber$OR), 2)
+round(mean(silber$z_score), 2)
 
 priors <- c(
-  prior(normal(1, 1), class = Intercept),
+  prior(normal(0, 1), class = Intercept),
   prior(cauchy(0, 1), class = sd)
@@
 silber_sd <- brm(
-  OR ~ (1 | Team),
+  z_score ~ (1 | Team),
   data = silber,
@@
   tibble::tibble(
-    odds = rnorm(n, 1, sd),
+    z_score = rnorm(n, 0, sd),
     # no measurement error model for the simulation
@@
   meta_bm <- brms::brm(
-    odds ~
+    z_score ~
       (1 | team),
@@
     chain = 4,
+    iter = 6000,
     cores = 4,

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:bug: - output full summary of simulations
:art: - add plot code for sample size simulations

@@
   data <- simulate_data(n, sd)
+
+  cat("Model:", n, sd, "\n")
   brm_model <- run_brm(data)
 
-  sd_team <- as_tibble(summary(brm_model)$team)
+  sd_team <- summary(brm_model)
 
@@
 ```{r run-sims}
+sample_file <- "./models/sims/sample_sims.rds"
+
+if (file.exists(sample_file)) {
+  sample_sims <- readRDS(sample_file)
+} else {
   sample_sims <- tibble(
@@
 
-saveRDS(sample_sims, "./models/sims/sample_sims.rds")
+  saveRDS(sample_sims, sample_file)
+}
 ```
@@
 ```{r plot, eval=FALSE, include=FALSE}
-sd_20 <- tibble(
-  team_sd = quantiles,
-  sd = sds_20,
-  min = sapply(sds_20, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds_20, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 20
+sample_sims <- sample_sims %>%
+  mutate(
+    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
   )
 
-sd_25 <- tibble(
-  team_sd = quantiles,
-  sd = sds_25,
-  min = sapply(sds_25, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds_25, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 25
-)
-
-sd_30 <- tibble(
-  team_sd = quantiles,
-  sd = sds_30,
-  min = sapply(sds_30, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds_30, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 30
-)
-
-sd_35 <- tibble(
-  team_sd = quantiles,
-  sd = sds_35,
-  min = sapply(sds_35, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds_35, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 35
-)
-
-sd_40 <- tibble(
-  team_sd = quantiles,
-  sd = sds_40,
-  min = sapply(sds_40, function(.x) inverseCDF(0.025, phcauchy, .x)),
-  max = sapply(sds_40, function(.x) inverseCDF(0.975, phcauchy, .x)),
-  width = max - min,
-  n = 40
-)
-
-bind_rows(sd_20, sd_25,sd_30, sd_35, sd_40) %>%
-  ggplot(aes(team_sd, width, colour = as.factor(n))) +
+sample_sims %>%
+  ggplot(aes(quants, cri, colour = as.factor(n_teams))) +
   geom_line() +
@@
   geom_hline(yintercept = 1) +
-  annotate("text", 0.9, 1.3, label = "1 SD") +
   geom_hline(yintercept = 2, linetype = "dashed") +
-  annotate("text", 0.9, 2.3, label = "2 SD") +
-  geom_hline(yintercept = 3, linetype = "dotted") +
-  annotate("text", 0.9, 3.3, label = "3 SD") +
-  ylim(0, 8) +
-  scale_color_brewer() +
+  scale_x_continuous(breaks = quantiles) +
+  scale_color_brewer(type = "seq", palette = "BuPu") +
   labs(
@@
     x = "Teams' true standard deviation",
-    y = "95% CrI width (standard units)",
+    y = "95% CrI width",
     colour = "N of teams"

### 2021-04-16 scripts/r/sample-size/sample-size.Rmd
:building_construction: - test simulations

@@
 } else {
-  sample_sims <- tibble(
-    n_teams = n_ts_qs$n_teams,
-    quants = n_ts_qs$quantiles,
-    sd_team = map2(
-      n_teams, quants,
-      ~run_simulations(.x, .y)
-    )
-  )
-
-  saveRDS(sample_sims, sample_file)
+  # sample_sims <- tibble(
+  #   n_teams = n_ts_qs$n_teams,
+  #   quants = n_ts_qs$quantiles,
+  #   sd_team = map2(
+  #     n_teams, quants,
+  #     ~run_simulations(.x, .y)
+  #   )
+  # )
+  # 
+  # saveRDS(sample_sims, sample_file)
+  print("why?")
 }
@@
 
-```{r plot, eval=FALSE, include=FALSE}
+```{r plot}
 sample_sims <- sample_sims %>%

### 2021-04-17 scripts/r/sample-size/sample-size.Rmd
:sparkles: - plot sample size simulations

@@
 library(tidyverse)
-theme_set(theme_light())
+theme_set(theme_light(base_family = "Lato"))
 library(brms)
@@
 if (file.exists(sample_file)) {
+  cat("Reading file...\n")
   sample_sims <- readRDS(sample_file)
+  cat("Done!")
 } else {
-  # sample_sims <- tibble(
-  #   n_teams = n_ts_qs$n_teams,
-  #   quants = n_ts_qs$quantiles,
-  #   sd_team = map2(
-  #     n_teams, quants,
-  #     ~run_simulations(.x, .y)
-  #   )
-  # )
-  # 
-  # saveRDS(sample_sims, sample_file)
-  print("why?")
+  sample_sims <- tibble(
+    n_teams = n_ts_qs$n_teams,
+    quants = n_ts_qs$quantiles,
+    sd_team = map2(
+      n_teams, quants,
+      ~run_simulations(.x, .y)
+    )
+  )
+
+  saveRDS(sample_sims, sample_file)
 }
@@
 
+labels <- tibble(
+  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
+  y = c(1.25, 0.7, 1.5, 0.1, 0.8),
+  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
+)
+
+arrows <- tibble(
+    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
+    y1 = c(1.15, 0.6, 1.4, 0.1, 0.9),
+    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
+    y2 = c(0.8, 0.45, 1.2, 0.1, 1.1)
+  )
+
 sample_sims %>%
-  ggplot(aes(quants, cri, colour = as.factor(n_teams))) +
-  geom_line() +
-  geom_point(size = 4) +
+  ggplot(aes(quants, cri)) +
+  geom_line(aes(colour = as.factor(n_teams))) +
+  geom_point(aes(colour = as.factor(n_teams)), size = 4) +
   geom_hline(yintercept = 1) +
   geom_hline(yintercept = 2, linetype = "dashed") +
-  scale_x_continuous(breaks = quantiles) +
-  scale_color_brewer(type = "seq", palette = "BuPu") +
+  geom_text(
+    data = labels, aes(x, y, label = labs),
+    family = "Lato"
+  ) +
+  geom_curve(
+    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
+    arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
+    color = "gray20", curvature = 0.3
+  ) +
+  scale_x_continuous(breaks = round(quantiles, 2)) +
+  scale_color_manual(values = c("#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#6e016b")) +
   labs(
@@
     y = "95% CrI width",
-    colour = "N of teams"
+    colour = "N of teams",
+    caption = "The values on the x-axis are the quartiles (0, 0.25, 0.5, 0.75, 1)\nof the estimated teams' SD from Silberzahn et al."
   )
 
-ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5)
+ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5, device = cairo_pdf)
 ```

### 2021-04-18 scripts/r/sample-size/sample-size.Rmd
edited, but doesn't run

@@
 # set weakly informative priors
-# mean OR
+# mean z-score
 round(mean(silber$z_score), 2)
 
+set.seed(99)
+
 priors <- c(
-  prior(normal(0, 1), class = Intercept),
+  prior(normal(2, 2), class = Intercept),
   prior(cauchy(0, 1), class = sd)
@@
   cores = 4,
-  backend = "cmdstanr", threads = threading(4),
-  control = list(adapt_delta = 0.99999, max_treedepth = 15),
+  #backend = "cmdstanr", threads = threading(4),
+  control = list(adapt_delta = 0.99999999, max_treedepth = 15),
   file = "./models/sims/silber_sd"

### 2021-04-18 scripts/r/sample-size/sample-size.Rmd
:zap: - use weak priors and set seed

@@
 library(tidybayes)
+my_seed <- 99
 ```
@@
 
-set.seed(99)
-
 priors <- c(
-  prior(normal(2, 2), class = Intercept),
+  prior(normal(0, 3), class = Intercept),
   prior(cauchy(0, 1), class = sd)
@@
   cores = 4,
-  #backend = "cmdstanr", threads = threading(4),
-  control = list(adapt_delta = 0.99999999, max_treedepth = 15),
+  seed = my_seed,
+  backend = "cmdstanr", threads = threading(4),
+  control = list(adapt_delta = 0.9999, max_treedepth = 15),
   file = "./models/sims/silber_sd"
@@
   priors <- c(
-    brms::prior(normal(0, 1), class = Intercept),
+    brms::prior(normal(0, 3), class = Intercept),
     brms::prior(cauchy(0, 1), class = sd)
@@
     cores = 4,
+    seed = my_seed,
     backend = "cmdstanr", threads = brms::threading(4),

### 2021-05-02 scripts/r/sample-size/sample-size.Rmd
run 10 interations per n/sd combos

@@
 quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])
-n_teams <- seq(15, 40, by = 5)
+n_teams <- seq(5, 40, by = 5)
 
@@
 
+  sd_team_i <- numeric()
+
   cat("Model:", n, sd, "\n")
+
+  for (iter in 1:10) {
+    cat("   Iteration", iter, "\n")
     brm_model <- run_brm(data)
+    brm_summ <- summary(brm_model)
+    sd_team_i <- c(sd_team_i, brm_summ$random$team[4] - brm_summ$random$team[3]) 
+  }
 
-  sd_team <- summary(brm_model)
+  sd_team_mean <- mean(sd_team_i, na.rm = TRUE)
+  sd_team_sd <- sd(sd_team_i, na.rm = TRUE)
 
-  return(sd_team)
+  return(list(sd_team_mean, sd_team_sd))
 }
@@
 
-```{r plot}
+```{r plot, eval=FALSE}
 sample_sims <- sample_sims %>%

### 2021-05-03 scripts/r/sample-size/sample-size.Rmd
:bug: - set seed at beginning

@@
 my_seed <- 99
+set.seed(my_seed)
 ```
@@
     cores = 4,
-    seed = my_seed,
     backend = "cmdstanr", threads = brms::threading(4),
@@
 
-```{r plot, eval=FALSE}
-sample_sims <- sample_sims %>%
-  mutate(
-    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
-  )
+```{r plot}
+sample_cri <- sample_sims %>%
+  unnest(sd_team) %>%
+  mutate(sd_team = unlist(sd_team)) %>% 
+  filter(sd_team > 0) %>%
+  rename(cri = sd_team)
 
@@
   x = c(0.5, 0.25, 0.9, 0.3, 1.3),
-  y = c(1.25, 0.7, 1.5, 0.1, 0.8),
+  y = c(1.25, 0.7, 1.5, 0.1, 1.15),
   labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
@@
     x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
-    y1 = c(1.15, 0.6, 1.4, 0.1, 0.9),
+    y1 = c(1.15, 0.6, 1.4, 0.1, 1.2),
     x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
-    y2 = c(0.8, 0.45, 1.2, 0.1, 1.1)
+    y2 = c(0.8, 0.45, 1.2, 0.1, 1.39)
   )
 
-sample_sims %>%
+sample_cri %>%
   ggplot(aes(quants, cri)) +
@@
   scale_x_continuous(breaks = round(quantiles, 2)) +
-  scale_color_manual(values = c("#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#6e016b")) +
+  scale_color_manual(values = c("#e0ecf4", "#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#810f7c", "#4d004b")) +
   labs(

### 2021-05-03 scripts/r/sample-size/sample-size.Rmd
:recycle: - refactor comments and add logger

@@
 library(tidybayes)
+library(logger)
 my_seed <- 99
@@
 
+# Set up
+
+We first create the necessary directories, if they don't exist already.
+
 ```{r dirs}
-# Create dirs to save files to if they don't exist
+# Save simulation output here
 dir.create("./models/sims", FALSE, TRUE)
+# Save figure output here
 dir.create("./figs/sample-size", FALSE)
@@
 
+# Estimate teams' standard deviation
+
+We obtain an estimate of the teams' standard deviation based on data from Silberzahn et al.
+
 ```{r Silberzahn}
-# load in Silberzahn et al. data: https://osf.io/fa743/
+# Load in Silberzahn et al. data: https://osf.io/fa743/
 silber <- read_csv("https://osf.io/fa743/download") %>%
@@
   ) %>%
+  # Filter out extremely high z_scores
   filter(z_score < 6)
 
-## run model on OR to estimate between teams SD
-
-# set weakly informative priors
-# mean z-score
+# Mean z-score
 round(mean(silber$z_score), 2)
 
+# Set weakly informative priors for intercept and scale parameters.
 priors <- c(
@@
 
-# run simple model
+# Run brm to estimate teams' SD (= `(1 | Team)` in the model)
 silber_sd <- brm(
@@
   seed = my_seed,
+  # Use cmdstanr to enable multi-core multi-threading processing
   backend = "cmdstanr", threads = threading(4),
@@
 
-# extract SD estimate and 95 CrI
-SD <- summary(silber_sd)$random[[1]][1]
-lower <- summary(silber_sd)$random[[1]][3]
-upper <- summary(silber_sd)$random[[1]][4]
+# Extract SD estimate and 95 CrI
+SD <- summary(silber_sd)$random$Team[1]
+lower <- summary(silber_sd)$random$Team[3]
+upper <- summary(silber_sd)$random$Team[4]
 
+# Create a vector of quantiles of the estimated teams' SD
+# min, 1st quartile, mean, 3rd quartile, max = 0.00 0.25 0.50 0.75 1.00
 quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
@@
 
+# Prepare functions for simulation
+
+The following functions define routines to simulate data, fir the models to the data, and set up the simulation loop.
+
 ```{r functions}
+# Simulate data ####
+# For each iteration in the simulation loop, simulate data table of z-scores
+# n = number of teams
+# sd = teams' SD used to simulate z-scores
 simulate_data <- function(n, sd) {
@@
     z_score = rnorm(n, 0, sd),
-    # no measurement error model for the simulation
-    # es_se = rhcauchy(n, 0.15),
     team = letters[1:n]
@@
 
+# Fit brm to simulated data ####
 run_brm <- function(data) {
+  # weakly informative priors
   priors <- c(
@@
 
+  # fit brm
   meta_bm <- brms::brm(
@@
 
+# Simulation iteration loop ####
+# This function defines the simulation loop.
+# The mean and SD of the simulated teams' SD across 10 iterations (per
+# n-teams/sd combos) are returned.
 run_simulations <- function(n, sd) {
@@
 
-  cat("Model:", n, sd, "\n")
+  log_info("Model: {n}, {sd}")
 
   for (iter in 1:10) {
-    cat("   Iteration", iter, "\n")
+    log_info("--- Iteration {iter}")
     brm_model <- run_brm(data)
@@
 
+# Run the simulations
+
 ```{r run-sims}
@@
 
+# If results file already exists, read it. Otherwise run the simulations.
 if (file.exists(sample_file)) {
-  cat("Reading file...\n")
+  # read results file
+  log_info("Reading file...\n")
   sample_sims <- readRDS(sample_file)
-  cat("Done!")
+  log_info("Done!")
 } else {
+  # run simulations
   sample_sims <- tibble(
@@
 
+  # save results to file
   saveRDS(sample_sims, sample_file)
@@
 ```
+
+# Plot results
 

### 2021-05-03 scripts/r/sample-size/sample-size.Rmd
:chart_with_upwards_trend: - generate plot of sample size simulations

@@
 sample_cri <- sample_sims %>%
-  unnest(sd_team) %>%
-  mutate(sd_team = unlist(sd_team)) %>% 
-  filter(sd_team > 0) %>%
-  rename(cri = sd_team)
+  mutate(
+    cri = as.numeric(map(sd_team, ~.x[[1]])),
+    cri_sd = as.numeric(map(sd_team, ~.x[[2]]))
+  )
 
@@
   x = c(0.5, 0.25, 0.9, 0.3, 1.3),
-  y = c(1.25, 0.7, 1.5, 0.1, 1.15),
+  y = c(1.25, 0.7, 1.5, 0.1, 0.9),
   labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
@@
     x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
-    y1 = c(1.15, 0.6, 1.4, 0.1, 1.2),
+    y1 = c(1.15, 0.6, 1.4, 0.1, 1),
     x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
-    y2 = c(0.8, 0.45, 1.2, 0.1, 1.39)
+    y2 = c(0.8, 0.45, 1.2, 0.1, 1.2)
   )

### 2021-05-10 scripts/r/simulations/simulations.Rmd
:sparkles: - integrate sample size sims to simulations.Rmd

@@
 
+# Set up
+
 ```{r setup, include=FALSE}
@@
 library(tidyverse)
-theme_set(theme_light())
+theme_set(theme_light(base_family = "Lato"))
 library(patchwork)
@@
 library(betapart)
-# library(summarytools)
-my_seed <- 115116106
+library(tidybayes)
+library(logger)
+my_seed <- 99
+set.seed(my_seed)
 ```
 
-```{r create-dir, include=FALSE}
-dir.create("./models/sim/", F, recursive = T)
+We first create the necessary directories, if they don't exist already.
+
+```{r dirs}
+# Save simulation output here
+dir.create("./models/sims", FALSE, TRUE)
+# Save figure output here
+dir.create("./figs/sample-size", FALSE)
+```
+
+# Sample size
+
+## Estimate teams' standard deviation
+
+We obtain an estimate of the teams' standard deviation based on data from Silberzahn et al.
+
+```{r Silberzahn}
+# Load in Silberzahn et al. data: https://osf.io/fa743/
+silber <- read_csv("https://osf.io/fa743/download") %>%
+  mutate(
+    z_score = log(OR) / ((log(OR) - log(OR_lo)) / 1.96)
+  ) %>%
+  # Filter out extremely high z_scores
+  filter(z_score < 6)
+
+# Mean z-score
+round(mean(silber$z_score), 2)
+
+# Set weakly informative priors for intercept and scale parameters.
+priors <- c(
+  prior(normal(0, 3), class = Intercept),
+  prior(cauchy(0, 1), class = sd)
+)
+
+# Run brm to estimate teams' SD (= `(1 | Team)` in the model)
+silber_sd <- brm(
+  z_score ~ (1 | Team),
+  data = silber,
+  prior = priors,
+  chain = 4,
+  iter = 4000,
+  cores = 4,
+  seed = my_seed,
+  # Use cmdstanr to enable multi-core multi-threading processing
+  backend = "cmdstanr", threads = threading(4),
+  control = list(adapt_delta = 0.9999, max_treedepth = 15),
+  file = "./models/sims/silber_sd"
+)
+
+# Extract SD estimate and 95 CrI
+SD <- summary(silber_sd)$random$Team[1]
+lower <- summary(silber_sd)$random$Team[3]
+upper <- summary(silber_sd)$random$Team[4]
+
+# Create a vector of quantiles of the estimated teams' SD
+# min, 1st quartile, mean, 3rd quartile, max = 0.00 0.25 0.50 0.75 1.00
+quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
+quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])
+n_teams <- seq(5, 40, by = 5)
+
+# Get all unique combos of number of teams and quantiles of SD.
+n_ts_qs <- expand_grid(n_teams, quantiles)
+```
+
+## Prepare functions for simulation
+
+The following functions define routines to simulate data, fir the models to the data, and set up the simulation loop.
+
+```{r functions}
+# Simulate data ####
+# For each iteration in the simulation loop, simulate data table of z-scores
+# n = number of teams
+# sd = teams' SD used to simulate z-scores
+simulate_data <- function(n, sd) {
+  tibble::tibble(
+    z_score = rnorm(n, 0, sd),
+    team = letters[1:n]
+  )
+}
+
+# Fit brm to simulated data ####
+run_brm <- function(data) {
+  # weakly informative priors
+  priors <- c(
+    brms::prior(normal(0, 3), class = Intercept),
+    brms::prior(cauchy(0, 1), class = sd)
+  )
+
+  # fit brm
+  meta_bm <- brms::brm(
+    z_score ~
+      (1 | team),
+    data = data,
+    prior = priors,
+    chain = 4,
+    iter = 6000,
+    cores = 4,
+    backend = "cmdstanr", threads = brms::threading(4),
+    control = list(adapt_delta = 0.9999, max_treedepth = 15),
+  )
+
+  return(meta_bm)
+}
+
+# Simulation iteration loop ####
+# This function defines the simulation loop.
+# The mean and SD of the simulated teams' SD across 10 iterations (per
+# n-teams/sd combos) are returned.
+run_simulations <- function(n, sd) {
+  data <- simulate_data(n, sd)
+
+  sd_team_i <- numeric()
+
+  log_info("Model: {n}, {sd}")
+
+  for (iter in 1:10) {
+    log_info("--- Iteration {iter}")
+    brm_model <- run_brm(data)
+    brm_summ <- summary(brm_model)
+    sd_team_i <- c(sd_team_i, brm_summ$random$team[4] - brm_summ$random$team[3]) 
+  }
+
+  sd_team_mean <- mean(sd_team_i, na.rm = TRUE)
+  sd_team_sd <- sd(sd_team_i, na.rm = TRUE)
+
+  return(list(sd_team_mean, sd_team_sd))
+}
+```
+
+## Run the simulations
+
+```{r run-sample-size}
+sample_file <- "./models/sims/sample_sims.rds"
+
+# If results file already exists, read it. Otherwise run the simulations.
+if (file.exists(sample_file)) {
+  # read results file
+  log_info("Reading file...\n")
+  sample_sims <- readRDS(sample_file)
+  log_info("Done!")
+} else {
+  # run simulations
+  sample_sims <- tibble(
+    n_teams = n_ts_qs$n_teams,
+    quants = n_ts_qs$quantiles,
+    sd_team = map2(
+      n_teams, quants,
+      ~run_simulations(.x, .y)
+    )
+  )
+
+  # save results to file
+  saveRDS(sample_sims, sample_file)
+}
+```
+
+## Plot results
+
+```{r plot-sample-size}
+sample_cri <- sample_sims %>%
+  mutate(
+    cri = as.numeric(map(sd_team, ~.x[[1]])),
+    cri_sd = as.numeric(map(sd_team, ~.x[[2]]))
+  )
+
+labels <- tibble(
+  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
+  y = c(1.25, 0.7, 1.5, 0.1, 0.9),
+  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
+)
+
+arrows <- tibble(
+    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
+    y1 = c(1.15, 0.6, 1.4, 0.1, 1),
+    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
+    y2 = c(0.8, 0.45, 1.2, 0.1, 1.2)
+  )
+
+sample_cri %>%
+  ggplot(aes(quants, cri)) +
+  geom_line(aes(colour = as.factor(n_teams))) +
+  geom_point(aes(colour = as.factor(n_teams)), size = 4) +
+  geom_hline(yintercept = 1) +
+  geom_hline(yintercept = 2, linetype = "dashed") +
+  geom_text(
+    data = labels, aes(x, y, label = labs),
+    family = "Lato"
+  ) +
+  geom_curve(
+    data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
+    arrow = arrow(length = unit(0.07, "inch")), size = 0.4,
+    color = "gray20", curvature = 0.3
+  ) +
+  scale_x_continuous(breaks = round(quantiles, 2)) +
+  scale_color_manual(values = c("#e0ecf4", "#bfd3e6", "#9ebcda", "#8c96c6", "#8c6bb1", "#88419d", "#810f7c", "#4d004b")) +
+  labs(
+    title = "95% CrI width depending on teams' true SD and number of teams",
+    x = "Teams' true standard deviation",
+    y = "95% CrI width",
+    colour = "N of teams",
+    caption = "The values on the x-axis are the quartiles (0, 0.25, 0.5, 0.75, 1)\nof the estimated teams' SD from Silberzahn et al."
+  )
+
+ggsave("./figs/sample-size/cri-width-nteams-true-sd.pdf", width = 7, height = 5, device = cairo_pdf)
 ```

### 2021-05-10 scripts/r/simulations/simulations.Rmd
:bug: - update sims paths

@@
   seed = my_seed,
-  file = "./models/sim/meta_bm_ppred"
+  file = "./models/sims/meta_bm_ppred"
 )
@@
   cores = 4,
-  file = "./models/sim/meta_bm"
+  file = "./models/sims/meta_bm"
 )
@@
   cores = 4,
-  file = "./models/sim/predictors_bm"
+  file = "./models/sims/predictors_bm"
 )

### 2021-05-10 RR_manuscript/Draft_RR.Rmd
:memo: - include sample-size justification and ref to Aczel 2021

@@
 
-In this study, we will follow the data collection procedure proposed by @Parker2020.
+In this study, we will follow the procedures proposed by @Parker2020 and @aczel2021.
 The project involves the following five phases:
@@
 "Join Project" will link to the intake form.]
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.
+For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
 Recruitment for this project will commence upon receiving in-principle acceptance.
-As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytic estimate of the investigated effect *per se*.
-Given the scarcity of previous meta-analytic studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
-Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
+As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
+To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from @silberzahn2018many.
+Variability among teams was operationalised as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
+At the mean teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
+We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.
 
@@
 Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
+Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
@@
 If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
+Model refitting will also constitute a way of validating the reported analyses, a step recommended by @aczel2021.
 
@@
 
-## Phase 6: Collaborative Write-Up of Manuscript
+## Phase 5: Collaborative Write-Up of Manuscript
 

### 2021-05-10 RR_manuscript/Draft_RR.Rmd
:bug: - fix citations causing error

@@
 @dutilh2019 and @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology; and @botvinik-nezer2020 on neuroimaging data].
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also @Parker2020 on analytic flexibility in ecology, and @botvinik-nezer2020 on neuroimaging data).
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.

### 2021-05-10 RR_manuscript/Draft_RR.tex
:memo: - render draft RR

@@
 \citet{dutilh2019} and \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citetext{\citealp[see also][ on analytic flexibility in ecology]{Parker2020}; \citealp[and][ on neuroimaging data]{botvinik-nezer2020}}.
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also \citet{Parker2020} on analytic flexibility in ecology, and \citet{botvinik-nezer2020} on neuroimaging data).
 \citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
 (A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
@@
 
-In this study, we will follow the data collection procedure proposed by \citet{Parker2020}.
+In this study, we will follow the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
 The project involves the following five phases:
@@
 ``Join Project'' will link to the intake form.}
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
+The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
 Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.
+For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
 Recruitment for this project will commence upon receiving in-principle acceptance.
-As outlined above, our aim is to assess the variability of the reported effects and how these are affected by a set of predictors, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
-Given the scarcity of previous meta-analytic studies that directly investigate researcher's degrees of freedom, as reviewed in the introduction, we are not able to establish a properly-grounded minimal sample size.
-Thus, we aim to recruit as many teams as possible, within the resource and time limits of the project.
+As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
+To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from \citet{silberzahn2018many}.
+Variability among teams was operationalised as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
+At the mean teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
+We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50\% drop in participation---we expect to be a sufficient sample size.
 
@@
 Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
+Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
 Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
@@
 If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
+Model refitting will also constitute a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
 
@@
 
-\hypertarget{phase-6-collaborative-write-up-of-manuscript}{%
-\subsection{Phase 6: Collaborative Write-Up of Manuscript}\label{phase-6-collaborative-write-up-of-manuscript}}
+\hypertarget{phase-5-collaborative-write-up-of-manuscript}{%
+\subsection{Phase 5: Collaborative Write-Up of Manuscript}\label{phase-5-collaborative-write-up-of-manuscript}}
 

### 2021-05-13 RR_manuscript/Draft_RR.Rmd
fixed types

@@
 As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
-To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from @silberzahn2018many.
+To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
 Variability among teams was operationalised as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
 At the mean teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.
+We have received initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.
 

### 2021-05-13 RR_manuscript/Draft_RR.Rmd
reknited

@@
 Variability among teams was operationalised as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
-At the mean teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
+For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
 We have received initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.

### 2021-05-13 RR_manuscript/Draft_RR.tex
reknited

@@
 Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions \citep{roettger2019emergent}.
-Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}.
+Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.~][]{wicherts2016, charles2019, roettger2019researcher}.
 This notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
+Despite recent efforts to improve transparency and reproducibility \citep[e.g.~][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
 
@@
 Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
+The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories \citep[e.g.~][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
 (A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
@@
 These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
-These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
+These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.~][]{wicherts2016}.
 In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
@@
 Intonation marks discourse-relevant referents for being new or given information, to guide the listeners' interpretation of incoming messages.
-Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
+Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations \citep[e.g.~][]{dimitrova2008prosodic, dimitrova2009did}.
 Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referents such as \emph{yellow banana}.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
@@
 As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
-To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from \citet{silberzahn2018many}.
+To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
 Variability among teams was operationalised as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
-At the mean teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50\% drop in participation---we expect to be a sufficient sample size.
+For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
+We have received initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50\% drop in participation---we expect to be a sufficient sample size.
 

### 2021-07-28 RR_manuscript/Draft_RR.Rmd
Simple changes
Move researcher degrees of freedom statement to new para
Change research of speech to 'intersection' of cog sci
Add mention of speech categories before talking about segments (probably not enough)
Change order of /t, d/ to /d, t/
Making > make
Define focus

@@
 Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
+
 These researcher degrees of freedom are both a blessing and a curse.
-
 They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
@@
 
-Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
+Research on speech lies at the intersection of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
 One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).
@@
 Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
-Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
+Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds or speech categories.
 The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
@@
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].
+For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/d, t/) [@hawkins2004influence].
 
@@
 Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
-Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and making communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and make communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
+Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor. 
+For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
 If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).

### 2021-08-10 RR_manuscript/Draft_RR.Rmd
some edits of RR

@@
 Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
-These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
-Human behavior is complex and offers many ways to be translated into numbers.
+These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to how already obtained numbers are statistically analyzed.
+Those numbers are usually the result of a complex measurement process that translates human behavior into numbers.
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
@@
 Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
+One aim of this study is to replicate previous many-analyses projects, confirming the large amount of flexibility observed in statistical analyses.
+A second aim is to extend these findings and estimate the amount of flexibility observed during measurement and operationalization.
 
@@
 
-Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
+Data analysis comes with many decisions, for example how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
+Humans filter the world in irrational ways [e.g., @tversky1974judgment], see coherent patterns in randomness [@brugger2001], convince themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceive events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
 In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
@@
 
+Extending on the many analyst approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but by the research question itself.
+This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
+The authors argue that the observed heterogeneity across analysts might be driven by flexibility in interpreting the research question.
+TRANSITION SENTENCE
+
 In those disciplines concerned with communication, human behavior sometimes corresponds to multidimensional visual or acoustic signals.
@@
 Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
-Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds or speech categories.
+Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
 The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
 
-Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.
-they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g.
+From a phonetic viewpoint, linguistically relevant units are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
+The acoustic parameters of units are usually asynchronous, i.e.
+they appear at different time points in the unfolding signal, and overlap with parameters of other units [e.g.
 @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
@@
 To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
-The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
+The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.^[Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.]
 In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.
@@
 when there is just one banana).
-This account, however, has mainly focused on content selection [@gatt2013we], i.e.
-whether a certain referential expression is chosen or not, while not taking into consideration the indexical potential of speech.
+This account, however, has mainly focused on content selection [@gatt2013we].
 
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor. 
+Focused units denote the set of all (contextually relevant) alternatives [e.g.
+@rooth1992theory].Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor.
 For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
@@
 
-1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review data analyses.
+1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
 2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
@@
 To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
-Variability among teams was operationalised as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
+Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
 For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-We have received initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50% drop in participation---we expect to be a sufficient sample size.
+Thus in order to achieve our main goal, i.e.
+estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
+Given the exploratory nature of our study, however, we will sample as many analysts as possible.
+We have received initial expression of interest to participate from more than 200 analysts.
 
-We will simultaneously recruit volunteers to peer-review the analyses conducted by the analysis teams through the same channels.
-Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer-reviewer to review a minimum of four analyses.
-If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
 
-All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
+All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
 Informed consent will be obtained as part of the intake form.
@@
 
-At a minimum, each analysis will be evaluated by four different reviewers, and each peer-reviewer will be randomly assigned to analyses from at least four analysis teams (the exact number will depend on the number of analysis teams and peer-reviewers recruited).
-Each peer-reviewer will register and answer a demographic and expertise questionnaire identical to that asked of the analysts.
+Each analysis will be evaluated by four different analysts teams who function as peer-reviewers. Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
 Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
@@
 All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).^[Link for peer-review: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
-Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
+Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2021-08-10 RR_manuscript/Draft_RR.Rmd
more edits

@@
 Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
-One aim of this study is to replicate previous many-analyses projects, confirming the large amount of flexibility observed in statistical analyses.
-A second aim is to extend these findings and estimate the amount of flexibility observed during measurement and operationalization.
+Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, probing previously observed flexibility in statistical analyses in order to independently confirm previously published findings and probe its generalizability to other disciplines (here speech sciences).
+Second, our study extends previous findings and estimates the amount of observed flexibility in quantifying complex human behavior (here human speech). 
+This is important because previous studies might have investigated only the lower bound of variability across analysts because analysts did not have to quantify the variables under investigation but were instead already provided with numerical data.
 
@@
 
-Extending on the many analyst approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but by the research question itself.
-This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
-The authors argue that the observed heterogeneity across analysts might be driven by flexibility in interpreting the research question.
+Extending on the many analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions. 
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself. 
+This is in line with a recent re-analysis of the study by @silberzahn2018many by @auspurg2021has.
+The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might be driven by flexibility in interpreting the research question.
 TRANSITION SENTENCE
 
-In those disciplines concerned with communication, human behavior sometimes corresponds to multidimensional visual or acoustic signals.
+In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual or acoustic signals.
 The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.

### 2021-08-17 RR_manuscript/Draft_RR.Rmd
:recycle: - rephrase introduction to highlight

@@
 These researcher degrees of freedom are both a blessing and a curse.
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypotheses [e.g., @box1976science; @tukey1977exploratory; @de2014thought].
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
 Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
-These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to how already obtained numbers are statistically analyzed.
-Those numbers are usually the result of a complex measurement process that translates human behavior into numbers.
+These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.
+These data can in fact be the result of complex measurement processes that translate a phenomenon, such as human behavior, into numbers.
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under study.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
+<!-- Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
+-->
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
+In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
 <!-- TODOLATER: include number of teams when known -->
-Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
-Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, probing previously observed flexibility in statistical analyses in order to independently confirm previously published findings and probe its generalizability to other disciplines (here speech sciences).
-Second, our study extends previous findings and estimates the amount of observed flexibility in quantifying complex human behavior (here human speech). 
-This is important because previous studies might have investigated only the lower bound of variability across analysts because analysts did not have to quantify the variables under investigation but were instead already provided with numerical data.
+Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
+Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
+Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
 

### 2021-08-17 RR_manuscript/Draft_RR.Rmd
:recycle: - rephrase many-analists review section

@@
 
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to inferential statistics or the architecture of computational models.
+Extending on the many-analysts approach, @landy2018crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
+This is in line with a recent re-analysis of the study by @silberzahn2018many by @auspurg2021has.
+The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might be driven by flexibility in interpreting the research question.
+
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to statistical inference or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
@@
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
-Taken together, these aspects alone exponentially increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
-
-Extending on the many analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions. 
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself. 
-This is in line with a recent re-analysis of the study by @silberzahn2018many by @auspurg2021has.
-The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might be driven by flexibility in interpreting the research question.
-TRANSITION SENTENCE
+Taken together, these aspects alone dramatically increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
 
@@
 The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved in the operationalization and measuring of complex signals.
+The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.
 

### 2021-08-19 RR_manuscript/Draft_RR.Rmd
♻️ - minor edits re study scope

@@
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
 The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.^[Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.]

### 2021-08-19 RR_manuscript/Draft_RR.tex
♻️ - minor edits re study scope

--- 2021-05-10 RR_manuscript/Draft_RR.tex
@@
 Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
+
 These researcher degrees of freedom are both a blessing and a curse.
-
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis \citep[e.g.,][]{box1976science, tukey1977exploratory, de2014thought}.
+They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypotheses \citep[e.g.,][]{box1976science, tukey1977exploratory, de2014thought}.
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted \citep{simmons2011false}.
 Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set \citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik2020variability}.
-These studies, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference.
-Human behavior is complex and offers many ways to be translated into numbers.
+These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.
+These data can in fact be the result of complex measurement processes that translate a phenomenon, such as human behavior, into numbers.
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under study.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
-Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.
 
-In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex signal and decisions regarding the statistical analysis.
-Specifically, we discuss the impact of analytic decision making on research results obtained by N teams who had access to the same set of acoustic recordings in order to answer the same research question.
+In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
+Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
+Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
+Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
 
@@
 
-Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
+Data analysis comes with many decisions, for example how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, seeing coherent patterns in randomness \citep{brugger2001}, convincing themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceiving events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
+Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, see coherent patterns in randomness \citep{brugger2001}, convince themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceive events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
 In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
@@
 
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to inferential statistics or the architecture of computational models.
+Extending on the many-analysts approach, \citet{landy2018crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
+This is in line with a recent re-analysis of the study by \citet{silberzahn2018many} by \citet{auspurg2021has}.
+The authors argue that the observed heterogeneity across analysts in \citet{silberzahn2018many} might be driven by flexibility in interpreting the research question.
+
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to statistical inference or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
@@
 The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
-Taken together, these aspects alone exponentially increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
+Taken together, these aspects alone dramatically increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
 
-In those disciplines concerned with communication, human behavior sometimes corresponds to multidimensional visual or acoustic signals.
+In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual or acoustic signals.
 The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved in the operationalization and measuring of complex signals.
+The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.
 
@@
 
-Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
-The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
+From a phonetic viewpoint, linguistically relevant units are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
+The acoustic parameters of units are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other units \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
 A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
@@
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) \citep{hawkins2004influence}.
+For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/d, t/) \citep{hawkins2004influence}.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
 (A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
@@
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
-The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.
+To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.\footnote{Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.}
 In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.
@@
 Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
-Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and making communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and make communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
 Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
 For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~whether a certain referential expression is chosen or not, while not taking into consideration the indexical potential of speech.
+This account, however, has mainly focused on content selection \citep{gatt2013we}.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/research/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-If the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is in focus (the Noun Focus condition, NF).
+Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor.
+For instance, if the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is in focus (the Noun Focus condition, NF).
 If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
@@
 \item
-  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review data analyses.
+  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
 \item
@@
 As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
-To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variablity extracted from \citet{silberzahn2018many}.
-Variability among teams was operationalised as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
-At the mean teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-We have recieved initial expression of interest to participate from more than 200 analysts, which---even after assuming a 50\% drop in participation---we expect to be a sufficient sample size.
+To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
+Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
+For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
+Thus in order to achieve our main goal, i.e.~estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
+Given the exploratory nature of our study, however, we will sample as many analysts as possible.
+We have received initial expression of interest to participate from more than 200 analysts.
 
-We will simultaneously recruit volunteers to peer-review the analyses conducted by the analysis teams through the same channels.
-Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer-reviewer to review a minimum of four analyses.
-If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
+After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
 
-All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
+All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
 Informed consent will be obtained as part of the intake form.
@@
 All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
-Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts and peer-reviewers.
+Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
 Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.

### 2021-08-20 RR_manuscript/Draft_RR.Rmd
minor edits based on reviews

@@
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game.
+To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game, following expermintal procedures typical of the field.
 The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Focused units denote the set of all (contextually relevant) alternatives [e.g.
-@rooth1992theory].Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor.
-For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
+Focused units denote the set of all (contextually relevant) alternatives [e.g. @rooth1992theory].
+Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
+For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus (the Noun Focus condition, NF).
 If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).
@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+For the present study, N analysis teams will receive access to the entire data set generated by the production study.
+The data set is constituded by audio recordings and annotation files in a format that is typical for the field.
+The teams will be instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 
@@
 
-Since we will obtain scores for each member in the analytic teams, we will calculate the team mean and standard deviation for each predictor.
+To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we will calculate the mean and standard deviation of these predictors for each team.
 These will be entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
+The expedient of using a measurement-error term (which includes the teams' standard deviation) ensures information about within-team variance is not lost (which would be the case if including the mean only).
 

### 2021-08-20 RR_manuscript/Draft_RR.tex
minor edits based on reviews

@@
 
-\title{Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses}
+\title{Multidimensional signals and analytic flexibility: Estimating degrees of
+freedom in human speech analyses}
 
@@
 
-\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{3}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
+\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian
+University Munich, Germany.}\\\affilnum{2}{Department of Spanish and Portuguese, Rutgers University, New Brunswick,
+United States}\\\affilnum{3}{Department of Linguistics and Scandinavian Studies, University of Oslo,
+Oslo, Norway}}
 
@@
 \begin{abstract}
-Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
-Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
-Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time.
-Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
-In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
-Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
+Recent efforts to replicate published findings have uncovered
+surprisingly low success rates across disciplines. Moreover, several
+studies have highlighted the large degree of analytic flexibility in
+data analysis which can lead to substantially different conclusions
+based on the same data set. Thus, researchers have expressed their
+concerns that these researcher degrees of freedom might facilitate bias
+and can lead to claims that do not stand the test of time. Even greater
+flexibility is to be expected in fields in which the primary data lend
+themselves to a variety of possible operationalizations. The
+multidimensional, temporally extended nature of speech constitutes an
+ideal testing ground for assessing the variability in analytic
+approaches that derives not only from aspects of statistical modelling
+but also from decisions regarding the quantification of the measured
+behavior. In the present study, we will give the same speech production
+dataset to N teams of researchers and will ask them to answer the same
+research question. Using Bayesian meta analytical tools, we will
+quantify this variability and relate it to predictors related to the
+analysts and their analyses.
 \end{abstract}
 
-\keywords{crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis}
+\keywords{crowdsourcing science, data analysis, scientific transparency, speech,
+acoustic analysis}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
-In order to effectively accumulate knowledge, science needs (i) to produce data that can be replicated using the original methods and (ii) to arrive at robust conclusions substantiated by such data.
-In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates \citep[e.g.,][]{open2015estimating, camerer2018evaluating} leading to what is now referred to as the \emph{replication crisis}.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
-The latter situation has been referred to as the \emph{inference crisis} \citep{rotello2015more, starns2019assessing} and is, among other things, rooted in the inherent flexibility of data analysis \citep[often referred to as researcher degrees of freedom:][]{simmons2011false, gelman2014statistical}.
-Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
-Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
+In order to effectively accumulate knowledge, science needs (i) to
+produce data that can be replicated using the original methods and (ii)
+to arrive at robust conclusions substantiated by such data. In recent
+coordinated efforts to replicate published findings, scientific
+disciplines have uncovered surprisingly low success rates
+\citep[e.g.,][]{open2015estimating, camerer2018evaluating} leading to
+what is now referred to as the \emph{replication crisis}. Beyond the
+difficulties of replicating scientific findings, a growing body of
+evidence suggests that the conceptual conclusions are often variable
+even when researchers have access to the same data. The latter situation
+has been referred to as the \emph{inference crisis}
+\citep{rotello2015more, starns2019assessing} and is, among other things,
+rooted in the inherent flexibility of data analysis \citep[often
+referred to as researcher degrees of
+freedom:][]{simmons2011false, gelman2014statistical}. Data analysis
+involves many different steps, such as inspecting, organizing,
+transforming, and modeling the data, to name a few. Along the way,
+different methodological and analytic choices need to be made, all of
+which may influence the final interpretation of the data.
 
 These researcher degrees of freedom are both a blessing and a curse.
-They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypotheses \citep[e.g.,][]{box1976science, tukey1977exploratory, de2014thought}.
-They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted \citep{simmons2011false}.
-Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set \citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik2020variability}.
-These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.
-These data can in fact be the result of complex measurement processes that translate a phenomenon, such as human behavior, into numbers.
-This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under study.
-This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
+They are a blessing because they afford us the opportunity to look at
+nature from different angles, which, in turn, allows us to make
+important discoveries and generate new hypotheses
+\citep[e.g.,][]{box1976science, tukey1977exploratory, de2014thought}.
+They are a curse because idiosyncratic choices can lead to categorically
+different interpretations, which eventually find their way into the
+publication record where they are taken for granted
+\citep{simmons2011false}. Recent projects have shown that the
+variability between different data analysts is vast and can lead
+independent researchers to draw different conclusions from the same data
+set
+\citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik2020variability}.
+These studies, however, might still underestimate the extent to which
+analysts vary because data analysis is not restricted to the statistical
+analysis of ready-made numeric data. These data can in fact be the
+result of complex measurement processes that translate a phenomenon,
+such as human behavior, into numbers. This is particularly true for
+fields that draw conclusions about human behavior and cognition from
+multidimensional data like audio or video data. In fields working on
+human speech production, for example, researchers need to make numerous
+decisions about what to measure and how to measure it, in other words,
+how to operationalise the phenomenon under study. This is not trivial,
+given the temporal extension of the acoustic signal and its complex
+structural composition.
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
-Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
-Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
-This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
+In this article, we investigate the impact of analytic choices on
+research results when many analyst teams analyze the same speech
+production data set, a process that involves both decisions regarding
+the \emph{operationalization} of a complex signal and decisions
+regarding \emph{statistical analysis}. Specifically, we discuss the
+degree of variability in research results obtained by N teams who had to
+choose the operationalisation and statistical procedures to answer the
+same research question, on the basis of the same same set of speech
+recordings. Our goals are twofold: First, our study conceptually
+replicates previous many-analyses projects, by probing the effects of
+different statistical analyses and by assessing the generalizability of
+published findings to other disciplines (here, the speech sciences).
+Second, our study extends the scope of inquiry to include flexibility in
+the operationalisation of complex human behavior (here, human speech).
+This is an important addition in that the increased number of ``forking
+paths'' in the ``garden of analytic choices'', deriving from the many
+decisions involved in quantification, might reveal a higher degree of
+variability across analysts than what previously observed.
 
-\hypertarget{researcher-degrees-of-freedom}{%
-\subsection{Researcher degrees of freedom}\label{researcher-degrees-of-freedom}}
+\subsection{Researcher degrees of
+freedom}\label{researcher-degrees-of-freedom}
 
-Data analysis comes with many decisions, for example how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision-making procedure to apply.
-This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, see coherent patterns in randomness \citep{brugger2001}, convince themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceive events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
-In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
+Data analysis comes with many decisions, for example how to measure a
+given phenomenon or behavior, which data to submit to statistical
+modeling and which to exclude in the final analysis, or what inferential
+decision-making procedure to apply. This can be problematic because
+humans show cognitive biases that can lead to erroneous inferences.
+Humans filter the world in irrational ways
+\citep[e.g.,][]{tversky1974judgment}, see coherent patterns in
+randomness \citep{brugger2001}, convince themselves of the validity of
+prior expectations \citep[``I knew it'',][]{nickerson1998confirmation},
+and perceive events as being plausible in hindsight \citep[``I knew it
+all along'',][]{fischhoff1975hindsight}. In conjunction with an academic
+incentive system that rewards certain discovery processes more than
+others \citep{sterling1959publication, koole2012rewarding}, we often
+find ourselves exploring many possible analytic pipelines, but only
+reporting a selected few.
 
-This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured \citep{roettger2019researcher}.
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions \citep{roettger2019emergent}.
-Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}.
-This notwithstanding, there are still many unknowns regarding the extent of analytic plurality in practice.
+This issue is particularly amplified in fields in which the raw data
+lend themselves to many possible ways of being measured
+\citep{roettger2019researcher}. Combined with a wide variety of
+methodological and theoretical traditions as well as varying levels of
+statistical training across subfields, the inherent flexibility of data
+analysis might lead to a vast plurality of analytic approaches that can
+lead to different scientific conclusions \citep{roettger2019emergent}.
+Analytic flexibility has been widely discussed from a conceptual point
+of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method}
+and in regard to its application in individual scientific fields
+\citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}. This
+notwithstanding, there are still many unknowns regarding the extent of
+analytic plurality in practice.
 
-Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
-These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
-Moreover, the same data could lead to very different conclusions depending on the analytic path taken by the researcher.
-However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
+Consequently, it is likely that a good part of published papers present
+overconfident interpretations of data and statistical results based on
+idiosyncratic analytic strategies
+\citep[e.g.,][]{simmons2011false, gelman2014statistical}. These
+interpretations, and the conclusions that derive from them, are thus
+associated with an unknown degree of uncertainty (dependent on the
+strength of evidence provided) and with an unknown degree of
+generalizability (dependent on the chosen analysis). Moreover, the same
+data could lead to very different conclusions depending on the analytic
+path taken by the researcher. However, instead of being critically
+evaluated, scientific results often remain unchallenged in the
+publication record. Despite recent efforts to improve transparency and
+reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical}
+and the advent of freely available and accessible infrastructures, such
+as those provided by the Open Science Framework (osf.io), critical
+re-analyses of published analytic strategies are still uncommon because
+data sharing remains rare \citep{wicherts2006poor}.
 
-\hypertarget{crowdsourcing-alternative-analyses}{%
-\subsection{Crowdsourcing alternative analyses}\label{crowdsourcing-alternative-analyses}}
+\subsection{Crowdsourcing alternative
+analyses}\label{crowdsourcing-alternative-analyses}
 
-Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
-Analytic approaches and consequently the results varied widely between teams.
-Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
-Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
-Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.
+Recent collaborative attempts have started to shed light on how
+different analysts tackle the same data set and have revealed a large
+amount of variability. In a collaborative effort,
+\citet{silberzahn2018many} let twenty-nine independent analysis teams
+address the same research hypothesis. Analytic approaches and
+consequently the results varied widely between teams. Sixty-nine percent
+of the teams found support for the hypothesis, and 31\% did not. Out of
+the 29 analytic strategies, there were 21 unique combinations of
+covariates. Importantly, the observed variability was neither predicted
+by the team's preconceptions about the phenomenon under investigation
+nor by peer ratings of the quality of their analyses. The authors
+results suggest that analytic plurality may be an inevitable byproduct
+of the scientific process and not necessarily driven by different levels
+of expertise nor bias.
 
-Several other recent studies corroborated this analytic flexibility across different disciplines.
-\citet{dutilh2019} and \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also \citet{Parker2020} on analytic flexibility in ecology, and \citet{botvinik-nezer2020} on neuroimaging data).
-\citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
-Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
+Several other recent studies corroborated this analytic flexibility
+across different disciplines. \citet{dutilh2019} and
+\citet{starns2019assessing} investigated analysts' choices when
+inferring theoretical constructs based on the same data set using
+computational models. Both studies revealed vastly different modeling
+strategies, even though scientific conclusions were similar across
+analysis teams (see also \citet{Parker2020} on analytic flexibility in
+ecology, and \citet{botvinik-nezer2020} on neuroimaging data).
+\citet{bastiaansen2020} crowdsourced clinical recommendations based on
+analyses of an individual patient. Results suggests that analysts
+differed substantially regarding decisions related to both the
+statistical analysis of the data and the theoretical rationale behind
+interpreting the statistical results.
 
-Extending on the many-analysts approach, \citet{landy2018crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
-This is in line with a recent re-analysis of the study by \citet{silberzahn2018many} by \citet{auspurg2021has}.
-The authors argue that the observed heterogeneity across analysts in \citet{silberzahn2018many} might be driven by flexibility in interpreting the research question.
+Extending on the many-analysts approach, \citet{landy2018crowdsourcing}
+asked 15 research teams to independently design studies to answer the
+same research questions. Again, they found vast heterogeneity in
+researchers' conclusions which was not predicted by the researchers'
+expertise but seem to be more dependent on the research question itself.
+This is in line with a recent re-analysis of the study by
+\citet{silberzahn2018many} by \citet{auspurg2021has}. The authors argue
+that the observed heterogeneity across analysts in
+\citet{silberzahn2018many} might be driven by flexibility in
+interpreting the research question.
 
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to statistical inference or the architecture of computational models.
-In these studies the data sets were fixed and neither data collection nor measurement could be changed.
-However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
-This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
+While these studies attested a large degree of analytic flexibility with
+possibly impactful consequences, they only investigated analytic
+decisions related to statistical inference or the architecture of
+computational models. In these studies the data sets were fixed and
+neither data collection nor measurement could be changed. However, in
+many fields the primary raw data are complex signals that need to be
+operationalized relative to a theoretically motivated research question.
+This is especially true in the social sciences, where the phenomenon
+under investigation corresponds to both observable and unobservable
+human behavior.
 
-Decisions about how to measure a theoretical construct related to human behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
-For instance, \citet{flake2020} discuss the cascading impact that different practices can have on psychometric research.
-The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
-Taken together, these aspects alone dramatically increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
+Decisions about how to measure a theoretical construct related to human
+behavior or its underlying cognitive processes might interact with
+downstream decisions about statistical modeling and vice versa. For
+instance, \citet{flake2020} discuss the cascading impact that different
+practices can have on psychometric research. The authors highlight,
+among others, the following degrees of freedom in the choice and
+development of measures: definition of the theoretical construct,
+justification of the selected measure, description of the measure and of
+how it maps onto the construct, response coding and related
+transformations, and post-hoc modifications to the chosen measure. Taken
+together, these aspects alone dramatically increase the combinations of
+possible analytic choices, and hence flexibility in research outcomes.
 
-In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual or acoustic signals.
-The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.
+In those disciplines concerned with communication, human behavior often
+corresponds to multidimensional visual or acoustic signals. The complex
+nature of this data multiplies the number of possible analytic
+approaches, thus further increasing analytic flexibility. The present
+study looks at experimentally elicited speech production data in order
+to understand how this flexibility manifests itself in a scenario where
+several procedures are involved not only in the statistical analysis of
+numeric data, but also in the operationalization and measuring of
+complex signals necessary to derive such data.
 
-\hypertarget{s:operspeech}{%
-\subsection{Operationalizing speech}\label{s:operspeech}}
+\hypertarget{s:operspeech}{\subsection{Operationalizing
+speech}\label{s:operspeech}}
 
-Research on speech lies at the intersection of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
-One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).
+Research on speech lies at the intersection of the cognitive sciences,
+informing psychological models of language, categorization, and memory,
+guiding methods for diagnosis and therapy of speech disorders, and
+facilitating advancement in automatic speech recognition and speech
+synthesis. One major challenge in the speech sciences is the mapping
+between communicative intentions (the unobserved behavior) and their
+physical manifestation (the observed behavior).
 
-Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important analytic decision.
-Take for example the following sentence in (1).
+Speech is a complex signal that is characterized by structurally
+different acoustic landmarks distributed throughout different temporal
+domains. Thus, choosing how to measure a phenomenon of interest is an
+important analytic decision. Take for example the following sentence in
+(1).
 
-\vspace{1em}
+\vspace{1em} (1) ``I can't bear another meeting on Zoom.'' \vspace{1em}
 
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\tightlist
-\item
-  ``I can't bear another meeting on Zoom.''
-  \vspace{1em}
-\end{enumerate}
+Depending on the speaker's intention, this sentence can be said in
+different ways. For instance, if the speaker is exhausted by all their
+meetings, they might acoustically highlight the word \emph{another} or
+\emph{meeting} to contrast it with more pleasant activities. If, on the
+other hand, the speaker is just tired of video conferences, as opposed
+to say face-to-face meetings, they might acoustically highlight the word
+\emph{Zoom}.
 
-Depending on the speaker's intention, this sentence can be said in different ways.
-For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with more pleasant activities.
-If, on the other hand, the speaker is just tired of video conferences, as opposed to say face-to-face meetings, they might acoustically highlight the word \emph{Zoom}.
+If we decide to compare the speech signal associated with these two
+intentions, how can we quantify the difference between them? In other
+words, given their physical manifestation (speech), what do we measure
+and how do we measure it? Because of the continuous and transient nature
+of speech, identifying speech parameters and temporal domains within
+which to measure those parameters becomes a non-trivial task. Utterances
+stretch over several thousand milliseconds and contain different levels
+of linguistically relevant units such as phrases, words, syllables, and
+individual sounds. The researcher is thus confronted with a considerable
+number of parameters and combinations thereof to choose from.
 
-If we decide to compare the speech signal associated with these two intentions, how can we quantify the difference between them?
-In other words, given their physical manifestation (speech), what do we measure and how do we measure it?
-Because of the continuous and transient nature of speech, identifying speech parameters and temporal domains within which to measure those parameters becomes a non-trivial task.
-Utterances stretch over several thousand milliseconds and contain different levels of linguistically relevant units such as phrases, words, syllables, and individual sounds.
-The researcher is thus confronted with a considerable number of parameters and combinations thereof to choose from.
+From a phonetic viewpoint, linguistically relevant units are inherently
+multidimensional and dynamic: they consist of clusters of parameters
+that are modulated over time. The acoustic parameters of units are
+usually asynchronous, i.e.~they appear at different time points in the
+unfolding signal, and overlap with parameters of other units
+\citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
+A classical example is the distinction between voiced and voiceless
+stops in English (i.e. /b/ and /p/ in \emph{bear} vs \emph{pear}). This
+contrast is manifested by many acoustic features which can differ
+depending on several factors, such as position of the consonant in the
+word and surrounding sounds \citep{lisker1977rapid}. Furthermore,
+correlates of the contrast can even be found away from the consonant, in
+temporally distant speech units. For example, the initial /l/ of the
+English words \emph{led} and \emph{let} is affected by the voicing of
+the final consonant (/d, t/) \citep{hawkins2004influence}.
 
-From a phonetic viewpoint, linguistically relevant units are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
-The acoustic parameters of units are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other units \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
-A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
-This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
-Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
-For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/d, t/) \citep{hawkins2004influence}.
+The multiplicity of phonetic measurements grows exponentially if we look
+at larger temporal domains as is the case for suprasegmental aspects of
+speech. For example, studies investigating acoustic correlates of word
+stress (e.g.~the difference between \emph{ínsight} and \emph{incíte})
+use a wide variety of measurements, including temporal characteristics
+(duration of certain segments or sub-segmental intervals), spectral
+characteristics (intensity, formants, and spectral tilt), and
+measurements related to fundamental frequency (f0)
+\citep[e.g.,][]{gordon2017acoustic}. Moving on to the expression of
+higher-level functions, like information structure and discourse
+pragmatics, relevant acoustic cues can be distributed throughout even
+larger domains, such as phrases and whole utterances
+\citep[e.g.,][]{ladd2008intonational}. Differences in position, shape,
+and alignment of pitch modulations over multiple locations within a
+sentence are correlated with differences in discourse functions
+\citep[e.g.,][]{niebuhr2011}. The latter can also be expressed by global
+vs local pitch modulations \citep{heuven2002}, as well as acoustic
+information within the temporal or spectral domain
+\citep[e.g.,][]{van2005speech}. Extra-linguistic information, like the
+speaker's intentions, levels of emotional arousal or social identity,
+are also conveyed by broad-domain parameters, such as voice quality,
+rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
 
-The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
-Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
-The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
-Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
-
-In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
-The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{Zoom}.
+In short, when testing hypotheses on speech production data, researchers
+are faced with many choices and possibilities. The larger the functional
+domain (e.g.~segments vs words vs utterances), the higher the number of
+conceivable operationalizations. For example, several decisions have to
+be made when comparing the two realizations of the sentence in (1), one
+of which is intended to signal emphasis on \emph{another} and one of
+which emphasizes \emph{Zoom}.
 
@@
 
-Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{Zoom}?
-Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
-Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, or something else?
+Do we compare only the word \emph{another} in (2a) and (2b), or also the
+word \emph{Zoom}? Do we measure utterance-wide acoustic profiles, whole
+words, or just the stressed syllables? Do we average across the chosen
+time domain or do we measure a specific point in time? Do we measure
+fundamental frequency, intensity, or something else?
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
-(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
-The green boxes mark the word \emph{another} in both sentences; (C) Spectrogram and f0 track of the word \emph{another}, exemplifying possible operationalizations of differences in f0.}\label{fig:forkingPaths}
+\includegraphics[width=1\linewidth]{/homes/s.coretta/repos/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated
+with acoustic analyses. (A) An example of multiple possible and
+justifiable decisions when comparing two utterances; (B) Waveform and
+fundamental frequency (f0) track of the utterances \emph{I can't bear
+ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on
+ZOOM}. The green boxes mark the word \emph{another} in both sentences;
+(C) Spectrogram and f0 track of the word \emph{another}, exemplifying
+possible operationalizations of differences in f0.}\label{fig:forkingPaths}
 \end{figure}
 
-When looking at phrase-level temporal domains, the number of alternative analytic pipelines increases substantially.
-Figure \ref{fig:forkingPaths}A shows a typical example of a decision tree with which speech researchers are often confronted.
-Each of the four analytic decisions in the example have different possible options.
-Here only one particular path has been taken, and a different one would likely produce quite different results.
-Once we have decided to compare fundamental frequency of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
-As Figures \ref{fig:forkingPaths}B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
-We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data in previous work \citep[see][]{gordon2017acoustic}.
-But the journey in the garden of analytic paths goes on.
-Other important operationalization steps could involve filtering the audio signal, smoothing the extracted f0 track, removing values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.
+When looking at phrase-level temporal domains, the number of alternative
+analytic pipelines increases substantially. Figure
+\ref{fig:forkingPaths}A shows a typical example of a decision tree with
+which speech researchers are often confronted. Each of the four analytic
+decisions in the example have different possible options. Here only one
+particular path has been taken, and a different one would likely produce
+quite different results. Once we have decided to compare fundamental
+frequency of the word \emph{another} across the two utterances, there
+are still many choices to be made, all of which need to be justified. As
+Figures \ref{fig:forkingPaths}B-C illustrate, we could measure f0 at
+specific points in time like the onset of the temporal window, the
+offset, or the midpoint. We could also measure the value or time of the
+minimum or maximum f0 value. We could summarize f0 across the entire
+window and extract the mean, median or standard deviation of f0, all of
+which have been used to analyze speech data in previous work
+\citep[see][]{gordon2017acoustic}. But the journey in the garden of
+analytic paths goes on. Other important operationalization steps could
+involve filtering the audio signal, smoothing the extracted f0 track,
+removing values that substantially deviate from surrounding values or
+expectations, either manually or automatically, and so on.
 
-These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
-These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
-In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
-The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
-The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.\footnote{Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.}
-In the following section we introduce the research question and the experimental procedure of said project, and we describe the resulting data set as used in the current study.
+These decisions are intended to be made prior to any statistical
+analysis, but are at times revised a posteriori in light of unforeseen
+or surprising outcomes (i.e.~after data collection and/or preliminary
+analyses). These myriads of possible decisions are multiplied by those
+researcher degrees of freedom related to statistical analysis
+\citep[e.g.][]{wicherts2016}. In sum, speech data is made of complex
+physical signals that generates an as-of-yet unappreciated amount of
+analytic flexibility in the choice of measures and operationalizations.
+The present paper probes this garden of forking paths in the analysis of
+speech. To assess the variability in data analysis pipelines, including
+both operationalization and statistical analysis, across independent
+researchers, we provided analytic teams with an experimentally elicited
+speech production data set. The data set derives from the unpublished
+research project \emph{Prosodic encoding of redundant referring
+expressions}, which set out to investigate whether speakers acoustically
+modify utterances to signal unexpected referring expressions.\footnote{Results
+  of this research project were neither published nor publicly presented
+  and are stored on a private OSF repository.} In the following section
+we introduce the research question and the experimental procedure of
+said project, and we describe the resulting data set as used in the
+current study.
 
-\hypertarget{s:dataset}{%
-\subsection{The data set: The acoustic properties of atypical modifiers}\label{s:dataset}}
+\hypertarget{s:dataset}{\subsection{The data set: The acoustic
+properties of atypical modifiers}\label{s:dataset}}
 
-Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
-It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
-The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
-Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy \citep{grice1975logic}.
-Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+Referring is one of the most basic and prevalent uses of language and
+one of the most widely researched areas in language science. It is an
+open question how speakers choose a referring expression when they want
+to refer to a specific entity like a banana. The context within which an
+entity occurs (i.e., with other non-fruits, other fruits, or other
+bananas) plays a large part in determining the choice of referring
+expressions. Generally, speakers aim to be as informative as possible to
+uniquely establish reference to the intended object, but they are also
+resource-efficient in that they avoid redundancy \citep{grice1975logic}.
+Thus one would expect the use of a modifier, for example, only if it is
+necessary for disambiguation. For instance, one might use the adjective
+\emph{yellow} to describe a banana in a situation in which there is a
+yellow and a less ripe green banana available, but not when there is
+only one banana to begin with.
 
-Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
-Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and make communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
-Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
-For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection \citep{gatt2013we}.
+Despite the coherent idea that speakers are both rational and efficient,
+there is much evidence that speakers are often over-informative.
+Speakers use referring expressions that are more specific than strictly
+necessary for the unambiguous identification of the intended referent
+\citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant},
+which has been argued to facilitate object identification and make
+communication between speakers and listeners more efficient
+\citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
+Recent findings suggest that the utility of a referring expression
+depends on how good it is for a listener (compared to other referring
+expressions) to identify a target object. For example,
+\citet{degen2020redundancy} showed that modifiers that are less typical
+for a given referent (e.g.~a blue banana) are more likely to be used in
+an over-informative scenario (e.g.~when there is just one banana). This
+account, however, has mainly focused on content selection
+\citep{gatt2013we}.
 
-Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications \citep[e.g.,][]{ladd2008intonational}.
-Most prominently, languages use intonation to signal discourse relationships between referents, among other functions.
-Intonation marks discourse-relevant referents for being new or given information, to guide the listeners' interpretation of incoming messages.
-Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
-Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referents such as \emph{yellow banana}.
-These results are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension.
-However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalizability of the studies' conclusions.
+Even when morphosyntactically identical expressions are involved,
+speakers can modulate utterances via suprasegmental acoustic properties
+like temporal and spectral modifications
+\citep[e.g.,][]{ladd2008intonational}. Most prominently, languages use
+intonation to signal discourse relationships between referents, among
+other functions. Intonation marks discourse-relevant referents for being
+new or given information, to guide the listeners' interpretation of
+incoming messages. Beyond structuring information relative to the
+discourse, a few studies suggested that speakers might use intonation to
+signal atypical lexical combinations
+\citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}. Referential
+expressions such as \emph{blue banana} were produced with greater
+prosodic prominence than more typical referents such as \emph{yellow
+banana}. These results are in line with the idea of resource-efficient,
+rational language users who modulate their speech in order to facilitate
+listeners' comprehension. However, the above studies are based on a
+rather small sample size (10 participants) and on potentially
+anti-conservative statistical analyses, leaving reason to doubt the
+generalizability of the studies' conclusions.
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game.
-The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
-The subject and confederate were seated at the opposite sides of a table, each facing one of two computer screens.
-The participant and the experimenter could not see each other nor each others' screens.
-Figure \ref{fig:procedural} shows the experimental procedure time-line.
-After a familiarization phase, the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.
-One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
-Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
+To further illuminate the question of whether speakers modify speech to
+signal atypical referents, and overcome some of the limitations of
+previous work, thirty native German speakers were recorded in a
+production study while interacting with a confederate (one of the
+experimenters) in a referential game, following expermintal procedures
+typical of the field. The participants had to verbally instruct the
+confederate to select a specified target object out of four objects
+presented on a screen. The subject and confederate were seated at the
+opposite sides of a table, each facing one of two computer screens. The
+participant and the experimenter could not see each other nor each
+others' screens. Figure \ref{fig:procedural} shows the experimental
+procedure time-line. After a familiarization phase, the subject first
+saw four colored objects in the top left, top right, bottom left, and
+bottom right corners of the screen. One of the objects served as the
+target, another as the competitor, and the remaining two objects served
+as distractors. Objects were referred to using noun phrases consisting
+of an adjective modifier denoting color and a modified object (e.g.
+\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber',
+\emph{Rote Socken} `red socks').
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
-The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
-After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
-Reading the orthographic instructions out loud, the speaker gives the confederate verbal instructions onto which referent they should drag the cube (c).
-The confederate, in turn, drags the black cube onto the target referent (d).
-Both the arrow and the orthographic instruction disappear from the speaker's screen and a new referent is indicated by an arrow on the same display alongside a new orthographic instruction (e).
-The speaker gives the confederate verbal instructions (f) which the confederate follows by dragging the cube onto the next referent (g).}\label{fig:procedural}
+\includegraphics[width=1\linewidth]{/homes/s.coretta/repos/many_analyses/figs/procedure_plot} \caption{Experimental procedure. The upper row illustrates the
+trial sequence for the speaker (participant) and the lower row
+illustrates the trial sequence for the confederate. After a preview of
+1500ms the speaker sees an arrow indicating one of the referent (b).
+Reading the orthographic instructions out loud, the speaker gives the
+confederate verbal instructions onto which referent they should drag the
+cube (c). The confederate, in turn, drags the black cube onto the target
+referent (d). Both the arrow and the orthographic instruction disappear
+from the speaker's screen and a new referent is indicated by an arrow on
+the same display alongside a new orthographic instruction (e). The
+speaker gives the confederate verbal instructions (f) which the
+confederate follows by dragging the cube onto the next referent (g).}\label{fig:procedural}
 \end{figure}
 
-In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der COLOR OBJECT ablegen} `You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
-After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der COLOR OBJECT ablegen} `And now, you have to put the cube on top of the COLOR OBJECT') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
-The second utterance in the trial was the critical trial for analysis.
+In the center of the screen, a black cube was displayed, which could be
+moved by the experimenter. The participant would read a sentence prompt
+out loud (\emph{Du sollst den Würfel auf der COLOR OBJECT ablegen} `You
+have to put the cube on top of the COLOR OBJECT') to instruct the
+experimenter to drag the cube on top of one of the four depicted objects
+(the \emph{competitor}) using the mouse. After the experimenter had
+moved the cube as instructed, the subject would read another sentence
+prompt (\emph{Und jetzt sollst du den Würfel auf der COLOR OBJECT
+ablegen} `And now, you have to put the cube on top of the COLOR OBJECT')
+instructing the experimenter to move the cube on top of a different
+object (the \emph{target}). The second utterance in the trial was the
+critical trial for analysis.
 
-The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor.
-For instance, if the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is in focus (the Noun Focus condition, NF).
-If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
-The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
-Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming and production studies from the \emph{Prosodic encoding of redundant referring expressions} project, which was given to the analysts with the data set, can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
-Each subject produced 15 critical trials (NF condition).
-Each trial was repeated twice, yielding a total of 30 trials per participant and a grand-total of 900 (\(15 \times 2 \times 30\) participants) spoken utterances.
+The two sentence prompts were used to create a focus contrast between
+the competitor and the target object. Focused units denote the set of
+all (contextually relevant) alternatives
+\citep[e.g.][]{rooth1992theory}. Concretely, a focus contrast marks one
+of more elements in a sentence as prominent, by different linguistic
+means depending on the language. For instance, if the competitor and
+target objects differ but their color did not (e.g. \emph{yellow banana}
+vs \emph{yellow tomato}), the noun is said to be in focus (the Noun
+Focus condition, NF). If the objects are the same but differ in color
+(e.g. \emph{yellow banana} vs \emph{blue banana}), the color adjective
+is in focus (the Adjective Focus condition, AF). If both the color and
+the object differ (e.g. \emph{yellow banana} vs \emph{blue tomato}), the
+the whole noun phrase is in focus (the Adjective/Noun Focus condition,
+ANF). The NF condition constituted the experimentally relevant
+condition, while the AF and ANF conditions acted as fillers. Crucially,
+the color-object combinations in the Noun Focus (NF) condition were
+manipulated with respect to their typicality. The combinations were
+either typical (e.g. \emph{orange mandarin}), medium typical (e.g.
+\emph{green tomato}), or atypical (e.g. \emph{yellow cherry}), as
+established by a norming study that was conducted prior to the
+production experiment just described.\footnote{A detailed description of
+  the norming and production studies from the \emph{Prosodic encoding of
+  redundant referring expressions} project, which was given to the
+  analysts with the data set, can be found in
+  \texttt{methods\_norm\_prod.pdf} at (temporary link)
+  \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
+Each subject produced 15 critical trials (NF condition). Each trial was
+repeated twice, yielding a total of 30 trials per participant and a
+grand-total of 900 (\(15 \times 2 \times 30\) participants) spoken
+utterances.
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+For the present study, N analysis teams will receive access to the
+entire data set generated by the production study. The data set is
+constituded by audio recordings and annotation files in a format that is
+typical for the field. The teams will be instructed to answer the
+following research question, using the provided data set: \emph{Do
+speakers acoustically modify utterances to signal atypical word
+combinations?}
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\section{Methods}\label{methods}
 
-As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
-Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
-The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
+As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing
+speech}, researchers are faced with a large amount of analytic choices
+when analyzing a multidimensional signal such as speech. Analysts must
+identify and operationalize relevant measurements, as well as the
+temporal domain(s) from which these measurements are to be taken, and
+then possibly transform said measurements before submitting them to
+statistical models, which must be chosen alongside inferential criteria.
+The complexity of speech data constitutes the ideal testing ground to
+assess the upper bound of analytic flexibility that social science might
+face across disciplines. We will employ a meta-analytic approach to
+assess (i) the variability of the reported effects, and (ii) how
+analytic and researcher-related predictors affect the final results.
 
-In this study, we will follow the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
-The project involves the following five phases:
+In this study, we will follow the procedures proposed by
+\citet{Parker2020} and \citet{aczel2021}. The project involves the
+following five phases:
 
@@
 \item
-  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
+  \textsc{Recruitment}: We will recruit independent groups of
+  researchers to analyze the data and review others' data analyses.
 \item
-  \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+  \textsc{Team Analysis}: We will give researchers access to the speech
+  corpus and let them analyze the data as they see fit.
 \item
-  \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
+  \textsc{Review}: We will ask reviewers to generate peer-review ratings
+  of the analyses based on methods (not results).
 \item
-  \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
+  \textsc{Meta-analysis}: We will evaluate variability among the
+  different analyses and how different predictors affect the outcomes.
 \item
-  \textsc{Write-up}: We will collaboratively produce the final manuscript.
+  \textsc{Write-up}: We will collaboratively produce the final
+  manuscript.
 \end{enumerate}
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
-The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
-The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
+We estimate that this process, from the time of an in-principle
+acceptance of this Stage 1 Registered Report to the end of Phase 5, will
+take nine months. The factor most likely to delay our time-line is the
+rate of completion of the original set of analyses by independent
+analysis teams. The following sections report the criteria for sample
+size, data exclusions, data manipulations, and all the measures in the
+study.
 
-\hypertarget{phase-1-recruitment-of-analysts-and-initial-survey}{%
-\subsection{Phase 1: Recruitment of analysts and initial survey}\label{phase-1-recruitment-of-analysts-and-initial-survey}}
+\subsection{Phase 1: Recruitment of analysts and initial
+survey}\label{phase-1-recruitment-of-analysts-and-initial-survey}
 
-An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).\footnote{``Questions'' and ``Join Project'' buttons will be functioning when recruitment starts.
-``Join Project'' will link to the intake form.}
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
-The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
-Researchers can choose to work independently or in a small team.
-For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
-Recruitment for this project will commence upon receiving in-principle acceptance.
-As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
-To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
-Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
-For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-Thus in order to achieve our main goal, i.e.~estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
-Given the exploratory nature of our study, however, we will sample as many analysts as possible.
-We have received initial expression of interest to participate from more than 200 analysts.
+An online landing page will provide a general description of the
+project, including a short pre-recorded slide-show that summarizes the
+data set and research question
+(\url{https://many-speech-analyses.github.io}).\footnote{``Questions''
+  and ``Join Project'' buttons will be functioning when recruitment
+  starts. ``Join Project'' will link to the intake form.} The project
+will be advertised via social media, using mailing lists for linguistic
+and psychological societies, and via word of mouth. The target
+population comprises active speech science researchers with a
+graduate/doctoral degree (or currently studying for a graduate/doctoral
+degree) in relevant disciplines. Researchers can choose to work
+independently or in a small team. For the sake of simplicity, we will
+refer both to a single researcher and teams as
+\textsc{analysis teams}.\footnote{Terms in small caps in this and later
+  sections are included with their definition in the glossary at the end
+  of the paper for the reader's convenience.} Recruitment for this
+project will commence upon receiving in-principle acceptance. As
+outlined above, our primary aim is to assess the variability of the
+reported effects, rather than the meta-analytic estimate of the
+investigated effect \emph{per se}. To estimate the degree of uncertainty
+around effect variability as driven by number of teams, we ran a series
+of sample size simulations with values of variability extracted from
+\citet{silberzahn2018many}. Variability among teams was operationalized
+as the standard deviation of the teams' reported effects from
+\citet{silberzahn2018many} (which we \emph{z}-scored prior to
+simulations to make it comparable to our study). For the mean of the
+teams' true standard deviation (0.68 \emph{z}-score), the simulation
+indicates that the degree of uncertainty around the estimated teams'
+standard deviation will be below 1 SD at any sample size greater than 10
+teams. Thus in order to achieve our main goal, i.e.~estimating
+variability among teams, we consider a minimum sample size of 10 teams
+as sufficient. Given the exploratory nature of our study, however, we
+will sample as many analysts as possible. We have received initial
+expression of interest to participate from more than 200 analysts.
 
-After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
+After submitting their analyses, we will ask analysts to also function
+as peer-reviewers. Each team must review four other analyses.
 
-All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-Informed consent will be obtained as part of the intake form.
+All analysts will share co-authorship on this manuscript and will
+participate in the collaborative process of producing the final
+manuscript. Informed consent will be obtained as part of the intake
+form.
 
-\hypertarget{phase-2-primary-data-analyses}{%
-\subsection{Phase 2: Primary Data Analyses}\label{phase-2-primary-data-analyses}}
+\subsection{Phase 2: Primary Data
+Analyses}\label{phase-2-primary-data-analyses}
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
-PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Questionnaires component.}.
-The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
-To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Data component.}).
+The analysis teams will register for participation and each of the
+analysts individually will answer a demographic and expertise
+questionnaire (\texttt{intake\_form.pdf}). PDF versions of all the
+questionnaires used in this study are available at LINK\footnote{Temporary
+  link:
+  \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f},
+  Questionnaires component.}. The questionnaire collects information on
+the analysts current position and self-estimated breadth and level of
+statistical expertise and acoustic analysis skills. We will then request
+that they answer the question: \emph{Do speakers acoustically modify
+utterances to signal atypical word combinations?} To do so, they will be
+given the data generated by the experiment described in Section
+\protect\hyperlink{s:dataset}{The data set}. The data will include the
+audio recordings with corresponding time-aligned transcriptions in the
+form of Praat TextGrid files (LINK\footnote{Temporary link:
+  \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f},
+  Data component.}).
 
-Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
+Once their analysis is complete, they will answer a structured
+questionnaire (\texttt{analytic\_quest.pdf}), providing information
+about their analysis technique, an explanation of their analytic
+choices, their quantitative results, and a statement describing their
+conclusions. They will also upload their analysis files (including the
+additionally derived data and text files that were used to extract and
+pre-process the acoustic data), their analysis code (if applicable), and
+a detailed journal-ready analysis section.
 
-\hypertarget{phase-3-peer-review-of-analyses}{%
-\subsection{Phase 3: Peer Review of Analyses}\label{phase-3-peer-review-of-analyses}}
+\subsection{Phase 3: Peer Review of
+Analyses}\label{phase-3-peer-review-of-analyses}
 
-Each analysis will be evaluated by four different analysts teams who function as peer-reviewers. Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
-Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
-The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+Each analysis will be evaluated by four different analysts teams who
+function as peer-reviewers. Each peer-reviewer will be randomly assigned
+to analyses from at least four analysis teams. Reviewers will evaluate
+the methods of each of their assigned analyses one at a time in a
+sequence determined by the initiating authors. The sequences will be
+systematically assigned so that, if possible, each analysis is allocated
+to each position in the sequence for at least one reviewer.
 
-The process for a single reviewer will be as follows.
-First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
-To help reviewers calibrate their rating, they will be given the following guidelines:
+The process for a single reviewer will be as follows. First, the
+reviewer will receive a description of the methods of a single analysis.
+This will include the narrative methods section, the analysis team's
+answers to the questionnaire regarding their methods, including analysis
+code and the data set. The reviewer will then be asked in an online
+questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the
+acoustic and the statistical analyses and to provide an overall rating,
+using a scale of 0-100, respectively. To help reviewers calibrate their
+rating, they will be given the following guidelines:
 
@@
   \item
-    A perfect analysis with no conceivable improvements from the reviewer.
+    A perfect analysis with no conceivable improvements from the
+    reviewer.
   \end{enumerate}
@@
   \item
-    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
+    An imperfect analysis but the needed changes are unlikely to
+    dramatically alter final interpretation.
   \end{enumerate}
@@
   \item
-    A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
+    A flawed analysis likely to produce either an unreliable estimate of
+    the relationship or an over-precise estimate of uncertainty.
   \end{enumerate}
@@
   \item
-    A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty.
+    A flawed analysis likely to produce an unreliable estimate of the
+    relationship and an over-precise estimate of uncertainty.
   \end{enumerate}
@@
   \item
-    A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.
+    A dangerously misleading analysis, certain to produce both an
+    estimate that is wrong and a substantially over-precise estimate of
+    uncertainty that places undue confidence in the incorrect estimate.
   \end{enumerate}
@@
 
-The reviewers will also be given the option to include further comments in a text box for each of the three ratings.
+The reviewers will also be given the option to include further comments
+in a text box for each of the three ratings.
 
-After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
-This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+After submitting the review, a methods section from a second analysis
+will then be made available to the reviewer. This same sequence will be
+followed until all analyses allocated to a given reviewer have been
+provided and reviewed. After providing the final review, the reviewer
+will be simultaneously presented with all four (or more) methods
+sections that the reviewer has just completed reviewing, the option to
+revise their original ratings, and a text box to provide an explanation.
 
-\hypertarget{phase-4-evaluating-variation}{%
-\subsection{Phase 4: Evaluating variation}\label{phase-4-evaluating-variation}}
+\subsection{Phase 4: Evaluating
+variation}\label{phase-4-evaluating-variation}
 
-The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. We will not conduct confirmatory tests of any a priori hypotheses. We consider our analysis exploratory.
+The initiating authors (SC, JC, TR) will conduct the analyses outlined
+in this section. We will not conduct confirmatory tests of any a priori
+hypotheses. We consider our analysis exploratory.
 
-\hypertarget{descriptive-statistics}{%
-\subsubsection{Descriptive statistics}\label{descriptive-statistics}}
+\subsubsection{Descriptive statistics}\label{descriptive-statistics}
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
+We will calculate summary statistics describing variation among
+analyses, including (a) the nature and number of acoustic measures
+(e.g.~f0 or duration), (b) the operationalization and the temporal
+domain of measurement (e.g.~mean of an interval or value at specified
+point in time), (c) the nature and number of model parameters for both
+fixed and random effects (if applicable), (d) the nature and reasoning
+behind inferential assessments (e.g.~dichotomous decision based on
+\emph{p}-values, ordinal decision based on a Bayes factor), as well as
+the (e) mean, (f) standard deviation and (g) range of the standardized
+effect sizes (see the next section for the standardization procedure).
 
-\hypertarget{s:meta-est}{%
-\subsubsection{Meta-analytic estimation}\label{s:meta-est}}
+\subsubsection{Meta-analytic estimation}\label{s:meta-est}
 
-We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
+We will investigate the variability in \textsc{reported effect sizes}
+using Bayesian meta-analytic techniques. As the measure of variability,
+we will take the meta-analytic \textsc{group-level standard deviation}
+(\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the
+analysis teams.
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
-Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-Factor-level ordering for each categorical variable will mirror that of the original analyses.
-Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
-For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e.~only the distribution of the data determines the posterior distribution).
-If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
-Model refitting will also constitute a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
+Based on the common practices currently in place within the field, we
+anticipate that researchers will use multilevel regression models, thus
+common measurements of effect size, such as Cohen's \(d\), may be
+inappropriate. Furthermore, \citet{aczel2021} suggest that directly
+asking analysts to report standardized effect sizes could bias the
+choice of analyses towards types that more straightforwardly return a
+standardized effect. Since the variables used by the analysis teams
+might substantially differ in their measurement scales (e.g, Hertz for
+frequency vs milliseconds for duration), we will standardize all
+reported effects by refitting each \textsc{reported model} with centered
+and scaled continuous variables (\emph{z}-scores, i.e.~the observed
+values subtracted from the mean divided by the standard deviation) and
+sum-coded factor variables. Factor-level ordering for each categorical
+variable will mirror that of the original analyses. Each
+\textsc{standardized model} will be fitted as a Bayesian regression
+model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms
+\citep{burkner2017} in R \citep{R-base}. For those reported models that
+were originally fitted within a frequentist approach, uniform
+distributions will be used as the priors of all parameters (with the
+restriction that only positive numbers will be included for scale
+parameters), to approximate the estimation procedure of frequentist
+models (i.e.~only the distribution of the data determines the posterior
+distribution). If a team has fitted Bayesian models, the same priors as
+reported by the team will be used in fitting the respective standardized
+model. Model refitting will also constitute a way of validating the
+reported analyses, a step recommended by \citet{aczel2021}.
 
-The coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models will be used as the \textsc{standardized effect size} (\(\eta_i\)) of each reported model.
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each standardized effect size as the \textsc{standardized standard error} (\(\text{se}_i\)).
-This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
-As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
+The coefficients of the critical predictors (i.e.~critical according to
+the analysis teams' self-reported inferential criteria) obtained from
+the standardized models will be used as the
+\textsc{standardized effect size} (\(\eta_i\)) of each reported model.
+If multiple predictors within a single analysis have been reported as
+critical, each will be included in the meta-analytic model (described in
+details in the next paragraph). Moreover, to account for the differing
+degree of uncertainty around each standardized effect size, we will use
+the standard deviation of each standardized effect size as the
+\textsc{standardized standard error} (\(\text{se}_i\)). This will enable
+us to fit a so-called ``measurement-error'' model, in which both the
+standardized effect sizes and their respective standard errors are
+entered in the meta-analytic model. As a desired consequence, effect
+sizes with a greater standard error will be weighted less than those
+with a smaller standard error in the meta-analytic calculations.
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we will conduct a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
-The outcome variable will be the set of standardized effect sizes \(\eta_i\).
-The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution \citep{knight2000}.
-The analysis teams will be entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
-The standard errors \(\text{se}_i\) will be included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-In case of divergent transitions, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
+After having obtained the standardized effect sizes \(\eta_i\) with
+related standard errors \(\text{se}_i\), for each critical predictor of
+the individual reported model, we will conduct a
+\textsc{Bayesian random-effects meta-analysis} using a multilevel
+(intercept-only) regression model. The outcome variable will be the set
+of standardized effect sizes \(\eta_i\). The likelihood of \(\eta_i\) is
+assumed to correspond to a normal distribution \citep{knight2000}. The
+analysis teams will be entered as a group-level effect (i.e.,
+\texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the
+frequentist literature). The standard errors \(\text{se}_i\) will be
+included as the standard deviation of \(\eta_i\) to fit a
+measurement-error model, as discussed above. We will use regularizing
+weakly-informative priors for the intercept \(\alpha\)
+(\(Normal(0, 1)\)) and for the group-level standard deviation
+\(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)). We will fit this
+model with 4 chains of Hamiltonian Monte-Carlo sampling for the
+estimation of the joint posterior distribution, using the No U-Turn
+Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000
+iterations (2000 for warm-up) per chain, distributed across 4 processing
+cores. In case of divergent transitions, we will increase
+\texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of
+iterations in this order until we obtain a model fit with no divergent
+transitions. The code used to run the model can be found at
+\url{https://many-speech-analyses.github.io/suppl/simulations.html}.
 
-The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
-The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
-Crucially, the posterior distribution of the \href{.smallcaps}{group-level standard deviation} \(\sigma_{\alpha_{\text{t}}}\) (i.e.~the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between the teams' analyses on a standardized scale.
+The posterior distribution of the population-level intercept \(\alpha\)
+will allow us to estimate the range of probable values of the
+standardized effect size \(\hat{\eta}\). The posterior distribution will
+further allow us to investigate the effect of a set of analytic and
+researcher-related predictors, detailed in the next section. Crucially,
+the posterior distribution of the \href{.smallcaps}{group-level standard
+deviation} \(\sigma_{\alpha_{\text{t}}}\) (i.e.~the standard deviation
+of the group-level effect of team) will allow us to quantify the degree
+of variation between the teams' analyses on a standardized scale.
 
-\hypertarget{anares-preds}{%
-\subsubsection{Analytic and researcher-related predictors affecting effect sizes}\label{anares-preds}}
+\subsubsection{Analytic and researcher-related predictors affecting
+effect sizes}\label{anares-preds}
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
+As a second step, we will investigate the extent to which the individual
+standardized effect sizes are affected by a series of
+\textsc{analytic and researcher-related predictors}.
 
-\textbf{Analytic predictors}. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
+\textbf{Analytic predictors}. We will estimate the influence of the
+following predictors related to the analytic characteristics of each
+team's reported analysis:
 
@@
 \item
-  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model {[}numeric{]}.
+  \emph{Measure of uniqueness} of individual analyses for the set of
+  predictors in each model {[}numeric{]}.
 \item
-  \emph{Measure of conservativeness} of the model specification, as the number of random/group-level effects included {[}numeric{]}.
+  \emph{Measure of conservativeness} of the model specification, as the
+  number of random/group-level effects included {[}numeric{]}.
 \item
-  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out {[}numeric{]}.
+  \emph{Number of post-hoc changes to the acoustic measurements} the
+  teams will report to have carried out {[}numeric{]}.
 \item
-  \emph{Number of models} the teams will report to have run {[}numeric{]}.
+  \emph{Number of models} the teams will report to have run
+  {[}numeric{]}.
 \item
-  \emph{Major dimension} that has been measured to answer the research question {[}categorical{]}.
+  \emph{Major dimension} that has been measured to answer the research
+  question {[}categorical{]}.
 \item
-  \emph{Temporal window} that the measurement is taken over {[}categorical{]}.
+  \emph{Temporal window} that the measurement is taken over
+  {[}categorical{]}.
 \item
-  \emph{Average peer-review rating}, as the mean of the overall peer-review ratings for each analysis {[}numeric{]}.
+  \emph{Average peer-review rating}, as the mean of the overall
+  peer-review ratings for each analysis {[}numeric{]}.
 \end{itemize}
 
-Following \citet{Parker2020}, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index \citep[SDI,][]{dice1945, sorensen1948}.
-The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
+Following \citet{Parker2020}, the measure of uniqueness of predictors
+will be assessed by the Sørensen-Dice Index
+\citep[SDI,][]{dice1945, sorensen1948}. The SDI is an index typically
+used in ecology research to compare species composition across sites.
+For our purposes, we will treat predictors as species and individual
+analyses as sites. For each pair of analyses \((X, Y)\), the SDI will be
+obtained using the following formula:
 
@@
 
-where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
+where \(|X \cap Y|\) is the number of variables common to both models in
+the pair, and \(|X|+|Y|\) is the sum of the number of variables that
+occur in each model.
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
+In order to generate a unique SDI for each analysis team, we will
+calculate the average of all pairwise SDIs for all pairs of analyses
+using the \texttt{beta.pair()} function in the betapart R package
+\citep{baselga2020}.
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
-The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}.
-Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
-These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+The major measurement dimension of each analysis will be categorized
+according to the following possible groups: \emph{duration},
+\emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral
+properties} (e.g.~frequency, center of gravity, harmonics difference,
+etc.), and \emph{other measures} (e.g.~principal components, vowel
+dispersion, etc.). The temporal window that the measurement is taken
+over is defined by the target linguistic unit. We assume the following
+relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word},
+\emph{phrase}. Since each analysis will receive more than one
+peer-review rating, we will calculate the mean rating and its standard
+deviation for each. These will be entered in the model formula as a
+measurement-error term (\texttt{me(mean,\ sd)} in brms).
 
-\textbf{Researcher-related factors}. We will also include the following predictors:
+\textbf{Researcher-related factors}. We will also include the following
+predictors:
 
@@
 \item
-  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students {[}numeric{]}.
+  \emph{Research experience} as the elapsed time from receiving the PhD.
+  Negative values will indicate that the person is a student or graduate
+  students {[}numeric{]}.
 \item
-  \emph{Initial belief} in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire {[}numeric{]}.
+  \emph{Initial belief} in the presence of an effect of atypical
+  noun-adjective pairs on acoustics, as answered during the intake
+  questionnaire {[}numeric{]}.
 \end{itemize}
 
-Since we will obtain scores for each member in the analytic teams, we will calculate the team mean and standard deviation for each predictor.
-These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+To obtain an aggregated research experience score and initial belief
+score for each team based on the members' individual scores, we will
+calculate the mean and standard deviation of these predictors for each
+team. These will be entered in the model formula as a measurement-error
+term (\texttt{me(mean,\ sd)} in brms). The expedient of using a
+measurement-error term (which includes the teams' standard deviation)
+ensures information about within-team variance is not lost (which would
+be the case if including the mean only).
 
-\textbf{Model specification}. The model will be fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model will be the standardized effect sizes and related standard deviation.
+\textbf{Model specification}. The model will be fitted as a
+measurement-error model, with the predictors detailed in the preceding
+paragraphs. The outcome variable of the model will be the standardized
+effect sizes and related standard deviation.
 
-A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
-The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
-The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for the intercept and the predictors we will use a normal distribution with mean 0 and standard deviation 1.
-The model will be run with the same settings as with the meta-analytic model.
-The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
+A normal distribution will be used as the likelihood function of
+\(\alpha_{t[i]}\). The mean of \(\alpha_{t[i]}\) is modeled on the basis
+of the overall intercept \(\beta\) and on the coefficients of each
+predictor. The numeric predictors will be centered and scaled and the
+categorical predictors will be sum coded. As the prior for the intercept
+and the predictors we will use a normal distribution with mean 0 and
+standard deviation 1. The model will be run with the same settings as
+with the meta-analytic model. The code used to run the model can be
+found at
+\url{https://many-speech-analyses.github.io/suppl/simulations.html}.
 
-\hypertarget{ana-archive}{%
-\subsubsection{Data management}\label{ana-archive}}
+\subsubsection{Data management}\label{ana-archive}
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
-Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
-Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
-We will also archive copies of our survey instruments from analysts and peer-reviewers.
+All relevant data, code, and materials will be publicly archived on the
+Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for
+  peer-review:
+  \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+Archived data will include the original data set distributed to all
+analysts, any edited versions of the data analyzed by individual teams,
+and the data we analyze with our meta-analyses, which include the
+standardized effect sizes, the statistics describing variation in model
+structure among analysis teams, and the anonymized answers to our
+questionnaires of analysts. Similarly, we will archive both the analysis
+code used for each individual analysis and the code from our
+meta-analyses. We will also archive copies of our survey instruments
+from analysts and peer-reviewers.
 
-We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
-We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+We will exclude from our synthesis any individual analysis submitted
+after we have completed peer review or those unaccompanied by analysis
+files that allow us to understand what the analysts did. We will also
+exclude any individual analysis that does not produce an outcome that
+can be interpreted as an answer to our primary question.
 
-\hypertarget{phase-5-collaborative-write-up-of-manuscript}{%
-\subsection{Phase 5: Collaborative Write-Up of Manuscript}\label{phase-5-collaborative-write-up-of-manuscript}}
+\subsection{Phase 5: Collaborative Write-Up of
+Manuscript}\label{phase-5-collaborative-write-up-of-manuscript}
 
-Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
+Analysts and initiating authors will discuss the limitations, results,
+and implications of the study and collaborate on writing the final
+manuscript for review as a stage-2 Registered Report.
 
-\hypertarget{author-contributions}{%
-\section{Author contributions}\label{author-contributions}}
+\section{Author contributions}\label{author-contributions}
 
-See image at LINK {[}for peer-review, see figure \texttt{credit-taxonomy.png} attached with submission{]}.
+See image at LINK {[}for peer-review, see figure
+\texttt{credit-taxonomy.png} attached with submission{]}.
 
-\hypertarget{conflicts-of-interest}{%
-\section{Conflicts of interest}\label{conflicts-of-interest}}
+\section{Conflicts of interest}\label{conflicts-of-interest}
 
@@
 
-\hypertarget{glossary}{%
-\section{Glossary}\label{glossary}}
+\section{Glossary}\label{glossary}
 
@@
 \item
-  \textbf{Reported effect sizes}: effect sizes reported by each analysis team.
+  \textbf{Reported effect sizes}: effect sizes reported by each analysis
+  team.
 \item
@@
 \item
-  \textbf{Standardized effect sizes}: (\(\eta_i\)) effect sizes returned by the standardized models.
+  \textbf{Standardized effect sizes}: (\(\eta_i\)) effect sizes returned
+  by the standardized models.
 \item
-  \textbf{Standardized standard error}: (\(\text{se}_i\)) standard deviation of the standardized effect sizes.
+  \textbf{Standardized standard error}: (\(\text{se}_i\)) standard
+  deviation of the standardized effect sizes.
 \item
-  \textbf{Bayesian random-effects meta-analysis} and \textbf{meta-analytic model}: multilevel intercept-only regression model for meta-analysis.
+  \textbf{Bayesian random-effects meta-analysis} and
+  \textbf{meta-analytic model}: multilevel intercept-only regression
+  model for meta-analysis.
 \item
-  \textbf{Meta-analytic group-level standard deviation}: (\(\sigma_{\alpha_{\text{t}}}\)) standard deviation of the group-level effect of team returned by the meta-analytic model.
+  \textbf{Meta-analytic group-level standard deviation}:
+  (\(\sigma_{\alpha_{\text{t}}}\)) standard deviation of the group-level
+  effect of team returned by the meta-analytic model.
 \item
-  \textbf{Analytic and researcher-related predictors}: predictors used in the model that assess the effect of analytic and researcher-related factors on the standardized effects.
+  \textbf{Analytic and researcher-related predictors}: predictors used
+  in the model that assess the effect of analytic and researcher-related
+  factors on the standardized effects.
 \end{itemize}

### 2021-08-30 RR_manuscript/Draft_RR.tex
♻️ - add citation to stevens 2000

--- 2021-08-19 RR_manuscript/Draft_RR.tex
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, or something else?
+Do we measure fundamental frequency, intensity, or something else \citep{stevens2000}?
 
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.Concretely, a focus contrast encodes information that is assumed to be contrary to the presuppositions of the interlocutor.
-For instance, if the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is in focus (the Noun Focus condition, NF).
+Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.
+Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
+For instance, if the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is said to be in focus (the Noun Focus condition, NF).
 If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study and will be instructed to answer the following research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+For the present study, N analysis teams will receive access to the entire data set generated by the production study.
+The data set is constituded by audio recordings and annotation files in a format that is typical for the field.
+The teams will be instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 
@@
 
-Since we will obtain scores for each member in the analytic teams, we will calculate the team mean and standard deviation for each predictor.
+To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we will calculate the mean and standard deviation of these predictors for each team.
 These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+The expedient of using a measurement-error term (which includes the teams' standard deviation) ensures information about within-team variance is not lost (which would be the case if including the mean only).
 

### 2021-09-04 RR_manuscript/Draft_RR.Rmd
♻️ - add citation to stevens 2000
new plot and first edits (not done yet)

@@
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates [e.g., @open2015estimating; @camerer2018evaluating] leading to what is now referred to as the *replication crisis*.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that researchers' conclusions often vary even when they have access to the same data.
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
@@
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under study.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under investigation.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
@@
 <!-- TODOLATER: include number of teams when known -->
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
+Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of raw data (here, speech recordings).
 Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
 Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
-This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
+This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
 
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions [@roettger2019emergent].
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of quantitative training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions [@roettger2019emergent].
 Analytic flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g.
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
+In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
 Analytic approaches and consequently the results varied widely between teams.
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.
+
+The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
 
@@
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
-Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
+Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
@@
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
-This is in line with a recent re-analysis of the study by @silberzahn2018many by @auspurg2021has.
-The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might be driven by flexibility in interpreting the research question.
+This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
+The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might have been driven by flexibility in statistically interpreting the research question.
 
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to statistical inference or the architecture of computational models.
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
+Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking path related to measurement.
+
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
@@
 
-In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual or acoustic signals.
-The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.
+In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual and/or acoustic signals.
+The complex nature of this data exponentiates the number of possible analytic approaches, thus further increasing analytic flexibility.
+In order to estimate this increased flexibility, the present study looks at experimentally elicited speech production data.  
+<!--in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.-->
 
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important analytic decision.
+Thus, choosing how to measure a phenomenon of interest is an important analytic step.
 Take for example the following sentence in (1).
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, or something else?
+Do we measure fundamental frequency, intensity, or something else [@stevens2000]?
 

### 2021-09-11 RR_manuscript/Draft_RR.Rmd
♻️ - fix biblio info

--- 2021-08-20 RR_manuscript/Draft_RR.Rmd
@@
 
-Extending on the many-analysts approach, @landy2018crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
+Extending on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.

### 2021-09-11 RR_manuscript/Draft_RR.tex
♻️ - fix biblio info

@@
 
-Extending on the many-analysts approach, \citet{landy2018crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
+Extending on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.

### 2021-09-12 RR_manuscript/Draft_RR.Rmd
final edits

@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important analytic step.
+Thus, choosing how to measure a communictive intention of interest is an important analytic step.
 Take for example the following sentence in (1).
@@
 the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
-Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
+Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
@@
 
-In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom*.
+For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom* (see 2a and 2b).
 
@@
 Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
-Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
+Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
 Do we average across the chosen time domain or do we measure a specific point in time?
@@
 Each of the four analytic decisions in the example have different possible options.
-Here only one particular path has been taken, and a different one would likely produce quite different results.
+Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
 Once we have decided to compare fundamental frequency of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
+
 In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provide analytic teams with an experimentally elicited speech production data set.
 The data set derives from the unpublished research project *Prosodic encoding of redundant referring expressions*, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.^[Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.]
@@
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science. 
-It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
+When trying to refer to a banana, what does a speaker say and how do they say it in a given context.
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
@@
 when there is just one banana).
-This account, however, has mainly focused on content selection [@gatt2013we].
+This account, however, has mainly focused on content selection [@gatt2013we], i.e. what words to use.
 
 Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications [e.g., @ladd2008intonational].
-Most prominently, languages use intonation to signal discourse relationships between referents, among other functions.
+Most prominently, languages can use intonation to signal discourse relationships between referents.
 Intonation marks discourse-relevant referents for being new or given information, to guide the listeners’ interpretation of incoming messages.
@@
 These results are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension.
-However, the above studies are based on a rather small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalizability of the studies' conclusions.
+However, the above studies are based on a small sample size (10 participants) and on potentially anti-conservative statistical analyses, leaving reason to doubt the generalizability of the studies' conclusions.
 
-To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game, following expermintal procedures typical of the field.
+To further illuminate the question of whether speakers modify speech to signal atypical referents, and overcome some of the limitations of previous work, thirty native German speakers were recorded in a production study while interacting with a confederate (one of the experimenters) in a referential game, following experimental procedures typical of the field.
 The participants had to verbally instruct the confederate to select a specified target object out of four objects presented on a screen.
@@
 Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus (the Noun Focus condition, NF).
+For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
 If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).
@@
 For the present study, N analysis teams will receive access to the entire data set generated by the production study.
-The data set is constituded by audio recordings and annotation files in a format that is typical for the field.
+The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
 The teams will be instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*

### 2021-09-14 RR_manuscript/Draft_RR.Rmd
include reference to recruitment form and analytical approach questionnaire, includes temp. links

@@
 In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
-Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
+Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
@@
 <!-- TODOLATER: include number of teams when known -->
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of raw data (here, speech recordings).
-Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
-Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
+(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
 This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
@@
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective *yellow* to describe a banana in a situation in which there are a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
 
@@
 Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color did not (e.g. *yellow banana* vs *yellow tomato*), the noun is in focus (the Noun Focus condition, NF).
+For instance, if the competitor and target objects differ but their color does not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus.
+We call this the Noun Focus condition, or NF for short.
 If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), the the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
+If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), then the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
+
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
+The main repository holds three OSF components, `Data`, `Questionnaires`, and `Cache`, and it is linked to the GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
+Social media advertising will be accompanied by a short recruitment form available at LINK.^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Recruitment form.]
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
+All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Analytical approach form.]).
 Researchers can choose to work independently or in a small team.
@@
 After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
-
 All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
@@
 The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
-PDF versions of all the questionnaires used in this study are available at LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Questionnaires component.].
+A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Data component.]).
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.
 
@@
 
-Each analysis will be evaluated by four different analysts teams who function as peer-reviewers. Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
+Each analysis will be evaluated by four different analysts teams who function as peer-reviewers.
+Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
 Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
@@
 
-The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. We will not conduct confirmatory tests of any a priori hypotheses. We consider our analysis exploratory.
+The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
+We will not conduct confirmatory tests of any a priori hypotheses.
+We consider our analysis exploratory.
 
@@
 y <- c("b", "d", "e", "f")
-(2 * length(intersect(x,y))) / (length(x) + length(y))
+(2 * length(intersect(x, y))) / (length(x) + length(y))
 ```
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).^[Link for peer-review: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
+<!-- Had to remove footnote because there were too many footnotes and not enough symbols -->
+
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>, link for peer-review: <https://bit.ly/3AqU1ul>).
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.

### 2021-09-15 RR_manuscript/Draft_RR.Rmd
♻️ - fixes to RR

--- 2021-09-14 RR_manuscript/Draft_RR.Rmd
@@
 
-The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
-The main repository holds three OSF components, `Data`, `Questionnaires`, and `Cache`, and it is linked to the GitHub repository.
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at LINK.^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
+The main repository holds two OSF components, `Data` and `Questionnaires`, and it is linked to the GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
-Social media advertising will be accompanied by a short recruitment form available at LINK.^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Recruitment form.]
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
-All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (LINK^[Temporary link: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>, Analytical approach form.]).
 Researchers can choose to work independently or in a small team.
@@
 After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
+
 All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
@@
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
-A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
+The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).^[A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://osf.io/h6z8w/?view_only=6faaae5feabe4eed800a7c142fcda06f>.
+The direct link to the intake form questionnaire is <https://osf.io/w7db5/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
-These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.^[These can be found in the `Data` component at <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
 
-Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.^[Direct link: <https://osf.io/ad862/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
@@
 This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.^[Direct link: <https://osf.io/a3urw/?view_only=6faaae5feabe4eed800a7c142fcda06f>.]
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>, link for peer-review: <https://bit.ly/3AqU1ul>).
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>, for peer-review: <https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f>).
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.

### 2021-09-15 RR_manuscript/Draft_RR.tex
♻️ - fixes to RR

@@
 In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
-Using Bayesian meta analytical tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
+Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
 \end{abstract}
@@
 In recent coordinated efforts to replicate published findings, scientific disciplines have uncovered surprisingly low success rates \citep[e.g.,][]{open2015estimating, camerer2018evaluating} leading to what is now referred to as the \emph{replication crisis}.
-Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that the conceptual conclusions are often variable even when researchers have access to the same data.
+Beyond the difficulties of replicating scientific findings, a growing body of evidence suggests that researchers' conclusions often vary even when they have access to the same data.
 The latter situation has been referred to as the \emph{inference crisis} \citep{rotello2015more, starns2019assessing} and is, among other things, rooted in the inherent flexibility of data analysis \citep[often referred to as researcher degrees of freedom:][]{simmons2011false, gelman2014statistical}.
@@
 In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same same set of speech recordings.
-Our goals are twofold: First, our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences).
-Second, our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
-This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed.
+Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
+(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
 
@@
 This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured \citep{roettger2019researcher}.
-Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions \citep{roettger2019emergent}.
+Combined with a wide variety of methodological and theoretical traditions as well as varying levels of quantitative training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions \citep{roettger2019emergent}.
 Analytic flexibility has been widely discussed from a conceptual point of view \citep{simmons2011false, wagenmakers2012agenda, nosek2014method} and in regard to its application in individual scientific fields \citep[e.g.][]{wicherts2016, charles2019, roettger2019researcher}.
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
+In a seminal collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
 Analytic approaches and consequently the results varied widely between teams.
@@
 \citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
-Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
+Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
@@
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
-This is in line with a recent re-analysis of the study by \citet{silberzahn2018many} by \citet{auspurg2021has}.
-The authors argue that the observed heterogeneity across analysts in \citet{silberzahn2018many} might be driven by flexibility in interpreting the research question.
+This is in line with a recent re-analysis of \citet{silberzahn2018many} by \citet{auspurg2021has}.
+The authors argue that the observed heterogeneity across analysts in \citet{silberzahn2018many} might have been driven by flexibility in statistically interpreting the research question.
 
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they only investigated analytic decisions related to statistical inference or the architecture of computational models.
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
+Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking path related to measurement.
+
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
@@
 
-In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual or acoustic signals.
-The complex nature of this data multiplies the number of possible analytic approaches, thus further increasing analytic flexibility.
-The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where several procedures are involved not only in the statistical analysis of numeric data, but also in the operationalization and measuring of complex signals necessary to derive such data.
+In those disciplines concerned with communication, human behavior often corresponds to multidimensional visual and/or acoustic signals.
+The complex nature of this data exponentiates the number of possible analytic approaches, thus further increasing analytic flexibility.
+In order to estimate this increased flexibility, the present study looks at experimentally elicited speech production data.\\
 
@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a phenomenon of interest is an important analytic decision.
+Thus, choosing how to measure a communictive intention of interest is an important analytic step.
 Take for example the following sentence in (1).
@@
 For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
-Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
+Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
@@
 
-In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
-For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{Zoom}.
+For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{Zoom} (see 2a and 2b).
 
@@
 Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{Zoom}?
-Do we measure utterance-wide acoustic profiles, whole words, or just the stressed syllables?
+Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
 Do we average across the chosen time domain or do we measure a specific point in time?
@@
 Each of the four analytic decisions in the example have different possible options.
-Here only one particular path has been taken, and a different one would likely produce quite different results.
+Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
 Once we have decided to compare fundamental frequency of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
@@
 These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
+
 In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
-To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provided analytic teams with an experimentally elicited speech production data set.
+To assess the variability in data analysis pipelines, including both operationalization and statistical analysis, across independent researchers, we provide analytic teams with an experimentally elicited speech production data set.
 The data set derives from the unpublished research project \emph{Prosodic encoding of redundant referring expressions}, which set out to investigate whether speakers acoustically modify utterances to signal unexpected referring expressions.\footnote{Results of this research project were neither published nor publicly presented and are stored on a private OSF repository.}
@@
 Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
-It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
+When trying to refer to a banana, what does a speaker say and how do they say it in a given context.
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
@@
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there are a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
 
@@
 For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
-This account, however, has mainly focused on content selection \citep{gatt2013we}.
+This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~what words to use.
 
 Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications \citep[e.g.,][]{ladd2008intonational}.
-Most prominently, languages use intonation to signal discourse relationships between referents, among other functions.
+Most prominently, languages can use intonation to signal discourse relationships between referents.
 Intonation marks discourse-relevant referents for being new or given information, to guide the listeners' interpretation of incoming messages.
@@
 Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color did not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is said to be in focus (the Noun Focus condition, NF).
+For instance, if the competitor and target objects differ but their color does not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is said to be in focus.
+We call this the Noun Focus condition, or NF for short.
 If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), the the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
+If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), then the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 For the present study, N analysis teams will receive access to the entire data set generated by the production study.
-The data set is constituded by audio recordings and annotation files in a format that is typical for the field.
+The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
 The teams will be instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
@@
 The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
+
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at LINK.\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+The main repository holds two OSF components, \texttt{Data} and \texttt{Questionnaires}, and it is linked to the GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
-PDF versions of all the questionnaires used in this study are available at LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Questionnaires component.}.
+The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://osf.io/h6z8w/?view_only=6faaae5feabe4eed800a7c142fcda06f}.
+The direct link to the intake form questionnaire is \url{https://osf.io/w7db5/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files (LINK\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}, Data component.}).
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{These can be found in the \texttt{Data} component at \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
 
-Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.\footnote{Direct link: \url{https://osf.io/ad862/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
@@
 This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.\footnote{Direct link: \url{https://osf.io/a3urw/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).\footnote{Link for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}).
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.

### 2021-09-15 RR_manuscript/Draft_RR.tex
♻️ - mv links to main text; rm individual links

@@
 
-The project OSF repository contains all the materials mentioned in this paper and can be accessed at LINK.\footnote{Temporary link: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
-The main repository holds two OSF components, \texttt{Data} and \texttt{Questionnaires}, and it is linked to the GitHub repository.
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
+The main repository holds three OSF components, \texttt{Data}, \texttt{Questionnaires}, and \texttt{Cache}, and it is linked to the GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).\footnote{A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://osf.io/h6z8w/?view_only=6faaae5feabe4eed800a7c142fcda06f}.
-The direct link to the intake form questionnaire is \url{https://osf.io/w7db5/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
+A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
 The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.\footnote{These can be found in the \texttt{Data} component at \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.
 
-Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.\footnote{Direct link: \url{https://osf.io/ad862/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
 They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
@@
 This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.\footnote{Direct link: \url{https://osf.io/a3urw/?view_only=6faaae5feabe4eed800a7c142fcda06f}.}
+The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
 To help reviewers calibrate their rating, they will be given the following guidelines:
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, for peer-review: \url{https://osf.io/3bmcp/?view_only=6faaae5feabe4eed800a7c142fcda06f}).
+All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, link for peer-review: \url{https://bit.ly/3AqU1ul}).
 Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.

### 2021-09-15 RR_manuscript/Draft_RR.Rmd
♻️ - use shortened links

@@
 *green tomato*), or atypical (e.g.
-*yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming and production studies from the *Prosodic encoding of redundant referring expressions* project, which was given to the analysts with the data set, can be found in `methods_norm_prod.pdf` at (temporary link) <https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f>]
+*yellow cherry*), as established by a norming study that was conducted prior to the production experiment just described.^[A detailed description of the norming and production studies from the *Prosodic encoding of redundant referring expressions* project, which was given to the analysts with the data set, can be found in `methods_norm_prod.pdf` at <https://bit.ly/3Ahawc7>.]
 Each subject produced 15 critical trials (NF condition).
@@
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
+Social media advertising will be accompanied by a short recruitment form (`recruitment_form.pdf`)
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
+All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
 Researchers can choose to work independently or in a small team.
@@
 To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
+The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
 Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
 For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-Thus in order to achieve our main goal, i.e.
-estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
+Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
 Given the exploratory nature of our study, however, we will sample as many analysts as possible.

### 2021-09-15 RR_manuscript/Draft_RR.tex
♻️ - use shortened links

@@
 Crucially, the color-object combinations in the Noun Focus (NF) condition were manipulated with respect to their typicality.
-The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming and production studies from the \emph{Prosodic encoding of redundant referring expressions} project, which was given to the analysts with the data set, can be found in \texttt{methods\_norm\_prod.pdf} at (temporary link) \url{https://osf.io/5agn9/?view_only=3429acfd8eae4f0aafe2e17ad5b0983f}}
+The combinations were either typical (e.g.~\emph{orange mandarin}), medium typical (e.g.~\emph{green tomato}), or atypical (e.g.~\emph{yellow cherry}), as established by a norming study that was conducted prior to the production experiment just described.\footnote{A detailed description of the norming and production studies from the \emph{Prosodic encoding of redundant referring expressions} project, which was given to the analysts with the data set, can be found in \texttt{methods\_norm\_prod.pdf} at \url{https://bit.ly/3Ahawc7}.}
 Each subject produced 15 critical trials (NF condition).
@@
 The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+Social media advertising will be accompanied by a short recruitment form (\texttt{recruitment\_form.pdf})
 The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
+All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
 Researchers can choose to work independently or in a small team.
@@
 To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
+The code is available at \url{https://many-speech-analyses.github.io/suppl/simulations.html}, Section 2.\footnote{Cached model outputs can be found at \url{https://bit.ly/3AgdHAN}.}
 Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).

### 2021-09-17 RR_manuscript/Draft_RR.Rmd
♻️ - start new paragraph
final ms

@@
   org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
-corrauth: "Stefano Coretta"
-email: "s.coretta@lmu.de"
+corrauth: "Timo B. Roettger"
+email: "timo.b.roettger@iln.uio.no"
 abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
@@
 Recruitment for this project will commence upon receiving in-principle acceptance.
+
 As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.

### 2021-09-17 RR_manuscript/Draft_RR.tex
♻️ - start new paragraph
final ms

@@
 
-\corrauth{Stefano Coretta}
+\corrauth{Timo B. Roettger}
 
-\email{\href{mailto:s.coretta@lmu.de}{\nolinkurl{s.coretta@lmu.de}}}
+\email{\href{mailto:timo.b.roettger@iln.uio.no}{\nolinkurl{timo.b.roettger@iln.uio.no}}}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
 (A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
@@
 Recruitment for this project will commence upon receiving in-principle acceptance.
+
 As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.

### 2021-12-01 docs/collaborator_agreement/collaborator_agreement.Rmd
✨ - add collaborator agreement

---
title: "Collaborator Agreement"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This agreement provides guidelines for the paper: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses" accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)

### How do I become an author on the paper ?

You can become author of this paper by fulfilling all of the following requirements:

- Analyse (as an individual or in a team) the dataset to answer the research question as you see fit.
- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-14, 23.59 UTC.
- Review (as an individual or in a team) four analyses reports and submit the review report by 2022-05-31, 23.59 UTC)
- Read and approve the final manuscript (due 2022-08-31, 23.59 UTC)

Author contributions will be reported on research products using the [CRediT taxonomy](https://www.cell.com/pb/assets/raw/shared/guidelines/CRediT-taxonomy.pdf). The [Tenzing app](https://osf.io/preprints/metaarxiv/b6ywe/) may be a helpful tool to collect this contributorship information.

Principal Investigators (PIs) of contributing labs are responsible for their students and staff working on the project. This includes: honestly reporting the contributions of their lab members, evaluating whether contributions merit authorship according to the above statement and the CRediT table, and verifying that contributions are correctly described in any formal publication.

### How will authorship order be determined?

Authorship order will be organized into the following sections, with order determined as listed below.

*Section 1 (project coordinators)*. The project coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger). These three authors will be listed: Coretta, Casillas, ..., Roettger-

The coordinators have formulated the research goals and aims, developed the methodology and curated the materials, wrote, submitted and revised the Registered Report, recruited analysts and administered the project. The coordinators will also analyse the results, draft the final parts of the manuscript (Results, Discussion, Conclusion) and will incorporate comments and suggestions from all authors to create the final version of the manuscript.

*Section 2 (design of study materials and data collection)*. Two additional authors that were involved in study design and data collection (Simon Roessig, Michael Franke), will occupy position 3 and 4 in the author list.

*Section 3 (analysts)*. Position from 5 on will be occupied by all analysts involved in alphabetical order.

The final author list will be the following:
Coretta, Casillas, Roessig, Franke, ... , Roettger

### How do we handle dissenting opinions about scientific products?

In large-scale collaborations, disagreements are inevitable. Project coordinators are expected to carefully consider dissenting opinions from collaborators and, to whatever extent is reasonable, discuss the issue with the dissenter. Final decisions about the scientific product, nevertheless, will be left to the project coordinators.

### How do we handle authorship on secondary papers for this project?

It is possible that this project results in secondary papers that are based on the project’s research products. For example, the data manager for this project will lead the writing of a data paper that fully and completely documents the contents and structure of the project’s primary dataset. Prior to the full public release of the project, secondary papers should only be initiated with the consent of the project coordinators. After full public release, projects may be freely initiated without any special permission from the lead team. The only exception to these rules are projects with a primarily pedagogical purpose (for example, Master's theses). These may be initiated at any time without any special permissions from the lead team, as long as the written reports based on these projects are not disseminated publicly before the full public release of the main project. If you are working on an educational project and your institution requires posting your thesis to a public repository (such as a library repository), contact the lead team for guidance.

All secondary projects should be governed by their own collaboration agreement. By default, authors on the main paper will not be counted as authors on secondary papers. However, secondary papers should cite the primary written public report of the main project.

### Conduct

Each contributor is personally accountable for the accuracy and integrity of their work on this project. This includes ensuring that (1) you are operating in accordance with your local research rules and regulations, (2) your specific research products are honest and accurate (e.g., data, translations, code), and (3) your description of your role on the project is accurate.

### Press

Initial press releases will be coordinated by the Project coordinators. All collaborators are strongly encouraged to speak to the press, but are expected to (1) emphasize the highly collaborative nature of the research project and (2) encourage the interviewer to reach out to various members of the team.

Dissemination of results will depend on the journal embargo policies.

### Contact

We encourage you to ask questions and raise concerns about project-related matters as soon as possible. You can direct all questions to the project coordinators at <manyspeech@gmail.com>.

### 2021-12-05 docs/collaborator_agreement/collaborator_agreement.Rmd
♻️ - editcollab agreement

@@
 
-This agreement provides guidelines for the paper: "Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses" accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)
+This agreement provides guidelines for the paper: *Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses* accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)
 
@@
 - Analyse (as an individual or in a team) the dataset to answer the research question as you see fit.
-- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-14, 23.59 UTC.
+- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-15, 23.59 UTC.
 - Review (as an individual or in a team) four analyses reports and submit the review report by 2022-05-31, 23.59 UTC)
@@
 
-Principal Investigators (PIs) of contributing labs are responsible for their students and staff working on the project.
+The Team Coordinators (TCs) of contributing teams are responsible for their students and staff working on the project.
 This includes: honestly reporting the contributions of their lab members, evaluating whether contributions merit authorship according to the above statement and the CRediT table, and verifying that contributions are correctly described in any formal publication.
@@
 
-*Section 1 (project coordinators)*.
-The project coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger).
+**Section 1** Pproject Coordinators).
+The Project Coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger).
 These three authors will be listed: Coretta, Casillas, ..., Roettger-
@@
 
-*Section 2 (design of study materials and data collection)*.
+**Section 2** (design of study materials and data collection).
 Two additional authors that were involved in study design and data collection (Simon Roessig, Michael Franke), will occupy position 3 and 4 in the author list.
 
-*Section 3 (analysts)*. Position from 5 on will be occupied by all analysts involved in alphabetical order.
+**Section 3** (analysts). Position from 5 on will be occupied by all analysts involved in alphabetical order.
 
@@
 
-Each contributor is personally accountable for the accuracy and integrity of their work on this project.
-This includes ensuring that (1) you are operating in accordance with your local research rules and regulations, (2) your specific research products are honest and accurate (e.g., data, translations, code), and (3) your description of your role on the project is accurate.
+Each contributor is personally accountable for the accuracy and integrity of their work on this project. This includes ensuring that:
+
+1. You are operating in accordance with your local research rules and regulations.
+2. Your specific research products are honest and accurate (e.g., data, translations, code).
+3. Your description of your role on the project is accurate.
 
@@
 
-Initial press releases will be coordinated by the Project coordinators.
-All collaborators are strongly encouraged to speak to the press, but are expected to (1) emphasize the highly collaborative nature of the research project and (2) encourage the interviewer to reach out to various members of the team.
+Initial press releases will be coordinated by the Project coordinators. All collaborators are strongly encouraged to speak to the press, but are expected to:
+
+1. Emphasize the highly collaborative nature of the research project.
+2. Encourage the interviewer to reach out to various members of the team.
 

### 2021-12-16 docs/methods_norm_prod/methods_norm_prod.tex
🐛 - fix dead link to pics

@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+                                %%% MODIFIED: unicode-math conflics with expex; mathspects conflicts with glossaries/leipzig
+  \usepackage{fontspec} % \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 
-All pictures with natural and manipulated colors are available here: \url{https://osf.io/rdtx5/}.
+All pictures with natural and manipulated colors are available here: \url{https://osf.io/5vj2z/?view_only=076bc1dbb95146fd85547f826d1edf65}.
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth]{/Users/ste/repos/many_analyses/figs/typicality_examples}
+{\centering \includegraphics[width=0.6\linewidth]{/Users/ste/repos/many-speech/many_analyses/figs/typicality_examples}
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_competitor}
+{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many-speech/many_analyses/figs/sample_experiment_screen_competitor}
 
@@
 
-{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many_analyses/figs/sample_experiment_screen_target}
+{\centering \includegraphics[width=0.6\linewidth,frame]{/Users/ste/repos/many-speech/many_analyses/figs/sample_experiment_screen_target}
 

### 2022-04-18 scripts/r/teams-analyses.Rmd
♻️ - team analyses

---
title: "Teams analyses"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(magrittr)
```

```{r team-analyses}
teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_April 17, 2022_06.35.csv") %>%
  # Get rid of unused columns
  select(-(EndDate:UserLanguage))

# Extract the full questions text for later use
full_q_text <- teams_analyses[1,]

teams_analyses %<>% slice(-(1:2)) %>%
  # Remove test submissions
  filter(
    str_length(Q2) > 1,
    Q7 != "tba",
    StartDate != "2022-04-06 09:41:44"
  ) %>%
  # Clean
  mutate(
    Q17 = str_remove_all(Q17, '"'),
    Q17 = str_replace(Q17, "speech-and-recreation", "procambarus_mahogoni"),
    Q17 = str_replace(Q17, "paralichtys_undulatus", "paralichthys_undulatus")
  )

# Include missing OSF component names, due to inclusion of question after a few first submissions.
teams_analyses$Q17[1] <- "lasionycteris_altavela"
teams_analyses$Q16[1] <- "https://osf.io/aes8n/?view_only=232b2de4e8254af5832d63baa2a9450a"
teams_analyses$Q17[2] <- "petauroides_fistulator"
teams_analyses$Q16[2] <- "https://osf.io/k5bxr/?view_only=8d16018b339f4db58584bec4a89ccd0e"
teams_analyses$Q17[3] <- "pervagor_meeki"
teams_analyses$Q16[3] <- "https://osf.io/sfhn5/?view_only=a8cec2e3e26043f2ab0218c7a02694f2"
```

```{r review}
the_sheet <- "https://docs.google.com/spreadsheets/d/1vFPjZkB4naCNj10v0BuEWQDvo34okmcN1Mv7VkZL9po/edit#gid=0"

review <- read_sheet(the_sheet) %>%
  left_join(teams_analyses %>% select(Q17, Q16), by = c("Animal" = "Q17"))
```

### 2022-04-18 scripts/r/teams-analyses.Rmd
♻️ - save team analyses cleaned

@@
 teams_analyses$Q16[3] <- "https://osf.io/sfhn5/?view_only=a8cec2e3e26043f2ab0218c7a02694f2"
+
+write_csv(teams_analyses, "data/questionnaires/msa_data_analysis_questionnaire_cleaned.csv")
 ```

### 2022-04-19 scripts/r/teams-analyses.Rmd
♻️ - update analysis questionnaire

@@
 ```{r team-analyses}
-teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_April 17, 2022_06.35.csv") %>%
+teams_analyses <- read_csv("data/questionnaires/msa_data_analysis_questionnaire_April 19, 2022_08.06.csv") %>%
   # Get rid of unused columns
@@
 
-```{r review}
+```{r review, eval=FALSE}
 the_sheet <- "https://docs.google.com/spreadsheets/d/1vFPjZkB4naCNj10v0BuEWQDvo34okmcN1Mv7VkZL9po/edit#gid=0"

### 2022-04-19 scripts/r/teams-analyses.Rmd
✨ - prepare files with analytic questionnaire responses

@@
 library(magrittr)
+library(glue)
 ```
@@
 ```
+
+```{r}
+dir.create("data/questionnaires/msa_data_analysis_files/", showWarnings = FALSE)
+
+n_teams <- nrow(teams_analyses)
+
+for (team in 1:n_teams) {
+  animal <- teams_analyses$Q17[team]
+  file_name <- as.character(glue("data/questionnaires/msa_data_analysis_files/{animal}.txt"))
+
+  txt <- ""
+
+  for (q in 4:15) {
+    txt <- paste(
+      txt,
+      full_q_text[1,q], "\n",
+      teams_analyses[team,q],
+      "\n\n",
+      "------------------------------------------------------------------------"
+      , "\n\n",
+      sep = "\n"
+    )
+  }
+
+  write_file(txt, file_name)
+}
+```

### 2022-04-21 scripts/r/03-analyses-coding.Rmd
✨ - new analysis scripts

---
title: "03 - Analyses coding"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(ggmosaic)
library(googlesheets4)
library(magrittr)
library(glue)
```

```{r coding}
the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"

coding <- read_sheet(the_sheet) %>%
  mutate(
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "multivariate", "other")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  )

```

```{r}
coding %>%
  ggplot(aes(model)) +
  geom_bar()
```

```{r}
coding %>%
  drop_na(outcome, temporal_window) %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
```

```{r}
coding %>%
  drop_na(outcome, temporal_window) %>%
  filter(
    outcome %in% c("duration", "f0", "intensity"),
    temporal_window %in% c("segment", "word", "phrase", "sentence")
  ) %>%
  droplevels() %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
```

### 2022-06-04 data/analyses/README.Rmd
set up refit pipeline

--- 2021-12-05 docs/collaborator_agreement/collaborator_agreement.Rmd
@@
 ---
-title: "Collaborator Agreement"
-output: pdf_document
+title: "Analyses"
+output: github_document
+date: 'Last update: `r Sys.Date()`'
 ---
@@
 ```
-
-This agreement provides guidelines for the paper: *Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses* accepted as a [Registered Report](https://www.cos.io/initiatives/registered-reports) at Advances in Methods and Practices in Psychological Science ([AMPPS](https://www.psychologicalscience.org/publications/ampps).)
-
-### How do I become an author on the paper ?
-
-You can become author of this paper by fulfilling all of the following requirements:
-
-- Analyse (as an individual or in a team) the dataset to answer the research question as you see fit.
-- Submit your analysis report (as an individual or in a team), in the form of "Methods" and "Results" sections, and fill in a data analysis questionnaire by 2022-04-15, 23.59 UTC.
-- Review (as an individual or in a team) four analyses reports and submit the review report by 2022-05-31, 23.59 UTC)
-- Read and approve the final manuscript (due 2022-08-31, 23.59 UTC)
-
-Author contributions will be reported on research products using the [CRediT taxonomy](https://www.cell.com/pb/assets/raw/shared/guidelines/CRediT-taxonomy.pdf).
-The [Tenzing app](https://osf.io/preprints/metaarxiv/b6ywe/) may be a helpful tool to collect this contributorship information.
-
-The Team Coordinators (TCs) of contributing teams are responsible for their students and staff working on the project.
-This includes: honestly reporting the contributions of their lab members, evaluating whether contributions merit authorship according to the above statement and the CRediT table, and verifying that contributions are correctly described in any formal publication.
-
-### How will authorship order be determined?
-
-Authorship order will be organized into the following sections, with order determined as listed below.
-
-**Section 1** Pproject Coordinators).
-The Project Coordinators (Stefano Coretta, Joseph Casillas, and Timo Roettger) will occupy first and second author positions, respectively (Stefano Coretta and Joseph Casillas) and the last author positions (Timo Roettger).
-These three authors will be listed: Coretta, Casillas, ..., Roettger-
-
-The coordinators have formulated the research goals and aims, developed the methodology and curated the materials, wrote, submitted and revised the Registered Report, recruited analysts and administered the project.
-The coordinators will also analyse the results, draft the final parts of the manuscript (Results, Discussion, Conclusion) and will incorporate comments and suggestions from all authors to create the final version of the manuscript.
-
-**Section 2** (design of study materials and data collection).
-Two additional authors that were involved in study design and data collection (Simon Roessig, Michael Franke), will occupy position 3 and 4 in the author list.
-
-**Section 3** (analysts). Position from 5 on will be occupied by all analysts involved in alphabetical order.
-
-The final author list will be the following:
-Coretta, Casillas, Roessig, Franke, ... , Roettger
-
-### How do we handle dissenting opinions about scientific products?
-
-In large-scale collaborations, disagreements are inevitable.
-Project coordinators are expected to carefully consider dissenting opinions from collaborators and, to whatever extent is reasonable, discuss the issue with the dissenter.
-Final decisions about the scientific product, nevertheless, will be left to the project coordinators.
-
-### How do we handle authorship on secondary papers for this project?
-
-It is possible that this project results in secondary papers that are based on the project’s research products.
-For example, the data manager for this project will lead the writing of a data paper that fully and completely documents the contents and structure of the project’s primary dataset.
-Prior to the full public release of the project, secondary papers should only be initiated with the consent of the project coordinators.
-After full public release, projects may be freely initiated without any special permission from the lead team.
-The only exception to these rules are projects with a primarily pedagogical purpose (for example, Master's theses).
-These may be initiated at any time without any special permissions from the lead team, as long as the written reports based on these projects are not disseminated publicly before the full public release of the main project.
-If you are working on an educational project and your institution requires posting your thesis to a public repository (such as a library repository), contact the lead team for guidance.
-
-All secondary projects should be governed by their own collaboration agreement.
-By default, authors on the main paper will not be counted as authors on secondary papers.
-However, secondary papers should cite the primary written public report of the main project.
-
-### Conduct
-
-Each contributor is personally accountable for the accuracy and integrity of their work on this project. This includes ensuring that:
-
-1. You are operating in accordance with your local research rules and regulations.
-2. Your specific research products are honest and accurate (e.g., data, translations, code).
-3. Your description of your role on the project is accurate.
-
-### Press
-
-Initial press releases will be coordinated by the Project coordinators. All collaborators are strongly encouraged to speak to the press, but are expected to:
-
-1. Emphasize the highly collaborative nature of the research project.
-2. Encourage the interviewer to reach out to various members of the team.
-
-Dissemination of results will depend on the journal embargo policies.
-
-### Contact
-
-We encourage you to ask questions and raise concerns about project-related matters as soon as possible. You can direct all questions to the project coordinators at <manyspeech@gmail.com>.

### 2022-06-04 scripts/r/04-refit/refit-jvc.Rmd
set up refit pipeline

---
title: "Re-fit"
subtitle: "JVC"
output: html_document
date: "Last update: `r Sys.Date()`"
---

### 2022-06-04 scripts/r/04-refit/refit-sc.Rmd
set up refit pipeline

---
title: "Re-fit"
subtitle: "SC"
output: html_document
date: "Last update: `r Sys.Date()`"
---

### 2022-06-10 scripts/r/03-analyses-coding.Rmd
✨ - add code to download analyses

@@
 library(glue)
+library(osfr)
+library(cli)
 ```
+
+# Read coding sheet
 
@@
 ```
+
+# Download OSF components
+
+First, we get a list of the OSF components in the Teams Analyses component. (It takes a few seconds)
+
+```{r}
+assigned <- coding %>%
+  select(team, animal, assigned_to) %>%
+  distinct()
+
+comps <- osf_retrieve_node("https://osf.io/n3fyd/") %>%
+  osf_ls_nodes(n_max = Inf) %>%
+  left_join(y = assigned, by = c("name" = "animal"))
+```
+
+Now we get only those components that are assigned to you. Tell me who you are when prompt.
+
+```{r}
+who <- menu(c("Ste", "Joseph", "Timo"), "Who are you?")
+
+whos <- c("sc", "jvc", "tr")
+your_comps <- comps %>%
+  filter(assigned_to == whos[who])
+dir.create(glue("./data/analyses/{whos[who]}"), showWarnings = FALSE, recursive = TRUE)
+```
+
+And now we download the components in `data/analyses/`
+
+```{r}
+for (comp in 1:nrow(your_comps)) {
+  name <- your_comps$name[comp]
+  files <- osf_ls_files(your_comps[comp,])
+  dir <- glue("./data/analyses/{whos[who]}/{name}")
+  dir.create(dir, showWarnings = FALSE, recursive = TRUE)
+  cli_h1(name)
+  osf_download(
+    files,
+    path = dir,
+    recurse = TRUE,
+    conflicts = "skip",
+    verbose = TRUE, progress = TRUE
+  )
+}
+```
+
+# Basic plots
 

### 2022-06-11 scripts/r/03-analyses-coding.Rmd
add code to get models and extract estimates, ses

@@
 ```
+
+# Refit models
+
+This is just a copy/paste of what I had in the other rmd file. 
+It still needs to be cleaned up (there is probably overlap with the code above in terms of packages loaded, etc.).
+
+```{r}
+#| label: load-libs
+#| message: false
+#| warning: false
+library("here")
+library("fs")
+library("dplyr")
+library("tidyr")
+library("forcats")
+library("ggplot2")
+library("stringr")
+library("strex")
+library("purrr")
+library("broom")
+library("broom.mixed")
+```
+
+A few helpers.
+
+```{r}
+#| label: helpers
+
+# Plotting theme because Im extra
+clean_theme <- function(...) {
+  list(
+    theme_minimal(), 
+    theme(
+      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
+  )
+}
+
+# Functional sequence to get relevant info from Rds files
+clean_up <- . %>% 
+  tidy(effects = "fixed") %>% 
+  suppressWarnings() %>% 
+  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
+  select(term, estimate, se = std.error)
+
+```
+
+## Load models
+
+```{r}
+#| label: load-models
+#| eval: false
+
+# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"
+msa_models <- dir_ls(path = here("models"), regexp = ".rds$") %>% 
+  as_tibble() %>% 
+  transmute(path = value, 
+    mod_name = str_remove(path, here("models/")), 
+    mod_name = str_remove(mod_name, ".rds"), 
+    model = map(path, ~ readRDS(file = .))) %>% 
+  separate(mod_name, 
+    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
+    sep = "_", remove = F) %>% 
+  unite(group, word1, word2, sep = "_") %>% 
+  select(group, mod_name:model) %>% 
+  mutate(sum = map(model, clean_up)) %>% 
+  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+```
+
+## Table
+
+```{r}
+#| label: effect-table
+#| eval: false
+
+# Simple pandoc table of the models, estimates, se, etc.
+msa_models %>% 
+  unnest(sum) %>% 
+  select(-model) %>% 
+  knitr::kable(format = "pandoc")
+
+```
+
+## Plot
+
+```{r}
+#| label: forest-plot
+#| eval: false
+
+# Simple forest plot of the estimates +/- SE
+msa_models %>% 
+  unnest(sum) %>% 
+  mutate(typicality_lab = if_else(typicality == "cat", 
+    "Typicality = categorical", "Typicality = continuous"), 
+    mod_name = fct_reorder(mod_name, estimate)) %>% 
+  ggplot() + 
+  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
+  aes(x = estimate, y = mod_name) + 
+  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
+    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
+  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
+  labs(y = "Model", x = "Estimate ± SE") + 
+  clean_theme() + 
+  theme(strip.text.x = element_text(hjust = 0))
+```

### 2022-06-11 scripts/r/04-refit/refit-sc.Rmd
♻️ - start refitting sc models

@@
 ---
+
+```{r setup}
+knitr::opts_knit$set(root.dir = here::here())
+library(tidyverse)
+library(brms)
+```
+
+# dermatolepis_aculeatus
+
+```{r}
+msa_data <- read_csv("./data/analyses/sc/dermatolepis_aculeatus/Many Speech Analyses_measurements.csv") %>%
+  mutate(
+    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
+    adj_pitch_max.norms = scale(adj_pitch_max) %>% as.numeric(),
+    noun_pitch_max.norms= scale(noun_pitch_max) %>% as.numeric(),
+    phrase_pitch_max.norms= scale(phrase_pitch_max) %>% as.numeric()
+  ) %>%
+  filter(
+    exclude == "N",
+    condition == "NF"
+  ) %>%
+  drop_na()
+```
+
+```{r}
+# LME  noun model with one fixed effect, two random effects: speaker, noun
+dermatolepis_aculeatus_1_pitch_cat <- brm(
+  noun_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | noun),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "./data/analyses/models/dermatolepis_aculeatus_1_pitch_cat"
+)
+
+# LME  adjective model with one fixed effect, two random effects: speaker, adjective
+dermatolepis_aculeatus_2_pitch_cat <- brm(
+  adj_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "./data/analyses/models/dermatolepis_aculeatus_2_pitch_cat"
+)
+
+# LME  phrase model with one fixed effect, two random effects: speaker, phrase
+dermatolepis_aculeatus_3_pitch_cat <- brm(
+  phrase_pitch_max.norms ~ effect_cat + (1 | speaker) + (1 | phrase),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "./data/analyses/models/dermatolepis_aculeatus_3_pitch_cat"
+)
+```
+
+# epinephelus_aztecus
+
+# eriphia_laterispinis
+
+```{r}
+# listing all available csv files (30 participants in the production study)
+trials_files <- list.files(
+    path = "./osf/data/production/trial-lists/",
+    pattern = ".csv", full.names = TRUE
+    )
+
+# importing and reshaping all csv files at once
+trials <- map_dfr(
+    .x = trials_files,
+    .f = read.csv
+    )
+
+msa_data <- read.csv("data/analyses/sc/eriphia_laterispinis/processed_data/summary_data.csv") %>%
+    # keeping only the NF condition
+    filter(Condition == "NF") %>%
+    # retrieving the trial information
+    left_join(x = ., y = trials, by = c("speaker", "trial") ) %>%
+    # keeping only the relevant columns
+    select(
+        speaker, trial, condition,
+        mean_f0, mean_int, duration,
+        typicality, typ_mean, typ_sd, typ_median
+        ) %>%
+    # normalising measures per speaker
+    group_by(speaker) %>%
+    mutate(
+        mean_f0 = scale(mean_f0) %>% as.numeric(),
+        mean_int = scale(mean_int) %>% as.numeric(),
+        duration = scale(duration) %>% as.numeric()
+        ) %>%
+    # un-grouping
+    ungroup() %>%
+    # filtering out medium typical items
+    filter(typicality != "medium")  %>%
+    # converts to factor
+    mutate(effect_cat = factor(x = typicality, levels = c("atypical", "typical")))
+```
+
+```{r}
+priors <- c(
+    prior(normal(0, 1), class = Intercept),
+    prior(normal(0, 1), class = b),
+    prior(exponential(0.1), class = sd, resp = "duration"),
+    prior(exponential(0.1), class = sigma, resp = "duration"),
+    prior(exponential(0.1), class = sd, resp = "meanf0"),
+    prior(exponential(0.1), class = sigma, resp = "meanf0"),
+    prior(exponential(0.1), class = sd, resp = "meanint"),
+    prior(exponential(0.1), class = sigma, resp = "meanint")
+    )
+
+# fitting the varying intercept model
+# 4 chains with each 8000 post warm-up posterior samples
+eriphia_laterispinis_1_mult_cat <- brm(
+  bf(mvbind(mean_f0, mean_int, duration) ~
+    1 + effect_cat + (1 | speaker) ) +
+    set_rescor(rescor = TRUE),
+  prior = priors,
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/eriphia_laterispinis_1_mult_cat"
+)
+```
+
+# genyonemus_evotis
+
+# hoplostethus_macrosteus
+
+```{r}
+msa_data <- read_csv("./data/analyses/sc/hoplostethus_macrosteus/Analysis materials/Results_clean.csv") %>%
+  mutate(
+    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
+    color = factor(color),
+    durmsec = scale(durmsec) %>% as.numeric(),
+    intensity_maximum = scale(intensity_maximum) %>% as.numeric()
+  )
+
+contrasts(msa_data$color) <- "contr.sum"
+```
+
+```{r}
+hoplostethus_macrosteus_1_dur_cat <- brm(
+  durmsec ~ Observation + effect_cat + color + (1|Participant),
+  data = Results_noDurOutliers,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/hoplostethus_macrosteus_1_dur_cat"
+)
+
+hoplostethus_macrosteus_2_int_cat <- brm(
+  intensity_maximum ~ Observation + effect_cat + color + (1|Participant),
+  data = Results_noIntOutliers,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/hoplostethus_macrosteus_2_int_cat"
+)
+```
+
+# neosilurus_omanensis
+
+```{r}
+
+```
+
+# paralichthys_undulatus
+
+```{r}
+msa_data <- read_delim("./data/analyses/sc/paralichthys_undulatus/Data files/MSA-measurements.txt", delim = "\t") %>%
+  mutate(
+    Typicality = recode(Typicality, atyp = "atypical", med = "medium", typ = "typical"),
+    effect_cat = factor(Typicality, levels = c("atypical", "medium", "typical")),
+    Word.type = factor(Word.type),
+    RangeST = scale(RangeST) %>% as.numeric()
+  )
+
+contrasts(msa_data$Word.type) <- "contr.sum"
+```
+
+```{r}
+paralichthys_undulatus_1_f0_cat <- brm(
+  RangeST ~ Word.type + Typicality + (1|Speaker) + (1|Word),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat"
+)
+```
+
+# petauroides_fistulator
+
+GAM but team reported parametric effects so we could include those.
+
+# polymetme_brevirostrum
+
+```{r}
+# Get datasets
+praat_data <- read_delim("./data/analyses/sc/polymetme_brevirostrum/Data/acoustic_results.txt", delim = "\t")
+norming_data <- read_csv("./data/analyses/sc/polymetme_brevirostrum/Data/ratings_summary.csv")
+ratings <- read_csv("./osf/data/norming/ratings/ratings.csv")
+foods <- list('aprikose','kirsche','moehre','gurke','erbsen','tomate','kartoffeln','banane','zitrone','bohnen','erdbeere','mandarine','walnuss')
+# Get rid of that pesky case marking and include typicality bins
+msa_data <- norming_data %>%
+  filter(colour %in% list('braun','gelb','gruen','rot','orange')) %>% 
+  mutate(
+    object = tolower(object),
+    Typicality = case_when(
+      typ_median >= 90 ~ "typical",
+      typ_median < 25 ~ "atypical",
+      typ_median >= 25 & typ_median < 90 ~ "medium"
+    ),
+    colour = recode(colour, "braun"="braunen", "gelb"="gelben", "gruen"="gruenen", "rot"="roten", "orange"="orangen")
+  ) %>%
+  right_join(., praat_data, by = c("colour"="Adjective", "object"="Noun")) %>%
+  filter(is.na(Notes)) %>%
+  mutate(
+    across(contains("f0"), function(x) {ifelse(x == "--undefined--", NA, x)}),
+    Category = ifelse(object %in% foods, "FOOD", "NONFOOD"),
+    effect_cat = factor(Typicality, levels = c("atypical", "medium", "typical")),
+    Adj_Dur = scale(Adj_Dur) %>% as.numeric(),
+    Condition = factor(Condition),
+    Category = factor(Category)
+  )
+
+contrasts(msa_data$Category) <- "contr.sum"
+contrasts(msa_data$Condition) <- "contr.sum"
+```
+
+```{r}
+polymetme_brevirostrum_1_dur_cat <- brm(
+  Adj_Dur ~ Condition * effect_cat * Category + (Condition * effect_cat || Speaker) + (Condition || object) + (effect_cat || colour),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat"
+)
+```
+
+# saron_pictus
+
+# stygobromus_tyraica
+
+ML.

### 2022-06-11 scripts/r/04-refit/refit-jvc.Rmd
push refit-jvc for testing

@@
 subtitle: "JVC"
-output: html_document
+output: 
+  html_document:
+    toc: true
 date: "Last update: `r Sys.Date()`"
+editor_options: 
+  chunk_output_type: console
 ---
+
+```{r}
+#| label: setup
+#| include: false
+knitr::opts_chunk$set(
+  echo = TRUE, 
+  message = FALSE, 
+  warning = FALSE
+  )
+knitr::opts_knit$set(root.dir = here::here())
+```
+
+```{r}
+#| label: libs
+library("here")
+library("stringr")
+library("dplyr")
+library("readr")
+library("lme4")
+library("brms")
+```
+
+# anomalocaris_ornata
+# anthracoceros_coronata
+# arapaima_modularis
+# comanthina_maculatus
+# cromileptes_saxatilis
+# ctenosaura_limax
+# gnathosaurus_canadensis
+# gymnothorax_spinulosus
+# haematopus_fossor
+
+# lasionycteris_altavela
+
+```{r}
+#| label: lasionycteris_altavela-load-data
+# Relevant code is in 'analysis.Rmd'
+# Starting at line 327
+
+intensity_final <- read_csv(
+  here("data", "analyses", "jvc", "lasionycteris_altavela", 
+    "intensity_df.csv")) # load this is in
+
+# just look at noun focus trials
+intensity_DF <- subset(intensity_final, label == "NF")
+
+#
+# JVC: ORIGINAL MODEL (singular fit)
+#
+intensity_model_lmer <- lmer(Intensity ~ typ_mean + (1|target_name)+ (1|filename) + (1|filename:target_name),
+                       data = intensity_DF)
+
+#
+# JVC: Standardized model
+# - Model contains two variables to standardize: Intensity and typ_mean 
+# - Both variables are continuous, parameter estimate for typ_mean will be 
+#   effect size (named effect_con)
+#
+MSA_lasionycteris_altavela_intensity_DF <- intensity_DF %>% 
+  mutate(int_z = (Intensity - mean(Intensity)) / sd(Intensity), 
+    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean))
+
+lasionycteris_altavela_1_int_con <- brm(
+  int_z ~ effect_con + 
+    (1|target_name) + (1|filename) + (1|filename:target_name), 
+  data = MSA_lasionycteris_altavela_intensity_DF, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "lasionycteris_altavela_1_int_con")
+  )
+```
+
+# linckia_nattereri
+# lycodes_bradfieldi
+# naso_cassivellaunos
+# trapezia_cantonensis
+# trigonias_lachneri

### 2022-06-12 scripts/r/03-analyses-coding.Rmd
♻️ - edit analyses coding; add plots

@@
   geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
+```
+
+```{r}
+coding %>%
+  drop_na(outcome, operationalisation) %>%
+  filter(
+    outcome %in% c("duration", "f0", "intensity"),
+    temporal_window %in% c("segment", "word", "phrase", "sentence")
+  ) %>%
+  droplevels() %>%
+  ggplot() +
+  geom_mosaic(aes(x = product(outcome, operationalisation), fill = outcome))
+```
+
+```{r}
+coding %>%
+  select(framework:operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
+  distinct()
+```
+
+```{r}
+coding %>%
+  select(team, n_models) %>%
+  distinct() %>%
+  drop_na() %>%
+  summarise(mean(n_models), median(n_models), sd(n_models), min(n_models), max(n_models))
 ```

### 2022-06-12 scripts/r/04-refit/refit-sc.Rmd
♻️ - edit refit sc

@@
 # epinephelus_aztecus
+
+Lavaan.
 
@@
 
+File missing.
+
 ```{r}
@@
 # neosilurus_omanensis
+
+Script missing.
 
@@
 
+100% divergent transitions.
+
 ```{r}
@@
 
+```{r}
+# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
+trial_dat <- list.files(path = "./osf/data/production/trial-lists/",
+                       pattern = "*.csv",
+                       full.names = TRUE) %>%
+  lapply(read_csv) %>%                              
+  bind_rows
+
+# Reading in the results file output by the Praat script
+d <- read.delim("./data/analyses/sc/saron_pictus/results.txt",
+                fileEncoding = "UTF-16")
+
+# Saving original number of rows
+N <- nrow(d)
+
+# Getting rid of columns we won't need from trial_dat
+trial_dat <- trial_dat[trial_dat$condition == "NF",]
+
+# Changing the trial_dat colours to the inflected forms to match the utterances
+trial_dat$target_colour[trial_dat$target_colour == "gelb"] <- "gelben"
+trial_dat$target_colour[trial_dat$target_colour == "orange"] <- "orangen"
+trial_dat$target_colour[trial_dat$target_colour == "braun"] <- "braunen"
+trial_dat$target_colour[trial_dat$target_colour == "rot"] <- "roten"
+trial_dat$target_colour[trial_dat$target_colour == "gruen"] <- "gruenen"
+
+# Saving the target colours present in the data-set into a vector
+colours <- c("gelben", "orangen", "braunen", "roten", "gruenen")
+
+# Subsetting to only target nouns and adjectives
+d <- d[d$word_label %in% trial_dat$target_name | d$word_label %in% trial_dat$target_colour,]
+d <- droplevels(d)
+
+# Merging the data from Praat with the trial data
+d <- merge(d, trial_dat, 
+            by = c("speaker", "trial", "condition"))
+
+# Lumping all trial problems together
+d$trial_status <- ifelse(d$notes == "", "Good", "Bad")
+
+# Creating a column specifying whether a word is an adjective or noun
+d$word_class <- ifelse(d$word_label %in% colours, "adjective", "noun")
+
+# Creating a column with duration in milliseconds instead of seconds
+d$dur_ms <- d$word_duration*1000
+
+# Transforming trial to have a max value of 1
+d$trial_minmax <- (d$trial - min(d$trial)) / (max(d$trial) - min(d$trial))
+
+# Creating a data-set that is only adjectives
+adj <- d[d$word_class == "adjective",]
+
+# Removing trials with problems
+adj <- adj[adj$notes == "",]
+adj$effect_cat <- factor(adj$typicality,
+                         levels = c("atypical", "medium", "typical"))
+
+adj <- adj %>%
+  mutate(
+    trial_minmax = scale(trial_minmax) %>% as.numeric(),
+    dur_ms = scale(log(dur_ms)) %>% as.numeric()
+  )
+
+model_formula <- bf(dur_ms ~
+                      effect_cat +
+                      trial_minmax +
+                      (effect_cat + trial_minmax | speaker) +
+                      (effect_cat + trial_minmax | word_label))
+
+# Setting weakly-informative priors for lognormal model
+lognormal_priors <- c(
+  prior(normal(5.5, 1), class = "Intercept"),
+  prior(normal(0, 0.5), class = "b"),
+  prior(normal(0, 1), class = "sd"),
+  prior(normal(0, 1), class = "sigma"),
+  prior(lkj(2), class = "cor")
+)
+
+# Fitting the lognormal model to data
+saron_pictus_1_dur_cat <- brm(
+  model_formula,
+  data = adj,
+  family = gaussian,
+  prior = lognormal_priors,
+  backend = "cmdstanr",
+  control = list(adapt_delta = 0.99, max_treedepth = 12),
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/saron_pictus_1_dur_cat"
+)
+```
+
 # stygobromus_tyraica
@@
 ML.
+
+# swiftia_ruber
+
+Bayesian B-splines.
+
+# trachurus_riukiuensis
+
+# varanus_eulophotes

### 2022-06-12 scripts/r/03-analyses-coding.Rmd
♻️ - edit code to get model estimates

--- 2022-06-10 scripts/r/03-analyses-coding.Rmd
@@
 library(cli)
+library("here")
+library("fs")
+library("forcats")
+library("strex")
+library("purrr")
+library("broom")
+library("broom.mixed")
 ```
@@
 
-```{r}
+```{r comps}
 assigned <- coding %>%
@@
 
-```{r}
+```{r who}
 who <- menu(c("Ste", "Joseph", "Timo"), "Who are you?")
@@
 
-```{r}
+```{r download}
 for (comp in 1:nrow(your_comps)) {
@@
 
-# Basic plots
+# Refit models
+
+Now that the components have been downloaded, we can start refitting the models using the scripts in `scripts/r/04-refit/`.
+
+# Get estimated from refitted models
+
+A few helpers.
+
+```{r helpers}
+# Plotting theme because Im extra
+clean_theme <- function(...) {
+  list(
+    theme_minimal(), 
+    theme(
+      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
+  )
+}
+
+# Functional sequence to get relevant info from Rds files
+clean_up <- . %>% 
+  tidy(effects = "fixed") %>% 
+  suppressWarnings() %>% 
+  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
+  select(term, estimate, se = std.error)
+```
+
+```{r load-models}
+msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
+  as_tibble() %>% 
+  transmute(path = value,
+    mod_name = str_remove(path, here("data/analyses/models/")), 
+    mod_name = str_remove(mod_name, ".rds"), 
+    model = map(path, ~ readRDS(file = .))) %>% 
+  separate(mod_name, 
+    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
+    sep = "_", remove = F) %>% 
+  unite(group, word1, word2, sep = "_") %>% 
+  select(group, mod_name:model) %>% 
+  mutate(sum = map(model, clean_up)) %>% 
+  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+```
+
+```{r effect-table}
+# Simple pandoc table of the models, estimates, se, etc.
+msa_models %>% 
+  unnest(sum) %>% 
+  select(-model) %>% 
+  knitr::kable(format = "pandoc")
+```
+
+```{r forest-plot}
+# Simple forest plot of the estimates +/- SE
+msa_models %>% 
+  unnest(sum) %>% 
+  mutate(
+    typicality_lab = if_else(
+      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
+    ), 
+    mod_name = fct_reorder(mod_name, estimate)
+  ) %>% 
+  ggplot(aes(x = estimate, y = mod_name)) + 
+  geom_vline(xintercept = 0) +
+  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
+    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
+  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
+  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
+  labs(y = "Model", x = "Estimate ± SE") + 
+  clean_theme() + 
+  theme(strip.text.x = element_text(hjust = 0))
+```
+
+# Analyses coding plots
 
@@
 ```
+
+```{r}
+coding %>%
+  drop_na(outcome, operationalisation) %>%
+  filter(
+    outcome %in% c("duration", "f0", "intensity"),
+    temporal_window %in% c("segment", "word", "phrase", "sentence")
+  ) %>%
+  droplevels() %>%
+  ggplot() +
+  geom_mosaic(aes(x = product(outcome, operationalisation), fill = outcome))
+```
+
+```{r}
+coding %>%
+  select(framework:operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
+  distinct()
+```
+
+```{r}
+coding %>%
+  select(team, n_models) %>%
+  distinct() %>%
+  drop_na() %>%
+  summarise(mean(n_models), median(n_models), sd(n_models), min(n_models), max(n_models))
+```

### 2022-06-13 scripts/r/04-refit/refit-sc.Rmd
♻️ - edit refit sc

@@
 library(tidyverse)
+library(plyr)
 library(brms)
@@
 
+```{r}
+#Read in output file from Praat script
+msa <- read.delim("./data/analyses/sc/trachurus_riukiuensis/MSA-Praat-output.txt", na.strings = "--undefined--")
+
+#Read in list of NF trials (this is an edited version of one of the trial-lists on OSF)
+triallist <- read.csv("./data/analyses/sc/trachurus_riukiuensis/MSA-triallist.csv")
+
+#Merge them together
+msa2 <- merge(msa, triallist, by=c("noun","condition"))
+#Adjust factor
+msa2$comment <- as.factor(msa2$comment)
+#Remove errors (31/900) and hesitation utterances (20/900) ~ 6% of data removed
+data <- subset(msa2, comment=="NA" | comment=="noise")
+
+#Remove JW_3; too many errors and hesitations
+data <- subset(data, participant!="JW_3")
+
+#Adjust typicality variable as dummy coded factor
+data$effect_cat <- factor(data$typicality, levels = c("atypical", "medium", "typical"))
+
+#Calculate a by participant median for each f0 measure and the median absolute deviation
+#See Leys, C., Ley, C., Klein, O., Bernard, P., & Licata, L.
+(2013).
+Detecting outliers: Do not use standard deviation around the mean, use absolute deviation around the median.
+Journal of Experimental Social Psychology, 49(4), 764-766.
+by.participant.median <- data %>%
+  group_by(participant) %>%
+  dplyr::summarise( n.mad = mad(noun_peakf0), n.median = median(noun_peakf0),
+             adj.mad = mad(adj_peakf0), adj.median = median(adj_peakf0),
+             art.mad = mad(art_peakf0), art.median = median(art_peakf0),)
+
+#Merge by participant with full data
+data.mm <- merge(by.participant.median, data)
+
+#Create new dataframes for each f0 measure by removing less than 2.5 times median absolute deviation
+noun <- subset(data.mm, noun_peakf0 > n.median-(2.5*n.mad))
+#noun peak f0 removed 28 data points
+
+adjective <- subset(data.mm, adj_peakf0 > adj.median-(2.5*adj.mad))
+#adj peak f0 removed 14 data points
+
+article <- subset(data.mm, art_peakf0 > art.median-(2*art.mad))
+#art peak f0 removed 160 data points NOTE we use 2 times median absolute deviation to remove all creaky voice tokens
+
+# scale
+data <- data %>%
+  mutate(
+    art_dur = scale(art_dur) %>% as.numeric(),
+    adj_dur = scale(adj_dur) %>% as.numeric()
+  )
+
+article <- article %>%
+  mutate(
+    art_peakf0 = scale(art_peakf0) %>% as.numeric()
+  )
+
+adjective <- adjective %>%
+  mutate(
+    adj_peakf0 = scale(adj_peakf0) %>% as.numeric()
+  )
+
+noun <- noun %>%
+  mutate(
+    noun_peakf0 = scale(noun_peakf0) %>% as.numeric()
+  )
+```
+
+```{r}
+trachurus_riukiuensis_1_durart_cat <- brm(
+  art_dur ~ effect_cat + (1 | participant) + (1 | noun),
+  data = data,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/trachurus_riukiuensis_1_durart_cat"
+)
+
+trachurus_riukiuensis_2_f0art_cat <- brm(
+  art_peakf0 ~ effect_cat + (1 | participant),
+  data = article,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/trachurus_riukiuensis_2_f0art_cat"
+)
+
+trachurus_riukiuensis_3_duradj_cat <- brm(
+  adj_dur ~ effect_cat + (1|participant) + (1|noun),
+  data = data,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/trachurus_riukiuensis_3_duradj_cat"
+)
+
+trachurus_riukiuensis_4_f0adj_cat <- brm(
+  adj_peakf0 ~ effect_cat + (1|participant) + (1|noun),
+  data = adjective,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/trachurus_riukiuensis_4_f0adj_cat"
+)
+
+trachurus_riukiuensis_5_f0noun_cat <- brm(
+  noun_peakf0 ~ effect_cat + (1|participant) + (1|noun),
+  data = noun,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/trachurus_riukiuensis_5_f0noun_cat"
+)
+```
+
 # varanus_eulophotes
+
+```{r}
+# reading in data
+f0data <- read.csv("./data/analyses/sc/varanus_eulophotes/analysis/f0data-complete.csv", header = T)
+
+# new dataframe with only typicality-rated data
+f0data_cor <- f0data[f0data$typicality !="NA" & !is.na(f0data$typicality),]
+f0data_cor$avgF0 <- as.numeric(f0data_cor$avgF0) # coercing types...
+f0data_cor$effect_cat <- factor(f0data_cor$typicality, levels = c("atypical", "medium", "typical"))
+
+##### DESCRIPTIVE STATS and GRAPHS ###########
+# centering f0 values within speakers
+f0data_cor <- ddply(f0data_cor, c("speaker"), transform, centeredF0 = scale(avgF0, scale=F)) # centered
+f0data_cor <- ddply(f0data_cor, c("speaker"), transform, scaledF0 = scale(avgF0)) # z-scores
+```
+
+```{r}
+varanus_eulophotes_1_f0_cat <- brm(
+  scaledF0 ~ effect_cat + (1|speaker),
+  data = f0data_cor,
+  backend = "cmdstanr",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  file = "data/analyses/models/varanus_eulophotes_1_f0_cat"
+)
+```

### 2022-06-13 scripts/r/03-analyses-coding.Rmd
♻️ - add code to upload refitted models to OSF

@@
 
-Now that the components have been downloaded, we can start refitting the models using the scripts in `scripts/r/04-refit/`.
+Now that the components have been downloaded, we can refit the models using the scripts in `scripts/r/04-refit/`.
+
+Once all your models have been refitted, you can upload them to the OSF, in the Cache component, `models/refitted/` folder.
+
+Here's some code that does that for you.
+
+```{r upload-refitted}
+cache <- osf_retrieve_node("wds2m")
+refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
+  filter(name == "refitted")
+models <- list.files(
+  "./data/analyses/models",
+  full.names = TRUE
+)
+
+osf_upload(
+  refitted,
+  path = models,
+  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
+)
+```
 

### 2022-06-13 scripts/r/03-analyses-coding.Rmd
♻️ - add code to download refitted models from OSF

@@
 # Get estimated from refitted models
+
+We first download all the refitted models .rds files from the OSF
+
+```{r download-refitted}
+cache <- osf_retrieve_node("wds2m")
+refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)
+
+osf_download(
+  refitted_rds,
+  path = "./data/analyses/models/",
+  conflicts = "skip", progress = TRUE, verbose = TRUE
+)
+```
 

### 2022-06-14 scripts/r/04-refit/refit-jvc.Rmd
add haematopus_fossor and test

@@
 ---
+
+# Setup
 
@@
 library("here")
+library("fs")
+library("dplyr")
+library("tidyr")
+library("readr")
+library("forcats")
+library("ggplot2")
 library("stringr")
-library("dplyr")
-library("readr")
+library("strex")
+library("purrr")
 library("lme4")
 library("brms")
+library("broom")
+library("broom.mixed")
 ```
 
-# anomalocaris_ornata
-# anthracoceros_coronata
-# arapaima_modularis
-# comanthina_maculatus
-# cromileptes_saxatilis
-# ctenosaura_limax
-# gnathosaurus_canadensis
-# gymnothorax_spinulosus
-# haematopus_fossor
+```{r}
+#| label: helpers
+#| include: false
+# Plotting theme because Im extra
+clean_theme <- function(...) {
+  list(
+    theme_minimal(), 
+    theme(
+      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
+  )
+}
 
-# lasionycteris_altavela
+# Functional sequence to get relevant info from Rds files
+clean_up <- . %>% 
+  tidy(effects = "fixed") %>% 
+  suppressWarnings() %>% 
+  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
+  select(term, estimate, se = std.error)
+```
+
+# Refits
+
+## anomalocaris_ornata
+
+## anthracoceros_coronata
+
+## arapaima_modularis
+
+## comanthina_maculatus
+
+## cromileptes_saxatilis
+
+## ctenosaura_limax
+
+## gnathosaurus_canadensis
+
+## gymnothorax_spinulosus
+
+## haematopus_fossor
 
 ```{r}
-#| label: lasionycteris_altavela-load-data
+#| label: haematopus_fossor
+
+directory <- here("data", "trial-lists")
+list_of_files = dir(here("data", "trial-lists"))
+
+trial_data = data.frame()
+for(file in list_of_files) {
+  this_file = read.csv(paste0(directory, "/", file), stringsAsFactors = FALSE)
+  trial_data = rbind(trial_data, this_file)
+}
+
+trial_data$typicality = factor(trial_data$typicality)
+contrasts(trial_data$typicality) = contr.helmert(3)
+dimnames(contrasts(trial_data$typicality))[[2]] = c("atypical", "typical")
+
+#
+# DURATION
+#
+
+# Get duration data
+duration <- read_csv(here("data", "analyses", "jvc", "haematopus_fossor", 
+  "details", "analysis", "wordDurations.csv")) %>% 
+  filter(adj != "")
+
+# Merge in trial data
+duration$speaker = gsub(".TextGrid", "", duration$participant)
+duration_full = merge(duration, trial_data)
+
+# Remove errors
+duration_full = filter(duration_full, comments!="hesitation break")
+
+# Centre relevant variables
+duration_full$adjdur.c = scale(duration_full$adjdur, scale=FALSE)
+duration_full$noundur.c = scale(duration_full$noundur, scale=FALSE)
+duration_full$framedur.c = scale(duration_full$framedur, scale=FALSE)
+
+# LME models
+# Adjective duration
+adj_duration_model = lmer(adjdur.c ~ trial * typicality + (1 | adj) + (1 | speaker), duration_full)
+
+# Noun duration
+noun_duration_model = lmer(noundur.c ~ trial * typicality + (1 | noun) + (1 | speaker), duration_full)
+
+# Frame duration
+frame_duration_model = lmer(framedur.c ~ trial * typicality + (1 | speaker), duration_full)
+
+#
+# JVC: setup df
+#
+MSA_duration_df <- duration_full %>% 
+  mutate(across(c("adjdur", "noundur", "framedur"), .fns = scale, 
+    .names = "{.col}_z")) %>% 
+  mutate(effect_cat = C(typicality, treatment))
+
+# Adjective duration
+haematopus_fossor_1_adjdur_cat <- brm(
+  adjdur_z ~ trial * effect_cat + 
+    (1 | adj) + (1 | speaker), 
+  data = MSA_duration_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_1_adjdur_cat")
+  )
+
+# Noun duration
+haematopus_fossor_2_noundur_cat <- brm(
+  noundur_z ~ trial * effect_cat + 
+    (1 | noun) + (1 | speaker), 
+  data = MSA_duration_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_2_noundur_cat")
+)
+
+# Frame duration
+haematopus_fossor_3_framedur_cat <- brm(
+  framedur_z ~ trial * effect_cat + 
+    (1 | speaker), 
+  data = MSA_duration_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_3_framedur_cat")
+)
+
+#
+# JVC: same for Vowel
+#
+vowel <- read_csv(here("data", "analyses", "jvc", "haematopus_fossor", 
+  "details", "analysis", "vowelMeasurements.csv"), na = "--undefined--") %>% 
+  # Get rid of data with no word or vowel label
+  filter(word != "", vowel != "")
+
+# Merge in trial data
+vowel$speaker = gsub("\\.", "", vowel$participant)
+vowel_full = merge(vowel, trial_data)
+
+# Fix typos in word names
+vowel_full$word = gsub("banana","banane", vowel_full$word)
+vowel_full$word = gsub("braunen0","braunen", vowel_full$word)
+vowel_full$word = gsub("erbeere","erdbeere", vowel_full$word)
+vowel_full$word = gsub("greunen","gruenen", vowel_full$word)
+vowel_full$word = gsub("gruenen ","gruenen", vowel_full$word)
+vowel_full$word = gsub("orangen ","orangen", vowel_full$word)
+vowel_full$word = gsub("orangenen","orangen", vowel_full$word)
+vowel_full$word = gsub("Paprika","paprika", vowel_full$word)
+vowel_full$word = gsub("traubenn","trauben", vowel_full$word)
+
+# Fix typos in vowel label and exclude erroneously segmented segments
+vowel_full = vowel_full %>% filter(!vowel %in% c(" ", "@0", "&0", "a0", "e0", "r"))
+vowel_full$vowel = gsub("gelben","E1", vowel_full$vowel)
+vowel_full$vowel = gsub("E1o","E1", vowel_full$vowel)
+vowel_full$vowel = gsub("01","o1", vowel_full$vowel)
+vowel_full$vowel = gsub("I.*","I1", vowel_full$vowel)
+vowel_full$vowel = gsub("y.*","y1", vowel_full$vowel)
+
+# Define nouns and adjectives
+list_of_nouns = c("aprikose", "banane", "bohnen", "erbsen", "erdberre", "gurken", "kartoffeln", "kirche", "mandarine", "moehre", "paprika", "tomate", "trauben", "walnuss", "zitrone")
+vowel_full$pos = ifelse(vowel_full$word %in% list_of_nouns, "noun", "adj")
+
+# Define centralisation metric
+vowel_full = vowel_full %>% 
+  group_by(speaker) %>% 
+  mutate(centralisation = sqrt((F1 - mean(F1, na.rm=TRUE))^2 + (F2 - mean(F2, na.rm=TRUE))^2))
+
+#############
+# Analyses
+#############
+
+adj_full = vowel_full %>% filter(pos == "adj")
+noun_full = vowel_full %>% filter(pos == "noun")
+
+# Centre the variables
+noun_full$duration.c = scale(noun_full$duration, scale=FALSE)
+noun_full$intensity.c = scale(noun_full$intensity, scale=FALSE)
+noun_full$centralisation.c = scale(noun_full$centralisation, scale=FALSE)
+adj_full$duration.c = scale(adj_full$duration, scale=FALSE)
+adj_full$intensity.c = scale(adj_full$intensity, scale=FALSE)
+adj_full$centralisation.c = scale(adj_full$centralisation, scale=FALSE)
+
+# Duration analysis
+adj_vowel_duration_model = lmer(duration.c ~ trial * typicality + (1 | word) + (1 | speaker), adj_full)
+noun_vowel_duration_model = lmer(duration.c ~ trial * typicality + (1 | word) + (1 | speaker), noun_full)
+
+# Intensity analysis
+adj_vowel_int_model = lmer(intensity.c ~ trial * typicality + (1 | word) + (1 | speaker), adj_full)
+noun_vowel_int_model = lmer(intensity.c ~ trial * typicality + (1 | word) + (1 | speaker), noun_full)
+
+# Centralisation analysis
+adj_vowel_cent_model = lmer(centralisation.c ~ trial * typicality + (1 | word) + (1 | speaker), adj_full)
+noun_vowel_cent_model = lmer(centralisation.c ~ trial * typicality + (1 | word) + (1 | speaker), noun_full)
+
+#
+# JVC: standardize predictors
+#
+MSA_vowel_noun_df <- noun_full %>% 
+  mutate(across(c("duration", "intensity", "centralisation"), .fns = scale, 
+    .names = "{.col}_z")) %>% 
+  mutate(effect_cat = C(typicality, treatment))
+
+MSA_vowel_adj_df <- adj_full %>% 
+  mutate(across(c("duration", "intensity", "centralisation"), .fns = scale, 
+    .names = "{.col}_z")) %>% 
+  mutate(effect_cat = C(typicality, treatment))
+
+#
+# JVC: refit models
+#
+
+# Duration analysis
+haematopus_fossor_4_adjvoweldur_cat <- brm(
+  duration_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_adj_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_4_adjvoweldur_cat")
+)
+
+haematopus_fossor_5_nounvoweldur_cat <- brm(
+  duration_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_noun_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_5_nounvoweldur_cat")
+)
+
+# Intensity analysis
+haematopus_fossor_6_adjvowelint_cat <- brm(
+  intensity_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_adj_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_6_adjvowelint_cat")
+)
+
+haematopus_fossor_7_nounvowelint_cat <- brm(
+  intensity_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_noun_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_7_nounvowelint_cat")
+)
+
+# Centralisation analysis
+haematopus_fossor_8_adjvowelcent_cat <- brm(
+  centralisation_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_adj_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_8_adjvowelcent_cat")
+)
+
+haematopus_fossor_9_nounvowelcent_cat <- brm(
+  centralisation_z ~ trial * effect_cat + 
+    (1 | word) + (1 | speaker), 
+  data = MSA_vowel_noun_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "haematopus_fossor_9_nounvowelcent_cat")
+)
+```
+
+## lasionycteris_altavela
+
+```{r}
+#| label: lasionycteris_altavela
 # Relevant code is in 'analysis.Rmd'
@@
 
-# linckia_nattereri
-# lycodes_bradfieldi
-# naso_cassivellaunos
-# trapezia_cantonensis
-# trigonias_lachneri
+## linckia_nattereri
+
+## lycodes_bradfieldi
+
+## naso_cassivellaunos
+
+## trapezia_cantonensis
+
+## trigonias_lachneri
+
+# Results
+
+## Load models
+
+```{r}
+#| label: load-models
+
+# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"
+msa_models <- dir_ls(path = here("data", "analyses", "models"), regexp = ".rds$") %>% 
+  as_tibble() %>% 
+  transmute(path = value, 
+    mod_name = str_remove(path, here("data", "analyses", "models/")), 
+    mod_name = str_remove(mod_name, ".rds"), 
+    model = map(path, ~ readRDS(file = .))) %>% 
+  separate(mod_name, 
+    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
+    sep = "_", remove = F) %>% 
+  unite(group, word1, word2, sep = "_") %>% 
+  select(group, mod_name:model) %>% 
+  mutate(sum = map(model, clean_up)) %>% 
+  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+```
+
+## Table
+
+```{r}
+#| label: effect-table
+
+# Simple pandoc table of the models, estimates, se, etc.
+msa_models %>% 
+  unnest(sum) %>% 
+  select(-model) %>% 
+  knitr::kable(format = "pandoc")
+
+```
+
+## Plot
+
+```{r}
+#| label: forest-plot
+
+# Simple forest plot of the estimates +/- SE
+msa_models %>% 
+  unnest(sum) %>% 
+  mutate(typicality_lab = if_else(typicality == "cat", 
+    "Typicality = categorical", "Typicality = continuous"), 
+    mod_name = fct_reorder(mod_name, estimate)) %>% 
+  ggplot() + 
+  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
+  aes(x = estimate, y = mod_name) + 
+  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
+    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
+  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
+  labs(y = "Model", x = "Estimate ± SE") + 
+  clean_theme() + 
+  theme(strip.text.x = element_text(hjust = 0))
+```

### 2022-06-15 scripts/r/04-refit/refit-sc.Rmd

@@
 
-File missing.
-
 ```{r}
@@
   durmsec ~ Observation + effect_cat + color + (1|Participant),
-  data = Results_noDurOutliers,
+  data = msa_data,
   cores = 4,
@@
   intensity_maximum ~ Observation + effect_cat + color + (1|Participant),
-  data = Results_noIntOutliers,
+  data = msa_data,
   cores = 4,

### 2022-06-15 scripts/r/04_refit/refit_sc.Rmd
♻️ - edit refit sc

--- 2022-06-15 scripts/r/04-refit/refit-sc.Rmd
@@
 library(plyr)
+library(mgcv)
 library(brms)
@@
 
+Difficult case.
+
 # hoplostethus_macrosteus
@@
 
-Script missing.
+```{r}
+msa_data <- read.csv("./data/analyses/sc/neosilurus_omanensis/annotated_cleaned_data_v7.csv", stringsAsFactors = T, header = T) %>%
+  mutate(
+    effect_cat = factor(typ_cat, levels = c("atypical", "medium", "typical"))
+  )
+
+contrasts(msa_data$Condition) <- "contr.sum"
+```
 
 ```{r}
+neosilurus_omanensis_1_f0rat_cat <- brm(
+  PitchRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat"
+)
 
+neosilurus_omanensis_2_f0ranrat_cat <- brm(
+  PitchRangeRatioAtoU ~ effect_cat + (1|Participant) + (1|Adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat"
+)
+
+# Convergence issues
+neosilurus_omanensis_3_f0varrat_cat <- brm(
+  PitchVariationRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat"
+)
+
+neosilurus_omanensis_4_f0riserat_cat <- brm(
+  PitchRiseRatio ~ effect_cat + (1|Participant) + (1|Adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat"
+)
+
+# Convergence issues
+neosilurus_omanensis_5_srrat_cat <- brm(
+  SpeechRateRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
+  data = msa_data,
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat"
+)
 ```
@@
 paralichthys_undulatus_1_f0_cat <- brm(
-  RangeST ~ Word.type + Typicality + (1|Speaker) + (1|Word),
+  RangeST ~ Word.type + effect_cat + (1|Speaker) + (1|Word),
   data = msa_data,
@@
 GAM but team reported parametric effects so we could include those.
+
+```{r}
+load("./data/analyses/sc/petauroides_fistulator/mdl_data.RData")
+
+msa_data <- mdl_data %>%
+  mutate(
+    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical"))
+  )
+```
+
+```{r}
+petauroides_fistulator_1_f0_cat <- gam(
+  pitch_st ~
+    effect_cat +
+    s(id) +
+    s(trial, bs = "re") +
+    s(speaker, bs = "re") +
+    s(target_name, bs = "re") +
+    s(target_colour, bs = "re") +
+    s(competitor_name, bs = "re") +
+    s(competitor_colour, bs = "re") +
+    s(distractor1_name, bs = "re") +
+    s(distractor1_colour, bs = "re") +
+    s(distractor2_name, bs = "re") +
+    s(distractor2_colour, bs = "re"),
+  data = msa_data
+)
+
+saveRDS(petauroides_fistulator_1_f0_cat, "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds")
+```
 
@@
 
-100% divergent transitions.
+Convergence issues.
 

### 2022-06-15 scripts/r/03_analyses_coding.Rmd
♻️ - rename files from - to _

--- 2022-06-13 scripts/r/03-analyses-coding.Rmd
@@
   name <- your_comps$name[comp]
-  files <- osf_ls_files(your_comps[comp,])
+  files <- osf_ls_files(your_comps[comp,], n_max = Inf)
   dir <- glue("./data/analyses/{whos[who]}/{name}")

### 2022-06-16 scripts/r/02_teams_reviews.Rmd

---
title: "02 - Teams reviews"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(magrittr)
library(glue)
```

```{r}
cols <- str_split("StartDate,EndDate,Status,IPAddress,Progress,Duration (in seconds),Finished,RecordedDate,ResponseId,RecipientLastName,RecipientFirstName,RecipientEmail,ExternalReference,LocationLatitude,LocationLongitude,DistributionChannel,UserLanguage,Q2,Q3,Q5_2,Q5_3,Q5_4,Q6,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15", ",")

reviews <- read_csv(list.files("data/peer_review/", full.names = TRUE), skip = 3, col_names = cols[[1]]) %>%
  mutate(
    q6 = case_when(
      Q6 == "deeply flawed and unpublishable." ~ 0,
      Q6 == "publishable with major revision." ~ 1,
      Q6 == "publishable with minor revision." ~ 2,
      Q6 == "publishable as is." ~ 3
    )
  )
```

### 2022-06-16 data/osf/norming/README.Rmd

--- 2021-01-05 osf/comps/data/norming/README.Rmd
@@
 - The `images/` directory contains the re-colored images used in the norming study.
-- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.
+- The `ratings/` directory holds an aggregated `ratings.csv` file with the typicality ratings of each image/object for each participant.
 
-The `tipicality.csv` file has the following columns:
+# Ratings
 
-- `prolific id`: The participant/trial id.
-- `object`: The name of the object represented in the image.
+The `ratings.csv` file represents the raw data collected from the norming experiment and has the following columns:
+
+- `subject_id`: The participant/trial id.
+- `object`: The name of the object illustrated in the image.
 - `typicality`: The typicality rating (numeric, `1-100`, `1` = most atypical, `100` = most typical).
 - `colour`: The color of the object in the image.
+- `object_en`: The english translation of `object`
+- `colour_en`: The english translation of `colour`
 
-```{r retrieve}
-# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
-osf_repo <- osf_retrieve_node("3bmcp")
-# Repo components
-osf_comps <- osf_ls_nodes(osf_repo)
-# Dataset & Materials component
-data_comp <- osf_comps %>% filter(name == "Data")
-```
+The `ratings_summary.csv` represents the aggregated typicality ratings across combinations of object and color.
+The file has the following columns:
 
-```{r data_files, include=TRUE}
-osf_ls_files(data_comp, "norming") %>%
-  select(name) %>%
-  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
-  arrange(name)
-```
+- `object`: The name of the object illustrated in the image.
+- `colour`: The color of the object in the image.
+- `object_en`: The english translation of `object`.
+- `colour_en`: The english translation of `colour`.
+- `typ_mean`: The mean typicality rating.
+- `typ_sd`: The standard deviation of the typicality ratings .
+- `typ_median`: The median typicality rating.

### 2022-06-16 scripts/r/03_analyses_coding.Rmd

@@
 
-Now we get only those components that are assigned to you. Tell me who you are when prompt.
+Now we get only those components that are assigned to you. Tell me who you are when prompted.
 
@@
 
-And now we download the components in `data/analyses/`
+And now we download the components in `data/analyses/` (it will take some time!).
 
@@
 
+# Upload refitted models to OSF
+
 Once all your models have been refitted, you can upload them to the OSF, in the Cache component, `models/refitted/` folder.
 
-Here's some code that does that for you.
+Here's the code that does that for you.
 
@@
 
-# Get estimated from refitted models
+# Download all refitted models
 
-We first download all the refitted models .rds files from the OSF
+We first download all the refitted models .rds files from the OSF.
 
@@
 
-A few helpers.
+# Get estimates from refitted models
+
+Now we can extract the relevant estimates from the refitted models.
+
+A few helper functions.
 
 ```{r helpers}
-# Plotting theme because Im extra
+# Plotting theme
 clean_theme <- function(...) {
@@
 
+Load all the models.
+
 ```{r load-models}
@@
   mutate(sum = map(model, clean_up)) %>% 
-  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+  # because it warns every time that some coef have underscores and its annoying
+  suppressWarnings()
 ```
 
+Simple pandoc table of the models, estimates, se, etc.
+
 ```{r effect-table}
-# Simple pandoc table of the models, estimates, se, etc.
 msa_models %>% 
@@
 
+Simple forest plot of the estimates +/- SE
+
 ```{r forest-plot}
-# Simple forest plot of the estimates +/- SE
 msa_models %>% 

### 2022-06-16 scripts/r/04_refit/refit_jvc.Rmd
testing after merge

--- 2022-06-14 scripts/r/04-refit/refit-jvc.Rmd
@@
 
-directory <- here("data", "trial-lists")
-list_of_files = dir(here("data", "trial-lists"))
+directory <- here("data", "osf", "production", "trial-lists")
+list_of_files = dir(here("data", "osf", "production", "trial-lists"))
 
@@
 #
-intensity_model_lmer <- lmer(Intensity ~ typ_mean + (1|target_name)+ (1|filename) + (1|filename:target_name),
-                       data = intensity_DF)
+intensity_model_lmer <- lmer(
+  Intensity ~ typ_mean + 
+    (1|target_name) + 
+    (1|filename) + 
+    (1|filename:target_name), 
+  data = intensity_DF
+  )
 

### 2022-06-16 scripts/r/03_analyses_coding.Rmd
♻️ - edit analyses coding to remove model objects from tibble

@@
 clean_up <- . %>% 
-  tidy(effects = "fixed") %>% 
+  tidy(effects = "fixed", parametric = TRUE) %>% 
   suppressWarnings() %>% 
@@
   # because it warns every time that some coef have underscores and its annoying
-  suppressWarnings()
+  suppressWarnings() %>%
+  select(-model)
 ```
@@
   unnest(sum) %>%
-  select(-model) %>% 
   knitr::kable(format = "pandoc")

### 2022-06-16 scripts/r/04_refit/refit_sc.Rmd
♻️ - edit refit sc

@@
 ```{r}
-msa_data <- read.csv("./data/analyses/sc/neosilurus_omanensis/annotated_cleaned_data_v7.csv", stringsAsFactors = T, header = T) %>%
+msa_data <- read_csv("./data/analyses/sc/neosilurus_omanensis/annotated_cleaned_data_v7.csv") %>%
   mutate(
-    effect_cat = factor(typ_cat, levels = c("atypical", "medium", "typical"))
+    effect_cat = factor(typ_cat, levels = c("atypical", "medium", "typical")),
+    PitchRatioAtoU = scale(PitchRatioAtoU) %>% as.numeric(),
+    PitchRangeRatioAtoU = scale(PitchRangeRatioAtoU) %>% as.numeric(),
+    PitchVariationRatioAtoU = scale(PitchVariationRatioAtoU) %>% as.numeric(),
+    PitchRiseRatio = scale(PitchRiseRatio) %>% as.numeric(),
+    SpeechRateRatioAtoU = scale(SpeechRateRatioAtoU) %>% as.numeric(),
+    Condition = as.factor(Condition)
   )
@@
 
-# Convergence issues
+# Team also had interaction effect_cat:Condition which leads to convergence issues
+# since typ:AF = 0 and atyp:ANF = 0
 neosilurus_omanensis_3_f0varrat_cat <- brm(
-  PitchVariationRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
+  PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
   data = msa_data,
@@
 
-# Convergence issues
+# Team also had interaction effect_cat:Condition which leads to convergence issues
+# since typ:AF = 0 and atyp:ANF = 0
 neosilurus_omanensis_5_srrat_cat <- brm(
-  SpeechRateRatioAtoU ~ effect_cat * Condition + (1|Participant) + (1|Adjective),
+  SpeechRateRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
   data = msa_data,
@@
   mutate(
-    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical"))
+    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
+    pitch_st = scale(pitch_st) %>% as.numeric()
   )
@@
 ```{r}
-petauroides_fistulator_1_f0_cat <- gam(
+petauroides_fistulator_1_f0_cat <- bam(
   pitch_st ~
@@
     s(distractor2_colour, bs = "re"),
-  data = msa_data
+  data = msa_data,
+  cluster = parallel::makeCluster(8)
 )
@@
 norming_data <- read_csv("./data/analyses/sc/polymetme_brevirostrum/Data/ratings_summary.csv")
-ratings <- read_csv("./osf/data/norming/ratings/ratings.csv")
+ratings <- read_csv("./data/osf/norming/ratings/ratings.csv")
 foods <- list('aprikose','kirsche','moehre','gurke','erbsen','tomate','kartoffeln','banane','zitrone','bohnen','erdbeere','mandarine','walnuss')
@@
     across(contains("f0"), function(x) {ifelse(x == "--undefined--", NA, x)}),
-    Category = ifelse(object %in% foods, "FOOD", "NONFOOD"),
+    Category = as.factor(ifelse(object %in% foods, "FOOD", "NONFOOD")),
     effect_cat = factor(Typicality, levels = c("atypical", "medium", "typical")),
     Adj_Dur = scale(Adj_Dur) %>% as.numeric(),
-    Condition = factor(Condition),
-    Category = factor(Category)
+    Condition = as.factor(Condition),
+    Category = as.factor(Category)
   )
@@
 
-Convergence issues.
-
 ```{r}
 polymetme_brevirostrum_1_dur_cat <- brm(
-  Adj_Dur ~ Condition * effect_cat * Category + (Condition * effect_cat || Speaker) + (Condition || object) + (effect_cat || colour),
+  Adj_Dur ~ Condition * effect_cat + effect_cat * Category + (Condition * effect_cat | Speaker) + (Condition | object) + (effect_cat | colour),
   data = msa_data,
-  cores = 4,
-  threads = threading(2, grainsize = 100), 
+  chains = 1,
+  cores = 8,
+  threads = threading(8, grainsize = 100), 
   backend = "cmdstanr",

### 2022-06-23 scripts/r/04_refit/refit_tr.Rmd
first commit with glitchy rmd

---
title: "Re-fit"
subtitle: "TR"
output: html_document
date: "Last update: `r Sys.Date()`"
---

```{r setup}
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )
knitr::opts_knit$set(root.dir = here::here())

# libs
library("here")
library("fs")
library("dplyr")
library("tidyr")
library("readr")
library("forcats")
library("ggplot2")
library("stringr")
library("strex")
library("purrr")
library("lme4")
library("brms")
library("broom")
library("broom.mixed")
library("readxl")
library("optimx")

# Plotting theme because Joseph is extra
clean_theme <- function(...) {
  list(
    theme_minimal(), 
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
  )
}

# Functional sequence to get relevant info from Rds files
clean_up <- . %>% 
  tidy(effects = "fixed") %>% 
  suppressWarnings() %>% 
  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
  select(term, estimate, se = std.error)

```
```

# trachyphyllia_lappa

```{r trachyphyllia_lappa_setup}

path <- "./data/analyses/tr/trachyphyllia_lappa"

path_trial = paste0(path, "/trial_level_data/")
msa <- list.files(path = path_trial, pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv,  col_types = cols( .default = col_character())) %>% 
  bind_rows %>%
  mutate(trial = as.numeric(trial))

# analyze only NF condition with the first 35 trials
msa_nf = msa %>% filter(condition == "NF" & trial < 36)

results_path = paste0(path, "/acoustic_measurements/errors.txt")
errorfile = read.delim(results_path, skipNul = TRUE, fileEncoding="latin1", header = TRUE) %>%
  mutate(label = as.factor(label)) %>%
  group_by(speaker) %>%
  mutate(trial = as.integer(row_number()/2))

main_errors = errorfile %>% filter(!label %in% "") %>% filter(trial < 36) %>%
  filter(!label %in% c("team_add", "team_delete") )

main_errors %>% group_by(label) %>% summarise(trials = n()) %>%
       mutate(percent = trials/sum(trials))

results_path = paste0(path, "/acoustic_measurements/durations.txt")
durations = read.delim(results_path,skipNul = TRUE, fileEncoding="latin1", header = TRUE) 
newnames = c("speaker", "phrase", "duration")

durations = durations %>%
  rename_with(~ newnames[which(names(durations) == .x)], .cols = names(durations))%>%
  group_by(speaker) %>%
  mutate(trial = as.integer(gl(n(), 11, n()))) %>% 
  group_by(speaker, trial) %>%
  mutate(word = row_number()) %>%
filter(word %in% c(9,10)) %>%
  ## merge with msa data
  left_join(msa_nf %>% select(speaker,trial, condition, typicality, target_colour) %>%
              mutate(trial = as.integer(trial))) %>%
  filter(!is.na(condition))

# combine with phrase info
phrase_data = durations %>% select(speaker, trial, phrase) %>%
  group_by(speaker, trial) %>%
   summarise(phrase = paste(phrase, collapse = "-"))

durations = durations %>% select(-phrase) %>%
  left_join(phrase_data)

# exclude error trials
durations = durations %>% left_join(main_errors) %>%
  filter(is.na(label))

durations %>% group_by(speaker) %>% summarise(n=n()/2) %>%
  summarise(mean_trials = mean(n), sd_trials = sd(n))

# pitch extraction
results_path = paste0(path,"/acoustic_measurements/pitchresults.txt")
pitchfile = read.delim(results_path, skipNul = TRUE, fileEncoding="latin1", header = TRUE)
newnames = c("speaker", "phrase", "maximum","minimum")

pitchfile = pitchfile %>%
  rename_with(~ newnames[which(names(pitchfile) == .x)], .cols = names(pitchfile))%>%
  group_by(speaker) %>%
  mutate(trial = as.integer(gl(n(), 11, n()))) %>% 
  group_by(speaker, trial) %>%
  mutate(word = row_number()) %>%
filter(word %in% c(9,10)) %>%
  ## merge with msa data
  left_join(msa_nf %>% select(speaker,trial, condition, typicality, target_colour) %>%
              mutate(trial = as.integer(trial))) %>%
  filter(!is.na(condition)) %>%
  pivot_longer(names_to = "pitch", cols = minimum:maximum) %>%
  mutate(value = ifelse(value == "--undefined--", NA, value),
         value = as.numeric(value))

pitchfile = pitchfile %>% select(-phrase) %>%
  left_join(phrase_data)

# exclude errors
pitchfile = pitchfile %>% left_join(main_errors) %>%
  filter(is.na(label)) %>%
# pitch into wide 
  pivot_wider(names_from = pitch, values_from = value)%>%
  mutate(range = maximum - minimum)

```

```{r trachyphyllia_lappa_models}

ctrl = lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
                   optimizer = "optimx", optCtrl  = list(method="bobyqa", maxfun = 2e+6))

duration_int = duration ~ typicality*target_colour + 
  (typicality + target_colour  | speaker) + (1 | phrase)
duration_noint = duration ~ typicality + target_colour + 
  (typicality + target_colour  | speaker) + (1 | phrase)

pitch_min_int = minimum ~ typicality * target_colour + (typicality + target_colour  | speaker)+ 
  (1 | phrase)
pitch_min_noint = minimum ~ typicality + target_colour + (typicality + target_colour  | speaker)+ 
  (1 | phrase)

pitch_max_int = maximum ~ typicality * target_colour + (typicality + target_colour  | speaker)+
   (1 | phrase)
pitch_max_noint = maximum ~ typicality + target_colour + (typicality + target_colour  | speaker)+
   (1 | phrase)

pitch_range_noint = range ~ typicality + target_colour + (typicality + target_colour  | speaker)+
   (1 | phrase)
pitch_range_int = range ~ typicality * target_colour + (typicality + target_colour  | speaker)+
   (1 | phrase)

# adjective models - duration
duration_adj_data = durations %>% filter(word == 9) %>% 
  mutate(type = "adjective")

# TR: no interaction better fit, so chosen by the analysts
duration_adj_model_noint = lme4::lmer(data = duration_adj_data, duration_noint, control=ctrl)

# nouns models - duration
duration_noun_data = durations %>% filter(word == 10) %>% mutate(type = "noun")

# TR: interaction model picked
duration_noun_model_int =lme4::lmer(data = duration_noun_data, duration_int, control=ctrl)

# adjective model - pitch
pitch_adj_data = pitchfile %>% filter(word == 9)%>% mutate(type = "adjective")
pitch_noun_data = pitchfile %>% filter(word == 10)%>%mutate(type = "noun")

pitch_adj_model_max_noint = lme4::lmer(data = pitch_adj_data,pitch_max_noint, control = ctrl) 
pitch_adj_model_min_noint = lme4::lmer(data = pitch_adj_data, pitch_min_noint, control = ctrl)
pitch_adj_model_range_noint = lme4::lmer(data = pitch_adj_data, pitch_range_noint, control = ctrl)

pitch_noun_model_max_noint = lme4::lmer(data = pitch_noun_data,pitch_max_noint, control = ctrl) 
pitch_noun_model_min_noint = lme4::lmer(data = pitch_noun_data, pitch_min_noint, control = ctrl)
pitch_noun_model_range_noint = lme4::lmer(data = pitch_noun_data, pitch_range_noint, control = ctrl)

```

```{r trachyphyllia_lappa_fitting}

# standardize
duration_adj_data_temp <- duration_adj_data %>% 
  mutate(duration_s = (duration - mean(duration, na.rm =TRUE)) / sd(duration,  na.rm = TRUE),
  # dummy-code typicality
  typicality = as.factor(typicality),
  target_colour = as.factor(target_colour),
  effect_cat = C(typicality, treatment),
  # sum-code categorical predictors
  target_colour_s = C(target_colour, sum)
  )

duration_noun_data <- duration_noun_data %>% 
  mutate(
         # scale continuous variables
         duration_s = (duration - mean(duration, na.rm = TRUE)) / sd(duration,  na.rm = TRUE),
         # dummy-code typicality
         typicality = as.factor(typicality),
         target_colour = as.factor(target_colour),
         effect_cat = C(typicality, treatment),
         # sum-code categorical predictors
         target_colour_s = C(target_colour, sum)
  )

pitch_adj_data <- pitch_adj_data %>% 
  mutate(
         # scale continuous variables
         minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
         maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
         range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
         # dummy-code typicality
         typicality = as.factor(typicality),
         target_colour = as.factor(target_colour),
         effect_cat = C(typicality, treatment),
         # sum-code categorical predictors
         target_colour_s = C(target_colour, sum)
  )

pitch_noun_data <- pitch_noun_data %>% 
  mutate(
         # scale continuous variables
         minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
         maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
         range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
         # dummy-code typicality
         typicality = as.factor(typicality),
         target_colour = as.factor(target_colour),
         effect_cat = C(typicality, treatment),
         # sum-code categorical predictors
         target_colour_s = C(target_colour, sum)
  )

# run brms equivalents
trachyphyllia_lappa_1_duradj_cat <- brm(
  duration_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = duration_adj_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_1_duradj_cat"
  )

trachyphyllia_lappa_2_f0maxadj_cat <- brm(
  maximum_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = pitch_adj_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_2_f0maxadj_cat"
  )

trachyphyllia_lappa_3_f0minadj_cat <- brm(
  minimum_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = pitch_adj_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_3_f0minadj_cat"
  )

trachyphyllia_lappa_4_f0rangeadj_cat <- brm(
  range_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = pitch_adj_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_4_f0rangeadj_cat"
  )

trachyphyllia_lappa_5_durnoun_cat <- brm(
  duration_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = duration_noun_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_5_durnoun_cat"
  )

trachyphyllia_lappa_6_f0maxnoun_cat <- brm(
  maximum_s ~  typicality + target_colour + 
      (typicality + target_colour | speaker) + 
      (1 | phrase),
  data = pitch_noun_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_6_f0maxnoun_cat"
  )

trachyphyllia_lappa_7_f0minnoun_cat <- brm(
  minimum_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = pitch_noun_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_7_f0minnoun_cat"
  )

trachyphyllia_lappa_8_f0rangenoun_cat <- brm(
  range_s ~  typicality + target_colour + 
      (typicality + target_colour  | speaker) + 
      (1 | phrase),
  data = pitch_noun_data, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/trachyphyllia_lappa_8_f0rangenoun_cat"
  )

```

# alosa_atun

```{r alosa_atun_setup}

MSA_combined <- readRDS("./data/analyses/tr/alosa_atun/alosa_atun_data.rds", refhook = NULL)

MSA_combined$meanPitch = as.numeric(MSA_combined$meanPitch)

MSA_combined_all <-
MSA_combined %>%
  filter(Text == "der",
         After.Match != "Würfel") %>%
  filter(!is.na(meanPitch))

MSA_combined_all <-
MSA_combined_all %>%
  filter(!is.na(Target.word.duration))

MSA_combined_all <-
MSA_combined_all %>%
  filter(!is.na(condition)) %>%
  filter(condition != "NA")

# create summary of F1 and F2 values based on speaker and vowels. sd_limit, max and min variables are used for outlier removal in the next step

sd_limit = 2.5

#set this to the +/- sd limit you want to filter outliers by

MSA_summstats <- MSA_combined_all %>%
  group_by(Transcript, Target.segment) %>%
  summarise(mean_F1 = mean(f1_time_0_5),
            mean_F2 = mean(f2_time_0_5),
            mean_amp = mean(maxIntensity),
            mean_pitch = mean(meanPitch),
            mean_durSeg = mean(Target.segment.duration),
            mean_durWord = mean(Target.word.duration),
            sd_F1 = sd(f1_time_0_5),
            sd_F2 = sd(f2_time_0_5),
            sd_amp = sd(maxIntensity),
            sd_pitch = sd(meanPitch),
            sd_durSeg = sd(Target.segment.duration),
            sd_durWord = sd(Target.word.duration),
            max_F1 = mean(f1_time_0_5) + sd_limit*(sd(f1_time_0_5)),
            min_F1 = mean(f1_time_0_5) - sd_limit*(sd(f1_time_0_5)),
            max_F2 = mean(f2_time_0_5) + sd_limit*(sd(f2_time_0_5)),
            min_F2 = mean(f2_time_0_5) - sd_limit*(sd(f2_time_0_5)),
            max_amp = mean(maxIntensity) + sd_limit*(sd(maxIntensity)),
            min_amp = mean(maxIntensity) - sd_limit*(sd(maxIntensity)),
            max_pitch = mean(meanPitch) + sd_limit*(sd(meanPitch)),
            min_pitch = mean(meanPitch) - sd_limit*(sd(meanPitch)),
            max_durSeg = mean(Target.segment.duration) + sd_limit*(sd(Target.segment.duration)),
            min_durSeg = mean(Target.segment.duration) - sd_limit*(sd(Target.segment.duration)),
            max_durWord = mean(Target.word.duration) + sd_limit*(sd(Target.word.duration)),
            min_durWord = mean(Target.word.duration) - sd_limit*(sd(Target.word.duration)))

#store the outlier tokens data

outlier_tokens <- MSA_combined_all %>%
  left_join(., MSA_summstats) %>%
  mutate(outlier = ifelse(f1_time_0_5 > min_F1 &
                            f1_time_0_5 < max_F1 &
                            f2_time_0_5 > min_F2 &
                            f2_time_0_5 < max_F2 &
                            maxIntensity > min_amp &
                            maxIntensity < max_amp &
                            meanPitch > min_pitch &
                            meanPitch < max_pitch &
                            Target.segment.duration > min_durSeg &
                            Target.segment.duration < max_durSeg &
                            Target.word.duration > min_durWord &
                            Target.word.duration < max_durWord &
                            f2_time_0_5 > 800,  
                          FALSE,
                          TRUE)) %>%
  group_by(Transcript, Target.segment) %>%
  filter(outlier == TRUE) %>%
  ungroup()

#add the summary statistics and filter out outliers

MSA_combined_pruned <- MSA_combined_all %>%
  left_join(., MSA_summstats) %>%
  mutate(outlier = ifelse(f1_time_0_5 > min_F1 &
                            f1_time_0_5 < max_F1 &
                            f2_time_0_5 > min_F2 &
                            f2_time_0_5 < max_F2 &
                            maxIntensity > min_amp &
                            maxIntensity < max_amp &
                            meanPitch > min_pitch &
                            meanPitch < max_pitch &
                            Target.segment.duration > min_durSeg &
                            Target.segment.duration < max_durSeg &
                            Target.word.duration > min_durWord &
                            Target.word.duration < max_durWord &
                            f2_time_0_5 > 800,  
                          FALSE,
                          TRUE)) %>%
  group_by(Transcript, Target.segment) %>%
  filter(outlier == FALSE) %>%
  ungroup()

#get new summary values
MSA_summstats <- MSA_combined_pruned %>%
  group_by(Transcript, Target.segment) %>%
  summarise(n_tokens_vowel = n(),
            mean_F1 = mean(f1_time_0_5),
            mean_F2 = mean(f2_time_0_5),
            mean_amp = mean(maxIntensity),
            mean_durSeg = mean(Target.segment.duration),
            mean_durWord = mean(Target.word.duration),
            mean_pitch = mean(meanPitch),
            sd_F1 = sd(f1_time_0_5),
            sd_F2 = sd(f2_time_0_5),
            sd_amp = sd(maxIntensity),
            sd_durSeg = sd(Target.segment.duration),
            sd_durWord = sd(Target.word.duration),
            sd_pitch = sd(meanPitch)) %>%
  ungroup()

MSA_controls <-
MSA_combined %>%
  filter(Text == "den") %>%
  filter(Target.segment == "e" | Target.segment == "@" ) %>%
  filter(After.Match == "Würfel")

MSA_combined_pruned$item = paste(MSA_combined_pruned$Transcript, MSA_combined_pruned$trialnumber, MSA_combined_pruned$trialtype)

MSA_controls$item = paste(MSA_controls$Transcript, MSA_controls$trialnumber, MSA_controls$trialtype)

MSA_controls_selected = MSA_controls %>% select(item, meanPitch, maxIntensity)
names(MSA_controls_selected) = c("item", "controlPitch", "controlIntensity")

MSA_final = left_join(MSA_combined_pruned, MSA_controls_selected, by="item")

MSA_final$Pause.duration = MSA_final$Token.plus.1.word.start - MSA_final$Target.word.end

MSA_finale <-
  MSA_final %>%
  filter(Target.segment == "e")

MSA_finalschwa <-
  MSA_final %>%
  filter(Target.segment == "@")

MSA_finale$eduration = MSA_finale$Target.segment.duration
MSA_finalschwa$schwaduration = MSA_finalschwa$Target.segment.duration
MSA_finalschwa$schwaF1 = MSA_finalschwa$f1_time_0_5
MSA_finalschwa$schwaF2 = MSA_finalschwa$f2_time_0_5

MSA_interimschwa = MSA_finalschwa %>% select(item, schwaduration, schwaF1, schwaF2)
MSA_both = left_join(MSA_finale, MSA_interimschwa, by="item")
MSA_both = MSA_both %>% filter(!is.na(schwaduration))
MSA_both$DiphDur = MSA_both$Target.segment.duration + MSA_both$schwaduration
MSA_both$DurRat = MSA_both$Target.segment.duration / MSA_both$schwaduration
MSA_both$ED = sqrt((MSA_both$f1_time_0_5-MSA_both$schwaF1)^2 + (MSA_both$f2_time_0_5-MSA_both$schwaF2)^2)

```

```{r alosa_atun_models}

# schwa analyses
model_f1c <-
MSA_finale %>%
  lmer(., formula=f1_time_0_5 ~
         (P.typ_mean + condition + scaledtrialnumber) + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

model_f2c <-
  MSA_finale %>%
  lmer(., formula=f2_time_0_5 ~ 
         (P.typ_mean + condition + scaledtrialnumber) + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

model_ampc <-
  MSA_finale %>%
  lmer(., formula=maxIntensity ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute + controlIntensity +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

model_pitchc <-
  MSA_finale %>%
    mutate(meanPitch = as.integer(meanPitch)) %>%
  lmer(., formula=meanPitch ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute + controlPitch +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

model_durSegc <-
  MSA_finale %>%
  lmer(., formula=Target.segment.duration ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

# schwa offglide analysis
shmodel_f1c <-
MSA_finalschwa %>%
  lmer(., formula=f1_time_0_5 ~
         (P.typ_mean + condition + scaledtrialnumber) + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

shmodel_f2c <-
  MSA_finalschwa %>%
  lmer(., formula=f2_time_0_5 ~ 
         (P.typ_mean + condition + scaledtrialnumber) + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

shmodel_ampc <-
  MSA_finalschwa %>%
  lmer(., formula=maxIntensity ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute + controlIntensity +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

shmodel_pitchc <-
  MSA_finalschwa %>%
    mutate(meanPitch = as.integer(meanPitch)) %>%
  lmer(., formula=meanPitch ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute + controlPitch +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

shmodel_durSegc <-
  MSA_finalschwa %>%
  lmer(., formula=Target.segment.duration ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

# schwa + schwa offglide analysis
combo_model_DiphDurc <-
  MSA_both %>%
  lmer(., formula=DiphDur ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

combo_model_EDc <-
  MSA_both %>%
  lmer(., formula=ED ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

combo_model_DurRatc <-
  MSA_both %>%
  lmer(., formula=DurRat ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

# model word duration and pause duration
model_durWordc <-
  MSA_finale %>%
  lmer(., formula=Target.word.duration ~ 
         (P.typ_mean + condition + scaledtrialnumber)   + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

model_Pausec <-
  MSA_finale %>%
  lmer(., formula=Pause.duration ~ 
         (P.typ_mean + condition + scaledtrialnumber)  + syllablesPerMinute +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

# speech rate (focuses on an interaction effect)
combo_model_rated <-
  MSA_both %>%
  lmer(., formula=syllablesPerMinute ~ 
         condition * P.typ_mean + scaledtrialnumber +
         (1 | Transcript) + 
         (1 | P.Adj),
       verbose = 0)

```

```{r alosa_atun_refitting_TR}

# standardize datasets for schwa analyses
MSA_finale <- MSA_finale %>% 
  mutate(
         # scale continuous variables
         f1_time_0_5_s = (f1_time_0_5 - mean(f1_time_0_5, na.rm = TRUE)) / sd(f1_time_0_5,  na.rm = TRUE),
         f2_time_0_5_s = (f2_time_0_5 - mean(f2_time_0_5, na.rm = TRUE)) / sd(f2_time_0_5,  na.rm = TRUE),
         maxIntensity_s = (maxIntensity - mean(maxIntensity, na.rm = TRUE)) / sd(maxIntensity,  na.rm = TRUE),
         meanPitch = as.integer(meanPitch),
         meanPitch_s = (meanPitch - mean(meanPitch, na.rm = TRUE)) / sd(meanPitch,  na.rm = TRUE),
         Target.segment.duration_s = (Target.segment.duration - mean(Target.segment.duration, na.rm = TRUE)) / sd(Target.segment.duration,  na.rm = TRUE),
         Target.word.duration_s = (Target.word.duration - mean(Target.word.duration, na.rm = TRUE)) / sd(Target.word.duration,  na.rm = TRUE),
         Pause.duration_s = (Pause.duration - mean(Pause.duration, na.rm = TRUE)) / sd(Pause.duration,  na.rm = TRUE),
         syllablesPerMinute_s = (syllablesPerMinute - mean(syllablesPerMinute, na.rm = TRUE)) / sd(syllablesPerMinute,  na.rm = TRUE),
         controlPitch_s = (controlPitch - mean(controlPitch, na.rm = TRUE)) / sd(controlPitch,  na.rm = TRUE),
         controlIntensity_s = (controlIntensity - mean(controlIntensity, na.rm = TRUE)) / sd(controlIntensity,  na.rm = TRUE),
         effect_con = (P.typ_mean - mean(P.typ_mean, na.rm = TRUE)) / sd(P.typ_mean,  na.rm = TRUE),
         # sum-code categorical predictors
         condition_s = C(as.factor(condition), sum)
  )

# standardize datasets for schwa offglide analyses
MSA_finalschwa <- MSA_finalschwa %>% 
  mutate(
         # scale continuous variables
         f1_time_0_5_s = (f1_time_0_5 - mean(f1_time_0_5, na.rm = TRUE)) / sd(f1_time_0_5,  na.rm = TRUE),
         f2_time_0_5_s = (f2_time_0_5 - mean(f2_time_0_5, na.rm = TRUE)) / sd(f2_time_0_5,  na.rm = TRUE),
         maxIntensity_s = (maxIntensity - mean(maxIntensity, na.rm = TRUE)) / sd(maxIntensity,  na.rm = TRUE),
         meanPitch = as.integer(meanPitch),
         meanPitch_s = (meanPitch - mean(meanPitch, na.rm = TRUE)) / sd(meanPitch,  na.rm = TRUE),
         Target.segment.duration_s = (Target.segment.duration - mean(Target.segment.duration, na.rm = TRUE)) / sd(Target.segment.duration,  na.rm = TRUE),
         syllablesPerMinute_s = (syllablesPerMinute - mean(syllablesPerMinute, na.rm = TRUE)) / sd(syllablesPerMinute,  na.rm = TRUE),
         controlPitch_s = (controlPitch - mean(controlPitch, na.rm = TRUE)) / sd(controlPitch,  na.rm = TRUE),
         controlIntensity_s = (controlIntensity - mean(controlIntensity, na.rm = TRUE)) / sd(controlIntensity,  na.rm = TRUE),
         effect_con = (P.typ_mean - mean(P.typ_mean, na.rm = TRUE)) / sd(P.typ_mean,  na.rm = TRUE),
         # sum-code categorical predictors
         condition_s = C(as.factor(condition), sum)
  )

# standardize datasets for schwa + schwa offglide analyses
MSA_both <- MSA_both %>% 
  mutate(
         # scale continuous variables
         DiphDur_s = (DiphDur - mean(DiphDur, na.rm = TRUE)) / sd(DiphDur,  na.rm = TRUE),
         ED_s = (ED - mean(ED, na.rm = TRUE)) / sd(ED,  na.rm = TRUE),
         DurRat_s = (DurRat - mean(DurRat, na.rm = TRUE)) / sd(DurRat,  na.rm = TRUE),
         syllablesPerMinute_s = (syllablesPerMinute - mean(syllablesPerMinute, na.rm = TRUE)) / sd(syllablesPerMinute,  na.rm = TRUE),
         effect_con = (P.typ_mean - mean(P.typ_mean, na.rm = TRUE)) / sd(P.typ_mean,  na.rm = TRUE),
         # sum-code categorical predictors
         condition_s = C(as.factor(condition), sum)
  )

# run brms equivalent for schwa
alosa_atun_4_f1schwa_con <- brm(
  f1_time_0_5_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  data = MSA_finale, 
  seed = 111,
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_4_f1schwa_con"
  )

alosa_atun_5_f2schwa_con <- brm(
  f2_time_0_5_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_5_f2schwa_con"
  )

alosa_atun_2_intschwa_con <- brm(
  maxIntensity_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s + controlIntensity_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_2_intschwa_con"
  )

alosa_atun_1_f0schwa_con <- brm(
  meanPitch_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s + controlPitch_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_1_f0schwa_con"
  )

alosa_atun_3_durschwa_con <- brm(
  Target.segment.duration_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_3_durschwa_con"
  )

# run brms equivalent for schwa offglide
alosa_atun_9_f1off_con <- brm(
  f1_time_0_5_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finalschwa, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_9_f1off_con"
  )

alosa_atun_10_f2off_con <- brm(
  f2_time_0_5_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finalschwa, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_10_f2off_con"
  )

alosa_atun_7_intoff_con <- brm(
  maxIntensity_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s + controlIntensity_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finalschwa, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_7_intoff_con"
  )

alosa_atun_6_f0off_con <- brm(
  meanPitch_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s + controlPitch_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finalschwa, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_6_f0off_con"
  )

alosa_atun_8_duroff_con <- brm(
  Target.segment.duration_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finalschwa, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_8_duroff_con"
  )

# run brms equivalent for schwa + schwa offglide analysis
alosa_atun_11_durboth_con <- brm(
  DiphDur_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_both, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_11_durboth_con"
  )

alosa_atun_12_durrelboth_con <- brm(
  DurRat_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_both, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_12_durrelboth_con"
  )

alosa_atun_13_EDboth_con <- brm(
  ED_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_both, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_13_EDboth_con"
  )

# run brms equivalent for word duration
alosa_atun_14_worddur_con <- brm(
  Target.word.duration_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_14_worddur_con"
  )

# run brms equivalent for pause duration
alosa_atun_15_pausedur_con <- brm(
  Pause.duration_s ~ 
         (effect_con + condition_s + scaledtrialnumber) + syllablesPerMinute_s +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_finale, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_15_pausedur_con"
  )

# run brms equivalent for speech rate
alosa_atun_16_speechrate_con <- brm(
  syllablesPerMinute_s ~ 
         effect_con * condition_s + scaledtrialnumber +
         (1 | Transcript) + 
         (1 | P.Adj), 
  seed = 111,
  data = MSA_both, 
  cores = 4,  
  file = "./data/analyses/models/alosa_atun_16_speechrate_con"
  )

```

# psittacula_scabriculus

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# eosipterus_pytyopsittacus

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# pseudopleuronectes_assasi

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# pervagor_meeki

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# procambarus_maculosus

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# ceratophrys_elephantotus

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# clione_dorsalis

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# aracana_bitatawa

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# dunkleosteus_inscriptus

```{r dunkleosteus_inscriptus_setup}

path <- "./data/analyses/tr/dunkleosteus_inscriptus/data/"

flist_times  <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^timings(.*)xlsx")
get_times    <- lapply(paste0(path, flist_times), read_excel)
times        <- bind_rows(get_times)

flist_trials <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^trials(.*)xlsx")
get_trials   <- lapply(paste0(path, flist_trials), read_excel)
trials       <- bind_rows(get_trials)

mfields      <- c( "trial","speaker" )
dat          <- merge( trials, times, by=mfields )

dat$condition      <- factor(dat$condition)
dat$typicality     <- factor(dat$typicality)
dat$target_name    <- factor(dat$target_name)
dat$target_colour  <- factor(dat$target_colour)

# correct constituent names exported by <extract_timings_MSA.m> and 
# calculate additional durations derived from from Praat intervals
dat$dur_n    <- dat$dur_np
dat$dur_np   <- dat$dur_ap
dat$dur_a    <- dat$dur_np - dat$dur_n
dat$dur_ap   <- NULL
dat$rel_a    <- dat$dur_a / dat$dur_dp
dat$rel_n    <- dat$dur_n / dat$dur_dp

## check extremely long utterances
dur_ip_max     <- mean(dat$dur_ip) + 2.5*sd(dat$dur_ip)
#(dat_long_ip   <- dat[ dat$dur_ip>dur_ip_max, ])
# 28 utterances longer than 3.91s rechecked with <check_maus.m>
# all 28 invalid: misproduced, contain hesitations, or are incorrectly segmented
# remove all trials longer than 2.5sd mean duration:
dat  <- dat[ !(dat$dur_ip > dur_ip_max ), ]

## check duration extrema: preposition phrase 'auf ...'
dur_pp_min     <- mean(dat$dur_pp) - 2*sd(dat$dur_pp)
#(dat_short_pp  <- dat[ dat$dur_pp < dur_pp_min, ])
# 4 trials with PPs shorter than 728ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_pp < dur_pp_min ), ]

dur_pp_max     <- mean(dat$dur_pp) + 3*sd(dat$dur_pp)
#(dat_long_pp   <- dat[ dat$dur_pp > dur_pp_max, ])
# 19 trials with PPs longer than 2.03s rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_pp > dur_pp_max ), ]

## check duration extrema: target determiner phrase
dur_dp_min     <- mean(dat$dur_dp) - 2*sd(dat$dur_dp)
#(dat_short_dp  <- dat[ dat$dur_dp < dur_dp_min, ])
# 5 trials with target DPs shorter than 629ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_dp < dur_dp_min ), ]

dur_dp_max     <- mean(dat$dur_dp) + 3.1*sd(dat$dur_dp)
#(dat_long_dp   <- dat[ dat$dur_dp > dur_dp_max, ])
# 5 trials with target DPs longer than 1.75s rechecked with <check_maus.m>
# mainly just long words/slow speech rate: don't remove from dataset

## check duration extrema: target noun phrase
dur_np_min     <- mean(dat$dur_np) - 2*sd(dat$dur_np)
#(dat_short_np  <- dat[ dat$dur_np < dur_np_min, ])
# 26 trials with target NPs shorter than 460ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_np < dur_np_min ), ]

dur_np_max     <- mean(dat$dur_np) + 3.1*sd(dat$dur_np)
#(dat_long_np   <- dat[ dat$dur_np > dur_np_max, ])
# 3 trials with target APs longer than 1.55s rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_np > dur_np_max ), ]

## check duration extrema: target nouns
dur_n_min     <- mean(dat$dur_n) - 1.8*sd(dat$dur_n)
#(dat_short_n  <- dat[ dat$dur_n < dur_n_min, ])
# 28 trials with target nouns shorter than 217ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_n < dur_n_min ), ]

dur_n_max     <- mean(dat$dur_n) + 2.5*sd(dat$dur_n)
#(dat_long_n   <- dat[ dat$dur_n > dur_n_max, ])
# 23 trials with target nouns longer than 875ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_n > dur_n_max ), ]

## check duration extrema: target adjectives
dur_a_min     <- mean(dat$dur_a) - 1.6*sd(dat$dur_a)
#(dat_short_a  <- dat[ dat$dur_a < dur_a_min, ])
# 25 trials with target adjectives shorter than 173ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_a < dur_a_min ), ]

dur_a_max     <- mean(dat$dur_a) + 3.85*sd(dat$dur_a)
#(dat_long_a   <- dat[ dat$dur_a > dur_a_max, ])
# 4 trials with target adjectives longer than 947ms rechecked with <check_maus.m>
# all involve some segmentation inaccuracies: remove from dataset
dat  <- dat[ !(dat$dur_a > dur_a_max ), ]

## ===== select trials eliciting target words in NF condition  =====
dat_nf  <- dat[ (dat$condition=='NF'), ]
dat_nf$condition   <- factor(dat_nf$condition)
dat_nf$typicality  <- factor(dat_nf$typicality)

```

```{r dunkleosteus_inscriptus_models}

## Bayesian model:
fm2 <- rel_n ~ typicality + (1|speaker) + (1|target_name) + (1|target_colour)
fm2a <- dur_n ~ typicality + (1|speaker) + (1|target_name) + (1|target_colour)
fm3 <- rel_a ~ typicality + (1|speaker) + (1|target_name) + (1|target_colour)
fm3a <- dur_a ~ typicality + (1|speaker) + (1|target_name) + (1|target_colour)
fm4  <- dur_np ~ typicality + (1|speaker) + (1|target_name) + (1|target_colour)

# TR: claimed to run fm2a and fm3a as Bayesian, but scripts do not provide these models, so I take the frequentist ones
lm2a <- lmer(fm2a, data=dat)
lm3a <- lmer(fm3a, data=dat)

# TR: They specified priors but ended up running default priors (strange), also unclear which data are used, subsetted ones ("dat_nf") or full data ("dat"). I will pick dat for all. 
pri2 <- get_prior( formula=fm2, data=dat )
pri3 <- get_prior( formula=fm3, data=dat )
pri4 <- get_prior( formula=fm4, data=dat )

# TR: add cores to fit quicker
bm2   <- brm( fm2, dat, prior=pri2, cores = 4 )
bm3   <- brm( fm3, dat, prior=pri3, cores = 4 )
bm4   <- brm( fm4, dat, prior=pri4, cores = 4 )

```

```{r dunkleosteus_inscriptus_refitting}

# standardizing 
dat <- dat %>% 
  mutate(
         # scale continuous variables
         rel_n_s = (rel_n - mean(rel_n, na.rm = TRUE)) / sd(rel_n,  na.rm = TRUE),
         rel_a_s = (rel_a - mean(rel_a, na.rm = TRUE)) / sd(rel_a,  na.rm = TRUE),
         dur_n_s = (dur_n - mean(dur_n, na.rm = TRUE)) / sd(dur_n,  na.rm = TRUE),
         dur_a_s = (dur_a - mean(dur_a, na.rm = TRUE)) / sd(dur_a,  na.rm = TRUE),
         dur_np_s = (dur_np - mean(dur_np, na.rm = TRUE)) / sd(dur_np,  na.rm = TRUE),
         effect_cat = C(typicality, treatment)
  )

# run brms on standardized models
dunkleosteus_inscriptus_1_relndur_cat <- brm(
  rel_n_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_1_relndur_cat"
  )

# did initially not converge, adjusted adapt_delta to 0.9999  
dunkleosteus_inscriptus_2_ndur_cat <- brm(
  dur_n_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  control = list(adapt_delta = 0.9999),
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_2_ndur_cat"
  )

dunkleosteus_inscriptus_3_reladur_cat <- brm(
  rel_a_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_3_reladur_cat"
  )

dunkleosteus_inscriptus_4_adur_cat <- brm(
  dur_a_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_4_adur_cat"
  )

dunkleosteus_inscriptus_5_npdur_cat <- brm(
  dur_a_s ~ 
         effect_cat + 
         (1|speaker) + 
         (1|target_name) + 
         (1|target_colour),
  seed = 111,
  data = dat, 
  cores = 4,  
  file = "./data/analyses/models/dunkleosteus_inscriptus_5_npdur_cat"
  )

```

# nestor_idahoensis

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# sphyrna_ellioti

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# chelonia_brummeri

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# procambarus_mahogoni

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# aratinga_lugubris

```{r authors setup}

```

```{r their_models}

```

```{r refitting}

```

# summary

## Load models

```{r}
#| label: load-models
# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"

msa_models <- dir_ls(path = here("data", "analyses", "models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(path = value, 
    mod_name = str_remove(path, here("data", "analyses", "models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))) %>% 
  separate(mod_name, 
    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
    sep = "_", remove = F) %>% 
  unite(group, word1, word2, sep = "_") %>% 
  select(group, mod_name:model) %>% 
  mutate(sum = map(model, clean_up)) %>% 
  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
```

## Table

```{r}
#| label: effect-table
# Simple pandoc table of the models, estimates, se, etc.
msa_models %>% 
  unnest(sum) %>% 
  select(-model) %>% 
  knitr::kable(format = "pandoc")
```

## Plot

```{r}
#| label: forest-plot
# Simple forest plot of the estimates +/- SE
msa_models %>% 
  unnest(sum) %>% 
  mutate(typicality_lab = if_else(typicality == "cat", 
    "Typicality = categorical", "Typicality = continuous"), 
    mod_name = fct_reorder(mod_name, estimate)) %>% 
  ggplot() + 
  facet_wrap(~ typicality_lab, ncol = 1, scales = "free_y") + 
  aes(x = estimate, y = mod_name) + 
  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
  geom_vline(xintercept = 0, lty = "dashed", color = "grey") +
  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
  labs(y = "Model", x = "Estimate ± SE") + 
  clean_theme() + 
  theme(strip.text.x = element_text(hjust = 0))
```

### 2022-06-24 scripts/r/02_teams_reviews.Rmd
✨ - upload reviews to osf components

@@
     )
-  )
+  ) %>%
+  drop_na(Q3) %>%
+  filter(Finished == TRUE)
 ```
+
+```{r analytic-quest}
+dir.create("data/peer_review/msa_reviews/", showWarnings = FALSE)
+
+for (team in unique(reviews$Q3)) {
+  file_name <- as.character(glue("data/peer_review/msa_reviews/{team}.csv"))
+
+  reviews %>%
+    filter(Q3 == team) %>%
+    select(-(StartDate:Q2)) %>%
+    write_csv(file_name)
+}
+```

### 2022-06-24 scripts/r/04_refit/refit_jvc.Rmd
halfish way

@@
   )
+
 knitr::opts_knit$set(root.dir = here::here())
@@
 library("readr")
+library("readxl")
 library("forcats")
@@
   select(term, estimate, se = std.error)
+
+# Function for printing unordered lists
+print_status <- function(name) {
+  filter(teams, team == name) %>% 
+  pivot_longer(cols = -team, names_to = "var", values_to = "val") %>% 
+  mutate(out = glue::glue("- {var}: {val}\n")) %>% 
+  pull(out) 
+}
 ```
@@
 
+**Teams**:
+
+```{r}
+#| label: teams
+#| echo: false
+teams <- tribble(
+  ~'team',                  ~"Reviewed", ~'Included', 
+  "anomalocaris_ornata",      TRUE,           TRUE,
+  "anthracoceros_coronata",   TRUE,           TRUE,
+  "arapaima_modularis",       TRUE,           TRUE,
+  "comanthina_maculatus",     TRUE,           TRUE,
+  "cromileptes_saxatilis",    TRUE,           TRUE,
+  "ctenosaura_limax",         TRUE,           FALSE,
+  "gnathosaurus_canadensis",  FALSE,          FALSE,
+  "gymnothorax_spinulosus",   FALSE,          FALSE,
+  "haematopus_fossor",        TRUE,           TRUE,
+  "lasionycteris_altavela",   TRUE,           TRUE,
+  "linckia_nattereri",        FALSE,          FALSE,
+  "lycodes_bradfieldi",       FALSE,          FALSE,
+  "naso_cassivellaunos",      FALSE,          FALSE,
+  "trapezia_cantonensis",     FALSE,          FALSE,
+  "trigonias_lachneri",       FALSE,          FALSE,
+  )
+
+knitr::kable(teams)
+```
+
+**Current status**:
+
+```{r}
+#| label: status
+#| echo: false
+teams %>% 
+  summarize(Reviewed = mean(Reviewed), Included = mean(Included)) %>% 
+  pivot_longer(cols = everything(), names_to = " ", values_to = "%") %>% 
+  mutate(`%` = round(`%` * 100, 2)) %>% 
+  knitr::kable(format = "pipe")
+```
+
 ## anomalocaris_ornata
+
+```{r}
+#| label: print_anomalocaris_ornata
+#| echo: false
+#| results: 'asis'
+print_status("anomalocaris_ornata")
+```
+
+```{r}
+#| label: anomalocaris_ornata
+
+# Analyst team setup
+main.df <- read.csv2(here("data", "analyses", "jvc", 
+  "anomalocaris_ornata", "MSA", "data", "data_frame.csv")
+  )
+
+df.int <- main.df %>%
+  filter(keep == "yes") %>%  
+  filter(condition == "NF") %>% 
+  mutate(typicality = fct_relevel(typicality, "typical", "medium", "atypical"))
+
+df.int$Mean_dB <- as.numeric(df.int$Mean_dB)
+
+# F0
+df.f0 <- main.df
+df.f0 <- df.f0 %>%
+  #filter(stress == "stressed") %>%
+  filter(keep == "yes") %>% 
+  filter(condition == "NF") %>%
+  #filter(phoneme %in% c("AO","AW","IH","o","OEH","UH","AH","EH","EH?","u","a?","i","i?" )) %>% 
+  gather(f0_point, f0, F0AtPoint1, F0AtPoint2, F0AtPoint3, F0AtPoint4,
+         F0AtPoint5,F0AtPoint6,F0AtPoint7,F0AtPoint8,F0AtPoint9,F0AtPoint10)%>% 
+  filter(f0 !="--undefined--")%>% 
+  mutate(typicality = fct_relevel(typicality, "typical", "medium", "atypical")) %>% 
+  group_by(voice_type, col_obj)
+
+df.f0$f0 <- as.numeric(df.f0$f0)
+outliers <- boxplot(df.f0$f0, plot=F)$out
+f0.clean <- df.f0[-which(df.f0$f0 %in% outliers),]
+f0.clean <- f0.clean %>% 
+  ungroup() %>% 
+  group_by(speaker) %>% 
+  mutate(f0min = min(f0)) %>%
+  mutate(f0sem=(12*log(f0 /f0min))/log(2)) %>% 
+  ungroup()
+
+under <- f0.clean %>% 
+  filter(f0<150)
+over <- f0.clean %>% 
+  filter(f0>150)
+
+# Vowel
+vowel.df <- main.df
+vowel.df$Duration_in_ms <- as.numeric(vowel.df$Duration_in_ms)
+vowel.df <- vowel.df %>%
+  filter(keep == "yes") %>%  
+  filter(condition == "NF") %>% 
+  filter(stress =="stressed") %>% 
+  mutate(typicality = fct_relevel(typicality, "typical", "medium","atypical")) %>%
+  filter(Duration_in_ms>40)
+
+# FREQ MODELS
+mod1 <- lmer(Mean_dB^2~typicality*col_obj+voice_type+(1+col_obj|speaker),df.int)
+mod2 <- lmer(f0sem~col_obj*typicality+voice_type+(1+col_obj|speaker),under)
+mod3 <- lmer(f0sem~col_obj*typicality+voice_type+(1+col_obj|speaker),over)
+mod4 <- lmer(Duration_in_ms~typicality*col_obj+(1|Word)+(1|speaker),data = vowel.df)
+
+#
+# JVC: Setup and reanalyses
+#
+
+# Intensity
+MSA_int_df <- df.int %>% 
+  mutate(mean_db_2 = Mean_dB ^ 2, 
+    db_z = (mean_db_2 - mean(mean_db_2)) / sd(mean_db_2), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    col_obj = as.factor(col_obj), 
+    col_obj = C(col_obj, sum), 
+    voice_type = as.factor(voice_type), 
+    voice_type = C(voice_type, sum)
+)
+
+# Intensity model
+anomalocaris_ornata_1_int_cat <- brm(
+  db_z ~ effect_cat * col_obj + voice_type + 
+    (1 + col_obj | speaker), 
+  data = MSA_int_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "anomalocaris_ornata_1_int_cat")
+  )
+
+# Pitch "under"
+MSA_under_df <- under %>% 
+  mutate(f0sem_z = (f0sem - mean(f0sem)) / sd(f0sem), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    col_obj = as.factor(col_obj), 
+    col_obj = C(col_obj, sum), 
+    voice_type = as.factor(voice_type), 
+    voice_type = C(voice_type, sum)
+  )
+
+# Pitch "under" model
+anomalocaris_ornata_2_f0under_cat <- brm(
+  f0sem_z ~ effect_cat * col_obj + voice_type + 
+    (1 + col_obj | speaker), 
+  data = MSA_under_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "anomalocaris_ornata_2_f0under_cat")
+  )
+
+# Pitch "over"
+MSA_over_df <- over %>% 
+  mutate(f0sem_z = (f0sem - mean(f0sem)) / sd(f0sem), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    col_obj = as.factor(col_obj), 
+    col_obj = C(col_obj, sum), 
+    voice_type = as.factor(voice_type), 
+    voice_type = C(voice_type, sum)
+  )
+
+# Pitch "over" model
+anomalocaris_ornata_3_f0over_cat <- brm(
+  f0sem_z ~ effect_cat * col_obj + voice_type + 
+    (1 + col_obj | speaker), 
+  data = MSA_over_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  control = list(max_treedepth = 15), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "anomalocaris_ornata_3_f0over_cat")
+  )
+
+# Duration
+MSA_durvowel_df <- vowel.df %>% 
+  mutate(dur_z = (Duration_in_ms - mean(Duration_in_ms)) / sd(Duration_in_ms), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    col_obj = as.factor(col_obj), 
+    col_obj = C(col_obj, sum)
+  )
+
+anomalocaris_ornata_4_durvowel_cat <- brm(
+  dur_z ~ effect_cat * col_obj + 
+    (1 | Word) + (1 | speaker), 
+  data = MSA_durvowel_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "anomalocaris_ornata_4_durvowel_cat")
+  )
+
+```
 
@@
 
+```{r}
+#| label: print_anthracoceros_coronata
+#| echo: false
+#| results: 'asis'
+print_status("anthracoceros_coronata")
+```
+
+```{r}
+#| label: anthracoceros_coronata
+
+data_long <- read_csv(here("data", "analyses", "jvc", "anthracoceros_coronata", 
+  "data", "data_long.csv"))
+
+# Fit LME models (dont converge and not used)
+overall_models <- data_long %>% 
+  group_by(variable) %>% 
+  nest() %>% 
+  mutate(model = map(data, ~ lmer(value ~ typ_mean + (1|speaker), data = .)),
+         tidy = map(model, broom.mixed::tidy, effects = c("fixed", "ran_vals"), conf.int = TRUE, conf.level =.95)) %>% 
+  unnest(tidy) %>% 
+  select(-model)
+
+# Standard lm
+overall_models_lm <- data_long %>% 
+  group_by(variable) %>% 
+  nest() %>% 
+  mutate(model = map(data, ~ lm(value ~ typ_mean, data = .)),
+         tidy = map(model, tidy, conf.int = TRUE, conf.level =.95)) %>% 
+  unnest(tidy) %>% 
+  select(-data, -model)
+
+#
+# JVC: setup and refit
+#
+MSA_ac_all_df <- data_long %>% 
+  group_by(variable) %>% 
+  mutate(value_z = (value - mean(value, na.rm = T)) / sd(value, na.rm = T)) %>% 
+  ungroup() %>% 
+  mutate(effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean))
+
+# A_max_pitch
+anthracoceros_coronata_1_pitchadj_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "A_max_pitch"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_1_pitchadj_con")
+  )
+
+# N_max_pitch
+anthracoceros_coronata_2_pitchnoun_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "N_max_pitch"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_2_pitchnoun_con")
+  )
+
+# A_max_intens
+anthracoceros_coronata_3_intadj_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "A_max_intens"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_3_intadj_con")
+  )
+
+# N_max_intens
+anthracoceros_coronata_4_intnoun_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "N_max_intens"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_4_intnoun_con")
+  )
+
+# A_dur_log
+anthracoceros_coronata_5_duradj_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "A_dur_log"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_5_duradj_con")
+  )
+
+# N_dur_log
+anthracoceros_coronata_6_durnoun_con <- brm(
+  value_z ~ effect_con, 
+  data = filter(MSA_ac_all_df, variable == "N_dur_log"), 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", 
+    "anthracoceros_coronata_6_durnoun_con")
+  )
+```
+
 ## arapaima_modularis
+
+```{r}
+#| label: print_arapaima_modularis
+#| echo: false
+#| results: 'asis'
+print_status("arapaima_modularis")
+```
+
+```{r}
+#| label: arapaima_modularis
+
+data_manyspeech <- read.csv(here("data", "analyses", "jvc", 
+  "arapaima_modularis", "sheet_data_pitch.csv"))
+
+#convert factors and numeric
+data_manyspeech$typicality <- factor(data_manyspeech$typicality)
+data_manyspeech$target_colour <- factor(data_manyspeech$target_colour)
+data_manyspeech$pitch_max_hz <- as.numeric(data_manyspeech$pitch_max_hz)
+data_manyspeech$exclude <- factor(data_manyspeech$exclude)
+
+#select variables to be used, exclude error items
+clean_data <- data_manyspeech %>%
+  select(condition, speaker, typicality, target_colour, pitch_max_hz, exclude) %>%
+  filter(condition == "NF",
+    exclude == "No")
+
+#Main stats
+summary_clean_data <- clean_data %>%
+  group_by(speaker, typicality) %>%
+  rstatix::get_summary_stats(pitch_max_hz)
+
+#rename outcome variable 
+names(summary_clean_data)[names(summary_clean_data) == 'mean'] <- 'mean_pitch'
+
+#exclude three speakers who had typycality conditions < 6
+clean_data_2 <- clean_data %>%
+  filter(speaker != "EM",
+         speaker != "IP",
+         speaker != "JW_3")
+
+#New main stats without 3 excluded participants
+data_for_analysis <- clean_data_2 %>%
+  group_by(speaker, typicality) %>%
+  rstatix::get_summary_stats(pitch_max_hz)
+
+names(data_for_analysis)[names(data_for_analysis) == 'mean'] <- 'mean_pitch'
+
+#find ouliers
+outliers <- data_for_analysis %>%
+  group_by(typicality) %>%
+  rstatix::identify_outliers(mean_pitch)
+  #13 outlier data points were found
+
+#continue without outliers
+data_for_analysis_noOL <- data_for_analysis %>%
+  filter(speaker != "AL",
+         speaker != "JR",
+         speaker != "PS",
+         speaker != "TB")
+
+# Original model
+mod1_am <- ez::ezANOVA(data = data_for_analysis_noOL,
+        wid = speaker,
+        within = typicality,
+        dv = mean_pitch,
+        type = 3)
+
+#
+# JVC: setup df
+#
+MSA_arapaima_modularis_df <- data_for_analysis_noOL %>% 
+  mutate(pitch_z = (mean_pitch - mean(mean_pitch)) / sd(mean_pitch), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"))
+
+# Model
+arapaima_modularis_1_f0_cat <- brm(
+  pitch_z ~ effect_cat, 
+  data = MSA_arapaima_modularis_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "arapaima_modularis_1_f0_cat")
+  )
+```
 
@@
 
+```{r}
+#| label: print_comanthina_maculatus
+#| echo: false
+#| results: 'asis'
+print_status("comanthina_maculatus")
+```
+
+```{r}
+#| label: comanthina_maculatus
+
+# No code provided
+MSA_comanthina_maculatus_df <- read_xlsx(here("data", "analyses", "jvc", 
+  "comanthina_maculatus", "0 Clean Data.xlsx"), na = "--undefined--") %>% 
+  select(key:typicality, 
+    tonic_vowel_duration, tonic_vowel_intensity, tonic_vowel_F0) %>% 
+  na.omit() %>% 
+  filter(typicality != "medium") %>% 
+  mutate(across(starts_with("tonic"), .fns = scale, .names = "{.col}_z")) %>% 
+  mutate(effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment))
+
+# Model
+comanthina_maculatus_1_dur_cat <- brm(
+  tonic_vowel_duration_z ~ effect_cat, 
+  data = MSA_comanthina_maculatus_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "comanthina_maculatus_1_dur_cat")
+  )
+
+comanthina_maculatus_2_int_cat <- brm(
+  tonic_vowel_intensity_z ~ effect_cat, 
+  data = MSA_comanthina_maculatus_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "comanthina_maculatus_2_int_cat")
+  )
+
+comanthina_maculatus_3_f0_cat <- brm(
+  tonic_vowel_F0_z ~ effect_cat, 
+  data = MSA_comanthina_maculatus_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "comanthina_maculatus_3_f0_cat")
+  )
+```
+
 ## cromileptes_saxatilis
+
+```{r}
+#| label: print_cromileptes_saxatilis
+#| echo: false
+#| results: 'asis'
+print_status("cromileptes_saxatilis")
+```
+
+```{r}
+#| label: cromileptes_saxatilis
+
+cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "processed_data", "NF_durations.csv")) %>% 
+  filter(typicality != "medium")
+
+mod_priors <- c(
+  prior("normal(-1, 1)", class="Intercept"),
+  prior("normal(0, 2)", class="b"),
+  prior("student_t(3, 0, 1)", class="sd"),
+  prior("lkj(2)", class="L")
+)
+
+# Original model
+if(F) {
+set.seed(12341234)
+mod <- brm(colour_dur ~ 
+             typicality + 
+             (1 + typicality | target_colour) + 
+             (1 | target_name) + 
+             (1 | speaker),
+           data=cromileptes_saxatilis_durs, cores=4,
+           family=lognormal(),
+           prior=mod_priors,
+           control=list(adapt_delta=0.99,
+                        max_treedepth=16),
+           iter=4000,
+           warmup=2000)
+}
+
+#
+# JVC refits
+#
+
+MSA_cromileptes_saxatilis_df <- cromileptes_saxatilis_durs %>% 
+  mutate(colour_dur_log = log(colour_dur), 
+    colour_dur_z = (colour_dur_log - mean(colour_dur_log)) / sd(colour_dur_log), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment))
+
+cromileptes_saxatilis_1_dur_cat <- brm(
+  colour_dur_z ~ effect_cat + 
+    (1 + typicality | target_colour) + 
+    (1 | target_name) + 
+    (1 | speaker), 
+  data = MSA_cromileptes_saxatilis_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "cromileptes_saxatilis_1_dur_cat")
+  )
+```
 
@@
 
+```{r}
+#| label: print_ctenosaura_limax
+#| echo: false
+#| results: 'asis'
+print_status("ctenosaura_limax")
+```
+
+```{r}
+#| label: ctenosaura_limax
+
+```
+
 ## gnathosaurus_canadensis
+
+```{r}
+#| label: print_gnathosaurus_canadensis
+#| echo: false
+#| results: 'asis'
+print_status("gnathosaurus_canadensis")
+```
+
+```{r}
+
+```
 
@@
 
+```{r}
+#| label: print_gymnothorax_spinulosus
+#| echo: false
+#| results: 'asis'
+print_status("gymnothorax_spinulosus")
+```
+
 ## haematopus_fossor
+
+```{r}
+#| label: print_haematopus_fossor
+#| echo: false
+#| results: 'asis'
+print_status("haematopus_fossor")
+```
 
@@
 ```{r}
+#| label: print_lasionycteris_altavela
+#| echo: false
+#| results: 'asis'
+print_status("lasionycteris_altavela")
+```
+
+```{r}
 #| label: lasionycteris_altavela
@@
 
+```{r}
+#| label: print_linckia_nattereri
+#| echo: false
+#| results: 'asis'
+print_status("linckia_nattereri")
+```
+
 ## lycodes_bradfieldi
+
+```{r}
+#| label: print_lycodes_bradfieldi
+#| echo: false
+#| results: 'asis'
+print_status("lycodes_bradfieldi")
+```
 
@@
 
+```{r}
+#| label: print_naso_cassivellaunos
+#| echo: false
+#| results: 'asis'
+print_status("naso_cassivellaunos")
+```
+
 ## trapezia_cantonensis
 
+```{r}
+#| label: print_trapezia_cantonensis
+#| echo: false
+#| results: 'asis'
+print_status("trapezia_cantonensis")
+```
+
 ## trigonias_lachneri
+
+```{r}
+#| label: print_trigonias_lachneri
+#| echo: false
+#| results: 'asis'
+print_status("trigonias_lachneri")
+```
 
@@
 
-# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"
-msa_models <- dir_ls(path = here("data", "analyses", "models"), regexp = ".rds$") %>% 
+msa_models <- dir_ls(path = here("data", "analyses", "models"), 
+  regexp = ".rds$") %>% 
   as_tibble() %>% 
@@
   mutate(sum = map(model, clean_up)) %>% 
-  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+  suppressWarnings() 
 ```
@@
   aes(x = estimate, y = mod_name) + 
+  geom_vline(xintercept = 0, lty = 3) + 
   geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
-    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
-  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
+    color = "#cc0033", alpha = 0.5, size = 1.5, lineend = "round") + 
+  geom_point(color = "#cc0033", pch = 21, stroke = 1.5, size = 1.6) + 
   labs(y = "Model", x = "Estimate ± SE") + 

### 2022-06-27 scripts/r/04_refit/refit_tr.Rmd
refit

@@
 library("optimx")
+library("MuMIn")
+library("fda")
+library("abind")
+library("data.table")
+library("magrittr")
+library("tidyverse")
+
+# NOTE: one of the many packages interferes with tidyverse, so the select function throws an error!
 
@@
   filter(term %in% c("effect_cattypical", "effect_con")) %>% 
-  select(term, estimate, se = std.error)
-
-```
+  dplyr::select(term, estimate, se = std.error)
+
 ```
@@
 # adjective model - pitch
-pitch_adj_data = pitchfile %>% filter(word == 9)%>% mutate(type = "adjective")
-pitch_noun_data = pitchfile %>% filter(word == 10)%>%mutate(type = "noun")
+pitch_adj_data = pitchfile %>% filter(word == 9) %>% mutate(type = "adjective")
+pitch_noun_data = pitchfile %>% filter(word == 10) %>% mutate(type = "noun")
 
@@
 # standardize
-duration_adj_data_temp <- duration_adj_data %>% 
-  mutate(duration_s = (duration - mean(duration, na.rm =TRUE)) / sd(duration,  na.rm = TRUE),
+duration_adj_data <- duration_adj_data %>% 
+  mutate(
+    #duration_s = (duration - mean(duration, na.rm = TRUE)) / sd(duration,  na.rm = TRUE),
+    # does not work and I don't know why. 
     # dummy-code typicality
     typicality = as.factor(typicality),
-  target_colour = as.factor(target_colour),
-  effect_cat = C(typicality, treatment),
-  # sum-code categorical predictors
-  target_colour_s = C(target_colour, sum)
-  )
+    target_colour_s = as.factor(target_colour),
+    effect_cat = C(typicality, treatment))
+
+contrasts(duration_adj_data$target_colour_s) <- contr.sum(5)
+
+duration_adj_data$duration_s = (duration_adj_data$duration - mean(duration_adj_data$duration, na.rm = TRUE)) / sd(duration_adj_data$duration,  na.rm = TRUE)
 
@@
          # scale continuous variables
-         duration_s = (duration - mean(duration, na.rm = TRUE)) / sd(duration,  na.rm = TRUE),
+         # duration_s = (duration - mean(duration, na.rm = TRUE)) / sd(duration,  na.rm = TRUE),
          # dummy-code typicality
          typicality = as.factor(typicality),
-         target_colour = as.factor(target_colour),
-         effect_cat = C(typicality, treatment),
-         # sum-code categorical predictors
-         target_colour_s = C(target_colour, sum)
-  )
+         target_colour_s = as.factor(target_colour),
+         effect_cat = C(typicality, treatment)
+  )
+
+contrasts(duration_noun_data$target_colour_s) <- contr.sum(5)
+
+duration_noun_data$duration_s = (duration_noun_data$duration - mean(duration_noun_data$duration, na.rm = TRUE)) / sd(duration_noun_data$duration,  na.rm = TRUE)
 
@@
          # scale continuous variables
-         minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
-         maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
-         range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
+         # minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
+         # maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
+         # range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
          # dummy-code typicality
          typicality = as.factor(typicality),
-         target_colour = as.factor(target_colour),
-         effect_cat = C(typicality, treatment),
-         # sum-code categorical predictors
-         target_colour_s = C(target_colour, sum)
-  )
+         target_colour_s = as.factor(target_colour),
+         effect_cat = C(typicality, treatment)
+  )
+
+contrasts(pitch_adj_data$target_colour_s) <- contr.sum(5)
+
+pitch_adj_data$minimum_s = (pitch_adj_data$minimum - mean(pitch_adj_data$minimum, na.rm = TRUE)) / sd(pitch_adj_data$minimum,  na.rm = TRUE)
+pitch_adj_data$maximum_s = (pitch_adj_data$maximum - mean(pitch_adj_data$maximum, na.rm = TRUE)) / sd(pitch_adj_data$maximum,  na.rm = TRUE)
+pitch_adj_data$range_s = (pitch_adj_data$range - mean(pitch_adj_data$range, na.rm = TRUE)) / sd(pitch_adj_data$range,  na.rm = TRUE)
 
@@
          # scale continuous variables
-         minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
-         maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
-         range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
+         #minimum_s = (minimum - mean(minimum, na.rm = TRUE)) / sd(minimum,  na.rm = TRUE),
+         #maximum_s = (maximum - mean(maximum, na.rm = TRUE)) / sd(maximum,  na.rm = TRUE),
+         #range_s = (range - mean(range, na.rm = TRUE)) / sd(range,  na.rm = TRUE),
          # dummy-code typicality
          typicality = as.factor(typicality),
-         target_colour = as.factor(target_colour),
+         target_colour_s = as.factor(target_colour),
          effect_cat = C(typicality, treatment),
          # sum-code categorical predictors
-         target_colour_s = C(target_colour, sum)
-  )
+         # target_colour_s = C(target_colour, sum, 5)
+  )
+
+# sum-code categorical predictors
+contrasts(pitch_noun_data$target_colour_s) <- contr.sum(5)
+
+pitch_noun_data$minimum_s = (pitch_noun_data$minimum - mean(pitch_noun_data$minimum, na.rm = TRUE)) / sd(pitch_noun_data$minimum,  na.rm = TRUE)
+pitch_noun_data$maximum_s = (pitch_noun_data$maximum - mean(pitch_noun_data$maximum, na.rm = TRUE)) / sd(pitch_noun_data$maximum,  na.rm = TRUE)
+pitch_noun_data$range_s = (pitch_noun_data$range - mean(pitch_noun_data$range, na.rm = TRUE)) / sd(pitch_noun_data$range,  na.rm = TRUE)
 
@@
 trachyphyllia_lappa_1_duradj_cat <- brm(
-  duration_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  duration_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
@@
 trachyphyllia_lappa_2_f0maxadj_cat <- brm(
-  maximum_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  maximum_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
@@
 trachyphyllia_lappa_3_f0minadj_cat <- brm(
-  minimum_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  minimum_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) +  
       (1 | phrase),
@@
 trachyphyllia_lappa_4_f0rangeadj_cat <- brm(
-  range_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  range_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
@@
 
+# refitted with more samples because of the interaction
 trachyphyllia_lappa_5_durnoun_cat <- brm(
-  duration_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  duration_s ~  effect_cat * target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
   data = duration_noun_data, 
+  iter = 4000,
+  control = list(adapt_delta = 0.9999),
   seed = 111,
@@
 trachyphyllia_lappa_6_f0maxnoun_cat <- brm(
-  maximum_s ~  typicality + target_colour + 
-      (typicality + target_colour | speaker) + 
+  maximum_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
@@
 trachyphyllia_lappa_7_f0minnoun_cat <- brm(
-  minimum_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  minimum_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) +  
       (1 | phrase),
@@
 trachyphyllia_lappa_8_f0rangenoun_cat <- brm(
-  range_s ~  typicality + target_colour + 
-      (typicality + target_colour  | speaker) + 
+  range_s ~  effect_cat + target_colour_s + 
+      (typicality + target_colour_s  | speaker) + 
       (1 | phrase),
@@
          # sum-code categorical predictors
-         condition_s = C(as.factor(condition), sum)
+         condition_s = as.factor(condition),
+         condition_s = C(condition_s, sum)
   )
@@
 
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
+```{r pervagor_meeki_setup}
+
+data = read.csv("./data/analyses/tr/pervagor_meeki/Data/ManySpeech_Praat_merged_data.csv", header=T)
+
+data$Duration_ms = data$Duration*1000
+data_to_analyze <- data
+
+########## SET CONTRASTS ############
+
+###### set sum contrasts (compare to grand mean)
+data_to_analyze$typicality = factor(data_to_analyze$typicality)
+
+contrasts(data_to_analyze$typicality) = contr.treatment(3)
+
+########### REMOVE OUTLIERS ###########
+
+# TRIMMING >3 SD AND <3 SD, by SPEAKER
+
+########### MEAN PITCH (semitones) ##################
+data_meanf0_trim <- data_to_analyze %>% group_by(speaker) %>%
+  mutate(avg = mean(Mean_f0_st), stdev = sd(Mean_f0_st)) %>%  
+  filter(Mean_f0_st <= (3*stdev)+avg & 
+           Mean_f0_st >= avg-(3*stdev)) %>%  
+  select(colnames(data_to_analyze)) %>%
+  as.data.frame()
+
+########### MAX PITCH (semitones) ##################
+data_maxf0_trim <- data_to_analyze %>% group_by(speaker) %>%
+  mutate(avg = mean(Max_f0_st), stdev = sd(Max_f0_st)) %>%  
+  filter(Max_f0_st <= (3*stdev)+avg & 
+           Max_f0_st >= avg-(3*stdev)) %>%  
+  select(colnames(data_to_analyze)) %>%
+  as.data.frame()
+
+########### INTENSITY (Praat measurements) ##################
+data_int_trim <- data_to_analyze %>% group_by(speaker) %>%
+  mutate(avg = mean(Overall_Intensity), stdev = sd(Overall_Intensity)) %>%  
+  filter(Overall_Intensity <= (3*stdev)+avg & 
+           Overall_Intensity >= avg-(3*stdev)) %>% 
+  select(colnames(data_to_analyze)) %>%
+  as.data.frame()
+
+########### DURATION ##################
+data_dur_trim <- data_to_analyze %>% group_by(speaker) %>%
+  mutate(avg = mean(Duration_ms), stdev = sd(Duration_ms)) %>%  
+  filter(Duration_ms <= (3*stdev)+avg & #slow RTs greater than 3 SD
+           Duration_ms >= avg-(3*stdev)) %>%  #fast RTs less than 3 SD
+  select(colnames(data_to_analyze)) %>%
+  as.data.frame()
+
+##################### MODELS ############################
+
+#set which contrast is dropped from the models
+
+#run models twice:
+#base = 3: drop typical
+#base = 2: drop medium
+base_n = 3
+
+########### MEAN PITCH (semitones) ##################
+
+contrasts(data_meanf0_trim$typicality) = contr.treatment(3,base=base_n)
+contrasts(data_meanf0_trim$typicality)
+
+```
+
+```{r pervagor_meeki_models}
+
+# mean F0
+  #NOUN MODEL
+  summary( meanf0_mod <- lmer (Mean_f0_st ~ typicality
+                               + (typicality | speaker),
+                               data = data_meanf0_trim[data_meanf0_trim$word_type == "target_name",],
+                               control=lmerControl(optimizer="bobyqa")))
+
+  #ADJECTIVE MODEL
+  summary( meanf0_mod <- lmer (Mean_f0_st ~ typicality
+                               + (1 | speaker)
+                               + (1 | target_word),
+                               data = data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",],
+                               control=lmerControl(optimizer="bobyqa")))
+
+# max F0
+   #NOUN MODEL
+   summary( maxf0_mod <- lmer (Max_f0_st ~ typicality
+                              + (1 | speaker),
+                              data = data_maxf0_trim[data_maxf0_trim$word_type == "target_name",],
+                              control=lmerControl(optimizer="bobyqa")))
+
+  #ADJECTIVE MODEL
+  summary( maxf0_mod <- lmer (Max_f0_st ~ typicality
+                              + (1 | speaker)
+                              + (1 | target_word),
+                              data = data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",],
+                              control=lmerControl(optimizer="bobyqa")))
+
+# int
+  #NOUN MODEL
+  summary( int_mod <- lmer (Overall_Intensity ~ typicality
+                            + (1 | speaker),
+                            data = data_int_trim[data_int_trim$word_type == "target_name",],
+                            control=lmerControl(optimizer="bobyqa")))
+
+  #ADJECTIVE MODEL
+  summary( int_mod <- lmer (Overall_Intensity ~ typicality
+                            + (1 | speaker)
+                            + (typicality | target_word),
+                            data = data_int_trim[data_int_trim$word_type == "target_colour",],
+                            control=lmerControl(optimizer="bobyqa")))
+
+# duration  
+  #NOUN MODEL
+  summary( dur_mod <- lmer (Duration_ms ~ typicality
+                            + (1 | speaker),
+                            data = data_dur_trim[data_dur_trim$word_type == "target_name",],
+                            control=lmerControl(optimizer="bobyqa")))
+
+  #ADJECTIVE MODEL
+  summary( dur_mod <- lmer (Duration_ms ~ typicality
+                            + (1 | speaker)
+                            + (typicality | target_word),
+                            data = data_dur_trim[data_dur_trim$word_type == "target_colour",],
+                            control=lmerControl(optimizer="bobyqa")))
+```
+
+```{r pervagor_meeki_refitting}
+
+# scale
+data_int_trim <- data_int_trim %>% 
+  mutate(
+    Overall_Intensity_s = (Overall_Intensity - mean(Overall_Intensity, na.rm = TRUE)) / sd(Overall_Intensity,  na.rm = TRUE),
+    effect_cat = as.factor(typicality),
+    effect_cat = C(effect_cat, treatment)
+  )
+
+data_meanf0_trim <- data_meanf0_trim %>% 
+  mutate(
+    Mean_f0_st_s = (Mean_f0_st - mean(Mean_f0_st, na.rm = TRUE)) / sd(Mean_f0_st,  na.rm = TRUE),
+    effect_cat = as.factor(typicality),
+    effect_cat = C(effect_cat, treatment)
+  )
+
+data_maxf0_trim <- data_maxf0_trim %>% 
+  mutate(
+    Max_f0_st_s = (Max_f0_st - mean(Max_f0_st, na.rm = TRUE)) / sd(Max_f0_st,  na.rm = TRUE),
+    effect_cat = as.factor(typicality),
+    effect_cat = C(effect_cat, treatment)
+  )
+
+data_dur_trim <- data_dur_trim %>% 
+  mutate(
+    Duration_ms_s = (Duration_ms - mean(Duration_ms, na.rm = TRUE)) / sd(Duration_ms,  na.rm = TRUE),
+    effect_cat = as.factor(typicality),
+    effect_cat = C(effect_cat, treatment)
+  )
+
+pervagor_meeki_1_intnoun_cat <- brm(
+  Overall_Intensity_s ~ 
+         effect_cat + 
+         (1|speaker),
+  seed = 111,
+  data = data_int_trim[data_int_trim$word_type == "target_name",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_1_intnoun_cat"
+  )
+
+pervagor_meeki_2_f0meannoun_cat <- brm(
+  Mean_f0_st_s ~ 
+         effect_cat + 
+         + (effect_cat | speaker),
+  seed = 111,
+  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_name",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_2_f0meannoun_cat"
+  )
+
+pervagor_meeki_3_f0maxnoun_cat <- brm(
+  Max_f0_st_s ~ 
+         effect_cat + 
+         + (1| speaker),
+  seed = 111,
+  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_name",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_3_f0maxnoun_cat"
+  )
+
+pervagor_meeki_4_durnoun_cat <- brm(
+  Duration_ms_s ~ 
+         effect_cat + 
+         + (1| speaker),
+  seed = 111,
+  data = data_dur_trim[data_dur_trim$word_type == "target_name",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_4_durnoun_cat"
+  )
+
+pervagor_meeki_5_intadj_cat <- brm(
+  Overall_Intensity_s ~ 
+         effect_cat 
+         + (1 | speaker)
+         + (effect_cat | target_word),
+  seed = 111,
+  data = data_int_trim[data_int_trim$word_type == "target_colour",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_5_intadj_cat"
+  )
+
+pervagor_meeki_6_f0meanadj_cat <- brm(
+  Mean_f0_st_s ~ 
+         effect_cat + 
+         + (1 | speaker)
+         + (1 | target_word),
+  seed = 111,
+  data = data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_6_f0meanadj_cat"
+  )
+
+pervagor_meeki_7_f0maxadj_cat <- brm(
+  Max_f0_st_s ~ 
+         effect_cat + 
+         + (1 | speaker)
+         + (1 | target_word),
+  seed = 111,
+  data = data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_7_f0maxadj_cat"
+  )
+
+pervagor_meeki_8_duradj_cat <- brm(
+  Duration_ms_s ~ 
+         effect_cat + 
+          + (1 | speaker)
+          + (effect_cat | target_word),
+  seed = 111,
+  data = data_dur_trim[data_dur_trim$word_type == "target_colour",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_8_duradj_cat"
+  )
 
@@
 
-```{r authors setup}
+```{r procambarus_maculosus_setup}
+
+getPCscores <- function(fpcaObj) {
+  if (is.matrix(fpcaObj$scores)) {
+    fpcaObj$scores
+  } else if (is.array(fpcaObj$scores) & length(dim(fpcaObj$scores)) == 3) {
+    apply(fpcaObj$scores, 1:2, sum)
+  } else {
+    stop("getPCscores: invalid input fpcaObj")
+  }
+}
+
+##### load data #####
+
+data <- read.delim("./data/analyses/tr/selectedData.txt", header = T, sep = "") %>% 
+  as_tibble() # %>% 
+  # filter(sex == "female") # only run on female data!
+
+data = read.csv("./data/analyses/tr/pervagor_meeki/Data/ManySpeech_Praat_merged_data.csv", header=T)
+
+info <- data %>% 
+  select(sl_rowIdx, bundle, vowel, speaker, sex, typicality, word) %>% 
+  unique()
+
+##### FPCA #####
+
+# set parameters
+nKnots <- 6
+lambda <- 1e-8
+Lfdobj <- 2
+nOrder <- 2 + Lfdobj
+nBasis <- nKnots + nOrder - 2
+
+# create a basis for B-splines
+basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = nBasis, norder = nOrder)
+
+# define functional parameter object (will be used to estimate functional parameters later)
+fdParObj <- fdPar(fdobj = basis, Lfdobj = Lfdobj, lambda = lambda)
+
+coef <- data %>%
+  group_by(sl_rowIdx) %>%
+  summarise(coef = c(smooth.basis(argvals = times_norm, y = F0, fdParObj)$fd$coefs),
+            coefId = seq_len(nBasis)) %>%
+  ungroup() %>%
+  pivot_wider(names_from = coefId, values_from = coef) %>%
+  select(-sl_rowIdx) %>% 
+  abind(along = 2) %>%
+  aperm(c(2,1))
+
+# check class and dimension
+coef %>% class() # array
+coef %>% dim()   # 8 842; 8 671
+
+# create functional data object
+y_fd <- fd(coef = coef, basisobj = basis)
+
+# this is the actual FPCA
+nPCs <- 3
+y_pcafd <- pca.fd(y_fd, nharm = nPCs, fdParObj)
+# saveRDS(y_pcafd, file = "./pcafd.rds")
+
+y_pcafd$varprop 
+# both sexes: 0.92432242 0.04662226 0.01509360
+# only female: 0.87031521 0.08118398 0.02410822
+
+info %<>% 
+  cbind(y_pcafd %>% getPCscores) %>%
+  rename(s1 = `1`, s2 = `2`, s3 = `3`) %>% 
+  as_tibble()
+# write.table(info, "./PCscores.txt")
+
+##### interpretation #####
+
+tx <- seq(1/1000, 1, by = 1/1000)
+
+curves <- expand.grid(time = tx,
+                      PC = 1:3,
+                      perturbation = c(-1, 0, 1)
+) %>% setDT
+
+sd_score <- info %>% summarise_at(vars(s1:s3), sd) %>% as.numeric()
+
+curves[, value := (y_pcafd$meanfd$coefs[,1] + perturbation * sd_score[PC] * y_pcafd$harmonics$coefs[,PC]) %>% 
+         fd(., basis) %>%
+         eval.fd(tx, .),
+       by = .(PC, perturbation)]
+
+reconstruct <- curves %>% mutate(per = ifelse(perturbation == 0, "mu[F0](t)",
+                                              ifelse(perturbation == 1, "mu[F0](t) + sigma[s[k]] %.% PCk[F0](t)",
+                                                     "mu[F0](t) - sigma[s[k]] %.% PCk[F0](t)")),
+                                 k = case_when(PC == 1 ~ "k == 1",
+                                               PC == 2 ~ "k == 2",
+                                               PC == 3 ~ "k == 3"))
+
+reconstruct$per <- factor(reconstruct$per)
+
+levels(reconstruct$per) = list("mu[F0](t) - sigma[s[k]] %.% PCk[F0](t)" = "0",
+                               "mu[F0](t)" = "1",
+                               "mu[F0](t) + sigma[s[k]] %.% PCk[F0](t)" = "2")
+
+pl <- ggplot(reconstruct) + 
+  aes(x = time, y = value) + 
+  geom_line(size = 1.2) + 
+  facet_grid(k~per, labeller = label_parsed) +
+  xlab("Normalised Time") + ylab("F0 [Hz]") + theme + 
+  guides(linetype = guide_legend(override.aes = list(size = 1)))
+ggsave(filename = "./PCcurves.png", plot = pl, width = 25, height = 20, unit = "cm")
+
+pl <- ggplot(info %>% pivot_longer(cols = s1:s3) %>% 
+               mutate(score = case_when(name == "s1" ~ "s[1]",
+                                        name == "s2" ~ "s[2]",
+                                        name == "s3" ~ "s[3]"))) + 
+  aes(x = 0, y = value, fill = typicality) + 
+  facet_grid(score~., scales = "free_y", labeller = label_parsed, switch = "y") + 
+  geom_boxplot() + ylab("") + xlab("") +
+  theme + theme(strip.background.y = element_rect(fill = "white"), 
+                strip.placement = "outside",
+                legend.margin = margin(t = -15))
+ggsave(filename = "./PCscores.png", plot = pl, width = 18, height = 18, unit = "cm")
+
+##### different interpretation #####
+
+tx <- seq(1/1000, 1, by = 1/1000)
+
+curves <- expand.grid(time = tx,
+                      PC = 1:2,
+                      perturbation = seq(-1, 1, by = .25)
+) %>% setDT
+
+sd_score <- info %>% summarise_at(vars(s1:s3), sd) %>% as.numeric()
+
+curves[, value := (y_pcafd$meanfd$coefs[,1] + perturbation * sd_score[PC] * y_pcafd$harmonics$coefs[,PC]) %>% 
+         fd(., basis) %>%
+         eval.fd(tx, .),
+       by = .(PC, perturbation)]
+
+PC_labeller <- as_labeller(function(x) paste0('PC', x))
+
+pl <- ggplot(curves) +
+  aes(x = time, y = value, col = perturbation, group = perturbation) +
+  geom_line(size = 1.2) +
+  scale_color_gradient2(name = "P ", low = "cornflowerblue", mid = "grey", high = "darkgoldenrod1") +
+  facet_grid(~PC, labeller = PC_labeller) +
+  geom_line(data = curves[perturbation == 0], color = "black", size = 1.5) +
+  xlab("Normalised Time") + ylab("F0 [Hz]") +
+  theme + theme(legend.direction = "horizontal", 
+                legend.title = element_text(),
+                legend.text = element_text(size = 12))
+ggsave(filename = "./PCcurves_col.png", plot = pl, width = 20, height = 12, unit = "cm")
 
@@
 
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
+```{r chelonia_brummeri_setup}
+
+# function to convert hz to semitone
+f2st <- function(hz, base) {
+  f0_st <- 12 * log2(hz / base)
+  return(f0_st)
+}
+
+#################
+### Load data ###
+#################
+d <- read_delim("./data/analyses/tr/chelonia_brummeri/analysis/german_msa_prosody.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
+syll <- read_csv("./data/analyses/tr/chelonia_brummeri/analysis/syllables.csv")
+
+#######################
+### Data processing ###
+#######################
+# Remove errors and hesitations
+d_orig <- d
+d <- subset(d, is.na(notes))
+
+# Retain only NF condition which is the only one with typicality ratings
+d <- subset(d, cond == "NF")
+
+# label half
+# d$half <- ifelse(d$nTrial <= 35, "first", "second")
+# TR: DID not reproduce, needed to change nTrial to trial
+d$half <- ifelse(d$trial <= 35, "first", "second")
+
+# Get durations in ms
+d$adj_vdur <- (d$adj_v_end - d$adj_v_start) * 1000
+d$utt_dur <- d$utt_dur*1000
+
+# Get relative duration (NF cond only)
+d <- merge(d, syll, by = "noun")
+d$avg_syll_dur <- d$utt_dur / d$n_syll
+d$rel_dur <- d$adj_vdur - d$avg_syll_dur
+
+# Convert pascal to dB
+d$adj_v_intens <- 20*log10(d$adj_v_amp/0.00002)
+d$utt_intens <- 20*log10(d$utt_amp/0.00002)
+
+# Get relative intensity
+d$rel_intens <- d$adj_v_intens - d$utt_intens
+
+# Convert hertz to semitone
+d$adj_maxf0 <- as.numeric(as.character(d$adj_maxf0))
+d$adj_time_maxf0 <- as.numeric(as.character(d$adj_time_maxf0))
+d$adj_minf0 <- as.numeric(as.character(d$adj_minf0))
+d$adj_time_minf0 <- as.numeric(as.character(d$adj_time_minf0))
+
+# get f0 min for each participant from the two min columns
+bases <- c()
+my_subjects <- unique(d$subj)
+for (i in 1:length(my_subjects)) {
+  tmp <- subset(d, subj == my_subjects[i])
+  minf0 <- min(tmp$adj_minf0, na.rm = T)
+  bases <- append(bases, minf0)
+}
+
+bases <- cbind(my_subjects, bases)
+bases <- data.frame(bases)
+colnames(bases) <- c("subj", "minf0")
+d <- merge(d, bases, by = "subj")
+d$minf0 <- as.numeric(as.character(d$minf0))
+
+d$adj_maxf0_st <- f2st(d$adj_maxf0, d$minf0)
+d$adj_minf0_st <- f2st(d$adj_minf0, d$minf0)
+d$f0range_st <- d$adj_maxf0_st - d$adj_minf0_st
+
+```
+
+```{r chelonia_brummeri_models}
+
+# treatment coding with baseline = typical
+d$nTypicality1 <- ifelse(d$typicality == "atypical", 1, 0)
+d$nTypicality2 <- ifelse(d$typicality == "medium", 1, 0)
+
+# syllable structure
+d$syll_structure <- ifelse(d$adj %in% c("roten"), "CV", ifelse(d$adj %in% c("gruenen", "braunen"), "CCV", "CVC"))
+d$nSyll1 <- ifelse(d$syll_structure == "CCV", 1, ifelse(d$syll_structure == "CV", -1, 0))
+d$nSyll2 <- ifelse(d$syll_structure == "CVC", 1, ifelse(d$syll_structure == "CV", -1, 0))
+
+# center DVs
+d$Nreldur <- d$rel_dur - mean(d$rel_dur)
+d$Nrelintens <- d$rel_intens - mean(d$rel_intens)
+d$Nadj_maxf0_st <- d$adj_maxf0_st - mean(d$adj_maxf0_st)
+d$Nf0range_st <- d$f0range_st - mean(d$f0range_st)
+d$Nadj_maxf0 <- d$adj_maxf0 - mean(d$adj_maxf0)
+# TR: does not reproduce
+# d$Nadj_maxf0_erb <- d$adj_maxf0_erb - mean(d$adj_maxf0_erb)
+# TR: I assume, the authors meant st?
+d$Nf0range_st <- d$f0range_st - mean(d$f0range_st)
+d$nTrial <- d$trial - 35
+
+# run models 
+# TR: added cores to speed up
+fit_reldur2 <- brm(Nreldur ~ nTypicality1*nTrial + nTypicality2*nTrial + nSyll1 + nSyll2 + (1 + nTypicality1  + nTypicality2 |subj) + (1 | adj), d, control = list(adapt_delta = 0.99), cores = 4, prior = c(
+  prior(normal(0, 200), class = Intercept),
+  prior(normal(0, 200), class = b, coef = nTypicality1),
+  prior(normal(0, 200), class = b, coef = nTypicality2),
+  prior(normal(0, 200), class = b, coef = nTrial), 
+  prior(normal(0, 200), class = b, coef = nSyll1),
+  prior(normal(0, 200), class = b, coef = nSyll2))
+)
+
+fit_relintens2 <- brm(Nrelintens ~ nTypicality1*nTrial + nTypicality2*nTrial + nSyll1 + nSyll2 + (1 + nTypicality1  + nTypicality2 |subj) + (1 | adj), d, control = list(adapt_delta = 0.99), cores = 4, prior = c(
+  prior(normal(0, 4), class = Intercept), 
+  prior(normal(0, 4), class = b, coef = nTypicality1),
+  prior(normal(0, 4), class = b, coef = nTypicality2), 
+  prior(normal(0, 4), class = b, coef = nTrial),
+  prior(normal(0, 4), class = b, coef = nSyll1),
+  prior(normal(0, 4), class = b, coef = nSyll2))
+)
+
+fit_maxf0st2 <- brm(Nadj_maxf0_st ~ nTypicality1*nTrial + nTypicality2*nTrial + nSyll1 + nSyll2 + (1 + nTypicality1  + nTypicality2 |subj) + (1 | adj), d, control = list(adapt_delta = 0.9999, cores = 4, max_treedepth = 15), iter = 4000, prior = c(
+  prior(normal(0, 7), class = Intercept),
+  prior(normal(0, 7), class = b, coef = nTypicality1),
+  prior(normal(0, 7), class = b, coef = nTypicality2),
+  prior(normal(0, 7), class = b, coef = nTrial),
+  prior(normal(0, 7), class = b, coef = nSyll1),
+  prior(normal(0, 7), class = b, coef = nSyll2))
+)
+
+fit_f0range2 <- brm(Nf0range_st ~ nTypicality1*nTrial + nTypicality2*nTrial + nSyll1 + nSyll2 + (1 + nTypicality1  + nTypicality2 |subj) + (1 | adj), d, control = list(adapt_delta = 0.9999, cores = 4, max_treedepth = 15), iter = 4000, prior = c(
+  prior(normal(0, 7), class = Intercept),
+  prior(normal(0, 7), class = b, coef = nTypicality1),
+  prior(normal(0, 7), class = b, coef = nTypicality2),
+  prior(normal(0, 7), class = b, coef = nTrial),
+  prior(normal(0, 7), class = b, coef = nSyll1),
+  prior(normal(0, 7), class = b, coef = nSyll2))
+)
+
+```
+
+```{r chelonia_brummeri_refitting}
+
+# standardize
+d <- d %>% 
+  mutate(
+    Nreldur_s = (Nreldur - mean(Nreldur, na.rm = TRUE)) / sd(Nreldur,  na.rm = TRUE),
+    Nrelinten_s = (Nrelintens - mean(Nrelintens, na.rm = TRUE)) / sd(Nrelintens,  na.rm = TRUE),
+    Nadj_maxf0_st_s = (Nadj_maxf0_st - mean(Nadj_maxf0_st, na.rm = TRUE)) / sd(Nadj_maxf0_st,  na.rm = TRUE),
+    Nf0range_st_s = (Nf0range_st - mean(Nf0range_st, na.rm = TRUE)) / sd(Nf0range_st,  na.rm = TRUE),
+    nTrial_s = (nTrial - mean(nTrial, na.rm = TRUE)) / sd(nTrial,  na.rm = TRUE),
+    effect_cat = C(as.factor(typicality), treatment),
+    syll_structure_s = C(as.factor(syll_structure), sum)
+  )
+
+# refit models 
+# TR: instead of hard coding treatment coding as the authors did, we simplify the model by using deviation coding for typicality
+# duration
+chelonia_brummeri_1_dur_cat <- brm(
+  Nreldur_s ~ 
+         effect_cat*nTrial_s + 
+         syll_structure_s + 
+         (1 + effect_cat |subj) + 
+         (1 | adj),
+  seed = 111,
+  data = d, 
+  cores = 4,  
+  file = "./data/analyses/models/chelonia_brummeri_1_dur_cat"
+  )
+
+# intensity
+chelonia_brummeri_2_int_cat <- brm(
+  Nrelinten_s ~ 
+           effect_cat*nTrial_s + 
+         syll_structure_s + 
+         (1 + effect_cat |subj) + 
+         (1 | adj),
+  seed = 111,
+  data = d, 
+  cores = 4,  
+  file = "./data/analyses/models/chelonia_brummeri_2_int_cat"
+  )
+
+# f0 range
+chelonia_brummeri_3_f0range_cat <- brm(
+  Nf0range_st_s ~ 
+         effect_cat*nTrial_s + 
+         syll_structure_s + 
+         (1 + effect_cat |subj) + 
+         (1 | adj),
+  seed = 111,
+  data = d, 
+  cores = 4,  
+  file = "./data/analyses/models/chelonia_brummeri_3_f0range_cat"
+  )
+
+# f0 max
+chelonia_brummeri_4_f0max_cat <- brm(
+  Nadj_maxf0_st_s ~ 
+          effect_cat*nTrial_s + 
+         syll_structure_s + 
+         (1 + effect_cat |subj) + 
+         (1 | adj),
+  seed = 111,
+  data = d, 
+  cores = 4,  
+  file = "./data/analyses/models/chelonia_brummeri_4_f0max_cat"
+  )
 
@@
 
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
+```{r procambarus_mahogoni_setup}
+
+# read csv
+msa_data_raw <- read_csv("./data/analyses/tr/procambarus_mahogoni/MSA-data.csv")
+
+# transform raw data 
+msa_data <- msa_data_raw %>%
+mutate(v1_duration_c_std = (v1_duration_c - mean(v1_duration_c)) / sd(v1_duration_c),
+       v1_pitch_mean_c_std = (v1_pitch_mean_c - mean(v1_pitch_mean_c)) / sd(v1_pitch_mean_c),
+       v1_int_mean_c_std = (v1_int_mean_c - mean(v1_int_mean_c)) / sd(v1_int_mean_c))
+
+```
+
+```{r procambarus_mahogoni_models}
+
+mod1 <- lmer(v1_duration_c_std ~ typ_median +
+                     (1|participant) + (1|typ_median), data = msa_data)
+
+mod2 <- lmer(v1_pitch_mean_c_std ~ typ_median +
+               (1|participant) + (1|typ_median), data = msa_data)
+
+mod3 <- lmer(v1_int_mean_c_std ~ typ_median +
+               (1|participant) + (1|typ_median), data = msa_data)
+
+```
+
+```{r procambarus_mahogoni_refitting}
+
+# standardize
+msa_data <- msa_data %>% 
+  mutate(effect_con = (typ_median - mean(typ_median, na.rm = TRUE)) / sd(typ_median,  na.rm = TRUE))
+
+procambarus_mahogoni_1_dur_con <- brm(
+  v1_duration_c_std ~ 
+         effect_con + 
+         (1|participant) + 
+         (1|effect_con),
+  seed = 111,
+  data = msa_data, 
+  cores = 4,  
+  file = "./data/analyses/models/procambarus_mahogoni_1_dur_con"
+  )
+
+procambarus_mahogoni_2_f0_con <- brm(
+  v1_pitch_mean_c_std ~ 
+         effect_con + 
+         (1|participant) + 
+         (1|effect_con),
+  seed = 111,
+  data = msa_data, 
+  cores = 4,  
+  file = "./data/analyses/models/procambarus_mahogoni_2_f0_con"
+  )
+
+procambarus_mahogoni_3_int_con <- brm(
+  v1_int_mean_c_std ~ 
+         effect_con + 
+         (1|participant) + 
+         (1|effect_con),
+  seed = 111,
+  data = msa_data, 
+  cores = 4,  
+  file = "./data/analyses/models/procambarus_mahogoni_3_int_con"
+  )
 
@@
   unite(group, word1, word2, sep = "_") %>% 
-  select(group, mod_name:model) %>% 
+  dplyr::select(group, mod_name:model) %>% 
   mutate(sum = map(model, clean_up)) %>% 
   suppressWarnings() # because it warns every time that some coef have underscores and its annoying
+
 ```
@@
   ggplot() + 
-  facet_wrap(~ typicality_lab, ncol = 1, scales = "free_y") + 
-  aes(x = estimate, y = mod_name) + 
+  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
+  aes(x = estimate, y = mod_name, color = group) + 
   geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
-    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
+    #color = "#cc0033", 
+    alpha = 0.5, size = 3, lineend = "round") + 
   geom_vline(xintercept = 0, lty = "dashed", color = "grey") +
-  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) + 
+  geom_point(pch = 21, stroke = 3, size = 3.1) + 
   labs(y = "Model", x = "Estimate ± SE") + 
@@
   theme(strip.text.x = element_text(hjust = 0))
-```
+
+```

### 2022-06-28 scripts/r/03_analyses_coding.Rmd
♻️ - use 95% CI in forest plot

@@
   geom_vline(xintercept = 0) +
-  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
+  geom_segment(aes(x = estimate - se * 1.96, xend = estimate + se * 1.96, yend = mod_name), 
     color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 

### 2022-06-28 scripts/r/03_analyses_coding.Rmd
♻️ - update analyses coding rmd

--- 2022-06-16 scripts/r/03_analyses_coding.Rmd
@@
   unnest(sum) %>%
+  filter(mod_name != "polymetme_brevirostrum_1_dur_cat") %>%
   mutate(

### 2022-06-28 scripts/r/04_refit/refit_sc.Rmd
♻️ - use seed when refitting models

@@
 library(brms)
+my_seed = 8891
 ```
@@
   backend = "cmdstanr",
-  file = "./data/analyses/models/dermatolepis_aculeatus_1_pitch_cat"
+  file = "./data/analyses/models/dermatolepis_aculeatus_1_pitch_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "./data/analyses/models/dermatolepis_aculeatus_2_pitch_cat"
+  file = "./data/analyses/models/dermatolepis_aculeatus_2_pitch_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "./data/analyses/models/dermatolepis_aculeatus_3_pitch_cat"
+  file = "./data/analyses/models/dermatolepis_aculeatus_3_pitch_cat",
+  seed = my_seed
 )
@@
 trials_files <- list.files(
-    path = "./osf/data/production/trial-lists/",
+    path = "./data/osf/production/trial-lists/",
     pattern = ".csv", full.names = TRUE
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/eriphia_laterispinis_1_mult_cat"
+  file = "data/analyses/models/eriphia_laterispinis_1_mult_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/hoplostethus_macrosteus_1_dur_cat"
+  file = "data/analyses/models/hoplostethus_macrosteus_1_dur_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/hoplostethus_macrosteus_2_int_cat"
+  file = "data/analyses/models/hoplostethus_macrosteus_2_int_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat"
+  file = "data/analyses/models/neosilurus_omanensis_1_f0rat_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat"
+  file = "data/analyses/models/neosilurus_omanensis_2_f0ranrat_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat"
+  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat"
+  file = "data/analyses/models/neosilurus_omanensis_4_f0riserat_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat"
+  file = "data/analyses/models/neosilurus_omanensis_5_srrat_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat"
+  file = "data/analyses/models/paralichthys_undulatus_1_f0_cat",
+  seed = my_seed
 )
@@
   backend = "cmdstanr",
-  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat"
+  file = "data/analyses/models/polymetme_brevirostrum_1_dur_cat",
+  seed = my_seed
 )
@@
 # The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
-trial_dat <- list.files(path = "./osf/data/production/trial-lists/",
+trial_dat <- list.files(path = "./data/osf/production/trial-lists/",
                        pattern = "*.csv",
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/saron_pictus_1_dur_cat"
+  file = "data/analyses/models/saron_pictus_1_dur_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/trachurus_riukiuensis_1_durart_cat"
+  file = "data/analyses/models/trachurus_riukiuensis_1_durart_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/trachurus_riukiuensis_2_f0art_cat"
+  file = "data/analyses/models/trachurus_riukiuensis_2_f0art_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/trachurus_riukiuensis_3_duradj_cat"
+  file = "data/analyses/models/trachurus_riukiuensis_3_duradj_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/trachurus_riukiuensis_4_f0adj_cat"
+  file = "data/analyses/models/trachurus_riukiuensis_4_f0adj_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/trachurus_riukiuensis_5_f0noun_cat"
+  file = "data/analyses/models/trachurus_riukiuensis_5_f0noun_cat",
+  seed = my_seed
 )
@@
   threads = threading(2, grainsize = 100), 
-  file = "data/analyses/models/varanus_eulophotes_1_f0_cat"
+  file = "data/analyses/models/varanus_eulophotes_1_f0_cat",
+  seed = my_seed
 )

### 2022-07-08 scripts/r/03_analyses_coding.Rmd
♻️ - add descriptive plots to 03_analyses_coding

@@
     temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
-  )
+  ) %>%
+  drop_na(model_id)
 
@@
 coding %>%
+  ggplot(aes(framework)) +
+  geom_bar()
+```
+
+```{r}
+coding %>%
   ggplot(aes(model)) +
+  geom_bar()
+```
+
+```{r}
+coding %>%
+  ggplot(aes(family)) +
+  geom_bar()
+
+coding %>%
+  ggplot(aes(outcome, fill = family)) +
   geom_bar()
@@
 coding %>%
+  count(operationalisation) %>%
+  ggplot(
+    aes(reorder(operationalisation, desc(n)), n)
+    ) +
+  geom_bar(stat = "identity")
+```
+
+```{r}
+coding %>%
   drop_na(outcome, operationalisation) %>%
@@
 coding %>%
-  select(framework:operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
+  select(framework:outcome, operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
   distinct()

### 2022-07-12 scripts/r/04_refit/refit_sc.Rmd
♻️ - update sc refit

@@
 
+# nestor_idahoensis
+
+```{r}
+msa_data <- read_csv("./data/analyses/sc/nestor_idahoensis/msa_data_v2.csv", na = c("", "--undefined--")) %>%
+  mutate(
+    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
+    f0 = scale(log(f0)) %>% as.numeric(),
+    duration = scale(log(duration)) %>% as.numeric(),
+    f15 = scale(log(f15)) %>% as.numeric(),
+    f25 = scale(log(f25)) %>% as.numeric()
+  )
+```
+
+Not sure which priors to use after scaling.
+
+```{r}
+priors2 = c(
+  #weakly informative priors for intercepts and beta for each response variable
+  prior(normal(0,1.5), class = Intercept, resp = f0),
+  prior(normal(0,1.5), class = b, resp = f0),
+  prior(normal(0,1.5), class = Intercept, resp = duration),
+  prior(normal(0,1.5), class = b, resp = duration),
+  prior(normal(0,1.5), class = Intercept, resp = f15),
+  prior(normal(0,1), class = b, resp = f15),
+  prior(normal(0,1), class = Intercept, resp = f25),
+  prior(normal(0,1), class = b, resp = f25),
+  #weakly informative priors for random effects (slopes)
+  prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
+  prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
+  prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
+  prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
+  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
+  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
+  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
+  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
+  #weakly informative priors for the correlation between random intercept and slope
+  prior(lkj(2), class = cor, group = ID),
+  prior(lkj(2), class = cor, group = targetWord),
+  prior(cauchy(0, 1), class = sigma, resp=f0),
+  prior(cauchy(0, 1), class = sigma, resp=duration),
+  prior(cauchy(0, 1), class = sigma, resp=f15),
+  prior(cauchy(0, 1), class = sigma, resp=f25)
+)
+
+nestor_idahoensis_1_mult_cat <- brm(
+  mvbind(f0, duration, f15, f25) ~
+    effect_cat +
+    (1|ID) + (1|targetWord) +
+    (0 + typicality|ID) +
+    (0 + typicality|targetWord),
+  data = msa_data,
+  family = gaussian(),
+  prior = priors2, chains = 4, cores = 4,
+  threads = threading(2, grainsize = 100),
+  backend = "cmdstanr",
+  # control = list(max_treedepth = 15, adapt_delta = 0.9),
+  file = "./data/analyses/models/nestor_idahoensis_1_mult_cat.rds",
+  seed = my_seed
+)
+```
+
 # paralichthys_undulatus
@@
 ```{r}
+the_file <- "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds"
+
+if (file.exists(the_file)) {
+  petauroides_fistulator_1_f0_cat <- readRDS(the_file)
+} else {
   petauroides_fistulator_1_f0_cat <- bam(
@@
   )
-
-saveRDS(petauroides_fistulator_1_f0_cat, "./data/analyses/models/petauroides_fistulator_1_f0_cat.rds")
+  saveRDS(petauroides_fistulator_1_f0_cat, the_file)
+}
 ```
@@
   file = "data/analyses/models/saron_pictus_1_dur_cat",
+  seed = my_seed
+)
+```
+
+# sphyrna_ellioti
+
+```{r}
+pro_df <- read.csv("data/analyses/sc/sphyrna_ellioti/Data & Analysis Files/ManySpeech_ProsodyTrialsData.csv")
+
+#Some intervals are blank, so delete those:
+
+pro_df <- pro_df[!pro_df$AFI=="",]
+
+#Create a column that specifies the part of speech of the phrase of interest:
+
+pro_df <- pro_df %>%
+  mutate(POS = case_when(
+    n.interval == "10" ~ "Adj",
+    n.interval == "11" ~ "Noun"
+  ))
+
+#Convert continuous variables from character type to numeric:
+
+pro_df$Duration..ms.<- as.numeric(pro_df$Duration..ms.)
+pro_df$Intensity <- as.numeric(pro_df$Intensity)
+pro_df$fo1 <- as.numeric(pro_df$fo1)
+pro_df$fo2 <- as.numeric(pro_df$fo2)
+pro_df$fo3.Hz. <- as.numeric(pro_df$fo3.Hz.)
+
+#Centering F0 values by speaker:
+
+pro_df <- pro_df %>%
+  group_by(speaker) %>% 
+  mutate(mfo1 = mean(fo1),
+         mfo2 = mean(fo2),
+         mfo3 = mean(fo3.Hz.),
+         cfo1 = fo1-mfo1,
+         cfo2 = fo2-mfo2,
+         cfo3 = fo3.Hz.-mfo3)
+
+#For now, let's just look at the critical Adjectives and Nouns:
+
+phrase_df <- pro_df %>% drop_na(POS)
+
+#Filling out the typicality columns for the AF and ANF conditions from the typicality mean scores
+#based on the thresholds provided by the experimenters:
+
+msa_data <- phrase_df %>%
+  mutate(typicality = case_when(
+    typ_mean < 25 ~ "atypical",
+    typ_mean > 25 & typ_mean < 90 ~ "medium",
+    typ_mean > 90 ~ "typical"
+  ))
+
+msa_data$POS <- as.factor(phrase_df$POS)
+msa_data$typicality <- as.factor(phrase_df$typicality)
+msa_data$condition <- as.factor(phrase_df$condition)
+msa_data$AFI <- as.factor(phrase_df$AFI)
+
+msa_data <- msa_data %>%
+  mutate(
+    eff_cont = scale(typ_mean) %>% as.numeric(),
+    duration = log(Duration..ms.) %>% scale() %>% as.numeric(),
+    intensity = scale(Intensity) %>% as.numeric(),
+    cfo1 = scale(cfo1) %>% as.numeric(),
+    cfo2 = scale(cfo2) %>% as.numeric(),
+    cfo3 = scale(cfo3) %>% as.numeric()
+  )
+
+contrasts(msa_data$POS) <- "contr.sum"
+contrasts(msa_data$condition) <- "contr.sum"
+```
+
+```{r}
+sphyrna_ellioti_dur_cat <- brm(
+  duration ~
+    POS * condition * eff_cont +
+    (POS|speaker) + (POS|AFI),
+  data = msa_data,
+  file = "./data/analyses/models/sphyrna_ellioti_dur_cat.rds",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  seed = my_seed
+)
+
+sphyrna_ellioti_int_cat <- brm(
+  intensity ~
+    POS * condition * eff_cont +
+    (POS|speaker) + (POS|AFI),
+  data = msa_data,
+  file = "./data/analyses/models/sphyrna_ellioti_int_cat.rds",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  seed = my_seed
+)
+
+sphyrna_ellioti_cfo1_cat <- brm(
+  cfo1 ~
+    POS * condition * eff_cont +
+    (POS|speaker) + (POS|AFI),
+  data = msa_data,
+  file = "./data/analyses/models/sphyrna_ellioti_cfo1_cat.rds",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  seed = my_seed
+)
+
+sphyrna_ellioti_cfo2_cat <- brm(
+  cfo2 ~
+    POS * condition * eff_cont +
+    (POS|speaker) + (POS|AFI),
+  data = msa_data,
+  file = "./data/analyses/models/sphyrna_ellioti_cfo2_cat.rds",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
+  seed = my_seed
+)
+sphyrna_ellioti_cf03_cat <- brm(
+  cfo3 ~
+    POS * condition * eff_cont +
+    (POS|speaker) + (POS|AFI),
+  data = msa_data,
+  file = "./data/analyses/models/sphyrna_ellioti_cf03_cat.rds",
+  cores = 4,
+  threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr",
   seed = my_seed

### 2022-07-14 scripts/r/04_refit/refit_jvc.Rmd
Timo models added

@@
   filter(term %in% c("effect_cattypical", "effect_con")) %>% 
-  select(term, estimate, se = std.error)
+  dplyr::select(term, estimate, se = std.error)
 
@@
   "ctenosaura_limax",         TRUE,           FALSE,
-  "gnathosaurus_canadensis",  FALSE,          FALSE,
-  "gymnothorax_spinulosus",   FALSE,          FALSE,
+  "gnathosaurus_canadensis",  TRUE,           TRUE,
+  "gymnothorax_spinulosus",   TRUE,           TRUE,
   "haematopus_fossor",        TRUE,           TRUE,
   "lasionycteris_altavela",   TRUE,           TRUE,
-  "linckia_nattereri",        FALSE,          FALSE,
-  "lycodes_bradfieldi",       FALSE,          FALSE,
-  "naso_cassivellaunos",      FALSE,          FALSE,
-  "trapezia_cantonensis",     FALSE,          FALSE,
-  "trigonias_lachneri",       FALSE,          FALSE,
+  "linckia_nattereri",        TRUE,           FALSE,
+  "lycodes_bradfieldi",       TRUE,           FALSE,
+  "naso_cassivellaunos",      TRUE,           TRUE,
+  "trapezia_cantonensis",     TRUE,           TRUE,
+  "trigonias_lachneri",       TRUE,           TRUE,
+  "psittacula_scabriculus",   TRUE,           TRUE, 
+  "clione_dorsalis",          TRUE,           TRUE
   )
@@
 ```{r}
+#| label: gnathosaurus_canadensis
+
+# Load teams data
+gnathosaurus_canadensis_typ <- read_xlsx(here("data", "analyses", "jvc", 
+  "gnathosaurus_canadensis", "typ.xlsx"))
+
+# Refit original model
+f_test <- friedman.test(
+  y = gnathosaurus_canadensis_typ$median_st_diff, 
+  groups = gnathosaurus_canadensis_typ$typicality, 
+  blocks = gnathosaurus_canadensis_typ$speaker
+  )
+
+#
+# JVC refits
+#
+
+MSA_gnathosaurus_canadensis_df <- gnathosaurus_canadensis_typ %>% 
+  mutate(median_diff_z = (median_st_diff - mean(median_st_diff)) / sd(median_st_diff),
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment))
+
+gnathosaurus_canadensis_1_f0diff_cat <- brm(
+  median_diff_z ~ effect_cat, 
+  data = MSA_gnathosaurus_canadensis_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "gnathosaurus_canadensis_1_f0diff_cat")
+  )
 
@@
 print_status("gymnothorax_spinulosus")
+```
+
+```{r}
+#| label: gymnothorax_spinulosus
+
+gymnothorax_spinulosus_data <- read.csv2(here("data", "analyses", "jvc", "gymnothorax_spinulosus", "Many_speech_final_3.csv"), dec = ".") %>% 
+  mutate(measure = vowel_intensity_diff, 
+    speaker = as.factor(speaker), 
+    trial = as.factor(trial), 
+    condition = as.factor(condition), 
+    token = as.factor(token), 
+    target_colour = as.factor(target_colour))
+
+# Exclusion process
+sd_intensity <- sd(gymnothorax_spinulosus_data$vowel_intensity_diff)
+min_int_diff <- median(gymnothorax_spinulosus_data$vowel_intensity_diff)-1.5*sd_intensity
+max_int_diff <- median(gymnothorax_spinulosus_data$vowel_intensity_diff)+1.5*sd_intensity
+gymnothorax_spinulosus_data$exclude <- 0
+gymnothorax_spinulosus_data[which(gymnothorax_spinulosus_data$vowel_intensity_diff<min_int_diff),]$exclude <- 1
+gymnothorax_spinulosus_data$exclude <- factor(gymnothorax_spinulosus_data$exclude)
+gymnothorax_spinulosus_int <- gymnothorax_spinulosus_data[which(gymnothorax_spinulosus_data$exclude==0),]
+gymnothorax_spinulosus_int$typ_mean <- gymnothorax_spinulosus_int$typ_mean/100
+
+#
+# Fit original model
+#
+fit0 <- lmer(measure ~ condition * typ_mean + 
+    (1|target_colour) + 
+    (1|speaker),
+  data = gymnothorax_spinulosus_int, 
+  REML = FALSE , 
+  na.action = na.exclude
+  )
+
+# Set up post hoc comparisons
+contmat <- rbind(c(0,0,0,1,0,0), c(0,0,0,1,1,0), c(0,0,0,1,0,1))
+rownames(contmat) <- c('pente AF','pente ANF','pente NF')
+comp_mult <- summary(multcomp::glht(fit0, linfct = contmat))
+comp_mult
+
+#
+# JVC refits
+#
+MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
+  mutate(measure_z = (measure - mean(measure)) / sd(measure),
+    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
+  filter(condition == "AF")
+
+gymnothorax_spinulosus_1_intdiff_con <- brm(
+  measure_z ~ effect_con + 
+    (1|target_colour) + 
+    (1|speaker), 
+  data = MSA_gymnothorax_spinulosus_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
+  )
+
 ```
@@
 
+```{r}
+#| label: linckia_nattereri
+
+linckia_nattereri_dat <- read.csv(here("data", "analyses", "jvc", 
+"linckia_nattereri", "ResultsNF2.csv")) %>% 
+  mutate(typicality = as.factor(typicality))
+
+# Fit original bayesian models with default priors
+
+```
+
+NOTE: Fit bayesian logistic regression model (typicality = DV) with 10 continuous predictors. ASK stef and timo for suggestions.
+
 ## lycodes_bradfieldi
@@
 
+```{r}
+#| label: lycodes_bradfieldi
+
+```
+
+Processed data not available.
+
 ## naso_cassivellaunos
@@
 
+```{r}
+#| label: naso_cassivellaunos
+
+msa <- read_csv(here("data", "analyses", "jvc", "naso_cassivellaunos", 
+  "ProPer_MSA", "data_tables", "ProPer_MSA_scores.csv"))
+msa <- msa[msa$syllable %in% c("A_P*", "A_F", "N_P*", "N_F"),]
+msa$syllable <- factor(msa$syllable, levels = c("A_P*", "A_F", "N_P*", "N_F"), labels = c("A_Penult", "A_Final", "N_Penult", "N_Final"), ordered = FALSE)
+# Set "typical" the 1st / reference level
+msa$typicality <- factor(msa$typicality, levels = c("typical", "medium", "atypical"))
+# Set "atypical" the 1st / reference level
+#msa$typicality <- factor(msa$typicality, levels = c("atypical", "medium", "typical"))
+
+# Reorder target_name wrt typicality
+msa$target_name <- factor(msa$target_name)
+msa$target_name <- fct_reorder(msa$target_name, as.numeric(msa$typicality))
+
+load(here("data", "analyses", "jvc", "naso_cassivellaunos", 
+  "Bayesian analysis", "Mass_Models.rda"))
+
+#
+# JVC refit
+#
+
+MSA_naso_cassivellaunos_data <- msa %>% 
+  mutate(mass_rel_log = log(mass_rel), 
+    mass_rel_z = (mass_rel_log - mean(mass_rel_log)) / sd(mass_rel_log), 
+    DeltaF0_rel_z = (DeltaF0_rel - mean(DeltaF0_rel)) / sd(DeltaF0_rel), 
+    sync_rel_z = (sync_rel - mean(sync_rel)) / sd(sync_rel), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    syllable = C(syllable, sum))
+
+naso_cassivellaunos_1_mass_cat <- brm(
+  mass_rel_z ~ effect_cat * syllable +  
+    (1 + effect_cat * syllable | speaker), 
+  data = MSA_naso_cassivellaunos_data, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "naso_cassivellaunos_1_mass_cat")
+  )
+
+naso_cassivellaunos_2_f0delta_cat <- brm(
+  DeltaF0_rel_z ~ effect_cat * syllable +  
+    (1 + effect_cat * syllable | speaker), 
+  data = MSA_naso_cassivellaunos_data, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "naso_cassivellaunos_2_f0delta_cat")
+  )
+
+naso_cassivellaunos_3_syncrel_cat <- brm(
+  sync_rel_z ~ effect_cat * syllable +  
+    (1 + effect_cat * syllable | speaker), 
+  data = MSA_naso_cassivellaunos_data, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "naso_cassivellaunos_3_syncrel_cat")
+  )
+
+```
+
 ## trapezia_cantonensis
@@
 
+```{r}
+#| label: trapezia_cantonensis
+
+if(F) {
+msa_raw <- tibble(
+  path = Sys.glob(
+    glue::glue("{here('./data/analyses/jvc/trapezia_cantonensis/')}/audio_chunks/*/_FastTrack/csvs/*.csv")), 
+  file = map(path, read_csv, progress = FALSE, show_col_types = FALSE)) %>%
+    unnest(file)
+
+typicality <- tribble(
+    ~"adj", ~"noun", ~"typicality",
+    "gelben",  "Kirsche", "atypical",
+    "gruenen", "Moehre",  "atypical",
+    "roten",   "Gurke",   "atypical",
+    "orangen", "Trauben", "atypical",
+    "braunen", "Paprika", "atypical",
+    "gelben",  "Erbsen",     "medium",
+    "gruenen", "Tomate",     "medium", 
+    "roten",   "Aprikose",   "medium",
+    "orangen", "Kartoffeln", "medium",
+    "braunen", "Banane",     "medium",
+    "gelben",  "Zitrone",   "typical",
+    "gruenen", "Bohnen",    "typical",
+    "roten",   "Erdbeere",  "typical",
+    "orangen", "Mandarine", "typical",
+    "braunen", "Walnuss",   "typical",
+    "gelben", "Sonnenbrille",   "non-food",
+    "gelben", "Socken",         "non-food",
+    "gelben", "Waescheklammer", "non-food",
+    "gruenen", "Sonnenbrille",   "non-food",
+    "gruenen", "Socken",         "non-food",
+    "gruenen", "Bueroklammer",   "non-food",
+    "roten", "Socken",         "non-food",
+    "roten", "Bueroklammer",   "non-food",
+    "roten", "Waescheklammer", "non-food",
+    "orangen", "Socken",         "non-food",
+    "orangen", "Bueroklammer",   "non-food",
+    "orangen", "Waescheklammer", "non-food",
+    "braunen", "Sonnenbrille",   "non-food",
+    "braunen", "Bueroklammer",   "non-food",
+    "braunen", "Waescheklammer", "non-food"
+)
+
+beast_path <- "/Users/casillas/academia/research/in_progress/many_speech_analyses/many_analyses/./data/analyses/jvc/trapezia_cantonensis//audio_chunks/"
+
+msa_processed <- msa_raw %>% 
+  mutate(path = str_remove_all(path, beast_path), 
+    path = str_remove_all(path, "/.*/_FastTrack/csvs/"),
+    path = str_remove_all(path, "_\\d+\\.csv")) %>% 
+    separate(path, into = c("art", "adj", "noun", "speaker_trial"), 
+      sep = "_", extra = "merge") %>%
+    mutate(noun = str_remove_all(noun, "/")) %>% 
+    separate(speaker_trial, into = c("speaker", "trial"), 
+      sep = "_(?=\\d+\\Z)") %>%
+    # Add the typicality ratings
+    left_join(typicality, by = c("adj", "noun")) %>%
+    # Get normalized time, and duration
+    group_by(speaker, trial) %>%
+    mutate(percent = time / max(time),
+           dur = max(time) - min(time),
+           .after = time) %>%
+    ungroup()
+
+msa_for_dur <- msa_processed %>%
+  dplyr::select(art, adj, noun, speaker, trial, dur, typicality) %>%
+  distinct() %>%
+  mutate(typicality = factor(typicality, 
+    levels = c("typical", "medium", "atypical", "non-food")))
+
+write_csv(msa_for_dur, 
+  file = here("data", "analyses", "jvc", "trapezia_cantonensis", "jvc_tidy.csv"))
+
+dur_lmer <- lmer(
+  dur ~ typicality + 
+    (1|adj) + (1|speaker), 
+  data = msa_for_dur
+  )
+
+}
+
+#
+# JVC refit
+#
+
+MSA_trapezia_cantonensis_data <- read_csv(
+  here("data", "analyses", "jvc", "trapezia_cantonensis", "jvc_tidy.csv")
+  ) %>% 
+  mutate_if(is.character, as.factor) %>% 
+  mutate(dur_z = (dur - mean(dur)) / sd(dur), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"))
+
+trapezia_cantonensis_4_dur_cat <- brm(
+  dur_z ~ effect_cat +  
+    (1|adj) + (1|speaker), 
+  data = MSA_trapezia_cantonensis_data, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "trapezia_cantonensis_4_dur_cat")
+  )
+
+```
+
 ## trigonias_lachneri
@@
 print_status("trigonias_lachneri")
+```
+
+```{r}
+#| label: trigonias_lachneri
+
+msa <- read.csv(here("data", "analyses", "jvc", "trigonias_lachneri", 
+  "CSV", "whole_no_errors.csv"))
+
+msa_linear <- subset(msa, select = c(participant, spi, speaker, trial, condition, typicality, target_colour,typ_mean))
+#correcting variable types in R
+msa_linear$participant <- as.factor(msa_linear$participant)
+msa_linear$speaker <- as.factor(msa_linear$speaker)
+msa_linear$trial <- as.integer(msa_linear$trial)
+msa_linear$spi <- as.numeric(msa_linear$spi)
+msa_linear$condition <- as.factor(msa_linear$condition)
+msa_linear$typicality <- as.factor(msa_linear$typicality)
+msa_linear$target_colour <- as.factor(msa_linear$target_colour)
+
+spi_base <- msa_linear %>%
+  filter(condition %in% "NF")
+spi_base$spi <- log(spi_base$spi)
+
+spi.var.md <- lmer(spi ~ typ_mean + 
+    (1 + typ_mean|target_colour) + 
+    (1 + typ_mean|speaker), 
+  data = spi_base, 
+  control=lmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)), 
+  REML = TRUE)
+
+#
+# JVC refit
+#
+
+MSA_trigonias_lachneri_spi_data <- spi_base %>% 
+  mutate(spi_z = (spi - mean(spi, na.rm = T)) / sd(spi, na.rm = T)) %>% 
+  mutate(effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean))
+
+trigonias_lachneri_1_spi_con <- brm(
+  spi_z ~ effect_con, 
+  data = MSA_trigonias_lachneri_spi_data, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", 
+  file = here("data", "analyses", "models", "trigonias_lachneri_1_spi_con")
+  )
+
+```
+
+## psittacula_scabriculus
+
+```{r}
+#| label: print_psittacula_scabriculus
+#| echo: false
+#| results: 'asis'
+print_status("psittacula_scabriculus")
+```
+
+```{r}
+#| label: psittacula_scabriculus
+
+MSA_psittacula_scabriculus_raw <- read_xlsx(
+  path = here("data", "analyses", "jvc", "psittacula_scabriculus", 
+    "Data_and_analysis", "psittacula_scabriculus_full_dataset_checked.xlsx"))
+
+MSA <- MSA_psittacula_scabriculus_raw %>%
+  arrange(target_name) %>% #orders the rows of the data by the target_name column
+  group_by(target_name) %>% #group by the target name
+  transform(items = as.numeric(factor(target_name)))%>% #transform target name into a item
+  select(items, target_name, everything()
+         ) #select all variables from items and target_name
+
+MSAcomplete <- MSA %>% 
+  filter (condition == 'NF') %>% 
+  filter (avgdur > 0)
+
+#count notpronounced for each vowel (1,2,3,4)
+M_not <- MSAcomplete %>%
+  filter(dur1 == "notpronounced"|dur2 == "notpronounced"|dur3 == "notpronounced"|dur4 == "notpronounced")
+
+dur1_not <- M_not%>%
+  filter(dur1 == "notpronounced")
+dur2_not <- M_not%>%
+  filter(dur2 == "notpronounced")
+dur3_not <- M_not%>%
+  filter(dur3 == "notpronounced")
+dur4_not <- M_not%>%
+  filter(dur4 == "notpronounced")
+
+#Convert the average duration from character to number. 
+MSAcomplete$avgdur <- as.numeric(MSAcomplete$avgdur)
+
+regularizing_priors <- prior('normal(0, 1)', class = 'b')
+options(mc.cores=parallel::detectCores())
+# Original model
+set.seed(42)
+
+if(F) {
+MSA_mdl <- brm(
+  avgdur ~ 1 + typicality + 
+    (1 + typicality |participant) +  
+    (1 + typicality |items), 
+  data = MSAcomplete, 
+  prior = regularizing_priors,  
+  seed = 42, init = 0, cores = 4, 
+  chains = 4, warmup = 2000, iter = 4000)
+}
+
+#
+# JVC refit
+#
+
+msa_psittacula_scabriculus_df <- MSAcomplete %>% 
+  mutate(avgdur_z = (avgdur - mean(avgdur)) / sd(avgdur), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"))
+
+psittacula_scabriculus_1_dur_cat <- brm(
+  avgdur_z ~ effect_cat +  
+    (1 + effect_cat | participant) +  
+    (1 + effect_cat | items), 
+  data = msa_psittacula_scabriculus_df, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "psittacula_scabriculus_1_dur_cat")
+  )
+
+```
+
+## clione_dorsalis
+
+```{r}
+#| label: print_clione_dorsalis
+#| echo: false
+#| results: 'asis'
+print_status("clione_dorsalis")
+```
+
+```{r}
+#| label: clione_dorsalis
+
+#read and clean the data
+data_formants_duration <- read.csv(
+  here("data", "analyses", "jvc", "clione_dorsalis", 
+  "MSA_formantlog.csv"))
+data_vs <- read.csv(
+    here("data", "analyses", "jvc", "clione_dorsalis", 
+    "MSA_formantlog_vowel space area.csv"))
+
+data_no_NA <- subset(data_formants_duration, typicality != "NA")
+data_formant_midpoint <- subset(data_no_NA, timept == "3")
+data_vs <- plyr::rename(data_vs, c("atypical"="vowel_space_area"))
+data_2 <- subset(data_vs, timepoint == "2")
+data_4 <- subset(data_vs, timepoint == "4")
+formants_tp_2 <- subset(data_no_NA, timept == "2")
+formants_tp_4 <- subset(data_no_NA, timept == "4")
+
+# REfit original models
+duration.mod <- lmer(word.duration ~ typicality + vowel + gender + (1|filename), data=data_formant_midpoint)
+
+vsa.mod.2 <- lmer(vowel_space_area ~ typicality + (1|subject),data=data_2)
+vsa.mod.4 <- lmer(vowel_space_area ~ typicality + (1|subject),data=data_4)
+
+###F1 and F2 models
+mod.4 <- lmer(f1 ~ typicality*vowel + gender + (1|filename), data=formants_tp_2)
+mod.5 <- lmer(f2 ~ typicality*vowel + gender + (1|filename), data=formants_tp_2)
+mod.6 <- lmer(f1 ~ typicality*vowel + gender + (1|filename), data=formants_tp_4)
+mod.7 <- lmer(f2 ~ typicality*vowel + gender + (1|filename), data=formants_tp_4)
+
+#
+# JVC refit
+#
+msa_clione_dorsalis_mp <- data_formant_midpoint %>% 
+  mutate(
+    word_duration_z = (word.duration - mean(word.duration)) / sd(word.duration), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    vowel = as.factor(vowel), 
+    vowel = C(vowel, sum), 
+    gender = as.factor(gender), 
+    gender = C(gender, sum)
+    )
+
+clione_dorsalis_1_mp_cat <- brm(
+  word_duration_z ~ effect_cat + vowel + gender + 
+    (1|filename), 
+  data = msa_clione_dorsalis_mp, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_1_mp_cat")
+  )
+
+msa_clione_dorsalis_vs <- data_2 %>% 
+  mutate(
+    vowel_space_area_z = (vowel_space_area - mean(vowel_space_area)) / sd(vowel_space_area), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+  )
+
+clione_dorsalis_2_vs_cat <- brm(
+  vowel_space_area_z ~ effect_cat + 
+    (1 | subject), 
+  data = msa_clione_dorsalis_vs, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_2_vs_cat")
+  )
+
+msa_clione_dorsalis_vs4 <- data_4 %>% 
+  mutate(
+    vowel_space_area_z = (vowel_space_area - mean(vowel_space_area)) / sd(vowel_space_area), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+  )
+
+clione_dorsalis_3_vs4_cat <- brm(
+  vowel_space_area_z ~ effect_cat + 
+    (1 | subject), 
+  data = msa_clione_dorsalis_vs4, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_3_vs4_cat")
+  )
+
+msa_clione_dorsalis_f1f22 <- formants_tp_2 %>% 
+  mutate(
+    f1_z = (f1 - mean(f1)) / sd(f1), 
+    f2_z = (f2 - mean(f2)) / sd(f2), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    vowel = as.factor(vowel), 
+    vowel = C(vowel, sum), 
+    gender = as.factor(gender), 
+    gender = C(gender, sum)
+  )
+
+clione_dorsalis_4_f12_cat <- brm(
+  f1_z ~ effect_cat + vowel + gender + 
+    (1|filename), 
+  data = msa_clione_dorsalis_f1f22, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_4_f12_cat")
+  )
+
+clione_dorsalis_5_f22_cat <- brm(
+  f2_z ~ effect_cat + vowel + gender + 
+    (1|filename), 
+  data = msa_clione_dorsalis_f1f22, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_5_f22_cat")
+  )
+
+msa_clione_dorsalis_f1f24 <- formants_tp_4 %>% 
+  mutate(
+    f1_z = (f1 - mean(f1)) / sd(f1), 
+    f2_z = (f2 - mean(f2)) / sd(f2), 
+    effect_cat = as.factor(typicality), 
+    effect_cat = C(effect_cat, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical"), 
+    vowel = as.factor(vowel), 
+    vowel = C(vowel, sum), 
+    gender = as.factor(gender), 
+    gender = C(gender, sum)
+  )
+
+clione_dorsalis_6_f14_cat <- brm(
+  f1_z ~ effect_cat + vowel + gender + 
+    (1|filename), 
+  data = msa_clione_dorsalis_f1f24, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_6_f14_cat")
+  )
+
+clione_dorsalis_7_f24_cat <- brm(
+  f2_z ~ effect_cat + vowel + gender + 
+    (1|filename), 
+  data = msa_clione_dorsalis_f1f24, 
+  cores = 4, threads = threading(2, grainsize = 100), 
+  backend = "cmdstanr", seed = 06022016, 
+  file = here("data", "analyses", "models", "clione_dorsalis_7_f24_cat")
+  )
+
 ```
@@
   unite(group, word1, word2, sep = "_") %>% 
-  select(group, mod_name:model) %>% 
+  dplyr::select(group, mod_name:model) %>% 
   mutate(sum = map(model, clean_up)) %>% 
@@
   unnest(sum) %>% 
-  select(-model) %>% 
+  dplyr::select(-model) %>% 
   knitr::kable(format = "pandoc")
@@
 #| label: forest-plot
+#| fig.height: 8
 

### 2022-07-14 scripts/r/03_analyses_coding.Rmd

@@
 assigned <- coding %>%
-  select(team, animal, assigned_to) %>%
+  dplyr::select(team, animal, assigned_to) %>%
   distinct()
@@
   geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
-  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") +
+  facet_wrap(typicality_lab ~ ., ncol = 2, scales = "free") +
   labs(y = "Model", x = "Estimate ± SE") + 

### 2022-07-14 scripts/r/04_refit/refit_tr.Rmd

@@
 # libs
-library("here")
-library("fs")
-library("dplyr")
-library("tidyr")
-library("readr")
-library("forcats")
-library("ggplot2")
-library("stringr")
-library("strex")
-library("purrr")
-library("lme4")
-library("brms")
-library("broom")
-library("broom.mixed")
-library("readxl")
-library("optimx")
-library("MuMIn")
-library("fda")
-library("abind")
-library("data.table")
-library("magrittr")
-library("tidyverse")
+library(tidyverse)
+library(brms)
+library(readxl)
 
@@
 
-# psittacula_scabriculus
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# eosipterus_pytyopsittacus
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# pseudopleuronectes_assasi
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
 # pervagor_meeki
@@
 
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# ceratophrys_elephantotus
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# clione_dorsalis
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# aracana_bitatawa
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
 # dunkleosteus_inscriptus
@@
   )
-
-```
-
-# nestor_idahoensis
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
-
-```
-
-# sphyrna_ellioti
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
 
@@
   )
-
-```
-
-# aratinga_lugubris
-
-```{r authors setup}
-
-```
-
-```{r their_models}
-
-```
-
-```{r refitting}
 

### 2022-07-14 scripts/r/03_analyses_coding.Rmd
✨ - save all estimates in msa_models

@@
   select(-model)
+
+saveRDS(msa_models, "./data/analyses/msa_models.rds")
 ```

### 2022-07-14 scripts/r/04_refit/refit_sc.Rmd
🐛 - fix missing model number in sphyrna refitted models

@@
 ```{r}
-sphyrna_ellioti_dur_cat <- brm(
+sphyrna_ellioti_1_dur_cat <- brm(
   duration ~
@@
   data = msa_data,
-  file = "./data/analyses/models/sphyrna_ellioti_dur_cat.rds",
+  file = "./data/analyses/models/sphyrna_ellioti_1_dur_cat.rds",
   cores = 4,
@@
 
-sphyrna_ellioti_int_cat <- brm(
+sphyrna_ellioti_2_int_cat <- brm(
   intensity ~
@@
   data = msa_data,
-  file = "./data/analyses/models/sphyrna_ellioti_int_cat.rds",
+  file = "./data/analyses/models/sphyrna_ellioti_2_int_cat.rds",
   cores = 4,
@@
 
-sphyrna_ellioti_cfo1_cat <- brm(
+sphyrna_ellioti_3_cfo1_cat <- brm(
   cfo1 ~
@@
   data = msa_data,
-  file = "./data/analyses/models/sphyrna_ellioti_cfo1_cat.rds",
+  file = "./data/analyses/models/sphyrna_ellioti_3_cfo1_cat.rds",
   cores = 4,
@@
 
-sphyrna_ellioti_cfo2_cat <- brm(
+sphyrna_ellioti_4_cfo2_cat <- brm(
   cfo2 ~
@@
   data = msa_data,
-  file = "./data/analyses/models/sphyrna_ellioti_cfo2_cat.rds",
+  file = "./data/analyses/models/sphyrna_ellioti_4_cfo2_cat.rds",
   cores = 4,
@@
 )
-sphyrna_ellioti_cf03_cat <- brm(
+sphyrna_ellioti_5_cf03_cat <- brm(
   cfo3 ~
@@
   data = msa_data,
-  file = "./data/analyses/models/sphyrna_ellioti_cf03_cat.rds",
+  file = "./data/analyses/models/sphyrna_ellioti_5_cf03_cat.rds",
   cores = 4,

### 2022-07-14 scripts/r/03_analyses_coding.Rmd
✨ - update msa_models and add plots

@@
   ) %>%
-  drop_na(model_id)
-
+  drop_na(model_n)
 ```
@@
     theme(
-      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
-      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_blank(),
       panel.grid.major = element_line(colour = 'grey90', size = 0.15),
-      panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15),
+      strip.text.x = element_text(hjust = 0),
+      axis.text.x = element_blank()
+    )
   )
@@
 # Functional sequence to get relevant info from Rds files
-clean_up <- . %>% 
-  tidy(effects = "fixed", parametric = TRUE) %>% 
-  suppressWarnings() %>% 
-  filter(term %in% c("effect_cattypical", "effect_con")) %>% 
-  select(term, estimate, se = std.error)
+clean_up <- function(model) {
+  effs <- suppressWarnings(tidy(model, effects = "fixed", parametric = TRUE)) %>% 
+  filter(term %in% c("effect_catmedium", "effect_cattypical", "effect_con"))
+  if (!("response" %in% colnames(effs))) {
+    effs$response <- "none"
+  }
+  effs <- effs %>%
+  select(outcome_mult = response, term, estimate, se = std.error)
+
+  return(effs)
+}
 ```
@@
   as_tibble() %>% 
-  transmute(path = value,
+  transmute(
+    path = value,
     mod_name = str_remove(path, here("data/analyses/models/")), 
     mod_name = str_remove(mod_name, ".rds"), 
-    model = map(path, ~ readRDS(file = .))) %>% 
-  separate(mod_name, 
-    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
-    sep = "_", remove = F) %>% 
-  unite(group, word1, word2, sep = "_") %>% 
-  select(group, mod_name:model) %>% 
-  mutate(sum = map(model, clean_up)) %>% 
-  # because it warns every time that some coef have underscores and its annoying
-  suppressWarnings() %>%
-  select(-model)
+    model = map(path, ~ readRDS(file = .))
+  ) %>% 
+  separate(
+    mod_name, 
+    into = c("word1", "word2", "model_n", "model_outcome", "typicality"), 
+    sep = "_", remove = F,
+    convert = TRUE
+  ) %>% 
+  unite(animal, word1, word2, sep = "_") %>% 
+  select(animal, model_n:model) %>% 
+  mutate(summaries = map(model, clean_up)) %>%
+  select(-model) %>%
+  unnest(summaries) %>%
+  mutate(
+    typ_level = case_when(
+      term == "effect_cattypical" ~ "typical",
+      term == "effect_catmedium" ~ "medium"
+    ),
+    typicality = ifelse(typicality == "con", "continuous", "categorical"),
+    model_id = paste(animal, model_n, sep = "_")
+  ) %>%
+  select(animal, model_n, model_id, model_outcome, outcome_mult, typicality, typ_level, estimate, se) %>%
+  mutate(
+    outcome_mult = case_when(
+      outcome_mult == "none" ~ NA_character_,
+      outcome_mult == "meanf0" ~ "f0",
+      outcome_mult == "meanint" ~ "intensity",
+      outcome_mult == "duration" ~ "duration",
+      outcome_mult == "f0" ~ "f0",
+      outcome_mult == "f15" ~ "formants_1",
+      outcome_mult == "f25" ~ "formants_2"
+    )
+  ) %>%
+  left_join(y = coding) %>%
+  mutate(
+    model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
+    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_"))
+  )
 
@@
 msa_models %>% 
-  unnest(sum) %>%
   knitr::kable(format = "pandoc")
@@
 
-Simple forest plot of the estimates +/- SE
+Simple forest plot of the estimates and 95% CrIs.
 
@@
 msa_models %>%
-  unnest(sum) %>%
-  filter(mod_name != "polymetme_brevirostrum_1_dur_cat") %>%
-  mutate(
-    typicality_lab = if_else(
-      typicality == "cat", "Typicality = categorical", "Typicality = continuous"
-    ), 
-    mod_name = fct_reorder(mod_name, estimate)
-  ) %>% 
-  ggplot(aes(x = estimate, y = mod_name)) + 
-  geom_vline(xintercept = 0) +
-  geom_segment(aes(x = estimate - se * 1.96, xend = estimate + se * 1.96, yend = mod_name), 
-    color = "#cc0033", alpha = 0.5, size = 3, lineend = "round") + 
-  geom_point(color = "#cc0033", pch = 21, stroke = 3, size = 3.1) +
-  facet_wrap(typicality_lab ~ ., ncol = 2, scales = "free") +
-  labs(y = "Model", x = "Estimate ± SE") + 
-  clean_theme() + 
-  theme(strip.text.x = element_text(hjust = 0))
+  filter(animal != "polymetme_brevirostrum") %>%
+  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
+  geom_hline(yintercept = 0) +
+  geom_segment(
+    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
+    alpha = 0.5, size = 1, lineend = "round"
+  ) + 
+  geom_point(pch = 21, stroke = 2, size = 1) +
+  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
+  scale_colour_brewer(palette = "Set1", type = "qual") +
+  labs(y = "Estimate (z-scores)") + 
+  clean_theme() 
+```
+
+```{r forest-plot-2}
+msa_models %>%
+  filter(animal != "polymetme_brevirostrum") %>%
+  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = estimate)) + 
+  geom_hline(yintercept = 0) +
+  geom_segment(
+    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
+    alpha = 0.5, size = 1, lineend = "round"
+  ) + 
+  geom_point(pch = 21, stroke = 2, size = 1) +
+  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
+  scale_colour_gradientn(colours = c("#d95f02", "#dfc27d", "#80cdc1", "#018571"), limits = c(-1, 1)) +
+  labs(y = "Estimate (z-scores)") + 
+  clean_theme() 
 ```

### 2022-07-15 scripts/r/03_analyses_coding.Rmd
♻️ - restructure analysis_coding.Rmd

@@
 library("broom.mixed")
+
+# Plotting theme
+clean_theme <- function(...) {
+  list(
+    theme_minimal(), 
+    theme(
+      axis.title.x = element_blank(),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15),
+      strip.text.x = element_text(hjust = 0),
+      axis.text.x = element_blank()
+    )
+  )
+}
 ```
@@
 
-# Download OSF components
+# Teams' analyses
+
+## Download OSF components
 
@@
 
-# Refit models
+## Refit models
 
@@
 
-# Upload refitted models to OSF
+## Upload refitted models to OSF
 
@@
 
-# Download all refitted models
+## Download all refitted models
 
-We first download all the refitted models .rds files from the OSF.
+We download all the refitted models `.rds` files from the OSF.
 
@@
 
-A few helper functions.
+The following functions extracts the estimates.
 
-```{r helpers}
-# Plotting theme
-clean_theme <- function(...) {
-  list(
-    theme_minimal(), 
-    theme(
-      axis.title.x = element_blank(),
-      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
-      panel.grid.minor = element_line(colour = 'grey90', size = 0.15),
-      strip.text.x = element_text(hjust = 0),
-      axis.text.x = element_blank()
-    )
-  )
-}
-
-# Functional sequence to get relevant info from Rds files
+```{r clean-up}
 clean_up <- function(model) {
@@
 
-Load all the models.
+Now we load all the models and apply `clean_up()` to get the estimates.
 
@@
 msa_models %>%
+  select(model_id, estimate, se) %>%
   knitr::kable(format = "pandoc")
@@
 
+# Plotting
+
 Simple forest plot of the estimates and 95% CrIs.
 
-```{r forest-plot}
+```{r fp-outcome}
 msa_models %>%
@@
   facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
+  scale_colour_brewer(palette = "Set1", type = "qual") +
+  labs(y = "Estimate (z-scores)") + 
+  clean_theme() 
+```
+
+```{r fp-outcome-facet}
+msa_models %>%
+  filter(animal != "polymetme_brevirostrum") %>%
+  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
+  geom_hline(yintercept = 0) +
+  geom_segment(
+    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
+    alpha = 0.5, size = 1, lineend = "round"
+  ) + 
+  geom_point(pch = 21, stroke = 2, size = 1) +
+  facet_grid(outcome ~ typicality, scales = "free") +
   scale_colour_brewer(palette = "Set1", type = "qual") +
@@
 ```
-
-# Analyses coding plots
 

### 2022-07-15 scripts/r/03_analyses_coding.Rmd
♻️ - fix outcome columns in msa_models

@@
 
-```{r}
+```{r frameworks}
 coding %>%
@@
 
-```{r}
+```{r models}
 coding %>%
@@
 
-```{r}
+```{r family}
 coding %>%
@@
 
-```{r}
+```{r temporal-w}
 coding %>%
@@
 
-```{r}
+```{r temporal-w-2}
 coding %>%
@@
 
-```{r}
+```{r operation}
 coding %>%
+  drop_na(operationalisation) %>%
   count(operationalisation) %>%
@@
 
-```{r}
+```{r operation-2}
 coding %>%
@@
 
-```{r}
+# Unique model combinations
+
+```{r combos}
 coding %>%
@@
 
-```{r}
+```{r n-models}
 coding %>%

### 2022-07-15 scripts/r/03_analyses_coding.Rmd
🐛 - fix factors in msa_models

@@
 coding <- read_sheet(the_sheet) %>%
-  mutate(
-    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "multivariate", "other")),
-    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
-  ) %>%
   drop_na(model_n)
@@
     model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
-    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_"))
+    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_")),
+    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "other")),
+    typicality = factor(typicality, levels = c("categorical", "continuous")),
+    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
   )

### 2022-07-17 scripts/r/01_teams_analyses.Rmd
♻️ - join intake, reviews and models

--- 2022-04-19 scripts/r/teams-analyses.Rmd
@@
 
-```{r review, eval=FALSE}
-the_sheet <- "https://docs.google.com/spreadsheets/d/1vFPjZkB4naCNj10v0BuEWQDvo34okmcN1Mv7VkZL9po/edit#gid=0"
-
-review <- read_sheet(the_sheet) %>%
-  left_join(teams_analyses %>% select(Q17, Q16), by = c("Animal" = "Q17"))
-```
-
-```{r}
+```{r analytic-quest}
 dir.create("data/questionnaires/msa_data_analysis_files/", showWarnings = FALSE)

### 2022-07-17 scripts/r/03_analyses_coding.Rmd
♻️ - join intake, reviews and models

@@
   drop_na(model_n)
+```
+
+# Read intake forms
+
+We will join the intake forms with `msa_models`.
+
+```{r intake}
+other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"
+
+team_animal_coord <- read_sheet(other_sheet)
+
+msa_intake <- read_csv("./data/questionnaires/msa_intake_form.csv") %>%
+  filter(row_number() != 2)
+msa_intake_qs <- msa_intake[1,]
+msa_intake <- msa_intake[-1,]
+
+msa_intake <- msa_intake %>%
+  mutate(
+    Q6 = case_when(
+      Q6 == "Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
+      Q6 == "University of Birmingham team under the team coordinator Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
+      Q6 == "Vincent Hughes" ~ "Vince Hughes",
+      Q6 == "Tiphaine Cordelier" ~ "Tiphaine Caudrelier",
+      Q6 == "Scott Perry" ~ "Scott James Perry",
+      Q6 == "Scott James Perru" ~ "Scott James Perry",
+      Q6 == "Nicole Rodriquez" ~ "Nicole Rodriguez",
+      Q6 == "Michael Gradoville (Arizona State Univ.)" ~ "Michael Gradoville",
+      Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
+      Q6 == "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)" ~ "Dušan Nikolić",
+      Q6 == "Dusan Nikolic" ~ "Dušan Nikolić",
+      Q6 == "Dušan Nickolić" ~ "Dušan Nikolić",
+      Q6 == "Alicea Megan Brown" ~ "Alicia M Brown",
+      Q6 == "Alicia Brown" ~ "Alicia M Brown",
+      Q6 == "Ali A-Hoorie" ~ "Ali H. Al-Hoorie",
+      Q6 == "Ali Al-Hoorie" ~ "Ali H. Al-Hoorie",
+      Q6 == "Dr Rory Turnbull" ~ "Rory Turnbull",
+      Q6 == "Dr. Reenu Punnoose" ~ "Reenu Punnoose",
+      TRUE ~ Q6
+    ),
+    Q5 = as.numeric(Q5),
+    Q7_1 = as.numeric(Q7_1)
+  )
+
+msa_intake_teams <- msa_intake %>%
+  group_by(Q6) %>%
+  summarise(
+    years_from_phd = mean(Q5, na.rm = TRUE),
+    years_from_phd_sd = sd(Q5, na.rm = TRUE),
+    prior_belief = mean(Q7_1, na.rm = TRUE),
+    prior_belief_sd = sd(Q7_1, na.rm = TRUE)
+  ) %>%
+  full_join(y = team_animal_coord, by = c("Q6" = "coordinator")) %>%
+  select(-Q6)
+```
+
+# Read reviews
+
+```{r}
+msa_reviews <- readRDS("./data/peer_review/msa_reviews.rds")
+
+msa_reviews_teams <- msa_reviews %>%
+  group_by(Q3) %>%
+  summarise(
+    phon_rating = mean(Q5_2, na.rm = TRUE),
+    phon_sd = sd(Q5_2, na.rm = TRUE),
+    stat_rating = mean(Q5_3, na.rm = TRUE),
+    stat_sd = sd(Q5_3, na.rm = TRUE),
+    all_rating = mean(Q5_4, na.rm = TRUE),
+    all_sd = sd(Q5_4, na.rm = TRUE),
+  )
 ```
@@
     temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
-  )
+  ) %>%
+  left_join(y = msa_intake_teams) %>%
+  left_join(y = msa_reviews_teams, by = c("animal" = "Q3"))
 

### 2022-08-03 scripts/r/04_refit/refit_jvc.Rmd
update code to fix issues describes in #123

@@
   mutate(measure_z = (measure - mean(measure)) / sd(measure),
-    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
+    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean), 
+    typ_mean_z = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
   filter(condition == "AF")
@@
 gymnothorax_spinulosus_1_intdiff_con <- brm(
-  measure_z ~ effect_con + 
+  measure_z ~ effect_con * typ_mean_z + 
     (1|target_colour) + 
@@
   backend = "cmdstanr", seed = 06022016, 
+  control = list(max_treedepth = 14), 
   file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
@@
 
-```
-
-Processed data not available.
+# JVC: load data
+
+msa_lycodes_bradfieldi <- read_csv(here("data", "analyses", "jvc", 
+  "lycodes_bradfieldi", "processed-data", "all_trial_data_nas_removed.csv")) %>% 
+  mutate(typicality = as.factor(typicality), 
+    effect_cat = C(typicality, treatment), 
+    effect_cat = fct_relevel(effect_cat, "atypical")
+)
+
+```
+
+Processed data does not include DVs.
 
@@
 trigonias_lachneri_1_spi_con <- brm(
-  spi_z ~ effect_con, 
+  spi_z ~ effect_con + 
+    (1 + typ_mean|target_colour) + 
+    (1 + typ_mean|speaker),
   data = MSA_trigonias_lachneri_spi_data, 
@@
   backend = "cmdstanr", 
+  control = list(adapt_delta = 0.99), 
   file = here("data", "analyses", "models", "trigonias_lachneri_1_spi_con")

### 2022-08-13 RR_manuscript/results_notes.Rmd
started to write up results

---
title: "results notes"
author: "Timo Roettger"
date: "2022-08-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(faux)

```

## Sample Charactaristics

```{r}

msa_models <- readRDS("./data/analyses/msa_models.rds") %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

# number of teams
no_teams = length(unique(msa_models$team))

# number of analyses
no_analyses = nrow(msa_models)

# average analyses
mean_analyses <- msa_models %>% 
  group_by(team) %>% 
  summarise(max_models = max(model_n)) %>% 
  group_by() %>% 
  summarise(mean_models = mean(max_models))

# outcomes
outcome_n <- msa_models %>% 
  count(outcome) %>% 
  summarise(prop = n / sum(n))

# windows
window_n <- msa_models %>% 
  count(temporal_window) %>% 
  summarise(prop = n / sum(n))

# predictors
predictor_n <- msa_models %>% 
  summarise(mean_predictor = mean(n_predictors, na.rm = TRUE))

# typicality op
typicality_n <- msa_models %>% 
  count(typicality_operationalization) %>% 
  summarise(prop = n / sum(n))

# framework
framework_n <- msa_models %>% 
  count(framework) %>% 
  summarise(prop = n / sum(n))

# model
model_n <- msa_models %>% 
  count(model) %>% 
  summarise(prop = n / sum(n))

# random
random_n <- msa_models %>% 
  filter(model == "linear model") %>% 
  count(random_effects) %>% 
  summarise(prop = n / sum(n))

# random terms
rterms_n <- msa_models %>% 
  filter(n_random != 0) %>% 
  summarise(mean_rterms = mean(n_random, na.rm = TRUE))

```

# Sample characteristics

[all of this or most of this should go into a nice overview table]

`r no_teams` teams initially signed up to participate. xx dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining xx teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

Of the submitted teams, teams consisted of an average of xx analysts (sd = xx), with an average of post PhD experience of xx years (sd = xx).

The teams have submitted `r no_analyses` to answer the research question. 
On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
Analytical approaches widely varied along the following dimensions: 
Teams differed in what and how they measured the acoustic signal, including chosing different aspects of the acoustic signal, the temporal window over which they measured, the concrete operationalization of how they measured said acoustic properties.

`r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.

`r round(window_n[[1,1]],2) * 100`\% of models measured acoustic properties on the level of the segment (e.g. one vowel), `r round(window_n[[2,1]],2) * 100`\% on the level of the word (e.g. the noun), `r round(window_n[[3,1]],2) * 100`\% on the level of the phrase (e.g. the noun phrase including determiner and adjective, e.g. "the green banana"), `r round(window_n[[4,1]],2) * 100`\% on the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.

TO ADD. LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE

Teams also differed in what predictors they chose and how they operationalized them.
On average, models included `r predictor_n` different predictors (counting only conceptually different predictors), i.e. in addition to the critical predictor, typicality of the adjective noun combinations, on average, each teams included one additional predictor in their models, including LIST CO-OCCURING IVS

The most relevant predictor, typicality, was operationalized in different ways. 
It was operationalized as categorical in `r round(typicality_n[[1,1]],2) * 100`\% of models, continuous with the mean typicality rating in `r round(typicality_n[[2,1]],2) * 100`\% of models, and continuous with the median typicality rating in `r round(typicality_n[[3,1]],2) * 100`\% of models.

This multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.

The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). (`r round(framework_n[[1,1]],2) * 100`\% were rooted in a Bayesian framework. 
While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data. 
The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun. 
The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects (REFERENCE). 
`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects, `r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
On average, teams that specified random effects, included `r rterms_n` random terms in their models.

### 2022-08-16 scripts/r/03_analyses_coding.Rmd
✨ - add SDI to msa_models

@@
 
+This function is for calculation of the SDI.
+
+```{r sdi-mean}
+sdi_mean <- function(preds) {
+  bpair <- tibble::tibble(preds) %>% tidyr::unnest_wider(preds, names_sep = ".") %>%
+    as.matrix() %>%
+    betapart::beta.pair(.)
+  sdim <- as.matrix(bpair$beta.sor)
+  diag(sdim) <- NA
+  rowSums(sdim, na.rm = T) / length(preds)
+}
+```
+
 Now we load all the models and apply `clean_up()` to get the estimates.
@@
   left_join(y = msa_intake_teams) %>%
-  left_join(y = msa_reviews_teams, by = c("animal" = "Q3"))
+  left_join(y = msa_reviews_teams, by = c("animal" = "Q3")) %>%
+  # We have excluded a few extra models so keeping them out at this stage
+  filter(exclude == "no") %>%
+  # We nest all the population predictors in the coding sheet to calculate the SDI
+  nest(pop_pred = typicality_cont:`2interaction_typicality_cont_typ_mean_z`) %>%
+  mutate(
+    pop_sdi = sdi_mean(pop_pred)
+  )
 

### 2022-08-17 RR_manuscript/results_notes.Rmd
results notes

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      message = FALSE)
 
-library(tidyverse)
+library(brms)
 library(faux)
+library(dplyr)
+library(ggplot2)
+library(tidybayes)
 
@@
   )
+
+# average phd experience
+phd_mean <- msa_models %>% 
+  select(team, years_from_phd) %>% 
+  distinct(team, years_from_phd) %>% 
+  summarise(mean_phd = mean(years_from_phd, na.rm = TRUE),
+            sd_phd = sd(years_from_phd, na.rm = TRUE),
+            min_phd = min(years_from_phd, na.rm = TRUE),
+            max_phd = max(years_from_phd, na.rm = TRUE))
+
+prior_mean <- msa_models %>% 
+  select(team, prior_belief) %>% 
+  distinct(team, prior_belief) %>% 
+  summarise(mean_prior = mean(prior_belief, na.rm = TRUE),
+            sd_prior = sd(prior_belief, na.rm = TRUE),
+            min_prior = min(prior_belief, na.rm = TRUE),
+            max_prior = max(prior_belief, na.rm = TRUE))
 
@@
 
+# unique models
+#msa_models %>% distinct(n_coefficients, n_random, random_effects)
+
+# review ratings
+review_mean <- msa_models %>% 
+  summarise(mean_prating = mean(phon_rating, na.rm = TRUE),
+            sd_prating = sd(phon_rating, na.rm = TRUE),
+            mean_srating = mean(stat_rating, na.rm = TRUE),
+            sd_srating = sd(stat_rating, na.rm = TRUE))
+
 ```
@@
 # Sample characteristics
+In the following, we will describe the characteristics of our ananlyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
 
-[all of this or most of this should go into a nice overview table]
+<!-- TR: some of this or most of this should go into a nice overview table -->
+
+## Team properties
 
@@
 
-Of the submitted teams, teams consisted of an average of xx analysts (sd = xx), with an average of post PhD experience of xx years (sd = xx).
+Of the submitted teams, teams consisted of an average of xx analysts (sd = xx) <!-- TR: Where is this info?
+-->, with an average of post PhD experience of `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) ranging from `r round(phd_mean[[3]],1)` years, i.e.
+PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
 
+Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating an overall rather high prior plausibility of the hypothesis.
+
+## Acoustic analysis 
 The teams have submitted `r no_analyses` to answer the research question. 
@@
 
-TO ADD. LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE
+TO ADD: LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE
 
@@
 
+## Statistical analysis 
 This multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
@@
 On average, teams that specified random effects, included `r rterms_n` random terms in their models.
+
+TO ADD: LOOK AT MODELS AND COUNT UNIQUE MODELS.
+
+## Review ratings 
+The mean rating of the quality of acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the queality of statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
+For reference, the scale of the rating anchored a point grade of 75 as "an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation" indicating a rather high confidence of reviewers that the provided analyses yield appropriate answers to the research question.
+
+# Meta analysis
+```{r}
+
+meta_bm <- readRDS("./data/meta_analysis/meta_bm.rds")
+
+meta_intercept <- fixef(meta_bm)
+meta_random <- ranef(meta_bm)
+
+# wrangle by hand 
+post_meta <- meta_bm %>%
+  spread_draws(b_Intercept, r_model_id[model,]) %>%
+  mutate(model_mean = b_Intercept + r_model_id) %>% 
+  group_by(model) %>% 
+  dplyr::summarise(post_mean = mean(model_mean),
+            lower95 = quantile(model_mean, probs = .025),
+            higher95 = quantile(model_mean, probs = .975)
+            ) %>% 
+  # this basically needs to be fed by whether or not the authors considered there to be an effect
+  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
+                                          higher95 < 0 ~ "positive",
+                                          TRUE ~ "not compelling")))
+
+compelling_results <- post_meta %>% 
+  count(compelling) %>% 
+  summarise(prop = n / sum(n))
+
+compelling_count <- table(post_meta$compelling)
+
+```
+
+## SUBHEADER 1
+
+The Bayesian random effects meta analysis estimates the range of probable values of the standardized effect size of `r round(meta_intercept[1],3)` (95\% CrI = [`r round(meta_intercept[3],3)`, `r round(meta_intercept[3],4)`]).
+In other words, if we were to assume that there is a true underlying effect and we consider each model an attempt to estimate this effect randomly drawn from a population of models, our best guess about the underlying effect is that it is `r round(meta_intercept[1],3)` standard deviations above zero, corresponding to atypical word combinations having `r round(meta_intercept[1],3)` standard deviations higher acoustic values (e.g.
+duration) than typical word combinations.
+CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES). 
+This is not only a extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but the range of probably values also includes zero.
+So, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not point zero to begin with.
+This population effect is dwarfed by the estimated standard deviation between different models (EXTRACT BETA AND CRIS). 
+(ref:meta_plot1) plots the estimated model outputs for all submitted models according to size. 
+Note that given the nature of acoustic operationalization, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
+longer duration, or higher f0).
+Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not overlap with zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+
+```{r 'plot_meta1', echo = FALSE, fig.cap="(ref:meta_plot1)", out.width="100%"}
+
+knitr::include_graphics("./plots/meta_plot1.png")
+
+```
+
+## SUBHEADER 2
+After assessing the variability across models, we now turn towards estiamting the impact of a series of predictors to predict model outcomes.

### 2022-08-17 scripts/r/03_analyses_coding.Rmd
loaded tidyverse manually

@@
 knitr::opts_knit$set(root.dir = here::here())
-library(tidyverse)
+#library(tidyverse)
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(readr)
 library(ggmosaic)

### 2022-08-17 RR_manuscript/results_notes.Rmd

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,
-                      warning = FALSE,
-                      message = FALSE)
+knitr::opts_chunk$set(echo = FALSE)
 
@@
 # unique models
-#msa_models %>% distinct(n_coefficients, n_random, random_effects)
+msa_models %>% distinct(n_coefficients, n_random, random_effects)
 
@@
 
-## SUBHEADER 1
-
 The Bayesian random effects meta analysis estimates the range of probable values of the standardized effect size of `r round(meta_intercept[1],3)` (95\% CrI = [`r round(meta_intercept[3],3)`, `r round(meta_intercept[3],4)`]).
@@
 longer duration, or higher f0).
-Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not overlap with zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+Notably, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not overlap with zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
 
@@
 ```
-
-## SUBHEADER 2
-After assessing the variability across models, we now turn towards estiamting the impact of a series of predictors to predict model outcomes.

### 2022-08-17 scripts/r/02_teams_reviews.Rmd

@@
 
-reviews <- read_csv(list.files("data/peer_review/", full.names = TRUE), skip = 3, col_names = cols[[1]]) %>%
+msa_reviews <- read_csv(list.files("data/peer_review/", pattern = ".csv", include.dirs = FALSE, full.names = TRUE), skip = 3, col_names = cols[[1]]) %>%
   mutate(
@@
   filter(Finished == TRUE)
+
+saveRDS(msa_reviews, "./data/peer_review/msa_reviews.rds")
 ```
@@
 
-  reviews %>%
+  msa_reviews %>%
     filter(Q3 == team) %>%

### 2022-08-17 scripts/r/04_refit/refit_sc.Rmd
♻️ - excluded polymetme_brevirostrum
We have excluded this because of fixed-effect matrix rank deficiency
given that many combination of Condition * effect_cat do not exist
in the data.

@@
 
-```{r}
+We have excluded this because of fixed-effect matrix rank deficiency given that many combination of Condition * effect_cat do not exist in the data.
+
+```{r eval=FALSE}
 # Get datasets
@@
 
-```{r}
+```{r eval=FALSE}
 polymetme_brevirostrum_1_dur_cat <- brm(

### 2022-08-17 scripts/r/04_refit/refit_sc.Rmd
♻️ - refit nestor_idahoensis with default priors

@@
 
-Not sure which priors to use after scaling.
+~~Not sure which priors to use after scaling.~~
+
+We have decided to use default (flat) priors.
 
 ```{r}
-priors2 = c(
-  #weakly informative priors for intercepts and beta for each response variable
-  prior(normal(0,1.5), class = Intercept, resp = f0),
-  prior(normal(0,1.5), class = b, resp = f0),
-  prior(normal(0,1.5), class = Intercept, resp = duration),
-  prior(normal(0,1.5), class = b, resp = duration),
-  prior(normal(0,1.5), class = Intercept, resp = f15),
-  prior(normal(0,1), class = b, resp = f15),
-  prior(normal(0,1), class = Intercept, resp = f25),
-  prior(normal(0,1), class = b, resp = f25),
-  #weakly informative priors for random effects (slopes)
-  prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
-  prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
-  prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
-  prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
-  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
-  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
-  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
-  prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
-  #weakly informative priors for the correlation between random intercept and slope
-  prior(lkj(2), class = cor, group = ID),
-  prior(lkj(2), class = cor, group = targetWord),
-  prior(cauchy(0, 1), class = sigma, resp=f0),
-  prior(cauchy(0, 1), class = sigma, resp=duration),
-  prior(cauchy(0, 1), class = sigma, resp=f15),
-  prior(cauchy(0, 1), class = sigma, resp=f25)
-)
+# priors2 = c(
+#   #weakly informative priors for intercepts and beta for each response variable
+#   prior(normal(0,1.5), class = Intercept, resp = f0),
+#   prior(normal(0,1.5), class = b, resp = f0),
+#   prior(normal(0,1.5), class = Intercept, resp = duration),
+#   prior(normal(0,1.5), class = b, resp = duration),
+#   prior(normal(0,1.5), class = Intercept, resp = f15),
+#   prior(normal(0,1), class = b, resp = f15),
+#   prior(normal(0,1), class = Intercept, resp = f25),
+#   prior(normal(0,1), class = b, resp = f25),
+#   #weakly informative priors for random effects (slopes)
+#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f0),
+#   prior(cauchy(0,0.1), class = sd, group = ID, resp = duration),
+#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f15),
+#   prior(cauchy(0,0.1), class = sd, group = ID, resp = f25),
+#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f0),
+#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = duration),
+#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f15),
+#   prior(cauchy(0,0.1), class = sd, group = targetWord, resp = f25),
+#   #weakly informative priors for the correlation between random intercept and slope
+#   prior(lkj(2), class = cor, group = ID),
+#   prior(lkj(2), class = cor, group = targetWord),
+#   prior(cauchy(0, 1), class = sigma, resp=f0),
+#   prior(cauchy(0, 1), class = sigma, resp=duration),
+#   prior(cauchy(0, 1), class = sigma, resp=f15),
+#   prior(cauchy(0, 1), class = sigma, resp=f25)
+# )
 
@@
   family = gaussian(),
-  prior = priors2, chains = 4, cores = 4,
+  # prior = priors2,
+  chains = 4, cores = 4,
   threads = threading(2, grainsize = 100),
@@
 ```
+
+Warning: 6 of 4000 (0.0%) transitions ended with a divergence.
 

### 2022-08-18 scripts/r/04_refit/refit_jvc.Rmd
edits

@@
     effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean), 
-    typ_mean_z = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
-  filter(condition == "AF")
+    condition_s = as.factor(condition),
+    condition_s = C(condition_s, sum))
+#  filter(condition == "AF")
 
 gymnothorax_spinulosus_1_intdiff_con <- brm(
-  measure_z ~ effect_con * typ_mean_z + 
+  measure_z ~ effect_con * condition_s + 
     (1|target_colour) + 

### 2022-08-23 RR_manuscript/results_notes.Rmd
rerun model

--- 2022-08-17 RR_manuscript/results_notes.Rmd
@@
 
+<!-- TR: not just 30 right? Please add the accurate infor here -->
+
 Of the submitted teams, teams consisted of an average of xx analysts (sd = xx) <!-- TR: Where is this info?
--->, with an average of post PhD experience of `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) ranging from `r round(phd_mean[[3]],1)` years, i.e.
+-->.
+Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e.
 PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
 
-Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating an overall rather high prior plausibility of the hypothesis.
+Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating that analysts had an overall rather high prior plausibility of the hypothesis (scale ranged from 0 to 100).
+
+The teams have submitted `r no_analyses` models to answer the research question. 
+On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
+Analytical approaches widely varied along the following dimensions: 
+First, teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, the concrete operationalization of how they measured said acoustic properties.
 
 ## Acoustic analysis 
-The teams have submitted `r no_analyses` to answer the research question. 
-On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
-Analytical approaches widely varied along the following dimensions: 
-Teams differed in what and how they measured the acoustic signal, including chosing different aspects of the acoustic signal, the temporal window over which they measured, the concrete operationalization of how they measured said acoustic properties.
-
 `r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.
 
-`r round(window_n[[1,1]],2) * 100`\% of models measured acoustic properties on the level of the segment (e.g.
-one vowel), `r round(window_n[[2,1]],2) * 100`\% on the level of the word (e.g.
-the noun), `r round(window_n[[3,1]],2) * 100`\% on the level of the phrase (e.g.
+`r round(window_n[[1,1]],2) * 100`\% of models measured acoustic properties at the level of the segment (e.g.
+comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% at the level of the word (e.g.
+comparing the acoustic profile of "banana"), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g.
 the noun phrase including determiner and adjective, e.g.
-"the green banana"), `r round(window_n[[4,1]],2) * 100`\% on the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
+"the green banana"), `r round(window_n[[4,1]],2) * 100`\% at the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
 
@@
 
-Teams also differed in what predictors they chose and how they operationalized them.
-On average, models included `r predictor_n` different predictors (counting only conceptually different predictors), i.e.
-in addition to the critical predictor, typicality of the adjective noun combinations, on average, each teams included one additional predictor in their models, including LIST CO-OCCURING IVS
+## Statistical analysis 
+Second, this multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the choice of predictor and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
 
-The most relevant predictor, typicality, was operationalized in different ways. 
-It was operationalized as categorical in `r round(typicality_n[[1,1]],2) * 100`\% of models, continuous with the mean typicality rating in `r round(typicality_n[[2,1]],2) * 100`\% of models, and continuous with the median typicality rating in `r round(typicality_n[[3,1]],2) * 100`\% of models.
+On average, models included `r round(predictor_n,2)` different predictors (counting only conceptually different predictors), i.e.
+in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
+Predictors included LIST CO-OCCURING IVS...
 
-## Statistical analysis 
-This multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
+The original dataset allowed to operationalize the most relevant predictor, typicality, in different ways. 
+It was operationalized as categorical (e.g.
+typical vs.
+atypical) in `r round(typicality_n[[1,1]],2) * 100`\% of models, continuous (on a scale from 0-100) with the mean typicality rating in `r round(typicality_n[[2,1]],2) * 100`\% of models, and continuous with the median typicality rating in `r round(typicality_n[[3,1]],2) * 100`\% of models.
 
-The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). (`r round(framework_n[[1,1]],2) * 100`\% were rooted in a Bayesian framework. 
+The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). `r round(framework_n[[1,1]],2) * 100`\% were rooted in a Bayesian framework. 
 While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
@@
 The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects (REFERENCE). 
-`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects, `r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
-On average, teams that specified random effects, included `r rterms_n` random terms in their models.
+`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all, so effectively ignoring these non-independences.
+`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
+On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models.
 
@@
 ## Review ratings 
-The mean rating of the quality of acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the queality of statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
-For reference, the scale of the rating anchored a point grade of 75 as "an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation" indicating a rather high confidence of reviewers that the provided analyses yield appropriate answers to the research question.
+Teams reviewed each other analyses for both the acoustic analysis and the statistical analysis. 
+The mean rating of the quality of the acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the quality of the statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
+For reference, the scale of the rating anchored a point grade of 75 as "an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation", indicating a rather high confidence of reviewers that the provided analyses yield appropriate (yet "imperfect") answers to the research question.
 
@@
 duration) than typical word combinations.
+
 CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).
-This is not only a extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but the range of probably values also includes zero.
+
+This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but the range of probably values also includes zero.
 So, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not point zero to begin with.
-This population effect is dwarfed by the estimated standard deviation between different models (EXTRACT BETA AND CRIS). 
+Moreover, the population effect is dwarfed by the estimated standard deviation between different models (EXTRACT BETA AND CRIS). 
 (ref:meta_plot1) plots the estimated model outputs for all submitted models according to size. 
-Note that given the nature of acoustic operationalization, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
-longer duration, or higher f0).
+Note that given the nature and wide variety of acoustic operationalization, there is not always a natural interpretation of the scale. 
+However, in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g. longer duration, higher f0, etc.).
 Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not overlap with zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
@@
 ## SUBHEADER 2
-After assessing the variability across models, we now turn towards estiamting the impact of a series of predictors to predict model outcomes.
+After assessing the variability across models, we now turn towards estimating the impact of a series of predictors to predict model outcomes.

### 2022-09-01 RR_manuscript/Draft_RR.Rmd
wrote discussion draft

@@
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted [@simmons2011false].
-Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik2020variability].
+Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set [e.g., @silberzahn2018many; @starns2019assessing; @botvinik-nezer2020].
 These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.

### 2022-09-01 RR_manuscript/results_notes.Rmd
exploring the coef conundrum
wrote discussion draft

@@
 ```
-
-## Sample Charactaristics
 
@@
 
-<!-- TR: not just 30 right? Please add the accurate infor here -->
+<!-- TR: not just 30 right? Please add the accurate info here -->
 
@@
 
-TO ADD: LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE
+<!-- TR: TO ADD: LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE-->
 
@@
 
-TO ADD: LOOK AT MODELS AND COUNT UNIQUE MODELS.
+<!-- TR: TO ADD: TO ADD: LOOK AT MODELS AND COUNT UNIQUE MODELS.-->
 
@@
 
-## SUBHEADER 1
+## Estimating the crowd sourced effect size
 
-The Bayesian random effects meta analysis estimates the range of probable values of the standardized effect size of `r round(meta_intercept[1],3)` (95\% CrI = [`r round(meta_intercept[3],3)`, `r round(meta_intercept[3],4)`]).
-In other words, if we were to assume that there is a true underlying effect and we consider each model an attempt to estimate this effect randomly drawn from a population of models, our best guess about the underlying effect is that it is `r round(meta_intercept[1],3)` standard deviations above zero, corresponding to atypical word combinations having `r round(meta_intercept[1],3)` standard deviations higher acoustic values (e.g.
-duration) than typical word combinations.
+The Bayesian random effects model estimates the range of probable values of the standardized effect size between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` (95\% CrI, mean = `r round(meta_intercept[1],3)`)
+In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],3)` standard deviations above zero.
+This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],3)` standard deviations higher acoustic values (e.g.
+duration, f0 etc,) than typical word combinations.
 
-CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).
+<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).-->
 
-This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but the range of probably values also includes zero.
-So, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not point zero to begin with.
-Moreover, the population effect is dwarfed by the estimated standard deviation between different models (EXTRACT BETA AND CRIS). 
-(ref:meta_plot1) plots the estimated model outputs for all submitted models according to size. 
-Note that given the nature and wide variety of acoustic operationalization, there is not always a natural interpretation of the scale. 
-However, in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g. longer duration, higher f0, etc.).
-Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not overlap with zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but there is also much uncertainty around this estimate and the range of probably values includes zero.
+Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not point zero to begin with. 
+Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but 
+if there is an effect of typicality, it is very small.
+Moreover, this population estimate is half the size of the estimated standard deviation between different models <!-- TR: EXTRACT BETA AND CRIS).--> 
+(ref:meta_plot1) illustrates the estimated model outputs for all submitted models according to size. 
+Note that given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
+longer duration, higher f0, etc.).
+Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+
+<!-- TR: ADD PARAGRAPH ON HOW MANY CLAIMED THERE TO BE AN EFFECT.-->
 
@@
 
-## SUBHEADER 2
-After assessing the variability across models, we now turn towards estimating the impact of a series of predictors to predict model outcomes.
+## Can we predict the estimate?
+After assessing the variability across models, we now turn toward estimating the impact of a series of predictors the analysts model estimates 
+There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic (REF)?
+
+(ref:meta_plot1), panel C, displays the coefficients alongside 80% and 95% credible intervals for all model predictors.
+
+<!-- TR: ADD TABLE HERE TOO?-->
+
+The model suggests that most team-specific predictors yield very small mean estimates and 95% credibile intervals that include zero, leaving us highly uncertain about their direction. 
+Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
+Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates. 
+This suggests that the analysts' results very much depend on the choice of predictors. 
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. duration or f0) and the choice of temporal window affected the results. 
+(ref:meta_plot1) displays the posterior estimates for the measurement outcome (i.e.
+what acoustic dimension was measured, panel A) and measurement window (i.e.
+what is the unit over which was measured, panel B).
+If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytical estimate.
+If on the other hand, vowel formants were measured, estimates are higher than the meta analytical estimate.
+Similarly, if acoustic parameters were measured within individual segments (e.g.
+the vowel of the noun), estimates are lower than the meta analytical estimate, and if acoustic parameters were measured across whole phrases (e.g.
+"the blue banana"), the estimates are generally higher.
+In other words, depending on the choice of measurement, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+
+```{r 'plot_meta2', echo = FALSE, fig.cap="(ref:meta_plot1)", out.width="100%"}
+
+knitr::include_graphics("./plots/alltogether.png")
+
+```
+
+# Discussion drafty
+## Summary
+We gave XX analyst teams the same acoustic dataset to answer the same research question. 
+In order to answer the question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
+This complex process led to a large garden of forking paths.  
+Each individual analyst team chose unique paths to acoustically measure, operationalize and statistical analyse the data.
+Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
+The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
+Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+These findings are very much in line with previous crowd-sourced projects that suggested variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF).
+Given the mounting evidence, Breznau et al.
+(2021) concluded that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytical decisions."
+Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
+
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices. 
+Human speech is a complex multidimensional signal. 
+Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in. 
+Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
+For example, measurements related to fundamental frequency tended to results in lower estimates while measurements related to vowel formants tended to yield higher estimates. 
+This asymmetry can have several causes: 
+First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and / or manifests itself negatively in one acoustic measure but positively in another.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question and lead to strong bias. 
+Many researchers targeted f0-related measures since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
+@grice2017integrating; @turnbull2017role].
+Third, ADD REASONS. 
+Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against an theoretically relevant effect.
+
+## Lessons for the methodological reform movement
+The current results point to important barriers for successful knowledge accumulation. 
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
+One of the suggested paths forward is for researchers to directly replicate more [@open2015estimating; REFS, REFS].
+While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) show that replicating more is not enough.
+There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative results relative to all possible procedures that could have been applied to the research question.
+Well-trained and experienced speech researchers not only applied completely different approaches to the same analytical question, they also seem to consider all these alternative approaches applied by other teams acceptable.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility". 
+Now that researchers know that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of their data, they should calibrate their (un)certainty in the strength of the evidence and, in turn, communicate that uncertainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggest that we need stronger quantitative theories about how measurement systems (here the acoustic signal) and underlying theoretical construct (here the phonetic expression of typicality) relate to each other.
+Researchers ideally specify the derivation chain [@dubin1970theory;@meehl1990summaries], i.e.
+the link between theoretical construct and quantitative system, prior to data collection and analysis, including defining concepts and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, defining target measurements and statistical predictions, including possible (and impossible) effect magnitudes.
+Without well defined derivation chains, researchers "are not even wrong" [@scheel2022most] because falsified predictions cannot  tell us much about the theoretical constructs that they are after.
+
+In light of the observed analytical flexibility, what can researchers do to appropriately calibrate their confidence in their claims?
+First of all, through sharing of materials, data and statistical protocols, researchers can make their idiosyncratic choices transparent to others (REF). 
+This enables critical evaluation and robustness checks by other researchers (REF).
+Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], researches should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analysis.
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., CITE Praat, EMU CITE)]].
+
+ADD
+
+Second, making analytical pathways completely re-traceable does not change the fact that analysts apply different analytical approaches. 
+Crowd-sourcing projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensus estimate using meta-analytical techniques. 
+This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large theoretical or practical consequences.
+
+Third, if researchers have a good understanding of relevant analytical degrees of freedom, they could apply all conceivable analytical strategies and compare the results across all combinations of these choices.
+This approach is called multiverse analysis [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines. 
+Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
+Crowd-sourcing is limited by the sampled analyst and their biases. 
+Multiverse analysis is limited even further by the one group of researchers who define possible analytical pathways. 
+Eventually, a mature scientific discipline should develop strong quantitative theories of how theoretical constructs manifest themselves in the measurement system, i.e.
+in the present case how communicative pressures of functions are expressed in the acoustic signal.
+Recently, researchers across the cognitive science have raised awareness of a general lack of quantitative theory, calling for establishing appropriate derivation chains and formalizing verbal theories mathematically [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+
+## Caveats
+Our study has several limitations that need to be considered when evaluating our results. 
+First of all, our sample is an opportunity sample. 
+We have advertise the project through online platforms which might lead to the exclusion of certain potential researcher groups.
+Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely too small to estimate meta-analytical estimates reliably.
+This is particularly important for the predictor evaluation.
+Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+
+ADD
+
+# Conclusion

### 2022-09-01 RR_manuscript/results_notes.Rmd
add analyst team descriptives

@@
 library(tidybayes)
+library(here)
 
@@
 
-msa_models <- readRDS("./data/analyses/msa_models.rds") %>%
+msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
   mutate(
@@
 
-# number of teams
+# number of teams (final)
 no_teams = length(unique(msa_models$team))
+
+# number of teams (initially)
+no_teams_init <- readr::read_csv(
+  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
+  select(Q6) %>% # Questions asking for team leader
+  filter(!(row_number() %in% c(1, 2))) %>% 
+  distinct() %>% 
+  nrow
 
@@
 # Sample characteristics
-In the following, we will describe the characteristics of our ananlyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
+
+In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
 
@@
 
-`r no_teams` teams initially signed up to participate. xx dropped out of the project during the analysis phase^[ADD REASONS]. 
-The remaining xx teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
+`r no_teams_init %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
+`r (no_teams_init - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
+The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
 
@@
 
-meta_bm <- readRDS("./data/meta_analysis/meta_bm.rds")
+meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))
 
@@
 
-knitr::include_graphics("./plots/meta_plot1.png")
+knitr::include_graphics(here("./plots/meta_plot1.png"))
 
@@
 
-knitr::include_graphics("./plots/alltogether.png")
+knitr::include_graphics(here("./plots/alltogether.png"))
 

### 2022-09-01 RR_manuscript/results_notes.Rmd
name unnamed chunks

@@
 
-```{r}
+```{r, 'load-data'}
 
@@
 ## Acoustic analysis
+
 `r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.
@@
 # Meta analysis
-```{r}
+
+```{r, 'load-meta-analysis'}
 
@@
 # Discussion drafty
+
 ## Summary
+
 We gave XX analyst teams the same acoustic dataset to answer the same research question. 

### 2022-09-01 RR_manuscript/results_notes.Rmd
added team descriptives from initial sign ups

@@
 
-# number of teams (initially)
-no_teams_init <- readr::read_csv(
+# Get DF of all members with leader names
+#
+# NOTE: This can be simplified using 03_analyses_coding.Rmd
+# I'll come back to this later and rewrite
+#
+team_leaders <- readr::read_csv(
   here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
-  select(Q6) %>% # Questions asking for team leader
+  select(ResponseId, Q6) %>% # Questions asking for team leader
   filter(!(row_number() %in% c(1, 2))) %>% 
-  distinct() %>% 
-  nrow
+  mutate(leader = Q6, 
+    leader = case_when(
+    Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali Al-Hoorie", 
+    Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia Brown", 
+    Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
+    Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
+    Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dusan Nikolic", 
+    Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
+    Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
+    Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perru", 
+    Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
+    Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
+    Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vincent Hughes", 
+    TRUE ~ leader
+  )) %>% 
+  select(ResponseId, leader)
+
+# Team descriptives
+#  - number of teams (initially)
+#  - Avg size of each team
+team_desc <- team_leaders %>% 
+  group_by(leader) %>% 
+  mutate(member_num = seq_along(ResponseId)) %>% 
+  group_by(leader) %>% 
+  mutate(n_members = max(member_num)) %>% 
+  distinct(leader, n_members) %>% 
+  ungroup() %>% 
+  summarize(n_teams = nrow(.), 
+            mean_size = mean(n_members), 
+            sd_size = sd(n_members), 
+            median_size = median(n_members))
+
+# Need to join team leaders with msa_models$team to get the number of members on 
+# each team (unless this data already lives somewhere else) 
+# We could use : 
+# https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit#gid=0 
+# But I'm thinking we need to make anonymous the team leader name info (offline) 
+# for any of this to be a permanent solution.
 
@@
 
-`r no_teams_init %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
-`r (no_teams_init - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
+`r team_desc$n_teams %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
+`r (team_desc$n_teams - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
 The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
@@
 <!-- TR: not just 30 right? Please add the accurate info here -->
+<!-- 
+JVC: I pulled the initial total from the uptake doc (see line 58-n) 
+I think this is the most accurate count, by Stef might have another way
+-->
 

### 2022-09-02 RR_manuscript/results_notes.Rmd
🐛 - edits to results section
Fixed a few typos, re-styled, and expanded on a few areas.

@@
 On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
-Analytical approaches widely varied along the following dimensions: 
+analytic approaches widely varied along the following dimensions:
 First, teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, the concrete operationalization of how they measured said acoustic properties.
@@
 what is the unit over which was measured, panel B).
-If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytical estimate.
-If on the other hand, vowel formants were measured, estimates are higher than the meta analytical estimate.
+If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
+If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
 Similarly, if acoustic parameters were measured within individual segments (e.g.
-the vowel of the noun), estimates are lower than the meta analytical estimate, and if acoustic parameters were measured across whole phrases (e.g.
+the vowel of the noun), estimates are lower than the meta analytic estimate, and if acoustic parameters were measured across whole phrases (e.g.
 "the blue banana"), the estimates are generally higher.
@@
 
-We gave XX analyst teams the same acoustic dataset to answer the same research question. 
-In order to answer the question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
-This complex process led to a large garden of forking paths.  
-Each individual analyst team chose unique paths to acoustically measure, operationalize and statistical analyse the data.
+We gave XX analyst teams the same speech dataset to answer the same research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*.
+In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
+As shown by the results of this meta-anlyitic study, such complex process has led to a wide "garden of forking paths", i.e. to a wide range of combinations of possible analitic decisions.
+Each individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
 Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
@@
 Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
-These findings are very much in line with previous crowd-sourced projects that suggested variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF).
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF).
 Given the mounting evidence, Breznau et al.
-(2021) concluded that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytical decisions."
+(2021) conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."
 Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
@@
 Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
-For example, measurements related to fundamental frequency tended to results in lower estimates while measurements related to vowel formants tended to yield higher estimates. 
-This asymmetry can have several causes: 
-First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and / or manifests itself negatively in one acoustic measure but positively in another.
-Second, certain measurement choices might be associated with stronger expectations relative to the research question and lead to strong bias. 
-Many researchers targeted f0-related measures since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
+For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
+This asymmetry can have several causes.
+First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
+Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
 @grice2017integrating; @turnbull2017role].
 Third, ADD REASONS. 
-Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against an theoretically relevant effect.
+Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
 
 ## Lessons for the methodological reform movement
-The current results point to important barriers for successful knowledge accumulation. 
+
+The current results point to important barriers for successful accumulation of knowledge.
 The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
-One of the suggested paths forward is for researchers to directly replicate more [@open2015estimating; REFS, REFS].
-While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) show that replicating more is not enough.
-There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative results relative to all possible procedures that could have been applied to the research question.
-Well-trained and experienced speech researchers not only applied completely different approaches to the same analytical question, they also seem to consider all these alternative approaches applied by other teams acceptable.
+One of the suggested paths forward is for researchers to directly replicate previous study more often [@open2015estimating; REFS, REFS].
+While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is not enough.
+There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
+Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
-Now that researchers know that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of their data, they should calibrate their (un)certainty in the strength of the evidence and, in turn, communicate that uncertainty appropriately.
-The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggest that we need stronger quantitative theories about how measurement systems (here the acoustic signal) and underlying theoretical construct (here the phonetic expression of typicality) relate to each other.
-Researchers ideally specify the derivation chain [@dubin1970theory;@meehl1990summaries], i.e.
-the link between theoretical construct and quantitative system, prior to data collection and analysis, including defining concepts and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, defining target measurements and statistical predictions, including possible (and impossible) effect magnitudes.
-Without well defined derivation chains, researchers "are not even wrong" [@scheel2022most] because falsified predictions cannot  tell us much about the theoretical constructs that they are after.
 
-In light of the observed analytical flexibility, what can researchers do to appropriately calibrate their confidence in their claims?
-First of all, through sharing of materials, data and statistical protocols, researchers can make their idiosyncratic choices transparent to others (REF). 
-This enables critical evaluation and robustness checks by other researchers (REF).
-Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], researches should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analysis.
+A desired outcome of knowomg that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+<!-- TODO: add ref to "process and statistical model" in McElreath -->
+We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
+
+In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+This enables critical evaluation and robustness checks by other fellow researchers (REF).
+Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
+<!-- TODO: cite Praat, EMU, MFA, Formant tracking etc -->
 Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., CITE Praat, EMU CITE)]].
@@
 
-Second, making analytical pathways completely re-traceable does not change the fact that analysts apply different analytical approaches. 
-Crowd-sourcing projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensus estimate using meta-analytical techniques. 
-This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large theoretical or practical consequences.
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Crowd-source projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
 
-Third, if researchers have a good understanding of relevant analytical degrees of freedom, they could apply all conceivable analytical strategies and compare the results across all combinations of these choices.
-This approach is called multiverse analysis [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines. 
+Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+This approach is called "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
 Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
-Crowd-sourcing is limited by the sampled analyst and their biases. 
-Multiverse analysis is limited even further by the one group of researchers who define possible analytical pathways. 
-Eventually, a mature scientific discipline should develop strong quantitative theories of how theoretical constructs manifest themselves in the measurement system, i.e.
+Crowd-sourcing is limited by the sampled analysts and their biases.
+Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
+Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
 in the present case how communicative pressures of functions are expressed in the acoustic signal.
-Recently, researchers across the cognitive science have raised awareness of a general lack of quantitative theory, calling for establishing appropriate derivation chains and formalizing verbal theories mathematically [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+More recently, researchers across the cognitive sciences have also raised awareness of a general lack of detailed quantitative hypotheses, calling for establishing appropriate derivation chains and formalizing verbal expectations mathematically [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
 ## Caveats
+
 Our study has several limitations that need to be considered when evaluating our results. 
@@
 We have advertise the project through online platforms which might lead to the exclusion of certain potential researcher groups.
-Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely too small to estimate meta-analytical estimates reliably.
+Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely too small to estimate meta-analytic estimates reliably.
 This is particularly important for the predictor evaluation.

### 2022-09-02 RR_manuscript/results_notes.Rmd
♻️ - edit results section
♻️ - edit caveats

@@
 date: "2022-08-13"
-output: html_document
+output:
+  html_document:
+    number_sections: true
 ---
@@
 
+## Between-team variability
+
+<!-- TODO: discuss between-team variability -->
+
 ## Estimating the crowd sourced effect size
@@
 
+<!-- Brainstorm of ideas -->
+
+- Analytic flexibility applies to us (as principal investigators) too.
+- Research question was vague enough to possibily inflate between-team variability (REF, Hannah Fraser; although it is a typical kind of question, as found in the literature).
+We do relate analytical flexibility with underspecified hypothesis in the previous section.
+- This should be replicated with a different question/data set.
+- With this study, we can suggest that at a minimum this is the between-team variability, but need more studies like this one.
+- Generalisability to linguistics/language sciences tout-court is limited. Need to do same with other fields, like language development, historical data, sociolinguistics, etc.
+- The focus is on quantitative data analysis, so that we expect the issues raised here to apply differently or not at all to qualitative data analysis.
+- We have not investigated researcher positionality, which is known to be an important factor.
+
 # Conclusion

### 2022-09-02 RR_manuscript/results_notes.Rmd
add sample descriptives, include in text

--- 2022-09-01 RR_manuscript/results_notes.Rmd
@@
 library(here)
+library(googlesheets4)
 
@@
 
+# Helper function to print table data easier
+split_to_list <- function(.data, ...) {
+  dots <- rlang::enquos(...)
+  for (var in seq_along(dots)) {
+    var_name <- rlang::as_name(dots[[var]])
+    .data <- purrr::map_depth(
+      .x = .data,
+      .depth = var - 1,
+      .f = function(xs) split(xs, xs[var_name])
+    )
+  }
+  .data
+}
+
+team_sheet <- "https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit?usp=sharing"
+teams <- read_sheet(team_sheet)
+
 # Get DF of all members with leader names
-#
-# NOTE: This can be simplified using 03_analyses_coding.Rmd
-# I'll come back to this later and rewrite
-#
 team_leaders <- readr::read_csv(
@@
          leader = case_when(
-    Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali Al-Hoorie", 
-    Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia Brown", 
+           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
+           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
            Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
            Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
-    Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dusan Nikolic", 
+           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
            Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
            Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
-    Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perru", 
+           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
            Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
            Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
-    Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vincent Hughes", 
+           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
+           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
            TRUE ~ leader
@@
 
+# Teams on OSF
+teams_on_osf <- teams %>% 
+  filter(added_on_osf == "yes") %>% 
+  pull(coordinator)
+
+# Teams with submitted analyses
+teams_used_in_analysis <- teams %>% 
+  filter(animal %in% msa_models$animal) %>% 
+  pull(coordinator)
+
 # Team descriptives
@@
 #  - Avg size of each team
-team_desc <- team_leaders %>% 
+team_desc_df <- bind_rows(
+  team_leaders %>% 
     group_by(leader) %>% 
@@
               sd_size = sd(n_members), 
-            median_size = median(n_members))
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Initial"), 
+  team_leaders %>% 
+    filter(leader %in% teams_on_osf) %>% 
+    group_by(leader) %>% 
+    mutate(member_num = seq_along(ResponseId)) %>% 
+    group_by(leader) %>% 
+    mutate(n_members = max(member_num)) %>% 
+    distinct(leader, n_members) %>% 
+    ungroup() %>% 
+    summarize(n_teams = nrow(.), 
+              mean_size = mean(n_members), 
+              sd_size = sd(n_members), 
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Submitted"), 
+  team_leaders %>% 
+    filter(leader %in% teams_used_in_analysis) %>% 
+    group_by(leader) %>% 
+    mutate(member_num = seq_along(ResponseId)) %>% 
+    group_by(leader) %>% 
+    mutate(n_members = max(member_num)) %>% 
+    distinct(leader, n_members) %>% 
+    ungroup() %>% 
+    summarize(n_teams = nrow(.), 
+              mean_size = mean(n_members), 
+              sd_size = sd(n_members), 
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Final")
+  ) %>% 
+  mutate_if(is.numeric, round, digits = 2)
 
-# Need to join team leaders with msa_models$team to get the number of members on 
-# each team (unless this data already lives somewhere else) 
-# We could use : 
-# https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit#gid=0 
-# But I'm thinking we need to make anonymous the team leader name info (offline) 
-# for any of this to be a permanent solution.
+team_desc_list <- team_desc_df %>% 
+  tidyr::pivot_longer(cols = n_teams:median_size, names_to = "metric", values_to = "val") %>% 
+  split_to_list(stage, metric)
+
+# Example usage
+# team_desc_list$Initial$n_teams$val
 
@@
 
-`r team_desc$n_teams %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
-`r (team_desc$n_teams - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
-The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
+`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS].
+The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
 
-<!-- TR: not just 30 right? Please add the accurate info here -->
-<!-- 
-JVC: I pulled the initial total from the uptake doc (see line 58-n) 
-I think this is the most accurate count, by Stef might have another way
--->
-
-Of the submitted teams, teams consisted of an average of xx analysts (sd = xx) <!-- TR: Where is this info?
--->.
+Of the submitted teams, teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
 Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e.
 PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
+
+```{r}
+#| label: team-descriptives-table
+#| echo: false
+#| eval: false
+team_desc_df %>% 
+  mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
+  select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
+  knitr::kable(align = c("l", "r", "r", "r"), 
+               caption = "Caption test", 
+               label = "team-descriptives-table")
+```
 

### 2022-09-05 RR_manuscript/results_notes.Rmd
♻️ - add unique meas/model specs in results

@@
 library(dplyr)
+library(tidyr)
 library(ggplot2)
@@
 
-```{r, 'load-data'}
+```{r load-data}
 
@@
 
+# acoustic operationalizations
+# Gross operationalization of acoustic operationalization
+unique_acou_oper <- msa_models %>%
+  unite("unique_oper", outcome, operationalisation, operationalisation_notes, na.rm = TRUE) %>%
+  count(unique_oper)
+
 # average analyses
@@
 
-# unique models
-#msa_models %>% distinct(n_coefficients, n_random, random_effects)
+# unique model specs, discarding random effects
+unique_model_specs <- msa_models %>%
+  select(framework:outcome, pop_pred) %>%
+  unnest(pop_pred) %>%
+  distinct()
 
@@
 "the green banana"), `r round(window_n[[4,1]],2) * 100`\% at the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
 
 <!-- TR: TO ADD: LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE-->
+<!-- SC: I have added the number of unique meas. specs but we might want to discuss this. -->
 
 ## Statistical analysis
+
 Second, this multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the choice of predictor and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
 
+<!-- TODO: list co-occurring predictors -->
 On average, models included `r round(predictor_n,2)` different predictors (counting only conceptually different predictors), i.e.
@@
 On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
-
-<!-- TR: TO ADD: TO ADD: LOOK AT MODELS AND COUNT UNIQUE MODELS.-->
+Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
 
 ## Review ratings
+
 Teams reviewed each other analyses for both the acoustic analysis and the statistical analysis. 

### 2022-09-05 RR_manuscript/results_notes.Rmd
♻️ - edit between-team variability section

@@
 
-```{r, 'load-meta-analysis'}
-
+```{r load-meta-analysis}
 meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))
@@
 compelling_count <- table(post_meta$compelling)
-
 ```
@@
 <!-- TODO: discuss between-team variability -->
+<!-- TODO: This is more like between-model variability -->
+
+As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e.
+the standard deviation of the group-level effect of team `(!!!
+we have now model_id)` returned by the meta-analytic model.
+
+According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% confidence.
+This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
+We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.
+
+<!-- TODO: Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->
 
@@
 - We have not investigated researcher positionality, which is known to be an important factor.
+- Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did).
 

### 2022-09-06 RR_manuscript/results_notes.Rmd
edited discussion

@@
 
-Of the submitted teams, teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
+Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
 Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e.
@@
 
-Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating that analysts had an overall rather high prior plausibility of the hypothesis (scale ranged from 0 to 100).
+Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating that analysts had an overall rather high prior plausibility of the investigated relationship between prosody and typicality (scale ranged from 0 to 100).
 
@@
 On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
-analytic approaches widely varied along the following dimensions:
-First, teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, the concrete operationalization of how they measured said acoustic properties.
+Crucially, analytic approaches widely varied in how they acoustically analysed the speech signal and how the statistically analysed the extracted values.
 
 ## Acoustic analysis 
-
+Teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, and the concrete operationalization of how they measured those acoustic properties.
 `r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.
+<!-- TR: Do we want to list some of them?-->
 
@@
 
-<!-- TR: TO ADD: LOOK AT OPERATIONALIZATIONS AND SEE HOW MANY UNIQUE MEASUREMENTS SPECIFICATIONS WERE DONE-->
 <!-- SC: I have added the number of unique meas. specs but we might want to discuss this. -->
+<!-- TR: How did you do this?-->
 
@@
 
-Second, this multiverse of measurement choices is exponentiated with choices during the statistical analysis, including the choice of predictor and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
+The multiverse of acoustic measurement choices is exponentiated with choices during the statistical analysis, including the predictors and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
 
-<!-- TODO: list co-occurring predictors -->
-On average, models included `r round(predictor_n,2)` different predictors (counting only conceptually different predictors), i.e.
+On average, models included `r round(predictor_n,1)` different predictors (counting only conceptually different predictors), i.e.
 in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
-Predictors included LIST CO-OCCURING IVS...
+Predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or gender of the speaker.
 
@@
 
-The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). `r round(framework_n[[1,1]],2) * 100`\% were rooted in a Bayesian framework. 
+The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). `r round(framework_n[[1,1]],2) * 100`\% were operating in a Bayesian framework. 
 While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun. 
-The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects (REFERENCE). 
-`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all, so effectively ignoring these non-independences.
+The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects [e.g., @gelman2006data; @schielzeth2009conclusions]. 
+`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
+<!-- TODO: We need to check if these model pooled -->
 `r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
@@
 Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of `r nrow(unique_model_specs)` different model specifications. 
+<!-- TR: If done on team level did every team have a different mdoel?  -->
 
@@
 
-Teams reviewed each other analyses for both the acoustic analysis and the statistical analysis. 
+Teams reviewed each others' analyses for both the acoustic analysis and the statistical analysis. 
 The mean rating of the quality of the acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the quality of the statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
@@
 
-According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% confidence.
+According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% credibility.
 This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
@@
 The Bayesian random effects model estimates the range of probable values of the standardized effect size between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` (95\% CrI, mean = `r round(meta_intercept[1],3)`)
-In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],3)` standard deviations above zero.
-This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],3)` standard deviations higher acoustic values (e.g.
+In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],2)` standard deviations above zero.
+This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],2)` standard deviations higher acoustic values (e.g.
 duration, f0 etc,) than typical word combinations.
@@
 This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but there is also much uncertainty around this estimate and the range of probably values includes zero.
-Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not point zero to begin with. 
-Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but 
-if there is an effect of typicality, it is very small.
+Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with. 
+Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
 Moreover, this population estimate is half the size of the estimated standard deviation between different models <!-- TR: EXTRACT BETA AND CRIS).-->
+
 (ref:meta_plot1) illustrates the estimated model outputs for all submitted models according to size. 
-Note that given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
 longer duration, higher f0, etc.).
@@
 
-knitr::include_graphics(here("./plots/meta_plot1.png"))
+#knitr::include_graphics(here("./plots/meta_plot1.png"))
 
@@
 ## Can we predict the estimate?
-After assessing the variability across models, we now turn toward estimating the impact of a series of predictors the analysts model estimates 
-There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic (REF)?
+After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
+There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
 
@@
 
-The model suggests that most team-specific predictors yield very small mean estimates and 95% credibile intervals that include zero, leaving us highly uncertain about their direction. 
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytical estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
 Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
@@
 Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates. 
-This suggests that the analysts' results very much depend on the choice of predictors. 
+This suggests that the analysts' results very much depend on their choice of predictors. 
 Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. duration or f0) and the choice of temporal window affected the results. 
@@
 
-knitr::include_graphics(here("./plots/alltogether.png"))
+#knitr::include_graphics(here("./plots/alltogether.png"))
 
@@
 In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
-As shown by the results of this meta-anlyitic study, such complex process has led to a wide "garden of forking paths", i.e. to a wide range of combinations of possible analitic decisions.
-Each individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
+As shown by the results of this meta-analytic study, such complex process has led to a wide "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
+Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
 Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
@@
 Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
-These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience (REF,REF,REF).
-Given the mounting evidence, Breznau et al.
-(2021) conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many, @breznau2021observing].
+Given the mounting evidence, @breznau2021observing conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."
 Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
@@
 
+It particularly struck us that teams did not follow our instructions to only submit a single effect size. 
+Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
+Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini & Hochberg 1995).
+It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.
+2012, Simmon et al.
+2011) while null results remain unreported (Sterling 1959, REF).
+Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+
 ## Lessons for the methodological reform movement
@@
 One of the suggested paths forward is for researchers to directly replicate previous study more often [@open2015estimating; REFS, REFS].
-While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is not enough.
+While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
@@
 
-A desired outcome of knowomg that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
@@
 More recently, researchers across the cognitive sciences have also raised awareness of a general lack of detailed quantitative hypotheses, calling for establishing appropriate derivation chains and formalizing verbal expectations mathematically [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+The presented data clearly support a call of improving the link between our theoretical constructs and our quantitative predictions.
 
@@
 First of all, our sample is an opportunity sample. 
-We have advertise the project through online platforms which might lead to the exclusion of certain potential researcher groups.
-Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely too small to estimate meta-analytic estimates reliably.
+We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
+Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
 This is particularly important for the predictor evaluation.

### 2022-09-07 RR_manuscript/results_notes.Rmd
more work on discussion

@@
 in the present case how communicative pressures of functions are expressed in the acoustic signal.
-More recently, researchers across the cognitive sciences have also raised awareness of a general lack of detailed quantitative hypotheses, calling for establishing appropriate derivation chains and formalizing verbal expectations mathematically [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
-The presented data clearly support a call of improving the link between our theoretical constructs and our quantitative predictions.
+This can be achieved by formalizing verbal expectations mathematically or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
 ## Caveats
-
 Our study has several limitations that need to be considered when evaluating our results. 
-First of all, our sample is an opportunity sample. 
+First, there is potential for bias.
+The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
+This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable. 
+However, our results should be independently re-analysed and replicated using a different research question.
+Moreover, our sample is an opportunity sample. 
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
@@
 Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
+This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has].
+However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see @scheel2022most) a common phenomenon. 
+For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
+<!-- TR: still adding this? Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did). -->
+- We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->
 
-ADD
+Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.
 
-<!-- Brainstorm of ideas -->
-
-- Analytic flexibility applies to us (as principal investigators) too.
-- Research question was vague enough to possibily inflate between-team variability (REF, Hannah Fraser; although it is a typical kind of question, as found in the literature).
-We do relate analytical flexibility with underspecified hypothesis in the previous section.
-- This should be replicated with a different question/data set.
-- With this study, we can suggest that at a minimum this is the between-team variability, but need more studies like this one.
-- Generalisability to linguistics/language sciences tout-court is limited. Need to do same with other fields, like language development, historical data, sociolinguistics, etc.
-- The focus is on quantitative data analysis, so that we expect the issues raised here to apply differently or not at all to qualitative data analysis.
-- We have not investigated researcher positionality, which is known to be an important factor.
-- Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did).
+Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+Our focus was on quantitative analyses that require operationalization of a multidimensional signal.
+While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
+It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.
 

### 2022-09-07 RR_manuscript/Draft_RR.Rmd
♻️ - move results notes to draft rr

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 knitr::opts_knit$set(root.dir = here::here())
@@
 library(extraDistr)
+library(faux)
+library(tidybayes)
+library(here)
+library(googlesheets4)
 ```
@@
 ```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
-knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"))
+knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"), error = FALSE)
 ```
@@
 ```{r 'procedural', echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
-knitr::include_graphics(here::here("figs", "procedure_plot.png"))
+knitr::include_graphics(here::here("figs", "procedure_plot.png"), error = FALSE)
 ```
@@
 
+# Results
+
+```{r load-models, message=FALSE, warning=FALSE}
+msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
+  mutate(
+    outcome = as.factor(outcome),
+    typicality = as.factor(typicality),
+    temporal_window = as.factor(temporal_window)
+  ) %>%
+  droplevels() %>%
+  mutate(
+    outcome = contr_code_sum(outcome),
+    typicality = contr_code_sum(typicality),
+    temporal_window = contr_code_sum(temporal_window)
+  )
+
+# average phd experience
+phd_mean <- msa_models %>% 
+  select(team, years_from_phd) %>% 
+  distinct(team, years_from_phd) %>% 
+  summarise(mean_phd = mean(years_from_phd, na.rm = TRUE),
+            sd_phd = sd(years_from_phd, na.rm = TRUE),
+            min_phd = min(years_from_phd, na.rm = TRUE),
+            max_phd = max(years_from_phd, na.rm = TRUE))
+
+prior_mean <- msa_models %>% 
+  select(team, prior_belief) %>% 
+  distinct(team, prior_belief) %>% 
+  summarise(mean_prior = mean(prior_belief, na.rm = TRUE),
+            sd_prior = sd(prior_belief, na.rm = TRUE),
+            min_prior = min(prior_belief, na.rm = TRUE),
+            max_prior = max(prior_belief, na.rm = TRUE))
+
+# number of teams (final)
+no_teams = length(unique(msa_models$team))
+
+# Helper function to print table data easier
+split_to_list <- function(.data, ...) {
+  dots <- rlang::enquos(...)
+  for (var in seq_along(dots)) {
+    var_name <- rlang::as_name(dots[[var]])
+    .data <- purrr::map_depth(
+      .x = .data,
+      .depth = var - 1,
+      .f = function(xs) split(xs, xs[var_name])
+    )
+  }
+  .data
+}
+
+team_sheet <- "https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit?usp=sharing"
+teams <- read_sheet(team_sheet)
+
+# Get DF of all members with leader names
+team_leaders <- readr::read_csv(
+  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
+  select(ResponseId, Q6) %>% # Questions asking for team leader
+  filter(!(row_number() %in% c(1, 2))) %>% 
+  mutate(leader = Q6, 
+         leader = case_when(
+           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
+           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
+           Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
+           Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
+           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
+           Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
+           Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
+           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
+           Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
+           Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
+           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
+           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
+           TRUE ~ leader
+         )) %>% 
+  select(ResponseId, leader)
+
+# Teams on OSF
+teams_on_osf <- teams %>% 
+  filter(added_on_osf == "yes") %>% 
+  pull(coordinator)
+
+# Teams with submitted analyses
+teams_used_in_analysis <- teams %>% 
+  filter(animal %in% msa_models$animal) %>% 
+  pull(coordinator)
+
+# Team descriptives
+#  - number of teams (initially)
+#  - Avg size of each team
+team_desc_df <- bind_rows(
+  team_leaders %>% 
+    group_by(leader) %>% 
+    mutate(member_num = seq_along(ResponseId)) %>% 
+    group_by(leader) %>% 
+    mutate(n_members = max(member_num)) %>% 
+    distinct(leader, n_members) %>% 
+    ungroup() %>% 
+    summarize(n_teams = nrow(.), 
+              mean_size = mean(n_members), 
+              sd_size = sd(n_members), 
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Initial"), 
+  team_leaders %>% 
+    filter(leader %in% teams_on_osf) %>% 
+    group_by(leader) %>% 
+    mutate(member_num = seq_along(ResponseId)) %>% 
+    group_by(leader) %>% 
+    mutate(n_members = max(member_num)) %>% 
+    distinct(leader, n_members) %>% 
+    ungroup() %>% 
+    summarize(n_teams = nrow(.), 
+              mean_size = mean(n_members), 
+              sd_size = sd(n_members), 
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Submitted"), 
+  team_leaders %>% 
+    filter(leader %in% teams_used_in_analysis) %>% 
+    group_by(leader) %>% 
+    mutate(member_num = seq_along(ResponseId)) %>% 
+    group_by(leader) %>% 
+    mutate(n_members = max(member_num)) %>% 
+    distinct(leader, n_members) %>% 
+    ungroup() %>% 
+    summarize(n_teams = nrow(.), 
+              mean_size = mean(n_members), 
+              sd_size = sd(n_members), 
+              median_size = median(n_members)) %>% 
+    mutate(stage = "Final")
+  ) %>% 
+  mutate_if(is.numeric, round, digits = 2)
+
+team_desc_list <- team_desc_df %>% 
+  tidyr::pivot_longer(cols = n_teams:median_size, names_to = "metric", values_to = "val") %>% 
+  split_to_list(stage, metric)
+
+# Example usage
+# team_desc_list$Initial$n_teams$val
+
+# number of analyses
+no_analyses = nrow(msa_models)
+
+# acoustic operationalizations
+# Gross operationalization of acoustic operationalization
+unique_acou_oper <- msa_models %>%
+  unite("unique_oper", outcome, operationalisation, operationalisation_notes, na.rm = TRUE) %>%
+  count(unique_oper)
+
+# average analyses
+mean_analyses <- msa_models %>% 
+  group_by(team) %>% 
+  summarise(max_models = max(model_n)) %>% 
+  group_by() %>% 
+  summarise(mean_models = mean(max_models))
+
+# outcomes
+outcome_n <- msa_models %>% 
+  count(outcome) %>% 
+  summarise(prop = n / sum(n))
+
+# windows
+window_n <- msa_models %>% 
+  count(temporal_window) %>% 
+  summarise(prop = n / sum(n))
+
+# predictors
+predictor_n <- msa_models %>% 
+  summarise(mean_predictor = mean(n_predictors, na.rm = TRUE))
+
+# typicality op
+typicality_n <- msa_models %>% 
+  count(typicality_operationalization) %>% 
+  summarise(prop = n / sum(n))
+
+# framework
+framework_n <- msa_models %>% 
+  count(framework) %>% 
+  summarise(prop = n / sum(n))
+
+# model
+model_n <- msa_models %>% 
+  count(model) %>% 
+  summarise(prop = n / sum(n))
+
+# random
+random_n <- msa_models %>% 
+  filter(model == "linear model") %>% 
+  count(random_effects) %>% 
+  summarise(prop = n / sum(n))
+
+# random terms
+rterms_n <- msa_models %>% 
+  filter(n_random != 0) %>% 
+  summarise(mean_rterms = mean(n_random, na.rm = TRUE))
+
+# unique model specs, discarding random effects
+unique_model_specs <- msa_models %>%
+  select(framework:outcome, pop_pred) %>%
+  unnest(pop_pred) %>%
+  distinct()
+
+# review ratings
+review_mean <- msa_models %>% 
+  summarise(mean_prating = mean(phon_rating, na.rm = TRUE),
+            sd_prating = sd(phon_rating, na.rm = TRUE),
+            mean_srating = mean(stat_rating, na.rm = TRUE),
+            sd_srating = sd(stat_rating, na.rm = TRUE))
+```
+
+## Sample description
+
+In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
+
+<!-- TR: some of this or most of this should go into a nice overview table -->
+
+### Team properties
+
+`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS].
+The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
+
+Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
+Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e.
+PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
+
+```{r}
+#| label: team-descriptives-table
+#| echo: false
+#| eval: false
+team_desc_df %>% 
+  mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
+  select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
+  knitr::kable(align = c("l", "r", "r", "r"), 
+               caption = "Caption test", 
+               label = "team-descriptives-table")
+```
+
+Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating that analysts had an overall rather high prior plausibility of the investigated relationship between prosody and typicality (scale ranged from 0 to 100).
+
+The teams have submitted `r no_analyses` models to answer the research question. 
+On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
+Crucially, analytic approaches widely varied in how they acoustically analysed the speech signal and how the statistically analysed the extracted values.
+
+### Acoustic analysis
+
+Teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, and the concrete operationalization of how they measured those acoustic properties.
+`r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.
+<!-- TR: Do we want to list some of them?-->
+
+`r round(window_n[[1,1]],2) * 100`\% of models measured acoustic properties at the level of the segment (e.g.
+comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% at the level of the word (e.g.
+comparing the acoustic profile of "banana"), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g.
+the noun phrase including determiner and adjective, e.g.
+"the green banana"), `r round(window_n[[4,1]],2) * 100`\% at the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
+
+<!-- SC: I have added the number of unique meas. specs but we might want to discuss this. -->
+<!-- TR: How did you do this?-->
+
+### Statistical analysis
+
+The multiverse of acoustic measurement choices is exponentiated with choices during the statistical analysis, including the predictors and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
+
+On average, models included `r round(predictor_n,1)` different predictors (counting only conceptually different predictors), i.e.
+in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
+Predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or gender of the speaker.
+
+The original dataset allowed to operationalize the most relevant predictor, typicality, in different ways. 
+It was operationalized as categorical (e.g.
+typical vs.
+atypical) in `r round(typicality_n[[1,1]],2) * 100`\% of models, continuous (on a scale from 0-100) with the mean typicality rating in `r round(typicality_n[[2,1]],2) * 100`\% of models, and continuous with the median typicality rating in `r round(typicality_n[[3,1]],2) * 100`\% of models.
+
+The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). `r round(framework_n[[1,1]],2) * 100`\% were operating in a Bayesian framework. 
+While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
+The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun. 
+The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects [e.g., @gelman2006data; @schielzeth2009conclusions]. 
+`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
+<!-- TODO: We need to check if these model pooled -->
+`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
+On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
+Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of `r nrow(unique_model_specs)` different model specifications. 
+<!-- TR: If done on team level did every team have a different mdoel?  -->
+
+### Review ratings
+
+Teams reviewed each others' analyses for both the acoustic analysis and the statistical analysis. 
+The mean rating of the quality of the acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the quality of the statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
+For reference, the scale of the rating anchored a point grade of 75 as "an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation", indicating a rather high confidence of reviewers that the provided analyses yield appropriate (yet "imperfect") answers to the research question.
+
+## Meta analysis
+
+```{r load-meta-analysis}
+meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))
+
+meta_intercept <- fixef(meta_bm)
+meta_random <- ranef(meta_bm)
+
+# wrangle by hand 
+post_meta <- meta_bm %>%
+  spread_draws(b_Intercept, r_model_id[model,]) %>%
+  mutate(model_mean = b_Intercept + r_model_id) %>% 
+  group_by(model) %>% 
+  dplyr::summarise(post_mean = mean(model_mean),
+            lower95 = quantile(model_mean, probs = .025),
+            higher95 = quantile(model_mean, probs = .975)
+            ) %>% 
+  # this basically needs to be fed by whether or not the authors considered there to be an effect
+  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
+                                          higher95 < 0 ~ "positive",
+                                          TRUE ~ "not compelling")))
+
+compelling_results <- post_meta %>% 
+  count(compelling) %>% 
+  summarise(prop = n / sum(n))
+
+compelling_count <- table(post_meta$compelling)
+```
+
+### Between-team variability
+
+<!-- TODO: discuss between-team variability -->
+<!-- TODO: This is more like between-model variability -->
+
+As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e.
+the standard deviation of the group-level effect of team `(!!!
+we have now model_id)` returned by the meta-analytic model.
+
+According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% credibility.
+This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
+We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.
+
+<!-- TODO: Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->
+
+### Estimating the crowd sourced effect size
+
+The Bayesian random effects model estimates the range of probable values of the standardized effect size between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` (95\% CrI, mean = `r round(meta_intercept[1],3)`)
+In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],2)` standard deviations above zero.
+This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],2)` standard deviations higher acoustic values (e.g.
+duration, f0 etc,) than typical word combinations.
+
+<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).-->
+
+This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but there is also much uncertainty around this estimate and the range of probably values includes zero.
+Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with. 
+Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
+Moreover, this population estimate is half the size of the estimated standard deviation between different models <!-- TR: EXTRACT BETA AND CRIS).-->
+
+(ref:meta_plot1) illustrates the estimated model outputs for all submitted models according to size. 
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
+longer duration, higher f0, etc.).
+Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+
+<!-- TR: ADD PARAGRAPH ON HOW MANY CLAIMED THERE TO BE AN EFFECT.-->
+
+```{r 'plot-meta1', echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
+knitr::include_graphics(here::here("./plots/meta_plot1.png"), error = FALSE)
+```
+
+### Can we predict the estimate?
+After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
+There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
+
+(ref:meta_plot1), panel C, displays the coefficients alongside 80% and 95% credible intervals for all model predictors.
+
+<!-- TR: ADD TABLE HERE TOO?-->
+
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytical estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
+Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
+Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates. 
+This suggests that the analysts' results very much depend on their choice of predictors. 
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. duration or f0) and the choice of temporal window affected the results. 
+(ref:meta_plot1) displays the posterior estimates for the measurement outcome (i.e.
+what acoustic dimension was measured, panel A) and measurement window (i.e.
+what is the unit over which was measured, panel B).
+If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
+If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
+Similarly, if acoustic parameters were measured within individual segments (e.g.
+the vowel of the noun), estimates are lower than the meta analytic estimate, and if acoustic parameters were measured across whole phrases (e.g.
+"the blue banana"), the estimates are generally higher.
+In other words, depending on the choice of measurement, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+
+```{r 'plot-meta2', echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
+knitr::include_graphics(here::here("./plots/alltogether.png"), error = FALSE)
+```
+
+# Discussion
+
+## Summary
+
+We gave XX analyst teams the same speech dataset to answer the same research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*.
+In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
+As shown by the results of this meta-analytic study, such complex process has led to a wide "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
+Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
+Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
+The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
+Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many, @breznau2021observing].
+Given the mounting evidence, @breznau2021observing conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."
+Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
+
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices. 
+Human speech is a complex multidimensional signal.
+Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in. 
+Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
+For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
+This asymmetry can have several causes.
+First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
+Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
+@grice2017integrating; @turnbull2017role].
+Third, ADD REASONS. 
+Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
+
+It particularly struck us that teams did not follow our instructions to only submit a single effect size. 
+Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
+Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini & Hochberg 1995).
+It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.
+2012, Simmon et al.
+2011) while null results remain unreported (Sterling 1959, REF).
+Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+
+## Lessons for the methodological reform movement
+
+The current results point to important barriers for successful accumulation of knowledge.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
+One of the suggested paths forward is for researchers to directly replicate previous study more often [@open2015estimating; REFS, REFS].
+While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
+There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
+Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
+
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+<!-- TODO: add ref to "process and statistical model" in McElreath -->
+We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
+
+In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+This enables critical evaluation and robustness checks by other fellow researchers (REF).
+Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
+<!-- TODO: cite Praat, EMU, MFA, Formant tracking etc -->
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., CITE Praat, EMU CITE)]].
+
+ADD
+
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Crowd-source projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
+
+Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+This approach is called "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
+Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
+Crowd-sourcing is limited by the sampled analysts and their biases.
+Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
+Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
+in the present case how communicative pressures of functions are expressed in the acoustic signal.
+This can be achieved by formalizing verbal expectations mathematically or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+
+## Caveats
+Our study has several limitations that need to be considered when evaluating our results. 
+First, there is potential for bias.
+The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
+This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable. 
+However, our results should be independently re-analysed and replicated using a different research question.
+Moreover, our sample is an opportunity sample. 
+We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
+Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
+This is particularly important for the predictor evaluation.
+Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
+This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has].
+However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see @scheel2022most) a common phenomenon. 
+For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
+<!-- TR: still adding this? Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did). -->
+- We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->
+
+Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.
+
+Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+Our focus was on quantitative analyses that require operationalization of a multidimensional signal.
+While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
+It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.
+
+# Conclusion
+
 # Author contributions

### 2022-09-07 RR_manuscript/Draft_RR.tex
♻️ - move results notes to draft rr

@@
 They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted \citep{simmons2011false}.
-Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set \citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik2020variability}.
+Recent projects have shown that the variability between different data analysts is vast and can lead independent researchers to draw different conclusions from the same data set \citep[e.g.,][]{silberzahn2018many, starns2019assessing, botvinik-nezer2020}.
 These studies, however, might still underestimate the extent to which analysts vary because data analysis is not restricted to the statistical analysis of ready-made numeric data.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
+\includegraphics[width=1\linewidth]{../figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
 (A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{/Users/timoroettger/Research/ManySpeechAnalyses/many_analyses/figs/procedure_plot} \caption{Experimental procedure.
+\includegraphics[width=1\linewidth]{../figs/procedure_plot} \caption{Experimental procedure.
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{sample-description}{%
+\subsection{Sample description}\label{sample-description}}
+
+In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
+
+\hypertarget{team-properties}{%
+\subsubsection{Team properties}\label{team-properties}}
+
+Eighty-Four teams initially signed up to participate.
+Fifty-Four of the proposed teams dropped out of the project during the analysis phase\footnote{ADD REASONS}.
+The remaining 30 teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
+
+Submitting teams consisted of an average of 3.63 analysts (sd = 2.8).
+Analysts had on average 4.8 years (sd = 4.2) post PhD experience, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
+
+Analysts prior belief in the effect under investigation ranged from 48.5 to 92 with an average of 69.2 (sd = 11.3), indicating that analysts had an overall rather high prior plausibility of the investigated relationship between prosody and typicality (scale ranged from 0 to 100).
+
+The teams have submitted 170 models to answer the research question.
+On average, teams submitted 3.6 models.
+Crucially, analytic approaches widely varied in how they acoustically analysed the speech signal and how the statistically analysed the extracted values.
+
+\hypertarget{acoustic-analysis}{%
+\subsubsection{Acoustic analysis}\label{acoustic-analysis}}
+
+Teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, and the concrete operationalization of how they measured those acoustic properties.
+33\% of models used a duration measure as the outcome variable, 36\% used a f0 measure, 15\% used a formant measure, 14\% used an intensity measure, and 3\% used a different measure.
+
+45\% of models measured acoustic properties at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% at the level of the word (e.g.~comparing the acoustic profile of ``banana''), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% at the level of the whole sentence, and 5\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
+
+\hypertarget{statistical-analysis}{%
+\subsubsection{Statistical analysis}\label{statistical-analysis}}
+
+The multiverse of acoustic measurement choices is exponentiated with choices during the statistical analysis, including the predictors and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
+
+On average, models included 1.9 different predictors (counting only conceptually different predictors), i.e.~in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
+Predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or gender of the speaker.
+
+The original dataset allowed to operationalize the most relevant predictor, typicality, in different ways.
+It was operationalized as categorical (e.g.~typical vs.~atypical) in 78\% of models, continuous (on a scale from 0-100) with the mean typicality rating in 19\% of models, and continuous with the median typicality rating in 1\% of models.
+
+The majority of models were rooted in the frequentist framework (80\%). 20\% were operating in a Bayesian framework.
+While teams almost exclusively used linear models to analyze their data (98\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
+The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
+The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
+7\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+64\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
+On average, teams that specified random effects, included 2.4 random terms in their models.
+Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 45 different model specifications.
+
+\hypertarget{review-ratings}{%
+\subsubsection{Review ratings}\label{review-ratings}}
+
+Teams reviewed each others' analyses for both the acoustic analysis and the statistical analysis.
+The mean rating of the quality of the acoustic analyses was 74.6 (sd = 11.1); the mean rating of the quality of the statistical analysis was 73.9 (sd = 14.1).
+For reference, the scale of the rating anchored a point grade of 75 as ``an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation'', indicating a rather high confidence of reviewers that the provided analyses yield appropriate (yet ``imperfect'') answers to the research question.
+
+\hypertarget{meta-analysis}{%
+\subsection{Meta analysis}\label{meta-analysis}}
+
+\begin{verbatim}
+## Warning: `gather_()` was deprecated in tidyr 1.2.0.
+## Please use `gather()` instead.
+## This warning is displayed once every 8 hours.
+## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
+\end{verbatim}
+
+\hypertarget{between-team-variability}{%
+\subsubsection{Between-team variability}\label{between-team-variability}}
+
+As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team \texttt{(!!!\ we\ have\ now\ model\_id)} returned by the meta-analytic model.
+
+According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95\% credibility.
+This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
+We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.
+
+\hypertarget{estimating-the-crowd-sourced-effect-size}{%
+\subsubsection{Estimating the crowd sourced effect size}\label{estimating-the-crowd-sourced-effect-size}}
+
+The Bayesian random effects model estimates the range of probable values of the standardized effect size between -0.01 and 0.04 (95\% CrI, mean = 0.016)
+In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is 0.02 standard deviations above zero.
+This outcome thus estimates that atypical word combinations have 0.02 standard deviations higher acoustic values (e.g.~duration, f0 etc,) than typical word combinations.
+
+This is not only an extremely small effect , but there is also much uncertainty around this estimate and the range of probably values includes zero.
+Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with.
+Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
+Moreover, this population estimate is half the size of the estimated standard deviation between different models
+
+(ref:meta\_plot1) illustrates the estimated model outputs for all submitted models according to size.
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.).
+Notably, while the majority of models yielded inconclusive results, there are 28 model estimates for which the 95\% credible interval does not contain zero (16\%).
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../plots/meta_plot1} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
+\end{figure}
+
+\hypertarget{can-we-predict-the-estimate}{%
+\subsubsection{Can we predict the estimate?}\label{can-we-predict-the-estimate}}
+
+After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
+There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?
+
+(ref:meta\_plot1), panel C, displays the coefficients alongside 80\% and 95\% credible intervals for all model predictors.
+
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytical estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
+Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI).
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates.
+This suggests that the analysts' results very much depend on their choice of predictors.
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~duration or f0) and the choice of temporal window affected the results.
+(ref:meta\_plot1) displays the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which was measured, panel B).
+If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
+If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
+Similarly, if acoustic parameters were measured within individual segments (e.g.~the vowel of the noun), estimates are lower than the meta analytic estimate, and if acoustic parameters were measured across whole phrases (e.g.~``the blue banana''), the estimates are generally higher.
+In other words, depending on the choice of measurement, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{../plots/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
+\end{figure}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{summary}{%
+\subsection{Summary}\label{summary}}
+
+We gave XX analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
+In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
+As shown by the results of this meta-analytic study, such complex process has led to a wide ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
+Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
+Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
+The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
+Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
+Given the mounting evidence, \citet{breznau2021observing} conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''
+Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
+
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices.
+Human speech is a complex multidimensional signal.
+Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in.
+Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
+For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
+This asymmetry can have several causes.
+First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
+Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Third, ADD REASONS.
+Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
+
+It particularly struck us that teams did not follow our instructions to only submit a single effect size.
+Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
+Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini \& Hochberg 1995).
+It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.~2012, Simmon et al.~2011) while null results remain unreported (Sterling 1959, REF).
+Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+
+\hypertarget{lessons-for-the-methodological-reform-movement}{%
+\subsection{Lessons for the methodological reform movement}\label{lessons-for-the-methodological-reform-movement}}
+
+The current results point to important barriers for successful accumulation of knowledge.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
+One of the suggested paths forward is for researchers to directly replicate previous study more often {[}\citet{open2015estimating}; REFS, REFS{]}.
+While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
+There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
+Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.
+
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
+
+In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+This enables critical evaluation and robustness checks by other fellow researchers (REF).
+Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process {[}e.g., CITE Praat, EMU CITE){]}{]}.
+
+ADD
+
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Crowd-source projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
+
+Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+This approach is called ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
+Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
+Crowd-sourcing is limited by the sampled analysts and their biases.
+Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
+Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
+This can be achieved by formalizing verbal expectations mathematically or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+
+\hypertarget{caveats}{%
+\subsection{Caveats}\label{caveats}}
+
+Our study has several limitations that need to be considered when evaluating our results.
+First, there is potential for bias.
+The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
+This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom.
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable.
+However, our results should be independently re-analysed and replicated using a different research question.
+Moreover, our sample is an opportunity sample.
+We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
+Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
+This is particularly important for the predictor evaluation.
+Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
+However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see \citet{scheel2022most}) a common phenomenon.
+For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
+- We have not investigated researcher positionality, which is known to be an important factor.
+
+Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.
+
+Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+Our focus was on quantitative analyses that require operationalization of a multidimensional signal.
+While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
+It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
 \hypertarget{author-contributions}{%

### 2022-09-07 RR_manuscript/Draft_RR.Rmd
♻️ - merge latest changes from timo

@@
 Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini & Hochberg 1995).
-It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.
-2012, Simmon et al.
-2011) while null results remain unreported (Sterling 1959, REF).
-Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [Tukey 1953, @benjamini1995controlling].
+<!-- TR: couldnt find bibtex of tukey: Tukey, J. W. (1953). The problem of multiple comparisons. Multiple comparisons. -->
+It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
 
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
-One of the suggested paths forward is for researchers to directly replicate previous study more often [@open2015estimating; REFS, REFS].
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., REFERENCE].
+One of the suggested paths forward is for researchers to directly replicate previous study more often [e.g., @open2015estimating; @camerer2018evaluating].
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
+The quantitative sciences are in an inference crisis [@rotello2015more; @starns2019assessing].
+Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
@@
 In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
-First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
+It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018). 
+It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
 This enables critical evaluation and robustness checks by other fellow researchers (REF).

### 2022-09-07 RR_manuscript/results_notes.Rmd

@@
 Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini & Hochberg 1995).
-It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.
-2012, Simmon et al.
-2011) while null results remain unreported (Sterling 1959, REF).
-Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [Tukey 1953, @benjamini1995controlling]
+<!-- TR: couldnt find bibtex of tukey: Tukey, J. W. (1953). The problem of multiple comparisons. Multiple comparisons. -->
+It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
 
 ## Lessons for the methodological reform movement
-
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
-One of the suggested paths forward is for researchers to directly replicate previous study more often [@open2015estimating; REFS, REFS].
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., REFERENCE].
+One of the suggested paths forward is for researchers to directly replicate previous study more often [e.g., @open2015estimating; @camerer2018evaluating].
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
+The quantitative sciences are in an inference crisis [@rotello2015more; @starns2019assessing].
+Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
@@
 In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
-First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
+It furtherenables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018). 
+It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
+
 This enables critical evaluation and robustness checks by other fellow researchers (REF).

### 2022-09-08 RR_manuscript/Draft_RR.Rmd
♻️ - edit results in draft

@@
 
-## Sample description
+## Descriptive statistics
 
@@
 
-## Meta analysis
+## Meta-analytic estimation
+
+<!-- TODO: add background info and use consistent terminology -->
+This section deals with the meta-analytic analysis of the results submitted by the teams.
+We first report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
 
 ```{r load-meta-analysis}
+# Preregistered ----
+meta_bm_prereg <- readRDS(here("./data/meta_analysis/meta_bm_prereg.rds"))
+
+meta_intercept_prereg <- fixef(meta_bm_prereg)
+meta_random_prereg <- ranef(meta_bm_prereg)
+
+# wrangle by hand 
+post_meta_prereg <- meta_bm_prereg %>%
+  spread_draws(b_Intercept, r_animal[team,]) %>%
+  mutate(team_mean = b_Intercept + r_animal) %>% 
+  group_by(team) %>% 
+  dplyr::summarise(post_mean = mean(team_mean),
+            lower95 = quantile(team_mean, probs = .025),
+            higher95 = quantile(team_mean, probs = .975)
+            ) %>% 
+  # this basically needs to be fed by whether or not the authors considered there to be an effect
+  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
+                                          higher95 < 0 ~ "positive",
+                                          TRUE ~ "not compelling")))
+
+compelling_results_prereg <- post_meta_prereg %>% 
+  count(compelling) %>% 
+  summarise(prop = n / sum(n))
+
+compelling_count_prereg <- table(post_meta_prereg$compelling)
+
+# Model ID ----
+
 meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))
@@
 compelling_count <- table(post_meta$compelling)
+
+# Nested ----
+
+meta_bm_nest <- readRDS(here("./data/meta_analysis/meta_bm_nest.rds"))
+
+meta_intercept_nest <- fixef(meta_bm_nest)
+meta_random_nest <- ranef(meta_bm_nest)
+
+# wrangle by hand 
+post_meta_nest <- meta_bm_nest %>%
+  spread_draws(b_Intercept, `r_animal:model_id`[model,]) %>%
+  mutate(model_mean = b_Intercept + `r_animal:model_id`) %>% 
+  group_by(model) %>% 
+  dplyr::summarise(post_mean = mean(model_mean),
+            lower95 = quantile(model_mean, probs = .025),
+            higher95 = quantile(model_mean, probs = .975)
+            ) %>% 
+  # this basically needs to be fed by whether or not the authors considered there to be an effect
+  mutate(compelling = as.factor(case_when(lower95 > 0 ~ "negative",
+                                          higher95 < 0 ~ "positive",
+                                          TRUE ~ "not compelling")))
+
+compelling_results_nest <- post_meta_nest %>% 
+  count(compelling) %>% 
+  summarise(prop = n / sum(n))
+
+compelling_count_nest <- table(post_meta_nest$compelling)
 ```
@@
 ### Between-team variability
-
-<!-- TODO: discuss between-team variability -->
-<!-- TODO: This is more like between-model variability -->
 
@@
 As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e.
-the standard deviation of the group-level effect of team `(!!!
-we have now model_id)` returned by the meta-analytic model.
-
-According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95% credibility.
-This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
-We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.
+the standard deviation of the group-level effect of team returned by the meta-analytic model.
+
+According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.
+
+**Non-preregistered**. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
+We have run two further non-preregistered meta-analytic models:
+
+1. A model with model ID instead of team as the group-level effect (`(1|model_id)`).
+2. A model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`).
+
+Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95% credibility.
+This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
+
+As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
+On the other hand, the posterior 95% CrI for team in the second non-preregistered model is 0-0.05 standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+
+We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.
 
@@
 
-### Estimating the crowd sourced effect size
-
-The Bayesian random effects model estimates the range of probable values of the standardized effect size between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` (95\% CrI, mean = `r round(meta_intercept[1],3)`)
-In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is `r round(meta_intercept[1],2)` standard deviations above zero.
-This outcome thus estimates that atypical word combinations have `r round(meta_intercept[1],2)` standard deviations higher acoustic values (e.g.
-duration, f0 etc,) than typical word combinations.
-
-<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES (ALTERNATIVELY IN IQ VALUES).-->
-
-This is not only an extremely small effect <!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->, but there is also much uncertainty around this estimate and the range of probably values includes zero.
-Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with. 
-Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
-Moreover, this population estimate is half the size of the estimated standard deviation between different models <!-- TR: EXTRACT BETA AND CRIS).-->
-
-(ref:meta_plot1) illustrates the estimated model outputs for all submitted models according to size. 
-Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.
-longer duration, higher f0, etc.).
-Notably, while the majority of models yielded inconclusive results, there are `r compelling_count[[1]] + compelling_count[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results[[1,1]] + compelling_results[[3,1]]), 2) * 100`\%).
+### Meta-analytic intercept
+
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
+In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.
+duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+
+<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES, like we do with team variability (ALTERNATIVELY IN IQ VALUES).-->
+
+<!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->
+
+**Non-preregistered**. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
+In the first model, the meta-analytic intercept estimate is between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept[1],3)`).
+This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
+Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
+The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).
+
+(ref:meta_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
+longer duration, higher f0, etc.), as mentioned above.
+Notably, while the majority of models yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
 
@@
 
-```{r 'plot-meta1', echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
-knitr::include_graphics(here::here("./plots/meta_plot1.png"), error = FALSE)
+```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
+knitr::include_graphics(here::here("./figs/meta_plot1_nest.png"), error = FALSE)
 ```
 
-### Can we predict the estimate?
-After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
+## Analytic and researcher-related predictors
+
+After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
 There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
@@
 
-```{r 'plot-meta2', echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
-knitr::include_graphics(here::here("./plots/alltogether.png"), error = FALSE)
+```{r plot-meta2, echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
+knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
 ```
@@
 ## Caveats
+
 Our study has several limitations that need to be considered when evaluating our results. 

### 2022-09-08 RR_manuscript/Draft_RR.tex
♻️ - edit results in draft

@@
 
-\hypertarget{sample-description}{%
-\subsection{Sample description}\label{sample-description}}
+\hypertarget{descriptive-statistics-1}{%
+\subsection{Descriptive statistics}\label{descriptive-statistics-1}}
 
@@
 
-\hypertarget{meta-analysis}{%
-\subsection{Meta analysis}\label{meta-analysis}}
+\hypertarget{meta-analytic-estimation}{%
+\subsection{Meta-analytic estimation}\label{meta-analytic-estimation}}
 
-\begin{verbatim}
-## Warning: `gather_()` was deprecated in tidyr 1.2.0.
-## Please use `gather()` instead.
-## This warning is displayed once every 8 hours.
-## Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
-\end{verbatim}
+This section deals with the meta-analytic analysis of the results submitted by the teams.
+We first report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
 
@@
 As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team \texttt{(!!!\ we\ have\ now\ model\_id)} returned by the meta-analytic model.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.
 
-According to the meta-analytic model, the group-level standard deviation is between 0.11 and 0.15 standard units, at 95\% credibility.
-This means that the deviations of any individual model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
-We illustrate what this means in actual acoustic measures by means of examples, taking the mean sample standard deviation of each measure from the sample data.
+According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95\% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.
 
-\hypertarget{estimating-the-crowd-sourced-effect-size}{%
-\subsubsection{Estimating the crowd sourced effect size}\label{estimating-the-crowd-sourced-effect-size}}
+\textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
+We have run two further non-preregistered meta-analytic models:
 
-The Bayesian random effects model estimates the range of probable values of the standardized effect size between -0.01 and 0.04 (95\% CrI, mean = 0.016)
-In other words, if we were to assume that there is a true underlying effect of typicality and we consider each analysis randomly drawn from a population of possible analysis attempts, our best guess about the underlying effect is that it is 0.02 standard deviations above zero.
-This outcome thus estimates that atypical word combinations have 0.02 standard deviations higher acoustic values (e.g.~duration, f0 etc,) than typical word combinations.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  A model with model ID instead of team as the group-level effect (\texttt{(1\textbar{}model\_id)}).
+\item
+  A model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}).
+\end{enumerate}
 
-This is not only an extremely small effect , but there is also much uncertainty around this estimate and the range of probably values includes zero.
-Thus, given the data, the model, and our prior assumptions, we cannot be very certain that there actually is an effect that is not zero to begin with.
-Since we do not know the true value of the underlying effect, we cannot conclude anything from this finding, but if there is an effect of typicality, it is very small.
-Moreover, this population estimate is half the size of the estimated standard deviation between different models
+Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95\% credibility.
+This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
 
-(ref:meta\_plot1) illustrates the estimated model outputs for all submitted models according to size.
-Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to atypical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.).
-Notably, while the majority of models yielded inconclusive results, there are 28 model estimates for which the 95\% credible interval does not contain zero (16\%).
+As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
+On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0-0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+
+We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.
+
+\hypertarget{meta-analytic-intercept}{%
+\subsubsection{Meta-analytic intercept}\label{meta-analytic-intercept}}
+
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.022 and 0.023 standard units (95\% CrI, mean = 0.001).
+In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.~duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+
+\textbf{Non-preregistered}. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
+In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.016).
+This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
+Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
+The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).
+
+(ref:meta\_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
+Notably, while the majority of models yields inconclusive results, there are 25 model estimates for which the 95\% credible interval does not contain zero (15\%).
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../plots/meta_plot1} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_nest} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
 \end{figure}
 
-\hypertarget{can-we-predict-the-estimate}{%
-\subsubsection{Can we predict the estimate?}\label{can-we-predict-the-estimate}}
+\hypertarget{analytic-and-researcher-related-predictors}{%
+\subsection{Analytic and researcher-related predictors}\label{analytic-and-researcher-related-predictors}}
 
-After assessing the variability across models, we now turn toward estimating the impact of a series of predictors on the analysts' model estimates.
+After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
 There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../plots/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
+\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
 \end{figure}
@@
 Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for (Tukey 1954, Benjamini \& Hochberg 1995).
-It also invites bias, leading to the selective reporting of those tests that yield a desirable outcome (Kerr 1998, John et al.~2012, Simmon et al.~2011) while null results remain unreported (Sterling 1959, REF).
-Our data suggest that fields that use highly complex raw data such as speech should be particularly cautious when analyzing their data.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
+It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
 
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature (REFS).
-One of the suggested paths forward is for researchers to directly replicate previous study more often {[}\citet{open2015estimating}; REFS, REFS{]}.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature {[}e.g., REFERENCE{]}.
+One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Well-trained and experienced speech researchers in this study not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as the peer-ratings suggest.
+The quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
+Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.
@@
 In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
-First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others (REF).
+First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
+It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018).
+It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
 This enables critical evaluation and robustness checks by other fellow researchers (REF).

### 2022-09-09 scripts/r/04_refit/refit_tr.Rmd
fixed typo
Use here for paths to avoid copy/pasting millions of lines of code

@@
 library(readxl)
+library(lme4)
 
@@
 
-path <- "./data/analyses/tr/trachyphyllia_lappa"
+path <- here("data", "analyses", "tr", "trachyphyllia_lappa")
 
@@
 
-MSA_combined <- readRDS("./data/analyses/tr/alosa_atun/alosa_atun_data.rds", refhook = NULL)
+MSA_combined <- readRDS(here("data", "analyses", "tr", "alosa_atun", "alosa_atun_data.rds"), refhook = NULL)
 
@@
 
-data = read.csv("./data/analyses/tr/pervagor_meeki/Data/ManySpeech_Praat_merged_data.csv", header=T)
+data = read.csv(here("data", "analyses", "tr", "pervagor_meeki", "Data", "ManySpeech_Praat_merged_data.csv"), header=T)
 
@@
 
-path <- "./data/analyses/tr/dunkleosteus_inscriptus/data/"
-
-flist_times  <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^timings(.*)xlsx")
+path <- here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data/")
+
+flist_times  <- list.files(path = here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data"), pattern = "^timings(.*)xlsx")
 get_times    <- lapply(paste0(path, flist_times), read_excel)
@@
 
-flist_trials <- list.files(path = "./data/analyses/tr/dunkleosteus_inscriptus/data/", pattern = "^trials(.*)xlsx")
+flist_trials <- list.files(path = here("data", "analyses", "tr", "dunkleosteus_inscriptus", "data"), pattern = "^trials(.*)xlsx")
 get_trials   <- lapply(paste0(path, flist_trials), read_excel)
@@
 dunkleosteus_inscriptus_5_npdur_cat <- brm(
-  dur_a_s ~ 
+  dur_np_s ~ 
          effect_cat + 
@@
 #################
-d <- read_delim("./data/analyses/tr/chelonia_brummeri/analysis/german_msa_prosody.txt", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
-syll <- read_csv("./data/analyses/tr/chelonia_brummeri/analysis/syllables.csv")
+d <- read_delim(here("data", "analyses", "tr", "chelonia_brummeri", "analysis", "german_msa_prosody.txt"), delim = "\t", escape_double = FALSE, trim_ws = TRUE)
+syll <- read_csv(here("data", "analyses", "tr", "chelonia_brummeri", "analysis", "syllables.csv"))
 
@@
 # read csv
-msa_data_raw <- read_csv("./data/analyses/tr/procambarus_mahogoni/MSA-data.csv")
+msa_data_raw <- read_csv(here("data", "analyses", "tr", "procambarus_mahogoni", "MSA-data.csv"))
 

### 2022-09-09 scripts/r/07_team-sds.Rmd
Get means/sds and put them in a pretty csv

---
title: "Extract team means and SDs"
author: "Joseph V. Casillas"
output: 
  html_document: 
    toc: yes
    toc_depth: 1
    number_sections: yes
date: "Last update: `r Sys.Date()`"
---

```{r}
#| label: setup
#| include: false

# Knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE)

# Load libs
library("here")
library("tidyr")
library("dplyr")
library("osfr")
library("speakr")
library("glue")
library("googlesheets4")
library("forcats")
library("readr")
library("readxl")
library("brms")
library("lme4")
library("purrr")

```

# Overview

The purpose of this script is to extract the mean and standard deviation of every dependent variable (if it is f0, duration, or intensity) from each team included in the meta-analysis (`05_meta-analyses.Rmd`). 
Most of the code needed to accomplish this is already written, thus the script recycles already completed work and, where necessary, we use a few helpers to reduce work. 
The workflow is the following:

1. Get a list of the subset of teams that need to be downloaded (Max = 30 because the final model only includes 30 teams). 
2. Download the OSF components of the aforementioned subset of teams.
3. Use the code found in `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`) to get the final data frames used in the original analyses. 
4. Calculate mean/SD of the raw DVs (only f0, duration, and intensity). 
5. Store means/SDs in a separate .csv file in `data/analyses`.

# List of teams

```{r}
#| label: get-teams
#| message: false
#| warning: false

# Get team names from final meta-analytic model
teams <- readRDS(here("./data/analyses/msa_models.rds")) %>% 
  pull(animal) %>% 
  unique

# Get coding excel from google drive
assigned <- read_sheet("https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing")

# Use teams to subset excel file with all analyses, get those that include f0, 
# duration, and intensity
final_teams <- assigned %>% 
  filter(animal %in% teams, outcome %in% c("f0", "duration", "intensity"), 
         exclude == "no")

# Just the names
final_team_names <- final_teams %>% 
  pull(animal) %>% 
  unique

# Create dataframe (lookup table) with final teams names and the assigned coder 
final_team_name_and_coder <- final_teams %>% 
  select(animal, assigned_to) %>% 
  distinct()
```

Of the 30 teams included in the meta-analysis, `r length(final_team_names)` included either F0, duration or intensity in the analyses. 
Next, we download the OSF components of those `r length(final_team_names)` teams.

# Download OSF team components

```{r}
#| label: download-setup
#| eval: false

# Get OSF team components
osf_teams <- osf_retrieve_node("n3fyd")
teams_comps <- osf_ls_nodes(osf_teams, n_max = Inf)

# Function to download team components
#  - only those in final analysis
#  - only those including F0, pitch, duration
#  - separate by coder and put components in coder-specific directories
download_components <- function(coder) {
  # Get vector of team names by coder assignment
  my_assignment <- filter(final_team_name_and_coder, assigned_to == coder) %>% 
    pull(animal)

  # Loop through teams in my_assignment and download the corresponding OSF comp
  # to /data/analyses/{coder}
  for (team in 1:length(my_assignment)) {
    skip_to_next <- FALSE

    name <- my_assignment[team]
    dir.create(glue("./data/analyses/{coder}/{name}"), 
               recursive = TRUE, showWarnings = FALSE)

    tryCatch(
      osf_ls_files(teams_comps[team,], type = "folder") %>%
        osf_download(
          path = glue("./data/analyses/{coder}/{name}"),
            recurse = TRUE, verbose = TRUE, progress = TRUE, conflicts = "skip"
          ),
      error = function(e) {skip_to_next <<- TRUE}
    )

    if(skip_to_next) { next }
  }
}
```

```{r}
#| label: download-components
#| eval: false

# Download JVC
download_components(coder = "jvc")

# Download SC
download_components(coder = "sc")

# Download TR
download_components(coder = "tr")
```

# Get means and SDs

In order to get the data frame from each teams analysis, we will recycle code from `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`). 
We can pull in specific lines of code with the `source_part` function. 
If we can't source the lines directly without touching the refit_xx.Rmd files (because *some* people refuse to use `here`), then we will have to copy/paste code to this file and adjusts the paths like heathens.

```{r}
#| label: source-part
source_part <- function(file, start, end, ...) {
  # Set lines
  file.lines <- scan(
    file, 
    what = character(), 
    skip = start - 1, 
    nlines = end - start + 1, 
    sep = '\n'
    )
  # Collapse lines
  file.lines.collapsed <- paste(file.lines, collapse = '\n')
  # Source selection
  source(textConnection(file.lines.collapsed), ...)
}
```

We have the following number of OSF components for each coder:

```{r}
#| label: breakdown-by-coder
final_team_name_and_coder %>% 
  group_by(assigned_to) %>% 
  summarize(n = n_distinct(animal)) %>% 
  knitr::kable()
```

## JVC

```{r}
#| label: jvc-teams
#| echo: false
#| results: 'asis'
final_team_name_and_coder %>% 
  filter(assigned_to == "jvc") %>% 
  select(animal) %>% 
  arrange(animal) %>% 
  mutate(animal = glue("- {animal}")) %>% 
  pull

```

### anomalocaris_ornata

```{r}
#| label: anomalocaris_ornata
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 131, 
  end = 181
  )

# Means and SDs
anomalocaris_ornata_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anomalocaris_ornata", 1, "intensity", mean(df.int$Mean_dB^2),        sd(df.int$Mean_dB^2), 
  "anomalocaris_ornata", 2, "f0",        mean(under$f0sem),             sd(under$f0sem), 
  "anomalocaris_ornata", 3, "f0",        mean(over$f0sem),              sd(over$f0sem), 
  "anomalocaris_ornata", 4, "duration",  mean(vowel.df$Duration_in_ms), sd(vowel.df$Duration_in_ms)
)

# Check n models == n DVs
final_teams %>% filter(animal == "anomalocaris_ornata") %>% nrow == nrow(anomalocaris_ornata_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "anomalocaris_ornata") %>% pull(outcome) == anomalocaris_ornata_df %>% pull(dv)
```

### anthracoceros_coronata

```{r}
#| label: anthracoceros_coronata
#| eval: true

data_long <- read_csv(here("data", "analyses", "jvc", "anthracoceros_coronata", 
  "data", "data_from_tgs.csv")) %>% 
  mutate(A_dur_log = log(A_end - A_start), 
         N_dur_log = log(N_end - N_start))

# Means and SDs
anthracoceros_coronata_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "anthracoceros_coronata", 1, "f0",        mean(data_long$A_max_pitch),  sd(data_long$A_max_pitch), 
  "anthracoceros_coronata", 2, "f0",        mean(data_long$N_max_pitch, na.rm = T),  sd(data_long$N_max_pitch, na.rm = T), 
  "anthracoceros_coronata", 3, "intensity", mean(data_long$A_max_intens), sd(data_long$A_max_intens), 
  "anthracoceros_coronata", 4, "intensity", mean(data_long$N_max_intens), sd(data_long$N_max_intens), 
  "anthracoceros_coronata", 5, "duration",  mean(data_long$A_dur_log),    sd(data_long$A_dur_log), 
  "anthracoceros_coronata", 6, "duration",  mean(data_long$N_dur_log),    sd(data_long$N_dur_log), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "anthracoceros_coronata") %>% nrow == nrow(anthracoceros_coronata_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "anthracoceros_coronata") %>% pull(outcome) == anthracoceros_coronata_df %>% pull(dv)
```

### arapaima_modularis

```{r}
#| label: arapaima_modularis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 392, 
  end = 441
  )

# Means and SDs
arapaima_modularis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "arapaima_modularis", 1, "f0", mean(data_for_analysis_noOL$mean_pitch), sd(data_for_analysis_noOL$mean_pitch)
)

# Check n models == n DVs
final_teams %>% filter(animal == "arapaima_modularis") %>% nrow == nrow(arapaima_modularis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "arapaima_modularis") %>% pull(outcome) == arapaima_modularis_df %>% pull(dv)
```

### clione_dorsalis

```{r}
#| label: clione_dorsalis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1379, 
  end = 1395
  )

# Means and SDs
clione_dorsalis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "clione_dorsalis", 1, "duration", mean(data_formant_midpoint$word.duration), sd(data_formant_midpoint$word.duration)
)

# Check n models == n DVs
final_teams %>% filter(animal == "clione_dorsalis") %>% nrow == nrow(clione_dorsalis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "clione_dorsalis") %>% pull(outcome) == clione_dorsalis_df %>% pull(dv)
```

### comanthina_maculatus

```{r}
#| label: comanthina_maculatus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 478, 
  end = 489
  )

# Means and SDs
comanthina_maculatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "comanthina_maculatus", 1, "duration", mean(MSA_comanthina_maculatus_df$tonic_vowel_duration), sd(MSA_comanthina_maculatus_df$tonic_vowel_duration), 
  "comanthina_maculatus", 2, "intensity", mean(MSA_comanthina_maculatus_df$tonic_vowel_intensity), sd(MSA_comanthina_maculatus_df$tonic_vowel_intensity),  
  "comanthina_maculatus", 3, "f0", mean(MSA_comanthina_maculatus_df$tonic_vowel_F0), sd(MSA_comanthina_maculatus_df$tonic_vowel_F0), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "comanthina_maculatus") %>% nrow == nrow(comanthina_maculatus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "comanthina_maculatus") %>% pull(outcome) == comanthina_maculatus_df %>% pull(dv)
```

### cromileptes_saxatilis

```{r}
#| label: cromileptes_saxatilis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 527, 
  end = 530
  )

# Means and SDs
cromileptes_saxatilis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "cromileptes_saxatilis", 1, "duration", mean(cromileptes_saxatilis_durs$colour_dur), sd(cromileptes_saxatilis_durs$colour_dur)
)

# Check n models == n DVs
final_teams %>% filter(animal == "cromileptes_saxatilis") %>% nrow == nrow(cromileptes_saxatilis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "cromileptes_saxatilis") %>% pull(outcome) == cromileptes_saxatilis_df %>% pull(dv)
```

### gnathosaurus_canadensis

```{r}
#| label: gnathosaurus_canadensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 602, 
  end = 606
  )

# Means and SDs
gnathosaurus_canadensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gnathosaurus_canadensis", 1, "f0", mean(gnathosaurus_canadensis_typ$median_st_diff), sd(gnathosaurus_canadensis_typ$median_st_diff)
)

# Check n models == n DVs
final_teams %>% filter(animal == "gnathosaurus_canadensis") %>% nrow == nrow(gnathosaurus_canadensis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "gnathosaurus_canadensis") %>% pull(outcome) == gnathosaurus_canadensis_df %>% pull(dv)
```

### gymnothorax_spinulosus

```{r}
#| label: gymnothorax_spinulosus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 644, 
  end = 662
  )

# Means and SDs
gymnothorax_spinulosus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "gymnothorax_spinulosus", 1, "intensity", mean(gymnothorax_spinulosus_int$measure), sd(gymnothorax_spinulosus_int$measure)
)

# Check n models == n DVs
final_teams %>% filter(animal == "gymnothorax_spinulosus") %>% nrow == nrow(gymnothorax_spinulosus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "gymnothorax_spinulosus") %>% pull(outcome) == gymnothorax_spinulosus_df %>% pull(dv)
```

### haematopus_fossor

```{r}
#| label: haematopus_fossor
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 714, 
  end = 845
  )

# Means and SDs
haematopus_fossor_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "haematopus_fossor", 1, "duration", mean(duration_full$framedur), sd(duration_full$framedur), 
  "haematopus_fossor", 2, "duration", mean(duration_full$adjdur), sd(duration_full$adjdur), 
  "haematopus_fossor", 3, "duration", mean(duration_full$noundur), sd(duration_full$noundur), 
  "haematopus_fossor", 4, "duration", mean(adj_full$duration), sd(adj_full$duration), 
  "haematopus_fossor", 5, "duration", mean(noun_full$duration), sd(noun_full$duration), 
  "haematopus_fossor", 6, "intensity", mean(adj_full$intensity), sd(adj_full$intensity), 
  "haematopus_fossor", 7, "intensity", mean(noun_full$intensity), sd(noun_full$intensity), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "haematopus_fossor") %>% nrow == nrow(haematopus_fossor_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "haematopus_fossor") %>% pull(outcome) == haematopus_fossor_df %>% pull(dv)
```

### lasionycteris_altavela

```{r}
#| label: lasionycteris_altavela
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 955, 
  end = 962
  )

# Means and SDs
lasionycteris_altavela_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "lasionycteris_altavela", 1, "intensity", mean(intensity_DF$Intensity), sd(intensity_DF$Intensity),
)

# Check n models == n DVs
final_teams %>% filter(animal == "lasionycteris_altavela") %>% nrow == nrow(lasionycteris_altavela_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "lasionycteris_altavela") %>% pull(outcome) == lasionycteris_altavela_df %>% pull(dv)
```

### naso_cassivellaunos

```{r}
#| label: naso_cassivellaunos
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1054, 
  end = 1067
  )

# Means and SDs
naso_cassivellaunos_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "naso_cassivellaunos", 1, "f0", mean(msa$DeltaF0_rel), sd(msa$DeltaF0_rel), 
  "naso_cassivellaunos", 2, "f0", mean(msa$sync_rel), sd(msa$sync_rel),
)

# Check n models == n DVs
final_teams %>% filter(animal == "naso_cassivellaunos") %>% nrow == nrow(naso_cassivellaunos_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "naso_cassivellaunos") %>% pull(outcome) == naso_cassivellaunos_df %>% pull(dv)
```

### psittacula_scabriculus

```{r}
#| label: psittacula_scabriculus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1295, 
  end = 1327
  )

# Means and SDs
psittacula_scabriculus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "psittacula_scabriculus", 1, "duration", mean(MSAcomplete$avgdur), sd(MSAcomplete$avgdur), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "psittacula_scabriculus") %>% nrow == nrow(psittacula_scabriculus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "psittacula_scabriculus") %>% pull(outcome) == psittacula_scabriculus_df %>% pull(dv)
```

### trapezia_cantonensis

```{r}
#| label: trapezia_cantonensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1206, 
  end = 1214
  )

# Means and SDs
trapezia_cantonensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trapezia_cantonensis", 1, "duration", mean(MSA_trapezia_cantonensis_data$dur), sd(MSA_trapezia_cantonensis_data$dur), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "trapezia_cantonensis") %>% nrow == nrow(trapezia_cantonensis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "trapezia_cantonensis") %>% pull(outcome) == trapezia_cantonensis_df %>% pull(dv)
```

## SC

```{r}
#| label: sc-teams
#| echo: false
#| results: 'asis'
final_team_name_and_coder %>% 
  filter(assigned_to == "sc") %>% 
  select(animal) %>% 
  arrange(animal) %>% 
  mutate(animal = glue("- {animal}")) %>% 
  pull
```

### dermatolepis_aculeatus

```{r}
#| label: dermatolepis_aculeatus
#| eval: true

# This part won't work because some coders refuse to use `here`
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = 21, 
#  end = 32
#  )

msa_data <- read_csv(here("data", "analyses", "sc", "dermatolepis_aculeatus", 
  "Many Speech Analyses_measurements.csv")) %>%
  filter(exclude == "N", condition == "NF") %>%
  drop_na()

# Means and SDs
dermatolepis_aculeatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dermatolepis_aculeatus", 1, "f0", mean(msa_data$noun_pitch_max), sd(msa_data$noun_pitch_max), 
  "dermatolepis_aculeatus", 2, "f0", mean(msa_data$adj_pitch_max), sd(msa_data$adj_pitch_max), 
  "dermatolepis_aculeatus", 3, "f0", mean(msa_data$phrase_pitch_max), sd(msa_data$phrase_pitch_max), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "dermatolepis_aculeatus") %>% nrow == nrow(dermatolepis_aculeatus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "dermatolepis_aculeatus") %>% pull(outcome) == dermatolepis_aculeatus_df %>% pull(dv)
```

### eriphia_laterispinis

```{r}
#| label: eriphia_laterispinis
#| eval: true

# Can't source code because of path issues
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = 77, 
#  end = 88
#  )

# listing all available csv files (30 participants in the production study)
trials_files <- list.files(
    path = here("data", "osf", "production", "trial-lists/"),
    pattern = ".csv", full.names = TRUE
    )

# importing and reshaping all csv files at once
trials <- map_dfr(
    .x = trials_files,
    .f = read.csv
    )

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
msa_data <- read.csv(here("data", "analyses", "sc", "eriphia_laterispinis", 
    "processed_data", "summary_data.csv")) %>%
  filter(Condition == "NF") %>%
  left_join(x = ., y = trials, by = c("speaker", "trial") ) %>%
  select(speaker, trial, condition, mean_f0, mean_int, duration, typicality, 
    typ_mean, typ_sd, typ_median) %>%
  filter(typicality != "medium")

# Means and SDs
eriphia_laterispinis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "eriphia_laterispinis", 1, "f0",        mean(msa_data$mean_f0), sd(msa_data$mean_f0), 
  "eriphia_laterispinis", 2, "intensity", mean(msa_data$mean_int), sd(msa_data$mean_int), 
  "eriphia_laterispinis", 3, "duration",  mean(msa_data$duration), sd(msa_data$duration), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "eriphia_laterispinis") %>% nrow == nrow(eriphia_laterispinis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "eriphia_laterispinis") %>% pull(outcome) == eriphia_laterispinis_df %>% pull(dv)
```

### hoplostethus_macrosteus

```{r}
#| label: hoplostethus_macrosteus
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

msa_data <- read_csv(here("data", "analyses", "sc", "hoplostethus_macrosteus", 
    "Analysis materials", "Results_clean.csv")) %>%
  mutate(
    effect_cat = factor(typicality, levels = c("atypical", "medium", "typical")),
    color = factor(color)
  )

# Means and SDs
hoplostethus_macrosteus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "hoplostethus_macrosteus", 1, "duration",  mean(msa_data$durmsec), sd(msa_data$durmsec), 
  "hoplostethus_macrosteus", 2, "intensity", mean(msa_data$intensity_maximum), sd(msa_data$intensity_maximum), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "hoplostethus_macrosteus") %>% nrow == nrow(hoplostethus_macrosteus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "hoplostethus_macrosteus") %>% pull(outcome) == hoplostethus_macrosteus_df %>% pull(dv)
```

### neosilurus_omanensis

```{r}
#| label: neosilurus_omanensis
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

msa_data <- read_csv(here("data", "analyses", "sc", "neosilurus_omanensis", 
    "annotated_cleaned_data_v7.csv")) %>% 
  drop_na()

# Means and SDs
neosilurus_omanensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "neosilurus_omanensis", 1, "f0", mean(msa_data$PitchRatioAtoU), sd(msa_data$PitchRatioAtoU), 
  "neosilurus_omanensis", 2, "f0", mean(msa_data$PitchRangeRatioAtoU), sd(msa_data$PitchRangeRatioAtoU), 
  "neosilurus_omanensis", 4, "f0", mean(msa_data$PitchRiseRatio), sd(msa_data$PitchRiseRatio), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "neosilurus_omanensis") %>% nrow == nrow(neosilurus_omanensis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "neosilurus_omanensis") %>% pull(outcome) == neosilurus_omanensis_df %>% pull(dv)
```

### nestor_idahoensis

```{r}
#| label: nestor_idahoensis
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

msa_data <- read_csv(here("data", "analyses", "sc", "nestor_idahoensis", 
    "msa_data_v2.csv"), na = c("", "--undefined--")) %>%
  mutate(
    f0 = log(f0) %>% as.numeric(),
    duration = log(duration) %>% as.numeric(),
    f15 = log(f15) %>% as.numeric(),
    f25 = log(f25) %>% as.numeric()
  )

# Means and SDs
nestor_idahoensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "nestor_idahoensis", 1, "duration", mean(msa_data$duration), sd(msa_data$duration), 
  "nestor_idahoensis", 2, "f0",       mean(msa_data$f0), sd(msa_data$f0), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "nestor_idahoensis") %>% nrow == nrow(nestor_idahoensis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "nestor_idahoensis") %>% pull(outcome) == nestor_idahoensis_df %>% pull(dv)
```

### paralichthys_undulatus

```{r}
#| label: paralichthys_undulatus
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

msa_data <- read_delim(here("data", "analyses", "sc", "paralichthys_undulatus", 
    "Data files", "MSA-measurements.txt"), delim = "\t")

# Means and SDs
paralichthys_undulatus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "paralichthys_undulatus", 1, "f0", mean(msa_data$RangeST), sd(msa_data$RangeST), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "paralichthys_undulatus") %>% nrow == nrow(paralichthys_undulatus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "paralichthys_undulatus") %>% pull(outcome) == paralichthys_undulatus_df %>% pull(dv)
```

### petauroides_fistulator

```{r}
#| label: petauroides_fistulator
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

load(here("data", "analyses", "sc", "petauroides_fistulator", "mdl_data.RData"))

msa_data <- mdl_data %>% drop_na()

# Means and SDs
petauroides_fistulator_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "petauroides_fistulator", 1, "f0", mean(msa_data$pitch_st), sd(msa_data$pitch_st), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "petauroides_fistulator") %>% nrow == nrow(petauroides_fistulator_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "petauroides_fistulator") %>% pull(outcome) == petauroides_fistulator_df %>% pull(dv)
```

### saron_pictus

```{r}
#| label: saron_pictus
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

# Super long because somebody refuses to use `here` and I don't want to modify `refit_sc.Rmd`
# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
trial_dat <- list.files(path = here("data", "osf", "production", "trial-lists"),
                       pattern = "*.csv",
                       full.names = TRUE) %>%
  lapply(read_csv) %>%                              
  bind_rows

# Reading in the results file output by the Praat script
d <- read.delim(here("data", "analyses", "sc", "saron_pictus", "results.txt"),
                fileEncoding = "UTF-16")

# Saving original number of rows
N <- nrow(d)

# Getting rid of columns we won't need from trial_dat
trial_dat <- trial_dat[trial_dat$condition == "NF",]

# Changing the trial_dat colours to the inflected forms to match the utterances
trial_dat$target_colour[trial_dat$target_colour == "gelb"] <- "gelben"
trial_dat$target_colour[trial_dat$target_colour == "orange"] <- "orangen"
trial_dat$target_colour[trial_dat$target_colour == "braun"] <- "braunen"
trial_dat$target_colour[trial_dat$target_colour == "rot"] <- "roten"
trial_dat$target_colour[trial_dat$target_colour == "gruen"] <- "gruenen"

# Saving the target colours present in the data-set into a vector
colours <- c("gelben", "orangen", "braunen", "roten", "gruenen")

# Subsetting to only target nouns and adjectives
d <- d[d$word_label %in% trial_dat$target_name | d$word_label %in% trial_dat$target_colour,]
d <- droplevels(d)

# Merging the data from Praat with the trial data
d <- merge(d, trial_dat, 
            by = c("speaker", "trial", "condition"))

# Lumping all trial problems together
d$trial_status <- ifelse(d$notes == "", "Good", "Bad")

# Creating a column specifying whether a word is an adjective or noun
d$word_class <- ifelse(d$word_label %in% colours, "adjective", "noun")

# Creating a column with duration in milliseconds instead of seconds
d$dur_ms <- d$word_duration*1000

# Transforming trial to have a max value of 1
d$trial_minmax <- (d$trial - min(d$trial)) / (max(d$trial) - min(d$trial))

# Creating a data-set that is only adjectives
adj <- d[d$word_class == "adjective",]

# Removing trials with problems
adj <- adj[adj$notes == "",]
adj$effect_cat <- factor(adj$typicality,
                         levels = c("atypical", "medium", "typical"))

msa_data <- adj %>% drop_na()

# Means and SDs
saron_pictus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "saron_pictus", 1, "duration", mean(msa_data$dur_ms), sd(msa_data$dur_ms), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "saron_pictus") %>% nrow == nrow(saron_pictus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "saron_pictus") %>% pull(outcome) == saron_pictus_df %>% pull(dv)
```

### trachurus_riukiuensis

```{r}
#| label: trachurus_riukiuensis
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

#Read in output file from Praat script
msa <- read.delim(here("data", "analyses", "sc", "trachurus_riukiuensis", 
  "MSA-Praat-output.txt"), na.strings = "--undefined--")

#Read in list of NF trials (this is an edited version of one of the trial-lists on OSF)
triallist <- read.csv(here("data", "analyses", "sc", "trachurus_riukiuensis", 
  "MSA-triallist.csv"))

#Merge them together
msa2 <- merge(msa, triallist, by=c("noun","condition"))
#Adjust factor
msa2$comment <- as.factor(msa2$comment)
#Remove errors (31/900) and hesitation utterances (20/900) ~ 6% of data removed
data <- subset(msa2, comment=="NA" | comment=="noise")

#Remove JW_3; too many errors and hesitations
data <- subset(data, participant!="JW_3")

#Adjust typicality variable as dummy coded factor
data$effect_cat <- factor(data$typicality, levels = c("atypical", "medium", "typical"))

#Calculate a by participant median for each f0 measure and the median absolute deviation
#See Leys, C., Ley, C., Klein, O., Bernard, P., & Licata, L. (2013). Detecting outliers: Do not use standard deviation around the mean, use absolute deviation around the median. Journal of Experimental Social Psychology, 49(4), 764-766.
by.participant.median <- data %>%
  group_by(participant) %>%
  dplyr::summarise( n.mad = mad(noun_peakf0), n.median = median(noun_peakf0),
             adj.mad = mad(adj_peakf0), adj.median = median(adj_peakf0),
             art.mad = mad(art_peakf0), art.median = median(art_peakf0),)

#Merge by participant with full data
data.mm <- merge(by.participant.median, data)

#Create new dataframes for each f0 measure by removing less than 2.5 times median absolute deviation
noun <- subset(data.mm, noun_peakf0 > n.median-(2.5*n.mad))
#noun peak f0 removed 28 data points

adjective <- subset(data.mm, adj_peakf0 > adj.median-(2.5*adj.mad))
#adj peak f0 removed 14 data points

article <- subset(data.mm, art_peakf0 > art.median-(2*art.mad))
#art peak f0 removed 160 data points NOTE we use 2 times median absolute deviation to remove all creaky voice tokens

# Means and SDs
trachurus_riukiuensis_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachurus_riukiuensis", 1, "duration", mean(data$art_dur), sd(data$art_dur),
  "trachurus_riukiuensis", 2, "f0", mean(article$art_peakf0), sd(article$art_peakf0),
  "trachurus_riukiuensis", 3, "duration", mean(data$adj_dur), sd(data$adj_dur), 
  "trachurus_riukiuensis", 4, "f0", mean(adjective$adj_peakf0), sd(adjective$adj_peakf0),
  "trachurus_riukiuensis", 5, "f0", mean(noun$noun_peakf0), sd(noun$noun_peakf0),
)

# Check n models == n DVs
final_teams %>% filter(animal == "trachurus_riukiuensis") %>% nrow == nrow(trachurus_riukiuensis_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "trachurus_riukiuensis") %>% pull(outcome) == trachurus_riukiuensis_df %>% pull(dv)
```

### varanus_eulophotes

```{r}
#| label: varanus_eulophotes
#| eval: true

# Importing manually because `refit_sc.Rmd` overwrites original DVs with std DVs
# source_part(
#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
#  start = , 
#  end = 
#  )

# reading in data
f0data <- read.csv(here("data", "analyses", "sc", "varanus_eulophotes", 
    "analysis", "f0data-complete.csv"), header = T)

# new dataframe with only typicality-rated data
f0data_cor <- f0data[f0data$typicality !="NA" & !is.na(f0data$typicality),]
f0data_cor$avgF0 <- as.numeric(f0data_cor$avgF0) # coercing types...
f0data_cor$effect_cat <- factor(f0data_cor$typicality, levels = c("atypical", "medium", "typical"))
msa_data <- f0data_cor

# Means and SDs
varanus_eulophotes_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "varanus_eulophotes", 1, "f0", mean(msa_data$avgF0), sd(msa_data$avgF0), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "varanus_eulophotes") %>% nrow == nrow(varanus_eulophotes_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "varanus_eulophotes") %>% pull(outcome) == varanus_eulophotes_df %>% pull(dv)
```

## TR

```{r}
#| label: tr-teams
#| echo: false
#| results: 'asis'
final_team_name_and_coder %>% 
  filter(assigned_to == "tr") %>% 
  select(animal) %>% 
  arrange(animal) %>% 
  mutate(animal = glue("- {animal}")) %>% 
  pull
```

### alosa_atun

```{r}
#| label: alosa_atun
#| eval: true
#| message: false
#| warning: false
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 353, 
  end = 507
  )

# Means and SDs
alosa_atun_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "alosa_atun", 1,  "f0",        mean(MSA_finale$meanPitch), sd(MSA_finale$meanPitch), 
  "alosa_atun", 2,  "intensity", mean(MSA_finale$maxIntensity), sd(MSA_finale$maxIntensity), 
  "alosa_atun", 3,  "duration",  mean(MSA_finale$Target.segment.duration), sd(MSA_finale$Target.segment.duration), 
  "alosa_atun", 6,  "f0",        mean(MSA_finalschwa$meanPitch), sd(MSA_finalschwa$meanPitch), 
  "alosa_atun", 7,  "intensity", mean(MSA_finalschwa$maxIntensity), sd(MSA_finalschwa$maxIntensity), 
  "alosa_atun", 8,  "duration",  mean(MSA_finalschwa$Target.segment.duration), sd(MSA_finalschwa$Target.segment.duration), 
  "alosa_atun", 11, "duration",  mean(MSA_both$DiphDur), sd(MSA_both$DiphDur), 
  "alosa_atun", 12, "duration",  mean(MSA_both$DurRat), sd(MSA_both$DurRat), 
  "alosa_atun", 14, "duration",  mean(MSA_finale$Target.word.duration), sd(MSA_finale$Target.word.duration), 
  "alosa_atun", 15, "duration",  mean(MSA_finale$Pause.duration, na.rm = T), sd(MSA_finale$Pause.duration, na.rm = T), 
  "alosa_atun", 16, "duration",  mean(MSA_both$syllablesPerMinute), sd(MSA_both$syllablesPerMinute), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "alosa_atun") %>% nrow == nrow(alosa_atun_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "alosa_atun") %>% pull(outcome) == alosa_atun_df %>% pull(dv)
```

### chelonia_brummeri

```{r}
#| label: chelonia_brummeri
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1532, 
  end = 1601
  )

# Means and SDs
chelonia_brummeri_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "chelonia_brummeri", 1,  "duration",  mean(d$rel_dur), sd(d$rel_dur), 
  "chelonia_brummeri", 2,  "intensity", mean(d$rel_intens), sd(d$rel_intens), 
  "chelonia_brummeri", 3,  "f0",        mean(d$f0range_st), sd(d$f0range_st), 
  "chelonia_brummeri", 4,  "f0",        mean(d$adj_maxf0), sd(d$adj_maxf0), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "chelonia_brummeri") %>% nrow == nrow(chelonia_brummeri_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "chelonia_brummeri") %>% pull(outcome) == chelonia_brummeri_df %>% pull(dv)
```

### dunkleosteus_inscriptus

```{r}
#| label: dunkleosteus_inscriptus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1309, 
  end = 1420
  )

# Means and SDs
dunkleosteus_inscriptus_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "dunkleosteus_inscriptus", 1,  "duration", mean(dat$rel_n), sd(dat$rel_n), 
  "dunkleosteus_inscriptus", 2,  "duration", mean(dat$dur_n), sd(dat$dur_n), 
  "dunkleosteus_inscriptus", 3,  "duration", mean(dat$rel_a), sd(dat$rel_a), 
  "dunkleosteus_inscriptus", 4,  "duration", mean(dat$dur_a), sd(dat$dur_a), 
  "dunkleosteus_inscriptus", 5,  "duration", mean(dat$dur_np), sd(dat$dur_np),
)

# Check n models == n DVs
final_teams %>% filter(animal == "dunkleosteus_inscriptus") %>% nrow == nrow(dunkleosteus_inscriptus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "dunkleosteus_inscriptus") %>% pull(outcome) == dunkleosteus_inscriptus_df %>% pull(dv)
```

### pervagor_meeki

```{r}
#| label: pervagor_meeki
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 896, 
  end = 949
  )

# Means and SDs
pervagor_meeki_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "pervagor_meeki", 1,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), 
  "pervagor_meeki", 2,  "duration", mean(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_name",]$Duration_ms), 
  "pervagor_meeki", 3,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_name",]$Mean_f0_st), 
  "pervagor_meeki", 4,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_name",]$Max_f0_st), 
  "pervagor_meeki", 5,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_colour",]$Overall_Intensity), 
  "pervagor_meeki", 6,  "duration",  mean(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms), sd(data_dur_trim[data_dur_trim$word_type == "target_colour",]$Duration_ms),
  "pervagor_meeki", 7,  "f0", mean(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st), sd(data_meanf0_trim[data_meanf0_trim$word_type == "target_colour",]$Mean_f0_st),
  "pervagor_meeki", 8,  "f0", mean(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st), sd(data_maxf0_trim[data_maxf0_trim$word_type == "target_colour",]$Max_f0_st),
)

# Check n models == n DVs
final_teams %>% filter(animal == "pervagor_meeki") %>% nrow == nrow(pervagor_meeki_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "pervagor_meeki") %>% pull(outcome) == pervagor_meeki_df %>% pull(dv)
```

### procambarus_mahogoni

```{r}
#| label: procambarus_mahogoni
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1742, 
  end = 1745
  )

# Means and SDs
procambarus_mahogoni_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "procambarus_mahogoni", 1,  "duration",  mean(msa_data_raw$v1_duration_c), sd(msa_data_raw$v1_duration_c), 
  "procambarus_mahogoni", 2,  "f0",        mean(msa_data_raw$v1_pitch_mean_c), sd(msa_data_raw$v1_pitch_mean_c), 
  "procambarus_mahogoni", 3,  "intensity", mean(msa_data_raw$v1_int_mean_c), sd(msa_data_raw$v1_int_mean_c), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "procambarus_mahogoni") %>% nrow == nrow(procambarus_mahogoni_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "procambarus_mahogoni") %>% pull(outcome) == procambarus_mahogoni_df %>% pull(dv)
```

### trachyphyllia_lappa

```{r}
#| label: trachyphyllia_lappa
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 49, 
  end = 134
  )

duration_adj_data <- durations %>% filter(word == 9) %>% mutate(type = "adjective")
duration_noun_data <- durations %>% filter(word == 10) %>% mutate(type = "noun")
pitch_adj_data <- pitchfile %>% filter(word == 9) %>% mutate(type = "adjective")
pitch_noun_data <- pitchfile %>% filter(word == 10) %>% mutate(type = "noun")

# Means and SDs
trachyphyllia_lappa_df <- tribble(
  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "trachyphyllia_lappa", 1,  "duration", mean(duration_adj_data$duration), sd(duration_adj_data$duration), 
  "trachyphyllia_lappa", 2,  "f0",       mean(pitch_adj_data$maximum), sd(pitch_adj_data$maximum), 
  "trachyphyllia_lappa", 3,  "f0", mean(pitch_adj_data$minimum), sd(pitch_adj_data$minimum), 
  "trachyphyllia_lappa", 4,  "f0", mean(pitch_adj_data$range), sd(pitch_adj_data$range), 
  "trachyphyllia_lappa", 5,  "duration", mean(duration_noun_data$duration), sd(duration_noun_data$duration), 
  "trachyphyllia_lappa", 6,  "f0", mean(pitch_noun_data$maximum), sd(pitch_noun_data$maximum), 
  "trachyphyllia_lappa", 7,  "f0", mean(pitch_noun_data$minimum), sd(pitch_noun_data$minimum), 
  "trachyphyllia_lappa", 8,  "f0", mean(pitch_noun_data$range), sd(pitch_noun_data$range), 
)

# Check n models == n DVs
final_teams %>% filter(animal == "trachyphyllia_lappa") %>% nrow == nrow(trachyphyllia_lappa_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "trachyphyllia_lappa") %>% pull(outcome) == trachyphyllia_lappa_df %>% pull(dv)
```

# Build table

```{r}
#| label: build-tibble

# Comnine tibbles 
msa_mean_sd_df <- bind_rows(
  anomalocaris_ornata_df, 
  anthracoceros_coronata_df, 
  arapaima_modularis_df, 
  clione_dorsalis_df, 
  comanthina_maculatus_df, 
  cromileptes_saxatilis_df, 
  gnathosaurus_canadensis_df, 
  gymnothorax_spinulosus_df, 
  haematopus_fossor_df, 
  lasionycteris_altavela_df, 
  naso_cassivellaunos_df, 
  psittacula_scabriculus_df, 
  trapezia_cantonensis_df, 
  dermatolepis_aculeatus_df, 
  eriphia_laterispinis_df, 
  hoplostethus_macrosteus_df, 
  neosilurus_omanensis_df, 
  nestor_idahoensis_df, 
  paralichthys_undulatus_df, 
  petauroides_fistulator_df, 
  saron_pictus_df, 
  trachurus_riukiuensis_df, 
  varanus_eulophotes_df, 
  alosa_atun_df, 
  chelonia_brummeri_df, 
  dunkleosteus_inscriptus_df, 
  pervagor_meeki_df, 
  procambarus_mahogoni_df, 
  trachyphyllia_lappa_df
)

# Save as .csv
if(F) {
write_csv(msa_mean_sd_df, here("data", "analyses", "msa_mean_sd_df.csv"))
}

# Print to html for funsies
msa_mean_sd_df %>% 
  knitr::kable()
```

### 2022-09-09 scripts/r/07_team-sds.Rmd
join df with relevant data from vars from google sheet

@@
 # Knitr options
-knitr::opts_chunk$set(echo = TRUE, message = FALSE)
+knitr::opts_chunk$set(
+  echo = TRUE, 
+  message = FALSE
+  )
+
+knitr::opts_knit$set(root.dir = here::here())
 
@@
 anomalocaris_ornata_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
-  "anomalocaris_ornata", 1, "intensity", mean(df.int$Mean_dB^2),        sd(df.int$Mean_dB^2), 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "anomalocaris_ornata", 1, "intensity", mean(df.int$Mean_dB),        sd(df.int$Mean_dB), 
   "anomalocaris_ornata", 2, "f0",        mean(under$f0sem),             sd(under$f0sem), 
@@
 anthracoceros_coronata_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "anthracoceros_coronata", 1, "f0",        mean(data_long$A_max_pitch),  sd(data_long$A_max_pitch), 
@@
 arapaima_modularis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "arapaima_modularis", 1, "f0", mean(data_for_analysis_noOL$mean_pitch), sd(data_for_analysis_noOL$mean_pitch)
@@
 clione_dorsalis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "clione_dorsalis", 1, "duration", mean(data_formant_midpoint$word.duration), sd(data_formant_midpoint$word.duration)
@@
 comanthina_maculatus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "comanthina_maculatus", 1, "duration", mean(MSA_comanthina_maculatus_df$tonic_vowel_duration), sd(MSA_comanthina_maculatus_df$tonic_vowel_duration), 
@@
 cromileptes_saxatilis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "cromileptes_saxatilis", 1, "duration", mean(cromileptes_saxatilis_durs$colour_dur), sd(cromileptes_saxatilis_durs$colour_dur)
@@
 gnathosaurus_canadensis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "gnathosaurus_canadensis", 1, "f0", mean(gnathosaurus_canadensis_typ$median_st_diff), sd(gnathosaurus_canadensis_typ$median_st_diff)
@@
 gymnothorax_spinulosus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "gymnothorax_spinulosus", 1, "intensity", mean(gymnothorax_spinulosus_int$measure), sd(gymnothorax_spinulosus_int$measure)
@@
 haematopus_fossor_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "haematopus_fossor", 1, "duration", mean(duration_full$framedur), sd(duration_full$framedur), 
@@
 lasionycteris_altavela_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "lasionycteris_altavela", 1, "intensity", mean(intensity_DF$Intensity), sd(intensity_DF$Intensity),
@@
 naso_cassivellaunos_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
-  "naso_cassivellaunos", 1, "f0", mean(msa$DeltaF0_rel), sd(msa$DeltaF0_rel), 
-  "naso_cassivellaunos", 2, "f0", mean(msa$sync_rel), sd(msa$sync_rel),
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "naso_cassivellaunos", 2, "f0", mean(msa$DeltaF0_rel), sd(msa$DeltaF0_rel), 
+  "naso_cassivellaunos", 3, "f0", mean(msa$sync_rel), sd(msa$sync_rel),
 )
@@
 psittacula_scabriculus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "psittacula_scabriculus", 1, "duration", mean(MSAcomplete$avgdur), sd(MSAcomplete$avgdur), 
@@
 trapezia_cantonensis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
-  "trapezia_cantonensis", 1, "duration", mean(MSA_trapezia_cantonensis_data$dur), sd(MSA_trapezia_cantonensis_data$dur), 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "trapezia_cantonensis", 4, "duration", mean(MSA_trapezia_cantonensis_data$dur), sd(MSA_trapezia_cantonensis_data$dur), 
 )
@@
 
-# This part won't work because some coders refuse to use `here`
-# source_part(
-#  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
-#  start = 21, 
-#  end = 32
-#  )
+source_part(
+ file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
+ start = 21, 
+ end = 32
+)
 
@@
 dermatolepis_aculeatus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "dermatolepis_aculeatus", 1, "f0", mean(msa_data$noun_pitch_max), sd(msa_data$noun_pitch_max), 
@@
 eriphia_laterispinis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "eriphia_laterispinis", 1, "f0",        mean(msa_data$mean_f0), sd(msa_data$mean_f0), 
-  "eriphia_laterispinis", 2, "intensity", mean(msa_data$mean_int), sd(msa_data$mean_int), 
-  "eriphia_laterispinis", 3, "duration",  mean(msa_data$duration), sd(msa_data$duration), 
+  "eriphia_laterispinis", 1, "intensity", mean(msa_data$mean_int), sd(msa_data$mean_int), 
+  "eriphia_laterispinis", 1, "duration",  mean(msa_data$duration), sd(msa_data$duration), 
 )
@@
 hoplostethus_macrosteus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "hoplostethus_macrosteus", 1, "duration",  mean(msa_data$durmsec), sd(msa_data$durmsec), 
@@
 neosilurus_omanensis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "neosilurus_omanensis", 1, "f0", mean(msa_data$PitchRatioAtoU), sd(msa_data$PitchRatioAtoU), 
@@
 nestor_idahoensis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "nestor_idahoensis", 1, "duration", mean(msa_data$duration), sd(msa_data$duration), 
-  "nestor_idahoensis", 2, "f0",       mean(msa_data$f0), sd(msa_data$f0), 
+  "nestor_idahoensis", 1, "f0",       mean(msa_data$f0), sd(msa_data$f0), 
 )
@@
 paralichthys_undulatus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "paralichthys_undulatus", 1, "f0", mean(msa_data$RangeST), sd(msa_data$RangeST), 
@@
 petauroides_fistulator_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "petauroides_fistulator", 1, "f0", mean(msa_data$pitch_st), sd(msa_data$pitch_st), 
@@
 saron_pictus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "saron_pictus", 1, "duration", mean(msa_data$dur_ms), sd(msa_data$dur_ms), 
@@
 trachurus_riukiuensis_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "trachurus_riukiuensis", 1, "duration", mean(data$art_dur), sd(data$art_dur),
@@
 varanus_eulophotes_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "varanus_eulophotes", 1, "f0", mean(msa_data$avgF0), sd(msa_data$avgF0), 
@@
 alosa_atun_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "alosa_atun", 1,  "f0",        mean(MSA_finale$meanPitch), sd(MSA_finale$meanPitch), 
@@
 chelonia_brummeri_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "chelonia_brummeri", 1,  "duration",  mean(d$rel_dur), sd(d$rel_dur), 
@@
 dunkleosteus_inscriptus_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "dunkleosteus_inscriptus", 1,  "duration", mean(dat$rel_n), sd(dat$rel_n), 
@@
 pervagor_meeki_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "pervagor_meeki", 1,  "intensity", mean(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), sd(data_int_trim[data_int_trim$word_type == "target_name",]$Overall_Intensity), 
@@
 procambarus_mahogoni_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "procambarus_mahogoni", 1,  "duration",  mean(msa_data_raw$v1_duration_c), sd(msa_data_raw$v1_duration_c), 
@@
 trachyphyllia_lappa_df <- tribble(
-  ~"team", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
   "trachyphyllia_lappa", 1,  "duration", mean(duration_adj_data$duration), sd(duration_adj_data$duration), 
@@
 # Comnine tibbles 
-msa_mean_sd_df <- bind_rows(
+msa_mean_sd <- bind_rows(
   anomalocaris_ornata_df, 
@@
 
+msa_mean_sd_df <- left_join(
+  msa_mean_sd %>% 
+    arrange(animal) %>% 
+    mutate(row_n = row_number()), 
+  assigned %>%
+    filter(
+      animal %in% teams, 
+      exclude == "no", 
+      outcome %in% c("duration", "intensity", "f0")
+    ) %>% 
+    select(animal, model_n, outcome, transformation) %>% 
+    arrange(animal) %>% 
+    mutate(row_n = row_number()), 
+  by = c("animal", "row_n")
+) %>% 
+  mutate(model_n_match = if_else(model_n.x == model_n.y, 1, 0), 
+    transformation = case_when(
+      is.na(transformation) ~ 'none', 
+      transformation == "NA" ~ 'none', 
+      TRUE ~ transformation
+    )) %>% 
+  select(animal, model_n_rda = model_n.x, model_n_excel = model_n.y, model_n_match, 
+         dv, outcome, transformation, mean, sd)
+
 # Save as .csv

### 2022-09-09 RR_manuscript/Draft_RR.Rmd
♻️ - edit descriptive results

@@
 
-# acoustic operationalizations
-# Gross operationalization of acoustic operationalization
-unique_acou_oper <- msa_models %>%
-  unite("unique_oper", outcome, operationalisation, operationalisation_notes, na.rm = TRUE) %>%
-  count(unique_oper)
-
 # average analyses
@@
 
+The results section is divided into three parts.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by the team members.
+Second, we report the results of the meta-analytic model, focussing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
+
 ## Descriptive statistics
 
-In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
+In the following sections, we will describe the characteristics of the analysis teams that participated in the study and the analytic approaches they adopted.
+An important aspect that emerges from the descriptive analysis is the large variation in analytic strategies.
 
@@
 
-### Team properties
-
-`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
-`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS].
-The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
-
-Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
-Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e.
-PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
+### Characteristics of analytic teams
 
@@
 
-Analysts prior belief in the effect under investigation ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (sd = `r round(prior_mean[[2]],1)`), indicating that analysts had an overall rather high prior plausibility of the investigated relationship between prosody and typicality (scale ranged from 0 to 100).
-
-The teams have submitted `r no_analyses` models to answer the research question. 
-On average, teams submitted `r round(mean_analyses[[1]], 1)` models. 
-Crucially, analytic approaches widely varied in how they acoustically analysed the speech signal and how the statistically analysed the extracted values.
+`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate in the study.
+<!-- TODO: Add reasons for dropping out -->
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase^[ADD REASONS].
+The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
+These are the teams that are included in this study.
+
+Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
+
+Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
+Analysts had on average `r round(phd_mean[[1]],1)` years (SD = `r round(phd_mean[[2]],1)`) of experience after completing their PhD, ranging from `r round(phd_mean[[3]],1)` years, i.e.
+PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
+The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (SD = `r round(prior_mean[[2]],1)`).
+We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
+
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r round(mean_analyses[[1]], 1)` models per team.
+Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
+We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
 
@@
 
-Teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, and the concrete operationalization of how they measured those acoustic properties.
-`r round(outcome_n[[1,1]],2) * 100`\% of models used a duration measure as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used a f0 measure, `r round(outcome_n[[3,1]],2) * 100`\% used a formant measure, `r round(outcome_n[[4,1]],2) * 100`\% used an intensity measure, and `r round(outcome_n[[5,1]],2) * 100`\% used a different measure.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
+`r round(outcome_n[[1,1]],2) * 100`\% of models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
 <!-- TR: Do we want to list some of them?-->
 
-`r round(window_n[[1,1]],2) * 100`\% of models measured acoustic properties at the level of the segment (e.g.
-comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% at the level of the word (e.g.
-comparing the acoustic profile of "banana"), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g.
+```{r unique-acou-oper}
+# acoustic operationalizations
+# Gross operationalization of acoustic operationalization
+unique_acou_oper <- msa_models %>%
+  unite("unique_oper", outcome, operationalisation, operationalisation_notes, na.rm = TRUE) %>%
+  count(unique_oper)
+```
+
+`r round(window_n[[1,1]],2) * 100`\% of models obtained acoustic measures at the level of the segment (e.g.
+comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g.
+comparing the acoustic profile of *Banane* 'banana'), `r round(window_n[[3,1]],2) * 100`\% at the level of the phrase (e.g.
 the noun phrase including determiner and adjective, e.g.
-"the green banana"), `r round(window_n[[4,1]],2) * 100`\% at the level of the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
+"the green banana"), `r round(window_n[[4,1]],2) * 100`\% from the whole sentence, and `r round(window_n[[5,1]],2) * 100`\% used a different time window.
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
 
-<!-- SC: I have added the number of unique meas. specs but we might want to discuss this. -->
-<!-- TR: How did you do this?-->
-
 ### Statistical analysis
 
-The multiverse of acoustic measurement choices is exponentiated with choices during the statistical analysis, including the predictors and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
-
-On average, models included `r round(predictor_n,1)` different predictors (counting only conceptually different predictors), i.e.
-in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
-Predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or gender of the speaker.
-
-The original dataset allowed to operationalize the most relevant predictor, typicality, in different ways. 
-It was operationalized as categorical (e.g.
-typical vs.
-atypical) in `r round(typicality_n[[1,1]],2) * 100`\% of models, continuous (on a scale from 0-100) with the mean typicality rating in `r round(typicality_n[[2,1]],2) * 100`\% of models, and continuous with the median typicality rating in `r round(typicality_n[[3,1]],2) * 100`\% of models.
-
-The majority of models were rooted in the frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%). `r round(framework_n[[1,1]],2) * 100`\% were operating in a Bayesian framework. 
-While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
+The high variability of acoustic measurements is multiplied by the choices of statistical analysis, including the chosen inferential framework, the type of model, and the model specification, like choice of predictors, interactions and group-level (aka random) effects.
+
+The models included a mean of `r round(predictor_n)` different predictors (defined as variables or columns in the data table).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
+Among the predictors included in the models there were information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or speaker gender.
+
+The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
+Among the possible operationalizations, `r round(typicality_n[[1,1]],2) * 100`\% of models contained typicality as a categorical variable (e.g.
+atypical vs.
+typical), `r round(typicality_n[[2,1]],2) * 100`\%  used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while `r round(typicality_n[[3,1]],2) * 100`\% of the models used the median typicality rating.
+
+The majority of models were run within a frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%).
+`r round(framework_n[[1,1]],2) * 100`\% were run within a Bayesian framework.
+While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of linear models), teams differed drastically in how they accounted for dependencies within the data.
+
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
@@
 
-Teams reviewed each others' analyses for both the acoustic analysis and the statistical analysis. 
-The mean rating of the quality of the acoustic analyses was `r round(review_mean[[1]],1)` (sd = `r round(review_mean[[2]],1)`); the mean rating of the quality of the statistical analysis was `r round(review_mean[[3]],1)` (sd = `r round(review_mean[[4]],1)`).
-For reference, the scale of the rating anchored a point grade of 75 as "an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation", indicating a rather high confidence of reviewers that the provided analyses yield appropriate (yet "imperfect") answers to the research question.
+Teams reviewed each others' acoustic and statistical analyses.
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`).
+The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
+For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".
 

### 2022-09-09 RR_manuscript/Draft_RR.tex
♻️ - edit descriptive results

@@
 
+The results section is divided into three parts.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by the team members.
+Second, we report the results of the meta-analytic model, focussing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
+
 \hypertarget{descriptive-statistics-1}{%
@@
 
-In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.
+In the following sections, we will describe the characteristics of the analysis teams that participated in the study and the analytic approaches they adopted.
+An important aspect that emerges from the descriptive analysis is the large variation in analytic strategies.
 
-\hypertarget{team-properties}{%
-\subsubsection{Team properties}\label{team-properties}}
+\hypertarget{characteristics-of-analytic-teams}{%
+\subsubsection{Characteristics of analytic teams}\label{characteristics-of-analytic-teams}}
 
-Eighty-Four teams initially signed up to participate.
-Fifty-Four of the proposed teams dropped out of the project during the analysis phase\footnote{ADD REASONS}.
-The remaining 30 teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).
+Eighty-Four teams initially signed up to participate in the study.
+Fifty-Four of the signed-up teams dropped out during the analysis phase\footnote{ADD REASONS}.
+The remaining 30 teams submitted their analysis by the established deadline.
+These are the teams that are included in this study.
 
-Submitting teams consisted of an average of 3.63 analysts (sd = 2.8).
-Analysts had on average 4.8 years (sd = 4.2) post PhD experience, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
+Submitting teams consisted of an average of 3.63 individual analysts (SD = 2.8).
 
-Analysts prior belief in the effect under investigation ranged from 48.5 to 92 with an average of 69.2 (sd = 11.3), indicating that analysts had an overall rather high prior plausibility of the investigated relationship between prosody and typicality (scale ranged from 0 to 100).
+Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
+Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
+The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92 with an average of 69.2 (SD = 11.3).
+We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
 
-The teams have submitted 170 models to answer the research question.
-On average, teams submitted 3.6 models.
-Crucially, analytic approaches widely varied in how they acoustically analysed the speech signal and how the statistically analysed the extracted values.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 170 individual models to answer the research question, with a mean of 3.6 models per team.
+Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
+We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
 
@@
 
-Teams differed in what and how they measured the acoustic signal, including choosing different aspects of the acoustic signal, the temporal window over which they measured, and the concrete operationalization of how they measured those acoustic properties.
-33\% of models used a duration measure as the outcome variable, 36\% used a f0 measure, 15\% used a formant measure, 14\% used an intensity measure, and 3\% used a different measure.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
+33\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 15\% used vowel formants, 14\% intensity, and 3\% other measures.
 
-45\% of models measured acoustic properties at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% at the level of the word (e.g.~comparing the acoustic profile of ``banana''), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% at the level of the whole sentence, and 5\% used a different time window.
+45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
@@
 
-The multiverse of acoustic measurement choices is exponentiated with choices during the statistical analysis, including the predictors and their operationalization, the chosen inferential framework, the type of model, and their model architecture, specifically how they accounted for dependencies in the data via random effect specifications in their multilevel models.
+The high variability of acoustic measurements is multiplied by the choices of statistical analysis, including the chosen inferential framework, the type of model, and the model specification, like choice of predictors, interactions and group-level (aka random) effects.
 
-On average, models included 1.9 different predictors (counting only conceptually different predictors), i.e.~in addition to the critical predictor, typicality of the adjective noun combinations, most teams included additional predictors in their models.
-Predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or gender of the speaker.
+The models included a mean of 2 different predictors (defined as variables or columns in the data table).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
+Among the predictors included in the models there were information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or speaker gender.
 
-The original dataset allowed to operationalize the most relevant predictor, typicality, in different ways.
-It was operationalized as categorical (e.g.~typical vs.~atypical) in 78\% of models, continuous (on a scale from 0-100) with the mean typicality rating in 19\% of models, and continuous with the median typicality rating in 1\% of models.
+The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
+Among the possible operationalizations, 78\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 19\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 1\% of the models used the median typicality rating.
 
-The majority of models were rooted in the frequentist framework (80\%). 20\% were operating in a Bayesian framework.
-While teams almost exclusively used linear models to analyze their data (98\%, with a few exception using machine learning techniques or GAMs as a special case of a linear model), teams differed drastically in how they accounted for dependencies within the data.
+The majority of models were run within a frequentist framework (80\%).
+20\% were run within a Bayesian framework.
+While teams almost exclusively used linear models to analyze their data (98\%, with a few exception using machine learning techniques or GAMs as a special case of linear models), teams differed drastically in how they accounted for dependencies within the data.
+
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
@@
 
-Teams reviewed each others' analyses for both the acoustic analysis and the statistical analysis.
-The mean rating of the quality of the acoustic analyses was 74.6 (sd = 11.1); the mean rating of the quality of the statistical analysis was 73.9 (sd = 14.1).
-For reference, the scale of the rating anchored a point grade of 75 as ``an imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation'', indicating a rather high confidence of reviewers that the provided analyses yield appropriate (yet ``imperfect'') answers to the research question.
+Teams reviewed each others' acoustic and statistical analyses.
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.6 (SD = 11.1).
+The mean rating of the statistical analysis is 73.9 (SD = 14.1).
+For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
 

### 2022-09-10 scripts/r/04_refit/refit_tr.Rmd
rename, refit models from pervagor_meeki so the labels correspond with google sheet

@@
 library(lme4)
+library(here)
 
@@
 
-pervagor_meeki_2_f0meannoun_cat <- brm(
+pervagor_meeki_2_durnoun_cat <- brm(
+  Duration_ms_s ~ 
+         effect_cat + 
+         + (1| speaker),
+  seed = 111,
+  data = data_dur_trim[data_dur_trim$word_type == "target_name",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_2_durnoun_cat"
+  )
+
+pervagor_meeki_3_f0meannoun_cat <- brm(
   Mean_f0_st_s ~ 
@@
   cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_2_f0meannoun_cat"
-  )
-
-pervagor_meeki_3_f0maxnoun_cat <- brm(
+  file = "./data/analyses/models/pervagor_meeki_3_f0meannoun_cat"
+  )
+
+pervagor_meeki_4_f0maxnoun_cat <- brm(
   Max_f0_st_s ~ 
@@
   cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_3_f0maxnoun_cat"
-  )
-
-pervagor_meeki_4_durnoun_cat <- brm(
-  Duration_ms_s ~ 
-         effect_cat + 
-         + (1| speaker),
-  seed = 111,
-  data = data_dur_trim[data_dur_trim$word_type == "target_name",], 
-  cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_4_durnoun_cat"
+  file = "./data/analyses/models/pervagor_meeki_4_f0maxnoun_cat"
   )
@@
 
-pervagor_meeki_6_f0meanadj_cat <- brm(
+pervagor_meeki_6_duradj_cat <- brm(
+  Duration_ms_s ~ 
+         effect_cat + 
+          + (1 | speaker)
+          + (effect_cat | target_word),
+  seed = 111,
+  data = data_dur_trim[data_dur_trim$word_type == "target_colour",], 
+  cores = 4,  
+  file = "./data/analyses/models/pervagor_meeki_6_duradj_cat"
+  )
+
+pervagor_meeki_7_f0meanadj_cat <- brm(
   Mean_f0_st_s ~ 
@@
   cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_6_f0meanadj_cat"
-  )
-
-pervagor_meeki_7_f0maxadj_cat <- brm(
+  file = "./data/analyses/models/pervagor_meeki_7_f0meanadj_cat"
+  )
+
+pervagor_meeki_8_f0maxadj_cat <- brm(
   Max_f0_st_s ~ 
@@
   cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_7_f0maxadj_cat"
-  )
-
-pervagor_meeki_8_duradj_cat <- brm(
-  Duration_ms_s ~ 
-         effect_cat + 
-          + (1 | speaker)
-          + (effect_cat | target_word),
-  seed = 111,
-  data = data_dur_trim[data_dur_trim$word_type == "target_colour",], 
-  cores = 4,  
-  file = "./data/analyses/models/pervagor_meeki_8_duradj_cat"
+  file = "./data/analyses/models/pervagor_meeki_8_f0maxadj_cat"
   )

### 2022-09-10 scripts/r/03_analyses_coding.Rmd
♻️ - split 04_analyses_coding, update msa_models

@@
 Now that the components have been downloaded, we can refit the models using the scripts in `scripts/r/04-refit/`.
-
-## Upload refitted models to OSF
-
-Once all your models have been refitted, you can upload them to the OSF, in the Cache component, `models/refitted/` folder.
-
-Here's the code that does that for you.
-
-```{r upload-refitted}
-cache <- osf_retrieve_node("wds2m")
-refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
-  filter(name == "refitted")
-models <- list.files(
-  "./data/analyses/models",
-  full.names = TRUE
-)
-
-osf_upload(
-  refitted,
-  path = models,
-  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
-)
-```
-
-## Download all refitted models
-
-We download all the refitted models `.rds` files from the OSF.
-
-```{r download-refitted}
-cache <- osf_retrieve_node("wds2m")
-refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)
-
-osf_download(
-  refitted_rds,
-  path = "./data/analyses/models/",
-  conflicts = "skip", progress = TRUE, verbose = TRUE
-)
-```
-
-# Get estimates from refitted models
-
-Now we can extract the relevant estimates from the refitted models.
-
-The following functions extracts the estimates.
-
-```{r clean-up}
-clean_up <- function(model) {
-  effs <- suppressWarnings(tidy(model, effects = "fixed", parametric = TRUE)) %>% 
-  filter(term %in% c("effect_catmedium", "effect_cattypical", "effect_con"))
-  if (!("response" %in% colnames(effs))) {
-    effs$response <- "none"
-  }
-  effs <- effs %>%
-  select(outcome_mult = response, term, estimate, se = std.error)
-
-  return(effs)
-}
-```
-
-This function is for calculation of the SDI.
-
-```{r sdi-mean}
-sdi_mean <- function(preds) {
-  bpair <- tibble::tibble(preds) %>% tidyr::unnest_wider(preds, names_sep = ".") %>%
-    as.matrix() %>%
-    betapart::beta.pair(.)
-  sdim <- as.matrix(bpair$beta.sor)
-  diag(sdim) <- NA
-  rowSums(sdim, na.rm = T) / length(preds)
-}
-```
-
-Now we load all the models and apply `clean_up()` to get the estimates.
-
-```{r load-models}
-msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
-  as_tibble() %>% 
-  transmute(
-    path = value,
-    mod_name = str_remove(path, here("data/analyses/models/")), 
-    mod_name = str_remove(mod_name, ".rds"), 
-    model = map(path, ~ readRDS(file = .))
-  ) %>% 
-  separate(
-    mod_name, 
-    into = c("word1", "word2", "model_n", "model_outcome", "typicality"), 
-    sep = "_", remove = F,
-    convert = TRUE
-  ) %>% 
-  unite(animal, word1, word2, sep = "_") %>% 
-  select(animal, model_n:model) %>% 
-  mutate(summaries = map(model, clean_up)) %>%
-  select(-model) %>%
-  unnest(summaries) %>%
-  mutate(
-    typ_level = case_when(
-      term == "effect_cattypical" ~ "typical",
-      term == "effect_catmedium" ~ "medium"
-    ),
-    typicality = ifelse(typicality == "con", "continuous", "categorical"),
-    model_id = paste(animal, model_n, sep = "_")
-  ) %>%
-  select(animal, model_n, model_id, model_outcome, outcome_mult, typicality, typ_level, estimate, se) %>%
-  mutate(
-    outcome_mult = case_when(
-      outcome_mult == "none" ~ NA_character_,
-      outcome_mult == "meanf0" ~ "f0",
-      outcome_mult == "meanint" ~ "intensity",
-      outcome_mult == "duration" ~ "duration",
-      outcome_mult == "f0" ~ "f0",
-      outcome_mult == "f15" ~ "formants_1",
-      outcome_mult == "f25" ~ "formants_2"
-    )
-  ) %>%
-  left_join(y = coding) %>%
-  mutate(
-    model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
-    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_")),
-    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "other")),
-    typicality = factor(typicality, levels = c("categorical", "continuous")),
-    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
-  ) %>%
-  left_join(y = msa_intake_teams) %>%
-  left_join(y = msa_reviews_teams, by = c("animal" = "Q3")) %>%
-  # We have excluded a few extra models so keeping them out at this stage
-  filter(exclude == "no") %>%
-  # We nest all the population predictors in the coding sheet to calculate the SDI
-  nest(pop_pred = typicality_cont:`2interaction_typicality_cont_typ_mean_z`) %>%
-  mutate(
-    pop_sdi = sdi_mean(pop_pred)
-  )
-
-saveRDS(msa_models, "./data/analyses/msa_models.rds")
-```
-
-Simple pandoc table of the models, estimates, se, etc.
-
-```{r effect-table}
-msa_models %>%
-  select(model_id, estimate, se) %>%
-  knitr::kable(format = "pandoc")
-```
-
-# Plotting
-
-Simple forest plot of the estimates and 95% CrIs.
-
-```{r fp-outcome}
-msa_models %>%
-  filter(animal != "polymetme_brevirostrum") %>%
-  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
-  geom_hline(yintercept = 0) +
-  geom_segment(
-    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
-    alpha = 0.5, size = 1, lineend = "round"
-  ) + 
-  geom_point(pch = 21, stroke = 2, size = 1) +
-  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
-  scale_colour_brewer(palette = "Set1", type = "qual") +
-  labs(y = "Estimate (z-scores)") + 
-  clean_theme() 
-```
-
-```{r fp-outcome-facet}
-msa_models %>%
-  filter(animal != "polymetme_brevirostrum") %>%
-  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
-  geom_hline(yintercept = 0) +
-  geom_segment(
-    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
-    alpha = 0.5, size = 1, lineend = "round"
-  ) + 
-  geom_point(pch = 21, stroke = 2, size = 1) +
-  facet_grid(outcome ~ typicality, scales = "free") +
-  scale_colour_brewer(palette = "Set1", type = "qual") +
-  labs(y = "Estimate (z-scores)") + 
-  clean_theme()
-```
-
-```{r forest-plot-2}
-msa_models %>%
-  filter(animal != "polymetme_brevirostrum") %>%
-  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = estimate)) + 
-  geom_hline(yintercept = 0) +
-  geom_segment(
-    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
-    alpha = 0.5, size = 1, lineend = "round"
-  ) + 
-  geom_point(pch = 21, stroke = 2, size = 1) +
-  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
-  scale_colour_gradientn(colours = c("#d95f02", "#dfc27d", "#80cdc1", "#018571"), limits = c(-1, 1)) +
-  labs(y = "Estimate (z-scores)") + 
-  clean_theme() 
-```
-
-```{r frameworks}
-coding %>%
-  ggplot(aes(framework)) +
-  geom_bar()
-```
-
-```{r models}
-coding %>%
-  ggplot(aes(model)) +
-  geom_bar()
-```
-
-```{r family}
-coding %>%
-  ggplot(aes(family)) +
-  geom_bar()
-
-coding %>%
-  ggplot(aes(outcome, fill = family)) +
-  geom_bar()
-```
-
-```{r temporal-w}
-coding %>%
-  drop_na(outcome, temporal_window) %>%
-  ggplot() +
-  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
-```
-
-```{r temporal-w-2}
-coding %>%
-  drop_na(outcome, temporal_window) %>%
-  filter(
-    outcome %in% c("duration", "f0", "intensity"),
-    temporal_window %in% c("segment", "word", "phrase", "sentence")
-  ) %>%
-  droplevels() %>%
-  ggplot() +
-  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
-```
-
-```{r operation}
-coding %>%
-  drop_na(operationalisation) %>%
-  count(operationalisation) %>%
-  ggplot(
-    aes(reorder(operationalisation, desc(n)), n)
-    ) +
-  geom_bar(stat = "identity")
-```
-
-```{r operation-2}
-coding %>%
-  drop_na(outcome, operationalisation) %>%
-  filter(
-    outcome %in% c("duration", "f0", "intensity"),
-    temporal_window %in% c("segment", "word", "phrase", "sentence")
-  ) %>%
-  droplevels() %>%
-  ggplot() +
-  geom_mosaic(aes(x = product(outcome, operationalisation), fill = outcome))
-```
-
-# Unique model combinations
-
-```{r combos}
-coding %>%
-  select(framework:outcome, operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
-  distinct()
-```
-
-```{r n-models}
-coding %>%
-  select(team, n_models) %>%
-  distinct() %>%
-  drop_na() %>%
-  summarise(mean(n_models), median(n_models), sd(n_models), min(n_models), max(n_models))
-```

### 2022-09-10 RR_manuscript/Draft_RR.tex
♻️ - update RR draft after updated models

@@
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 170 individual models to answer the research question, with a mean of 3.6 models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 181 individual models to answer the research question, with a mean of 3.6 models per team.
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-33\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 15\% used vowel formants, 14\% intensity, and 3\% other measures.
+34\% of models used a measure of duration as the outcome variable, 39\% used fundamental frequency (f0), 13\% used vowel formants, 13\% intensity, and 2\% other measures.
 
-45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
-Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
+41\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 49\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 3\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of 54 different measurement specifications.
 
@@
 The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
-Among the possible operationalizations, 78\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 19\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 1\% of the models used the median typicality rating.
+Among the possible operationalizations, 80\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 17\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 2\% of the models used the median typicality rating.
 
-The majority of models were run within a frequentist framework (80\%).
-20\% were run within a Bayesian framework.
+The majority of models were run within a frequentist framework (81\%).
+19\% were run within a Bayesian framework.
 While teams almost exclusively used linear models to analyze their data (98\%, with a few exception using machine learning techniques or GAMs as a special case of linear models), teams differed drastically in how they accounted for dependencies within the data.
@@
 The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
-7\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-64\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
+6\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+63\% specified random intercepts only, and 31\% specified random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included 2.4 random terms in their models.
-Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 45 different model specifications.
+Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 44 different model specifications.
 
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.6 (SD = 11.1).
-The mean rating of the statistical analysis is 73.9 (SD = 14.1).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.9 (SD = 11.3).
+The mean rating of the statistical analysis is 74 (SD = 13.8).
 For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
@@
 
-The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.022 and 0.023 standard units (95\% CrI, mean = 0.001).
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
 In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.~duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
@@
 \textbf{Non-preregistered}. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
-In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.016).
+In the first model, the meta-analytic intercept estimate is between -0.01 and 0.025 standard units (95\% CrI, mean = 0.008).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
@@
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
-Notably, while the majority of models yields inconclusive results, there are 25 model estimates for which the 95\% credible interval does not contain zero (15\%).
+Notably, while the majority of models yields inconclusive results, there are 21 model estimates for which the 95\% credible interval does not contain zero (12\%).
 

### 2022-09-12 RR_manuscript/Draft_RR.tex
🐛 - fixes #161

--- 2022-09-09 RR_manuscript/Draft_RR.tex
@@
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 170 individual models to answer the research question, with a mean of 3.6 models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 100 individual models to answer the research question, with a mean of 3.6 models per team.
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-33\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 15\% used vowel formants, 14\% intensity, and 3\% other measures.
+34\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 14\% used vowel formants, 13\% intensity, and 3\% other measures.
 
 45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
-Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
 
@@
 The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
-Among the possible operationalizations, 78\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 19\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 1\% of the models used the median typicality rating.
+Among the possible operationalizations, 79\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 18\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 2\% of the models used the median typicality rating.
 
@@
 The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
-7\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-64\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
+5\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+66\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included 2.4 random terms in their models.
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.6 (SD = 11.1).
-The mean rating of the statistical analysis is 73.9 (SD = 14.1).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2).
+The mean rating of the statistical analysis is 73.8 (SD = 14.1).
 For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
@@
 \textbf{Non-preregistered}. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
-In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.016).
+In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.015).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
@@
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
-Notably, while the majority of models yields inconclusive results, there are 25 model estimates for which the 95\% credible interval does not contain zero (15\%).
+Notably, while the majority of models yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
 

### 2022-09-12 RR_manuscript/Draft_RR.Rmd
🐛 - fixes #161
♻️ - edit rr with uptodate results

@@
 library(googlesheets4)
+library(broom.mixed)
 ```
@@
 
-```{r 'forkingPaths', echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
+```{r forkingPaths, echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
 knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"), error = FALSE)
@@
 
-```{r 'procedural', echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
+```{r procedural, echo=FALSE, fig.cap="(ref:procedural)", out.width="100%"}
 knitr::include_graphics(here::here("figs", "procedure_plot.png"), error = FALSE)
@@
 ```{r load-models, message=FALSE, warning=FALSE}
+msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
+  filter(transformation == "none", mean > 10)
+
 msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
@@
 # number of analyses
-no_analyses = nrow(msa_models)
+no_analyses <- msa_models %>%
+  select(animal, model_n) %>%
+  distinct() %>%
+  nrow()
 
@@
 meta_random_prereg <- ranef(meta_bm_prereg)
+meta_bm_prereg_tidy <- tidy(meta_bm_prereg)
 
@@
 meta_random <- ranef(meta_bm)
+meta_bm_tidy <- tidy(meta_bm)
 
@@
 meta_random_nest <- ranef(meta_bm_nest)
+meta_bm_nest_tidy <- tidy(meta_bm_nest)
 
@@
 
-According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95% credibility.
+According to the meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
 This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.
@@
 
-Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95% credibility.
+Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
 This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
@@
 As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
-On the other hand, the posterior 95% CrI for team in the second non-preregistered model is 0-0.05 standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+On the other hand, the posterior 95% CrI for team in the second non-preregistered model is `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
 

### 2022-09-12 RR_manuscript/Draft_RR.tex
♻️ - edit rr with uptodate results

@@
 As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
-On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0-0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
 

### 2022-09-12 scripts/r/07_team-sds.Rmd

@@
   start = 1532, 
-  end = 1601
+  end = 1600
   )
@@
     ) %>% 
-    select(animal, model_n, outcome, transformation) %>% 
+    select(animal, model_n, temporal_window, outcome, transformation) %>% 
     arrange(animal) %>% 
@@
   select(animal, model_n_rda = model_n.x, model_n_excel = model_n.y, model_n_match, 
-         dv, outcome, transformation, mean, sd)
+         temporal_window, dv, outcome, transformation, mean, sd)
 

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit msa sd

@@
 ```{r load-models, message=FALSE, warning=FALSE}
-msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
-  filter(transformation == "none", mean > 10)
-
 msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
@@
 compelling_count_nest <- table(post_meta_nest$compelling)
+
+# MSA SD ----
+
+msa_mean_sd_df <- read_csv("data/analyses/msa_mean_sd_df.csv") %>%
+  filter(transformation == "none", mean > 10, temporal_window != "sentence")
+
+meta_sd_clo <- meta_bm_tidy$conf.low[["sd_model_id__Intercept"]] 
+meta_sd_chi <- meta_bm_tidy$conf.high[["sd_model_id__Intercept"]]
+
+msa_sd <- msa_mean_sd_df %>% group_by(outcome, temporal_window) %>%
+  summarise(
+    sd_min = min(sd),
+    sd_med = mean(sd),
+    sd_max = max(sd),
+    .groups = "drop"
+  )
+
+msa_sd_
 ```

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit RR; include new shrinkage plot

@@
     sd_min = min(sd),
-    sd_med = mean(sd),
+    # sd_mean = mean(sd),
     sd_max = max(sd),
@@
 
-msa_sd_
+msa_sd_sd_lo <- msa_sd %>%
+  mutate(
+    across(starts_with("sd_"), ~.x * meta_sd_clo),
+    ci = "low"
+  ) %>%
+  pivot_longer(sd_min:sd_max, names_to = "sd")
+msa_sd_sd_hi <- msa_sd %>%
+  mutate(
+    across(starts_with("sd_"), ~.x * meta_sd_chi),
+    ci = "high"
+  ) %>%
+  pivot_longer(sd_min:sd_max, names_to = "sd")
+
+msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi)
 ```
@@
 ```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
-knitr::include_graphics(here::here("./figs/meta_plot1_nest.png"), error = FALSE)
+knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
 ```

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit between-teams variability section

@@
   mutate(
-    across(starts_with("sd_"), ~.x * meta_sd_clo),
+    across(starts_with("sd_"), ~.x * meta_sd_clo * 1.96),
     ci = "low"
@@
   mutate(
-    across(starts_with("sd_"), ~.x * meta_sd_chi),
+    across(starts_with("sd_"), ~.x * meta_sd_chi * 1.96),
     ci = "high"
@@
 
-msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi)
+msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi) %>%
+  mutate(value = round(value, 1)) %>%
+  pivot_wider(names_from = c(ci, sd), values_from = value) %>%
+  unite("low", low_sd_min, low_sd_max, sep = "-") %>%
+  unite("high", high_sd_min, high_sd_max, sep = "-") %>%
+  mutate(
+    unit = c("ms", "ms", "hz", "hz", "dB", "dB")
+  )
 ```
@@
 
-We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.
+```{r}
+knitr::kable(msa_sd, digits = 1)
+```
+
+We illustrate what this means in actual acoustic measures by means of examples.
+For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
+We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.
+
+Table XXX reports the minimum and maximum SD values taken from a representative range.
+If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
+Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)`, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: $33.4 * 0.11 = 3.8$ ms, $51.4 * 0.11 = 5.7$ ms;  $33.4 * 0.15 = 5$ ms, $51.4 * 0.15 = 7.7$ ms.
+We can thus calculate 95% intervals of the estimated between-model variability in milliseconds: `r round(3.8*1.96, 1)`-`r round(5.7*1.96, 1)` ms based on the low CI estimate 0.11, `r round(5*1.96, 1)`-`r round(7.7*1.96, 1)` ms based on the high CI estimate 0.15.
+
+```{r}
+msa_sd_sd
+```
 
@@
 <!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES, like we do with team variability (ALTERNATIVELY IN IQ VALUES).-->
-
-<!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->
 

### 2022-09-13 RR_manuscript/Draft_RR.tex
♻️ - edit RR; include new shrinkage plot
♻️ - edit between-teams variability section

@@
 
-We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.
+\begin{tabular}{l|l|r|r}
+\hline
+outcome & temporal\_window & sd\_min & sd\_max\\
+\hline
+duration & segment & 33.4 & 51.4\\
+\hline
+duration & word & 32.6 & 119.8\\
+\hline
+f0 & segment & 40.2 & 44.6\\
+\hline
+f0 & word & 4.0 & 47.2\\
+\hline
+intensity & segment & 3.3 & 7.1\\
+\hline
+intensity & word & 3.5 & 3.9\\
+\hline
+\end{tabular}
+
+We illustrate what this means in actual acoustic measures by means of examples.
+For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
+We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.
+
+Table XXX reports the minimum and maximum SD values taken from a representative range.
+If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
+Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
+We can thus calculate 95\% intervals of the estimated between-model variability in milliseconds: 7.4-11.2 ms based on the low CI estimate 0.11, 9.8-15.1 ms based on the high CI estimate 0.15.
+
+\begin{verbatim}
+## # A tibble: 6 x 5
+##   outcome   temporal_window low      high     unit 
+##   <chr>     <chr>           <chr>    <chr>    <chr>
+## 1 duration  segment         7.4-11.4 10-15.4  ms   
+## 2 duration  word            7.2-26.5 9.8-35.8 ms   
+## 3 f0        segment         8.9-9.8  12-13.3  hz   
+## 4 f0        word            0.9-10.4 1.2-14.1 hz   
+## 5 intensity segment         0.7-1.6  1-2.1    dB   
+## 6 intensity word            0.8-0.9  1-1.2    dB
+\end{verbatim}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/meta_plot1_nest} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
 \end{figure}

### 2022-09-15 RR_manuscript/Draft_RR.Rmd
Timo edits

@@
 The results section is divided into three parts.
-We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by the team members.
-Second, we report the results of the meta-analytic model, focussing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by other teams.
+Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
@@
 Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
-
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
+For example, if we look at those analyses who targeted fundamental frequency (f0), it was operationalized in a myriad of ways including as the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement was taken from the interval of a vowel in the article, the adjective or noun, or in the word interval of article, adjective or noun, or the noun phrase interval or the entire phrase. 
+Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
 
@@
 This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
-Among the predictors included in the models there were information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, or speaker gender.
+Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
 
@@
 
+<!-- TR: I count 9 GAMS, how can that amount to only 2%  -->
+
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
@@
 `r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
-<!-- TODO: We need to check if these model pooled -->
-`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified random intercepts and random slopes to account for the non-independence.
+<!-- TR: Did we confirm this?
+-->
+`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
 Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of `r nrow(unique_model_specs)` different model specifications. 
-<!-- TR: If done on team level did every team have a different mdoel?  -->
+<!-- TR: what do you mean with "discarding random effect? Do you mean if we ignore the variation there?  The sentence does compute for me-->
+<!-- TR: Now that we have the number for different acoustic operationalizations and the number for different statistical models we can calculate the possible unique combinations r nrow(unique_model_specs) * nrow(unique_acou_oper).
+I mention this in the discussion.
+If ok, delete comment-->
 
@@
 
-As explained in the **Methods** section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
+As explained in the **Methods** section, the primary aim of this analysis is to assess the degree of between-team variability.
 As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e.
@@
 **Non-preregistered**. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
-We have run two further non-preregistered meta-analytic models:
+We have run two further non-preregistered meta-analytic models to account for this added hierarchical layer:
 
@@
 
-As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
-On the other hand, the posterior 95% CrI for team in the second non-preregistered model is `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+The second non-preregistered model yields a similar model ID estimate to that of the first non-preregistered model.
+However, the posterior 95% CrI for between-team variability in the second non-preregistered model is `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+One interpretation of these estimates is that the variability of effects is larger within teams than it is across teams.
+
+<!-- TR: follow up on this within team variability-->
 
@@
 For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
-We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.
+We then selected values of standard deviations for the three outcome measurements extracted either from specific segments or words across the data tables submitted by the teams (i.e.
+how variable were their raw measures).
+
+<!-- TR: This is all really confusing. I know what you mean only because we talked about it.-->
 
 Table XXX reports the minimum and maximum SD values taken from a representative range.
-If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
+If we look at segments (e.g. measures of individual vowels), duration measurements (as taken by the teams who used duration) have standard deviations that range between 33.4 and 51.4 ms.
 Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)`, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: $33.4 * 0.11 = 3.8$ ms, $51.4 * 0.11 = 5.7$ ms;  $33.4 * 0.15 = 5$ ms, $51.4 * 0.15 = 7.7$ ms.
 We can thus calculate 95% intervals of the estimated between-model variability in milliseconds: `r round(3.8*1.96, 1)`-`r round(5.7*1.96, 1)` ms based on the low CI estimate 0.11, `r round(5*1.96, 1)`-`r round(7.7*1.96, 1)` ms based on the high CI estimate 0.15.
+
+<!-- TR: Sorry but this is unreadable. I will completely overhaul it.-->
 
@@
 duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
-
-<!-- TR: CONTEXTUALIZE IN CONCRETE ACOUSTIC VALUES, like we do with team variability (ALTERNATIVELY IN IQ VALUES).-->
 
@@
 
-(ref:meta_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
+(ref:meta_plot1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
@@
 
-We gave XX analyst teams the same speech dataset to answer the same research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*.
-In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
-As shown by the results of this meta-analytic study, such complex process has led to a wide "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
-Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
+We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech dataset to answer the same research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*.
+In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
+This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
+Analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing their statistical model, amounting to `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations.
+This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.
+
 Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
 In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
-The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
+The observed variation was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
 Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
@@
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger biases.
 Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
 @grice2017integrating; @turnbull2017role].
-Third, ADD REASONS. 
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
 
-It particularly struck us that teams did not follow our instructions to only submit a single effect size. 
+It particularly struck us that most teams submitted many different models. 
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
@@
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
+Fields such as the speech sciences who generate knowledge based on multidimensional data, should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., REFERENCE].
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., @vazire2017quality, @fidler2018reproducibility].
 One of the suggested paths forward is for researchers to directly replicate previous study more often [e.g., @open2015estimating; @camerer2018evaluating].
@@
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-The quantitative sciences are in an inference crisis [@rotello2015more; @starns2019assessing].
-Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
+Beyond a replication crisis, the quantitative sciences are in an inference crisis [@rotello2015more; @starns2019assessing].
+Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, peer ratings also suggest that they considered most of these alternative approaches acceptable.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
 
-A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
-The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to  different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
 <!-- TODO: add ref to "process and statistical model" in McElreath -->
@@
 
+<!-- TR: This preceding section rocks IMO -->
+
 In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
-It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018). 
-It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
-This enables critical evaluation and robustness checks by other fellow researchers (REF).
+It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility [@lebel2018unified]. 
+It allows for alternative analyses to establish analytic robustness [@steegen2016increasing] and strengthens attempts to synthesize evidence via meta-analyses [e.g., @nicenboim2018using]
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-<!-- TODO: cite Praat, EMU, MFA, Formant tracking etc -->
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., CITE Praat, EMU CITE)]].
-
-ADD
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat, EMU: @winkelmann2017emu].
+
+<!-- TODO: MFA, Formant tracking etc -->
 
@@
 This approach is called "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
+
 Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored. 
@@
 Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
-Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
+Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
 in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved by formalizing verbal expectations mathematically or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+This can be achieved by mathematically formalizing verbal expectations  or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
 ## Caveats
-
 Our study has several limitations that need to be considered when evaluating our results. 
@@
 This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
-We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable. 
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable. 
 However, our results should be independently re-analysed and replicated using a different research question.
@@
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
-Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
-This is particularly important for the predictor evaluation.
+While the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate for example the impact of certain predictors reliably.
 Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
-<!-- TR: still adding this? Meta-analytic model has model_id instead of team, so we are not accounting for the fact that teams have submitted multiple analyses (but not all of them did). -->
+
 - We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->
 
-Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.
+Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
 
 Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
-Our focus was on quantitative analyses that require operationalization of a multidimensional signal.
-While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
+We focused on quantitative analyses that require operationalization of a multidimensional signal. 
+While some of our results can be informative for other disciplines that worke with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
 This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods. 
-It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.
+It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
 

### 2022-09-15 RR_manuscript/Draft_RR.tex
Timo edits

@@
 Submitting teams consisted of an average of 3.63 individual analysts (SD = 2.8).
-
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
+For example,
 
@@
 5\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-66\% specified random intercepts only, and 29\% specified random intercepts and random slopes to account for the non-independence.
+66\% specified random intercepts only, and 29\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included 2.4 random terms in their models.
@@
 
-As for the second non-preregistered model, the posterior estimate for model ID is identical to that of the first non-preregistered model.
+On the one hand, the second non-preregistered model reveals that the posterior estimate for model ID is identical to that of the first non-preregistered model.
 On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
@@
 For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
-We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.
+We then selected values of standard deviations for the three outcome measurements extracted either from specific segments or words across the data tables submitted by the teams (i.e.~how variable were their raw measures).
 
 Table XXX reports the minimum and maximum SD values taken from a representative range.
-If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
+If we look at segments (e.g.~measures of individual vowels), duration measurements (as taken by the teams who used duration) have standard deviations that range between 33.4 and 51.4 ms.
 Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
@@
 
-(ref:meta\_plot1) illustrates the individual model intercepts, sorted in ascending order based on their mean.
+(ref:meta\_plot1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.

### 2022-09-16 RR_manuscript/Draft_RR.Rmd
♻️ - add reason for team dropping

@@
 <!-- TODO: Add reasons for dropping out -->
-`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase^[ADD REASONS].
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase.
+One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up.
+[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
+We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
 The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.

### 2022-09-16 RR_manuscript/Draft_RR.tex
♻️ - add reason for team dropping

@@
 Eighty-Four teams initially signed up to participate in the study.
-Fifty-Four of the signed-up teams dropped out during the analysis phase\footnote{ADD REASONS}.
+Fifty-Four of the signed-up teams dropped out during the analysis phase.
+One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``The reason is that {[}\ldots{]} the project's approach is too much top-down instead of bottom-up.
+{[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
+We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
 The remaining 30 teams submitted their analysis by the established deadline.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
-For example,
+For example, if we look at those analyses who targeted fundamental frequency (f0), it was operationalized in a myriad of ways including as the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement was taken from the interval of a vowel in the article, the adjective or noun, or in the word interval of article, adjective or noun, or the noun phrase interval or the entire phrase.
+Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
 
@@
 
-As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
+As explained in the \textbf{Methods} section, the primary aim of this analysis is to assess the degree of between-team variability.
 As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.
@@
 \textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
-We have run two further non-preregistered meta-analytic models:
+We have run two further non-preregistered meta-analytic models to account for this added hierarchical layer:
 
@@
 
-On the one hand, the second non-preregistered model reveals that the posterior estimate for model ID is identical to that of the first non-preregistered model.
-On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+The second non-preregistered model yields a similar model ID estimate to that of the first non-preregistered model.
+However, the posterior 95\% CrI for between-team variability in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+One interpretation of these estimates is that the variability of effects is larger within teams than it is across teams.
 
@@
 
-We gave XX analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
-In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
-As shown by the results of this meta-analytic study, such complex process has led to a wide ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
-Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
+We gave 30 analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
+In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
+This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
+Analyses exhibited at least 45 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2340 possible unique combinations.
+This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.
+
 Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
 In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
-The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
+The observed variation was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
 Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
@@
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
+Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger biases.
 Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
-Third, ADD REASONS.
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
 
-It particularly struck us that teams did not follow our instructions to only submit a single effect size.
+It particularly struck us that most teams submitted many different models.
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
@@
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
+Fields such as the speech sciences who generate knowledge based on multidimensional data, should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature {[}e.g., REFERENCE{]}.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[e.g.,][\citet{fidler2018reproducibility}]{vazire2017quality}.
 One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
@@
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-The quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
-Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
+Beyond a replication crisis, the quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
+Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, peer ratings also suggest that they considered most of these alternative approaches acceptable.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.
 
-A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
-The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
 We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
@@
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
-It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018).
-It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
-This enables critical evaluation and robustness checks by other fellow researchers (REF).
+It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
+It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process {[}e.g., CITE Praat, EMU CITE){]}{]}.
-
-ADD
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}]{boersma2021praat}.
 
@@
 This approach is called ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
+
 Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
@@
 Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
-Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved by formalizing verbal expectations mathematically or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
+This can be achieved by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom.
-We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable.
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
 However, our results should be independently re-analysed and replicated using a different research question.
@@
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
-Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
-This is particularly important for the predictor evaluation.
+While the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate for example the impact of certain predictors reliably.
 Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
-- We have not investigated researcher positionality, which is known to be an important factor.
 
-Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.
+\begin{itemize}
+\tightlist
+\item
+  We have not investigated researcher positionality, which is known to be an important factor.
+\end{itemize}
+
+Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
 
 Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
-Our focus was on quantitative analyses that require operationalization of a multidimensional signal.
-While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
+We focused on quantitative analyses that require operationalization of a multidimensional signal.
+While some of our results can be informative for other disciplines that worke with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
 This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
-It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.
+It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
 

### 2022-09-16 RR_manuscript/Draft_RR.Rmd
♻️ - edit counts by using models, not coefficients

@@
 # number of analyses
-no_analyses <- msa_models %>%
-  select(animal, model_n) %>%
-  distinct() %>%
+msa_models_unique <- msa_models %>%
+  select(animal, model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
+  distinct()
+
+no_analyses <- msa_models_unique %>%
   nrow()
@@
 # average analyses
-mean_analyses <- msa_models %>% 
-  group_by(team) %>% 
+mean_analyses <- msa_models_unique %>% 
+  group_by(animal) %>% 
   summarise(max_models = max(model_n)) %>% 
@@
 # outcomes
-outcome_n <- msa_models %>% 
+outcome_n <- msa_models_unique %>% 
   count(outcome) %>% 
@@
 # windows
-window_n <- msa_models %>% 
+window_n <- msa_models_unique %>% 
   count(temporal_window) %>% 
@@
 # predictors
-predictor_n <- msa_models %>% 
+predictor_n <- msa_models_unique %>% 
   summarise(mean_predictor = mean(n_predictors, na.rm = TRUE))
@@
 # typicality op
-typicality_n <- msa_models %>% 
+typicality_n <- msa_models_unique %>% 
   count(typicality_operationalization) %>% 
@@
 # framework
-framework_n <- msa_models %>% 
+framework_n <- msa_models_unique %>% 
   count(framework) %>% 
@@
 # model
-model_n <- msa_models %>% 
+model_n <- msa_models_unique %>% 
   count(model) %>% 
@@
 # random
-random_n <- msa_models %>% 
+random_n <- msa_models_unique %>% 
   filter(model == "linear model") %>% 
@@
 # random terms
-rterms_n <- msa_models %>% 
+rterms_n <- msa_models_unique %>% 
   filter(n_random != 0) %>% 
@@
 
-# unique model specs, discarding random effects
-unique_model_specs <- msa_models %>%
+# unique model specs, NOT including random effects
+unique_model_specs <- msa_models_unique %>%
   select(framework:outcome, pop_pred) %>%
+  unnest(pop_pred) %>%
+  distinct()
+
+# unique acoustic and model specs, NOT including random effects
+unique_acou_stat <- msa_models %>%
+  select(model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
   unnest(pop_pred) %>%
@@
 `r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate in the study.
-<!-- TODO: Add reasons for dropping out -->
 `r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase.
@@
 # Gross operationalization of acoustic operationalization
-unique_acou_oper <- msa_models %>%
+unique_acou_oper <- msa_models_unique %>%
   unite("unique_oper", outcome, operationalisation, operationalisation_notes, na.rm = TRUE) %>%
@@
 `r round(framework_n[[1,1]],2) * 100`\% were run within a Bayesian framework.
-While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, with a few exception using machine learning techniques or GAMs as a special case of linear models), teams differed drastically in how they accounted for dependencies within the data.
-
-<!-- TR: I count 9 GAMS, how can that amount to only 2%  -->
+While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, teams differed drastically in how they accounted for dependencies within the data.
+<!-- TODO: The calculations in these sections are based on the INCLUDED models only.
+We are not counting the SUBMITTED models that have been excluded.
+We might want to add counts for when including the excluded models -->
 
@@
 On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models.
-Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of `r nrow(unique_model_specs)` different model specifications. 
-<!-- TR: what do you mean with "discarding random effect? Do you mean if we ignore the variation there?  The sentence does compute for me-->
-<!-- TR: Now that we have the number for different acoustic operationalizations and the number for different statistical models we can calculate the possible unique combinations r nrow(unique_model_specs) * nrow(unique_acou_oper).
-I mention this in the discussion.
-If ok, delete comment-->
+
+Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
+When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
 

### 2022-09-16 RR_manuscript/Draft_RR.tex
♻️ - edit counts by using models, not coefficients

@@
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 100 individual models to answer the research question, with a mean of 3.6 models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 models per team.
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-34\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 14\% used vowel formants, 13\% intensity, and 3\% other measures.
+35\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 12\% used vowel formants, 14\% intensity, and 3\% other measures.
 
-45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
+45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
@@
 The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
-Among the possible operationalizations, 79\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 18\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 2\% of the models used the median typicality rating.
+Among the possible operationalizations, 72\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 24\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
 
-The majority of models were run within a frequentist framework (80\%).
-20\% were run within a Bayesian framework.
-While teams almost exclusively used linear models to analyze their data (98\%, with a few exception using machine learning techniques or GAMs as a special case of linear models), teams differed drastically in how they accounted for dependencies within the data.
+The majority of models were run within a frequentist framework (83\%).
+17\% were run within a Bayesian framework.
+While teams almost exclusively used linear models to analyze their data (98\%, teams differed drastically in how they accounted for dependencies within the data.
 
@@
 The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
-5\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-66\% specified random intercepts only, and 29\% specified both random intercepts and random slopes to account for the non-independence.
-On average, teams that specified random effects, included 2.4 random terms in their models.
-Based on statistical framework, type of model, distribution family, fixed terms, and discarding random effects, there were a total of 45 different model specifications.
+8\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+65\% specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
+On average, teams that specified random effects, included 2.5 random terms in their models.
+
+Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
+When considering both acoustic and statistical analysis, we have found a grand total of 104, i.e.~each submitted analysis was unique.
 
@@
 This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
-Analyses exhibited at least 45 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2340 possible unique combinations.
+Analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2444 possible unique combinations.
 This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.

### 2022-09-16 RR_manuscript/Draft_RR.Rmd
🐛 - reintroduce timo's edits to RR

@@
 
-<!-- TR: some of this or most of this should go into a nice overview table -->
+<!-- TODO: some of this or most of this should go into a nice overview table -->
 
@@
 
-The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
 `r round(outcome_n[[1,1]],2) * 100`\% of models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
-<!-- TR: Do we want to list some of them?-->
+<!-- TODO: check that all proportions refer to models and not to coefficients -->
 
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
-For example, if we look at those analyses who targeted fundamental frequency (f0), it was operationalized in a myriad of ways including as the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
-The measurement was taken from the interval of a vowel in the article, the adjective or noun, or in the word interval of article, adjective or noun, or the noun phrase interval or the entire phrase. 
+For example, if we consider those analyses who targetfundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
@@
 
-The high variability of acoustic measurements is multiplied by the choices of statistical analysis, including the chosen inferential framework, the type of model, and the model specification, like choice of predictors, interactions and group-level (aka random) effects.
+The large decision space related to how the acoustic signal was measured is further expanded by the choices in the statistical analysis, including the chosen inferential framework, the type of model, and the model specification, including choice of predictors, interactions and group-level effects.
 
 The models included a mean of `r round(predictor_n)` different predictors (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least one additional predictor.
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
-We first report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
+First, we report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
 
@@
 
-As explained in the **Methods** section, the primary aim of this analysis is to assess the degree of between-team variability.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), i.e.
-the standard deviation of the group-level effect of team returned by the meta-analytic model.
-
-According to the meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.
-
-**Non-preregistered**. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
-We have run two further non-preregistered meta-analytic models to account for this added hierarchical layer:
-
-1. A model with model ID instead of team as the group-level effect (`(1|model_id)`).
-2. A model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`).
-
-Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
-
-The second non-preregistered model yields a similar model ID estimate to that of the first non-preregistered model.
-However, the posterior 95% CrI for between-team variability in the second non-preregistered model is `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
-One interpretation of these estimates is that the variability of effects is larger within teams than it is across teams.
-
-<!-- TR: follow up on this within team variability-->
-
-```{r}
-knitr::kable(msa_sd, digits = 1)
-```
-
-We illustrate what this means in actual acoustic measures by means of examples.
-For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
-We then selected values of standard deviations for the three outcome measurements extracted either from specific segments or words across the data tables submitted by the teams (i.e.
-how variable were their raw measures).
-
-<!-- TR: This is all really confusing. I know what you mean only because we talked about it.-->
-
-Table XXX reports the minimum and maximum SD values taken from a representative range.
-If we look at segments (e.g. measures of individual vowels), duration measurements (as taken by the teams who used duration) have standard deviations that range between 33.4 and 51.4 ms.
-Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)`, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: $33.4 * 0.11 = 3.8$ ms, $51.4 * 0.11 = 5.7$ ms;  $33.4 * 0.15 = 5$ ms, $51.4 * 0.15 = 7.7$ ms.
-We can thus calculate 95% intervals of the estimated between-model variability in milliseconds: `r round(3.8*1.96, 1)`-`r round(5.7*1.96, 1)` ms based on the low CI estimate 0.11, `r round(5*1.96, 1)`-`r round(7.7*1.96, 1)` ms based on the high CI estimate 0.15.
-
-<!-- TR: Sorry but this is unreadable. I will completely overhaul it.-->
-
-```{r}
-msa_sd_sd
-```
-
-<!-- TODO: Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->
+The primary aim of this analysis is to assess the degree of between-team.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$).
+
+According to the preregistered meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
+
+**Non-preregistered**. However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption. 
+To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`), which allows us to estimate both the between-team variation along with the between-analysis variation.
+This analysis was not preregistered and should thus be interpreted with caution.[^Note that before this we have also run a model with just model ID as the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.]
+
+<!-- Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
+This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.-->
+
+The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+The posterior 95% CrI for between-analysis variability (nested in teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
+Taken these two models together, it appears as if the variability of reported effects between any model (within team or across) is substantially larger than variability across teams.
+We come back to this important observation later.
 
@@
 
+After assessing the variation between teams and analyses, we now turn towards the meta-analytic estimate of the effect of typicality on acoustic parameters.
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
-In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.
-duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
-
-**Non-preregistered**. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
-In the first model, the meta-analytic intercept estimate is between `r round(meta_intercept[3],3)` and `r round(meta_intercept[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept[1],3)`).
+In other words, and from a very naive statistical perspective, our best guess is that speakers do not encode typicality in the acoustic signal (e.g.
+by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+
+**Non-preregistered**. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as random effects.
+In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_nest[1],3)`).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
 Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
-The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).
 
@@
 longer duration, higher f0, etc.), as mentioned above.
-Notably, while the majority of models yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
-
-<!-- TR: ADD PARAGRAPH ON HOW MANY CLAIMED THERE TO BE AN EFFECT.-->
+When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
+Estimates ranged between `r min(msa_models$estimate)` to `r max(msa_models$estimate)` standard units.
+
+While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
 
@@
 
-After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
-There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
-
-(ref:meta_plot1), panel C, displays the coefficients alongside 80% and 95% credible intervals for all model predictors.
-
-<!-- TR: ADD TABLE HERE TOO?-->
-
-The model suggests that most team-specific predictors yield very small deviations from the meta-analytical estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
+After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the observed variation.
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
+
+<!-- TODO:extract and fill in estimates and 95% CrIs as indicated below -->
+(ref:meta_plot1), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals. 
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
 Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
-Interestingly, the model uniqueness, i.e. how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates. 
+Interestingly, the model uniqueness, i.e.
+how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
 This suggests that the analysts' results very much depend on their choice of predictors. 
-Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. duration or f0) and the choice of temporal window affected the results. 
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or formants) and the choice of temporal window affected the results. 
 (ref:meta_plot1) displays the posterior estimates for the measurement outcome (i.e.
 what acoustic dimension was measured, panel A) and measurement window (i.e.
-what is the unit over which was measured, panel B).
+what is the unit over which the outcome was measured, panel B).
 If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
 If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
-Similarly, if acoustic parameters were measured within individual segments (e.g.
-the vowel of the noun), estimates are lower than the meta analytic estimate, and if acoustic parameters were measured across whole phrases (e.g.
-"the blue banana"), the estimates are generally higher.
-In other words, depending on the choice of measurement, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
+In other words, depending on the choice of measurement and the measurment window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
 
@@
 
-We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech dataset to answer the same research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*.
+We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech data set to answer the same research question: *Do 
+speakers acoustically modify utterances to signal atypical word combinations?*.
 In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
@@
 Analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing their statistical model, amounting to `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations.
-This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.
-
-Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+Note that this is a conservative estimate of the multiverse of analytical decisions for our research question (ignoring further degrees of freedom like e.g.
+acoustic parameter extraction, outlier treatment, and transformations).
+
+To gain a better intuition about the amount of variability we will ground the results in actual acoustic measures.
+We calculated how much raw data measures for duration, fundamental frequency and intensity varied within teams (by extracting their standard deviation). 
+Consider them an indication of how much said outcome measures generally vary after being extracted from the signal (see xx for an overview <!-- TODO: add link to a vignette-->). 
+We can now use these value of variation and interpret the meta-analytic estimates relative to it.
+For example, for those analyses that analyzed the duration of segments (e.g.
+the duration of the stressed vowel in banAna), duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values.
+The reported effect estimates from teams varied between `r min(msa_models$estimate)` and `r max(msa_models$estimate)` standard units which corresponds to duration values ranging from `r min(msa_models$estimate) * 33.4 ` to `r max(msa_models$estimate) * 51.4`.
+If we are more conservative and only convert the meta-analytic estimates of between-analysis variation, we obtain an estimate of between-team variability in milliseconds that ranges from `r round(3.8*1.96, 1)` to `r round(7.7*1.96, 1)` (at 95% credibility).^[minimum SD of duration measures multiplied by lower 95% CrI of meta analysis: $33.4 * 0.11 = 3.8$ ms; maximum SD of duration measures multiplied by upper 95% CrI of of meta analysis: $51.4 * 0.15 = 7.7$ ms].
+
+While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
+For example, XXms is considered the just noticeable difference, i.e.
+the threshold under which human are claimed not to be able to distinguish them {REF}.
+<!-- TODO: Stefano add ref here and values from your work-->
+<!-- TODO: Add a second possible phenomenon from articulation-->
+Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which surrounds duration effects ranging from 7-15ms [@nicenboim2018using]. 
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].  
+The fact that there seems to be idios
+Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction is thus concerning and might lead to theoretically completely opposing interpretations.
+
+```{r}
+#msa_sd_sd
+```
+
+<!-- TODO (SC): Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->
+
+```{r}
+#knitr::kable(msa_sd, digits = 1)
+```
+
+And this variation seems somewhat random. 
+For example, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
 In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
@@
 These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many, @breznau2021observing].
-Given the mounting evidence, @breznau2021observing conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."
+Following @breznau2021observing, we are bound to conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."[p.9].
 Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices. 
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to very much depend on certain measurement choices. 
 Human speech is a complex multidimensional signal.
@@
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger biases.
-Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 [e.g.
+Since we do not know the truth and our best guess based on the meta analysis suggest no relationship, this remains speculative.
+Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Many researchers targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
 @grice2017integrating; @turnbull2017role].
+Moreover, prior work as actually suggested a relationship between typicality and f0 [e.g. @dimitrova2008prosodic; @dimitrova2009did]. 
+Researchers might have heard about those findings, nudging their analysis choices slightly into a particular direction.
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect. 
-
-It particularly struck us that most teams submitted many different models. 
+This conclusion is further supported by the fact that between-team variability was lower than between model variability. 
+This is an important observation when put into context of the fact that most teams submitted many different models. 
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [Tukey 1953, @benjamini1995controlling].
@@
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
-Fields such as the speech sciences who generate knowledge based on multidimensional data, should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+Fields such as the speech sciences that advance their theories based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 
-A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to  different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+A desired outcome of knowing that different butc reasonable measurement choices or statistical approaches might lead to  different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
@@
 Our study has several limitations that need to be considered when evaluating our results. 
-First, there is potential for bias. 
+Importantly, there is potential for bias. 
 The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
-
-- We have not investigated researcher positionality, which is known to be an important factor.  <!-- TR:@stef explain here -->
-
+In light of these possible sources of bias, a field can benefit from explicit positionality statement [e.g., @fox2021open]
+Researchers do not analyse data in a vaccuum.
+It is important recognize and disclose one’s positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
 Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
-
-Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+Beyond the potential for bias, our study lacks generalizability. 
+The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
 We focused on quantitative analyses that require operationalization of a multidimensional signal. 
-While some of our results can be informative for other disciplines that worke with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods. 
+While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods rather than quantitatively.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
@@
 # Conclusion
+
+In recent efforts several studies have highlighted the large degree of analytic flexibility in data analysis. 
+When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that invites bias and might weaken the strength of confidence in the published literature.
+Going beyond previous empirical studies, the current paper looked at many speech production analyses. 
+Speech is a multidimensional signal that allows for great flexibility because the primary data lend themselves to a variety of possible operationalizations. 
+30 teams of speech scientists analyzed the same data set. 
+Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical approaches.
+Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
+Quantitatively, the between-team and between-analysis variation of estimates is so large that it crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio mechanical thresholds.
+In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
+Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction. 
+That together with the large between-analysis variation and the tendency to test the same research question on multiple outcome variables suggest that the vast plurality of acceptable analysis approaches is expected to frequently lead to inconclusive results.
+We suggest that fields that base their scientific claims on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and mulitverse analyses when evaluating epistomologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by formalisation and computational models.
 

### 2022-09-18 RR_manuscript/Draft_RR.tex

@@
 
-The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choosing specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
 35\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 12\% used vowel formants, 14\% intensity, and 3\% other measures.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
-For example, if we look at those analyses who targeted fundamental frequency (f0), it was operationalized in a myriad of ways including as the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
-The measurement was taken from the interval of a vowel in the article, the adjective or noun, or in the word interval of article, adjective or noun, or the noun phrase interval or the entire phrase.
+For example, if we consider those analyses who targetfundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
@@
 
-The high variability of acoustic measurements is multiplied by the choices of statistical analysis, including the chosen inferential framework, the type of model, and the model specification, like choice of predictors, interactions and group-level (aka random) effects.
+The large decision space related to how the acoustic signal was measured is further expanded by the choices in the statistical analysis, including the chosen inferential framework, the type of model, and the model specification, including choice of predictors, interactions and group-level effects.
 
 The models included a mean of 2 different predictors (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least an additional predictor.
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least one additional predictor.
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 
-As explained in the \textbf{Methods} section, the primary aim of this analysis is to assess the degree of between-team variability.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.
+The primary aim of this analysis is to assess the degree of between-team.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)).
 
-According to the meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95\% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 2, 0.07 * 2) in standard units.
+According to the preregistered meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95\% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
 
-\textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
-We have run two further non-preregistered meta-analytic models to account for this added hierarchical layer:
+\textbf{Non-preregistered}.
+However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption.
+To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}), which allows us to estimate both the between-team variation along with the between-analysis variation.
+This analysis was not preregistered and should thus be interpreted with caution.{[}\^{}Note that before this we have also run a model with just model ID as the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.{]}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  A model with model ID instead of team as the group-level effect (\texttt{(1\textbar{}model\_id)}).
-\item
-  A model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}).
-\end{enumerate}
-
-Based on the first non-preregistered model, the group-level standard deviation for model ID is between 0.11 and 0.15 standard units, at 95\% credibility.
-This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.
-
-The second non-preregistered model yields a similar model ID estimate to that of the first non-preregistered model.
-However, the posterior 95\% CrI for between-team variability in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
-One interpretation of these estimates is that the variability of effects is larger within teams than it is across teams.
-
-\begin{tabular}{l|l|r|r}
-\hline
-outcome & temporal\_window & sd\_min & sd\_max\\
-\hline
-duration & segment & 33.4 & 51.4\\
-\hline
-duration & word & 32.6 & 119.8\\
-\hline
-f0 & segment & 40.2 & 44.6\\
-\hline
-f0 & word & 4.0 & 47.2\\
-\hline
-intensity & segment & 3.3 & 7.1\\
-\hline
-intensity & word & 3.5 & 3.9\\
-\hline
-\end{tabular}
-
-We illustrate what this means in actual acoustic measures by means of examples.
-For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
-We then selected values of standard deviations for the three outcome measurements extracted either from specific segments or words across the data tables submitted by the teams (i.e.~how variable were their raw measures).
-
-Table XXX reports the minimum and maximum SD values taken from a representative range.
-If we look at segments (e.g.~measures of individual vowels), duration measurements (as taken by the teams who used duration) have standard deviations that range between 33.4 and 51.4 ms.
-Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
-We can thus calculate 95\% intervals of the estimated between-model variability in milliseconds: 7.4-11.2 ms based on the low CI estimate 0.11, 9.8-15.1 ms based on the high CI estimate 0.15.
-
-\begin{verbatim}
-## # A tibble: 6 x 5
-##   outcome   temporal_window low      high     unit 
-##   <chr>     <chr>           <chr>    <chr>    <chr>
-## 1 duration  segment         7.4-11.4 10-15.4  ms   
-## 2 duration  word            7.2-26.5 9.8-35.8 ms   
-## 3 f0        segment         8.9-9.8  12-13.3  hz   
-## 4 f0        word            0.9-10.4 1.2-14.1 hz   
-## 5 intensity segment         0.7-1.6  1-2.1    dB   
-## 6 intensity word            0.8-0.9  1-1.2    dB
-\end{verbatim}
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
+The posterior 95\% CrI for between-analysis variability (nested in teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
+Taken these two models together, it appears as if the variability of reported effects between any model (within team or across) is substantially larger than variability across teams.
+We come back to this important observation later.
 
@@
 
+After assessing the variation between teams and analyses, we now turn towards the meta-analytic estimate of the effect of typicality on acoustic parameters.
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
-In other words, our best guess is that typical and atypical word combinations might not differ in acoustic measures (e.g.~duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+In other words, and from a very naive statistical perspective, our best guess is that speakers do not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
 
-\textbf{Non-preregistered}. As mentioned in the previous section, we have run two further models, one using model ID instead of team and the second using team and model ID nested within team.
-In the first model, the meta-analytic intercept estimate is between -0.01 and 0.04 standard units (95\% CrI, mean = 0.015).
+\textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as random effects.
+In this non-preregistered model, the meta-analytic intercept estimate is between -0.013 and 0.04 standard units (95\% CrI, mean = 0.014).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
 Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
-The estimated intercept from the second model (with nested group-level effects) is virtually identical to the first (with only model ID as group-level effect).
 
@@
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
-Notably, while the majority of models yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
+When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
+Estimates ranged between -0.6544004 to 0.9885856 standard units.
+
+While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
 
@@
 
-After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the estimated intercept.
-There is a lot of variation, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?
+After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the observed variation.
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?
 
-(ref:meta\_plot1), panel C, displays the coefficients alongside 80\% and 95\% credible intervals for all model predictors.
-
-The model suggests that most team-specific predictors yield very small deviations from the meta-analytical estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
+(ref:meta\_plot1), panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
 Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI).
-Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates.
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
 This suggests that the analysts' results very much depend on their choice of predictors.
-Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~duration or f0) and the choice of temporal window affected the results.
-(ref:meta\_plot1) displays the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which was measured, panel B).
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~f0 or formants) and the choice of temporal window affected the results.
+(ref:meta\_plot1) displays the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which the outcome was measured, panel B).
 If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
 If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
-Similarly, if acoustic parameters were measured within individual segments (e.g.~the vowel of the noun), estimates are lower than the meta analytic estimate, and if acoustic parameters were measured across whole phrases (e.g.~``the blue banana''), the estimates are generally higher.
-In other words, depending on the choice of measurement, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
+In other words, depending on the choice of measurement and the measurment window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
 
@@
 
-We gave 30 analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
+We gave 30 analyst teams the same speech data set to answer the same research question: \emph{Do
+speakers acoustically modify utterances to signal atypical word combinations?}.
 In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
@@
 Analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2444 possible unique combinations.
-This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.
+Note that this is a conservative estimate of the multiverse of analytical decisions for our research question (ignoring further degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations).
 
-Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+To gain a better intuition about the amount of variability we will ground the results in actual acoustic measures.
+We calculated how much raw data measures for duration, fundamental frequency and intensity varied within teams (by extracting their standard deviation).
+Consider them an indication of how much said outcome measures generally vary after being extracted from the signal (see xx for an overview ).
+We can now use these value of variation and interpret the meta-analytic estimates relative to it.
+For example, for those analyses that analyzed the duration of segments (e.g.~the duration of the stressed vowel in banAna), duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values.
+The reported effect estimates from teams varied between -0.6544004 and 0.9885856 standard units which corresponds to duration values ranging from -21.856972 to 50.8132988.
+If we are more conservative and only convert the meta-analytic estimates of between-analysis variation, we obtain an estimate of between-team variability in milliseconds that ranges from 7.4 to 15.1 (at 95\% credibility).\footnote{minimum SD of duration measures multiplied by lower 95\% CrI of meta analysis: \(33.4 * 0.11 = 3.8\) ms; maximum SD of duration measures multiplied by upper 95\% CrI of of meta analysis: \(51.4 * 0.15 = 7.7\) ms}.
+
+While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
+For example, XXms is considered the just noticeable difference, i.e.~the threshold under which human are claimed not to be able to distinguish them \{REF\}.
+Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which surrounds duration effects ranging from 7-15ms \citep{nicenboim2018using}.
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.\\
+The fact that there seems to be idios
+Expecting random variation between different analysts of 7 to 15 in one or the other direction is thus concerning and might lead to theoretically completely opposing interpretations.
+
+And this variation seems somewhat random.
+For example, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
 In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
@@
 These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
-Given the mounting evidence, \citet{breznau2021observing} conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''
+Following \citet{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''{[}p.9{]}.
 Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices.
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to very much depend on certain measurement choices.
 Human speech is a complex multidimensional signal.
@@
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger biases.
-Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Since we do not know the truth and our best guess based on the meta analysis suggest no relationship, this remains speculative.
+Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Many researchers targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Moreover, prior work as actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
+Researchers might have heard about those findings, nudging their analysis choices slightly into a particular direction.
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
-
-It particularly struck us that most teams submitted many different models.
+This conclusion is further supported by the fact that between-team variability was lower than between model variability.
+This is an important observation when put into context of the fact that most teams submitted many different models.
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
-Fields such as the speech sciences who generate knowledge based on multidimensional data, should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+Fields such as the speech sciences that advance their theories based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 
-A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+A desired outcome of knowing that different butc reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
@@
 Our study has several limitations that need to be considered when evaluating our results.
-First, there is potential for bias.
+Importantly, there is potential for bias.
 The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
-
-\begin{itemize}
-\tightlist
-\item
-  We have not investigated researcher positionality, which is known to be an important factor.
-\end{itemize}
-
+In light of these possible sources of bias, a field can benefit from explicit positionality statement \citep[e.g.,][]{fox2021open}
+Researchers do not analyse data in a vaccuum.
+It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
 Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
-
-Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+Beyond the potential for bias, our study lacks generalizability.
+The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
 We focused on quantitative analyses that require operationalization of a multidimensional signal.
-While some of our results can be informative for other disciplines that worke with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
+While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods rather than quantitatively.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
@@
 \section{Conclusion}\label{conclusion}}
+
+In recent efforts several studies have highlighted the large degree of analytic flexibility in data analysis.
+When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that invites bias and might weaken the strength of confidence in the published literature.
+Going beyond previous empirical studies, the current paper looked at many speech production analyses.
+Speech is a multidimensional signal that allows for great flexibility because the primary data lend themselves to a variety of possible operationalizations.
+30 teams of speech scientists analyzed the same data set.
+Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical approaches.
+Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
+Quantitatively, the between-team and between-analysis variation of estimates is so large that it crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio mechanical thresholds.
+In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
+Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction.
+That together with the large between-analysis variation and the tendency to test the same research question on multiple outcome variables suggest that the vast plurality of acceptable analysis approaches is expected to frequently lead to inconclusive results.
+We suggest that fields that base their scientific claims on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and mulitverse analyses when evaluating epistomologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by formalisation and computational models.
 

### 2022-09-18 scripts/r/00_credit_taxonomy.R
remove credit plot and code

@@ -1,24 +1,0 @@
-# CRediT taxonomy
-
-library(tidyverse)
-
-credit <- read_csv(here::here("./data/meta/credit-taxonomy.csv")) %>%
-  pivot_longer(SC:TR, names_to = "author", values_to = "value") %>%
-  mutate(
-    author = factor(author, levels = c("SC", "JVC", "TR")),
-    value = ifelse(is.na(value), 0.2, value)
-  )
-
-credit %>%
-  ggplot(aes(author, Roles)) +
-  geom_point(aes(alpha = value)) +
-  scale_y_discrete(limits = rev) +
-  scale_x_discrete(position = "top") +
-  labs(
-    x = element_blank(), y = element_blank(),
-    caption = "CRediT (Contributor Roles Taxonomy), http://credit.niso.org."
-  ) +
-  theme_light() +
-  theme(legend.position = "none", text = element_text(size = 8))
-
-ggsave(here::here("./figs/credit-taxonomy.png"), width = 3, height = 3)

### 2022-09-18 RR_manuscript/Draft_RR.Rmd
include desc table (draft), fix typos

@@
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a communictive intention of interest is an important analytic step.
+Thus, choosing how to measure a communicative intention of interest is an important analytic step.
 Take for example the following sentence in (1).
@@
 
+\phantom{.}
+
 ```{r}
@@
 #| echo: false
-#| eval: false
-team_desc_df %>% 
-  mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
-  select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
-  knitr::kable(align = c("l", "r", "r", "r"), 
-               caption = "Caption test", 
-               label = "team-descriptives-table")
+#| results: 'asis'
+#| eval: true
+
+# team_desc_df %>% 
+#   mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
+#   select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
+#   knitr::kable(align = c("l", "r", "r", "r"), 
+#                caption = "Caption test", 
+#                label = "team-descriptives-table")
+
+# Team descriptives
+tbl_team_desc <- msa_models %>% 
+  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
+         all_rating) %>% 
+  group_by(animal) %>% 
+  summarize(across(years_from_phd:all_rating, mean)) %>% 
+  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
+  na.omit() %>% 
+  group_by(metric) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
+  mutate_if(is.numeric, round, digits = 2) %>% 
+  mutate(desc = "team_desc", 
+    metric = fct_relevel(metric, "years_from_phd"), 
+   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+    Metric = case_when(
+      metric == "years_from_phd" ~ "Years since PhD", 
+      metric == "stat_rating" ~ "Statistical ability", 
+      metric == "prior_belief" ~ "Prior belief of $H_{1}$", 
+      metric == "phon_rating" ~ "Phon rating", 
+      metric == "all_rating" ~ "all rating"), 
+    label = glue::glue("{desc}_{metric}")) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
+  add_row(label = " ", desc = "team_desc", Metric = " ", 
+          Min. = NA, Max = NA, `Mean (SD)` = NA, avg = NA, sd = NA) %>% 
+  mutate(across(-c("label", "desc", "Metric"), ~replace(., is.na(.), " ")))
+
+# Model descriptives 
+tbl_model_desc <- msa_models %>% 
+  select(animal, n_predictors:n_random, n_models) %>% 
+  group_by(animal) %>% 
+  summarize(across(everything(), mean)) %>% 
+  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
+  na.omit() %>% 
+  group_by(metric) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
+  mutate_if(is.numeric, round, digits = 2) %>% 
+  mutate(desc = "model_desc", 
+    metric = fct_relevel(metric, "n_models"), 
+    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+    Metric = case_when(
+      metric == "n_coefficients" ~ "n. coefficients", 
+      metric == "n_models" ~ "n. models", 
+      metric == "n_predictors" ~ "n. predictors", 
+      metric == "n_random" ~ "n. random effects", 
+      metric == "n_random_int" ~ "n. random intercepts", 
+      metric == "n_random_slo" ~ "n. random slopes", 
+      metric == "n_random_smooth" ~ "n. random smooths",
+      metric == "n_terms" ~ "n. terms"), 
+    label = glue::glue("{desc}_{metric}")) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
+  mutate(across(-c("desc", "Metric"), as.character))
+
+# Combine in single tibble (for printing in prose and table)
+tbl_team_model_desc <- bind_rows(tbl_team_desc, tbl_model_desc) %>% 
+  mutate(desc = case_when(
+    Metric != "all rating" & desc == "team_desc" ~ " ", 
+    Metric != "n. coefficients" & desc == "model_desc" ~ " ", 
+    TRUE ~ desc), 
+    desc = case_when(
+      desc == "team_desc" ~ "Teams", 
+      desc == "model_desc" ~ "Models", 
+      TRUE ~ " "))
+
+tbl_team_model_desc %>% 
+  select(Descriptives = desc, Metric, Min., Max, `Mean (SD)`) %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
+    linesep = "", align = c("l", "l", "r", "r", "r"))
+
 ```
 
-`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate in the study.
-`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase.
+`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study.
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
 One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up.
@@
 We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
@@
 
-`r round(window_n[[1,1]],2) * 100`\% of models obtained acoustic measures at the level of the segment (e.g.
+`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models obtained acoustic measures at the level of the segment (e.g.
 comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
-For example, if we consider those analyses who targetfundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
 The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic]. 
-In light of these possible sources of bias, a field can benefit from explicit positionality statement [e.g., @fox2021open]
+In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @fox2021open]
 Researchers do not analyse data in a vaccuum.

### 2022-09-18 RR_manuscript/Draft_RR.tex
include desc table (draft), fix typos

@@
 
-Eighty-Four teams initially signed up to participate in the study.
-Fifty-Four of the signed-up teams dropped out during the analysis phase.
+\phantom{.}
+
+\begin{tabular}{llrrr}
+\toprule
+Descriptives & Metric & Min. & Max & Mean (SD)\\
+\midrule
+Teams & all rating & 39 & 88.67 & 69.95 (14.34)\\
+ & Phon rating & 41.25 & 88.33 & 71.51 (13.92)\\
+ & Prior belief of $H_{1}$ & 48.5 & 92 & 69.19 (11.33)\\
+ & Statistical ability & 33 & 93.33 & 69.46 (16.52)\\
+ & Years since PhD & -3.75 & 12.38 & 4.77 (4.16)\\
+ &  &  &  & \\
+Models & n. coefficients & 1 & 11 & 3.5 (2.75)\\
+ & n. models & 1 & 16 & 3.67 (3.44)\\
+ & n. predictors & 1 & 4.2 & 1.59 (0.85)\\
+ & n. random effects & 0 & 10 & 2.47 (2.05)\\
+ & n. random intercepts & 0 & 10 & 1.91 (1.77)\\
+ & n. random slopes & 0 & 4 & 0.63 (1.07)\\
+ & n. random smooths & 0 & 0 & 0 (0)\\
+ & n. terms & 1 & 4.27 & 1.78 (1.08)\\
+\bottomrule
+\end{tabular}
+
+Eighty-four teams initially signed up to participate in the study.
+Fifty-four of the signed-up teams dropped out during the analysis phase.
 One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``The reason is that {[}\ldots{]} the project's approach is too much top-down instead of bottom-up.
@@
 We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 The remaining 30 teams submitted their analysis by the established deadline.
@@
 
-45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
+Forty-five percent of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
-For example, if we consider those analyses who targetfundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
 The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
-In light of these possible sources of bias, a field can benefit from explicit positionality statement \citep[e.g.,][]{fox2021open}
+In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{fox2021open}
 Researchers do not analyse data in a vaccuum.

### 2022-09-19 scripts/r/00_credit_taxonomy.R
put these back (thought they werent going to be used). oops. lol.

@@ -1,0 +1,24 @@
+# CRediT taxonomy
+
+library(tidyverse)
+
+credit <- read_csv(here::here("./data/metadata/credit-taxonomy.csv")) %>%
+  pivot_longer(SC:TR, names_to = "author", values_to = "value") %>%
+  mutate(
+    author = factor(author, levels = c("SC", "JVC", "TR")),
+    value = ifelse(is.na(value), 0.2, value)
+  )
+
+credit %>%
+  ggplot(aes(author, Roles)) +
+  geom_point(aes(alpha = value)) +
+  scale_y_discrete(limits = rev) +
+  scale_x_discrete(position = "top") +
+  labs(
+    x = element_blank(), y = element_blank(),
+    caption = "CRediT (Contributor Roles Taxonomy), http://credit.niso.org."
+  ) +
+  theme_light() +
+  theme(legend.position = "none", text = element_text(size = 8))
+
+ggsave(here::here("./figs/credit-taxonomy.png"), width = 3, height = 3)

### 2022-09-19 RR_manuscript/Draft_RR.Rmd
add more refs

@@
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [Tukey 1953, @benjamini1995controlling].
-<!-- TR: couldnt find bibtex of tukey: Tukey, J. W. (1953). The problem of multiple comparisons. Multiple comparisons. -->
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [@tukey1953].
+<!-- TR: couldnt find bibtex of tukey: Tukey, J. W. (1953). The problem of multiple comparisons. Multiple comparisons. 
+JVC: I found it as an unpublished report and added tukey1953 to the refs file. Not sure if that is better than [Tukey 1953, as cited in @benjamini1995controlling] or not.-->
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
@@
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
-<!-- TODO: add ref to "process and statistical model" in McElreath -->
+<!-- TODO: add ref to "process and statistical model" in McElreath 
+JVC: added @mcelreath2020 to bib file. -->
 We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.

### 2022-09-19 RR_manuscript/Draft_RR.tex
add more refs

@@
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep{tukey1953}.
 It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.

### 2022-09-19 RR_manuscript/Draft_RR.Rmd
update table, added section at the end of statistical analyses re. number of teams claiming an effect

@@
 # review ratings
+# NOTE: Stef or Timo, this doesnt take into account repeated values per team
 review_mean <- msa_models %>% 
@@
 
-\phantom{.}
-
+`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study.
+`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
+One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up.
+[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
+We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
+The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
+These are the teams that are included in this study.
+Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses.
+
+Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
+Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
+Analysts had on average `r round(phd_mean[[1]],1)` years (SD = `r round(phd_mean[[2]],1)`) of experience after completing their PhD, ranging from `r round(phd_mean[[3]],1)` years, i.e.
+PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
+The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (SD = `r round(prior_mean[[2]],1)`).
+We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
+
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r round(mean_analyses[[1]], 1)` models per team.
+Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
+We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
+
+<!-- Begin Table --> 
+\vspace{0.2in}
 ```{r}
@@
 #                label = "team-descriptives-table")
+
+# Round and format numbers to exactly N digits
+specify_decimal <- function(x, k) {
+  out <- trimws(format(round(x, k), nsmall = k))
+  return(out)
+}
 
@@
   group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
-  mutate_if(is.numeric, round, digits = 2) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+            sd = sd(vals, na.rm = T)) %>% 
+  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
+  mutate(across(-c("metric", "min", "max"), specify_decimal, k = 2)) %>% 
   mutate(desc = "team_desc", 
@@
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+    Range = glue::glue("{min}--{max}"), 
     Metric = case_when(
       metric == "years_from_phd" ~ "Years since PhD", 
-      metric == "stat_rating" ~ "Statistical ability", 
-      metric == "prior_belief" ~ "Prior belief of $H_{1}$", 
-      metric == "phon_rating" ~ "Phon rating", 
-      metric == "all_rating" ~ "all rating"), 
+      metric == "stat_rating" ~ "Self-report statistical ability", 
+      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
+      metric == "phon_rating" ~ "Acoustic analysis rating", 
+      metric == "all_rating" ~ "Overall peer review rating"), 
     label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
   add_row(label = " ", desc = "team_desc", Metric = " ", 
-          Min. = NA, Max = NA, `Mean (SD)` = NA, avg = NA, sd = NA) %>% 
+          Min. = NA, Max = NA, `Mean (SD)` = NA, avg = NA, sd = NA, Range = NA) %>% 
   mutate(across(-c("label", "desc", "Metric"), ~replace(., is.na(.), " ")))
@@
   group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
-  mutate_if(is.numeric, round, digits = 2) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+            sd = sd(vals, na.rm = T)) %>% 
+  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
+  mutate(across(-c("metric", "min", "max"), specify_decimal, k = 2)) %>% 
   mutate(desc = "model_desc", 
@@
     `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+    Range = glue::glue("{min}--{max}"), 
     Metric = case_when(
@@
     label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
   mutate(across(-c("desc", "Metric"), as.character))
@@
   mutate(desc = case_when(
-    Metric != "all rating" & desc == "team_desc" ~ " ", 
+    Metric != "Overall peer review rating" & desc == "team_desc" ~ " ", 
     Metric != "n. coefficients" & desc == "model_desc" ~ " ", 
@@
       desc == "model_desc" ~ "Models", 
-      TRUE ~ " "))
+      TRUE ~ " ")
+    )
 
 tbl_team_model_desc %>% 
-  select(Descriptives = desc, Metric, Min., Max, `Mean (SD)`) %>% 
+  select(Descriptives = desc, Metric, Range, `Mean (SD)`) %>% 
   knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "l", "r", "r", "r"))
+    linesep = "", align = c("l", "l", "c", "r"), 
+    caption = "Descriptive statistics for teams and models included in the 
+    meta-analysis (n = 30).",
+    label = "team-descriptives-table"
+    ) %>% 
+  kableExtra::kable_styling(., font_size = 11)
 
 ```
-
-`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study.
-`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
-One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up.
-[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
-We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
-The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
-These are the teams that are included in this study.
-
-Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
-Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
-Analysts had on average `r round(phd_mean[[1]],1)` years (SD = `r round(phd_mean[[2]],1)`) of experience after completing their PhD, ranging from `r round(phd_mean[[3]],1)` years, i.e.
-PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
-The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (SD = `r round(prior_mean[[2]],1)`).
-We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
-
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r round(mean_analyses[[1]], 1)` models per team.
-Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
-We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
+\vspace{0.2in}
+<!-- END: Table -->
 
@@
 
+<!-- Found effect 
+JVC: this code is ready to go, but not all the rows in the google sheet are 
+filled out (approx. 40 missing)
+--> 
+```{r}
+#| label: found-effect
+#| echo: false
+
+found_effect <- msa_models %>% 
+  select(animal, model_n, found_effect) %>% 
+  na.omit() %>% 
+  mutate(effect = if_else(found_effect == "yes", 1, 0))
+
+atleast_1_effect <- found_effect %>% 
+  group_by(animal) %>% 
+  summarize(total = sum(effect)) %>% 
+  filter(total != 0)
+
+# Overall N of analyses claiming an effect
+n_effects <- sum(found_effect$effect)
+
+# Percent of effects
+perc_effects <- (n_effects / nrow(msa_models) * 100) %>% round(., 2)
+
+# N of teams claiming an effect
+n_atleast_1 <- nrow(atleast_1_effect)
+
+# Percent of teams claiming an effect
+perc_atleast_1 <- (n_atleast_1 / length(unique(msa_models$animal))) * 100
+```
+
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
 When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
+Of the submitted analyses, `r n_effects` claimed to have found a statistically reliable effect (`r perc_effects`%). 
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) submitting analyses reported at least one found effect.
 

### 2022-09-19 RR_manuscript/Draft_RR.tex
update table, added section at the end of statistical analyses re. number of teams claiming an effect

@@
 \providecommand{\tightlist}{\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 
@@
 
-\phantom{.}
-
-\begin{tabular}{llrrr}
-\toprule
-Descriptives & Metric & Min. & Max & Mean (SD)\\
-\midrule
-Teams & all rating & 39 & 88.67 & 69.95 (14.34)\\
- & Phon rating & 41.25 & 88.33 & 71.51 (13.92)\\
- & Prior belief of $H_{1}$ & 48.5 & 92 & 69.19 (11.33)\\
- & Statistical ability & 33 & 93.33 & 69.46 (16.52)\\
- & Years since PhD & -3.75 & 12.38 & 4.77 (4.16)\\
- &  &  &  & \\
-Models & n. coefficients & 1 & 11 & 3.5 (2.75)\\
- & n. models & 1 & 16 & 3.67 (3.44)\\
- & n. predictors & 1 & 4.2 & 1.59 (0.85)\\
- & n. random effects & 0 & 10 & 2.47 (2.05)\\
- & n. random intercepts & 0 & 10 & 1.91 (1.77)\\
- & n. random slopes & 0 & 4 & 0.63 (1.07)\\
- & n. random smooths & 0 & 0 & 0 (0)\\
- & n. terms & 1 & 4.27 & 1.78 (1.08)\\
-\bottomrule
-\end{tabular}
-
 Eighty-four teams initially signed up to participate in the study.
@@
 These are the teams that are included in this study.
+Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
 
@@
 We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
+
+\vspace{0.2in}
+\begin{table}
+
+\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams and models included in the 
+    meta-analysis (n = 30).}
+\centering
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{llcr}
+\toprule
+Descriptives & Metric & Range & Mean (SD)\\
+\midrule
+Teams & Overall peer review rating & 39--89 & 69.95 (14.34)\\
+ & Acoustic analysis rating & 41--88 & 71.51 (13.92)\\
+ & Prior belief in $H_{1}$ & 48--92 & 69.19 (11.33)\\
+ & Self-report statistical ability & 33--93 & 69.46 (16.52)\\
+ & Years since PhD & -4--12 & 4.77 (4.16)\\
+ &  &  & \\
+Models & n. coefficients & 1--11 & 3.50 (2.75)\\
+ & n. models & 1--16 & 3.67 (3.44)\\
+ & n. predictors & 1--4 & 1.59 (0.85)\\
+ & n. random effects & 0--10 & 2.47 (2.05)\\
+ & n. random intercepts & 0--10 & 1.91 (1.77)\\
+ & n. random slopes & 0--4 & 0.63 (1.07)\\
+ & n. random smooths & 0--0 & 0.00 (0.00)\\
+ & n. terms & 1--4 & 1.78 (1.08)\\
+\bottomrule
+\end{tabular}
+\end{table}
+\vspace{0.2in}
 
@@
 When considering both acoustic and statistical analysis, we have found a grand total of 104, i.e.~each submitted analysis was unique.
+Of the submitted analyses, 37 claimed to have found a statistically reliable effect (21.76\%).
+Nine teams out of the thirty (30\%) submitting analyses reported at least one found effect.
 

### 2022-09-20 RR_manuscript/Draft_RR.Rmd
add categorical factors table and printing function

@@
 # number of analyses
+# JVC: Why is this the number of total analyses and not nrow(msa_models)?
 msa_models_unique <- msa_models %>%
@@
 An important aspect that emerges from the descriptive analysis is the large variation in analytic strategies.
-
-<!-- TODO: some of this or most of this should go into a nice overview table -->
 
@@
   return(out)
+}
+
+# Print values from tibble for article
+pull_from_tib <- function(df, col, row, val) {
+  col <- enquo(col)
+  row <- enquo(row)
+  val <- enquo(val)
+  val <- filter(df, !!col == !!row) %>% pull(!!val)
+  return(val)
 }
@@
     ) %>% 
-  kableExtra::kable_styling(., font_size = 11)
+  kableExtra::kable_styling(., font_size = 10)
 
@@
 <!-- END: Table -->
+
+<!-- Begin Table 2 --> 
+\vspace{0.2in}
+```{r}
+#| label: categorical-descriptives-table
+#| echo: false
+#| results: 'asis'
+#| eval: true
+
+# Descriptives of categorical variables
+tbl_categorical_desc <- msa_models %>% 
+  select(animal, outcome, temporal_window, typicality_operationalization, 
+  framework, model) %>% 
+  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
+  na.omit() %>% 
+  group_by(metric) %>% 
+  count(val) %>% 
+  group_by(metric) %>% 
+  mutate(prop = n / sum(n), perc = prop * 100, 
+    Metric = case_when(
+      metric == "temporal_window" ~ "Temporal window", 
+      metric == "typicality_operationalization" ~ "Typicality operationalization", 
+      TRUE ~ metric
+    ), 
+    Metric = str_to_sentence(Metric), 
+    Type = case_when(
+      val != "GAM" ~ str_to_sentence(val), 
+      TRUE ~ val
+    )) %>% 
+  mutate(across(c("prop", "perc"), specify_decimal, k = 2)) %>% 
+  unite(label, c("metric", "val")) %>% 
+  mutate(label = str_replace_all(label, " ", "_"), 
+         label = str_remove_all(label, "\\(|\\)"))
+
+tbl_categorical_desc %>% 
+  select(Metric, Type, n, `\\%` = perc) %>% 
+  mutate(Metric = case_when(
+    Type != "Bayesian" & Metric == "Framework" ~ " ", 
+    Type != "GAM" & Metric == "Model" ~ " ", 
+    Type != "Duration" & Metric == "Outcome" ~ " ", 
+    Type != "Other" & Metric == "Temporal window" ~ " ", 
+    Type != "Categorical" & Metric == "Typicality operationalization" ~ " ", 
+    TRUE ~ Metric)
+    ) %>% 
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 2) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 6) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 12) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 18) %>%
+  mutate(across(-c("Metric", "Type"), ~replace(., is.na(.), " "))) %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
+    linesep = "", align = c("l", "l", "r", "r"), 
+    caption = "Descriptive statistics for model stuff.",
+    label = "categorical-descriptives-table"
+    ) %>% 
+  kableExtra::kable_styling(., font_size = 10)
+
+# pull_from_tib(tbl_categorical_desc, label, "framework_bayesian", n)
+
+```
+<!-- END Table 2 -->
 

### 2022-09-20 RR_manuscript/Draft_RR.tex
add categorical factors table and printing function

@@
 \centering
-\fontsize{11}{13}\selectfont
+\fontsize{10}{12}\selectfont
 \begin{tabular}[t]{llcr}
@@
 \vspace{0.2in}
+
+\vspace{0.2in}
+\begin{table}
+
+\caption{\label{tab:categorical-descriptives-table}Descriptive statistics for model stuff.}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+Metric & Type & n & \%\\
+\midrule
+Framework & Bayesian & 34 & 20.00\\
+ & Frequentist & 136 & 80.00\\
+ &  &  & \\
+Model & GAM & 2 & 1.18\\
+ & Linear model & 166 & 97.65\\
+ & Other & 2 & 1.18\\
+ &  &  & \\
+Outcome & Duration & 57 & 33.53\\
+ & F0 & 62 & 36.47\\
+ & Formants & 24 & 14.12\\
+ & Intensity & 22 & 12.94\\
+ & Other & 5 & 2.94\\
+ &  &  & \\
+Temporal window & Other & 8 & 4.73\\
+ & Phrase & 6 & 3.55\\
+ & Segment & 76 & 44.97\\
+ & Sentence & 4 & 2.37\\
+ & Word & 75 & 44.38\\
+ &  &  & \\
+Typicality operationalization & Categorical & 135 & 80.36\\
+ & Continuous (mean) & 30 & 17.86\\
+ & Continuous (median) & 3 & 1.79\\
+\bottomrule
+\end{tabular}
+\end{table}
 

### 2022-09-21 RR_manuscript/Draft_RR.Rmd

--- 2022-09-19 RR_manuscript/Draft_RR.Rmd
@@
 
+```{r}
+#| label: helper-functions
+# Round and format numbers to exactly N digits
+specify_decimal <- function(x, k) {
+  out <- trimws(format(round(x, k), nsmall = k))
+  return(out)
+}
+
+# Print values from tibble for article
+pull_from_tib <- function(df, col, row, val) {
+  col <- enquo(col)
+  row <- enquo(row)
+  val <- enquo(val)
+  val <- filter(df, !!col == !!row) %>% pull(!!val)
+  return(val)
+}
+```
+
 # Introduction
@@
               sd_size = sd(n_members), 
-              median_size = median(n_members)) %>% 
+              median_size = median(n_members), 
+              min = min(n_members), 
+              max = max(n_members)) %>% 
     mutate(stage = "Final")
   ) %>% 
-  mutate_if(is.numeric, round, digits = 2)
+  mutate_if(is.numeric, round, digits = 1)
 
@@
 msa_models_unique <- msa_models %>%
-  select(animal, model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
+  select(animal, model_n, outcome, typicality_operationalization, framework, 
+         model, temporal_window, random_effects, n_random, phon_rating, 
+         stat_rating, n_predictors, pop_pred, operationalisation, 
+         operationalisation_notes) %>%
   distinct()
@@
 unique_acou_stat <- msa_models %>%
-  select(model_n, outcome, typicality_operationalization, framework, model, temporal_window, random_effects, n_random, phon_rating, stat_rating, n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
+  select(model_n, outcome, typicality_operationalization, framework, model, 
+         temporal_window, random_effects, n_random, phon_rating, stat_rating, 
+         n_predictors, pop_pred, operationalisation, operationalisation_notes) %>%
   unnest(pop_pred) %>%
@@
 # review ratings
+# NOTE: Stef or Timo, this doesnt take into account repeated values per team
+# so the denominator is inflated (alosa_atun has 16 models but the phon_rating 
+# is the same for each so the mean is dividing by an inflated denominator)
+# I suggest using the following: 
+#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", avg)`
+#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", sd)`
+
 review_mean <- msa_models %>% 
@@
             sd_srating = sd(stat_rating, na.rm = TRUE))
-```
-
-The results section is divided into three parts.
-We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by other teams.
-Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
-Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-
-## Descriptive statistics
-
-In the following sections, we will describe the characteristics of the analysis teams that participated in the study and the analytic approaches they adopted.
-An important aspect that emerges from the descriptive analysis is the large variation in analytic strategies.
-
-<!-- TODO: some of this or most of this should go into a nice overview table -->
-
-### Characteristics of analytic teams
-
-\phantom{.}
-
-```{r}
-#| label: team-descriptives-table
-#| echo: false
-#| results: 'asis'
-#| eval: true
-
-# team_desc_df %>% 
-#   mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
-#   select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
-#   knitr::kable(align = c("l", "r", "r", "r"), 
-#                caption = "Caption test", 
-#                label = "team-descriptives-table")
+
+#
+# TABLE 1 PREP
+#
 
@@
   group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
-  mutate_if(is.numeric, round, digits = 2) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+            sd = sd(vals, na.rm = T)) %>% 
+  add_row(.before = 1, 
+    metric = "size", 
+    min = team_desc_df %>% filter(stage == "Final") %>% pull(min), 
+    max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
+    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
+    sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
+  mutate(across(-metric, specify_decimal, k = 1)) %>% 
   mutate(desc = "team_desc", 
-    metric = fct_relevel(metric, "years_from_phd"), 
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+    Range = glue::glue("{min}--{max}"), 
     Metric = case_when(
+      metric == "size" ~ "Team size", 
       metric == "years_from_phd" ~ "Years since PhD", 
-      metric == "stat_rating" ~ "Statistical ability", 
-      metric == "prior_belief" ~ "Prior belief of $H_{1}$", 
-      metric == "phon_rating" ~ "Phon rating", 
-      metric == "all_rating" ~ "all rating"), 
+      metric == "stat_rating" ~ "Self-report statistical ability", 
+      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
+      metric == "phon_rating" ~ "Acoustic analysis rating", 
+      metric == "all_rating" ~ "Overall peer review rating"), 
     label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
-  add_row(label = " ", desc = "team_desc", Metric = " ", 
-          Min. = NA, Max = NA, `Mean (SD)` = NA, avg = NA, sd = NA) %>% 
-  mutate(across(-c("label", "desc", "Metric"), ~replace(., is.na(.), " ")))
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)
+
+#
+# TABLE 2 PREP
+#
+
+# Descriptives of categorical variables in acoustic analyses
+tbl_categorical_desc <- msa_models_unique %>% 
+  select(animal, outcome, temporal_window, typicality_operationalization, 
+  framework, model) %>% 
+  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
+  na.omit() %>% 
+  group_by(metric) %>% 
+  count(val) %>% 
+  group_by(metric) %>% 
+  mutate(prop = n / sum(n), perc = prop * 100, 
+    Metric = case_when(
+      metric == "temporal_window" ~ "Temporal window", 
+      metric == "typicality_operationalization" ~ "Typicality operationalization", 
+      TRUE ~ metric
+    ), 
+    Metric = str_to_sentence(Metric), 
+    Type = case_when(
+      val != "GAM" ~ str_to_sentence(val), 
+      TRUE ~ val
+    )) %>% 
+  mutate(across(c("prop", "perc"), specify_decimal, k = 1)) %>% 
+  unite(label, c("metric", "val")) %>% 
+  mutate(label = str_replace_all(label, " ", "_"), 
+         label = str_remove_all(label, "\\(|\\)"))
+
+#
+# TABLE 3 PREP
+#
 
@@
   group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals), sd = sd(vals)) %>% 
-  mutate_if(is.numeric, round, digits = 2) %>% 
+  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+            sd = sd(vals, na.rm = T)) %>% 
+  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
+  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
   mutate(desc = "model_desc", 
@@
     label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
   mutate(across(-c("desc", "Metric"), as.character))
 
-# Combine in single tibble (for printing in prose and table)
-tbl_team_model_desc <- bind_rows(tbl_team_desc, tbl_model_desc) %>% 
-  mutate(desc = case_when(
-    Metric != "all rating" & desc == "team_desc" ~ " ", 
-    Metric != "n. coefficients" & desc == "model_desc" ~ " ", 
-    TRUE ~ desc), 
-    desc = case_when(
-      desc == "team_desc" ~ "Teams", 
-      desc == "model_desc" ~ "Models", 
-      TRUE ~ " "))
-
-tbl_team_model_desc %>% 
-  select(Descriptives = desc, Metric, Min., Max, `Mean (SD)`) %>% 
-  knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "l", "r", "r", "r"))
-
-```
+```
+
+The results section is divided into three parts.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by other teams.
+Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
+
+## Descriptive statistics
+
+In the following sections, we will describe the characteristics of the analysis teams that participated in the study and the analytic approaches they adopted.
+An important aspect that emerges from the descriptive analysis is the large variation in analytic strategies.
+
+### Characteristics of analytic teams
 
@@
 
-Submitting teams consisted of an average of `r team_desc_list$Final$mean_size$val` individual analysts (SD = `r team_desc_list$Final$sd_size$val`).
+Submitting teams consisted of an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` individual analysts (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`).
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
-Analysts had on average `r round(phd_mean[[1]],1)` years (SD = `r round(phd_mean[[2]],1)`) of experience after completing their PhD, ranging from `r round(phd_mean[[3]],1)` years, i.e.
-PhD students (or younger) to `r round(phd_mean[[4]],1)` years.
-The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r round(prior_mean[[3]],1)`  to `r round(prior_mean[[4]],1)` with an average of `r round(prior_mean[[1]],1)` (SD = `r round(prior_mean[[2]],1)`).
+Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
+PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years.
+The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
 We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r round(mean_analyses[[1]], 1)` models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", sd)`) models per team.
+Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses. 
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
 We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
+
+<!-- Begin Table 1 --> 
+\vspace{0.2in}
+```{r}
+#| label: team-descriptives-table
+#| results: 'asis'
+bind_rows(
+  tbl_team_desc, 
+  filter(tbl_model_desc, label == "model_desc_n_models")
+  ) %>% 
+  select(Metric, Range, `Mean (SD)`) %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
+    linesep = "", align = c("l", "c", "r"), 
+    caption = "Descriptive statistics for teams included in the 
+    meta-analysis (n = 30).",
+    label = "team-descriptives-table"
+    ) %>% 
+  kableExtra::kable_styling(., font_size = 11)
+```
+<!-- END: Table -->
 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
+Table \@ref(tab:categorical-descriptives-table) provides a summary of the acoustic analyses.
+
+<!-- Begin Table 2 --> 
+\vspace{0.2in}
+```{r}
+#| label: categorical-descriptives-table
+#| results: 'asis'
+
+tbl_categorical_desc %>% 
+  select(Metric, Type, n, `\\%` = perc) %>% 
+  group_by(Metric) %>% 
+  arrange(desc(n), .by_group = T) %>% 
+  ungroup() %>% 
+  mutate(Metric = case_when(
+    Type != "Frequentist" & Metric == "Framework" ~ " ", 
+    Type != "Linear model" & Metric == "Model" ~ " ", 
+    Type != "F0" & Metric == "Outcome" ~ " ", 
+    Type != "Segment" & Metric == "Temporal window" ~ " ", 
+    Type != "Categorical" & Metric == "Typicality operationalization" ~ " ", 
+    TRUE ~ Metric)
+    ) %>% 
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 2) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 6) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 12) %>%
+  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 18) %>%
+  mutate(across(-c("Metric", "Type"), ~replace(., is.na(.), " "))) %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
+    linesep = "", align = c("l", "l", "r", "r"), 
+    caption = "Descriptive statistics for model stuff.",
+    label = "categorical-descriptives-table"
+    ) %>% 
+  kableExtra::kable_styling(., font_size = 11)
+
+```
+<!-- END Table 2 -->
 
@@
 On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
+Table \@ref(tab:stats-descriptives-table) provides a summary of the statistical analyses.
+
+<!-- Found effect 
+JVC: this code is ready to go, but not all the rows in the google sheet are 
+filled out (approx. 40 missing)
+--> 
+```{r}
+#| label: found-effect
+#| echo: false
+
+found_effect <- msa_models %>% 
+  select(animal, model_n, found_effect) %>% 
+  na.omit() %>% 
+  mutate(effect = if_else(found_effect == "yes", 1, 0))
+
+atleast_1_effect <- found_effect %>% 
+  group_by(animal) %>% 
+  summarize(total = sum(effect)) %>% 
+  filter(total != 0)
+
+# Overall N of analyses claiming an effect
+n_effects <- sum(found_effect$effect)
+# Percent of effects
+perc_effects <- (n_effects / nrow(msa_models) * 100) %>% round(., 2)
+# N of teams claiming an effect
+n_atleast_1 <- nrow(atleast_1_effect)
+# Percent of teams claiming an effect
+perc_atleast_1 <- (n_atleast_1 / length(unique(msa_models$animal))) * 100
+```
 
@@
 When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
+Of the submitted analyses, `r n_effects` claimed to have found a statistically reliable effect (`r perc_effects`%). 
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) submitting analyses reported at least one found effect.
+
+<!-- Begin Table 3 --> 
+```{r}
+#| label: stats-descriptives-table
+#| results: 'asis'
+tbl_model_desc %>% 
+  select(Metric, Range, `Mean (SD)`) %>% 
+  filter(Metric != "n. random smooths") %>% 
+  mutate(Metric = str_remove_all(Metric, "n. "), 
+         Metric = str_to_sentence(Metric)) %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
+    linesep = "", align = c("l", "c", "r"), 
+    caption = "Descriptive statistics for statistical analyses included in the 
+    meta-analysis (n = 30).",
+    label = "stats-descriptives-table"
+    ) %>% 
+  kableExtra::kable_styling(., font_size = 11)
+```
+<!-- END: Table -->
 
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:team-descriptives-table)).
 The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).

### 2022-09-21 RR_manuscript/Draft_RR.tex

--- 2022-09-19 RR_manuscript/Draft_RR.tex
@@
 These are the teams that are included in this study.
-Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
 
-Submitting teams consisted of an average of 3.63 individual analysts (SD = 2.8).
+Submitting teams consisted of an average of 3.6 individual analysts (SD = 2.8).
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
 Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
-The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92 with an average of 69.2 (SD = 11.3).
+The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
 We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of (SD: ) models per team.
+Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 
-\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams and models included in the 
+\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams included in the 
     meta-analysis (n = 30).}
@@
 \fontsize{11}{13}\selectfont
-\begin{tabular}[t]{llcr}
+\begin{tabular}[t]{lcr}
 \toprule
-Descriptives & Metric & Range & Mean (SD)\\
+Metric & Range & Mean (SD)\\
 \midrule
-Teams & Overall peer review rating & 39--89 & 69.95 (14.34)\\
- & Acoustic analysis rating & 41--88 & 71.51 (13.92)\\
- & Prior belief in $H_{1}$ & 48--92 & 69.19 (11.33)\\
- & Self-report statistical ability & 33--93 & 69.46 (16.52)\\
- & Years since PhD & -4--12 & 4.77 (4.16)\\
- &  &  & \\
-Models & n. coefficients & 1--11 & 3.50 (2.75)\\
- & n. models & 1--16 & 3.67 (3.44)\\
- & n. predictors & 1--4 & 1.59 (0.85)\\
- & n. random effects & 0--10 & 2.47 (2.05)\\
- & n. random intercepts & 0--10 & 1.91 (1.77)\\
- & n. random slopes & 0--4 & 0.63 (1.07)\\
- & n. random smooths & 0--0 & 0.00 (0.00)\\
- & n. terms & 1--4 & 1.78 (1.08)\\
+Team size & 1.0--12.0 & 3.6 (2.8)\\
+Overall peer review rating & 39.0--88.7 & 70.0 (14.3)\\
+Acoustic analysis rating & 41.2--88.3 & 71.5 (13.9)\\
+Prior belief in $H_{1}$ & 48.5--92.0 & 69.2 (11.3)\\
+Self-report statistical ability & 33.0--93.3 & 69.5 (16.5)\\
+Years since PhD & -3.8--12.4 & 4.8 (4.2)\\
+n. models & 1--16 & 3.7 (3.4)\\
 \bottomrule
@@
 \end{table}
-\vspace{0.2in}
 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
+Table \ref{tab:categorical-descriptives-table} provides a summary of the acoustic analyses.
+
+\vspace{0.2in}
+\begin{table}
+
+\caption{\label{tab:categorical-descriptives-table}Descriptive statistics for model stuff.}
+\centering
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{llrr}
+\toprule
+Metric & Type & n & \%\\
+\midrule
+Framework & Frequentist & 86 & 82.7\\
+ & Bayesian & 18 & 17.3\\
+ &  &  & \\
+Model & Linear model & 102 & 98.1\\
+ & GAM & 1 & 1.0\\
+ & Other & 1 & 1.0\\
+ &  &  & \\
+Outcome & F0 & 37 & 35.6\\
+ & Duration & 36 & 34.6\\
+ & Intensity & 15 & 14.4\\
+ & Formants & 13 & 12.5\\
+ & Other & 3 & 2.9\\
+ &  &  & \\
+Temporal window & Segment & 47 & 45.6\\
+ & Word & 45 & 43.7\\
+ & Other & 4 & 3.9\\
+ & Sentence & 4 & 3.9\\
+ & Phrase & 3 & 2.9\\
+ &  &  & \\
+Typicality operationalization & Categorical & 75 & 72.8\\
+ & Continuous (mean) & 25 & 24.3\\
+ & Continuous (median) & 3 & 2.9\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 On average, teams that specified random effects, included 2.5 random terms in their models.
+Table \ref{tab:stats-descriptives-table} provides a summary of the statistical analyses.
 
@@
 
+\begin{table}
+
+\caption{\label{tab:stats-descriptives-table}Descriptive statistics for statistical analyses included in the 
+    meta-analysis (n = 30).}
+\centering
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{lcr}
+\toprule
+Metric & Range & Mean (SD)\\
+\midrule
+Coefficients & 1--11 & 3.5 (2.7)\\
+Models & 1--16 & 3.7 (3.4)\\
+Predictors & 1--4 & 1.6 (0.9)\\
+Random effects & 0--10 & 2.5 (2.1)\\
+Random intercepts & 0--10 & 1.9 (1.8)\\
+Random slopes & 0--4 & 0.6 (1.1)\\
+Terms & 1--4 & 1.8 (1.1)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{review-ratings}{%
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:team-descriptives-table}).
 The mean rating of the statistical analysis is 73.8 (SD = 14.1).

### 2022-09-22 RR_manuscript/Draft_RR.Rmd

@@
 The results section is divided into three parts.
-We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by other teams.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
 Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
@@
 
+The research compendium of study contains all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
+
 ## Descriptive statistics
@@
 `r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
-One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up.
+One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "[T]he project's approach is too much top-down instead of bottom-up.
 [...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
-We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+We find that this contribution clearly speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
 Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
-The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
+
+`r team_desc_list$Final$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analysis by the established deadline.
 These are the teams that are included in this study.
-
 Submitting teams consisted of an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` individual analysts (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`).
-Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
+Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
 Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
 PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years.
-The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
 We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_team_desc, label, "model_desc_n_models", sd)`) models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", sd)`) models per team.
 Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses. 
@@
 
-`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models obtained acoustic measures at the level of the segment (e.g.
+`r (round(window_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` percent of models used acoustic measures taken at the level of the segment (e.g.
 comparing the acoustic profile of a vowel), `r round(window_n[[2,1]],2) * 100`\% from the word level (e.g.
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
-For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
 The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
@@
 `r round(framework_n[[1,1]],2) * 100`\% were run within a Bayesian framework.
-While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%, teams differed drastically in how they accounted for dependencies within the data.
+While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%), teams differed drastically in how they accounted for dependencies within the data.
 <!-- TODO: The calculations in these sections are based on the INCLUDED models only.
@@
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
-The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects [e.g., @gelman2006data; @schielzeth2009conclusions]. 
+An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
 `r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
@@
 When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
-Of the submitted analyses, `r n_effects` claimed to have found a statistically reliable effect (`r perc_effects`%). 
-`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) submitting analyses reported at least one found effect.
+Of the 104 submitted models, `r n_effects` include a statistically reliable effect (`r perc_effects`%). 
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect.
 
@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
-First, we report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
+First, we report on the between-team variability estimate (i.e.
+the meta-analytic group-level standard deviation $$\sigma_{\alpha_{\text{t}}}$$), which is the focus of this study, followed by the meta-analytic estimate (i.e.
+the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
 
@@
 compelling_count_nest <- table(post_meta_nest$compelling)
-
+```
+
+### Between-team variability
+
+The primary aim of this analysis is to assess the degree of between-team variability.
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$).
+
+According to the preregistered meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
+
+**Non-preregistered**. However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption. 
+To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`), which allows us to estimate both the between-team variation along with the between-analysis variation.
+This analysis was not preregistered and should thus be interpreted with caution.^[Note that before running this model we have also run one with just model ID as the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.]
+
+<!-- Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
+This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.-->
+
+The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about ±0.1 standard units and 95% probability.
+The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
+Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than variability across individual teams.
+We come back to this important observation later.
+
+### Meta-analytic intercept
+
+After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realisation of sentences with adjective-noun combinations.
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g. by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+
+**Non-preregistered**. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
+In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, $\beta$ = `r round(meta_intercept_nest[1],3)`).
+This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
+Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
+
+\@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
+Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
+longer duration, higher f0, etc.), as mentioned above.
+When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
+Estimates ranged between `r min(msa_models$estimate)` to `r max(msa_models$estimate)` standard units.
+
+While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
+
+```{r plot-meta1, echo = FALSE, fig.cap="Standardized effect sizes (raw and after shrinkage).", out.width="100%"}
+knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
+```
+
+## Analytic and researcher-related predictors
+
+After assessing the variability across teams and models, we now turn to estimating the impact of a series of predictors on the reported standardized effects.
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing].
+
+<!-- TODO: extract and fill in estimates and 95% CrIs as indicated below -->
+Figure \@ref(fig:plot-meta2), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals. 
+The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
+Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
+Interestingly, the model uniqueness, i.e.
+how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
+This suggests that the analysts' results very much depend on their choice of predictors. 
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or formants) and the choice of temporal window affected the results. 
+Panels A and B of Figure \@ref(fig:plot-meta2) display the posterior estimates for the measurement outcome (i.e.
+what acoustic dimension was measured, panel A) and measurement window (i.e.
+what is the unit over which the outcome was measured, panel B).
+If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
+If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
+Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
+In other words, depending on the choice of measurement and the measurment window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+
+```{r plot-meta2, echo = FALSE, fig.cap="The effects of analytic and researcher-related predictors on the reported standardized effect sizes.", out.width="100%"}
+knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
+```
+
+# Discussion
+
+## Summary
+
+We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech data set to answer the same research question: *Do 
+speakers acoustically modify utterances to signal atypical word combinations?*
+In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and chose appropriate model predictors, and construct appropriate statistical models to answer the research question.
+This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
+The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing their statistical model.
+By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
+Note that this is a conservative estimate of the number of different analytical choices for our research question (ignoring further degrees of freedom like e.g.
+acoustic parameter extraction, outlier treatment, and transformations).
+
+To make the results somewhat more concrete, we will ground them in actual acoustic measures.
+We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, fundamental frequency and intensity, taken from different time windows. 
+These standard deviations can be considered as an indication of the variability in said acoustic measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.
+
+For example, for those analyses that investigated the duration of segments (e.g.
+the duration of the second vowel in *Banana*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
+The reported effect estimates from teams varied between `r min(msa_models$estimate)` and `r max(msa_models$estimate)` standard units which corresponds to duration values ranging from `r min(msa_models$estimate) * 33.4 ` to `r max(msa_models$estimate) * 51.4`.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, time 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms].
+
+While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
+For example, previous studies reported statistically robust effects of 8 and 16 ms [@coretta2019], down to 4.5 ms [@nowak2006]. 
+Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which involves duration effects ranging 7-15 ms [@nicenboim2018using]. 
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].
+
+Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction is thus concerning and might lead to opposing theoretical conclusions.
+
+```{r msa-sd}
 # MSA SD ----
@@
     across(starts_with("sd_"), ~.x * meta_sd_clo * 1.96),
-    ci = "low"
+    ci = "lower"
   ) %>%
@@
     across(starts_with("sd_"), ~.x * meta_sd_chi * 1.96),
-    ci = "high"
+    ci = "upper"
   ) %>%
@@
   pivot_wider(names_from = c(ci, sd), values_from = value) %>%
-  unite("low", low_sd_min, low_sd_max, sep = "-") %>%
-  unite("high", high_sd_min, high_sd_max, sep = "-") %>%
+  unite("lower", lower_sd_min, lower_sd_max, sep = "-") %>%
+  unite("upper", upper_sd_min, upper_sd_max, sep = "-") %>%
   mutate(
     unit = c("ms", "ms", "hz", "hz", "dB", "dB")
-  )
-```
-
-### Between-team variability
-
-The primary aim of this analysis is to assess the degree of between-team.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$).
-
-According to the preregistered meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
-
-**Non-preregistered**. However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption. 
-To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`), which allows us to estimate both the between-team variation along with the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.[^Note that before this we have also run a model with just model ID as the only (non-nested) group-level effect.
-The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.]
-
-<!-- Based on the first non-preregistered model, the group-level standard deviation for model ID is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the deviations of any individual analysis model from the meta-analytic effect estimate range between ±0.22 to ±0.3 (0.11 * 2, 0.15 * 2) in standard units.-->
-
-The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
-The posterior 95% CrI for between-analysis variability (nested in teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
-Taken these two models together, it appears as if the variability of reported effects between any model (within team or across) is substantially larger than variability across teams.
-We come back to this important observation later.
-
-### Meta-analytic intercept
-
-After assessing the variation between teams and analyses, we now turn towards the meta-analytic estimate of the effect of typicality on acoustic parameters.
-The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
-In other words, and from a very naive statistical perspective, our best guess is that speakers do not encode typicality in the acoustic signal (e.g.
-by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
-
-**Non-preregistered**. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as random effects.
-In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_nest[1],3)`).
-This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
-Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
-
-(ref:meta_plot1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
-Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
-longer duration, higher f0, etc.), as mentioned above.
-When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
-Estimates ranged between `r min(msa_models$estimate)` to `r max(msa_models$estimate)` standard units.
-
-While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
-
-```{r plot-meta1, echo = FALSE, fig.cap="(ref:metaPlot1)", out.width="100%"}
-knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
-```
-
-## Analytic and researcher-related predictors
-
-After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the observed variation.
-There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing]?
-
-<!-- TODO:extract and fill in estimates and 95% CrIs as indicated below -->
-(ref:meta_plot1), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals. 
-The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
-Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
-Interestingly, the model uniqueness, i.e.
-how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
-This suggests that the analysts' results very much depend on their choice of predictors. 
-Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or formants) and the choice of temporal window affected the results. 
-(ref:meta_plot1) displays the posterior estimates for the measurement outcome (i.e.
-what acoustic dimension was measured, panel A) and measurement window (i.e.
-what is the unit over which the outcome was measured, panel B).
-If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
-If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
-Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
-In other words, depending on the choice of measurement and the measurment window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
-
-```{r plot-meta2, echo = FALSE, fig.cap="(ref:metaPlot2)", out.width="100%"}
-knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
-```
-
-# Discussion
-
-## Summary
-
-We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech data set to answer the same research question: *Do 
-speakers acoustically modify utterances to signal atypical word combinations?*.
-In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
-This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
-Analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing their statistical model, amounting to `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations.
-Note that this is a conservative estimate of the multiverse of analytical decisions for our research question (ignoring further degrees of freedom like e.g.
-acoustic parameter extraction, outlier treatment, and transformations).
-
-To gain a better intuition about the amount of variability we will ground the results in actual acoustic measures.
-We calculated how much raw data measures for duration, fundamental frequency and intensity varied within teams (by extracting their standard deviation). 
-Consider them an indication of how much said outcome measures generally vary after being extracted from the signal (see xx for an overview <!-- TODO: add link to a vignette-->). 
-We can now use these value of variation and interpret the meta-analytic estimates relative to it.
-For example, for those analyses that analyzed the duration of segments (e.g.
-the duration of the stressed vowel in banAna), duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values.
-The reported effect estimates from teams varied between `r min(msa_models$estimate)` and `r max(msa_models$estimate)` standard units which corresponds to duration values ranging from `r min(msa_models$estimate) * 33.4 ` to `r max(msa_models$estimate) * 51.4`.
-If we are more conservative and only convert the meta-analytic estimates of between-analysis variation, we obtain an estimate of between-team variability in milliseconds that ranges from `r round(3.8*1.96, 1)` to `r round(7.7*1.96, 1)` (at 95% credibility).^[minimum SD of duration measures multiplied by lower 95% CrI of meta analysis: $33.4 * 0.11 = 3.8$ ms; maximum SD of duration measures multiplied by upper 95% CrI of of meta analysis: $51.4 * 0.15 = 7.7$ ms].
-
-While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, XXms is considered the just noticeable difference, i.e.
-the threshold under which human are claimed not to be able to distinguish them {REF}.
-<!-- TODO: Stefano add ref here and values from your work-->
-<!-- TODO: Add a second possible phenomenon from articulation-->
-Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which surrounds duration effects ranging from 7-15ms [@nicenboim2018using]. 
-This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].  
-The fact that there seems to be idios
-Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction is thus concerning and might lead to theoretically completely opposing interpretations.
+  ) %>%
+  rename("temporal window" = "temporal_window")
+```
 
 ```{r}
-#msa_sd_sd
-```
-
-<!-- TODO (SC): Add table with different outcomes, means (?) and SDs plus estimated deviations based on ±0.22/0.33 SDs. -->
-
-```{r}
-#knitr::kable(msa_sd, digits = 1)
-```
-
-And this variation seems somewhat random. 
+#| label: msa-sd-table
+#| results: 'asis'
+knitr::kable(msa_sd_sd, format = "latex", booktabs = T, escape = F, 
+  linesep = "", 
+  caption = "Estimated 95 per-cent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.",
+  label = "msa-sd-table"
+  ) %>% 
+kableExtra::kable_styling(., font_size = 11)
+```
+
+Furthermore, this variation does not seem to be systematic.
 For example, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
@@
 The observed variation was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams. 
-Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+Analyses received overall high peer-ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+
 These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many, @breznau2021observing].
-Following @breznau2021observing, we are bound to conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions."[p.9].
-Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
+Following @breznau2021observing [p.
+9], we are bound to conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions".
+Idiosyncratic variation across researchers might be a fact of life which we have to acknowledge and integrate into how we evaluate and present evidence.
 
@@
 Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in. 
-Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
+Some of these choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
 For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
-This asymmetry can have several causes.
+
+The asymmetry observed in the effect direction of different measurements can have several causes.
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Since we do not know the truth and our best guess based on the meta analysis suggest no relationship, this remains speculative.
+
 Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many researchers targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
+Many analysts that participated in this study targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
 @grice2017integrating; @turnbull2017role].
-Moreover, prior work as actually suggested a relationship between typicality and f0 [e.g. @dimitrova2008prosodic; @dimitrova2009did]. 
-Researchers might have heard about those findings, nudging their analysis choices slightly into a particular direction.
+Moreover, prior work has actually suggested a relationship between typicality and f0 [e.g. @dimitrova2008prosodic; @dimitrova2009did]. 
+Participating analysts might have been aware of those findings, which might have, subconsciously of otherwise, nudged their choices into one particular direction.
+
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
@@
 This is an important observation when put into context of the fact that most teams submitted many different models.
+
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for [@tukey1953].
-<!-- TR: couldnt find bibtex of tukey: Tukey, J. W. (1953). The problem of multiple comparisons. Multiple comparisons. 
-JVC: I found it as an unpublished report and added tukey1953 to the refs file. Not sure if that is better than [Tukey 1953, as cited in @benjamini1995controlling] or not.-->
-It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false] while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
-Fields such as the speech sciences that advance their theories based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for [@tukey1953].
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false], while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
+Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., @vazire2017quality, @fidler2018reproducibility].
-One of the suggested paths forward is for researchers to directly replicate previous study more often [e.g., @open2015estimating; @camerer2018evaluating].
+One of the suggested paths forward is for researchers to directly replicate previous studies more often [e.g., @open2015estimating; @camerer2018evaluating].
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, the quantitative sciences are in an inference crisis [@rotello2015more; @starns2019assessing].
-Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, peer ratings also suggest that they considered most of these alternative approaches acceptable.
+Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
+As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
 
-A desired outcome of knowing that different butc reasonable measurement choices or statistical approaches might lead to  different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to  different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
-<!-- TODO: add ref to "process and statistical model" in McElreath 
-JVC: added @mcelreath2020 to bib file. -->
+
 We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
 Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
-
-<!-- TR: This preceding section rocks IMO -->
 
@@
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat, EMU: @winkelmann2017emu].
-
-<!-- TODO: MFA, Formant tracking etc -->
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat, EMU: @winkelmann2017emu, the Montreal Forced Aligner @mcauliffe2017, ].
 
 Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
-Crowd-source projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
 This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
 
-Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
-This approach is called "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
+Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+This approach is called a "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
 
@@
 Crowd-sourcing is limited by the sampled analysts and their biases.
-Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
+Multiverse analyses are limited even further by the one group of researchers who define possible analytic pathways.
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
 in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved by mathematically formalizing verbal expectations  or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+This can be achieved, for example, by mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
@@
 Our study has several limitations that need to be considered when evaluating our results.
-Importantly, there is potential for bias. 
-The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+
+The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
 We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
-This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom. 
+This might have biased our own judgement during the analysis which itself came with many researcher degrees of freedom.
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable. 
-However, our results should be independently re-analysed and replicated using a different research question.
+We invite other researchers to re-analyse and try to replicate our results using a different research question.
+
 Moreover, our sample is an opportunity sample. 
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
-While the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate for example the impact of certain predictors reliably.
-Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty. 
-This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+While the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
+Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+
+This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has].
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
-In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @fox2021open]
-Researchers do not analyse data in a vaccuum.
-It is important recognize and disclose one’s positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
-Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
-Beyond the potential for bias, our study lacks generalizability. 
+
+In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018, @darwin2020, @fox2021open].
+Researchers do not analyse data in a vacuum.
+It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
+
+Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find is the variability that we have observed.
+
+Finally, our study focussed on the speech sciences.
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
@@
 While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods rather than quantitatively.
-It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are investigated using qualitative methods rather than quantitatively.
+It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
 
@@
 
-In recent efforts several studies have highlighted the large degree of analytic flexibility in data analysis. 
+In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
 When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
-This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that invites bias and might weaken the strength of confidence in the published literature.
-Going beyond previous empirical studies, the current paper looked at many speech production analyses. 
-Speech is a multidimensional signal that allows for great flexibility because the primary data lend themselves to a variety of possible operationalizations. 
-30 teams of speech scientists analyzed the same data set. 
-Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical approaches.
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.
+
+Going beyond previous empirical studies, the current paper looked at many analyses of speech data.
+Speech is a multidimensional signal that allows for great flexibility because it lend itself to a variety of possible operationalizations.
+In this study, 30 teams of speech scientists analyzed the same data set.
+Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
 Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
-Quantitatively, the between-team and between-analysis variation of estimates is so large that it crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio mechanical thresholds.
+Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical thresholds.
+
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
 Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction.
-That together with the large between-analysis variation and the tendency to test the same research question on multiple outcome variables suggest that the vast plurality of acceptable analysis approaches is expected to frequently lead to inconclusive results.
-We suggest that fields that base their scientific claims on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and mulitverse analyses when evaluating epistomologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by formalisation and computational models.
+That taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalisation and computational modelling.
 

### 2022-09-22 RR_manuscript/Draft_RR.tex

@@
 The results section is divided into three parts.
-We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings of these two as obtained by other teams.
+We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
 Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
+
+The research compendium of study contains all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
 
@@
 Fifty-four of the signed-up teams dropped out during the analysis phase.
-One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``The reason is that {[}\ldots{]} the project's approach is too much top-down instead of bottom-up.
+One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``{[}T{]}he project's approach is too much top-down instead of bottom-up.
 {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
-We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+We find that this contribution clearly speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
 Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
-The remaining 30 teams submitted their analysis by the established deadline.
+
+Thirty teams submitted their analysis by the established deadline.
 These are the teams that are included in this study.
-
 Submitting teams consisted of an average of 3.6 individual analysts (SD = 2.8).
-Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the distribution of the data to the teams.
+Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
 Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
-The analysts' prior belief in the effect under investigation on a scale from 0 to 100 ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
 We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of (SD: ) models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
 Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 
-Forty-five percent of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
+Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
-For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in a myriad of ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
 The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
@@
 17\% were run within a Bayesian framework.
-While teams almost exclusively used linear models to analyze their data (98\%, teams differed drastically in how they accounted for dependencies within the data.
+While teams almost exclusively used linear models to analyze their data (98\%), teams differed drastically in how they accounted for dependencies within the data.
 
 The data contains several dependencies between data points, with multiple data points coming from the same subject and with multiple data points being associated with the same adjective or noun.
-The appropriate way to account for this non-independence is by using multi-level models and specifying so-called random effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}.
+An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
 8\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
@@
 When considering both acoustic and statistical analysis, we have found a grand total of 104, i.e.~each submitted analysis was unique.
-Of the submitted analyses, 37 claimed to have found a statistically reliable effect (21.76\%).
-Nine teams out of the thirty (30\%) submitting analyses reported at least one found effect.
+Of the 104 submitted models, 37 include a statistically reliable effect (21.76\%).
+Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect.
 
@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
-First, we report on the between-team variability estimate, which is the focus of this study, followed by the meta-analytic intercept estimate.
+First, we report on the between-team variability estimate (i.e.~the meta-analytic group-level standard deviation \[\sigma_{\alpha_{\text{t}}}\]), which is the focus of this study, followed by the meta-analytic estimate (i.e.~the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
 
@@
 
-The primary aim of this analysis is to assess the degree of between-team.
+The primary aim of this analysis is to assess the degree of between-team variability.
 As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)).
@@
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}), which allows us to estimate both the between-team variation along with the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.{[}\^{}Note that before this we have also run a model with just model ID as the only (non-nested) group-level effect.
-The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.{]}
+This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before running this model we have also run one with just model ID as the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.}
 
-The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
-The posterior 95\% CrI for between-analysis variability (nested in teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
-Taken these two models together, it appears as if the variability of reported effects between any model (within team or across) is substantially larger than variability across teams.
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about ±0.1 standard units and 95\% probability.
+The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
+Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than variability across individual teams.
 We come back to this important observation later.
@@
 
-After assessing the variation between teams and analyses, we now turn towards the meta-analytic estimate of the effect of typicality on acoustic parameters.
+After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realisation of sentences with adjective-noun combinations.
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
-In other words, and from a very naive statistical perspective, our best guess is that speakers do not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
 
-\textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as random effects.
-In this non-preregistered model, the meta-analytic intercept estimate is between -0.013 and 0.04 standard units (95\% CrI, mean = 0.014).
+\textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
+In this non-preregistered model, the meta-analytic intercept estimate is between -0.013 and 0.04 standard units (95\% CrI, \(\beta\) = 0.014).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
@@
 
-(ref:meta\_plot1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
+\ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{Standardized effect sizes (raw and after shrinkage).}\label{fig:plot-meta1}
 \end{figure}
@@
 
-After assessing the variability across teams and models, we now turn toward estimating the impact of a series of predictors on the observed variation.
-There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}?
+After assessing the variability across teams and models, we now turn to estimating the impact of a series of predictors on the reported standardized effects.
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}.
 
-(ref:meta\_plot1), panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
+Figure \ref{fig:plot-meta2}, panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
@@
 Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~f0 or formants) and the choice of temporal window affected the results.
-(ref:meta\_plot1) displays the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which the outcome was measured, panel B).
+Panels A and B of Figure \ref{fig:plot-meta2} display the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which the outcome was measured, panel B).
 If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{(ref:metaPlot2)}\label{fig:plot-meta2}
+\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{The effects of analytic and researcher-related predictors on the reported standardized effect sizes.}\label{fig:plot-meta2}
 \end{figure}
@@
 We gave 30 analyst teams the same speech data set to answer the same research question: \emph{Do
-speakers acoustically modify utterances to signal atypical word combinations?}.
-In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
+speakers acoustically modify utterances to signal atypical word combinations?}
+In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and chose appropriate model predictors, and construct appropriate statistical models to answer the research question.
 This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
-Analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2444 possible unique combinations.
-Note that this is a conservative estimate of the multiverse of analytical decisions for our research question (ignoring further degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations).
+The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model.
+By multiplying the numbers of acoustic and model specifications, there are in principle 2444 possible unique combinations.
+Note that this is a conservative estimate of the number of different analytical choices for our research question (ignoring further degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations).
 
-To gain a better intuition about the amount of variability we will ground the results in actual acoustic measures.
-We calculated how much raw data measures for duration, fundamental frequency and intensity varied within teams (by extracting their standard deviation).
-Consider them an indication of how much said outcome measures generally vary after being extracted from the signal (see xx for an overview ).
-We can now use these value of variation and interpret the meta-analytic estimates relative to it.
-For example, for those analyses that analyzed the duration of segments (e.g.~the duration of the stressed vowel in banAna), duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values.
+To make the results somewhat more concrete, we will ground them in actual acoustic measures.
+We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, fundamental frequency and intensity, taken from different time windows.
+These standard deviations can be considered as an indication of the variability in said acoustic measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.
+
+For example, for those analyses that investigated the duration of segments (e.g.~the duration of the second vowel in \emph{Banana}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
 The reported effect estimates from teams varied between -0.6544004 and 0.9885856 standard units which corresponds to duration values ranging from -21.856972 to 50.8132988.
-If we are more conservative and only convert the meta-analytic estimates of between-analysis variation, we obtain an estimate of between-team variability in milliseconds that ranges from 7.4 to 15.1 (at 95\% credibility).\footnote{minimum SD of duration measures multiplied by lower 95\% CrI of meta analysis: \(33.4 * 0.11 = 3.8\) ms; maximum SD of duration measures multiplied by upper 95\% CrI of of meta analysis: \(51.4 * 0.15 = 7.7\) ms}.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms}.
 
 While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, XXms is considered the just noticeable difference, i.e.~the threshold under which human are claimed not to be able to distinguish them \{REF\}.
-Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which surrounds duration effects ranging from 7-15ms \citep{nicenboim2018using}.
-This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.\\
-The fact that there seems to be idios
-Expecting random variation between different analysts of 7 to 15 in one or the other direction is thus concerning and might lead to theoretically completely opposing interpretations.
+For example, previous studies reported statistically robust effects of 8 and 16 ms \citep{coretta2019}, down to 4.5 ms \citep{nowak2006}.
+Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which involves duration effects ranging 7-15 ms \citep{nicenboim2018using}.
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.
 
-And this variation seems somewhat random.
+Expecting random variation between different analysts of 7 to 15 in one or the other direction is thus concerning and might lead to opposing theoretical conclusions.
+
+\begin{table}
+
+\caption{\label{tab:msa-sd-table}Estimated 95 per-cent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.}
+\centering
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{lllll}
+\toprule
+outcome & temporal window & lower & upper & unit\\
+\midrule
+duration & segment & 7.4-11.4 & 10-15.4 & ms\\
+duration & word & 7.2-26.5 & 9.8-35.8 & ms\\
+f0 & segment & 8.9-9.8 & 12-13.3 & hz\\
+f0 & word & 0.9-10.4 & 1.2-14.1 & hz\\
+intensity & segment & 0.7-1.6 & 1-2.1 & dB\\
+intensity & word & 0.8-0.9 & 1-1.2 & dB\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+Furthermore, this variation does not seem to be systematic.
 For example, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
@@
 The observed variation was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
-Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+Analyses received overall high peer-ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
+
 These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
-Following \citet{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''{[}p.9{]}.
-Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.
+Following \citet[p.~9]{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions''.
+Idiosyncratic variation across researchers might be a fact of life which we have to acknowledge and integrate into how we evaluate and present evidence.
 
@@
 Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in.
-Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
+Some of these choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
 For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
-This asymmetry can have several causes.
+
+The asymmetry observed in the effect direction of different measurements can have several causes.
 First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
-Since we do not know the truth and our best guess based on the meta analysis suggest no relationship, this remains speculative.
+
 Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many researchers targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
-Moreover, prior work as actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
-Researchers might have heard about those findings, nudging their analysis choices slightly into a particular direction.
+Many analysts that participated in this study targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Moreover, prior work has actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
+Participating analysts might have been aware of those findings, which might have, subconsciously of otherwise, nudged their choices into one particular direction.
+
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
@@
 This is an important observation when put into context of the fact that most teams submitted many different models.
+
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep{tukey1953}.
-It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
-Fields such as the speech sciences that advance their theories based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for \citep{tukey1953}.
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
+Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
 
@@
 The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[e.g.,][\citet{fidler2018reproducibility}]{vazire2017quality}.
-One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
+One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, the quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
-Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, peer ratings also suggest that they considered most of these alternative approaches acceptable.
+Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
+As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
 Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.
 
-A desired outcome of knowing that different butc reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
+A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
 The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
+
 We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
@@
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}]{boersma2021praat}.
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}, the Montreal Forced Aligner \citet{mcauliffe2017},]{boersma2021praat}.
 
 Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
-Crowd-source projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
 This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
 
-Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
-This approach is called ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
+Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+This approach is called a ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
 
@@
 Crowd-sourcing is limited by the sampled analysts and their biases.
-Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
+Multiverse analyses are limited even further by the one group of researchers who define possible analytic pathways.
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+This can be achieved, for example, by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 Our study has several limitations that need to be considered when evaluating our results.
-Importantly, there is potential for bias.
-The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+
+The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
 We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
-This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom.
+This might have biased our own judgement during the analysis which itself came with many researcher degrees of freedom.
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
-However, our results should be independently re-analysed and replicated using a different research question.
+We invite other researchers to re-analyse and try to replicate our results using a different research question.
+
 Moreover, our sample is an opportunity sample.
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
-While the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate for example the impact of certain predictors reliably.
-Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
-This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+While the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
+Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+
+This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
@@
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
-In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{fox2021open}
-Researchers do not analyse data in a vaccuum.
+
+In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][\citet{darwin2020}, \citet{fox2021open}]{jafar2018}.
+Researchers do not analyse data in a vacuum.
 It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
-Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.
-Beyond the potential for bias, our study lacks generalizability.
+
+Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find is the variability that we have observed.
+
+Finally, our study focussed on the speech sciences.
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
@@
 
-In recent efforts several studies have highlighted the large degree of analytic flexibility in data analysis.
+In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
 When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
-This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that invites bias and might weaken the strength of confidence in the published literature.
-Going beyond previous empirical studies, the current paper looked at many speech production analyses.
-Speech is a multidimensional signal that allows for great flexibility because the primary data lend themselves to a variety of possible operationalizations.
-30 teams of speech scientists analyzed the same data set.
-Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical approaches.
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.
+
+Going beyond previous empirical studies, the current paper looked at many analyses of speech data.
+Speech is a multidimensional signal that allows for great flexibility because it lend itself to a variety of possible operationalizations.
+In this study, 30 teams of speech scientists analyzed the same data set.
+Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
 Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
-Quantitatively, the between-team and between-analysis variation of estimates is so large that it crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio mechanical thresholds.
+Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical thresholds.
+
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
 Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction.
-That together with the large between-analysis variation and the tendency to test the same research question on multiple outcome variables suggest that the vast plurality of acceptable analysis approaches is expected to frequently lead to inconclusive results.
-We suggest that fields that base their scientific claims on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and mulitverse analyses when evaluating epistomologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by formalisation and computational models.
+That taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalisation and computational modelling.
 

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
add one giant table for feedback

@@
    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
-    Range = glue::glue("{min}--{max}"), 
+    Range = glue::glue("{min} -- {max}"), 
     Metric = case_when(
@@
     `Mean (SD)` = glue::glue("{avg} ({sd})"), 
-    Range = glue::glue("{min}--{max}"), 
+    Range = glue::glue("{min} -- {max}"), 
     Metric = case_when(
@@
 At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", sd)`) models per team.
-Table \@ref(tab:team-descriptives-table) provides a summary of the contributing teams and their analyses. 
+Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 #| results: 'asis'
-bind_rows(
-  tbl_team_desc, 
-  filter(tbl_model_desc, label == "model_desc_n_models")
-  ) %>% 
+#| eval: false
+  tbl_team_desc %>% 
   select(Metric, Range, `Mean (SD)`) %>% 
   knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "c", "r"), 
+    linesep = "", align = c("l", "r", "r"), 
     caption = "Descriptive statistics for teams included in the 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
-Table \@ref(tab:categorical-descriptives-table) provides a summary of the acoustic analyses.
+Table \@ref(tab:descriptives-table) provides a summary of the acoustic analyses.
 
@@
 #| results: 'asis'
+#| eval: false
 
@@
 On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
-Table \@ref(tab:stats-descriptives-table) provides a summary of the statistical analyses.
+Table \@ref(tab:descriptives-table) provides a summary of the statistical analyses.
 
@@
 #| label: found-effect
-#| echo: false
 
@@
 #| results: 'asis'
+#| eval: false
 tbl_model_desc %>% 
@@
   knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "c", "r"), 
+    linesep = "", align = c("l", "l", "r"), 
     caption = "Descriptive statistics for statistical analyses included in the 
@@
 
+```{r}
+#| label: descriptives-table
+#| results: 'asis'
+library(kableExtra)
+bind_rows(
+  tbl_team_desc %>% 
+    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
+  tbl_categorical_desc %>% 
+    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
+    mutate(val1 = glue::glue("{val1}")), 
+  tbl_model_desc %>% 
+    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
+) %>% 
+  mutate(order = c(
+    1, 6, 5, 4, 3, 2, 
+    21, 20, 23, 22, 24, 
+    8, 7, 10, 9, 11, 
+    16, 15, 12, 14, 13, 
+    17, 18, 19, 
+    26, 25, 27, 28, 29, 30, 31, 32
+    )
+  ) %>% 
+  arrange(order) %>% 
+  select(-order) %>% 
+  mutate(desc = str_replace_all(desc, "team_desc", " "), 
+    desc = str_replace_all(desc, "model_desc", "N"), 
+    desc = case_when(
+      Metric != "n. models" & desc == "N" ~ " ", 
+      Metric != "Frequentist" & desc == "Framework" ~ " ", 
+      Metric != "Linear model" & desc == "Model" ~ " ", 
+      Metric != "F0" & desc == "Outcome" ~ " ", 
+      Metric != "Segment" & desc == "Temporal window" ~ " ", 
+      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
+      TRUE ~ desc)
+    ) %>% 
+  filter(Metric != "n. random smooths") %>% 
+  mutate(Metric = str_remove_all(Metric, "n. "), 
+         Metric = str_to_sentence(Metric)) %>% 
+  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
+    `\\bf{Mean (SD)}` = val2) %>% 
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
+    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
+  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
+    `\\bf{Mean (SD)}` = " ",  .before = 14) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
+    `\\bf{Mean (SD)}` = " ", .before = 20) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
+    `\\bf{Mean (SD)}` = " ", .before = 24) %>%
+  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 25) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
+    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
+    `\\bf{Mean (SD)}` = " ", .before = 32) %>%
+  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
+    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
+    .before = 33) %>%
+  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
+    longtable = F, linesep = "", 
+    caption = "Descriptive statistics of contributing teams (n = 30), acoustic 
+    analyses, and statistical analyses.",
+    label = "descriptives-table") %>% 
+  kable_styling(full_width = F, latex_options = "scale_down") %>% 
+  add_indent(c(9, 15, 21, 26, 29, 34)) %>% 
+  row_spec(8, hline_after = T) %>% 
+  row_spec(25, hline_after = T)
+```
+
 ### Review ratings
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:team-descriptives-table)).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:descriptives-table)).
 The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).

### 2022-09-23 RR_manuscript/Draft_RR.tex
add one giant table for feedback

@@
 At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
-Table \ref{tab:team-descriptives-table} provides a summary of the contributing teams and their analyses.
+Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
 Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
@@
 \vspace{0.2in}
-\begin{table}
-
-\caption{\label{tab:team-descriptives-table}Descriptive statistics for teams included in the 
-    meta-analysis (n = 30).}
-\centering
-\fontsize{11}{13}\selectfont
-\begin{tabular}[t]{lcr}
-\toprule
-Metric & Range & Mean (SD)\\
-\midrule
-Team size & 1.0--12.0 & 3.6 (2.8)\\
-Overall peer review rating & 39.0--88.7 & 70.0 (14.3)\\
-Acoustic analysis rating & 41.2--88.3 & 71.5 (13.9)\\
-Prior belief in $H_{1}$ & 48.5--92.0 & 69.2 (11.3)\\
-Self-report statistical ability & 33.0--93.3 & 69.5 (16.5)\\
-Years since PhD & -3.8--12.4 & 4.8 (4.2)\\
-n. models & 1--16 & 3.7 (3.4)\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
-Table \ref{tab:categorical-descriptives-table} provides a summary of the acoustic analyses.
+Table \ref{tab:descriptives-table} provides a summary of the acoustic analyses.
 
 \vspace{0.2in}
-\begin{table}
-
-\caption{\label{tab:categorical-descriptives-table}Descriptive statistics for model stuff.}
-\centering
-\fontsize{11}{13}\selectfont
-\begin{tabular}[t]{llrr}
-\toprule
-Metric & Type & n & \%\\
-\midrule
-Framework & Frequentist & 86 & 82.7\\
- & Bayesian & 18 & 17.3\\
- &  &  & \\
-Model & Linear model & 102 & 98.1\\
- & GAM & 1 & 1.0\\
- & Other & 1 & 1.0\\
- &  &  & \\
-Outcome & F0 & 37 & 35.6\\
- & Duration & 36 & 34.6\\
- & Intensity & 15 & 14.4\\
- & Formants & 13 & 12.5\\
- & Other & 3 & 2.9\\
- &  &  & \\
-Temporal window & Segment & 47 & 45.6\\
- & Word & 45 & 43.7\\
- & Other & 4 & 3.9\\
- & Sentence & 4 & 3.9\\
- & Phrase & 3 & 2.9\\
- &  &  & \\
-Typicality operationalization & Categorical & 75 & 72.8\\
- & Continuous (mean) & 25 & 24.3\\
- & Continuous (median) & 3 & 2.9\\
-\bottomrule
-\end{tabular}
-\end{table}
 
@@
 On average, teams that specified random effects, included 2.5 random terms in their models.
-Table \ref{tab:stats-descriptives-table} provides a summary of the statistical analyses.
+Table \ref{tab:descriptives-table} provides a summary of the statistical analyses.
 
@@
 
-\caption{\label{tab:stats-descriptives-table}Descriptive statistics for statistical analyses included in the 
-    meta-analysis (n = 30).}
+\caption{\label{tab:descriptives-table}Descriptive statistics of contributing teams (n = 30), acoustic 
+    analyses, and statistical analyses.}
 \centering
-\fontsize{11}{13}\selectfont
-\begin{tabular}[t]{lcr}
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{llrr}
 \toprule
-Metric & Range & Mean (SD)\\
+\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
 \midrule
-Coefficients & 1--11 & 3.5 (2.7)\\
-Models & 1--16 & 3.7 (3.4)\\
-Predictors & 1--4 & 1.6 (0.9)\\
-Random effects & 0--10 & 2.5 (2.1)\\
-Random intercepts & 0--10 & 1.9 (1.8)\\
-Random slopes & 0--4 & 0.6 (1.1)\\
-Terms & 1--4 & 1.8 (1.1)\\
+ & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
+ & Years since phd & -3.8 -- 12.4 & 4.8 (4.2)\\
+ & Self-report statistical ability & 33.0 -- 93.3 & 69.5 (16.5)\\
+ & Prior belief in $h_{1}$ & 48.5 -- 92.0 & 69.2 (11.3)\\
+ & Acoustic analysis rating & 41.2 -- 88.3 & 71.5 (13.9)\\
+ & Overall peer review rating & 39.0 -- 88.7 & 70.0 (14.3)\\
+ &  &  \vphantom{5} & \\
+\bf{Acoustic analyses} &  & \bf{n} & \bf{\%}\\
+\midrule
+\hspace{1em}Outcome & F0 & 37 & 35.6\\
+ & Duration & 36 & 34.6\\
+ & Intensity & 15 & 14.4\\
+ & Formants & 13 & 12.5\\
+ & Other & 3 & 2.9\\
+ &  &  \vphantom{4} & \\
+\hspace{1em}Temporal window & Segment & 47 & 45.6\\
+ & Word & 45 & 43.7\\
+ & Sentence & 4 & 3.9\\
+ & Phrase & 3 & 2.9\\
+ & Other & 4 & 3.9\\
+ &  &  \vphantom{3} & \\
+\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
+ & Continuous (mean) & 25 & 24.3\\
+ & Continuous (median) & 3 & 2.9\\
+ &  &  \vphantom{2} & \\
+\bf{Statistical analyses} &  & \bf{n} & \bf{\%}\\
+\midrule
+\hspace{1em}Framework & Frequentist & 86 & 82.7\\
+ & Bayesian & 18 & 17.3\\
+ &  &  \vphantom{1} & \\
+\hspace{1em}Model & Linear model & 102 & 98.1\\
+ & Gam & 1 & 1.0\\
+ & Other & 1 & 1.0\\
+ &  &  & \\
+ &  & \bf{Range} & \bf{Mean (SD)}\\
+\hspace{1em}N & Models & 1 -- 16 & 3.7 (3.4)\\
+ & Coefficients & 1 -- 11 & 3.5 (2.7)\\
+ & Predictors & 1 -- 4 & 1.6 (0.9)\\
+ & Random effects & 0 -- 10 & 2.5 (2.1)\\
+ & Random intercepts & 0 -- 10 & 1.9 (1.8)\\
+ & Random slopes & 0 -- 4 & 0.6 (1.1)\\
+ & Terms & 1 -- 4 & 1.8 (1.1)\\
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:team-descriptives-table}).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:descriptives-table}).
 The mean rating of the statistical analysis is 73.8 (SD = 14.1).

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
add report_posterior function, include predictor model estimates and CrIs

@@
   return(val)
+}
+
+# Function for reporting posteriors
+report_posterior <- function(df, param) {
+  # Extract wanted value from model output
+  est  <- df[df$param == param, "estimate"]
+  cis  <- df[df$param == param, "ci"]
+
+  capture.output(
+    paste0("($\\beta$ = ", est, ", 95\\% CrI = ", cis, ")", "\n") %>% 
+      cat()) %>% 
+      paste()
 }
@@
       metric == "size" ~ "Team size", 
-      metric == "years_from_phd" ~ "Years since PhD", 
+      metric == "years_from_phd" ~ "Years after PhD", 
       metric == "stat_rating" ~ "Self-report statistical ability", 
-      metric == "prior_belief" ~ "Prior belief in $H_{1}$", 
+      metric == "prior_belief" ~ "Prior belief", 
       metric == "phon_rating" ~ "Acoustic analysis rating", 
-      metric == "all_rating" ~ "Overall peer review rating"), 
+      metric == "all_rating" ~ "Peer rating"), 
     label = glue::glue("{desc}_{metric}")) %>% 
@@
 compelling_count_nest <- table(post_meta_nest$compelling)
+
+# Load MA with predictors
+# Generate tibble with estimate for printing to prose
+predictors_bm_rintercepts <- 
+  readRDS("./data/meta_analysis/predictors_bm_rintercepts.rds") %>%  
+  as_draws_df() %>% 
+  select(contains("b_")) %>% 
+  pivot_longer(cols = everything(), names_to = "param", values_to = "estimate") %>% 
+  group_by(param) %>% 
+  mean_qi(.width = 0.95) %>% 
+  transmute(param, estimate, lo = .lower, hi = .upper) %>% 
+  mutate_if(is.numeric, specify_decimal, 2) %>% 
+  mutate(param = str_remove_all(param, "b_"), 
+    param = str_remove_all(param, "outcome."), 
+    param = str_remove_all(param, "Mintercept"), 
+    param = str_remove_all(param, "temporal_window."), 
+    ci = glue::glue("[{lo}, {hi}]")
+    )
+
+# report_posterior(predictors_bm_rintercepts, "segment")
 ```
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
-Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI). 
+Neither analysts' prior beliefs in the phenomenon `r report_posterior(predictors_bm_rintercepts, "prior_belief_s")`, nor their seniority in terms of years after completing their PhD `r report_posterior(predictors_bm_rintercepts, "years_from_phd_s")` seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty `r report_posterior(predictors_bm_rintercepts, "all_rating_s")`.
 Interestingly, the model uniqueness, i.e.
-how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
+how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
 This suggests that the analysts' results very much depend on their choice of predictors. 
@@
 Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
-In other words, depending on the choice of measurement and the measurment window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+In other words, depending on the choice of measurement and the measurement window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
 

### 2022-09-23 RR_manuscript/Draft_RR.tex
add report_posterior function, include predictor model estimates and CrIs

@@
  & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
- & Years since phd & -3.8 -- 12.4 & 4.8 (4.2)\\
+ & Years after phd & -3.8 -- 12.4 & 4.8 (4.2)\\
  & Self-report statistical ability & 33.0 -- 93.3 & 69.5 (16.5)\\
- & Prior belief in $h_{1}$ & 48.5 -- 92.0 & 69.2 (11.3)\\
+ & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
  & Acoustic analysis rating & 41.2 -- 88.3 & 71.5 (13.9)\\
- & Overall peer review rating & 39.0 -- 88.7 & 70.0 (14.3)\\
+ & Peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
  &  &  \vphantom{5} & \\
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (ADD EST + 95CrI), nor their seniority in terms of years after completing their PhD (ADD EST + 95CrI) seem to compellingly affect model estimates.
-Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (ADD EST + 95CrI).
-Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (ADD EST + 95CrI).
+Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to compellingly affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
 This suggests that the analysts' results very much depend on their choice of predictors.

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
♻️ - update abstract and institutions

@@
 - name: Stefano Coretta*
-  num: 1
+  num: 1, 2
 - name: Joseph V. Casillas
-  num: 2
+  num: 3
 - name: Timo B. Roettger
-  num: 3
+  num: 4
 address:
 - num: 1
-  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.
+  org: Department of Linguistics and English Language, University of Edinburgh, United Kingdom
 - num: 2
+  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany
+- num: 3
   org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
-- num: 3
+- num: 4
   org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
-In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
-Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses."
+In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question.
+Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects."
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"

### 2022-09-23 RR_manuscript/Draft_RR.tex
♻️ - update abstract and institutions

@@
 
-\author{Stefano Coretta*\affilnum{1}, Joseph V. Casillas\affilnum{2}, Timo B. Roettger\affilnum{3}}
+\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Timo B. Roettger\affilnum{4}}
 
-\affiliation{\affilnum{1}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany.}\\\affilnum{2}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{3}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
+\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
 
@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
-In the present study, we will give the same speech production dataset to N teams of researchers and will ask them to answer the same research question.
-Using Bayesian meta-analytic tools, we will quantify this variability and relate it to predictors related to the analysts and their analyses.
+In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question.
+Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects.
 \end{abstract}

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
♻️ - edit methods phase 1-3; change tense to past

@@
 <!-- TODOLATER: include number of teams when known -->
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study.
+For the present study, 30 analysis teams have received access to the entire data set generated by the production study.
 The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
-The teams will be instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+The teams were instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
-
-In this study, we will follow the procedures proposed by @Parker2020 and @aczel2021.
-The project involves the following five phases:
-
-1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
-2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
-3. \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
-4. \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
-5. \textsc{Write-up}: We will collaboratively produce the final manuscript.
-
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
-The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
+We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
+
+In this study, we followed the procedures proposed by @Parker2020 and @aczel2021.
+The project involved the following five phases:
+
+1. \textsc{Recruitment}: We recruited independent groups of researchers to analyze the data and review others' data analyses.
+2. \textsc{Team Analysis}: We gave researchers access to the speech corpus and let them analyze the data as they saw fit.
+3. \textsc{Review}: We asked reviewers to generate peer-review ratings of the analyses based on methods (not results).
+4. \textsc{Meta-analysis}: We evaluated variability among the different analyses and how different predictors affected the outcomes.
+5. \textsc{Write-up}: We collaboratively produced the final manuscript.
+
+We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
+<!-- The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams. -->
+Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.
 
 The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
-The main repository holds three OSF components, `Data`, `Questionnaires`, and `Cache`, and it is linked to the GitHub repository.
+The repository holds three main OSF components (`Data`, `Teams analyses` and `Questionnaires`), and a link to the project's GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 
-An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts.
-"Join Project" will link to the intake form.]
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
-Social media advertising will be accompanied by a short recruitment form (`recruitment_form.pdf`)
-The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
-All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
-Researchers can choose to work independently or in a small team.
+An online landing page provided a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).
+The project was advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
+Social media advertising was accompanied by a short recruitment form (`recruitment_form.pdf`).
+The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
+All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
+Researchers could choose to work independently or in a small team.
 For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
-Recruitment for this project will commence upon receiving in-principle acceptance.
+Recruitment for this project commenced after having received in-principle acceptance.
 
@@
 For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
-Given the exploratory nature of our study, however, we will sample as many analysts as possible.
-We have received initial expression of interest to participate from more than 200 analysts.
-
-After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
-All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-Informed consent will be obtained as part of the intake form.
+Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
+Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
+We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).
+
+After submitting their analyses, we asked the analysts to also function as peer-reviewers.
+Each team had to review four other analyses.
+All analysts involved share co-authorship on this manuscript and participated in the collaborative process of producing the final manuscript.
+Informed consent was obtained as part of the intake form.
 
@@
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
+The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (`intake_form.pdf`).
 A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
-The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
-To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+We then requested that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+To do so, they were given the data generated by the experiment described in Section [The data set](#s:dataset).
+The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
 These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.
 
-Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
+Once their analysis was complete, they answered a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+They also uploaded their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
 
@@
 
-Each analysis will be evaluated by four different analysts teams who function as peer-reviewers.
-Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
-Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
-The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
-
-The process for a single reviewer will be as follows.
-First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
-To help reviewers calibrate their rating, they will be given the following guidelines:
+Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
+Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
+Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
+The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+
+The process for a single reviewer was as follows.
+First, the reviewer received a description of the methods of a single analysis.
+This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
+The reviewer was then asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+To help reviewers calibrate their rating, they were given the following guidelines:
 
@@
 
-The reviewers will also be given the option to include further comments in a text box for each of the three ratings.
-
-After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
-This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+The reviewers were also given the option to include further comments in a text box for each of the three ratings.
+
+After submitting the review, a methods section from a second analysis was then made available to the reviewer.
+This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
+We have decided to skip this last step due to time constrains.]
 

### 2022-09-23 RR_manuscript/Draft_RR.tex
♻️ - edit methods phase 1-3; change tense to past

@@
 In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
-Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
@@
 
-For the present study, N analysis teams will receive access to the entire data set generated by the production study.
+For the present study, 30 analysis teams have received access to the entire data set generated by the production study.
 The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
-The teams will be instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+The teams were instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
+We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
 
-In this study, we will follow the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
-The project involves the following five phases:
+In this study, we followed the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
+The project involved the following five phases:
 
@@
 \item
-  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
+  \textsc{Recruitment}: We recruited independent groups of researchers to analyze the data and review others' data analyses.
 \item
-  \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
+  \textsc{Team Analysis}: We gave researchers access to the speech corpus and let them analyze the data as they saw fit.
 \item
-  \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
+  \textsc{Review}: We asked reviewers to generate peer-review ratings of the analyses based on methods (not results).
 \item
-  \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
+  \textsc{Meta-analysis}: We evaluated variability among the different analyses and how different predictors affected the outcomes.
 \item
-  \textsc{Write-up}: We will collaboratively produce the final manuscript.
+  \textsc{Write-up}: We collaboratively produced the final manuscript.
 \end{enumerate}
 
-We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
-The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.
+We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
+Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.
 
 The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
-The main repository holds three OSF components, \texttt{Data}, \texttt{Questionnaires}, and \texttt{Cache}, and it is linked to the GitHub repository.
+The repository holds three main OSF components (\texttt{Data}, \texttt{Teams\ analyses} and \texttt{Questionnaires}), and a link to the project's GitHub repository.
 The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.
@@
 
-An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).\footnote{``Questions'' and ``Join Project'' buttons will be functioning when recruitment starts.
-``Join Project'' will link to the intake form.}
-The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
-Social media advertising will be accompanied by a short recruitment form (\texttt{recruitment\_form.pdf})
-The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
-All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
-Researchers can choose to work independently or in a small team.
+An online landing page provided a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).
+The project was advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
+Social media advertising was accompanied by a short recruitment form (\texttt{recruitment\_form.pdf}).
+The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
+All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
+Researchers could choose to work independently or in a small team.
 For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
-Recruitment for this project will commence upon receiving in-principle acceptance.
+Recruitment for this project commenced after having received in-principle acceptance.
 
@@
 For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
-Thus in order to achieve our main goal, i.e.~estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
-Given the exploratory nature of our study, however, we will sample as many analysts as possible.
-We have received initial expression of interest to participate from more than 200 analysts.
+Thus in order to achieve our main goal, i.e.~estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
+Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
+We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).
 
-After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
-All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
-Informed consent will be obtained as part of the intake form.
+After submitting their analyses, we asked the analysts to also function as peer-reviewers.
+Each team had to review four other analyses.
+All analysts involved share co-authorship on this manuscript and participated in the collaborative process of producing the final manuscript.
+Informed consent was obtained as part of the intake form.
 
@@
 
-The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
+The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
 A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
-The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
-To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+We then requested that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+To do so, they were given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
+The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
 These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.
 
-Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
-They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
+Once their analysis was complete, they answered a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
+They also uploaded their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.
 
@@
 
-Each analysis will be evaluated by four different analysts teams who function as peer-reviewers.
-Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
-Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
-The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
+Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
+Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
+The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
 
-The process for a single reviewer will be as follows.
-First, the reviewer will receive a description of the methods of a single analysis.
-This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
-The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
-To help reviewers calibrate their rating, they will be given the following guidelines:
+The process for a single reviewer was as follows.
+First, the reviewer received a description of the methods of a single analysis.
+This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
+The reviewer was then asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
+To help reviewers calibrate their rating, they were given the following guidelines:
 
@@
 
-The reviewers will also be given the option to include further comments in a text box for each of the three ratings.
+The reviewers were also given the option to include further comments in a text box for each of the three ratings.
 
-After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
-This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
-After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.
+After submitting the review, a methods section from a second analysis was then made available to the reviewer.
+This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.\footnote{We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
+We have decided to skip this last step due to time constrains.}
 

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
♻️ - finish editing methods; change tense to past; links to be added

@@
 In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
-<!-- TODOLATER: include number of teams when known -->
 Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
@@
 
-The initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
-We will not conduct confirmatory tests of any a priori hypotheses.
+The initiating authors (SC, JC, TR) conducted the analyses outlined in this section.
+We did not conduct confirmatory tests of any a priori hypotheses.
 We consider our analysis exploratory.
@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.
+We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.
 f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.
@@
 dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
+These summary statistics are reported in \@ref{descr-stats} of the Results section.
 
@@
 
-We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
-
-Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
+We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
+As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
+As we detail in Section \@ref{meta-est}, we have also run further non-preregistered analyses.
+For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.
+
+Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's $d$, might have been inappropriate.
 Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
+Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) and that was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-Factor-level ordering for each categorical variable will mirror that of the original analyses.
-Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
-For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e.
-only the distribution of the data determines the posterior distribution).
-If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
-Model refitting will also constitute a way of validating the reported analyses, a step recommended by @aczel2021.
+Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
+Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
+<!-- TODO: add link to refitting procedure -->
+Details about the refitting procedure can be found at LINK.
 
 The coefficients of the critical predictors (i.e.
-critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models will be used as the \textsc{standardized effect size} ($\eta_i$) of each reported model.
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each standardized effect size as the \textsc{standardized standard error} ($\text{se}_i$).
-This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
-As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
-
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we will conduct a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
-The outcome variable will be the set of standardized effect sizes $\eta_i$.
-The likelihood of $\eta_i$ is assumed to correspond to a normal distribution [@knight2000].
-The analysis teams will be entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
-The standard errors $\text{se}_i$ will be included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The code used to run the model can be found at <https://many-speech-analyses.github.io/suppl/simulations.html>.
+critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models were used as the \textsc{standardized effect size} ($\eta_i$) of each reported model.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we used the standard deviation of each standardized effect size as the \textsc{standardized standard error} ($\text{se}_i$).
+This enabled us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
+As a desired consequence, effect sizes with a greater standard error are weighted less than those with a smaller standard error in the meta-analytic calculations.
+
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
+The outcome variable was the set of standardized effect sizes $\eta_i$.
+The likelihood of $\eta_i$ was assumed to correspond to a normal distribution [@knight2000].
+The analysis teams were entered as a group-level effect (i.e., `(1 | team)`, called *random effect* in the frequentist literature).
+The standard errors $\text{se}_i$ were included as the standard deviation of $\eta_i$ to fit a measurement-error model, as discussed above.
+We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
+We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
+<!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
+The model did not incur in divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
+<!-- TODO: add link to meta-model code -->
+The code used to run the model can be found at <>.
 
@@
 
-The posterior distribution of the population-level intercept $\alpha$ will allow us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
-The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
+The posterior distribution of the population-level intercept $\alpha$ allowed us to estimate the range of probable values of the standardized effect size $\hat{\eta}$.
+The posterior distribution further allowed us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
 Crucially, the posterior distribution of the [group-level standard deviation](.smallcaps) $\sigma_{\alpha_{\text{t}}}$ (i.e.
-the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between the teams' analyses on a standardized scale.
+the standard deviation of the group-level effect of team) allowed us to quantify the degree of variation between the teams' analyses on a standardized scale.
 
@@
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
-
-**Analytic predictors**. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
+As a second step, we investigated the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
+
+**Analytic predictors**. We estimated the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
 
@@
 - *Measure of uniqueness* of individual analyses for the set of predictors in each model [numeric].
-- *Measure of conservativeness* of the model specification, as the number of random/group-level effects included [numeric].
-- *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out [numeric].
-- *Number of models* the teams will report to have run [numeric].
+<!-- - *Measure of conservativeness* of the model specification, as the number of random/group-level effects included [numeric]. -->
+<!-- - *Number of post-hoc changes to the acoustic measurements* the teams will report to have carried out [numeric]. -->
+- *Number of models* the teams reported to have run [numeric].
 - *Major dimension* that has been measured to answer the research question [categorical].
@@
 
-Following @Parker2020, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
+Following @Parker2020, the measure of uniqueness of predictors was assessed by the Sørensen-Dice Index [SDI, @dice1945; @sorensen1948].
 The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses $(X, Y)$, the SDI will be obtained using the following formula:
+For our purposes, we treated predictors as species and individual analyses as sites.
+For each pair of analyses $(X, Y)$, the SDI was obtained using the following formula:
 
@@
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].
-
-The major measurement dimension of each analysis will be categorized according to the following possible groups: *duration*, *amplitude*, *fundamental frequency*, *other spectral properties* (e.g.
+In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].
+
+The major measurement dimension of each analysis was categorized according to the following possible groups: *duration*, *intensity*, *fundamental frequency* (f0), *other spectral properties* (e.g.
 frequency, center of gravity, harmonics difference, etc.), and *other measures* (e.g.
@@
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*.
-Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
-These will be entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
-
-**Researcher-related factors**. We will also include the following predictors:
+We assume the following relevant linguistic units: *segment*, *syllable*, *word*, *phrase*, *sentence*.
+Since each analysis received more than one peer-review rating, we calculated the mean rating and its standard deviation for each.
+These were entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
+
+**Researcher-related factors**. We also included the following predictors:
 
@@
 
-To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we will calculate the mean and standard deviation of these predictors for each team.
-These will be entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
+To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we calculated the mean and standard deviation of these predictors for each team.
+These were entered in the model formula as a measurement-error term (`me(mean, sd)` in brms).
 The expedient of using a measurement-error term (which includes the teams' standard deviation) ensures information about within-team variance is not lost (which would be the case if including the mean only).
 
-**Model specification**. The model will be fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model will be the standardized effect sizes and related standard deviation.
-
-A normal distribution will be used as the likelihood function of $\alpha_{t[i]}$.
-The mean of $\alpha_{t[i]}$ is modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
-The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for the intercept and the predictors we will use a normal distribution with mean 0 and standard deviation 1.
-The model will be run with the same settings as with the meta-analytic model.
-The code used to run the model can be found at <https://many-speech-analyses.github.io/suppl/simulations.html>.
+We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
+We realised when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
+There was no team that declared to have made post-hoc changes to the analyses.
+
+**Model specification**. The model was fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model was the standardized effect sizes and related standard deviation.
+
+A normal distribution was used as the likelihood function of $\alpha_{t[i]}$.
+The mean of $\alpha_{t[i]}$ was modeled on the basis of the overall intercept $\beta$ and on the coefficients of each predictor.
+The numeric predictors were centered and scaled and the categorical predictors were sum coded.
+As the prior for the intercept and the predictors we used a normal distribution with mean 0 and standard deviation 1.
+The model was run with the same settings as with the meta-analytic model.
+<!-- TODO: add link to predictor model code -->
+The code used to run the model can be found at <LINK>.
 
@@
 
-<!-- Had to remove footnote because there were too many footnotes and not enough symbols -->
-
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>, link for peer-review: <https://bit.ly/3AqU1ul>).
-Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
-Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
-We will also archive copies of our survey instruments from analysts and peer-reviewers.
-
-We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
-We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+All relevant data, code, and materials have been publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
+Archived data includea the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
+Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
+We also archived copies of our survey instruments from analysts and peer-reviewers.
+
+We have exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
+We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+<!-- TODO: mention that there were some and add info in descriptive stats section? -->
 
@@
 
-Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
+The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.
 
@@
 
-## Descriptive statistics
+## Descriptive statistics {#descr-stats}
 
@@
 `r round(outcome_n[[1,1]],2) * 100`\% of models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
-<!-- TODO: check that all proportions refer to models and not to coefficients -->
 
@@
 `r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
-<!-- TR: Did we confirm this?
--->
 `r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
@@
 
-<!-- Found effect 
-JVC: this code is ready to go, but not all the rows in the google sheet are 
-filled out (approx. 40 missing)
---> 
 ```{r}
@@
 
-## Meta-analytic estimation
+## Meta-analytic estimation {#meta-est}
 
@@
 First, we report on the between-team variability estimate (i.e.
-the meta-analytic group-level standard deviation $$\sigma_{\alpha_{\text{t}}}$$), which is the focus of this study, followed by the meta-analytic estimate (i.e.
+the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$), which is the focus of this study, followed by the meta-analytic estimate (i.e.
 the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
@@
 
-<!-- TODO: extract and fill in estimates and 95% CrIs as indicated below -->
 Figure \@ref(fig:plot-meta2), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals. 

### 2022-09-23 RR_manuscript/Draft_RR.tex
♻️ - finish editing methods; change tense to past; links to be added

@@
 
-We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
+We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
+These summary statistics are reported in @ref\{descr-stats\} of the Results section.
 
@@
 
-We will investigate the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we will take the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
+We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
+As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
+As we detail in Section @ref\{meta-est\}, we have also run further non-preregistered analyses.
+For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.
 
-Based on the common practices currently in place within the field, we anticipate that researchers will use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), may be inappropriate.
+Based on the common practices currently in place within the field, we anticipated that researchers would use multilevel regression models, thus common measurements of effect size, such as Cohen's \(d\), might have been inappropriate.
 Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
-Factor-level ordering for each categorical variable will mirror that of the original analyses.
-Each \textsc{standardized model} will be fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
-For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), to approximate the estimation procedure of frequentist models (i.e.~only the distribution of the data determines the posterior distribution).
-If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.
-Model refitting will also constitute a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
+Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) and that was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
+Model refitting also constituted a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
+Details about the refitting procedure can be found at LINK.
 
-The coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models will be used as the \textsc{standardized effect size} (\(\eta_i\)) of each reported model.
-If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
-Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each standardized effect size as the \textsc{standardized standard error} (\(\text{se}_i\)).
-This will enable us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
-As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
+The coefficients of the critical predictors (i.e.~critical according to the analysis teams' self-reported inferential criteria) obtained from the standardized models were used as the \textsc{standardized effect size} (\(\eta_i\)) of each reported model.
+Moreover, to account for the differing degree of uncertainty around each standardized effect size, we used the standard deviation of each standardized effect size as the \textsc{standardized standard error} (\(\text{se}_i\)).
+This enabled us to fit a so-called ``measurement-error'' model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
+As a desired consequence, effect sizes with a greater standard error are weighted less than those with a smaller standard error in the meta-analytic calculations.
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we will conduct a \textsc{Bayesian random-effects meta-analysis} using a multilevel (intercept-only) regression model.
-The outcome variable will be the set of standardized effect sizes \(\eta_i\).
-The likelihood of \(\eta_i\) is assumed to correspond to a normal distribution \citep{knight2000}.
-The analysis teams will be entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
-The standard errors \(\text{se}_i\) will be included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
-We will use regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
-We will fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 4 processing cores.
-In case of divergent transitions, we will increase \texttt{adapt\_delta}, \texttt{tree\_depth}, and the number of iterations in this order until we obtain a model fit with no divergent transitions.
-The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
+The outcome variable was the set of standardized effect sizes \(\eta_i\).
+The likelihood of \(\eta_i\) was assumed to correspond to a normal distribution \citep{knight2000}.
+The analysis teams were entered as a group-level effect (i.e., \texttt{(1\ \textbar{}\ team)}, called \emph{random effect} in the frequentist literature).
+The standard errors \(\text{se}_i\) were included as the standard deviation of \(\eta_i\) to fit a measurement-error model, as discussed above.
+We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
+We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
+The model did not incur in divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
+The code used to run the model can be found at \textless\textgreater.
 
-The posterior distribution of the population-level intercept \(\alpha\) will allow us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
-The posterior distribution will further allow us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
-Crucially, the posterior distribution of the \href{.smallcaps}{group-level standard deviation} \(\sigma_{\alpha_{\text{t}}}\) (i.e.~the standard deviation of the group-level effect of team) will allow us to quantify the degree of variation between the teams' analyses on a standardized scale.
+The posterior distribution of the population-level intercept \(\alpha\) allowed us to estimate the range of probable values of the standardized effect size \(\hat{\eta}\).
+The posterior distribution further allowed us to investigate the effect of a set of analytic and researcher-related predictors, detailed in the next section.
+Crucially, the posterior distribution of the \href{.smallcaps}{group-level standard deviation} \(\sigma_{\alpha_{\text{t}}}\) (i.e.~the standard deviation of the group-level effect of team) allowed us to quantify the degree of variation between the teams' analyses on a standardized scale.
 
@@
 
-As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
+As a second step, we investigated the extent to which the individual standardized effect sizes are affected by a series of \textsc{analytic and researcher-related predictors}.
 
-\textbf{Analytic predictors}. We will estimate the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
+\textbf{Analytic predictors}. We estimated the influence of the following predictors related to the analytic characteristics of each team's reported analysis:
 
@@
 \item
-  \emph{Measure of conservativeness} of the model specification, as the number of random/group-level effects included {[}numeric{]}.
-\item
-  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out {[}numeric{]}.
-\item
-  \emph{Number of models} the teams will report to have run {[}numeric{]}.
+  \emph{Number of models} the teams reported to have run {[}numeric{]}.
 \item
@@
 
-Following \citet{Parker2020}, the measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index \citep[SDI,][]{dice1945, sorensen1948}.
+Following \citet{Parker2020}, the measure of uniqueness of predictors was assessed by the Sørensen-Dice Index \citep[SDI,][]{dice1945, sorensen1948}.
 The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we will treat predictors as species and individual analyses as sites.
-For each pair of analyses \((X, Y)\), the SDI will be obtained using the following formula:
+For our purposes, we treated predictors as species and individual analyses as sites.
+For each pair of analyses \((X, Y)\), the SDI was obtained using the following formula:
 
@@
 
-In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
+In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
 
-The major measurement dimension of each analysis will be categorized according to the following possible groups: \emph{duration}, \emph{amplitude}, \emph{fundamental frequency}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
+The major measurement dimension of each analysis was categorized according to the following possible groups: \emph{duration}, \emph{intensity}, \emph{fundamental frequency} (f0), \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
-We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}.
-Since each analysis will receive more than one peer-review rating, we will calculate the mean rating and its standard deviation for each.
-These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+We assume the following relevant linguistic units: \emph{segment}, \emph{syllable}, \emph{word}, \emph{phrase}, \emph{sentence}.
+Since each analysis received more than one peer-review rating, we calculated the mean rating and its standard deviation for each.
+These were entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
 
-\textbf{Researcher-related factors}. We will also include the following predictors:
+\textbf{Researcher-related factors}. We also included the following predictors:
 
@@
 
-To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we will calculate the mean and standard deviation of these predictors for each team.
-These will be entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
+To obtain an aggregated research experience score and initial belief score for each team based on the members' individual scores, we calculated the mean and standard deviation of these predictors for each team.
+These were entered in the model formula as a measurement-error term (\texttt{me(mean,\ sd)} in brms).
 The expedient of using a measurement-error term (which includes the teams' standard deviation) ensures information about within-team variance is not lost (which would be the case if including the mean only).
 
-\textbf{Model specification}. The model will be fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model will be the standardized effect sizes and related standard deviation.
+We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
+We realised when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
+There was no team that declared to have made post-hoc changes to the analyses.
 
-A normal distribution will be used as the likelihood function of \(\alpha_{t[i]}\).
-The mean of \(\alpha_{t[i]}\) is modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
-The numeric predictors will be centered and scaled and the categorical predictors will be sum coded.
-As the prior for the intercept and the predictors we will use a normal distribution with mean 0 and standard deviation 1.
-The model will be run with the same settings as with the meta-analytic model.
-The code used to run the model can be found at \url{https://many-speech-analyses.github.io/suppl/simulations.html}.
+\textbf{Model specification}. The model was fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
+The outcome variable of the model was the standardized effect sizes and related standard deviation.
+
+A normal distribution was used as the likelihood function of \(\alpha_{t[i]}\).
+The mean of \(\alpha_{t[i]}\) was modeled on the basis of the overall intercept \(\beta\) and on the coefficients of each predictor.
+The numeric predictors were centered and scaled and the categorical predictors were sum coded.
+As the prior for the intercept and the predictors we used a normal distribution with mean 0 and standard deviation 1.
+The model was run with the same settings as with the meta-analytic model.
+The code used to run the model can be found at .
 
@@
 
-All relevant data, code, and materials will be publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}, link for peer-review: \url{https://bit.ly/3AqU1ul}).
-Archived data will include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyze with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
-Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
-We will also archive copies of our survey instruments from analysts and peer-reviewers.
+All relevant data, code, and materials have been publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
+Archived data includea the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
+Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
+We also archived copies of our survey instruments from analysts and peer-reviewers.
 
-We will exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
-We will also exclude any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+We have exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
+We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
 
@@
 
-\hypertarget{descriptive-statistics-1}{%
-\subsection{Descriptive statistics}\label{descriptive-statistics-1}}
+\hypertarget{descr-stats}{%
+\subsection{Descriptive statistics}\label{descr-stats}}
 
@@
 
-\hypertarget{meta-analytic-estimation}{%
-\subsection{Meta-analytic estimation}\label{meta-analytic-estimation}}
+\hypertarget{meta-est}{%
+\subsection{Meta-analytic estimation}\label{meta-est}}
 
 This section deals with the meta-analytic analysis of the results submitted by the teams.
-First, we report on the between-team variability estimate (i.e.~the meta-analytic group-level standard deviation \[\sigma_{\alpha_{\text{t}}}\]), which is the focus of this study, followed by the meta-analytic estimate (i.e.~the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
+First, we report on the between-team variability estimate (i.e.~the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), which is the focus of this study, followed by the meta-analytic estimate (i.e.~the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
 

### 2022-09-24 RR_manuscript/Draft_RR.Rmd

@@
 `r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
-One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "[T]he project's approach is too much top-down instead of bottom-up.
-[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
-We find that this contribution clearly speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 
@@
 Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
-PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years.
+PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
-We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
+We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
@@
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
-When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)`, i.e. each submitted analysis was unique.
-Of the 104 submitted models, `r n_effects` include a statistically reliable effect (`r perc_effects`%). 
+<!-- TR: I am still confused, so if we were to ignore different random effect specifications that the number is x?
+Can we find a clearer way to express this, e.g.
+"When considering choices related to only statistical framework, type of model, distribution family and fixed terms, there were..." -->
+
+When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)` different analytic pipelines.
+In other words, each individual submitted analysis was unique.
+Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%). 
 `r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect.
@@
 
-\@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
+Figure \@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
@@
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
-Estimates ranged between `r min(msa_models$estimate)` to `r max(msa_models$estimate)` standard units.
+Estimates ranged between `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units.
 
@@
 These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between `r min(msa_models$estimate)` and `r max(msa_models$estimate)` standard units which corresponds to duration values ranging from `r min(msa_models$estimate) * 33.4 ` to `r max(msa_models$estimate) * 51.4`.
+The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)`.
 A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, time 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms].
@@
 While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, previous studies reported statistically robust effects of 8 and 16 ms [@coretta2019], down to 4.5 ms [@nowak2006]. 
-Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which involves duration effects ranging 7-15 ms [@nicenboim2018using]. 
+For example, the phenomenon of incomplete neutralization, a widely studied phenomenon, involves duration effects ranging from 7 to 15 ms [@nicenboim2018using].
 This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].
-
-Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction is thus concerning and might lead to opposing theoretical conclusions.
+Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts [@coretta2019], reduction [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
+Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many analysts that participated in this study targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
+Second and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
 @grice2017integrating; @turnbull2017role].
 Moreover, prior work has actually suggested a relationship between typicality and f0 [e.g. @dimitrova2008prosodic; @dimitrova2009did]. 
-Participating analysts might have been aware of those findings, which might have, subconsciously of otherwise, nudged their choices into one particular direction.
+Participating analysts might have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
 
@@
 This is an important observation when put into context of the fact that most teams submitted many different models.
-
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher].
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher, @simmons2011false].
+One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): "[T]he project's approach is too much top-down instead of bottom-up.
+[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
+We find that this statement speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for [@tukey1953].
-Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false], while null results remain unreported [e.g., @sterling1959publication, @rosenthal1979file].
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false], while null results remain unreported [@sterling1959publication, @rosenthal1979file].
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [e.g., @vazire2017quality, @fidler2018reproducibility].
-One of the suggested paths forward is for researchers to directly replicate previous studies more often [e.g., @open2015estimating; @camerer2018evaluating].
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [ @vazire2017quality, @fidler2018reproducibility].
+One of the suggested paths forward is for researchers to directly replicate previous studies more often [@open2015estimating, @camerer2018evaluating].
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
+Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more, @starns2019assessing].
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
@@
 
-We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory, @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
 Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
@@
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat, EMU: @winkelmann2017emu, the Montreal Forced Aligner @mcauliffe2017, ].
-
-Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat; EMU: @winkelmann2017emu; the Montreal Forced Aligner: @mcauliffe2017].
+
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
@@
 Our study has several limitations that need to be considered when evaluating our results. 
-
 The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
@@
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable. 
-We invite other researchers to re-analyse and try to replicate our results using a different research question.
+We invite other researchers to re-analyse our data and try to replicate our results using a different research question.
 
@@
 
-In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018, @darwin2020, @fox2021open].
+In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018; @darwin2020; @fox2021open].
 Researchers do not analyse data in a vacuum.
-It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
-
-Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find is the variability that we have observed.
-
-Finally, our study focussed on the speech sciences.
+It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
+
+Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
+
+Finally, our study focused on the speech sciences.
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
@@
 While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are investigated using qualitative methods rather than quantitatively.
+This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
-Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical thresholds.
+Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical values.
 

### 2022-09-24 RR_manuscript/Draft_RR.Rmd
clean up code, remove unused objects, simplify table labels, make sure table values match prose

@@
 library(broom.mixed)
+library(kableExtra)
 ```
@@
 #| label: helper-functions
+
 # Round and format numbers to exactly N digits
@@
 
-# Print values from tibble for article
+# Print values from tibble
 pull_from_tib <- function(df, col, row, val) {
@@
 
-# Function for reporting posteriors
+# Report posteriors in prose
 report_posterior <- function(df, param) {
@@
   )
-
-# average phd experience
-phd_mean <- msa_models %>% 
-  select(team, years_from_phd) %>% 
-  distinct(team, years_from_phd) %>% 
-  summarise(mean_phd = mean(years_from_phd, na.rm = TRUE),
-            sd_phd = sd(years_from_phd, na.rm = TRUE),
-            min_phd = min(years_from_phd, na.rm = TRUE),
-            max_phd = max(years_from_phd, na.rm = TRUE))
-
-prior_mean <- msa_models %>% 
-  select(team, prior_belief) %>% 
-  distinct(team, prior_belief) %>% 
-  summarise(mean_prior = mean(prior_belief, na.rm = TRUE),
-            sd_prior = sd(prior_belief, na.rm = TRUE),
-            min_prior = min(prior_belief, na.rm = TRUE),
-            max_prior = max(prior_belief, na.rm = TRUE))
-
-# number of teams (final)
-no_teams = length(unique(msa_models$team))
-
-# Helper function to print table data easier
-split_to_list <- function(.data, ...) {
-  dots <- rlang::enquos(...)
-  for (var in seq_along(dots)) {
-    var_name <- rlang::as_name(dots[[var]])
-    .data <- purrr::map_depth(
-      .x = .data,
-      .depth = var - 1,
-      .f = function(xs) split(xs, xs[var_name])
-    )
-  }
-  .data
-}
 
@@
     summarize(n_teams = nrow(.), 
+              n_analysts = sum(n_members), 
               mean_size = mean(n_members), 
@@
 
-team_desc_list <- team_desc_df %>% 
-  tidyr::pivot_longer(cols = n_teams:median_size, names_to = "metric", values_to = "val") %>% 
-  split_to_list(stage, metric)
-
-# Example usage
-# team_desc_list$Initial$n_teams$val
-
 # number of analyses
@@
          stat_rating, n_predictors, pop_pred, operationalisation, 
-         operationalisation_notes) %>%
+         operationalisation_notes, n_terms, n_coefficients, n_random_int, 
+         n_random_slo, n_random_smooth, n_random, n_models) %>%
   distinct()
@@
   group_by(animal) %>% 
-  summarise(max_models = max(model_n)) %>% 
-  group_by() %>% 
-  summarise(mean_models = mean(max_models))
+  summarise(max_n_models = max(model_n)) %>% 
+  summarise(
+    mean_models = mean(max_n_models), 
+    sd_models = sd(max_n_models), 
+    min_models = min(max_n_models), 
+    max_models = max(max_n_models), 
+    n_models = sum(max_n_models)
+  )
 
@@
 predictor_n <- msa_models_unique %>% 
-  summarise(mean_predictor = mean(n_predictors, na.rm = TRUE))
+  summarise(
+    mean_predictor = mean(n_predictors, na.rm = TRUE), 
+    sd_predictor = sd(n_predictors, na.rm = TRUE), 
+    min_predictor = min(n_predictors, na.rm = TRUE), 
+    max_predictor = max(n_predictors, na.rm = TRUE), 
+    n_predictor = sum(n_predictors, na.rm = TRUE)
+    )
 
@@
   filter(n_random != 0) %>% 
-  summarise(mean_rterms = mean(n_random, na.rm = TRUE))
+  summarise(
+    mean_rterms = mean(n_random, na.rm = TRUE), 
+    sd_rterms = sd(n_random, na.rm = TRUE), 
+    min_rterms = min(n_random, na.rm = TRUE), 
+    max_rterms = max(n_random, na.rm = TRUE), 
+    n_rterms = sum(n_random, na.rm = TRUE)
+    )
+
+# random intercepts
+rterms_int_n <- msa_models_unique %>% 
+  filter(n_random != 0) %>% 
+  summarise(
+    mean_rint = mean(n_random_int, na.rm = TRUE), 
+    sd_rint = sd(n_random_int, na.rm = TRUE), 
+    min_rint = min(n_random_int, na.rm = TRUE), 
+    max_rint = max(n_random_int, na.rm = TRUE), 
+    n_rint = sum(n_random_int, na.rm = TRUE)
+    )
+
+# random slopes
+rterms_slope_n <- msa_models_unique %>% 
+  filter(n_random != 0) %>% 
+  summarise(
+    mean_rslope = mean(n_random_slo, na.rm = TRUE), 
+    sd_rslope = sd(n_random_slo, na.rm = TRUE), 
+    min_rslope = min(n_random_slo, na.rm = TRUE), 
+    max_rslope = max(n_random_slo, na.rm = TRUE), 
+    n_rslope = sum(n_random_slo, na.rm = TRUE)
+    )
 
@@
 # review ratings
-# NOTE: Stef or Timo, this doesnt take into account repeated values per team
-# so the denominator is inflated (alosa_atun has 16 models but the phon_rating 
-# is the same for each so the mean is dividing by an inflated denominator)
-# I suggest using the following: 
-#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", avg)`
-#  `pull_from_tib(tbl_team_desc, label, "team_desc_phon_rating", sd)`
-
 review_mean <- msa_models %>% 
-  summarise(mean_prating = mean(phon_rating, na.rm = TRUE),
+  select(animal, phon_rating, stat_rating) %>% 
+  distinct() %>% 
+  summarise(
+    mean_prating = mean(phon_rating, na.rm = TRUE),
     sd_prating = sd(phon_rating, na.rm = TRUE), 
+    min_prating = min(phon_rating, na.rm = TRUE),
+    max_prating = max(phon_rating, na.rm = TRUE),
+    n_prating = sum(phon_rating, na.rm = TRUE),
     mean_srating = mean(stat_rating, na.rm = TRUE),
-            sd_srating = sd(stat_rating, na.rm = TRUE))
+    sd_srating = sd(stat_rating, na.rm = TRUE), 
+    min_srating = min(stat_rating, na.rm = TRUE), 
+    max_srating = max(stat_rating, na.rm = TRUE), 
+    n_srating = sum(stat_rating, na.rm = TRUE)
+    )
 
 #
-# TABLE 1 PREP
+# TABLE PREP
 #
@@
       metric == "years_from_phd" ~ "Years after PhD", 
-      metric == "stat_rating" ~ "Self-report statistical ability", 
+      metric == "stat_rating" ~ "Statistical analysis peer rating", 
       metric == "prior_belief" ~ "Prior belief", 
-      metric == "phon_rating" ~ "Acoustic analysis rating", 
-      metric == "all_rating" ~ "Peer rating"), 
+      metric == "phon_rating" ~ "Acoustic analysis peer rating", 
+      metric == "all_rating" ~ "Overall peer rating"), 
     label = glue::glue("{desc}_{metric}")) %>% 
@@
 #
-# TABLE 2 PREP
+# Descriptives of categorical variables in acoustic analyses
 #
-
-# Descriptives of categorical variables in acoustic analyses
 tbl_categorical_desc <- msa_models_unique %>% 
@@
 #
-# TABLE 3 PREP
+# Model descriptives 
 #
 
-# Model descriptives 
-tbl_model_desc <- msa_models %>% 
-  select(animal, n_predictors:n_random, n_models) %>% 
-  group_by(animal) %>% 
-  summarize(across(everything(), mean)) %>% 
-  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
-  na.omit() %>% 
-  group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
-            sd = sd(vals, na.rm = T)) %>% 
-  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
-  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
-  mutate(desc = "model_desc", 
-    metric = fct_relevel(metric, "n_models"), 
-    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
-    Range = glue::glue("{min} -- {max}"), 
+tbl_model_desc <- bind_rows(
+  mean_analyses %>% 
+  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
+  predictor_n %>% 
+  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
+  rterms_n %>% 
+  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
+  rterms_int_n %>% 
+  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
+  rterms_slope_n %>% 
+  pivot_longer(cols = everything(), names_to = "label", values_to = "vals")
+) %>% 
+  separate(label, c("Metric", "item"), sep = "_") %>% 
+  pivot_wider(names_from = Metric, values_from = vals) %>% 
+  mutate(across(c("mean", "sd"), specify_decimal, k = 1)) %>% 
+  mutate(
+    Metric = item, 
     Metric = case_when(
-      metric == "n_coefficients" ~ "n. coefficients", 
-      metric == "n_models" ~ "n. models", 
-      metric == "n_predictors" ~ "n. predictors", 
-      metric == "n_random" ~ "n. random effects", 
-      metric == "n_random_int" ~ "n. random intercepts", 
-      metric == "n_random_slo" ~ "n. random slopes", 
-      metric == "n_random_smooth" ~ "n. random smooths",
-      metric == "n_terms" ~ "n. terms"), 
-    label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range) %>% 
+      Metric == "models" ~ "Models", 
+      Metric == "predictor" ~ "Predictors", 
+      Metric == "rterms" ~ "Random terms", 
+      Metric == "rint" ~ "Intercept", 
+      Metric == "rslope" ~ "Slope"
+    ), 
+    desc = "model_desc", 
+    label = glue::glue("{desc}_{item}"), 
+    `Mean (SD)` = glue::glue("{mean} ({sd})"), 
+    Range = glue::glue("{min} -- {max}")) %>% 
+  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg = mean, 
+         sd, Range) %>% 
   mutate(across(-c("desc", "Metric"), as.character))
+
+#tbl_model_desc <- msa_models_unique %>% 
+#  select(animal, starts_with("n_")) %>% 
+#  group_by(animal) %>% 
+#  summarize(across(everything(), mean)) %>% 
+#  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
+#  na.omit() %>% 
+#  group_by(metric) %>% 
+#  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+#            sd = sd(vals, na.rm = T)) %>% 
+#  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
+#  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
+#  mutate(desc = "model_desc", 
+#    metric = fct_relevel(metric, "n_models"), 
+#    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
+#    Range = glue::glue("{min} -- {max}"), 
+#    Metric = case_when(
+#      metric == "n_coefficients" ~ "n. coefficients", 
+#      metric == "n_models" ~ "n. models", 
+#      metric == "n_predictors" ~ "n. predictors", 
+#      metric == "n_random" ~ "n. random effects", 
+#      metric == "n_random_int" ~ "n. random intercepts", 
+#      metric == "n_random_slo" ~ "n. random slopes", 
+#      metric == "n_random_smooth" ~ "n. random smooths",
+#      metric == "n_terms" ~ "n. terms"), 
+#    label = glue::glue("{desc}_{metric}")) %>% 
+#  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, 
+#    sd, Range) %>% 
+#  mutate(across(-c("desc", "Metric"), as.character))
 
@@
 
-`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study.
-`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
-
-`r team_desc_list$Final$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analysis by the established deadline.
+`r pull_from_tib(team_desc_df, stage, "Initial", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study, comprising `r pull_from_tib(team_desc_df, stage, "Initial", n_analysts)` analysts.
+`r (pull_from_tib(team_desc_df, stage, "Initial", n_teams) - pull_from_tib(team_desc_df, stage, "Final", n_teams)) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
+
+`r pull_from_tib(team_desc_df, stage, "Final", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analysis by the established deadline.
 These are the teams that are included in this study.
-Submitting teams consisted of an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` individual analysts (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`).
+The submitting teams comprised `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
@@
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_n_models", sd)`) models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
@@
 We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
-
-<!-- Begin Table 1 --> 
-\vspace{0.2in}
-```{r}
-#| label: team-descriptives-table
-#| results: 'asis'
-#| eval: false
-  tbl_team_desc %>% 
-  select(Metric, Range, `Mean (SD)`) %>% 
-  knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "r", "r"), 
-    caption = "Descriptive statistics for teams included in the 
-    meta-analysis (n = 30).",
-    label = "team-descriptives-table"
-    ) %>% 
-  kableExtra::kable_styling(., font_size = 11)
-```
-<!-- END: Table -->
 
@@
 
-<!-- Begin Table 2 --> 
-\vspace{0.2in}
-```{r}
-#| label: categorical-descriptives-table
-#| results: 'asis'
-#| eval: false
-
-tbl_categorical_desc %>% 
-  select(Metric, Type, n, `\\%` = perc) %>% 
-  group_by(Metric) %>% 
-  arrange(desc(n), .by_group = T) %>% 
-  ungroup() %>% 
-  mutate(Metric = case_when(
-    Type != "Frequentist" & Metric == "Framework" ~ " ", 
-    Type != "Linear model" & Metric == "Model" ~ " ", 
-    Type != "F0" & Metric == "Outcome" ~ " ", 
-    Type != "Segment" & Metric == "Temporal window" ~ " ", 
-    Type != "Categorical" & Metric == "Typicality operationalization" ~ " ", 
-    TRUE ~ Metric)
-    ) %>% 
-  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 2) %>%
-  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 6) %>%
-  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 12) %>%
-  add_row(Metric = " ", Type = " ", n = NA, `\\%` = NA, .after = 18) %>%
-  mutate(across(-c("Metric", "Type"), ~replace(., is.na(.), " "))) %>% 
-  knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "l", "r", "r"), 
-    caption = "Descriptive statistics for model stuff.",
-    label = "categorical-descriptives-table"
-    ) %>% 
-  kableExtra::kable_styling(., font_size = 11)
-
-```
-<!-- END Table 2 -->
-
 ### Statistical analysis
@@
 
-The models included a mean of `r round(predictor_n)` different predictors (defined as variables or columns in the data table).
+The models included a mean of `r round(predictor_n$mean_predictor)` different predictors (defined as variables or columns in the data table).
 This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least one additional predictor.
@@
 `r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
-On average, teams that specified random effects, included `r round(rterms_n,1)` random terms in their models. 
+On average, teams that specified random effects, included `r round(rterms_n$mean_rterms,1)` random terms in their models. 
 Table \@ref(tab:descriptives-table) provides a summary of the statistical analyses.
@@
 
-<!-- Begin Table 3 --> 
-```{r}
-#| label: stats-descriptives-table
-#| results: 'asis'
-#| eval: false
-tbl_model_desc %>% 
-  select(Metric, Range, `Mean (SD)`) %>% 
-  filter(Metric != "n. random smooths") %>% 
-  mutate(Metric = str_remove_all(Metric, "n. "), 
-         Metric = str_to_sentence(Metric)) %>% 
-  knitr::kable(format = "latex", booktabs = T, escape = F, 
-    linesep = "", align = c("l", "l", "r"), 
-    caption = "Descriptive statistics for statistical analyses included in the 
-    meta-analysis (n = 30).",
-    label = "stats-descriptives-table"
-    ) %>% 
-  kableExtra::kable_styling(., font_size = 11)
-```
-<!-- END: Table -->
-
+<!-- Begin Table --> 
 ```{r}
@@
 #| results: 'asis'
-library(kableExtra)
 bind_rows(
@@
   mutate(order = c(
-    1, 6, 5, 4, 3, 2, 
+    1, 6, 4, 3, 5, 2, 
     21, 20, 23, 22, 24, 
@@
     17, 18, 19, 
-    26, 25, 27, 28, 29, 30, 31, 32
+    25:29
     )
@@
     desc = case_when(
-      Metric != "n. models" & desc == "N" ~ " ", 
+      Metric != "Models" & desc == "N" ~ " ", 
       Metric != "Frequentist" & desc == "Framework" ~ " ", 
@@
     longtable = F, linesep = "", 
-    caption = "Descriptive statistics of contributing teams (n = 30), acoustic 
-    analyses, and statistical analyses.",
+    caption = glue::glue("Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis.
+The data set included analyses from {pull_from_tib(team_desc_df, stage, 'Final', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Final', n_analysts)} analysts."),
     label = "descriptives-table") %>%
@@
   add_indent(c(9, 15, 21, 26, 29, 34)) %>% 
+  add_indent(c(37, 38), all_cols = T) %>% 
   row_spec(8, hline_after = T) %>% 
@@
 ```
+<!-- END TABLE -->
 
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean[[1]],1)` (SD = `r round(review_mean[[2]],1)`, see Table \@ref(tab:descriptives-table)).
-The mean rating of the statistical analysis is `r round(review_mean[[3]],1)` (SD = `r round(review_mean[[4]],1)`).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean$mean_prating,1)` (SD = `r round(review_mean$sd_prating,1)`, see Table \@ref(tab:descriptives-table)).
+The mean rating of the statistical analysis is `r round(review_mean$mean_srating,1)` (SD = `r round(review_mean$sd_srating,1)`).
 For reference, as mentioned in the Methods section, a score of 75 was defined as "an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation", indicating that on average reviewers judged the provided analyses to be appropriate, although "imperfect".
@@
 
-We gave `r team_desc_list$Final$n_teams$val` analyst teams the same speech data set to answer the same research question: *Do 
+We gave `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` analyst teams the same speech data set to answer the same research question: *Do 
 speakers acoustically modify utterances to signal atypical word combinations?*

### 2022-09-24 RR_manuscript/Draft_RR.tex
clean up code, remove unused objects, simplify table labels, make sure table values match prose

@@
 
-Eighty-four teams initially signed up to participate in the study.
+Eighty-four teams initially signed up to participate in the study, comprising 211 analysts.
 Fifty-four of the signed-up teams dropped out during the analysis phase.
-One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``{[}T{]}he project's approach is too much top-down instead of bottom-up.
-{[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
-We find that this contribution clearly speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 
@@
 These are the teams that are included in this study.
-Submitting teams consisted of an average of 3.6 individual analysts (SD = 2.8).
+The submitting teams comprised 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years.
+Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years, suggesting that, on average, analyst were experienced researchers.
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
-We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between prosody and word combination typicality.
+We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.7 (SD: 3.4) models per team.
+At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
-
-\vspace{0.2in}
 
@@
 Table \ref{tab:descriptives-table} provides a summary of the acoustic analyses.
-
-\vspace{0.2in}
 
@@
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
-When considering both acoustic and statistical analysis, we have found a grand total of 104, i.e.~each submitted analysis was unique.
-Of the 104 submitted models, 37 include a statistically reliable effect (21.76\%).
+
+When considering both acoustic and statistical analysis, we have found a grand total of 104 different analytic pipelines.
+In other words, each individual submitted analysis was unique.
+Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
 Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect.
@@
 
-\caption{\label{tab:descriptives-table}Descriptive statistics of contributing teams (n = 30), acoustic 
-    analyses, and statistical analyses.}
+\caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis.
+The data set included analyses from 30 teams and  109 analysts.}
 \centering
@@
  & Years after phd & -3.8 -- 12.4 & 4.8 (4.2)\\
- & Self-report statistical ability & 33.0 -- 93.3 & 69.5 (16.5)\\
  & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
- & Acoustic analysis rating & 41.2 -- 88.3 & 71.5 (13.9)\\
- & Peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
+ & Acoustic analysis peer rating & 41.2 -- 88.3 & 71.5 (13.9)\\
+ & Statistical analysis peer rating & 33.0 -- 93.3 & 69.5 (16.5)\\
+ & Overall peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
  &  &  \vphantom{5} & \\
@@
  &  & \bf{Range} & \bf{Mean (SD)}\\
-\hspace{1em}N & Models & 1 -- 16 & 3.7 (3.4)\\
- & Coefficients & 1 -- 11 & 3.5 (2.7)\\
- & Predictors & 1 -- 4 & 1.6 (0.9)\\
- & Random effects & 0 -- 10 & 2.5 (2.1)\\
- & Random intercepts & 0 -- 10 & 1.9 (1.8)\\
- & Random slopes & 0 -- 4 & 0.6 (1.1)\\
- & Terms & 1 -- 4 & 1.8 (1.1)\\
+\hspace{1em}N & Models & 1 -- 16 & 3.6 (3.4)\\
+ & Predictors & 1 -- 5 & 2.0 (1.2)\\
+ & Random terms & 1 -- 10 & 2.5 (1.3)\\
+\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}1.9 (1.0)\\
+\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0.5 (0.9)\\
 \bottomrule
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 74.5 (SD = 11.2, see Table \ref{tab:descriptives-table}).
-The mean rating of the statistical analysis is 73.8 (SD = 14.1).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9, see Table \ref{tab:descriptives-table}).
+The mean rating of the statistical analysis is 69.5 (SD = 16.5).
 For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
@@
 
-\ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
+Figure \ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
 Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
-Estimates ranged between -0.6544004 to 0.9885856 standard units.
+Estimates ranged between -0.65 to 0.99 standard units.
 
@@
 These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between -0.6544004 and 0.9885856 standard units which corresponds to duration values ranging from -21.856972 to 50.8132988.
+The reported effect estimates from teams varied between -0.65 and 0.99 standard units which corresponds to duration values ranging from -21.86 to 50.81.
 A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms}.
@@
 While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, previous studies reported statistically robust effects of 8 and 16 ms \citep{coretta2019}, down to 4.5 ms \citep{nowak2006}.
-Another example is the phenomenon of incomplete neutralization, a widely studies phenomenon, which involves duration effects ranging 7-15 ms \citep{nicenboim2018using}.
+For example, the phenomenon of incomplete neutralization, a widely studied phenomenon, involves duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
 This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.
-
-Expecting random variation between different analysts of 7 to 15 in one or the other direction is thus concerning and might lead to opposing theoretical conclusions.
+Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts \citep{coretta2019}, reduction \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
+Expecting random variation between different analysts of 7 to 15 in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-Second and independent of a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many analysts that participated in this study targeted measures related to fundamental frequency (f0), since similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Second and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
 Moreover, prior work has actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
-Participating analysts might have been aware of those findings, which might have, subconsciously of otherwise, nudged their choices into one particular direction.
+Participating analysts might have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
 
@@
 This is an important observation when put into context of the fact that most teams submitted many different models.
-
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep[\citet{simmons2011false}]{roettger2019researcher}.
+One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): ``{[}T{]}he project's approach is too much top-down instead of bottom-up.
+{[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
+We find that this statement speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for \citep{tukey1953}.
-Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[\citet{rosenthal1979file}]{sterling1959publication}.
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[e.g.,][\citet{fidler2018reproducibility}]{vazire2017quality}.
-One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[\citet{fidler2018reproducibility}]{vazire2017quality}.
+One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[\citet{camerer2018evaluating}]{open2015estimating}.
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
+Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep[\citet{starns2019assessing}]{rotello2015more}.
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
@@
 
-We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep[\citet{meehl1990summaries}]{dubin1970theory}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
 Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
@@
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}, the Montreal Forced Aligner \citet{mcauliffe2017},]{boersma2021praat}.
+Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citetext{\citealp[e.g., Praat:][]{boersma2021praat}; \citealp[EMU:][]{winkelmann2017emu}; \citealp[the Montreal Forced Aligner:][]{mcauliffe2017}}.
 
-Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
@@
 Our study has several limitations that need to be considered when evaluating our results.
-
 The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
@@
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
-We invite other researchers to re-analyse and try to replicate our results using a different research question.
+We invite other researchers to re-analyse our data and try to replicate our results using a different research question.
 
@@
 
-In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][\citet{darwin2020}, \citet{fox2021open}]{jafar2018}.
+In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{jafar2018, darwin2020, fox2021open}.
 Researchers do not analyse data in a vacuum.
-It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers approaches and interpretations.
+It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
 
-Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find is the variability that we have observed.
+Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
 
-Finally, our study focussed on the speech sciences.
+Finally, our study focused on the speech sciences.
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.

### 2022-09-24 RR_manuscript/Draft_RR.Rmd
delete code that is no longer needed

@@
               sd_size = sd(n_members), 
-              median_size = median(n_members)) %>% 
+              median_size = median(n_members), 
+              min = min(n_members), 
+              max = max(n_members)) %>% 
     mutate(stage = "Initial"), 
@@
               sd_size = sd(n_members), 
-              median_size = median(n_members)) %>% 
+              median_size = median(n_members), 
+              min = min(n_members), 
+              max = max(n_members)) %>% 
     mutate(stage = "Submitted"), 
@@
   mutate(across(-c("desc", "Metric"), as.character))
-
-#tbl_model_desc <- msa_models_unique %>% 
-#  select(animal, starts_with("n_")) %>% 
-#  group_by(animal) %>% 
-#  summarize(across(everything(), mean)) %>% 
-#  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
-#  na.omit() %>% 
-#  group_by(metric) %>% 
-#  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
-#            sd = sd(vals, na.rm = T)) %>% 
-#  mutate(across(-c("metric", "avg", "sd"), round)) %>% 
-#  mutate(across(c("avg", "sd"), specify_decimal, k = 1)) %>% 
-#  mutate(desc = "model_desc", 
-#    metric = fct_relevel(metric, "n_models"), 
-#    `Mean (SD)` = glue::glue("{avg} ({sd})"), 
-#    Range = glue::glue("{min} -- {max}"), 
-#    Metric = case_when(
-#      metric == "n_coefficients" ~ "n. coefficients", 
-#      metric == "n_models" ~ "n. models", 
-#      metric == "n_predictors" ~ "n. predictors", 
-#      metric == "n_random" ~ "n. random effects", 
-#      metric == "n_random_int" ~ "n. random intercepts", 
-#      metric == "n_random_slo" ~ "n. random slopes", 
-#      metric == "n_random_smooth" ~ "n. random smooths",
-#      metric == "n_terms" ~ "n. terms"), 
-#    label = glue::glue("{desc}_{metric}")) %>% 
-#  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, 
-#    sd, Range) %>% 
-#  mutate(across(-c("desc", "Metric"), as.character))
 

### 2022-09-24 RR_manuscript/supplementary_materials.Rmd
add supplementary materials Rmd with complete descriptives table

---
title: "Supplementary materials"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = here::here())
library("dplyr")
library("ggplot2")
library("tidyr")
library("readr")
library("googlesheets4")
library("glue")
library("here")
library("fs")
library("forcats")
library("purrr")
library("stringr")
library("kableExtra")
```

```{r}
#| label: helpers

# Round and format numbers to exactly N digits
specify_decimal <- function(x, k) {
  out <- trimws(format(round(x, k), nsmall = k))
  return(out)
}

# Pull values from tibbles
pull_from_tib <- function(df, col, row, val) {
  col <- enquo(col)
  row <- enquo(row)
  val <- enquo(val)
  val <- filter(df, !!col == !!row) %>% pull(!!val)
  return(val)
}
```

```{r}
#| label: get-data

# Read in primary coding sheet
the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"

# Read in google sheet and join it with review data and phd/prior belief
# data
msa_models_unique <- left_join(
  read_sheet(the_sheet) %>% 
    filter(added_on_osf == "yes") %>% 
    select(
      animal, model_n, outcome, typicality_operationalization, 
      framework, model, temporal_window, random_effects, n_random, 
      n_predictors, operationalisation, n_terms, n_coefficients, n_random_int, 
      n_random_slo, n_random_smooth, n_models
      ) %>%
    distinct(), 
  readRDS("./data/peer_review/msa_reviews.rds") %>% 
    select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
           all_rating = Q5_4) %>% 
    group_by(animal) %>% 
    # Remove ratings from 2 teams that dropped
    filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
    summarize(phon_rating = mean(phon_rating), 
              stat_rating = mean(stat_rating), 
              all_rating = mean(all_rating)), 
  by = "animal"
) %>% 
  left_join(., 
    read_csv("./data/questionnaires/msa_intake_form_untidy.csv") %>%
      filter(added_on_osf == "yes", 
        !(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
      select(animal, years_from_phd, prior_belief), 
    by = "animal"
  )

#
# Create data frame with N of teams/team members at each phase of project
#

# Get google sheet
team_sheet <- "https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit?usp=sharing"

# Read in teams
teams <- read_sheet(team_sheet)

# Create DF of all members with leader names
team_leaders <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
         leader = case_when(
           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
           Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
           Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
           Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
           Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
           Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
           Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
           TRUE ~ leader
         )) %>% 
  select(ResponseId, leader)

# Vector of teams on OSF (for subsetting)
teams_on_osf <- teams %>% 
  filter(added_on_osf == "yes") %>% 
  pull(coordinator)

# Vector of teams with submitted analyses (for subsetting)
submitted_animals <- readRDS(here("./data/analyses/msa_models.rds")) %>% 
  pull(animal) %>% 
  unique
teams_used_in_analysis <- teams %>% 
  filter(animal %in% submitted_animals) %>% 
  pull(coordinator)

# Data frame of general team descriptives at each phase of project
#  - number of teams (initially, submitted and final)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              n_analysts = sum(n_members), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members), 
              min = min(n_members), 
              max = max(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 1)

#
# TABLE PREP
#

# Team descriptives
tbl_team_desc <- msa_models_unique %>% 
  select(animal, years_from_phd, prior_belief, phon_rating, stat_rating, 
         all_rating) %>% 
  group_by(animal) %>% 
  summarize(across(years_from_phd:all_rating, mean)) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
            sd = sd(vals, na.rm = T)) %>% 
  add_row(.before = 1, 
    metric = "size", 
    min = team_desc_df %>% filter(stage == "Submitted") %>% pull(min), 
    max = team_desc_df %>% filter(stage == "Submitted") %>% pull(max), 
    avg = team_desc_df %>% filter(stage == "Submitted") %>% pull(mean_size), 
    sd =  team_desc_df %>% filter(stage == "Submitted") %>% pull(sd_size)) %>% 
  mutate(across(-metric, specify_decimal, k = 1)) %>% 
  mutate(desc = "team_desc", 
   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
    Range = glue::glue("{min} -- {max}"), 
    Metric = case_when(
      metric == "size" ~ "Team size", 
      metric == "years_from_phd" ~ "Years after PhD", 
      metric == "stat_rating" ~ "Statistical analysis peer rating", 
      metric == "prior_belief" ~ "Prior belief", 
      metric == "phon_rating" ~ "Acoustic analysis peer rating", 
      metric == "all_rating" ~ "Overall peer rating"), 
    label = glue::glue("{desc}_{metric}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)

#
# Descriptives of categorical variables in acoustic analyses
#
tbl_categorical_desc <- msa_models_unique %>% 
  select(animal, outcome, temporal_window, typicality_operationalization, 
  framework, model) %>% 
  pivot_longer(cols = -animal, names_to = "metric", values_to = "val") %>% 
  na.omit() %>% 
  group_by(metric) %>% 
  count(val) %>% 
  group_by(metric) %>% 
  mutate(prop = n / sum(n), perc = prop * 100, 
    Metric = case_when(
      metric == "temporal_window" ~ "Temporal window", 
      metric == "typicality_operationalization" ~ "Typicality operationalization", 
      TRUE ~ metric
    ), 
    Metric = str_to_sentence(Metric), 
    Type = case_when(
      val != "GAM" ~ str_to_sentence(val), 
      TRUE ~ val
    )) %>% 
  mutate(across(c("prop", "perc"), specify_decimal, k = 1)) %>% 
  unite(label, c("metric", "val")) %>% 
  mutate(label = str_replace_all(label, " ", "_"), 
         label = str_remove_all(label, "\\(|\\)"))

#
# Model descriptives 
#

# Requires some annoying wrangling to get the right subtables
mean_analyses <- msa_models_unique %>% 
  group_by(animal) %>% 
  summarise(max_n_models = max(model_n)) %>% 
  summarise(
    mean_models = mean(max_n_models, na.rm = T), 
    sd_models = sd(max_n_models, na.rm = T), 
    min_models = min(max_n_models, na.rm = T), 
    max_models = max(max_n_models, na.rm = T), 
    n_models = sum(max_n_models, na.rm = T)
  )

predictor_n <- msa_models_unique %>% 
  summarise(
    mean_predictor = mean(n_predictors, na.rm = TRUE), 
    sd_predictor = sd(n_predictors, na.rm = TRUE), 
    min_predictor = min(n_predictors, na.rm = TRUE), 
    max_predictor = max(n_predictors, na.rm = TRUE), 
    n_predictor = sum(n_predictors, na.rm = TRUE)
    )

rterms_n <- msa_models_unique %>% 
  filter(n_random != 0) %>% 
  summarise(
    mean_rterms = mean(n_random, na.rm = TRUE), 
    sd_rterms = sd(n_random, na.rm = TRUE), 
    min_rterms = min(n_random, na.rm = TRUE), 
    max_rterms = max(n_random, na.rm = TRUE), 
    n_rterms = sum(n_random, na.rm = TRUE)
    )

# random intercepts
rterms_int_n <- msa_models_unique %>% 
  filter(n_random_int != 0) %>% 
  summarise(
    mean_rint = mean(n_random_int, na.rm = TRUE), 
    sd_rint = sd(n_random_int, na.rm = TRUE), 
    min_rint = min(n_random_int, na.rm = TRUE), 
    max_rint = max(n_random_int, na.rm = TRUE), 
    n_rint = sum(n_random_int, na.rm = TRUE)
    )

# random slopes
rterms_slope_n <- msa_models_unique %>% 
  filter(n_random != 0) %>% 
  summarise(
    mean_rslope = mean(n_random_slo, na.rm = TRUE), 
    sd_rslope = sd(n_random_slo, na.rm = TRUE), 
    min_rslope = min(n_random_slo, na.rm = TRUE), 
    max_rslope = max(n_random_slo, na.rm = TRUE), 
    n_rslope = sum(n_random_slo, na.rm = TRUE)
    )

# Now join them all together
tbl_model_desc <- bind_rows(
  mean_analyses %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  predictor_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_int_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals"), 
  rterms_slope_n %>% 
  pivot_longer(cols = everything(), names_to = "label", values_to = "vals")
) %>% 
  separate(label, c("Metric", "item"), sep = "_") %>% 
  pivot_wider(names_from = Metric, values_from = vals) %>% 
  mutate(across(c("mean", "sd"), specify_decimal, k = 1)) %>% 
  mutate(
    Metric = item, 
    Metric = case_when(
      Metric == "models" ~ "Models", 
      Metric == "predictor" ~ "Predictors", 
      Metric == "rterms" ~ "Random terms", 
      Metric == "rint" ~ "Intercept", 
      Metric == "rslope" ~ "Slope"
    ), 
    desc = "model_desc", 
    label = glue::glue("{desc}_{item}"), 
    `Mean (SD)` = glue::glue("{mean} ({sd})"), 
    Range = glue::glue("{min} -- {max}")) %>% 
  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg = mean, 
         sd, Range) %>% 
  mutate(across(-c("desc", "Metric"), as.character))

```

<!-- Begin Table --> 
```{r}
#| label: descriptives-table
#| results: 'asis'
bind_rows(
  tbl_team_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
  tbl_categorical_desc %>% 
    select(desc = Metric, Metric = Type, val1 = n, val2 = perc) %>% 
    mutate(val1 = glue::glue("{val1}")), 
  tbl_model_desc %>% 
    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
) %>% 
  mutate(order = c(
    1, 6, 4, 3, 5, 2, 
    25, 24, 26, 28, 27, 29, 
    30, 8, 7, 10, 9, 11, 
    12, 18, 17, 15, 14, 
    16, 13, 19, 
    20, 22, 21, 23, 
    31, 32, 33, 34, 35
    )
  ) %>% 
  arrange(order) %>% 
  select(-order) %>% 
  mutate(desc = str_replace_all(desc, "team_desc", " "), 
    desc = str_replace_all(desc, "model_desc", "N"), 
    desc = case_when(
      Metric != "Models" & desc == "N" ~ " ", 
      Metric != "Frequentist" & desc == "Framework" ~ " ", 
      Metric != "Linear model" & desc == "Model" ~ " ", 
      Metric != "F0" & desc == "Outcome" ~ " ", 
      Metric != "Word" & desc == "Temporal window" ~ " ", 
      Metric != "Categorical" & desc == "Typicality operationalization" ~ " ", 
      TRUE ~ desc)
    ) %>% 
  filter(Metric != "n. random smooths") %>% 
  mutate(Metric = str_remove_all(Metric, "n. "), 
         Metric = str_to_sentence(Metric)) %>% 
  rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
    `\\bf{Mean (SD)}` = val2) %>% 
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ",  .before = 15) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 22) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
  add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 29) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
    `\\bf{Mean (SD)}` = " ", .before = 33) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
    `\\bf{Mean (SD)}` = " ", .before = 38) %>%
  add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
    .before = 39) %>% 
  kbl(., booktabs = T, align = c("l", "l", "r", "r"), escape = F, 
    longtable = F, linesep = "", 
    caption = glue::glue("Descriptive statistics of all contributing teams and their acoustic and statistical analyses. The summary includes data from {pull_from_tib(team_desc_df, stage, 'Submitted', n_teams)} teams and  {pull_from_tib(team_desc_df, stage, 'Submitted', n_analysts)} analysts."), 
    label = "descriptives-table") %>%
  kable_styling(full_width = F, latex_options = "scale_down") %>% 
  add_indent(c(9, 16, 23, 30, 34, 40)) %>% 
  add_indent(43:44, all_cols = T) %>% 
  row_spec(8, hline_after = T) %>% 
  row_spec(29, hline_after = T)
```
<!-- END TABLE -->

### 2022-09-25 RR_manuscript/supplementary_materials.Rmd
fix machine learning typo

@@
   filter(Metric != "n. random smooths") %>% 
-  mutate(Metric = str_remove_all(Metric, "n. "), 
-         Metric = str_to_sentence(Metric)) %>% 
   rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 

### 2022-09-25 RR_manuscript/Draft_RR.Rmd
add prose explaining diff between submitted and included studies/numbers, reference supplementary materials

@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-
-The research compendium of study contains all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
+The research compendium of study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
 
@@
 `r pull_from_tib(team_desc_df, stage, "Initial", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams initially signed up to participate in the study, comprising `r pull_from_tib(team_desc_df, stage, "Initial", n_analysts)` analysts.
-`r (pull_from_tib(team_desc_df, stage, "Initial", n_teams) - pull_from_tib(team_desc_df, stage, "Final", n_teams)) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
-
-`r pull_from_tib(team_desc_df, stage, "Final", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analysis by the established deadline.
-These are the teams that are included in this study.
-The submitting teams comprised `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
+`r (pull_from_tib(team_desc_df, stage, "Initial", n_teams) - pull_from_tib(team_desc_df, stage, "Submitted", n_teams)) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` of the signed-up teams dropped out during the analysis phase.
+
+`r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
+The analyses from which it was possible to extract an effect size were included in the meta-analysis. 
+Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in this study.
+In what follows, we describe the characteristics of these teams and analyses, i.e., those included in the meta-analyses. 
+A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.
+
+The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.

### 2022-09-25 RR_manuscript/Draft_RR.tex
add prose explaining diff between submitted and included studies/numbers, reference supplementary materials

@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-
-The research compendium of study contains all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
+The research compendium of study containing all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
 
@@
 Eighty-four teams initially signed up to participate in the study, comprising 211 analysts.
-Fifty-four of the signed-up teams dropped out during the analysis phase.
+Thirty-eight of the signed-up teams dropped out during the analysis phase.
 
-Thirty teams submitted their analysis by the established deadline.
-These are the teams that are included in this study.
-The submitting teams comprised 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
+Forty-six teams submitted their analyses by the established deadline.
+The analyses from which it was possible to extract an effect size were included in the meta-analysis.
+Of the submitted analyses, the initiating authors identified 170 from 30 teams that were deemed eligible to be included in this study.
+In what follows, we describe the characteristics of these teams and analyses, i.e., those included in the meta-analyses.
+A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.
+
+The included analyses were provided by 30 teams, comprising 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.

### 2022-09-25 RR_manuscript/Draft_RR.Rmd
standardize am vs. uk english

@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question.
+In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
 Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects."
@@
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalise the phenomenon under investigation.
+In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalize the phenomenon under investigation.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
@@
 In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
-Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
-(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
 This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
@@
 
-These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.
+These decisions are intended to be made prior to any statistical analysis, but are at times revised *a posteriori* in light of unforeseen or surprising outcomes (i.e.
 after data collection and/or preliminary analyses).
@@
 The initiating authors (SC, JC, TR) conducted the analyses outlined in this section.
-We did not conduct confirmatory tests of any a priori hypotheses.
+We did not conduct confirmatory tests of any *a priori* hypotheses.
 We consider our analysis exploratory.
@@
 We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
-We realised when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
+We realized when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
 There was no team that declared to have made post-hoc changes to the analyses.
@@
 
-After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realisation of sentences with adjective-noun combinations.
+After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
@@
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable. 
-We invite other researchers to re-analyse our data and try to replicate our results using a different research question.
+We invite other researchers to re-analyze our data and try to replicate our results using a different research question.
 
@@
 In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018; @darwin2020; @fox2021open].
-Researchers do not analyse data in a vacuum.
+Researchers do not analyze data in a vacuum.
 It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
-When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
+When many different analysts have to analyze the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.
@@
 That taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
-We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalisation and computational modelling.
+We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modelling.
 

### 2022-09-25 RR_manuscript/Draft_RR.tex
standardize am vs. uk english

@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production dataset to 30 teams of researchers and asked them to answer the same research question.
+In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
 Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects.
@@
 In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
-Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
-(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
+(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
 This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
@@
 
-These decisions are intended to be made prior to any statistical analysis, but are at times revised a posteriori in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
+These decisions are intended to be made prior to any statistical analysis, but are at times revised \emph{a posteriori} in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
 These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
@@
 The initiating authors (SC, JC, TR) conducted the analyses outlined in this section.
-We did not conduct confirmatory tests of any a priori hypotheses.
+We did not conduct confirmatory tests of any \emph{a priori} hypotheses.
 We consider our analysis exploratory.
@@
 We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
-We realised when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
+We realized when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
 There was no team that declared to have made post-hoc changes to the analyses.
@@
 
-After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realisation of sentences with adjective-noun combinations.
+After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
@@
 We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
-We invite other researchers to re-analyse our data and try to replicate our results using a different research question.
+We invite other researchers to re-analyze our data and try to replicate our results using a different research question.
 
@@
 In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{jafar2018, darwin2020, fox2021open}.
-Researchers do not analyse data in a vacuum.
+Researchers do not analyze data in a vacuum.
 It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
-When many different analysts have to analyse the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
+When many different analysts have to analyze the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.

### 2022-09-26 RR_manuscript/Draft_RR.Rmd
typos and stuff

@@
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
+In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
 Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
@@
 (ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
-This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
+This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices"---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
 
@@
 
-Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
+Consequently, a good part of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
 These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
@@
 Despite recent efforts to improve transparency and reproducibility [e.g.
-@miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].
+@miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework ([osf.io](https://osf.io)), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].
 
@@
 In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
-Analytic approaches and consequently the results varied widely between teams.
+The analytic approaches and, consequently, the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
-
 The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
@@
 @dutilh2019 and @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also @Parker2020 on analytic flexibility in ecology, and @botvinik-nezer2020 on neuroimaging data).
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020, and @botvinik-nezer2020, regarding analytic flexibility in ecology and neuroimaging data, respectively].
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 Extending on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
 This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
@@
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
-Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking path related to measurement.
-
+Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking paths related to measurement. 
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
@@
 
-Depending on the speaker's intention, this sentence can be said in different ways.
+\noindent Depending on the speaker's intention, this sentence can be said in different ways.
 For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word *another* or *meeting* to contrast it with more pleasant activities.
@@
 @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
-A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
+A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs. *pear*).
 This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
@@
 
-The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
+The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains, as is the case with suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.
@@
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
-The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
+The latter can also be expressed by global vs. local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
 Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].
@@
 In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
-The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
+The larger the functional domain (e.g. segments vs. words vs. utterances), the higher the number of conceivable operationalizations.
 For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *Zoom* (see 2a and 2b).
@@
 
-Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
+\noindent Do we compare only the word *another* in (2a) and (2b), or also the word *Zoom*?
 Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
+We employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
 
 In this study, we followed the procedures proposed by @Parker2020 and @aczel2021.
-The project involved the following five phases:
+The project comprised the following five phases:
 
@@
 
-We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
+We initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would take nine months.
 <!-- The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams. -->
-Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.
+Phase 4 (meta-analysis) took longer than initially anticipated and the total duration of the project was approximately 12 months.
 
@@
 Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
-We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).
+We received initial expression of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).
 
@@
 Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
-The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
+The sequences were systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.
 
@@
 
-The reviewers were also given the option to include further comments in a text box for each of the three ratings.
+\noindent The reviewers were also given the option to include further comments in a text box for each of the three ratings.
 
 After submitting the review, a methods section from a second analysis was then made available to the reviewer.
-This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
-We have decided to skip this last step due to time constrains.]
+This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[Initially we planned to present simultaneously all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
+Ultimately, we decided to skip this step due to time constraints.]
 
@@
 We did not conduct confirmatory tests of any *a priori* hypotheses.
-We consider our analysis exploratory.
+We consider our analyses exploratory.
 
@@
 <!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
-The model did not incur in divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
+The model did not incur any divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
 <!-- TODO: add link to meta-model code -->
@@
 $$\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}$$
-
-where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
+\vspace{0.05in}
 
@@
 
+\noindent where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model.
 In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].
@@
 The numeric predictors were centered and scaled and the categorical predictors were sum coded.
-As the prior for the intercept and the predictors we used a normal distribution with mean 0 and standard deviation 1.
+We used a normal distribution with mean 0 and standard deviation 1 as the prior for the intercept and the predictors.
 The model was run with the same settings as with the meta-analytic model.
@@
 All relevant data, code, and materials have been publicly archived on the Open Science Framework (<https://osf.io/3bmcp/>).
-Archived data includea the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
+Archived data include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
 Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
@@
 
-We have exclude from our synthesis any individual analysis submitted after we have completed peer review or those unaccompanied by analysis files that allow us to understand what the analysts did.
+We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to understand what the analysts did.
 We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
+The research compendium of the study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
 
@@
 The analyses from which it was possible to extract an effect size were included in the meta-analysis. 
-Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in this study.
-In what follows, we describe the characteristics of these teams and analyses, i.e., those included in the meta-analyses. 
+Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis.
+In what follows, we describe the characteristics of these teams and analyses. 
 A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.
@@
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
-We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
-
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
+We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
+
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-`r round(outcome_n[[1,1]],2) * 100`\% of models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
+`r (round(outcome_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
 
@@
 The majority of models were run within a frequentist framework (`r round(framework_n[[2,1]],2) * 100`\%).
-`r round(framework_n[[1,1]],2) * 100`\% were run within a Bayesian framework.
+`r (round(framework_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent were run within a Bayesian framework.
 While teams almost exclusively used linear models to analyze their data (`r round(model_n[[2,1]],2) * 100`\%), teams differed drastically in how they accounted for dependencies within the data.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-`r round(random_n[[3,1]],2) * 100`\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
-`r round(random_n[[1,1]],2) * 100`\% specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
+`r (round(random_n[[3,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
+`r (round(random_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included `r round(rterms_n$mean_rterms,1)` random terms in their models. 
 Table \@ref(tab:descriptives-table) provides a summary of the statistical analyses. 
+Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
+<!-- TR: I am still confused, so if we were to ignore different random effect specifications that the number is x?
+Can we find a clearer way to express this, e.g.
+"When considering choices related to only statistical framework, type of model, distribution family and fixed terms, there were..." -->
 
@@
 ```
-
-Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
-<!-- TR: I am still confused, so if we were to ignore different random effect specifications that the number is x?
-Can we find a clearer way to express this, e.g.
-"When considering choices related to only statistical framework, type of model, distribution family and fixed terms, there were..." -->
 

### 2022-09-26 RR_manuscript/Draft_RR.tex

@@
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
+In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
 Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
@@
 (ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
-This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
+This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices''---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
 
@@
 
-Consequently, it is likely that a good part of published papers present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
+Consequently, a good part of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
 These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
@@
 However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
-Despite recent efforts to improve transparency and reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
+Despite recent efforts to improve transparency and reproducibility \citep[e.g.][]{miguel2014promoting, klein2018practical} and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (\href{https://osf.io}{osf.io}), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare \citep{wicherts2006poor}.
 
@@
 In a seminal collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
-Analytic approaches and consequently the results varied widely between teams.
+The analytic approaches and, consequently, the results varied widely between teams.
 Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-
 The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
@@
 \citet{dutilh2019} and \citet{starns2019assessing} investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
-Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams (see also \citet{Parker2020} on analytic flexibility in ecology, and \citet{botvinik-nezer2020} on neuroimaging data).
+Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citep[see also][and \citet{botvinik-nezer2020}, regarding analytic flexibility in ecology and neuroimaging data, respectively]{Parker2020}.
 \citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
@@
 Extending on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise but seem to be more dependent on the research question itself.
+Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
 This is in line with a recent re-analysis of \citet{silberzahn2018many} by \citet{auspurg2021has}.
@@
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
-Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking path related to measurement.
-
+Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking paths related to measurement.
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
@@
 
-Depending on the speaker's intention, this sentence can be said in different ways.
+\noindent Depending on the speaker's intention, this sentence can be said in different ways.
 For instance, if the speaker is exhausted by all their meetings, they might acoustically highlight the word \emph{another} or \emph{meeting} to contrast it with more pleasant activities.
@@
 The acoustic parameters of units are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other units \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
-A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
+A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs.~\emph{pear}).
 This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
@@
 
-The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
+The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains, as is the case with suprasegmental aspects of speech.
 For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
@@
 Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
-The latter can also be expressed by global vs local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
+The latter can also be expressed by global vs.~local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
 Extra-linguistic information, like the speaker's intentions, levels of emotional arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch \citep{foulkes2006, ogden2004, white2009}.
@@
 In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
-The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
+The larger the functional domain (e.g.~segments vs.~words vs.~utterances), the higher the number of conceivable operationalizations.
 For example, several decisions have to be made when comparing the two realizations of the sentence in (1), one of which is intended to signal emphasis on \emph{another} and one of which emphasizes \emph{Zoom} (see 2a and 2b).
@@
 
-Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{Zoom}?
+\noindent Do we compare only the word \emph{another} in (2a) and (2b), or also the word \emph{Zoom}?
 Do we measure utterance-wide acoustic profiles, whole words, or just stressed syllables?
@@
 The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
-We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
+We employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.
 
 In this study, we followed the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
-The project involved the following five phases:
+The project comprised the following five phases:
 
@@
 
-We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
-Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.
+We initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would take nine months.
+Phase 4 (meta-analysis) took longer than initially anticipated and the total duration of the project was approximately 12 months.
 
@@
 
-The reviewers were also given the option to include further comments in a text box for each of the three ratings.
+\noindent The reviewers were also given the option to include further comments in a text box for each of the three ratings.
 
 After submitting the review, a methods section from a second analysis was then made available to the reviewer.
-This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.\footnote{We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
-We have decided to skip this last step due to time constrains.}
+This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.\footnote{Initially we planned to present simultaneously all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
+Ultimately, we decided to skip this step due to time constraints.}
 
@@
 We did not conduct confirmatory tests of any \emph{a priori} hypotheses.
-We consider our analysis exploratory.
+We consider our analyses exploratory.
 
@@
 We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
-The model did not incur in divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
+The model did not incur any divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
 The code used to run the model can be found at \textless\textgreater.
@@
 \[\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}\]
+\vspace{0.05in}
 
-where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
-
+\noindent where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
 In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
@@
 All relevant data, code, and materials have been publicly archived on the Open Science Framework (\url{https://osf.io/3bmcp/}).
-Archived data includea the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
+Archived data include the original data set distributed to all analysts, any edited versions of the data analyzed by individual teams, and the data we analyzed with our meta-analyses, which include the standardized effect sizes, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our questionnaires of analysts.
 Similarly, we archived both the analysis code used for each individual analysis and the code from our meta-analyses.
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of study containing all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
+The research compendium of the study containing all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
 
@@
 The analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the submitted analyses, the initiating authors identified 170 from 30 teams that were deemed eligible to be included in this study.
-In what follows, we describe the characteristics of these teams and analyses, i.e., those included in the meta-analyses.
+Of the submitted analyses, the initiating authors identified 170 from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
+In what follows, we describe the characteristics of these teams and analyses.
 A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.
@@
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
-We take this to suggest that analysts had an overall rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
+We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams have submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-35\% of models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 12\% used vowel formants, 14\% intensity, and 3\% other measures.
+Thirty-five percent of the models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 12\% used vowel formants, 14\% intensity, and 3\% other measures.
 
@@
 The majority of models were run within a frequentist framework (83\%).
-17\% were run within a Bayesian framework.
+Seventeen percent were run within a Bayesian framework.
 While teams almost exclusively used linear models to analyze their data (98\%), teams differed drastically in how they accounted for dependencies within the data.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-8\% of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-65\% specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
+Eight percent of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects, included 2.5 random terms in their models.
 Table \ref{tab:descriptives-table} provides a summary of the statistical analyses.
-
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.

### 2022-09-26 RR_manuscript/Draft_RR.Rmd
small fixes

@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-`r (round(random_n[[3,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
+`r (round(random_n[[3,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
 `r (round(random_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
@@
 
-When considering both acoustic and statistical analysis, we have found a grand total of `r nrow(unique_acou_stat)` different analytic pipelines.
+When considering both acoustic and statistical analyses, we have found a grand total of `r nrow(unique_acou_stat)` different analytic pipelines.
 In other words, each individual submitted analysis was unique.
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean$mean_prating,1)` (SD = `r round(review_mean$sd_prating,1)`, see Table \@ref(tab:descriptives-table)).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is `r round(review_mean$mean_prating,1)` (SD = `r round(review_mean$sd_prating,1)`).
 The mean rating of the statistical analysis is `r round(review_mean$mean_srating,1)` (SD = `r round(review_mean$sd_srating,1)`).
@@
 
-According to the preregistered meta-analytic model, the group-level standard deviation for team is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
+According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between $\pm$ `r round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2)` to $\pm$ `r round((meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]] * 1.96), 2)` (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
 

### 2022-09-26 RR_manuscript/Draft_RR.tex
small fixes

@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-Eight percent of linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+Eight percent of the linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
 Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
@@
 
-When considering both acoustic and statistical analysis, we have found a grand total of 104 different analytic pipelines.
+When considering both acoustic and statistical analyses, we have found a grand total of 104 different analytic pipelines.
 In other words, each individual submitted analysis was unique.
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9, see Table \ref{tab:descriptives-table}).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9).
 The mean rating of the statistical analysis is 69.5 (SD = 16.5).
@@
 
-According to the preregistered meta-analytic model, the group-level standard deviation for team is between 0.03 and 0.07 standard units, at 95\% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between ±0.06 to ±0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
+According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units, at 95\% credibility.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between \(\pm\) 0.06 to \(\pm\) 0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
 

### 2022-09-27 RR_manuscript/Draft_RR.Rmd

@@
       paste()
+}
+
+pm  <- function(x) {
+  line <- glue::glue("$\\pm {x}$")
+  return(line)
 }
@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between $\pm$ `r round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2)` to $\pm$ `r round((meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]] * 1.96), 2)` (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` to `r pm(round((meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]] * 1.96), 2))` (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
 
@@
 
-The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about ±0.1 standard units and 95% probability.
+The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0.1)` standard units and 95% probability.
 The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
@@
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
-In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g. by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.
+by duration, f0 etc,) or, if they do, they do so by a maximum of `r pm(x = 0.02)` standard units.
 
@@
 
-While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
+While the majority of model estimates and their uncertainty after shrinkage (black, orange, and blue points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
 
@@
 The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)`.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, time 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms].
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, time 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms.]
 
@@
 #| results: 'asis'
-knitr::kable(msa_sd_sd, format = "latex", booktabs = T, escape = F, 
+msa_sd_sd %>% 
+  mutate(outcome = case_when(
+    outcome != "f0" ~ str_to_sentence(outcome), 
+    TRUE ~ outcome), 
+    `temporal window` = str_to_sentence(`temporal window`)) %>% 
+  janitor::clean_names(case = "sentence") %>% 
+  knitr::kable(format = "latex", booktabs = T, escape = F, 
     linesep = "", 
@@
 
-These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many, @breznau2021observing].
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many; @breznau2021observing].
 Following @breznau2021observing [p.
@@
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher, @simmons2011false].
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher; @simmons2011false].
 One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): "[T]he project's approach is too much top-down instead of bottom-up.
@@
 Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for [@tukey1953].
-Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking, @john2012measuring, @simmons2011false], while null results remain unreported [@sterling1959publication, @rosenthal1979file].
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
+The standard solution to this problem is to apply a correction for family-wise error (i.e., alpha inflation), which consequently reduces power. 
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking; @john2012measuring; @simmons2011false], while null results remain unreported [@sterling1959publication; @rosenthal1979file].
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [ @vazire2017quality, @fidler2018reproducibility].
-One of the suggested paths forward is for researchers to directly replicate previous studies more often [@open2015estimating, @camerer2018evaluating].
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [@vazire2017quality; @fidler2018reproducibility].
+One of the suggested paths forward is for researchers to directly replicate previous studies more often [@open2015estimating; @camerer2018evaluating].
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more, @starns2019assessing].
+Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al. refers to as "epistemic humility".
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what @breznau2021observing refer to as "epistemic humility" (p. 10).
 
@@
 
-We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory, @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
 Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
@@
 
-This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has].
-However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see @scheel2022most) a common phenomenon.
+However, we consider this very underspecification of research hypotheses in the field of speech science [and beyond, see @scheel2022most] a common phenomenon.
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
@@
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
-We focused on quantitative analyses that require operationalization of a multidimensional signal. 
+We focused on quantitative analyses that require the operationalization of a multidimensional signal. 
 While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are based on qualitative methods.
+This is an important point to make because the cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 Going beyond previous empirical studies, the current paper looked at many analyses of speech data.
-Speech is a multidimensional signal that allows for great flexibility because it lend itself to a variety of possible operationalizations.
+Speech is a multidimensional signal that allows for great flexibility because it lends itself to a variety of possible operationalizations.
 In this study, 30 teams of speech scientists analyzed the same data set.
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction.
-That taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other. 
+That, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
 We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modelling.

### 2022-09-27 RR_manuscript/Draft_RR.tex

@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units, at 95\% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between \(\pm\) 0.06 to \(\pm\) 0.14 (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
+This means that the mean deviations of any individual team from the meta-analytic effect estimate range between \(\pm 0.06\) to \(\pm 0.14\) (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
 
@@
 
-The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about ±0.1 standard units and 95\% probability.
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0.1\) standard units and 95\% probability.
 The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
@@
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
-In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of ±0.02 standard units.
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
 
@@
 
-While the majority of model estimates and their uncertainty (after shrinkage, black points and lines) yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
+While the majority of model estimates and their uncertainty after shrinkage (black, orange, and blue points and lines) yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
 
@@
 The reported effect estimates from teams varied between -0.65 and 0.99 standard units which corresponds to duration values ranging from -21.86 to 50.81.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms}.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
 
@@
 \toprule
-outcome & temporal window & lower & upper & unit\\
+Outcome & Temporal window & Lower & Upper & Unit\\
 \midrule
-duration & segment & 7.4-11.4 & 10-15.4 & ms\\
-duration & word & 7.2-26.5 & 9.8-35.8 & ms\\
-f0 & segment & 8.9-9.8 & 12-13.3 & hz\\
-f0 & word & 0.9-10.4 & 1.2-14.1 & hz\\
-intensity & segment & 0.7-1.6 & 1-2.1 & dB\\
-intensity & word & 0.8-0.9 & 1-1.2 & dB\\
+Duration & Segment & 7.4-11.4 & 10-15.4 & ms\\
+Duration & Word & 7.2-26.5 & 9.8-35.8 & ms\\
+f0 & Segment & 8.9-9.8 & 12-13.3 & hz\\
+f0 & Word & 0.9-10.4 & 1.2-14.1 & hz\\
+Intensity & Segment & 0.7-1.6 & 1-2.1 & dB\\
+Intensity & Word & 0.8-0.9 & 1-1.2 & dB\\
 \bottomrule
@@
 
-These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][]{silberzahn2018many, breznau2021observing}.
 Following \citet[p.~9]{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions''.
@@
 Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
-The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep[\citet{simmons2011false}]{roettger2019researcher}.
+The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher, simmons2011false}.
 One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): ``{[}T{]}he project's approach is too much top-down instead of bottom-up.
@@
 Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
-When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate, if not corrected for \citep{tukey1953}.
-Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking}, while null results remain unreported \citep[\citet{rosenthal1979file}]{sterling1959publication}.
+When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate.
+The standard solution to this problem is to apply a correction for family-wise error (i.e., alpha inflation), which consequently reduces power.
+Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep{kerr1998harking, john2012measuring, simmons2011false}, while null results remain unreported \citep{sterling1959publication, rosenthal1979file}.
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
@@
 The current results point to important barriers for successful accumulation of knowledge.
-The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[\citet{fidler2018reproducibility}]{vazire2017quality}.
-One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep[\citet{camerer2018evaluating}]{open2015estimating}.
+The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep{vazire2017quality, fidler2018reproducibility}.
+One of the suggested paths forward is for researchers to directly replicate previous studies more often \citep{open2015estimating, camerer2018evaluating}.
 While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep[\citet{starns2019assessing}]{rotello2015more}.
+Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what \citet{breznau2021observing} refer to as ``epistemic humility'' (p.~10).
 
@@
 
-We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep[\citet{meehl1990summaries}]{dubin1970theory}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
+We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
 Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
@@
 
-This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
-However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see \citet{scheel2022most}) a common phenomenon.
+However, we consider this very underspecification of research hypotheses in the field of speech science \citep[and beyond, see][]{scheel2022most} a common phenomenon.
 For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
@@
 The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
-We focused on quantitative analyses that require operationalization of a multidimensional signal.
+We focused on quantitative analyses that require the operationalization of a multidimensional signal.
 While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are based on qualitative methods.
+This is an important point to make because the cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one or the other direction.
-That taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other.
+That, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
 We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modelling.

### 2022-09-27 RR_manuscript/Draft_RR.Rmd
remove crossref for section

@@
 dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
-These summary statistics are reported in \@ref{descr-stats} of the Results section.
+These summary statistics are reported in *Descriptive statistics* of the Results section.
+<!-- Add crossref to final version: \@ref(descr-stats) -->
 
@@
 As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
-As we detail in Section \@ref{meta-est}, we have also run further non-preregistered analyses.
+As we detail in Section *Meta-analytic estimation*, we have also run further non-preregistered analyses. <!-- Add crossref to final version: \@ref(meta-est) -->
 For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.

### 2022-09-27 RR_manuscript/Draft_RR.tex
remove crossref for section

@@
 We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
-These summary statistics are reported in @ref\{descr-stats\} of the Results section.
+These summary statistics are reported in \emph{Descriptive statistics} of the Results section.
 
@@
 As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
-As we detail in Section @ref\{meta-est\}, we have also run further non-preregistered analyses.
+As we detail in Section \emph{Meta-analytic estimation}, we have also run further non-preregistered analyses.
 For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.

### 2022-10-13 scripts/r/09_credit_taxonomy.Rmd
add CRediT data and rmd

---
title: "Get CRediT"
author: "Joseph V. Casillas"
output: html_document
date: "Last upate: `r Sys.Date()`"
---

## Load libraries

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )

knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#| label: load-libs
library("googledrive")
library("xml2")
library("dplyr")
library("tidyr")
library("stringr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

## Get google sheet and tidy

```{r}
#| label: identify-download
# give gargle permission
drive_auth(email = TRUE)

# Locate file, check ID
drive_find(n_max = 5, type = "spreadsheet")

# Search by id (just checking)
drive_get(id = "1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA")

# Download to doc folder
drive_download(
  file = "MSA_tenzing_contribution", 
  path = "./data/CRediT/MSA_tenzing_contribution.csv", 
  type = "csv",
  overwrite = T
  )
```

```{r}
#| label: load-tidy-csv

# Create vector of surnames of initiating authors
initiating_authors <- c("Coretta", "Casillas", "Roessig", "Franke", "Roettger")

# Load data
all_data_temp <- read_csv("./data/CRediT/MSA_tenzing_contribution.csv") %>% 
  janitor::clean_names()

# Subset initiating authors
initiators <- all_data_temp %>% 
  filter(surname %in% initiating_authors) %>% 
  mutate(is_initiating = 1)

# Subset analysts
analysts <- all_data_temp %>% 
  filter(!(surname %in% initiating_authors)) %>% 
  mutate(is_initiating = 0) %>% 
  arrange(surname)

contributors <- bind_rows(initiators, analysts) %>% 
  mutate(middle_name = replace_na(middle_name, ""), 
         is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
  mutate(name = str_replace_all(name, "  ", " "))

```

## Author list

```{r}
#| label: print-names

author_list <- contributors %>% 
  pull(name) %>% 
  knitr::combine_words(words = .)
```

These are the authors:  
`r author_list`

## Institutions

```{r}
#| label: institutions
#| out.width: 100%
#| fig.height: 8

affiliations <- contributors %>% 
  count(primary_affiliation) %>% 
  arrange(n)

affiliations %>% 
  mutate(lab_truc = str_sub(primary_affiliation, 1, 30),
    lab_truc = fct_reorder(lab_truc, n, min)) %>% 
  ggplot() + 
  aes(x = n, y = lab_truc) + 
  geom_segment(aes(x = 0, xend = n, yend = lab_truc)) + 
  geom_point() + 
  labs(y = NULL) + 
  theme_bw(base_size = 9)
```

There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
`r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation. 
There were `r filter(contributors, is.na(email_address)) %>% nrow` assholes that didn't include their email (`r filter(contributors, is.na(email_address)) %>% pull(name) %>% knitr::combine_words(words = .)`).

## Contributor roles taxonomy

```{r}
#| label: contributor-roles-plot-initiators
#| out.width: 100%
#| fig.height: 4

initiating_names <- c("Stefano Coretta", "Joseph V. Casillas", 
                      "Simon Roessig", "Michael Franke", "Timo B. Roettger")

contributor_roles <- rev(c(
    "Conceptualization", "Data curation", "Formal Analysis",
    "Funding acquisition", "Investigation", "Methodology",
    "Project administration", "Resources", "Software", "Supervision",
    "Validation", "Visualization", "Writing - original draft",
    "Writing - review & editing"
  ))

cr_prep <- contributors %>% 
  select(name:writing_review_editing) %>% 
  pivot_longer(cols = -name, names_to = "contributor_roles", values_to = "val") %>% 
  mutate(val = as.numeric(val)) %>% 
  group_by(name, contributor_roles) %>% 
  mutate(order_x = seq_along(name)) %>% 
  group_by(name) %>% 
  mutate(order_y = seq_along(name)) %>% 
  ungroup() %>% 
  mutate(initials = gsub('\\b(\\pL)\\pL{2,}|.','\\U\\1', name, perl = TRUE), 
    is_initiating = if_else(name %in% initiating_names, 1, 0), 
    contributor_roles = fct_rev(contributor_roles))

cr_prep %>% 
  filter(is_initiating == 1) %>% 
  mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas", 
                            "Simon Roessig", "Michael Franke")) %>% 
  ggplot() +
  aes(x = name, y = contributor_roles, alpha = val) +
    geom_point(size = 3.5, pch = 18, show.legend = F) +
    scale_x_discrete(position = "top") + 
    scale_y_discrete(labels = contributor_roles) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = "Initiating authors", y = "Contributor roles",
         caption = "Author contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15)
    )

```

```{r}
#| label: contributor-roles-plot-analysts
#| out.width: 100%
#| fig.height: 10

cr_prep %>% 
  filter(is_initiating == 0) %>% 
  ggplot() +
  aes(y = initials, x = contributor_roles, alpha = val) +
    geom_point(size = 2, pch = 18, show.legend = F) +
    scale_x_discrete(position = "top", labels = rev(contributor_roles)) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = "Contributor roles", y = "Analysts",
         caption = "Author contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
      axis.text.x.top = element_text(angle = 45, hjust = 0, size = rel(0.6)), 
      axis.text.y = element_text(size = rel(0.6))
    )

```

### 2022-10-13 scripts/r/09_credit_taxonomy.Rmd
add comments to Rmd for CRediT

@@
 
+# Combine dfs in correct order
 contributors <- bind_rows(initiators, analysts) %>% 
@@
 
+# Get count of unique affiliations
 affiliations <- contributors %>% 
@@
 
+# Plot affiliations as a function of n
 affiliations %>% 
@@
 
-initiating_names <- c("Stefano Coretta", "Joseph V. Casillas", 
-                      "Simon Roessig", "Michael Franke", "Timo B. Roettger")
-
-contributor_roles <- rev(c(
+# Vector of formated contributor roles
+contributor_roles <- c(
     "Conceptualization", "Data curation", "Formal Analysis",
@@
     "Writing - review & editing"
-  ))
+  )
 
+# Format contributors for plotting
 cr_prep <- contributors %>% 
-  select(name:writing_review_editing) %>% 
-  pivot_longer(cols = -name, names_to = "contributor_roles", values_to = "val") %>% 
+  select(name:writing_review_editing, is_initiating) %>% 
+  pivot_longer(
+    cols = -c("name", "is_initiating"), 
+    names_to = "contributor_roles", 
+    values_to = "val"
+    ) %>% 
   mutate(val = as.numeric(val)) %>% 
@@
   mutate(initials = gsub('\\b(\\pL)\\pL{2,}|.','\\U\\1', name, perl = TRUE), 
-    is_initiating = if_else(name %in% initiating_names, 1, 0), 
     contributor_roles = fct_rev(contributor_roles))
 
+# Plot initiating authors
 cr_prep %>% 
@@
     scale_x_discrete(position = "top") + 
-    scale_y_discrete(labels = contributor_roles) + 
+    scale_y_discrete(limits = rev, labels = rev(contributor_roles)) + 
     scale_alpha_continuous(range = c(0.05, 1)) +
@@
   aes(y = initials, x = contributor_roles, alpha = val) +
-    geom_point(size = 2, pch = 18, show.legend = F) +
-    scale_x_discrete(position = "top", labels = rev(contributor_roles)) + 
+    geom_point(size = 1.75, pch = 18, show.legend = F) +
+    scale_x_discrete(labels = contributor_roles) + 
     scale_alpha_continuous(range = c(0.05, 1)) +
-    labs(x = "Contributor roles", y = "Analysts",
-         caption = "Author contributions based on CRediT taxonomy") +
+    labs(x = NULL, y = "Analysts",
+         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
     theme_minimal(base_size = 12, base_family = "Times") +
@@
       panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
-      axis.text.x.top = element_text(angle = 45, hjust = 0, size = rel(0.6)), 
-      axis.text.y = element_text(size = rel(0.6))
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
+                                     size = rel(0.6)), 
+      axis.text.y = element_text(size = rel(0.5))
     )

### 2022-10-14 scripts/r/09_credit_taxonomy.Rmd
pg-13

@@
 `r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation. 
-There were `r filter(contributors, is.na(email_address)) %>% nrow` assholes that didn't include their email (`r filter(contributors, is.na(email_address)) %>% pull(name) %>% knitr::combine_words(words = .)`).
+There were `r filter(contributors, is.na(email_address)) %>% nrow` individuals that didn't include their email (`r filter(contributors, is.na(email_address)) %>% pull(name) %>% knitr::combine_words(words = .)`).
 

### 2022-10-14 scripts/r/09_credit_taxonomy.Rmd
move timo to last, add emails

--- 2022-10-13 scripts/r/09_credit_taxonomy.Rmd
@@
   unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
-  mutate(name = str_replace_all(name, "  ", " "))
+  mutate(name = str_replace_all(name, "  ", " ")) %>% 
+  bind_rows(
+    slice(., which(name != "Timo B. Roettger")), 
+    slice(., which(name == "Timo B. Roettger"))
+    ) %>%
+  tail(nrow(.) / 2)
 
@@
 `r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
-There were `r filter(contributors, is.na(email_address)) %>% nrow` assholes that didn't include their email (`r filter(contributors, is.na(email_address)) %>% pull(name) %>% knitr::combine_words(words = .)`).
 

### 2022-10-17 RR_manuscript/Draft_RR.Rmd
google doc typos and style suggestions/corrections

@@
 Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modeling but also from decisions regarding the quantification of the measured behavior.
 In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
@@
 The latter situation has been referred to as the *inference crisis* [@rotello2015more; @starns2019assessing] and is, among other things, rooted in the inherent flexibility of data analysis [often referred to as researcher degrees of freedom: @simmons2011false; @gelman2014statistical].
-Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
+Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling data, to name a few.
 Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
@@
 (ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
-This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices"---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
+This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices"---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than previously observed, thus giving us a more realistic estimate of variability.
 
@@
 Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
-The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
+The authors' results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
 
@@
 @bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
-Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
-
-Extending on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
+Their results suggest that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
+
+Building on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
@@
 However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
-This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
+This is especially true in the Social Sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
 
@@
 For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
-The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
+The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, as well as post-hoc modifications to the chosen measure.
 Taken together, these aspects alone dramatically increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
@@
 
-Research on speech lies at the intersection of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
-One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).
+Research on speech lies at the intersection of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and treatment of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
+One major challenge in the Speech Sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).
 
 Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
-Thus, choosing how to measure a communicative intention of interest is an important analytic step.
-Take for example the following sentence in (1).
+Thus, choosing how to assess a communicative intention of interest is an important analytic step.
+Take for example the sentence in (1).
 
@@
 @jongman2000acoustic; @lisker1986voicing; @summerfield1981articulatory; @winter2014spoken].
-A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs. *pear*).
-This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
+A classic example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs. *pear*).
+This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and context of surrounding sounds [@lisker1977rapid].
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 
-In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speakers' intentions using speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g. segments vs. words vs. utterances), the higher the number of conceivable operationalizations.
@@
 Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
-Once we have decided to compare fundamental frequency of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
+Once we have decided to compare fundamental frequency (f0) of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
 As Figures \@ref(fig:forkingPaths)B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
+We could also measure the value or time of the f0 minimum or maximum.
 We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data in previous work [see @gordon2017acoustic].
@@
 after data collection and/or preliminary analyses).
-These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
-
-In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
+This multitude of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis [e.g. @wicherts2016].
+
+In sum, speech data is made of complex physical signals that generate an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
@@
 
-Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science. 
-When trying to refer to a banana, what does a speaker say and how do they say it in a given context.
+Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in Language Science. 
+When trying to refer to a banana, what does a speaker say and how do they say it in a given context?
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
@@
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective *yellow* to describe a banana in a situation in which there are a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective *yellow* to describe a banana in a situation in which there are both a yellow and a less ripe green banana available, but not when there is only one banana.
 
@@
 Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and make communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
-Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
+Recent findings suggest that the utility of referring expressions depends on how useful they are for a listener (compared to other referring expressions) to identify a target object.
 For example, @degen2020redundancy showed that modifiers that are less typical for a given referent (e.g.
@@
 
-Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications [e.g., @ladd2008intonational].
+Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via acoustic properties like temporal and spectral modifications [e.g., @ladd2008intonational].
 Most prominently, languages can use intonation to signal discourse relationships between referents.
 Intonation marks discourse-relevant referents for being new or given information, to guide the listeners’ interpretation of incoming messages.
-Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations [e.g.
+Beyond structuring information relative to the discourse, a few studies suggest that speakers might use intonation to signal atypical lexical combinations [e.g.
 @dimitrova2008prosodic; @dimitrova2009did].
@@
 Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.
-*Gelbe Zitrone* 'yellow lemon', *Rote Gurke* 'red cucumber', *Rote Socken* 'red socks').
+*gelbe Zitrone* 'yellow lemon', *rote Gurke* 'red cucumber', *rote Socken* 'red socks').
 
@@
 The upper row illustrates the trial sequence for the speaker (participant) and the lower row illustrates the trial sequence for the confederate.
-After a preview of 1500ms the speaker sees an arrow indicating one of the referent (b).
+After a preview of 1500ms the speaker sees an arrow indicating one of the referents (b).
 Reading the orthographic instructions out loud, the speaker gives the confederate verbal instructions onto which referent they should drag the cube (c).
@@
 In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participant would read a sentence prompt out loud (*Du sollst den Würfel auf der COLOR OBJECT ablegen* 'You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
+Participant read a sentence prompt out loud (*Du sollst den Würfel auf der COLOR OBJECT ablegen* 'You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the *competitor*) using the mouse.
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (*Und jetzt sollst du den Würfel auf der COLOR OBJECT ablegen* 'And now, you have to put the cube on top of the COLOR OBJECT') instructing the experimenter to move the cube on top of a different object (the *target*).
@@
 Focused units denote the set of all (contextually relevant) alternatives [e.g. @rooth1992theory].
-Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color does not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus.
-We call this the Noun Focus condition, or NF for short.
-If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), then the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
+Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language.
+For instance, if the competitor and target objects differ but their color does not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus (Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (Adjective Focus condition, AF).
+If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), then the whole noun phrase is in focus (Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 
-As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
+As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large number of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
@@
 All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
-Researchers could choose to work independently or in a small team.
+Researchers could choose to work independently or in small teams.
 For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
@@
 A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
-The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We then requested that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+We then requested that they answer the research question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
 To do so, they were given the data generated by the experiment described in Section [The data set](#s:dataset).
-The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
 These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.
@@
 
-Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
+Each analysis was evaluated by four different analysis teams who functioned as peer-reviewers.
 Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
@@
 
-After submitting the review, a methods section from a second analysis was then made available to the reviewer.
+After submitting the review, a methods section from a second analysis was made available to the reviewer.
 This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[Initially we planned to present simultaneously all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
@@
 We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where the groups are the analysis teams.
+As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where each analysis team represents a group.
 As we detail in Section *Meta-analytic estimation*, we have also run further non-preregistered analyses. <!-- Add crossref to final version: \@ref(meta-est) -->
@@
 Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) and that was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
+Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
@@
 We used regularizing weakly-informative priors for the intercept $\alpha$ ($Normal(0, 1)$) and for the group-level standard deviation $\sigma_{\alpha_{\text{t}}}$ ($HalfCauchy(0, 1)$).
-We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
+We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan [@stan2021], and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
 <!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
@@
 The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we treated predictors as species and individual analyses as sites.
+For our purposes, we treated predictors as *species* and individual analyses as *sites*.
 For each pair of analyses $(X, Y)$, the SDI was obtained using the following formula:
@@
 
-- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students [numeric].
+- *Research experience* as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate student [numeric].
 - *Initial belief* in the presence of an effect of atypical noun-adjective pairs on acoustics, as answered during the intake questionnaire [numeric].
@@
 
-We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to understand what the analysts did.
+We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
 We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of the study containing all the code and data presented here and can be found at <https://osf.io/3bmcp/>.
+The research compendium of the study, containing all the code and data presented here, can be found at <https://osf.io/3bmcp/>.
 
@@
 `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_sentence()` teams submitted their analyses by the established deadline. 
-The analyses from which it was possible to extract an effect size were included in the meta-analysis. 
+Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
 Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis.
@@
 Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
-PhD students (or younger) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
+PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
@@
 
-The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-`r (round(outcome_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used a measure of duration as the outcome variable, `r round(outcome_n[[2,1]],2) * 100`\% used fundamental frequency (f0), `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
+`r round(outcome_n[[2,1]],2) * 100 %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used fundamental frequency (f0) as the outcome variable, `r (round(outcome_n[[1,1]],2) * 100)`\% used a measure of duration, `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
 
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of `r nrow(unique_acou_oper)` different measurement specifications.
-For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
-The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
+For example, if we consider those analyses that target f0, we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of the article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects [e.g., @gelman2006data; @schielzeth2009conclusions], variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-`r (round(random_n[[3,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
+`r (round(random_n[[3,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences [@hurlbert1984pseudoreplication].
 `r (round(random_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
@@
 When considering both acoustic and statistical analyses, we have found a grand total of `r nrow(unique_acou_stat)` different analytic pipelines.
-In other words, each individual submitted analysis was unique.
+In other words, each individual analysis submitted was unique.
 Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%). 
@@
 The primary aim of this analysis is to assess the degree of between-team variability.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation $\sigma_{\alpha_{\text{t}}}$).
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation ($\sigma_{\alpha_{\text{t}}}$).
 
@@
 
-**Non-preregistered**. However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption. 
-To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id`), which allows us to estimate both the between-team variation along with the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.^[Note that before running this model we have also run one with just model ID as the only (non-nested) group-level effect.
-The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.]
+**Non-preregistered**. However, we did not take into account in our preregistration that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
+To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
+This analysis was not preregistered and should thus be interpreted with caution.^[Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.]
 
@@
 The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
-Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than variability across individual teams.
-We come back to this important observation later.
+Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
+We return to this important observation later.
 
@@
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
-Estimates ranged between `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units.
+Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units.
 
@@
 Interestingly, the model uniqueness, i.e.
-how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
+how unique the choice and combination of predictors is, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
 This suggests that the analysts' results very much depend on their choice of predictors. 
@@
 what is the unit over which the outcome was measured, panel B).
-If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
-If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
-Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
+If, on one hand, an acoustic dimension related to f0 was measured, estimates are lower than the meta-analytic estimate.
+If, on the other hand, vowel formants were measured, estimates are higher than the meta-analytic estimate.
+Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta-analytic estimate.
 In other words, depending on the choice of measurement and the measurement window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
@@
 speakers acoustically modify utterances to signal atypical word combinations?*
-In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and chose appropriate model predictors, and construct appropriate statistical models to answer the research question.
+In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and choose appropriate model predictors, and construct appropriate statistical models to answer the research question.
 This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
-The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing their statistical model.
+The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing the statistical model.
 By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
@@
 These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)`.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, time 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms.]
-
-While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, the phenomenon of incomplete neutralization, a widely studied phenomenon, involves duration effects ranging from 7 to 15 ms [@nicenboim2018using].
+The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)` ms.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, times 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms.]
+
+While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
+for example, the widely studied phenomenon of incomplete neutralization involves duration effects ranging from 7 to 15 ms [@nicenboim2018using].
 This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].
 Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts [@coretta2019], reduction [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
-Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience [e.g., @silberzahn2018many; @breznau2021observing].
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts' biases or experience [e.g., @silberzahn2018many; @breznau2021observing].
 Following @breznau2021observing [p.
-9], we are bound to conclude that "[...] we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions".
+9], we are bound to conclude that "[...] idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions".
 Idiosyncratic variation across researchers might be a fact of life which we have to acknowledge and integrate into how we evaluate and present evidence.
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to very much depend on certain measurement choices. 
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to highly depend on certain measurement choices. 
 Human speech is a complex multidimensional signal.
@@
 Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
-This conclusion is further supported by the fact that between-team variability was lower than between model variability.
+This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
 This is an important observation when put into context of the fact that most teams submitted many different models.
@@
 [...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
-We find that this statement speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
+We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
 Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
@@
 We should ideally specify the link between conceptual construct and quantitative system---the "derivation chain" [@dubin1970theory; @meehl1990summaries]---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
-Without well defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
+Without well-defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
 
@@
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
-It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility [@lebel2018unified]. 
-It allows for alternative analyses to establish analytic robustness [@steegen2016increasing] and strengthens attempts to synthesize evidence via meta-analyses [e.g., @nicenboim2018using]
+Sharing further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility [@lebel2018unified]. 
+It allows for alternative analyses to establish analytic robustness [@steegen2016increasing] and strengthens attempts to synthesize evidence via meta-analyses [e.g., @nicenboim2018using].
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results [@breznau2021observing], we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat; EMU: @winkelmann2017emu; the Montreal Forced Aligner: @mcauliffe2017].
+Within fields that deal with speech data, open source software that permits the extraction of acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process [e.g., Praat: @boersma2021praat; EMU: @winkelmann2017emu; the Montreal Forced Aligner: @mcauliffe2017].
 
@@
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
-in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved, for example, by mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+in the present case how communicative pressures of functions are expressed in the acoustic signal; which can be achieved, for example, by mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
@@
 This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
-Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects [@auspurg2021has].
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects [@auspurg2021has].
 However, we consider this very underspecification of research hypotheses in the field of speech science [and beyond, see @scheel2022most] a common phenomenon.
-For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
+For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
 
@@
 Researchers do not analyze data in a vacuum.
-It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
-
-Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
+It is important to recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
+
+Despite all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
 
 Finally, our study focused on the speech sciences.
-The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+The generalizability of our findings to other disciplines, and to other sub-disciplines of the language sciences specifically, is, of course, limited.
 We focused on quantitative analyses that require the operationalization of a multidimensional signal. 
 While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
+This is an important point to make because cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
-When many different analysts have to analyze the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
-This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to vastly different answers. 
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
 
@@
 Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
-Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research questions lies in the thousands.
+Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research question lies in the thousands.
 Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical values.
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other. 
-That, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
-We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modelling.
+Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other. 
+This result, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
 

### 2022-10-17 RR_manuscript/Draft_RR.Rmd
github typos, suggestions

@@
 Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modeling but also from decisions regarding the quantification of the measured behavior.
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
 In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
@@
 
-Consequently, a good part of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
+Consequently, a substantial body of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
 These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
@@
 Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
-Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
+Importantly, the observed variability was neither predicted by the teams' preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses. 
 The authors' results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
@@
 A classic example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs. *pear*).
-This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and context of surrounding sounds [@lisker1977rapid].
+This contrast is manifested by many acoustic features which can differ depending on several factors, such as the position of the consonant in the word and context of surrounding sounds [@lisker1977rapid].
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 Focused units denote the set of all (contextually relevant) alternatives [e.g. @rooth1992theory].
-Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color does not (e.g. *yellow banana* vs *yellow tomato*), the noun is said to be in focus (Noun Focus condition, NF).
-If the objects are the same but differ in color (e.g. *yellow banana* vs *blue banana*), the color adjective is in focus (Adjective Focus condition, AF).
-If both the color and the object differ (e.g. *yellow banana* vs *blue tomato*), then the whole noun phrase is in focus (Adjective/Noun Focus condition, ANF).
+Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language [@matic2013meanings; @BURDIN2015254].
+For instance, if the competitor and target objects differ but their color does not (e.g. *yellow banana* vs. *yellow tomato*), the noun is said to be in focus (Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g. *yellow banana* vs. *blue banana*), the color adjective is in focus (Adjective Focus condition, AF).
+If both the color and the object differ (e.g. *yellow banana* vs. *blue tomato*), then the whole noun phrase is in focus (Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
-We received initial expression of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).
+We received initial expressions of interest to participate from more than 200 analysts, though there was a substantial drop-out rate (see Section Results).
 
@@
 
-Each analysis was evaluated by four different analysis teams who functioned as peer-reviewers.
+Each analysis was evaluated by four different teams who functioned as peer-reviewers.
 Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
@@
 * 100. A perfect analysis with no conceivable improvements from the reviewer.
-* 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
+* 75. An imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation.
 * 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty.
@@
 f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.
-mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.
+mean of an interval or value at a specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.
 dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
@@
 Furthermore, @aczel2021 suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
+Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs.
+milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (*z*-scores, i.e.
 the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
@@
 **Model specification**. The model was fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model was the standardized effect sizes and related standard deviation.
+The outcome variables of the model were the standardized effect sizes and related standard deviation.
 
@@
 Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
-PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analyst were experienced researchers.
+PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analysts were experienced researchers.
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses. 
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
-`r round(outcome_n[[2,1]],2) * 100 %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used fundamental frequency (f0) as the outcome variable, `r (round(outcome_n[[1,1]],2) * 100)`\% used a measure of duration, `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
+`r (round(outcome_n[[2,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used fundamental frequency (f0) as the outcome variable, `r (round(outcome_n[[1,1]],2) * 100)`\% used a measure of duration, `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
 
@@
   filter(Metric != "n. random smooths") %>% 
-  mutate(Metric = str_remove_all(Metric, "n. "), 
-         Metric = str_to_sentence(Metric)) %>% 
+  mutate(Metric = str_remove_all(Metric, "n. ")) %>% 
   rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
@@
 In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.
-by duration, f0 etc,) or, if they do, they do so by a maximum of `r pm(x = 0.02)` standard units.
+by duration, f0, etc,) or, if they do, they do so by a maximum of `r pm(x = 0.02)` standard units.
 
@@
 Interestingly, the model uniqueness, i.e.
-how unique the choice and combination of predictors is, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
+how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
 This suggests that the analysts' results very much depend on their choice of predictors. 
@@
     linesep = "", 
-    caption = "Estimated 95 per-cent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.",
+    caption = "Estimated 95 percent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.",
     label = "msa-sd-table"
@@
 We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
+Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research question.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
@@
 Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
-Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help produce a consensual estimated effect using meta-analytic techniques.
 This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
@@
 We focused on quantitative analyses that require the operationalization of a multidimensional signal. 
-While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
+While some of our results can be informative for other disciplines that work with speech or audio/video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
 This is an important point to make because cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.

### 2022-10-17 RR_manuscript/Draft_RR.tex

@@
 Even greater flexibility is to be expected in fields in which the primary data lend themselves to a variety of possible operationalizations.
-The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches that derives not only from aspects of statistical modelling but also from decisions regarding the quantification of the measured behavior.
+The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
 In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
@@
 The latter situation has been referred to as the \emph{inference crisis} \citep{rotello2015more, starns2019assessing} and is, among other things, rooted in the inherent flexibility of data analysis \citep[often referred to as researcher degrees of freedom:][]{simmons2011false, gelman2014statistical}.
-Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling the data, to name a few.
+Data analysis involves many different steps, such as inspecting, organizing, transforming, and modeling data, to name a few.
 Along the way, different methodological and analytic choices need to be made, all of which may influence the final interpretation of the data.
@@
 (ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
-This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices''---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.
+This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices''---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than previously observed, thus giving us a more realistic estimate of variability.
 
@@
 
-Consequently, a good part of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
+Consequently, a substantial body of published papers likely present overconfident interpretations of data and statistical results based on idiosyncratic analytic strategies \citep[e.g.,][]{simmons2011false, gelman2014statistical}.
 These interpretations, and the conclusions that derive from them, are thus associated with an unknown degree of uncertainty (dependent on the strength of evidence provided) and with an unknown degree of generalizability (dependent on the chosen analysis).
@@
 Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
-Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
-The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
+Importantly, the observed variability was neither predicted by the teams' preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
+The authors' results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise or bias.
 
@@
 \citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
-Their results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
+Their results suggest that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
-Extending on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
+Building on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
 Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
@@
 For instance, \citet{flake2020} discuss the cascading impact that different practices can have on psychometric research.
-The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
+The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, as well as post-hoc modifications to the chosen measure.
 Taken together, these aspects alone dramatically increase the combinations of possible analytic choices, and hence flexibility in research outcomes.
@@
 The acoustic parameters of units are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other units \citep[e.g.][]{jongman2000acoustic, lisker1986voicing, summerfield1981articulatory, winter2014spoken}.
-A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs.~\emph{pear}).
-This contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds \citep{lisker1977rapid}.
+A classic example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs.~\emph{pear}).
+This contrast is manifested by many acoustic features which can differ depending on several factors, such as the position of the consonant in the word and context of surrounding sounds \citep{lisker1977rapid}.
 Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
@@
 
-In short, when testing hypotheses on speakers' intentions with speech production data, researchers are faced with many choices and possibilities.
+In short, when testing hypotheses on speakers' intentions using speech production data, researchers are faced with many choices and possibilities.
 The larger the functional domain (e.g.~segments vs.~words vs.~utterances), the higher the number of conceivable operationalizations.
@@
 Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
-Once we have decided to compare fundamental frequency of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
+Once we have decided to compare fundamental frequency (f0) of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
 As Figures \ref{fig:forkingPaths}B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
-We could also measure the value or time of the minimum or maximum f0 value.
+We could also measure the value or time of the f0 minimum or maximum.
 We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data in previous work \citep[see][]{gordon2017acoustic}.
@@
 These decisions are intended to be made prior to any statistical analysis, but are at times revised \emph{a posteriori} in light of unforeseen or surprising outcomes (i.e.~after data collection and/or preliminary analyses).
-These myriads of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
+This multitude of possible decisions are multiplied by those researcher degrees of freedom related to statistical analysis \citep[e.g.][]{wicherts2016}.
 
-In sum, speech data is made of complex physical signals that generates an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
+In sum, speech data is made of complex physical signals that generate an as-of-yet unappreciated amount of analytic flexibility in the choice of measures and operationalizations.
 The present paper probes this garden of forking paths in the analysis of speech.
@@
 
-Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
-When trying to refer to a banana, what does a speaker say and how do they say it in a given context.
+Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in Language Science.
+When trying to refer to a banana, what does a speaker say and how do they say it in a given context?
 The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
@@
 Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
-For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there are a yellow and a less ripe green banana available, but not when there is only one banana to begin with.
+For instance, one might use the adjective \emph{yellow} to describe a banana in a situation in which there are both a yellow and a less ripe green banana available, but not when there is only one banana.
 
@@
 Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and make communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
-Recent findings suggest that the utility of a referring expression depends on how good it is for a listener (compared to other referring expressions) to identify a target object.
+Recent findings suggest that the utility of referring expressions depends on how useful they are for a listener (compared to other referring expressions) to identify a target object.
 For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
@@
 
-Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications \citep[e.g.,][]{ladd2008intonational}.
+Even when morphosyntactically identical expressions are involved, speakers can modulate utterances via acoustic properties like temporal and spectral modifications \citep[e.g.,][]{ladd2008intonational}.
 Most prominently, languages can use intonation to signal discourse relationships between referents.
 Intonation marks discourse-relevant referents for being new or given information, to guide the listeners' interpretation of incoming messages.
-Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
+Beyond structuring information relative to the discourse, a few studies suggest that speakers might use intonation to signal atypical lexical combinations \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
 Referential expressions such as \emph{blue banana} were produced with greater prosodic prominence than more typical referents such as \emph{yellow banana}.
@@
 One of the objects served as the target, another as the competitor, and the remaining two objects served as distractors.
-Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{Gelbe Zitrone} `yellow lemon', \emph{Rote Gurke} `red cucumber', \emph{Rote Socken} `red socks').
+Objects were referred to using noun phrases consisting of an adjective modifier denoting color and a modified object (e.g.~\emph{gelbe Zitrone} `yellow lemon', \emph{rote Gurke} `red cucumber', \emph{rote Socken} `red socks').
 
@@
 In the center of the screen, a black cube was displayed, which could be moved by the experimenter.
-The participant would read a sentence prompt out loud (\emph{Du sollst den Würfel auf der COLOR OBJECT ablegen} `You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
+Participant read a sentence prompt out loud (\emph{Du sollst den Würfel auf der COLOR OBJECT ablegen} `You have to put the cube on top of the COLOR OBJECT') to instruct the experimenter to drag the cube on top of one of the four depicted objects (the \emph{competitor}) using the mouse.
 After the experimenter had moved the cube as instructed, the subject would read another sentence prompt (\emph{Und jetzt sollst du den Würfel auf der COLOR OBJECT ablegen} `And now, you have to put the cube on top of the COLOR OBJECT') instructing the experimenter to move the cube on top of a different object (the \emph{target}).
@@
 Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.
-Concretely, a focus contrast marks one of more elements in a sentence as prominent, by different linguistic means depending on the language.
-For instance, if the competitor and target objects differ but their color does not (e.g.~\emph{yellow banana} vs \emph{yellow tomato}), the noun is said to be in focus.
-We call this the Noun Focus condition, or NF for short.
-If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs \emph{blue banana}), the color adjective is in focus (the Adjective Focus condition, AF).
-If both the color and the object differ (e.g.~\emph{yellow banana} vs \emph{blue tomato}), then the whole noun phrase is in focus (the Adjective/Noun Focus condition, ANF).
+Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language \citep{matic2013meanings, BURDIN2015254}.
+For instance, if the competitor and target objects differ but their color does not (e.g.~\emph{yellow banana} vs.~\emph{yellow tomato}), the noun is said to be in focus (Noun Focus condition, NF).
+If the objects are the same but differ in color (e.g.~\emph{yellow banana} vs.~\emph{blue banana}), the color adjective is in focus (Adjective Focus condition, AF).
+If both the color and the object differ (e.g.~\emph{yellow banana} vs.~\emph{blue tomato}), then the whole noun phrase is in focus (Adjective/Noun Focus condition, ANF).
 The NF condition constituted the experimentally relevant condition, while the AF and ANF conditions acted as fillers.
@@
 
-As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
+As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large number of analytic choices when analyzing a multidimensional signal such as speech.
 Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
@@
 All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
-Researchers could choose to work independently or in a small team.
+Researchers could choose to work independently or in small teams.
 For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
@@
 A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
-The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
-We then requested that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
+We then requested that they answer the research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
 To do so, they were given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
-The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
+Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
 These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.
@@
 
-Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
+Each analysis was evaluated by four different teams who functioned as peer-reviewers.
 Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
@@
   \item
-    An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation.
+    An imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation.
   \end{enumerate}
@@
 
-After submitting the review, a methods section from a second analysis was then made available to the reviewer.
+After submitting the review, a methods section from a second analysis was made available to the reviewer.
 This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.\footnote{Initially we planned to present simultaneously all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation.
@@
 
-We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
+We calculated summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g.~f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at a specified point in time), (c) the nature and number of model parameters for both fixed and random effects (if applicable), (d) the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on \emph{p}-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the standardized effect sizes (see the next section for the standardization procedure).
 These summary statistics are reported in \emph{Descriptive statistics} of the Results section.
@@
 We investigated the variability in \textsc{reported effect sizes} using Bayesian meta-analytic techniques.
-As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where the groups are the analysis teams.
+As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where each analysis team represents a group.
 As we detail in Section \emph{Meta-analytic estimation}, we have also run further non-preregistered analyses.
@@
 Furthermore, \citet{aczel2021} suggest that directly asking analysts to report standardized effect sizes could bias the choice of analyses towards types that more straightforwardly return a standardized effect.
-Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration) and that was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
+Since the variables used by the analysis teams might have substantially differed in their measurement scales (e.g, Hertz for frequency vs.~milliseconds for duration) which was indeed the case, we have standardized all reported effects by refitting each \textsc{reported model} with centered and scaled continuous variables (\emph{z}-scores, i.e.~the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
 Each \textsc{standardized model} was fitted as a Bayesian regression model with Stan \citep{stan2021}, RStan \citep{stan2020a}, and brms \citep{burkner2017} in R \citep{R-base}.
@@
 We used regularizing weakly-informative priors for the intercept \(\alpha\) (\(Normal(0, 1)\)) and for the group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\) (\(HalfCauchy(0, 1)\)).
-We fitted this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
+We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
 The model did not incur any divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
@@
 The SDI is an index typically used in ecology research to compare species composition across sites.
-For our purposes, we treated predictors as species and individual analyses as sites.
+For our purposes, we treated predictors as \emph{species} and individual analyses as \emph{sites}.
 For each pair of analyses \((X, Y)\), the SDI was obtained using the following formula:
@@
 \item
-  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate students {[}numeric{]}.
+  \emph{Research experience} as the elapsed time from receiving the PhD. Negative values will indicate that the person is a student or graduate student {[}numeric{]}.
 \item
@@
 \textbf{Model specification}. The model was fitted as a measurement-error model, with the predictors detailed in the preceding paragraphs.
-The outcome variable of the model was the standardized effect sizes and related standard deviation.
+The outcome variables of the model were the standardized effect sizes and related standard deviation.
 
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of the study containing all the code and data presented here and can be found at \url{https://osf.io/3bmcp/}.
+The research compendium of the study, containing all the code and data presented here, can be found at \url{https://osf.io/3bmcp/}.
 
@@
 Forty-six teams submitted their analyses by the established deadline.
-The analyses from which it was possible to extract an effect size were included in the meta-analysis.
+Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
 Of the submitted analyses, the initiating authors identified 170 from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
@@
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or younger) to 12.4 years, suggesting that, on average, analyst were experienced researchers.
+Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
 The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 
-The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window over which they are taken from and how the measures are transformed.
-Thirty-five percent of the models used a measure of duration as the outcome variable, 36\% used fundamental frequency (f0), 12\% used vowel formants, 14\% intensity, and 3\% other measures.
+The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
+Thirty-six percent of the models used fundamental frequency (f0) as the outcome variable, 35\% used a measure of duration, 12\% used vowel formants, 14\% intensity, and 3\% other measures.
 
@@
 Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
-For example, if we consider those analyses that target fundamental frequency (f0), we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
-The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
+For example, if we consider those analyses that target f0, we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
+The measurement is sometimes taken from the interval of a vowel in the article, the adjective or noun; it is sometimes taken from the word interval of the article, adjective or noun; or it is taken from either the noun phrase interval or the entire sentence.
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-Eight percent of the linear models specified no random effects at all (without pooling their data), so effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+Eight percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
 Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
@@
 When considering both acoustic and statistical analyses, we have found a grand total of 104 different analytic pipelines.
-In other words, each individual submitted analysis was unique.
+In other words, each individual analysis submitted was unique.
 Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
@@
  & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
- & Years after phd & -3.8 -- 12.4 & 4.8 (4.2)\\
+ & Years after PhD & -3.8 -- 12.4 & 4.8 (4.2)\\
  & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
@@
 \hspace{1em}Model & Linear model & 102 & 98.1\\
- & Gam & 1 & 1.0\\
+ & GAM & 1 & 1.0\\
  & Other & 1 & 1.0\\
@@
 The primary aim of this analysis is to assess the degree of between-team variability.
-As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)).
+As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation (\(\sigma_{\alpha_{\text{t}}}\)).
 
@@
 \textbf{Non-preregistered}.
-However, we did not take into account that teams might submit multiple analyses/models in our preregistration which, if unaccounted for, violates the independence assumption.
-To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id}), which allows us to estimate both the between-team variation along with the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before running this model we have also run one with just model ID as the only (non-nested) group-level effect.
-The estimated group-level effect of model ID is identical to that of the nested model, so we will not further discuss it.}
+However, we did not take into account in our preregistration that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption.
+To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
+This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
+The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.}
 
@@
 The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
-Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than variability across individual teams.
-We come back to this important observation later.
+Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
+We return to this important observation later.
 
@@
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
-In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0 etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
 
@@
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
-Estimates ranged between -0.65 to 0.99 standard units.
+Estimates ranged from -0.65 to 0.99 standard units.
 
@@
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
-Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors is, affects the analysts estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
 This suggests that the analysts' results very much depend on their choice of predictors.
@@
 Panels A and B of Figure \ref{fig:plot-meta2} display the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which the outcome was measured, panel B).
-If an acoustic dimension related to f0 was measured, estimates are lower than the meta analytic estimate.
-If on the other hand, vowel formants were measured, estimates are higher than the meta analytic estimate.
-Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta analytic estimate.
+If, on one hand, an acoustic dimension related to f0 was measured, estimates are lower than the meta-analytic estimate.
+If, on the other hand, vowel formants were measured, estimates are higher than the meta-analytic estimate.
+Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta-analytic estimate.
 In other words, depending on the choice of measurement and the measurement window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
@@
 speakers acoustically modify utterances to signal atypical word combinations?}
-In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and chose appropriate model predictors, and construct appropriate statistical models to answer the research question.
+In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and choose appropriate model predictors, and construct appropriate statistical models to answer the research question.
 This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
-The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model.
+The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing the statistical model.
 By multiplying the numbers of acoustic and model specifications, there are in principle 2444 possible unique combinations.
@@
 These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between -0.65 and 0.99 standard units which corresponds to duration values ranging from -21.86 to 50.81.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, time 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
+The reported effect estimates from teams varied between -0.65 and 0.99 standard units, which corresponds to duration values ranging from -21.86 to 50.81 ms.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 ms at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
 
-While this might not immediately strike one as a lot of variation, it crosses several theoretically relevant thresholds for perception and articulation:
-For example, the phenomenon of incomplete neutralization, a widely studied phenomenon, involves duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
+While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
+for example, the widely studied phenomenon of incomplete neutralization involves duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
 This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.
 Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts \citep{coretta2019}, reduction \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
-Expecting random variation between different analysts of 7 to 15 in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+Expecting random variation between different analysts of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-\caption{\label{tab:msa-sd-table}Estimated 95 per-cent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.}
+\caption{\label{tab:msa-sd-table}Estimated 95 percent CrIs of deviation from the meta-analytic effect in acoustic measures, based on the lower and upper limits of the between-model variation.}
 \centering
@@
 
-These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][]{silberzahn2018many, breznau2021observing}.
-Following \citet[p.~9]{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions''.
+These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts' biases or experience \citep[e.g.,][]{silberzahn2018many, breznau2021observing}.
+Following \citet[p.~9]{breznau2021observing}, we are bound to conclude that ``{[}\ldots{]} idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions''.
 Idiosyncratic variation across researchers might be a fact of life which we have to acknowledge and integrate into how we evaluate and present evidence.
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to very much depend on certain measurement choices.
+While properties of the teams did not seem to systematically affect results, teams' estimates seem to highly depend on certain measurement choices.
 Human speech is a complex multidimensional signal.
@@
 {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
-We find that this statement speaks to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to answer one research question.
+We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
+Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research question.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate.
@@
 We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
-Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
+Without well-defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
 
@@
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
-It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
-It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}
+Sharing further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
+It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}.
 Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
-Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citetext{\citealp[e.g., Praat:][]{boersma2021praat}; \citealp[EMU:][]{winkelmann2017emu}; \citealp[the Montreal Forced Aligner:][]{mcauliffe2017}}.
+Within fields that deal with speech data, open source software that permits the extraction of acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citetext{\citealp[e.g., Praat:][]{boersma2021praat}; \citealp[EMU:][]{winkelmann2017emu}; \citealp[the Montreal Forced Aligner:][]{mcauliffe2017}}.
 
 Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
-Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help producing a consensual estimated effect using meta-analytic techniques.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help produce a consensual estimated effect using meta-analytic techniques.
 This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
@@
 Multiverse analyses are limited even further by the one group of researchers who define possible analytic pathways.
-Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
-This can be achieved, for example, by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal; which can be achieved, for example, by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
-Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects \citep{auspurg2021has}.
 However, we consider this very underspecification of research hypotheses in the field of speech science \citep[and beyond, see][]{scheel2022most} a common phenomenon.
-For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
+For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
 
@@
 Researchers do not analyze data in a vacuum.
-It is important recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
+It is important to recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
 
-Despite of all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
+Despite all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
 
 Finally, our study focused on the speech sciences.
-The generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
+The generalizability of our findings to other disciplines, and to other sub-disciplines of the language sciences specifically, is, of course, limited.
 We focused on quantitative analyses that require the operationalization of a multidimensional signal.
-While some of our results can be informative for other disciplines that work with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because the cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
+While some of our results can be informative for other disciplines that work with speech or audio/video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
+This is an important point to make because cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
-When many different analysts have to analyze the same data set to answer the same research questions, analysts drastically differ in how they approach this task, leading to vastly different answers to that research question.
-This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken the strength of confidence in the published literature.
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to vastly different answers.
+This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
 
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on team's estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other.
-That, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that the vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
-We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modelling.
+Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other.
+This result, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
 

### 2022-10-17 scripts/r/08_draft_comments.Rmd

---
title: "Get co-author comments on draft"
author: "Joseph V. Casillas"
output: html_document
date: "Last upate: `r Sys.Date()`"
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = TRUE, 
  message = FALSE, 
  warning = FALSE
  )

knitr::opts_knit$set(root.dir = here::here())
```

```{r}
#| label: load-libs
library("googledrive")
library("xml2")
library("dplyr")
library("tidyr")
library("ggplot2")
library("forcats")
library("readr")
library("kableExtra")
```

```{r}
#| label: identify-download
# give gargle permission
drive_auth(email = TRUE)

# Locate file, check ID
drive_find(n_max = 5, type = "document")

# Search by id (just checking)
drive_get(id = "1CFgRo93mRgifpuFOuQE3vNBeMW-H7ps9eD--vxH-6CQ")

# Download to doc folder
drive_download(
  file = "Draft_RR", 
  path = "./RR_manuscript/commented_draft/Draft_RR.docx", 
  type = "docx",
  overwrite = T
  )
```

```{r}
#| label: unzip-word
# Get word doc and unzip to 'unzipped' folder, will create if doesn't exist
system("unzip -o ./RR_manuscript/commented_draft/Draft_RR.docx -d ./RR_manuscript/commented_draft/unzipped/")
```

```{r}
#| label: get-xml
# Load xml file
comments_xml <- read_xml("./RR_manuscript/commented_draft/unzipped/word/comments.xml")

# Explore structure
xml_name(comments_xml)
xml_children(comments_xml) %>% head
# xml_structure(comments_xml) 
# Key structure is: <comment [author, id, date]>

# Get all comments
comments <- xml_find_all(comments_xml, ".//w:comment")
```

```{r}
#| label: create-df
# Create df
comments_df <- tibble(
  commenter = trimws(xml_attr(comments, "author")), 
  date = trimws(xml_attr(comments, "date")), 
  comment = trimws(xml_text(comments)), 
  type = "", 
  assigned = "", 
  solution = "", 
  done = "", 
  notes = ""
  ) %>% 
  arrange(commenter, date) %>% 
  write_csv("./data/rr_comments/comment_log.csv")
```

```{r}
#| label: comment-descriptives

# N commenters
comments_df$commenter %>% unique() %>% length

# N comments
nrow(comments_df)

# N comments per commenter
comments_df %>% 
  count(commenter) %>% 
  mutate(commenter = fct_reorder(commenter, n, min)) %>% 
  ggplot() + 
  aes(x = n, y = commenter) + 
  geom_segment(aes(x = 0, xend = n, yend = commenter)) + 
  geom_point() 
```

```{r}
#| label: print-df
comments_df %>% 
  kbl() %>%
  kable_paper("hover", full_width = F) %>% 
  scroll_box(height = "500px")
```

```{r}
#| label: upload-to-drive
#| eval: false
drive_upload(
  media = "./data/rr_comments/comment_log.csv", 
  path = "many_analyses_docs/rr_submission", 
  name = "comment_log", 
  type = "spreadsheet", 
  overwrite = TRUE
)
```

### 2022-10-18 RR_manuscript/Draft_RR.Rmd
first round of responses to teams by TR

@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
+In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question.
 Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects."
@@
 
-### Characteristics of analytic teams
+### Characteristics of analysis teams
 
@@
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses.
-Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
-We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
-Table \@ref(tab:descriptives-table) provides a summary of the acoustic analyses.
 
@@
 
-The models included a mean of `r round(predictor_n$mean_predictor)` different predictors (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least one additional predictor.
+The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `round(predictor_n$min_predictor,1)`-`round(predictor_n$max_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 typical), `r round(typicality_n[[2,1]],2) * 100`\%  used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while `r round(typicality_n[[3,1]],2) * 100`\% of the models used the median typicality rating.
+Note that the design of the experiment alongside its description indicated that the experiment was designed to categorically operationalize typicality.
+This possibly explains analysts' strong preference.
 
@@
 `r (round(random_n[[1,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent specified random intercepts only, and `r round(random_n[[2,1]],2) * 100`\% specified both random intercepts and random slopes to account for the non-independence.
-On average, teams that specified random effects, included `r round(rterms_n$mean_rterms,1)` random terms in their models. 
-Table \@ref(tab:descriptives-table) provides a summary of the statistical analyses. 
+On average, teams that specified random effects included `r round(rterms_n$mean_rterms,1)` random terms in their models. 
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of `r nrow(unique_model_specs)` different model specifications.
+
 <!-- TR: I am still confused, so if we were to ignore different random effect specifications that the number is x?
@@
 In other words, each individual analysis submitted was unique.
+
+Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation: 
+Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded both qualitatively (i.e.
+whether specific speech production instances were excluded or not) and quantitatively (i.e.
+whether data were trimmed or not).
+
+The question arises whether teams arrived at different conclusions. 
+Yes, they did.
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they themselves specified).
 Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%).
-`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect.
 
@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
+<!-- TODO: repeat exclusion criteria -->
 First, we report on the between-team variability estimate (i.e.
@@
 
-According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units, at 95% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` to `r pm(round((meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]] * 1.96), 2))` (0.3 * 1.96, 0.07 * 1.96) in standard units at 95% probability.
-
-**Non-preregistered**. However, we did not take into account in our preregistration that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
+According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units at 95% credibility.
+In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) with 95% credibility.”
+
+**Non-preregistered**. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
@@
 
+<!-- TR: The meta analytical estimate is basically meaningless, given that the scale is not interpretable and artificial negative and positive estimates cancel each other out.
+I wonder whether we should take this out -->
+
 Figure \@ref(fig:plot-meta1) illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
-Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.
-longer duration, higher f0, etc.), as mentioned above.
-When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed. 
+Given the nature and wide variety of acoustic operationalizations, there is no natural interpretation of the scale, so we cannot interpret the direction of estimates.
+When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed. 
 Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units. 
-
-While the majority of model estimates and their uncertainty after shrinkage (black, orange, and blue points and lines) yields inconclusive results, there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
-
-```{r plot-meta1, echo = FALSE, fig.cap="Standardized effect sizes (raw and after shrinkage).", out.width="100%"}
+We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale [@kamphaus2019clinical].
+The observed variability between teams corresponds to a difference in IQ up to 14.9 IQ points.
+While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.
+are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in blue, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
+
+```{r plot-meta1, echo = FALSE, fig.cap="Standardized effect sizes across all critical coefficients provided by the teams.
+Raw estimates are displayed in grey.
+Estimates after shrinkage as provided by the meta-analytical model are displayed in black/orange.", out.width="100%"}
 knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
@@
 After assessing the variability across teams and models, we now turn to estimating the impact of a series of predictors on the reported standardized effects.
-There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic [@breznau2021observing].
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is purely idiosyncratic [@breznau2021observing].
 
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon `r report_posterior(predictors_bm_rintercepts, "prior_belief_s")`, nor their seniority in terms of years after completing their PhD `r report_posterior(predictors_bm_rintercepts, "years_from_phd_s")` seem to compellingly affect model estimates.
+Neither analysts' prior beliefs in the phenomenon `r report_posterior(predictors_bm_rintercepts, "prior_belief_s")`, nor their seniority in terms of years after completing their PhD `r report_posterior(predictors_bm_rintercepts, "years_from_phd_s")` seem to affect model estimates.
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty `r report_posterior(predictors_bm_rintercepts, "all_rating_s")`.
+
 Interestingly, the model uniqueness, i.e.
 how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates `r report_posterior(predictors_bm_rintercepts, "pop_sdi_s")`.
-This suggests that the analysts' results very much depend on their choice of predictors. 
+
 Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or formants) and the choice of temporal window affected the results. 
@@
 If, on one hand, an acoustic dimension related to f0 was measured, estimates are lower than the meta-analytic estimate.
-If, on the other hand, vowel formants were measured, estimates are higher than the meta-analytic estimate.
+If, on the other hand, duration was measured, estimates are higher than the meta-analytic estimate.
 Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta-analytic estimate.
-In other words, depending on the choice of measurement and the measurement window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
-
-```{r plot-meta2, echo = FALSE, fig.cap="The effects of analytic and researcher-related predictors on the reported standardized effect sizes.", out.width="100%"}
+In other words, depending on the choice of measurement and the measurement window, analysts might have arrived at different conclusions about how and if typicality is expressed acoustically.
+
+It is due of the latter patterns that we need to interpret the results of the model with great caution. 
+Since there are combinations of analytical choices that appear to systematically result in lower or higher estimates and the fact that predictors are not fully crossed (i.e.
+we do not have the same amount of data for all combinations of e.g.
+outcome and temporal window), the estimates for certain predictors might be biased if predictors are collinear.
+This bias might be amplified by the fact that the scale has no natural way of being interpreted across all teams with different measurements cancelling each other out. 
+We checked correlations between predictors and while predictors do not seem to be highly collinear, the estimates might still be biased.
+
+```{r plot-meta2, echo = FALSE, fig.cap="The effects of analytic and researcher-related predictors on the reported standardized effect sizes.
+(A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black point indicates median, and shaded shape represents 50/80/95% highest density interval.
+(C) Mean posterior samples and 80/95% credible intervals for all predictors", out.width="100%"}
 knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
@@
 
-We gave `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` analyst teams the same speech data set to answer the same research question: *Do 
+We gave `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` analyst teams the same speech data set to answer the same research question: *Do 
 speakers acoustically modify utterances to signal atypical word combinations?*
-In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and choose appropriate model predictors, and construct appropriate statistical models to answer the research question.
+In order to answer this question, teams had to interpret the research question by
+operationalizing parameters of a multidimensional signal, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
 This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
@@
 By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
-Note that this is a conservative estimate of the number of different analytical choices for our research question (ignoring further degrees of freedom like e.g.
-acoustic parameter extraction, outlier treatment, and transformations).
-
-To make the results somewhat more concrete, we will ground them in actual acoustic measures.
+Note that this is a conservative estimate of the number of possible analytical choices for our research question, ignoring many other degrees of freedom like e.g.
+acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results [@breznau2021observing].
+
+To gain a better understanding of whether the observed variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
 We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, fundamental frequency and intensity, taken from different time windows. 
-These standard deviations can be considered as an indication of the variability in said acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.
-
-For example, for those analyses that investigated the duration of segments (e.g.
-the duration of the second vowel in *Banana*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.^[Note that these categories necessarily refer to variegated sets of measures.
+E.g.
+the domain word includs words that differed along several dimensions, including their length and their metrical structure.]
+
+For example, for those analyses that investigated the duration of vowels (e.g.
+the duration of the stressed vowel in *Banane*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
 These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
@@
 While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
-for example, the widely studied phenomenon of incomplete neutralization involves duration effects ranging from 7 to 15 ms [@nicenboim2018using].
+for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
 This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].
-Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts [@coretta2019], reduction [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
-Expecting random variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
+Thus, variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-Furthermore, this variation does not seem to be systematic.
-For example, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
+Furthermore, the observed variation does not seem to be systematic.
+For example, variation between teams was not predicted by the analysts' prior expectations about the phenomenon.
 In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
@@
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to highly depend on certain measurement choices. 
+It is important to note that we do not know whether there is an acoustic manifestation of typicality in the first place. 
+Looking at our data, one might argue (and this observation has been made by several teams during the collaborative write-up) that our sample of speech scientists converged on a qualitative conclusion, i.e.
+there is no relationship.
+However, if there truly is no underlying relationship, our results would suggest a concerning false positive rate with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
+This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
+If on the other hand there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`, with the majority of teams not detecting the effect.
+If the latter was true, the fact that the majority of teams converged on a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect.
+Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to the research question.
+
+While properties of the teams did not seem to systematically affect the results, teams' estimates seem to highly depend on certain measurement choices. 
 Human speech is a complex multidimensional signal.
 Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in. 
-Some of these choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another. 
-For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
+Some of these choices seem to result in estimates in one direction while others seem to result in estimates into another. 
+For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to duration tended to yield higher estimates.
 
@@
 
-Second and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Secondly and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
 Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
@@
 
-Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
+Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
 This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
@@
 We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
-Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research question.
+Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
+While this is a valid way to explore data and generate hypotheses, it is not suitable to test hyopotheses.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
-The standard solution to this problem is to apply a correction for family-wise error (i.e., alpha inflation), which consequently reduces power. 
+The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction). 
+However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way.
+They can nevertheless drastically inflate the false positive rate  [@roettger2019researcher].
 Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking; @john2012measuring; @simmons2011false], while null results remain unreported [@sterling1959publication; @rosenthal1979file].
@@
 Without well-defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
-
-In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
+Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise research question by preregistering their planned data analysis pipeline.
+
+In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
@@
 Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
-Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help produce a consensual estimated effect using meta-analytic techniques.
-This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
+Crowd-sourcing analyses is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
 
 Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+Such an analysis can provide insight into how much the conclusions change due analytical choices as well as which choices have the largest impact on the result.
 This approach is called a "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
@@
 Crowd-sourcing is limited by the sampled analysts and their biases.
-Multiverse analyses are limited even further by the one group of researchers who define possible analytic pathways.
+Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.
-in the present case how communicative pressures of functions are expressed in the acoustic signal; which can be achieved, for example, by mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
+Possible tool to strengthen quantitative theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
@@
 Our study has several limitations that need to be considered when evaluating our results.
-The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
-We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
-This might have biased our own judgement during the analysis which itself came with many researcher degrees of freedom.
-We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable. 
-We invite other researchers to re-analyze our data and try to replicate our results using a different research question.
-
-Moreover, our sample is an opportunity sample. 
+
+First, while the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
+Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+
+Second, uncertainty is further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects [@auspurg2021has].
+Beyond possible variation in how the research question is statistically interpreted, the analysts might have tried to answer different specific manifestations of the research question that was given to them (e.g.
+Do speakers modify f0 in atypical adjectives?).
+However, this very underspecification of research hypotheses in the field of speech science [and beyond, see @scheel2022most] is very common.
+For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
+
+Third, our design has artificially inflated the observed variability by encouraging  anti-coordination strategies. 
+Teams knew that there will other analyst teams and therefore might have chosen a "less canonical" analysis.
+Since analysts were guaranteed to become co-authors of a (in principle) guaranteed publication, such an anti-coordination approach was not explicitly disincentivized.
+
+Forth, our sample is an opportunity sample. 
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups. 
-While the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
-Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
-
-This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: *Do speakers acoustically modify utterances to signal atypical word combinations?*
-Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects [@auspurg2021has].
-However, we consider this very underspecification of research hypotheses in the field of speech science [and beyond, see @scheel2022most] a common phenomenon.
-For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
-
-In light of these possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018; @darwin2020; @fox2021open].
+The sampling strategy might also have given access to researchers who where not experienced enough in particular aspects of the acoustic analysis, possibly introducing uncommon analytical choices or poor quality analyses.
+However, to our knowledge, neither the peer review among teams nor the information gathered through our questionnaires indicated any obvious cases of quality outliers.
+
+In light of both the observed large variability between teams, and possible sources of bias, a field can benefit from explicit positionality statements [e.g., @jafar2018; @darwin2020; @fox2021open].
 Researchers do not analyze data in a vacuum. 
 It is important to recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
-
-Despite all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
-
-Finally, our study focused on the speech sciences.
-The generalizability of our findings to other disciplines, and to other sub-disciplines of the language sciences specifically, is, of course, limited.
-We focused on quantitative analyses that require the operationalization of a multidimensional signal. 
-While some of our results can be informative for other disciplines that work with speech or audio/video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
+For example, the coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+They have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
+This might have biased their own judgement during the analysis which itself came with many researcher degrees of freedom.
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of these analytical choices at least detectable and we invite other researchers to re-analyze our data and try to replicate our results using a different research question.
+
+Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
+The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
+We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech). 
+While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
+This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
-When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to vastly different answers. 
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e.
+is there evidence for a relationship or not) and vastly different effect magnitudes.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
@@
 Speech is a multidimensional signal that allows for great flexibility because it lends itself to a variety of possible operationalizations.
-In this study, 30 teams of speech scientists analyzed the same data set.
+In this study, 46 teams of speech scientists analyzed the same data set.
 Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other. 
-This result, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal. 
+This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
 We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.

### 2022-10-19 RR_manuscript/Draft_RR.Rmd
minor edits TR

@@
 In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question.
-Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects."
+Using Bayesian meta-analytic tools, we have observed substantial variability in reported effect sizes and their interpretation.
+We further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses."
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
@@
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
+In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of a linguistically relevant construct and decisions regarding *statistical analysis*.
 Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways [e.g., @tversky1974judgment], see coherent patterns in randomness [@brugger2001], convince themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceive events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
+Humans are biased [e.g., @tversky1974judgment], e.g.
+they see coherent patterns in randomness [@brugger2001], convince themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceive events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
 In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
+In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
 The analytic approaches and, consequently, the results varied widely between teams.
@@
 
-For the present study, 30 analysis teams have received access to the entire data set generated by the production study.
+For the present study, 46 analysis teams have received access to the entire data set generated by the production study.
 The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
@@
 For our purposes, we treated predictors as *species* and individual analyses as *sites*.
-For each pair of analyses $(X, Y)$, the SDI was obtained using the following formula:
+For each pair of analyses $(X, Y)$ (across and within teams), the SDI was obtained using the following formula:
 
@@
 frequency, center of gravity, harmonics difference, etc.), and *other measures* (e.g.
-principal components, vowel dispersion, etc.).
+derived measures such principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.

### 2022-10-19 RR_manuscript/Draft_RR.Rmd
last minor tweaks TR

@@
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalize the phenomenon under investigation.
+In fields working on speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalize the phenomenon under investigation.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
@@
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of a linguistically relevant construct and decisions regarding *statistical analysis*.
-Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the *operationalization* of linguistically relevant constructs and decisions regarding *statistical analysis*.
+Specifically, we discuss the degree of variability in research results obtained by 46 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
-(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
+(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, speech).
 This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices"---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than previously observed, thus giving us a more realistic estimate of variability.
@@
 
-## Crowdsourcing alternative analyses
+## Crowd-sourcing alternative analyses
 
@@
 The analytic approaches and, consequently, the results varied widely between teams.
-Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
+Twenty teams (69%) found support for the hypothesis, and 9 (31%) did not.
 Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
@@
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020, and @botvinik-nezer2020, regarding analytic flexibility in ecology and neuroimaging data, respectively].
-@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
+@bastiaansen2020 crowd-sourced clinical recommendations based on analyses of an individual patient.
 Their results suggest that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
-Building on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
-This is in line with a recent re-analysis of @silberzahn2018many by @auspurg2021has.
-The authors argue that the observed heterogeneity across analysts in @silberzahn2018many might have been driven by flexibility in statistically interpreting the research question.
-
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models.
+Building on the many-analysts approach, @landy2020crowdsourcing asked 15 research teams to independently design studies to answer five different research questions related to moral judgments.
+Again, they found vast heterogeneity across researchers' conclusions.
+The observed variation was not predicted by the researchers' expertise, but seem to vary for the five different research questions which might exhibit different degrees of theoretical underspecification.
+This is in line with @auspurg2021has who re-analyzed the red card study mentioned above.
+The authors argue that some of the observed heterogeneity across analysts in @silberzahn2018many might have been driven by flexibility in statistically interpreting the research question.
+
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to the study design, the statistical analysis or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
 Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking paths related to measurement. 
-However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
+However, in many fields the primary raw data are complex signals, for which theoretical constructs need to be operationalized relative to a theoretically motivated research question.
 This is especially true in the Social Sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
 
-Decisions about how to measure a theoretical construct related to human behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
+Decisions about how to measure theoretical constructs related to human behavior and cognition might interact with downstream decisions about statistical modeling and vice versa.
 For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
@@
 
-Speech is a complex signal that is characterized by structurally different acoustic landmarks distributed throughout different temporal domains.
+Speech signals are complex as they are characterized by structurally different acoustic parameters distributed throughout different temporal domains.
 Thus, choosing how to assess a communicative intention of interest is an important analytic step.
@@
 For example, studies investigating acoustic correlates of word stress (e.g.
-the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
+the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0, closely related to pitch which is uptake) [e.g., @gordon2017acoustic].
 Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
+Differences in position, shape, and alignment of f0 modulations over multiple locations within a sentence are correlated with differences in discourse functions [e.g., @niebuhr2011].
 The latter can also be expressed by global vs. local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, or something else [@stevens2000]?
+Do we measure f0, intensity, or something else [@stevens2000]?
 
@@
 (ref:forkingPaths) Illustration of the analytic flexibility associated with acoustic analyses.
-(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances *I can't bear ANOTHER meeting on Zoom* and *I can't bear another meeting on ZOOM*.
+(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and f0 track of the utterances *I can't bear ANOTHER meeting on Zoom* and *I can't bear another meeting on ZOOM*.
 The green boxes mark the word *another* in both sentences; (C) Spectrogram and f0 track of the word *another*, exemplifying possible operationalizations of differences in f0.
@@
 
-When looking at phrase-level temporal domains, the number of alternative analytic pipelines increases substantially.
+When looking at phrase-level temporal domains, the number of possible alternative analytic pipelines increases substantially.
 Figure \@ref(fig:forkingPaths)A shows a typical example of a decision tree with which speech researchers are often confronted.
@@
 Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
-Once we have decided to compare fundamental frequency (f0) of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
+Once we have decided to compare f0 of the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
 As Figures \@ref(fig:forkingPaths)B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
@@
 Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
-Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @westerbeek2015stored; @rubio2016redundant], which has been argued to facilitate object identification and make communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent [@sedivy2003pragmatic; @rubio2016redundant], which has been argued to facilitate object identification and make communication between speakers and listeners more efficient [@arts2011overspecification; @paraboni2007generating; @rubio2016redundant].
 Recent findings suggest that the utility of referring expressions depends on how useful they are for a listener (compared to other referring expressions) to identify a target object.
@@
 a blue banana) are more likely to be used in an over-informative scenario (e.g.
-when there is just one banana).
+when there is just one banana)[see also @westerbeek2015stored].
 This account, however, has mainly focused on content selection [@gatt2013we], i.e. what words to use.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Focused units denote the set of all (contextually relevant) alternatives [e.g. @rooth1992theory].
+Focused units denote the set of all (contextually relevant) alternatives [e.g., @rooth1992theory].
 Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language [@matic2013meanings; @BURDIN2015254].
@@
 The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
-All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
+All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytic approaches common in the speech sciences (`analytic_approach_quest.pdf`).
 Researchers could choose to work independently or in small teams.
@@
 The SDI is an index typically used in ecology research to compare species composition across sites. 
+It is a distance measure similar to Euclidean distance measures, but is more sensitive to more heterogeneous data sets and deemphesizes outliers.
 For our purposes, we treated predictors as *species* and individual analyses as *sites*.
@@
 \noindent where $|X \cap Y|$ is the number of variables common to both models in the pair, and $|X|+|Y|$ is the sum of the number of variables that occur in each model. 
+For example, if two pairs of models differ in either only one predictor (e.g.
+DV ~ typicality vs.
+DV ~ typicality + trial) or in two predictors (e.g.
+DV ~ typicality vs.
+DV ~ typicality + trial + speech rate), the latter model pair would exhibit a larger SDI than the former.
 In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the `beta.pair()` function in the betapart R package [@baselga2020].
 
-The major measurement dimension of each analysis was categorized according to the following possible groups: *duration*, *intensity*, *fundamental frequency* (f0), *other spectral properties* (e.g.
+The major measurement dimension of each analysis was categorized according to the following possible groups: *duration*, *intensity*, *f0*, *other spectral properties* (e.g.
 frequency, center of gravity, harmonics difference, etc.), and *other measures* (e.g.
@@
 We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
-We realized when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
-There was no team that declared to have made post-hoc changes to the analyses.
+When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
+Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.
 
@@
 The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.
+<!-- TODO: Add link to the collaborative document maybe? -->
 
@@
 We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
-Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability. 
+<!-- and the estimated meta-analytic effect of word combination typicality on speech acoustics.-->
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
-Of the submitted analyses, the initiating authors identified `r nrow(msa_models)` from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis.
+Of the `r n_effects` submitted analyses, the initiating authors identified `r nrow(msa_models)` critical model coefficients from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis.
 In what follows, we describe the characteristics of these teams and analyses. 
@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models (including `r nrow(msa_models)` critical model coefficients) to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
-`r (round(outcome_n[[2,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used fundamental frequency (f0) as the outcome variable, `r (round(outcome_n[[1,1]],2) * 100)`\% used a measure of duration, `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
+`r (round(outcome_n[[2,1]],2) * 100) %>% xfun::numbers_to_words() %>% str_to_sentence()` percent of the models used f0 as the outcome variable, `r (round(outcome_n[[1,1]],2) * 100)`\% used a measure of duration, `r round(outcome_n[[3,1]],2) * 100`\% used vowel formants, `r round(outcome_n[[4,1]],2) * 100`\% intensity, and `r round(outcome_n[[5,1]],2) * 100`\% other measures.
 
@@
 Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation: 
-Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded both qualitatively (i.e.
-whether specific speech production instances were excluded or not) and quantitatively (i.e.
+Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.
+whether specific speech production instances were excluded or not) and quantitative grounds (i.e.
 whether data were trimmed or not).
 
-The question arises whether teams arrived at different conclusions. 
-Yes, they did.
-`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they themselves specified).
+The question arises whether these unique analysis pipelines led to different conclusions. 
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
 Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%). 
+<!-- It looks like this is on the level of critical coefficients = 170, rather than submitted models, double check -->
 
@@
 the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
+<!-- TR: remove reference to meta-analytical estimate -->
 
@@
 **Non-preregistered**. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
+Teams were explicitly instructed to only submit one effect size without enforcing it. 
+As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
@@
 Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units. 
-We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale [@kamphaus2019clinical].
-The observed variability between teams corresponds to a difference in IQ up to 14.9 IQ points.
+We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale [@kamphaus2019clinical] which is defined by a standard deviation of 15.
+The observed variability of estimates between teams corresponds to variability in IQ measures up to 14.9 IQ points.
 While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.
@@
 Raw estimates are displayed in grey.
-Estimates after shrinkage as provided by the meta-analytical model are displayed in black/orange.", out.width="100%"}
+Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.", out.width="100%"}
 knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
@@
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty `r report_posterior(predictors_bm_rintercepts, "all_rating_s")`.
-
 Interestingly, the model uniqueness, i.e.
@@
 
-Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or formants) and the choice of temporal window affected the results. 
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g. f0 or duration) and the choice of measurement window affected the results. 
 Panels A and B of Figure \@ref(fig:plot-meta2) display the posterior estimates for the measurement outcome (i.e.
@@
 It is due of the latter patterns that we need to interpret the results of the model with great caution. 
-Since there are combinations of analytical choices that appear to systematically result in lower or higher estimates and the fact that predictors are not fully crossed (i.e.
+Since there are combinations of analytic choices that appear to systematically result in lower or higher estimates and the fact that predictors are not fully crossed (i.e.
 we do not have the same amount of data for all combinations of e.g.
-outcome and temporal window), the estimates for certain predictors might be biased if predictors are collinear.
+outcome and measurement window), the estimates for certain predictors might be biased if predictors are collinear.
 This bias might be amplified by the fact that the scale has no natural way of being interpreted across all teams with different measurements cancelling each other out. 
@@
 ```{r plot-meta2, echo = FALSE, fig.cap="The effects of analytic and researcher-related predictors on the reported standardized effect sizes.
-(A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black point indicates median, and shaded shape represents 50/80/95% highest density interval.
-(C) Mean posterior samples and 80/95% credible intervals for all predictors", out.width="100%"}
+(A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95% highest density intervals.
+(C) Mean posterior samples (white circles) and 80/95% credible intervals for all predictors", out.width="100%"}
 knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)
@@
 In order to answer this question, teams had to interpret the research question by
-operationalizing parameters of a multidimensional signal, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
-This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytical decisions.
+operationalizing constructs within multidimensional signals, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
+This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytic decisions.
 The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing the statistical model.
 By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
-Note that this is a conservative estimate of the number of possible analytical choices for our research question, ignoring many other degrees of freedom like e.g.
+Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.
 acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results [@breznau2021observing].
 
-To gain a better understanding of whether the observed variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
-We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, fundamental frequency and intensity, taken from different time windows. 
+Different analysis paths led to different categorical conclusions with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
+To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
+We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
 These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.^[Note that these categories necessarily refer to variegated sets of measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to variegated sets of measures.
 E.g.
-the domain word includs words that differed along several dimensions, including their length and their metrical structure.]
+the domain word includes words that differed along several dimensions, including their length and their metrical structure.]
 
@@
 the duration of the stressed vowel in *Banane*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
+These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
 The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)` ms.
@@
 for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
-This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against].
-Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
-Thus, variation between different analysts of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against] and has been replicated several times in both production and perception.
+Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction phenomena [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
+Thus, variation between different analyst teams of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-It is important to note that we do not know whether there is an acoustic manifestation of typicality in the first place. 
-Looking at our data, one might argue (and this observation has been made by several teams during the collaborative write-up) that our sample of speech scientists converged on a qualitative conclusion, i.e.
-there is no relationship.
-However, if there truly is no underlying relationship, our results would suggest a concerning false positive rate with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
-This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
-If on the other hand there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`, with the majority of teams not detecting the effect.
-If the latter was true, the fact that the majority of teams converged on a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect.
-Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to the research question.
-
 While properties of the teams did not seem to systematically affect the results, teams' estimates seem to highly depend on certain measurement choices. 
-Human speech is a complex multidimensional signal.
+Human speech entails complex multidimensional signals.
 Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in. 
 Some of these choices seem to result in estimates in one direction while others seem to result in estimates into another. 
-For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to duration tended to yield higher estimates.
+For example, measurements related to f0 tended to result in lower estimates while measurements related to duration tended to yield higher estimates.
 
@@
 Secondly and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
+Many analysts targeted measures related to f0, likely because similar functional relationships like information structure and predictability can be expressed by f0 [e.g.
 @grice2017integrating; @turnbull2017role].
 Moreover, prior work has actually suggested a relationship between typicality and f0 [e.g. @dimitrova2008prosodic; @dimitrova2009did]. 
-Participating analysts might have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
+Participating analysts could have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
 
@@
 Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
-While this is a valid way to explore data and generate hypotheses, it is not suitable to test hyopotheses.
+While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate. 
@@
 However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way. 
-They can nevertheless drastically inflate the false positive rate  [@roettger2019researcher].
+If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated [@roettger2019researcher]. 
 Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome [@kerr1998harking; @john2012measuring; @simmons2011false], while null results remain unreported [@sterling1959publication; @rosenthal1979file].
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+
+Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.
+there is no evidence for a relationship.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
+This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`, with the majority of teams not detecting the effect.
+If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
+Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.
 
@@
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what @breznau2021observing refer to as "epistemic humility" (p. 10).
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.
 
@@
 Without well-defined derivation chains, we "are not even wrong" [@scheel2022most] because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
-Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise research question by preregistering their planned data analysis pipeline.
+Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise version of the research question by preregistering their planned data analysis pipeline.
 
@@
 
-Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
@@
 Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
-Such an analysis can provide insight into how much the conclusions change due analytical choices as well as which choices have the largest impact on the result.
+Such an analysis can provide insight into how much the conclusions change due to analytic choices as well as which choices have neglible or large impact on the result. 
 This approach is called a "multiverse analysis" [e.g, @steegen2016increasing; @harder2020multiverse] and has recently gained popularity across disciplines.
@@
 in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tool to strengthen quantitative theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
 ## Caveats
-
 Our study has several limitations that need to be considered when evaluating our results.
@@
 Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects [@auspurg2021has].
-Beyond possible variation in how the research question is statistically interpreted, the analysts might have tried to answer different specific manifestations of the research question that was given to them (e.g.
+The analysts might also have tried to answer different specific manifestations of the research question that was given to them, leading to different choices down the line (e.g.
 Do speakers modify f0 in atypical adjectives?).
+It could be argued that some teams would have not specified such a vague research question to begin with which would have reduced the possible degrees of freedom substantially. 
 However, this very underspecification of research hypotheses in the field of speech science [and beyond, see @scheel2022most] is very common.
 For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress [e.g. @gordon2017acoustic].
-
-Third, our design has artificially inflated the observed variability by encouraging  anti-coordination strategies. 
+Research on acoustic markers of clinical conditions such as depression and schizophrenia are often difficult to compare due to the wide variety of different acoustic measures employed [e.g.
+@cummins2015review; @parola2022speech].
+
+Third, the design of this crowd-sourced study has artificially inflated the variability between teams by encouraging anti-coordination strategies. 
 Teams knew that there will other analyst teams and therefore might have chosen a "less canonical" analysis.
@@
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups. 
-The sampling strategy might also have given access to researchers who where not experienced enough in particular aspects of the acoustic analysis, possibly introducing uncommon analytical choices or poor quality analyses.
-However, to our knowledge, neither the peer review among teams nor the information gathered through our questionnaires indicated any obvious cases of quality outliers.
+The sampling strategy also might have given access to researchers who were less experienced in particular aspects of the data analysis, possibly introducing uncommon analytic choices or poor quality analyses.
+However, to our knowledge, neither the peer review among teams nor the information gathered through our questionnaires indicated any obvious cases of what one might consider incompetent analyses.
 
@@
 For example, the coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
-They have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field. 
+They have in the past used the lack of standardized analytic approaches as an argument for proposing behavior and policy changes in the field. 
 This might have biased their own judgement during the analysis which itself came with many researcher degrees of freedom.
-We hope we were able to make these degrees of freedom as well as the timing and reasoning of these analytical choices at least detectable and we invite other researchers to re-analyze our data and try to replicate our results using a different research question.
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of these analytic choices at least detectable and we invite other researchers to re-analyze our data and try to replicate our results using a different research question.
 
@@
 In this study, 46 teams of speech scientists analyzed the same data set.
-Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
-Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research question lies in the thousands.
+Analytic approaches differed vastly in terms of their operationalization of key constructs, as well as their statistical analyses.
+Given the observed variability, conservative estimates of the sheer number of possible analytic paths for this research question lies in the thousands.
 Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical values.
@@
 This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
-We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
+We suggest that fields that use multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
 

### 2022-10-19 RR_manuscript/Draft_RR.Rmd

@@
 
+# found-effect
+found_effect <- msa_models %>% 
+  select(animal, model_n, found_effect) %>% 
+  na.omit() %>% 
+  mutate(effect = if_else(found_effect == "yes", 1, 0))
+
+atleast_1_effect <- found_effect %>% 
+  group_by(animal) %>% 
+  summarize(total = sum(effect)) %>% 
+  filter(total != 0)
+
+# Overall N of analyses claiming an effect
+n_effects <- sum(found_effect$effect)
+# Percent of effects
+perc_effects <- (n_effects / nrow(msa_models) * 100) %>% round(., 2)
+# N of teams claiming an effect
+n_atleast_1 <- nrow(atleast_1_effect)
+# Percent of teams claiming an effect
+perc_atleast_1 <- (n_atleast_1 / length(unique(msa_models$animal))) * 100
+
 #
@@
 
-```{r}
-#| label: found-effect
-
-found_effect <- msa_models %>% 
-  select(animal, model_n, found_effect) %>% 
-  na.omit() %>% 
-  mutate(effect = if_else(found_effect == "yes", 1, 0))
-
-atleast_1_effect <- found_effect %>% 
-  group_by(animal) %>% 
-  summarize(total = sum(effect)) %>% 
-  filter(total != 0)
-
-# Overall N of analyses claiming an effect
-n_effects <- sum(found_effect$effect)
-# Percent of effects
-perc_effects <- (n_effects / nrow(msa_models) * 100) %>% round(., 2)
-# N of teams claiming an effect
-n_atleast_1 <- nrow(atleast_1_effect)
-# Percent of teams claiming an effect
-perc_atleast_1 <- (n_atleast_1 / length(unique(msa_models$animal))) * 100
-```
+<!-- Moved 'found-effect' code to beginning of results section -->
 
@@
 
-```{r plot-meta1, echo = FALSE, fig.cap="Standardized effect sizes across all critical coefficients provided by the teams.
+<!-- FIGURE -->
+(ref:plot-meta1) Standardized effect sizes across all critical coefficients provided by the teams.
 Raw estimates are displayed in grey.
-Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.", out.width="100%"}
+Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.
+
+```{r plot-meta1, echo = FALSE, fig.cap="(ref:plot-meta1)", out.width="100%"}
 knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
@@
 
-```{r plot-meta2, echo = FALSE, fig.cap="The effects of analytic and researcher-related predictors on the reported standardized effect sizes.
+<!-- Figure --> 
+(ref:plot-meta2) The effects of analytic and researcher-related predictors on the reported standardized effect sizes.
 (A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95% highest density intervals.
-(C) Mean posterior samples (white circles) and 80/95% credible intervals for all predictors", out.width="100%"}
+(C) Mean posterior samples (white circles) and 80/95% credible intervals for all predictors.
+
+```{r plot-meta2, echo = FALSE, fig.cap="(ref:plot-meta2)", out.width="100%"}
 knitr::include_graphics(here::here("./figs/alltogether.png"), error = FALSE)

### 2022-10-19 RR_manuscript/Draft_RR.tex

@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production data set to 30 teams of researchers and asked them to answer the same research question.
-Using Bayesian meta-analytic tools, we have observed substantial variability between teams and submitted analyses, with analytic and researcher-related predictors having little or no effect on the reported effects.
+In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question.
+Using Bayesian meta-analytic tools, we have observed substantial variability in reported effect sizes and their interpretation.
+We further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses.
 \end{abstract}
@@
 This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
-In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalize the phenomenon under investigation.
+In fields working on speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it, in other words, how to operationalize the phenomenon under investigation.
 This is not trivial, given the temporal extension of the acoustic signal and its complex structural composition.
 
-In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
-Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
+In this article, we investigate the impact of analytic choices on research results when many analyst teams examine the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of linguistically relevant constructs and decisions regarding \emph{statistical analysis}.
+Specifically, we discuss the degree of variability in research results obtained by 46 teams who had to choose the operationalization and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
 Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
-(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, human speech).
+(ii) our study extends the scope of inquiry to include flexibility in the operationalization of complex human behavior (here, speech).
 This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices''---derived from the many decisions involved in quantification---might reveal a higher degree of variability across analysts than previously observed, thus giving us a more realistic estimate of variability.
@@
 This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
-Humans filter the world in irrational ways \citep[e.g.,][]{tversky1974judgment}, see coherent patterns in randomness \citep{brugger2001}, convince themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceive events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
+Humans are biased \citep[e.g.,][]{tversky1974judgment}, e.g.~they see coherent patterns in randomness \citep{brugger2001}, convince themselves of the validity of prior expectations \citep[``I knew it'',][]{nickerson1998confirmation}, and perceive events as being plausible in hindsight \citep[``I knew it all along'',][]{fischhoff1975hindsight}.
 In conjunction with an academic incentive system that rewards certain discovery processes more than others \citep{sterling1959publication, koole2012rewarding}, we often find ourselves exploring many possible analytic pipelines, but only reporting a selected few.
@@
 
-\hypertarget{crowdsourcing-alternative-analyses}{%
-\subsection{Crowdsourcing alternative analyses}\label{crowdsourcing-alternative-analyses}}
+\hypertarget{crowd-sourcing-alternative-analyses}{%
+\subsection{Crowd-sourcing alternative analyses}\label{crowd-sourcing-alternative-analyses}}
 
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a seminal collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis.
+In a seminal collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
 The analytic approaches and, consequently, the results varied widely between teams.
-Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
+Twenty teams (69\%) found support for the hypothesis, and 9 (31\%) did not.
 Out of the 29 analytic strategies, there were 21 unique combinations of covariates.
@@
 Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams \citep[see also][and \citet{botvinik-nezer2020}, regarding analytic flexibility in ecology and neuroimaging data, respectively]{Parker2020}.
-\citet{bastiaansen2020} crowdsourced clinical recommendations based on analyses of an individual patient.
+\citet{bastiaansen2020} crowd-sourced clinical recommendations based on analyses of an individual patient.
 Their results suggest that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.
 
-Building on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer the same research questions.
-Again, they found vast heterogeneity in researchers' conclusions which was not predicted by the researchers' expertise, but rather seem to be more dependent on the research question itself.
-This is in line with a recent re-analysis of \citet{silberzahn2018many} by \citet{auspurg2021has}.
-The authors argue that the observed heterogeneity across analysts in \citet{silberzahn2018many} might have been driven by flexibility in statistically interpreting the research question.
-
-While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to statistical inference or the architecture of computational models.
+Building on the many-analysts approach, \citet{landy2020crowdsourcing} asked 15 research teams to independently design studies to answer five different research questions related to moral judgments.
+Again, they found vast heterogeneity across researchers' conclusions.
+The observed variation was not predicted by the researchers' expertise, but seem to vary for the five different research questions which might exhibit different degrees of theoretical underspecification.
+This is in line with \citet{auspurg2021has} who re-analyzed the red card study mentioned above.
+The authors argue that some of the observed heterogeneity across analysts in \citet{silberzahn2018many} might have been driven by flexibility in statistically interpreting the research question.
+
+While these studies attested a large degree of analytic flexibility with possibly impactful consequences, they focused on analytic decisions related to the study design, the statistical analysis or the architecture of computational models.
 In these studies the data sets were fixed and neither data collection nor measurement could be changed.
 Thus the estimates of variability found in the literature might reflect a lower bound only, ignoring large parts of the forking paths related to measurement.
-However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
+However, in many fields the primary raw data are complex signals, for which theoretical constructs need to be operationalized relative to a theoretically motivated research question.
 This is especially true in the Social Sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
 
-Decisions about how to measure a theoretical construct related to human behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
+Decisions about how to measure theoretical constructs related to human behavior and cognition might interact with downstream decisions about statistical modeling and vice versa.
 For instance, \citet{flake2020} discuss the cascading impact that different practices can have on psychometric research.
@@
 The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains, as is the case with suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0, closely related to pitch which is uptake) \citep[e.g.,][]{gordon2017acoustic}.
 Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.
-Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
+Differences in position, shape, and alignment of f0 modulations over multiple locations within a sentence are correlated with differences in discourse functions \citep[e.g.,][]{niebuhr2011}.
 The latter can also be expressed by global vs.~local pitch modulations \citep{heuven2002}, as well as acoustic information within the temporal or spectral domain \citep[e.g.,][]{van2005speech}.
@@
 Do we average across the chosen time domain or do we measure a specific point in time?
-Do we measure fundamental frequency, intensity, or something else \citep{stevens2000}?
+Do we measure f0, intensity, or something else \citep{stevens2000}?
 
@@
 \includegraphics[width=1\linewidth]{../figs/ForkingPaths} \caption{Illustration of the analytic flexibility associated with acoustic analyses.
-(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and fundamental frequency (f0) track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
+(A) An example of multiple possible and justifiable decisions when comparing two utterances; (B) Waveform and f0 track of the utterances \emph{I can't bear ANOTHER meeting on Zoom} and \emph{I can't bear another meeting on ZOOM}.
 The green boxes mark the word \emph{another} in both sentences; (C) Spectrogram and f0 track of the word \emph{another}, exemplifying possible operationalizations of differences in f0.}\label{fig:forkingPaths}
@@
 
-When looking at phrase-level temporal domains, the number of alternative analytic pipelines increases substantially.
+When looking at phrase-level temporal domains, the number of possible alternative analytic pipelines increases substantially.
 Figure \ref{fig:forkingPaths}A shows a typical example of a decision tree with which speech researchers are often confronted.
@@
 Here only one particular path has been taken. A different one would likely produce different results and might lead to different conclusions.
-Once we have decided to compare fundamental frequency (f0) of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
+Once we have decided to compare f0 of the word \emph{another} across the two utterances, there are still many choices to be made, all of which need to be justified.
 As Figures \ref{fig:forkingPaths}B-C illustrate, we could measure f0 at specific points in time like the onset of the temporal window, the offset, or the midpoint.
@@
 Despite the coherent idea that speakers are both rational and efficient, there is much evidence that speakers are often over-informative.
-Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, westerbeek2015stored, rubio2016redundant}, which has been argued to facilitate object identification and make communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
+Speakers use referring expressions that are more specific than strictly necessary for the unambiguous identification of the intended referent \citep{sedivy2003pragmatic, rubio2016redundant}, which has been argued to facilitate object identification and make communication between speakers and listeners more efficient \citep{arts2011overspecification, paraboni2007generating, rubio2016redundant}.
 Recent findings suggest that the utility of referring expressions depends on how useful they are for a listener (compared to other referring expressions) to identify a target object.
-For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana).
+For example, \citet{degen2020redundancy} showed that modifiers that are less typical for a given referent (e.g.~a blue banana) are more likely to be used in an over-informative scenario (e.g.~when there is just one banana)\citep[see also][]{westerbeek2015stored}.
 This account, however, has mainly focused on content selection \citep{gatt2013we}, i.e.~what words to use.
@@
 The two sentence prompts were used to create a focus contrast between the competitor and the target object.
-Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.][]{rooth1992theory}.
+Focused units denote the set of all (contextually relevant) alternatives \citep[e.g.,][]{rooth1992theory}.
 Concretely, a focus contrast marks one or more elements in a sentence as prominent, by different linguistic means depending on the language \citep{matic2013meanings, BURDIN2015254}.
@@
 The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
-All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
+All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytic approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
 Researchers could choose to work independently or in small teams.
@@
 The SDI is an index typically used in ecology research to compare species composition across sites.
+It is a distance measure similar to Euclidean distance measures, but is more sensitive to more heterogeneous data sets and deemphesizes outliers.
 For our purposes, we treated predictors as \emph{species} and individual analyses as \emph{sites}.
-For each pair of analyses \((X, Y)\), the SDI was obtained using the following formula:
+For each pair of analyses \((X, Y)\) (across and within teams), the SDI was obtained using the following formula:
 
@@
 \noindent where \(|X \cap Y|\) is the number of variables common to both models in the pair, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.
+For example, if two pairs of models differ in either only one predictor (e.g.~DV \textasciitilde{} typicality vs.~DV \textasciitilde{} typicality + trial) or in two predictors (e.g.~DV \textasciitilde{} typicality vs.~DV \textasciitilde{} typicality + trial + speech rate), the latter model pair would exhibit a larger SDI than the former.
 In order to generate a unique SDI for each analysis team, we calculated the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package \citep{baselga2020}.
 
-The major measurement dimension of each analysis was categorized according to the following possible groups: \emph{duration}, \emph{intensity}, \emph{fundamental frequency} (f0), \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~principal components, vowel dispersion, etc.).
+The major measurement dimension of each analysis was categorized according to the following possible groups: \emph{duration}, \emph{intensity}, \emph{f0}, \emph{other spectral properties} (e.g.~frequency, center of gravity, harmonics difference, etc.), and \emph{other measures} (e.g.~derived measures such principal components, vowel dispersion, etc.).
 The temporal window that the measurement is taken over is defined by the target linguistic unit.
@@
 We had initially planned to also include a measure of conservativeness of the model specification, as the number of random/group-level effects included and the number of post-hoc changes to the acoustic measurements the teams reported to have carried out.
-We realized when fitting the model that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
-There was no team that declared to have made post-hoc changes to the analyses.
+When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
+Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.
 
@@
 We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
-Second, we report the results of the meta-analytic model, focusing on between-team variability and the estimated meta-analytic effect of word combination typicality on speech acoustics.
+Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability.
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
@@
 
-\hypertarget{characteristics-of-analytic-teams}{%
-\subsubsection{Characteristics of analytic teams}\label{characteristics-of-analytic-teams}}
+\hypertarget{characteristics-of-analysis-teams}{%
+\subsubsection{Characteristics of analysis teams}\label{characteristics-of-analysis-teams}}
 
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the submitted analyses, the initiating authors identified 170 from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
+Of the 37 submitted analyses, the initiating authors identified 170 critical model coefficients from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
 In what follows, we describe the characteristics of these teams and analyses.
@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients) to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
-Crucially, the analytic approaches employed by the teams varied widely both in the acoustical analyses of the speech signal and in the statistical analyses of the obtained measures.
-We proceed to discuss these in the following sections, after which we provide an overview of the peer-review ratings.
 
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
-Thirty-six percent of the models used fundamental frequency (f0) as the outcome variable, 35\% used a measure of duration, 12\% used vowel formants, 14\% intensity, and 3\% other measures.
+Thirty-six percent of the models used f0 as the outcome variable, 35\% used a measure of duration, 12\% used vowel formants, 14\% intensity, and 3\% other measures.
 
@@
 Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.
-Table \ref{tab:descriptives-table} provides a summary of the acoustic analyses.
 
@@
 
-The models included a mean of 2 different predictors (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), there was on average at least one additional predictor.
+The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = \texttt{round(predictor\_n\$min\_predictor,1)}-\texttt{round(predictor\_n\$max\_predictor,1)}).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 Among the possible operationalizations, 72\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 24\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
+Note that the design of the experiment alongside its description indicated that the experiment was designed to categorically operationalize typicality.
+This possibly explains analysts' strong preference.
 
@@
 Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
-On average, teams that specified random effects, included 2.5 random terms in their models.
-Table \ref{tab:descriptives-table} provides a summary of the statistical analyses.
+On average, teams that specified random effects included 2.5 random terms in their models.
 Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
@@
 In other words, each individual analysis submitted was unique.
+
+Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation:
+Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.~whether specific speech production instances were excluded or not) and quantitative grounds (i.e.~whether data were trimmed or not).
+
+The question arises whether these unique analysis pipelines led to different conclusions.
+Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
 Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
-Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect.
 
@@
 
-According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units, at 95\% credibility.
-This means that the mean deviations of any individual team from the meta-analytic effect estimate range between \(\pm 0.06\) to \(\pm 0.14\) (0.3 * 1.96, 0.07 * 1.96) in standard units at 95\% probability.
+According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
+In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.06\) (0.07 * 1.96) with 95\% credibility.''
 
 \textbf{Non-preregistered}.
-However, we did not take into account in our preregistration that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption.
+However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption.
+Teams were explicitly instructed to only submit one effect size without enforcing it.
+As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
@@
 Figure \ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
-Given the nature and wide variety of acoustic operationalizations, there is not always a natural interpretation of the scale, but in most cases a positive effect corresponds to typical word combinations eliciting higher acoustic values (e.g.~longer duration, higher f0, etc.), as mentioned above.
-When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much teams' estimates differed.
+Given the nature and wide variety of acoustic operationalizations, there is no natural interpretation of the scale, so we cannot interpret the direction of estimates.
+When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed.
 Estimates ranged from -0.65 to 0.99 standard units.
-
-While the majority of model estimates and their uncertainty after shrinkage (black, orange, and blue points and lines) yields inconclusive results, there are 27 model estimates for which the 95\% credible interval does not contain zero (16\%).
+We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale \citep{kamphaus2019clinical} which is defined by a standard deviation of 15.
+The observed variability of estimates between teams corresponds to variability in IQ measures up to 14.9 IQ points.
+While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 16\%).
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{Standardized effect sizes (raw and after shrinkage).}\label{fig:plot-meta1}
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{Standardized effect sizes across all critical coefficients provided by the teams.
+Raw estimates are displayed in grey.
+Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.}\label{fig:plot-meta1}
 \end{figure}
@@
 After assessing the variability across teams and models, we now turn to estimating the impact of a series of predictors on the reported standardized effects.
-There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is idiosyncratic \citep{breznau2021observing}.
+There is a large amount of variation between and within teams, raising the question as to whether we can explain some of this variation or whether it is purely idiosyncratic \citep{breznau2021observing}.
 
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to compellingly affect model estimates.
+Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to affect model estimates.
 Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
 Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
-This suggests that the analysts' results very much depend on their choice of predictors.
-Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~f0 or formants) and the choice of temporal window affected the results.
+
+Looking at the most important choices during measurement, both the acoustic parameter under investigation (e.g.~f0 or duration) and the choice of measurement window affected the results.
 Panels A and B of Figure \ref{fig:plot-meta2} display the posterior estimates for the measurement outcome (i.e.~what acoustic dimension was measured, panel A) and measurement window (i.e.~what is the unit over which the outcome was measured, panel B).
 If, on one hand, an acoustic dimension related to f0 was measured, estimates are lower than the meta-analytic estimate.
-If, on the other hand, vowel formants were measured, estimates are higher than the meta-analytic estimate.
+If, on the other hand, duration was measured, estimates are higher than the meta-analytic estimate.
 Similarly, if acoustic parameters were measured across the entire sentence, estimates are lower than the meta-analytic estimate.
-In other words, depending on the choice of measurement and the measurement window, analysts arrived at opposite conclusions about how and if typicality is expressed acoustically.
+In other words, depending on the choice of measurement and the measurement window, analysts might have arrived at different conclusions about how and if typicality is expressed acoustically.
+
+It is due of the latter patterns that we need to interpret the results of the model with great caution.
+Since there are combinations of analytic choices that appear to systematically result in lower or higher estimates and the fact that predictors are not fully crossed (i.e.~we do not have the same amount of data for all combinations of e.g.~outcome and measurement window), the estimates for certain predictors might be biased if predictors are collinear.
+This bias might be amplified by the fact that the scale has no natural way of being interpreted across all teams with different measurements cancelling each other out.
+We checked correlations between predictors and while predictors do not seem to be highly collinear, the estimates might still be biased.
 
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{The effects of analytic and researcher-related predictors on the reported standardized effect sizes.}\label{fig:plot-meta2}
+\includegraphics[width=1\linewidth]{../figs/alltogether} \caption{The effects of analytic and researcher-related predictors on the reported standardized effect sizes.
+(A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95\% highest density intervals.
+(C) Mean posterior samples (white circles) and 80/95\% credible intervals for all predictors.}\label{fig:plot-meta2}
 \end{figure}
@@
 
-We gave 30 analyst teams the same speech data set to answer the same research question: \emph{Do
+We gave 46 analyst teams the same speech data set to answer the same research question: \emph{Do
 speakers acoustically modify utterances to signal atypical word combinations?}
-In order to answer this question, teams had to operationalize parameters of a multidimensional signal, operationalize and choose appropriate model predictors, and construct appropriate statistical models to answer the research question.
-This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
+In order to answer this question, teams had to interpret the research question by
+operationalizing constructs within multidimensional signals, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
+This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytic decisions.
 The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing the statistical model.
 By multiplying the numbers of acoustic and model specifications, there are in principle 2444 possible unique combinations.
-Note that this is a conservative estimate of the number of different analytical choices for our research question (ignoring further degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations).
-
-To make the results somewhat more concrete, we will ground them in actual acoustic measures.
-We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, fundamental frequency and intensity, taken from different time windows.
-These standard deviations can be considered as an indication of the variability in said acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, fundamental frequency and intensity.
-
-For example, for those analyses that investigated the duration of segments (e.g.~the duration of the second vowel in \emph{Banana}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytical estimates into milliseconds by multiplying those values with the standard units.
+Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results \citep{breznau2021observing}.
+
+Different analysis paths led to different categorical conclusions with 30\% of teams reported to have found at least one statistically reliable effect.
+To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
+We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows.
+These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.\footnote{Note that these categories necessarily refer to variegated sets of measures.
+E.g.
+the domain word includes words that differed along several dimensions, including their length and their metrical structure.}
+
+For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banane}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
 The reported effect estimates from teams varied between -0.65 and 0.99 standard units, which corresponds to duration values ranging from -21.86 to 50.81 ms.
@@
 While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
-for example, the widely studied phenomenon of incomplete neutralization involves duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
-This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against}.
-Vowel duration differences within this range have been reported across phenomena, associated with segmental contrasts \citep{coretta2019}, reduction \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
-Expecting random variation between different analysts of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against} and has been replicated several times in both production and perception.
+Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts \citep{coretta2019}, reduction phenomena \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
+Thus, variation between different analyst teams of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 
-While properties of the teams did not seem to systematically affect results, teams' estimates seem to highly depend on certain measurement choices.
-Human speech is a complex multidimensional signal.
+While properties of the teams did not seem to systematically affect the results, teams' estimates seem to highly depend on certain measurement choices.
+Human speech entails complex multidimensional signals.
 Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in.
-Some of these choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
-For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
+Some of these choices seem to result in estimates in one direction while others seem to result in estimates into another.
+For example, measurements related to f0 tended to result in lower estimates while measurements related to duration tended to yield higher estimates.
 
@@
 
-Second and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
-Many analysts targeted measures related to fundamental frequency (f0), likely because similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
+Secondly and orthogonal to a possible true relationship, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger researcher biases.
+Many analysts targeted measures related to f0, likely because similar functional relationships like information structure and predictability can be expressed by f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
 Moreover, prior work has actually suggested a relationship between typicality and f0 \citep[e.g.][]{dimitrova2008prosodic, dimitrova2009did}.
-Participating analysts might have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
-
-Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.
+Participating analysts could have been aware of those findings, which might have, subconsciously or otherwise, nudged their choices into one particular direction.
+
+Regardless of the cause of these systematic effects, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant prediction.
 This conclusion is further supported by the fact that between-team variability was lower than between-model variability.
@@
 We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
-Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research question.
+Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
+While this is a valid way to explore data and generate new hypotheses, it is not suitable for hypothesis testing.
 When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables is known to increase the false-positive (Type-I error) rate.
-The standard solution to this problem is to apply a correction for family-wise error (i.e., alpha inflation), which consequently reduces power.
+The well-established solution to this problem is to apply a correction for family-wise error (i.e., alpha correction).
+However, less clear-cut degrees of freedom such as observed in the present study can not be corrected for in a straightforward way.
+If uncorrected for, these degrees of freedom can nevertheless drastically inflate the false positive rate, even if different choices are highly correlated \citep{roettger2019researcher}.
 Another possible outcome of analytic flexibility as seen in this study is selective reporting of those tests that yield a desirable outcome \citep{kerr1998harking, john2012measuring, simmons2011false}, while null results remain unreported \citep{sterling1959publication, rosenthal1979file}.
 Fields such as the speech sciences that make theoretical advances based on multidimensional data should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.
+
+Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 30\% of teams reported to have found at least one statistically reliable effect.
+This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -29, with the majority of teams not detecting the effect.
+If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
+Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.
 
@@
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what \citet{breznau2021observing} refer to as ``epistemic humility'' (p.~10).
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.
 
@@
 Without well-defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.
-
-In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
+Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise version of the research question by preregistering their planned data analysis pipeline.
+
+In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
@@
 
-Second, making analytic pathways completely re-traceable does not change the fact that analysts apply idiosyncratic analytic approaches.
-Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and help produce a consensual estimated effect using meta-analytic techniques.
-This is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
+Crowd-sourcing analyses is obviously not always feasible in terms of required resources and time, but could be a consideration for claims that have large epistemological or practical consequences.
 
 Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+Such an analysis can provide insight into how much the conclusions change due to analytic choices as well as which choices have neglible or large impact on the result.
 This approach is called a ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
@@
 Crowd-sourcing is limited by the sampled analysts and their biases.
-Multiverse analyses are limited even further by the one group of researchers who define possible analytic pathways.
-Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal; which can be achieved, for example, by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Multiverse analyses are limited even further by the group of researchers who define possible analytic pathways.
+Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
+Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 Our study has several limitations that need to be considered when evaluating our results.
-The coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
-We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
-This might have biased our own judgement during the analysis which itself came with many researcher degrees of freedom.
-We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
-We invite other researchers to re-analyze our data and try to replicate our results using a different research question.
-
-Moreover, our sample is an opportunity sample.
+
+First, while the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
+Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
+
+Second, uncertainty is further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
+Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects \citep{auspurg2021has}.
+The analysts might also have tried to answer different specific manifestations of the research question that was given to them, leading to different choices down the line (e.g.~Do speakers modify f0 in atypical adjectives?).
+It could be argued that some teams would have not specified such a vague research question to begin with which would have reduced the possible degrees of freedom substantially.
+However, this very underspecification of research hypotheses in the field of speech science \citep[and beyond, see][]{scheel2022most} is very common.
+For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
+Research on acoustic markers of clinical conditions such as depression and schizophrenia are often difficult to compare due to the wide variety of different acoustic measures employed \citep[e.g.][]{cummins2015review, parola2022speech}.
+
+Third, the design of this crowd-sourced study has artificially inflated the variability between teams by encouraging anti-coordination strategies.
+Teams knew that there will other analyst teams and therefore might have chosen a ``less canonical'' analysis.
+Since analysts were guaranteed to become co-authors of a (in principle) guaranteed publication, such an anti-coordination approach was not explicitly disincentivized.
+
+Forth, our sample is an opportunity sample.
 We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
-While the total number of analyses is larger than most earlier crowd-sourcing projects, it is likely to be too small to reliably estimate the impact of certain predictors.
-Since predictors' values were not systematically distributed across teams, our estimates are characterized by large uncertainty.
-
-This uncertainty is possibly further inflated by the fact that the research question presented to the teams was vague, despite being of a kind normally found in the speech science literature: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
-Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analyses projects \citep{auspurg2021has}.
-However, we consider this very underspecification of research hypotheses in the field of speech science \citep[and beyond, see][]{scheel2022most} a common phenomenon.
-For example, researchers seem to have not yet agreed on how to acoustically measure cross-linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
-
-In light of these possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{jafar2018, darwin2020, fox2021open}.
+The sampling strategy also might have given access to researchers who were less experienced in particular aspects of the data analysis, possibly introducing uncommon analytic choices or poor quality analyses.
+However, to our knowledge, neither the peer review among teams nor the information gathered through our questionnaires indicated any obvious cases of what one might consider incompetent analyses.
+
+In light of both the observed large variability between teams, and possible sources of bias, a field can benefit from explicit positionality statements \citep[e.g.,][]{jafar2018, darwin2020, fox2021open}.
 Researchers do not analyze data in a vacuum.
 It is important to recognize and disclose one's positionality, i.e., a reflection about how educational background, social identity, power, experience and context might influence researchers' approaches and interpretations.
-
-Despite all these possible sources of bias and uncertainty, our study suggests that at least the minimum variability that we can expect to find across researchers is the rather concerning variability that we have observed.
-
-Finally, our study focused on the speech sciences.
-The generalizability of our findings to other disciplines, and to other sub-disciplines of the language sciences specifically, is, of course, limited.
-We focused on quantitative analyses that require the operationalization of a multidimensional signal.
-While some of our results can be informative for other disciplines that work with speech or audio/video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
-This is an important point to make because cognitive sciences, in general, and the language sciences, in particular, have many research areas that are based on qualitative methods.
+For example, the coordinating authors have engaged with meta-scientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
+They have in the past used the lack of standardized analytic approaches as an argument for proposing behavior and policy changes in the field.
+This might have biased their own judgement during the analysis which itself came with many researcher degrees of freedom.
+We hope we were able to make these degrees of freedom as well as the timing and reasoning of these analytic choices at least detectable and we invite other researchers to re-analyze our data and try to replicate our results using a different research question.
+
+Finally, the present study focused on a particular phenomenon within the speech sciences using a speech production data set with very specific properties.
+The generalizability of our findings to other disciplines, as well as to other sub-disciplines of the language sciences specifically, is, of course, limited.
+We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech).
+While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
+This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
-When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to vastly different answers.
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e.~is there evidence for a relationship or not) and vastly different effect magnitudes.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
@@
 Speech is a multidimensional signal that allows for great flexibility because it lends itself to a variety of possible operationalizations.
-In this study, 30 teams of speech scientists analyzed the same data set.
-Analytic approaches differed vastly in terms of their operationalization of the speech signal, as well as their statistical analyses.
-Given the observed variability, conservative estimates of the sheer number of possible analytical paths for this research question lies in the thousands.
+In this study, 46 teams of speech scientists analyzed the same data set.
+Analytic approaches differed vastly in terms of their operationalization of key constructs, as well as their statistical analyses.
+Given the observed variability, conservative estimates of the sheer number of possible analytic paths for this research question lies in the thousands.
 Quantitatively, the between-team and between-model variation of estimates crosses important theoretical thresholds as to what constitutes communicative, cognitive, or bio-mechanical values.
@@
 In line with previous findings, neither the perceived quality of analyses, nor the experience or prior beliefs of teams explained the observed variation.
-Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal, biasing their estimates in one direction or the other.
-This result, taken together with the meaningful between-model variation and the tendency to test the same research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
-We suggest that fields based on multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
+Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal.
+This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+We suggest that fields that use multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.
 

### 2022-10-21 RR_manuscript/Draft_RR.Rmd
♻️ - small edits to draft

@@
 For example, studies investigating acoustic correlates of word stress (e.g.
-the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0, closely related to pitch which is uptake) [e.g., @gordon2017acoustic].
+the difference between *ínsight* and *incíte*) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
 Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].

### 2022-10-21 RR_manuscript/Draft_RR.tex
♻️ - small edits to draft

@@
 The multiplicity of phonetic measurements grows exponentially if we look at larger temporal domains, as is the case with suprasegmental aspects of speech.
-For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0, closely related to pitch which is uptake) \citep[e.g.,][]{gordon2017acoustic}.
+For example, studies investigating acoustic correlates of word stress (e.g.~the difference between \emph{ínsight} and \emph{incíte}) use a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) \citep[e.g.,][]{gordon2017acoustic}.
 Moving on to the expression of higher-level communicative functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances \citep[e.g.,][]{ladd2008intonational}.

### 2022-10-21 RR_manuscript/Draft_RR.Rmd
♻️ - start working on #239 (WIP)

@@
               n_analysts = sum(n_members), 
-              mean_size = mean(n_members), 
+              median_size = median(n_members), 
               sd_size = sd(n_members), 
@@
   group_by(animal) %>% 
-  summarize(across(years_from_phd:all_rating, mean)) %>% 
+  summarize(across(years_from_phd:all_rating, median)) %>% 
   pivot_longer(cols = -animal, names_to = "metric", values_to = "vals") %>% 
@@
   group_by(metric) %>% 
-  summarize(min = min(vals), max = max(vals), avg = mean(vals, na.rm = T), 
+  summarize(min = min(vals), max = max(vals), Median = median(vals, na.rm = T), 
             sd = sd(vals, na.rm = T)) %>% 
@@
     max = team_desc_df %>% filter(stage == "Final") %>% pull(max), 
-    avg = team_desc_df %>% filter(stage == "Final") %>% pull(mean_size), 
+    Median = team_desc_df %>% filter(stage == "Final") %>% pull(median_size), 
     sd =  team_desc_df %>% filter(stage == "Final") %>% pull(sd_size)) %>% 
@@
   mutate(desc = "team_desc", 
-   `Mean (SD)` = glue::glue("{avg} ({sd})"), 
     Range = glue::glue("{min} -- {max}"), 
@@
     label = glue::glue("{desc}_{metric}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg, sd, Range)
+  select(label, desc, Metric, Min. = min, Max = max, Median, Range)
 
@@
     )) %>% 
-  mutate(across(c("prop", "perc"), specify_decimal, k = 1)) %>% 
+  mutate(across(c("prop", "perc"), specify_decimal, k = 0)) %>% 
   unite(label, c("metric", "val")) %>% 
@@
   pivot_wider(names_from = Metric, values_from = vals) %>% 
-  mutate(across(c("mean", "sd"), specify_decimal, k = 1)) %>% 
+  mutate(across(c("mean", "sd"), specify_decimal, k = 0)) %>% 
   mutate(
@@
     label = glue::glue("{desc}_{item}"), 
-    `Mean (SD)` = glue::glue("{mean} ({sd})"), 
+    Median = glue::glue("{mean}"), 
     Range = glue::glue("{min} -- {max}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg = mean, 
+  select(label, desc, Metric, Min. = min, Max = max, Median, avg = mean, 
          sd, Range) %>% 
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
-Of the `r n_effects` submitted analyses, the initiating authors identified `r nrow(msa_models)` critical model coefficients from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams that were deemed eligible to be included in the meta-analytic synthesis.
-In what follows, we describe the characteristics of these teams and analyses. 
+Of the analysis submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
+Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
+
+In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
 A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.
 
-The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_size", sd)`) individuals per team.
+The included analyses were provided by `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams, comprising `r pull_from_tib(team_desc_df, stage, "Final", n_analysts)` analysts, with a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_size", Median)` individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had on average `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", avg)` years (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", sd)`) of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
+Analysts had a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Median)` years of experience after completing their PhD, ranging from `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Min.)` years, i.e.
 PhD students (or less experienced) to `r pull_from_tib(tbl_team_desc, label, "team_desc_years_from_phd", Max)` years, suggesting that, on average, analysts were experienced researchers.
-The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with an average of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", avg)` (SD = `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", sd)`).
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Min.)` to `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Max)` with a median of `r pull_from_tib(tbl_team_desc, label, "team_desc_prior_belief", Median)`.
 We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models (including `r nrow(msa_models)` critical model coefficients) to answer the research question, with a mean of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", avg)` (SD: `r pull_from_tib(tbl_model_desc, label, "model_desc_models", sd)`) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of `r no_analyses` individual models (including `r nrow(msa_models)` critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of `r pull_from_tib(tbl_model_desc, label, "model_desc_models", Median)` models per team.
 Table \@ref(tab:descriptives-table) provides a summary of the contributing teams and their analyses.
@@
   tbl_team_desc %>% 
-    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`), 
+    select(desc, Metric, val1 = Range, val2 = Median), 
   tbl_categorical_desc %>% 
@@
   tbl_model_desc %>% 
-    select(desc, Metric, val1 = Range, val2 = `Mean (SD)`)
+    select(desc, Metric, val1 = Range, val2 = Median)
 ) %>% 
@@
   rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
-    `\\bf{Mean (SD)}` = val2) %>% 
+    `\\bf{Median}` = val2) %>% 
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
+    `\\bf{Median}` = " ", .before = 7) %>%
   add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 8) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ",  .before = 14) %>%
+    `\\bf{Median}` = " ",  .before = 14) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 20) %>%
+    `\\bf{Median}` = " ", .before = 20) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 24) %>%
+    `\\bf{Median}` = " ", .before = 24) %>%
   add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 25) %>%
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 25) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
-    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
+    `\\bf{Median}` = " ", .before = 28) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 32) %>%
+    `\\bf{Median}` = " ", .before = 32) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
+    `\\bf{Range}` = "\\bf{Range}", `\\bf{Median}` = "\\bf{Median}", 
     .before = 33) %>% 

### 2022-10-21 RR_manuscript/Draft_RR.tex
♻️ - start working on #239 (WIP)

@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the 37 submitted analyses, the initiating authors identified 170 critical model coefficients from 30 teams that were deemed eligible to be included in the meta-analytic synthesis.
-In what follows, we describe the characteristics of these teams and analyses.
+Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
+Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
+
+In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
 A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.
 
-The included analyses were provided by 30 teams, comprising 109 analysts, with an average of 3.6 (SD = 2.8) individuals per team.
+The included analyses were provided by 30 teams, comprising 109 analysts, with a median of 3.0 individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had on average 4.8 years (SD = 4.2) of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
-The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with an average of 69.2 (SD = 11.3).
+Analysts had a median of 5.8 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with a median of 70.0.
 We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients) to answer the research question, with a mean of 3.6 (SD: 3.4) models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 4 models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 \toprule
-\bf{Team characteristics} &    & \bf{Range} & \bf{Mean (SD)}\\
+\bf{Team characteristics} &    & \bf{Range} & \bf{Median}\\
 \midrule
- & Team size & 1.0 -- 12.0 & 3.6 (2.8)\\
- & Years after PhD & -3.8 -- 12.4 & 4.8 (4.2)\\
- & Prior belief & 48.5 -- 92.0 & 69.2 (11.3)\\
- & Acoustic analysis peer rating & 41.2 -- 88.3 & 71.5 (13.9)\\
- & Statistical analysis peer rating & 33.0 -- 93.3 & 69.5 (16.5)\\
- & Overall peer rating & 39.0 -- 88.7 & 70.0 (14.3)\\
+ & Team size & 1.0 -- 12.0 & 3.0\\
+ & Years after PhD & -3.8 -- 12.4 & 5.8\\
+ & Prior belief & 48.5 -- 92.0 & 70.0\\
+ & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
+ & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
+ & Overall peer rating & 39.0 -- 88.7 & 72.2\\
  &  &  \vphantom{5} & \\
@@
 \midrule
-\hspace{1em}Outcome & F0 & 37 & 35.6\\
- & Duration & 36 & 34.6\\
- & Intensity & 15 & 14.4\\
- & Formants & 13 & 12.5\\
- & Other & 3 & 2.9\\
+\hspace{1em}Outcome & F0 & 37 & 36\\
+ & Duration & 36 & 35\\
+ & Intensity & 15 & 14\\
+ & Formants & 13 & 12\\
+ & Other & 3 & 3\\
  &  &  \vphantom{4} & \\
-\hspace{1em}Temporal window & Segment & 47 & 45.6\\
- & Word & 45 & 43.7\\
- & Sentence & 4 & 3.9\\
- & Phrase & 3 & 2.9\\
- & Other & 4 & 3.9\\
+\hspace{1em}Temporal window & Segment & 47 & 46\\
+ & Word & 45 & 44\\
+ & Sentence & 4 & 4\\
+ & Phrase & 3 & 3\\
+ & Other & 4 & 4\\
  &  &  \vphantom{3} & \\
-\hspace{1em}Typicality operationalization & Categorical & 75 & 72.8\\
- & Continuous (mean) & 25 & 24.3\\
- & Continuous (median) & 3 & 2.9\\
+\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
+ & Continuous (mean) & 25 & 24\\
+ & Continuous (median) & 3 & 3\\
  &  &  \vphantom{2} & \\
@@
 \midrule
-\hspace{1em}Framework & Frequentist & 86 & 82.7\\
- & Bayesian & 18 & 17.3\\
+\hspace{1em}Framework & Frequentist & 86 & 83\\
+ & Bayesian & 18 & 17\\
  &  &  \vphantom{1} & \\
-\hspace{1em}Model & Linear model & 102 & 98.1\\
- & GAM & 1 & 1.0\\
- & Other & 1 & 1.0\\
+\hspace{1em}Model & Linear model & 102 & 98\\
+ & GAM & 1 & 1\\
+ & Other & 1 & 1\\
  &  &  & \\
- &  & \bf{Range} & \bf{Mean (SD)}\\
-\hspace{1em}N & Models & 1 -- 16 & 3.6 (3.4)\\
- & Predictors & 1 -- 5 & 2.0 (1.2)\\
- & Random terms & 1 -- 10 & 2.5 (1.3)\\
-\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}1.9 (1.0)\\
-\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0.5 (0.9)\\
+ &  & \bf{Range} & \bf{Median}\\
+\hspace{1em}N & Models & 1 -- 16 & 4\\
+ & Predictors & 1 -- 5 & 2\\
+ & Random terms & 1 -- 10 & 2\\
+\hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}2\\
+\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}1\\
 \bottomrule

### 2022-10-21 scripts/r/04-1_refit_workflow.Rmd
🚚 - rename file

---
title: "Model refitting workflow"
output: html_document
date: "`r Sys.Date()`"
---

This document describes the workflow for refitting the submitted models and extracting relevant
variables in preparation for the meta-analysis of the MSA data.

## Set up (download OSF components)

Each analyst codes a subset of the MSA data. Accordingly, each analyst
downloads only their subset of OSF components with the data from the
teams analyses.

To do so, run the code in `scripts/r/03-analyses-coding.Rmd`.

![](../../figs/03-analysis-coding.png)

When prompted by the code, select your identity. A folder with your
initials will be created in `data/analyses/`. For example:

![](../../figs/data-analyses-sc.png)

The rest of the code will download the OSF components into that
directory. (Total size will be ~1 to 4 GB).

## Workflow

1. Pick one of the downloaded teams components (see [Analyses coding](https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit#gid=0)).
2. Create a **new heading in your refit file** (`scripts/r/04-refit/refit-xx.Rmd` with the name of the team).
3. **Find the relevant analysis script** of the team
    1. **Run original model as is**.
         Flag if not converging in sheet (column `converged_orig`).
    1. Copy the necessary code in your refit file (`scripts/r/04-refit/refit-xx.Rmd`).
    1. Use the model(s) that are referred to and interpreted in the written report, compare with submitted form and indicate if one of the models has been singled out in submitted form. s
    1. If so, this should also be indicated in the sheet. If the team has multiple models and they do not single one out in the submitted form, run the following re-fitting procedure for all models (**note: be sure to follow naming conventions**, see below).
1. Inside your refit file, MSA team member reruns relevant analyses.
    1. **Standardize predictors**:
        1. Standardize all continuous variables (outcome and predictors) to mean = 0, sd = 1.
        1. Code categorical predictors thus:
            1. Typicality
                1. If categorical and two levels: set `atypical` as
                    reference and use dummy coding. Rename predictor to
                    `effect_cat`.
                1. If categorical and three levels: set `atypical` as
                    reference and use dummy coding. Rename predictor to
                    `effect_cat`.
                1. If continuous, standardize and rename predictor to
                    `effect_con`.
            1. Others:
                1. Sum coding.
        1. If analysts used model selection, use the model which
            analyst eventually chose unless final model did not include
            typicality. In that case, chose simplest model with
            typicality and their chosen critical predictors (e.g.
            analysts chose `Y ~ sex`, you rerun `Y ~ sex + effect_cat`).
    1. **Run standardized model**.
        1. Run standardized model with default priors or with original
            priors if original model was Bayesian and standardised.
        1. If model does not converge, flag in sheet (column
            `converged_std`. Non-convergence is operationalized as over
            20% of the posterior containing divergent transitions.
            1. If model has more than 20% of divergent transitions,
                change `adapt_delta` to 0.99, 0.9999, etc.
            2. If model still doesn't converge, add 2000 iterations.
            3. If tree_depth warning, adjust `max_treedepth` to 12, 14, etc.
        1. **Save model as .rds** file to the **models** directory
          (`data/analyses/models`).
            1. The `.rds` object name should include the team name, the
                model number, the outcome variable (use single words,
                without underscores: `int`, `nounint`, `adjint`, `phrasef0`,
                ..., and whether typicality was categorical or
                continuous (`cat`, `con`). Separate information using
                underscores. Here are two examples:
                `haematopus_fossor_9_nounvowelcent_cat`,
                `lasionycteris_altavela_1_int_con`.
            1. Note that the first two words will always be the team
                name, followed by the model number, followed by the
                outcome variable, and, finally, how typicality was
                coded.
        1. Below is an **example** of a fitted model following all the
            above naming conventions (Note: it also uses the
            `file` argument to automatically save the .rds file):

            ```
            lasionycteris_altavela_1_int_con <- brm(
              int_z ~ effect_con + 
                (1 | target_name) +
                (1 | filename) +
                (1 | filename:target_name), 
              data = MSA_df, 
              cores = 4,
              threads = threading(2, grainsize = 100), 
              backend = "cmdstanr", 
              file = here("data", "analyses", "models", "lasionycteris_altavela_1_int_con")
            )
            ```

1. Repeat for all analyses of MSA team member's subset.

2. Run `report.Rmd` file, commit/push to GitHub

### 2022-10-21 scripts/r/04-1_refitted.Rmd
🚚 - rename files

---
title: "04-1 - Refit"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
#library(tidyverse)
library(dplyr)
library(ggplot2)
library(tidyr)
library(readr)
library(ggmosaic)
library(googlesheets4)
library(magrittr)
library(glue)
library(osfr)
library(cli)
library("here")
library("fs")
library("forcats")
library("strex")
library("purrr")
library("broom")
library("broom.mixed")

# Plotting theme
clean_theme <- function(...) {
  list(
    theme_minimal(), 
    theme(
      axis.title.x = element_blank(),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15),
      strip.text.x = element_text(hjust = 0),
      axis.text.x = element_blank()
    )
  )
}
```

# Read coding sheet

```{r coding}
the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"

coding <- read_sheet(the_sheet) %>%
  drop_na(model_n)
```

# Read intake forms

We will join the intake forms with `msa_models`.

```{r intake}
other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"

team_animal_coord <- read_sheet(other_sheet)

msa_intake <- read_csv("./data/questionnaires/msa_intake_form.csv") %>%
  filter(row_number() != 2)
msa_intake_qs <- msa_intake[1,]
msa_intake <- msa_intake[-1,]

msa_intake <- msa_intake %>%
  mutate(
    Q6 = case_when(
      Q6 == "Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
      Q6 == "University of Birmingham team under the team coordinator Zlatomira IIchovska" ~ "Zlatomira Ilchovska",
      Q6 == "Vincent Hughes" ~ "Vince Hughes",
      Q6 == "Tiphaine Cordelier" ~ "Tiphaine Caudrelier",
      Q6 == "Scott Perry" ~ "Scott James Perry",
      Q6 == "Scott James Perru" ~ "Scott James Perry",
      Q6 == "Nicole Rodriquez" ~ "Nicole Rodriguez",
      Q6 == "Michael Gradoville (Arizona State Univ.)" ~ "Michael Gradoville",
      Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
      Q6 == "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)" ~ "Dušan Nikolić",
      Q6 == "Dusan Nikolic" ~ "Dušan Nikolić",
      Q6 == "Dušan Nickolić" ~ "Dušan Nikolić",
      Q6 == "Alicea Megan Brown" ~ "Alicia M Brown",
      Q6 == "Alicia Brown" ~ "Alicia M Brown",
      Q6 == "Ali A-Hoorie" ~ "Ali H. Al-Hoorie",
      Q6 == "Ali Al-Hoorie" ~ "Ali H. Al-Hoorie",
      Q6 == "Dr Rory Turnbull" ~ "Rory Turnbull",
      Q6 == "Dr. Reenu Punnoose" ~ "Reenu Punnoose",
      TRUE ~ Q6
    ),
    Q5 = as.numeric(Q5),
    Q7_1 = as.numeric(Q7_1)
  )

msa_intake_teams <- msa_intake %>%
  group_by(Q6) %>%
  summarise(
    years_from_phd = mean(Q5, na.rm = TRUE),
    years_from_phd_sd = sd(Q5, na.rm = TRUE),
    prior_belief = mean(Q7_1, na.rm = TRUE),
    prior_belief_sd = sd(Q7_1, na.rm = TRUE)
  ) %>%
  full_join(y = team_animal_coord, by = c("Q6" = "coordinator")) %>%
  select(-Q6)
```

# Read reviews

```{r}
msa_reviews <- readRDS("./data/peer_review/msa_reviews.rds")

msa_reviews_teams <- msa_reviews %>%
  group_by(Q3) %>%
  summarise(
    phon_rating = mean(Q5_2, na.rm = TRUE),
    phon_sd = sd(Q5_2, na.rm = TRUE),
    stat_rating = mean(Q5_3, na.rm = TRUE),
    stat_sd = sd(Q5_3, na.rm = TRUE),
    all_rating = mean(Q5_4, na.rm = TRUE),
    all_sd = sd(Q5_4, na.rm = TRUE),
  )
```

# Teams' analyses

## Upload refitted models to OSF

Once all your models have been refitted, you can upload them to the OSF, in the Cache component, `models/refitted/` folder.

Here's the code that does that for you.

```{r upload-refitted, eval=FALSE}
cache <- osf_retrieve_node("wds2m")
refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
  filter(name == "refitted")
models <- list.files(
  "./data/analyses/models",
  full.names = TRUE
)

osf_upload(
  refitted,
  path = models,
  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
)
```

## Download all refitted models

We download all the refitted models `.rds` files from the OSF.

```{r download-refitted, eval=FALSE}
cache <- osf_retrieve_node("wds2m")
refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)

osf_download(
  refitted_rds,
  path = "./data/analyses/models/",
  conflicts = "skip", progress = TRUE, verbose = TRUE
)
```

# Get estimates from refitted models

Now we can extract the relevant estimates from the refitted models.

The following functions extracts the estimates.

```{r clean-up}
clean_up <- function(model) {
  effs <- suppressWarnings(tidy(model, effects = "fixed", parametric = TRUE)) %>% 
  filter(term %in% c("effect_catmedium", "effect_cattypical", "effect_con"))
  if (!("response" %in% colnames(effs))) {
    effs$response <- "none"
  }
  effs <- effs %>%
  select(outcome_mult = response, term, estimate, se = std.error)

  return(effs)
}
```

This function is for calculation of the SDI.

```{r sdi-mean}
sdi_mean <- function(preds) {
  bpair <- tibble::tibble(preds) %>% tidyr::unnest_wider(preds, names_sep = ".") %>%
    as.matrix() %>%
    betapart::beta.pair(.)
  sdim <- as.matrix(bpair$beta.sor)
  diag(sdim) <- NA
  rowSums(sdim, na.rm = T) / length(preds)
}
```

Now we load all the models and apply `clean_up()` to get the estimates.

```{r load-models}
msa_models <- dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
  as_tibble() %>% 
  transmute(
    path = value,
    mod_name = str_remove(path, here("data/analyses/models/")), 
    mod_name = str_remove(mod_name, ".rds"), 
    model = map(path, ~ readRDS(file = .))
  ) %>% 
  separate(
    mod_name, 
    into = c("word1", "word2", "model_n", "model_outcome", "typicality"), 
    sep = "_", remove = F,
    convert = TRUE
  ) %>% 
  unite(animal, word1, word2, sep = "_") %>% 
  select(animal, model_n:model) %>% 
  mutate(summaries = map(model, clean_up)) %>%
  select(-model) %>%
  unnest(summaries) %>%
  mutate(
    typ_level = case_when(
      term == "effect_cattypical" ~ "typical",
      term == "effect_catmedium" ~ "medium"
    ),
    typicality = ifelse(typicality == "con", "continuous", "categorical"),
    model_id = paste(animal, model_n, sep = "_")
  ) %>%
  select(animal, model_n, model_id, model_outcome, outcome_mult, typicality, typ_level, estimate, se) %>%
  mutate(
    outcome_mult = case_when(
      outcome_mult == "none" ~ NA_character_,
      outcome_mult == "meanf0" ~ "f0",
      outcome_mult == "meanint" ~ "intensity",
      outcome_mult == "duration" ~ "duration",
      outcome_mult == "f0" ~ "f0",
      outcome_mult == "f15" ~ "formants_1",
      outcome_mult == "f25" ~ "formants_2"
    )
  ) %>%
  left_join(y = coding) %>%
  mutate(
    model_id = ifelse(is.na(outcome_mult), model_id, paste(model_id, outcome_mult, sep = "_")),
    model_id = ifelse(is.na(typ_level), model_id, paste(model_id, typ_level, sep = "_")),
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "other")),
    typicality = factor(typicality, levels = c("categorical", "continuous")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  ) %>%
  left_join(y = msa_intake_teams) %>%
  left_join(y = msa_reviews_teams, by = c("animal" = "Q3")) %>%
  # We have excluded a few extra models so keeping them out at this stage
  filter(exclude == "no") %>%
  # We nest all the population predictors in the coding sheet to calculate the SDI
  nest(pop_pred = typicality_cont:`2interaction_typicality_cont_typ_mean_z`) %>%
  mutate(
    pop_sdi = sdi_mean(pop_pred)
  )

saveRDS(msa_models, "./data/analyses/msa_models.rds")
```

Simple pandoc table of the models, estimates, se, etc.

```{r effect-table}
msa_models %>%
  select(model_id, estimate, se) %>%
  knitr::kable(format = "pandoc")
```

# Plotting

Simple forest plot of the estimates and 95% CrIs.

```{r fp-outcome}
msa_models %>%
  filter(animal != "polymetme_brevirostrum") %>%
  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
  geom_hline(yintercept = 0) +
  geom_segment(
    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
    alpha = 0.5, size = 1, lineend = "round"
  ) + 
  geom_point(pch = 21, stroke = 2, size = 1) +
  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
  scale_colour_brewer(palette = "Set1", type = "qual") +
  labs(y = "Estimate (z-scores)") + 
  clean_theme() 
```

```{r fp-outcome-facet}
msa_models %>%
  filter(animal != "polymetme_brevirostrum") %>%
  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = outcome)) + 
  geom_hline(yintercept = 0) +
  geom_segment(
    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
    alpha = 0.5, size = 1, lineend = "round"
  ) + 
  geom_point(pch = 21, stroke = 2, size = 1) +
  facet_grid(outcome ~ typicality, scales = "free") +
  scale_colour_brewer(palette = "Set1", type = "qual") +
  labs(y = "Estimate (z-scores)") + 
  clean_theme()
```

```{r forest-plot-2}
msa_models %>%
  filter(animal != "polymetme_brevirostrum") %>%
  ggplot(aes(x = reorder(model_id, estimate), y = estimate, colour = estimate)) + 
  geom_hline(yintercept = 0) +
  geom_segment(
    aes(y = estimate - se * 1.96, yend = estimate + se * 1.96, xend = model_id), 
    alpha = 0.5, size = 1, lineend = "round"
  ) + 
  geom_point(pch = 21, stroke = 2, size = 1) +
  facet_wrap(. ~ typicality, ncol = 1, scales = "free") +
  scale_colour_gradientn(colours = c("#d95f02", "#dfc27d", "#80cdc1", "#018571"), limits = c(-1, 1)) +
  labs(y = "Estimate (z-scores)") + 
  clean_theme() 
```

```{r frameworks}
coding %>%
  ggplot(aes(framework)) +
  geom_bar()
```

```{r models}
coding %>%
  ggplot(aes(model)) +
  geom_bar()
```

```{r family}
coding %>%
  ggplot(aes(family)) +
  geom_bar()

coding %>%
  ggplot(aes(outcome, fill = family)) +
  geom_bar()
```

```{r temporal-w}
coding %>%
  drop_na(outcome, temporal_window) %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
```

```{r temporal-w-2}
coding %>%
  drop_na(outcome, temporal_window) %>%
  filter(
    outcome %in% c("duration", "f0", "intensity"),
    temporal_window %in% c("segment", "word", "phrase", "sentence")
  ) %>%
  droplevels() %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, temporal_window), fill = outcome))
```

```{r operation}
coding %>%
  drop_na(operationalisation) %>%
  count(operationalisation) %>%
  ggplot(
    aes(reorder(operationalisation, desc(n)), n)
    ) +
  geom_bar(stat = "identity")
```

```{r operation-2}
coding %>%
  drop_na(outcome, operationalisation) %>%
  filter(
    outcome %in% c("duration", "f0", "intensity"),
    temporal_window %in% c("segment", "word", "phrase", "sentence")
  ) %>%
  droplevels() %>%
  ggplot() +
  geom_mosaic(aes(x = product(outcome, operationalisation), fill = outcome))
```

# Unique model combinations

```{r combos}
coding %>%
  select(framework:outcome, operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
  distinct()
```

```{r n-models}
coding %>%
  select(team, n_models) %>%
  distinct() %>%
  drop_na() %>%
  summarise(mean(n_models), median(n_models), sd(n_models), min(n_models), max(n_models))
```

### 2022-10-24 RR_manuscript/Draft_RR.tex
♻️ - adress issue #254

@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
+As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
 First, we report on the between-team variability estimate (i.e.~the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), which is the focus of this study, followed by the meta-analytic estimate (i.e.~the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
@@
 The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
+For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
+We discuss this in more details in the Discussion section.
+
 Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
@@
 
+The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
+This means that some of the effects on a particular response as observed in a specific location within the utterance might naturally be positive, while other negative, resulting in a meta-analytic intercept of about zero.
+We want to stress, however, that our focus is not on the meta-analytic intercept per se, but on the fact that a seemingly straightforward research question led to so many possible outcomes.
+More on this in the Discussion section.
+
 Figure \ref{fig:plot-meta1} illustrates the individual intercepts for critical typicality coefficients across models and teams, sorted in ascending order based on their mean.
@@
 Estimates ranged from -0.65 to 0.99 standard units.
-We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale \citep{kamphaus2019clinical} which is defined by a standard deviation of 15.
-The observed variability of estimates between teams corresponds to variability in IQ measures up to 14.9 IQ points.
+
 While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 16\%).
@@
 These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.\footnote{Note that these categories necessarily refer to variegated sets of measures.
-E.g.
-the domain word includes words that differed along several dimensions, including their length and their metrical structure.}
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.\footnote{Note that these categories necessarily refer to a variegated set of measures, for example the domain ``word'' includes words that differed along several dimensions, including their length and their metrical structure.}
 

### 2022-10-24 scripts/r/00_credit_taxonomy.R
♻️ - closes issue #250

@@ -1,24 +1,0 @@
-# CRediT taxonomy
-
-library(tidyverse)
-
-credit <- read_csv(here::here("./data/metadata/credit-taxonomy.csv")) %>%
-  pivot_longer(SC:TR, names_to = "author", values_to = "value") %>%
-  mutate(
-    author = factor(author, levels = c("SC", "JVC", "TR")),
-    value = ifelse(is.na(value), 0.2, value)
-  )
-
-credit %>%
-  ggplot(aes(author, Roles)) +
-  geom_point(aes(alpha = value)) +
-  scale_y_discrete(limits = rev) +
-  scale_x_discrete(position = "top") +
-  labs(
-    x = element_blank(), y = element_blank(),
-    caption = "CRediT (Contributor Roles Taxonomy), http://credit.niso.org."
-  ) +
-  theme_light() +
-  theme(legend.position = "none", text = element_text(size = 8))
-
-ggsave(here::here("./figs/credit-taxonomy.png"), width = 3, height = 3)

### 2022-10-24 scripts/r/03_analyses_download.Rmd

--- 2022-09-10 scripts/r/03_analyses_coding.Rmd
@@
 ---
-title: "03 - Analyses coding"
+title: "03 - Download teams analyses components"
 output: html_document
@@
 
-Now that the components have been downloaded, we can refit the models using the scripts in `scripts/r/04-refit/`.
+Now that the components have been downloaded, we can refit the models following the instructions in `04-1_refit_workflow`.

### 2022-10-24 RR_manuscript/Draft_RR.Rmd

@@
 
-<!-- TODO: add background info and use consistent terminology -->
 This section deals with the meta-analytic analysis of the results submitted by the teams.
 <!-- TODO: repeat exclusion criteria -->
+As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
 First, we report on the between-team variability estimate (i.e.
@@
 The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
+For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
+We discuss this in more details in the Discussion section.
+
 Taken together, the models suggest that the variability of reported effects between any model (within team or across) is substantially larger than the variability across individual teams.
@@
 I wonder whether we should take this out -->
+The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
+This means that some of the effects on a particular response as observed in a specific location within the utterance might naturally be positive, while other negative, resulting in a meta-analytic intercept of about zero.
+We want to stress, however, that our focus is not on the meta-analytic intercept per se, but on the fact that a seemingly straightforward research question led to so many possible outcomes.
+More on this in the Discussion section.
 
@@
 Estimates ranged from `r round(min(msa_models$estimate),2)` to `r round(max(msa_models$estimate),2)` standard units.
-We will interpret these standard units relative to phonetic measures in the discussion section, but to provide an intuition about the absolute scale of variation, we can express them on a standardized scale that does not require domain expertise: The IQ scale [@kamphaus2019clinical] which is defined by a standard deviation of 15.
-The observed variability of estimates between teams corresponds to variability in IQ measures up to 14.9 IQ points.
+
 While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.
@@
 These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to variegated sets of measures.
-E.g.
-the domain word includes words that differed along several dimensions, including their length and their metrical structure.]
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]
 

### 2022-10-25 RR_manuscript/Draft_RR.Rmd
reworked abstract, addressed some comments from Rory, added paragraph on same-ish analyses resulting in diff estimates

@@
 email: "timo.b.roettger@iln.uio.no"
-abstract: "Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
-Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
+abstract: "Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
 Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time.
@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question.
-Using Bayesian meta-analytic tools, we have observed substantial variability in reported effect sizes and their interpretation.
-We further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses."
+In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation.
+Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses.
+In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions"
 keywords: "crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis"
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a seminal collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
+In a pioneering collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
 The analytic approaches and, consequently, the results varied widely between teams.
@@
 For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
-We discuss this in more details in the Discussion section.
+We interpret these values in more details in the Discussion section.
 
@@
 
-Furthermore, the observed variation does not seem to be systematic.
+While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
+Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
+For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
+While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.
+mean, min, max, or range) and how their statistical model was constructed (i.e.
+the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
+As shown by [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+
+The observed variation does not seem to be systematic.
 For example, variation between teams was not predicted by the analysts' prior expectations about the phenomenon.
@@
 
-The current results point to important barriers for successful accumulation of knowledge.
+The current results point to important barriers to the successful accumulation of knowledge.
 The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature [@vazire2017quality; @fidler2018reproducibility].

### 2022-10-25 RR_manuscript/Draft_RR.Rmd
quick fix of meta-plot as discussed

--- 2022-10-24 RR_manuscript/Draft_RR.Rmd
@@
 ```{r plot-meta1, echo = FALSE, fig.cap="(ref:plot-meta1)", out.width="100%"}
-knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
+knitr::include_graphics(here::here("./figs/meta_plot1_raw.png"), error = FALSE)
 ```

### 2022-10-28 RR_manuscript/Draft_RR.Rmd
♻️ - address peer review comments

@@
 
-Each analysis was evaluated by four different teams who functioned as peer-reviewers.
+The analyses from each team were evaluated by four different teams who functioned as peer-reviewers.
 Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
@@
 First, the reviewer received a description of the methods of a single analysis.
-This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
+This included the narrative methods and results sections, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
 The reviewer was then asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.

### 2022-10-28 RR_manuscript/Draft_RR.Rmd
♻️ - add crossref

@@
 
-### Meta-analytic estimation {#s:meta-est}
+### Meta-analytic estimation
 
@@
 As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} ($\sigma_{\alpha_{\text{t}}}$, see below), where each analysis team represents a group.
-As we detail in Section *Meta-analytic estimation*, we have also run further non-preregistered analyses. <!-- Add crossref to final version: \@ref(meta-est) -->
+As we detail in the Results section below, we have also run further non-preregistered analyses.
 For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.
@@
 
-## Meta-analytic estimation {#meta-est}
+## Meta-analytic estimation {#meta-est-2}
 

### 2022-10-28 RR_manuscript/Draft_RR.tex
♻️ - add crossref

@@
 \begin{abstract}
-Recent efforts to replicate published findings have uncovered surprisingly low success rates across disciplines.
-Moreover, several studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
+Recent empirical studies have highlighted the large degree of analytic flexibility in data analysis which can lead to substantially different conclusions based on the same data set.
 Thus, researchers have expressed their concerns that these researcher degrees of freedom might facilitate bias and can lead to claims that do not stand the test of time.
@@
 The multidimensional, temporally extended nature of speech constitutes an ideal testing ground for assessing the variability in analytic approaches, which derives not only from aspects of statistical modeling, but also from decisions regarding the quantification of the measured behavior.
-In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question.
-Using Bayesian meta-analytic tools, we have observed substantial variability in reported effect sizes and their interpretation.
-We further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses.
+In the present study, we gave the same speech production data set to 46 teams of researchers and asked them to answer the same research question, resulting in substantial variability in reported effect sizes and their interpretation.
+Using Bayesian meta-analytic tools, we further find little to no evidence that the observed variability can be explained by analysts' prior beliefs, expertise or the perceived quality of their analyses.
+In light of this idiosyncratic variability, we recommend that researchers more transparently share details of their analysis, strengthen the link between theoretical construct and quantitative system and calibrate their (un)certainty in their conclusions
 \end{abstract}
@@
 Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.
-In a seminal collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
+In a pioneering collaborative effort, \citet{silberzahn2018many} let twenty-nine independent analysis teams address the same research hypothesis: whether soccer referees are more likely to give red cards to dark-skin-toned players than to light-skin-toned players.
 The analytic approaches and, consequently, the results varied widely between teams.
@@
 First, the reviewer received a description of the methods of a single analysis.
-This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
+This included the narrative methods and results sections, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
 The reviewer was then asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
@@
 
-\hypertarget{s:meta-est}{%
-\subsubsection{Meta-analytic estimation}\label{s:meta-est}}
+\hypertarget{meta-analytic-estimation}{%
+\subsubsection{Meta-analytic estimation}\label{meta-analytic-estimation}}
 
@@
 As the measure of variability, we took the meta-analytic \textsc{group-level standard deviation} (\(\sigma_{\alpha_{\text{t}}}\), see below), where each analysis team represents a group.
-As we detail in Section \emph{Meta-analytic estimation}, we have also run further non-preregistered analyses.
+As we detail in the Results section below, we have also run further non-preregistered analyses.
 For these we refer the reader to that section, while we only describe the preregistered analyses in the following paragraphs.
@@
 
-\hypertarget{meta-est}{%
-\subsection{Meta-analytic estimation}\label{meta-est}}
+\hypertarget{meta-est-2}{%
+\subsection{Meta-analytic estimation}\label{meta-est-2}}
 
@@
 For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
-We discuss this in more details in the Discussion section.
+We interpret these values in more details in the Discussion section.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{Standardized effect sizes across all critical coefficients provided by the teams.
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_raw} \caption{Standardized effect sizes across all critical coefficients provided by the teams.
 Raw estimates are displayed in grey.
@@
 
-Furthermore, the observed variation does not seem to be systematic.
+While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
+Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
+For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
+While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, min, max, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
+As shown by \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+
+The observed variation does not seem to be systematic.
 For example, variation between teams was not predicted by the analysts' prior expectations about the phenomenon.
@@
 
-The current results point to important barriers for successful accumulation of knowledge.
+The current results point to important barriers to the successful accumulation of knowledge.
 The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep{vazire2017quality, fidler2018reproducibility}.

### 2022-10-28 RR_manuscript/Draft_RR.Rmd

@@
 
-After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
+After having obtained the standardized effect sizes $\eta_i$ with related standard errors $\text{se}_i$, for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
 The outcome variable was the set of standardized effect sizes $\eta_i$.
@@
 <!-- In case of divergent transitions, we will increase `adapt_delta`, `tree_depth`, and the number of iterations in this order until we obtain a model fit with no divergent transitions. -->
-The model did not incur any divergent transitions ($\hat{R}$ was equal or lower than 1) and the estimated sample sizes were sufficient.
+The model did not incur any divergent transitions ($\hat{R}$ was not greater than 1) and the estimated sample sizes were sufficient.
 <!-- TODO: add link to meta-model code -->
@@
 We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
-We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
-<!-- TODO: mention that there were some and add info in descriptive stats section? -->
+We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
+For a list of exlcusion criteria, see Section Descriptive statistics below.
 
@@
 
-The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0.1)` standard units and 95% probability.
+The nested model yields a posterior 95% CrI for between-team variability of `r round(meta_bm_nest_tidy$conf.low[["sd_animal__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units ($\beta$ = 0.02, SD = 0.01), corresponding to a mean deviation range of about `r pm(x = 0)` to `r pm(x = 0.1)` standard units and 95% probability.
 The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
@@
 
+We have run a model as described in Section Analytic and researcher-related predictors affecting effect sizes above.
 Figure \@ref(fig:plot-meta2), panel C, displays the coefficients for all predictors alongside their 80% and 95% credible intervals.
@@
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect [@roettger2019researcher; @simmons2011false].
-One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): "[T]he project's approach is too much top-down instead of bottom-up.
-[...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
+We of course are not arguing that exploratory analyses should not be employed.
+Rather, we simply want to point out that if the theoretical underpinnings of the field were much clearer, different teams would have converged towards a limited set of analyses despite of a less specific research question.
+
+In relation to this aspect, one team coordinator decided to drop out of the project because of its approach being too top-down.
+The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
 We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
@@
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility [see @campbell1975 for an overview of the concept].
 
@@
 While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
-This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
+This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods [@haven2019].
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis. 
-When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e.
-is there evidence for a relationship or not) and vastly different effect magnitudes.
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ in how they approach this task, leading to both different qualitative answers (i.e.
+is there evidence for a relationship or not) and different effect magnitudes.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
+More specifically, what we find of particular relevance is the fact that commonly research proceeds based on publications from one research team at a time.
+If we imagine a situation where any of the 46 teams could have been *the* team publishing a study on this topic, it is immediately clear that that single study is just a very limited view.
+In light of this we want to stress that the field has to quickly move from one-off studies to collaborative approaches like the one employed here and to more frequent replication attempts for example by incentivizing replication through dedicated funding and editorial policies, among others.
 

### 2022-10-28 RR_manuscript/Draft_RR.tex

@@
 
-After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor of the individual reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
+After having obtained the standardized effect sizes \(\eta_i\) with related standard errors \(\text{se}_i\), for each critical predictor in each reported model, we conducted a \textsc{Bayesian random-effects meta-analysis} using a multi-level (intercept-only) regression model.
 The outcome variable was the set of standardized effect sizes \(\eta_i\).
@@
 We fit this model with 4 chains of Hamiltonian Monte-Carlo sampling for the estimation of the joint posterior distribution, using the No U-Turn Sampler (NUTS) as implemented in Stan \citep{stan2021}, and 4000 iterations (2000 for warm-up) per chain, distributed across 8 processing cores and 2 threads in within-chain parallelization.
-The model did not incur any divergent transitions (\(\hat{R}\) was equal or lower than 1) and the estimated sample sizes were sufficient.
+The model did not incur any divergent transitions (\(\hat{R}\) was not greater than 1) and the estimated sample sizes were sufficient.
 The code used to run the model can be found at \textless\textgreater.
@@
 We excluded from our synthesis any individual analysis submitted after peer review (Phase 3) or those unaccompanied by analysis files without which it was not possible to follow the research protocol.
-We also excluded any individual analysis that does not produce an outcome that can be interpreted as an answer to our primary question.
+We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
+For a list of exlcusion criteria, see Section Descriptive statistics below.
 
@@
 
-The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0.1\) standard units and 95\% probability.
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
 The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
@@
 
+We have run a model as described in Section Analytic and researcher-related predictors affecting effect sizes above.
 Figure \ref{fig:plot-meta2}, panel C, displays the coefficients for all predictors alongside their 80\% and 95\% credible intervals.
@@
 The complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher, simmons2011false}.
-One team coordinator gave the following reason for dropping out of the project (and allowed us to share this statement): ``{[}T{]}he project's approach is too much top-down instead of bottom-up.
-{[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
+We of course are not arguing that exploratory analyses should not be employed.
+Rather, we simply want to point out that if the theoretical underpinnings of the field were much clearer, different teams would have converged towards a limited set of analyses despite of a less specific research question.
+
+In relation to this aspect, one team coordinator decided to drop out of the project because of its approach being too top-down.
+The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
 We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
@@
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
-Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility.
+Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and a certain level of epistemic humility \citep[see][ for an overview of the concept]{campbell1975}.
 
@@
 While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
-This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods.
+This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods \citep{haven2019}.
 It is conceivable that the discussed issues apply differently or not at all to qualitative data analyses.
@@
 In recent efforts, several studies have highlighted the large degree of analytic flexibility in data analysis.
-When many different analysts have to analyze the same data set to answer the same research question, analysts differ drastically in how they approach this task, leading to both different qualitative answers (i.e.~is there evidence for a relationship or not) and vastly different effect magnitudes.
+When many different analysts have to analyze the same data set to answer the same research question, analysts differ in how they approach this task, leading to both different qualitative answers (i.e.~is there evidence for a relationship or not) and different effect magnitudes.
 This is concerning, as it can lead to substantially different conclusions based on the same data set, a state of affairs that can generate biased inferential decisions and might weaken confidence in the published literature.
+More specifically, what we find of particular relevance is the fact that commonly research proceeds based on publications from one research team at a time.
+If we imagine a situation where any of the 46 teams could have been \emph{the} team publishing a study on this topic, it is immediately clear that that single study is just a very limited view.
+In light of this we want to stress that the field has to quickly move from one-off studies to collaborative approaches like the one employed here and to more frequent replication attempts for example by incentivizing replication through dedicated funding and editorial policies, among others.
 

### 2022-10-28 scripts/r/09_credit_taxonomy.Rmd

@@
 
-```{r}
+```{r setup}
 #| label: setup
@@
 #| label: load-libs
-library("googledrive")
+library(googlesheets4)
 library("xml2")
@@
 #| label: identify-download
-# give gargle permission
-drive_auth(email = TRUE)
 
-# Locate file, check ID
-drive_find(n_max = 5, type = "spreadsheet")
-
-# Search by id (just checking)
-drive_get(id = "1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA")
+all_data_temp <- read_sheet("1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA") %>% 
+  janitor::clean_names()
 
 # Download to doc folder
-drive_download(
-  file = "MSA_tenzing_contribution", 
-  path = "./data/CRediT/MSA_tenzing_contribution.csv", 
-  type = "csv",
-  overwrite = T
-  )
+write_csv(all_data_temp, "data/CRediT/MSA_tenzing_contribution.csv")
 ```
@@
 initiating_authors <- c("Coretta", "Casillas", "Roessig", "Franke", "Roettger")
-
-# Load data
-all_data_temp <- read_csv("./data/CRediT/MSA_tenzing_contribution.csv") %>% 
-  janitor::clean_names()
 
@@
          caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
-    theme_minimal(base_size = 12, base_family = "Times") +
+    theme_light(base_size = 12, base_family = "Times") +
     theme(
@@
 
+ggsave("figs/credit-taxonomy.png", width = 14, height = 10)
 ```

### 2022-11-02 RR_manuscript/Draft_RR.Rmd

@@
 Of the analysis submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
-Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
+Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
 

### 2022-11-02 RR_manuscript/Draft_RR.Rmd
closes #260

@@
 
-The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://osf.io/3bmcp/>.
 The repository holds three main OSF components (`Data`, `Teams analyses` and `Questionnaires`), and a link to the project's GitHub repository.
@@
 To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
-The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
+The code is available at <https://many-speech-analyses.github.io/many_analyses/scripts/r/simulations/simulations>, Section 2.^[Cached model outputs can be found at <https://osf.io/wds2m/>.]
 Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
@@
 The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (`intake_form.pdf`).
-A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
+A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://osf.io/h6z8w/>.
 The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
-These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.
+These can be found in the `Data` component at <https://osf.io/5agn9/>.
 
@@
 Model refitting also constituted a way of validating the reported analyses, a step recommended by @aczel2021.
-<!-- TODO: add link to refitting procedure -->
-Details about the refitting procedure can be found at LINK.
+Details about the refitting procedure can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow>.
 
@@
 The model did not incur any divergent transitions ($\hat{R}$ was not greater than 1) and the estimated sample sizes were sufficient.
-<!-- TODO: add link to meta-model code -->
-The code used to run the model can be found at <>.
+The code used to run the model can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg>.
 
@@
 The model was run with the same settings as with the meta-analytic model.
-<!-- TODO: add link to predictor model code -->
-The code used to run the model can be found at <LINK>.
+The code used to run the model can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg>.
 
@@
 
-The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.
-<!-- TODO: Add link to the collaborative document maybe? -->
+The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.^[The comment history can be found at <https://docs.google.com/document/d/1CFgRo93mRgifpuFOuQE3vNBeMW-H7ps9eD--vxH-6CQ/edit?usp=sharing>.]
 
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of the study, containing all the code and data presented here, can be found at <https://osf.io/3bmcp/>.
+The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at <https://osf.io/3bmcp/>, in the `scripts/r/` folder.
 
@@
 Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%).
-<!-- It looks like this is on the level of critical coefficients = 170, rather than submitted models, double check -->
 
@@
 This section deals with the meta-analytic analysis of the results submitted by the teams.
-<!-- TODO: repeat exclusion criteria -->
 As discussed above, the analyses of only 30 teams out of all the submitted analysis were included in the meta-analytic model discussed here.
@@
 the intercept of the meta-analytic model, in other words, the estimated effect of typicality on the acoustic production of adjective-noun combinations).
-<!-- TR: remove reference to meta-analytical estimate -->
 
@@
 
-<!-- TR: The meta analytical estimate is basically meaningless, given that the scale is not interpretable and artificial negative and positive estimates cancel each other out.
-I wonder whether we should take this out -->
 The meta-analytic intercept conflates estimates from a variety of responses taken from very different places in the utterance (nouns, adjectives, determiners, entire phrases or sentences, etc).
@@
 While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.
-mean, min, max, or range) and how their statistical model was constructed (i.e.
+mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.
 the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
@@
 
-<!-- TODO: add LINK to credit -->
-See image at LINK [for peer-review, see figure `credit-taxonomy.png` attached with submission].
+See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png>.
 

### 2022-11-02 RR_manuscript/Draft_RR.tex
closes #260

@@
 
-The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
+The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://osf.io/3bmcp/}.
 The repository holds three main OSF components (\texttt{Data}, \texttt{Teams\ analyses} and \texttt{Questionnaires}), and a link to the project's GitHub repository.
@@
 To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
-The code is available at \url{https://many-speech-analyses.github.io/suppl/simulations.html}, Section 2.\footnote{Cached model outputs can be found at \url{https://bit.ly/3AgdHAN}.}
+The code is available at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/simulations/simulations}, Section 2.\footnote{Cached model outputs can be found at \url{https://osf.io/wds2m/}.}
 Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
@@
 The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
-A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
+A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://osf.io/h6z8w/}.
 The questionnaire collected information on the analysts' current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
@@
 Data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
-These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.
+These can be found in the \texttt{Data} component at \url{https://osf.io/5agn9/}.
 
@@
 Model refitting also constituted a way of validating the reported analyses, a step recommended by \citet{aczel2021}.
-Details about the refitting procedure can be found at LINK.
+Details about the refitting procedure can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow}.
 
@@
 The model did not incur any divergent transitions (\(\hat{R}\) was not greater than 1) and the estimated sample sizes were sufficient.
-The code used to run the model can be found at \textless\textgreater.
+The code used to run the model can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg}.
 
@@
 The model was run with the same settings as with the meta-analytic model.
-The code used to run the model can be found at .
+The code used to run the model can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/06_meta-analysis_prereg}.
 
@@
 
-The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.
+The initiating authors discussed the limitations, results, and implications of the study and collaborated with the analysts on writing the final manuscript for review as a stage-2 Registered Report.\footnote{The comment history can be found at \url{https://docs.google.com/document/d/1CFgRo93mRgifpuFOuQE3vNBeMW-H7ps9eD--vxH-6CQ/edit?usp=sharing}.}
 
@@
 Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
-The research compendium of the study, containing all the code and data presented here, can be found at \url{https://osf.io/3bmcp/}.
+The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at \url{https://osf.io/3bmcp/}, in the \texttt{scripts/r/} folder.
 
@@
 Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
-Reasons for exclusion were: use of Generalised Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
+Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
 
@@
 For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
-While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, min, max, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
+While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
 As shown by \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
@@
 
-See image at LINK {[}for peer-review, see figure \texttt{credit-taxonomy.png} attached with submission{]}.
+See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png}.
 

### 2022-11-02 RR_manuscript/supplementary_materials.Rmd
closes #244

@@
 # Read in primary coding sheet
-the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"
+the_sheet <- "data/analyses/analyses_coding.csv"
 
@@
 msa_models_unique <- left_join(
-  read_sheet(the_sheet) %>% 
+  read_csv(the_sheet) %>% 
     filter(added_on_osf == "yes") %>% 

### 2022-11-03 RR_manuscript/Draft_RR.Rmd
fixed figure 3

@@
 ```{r plot-meta1, echo = FALSE, fig.cap="(ref:plot-meta1)", out.width="100%"}
-knitr::include_graphics(here::here("./figs/meta_plot1_raw.png"), error = FALSE)
+knitr::include_graphics(here::here("./figs/meta_plot1_shrinkage.png"), error = FALSE)
 ```

### 2022-11-03 RR_manuscript/Draft_RR.Rmd
few minor fixes

@@
 The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `round(predictor_n$min_predictor,1)`-`round(predictor_n$max_predictor,1)`).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)`-`r `round(predictor_n$max_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units at 95% credibility.
-In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) with 95% credibility.”
+In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.high[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) with 95% credibility.”
 
@@
 the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
-As shown by [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+As shown by Breznau et al.[-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
 
@@
 The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
-We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
+We find that this attitude speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences. 
 Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
@@
 This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
@@
 We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech). 
-While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
+While we do believe that our qualitative conclusions hold across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
 This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods [@haven2019].
@@
 Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal. 
-This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to different conclusions.
 We suggest that fields that use multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.

### 2022-11-04 RR_manuscript/Draft_RR.Rmd

@@
 ```{r forkingPaths, echo=FALSE, fig.cap="(ref:forkingPaths)", out.width="100%"}
-knitr::include_graphics(here::here("figs", "ForkingPaths.tiff"), error = FALSE)
+knitr::include_graphics(here::here("figs", "ForkingPaths.png"), error = FALSE)
 ```

### 2022-11-04 RR_manuscript/Draft_RR.tex

@@
 The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = \texttt{round(predictor\_n\$min\_predictor,1)}-\texttt{round(predictor\_n\$max\_predictor,1)}).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1-\texttt{r}round(predictor\_n\$max\_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
-In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.06\) (0.07 * 1.96) with 95\% credibility.''
+In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.14\) (0.07 * 1.96) with 95\% credibility.''
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{../figs/meta_plot1_raw} \caption{Standardized effect sizes across all critical coefficients provided by the teams.
+\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{Standardized effect sizes across all critical coefficients provided by the teams.
 Raw estimates are displayed in grey.
@@
 While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
-As shown by \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+As shown by Breznau et al.\citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
 
@@
 The coordinator also expressed a preference to be able to explore and run a variety of descriptive analyses followed up with inferential statistics.
-We find that this statement speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
+We find that this attitude speaks to the main objective of the current study: investigate researchers' degrees of freedom in the speech sciences.
 Based on our personal experience with research in the field, it is common practice to test many different types of models, using many different types of measurements, to answer one research hypothesis.
@@
 This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -29, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -29\%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
@@
 We focused on quantitative analyses that require the operationalization of a multidimensional signal in an artificial elicitation situation (laboratory speech).
-While we do believe that our qualitative conclusions holds across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
+While we do believe that our qualitative conclusions hold across fields exhibiting similar methodologies, the detailed quantitative results will only be able to directly inform similar disciplines that work with speech or audio/video signals.
 This is an important point to make because cognitive sciences in general, and the language sciences in particular, have many research areas that are based on qualitative methods \citep{haven2019}.
@@
 Importantly however, we found some evidence for systematic effects on teams' estimates based on what and how they measured the speech signal.
-This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to inconclusive results.
+This result, taken together with the meaningful between-model variation and the tendency to test the research question on multiple outcome variables, suggests that a vast plurality of acceptable approaches is expected to frequently lead to different conclusions.
 We suggest that fields that use multidimensional data need to acknowledge these degrees of freedom, consider crowd-sourcing and multiverse analyses when evaluating epistemologically or practically important phenomena, and strengthen the link between theoretical predictions and the measurement system by means of mathematical formalization and computational modeling.

### 2022-11-04 scripts/r/03_analyses_download.Rmd

@@
 ```{r coding}
-the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"
+the_sheet <- "data/analyses/analyses_coding.csv"
 
-coding <- read_sheet(the_sheet) %>%
+coding <- read_csv(the_sheet) %>%
   drop_na(model_n)
@@
 ```{r intake}
-other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"
+other_sheet <- "data/metadata/team_animal_coord.csv"
 
-team_animal_coord <- read_sheet(other_sheet)
+team_animal_coord <- read_csv(other_sheet)
 

### 2022-11-04 scripts/r/04-1_refitted.Rmd

@@
 ---
-title: "04-1 - Refit"
+title: "04-1 - Refitted models"
 output: html_document

### 2022-11-04 scripts/r/09_credit_taxonomy.Rmd
update credit taxonomy, format author list

@@
 #| label: load-libs
-library(googlesheets4)
+library("googlesheets4")
 library("xml2")
@@
 #| label: identify-download
+#| eval: false
 
@@
 #| label: load-tidy-csv
+# Load data
+all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")
 
@@
 ```
+
+```{r}
+#| label: copy-author-list
+#| eval: false
+# Copy author list to the clipboard so it can be pasted in RR
+contributors %>% 
+  select(name) %>% 
+  mutate(name = glue::glue("- name: {name}\n")) %>% 
+  pull() %>% 
+  clipr::write_clip() 
+```

### 2022-11-04 RR_manuscript/Draft_RR.Rmd
add author list to rr

@@
   num: 3
+- name: Simon Roessig
+- name: Michael Franke
+- name: Ali H. Al-Hoorie
+- name: Jalal Al-Tamimi
+- name: Najd E. Alotaibi
+- name: Mohammed K. AlShakhori
+- name: Ruth M. Altmiller
+- name: Pablo Arantes
+- name: Angeliki Athanasopoulou
+- name: Melissa M. Baese-Berk
+- name: George Bailey
+- name: Cheman Baira A Sangma
+- name: Eleonora J. Beier
+- name: Gabriela M. Benavides
+- name: Nicole Benker
+- name: Emelia P. BensonMeyer
+- name: Nina R. Benway
+- name: Grant M. Berry
+- name: Liwen Bing
+- name: Christina Bjorndahl
+- name: Mariska Bolyanatz
+- name: Aaron Braver
+- name: Violet A. Brown
+- name: Alicia M. Brown
+- name: Alejna Brugos
+- name: Erin M. Buchanan
+- name: Tanna Butlin
+- name: Andrés Buxó-Lugo
+- name: Coline Caillol
+- name: Francesco Cangemi
+- name: Christopher Carignan
+- name: Sita Carraturo
+- name: Tiphaine Caudrelier
+- name: Eleanor Chodroff
+- name: Michelle Cohn
+- name: Johanna Cronenberg
+- name: Olivier Crouzet
+- name: Erica L. Dagar
+- name: Charlotte Dawson
+- name: Carissa A. Diantoro
+- name: Marie Dokovova
+- name: Wood Drake
+- name: Fengting Du
+- name: Margaux Dubuis
+- name: Florent Duême
+- name: Matthew Durward
+- name: Ander Egurtzegi
+- name: Mahmoud M. Elsherif
+- name: Janina Esser
+- name: Emmanuel Ferragne
+- name: Fernanda Ferreira
+- name: Lauren K. Fink
+- name: Sara Finley
+- name: Kurtis Foster
+- name: Paul Foulkes
+- name: Rosa Franzke
+- name: Gabriel Frazer-McKee
+- name: Robert Fromont
+- name: Christina García
+- name: Jason Geller
+- name: Camille L. Grasso
+- name: Pia Greca
+- name: Martine Grice
+- name: Magdalena S. Grose-Hodge
+- name: Amelia J. Gully
+- name: Caitlin Halfacre
+- name: Westerbeek Hans
+- name: Ivy Hauser
+- name: Jen Hay
+- name: Robert Haywood
+- name: Sam Hellmuth
+- name: Allison I. Hilger
+- name: Nicole Holliday
+- name: Damar Hoogland
+- name: Yaqian Huang
+- name: Vincent Hughes
+- name: Ane Icardo Isasa
+- name: Zlatomira G. Ilchovska
+- name: Hae-Sung Jeon
+- name: Jacq Jones
+- name: Mágat N. Junges
+- name: Stephanie Kaefer
+- name: Constantijn Kaland
+- name: Matthew C. Kelley
+- name: Niamh E. Kelly
+- name: Ghada Khattab
+- name: Emiel Krahmer
+- name: Dorota Krajewska
+- name: Andreas Krug
+- name: Abhilasha A. Kumar
+- name: Anna Lander
+- name: Tomas O. Lentz
+- name: Wanyin Li
+- name: Yanyu Li
+- name: Maria Lialiou
+- name: Ronaldo M. Lima Jr.
+- name: Justin J. H. Lo
+- name: Julio César López Otero
+- name: Bradley Mackay
+- name: Bethany MacLeod
+- name: Mel Mallard
+- name: Carol-Ann McConnellogue
+- name: George Moroz
+- name: Mridhula Murali
+- name: Ladislas Nalborczyk
+- name: Filip Nenadić
+- name: Jessica Nieder
+- name: Dušan Nikolić
+- name: Francisco G. S. Nogueira
+- name: Heather M. Offerman
+- name: Elisa Passoni
+- name: Maud Pélissier
+- name: Scott J. Perry
+- name: Alexandra M. Pfiffner
+- name: Michael Proctor
+- name: Ryan Rhodes
+- name: Nicole Rodríguez
+- name: Elizabeth Roepke
+- name: Jan P. Röer
+- name: Koolen Ruud
+- name: Lucia Sbacco
+- name: Rebecca Scarborough
+- name: Felix Schaeffler
+- name: Erik Schleef
+- name: Dominic Schmitz
+- name: Alexander Shiryaev
+- name: Márton Sóskuthy
+- name: Malin Spaniol
+- name: Joseph A. Stanley
+- name: Alyssa Strickler
+- name: Alessandro Tavano
+- name: Fabian Tomaschek
+- name: Benjamin V. Tucker
+- name: Rory Turnbull
+- name: Kingsley Ugwuanyi
+- name: Iñigo Urrestarazu-Porta
+- name: Ruben van de Vijver
+- name: Kristin J. Van Engen
+- name: Emiel van Miltenburg
+- name: Bruce Wang
+- name: Natasha Warner
+- name: Simon Wehrle
+- name: Seth Wiener
+- name: Stephen Winters
+- name: Sidney G.-J. Wong
+- name: Anna Wood
+- name: Jane Wottawa
+- name: Chenzi Xu
+- name: Germán Zárate-Sández
+- name: Georgia Zellou
+- name: Cong Zhang
+- name: Jian Zhu
 - name: Timo B. Roettger

### 2022-11-04 RR_manuscript/Draft_RR.tex
add author list to rr

@@
 
-\author{Stefano Coretta*\affilnum{1, 2}, Joseph V. Casillas\affilnum{3}, Timo B. Roettger\affilnum{4}}
+\author{Stefano Coretta*\affilnum{1, 2}, Joseph V.
+Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H.
+Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E.
+Alotaibi\affilnum{}, Mohammed K.
+AlShakhori\affilnum{}, Ruth M.
+Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M.
+Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J.
+Beier\affilnum{}, Gabriela M.
+Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P.
+BensonMeyer\affilnum{}, Nina R.
+Benway\affilnum{}, Grant M.
+Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A.
+Brown\affilnum{}, Alicia M.
+Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M.
+Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L.
+Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A.
+Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M.
+Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K.
+Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L.
+Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S.
+Grose-Hodge\affilnum{}, Amelia J.
+Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I.
+Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G.
+Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N.
+Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C.
+Kelley\affilnum{}, Niamh E.
+Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A.
+Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O.
+Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M.
+Lima Jr.\affilnum{}, Justin J.
+H.
+Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G.
+S.
+Nogueira\affilnum{}, Heather M.
+Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J.
+Perry\affilnum{}, Alexandra M.
+Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P.
+Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A.
+Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V.
+Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J.
+Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J.
+Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B.
+Roettger\affilnum{4}}
 

### 2022-11-05 RR_manuscript/supplementary_materials.Rmd
Add medians and range to supplementary table

@@
 date: "`r Sys.Date()`"
+header-includes: 
+  - \pagenumbering{gobble}
 ---
@@
     filter(!(animal %in% c("pervagor_adscensionis", "pseudodax_euryzona"))) %>% 
-    summarize(phon_rating = mean(phon_rating), 
-              stat_rating = mean(stat_rating), 
-              all_rating = mean(all_rating)), 
+    summarize(phon_rating = median(phon_rating), 
+              stat_rating = median(stat_rating), 
+              all_rating = median(all_rating)), 
   by = "animal"
@@
     max = team_desc_df %>% filter(stage == "Submitted") %>% pull(max), 
-    avg = team_desc_df %>% filter(stage == "Submitted") %>% pull(mean_size), 
+    Median = team_desc_df %>% filter(stage == "Submitted") %>% pull(median_size), 
     sd =  team_desc_df %>% filter(stage == "Submitted") %>% pull(sd_size)) %>% 
@@
     max_models = max(max_n_models, na.rm = T), 
+    median_models = median(max_n_models, na.rm = T), 
     n_models = sum(max_n_models, na.rm = T)
@@
     max_predictor = max(n_predictors, na.rm = TRUE), 
+    median_predictor = median(n_predictors, na.rm = T), 
     n_predictor = sum(n_predictors, na.rm = TRUE)
@@
     max_rterms = max(n_random, na.rm = TRUE), 
+    median_rterms = median(n_random, na.rm = TRUE), 
     n_rterms = sum(n_random, na.rm = TRUE)
@@
     max_rint = max(n_random_int, na.rm = TRUE), 
+    median_rint = median(n_random_int, na.rm = TRUE), 
     n_rint = sum(n_random_int, na.rm = TRUE)
@@
     max_rslope = max(n_random_slo, na.rm = TRUE), 
+    median_rslope = median(n_random_slo, na.rm = TRUE), 
     n_rslope = sum(n_random_slo, na.rm = TRUE)
@@
     label = glue::glue("{desc}_{item}"), 
-    `Mean (SD)` = glue::glue("{mean} ({sd})"), 
+    Median = glue::glue("{median}"), 
     Range = glue::glue("{min} -- {max}")) %>% 
-  select(label, desc, Metric, Min. = min, Max = max, `Mean (SD)`, avg = mean, 
+  select(label, desc, Metric, Min. = min, Max = max, Median, avg = mean, 
          sd, Range) %>% 
@@
   rename("\\bf{Team characteristics}" = desc, "  " = Metric, `\\bf{Range}` = val1, 
-    `\\bf{Mean (SD)}` = val2) %>% 
+    `\\bf{Median}` = val2) %>% 
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 7) %>%
+    `\\bf{Median}` = " ", .before = 7) %>%
   add_row(`\\bf{Team characteristics}` = "\\bf{Acoustic analyses}", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 8) %>%
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 8) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ",  .before = 15) %>%
+    `\\bf{Median}` = " ",  .before = 15) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 22) %>%
+    `\\bf{Median}` = " ", .before = 22) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 28) %>%
+    `\\bf{Median}` = " ", .before = 28) %>%
   add_row(`\\bf{Team characteristics}` = "\\bf{Statistical analyses}", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{n}", `\\bf{Mean (SD)}` = "\\bf{\\%}", .before = 29) %>%
+    `\\bf{Range}` = "\\bf{n}", `\\bf{Median}` = "\\bf{\\%}", .before = 29) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ",
-    `\\bf{Mean (SD)}` = " ", .before = 33) %>%
+    `\\bf{Median}` = " ", .before = 33) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", `\\bf{Range}` = " ", 
-    `\\bf{Mean (SD)}` = " ", .before = 38) %>%
+    `\\bf{Median}` = " ", .before = 38) %>%
   add_row(`\\bf{Team characteristics}` = " ", `  ` = " ", 
-    `\\bf{Range}` = "\\bf{Range}", `\\bf{Mean (SD)}` = "\\bf{Mean (SD)}", 
+    `\\bf{Range}` = "\\bf{Range}", `\\bf{Median}` = "\\bf{Median}", 
     .before = 39) %>% 
@@
     label = "descriptives-table") %>% 
-  kable_styling(full_width = F, latex_options = "scale_down") %>% 
+  kable_styling(full_width = F, font_size = 8, latex_options = "scale_down") %>% 
   add_indent(c(9, 16, 23, 30, 34, 40)) %>% 

### 2022-11-05 RR_manuscript/Draft_RR.tex
fix model_desc medians (see line 1046(old) or 1053(new))

@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 4 models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
  &  & \bf{Range} & \bf{Median}\\
-\hspace{1em}N & Models & 1 -- 16 & 4\\
+\hspace{1em}N & Models & 1 -- 16 & 3\\
  & Predictors & 1 -- 5 & 2\\
@@
 \hspace{1em} & \hspace{1em}Intercept & \hspace{1em}1 -- 10 & \hspace{1em}2\\
-\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}1\\
+\hspace{1em} & \hspace{1em}Slope & \hspace{1em}0 -- 4 & \hspace{1em}0\\
 \bottomrule

### 2022-11-05 RR_manuscript/Draft_RR.Rmd

@@
     max_models = max(max_n_models), 
+    median_models = median(max_n_models), 
     n_models = sum(max_n_models)
@@
     max_predictor = max(n_predictors, na.rm = TRUE), 
+    median_predictor = median(n_predictors, na.rm = TRUE), 
     n_predictor = sum(n_predictors, na.rm = TRUE)
@@
     max_prating = max(phon_rating, na.rm = TRUE),
+    median_prating = median(phon_rating, na.rm = TRUE),
     n_prating = sum(phon_rating, na.rm = TRUE),
@@
     max_srating = max(stat_rating, na.rm = TRUE), 
+    median_srating = median(stat_rating, na.rm = TRUE), 
     n_srating = sum(stat_rating, na.rm = TRUE)
@@
     label = glue::glue("{desc}_{item}"), 
-    Median = glue::glue("{mean}"), 
+    Median = glue::glue("{median}"), 
     Range = glue::glue("{min} -- {max}")) %>% 

### 2022-11-05 scripts/r/09_credit_taxonomy.Rmd

@@
 # Vector of formated contributor roles
-contributor_roles <- c(
+contributor_role <- c(
     "Conceptualization", "Data curation", "Formal Analysis",
@@
   mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas", 
-                            "Simon Roessig", "Michael Franke")) %>% 
+                            "Simon Roessig", "Michael Franke"), 
+    contributor_roles = str_replace_all(contributor_roles, "_", " "), 
+    contributor_roles = str_replace_all(contributor_roles, "ting ", "ting - "), 
+    contributor_roles = str_to_title(contributor_roles)
+    ) %>% 
   ggplot() +
@@
     scale_x_discrete(position = "top") + 
-    scale_y_discrete(limits = rev, labels = rev(contributor_roles)) + 
+    scale_y_discrete(limits = rev) + 
     scale_alpha_continuous(range = c(0.05, 1)) +
@@
   filter(is_initiating == 0) %>% 
+   mutate(
+    contributor_roles = str_replace_all(contributor_roles, "_", " "), 
+    contributor_roles = str_replace_all(contributor_roles, "ting ", "ting - "), 
+    contributor_roles = str_to_title(contributor_roles)
+    ) %>% 
   ggplot() +
@@
     geom_point(size = 1.75, pch = 18, show.legend = F) +
-    scale_x_discrete(labels = contributor_roles) + 
     scale_alpha_continuous(range = c(0.05, 1)) +

### 2022-11-05 RR_manuscript/Draft_RR.Rmd
fixes #270

@@
 In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
-A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials.
+A complete summary of all the analyses from the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` submitting teams is available in the supplementary materials at <https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf>.
 

### 2022-11-05 RR_manuscript/Draft_RR.tex
fixes #270

@@
 In what follows, we describe the characteristics of those teams whose analyses were included in the meta-analytic model.
-A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials.
+A complete summary of all the analyses from the 46 submitting teams is available in the supplementary materials at \url{https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf}.
 

### 2022-11-06 scripts/r/09_credit_taxonomy.Rmd
download csv and reknit with corrected sheet

@@
 library("googlesheets4")
+library("googledrive")
 library("xml2")
@@
 
+# give gargle permission
+drive_auth(email = TRUE)
+
+# Locate file, check ID
+drive_find(n_max = 5, type = "spreadsheet")
+
+# Old sheet
+#all_data_temp <- read_sheet("1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA") %>% 
+#  janitor::clean_names()
+
+# New sheet
 all_data_temp <- read_sheet("1lXmubF42sTCoOaECXGzo20GCFxX51MWFOKhX8euNtuA") %>% 
@@
 # Load data
-all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")
+#all_data_temp <- read_csv("data/CRediT/MSA_tenzing_contribution.csv")
+all_data_temp <- 
+  read_csv("data/CRediT/MSA_tenzing_contribution-corrected_contributions.csv") %>% 
+  janitor::clean_names()
 

### 2022-11-06 scripts/r/09_credit_taxonomy.Rmd
update fig with author names

@@
   mutate(middle_name = replace_na(middle_name, ""),
-    is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
+    is_initiating = if_else(surname %in% initiating_authors, 1, 0), 
+    initials = glue::glue("{str_sub(firstname, 1, 1)}{str_sub(middle_name, 1, 1)}{str_sub(surname, 1, 1)}")) %>% 
   unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
@@
 cr_prep <- contributors %>% 
-  select(name:writing_review_editing, is_initiating) %>% 
+  select(name:writing_review_editing, is_initiating, initials) %>% 
   pivot_longer(
-    cols = -c("name", "is_initiating"), 
+    cols = -c("name", "is_initiating", "initials"), 
     names_to = "contributor_roles", 
@@
   ungroup() %>% 
-  mutate(initials = gsub('\\b(\\pL)\\pL{2,}|.','\\U\\1', name, perl = TRUE), 
-    contributor_roles = fct_rev(contributor_roles))
+  mutate(contributor_roles = fct_rev(contributor_roles))
 
@@
   ggplot() +
-  aes(y = initials, x = contributor_roles, alpha = val) +
+  aes(y = name, x = contributor_roles, alpha = val) +
     geom_point(size = 1.75, pch = 18, show.legend = F) +

### 2022-11-06 scripts/r/09_credit_taxonomy.Rmd
move separate plot for initiators
separate plots for initiators, analysts, and all

@@
 
+ggsave("figs/credit-taxonomy-initiators.png", width = 7, height = 5)
+
 ```
@@
     scale_alpha_continuous(range = c(0.05, 1)) +
+    scale_y_discrete(limits = rev) + 
     labs(x = NULL, y = "Analysts",
@@
 
-ggsave("figs/credit-taxonomy.png", width = 14, height = 10)
+ggsave("figs/credit-taxonomy-analysts.png", width = 14, height = 10)
+```
+
+```{r}
+#| label: contributor-roles-plot-all
+#| out.width: 100%
+#| fig.height: 11
+
+cr_prep %>% 
+   mutate(
+    name = fct_reorder(name, is_initiating), 
+    contributor_roles = str_replace_all(contributor_roles, "_", " "), 
+    contributor_roles = str_replace_all(contributor_roles, "ting ", "ting - "), 
+    contributor_roles = str_to_title(contributor_roles)
+    ) %>% 
+  ggplot() +
+  aes(y = name, x = contributor_roles, alpha = val) +
+    geom_point(size = 1.75, pch = 18, show.legend = F) + 
+    scale_y_discrete(limits = rev) + 
+    scale_alpha_continuous(range = c(0.05, 1)) +
+    labs(x = NULL, y = "Contributors",
+         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
+    theme_light(base_size = 12, base_family = "Times") +
+    theme(
+      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
+        size = rel(0.6)), 
+      axis.text.y = element_text(size = rel(0.5))
+    )
+
+ggsave("figs/credit-taxonomy-all.png", width = 14, height = 10)
 ```

### 2022-11-07 scripts/r/09_credit_taxonomy.Rmd

--- 2022-11-06 scripts/r/09_credit_taxonomy.Rmd
@@
 # Create vector of surnames of initiating authors
-initiating_authors <- c("Coretta", "Casillas", "Roessig", "Franke", "Roettger")
+initiating_authors <- c("Coretta", "Casillas", "Roettger")
 
@@
   mutate(middle_name = replace_na(middle_name, ""),
-    is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
-  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
+    is_initiating = if_else(surname %in% initiating_authors, 1, 0), 
+    initials = glue::glue("{str_sub(firstname, 1, 1)}{str_sub(middle_name, 1, 1)}{str_sub(surname, 1, 1)}")) %>% 
+  unite(name, c("firstname", "middle_name", "surname"), sep = " ", remove = F) %>% 
   mutate(name = str_replace_all(name, "  ", " ")) %>% 
@@
 cr_prep <- contributors %>% 
-  select(name:writing_review_editing, is_initiating) %>% 
+  select(name, surname, conceptualization:writing_review_editing, is_initiating, initials) %>% 
   pivot_longer(
-    cols = -c("name", "is_initiating"), 
+    cols = -c("name", "surname", "is_initiating", "initials"), 
     names_to = "contributor_roles", 
@@
   filter(is_initiating == 1) %>% 
-  mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas", 
-                            "Simon Roessig", "Michael Franke"), 
+  mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas"), 
     contributor_roles = str_replace_all(contributor_roles, "_", " "), 
@@
   filter(is_initiating == 0) %>% 
-   mutate(
+  arrange(surname) %>% 
+  group_by(contributor_roles) %>% 
+  mutate(order = seq_along(name), 
+    name = fct_reorder(name, order), 
     contributor_roles = str_replace_all(contributor_roles, "_", " "), 
@@
   ggplot() +
-  aes(y = initials, x = contributor_roles, alpha = val) +
+  aes(y = name, x = contributor_roles, alpha = val) +
     geom_point(size = 1.75, pch = 18, show.legend = F) +
     scale_alpha_continuous(range = c(0.05, 1)) +
+    scale_y_discrete(limits = rev) + 
     labs(x = NULL, y = "Analysts",
@@
 
-ggsave("figs/credit-taxonomy.png", width = 14, height = 10)
+ggsave("figs/credit-taxonomy-analysts.png", width = 14, height = 10)
+```
+
+```{r}
+#| label: contributor-roles-plot-all
+#| out.width: 100%
+#| fig.height: 11
+
+cr_prep %>% 
+  arrange(surname) %>% 
+  group_by(contributor_roles) %>% 
+  mutate(order = seq_along(name), 
+    name = fct_reorder(name, order), 
+    contributor_roles = str_replace_all(contributor_roles, "_", " "), 
+    contributor_roles = str_replace_all(contributor_roles, "ting ", "ting - "), 
+    contributor_roles = str_to_title(contributor_roles)
+    ) %>% 
+  ggplot() +
+  aes(y = name, x = contributor_roles, alpha = val) +
+    geom_point(size = 1.75, pch = 18, show.legend = F) + 
+    scale_y_discrete(limits = rev) + 
+    scale_alpha_continuous(range = c(0.05, 1)) +
+    labs(x = NULL, y = "Contributors",
+         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
+    theme_light(base_size = 12, base_family = "Times") +
+    theme(
+      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
+      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
+      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
+      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
+        size = rel(0.6)), 
+      axis.text.y = element_text(size = rel(0.5))
+    )
+
+ggsave("figs/credit-taxonomy-all.png", width = 14, height = 10)
 ```

### 2022-11-07 scripts/r/09_credit_taxonomy.Rmd
update with new csv, add code to clip author, affiliations

@@
 initiating_authors <- c("Coretta", "Casillas", "Roettger")
+extras <- c("Roessig", "Franke")
 
@@
 
+# Subset initiating authors
+others <- all_data_temp %>% 
+  filter(surname %in% extras) %>% 
+  mutate(is_initiating = 1.5)
+
 # Subset analysts
 analysts <- all_data_temp %>% 
-  filter(!(surname %in% initiating_authors)) %>% 
+  filter(!(surname %in% c(initiating_authors, extras))) %>% 
   mutate(is_initiating = 0) %>% 
@@
 # Combine dfs in correct order
-contributors <- bind_rows(initiators, analysts) %>% 
+contributors <- bind_rows(initiators, others, analysts) %>% 
   mutate(middle_name = replace_na(middle_name, ""),
-    is_initiating = if_else(surname %in% initiating_authors, 1, 0), 
     initials = glue::glue("{str_sub(firstname, 1, 1)}{str_sub(middle_name, 1, 1)}{str_sub(surname, 1, 1)}")) %>% 
@@
 affiliations <- contributors %>% 
-  count(primary_affiliation) %>% 
+  count(primary_affiliation_university) %>% 
   arrange(n)
@@
 affiliations %>% 
-  mutate(lab_truc = str_sub(primary_affiliation, 1, 30),
+  mutate(lab_truc = str_sub(primary_affiliation_university, 1, 30),
     lab_truc = fct_reorder(lab_truc, n, min)) %>% 
@@
 There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
-`r filter(affiliations, is.na(primary_affiliation)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
+`r filter(affiliations, is.na(primary_affiliation_university)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
 
@@
 cr_prep %>% 
-  filter(is_initiating == 0) %>% 
+  filter(is_initiating != 1) %>% 
   arrange(surname) %>% 
@@
   clipr::write_clip()
+
+contributors %>% 
+  select(name, primary_affiliation_university) %>% 
+  transmute(
+    name, 
+    name_man = glue::glue("- name: {name}"), 
+    num_man = glue::glue("- num: {1:nrow(.) + 1}")
+  ) %>% 
+  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
+  pull(print) %>% 
+  clipr::write_clip()
+
+contributors %>% 
+  select(name, primary_affiliation_university, primary_affiliation_department) %>% 
+  transmute(
+    name, 
+    num_man = glue::glue("- num: {1:nrow(.) + 1}"), 
+    print = glue::glue("- org: {primary_affiliation_department}, {primary_affiliation_university}"), 
+  ) %>% 
+  pivot_longer(cols = -name, names_to = "col", values_to = "print") %>% 
+  pull(print) %>% 
+  clipr::write_clip() 
 ```

### 2022-11-12 docs/icphs2023/main.tex
add icphs 2023 template

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  a4paper,
  11pt,
  twocolumn]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{48,48,48}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{\textbf{#1}}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.87,0.87,0.75}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.86,0.86,0.80}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.76,0.75,0.62}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.75,0.75,0.82}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.94,0.94,0.82}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{\textbf{#1}}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
%------------------------------------------------------------------------------%
% PAPER TEMPLATE FOR ICPHS 2023 Prague                                         %
%                                                                              %
% Original template downloaded from:                                           %
% http://www.icphs2023.org/call-for-papers/                                    %
%                                                                              %
% Reformatted to work with Rmarkdown and R by:                                 %
% Joseph V. Casillas | Rutgers Univesity |11/11/2022                           %
%                                                                              %
% Available for download at:                                                   %
% https://github.com/jvcasillas/icphs2023_rmd_template                         %
%------------------------------------------------------------------------------%

% Packages
\usepackage{./includes/tex/icphs2023}
\usepackage{metalogo} 
\usepackage{epstopdf}
\usepackage{tipa}

% Links and urls must be black
%\hypersetup{urlcolor=black, citecolor=black, linkcolor=black}

% Packages removed from icphs2023.sty because of conflicts
% They have been added to the .Rmd yaml front matter
% \usepackage[latin1]{inputenc}
% \usepackage[T1]{fontenc}
% \usepackage[leqno,fleqn]{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{\vspace{-2.5em}}

\begin{document}

\title{Paper template for {ICPhS} 2023 Prague}
\author{Please write XXX instead of the name(s) of the author(s)}
\organization{Please write XXX instead of the affiliation(s)}
\email{please write XXX instead of the email address(es)}

\maketitle

\begin{abstract}
This is the layout specification and template definition for the papers of ICPhS XX (the 20th International Congress of Phonetic Sciences, which will be held in Prague, Czech Republic, August 7-11, 2023). 
This template is a revised version of the one used for Melbourne ICPhS XIX in 2019, originally generated from the template for Speech Prosody 2006 in Dresden.

The abstract may consist of more than one paragraph but must be kept within a 150-word limit. 
This abstract will be printed in the abstract booklet to be given out at the conference.
\end{abstract}

\keywords{There is space for up to five self-selected keywords (maximally two 
lines).}

\section{Introduction}

The following rules apply to all submitted papers:

\begin{itemize}
  \item they must be written in English
  \item they must not contain the name(s) of the author(s) (for
anonymous review)
  \item the maximum is four pages for Congress papers, plus up to one additional page of references. Papers for Plenary lectures can be longer
  \item they must be submitted in PDF format (cf.\ Section~4)
  \item the paper submission will occur via a web interface
\end{itemize}

This paper template can be found on the conference website. If there are
special questions or wishes regarding paper preparation and submission
for ICPhS 2023, correspondence should be addressed to
\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}}.
Information for full paper submission will be available on the web at
\url{https://www.icphs2023.org/}.

\section{Page layout and style}

The page layout should conform to the following rules. By far the
easiest way to meet these requirements is to use the supplied templates
and check details against this example file. If for some reason you
cannot use the template, please follow these rules as carefully as
possible, or contact the editors at
\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}} for
further instructions.

\subsection{Basic layout features}

\begin{itemize}
\item The layout is appropriate for A4 format.
\item Two columns are used
  except for the title part and possibly for large figures that need a
  full page width.
\item Left margin is 20 mm. Right margin will depend on
  the size of the paper. Column width is 80 mm.
\item Spacing between
  columns is 10 mm.
\item Top margin 25 mm (except first page which has 30
  mm to the title top). Bottom margin will depend on the size of the
  paper.
\item Text height (without headers and footers) is a maximum of
  235 mm.  Headers and footers should be left empty
\item Check indentations
  and spacings by comparing with this example file.
\end{itemize}

\subsubsection{Headings}

Section headings are centered in boldface with capitalized letters.
Sub-headings start at the left margin in the column with the first
letter capitalized and the rest of the heading in lower case.
Sub-sub-headings appear like sub-headings, except that they are in
italics and not boldface. See examples in this file. No more than 3
levels of headings should be used. Empty lines should be left above and
below each section heading.

\subsection{Text font}

Times or Times New Roman font is used for the main text. Recommended
font size is 11 points. Other font types may be used if needed for
special purposes. If using any non-Unicode fonts, these must be embedded
in the final PDF file.

The \LaTeX{} template can be used either with plain \LaTeX{} or
\XeLaTeX.

\subsection{Figures}

All figures should be centered on the column (or page, if the figure
spans both columns). Figure captions should follow each figure and have
the format given in Fig. \ref{fig:vowels}.

Figures should preferably be line drawings. If they contain grey shades
or colours, it should be checked that they print well on a high-quality
noncolour laser printer.

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=6cm]{./includes/figures/ipa.eps}
\caption{The vowel chart used in the International Phonetic
Alphabet (IPA).}\label{fig:vowels}
\end{center}
\end{figure}

\subsection{Tables}

An example of a table is shown as
Table\textasciitilde{}\ref{tab:decibel}. Somewhat different styles are
allowed according to the type and purpose of the table. Colour should
not be used, but grey shading is allowed. There should be a margin of
6\textasciitilde points (pt) above and below the table.

The caption text may be above or below the table, but this should be
consistent throughout the submission. Left and right indentation of the
caption should be 0.5\textasciitilde cm.

\begin{table}[!ht]
  \begin{center}
  \begin{tabular}{|c|c|}
  \hline
  \rowcolor[gray]{.75}
  ratio    & Decibels\\
  \hline
  $1/1$    & $0$\\
  $2/1$    & $6$\\
  $3.16$   & $10$\\
  $1/10$   & $-20$\\
  $10/1$   & $20$\\
  $100/1$  & $40$\\
  $1000/1$ & $60$\\
  \hline
  \end{tabular}
  \caption{This is an example of a table showing Decibel (dB)
  ratios.}\label{tab:decibel}
  \end{center}
\end{table}

\subsection{Equations}

Equations should be placed on separate lines and numbered. An example of
an equation is \begin{equation}\label{eq:tzero}
T_0 = \frac{1}{f_0}.
\end{equation} Numbers of equations can be on the right or on the left
margin of the text column.

\subsection{Examples}

Examples from other languages can either be presented in the body text,
or, if referred to elsewhere or particularly long and complex, can be
put on a separate, numbered line, as should be done for equations.

\subsection{Phonetic fonts}

We recommend that you use the \textsc{tipa} package for IPA phonetic
symbols. For information about how to access Unicode fonts in the Word
template, see \cite{IPA-SIL} or \cite{IPA-KEYBOARD}. The font you use
must be embedded. Please remember to check this, e.g.~by inspecting the
``Document Properties --- Fonts'\,' in Acrobat Reader.

\subsection{Page numbering}

Page numbers will be added electronically to the document later.
\textit{Please do not add page numbers and please do not insert
any footers or headers!}

\subsection{References}

Please use just the reference number in square brackets. Formulations
with author names like ``\ldots~as Ladefoged \cite{Ladefoged:2003}
showed that \ldots'' are acceptable but not ``as shown in {[}Ladefoged,
3{]}'' or ``as shown in (Ladefoged {[}3{]})''.

References are to be numbered in alphabetical order. Please double-check
the final version of your paper with regard to the correct
correspondence of references to their numbers.

\subsection{Hyperlinks}

Links to URLs or email addresses should be formatted as normal text,
\textit{not} as hyperlinks and not blue or underlined etc. Usually
hyperlinks to web pages are listed in the references section. If
required, line breaks can be placed within URLs after slashes or dashes
(cf.\textasciitilde{}\cite{IPA-SIL,IPA-KEYBOARD}), but doublecheck that
no hyphens are inserted.

\subsection{Footnotes and endnotes}

If footnotes cannot be avoided they should appear as
endnotes.\footnote{This footnote appears here as an endnote.}

\section{Multimedia files}

Multimedia data that are part of the paper are to be embedded in the
submitted PDF; they cannot be submitted as supplementary data. Any
images are to be included in the paper as Figures (see Section 2.3
above). It is the authors' responsibility to check image quality ahead
of submission. Audio examples are to be embedded within the PDF. To do
this, authors can generate the PDF, and then embed the audio files using
Adobe Acrobat Professional, or other software that offers the same
outcome, so that the audio is included in the PDF. The presence of audio
data should be identified in the text.

We encourage authors to illustrate video data using still photographs
from the video, and to include them as figures in the PDF. We cannot
accept embedded video files, but authors are welcome to refer readers to
a URL on the internet where these can be viewed.

\section{PDF details}

PDF files submitted must comply with the following requirements:

\begin{enumerate}
\item all special fonts and symbols must be embedded in the PDF
  file so that correct rendering of the PDF does not depend on the
  fonts installed on the viewer's computer
\item there must be no
  password protection on the PDF file, i.e. PDF files must not be
  protected by PDF security in any way, i.e. content extraction,
  document assembly, high resolution printing etc. must not be
  forbidden
\item PDF files should not contain any colours, hyperlinks,
  multimedia or 3D content, and no JavaScript or forms
\item PDF files
  should be no larger than 5 MB.
\end{enumerate}

\section{Anonymity}

In ICPhS 2023 submissions, an anonymous reviewing process will be used.
This means that for the first submission the name(s) of the author(s)
and their affiliation(s) \emph{must not} be mentioned. In addition,
please refrain from using acknowledgements. Please also try to make your
own previous research as anonymous as possible. As an example: do not
write ``In our previous study \cite{Stevens:1999} we could show\ldots''
but ``As shown in \cite{Stevens:1999}\ldots''. Or refer to your own
published or otherwise widely known work, and to that of the other
authors, in the ``Julius Caesar style'', i.e.~in the third person (for
example: his work, her work, their work). Reference as ``anonymous''
only work that you or the other authors have submitted for publication,
but which has not yet been published, e.g.~\cite{Anonymous:submitted}.

Please make sure that no author details appear in the Document
Properties of the PDF file.
\emph{For the revised paper submission author details are of course needed}.
Acknowledgements and references to one's own work are possible as usual.

\section{Format of references}

References are formatted using the IEEE standard (available in various
reference management systems like Zotero or Mendeley). If you do not use
a reference management system, please use the examples provided for
monographs \cite{Fant:1960}, contributions to volumes
\cite{Stevens:1999}, journal articles \cite{Beattie/etal:1982}, articles
in conference proceedings \cite{Ladefoged:2003}. Abbreviations of
well-known conferences and journals are possible
\cite{Peterson/Barney:1952}. Software tools \cite{Boril/Skarnitzl:2016}
are referenced according to authors' instructions.

\section{R scripts}

You can use knitr code chunks like in any .Rmd document:

\begin{Shaded}
\begin{Highlighting}[]
\DecValTok{2} \SpecialCharTok{+} \DecValTok{2}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 4
\end{verbatim}

This includes inline code: 2 + 2 = 4.

R scripts can be loaded as well:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"./includes/scripts/analysis.R"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

Which means you have access to any objects assigned in the script, like
Figure \ref{fig:ex_plot}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{cars\_plot}
\end{Highlighting}
\end{Shaded}

\begin{figure}[!h]
\caption{This is a figure caption.}\label{fig:ex_plot}

\begin{center}\includegraphics{main_files/figure-latex/ex_plot-1} \end{center}

\end{figure}

\bibliographystyle{./includes/bib/IEEEtran.bst}
\bibliography{./includes/bib/icphs2023.bib}

\theendnotes

\end{document}

### 2022-11-12 docs/icphs2023/includes/scripts/analysis.R

@@ -1,0 +1,9 @@
+
+library(tidyverse)
+
+
+cars_plot <- mtcars %>% 
+  ggplot(., aes(x = drat, y = mpg)) + 
+    geom_point() + 
+    geom_smooth(method = lm, formula = "y ~ x") + 
+    theme_test(base_size = 11, base_family = "Times")

### 2022-11-12 docs/icphs2023/main.Rmd

--- 2022-11-12 docs/icphs2023/main.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  a4paper,
-  11pt,
-  twocolumn]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{48,48,48}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{\textbf{#1}}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.87,0.87,0.75}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.86,0.86,0.80}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.76,0.75,0.62}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.75,0.75,0.82}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.94,0.94,0.82}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{\textbf{#1}}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-%------------------------------------------------------------------------------%
-% PAPER TEMPLATE FOR ICPHS 2023 Prague                                         %
-%                                                                              %
-% Original template downloaded from:                                           %
-% http://www.icphs2023.org/call-for-papers/                                    %
-%                                                                              %
-% Reformatted to work with Rmarkdown and R by:                                 %
-% Joseph V. Casillas | Rutgers Univesity |11/11/2022                           %
-%                                                                              %
-% Available for download at:                                                   %
-% https://github.com/jvcasillas/icphs2023_rmd_template                         %
-%------------------------------------------------------------------------------%
+---
+documentclass: article
+classoption: [a4paper,11pt,twocolumn]
+subparagraph: yes
+header-includes:
+  - \usepackage[utf8]{inputenc}
+  - \usepackage[T1]{fontenc}
+  #- \usepackage[leqno,fleqn]{amsmath}
+output:
+  pdf_document:
+    highlight: zenburn
+    includes:
+      before_body: includes/tex/doc_prefix.tex
+      in_header: includes/tex/header.tex
+    keep_tex: yes
+    number_sections: yes
+bibliography: includes/bib/icphs2023.bib
+---
 
-% Packages
-\usepackage{./includes/tex/icphs2023}
-\usepackage{metalogo} 
-\usepackage{epstopdf}
-\usepackage{tipa}
-
-% Links and urls must be black
-%\hypersetup{urlcolor=black, citecolor=black, linkcolor=black}
-
-% Packages removed from icphs2023.sty because of conflicts
-% They have been added to the .Rmd yaml front matter
-% \usepackage[latin1]{inputenc}
-% \usepackage[T1]{fontenc}
-% \usepackage[leqno,fleqn]{amsmath}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-
-\author{}
-\date{\vspace{-2.5em}}
-
-\begin{document}
-
-\title{Paper template for {ICPhS} 2023 Prague}
-\author{Please write XXX instead of the name(s) of the author(s)}
-\organization{Please write XXX instead of the affiliation(s)}
-\email{please write XXX instead of the email address(es)}
-
-\maketitle
-
-\begin{abstract}
-This is the layout specification and template definition for the papers of ICPhS XX (the 20th International Congress of Phonetic Sciences, which will be held in Prague, Czech Republic, August 7-11, 2023).
-This template is a revised version of the one used for Melbourne ICPhS XIX in 2019, originally generated from the template for Speech Prosody 2006 in Dresden.
-
-The abstract may consist of more than one paragraph but must be kept within a 150-word limit. 
-This abstract will be printed in the abstract booklet to be given out at the conference.
-\end{abstract}
-
-\keywords{There is space for up to five self-selected keywords (maximally two 
-lines).}
+```{r, 'setup', include=FALSE}
+library(knitr)
+f <- function(x, options) {
+  lab <- paste0(options$fig.lp, options$label)
+  paste(
+        "\\begin{figure}[!h]\n\\caption{", options$fig.cap.top, "}\\label{", lab,"}\n", 
+        hook_plot_tex(x, options), 
+        "\\end{figure}\n\n", sep = "")
+}
+knit_hooks$set(plot = f)
+```
 
@@
 \end{itemize}
-
-This paper template can be found on the conference website. If there are
-special questions or wishes regarding paper preparation and submission
-for ICPhS 2023, correspondence should be addressed to
-\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}}.
-Information for full paper submission will be available on the web at
-\url{https://www.icphs2023.org/}.
+This paper template can be found on the conference website. If there
+are special questions or wishes regarding paper preparation and
+submission for ICPhS 2023, correspondence should be addressed to
+icphs2023@guarant.cz. Information for full paper submission will be
+available on the web at \url{https://www.icphs2023.org/}.
 
@@
 
-The page layout should conform to the following rules. By far the
-easiest way to meet these requirements is to use the supplied templates
-and check details against this example file. If for some reason you
-cannot use the template, please follow these rules as carefully as
-possible, or contact the editors at
-\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}} for
-further instructions.
+The page layout should conform to the following rules.
+By far the easiest way to meet these requirements is to use the supplied templates and check details against this example file.
+If for some reason you cannot use the template, please follow these rules as carefully as possible, or contact the editors at icphs2023@guarant.cz for further instructions.
 
@@
 Section headings are centered in boldface with capitalized letters.
-Sub-headings start at the left margin in the column with the first
-letter capitalized and the rest of the heading in lower case.
-Sub-sub-headings appear like sub-headings, except that they are in
-italics and not boldface. See examples in this file. No more than 3
-levels of headings should be used. Empty lines should be left above and
-below each section heading.
+Sub-headings start at the left margin in the column with the first letter capitalized and the rest of the heading in lower case.
+Sub-sub-headings appear like sub-headings, except that they are in italics and not boldface.
+See examples in this file.
+No more than 3 levels of headings should be used.
+Empty lines should be left above and below each section heading.
 
@@
 
-Times or Times New Roman font is used for the main text. Recommended
-font size is 11 points. Other font types may be used if needed for
-special purposes. If using any non-Unicode fonts, these must be embedded
-in the final PDF file.
+Times or Times New Roman font is used for the main text.
+Recommended font size is 11 points.
+Other font types may be used if needed for special purposes.
+If using any non-Unicode fonts, these must be embedded in the final PDF file.
 
-The \LaTeX{} template can be used either with plain \LaTeX{} or
-\XeLaTeX.
+The \LaTeX{} template can be used either with plain \LaTeX{} or \XeLaTeX.
 
@@
 All figures should be centered on the column (or page, if the figure
-spans both columns). Figure captions should follow each figure and have
-the format given in Fig. \ref{fig:vowels}.
+spans both columns). Figure captions should follow each figure and
+have the format given in Fig. \ref{fig:vowels}.
 
-Figures should preferably be line drawings. If they contain grey shades
-or colours, it should be checked that they print well on a high-quality
-noncolour laser printer.
+Figures should preferably be line drawings. If they contain grey
+shades or colours, it should be checked that they print well on a
+high-quality noncolour laser printer.
 
@@
 
-An example of a table is shown as
-Table\textasciitilde{}\ref{tab:decibel}. Somewhat different styles are
-allowed according to the type and purpose of the table. Colour should
-not be used, but grey shading is allowed. There should be a margin of
-6\textasciitilde points (pt) above and below the table.
+An example of a table is shown as Table~\ref{tab:decibel}.  Somewhat
+different styles are allowed according to the type and purpose of the
+table. Colour should not be used, but grey shading is allowed. There
+should be a margin of 6~points (pt) above and below the table.
 
 The caption text may be above or below the table, but this should be
-consistent throughout the submission. Left and right indentation of the
-caption should be 0.5\textasciitilde cm.
+consistent throughout the submission. Left and right indentation of
+the caption should be 0.5~cm.
 
@@
 
-Equations should be placed on separate lines and numbered. An example of
-an equation is \begin{equation}\label{eq:tzero}
+Equations should be placed on separate lines and numbered. An example
+of an equation is
+\begin{equation}\label{eq:tzero}
 T_0 = \frac{1}{f_0}.
-\end{equation} Numbers of equations can be on the right or on the left
-margin of the text column.
+\end{equation}
+Numbers of equations can be on the right or on the left margin of the
+text column.
 
@@
 
-Examples from other languages can either be presented in the body text,
-or, if referred to elsewhere or particularly long and complex, can be
-put on a separate, numbered line, as should be done for equations.
+Examples from other languages can either be presented in the body text, or, if referred to elsewhere or particularly long and complex, can be put on a separate, numbered line, as should be done for equations.
 
@@
 
-We recommend that you use the \textsc{tipa} package for IPA phonetic
-symbols. For information about how to access Unicode fonts in the Word
-template, see \cite{IPA-SIL} or \cite{IPA-KEYBOARD}. The font you use
-must be embedded. Please remember to check this, e.g.~by inspecting the
-``Document Properties --- Fonts'\,' in Acrobat Reader.
+We recommend that you use the \textsc{tipa} package for IPA phonetic symbols.
+For information about how to access Unicode fonts in the Word template, see \cite{IPA-SIL} or \cite{IPA-KEYBOARD}.
+The font you use must be embedded.
+Please remember to check this,  e.g.
+by inspecting the ``Document Properties --- Fonts'' in Acrobat Reader.
 
@@
 
-Page numbers will be added electronically to the document later.
-\textit{Please do not add page numbers and please do not insert
+Page numbers will be added electronically to the document
+later. \textit{Please do not add page numbers and please do not insert
 any footers or headers!}
@@
 Please use just the reference number in square brackets. Formulations
-with author names like ``\ldots~as Ladefoged \cite{Ladefoged:2003}
-showed that \ldots'' are acceptable but not ``as shown in {[}Ladefoged,
-3{]}'' or ``as shown in (Ladefoged {[}3{]})''.
+with author names like "\ldots\ as Ladefoged \cite{Ladefoged:2003}
+showed that \ldots" are acceptable but not "as shown in [Ladefoged,
+3]" or "as shown in (Ladefoged [3])".
 
-References are to be numbered in alphabetical order. Please double-check
-the final version of your paper with regard to the correct
-correspondence of references to their numbers.
+References are to be numbered in alphabetical order. Please
+double-check the final version of your paper with regard to the
+correct correspondence of references to their numbers.
 
@@
 hyperlinks to web pages are listed in the references section. If
-required, line breaks can be placed within URLs after slashes or dashes
-(cf.\textasciitilde{}\cite{IPA-SIL,IPA-KEYBOARD}), but doublecheck that
-no hyphens are inserted.
+required, line breaks can be placed within URLs after slashes or
+dashes (cf.~\cite{IPA-SIL,IPA-KEYBOARD}), but doublecheck that no hyphens
+are inserted.
 
@@
 
-Multimedia data that are part of the paper are to be embedded in the
-submitted PDF; they cannot be submitted as supplementary data. Any
-images are to be included in the paper as Figures (see Section 2.3
-above). It is the authors' responsibility to check image quality ahead
-of submission. Audio examples are to be embedded within the PDF. To do
-this, authors can generate the PDF, and then embed the audio files using
-Adobe Acrobat Professional, or other software that offers the same
-outcome, so that the audio is included in the PDF. The presence of audio
-data should be identified in the text.
+Multimedia data that are part of the paper are to be embedded in the submitted PDF; they cannot be submitted as supplementary data.
+Any images are to be included in the paper as Figures (see Section 2.3 above).
+It is the authors' responsibility to check image quality ahead of submission.
+Audio examples are to be embedded within the PDF.
+To do this, authors can generate the PDF, and then embed the audio files using Adobe Acrobat Professional, or other software that offers the same outcome, so that the audio is included in the PDF.
+The presence of audio data should be identified in the text.
 
-We encourage authors to illustrate video data using still photographs
-from the video, and to include them as figures in the PDF. We cannot
-accept embedded video files, but authors are welcome to refer readers to
-a URL on the internet where these can be viewed.
+We encourage authors to illustrate video data using still photographs from the video, and to include them as figures in the PDF.
+We cannot accept embedded video files, but authors are welcome to refer readers to a URL on the internet where these can be viewed.
 
@@
 
-In ICPhS 2023 submissions, an anonymous reviewing process will be used.
-This means that for the first submission the name(s) of the author(s)
-and their affiliation(s) \emph{must not} be mentioned. In addition,
-please refrain from using acknowledgements. Please also try to make your
-own previous research as anonymous as possible. As an example: do not
-write ``In our previous study \cite{Stevens:1999} we could show\ldots''
-but ``As shown in \cite{Stevens:1999}\ldots''. Or refer to your own
-published or otherwise widely known work, and to that of the other
-authors, in the ``Julius Caesar style'', i.e.~in the third person (for
-example: his work, her work, their work). Reference as ``anonymous''
-only work that you or the other authors have submitted for publication,
-but which has not yet been published, e.g.~\cite{Anonymous:submitted}.
+In ICPhS 2023 submissions, an anonymous reviewing process will be used. This means that for the first submission the name(s) of the author(s) and
+their affiliation(s) \emph{must not} be mentioned.
+In addition, please refrain from using acknowledgements.
+Please also try to make your own previous research as anonymous as possible.
+As an example: do not write "In our previous study \cite{Stevens:1999} we could show\ldots" but "As shown in \cite{Stevens:1999}\ldots".
+Or refer to your own published or otherwise widely known work, and to that of the other authors, in the "Julius Caesar style", i.e.
+in the third person (for example: his work, her work, their work).
+Reference as "anonymous" only work that you or the other authors have submitted for publication, but which has not yet been published, e.g.
+\cite{Anonymous:submitted}.
 
-Please make sure that no author details appear in the Document
-Properties of the PDF file.
+Please make sure that no author details appear in the Document Properties of the PDF file.
 \emph{For the revised paper submission author details are of course needed}.
@@
 
-References are formatted using the IEEE standard (available in various
-reference management systems like Zotero or Mendeley). If you do not use
-a reference management system, please use the examples provided for
-monographs \cite{Fant:1960}, contributions to volumes
-\cite{Stevens:1999}, journal articles \cite{Beattie/etal:1982}, articles
-in conference proceedings \cite{Ladefoged:2003}. Abbreviations of
-well-known conferences and journals are possible
-\cite{Peterson/Barney:1952}. Software tools \cite{Boril/Skarnitzl:2016}
-are referenced according to authors' instructions.
+References are formatted using the IEEE standard (available in various reference management systems like Zotero or Mendeley).
+If you do not use a reference management system, please use the examples provided for monographs \cite{Fant:1960}, contributions to volumes \cite{Stevens:1999}, journal articles \cite{Beattie/etal:1982}, articles in conference proceedings \cite{Ladefoged:2003}.
+Abbreviations of
+well-known conferences and journals are possible \cite{Peterson/Barney:1952}. Software tools \cite{Boril/Skarnitzl:2016} are referenced according to authors' instructions.
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\DecValTok{2} \SpecialCharTok{+} \DecValTok{2}
-\end{Highlighting}
-\end{Shaded}
+```{r, 'chunk_ex'}
+2 + 2
+```
 
-\begin{verbatim}
-## [1] 4
-\end{verbatim}
-
-This includes inline code: 2 + 2 = 4.
+This includes inline code: 2 + 2 = `r 2 + 2`.
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{source}\NormalTok{(}\StringTok{"./includes/scripts/analysis.R"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
+```{r, 'load_script', echo=TRUE, message=FALSE, warning=FALSE}
+source("./includes/scripts/analysis.R")
+```
 
-Which means you have access to any objects assigned in the script, like
-Figure \ref{fig:ex_plot}:
+Which means you have access to any objects assigned in the script, like Figure 
+\ref{fig:ex_plot}:
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{cars\_plot}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[!h]
-\caption{This is a figure caption.}\label{fig:ex_plot}
-
-\begin{center}\includegraphics{main_files/figure-latex/ex_plot-1} \end{center}
-
-\end{figure}
+```{r, 'ex_plot', fig.align='center', fig.width=2.75, fig.height=1.5, fig.cap.top="This is a figure caption.", fig.pos='h', fig.lp='fig:'} 
+cars_plot
+```
 
@@
 \theendnotes
-
-\end{document}

### 2022-11-15 RR_manuscript/Draft_RR.Rmd
♻️ - add notice about auth affiliations
fix to proportion of "reliable effects"

@@
 
+> Authors' affiliations to be added later.
+
 # Introduction
@@
 `r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 104 submitted models, `r n_effects` were reported to show a statistically reliable effect (`r round(perc_effects,1)`%).
+Of the 170 critical model coefficients, `r n_effects` were claimed to show a statistically reliable effect (`r round(perc_effects,1)`%).
 

### 2022-11-19 RR_manuscript/Draft_RR.Rmd
add author affiliations

--- 2022-11-05 RR_manuscript/Draft_RR.Rmd
@@
 - name: Simon Roessig
+  num: 4
 - name: Michael Franke
+  num: 5
+- name: Byron Ahn
+  num: 6
 - name: Ali H. Al-Hoorie
+  num: 7
 - name: Jalal Al-Tamimi
+  num: 8
 - name: Najd E. Alotaibi
+  num: 9
 - name: Mohammed K. AlShakhori
+  num: 10
 - name: Ruth M. Altmiller
+  num: 11
 - name: Pablo Arantes
+  num: 12
 - name: Angeliki Athanasopoulou
+  num: 13
 - name: Melissa M. Baese-Berk
+  num: 14
 - name: George Bailey
+  num: 15
 - name: Cheman Baira A Sangma
+  num: 16
 - name: Eleonora J. Beier
+  num: 17
 - name: Gabriela M. Benavides
+  num: 18
 - name: Nicole Benker
+  num: 19
 - name: Emelia P. BensonMeyer
+  num: 20
 - name: Nina R. Benway
+  num: 21
 - name: Grant M. Berry
+  num: 22
 - name: Liwen Bing
+  num: 23
 - name: Christina Bjorndahl
+  num: 24
 - name: Mariska Bolyanatz
+  num: 25
 - name: Aaron Braver
+  num: 26
 - name: Violet A. Brown
+  num: 27
 - name: Alicia M. Brown
+  num: 28
 - name: Alejna Brugos
+  num: 29
 - name: Erin M. Buchanan
+  num: 30
 - name: Tanna Butlin
+  num: 31
 - name: Andrés Buxó-Lugo
+  num: 32
 - name: Coline Caillol
+  num: 33
 - name: Francesco Cangemi
+  num: 34
 - name: Christopher Carignan
+  num: 35
 - name: Sita Carraturo
+  num: 36
 - name: Tiphaine Caudrelier
+  num: 37
 - name: Eleanor Chodroff
+  num: 38
 - name: Michelle Cohn
+  num: 39
 - name: Johanna Cronenberg
+  num: 40
 - name: Olivier Crouzet
+  num: 41
 - name: Erica L. Dagar
+  num: 42
 - name: Charlotte Dawson
+  num: 43
 - name: Carissa A. Diantoro
+  num: 44
 - name: Marie Dokovova
-- name: Wood Drake
+  num: 45
+- name: Shiloh Drake
+  num: 46
 - name: Fengting Du
+  num: 47
 - name: Margaux Dubuis
+  num: 48
 - name: Florent Duême
+  num: 49
 - name: Matthew Durward
+  num: 50
 - name: Ander Egurtzegi
+  num: 51
 - name: Mahmoud M. Elsherif
+  num: 52
 - name: Janina Esser
+  num: 53
 - name: Emmanuel Ferragne
+  num: 54
 - name: Fernanda Ferreira
+  num: 55
 - name: Lauren K. Fink
+  num: 56
 - name: Sara Finley
+  num: 57
 - name: Kurtis Foster
+  num: 58
 - name: Paul Foulkes
+  num: 59
 - name: Rosa Franzke
+  num: 60
 - name: Gabriel Frazer-McKee
+  num: 61
 - name: Robert Fromont
+  num: 62
 - name: Christina García
+  num: 63
 - name: Jason Geller
+  num: 64
 - name: Camille L. Grasso
+  num: 65
 - name: Pia Greca
+  num: 66
 - name: Martine Grice
+  num: 67
 - name: Magdalena S. Grose-Hodge
+  num: 68
 - name: Amelia J. Gully
+  num: 69
 - name: Caitlin Halfacre
-- name: Westerbeek Hans
+  num: 70
 - name: Ivy Hauser
+  num: 71
 - name: Jen Hay
+  num: 72
 - name: Robert Haywood
+  num: 73
 - name: Sam Hellmuth
+  num: 74
 - name: Allison I. Hilger
+  num: 75
 - name: Nicole Holliday
+  num: 76
 - name: Damar Hoogland
+  num: 77
 - name: Yaqian Huang
+  num: 78
 - name: Vincent Hughes
+  num: 79
 - name: Ane Icardo Isasa
+  num: 80
 - name: Zlatomira G. Ilchovska
+  num: 81
 - name: Hae-Sung Jeon
+  num: 82
 - name: Jacq Jones
+  num: 83
 - name: Mágat N. Junges
+  num: 84
 - name: Stephanie Kaefer
+  num: 85
 - name: Constantijn Kaland
+  num: 86
 - name: Matthew C. Kelley
+  num: 87
 - name: Niamh E. Kelly
+  num: 88
+- name: Thomas Kettig
+  num: 89
 - name: Ghada Khattab
+  num: 90
+- name: Ruud Koolen
+  num: 91
 - name: Emiel Krahmer
+  num: 92
 - name: Dorota Krajewska
+  num: 93
 - name: Andreas Krug
+  num: 94
 - name: Abhilasha A. Kumar
+  num: 95
 - name: Anna Lander
+  num: 96
 - name: Tomas O. Lentz
+  num: 97
 - name: Wanyin Li
+  num: 98
 - name: Yanyu Li
+  num: 99
 - name: Maria Lialiou
+  num: 100
 - name: Ronaldo M. Lima Jr.
+  num: 101
 - name: Justin J. H. Lo
-- name: Julio César López Otero
+  num: 102
+- name: Julio Cesar Lopez Otero
+  num: 103
 - name: Bradley Mackay
+  num: 104
 - name: Bethany MacLeod
+  num: 105
 - name: Mel Mallard
-- name: Carol-Ann McConnellogue
+  num: 106
+- name: Carol-Ann Mary McConnellogue
+  num: 107
 - name: George Moroz
+  num: 108
 - name: Mridhula Murali
+  num: 109
 - name: Ladislas Nalborczyk
+  num: 110
 - name: Filip Nenadić
+  num: 111
 - name: Jessica Nieder
+  num: 112
 - name: Dušan Nikolić
+  num: 113
 - name: Francisco G. S. Nogueira
+  num: 114
 - name: Heather M. Offerman
+  num: 115
 - name: Elisa Passoni
+  num: 116
 - name: Maud Pélissier
+  num: 117
 - name: Scott J. Perry
+  num: 118
 - name: Alexandra M. Pfiffner
+  num: 119
 - name: Michael Proctor
+  num: 120
 - name: Ryan Rhodes
+  num: 121
 - name: Nicole Rodríguez
+  num: 122
 - name: Elizabeth Roepke
+  num: 123
 - name: Jan P. Röer
-- name: Koolen Ruud
+  num: 124
 - name: Lucia Sbacco
+  num: 125
 - name: Rebecca Scarborough
+  num: 126
 - name: Felix Schaeffler
+  num: 127
 - name: Erik Schleef
+  num: 128
 - name: Dominic Schmitz
+  num: 129
 - name: Alexander Shiryaev
+  num: 130
 - name: Márton Sóskuthy
+  num: 131
 - name: Malin Spaniol
+  num: 132
 - name: Joseph A. Stanley
+  num: 133
 - name: Alyssa Strickler
+  num: 134
 - name: Alessandro Tavano
+  num: 135
 - name: Fabian Tomaschek
+  num: 136
 - name: Benjamin V. Tucker
+  num: 137
 - name: Rory Turnbull
-- name: Kingsley Ugwuanyi
+  num: 138
+- name: Kingsley O. Ugwuanyi
+  num: 139
 - name: Iñigo Urrestarazu-Porta
+  num: 140
 - name: Ruben van de Vijver
+  num: 141
 - name: Kristin J. Van Engen
+  num: 142
 - name: Emiel van Miltenburg
+  num: 143
 - name: Bruce Wang
+  num: 144
 - name: Natasha Warner
+  num: 145
 - name: Simon Wehrle
+  num: 146
+- name: Hans Westerbeek
+  num: 147
 - name: Seth Wiener
+  num: 148
 - name: Stephen Winters
+  num: 149
 - name: Sidney G.-J. Wong
+  num: 150
 - name: Anna Wood
+  num: 151
 - name: Jane Wottawa
+  num: 152
 - name: Chenzi Xu
+  num: 153
 - name: Germán Zárate-Sández
+  num: 154
 - name: Georgia Zellou
+  num: 155
 - name: Cong Zhang
+  num: 156
 - name: Jian Zhu
+  num: 157
 - name: Timo B. Roettger
-  num: 4
+  num: 158
+
 address:
-- num: 1
+- num: 1, 2
   org: Department of Linguistics and English Language, University of Edinburgh, United Kingdom
-- num: 2
-  org: Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany
 - num: 3
-  org: Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States
+  org: Department of Spanish and Portuguese, Rutgers University, United States
 - num: 4
-  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway
+  org: Department of Linguistics, Cornell University, United States
+- num: 5
+  org: Department of General and Computational Linguistics, University of Tübingen, Germany
+- num: 6
+  org: Program in Linguistics, Princeton University, United States
+- num: 7
+  org: Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia
+- num: 8
+  org: Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France
+- num: 9
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 10
+  org: Department of Linguistics, University of Arizona, United States
+- num: 11
+  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
+- num: 12
+  org: Departamento de Letras, Universidade Federal de São Carlos, Brazil
+- num: 13
+  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
+- num: 14
+  org: Department of Linguistics, University of Oregon, United States
+- num: 15
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 16
+  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
+- num: 17
+  org: Department of Psychology, University of California, Davis, United States
+- num: 18
+  org: Department of Linguistics, University of Arizona, United States
+- num: 19
+  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
+- num: 20
+  org: NA, University of Pennsylvania, United States
+- num: 21
+  org: Department of Communication Sciences and Disorders, Syracuse University, United States
+- num: 22
+  org: Department of Spanish, Villanova University, United States
+- num: 23
+  org: Department of English Language and Linguistics, University of Birmingham, United Kingdom
+- num: 24
+  org: Department of Philosophy, Carnegie Mellon University, United States
+- num: 25
+  org: Department of Spanish & French Studies, Occidental College, United States
+- num: 26
+  org: Department of English, Texas Tech University, United States
+- num: 27
+  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
+- num: 28
+  org: Department of Spanish and Portuguese, University of Arizona, United States
+- num: 29
+  org: Division of Mathematics and Computer Science, Simmons University, United States
+- num: 30
+  org: Analytics, Harrisburg University of Science and Technology, United States
+- num: 31
+  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
+- num: 32
+  org: Department of Psychology, University at Buffalo, SUNY, United States
+- num: 33
+  org: Université Paris Cité, France
+- num: 34
+  org: IfL-Phonetik, University of Cologne, Germany
+- num: 35
+  org: Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom
+- num: 36
+  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
+- num: 37
+  org: Basque Center on Cognition Brain and Language, Spain
+- num: 38
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 39
+  org: Department of Linguistics, University of California, Davis, United States
+- num: 40
+  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
+- num: 41
+  org: LLING, UMR6310, Nantes Université / CNRS, France
+- num: 42
+  org: Department of Linguisticss and TESOL, University of Texas at Arlington, United States
+- num: 43
+  org: School of Psychology, Newcastle University, United Kingdom
+- num: 44
+  org: Department of Linguistics, University of Oregon, United States
+- num: 45
+  org: School of Psychological Sciences and Health, University of Strathclyde, United Kingdom
+- num: 46
+  org: Department of Linguistics, University of Oregon, United States
+- num: 47
+  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
+- num: 48
+  org: Department of comparative language science, Universität Zürich, Swizerland, Switzerland
+- num: 49
+  org: Basque Center on Cognition Brain and Language, Spain
+- num: 50
+  org: Department of Linguistics, University of Canterbury, New Zealand
+- num: 51
+  org: IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France
+- num: 52
+  org: Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom
+- num: 53
+  org: Statistics Group, Association for Diversity in Linguistics, Germany
+- num: 54
+  org: CLILLAC-ARP, Université Paris Cité, France
+- num: 55
+  org: Department of Psychology, University of California, Davis, United States
+- num: 56
+  org: Department of Music, Max Planck Institute for Empirical Aesthetics, Germany
+- num: 57
+  org: Department of Psychology, Pacific Lutheran University, United States
+- num: 58
+  org: Department of Linguistics, University of Oregon, United States
+- num: 59
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 60
+  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
+- num: 61
+  org: Department of languages, linguistics, and translation, Université Laval, Canada
+- num: 62
+  org: New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand
+- num: 63
+  org: Department of Languages, Literatures, and Cultures, Saint Louis University, United States
+- num: 64
+  org: Department of Psychology, Princeton University, United States
+- num: 65
+  org: LPC, Aix Marseille Univ, CNRS, France
+- num: 66
+  org: Institute of Phonetics and Speech Processing, University of Munich, Germany
+- num: 67
+  org: IfL-Phonetik, University of Cologne, Germany
+- num: 68
+  org: Department of English Language and Linguistics, University of Birmingham, United Kingdom
+- num: 69
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 70
+  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
+- num: 71
+  org: Department of Linguistics and TESOL, University of Texas at Arlington, United States
+- num: 72
+  org: New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand
+- num: 73
+  org: Ao Tawhiti Unlimited Discovery, New Zealand
+- num: 74
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 75
+  org: Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States
+- num: 76
+  org: Department of Linguistics and Cognitive Science, Pomona College, United States
+- num: 77
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 78
+  org: University of California, Los Angeles, United States
+- num: 79
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 80
+  org: Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States
+- num: 81
+  org: School of Psychology, University of Birmingham, United Kingdom
+- num: 82
+  org: School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom
+- num: 83
+  org: Department of Linguistics, University of Canterbury, Aotearoa
+- num: 84
+  org: Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil
+- num: 85
+  org: Department of Linguistics, University of Canterbury, New Zealand
+- num: 86
+  org: Institute of Linguistics, University of Cologne, Germany
+- num: 87
+  org: Department of Linguistics, University of Washington, United States
+- num: 88
+  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
+- num: 89
+  org: Department of Language and Linguistic Science, University of York, United Kingdom
+- num: 90
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 91
+  org: Department of Communication and Cognition, Tilburg University, Netherlands
+- num: 92
+  org: Department of Communication and Cognition, Tilburg University, the Netherlands
+- num: 93
+  org: Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain
+- num: 94
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 95
+  org: Department of Psychology, Bowdoin College, ME, United States
+- num: 96
+  org: Linguistic Convergence Laboratory, HSE University, Russia
+- num: 97
+  org: Department of Communication and Cognition, Tilburg University, the Netherlands
+- num: 98
+  org: School of Psychology, University of Birmingham, United Kingdom
+- num: 99
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 100
+  org: Institute of German Language I Linguistics, University of Cologne, Germany
+- num: 101
+  org: Department of English Language Studies, Federal University of Ceará, Brazil
+- num: 102
+  org: Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom
+- num: 103
+  org: Department of Hispanic Studies, University of Houston, United States
+- num: 104
+  org: Department of English and American Studies, University of Salzburg, Austria
+- num: 105
+  org: School of Linguistics & Language Studies, Carleton University, Canada
+- num: 106
+  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
+- num: 107
+  org: Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom
+- num: 108
+  org: HSE University, Russia
+- num: 109
+  org: Speech and Language Therapy, University of Strathclyde, United Kingdom
+- num: 110
+  org: LPC, Aix Marseille Univ, CNRS, France
+- num: 111
+  org: Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia
+- num: 112
+  org: Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany
+- num: 113
+  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
+- num: 114
+  org: Graduate Program in Linguistics, Federal University of Ceará, Brazil
+- num: 115
+  org: World Languages, Literatures and Cultures Department, University of Arkansas, United States
+- num: 116
+  org: Deparment of Linguistics, Queen Mary University of London, United Kingdom
+- num: 117
+  org: CLILLAC-ARP, Université Paris Cité, France
+- num: 118
+  org: Department of Linguistics, University of Alberta, Canada
+- num: 119
+  org: Department of Linguistics, University of California, Berkeley, United States
+- num: 120
+  org: Department of Linguistics, Macquarie University, Australia
+- num: 121
+  org: Center for Cognitive Science, Rutgers University, United States
+- num: 122
+  org: Department of Spanish and Portuguese, Rutgers University, United States
+- num: 123
+  org: Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States
+- num: 124
+  org: Department of Psychology, Witten/Herdecke University, Germany
+- num: 125
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 126
+  org: Department of Linguistics, University of Colorado Boulder, United States
+- num: 127
+  org: Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom
+- num: 128
+  org: Department of English and American Studies, University of Salzburg, Austria
+- num: 129
+  org: Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany
+- num: 130
+  org: Linguistic Convergence Laboratory, HSE University, Russia
+- num: 131
+  org: Department of Linguistics, University of British Columbia, Canada
+- num: 132
+  org: Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany
+- num: 133
+  org: Department of Linguistics, Brigham Young University, United States
+- num: 134
+  org: Department of Linguistics, University of Colorado Boulder, United States
+- num: 135
+  org: Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany
+- num: 136
+  org: Department of General Linguistics, University of Tübingen, Germany
+- num: 137
+  org: Department of Linguistics, University of Alberta, Canada
+- num: 138
+  org: School of English Literature, Language and Linguistics, Newcastle University, United Kingdom
+- num: 139
+  org: Department of English & Literary Studies, University of Nigeria, Nsukka, Nigeria
+- num: 140
+  org: IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France
+- num: 141
+  org: Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany
+- num: 142
+  org: Psychological and Brain Sciences, Washington University in Saint Louis, United States
+- num: 143
+  org: Department of Communication and Cognition, Tilburg University, the Netherlands
+- num: 144
+  org: Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China
+- num: 145
+  org: Department of Linguistics, University of Arizona, United States
+- num: 146
+  org: IfL-Phonetik, University of Cologne, Germany
+- num: 147
+  org: Department of Languages, Literature and Communication, Utrecht University, Netherlands
+- num: 148
+  org: Department of Modern Languages, Carnegie Mellon University, United States
+- num: 149
+  org: School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada
+- num: 150
+  org: Geospatial Research Institute, University of Canterbury, New Zealand
+- num: 151
+  org: Department of Linguistics, University of Oregon, United States
+- num: 152
+  org: Département de Lettres modernes, LIUM, LST, Le Mans Université, France
+- num: 153
+  org: NA, University of Oxford, United Kingdom
+- num: 154
+  org: Department of Spanish, Western Michigan University, United States
+- num: 155
+  org: Department of Linguistics, University of California, Davis, United States
+- num: 156
+  org: School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom
+- num: 157
+  org: School of Information, University of Michigan, Ann Arbor, United States
+- num: 158
+  org: Department of Linguistics and Scandinavian Studies, University of Oslo, Norway
+
 corrauth: "Timo B. Roettger"

### 2022-11-19 RR_manuscript/Draft_RR.tex
add author affiliations

@@
 \author{Stefano Coretta*\affilnum{1, 2}, Joseph V.
-Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H.
-Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E.
-Alotaibi\affilnum{}, Mohammed K.
-AlShakhori\affilnum{}, Ruth M.
-Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M.
-Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J.
-Beier\affilnum{}, Gabriela M.
-Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P.
-BensonMeyer\affilnum{}, Nina R.
-Benway\affilnum{}, Grant M.
-Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A.
-Brown\affilnum{}, Alicia M.
-Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M.
-Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L.
-Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A.
-Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M.
-Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K.
-Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L.
-Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S.
-Grose-Hodge\affilnum{}, Amelia J.
-Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I.
-Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G.
-Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N.
-Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C.
-Kelley\affilnum{}, Niamh E.
-Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A.
-Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O.
-Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M.
-Lima Jr.\affilnum{}, Justin J.
+Casillas\affilnum{3}, Simon Roessig\affilnum{4}, Michael Franke\affilnum{5}, Byron Ahn\affilnum{6}, Ali H.
+Al-Hoorie\affilnum{7}, Jalal Al-Tamimi\affilnum{8}, Najd E.
+Alotaibi\affilnum{9}, Mohammed K.
+AlShakhori\affilnum{10}, Ruth M.
+Altmiller\affilnum{11}, Pablo Arantes\affilnum{12}, Angeliki Athanasopoulou\affilnum{13}, Melissa M.
+Baese-Berk\affilnum{14}, George Bailey\affilnum{15}, Cheman Baira A Sangma\affilnum{16}, Eleonora J.
+Beier\affilnum{17}, Gabriela M.
+Benavides\affilnum{18}, Nicole Benker\affilnum{19}, Emelia P.
+BensonMeyer\affilnum{20}, Nina R.
+Benway\affilnum{21}, Grant M.
+Berry\affilnum{22}, Liwen Bing\affilnum{23}, Christina Bjorndahl\affilnum{24}, Mariska Bolyanatz\affilnum{25}, Aaron Braver\affilnum{26}, Violet A.
+Brown\affilnum{27}, Alicia M.
+Brown\affilnum{28}, Alejna Brugos\affilnum{29}, Erin M.
+Buchanan\affilnum{30}, Tanna Butlin\affilnum{31}, Andrés Buxó-Lugo\affilnum{32}, Coline Caillol\affilnum{33}, Francesco Cangemi\affilnum{34}, Christopher Carignan\affilnum{35}, Sita Carraturo\affilnum{36}, Tiphaine Caudrelier\affilnum{37}, Eleanor Chodroff\affilnum{38}, Michelle Cohn\affilnum{39}, Johanna Cronenberg\affilnum{40}, Olivier Crouzet\affilnum{41}, Erica L.
+Dagar\affilnum{42}, Charlotte Dawson\affilnum{43}, Carissa A.
+Diantoro\affilnum{44}, Marie Dokovova\affilnum{45}, Shiloh Drake\affilnum{46}, Fengting Du\affilnum{47}, Margaux Dubuis\affilnum{48}, Florent Duême\affilnum{49}, Matthew Durward\affilnum{50}, Ander Egurtzegi\affilnum{51}, Mahmoud M.
+Elsherif\affilnum{52}, Janina Esser\affilnum{53}, Emmanuel Ferragne\affilnum{54}, Fernanda Ferreira\affilnum{55}, Lauren K.
+Fink\affilnum{56}, Sara Finley\affilnum{57}, Kurtis Foster\affilnum{58}, Paul Foulkes\affilnum{59}, Rosa Franzke\affilnum{60}, Gabriel Frazer-McKee\affilnum{61}, Robert Fromont\affilnum{62}, Christina García\affilnum{63}, Jason Geller\affilnum{64}, Camille L.
+Grasso\affilnum{65}, Pia Greca\affilnum{66}, Martine Grice\affilnum{67}, Magdalena S.
+Grose-Hodge\affilnum{68}, Amelia J.
+Gully\affilnum{69}, Caitlin Halfacre\affilnum{70}, Ivy Hauser\affilnum{71}, Jen Hay\affilnum{72}, Robert Haywood\affilnum{73}, Sam Hellmuth\affilnum{74}, Allison I.
+Hilger\affilnum{75}, Nicole Holliday\affilnum{76}, Damar Hoogland\affilnum{77}, Yaqian Huang\affilnum{78}, Vincent Hughes\affilnum{79}, Ane Icardo Isasa\affilnum{80}, Zlatomira G.
+Ilchovska\affilnum{81}, Hae-Sung Jeon\affilnum{82}, Jacq Jones\affilnum{83}, Mágat N.
+Junges\affilnum{84}, Stephanie Kaefer\affilnum{85}, Constantijn Kaland\affilnum{86}, Matthew C.
+Kelley\affilnum{87}, Niamh E.
+Kelly\affilnum{88}, Thomas Kettig\affilnum{89}, Ghada Khattab\affilnum{90}, Ruud Koolen\affilnum{91}, Emiel Krahmer\affilnum{92}, Dorota Krajewska\affilnum{93}, Andreas Krug\affilnum{94}, Abhilasha A.
+Kumar\affilnum{95}, Anna Lander\affilnum{96}, Tomas O.
+Lentz\affilnum{97}, Wanyin Li\affilnum{98}, Yanyu Li\affilnum{99}, Maria Lialiou\affilnum{100}, Ronaldo M.
+Lima Jr.\affilnum{101}, Justin J.
 H.
-Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G.
+Lo\affilnum{102}, Julio Cesar Lopez Otero\affilnum{103}, Bradley Mackay\affilnum{104}, Bethany MacLeod\affilnum{105}, Mel Mallard\affilnum{106}, Carol-Ann Mary McConnellogue\affilnum{107}, George Moroz\affilnum{108}, Mridhula Murali\affilnum{109}, Ladislas Nalborczyk\affilnum{110}, Filip Nenadić\affilnum{111}, Jessica Nieder\affilnum{112}, Dušan Nikolić\affilnum{113}, Francisco G.
 S.
-Nogueira\affilnum{}, Heather M.
-Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J.
-Perry\affilnum{}, Alexandra M.
-Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P.
-Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A.
-Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V.
-Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J.
-Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J.
-Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B.
-Roettger\affilnum{4}}
-
-\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
+Nogueira\affilnum{114}, Heather M.
+Offerman\affilnum{115}, Elisa Passoni\affilnum{116}, Maud Pélissier\affilnum{117}, Scott J.
+Perry\affilnum{118}, Alexandra M.
+Pfiffner\affilnum{119}, Michael Proctor\affilnum{120}, Ryan Rhodes\affilnum{121}, Nicole Rodríguez\affilnum{122}, Elizabeth Roepke\affilnum{123}, Jan P.
+Röer\affilnum{124}, Lucia Sbacco\affilnum{125}, Rebecca Scarborough\affilnum{126}, Felix Schaeffler\affilnum{127}, Erik Schleef\affilnum{128}, Dominic Schmitz\affilnum{129}, Alexander Shiryaev\affilnum{130}, Márton Sóskuthy\affilnum{131}, Malin Spaniol\affilnum{132}, Joseph A.
+Stanley\affilnum{133}, Alyssa Strickler\affilnum{134}, Alessandro Tavano\affilnum{135}, Fabian Tomaschek\affilnum{136}, Benjamin V.
+Tucker\affilnum{137}, Rory Turnbull\affilnum{138}, Kingsley O.
+Ugwuanyi\affilnum{139}, Iñigo Urrestarazu-Porta\affilnum{140}, Ruben van de Vijver\affilnum{141}, Kristin J.
+Van Engen\affilnum{142}, Emiel van Miltenburg\affilnum{143}, Bruce Wang\affilnum{144}, Natasha Warner\affilnum{145}, Simon Wehrle\affilnum{146}, Hans Westerbeek\affilnum{147}, Seth Wiener\affilnum{148}, Stephen Winters\affilnum{149}, Sidney G.-J.
+Wong\affilnum{150}, Anna Wood\affilnum{151}, Jane Wottawa\affilnum{152}, Chenzi Xu\affilnum{153}, Germán Zárate-Sández\affilnum{154}, Georgia Zellou\affilnum{155}, Cong Zhang\affilnum{156}, Jian Zhu\affilnum{157}, Timo B.
+Roettger\affilnum{158}}
+
+\affiliation{\affilnum{1, 2}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{4}{Department of Linguistics, Cornell University, United States}\\\affilnum{5}{Department of General and Computational Linguistics, University of Tübingen, Germany}\\\affilnum{6}{Program in Linguistics, Princeton University, United States}\\\affilnum{7}{Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia}\\\affilnum{8}{Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France}\\\affilnum{9}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{10}{Department of Linguistics, University of Arizona, United States}\\\affilnum{11}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{12}{Departamento de Letras, Universidade Federal de São Carlos, Brazil}\\\affilnum{13}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{14}{Department of Linguistics, University of Oregon, United States}\\\affilnum{15}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{16}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{17}{Department of Psychology, University of California, Davis, United States}\\\affilnum{18}{Department of Linguistics, University of Arizona, United States}\\\affilnum{19}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{20}{NA, University of Pennsylvania, United States}\\\affilnum{21}{Department of Communication Sciences and Disorders, Syracuse University, United States}\\\affilnum{22}{Department of Spanish, Villanova University, United States}\\\affilnum{23}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{24}{Department of Philosophy, Carnegie Mellon University, United States}\\\affilnum{25}{Department of Spanish \& French Studies, Occidental College, United States}\\\affilnum{26}{Department of English, Texas Tech University, United States}\\\affilnum{27}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{28}{Department of Spanish and Portuguese, University of Arizona, United States}\\\affilnum{29}{Division of Mathematics and Computer Science, Simmons University, United States}\\\affilnum{30}{Analytics, Harrisburg University of Science and Technology, United States}\\\affilnum{31}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{32}{Department of Psychology, University at Buffalo, SUNY, United States}\\\affilnum{33}{Université Paris Cité, France}\\\affilnum{34}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{35}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{36}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{37}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{38}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{39}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{40}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{41}{LLING, UMR6310, Nantes Université / CNRS, France}\\\affilnum{42}{Department of Linguisticss and TESOL, University of Texas at Arlington, United States}\\\affilnum{43}{School of Psychology, Newcastle University, United Kingdom}\\\affilnum{44}{Department of Linguistics, University of Oregon, United States}\\\affilnum{45}{School of Psychological Sciences and Health, University of Strathclyde, United Kingdom}\\\affilnum{46}{Department of Linguistics, University of Oregon, United States}\\\affilnum{47}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{48}{Department of comparative language science, Universität Zürich, Swizerland, Switzerland}\\\affilnum{49}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{50}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{51}{IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{52}{Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom}\\\affilnum{53}{Statistics Group, Association for Diversity in Linguistics, Germany}\\\affilnum{54}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{55}{Department of Psychology, University of California, Davis, United States}\\\affilnum{56}{Department of Music, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{57}{Department of Psychology, Pacific Lutheran University, United States}\\\affilnum{58}{Department of Linguistics, University of Oregon, United States}\\\affilnum{59}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{60}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{61}{Department of languages, linguistics, and translation, Université Laval, Canada}\\\affilnum{62}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{63}{Department of Languages, Literatures, and Cultures, Saint Louis University, United States}\\\affilnum{64}{Department of Psychology, Princeton University, United States}\\\affilnum{65}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{66}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{67}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{68}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{69}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{70}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{71}{Department of Linguistics and TESOL, University of Texas at Arlington, United States}\\\affilnum{72}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{73}{Ao Tawhiti Unlimited Discovery, New Zealand}\\\affilnum{74}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{75}{Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States}\\\affilnum{76}{Department of Linguistics and Cognitive Science, Pomona College, United States}\\\affilnum{77}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{78}{University of California, Los Angeles, United States}\\\affilnum{79}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{80}{Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States}\\\affilnum{81}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{82}{School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom}\\\affilnum{83}{Department of Linguistics, University of Canterbury, Aotearoa}\\\affilnum{84}{Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil}\\\affilnum{85}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{86}{Institute of Linguistics, University of Cologne, Germany}\\\affilnum{87}{Department of Linguistics, University of Washington, United States}\\\affilnum{88}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{89}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{90}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{91}{Department of Communication and Cognition, Tilburg University, Netherlands}\\\affilnum{92}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{93}{Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain}\\\affilnum{94}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{95}{Department of Psychology, Bowdoin College, ME, United States}\\\affilnum{96}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{97}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{98}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{99}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{100}{Institute of German Language I Linguistics, University of Cologne, Germany}\\\affilnum{101}{Department of English Language Studies, Federal University of Ceará, Brazil}\\\affilnum{102}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{103}{Department of Hispanic Studies, University of Houston, United States}\\\affilnum{104}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{105}{School of Linguistics \& Language Studies, Carleton University, Canada}\\\affilnum{106}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{107}{Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom}\\\affilnum{108}{HSE University, Russia}\\\affilnum{109}{Speech and Language Therapy, University of Strathclyde, United Kingdom}\\\affilnum{110}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{111}{Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia}\\\affilnum{112}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{113}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{114}{Graduate Program in Linguistics, Federal University of Ceará, Brazil}\\\affilnum{115}{World Languages, Literatures and Cultures Department, University of Arkansas, United States}\\\affilnum{116}{Deparment of Linguistics, Queen Mary University of London, United Kingdom}\\\affilnum{117}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{118}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{119}{Department of Linguistics, University of California, Berkeley, United States}\\\affilnum{120}{Department of Linguistics, Macquarie University, Australia}\\\affilnum{121}{Center for Cognitive Science, Rutgers University, United States}\\\affilnum{122}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{123}{Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States}\\\affilnum{124}{Department of Psychology, Witten/Herdecke University, Germany}\\\affilnum{125}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{126}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{127}{Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom}\\\affilnum{128}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{129}{Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany}\\\affilnum{130}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{131}{Department of Linguistics, University of British Columbia, Canada}\\\affilnum{132}{Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany}\\\affilnum{133}{Department of Linguistics, Brigham Young University, United States}\\\affilnum{134}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{135}{Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{136}{Department of General Linguistics, University of Tübingen, Germany}\\\affilnum{137}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{138}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{139}{Department of English \& Literary Studies, University of Nigeria, Nsukka, Nigeria}\\\affilnum{140}{IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{141}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{142}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{143}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{144}{Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China}\\\affilnum{145}{Department of Linguistics, University of Arizona, United States}\\\affilnum{146}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{147}{Department of Languages, Literature and Communication, Utrecht University, Netherlands}\\\affilnum{148}{Department of Modern Languages, Carnegie Mellon University, United States}\\\affilnum{149}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{150}{Geospatial Research Institute, University of Canterbury, New Zealand}\\\affilnum{151}{Department of Linguistics, University of Oregon, United States}\\\affilnum{152}{Département de Lettres modernes, LIUM, LST, Le Mans Université, France}\\\affilnum{153}{NA, University of Oxford, United Kingdom}\\\affilnum{154}{Department of Spanish, Western Michigan University, United States}\\\affilnum{155}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{156}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{157}{School of Information, University of Michigan, Ann Arbor, United States}\\\affilnum{158}{Department of Linguistics and Scandinavian Studies, University of Oslo, Norway}}
 

### 2022-11-19 scripts/r/09_credit_taxonomy.Rmd
add author affiliations

@@
 library("tidyr")
+library("glue")
 library("stringr")
 library("ggplot2")
+library("ggtext")
 library("forcats")
@@
 library("kableExtra")
+library("countrycode")
 ```
@@
   read_csv("data/CRediT/MSA_tenzing_contribution-corrected_contributions.csv") %>% 
-  janitor::clean_names()
+  janitor::clean_names() %>% 
+  mutate(
+    primary_affiliation_country = if_else(
+      primary_affiliation_country == "Aotearoa", 
+      "New Zealand", 
+      .$primary_affiliation_country
+      ), 
+    cntry = countrycode(
+      primary_affiliation_country, 
+      origin = 'country.name', 
+      destination = 'iso3c'
+      ), 
+    flag = countrycode(
+      cntry, 
+      origin = 'iso3c', 
+      destination = 'unicode.symbol')
+    )
 
@@
 
+n_no_affiliation <- sum(is.na(contributors$primary_affiliation_university))
+
 # Plot affiliations as a function of n
@@
 There were `r nrow(contributors)` contributors from `r nrow(affiliations)` institutions. 
-`r filter(affiliations, is.na(primary_affiliation_university)) %>% pull(n) %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
+`r n_no_affiliation %>% xfun::numbers_to_words() %>% str_to_sentence()` analysts did not include their primary affiliation.
+
+## Countries
+
+```{r}
+#| label: analysts-by-country
+
+open <- "<img src="
+close <- " width='25' /><br>"
+
+n_countries <- contributors %>% 
+  count(primary_affiliation_country, flag) %>% 
+  arrange(n) %>% 
+  mutate(
+    country = primary_affiliation_country, 
+    labs = case_when(
+      country == "Australia" ~ glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
+      country == "Hong Kong SAR, China" ~ glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
+      country == "Nigeria" ~ glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
+      country == "Norway" ~ glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
+      country == "Saudi Arabia" ~ glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
+      country == "Serbia" ~ glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
+      country == "Switzerland" ~ glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
+      country == "Austria" ~ glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
+      country == "Russia" ~ glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
+      country == "Spain" ~ glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
+      country == "Brazil" ~ glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
+      country == "Netherlands" ~ glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
+      country == "New Zealand" ~ glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
+      country == "Canada" ~ glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
+      country == "France" ~ glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
+      country == "Germany" ~ glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
+      country == "United Kingdom" ~ glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
+      country == "United States" ~ glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
+    ), 
+    primary_affiliation_country = fct_reorder(primary_affiliation_country, n, max))
+
+n_countries %>% 
+  ggplot() + 
+  aes(x = n, y = primary_affiliation_country) + 
+  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
+  geom_point() + 
+  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
+  theme_bw(base_size = 9) + 
+  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
+  theme(axis.text.y = element_markdown(color = "black"))
+
+```
 
@@
 cr_prep <- contributors %>% 
-  select(name, surname, conceptualization:writing_review_editing, is_initiating, initials) %>% 
+  select(name, surname, conceptualization:writing_review_editing, 
+         is_initiating, initials) %>% 
   pivot_longer(
@@
 contributors %>% 
-  select(name, primary_affiliation_university) %>% 
+  select(name, 
+         primary_affiliation_department, 
+         primary_affiliation_university, 
+         primary_affiliation_country) %>% 
   transmute(
@@
 contributors %>% 
-  select(name, primary_affiliation_university, primary_affiliation_department) %>% 
+  select(name, 
+         primary_affiliation_department, 
+         primary_affiliation_university, 
+         primary_affiliation_country) %>% 
   transmute(
@@
     num_man = glue::glue("- num: {1:nrow(.) + 1}"), 
-    print = glue::glue("- org: {primary_affiliation_department}, {primary_affiliation_university}"), 
+    print = glue::glue("- org: {primary_affiliation_department}, {primary_affiliation_university}, {primary_affiliation_country}"), 
   ) %>% 

### 2022-11-19 scripts/r/09_credit_taxonomy.Rmd
add numbers to pionts

@@
   aes(x = n, y = primary_affiliation_country) + 
-  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
-  geom_point() + 
-  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
+  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country), size = 2) + 
+  geom_point(size = 6) + 
+  geom_text(aes(label = n), color = "white", size = 3) + 
+  labs(x = "n", y = NULL, 
+    title = glue("Number of analysts by country (n = {sum(n_countries$n)})")) + 
   theme_bw(base_size = 9) + 

### 2022-11-19 RR_manuscript/Draft_RR.Rmd
delete NA from upenn affiliation

@@
 - num: 20
-  org: NA, University of Pennsylvania, United States
+  org: University of Pennsylvania, United States
 - num: 21

### 2023-01-04 RR_manuscript/Draft_RR.tex
♻️ - fix typos listed in #282

--- 2022-11-05 RR_manuscript/Draft_RR.tex
@@
 \author{Stefano Coretta*\affilnum{1, 2}, Joseph V.
-Casillas\affilnum{3}, Simon Roessig\affilnum{}, Michael Franke\affilnum{}, Ali H.
-Al-Hoorie\affilnum{}, Jalal Al-Tamimi\affilnum{}, Najd E.
-Alotaibi\affilnum{}, Mohammed K.
-AlShakhori\affilnum{}, Ruth M.
-Altmiller\affilnum{}, Pablo Arantes\affilnum{}, Angeliki Athanasopoulou\affilnum{}, Melissa M.
-Baese-Berk\affilnum{}, George Bailey\affilnum{}, Cheman Baira A Sangma\affilnum{}, Eleonora J.
-Beier\affilnum{}, Gabriela M.
-Benavides\affilnum{}, Nicole Benker\affilnum{}, Emelia P.
-BensonMeyer\affilnum{}, Nina R.
-Benway\affilnum{}, Grant M.
-Berry\affilnum{}, Liwen Bing\affilnum{}, Christina Bjorndahl\affilnum{}, Mariska Bolyanatz\affilnum{}, Aaron Braver\affilnum{}, Violet A.
-Brown\affilnum{}, Alicia M.
-Brown\affilnum{}, Alejna Brugos\affilnum{}, Erin M.
-Buchanan\affilnum{}, Tanna Butlin\affilnum{}, Andrés Buxó-Lugo\affilnum{}, Coline Caillol\affilnum{}, Francesco Cangemi\affilnum{}, Christopher Carignan\affilnum{}, Sita Carraturo\affilnum{}, Tiphaine Caudrelier\affilnum{}, Eleanor Chodroff\affilnum{}, Michelle Cohn\affilnum{}, Johanna Cronenberg\affilnum{}, Olivier Crouzet\affilnum{}, Erica L.
-Dagar\affilnum{}, Charlotte Dawson\affilnum{}, Carissa A.
-Diantoro\affilnum{}, Marie Dokovova\affilnum{}, Wood Drake\affilnum{}, Fengting Du\affilnum{}, Margaux Dubuis\affilnum{}, Florent Duême\affilnum{}, Matthew Durward\affilnum{}, Ander Egurtzegi\affilnum{}, Mahmoud M.
-Elsherif\affilnum{}, Janina Esser\affilnum{}, Emmanuel Ferragne\affilnum{}, Fernanda Ferreira\affilnum{}, Lauren K.
-Fink\affilnum{}, Sara Finley\affilnum{}, Kurtis Foster\affilnum{}, Paul Foulkes\affilnum{}, Rosa Franzke\affilnum{}, Gabriel Frazer-McKee\affilnum{}, Robert Fromont\affilnum{}, Christina García\affilnum{}, Jason Geller\affilnum{}, Camille L.
-Grasso\affilnum{}, Pia Greca\affilnum{}, Martine Grice\affilnum{}, Magdalena S.
-Grose-Hodge\affilnum{}, Amelia J.
-Gully\affilnum{}, Caitlin Halfacre\affilnum{}, Westerbeek Hans\affilnum{}, Ivy Hauser\affilnum{}, Jen Hay\affilnum{}, Robert Haywood\affilnum{}, Sam Hellmuth\affilnum{}, Allison I.
-Hilger\affilnum{}, Nicole Holliday\affilnum{}, Damar Hoogland\affilnum{}, Yaqian Huang\affilnum{}, Vincent Hughes\affilnum{}, Ane Icardo Isasa\affilnum{}, Zlatomira G.
-Ilchovska\affilnum{}, Hae-Sung Jeon\affilnum{}, Jacq Jones\affilnum{}, Mágat N.
-Junges\affilnum{}, Stephanie Kaefer\affilnum{}, Constantijn Kaland\affilnum{}, Matthew C.
-Kelley\affilnum{}, Niamh E.
-Kelly\affilnum{}, Ghada Khattab\affilnum{}, Emiel Krahmer\affilnum{}, Dorota Krajewska\affilnum{}, Andreas Krug\affilnum{}, Abhilasha A.
-Kumar\affilnum{}, Anna Lander\affilnum{}, Tomas O.
-Lentz\affilnum{}, Wanyin Li\affilnum{}, Yanyu Li\affilnum{}, Maria Lialiou\affilnum{}, Ronaldo M.
-Lima Jr.\affilnum{}, Justin J.
+Casillas\affilnum{3}, Simon Roessig\affilnum{4}, Michael Franke\affilnum{5}, Byron Ahn\affilnum{6}, Ali H.
+Al-Hoorie\affilnum{7}, Jalal Al-Tamimi\affilnum{8}, Najd E.
+Alotaibi\affilnum{9}, Mohammed K.
+AlShakhori\affilnum{10}, Ruth M.
+Altmiller\affilnum{11}, Pablo Arantes\affilnum{12}, Angeliki Athanasopoulou\affilnum{13}, Melissa M.
+Baese-Berk\affilnum{14}, George Bailey\affilnum{15}, Cheman Baira A Sangma\affilnum{16}, Eleonora J.
+Beier\affilnum{17}, Gabriela M.
+Benavides\affilnum{18}, Nicole Benker\affilnum{19}, Emelia P.
+BensonMeyer\affilnum{20}, Nina R.
+Benway\affilnum{21}, Grant M.
+Berry\affilnum{22}, Liwen Bing\affilnum{23}, Christina Bjorndahl\affilnum{24}, Mariska Bolyanatz\affilnum{25}, Aaron Braver\affilnum{26}, Violet A.
+Brown\affilnum{27}, Alicia M.
+Brown\affilnum{28}, Alejna Brugos\affilnum{29}, Erin M.
+Buchanan\affilnum{30}, Tanna Butlin\affilnum{31}, Andrés Buxó-Lugo\affilnum{32}, Coline Caillol\affilnum{33}, Francesco Cangemi\affilnum{34}, Christopher Carignan\affilnum{35}, Sita Carraturo\affilnum{36}, Tiphaine Caudrelier\affilnum{37}, Eleanor Chodroff\affilnum{38}, Michelle Cohn\affilnum{39}, Johanna Cronenberg\affilnum{40}, Olivier Crouzet\affilnum{41}, Erica L.
+Dagar\affilnum{42}, Charlotte Dawson\affilnum{43}, Carissa A.
+Diantoro\affilnum{44}, Marie Dokovova\affilnum{45}, Shiloh Drake\affilnum{46}, Fengting Du\affilnum{47}, Margaux Dubuis\affilnum{48}, Florent Duême\affilnum{49}, Matthew Durward\affilnum{50}, Ander Egurtzegi\affilnum{51}, Mahmoud M.
+Elsherif\affilnum{52}, Janina Esser\affilnum{53}, Emmanuel Ferragne\affilnum{54}, Fernanda Ferreira\affilnum{55}, Lauren K.
+Fink\affilnum{56}, Sara Finley\affilnum{57}, Kurtis Foster\affilnum{58}, Paul Foulkes\affilnum{59}, Rosa Franzke\affilnum{60}, Gabriel Frazer-McKee\affilnum{61}, Robert Fromont\affilnum{62}, Christina García\affilnum{63}, Jason Geller\affilnum{64}, Camille L.
+Grasso\affilnum{65}, Pia Greca\affilnum{66}, Martine Grice\affilnum{67}, Magdalena S.
+Grose-Hodge\affilnum{68}, Amelia J.
+Gully\affilnum{69}, Caitlin Halfacre\affilnum{70}, Ivy Hauser\affilnum{71}, Jen Hay\affilnum{72}, Robert Haywood\affilnum{73}, Sam Hellmuth\affilnum{74}, Allison I.
+Hilger\affilnum{75}, Nicole Holliday\affilnum{76}, Damar Hoogland\affilnum{77}, Yaqian Huang\affilnum{78}, Vincent Hughes\affilnum{79}, Ane Icardo Isasa\affilnum{80}, Zlatomira G.
+Ilchovska\affilnum{81}, Hae-Sung Jeon\affilnum{82}, Jacq Jones\affilnum{83}, Mágat N.
+Junges\affilnum{84}, Stephanie Kaefer\affilnum{85}, Constantijn Kaland\affilnum{86}, Matthew C.
+Kelley\affilnum{87}, Niamh E.
+Kelly\affilnum{88}, Thomas Kettig\affilnum{89}, Ghada Khattab\affilnum{90}, Ruud Koolen\affilnum{91}, Emiel Krahmer\affilnum{92}, Dorota Krajewska\affilnum{93}, Andreas Krug\affilnum{94}, Abhilasha A.
+Kumar\affilnum{95}, Anna Lander\affilnum{96}, Tomas O.
+Lentz\affilnum{97}, Wanyin Li\affilnum{98}, Yanyu Li\affilnum{99}, Maria Lialiou\affilnum{100}, Ronaldo M.
+Lima Jr.\affilnum{101}, Justin J.
 H.
-Lo\affilnum{}, Julio César López Otero\affilnum{}, Bradley Mackay\affilnum{}, Bethany MacLeod\affilnum{}, Mel Mallard\affilnum{}, Carol-Ann McConnellogue\affilnum{}, George Moroz\affilnum{}, Mridhula Murali\affilnum{}, Ladislas Nalborczyk\affilnum{}, Filip Nenadić\affilnum{}, Jessica Nieder\affilnum{}, Dušan Nikolić\affilnum{}, Francisco G.
+Lo\affilnum{102}, Julio Cesar Lopez Otero\affilnum{103}, Bradley Mackay\affilnum{104}, Bethany MacLeod\affilnum{105}, Mel Mallard\affilnum{106}, Carol-Ann Mary McConnellogue\affilnum{107}, George Moroz\affilnum{108}, Mridhula Murali\affilnum{109}, Ladislas Nalborczyk\affilnum{110}, Filip Nenadić\affilnum{111}, Jessica Nieder\affilnum{112}, Dušan Nikolić\affilnum{113}, Francisco G.
 S.
-Nogueira\affilnum{}, Heather M.
-Offerman\affilnum{}, Elisa Passoni\affilnum{}, Maud Pélissier\affilnum{}, Scott J.
-Perry\affilnum{}, Alexandra M.
-Pfiffner\affilnum{}, Michael Proctor\affilnum{}, Ryan Rhodes\affilnum{}, Nicole Rodríguez\affilnum{}, Elizabeth Roepke\affilnum{}, Jan P.
-Röer\affilnum{}, Koolen Ruud\affilnum{}, Lucia Sbacco\affilnum{}, Rebecca Scarborough\affilnum{}, Felix Schaeffler\affilnum{}, Erik Schleef\affilnum{}, Dominic Schmitz\affilnum{}, Alexander Shiryaev\affilnum{}, Márton Sóskuthy\affilnum{}, Malin Spaniol\affilnum{}, Joseph A.
-Stanley\affilnum{}, Alyssa Strickler\affilnum{}, Alessandro Tavano\affilnum{}, Fabian Tomaschek\affilnum{}, Benjamin V.
-Tucker\affilnum{}, Rory Turnbull\affilnum{}, Kingsley Ugwuanyi\affilnum{}, Iñigo Urrestarazu-Porta\affilnum{}, Ruben van de Vijver\affilnum{}, Kristin J.
-Van Engen\affilnum{}, Emiel van Miltenburg\affilnum{}, Bruce Wang\affilnum{}, Natasha Warner\affilnum{}, Simon Wehrle\affilnum{}, Seth Wiener\affilnum{}, Stephen Winters\affilnum{}, Sidney G.-J.
-Wong\affilnum{}, Anna Wood\affilnum{}, Jane Wottawa\affilnum{}, Chenzi Xu\affilnum{}, Germán Zárate-Sández\affilnum{}, Georgia Zellou\affilnum{}, Cong Zhang\affilnum{}, Jian Zhu\affilnum{}, Timo B.
-Roettger\affilnum{4}}
-
-\affiliation{\affilnum{1}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{2}{Institute of Phonetics and Speech Processing, Ludwig-Maximilian University Munich, Germany}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, New Brunswick, United States}\\\affilnum{4}{Department of Linguistics and Scandinavian Studies, University of Oslo, Oslo, Norway}}
+Nogueira\affilnum{114}, Heather M.
+Offerman\affilnum{115}, Elisa Passoni\affilnum{116}, Maud Pélissier\affilnum{117}, Scott J.
+Perry\affilnum{118}, Alexandra M.
+Pfiffner\affilnum{119}, Michael Proctor\affilnum{120}, Ryan Rhodes\affilnum{121}, Nicole Rodríguez\affilnum{122}, Elizabeth Roepke\affilnum{123}, Jan P.
+Röer\affilnum{124}, Lucia Sbacco\affilnum{125}, Rebecca Scarborough\affilnum{126}, Felix Schaeffler\affilnum{127}, Erik Schleef\affilnum{128}, Dominic Schmitz\affilnum{129}, Alexander Shiryaev\affilnum{130}, Márton Sóskuthy\affilnum{131}, Malin Spaniol\affilnum{132}, Joseph A.
+Stanley\affilnum{133}, Alyssa Strickler\affilnum{134}, Alessandro Tavano\affilnum{135}, Fabian Tomaschek\affilnum{136}, Benjamin V.
+Tucker\affilnum{137}, Rory Turnbull\affilnum{138}, Kingsley O.
+Ugwuanyi\affilnum{139}, Iñigo Urrestarazu-Porta\affilnum{140}, Ruben van de Vijver\affilnum{141}, Kristin J.
+Van Engen\affilnum{142}, Emiel van Miltenburg\affilnum{143}, Bruce Wang\affilnum{144}, Natasha Warner\affilnum{145}, Simon Wehrle\affilnum{146}, Hans Westerbeek\affilnum{147}, Seth Wiener\affilnum{148}, Stephen Winters\affilnum{149}, Sidney G.-J.
+Wong\affilnum{150}, Anna Wood\affilnum{151}, Jane Wottawa\affilnum{152}, Chenzi Xu\affilnum{153}, Germán Zárate-Sández\affilnum{154}, Georgia Zellou\affilnum{155}, Cong Zhang\affilnum{156}, Jian Zhu\affilnum{157}, Timo B.
+Roettger\affilnum{158}}
+
+\affiliation{\affilnum{1, 2}{Department of Linguistics and English Language, University of Edinburgh, United Kingdom}\\\affilnum{3}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{4}{Department of Linguistics, Cornell University, United States}\\\affilnum{5}{Department of General and Computational Linguistics, University of Tübingen, Germany}\\\affilnum{6}{Program in Linguistics, Princeton University, United States}\\\affilnum{7}{Jubail English Language and Preparatory Year Institute, Royal Commission for Jubail and Yanbu, Saudi Arabia}\\\affilnum{8}{Laboratoire de Lingusitique Formelle (LLF), CNRS, Université Paris Cité, France}\\\affilnum{9}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{10}{Department of Linguistics, University of Arizona, United States}\\\affilnum{11}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{12}{Departamento de Letras, Universidade Federal de São Carlos, Brazil}\\\affilnum{13}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{14}{Department of Linguistics, University of Oregon, United States}\\\affilnum{15}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{16}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{17}{Department of Psychology, University of California, Davis, United States}\\\affilnum{18}{Department of Linguistics, University of Arizona, United States}\\\affilnum{19}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{20}{University of Pennsylvania, United States}\\\affilnum{21}{Department of Communication Sciences and Disorders, Syracuse University, United States}\\\affilnum{22}{Department of Spanish, Villanova University, United States}\\\affilnum{23}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{24}{Department of Philosophy, Carnegie Mellon University, United States}\\\affilnum{25}{Department of Spanish \& French Studies, Occidental College, United States}\\\affilnum{26}{Department of English, Texas Tech University, United States}\\\affilnum{27}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{28}{Department of Spanish and Portuguese, University of Arizona, United States}\\\affilnum{29}{Division of Mathematics and Computer Science, Simmons University, United States}\\\affilnum{30}{Analytics, Harrisburg University of Science and Technology, United States}\\\affilnum{31}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{32}{Department of Psychology, University at Buffalo, SUNY, United States}\\\affilnum{33}{Université Paris Cité, France}\\\affilnum{34}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{35}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{36}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{37}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{38}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{39}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{40}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{41}{LLING, UMR6310, Nantes Université / CNRS, France}\\\affilnum{42}{Department of Linguisticss and TESOL, University of Texas at Arlington, United States}\\\affilnum{43}{School of Psychology, Newcastle University, United Kingdom}\\\affilnum{44}{Department of Linguistics, University of Oregon, United States}\\\affilnum{45}{School of Psychological Sciences and Health, University of Strathclyde, United Kingdom}\\\affilnum{46}{Department of Linguistics, University of Oregon, United States}\\\affilnum{47}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{48}{Department of comparative language science, Universität Zürich, Swizerland, Switzerland}\\\affilnum{49}{Basque Center on Cognition Brain and Language, Spain}\\\affilnum{50}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{51}{IKER (UMR 5478), Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{52}{Department of Neuroscience, Psychology and Behaviour, University of Leicester, United Kingdom}\\\affilnum{53}{Statistics Group, Association for Diversity in Linguistics, Germany}\\\affilnum{54}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{55}{Department of Psychology, University of California, Davis, United States}\\\affilnum{56}{Department of Music, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{57}{Department of Psychology, Pacific Lutheran University, United States}\\\affilnum{58}{Department of Linguistics, University of Oregon, United States}\\\affilnum{59}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{60}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{61}{Department of languages, linguistics, and translation, Université Laval, Canada}\\\affilnum{62}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{63}{Department of Languages, Literatures, and Cultures, Saint Louis University, United States}\\\affilnum{64}{Department of Psychology, Princeton University, United States}\\\affilnum{65}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{66}{Institute of Phonetics and Speech Processing, University of Munich, Germany}\\\affilnum{67}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{68}{Department of English Language and Linguistics, University of Birmingham, United Kingdom}\\\affilnum{69}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{70}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{71}{Department of Linguistics and TESOL, University of Texas at Arlington, United States}\\\affilnum{72}{New Zealand Institute of Language, Brain and Behaviour, University of Canterbury, New Zealand}\\\affilnum{73}{Ao Tawhiti Unlimited Discovery, New Zealand}\\\affilnum{74}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{75}{Department of Speech, Language, and Hearing Sciences, University of Colorado Boulder, United States}\\\affilnum{76}{Department of Linguistics and Cognitive Science, Pomona College, United States}\\\affilnum{77}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{78}{University of California, Los Angeles, United States}\\\affilnum{79}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{80}{Department of Modern and Classical Languages and Literatures, California State University, Northridge, United States}\\\affilnum{81}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{82}{School of Humanities, Language and Global Studies, University of Central Lancashire, United Kingdom}\\\affilnum{83}{Department of Linguistics, University of Canterbury, Aotearoa}\\\affilnum{84}{Programa de Pós-Graduação em Letras, Federal University of Rio Grande do Sul, Brazil}\\\affilnum{85}{Department of Linguistics, University of Canterbury, New Zealand}\\\affilnum{86}{Institute of Linguistics, University of Cologne, Germany}\\\affilnum{87}{Department of Linguistics, University of Washington, United States}\\\affilnum{88}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{89}{Department of Language and Linguistic Science, University of York, United Kingdom}\\\affilnum{90}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{91}{Department of Communication and Cognition, Tilburg University, Netherlands}\\\affilnum{92}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{93}{Department of Linguistics and Basque Studies, University of the Basque Country UPV/EHU, Spain}\\\affilnum{94}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{95}{Department of Psychology, Bowdoin College, ME, United States}\\\affilnum{96}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{97}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{98}{School of Psychology, University of Birmingham, United Kingdom}\\\affilnum{99}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{100}{Institute of German Language I Linguistics, University of Cologne, Germany}\\\affilnum{101}{Department of English Language Studies, Federal University of Ceará, Brazil}\\\affilnum{102}{Department of Speech, Hearing and Phonetic Sciences, University College London, United Kingdom}\\\affilnum{103}{Department of Hispanic Studies, University of Houston, United States}\\\affilnum{104}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{105}{School of Linguistics \& Language Studies, Carleton University, Canada}\\\affilnum{106}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{107}{Population Health Sciences Institute - Faculty of Medical Sciences, Newcastle University, United Kingdom}\\\affilnum{108}{HSE University, Russia}\\\affilnum{109}{Speech and Language Therapy, University of Strathclyde, United Kingdom}\\\affilnum{110}{LPC, Aix Marseille Univ, CNRS, France}\\\affilnum{111}{Department of Psychology, Faculty of Media and Communications, Singidunum University, Serbia}\\\affilnum{112}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{113}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{114}{Graduate Program in Linguistics, Federal University of Ceará, Brazil}\\\affilnum{115}{World Languages, Literatures and Cultures Department, University of Arkansas, United States}\\\affilnum{116}{Deparment of Linguistics, Queen Mary University of London, United Kingdom}\\\affilnum{117}{CLILLAC-ARP, Université Paris Cité, France}\\\affilnum{118}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{119}{Department of Linguistics, University of California, Berkeley, United States}\\\affilnum{120}{Department of Linguistics, Macquarie University, Australia}\\\affilnum{121}{Center for Cognitive Science, Rutgers University, United States}\\\affilnum{122}{Department of Spanish and Portuguese, Rutgers University, United States}\\\affilnum{123}{Department of Speech, Language, and Hearing Sciences, Saint Louis University, United States}\\\affilnum{124}{Department of Psychology, Witten/Herdecke University, Germany}\\\affilnum{125}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{126}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{127}{Clinical Audiology, Speech and Language (CASL) Research Centre, Queen Margaret University Edinburgh, United Kingdom}\\\affilnum{128}{Department of English and American Studies, University of Salzburg, Austria}\\\affilnum{129}{Department of English and American Studies, Heinrich Heine University Düsseldorf, Germany}\\\affilnum{130}{Linguistic Convergence Laboratory, HSE University, Russia}\\\affilnum{131}{Department of Linguistics, University of British Columbia, Canada}\\\affilnum{132}{Department of Psychiatry and Psychotherapy, University Hospital Cologne, Germany}\\\affilnum{133}{Department of Linguistics, Brigham Young University, United States}\\\affilnum{134}{Department of Linguistics, University of Colorado Boulder, United States}\\\affilnum{135}{Department of Neuroscience, Max Planck Institute for Empirical Aesthetics, Germany}\\\affilnum{136}{Department of General Linguistics, University of Tübingen, Germany}\\\affilnum{137}{Department of Linguistics, University of Alberta, Canada}\\\affilnum{138}{School of English Literature, Language and Linguistics, Newcastle University, United Kingdom}\\\affilnum{139}{Department of English \& Literary Studies, University of Nigeria, Nsukka, Nigeria}\\\affilnum{140}{IKER-UMR5478, Centre National de la Recherche Scientifique (CNRS), France}\\\affilnum{141}{Institute of Linguistics, Heinrich-Heine University Düsseldorf, Germany}\\\affilnum{142}{Psychological and Brain Sciences, Washington University in Saint Louis, United States}\\\affilnum{143}{Department of Communication and Cognition, Tilburg University, the Netherlands}\\\affilnum{144}{Chinese and Bilingual Studies, Hong Kong Polytechnic University, Hong Kong SAR, China}\\\affilnum{145}{Department of Linguistics, University of Arizona, United States}\\\affilnum{146}{IfL-Phonetik, University of Cologne, Germany}\\\affilnum{147}{Department of Languages, Literature and Communication, Utrecht University, Netherlands}\\\affilnum{148}{Department of Modern Languages, Carnegie Mellon University, United States}\\\affilnum{149}{School of Languages, Linguistics, Literatures and Cultures, University of Calgary, Canada}\\\affilnum{150}{Geospatial Research Institute, University of Canterbury, New Zealand}\\\affilnum{151}{Department of Linguistics, University of Oregon, United States}\\\affilnum{152}{Département de Lettres modernes, LIUM, LST, Le Mans Université, France}\\\affilnum{153}{NA, University of Oxford, United Kingdom}\\\affilnum{154}{Department of Spanish, Western Michigan University, United States}\\\affilnum{155}{Department of Linguistics, University of California, Davis, United States}\\\affilnum{156}{School of Education, Communication and Language Studies - ECLS, Newcastle University, United Kingdom}\\\affilnum{157}{School of Information, University of Michigan, Ann Arbor, United States}\\\affilnum{158}{Department of Linguistics and Scandinavian Studies, University of Oslo, Norway}}
 
@@
 When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
-Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.
+Moreover, there was no team that declared to have made post-hoc changes to the analyses, thus we decided against including these two preregistered predictors in the model.
 
@@
 The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1-\texttt{r}round(predictor\_n\$max\_predictor,1)`).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = -4).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
+Of the 170 critical model coefficients, 37 were claimed to show a statistically reliable effect (21.8\%).
 
@@
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Possible tools to strengthen theoretical development are related to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 
-See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png}.
+See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy-all.png}.
 

### 2023-01-05 RR_manuscript/Draft_RR.Rmd
some edits

@@
 We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
-For a list of exlcusion criteria, see Section Descriptive statistics below.
+We also did no include analyses for which we could not extract standardized effect sizes. For a list of exclusion criteria, see Section Descriptive statistics below.
 
@@
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
+Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after sighting all analyses strategies.
 
@@
 (A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95% highest density intervals.
-(C) Mean posterior samples (white circles) and 80/95% credible intervals for all predictors.
+(C) Mean posterior samples (white circles) and 80/95% credible intervals for all predictors grouped into predictors related to (1) temporal window, (2) outcome variable, and (3) team/analysis.
 
@@
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an "inference crisis" [@rotello2015more; @starns2019assessing].
+Thus beyond a mere replication crisis, quantitative disciplines are going through an "inference crisis" [@rotello2015more; @starns2019assessing].
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
@@
 In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
+
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
@@
 
-Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
+Second, making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
@@
 in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+Possible tools to strengthen theoretical development relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].^[Although conceptually promising, in their current state, such formalized models typically work in spaces that are much lower in dimensionality than the complex systems in which we measure.
+Thus, future research should spend resources on attempting to quantitatively relate the abstract theoretical space to the complex measurement space.]
 
 ## Caveats
-Our study has several limitations that need to be considered when evaluating our results.
+Our study has several limitations that need to be considered when interpreting our results.
 

### 2023-01-10 RR_manuscript/Draft_RR.Rmd
some edits

@@
 When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e. more group-level effects = higher standard error).
-Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.
+Moreover, there was no team that declared to have made post-hoc changes to the analyses, thus we decided against including these two preregistered predictors in the model.
 
@@
 Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise version of the research question by preregistering their planned data analysis pipeline. 
-
-In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
+Preregistration, i.e.
+a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
+However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims:
 

### 2023-01-12 RR_manuscript/Draft_RR.Rmd
edits

--- 2022-11-19 RR_manuscript/Draft_RR.Rmd
@@
 The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)`-`r `round(predictor_n$max_predictor,1)`).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)- round(predictor_n$max_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+Possible tools to strengthen theoretical development are related to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
 
@@
 
-See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png>.
+See <https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy-all.png>.
 

### 2023-01-12 RR_manuscript/Draft_RR.Rmd

@@
 Details about the refitting procedure can be found at <https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow>.
+Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file  and variable naming conventions and the use of treatment contrasts instead of sum coding.
+All models converged ($\hat{R}$ was approximately 1) and only some had a small number of divergent transitions which were not deemed problematic (range XXX).
 
@@
 We also archived copies of our survey instruments from analysts and peer-reviewers.
+Further documents concerning the collaborative editing of the Registered Report can be found at <https://drive.google.com/drive/folders/1-DOcj1qtEkvWfzu_FrsxkIGfPS0DyLXB?usp=sharing>.
 
@@
 in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].^[Although conceptually promising, in their current state, such formalized models typically work in spaces that are much lower in dimensionality than the complex systems in which we measure.
-Thus, future research should spend resources on attempting to quantitatively relate the abstract theoretical space to the complex measurement space.]
+Possible tools to strengthen theoretical development relate to mathematically formalizing verbal expectations or using computational models [e.g., @van2020formalizing; @guest2021computational; @scheel2021hypothesis; @devezer2021case].
+Although conceptually promising, in their current state, such formalized models typically work in spaces that are much lower in dimensionality than the complex systems in which we measure.
+Thus, future research should spend resources on attempting to quantitatively relate the abstract theoretical space to the complex measurement space.
 

### 2023-01-12 RR_manuscript/Draft_RR.tex

@@
 Details about the refitting procedure can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow}.
+Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file and variable naming conventions and the use of treatment contrasts instead of sum coding.
+All models converged (\(\hat{R}\) was approximately 1) and only some had a small number of divergent transitions which were not deemed problematic (range XXX).
 
@@
 We also archived copies of our survey instruments from analysts and peer-reviewers.
+Further documents concerning the collaborative editing of the Registered Report can be found at \url{https://drive.google.com/drive/folders/1-DOcj1qtEkvWfzu_FrsxkIGfPS0DyLXB?usp=sharing}.
 
@@
 (A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95\% highest density intervals.
-(C) Mean posterior samples (white circles) and 80/95\% credible intervals for all predictors.}\label{fig:plot-meta2}
+(C) Mean posterior samples (white circles) and 80/95\% credible intervals for all predictors grouped into predictors related to (1) temporal window, (2) outcome variable, and (3) team/analysis.}\label{fig:plot-meta2}
 \end{figure}
@@
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
+Thus beyond a mere replication crisis, quantitative disciplines are going through an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
@@
 Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise version of the research question by preregistering their planned data analysis pipeline.
-
-In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
+Preregistration, i.e.~a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
+However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims:
+
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
@@
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development are related to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Possible tools to strengthen theoretical development relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
+Although conceptually promising, in their current state, such formalized models typically work in spaces that are much lower in dimensionality than the complex systems in which we measure.
+Thus, future research should spend resources on attempting to quantitatively relate the abstract theoretical space to the complex measurement space.
 
@@
 
-Our study has several limitations that need to be considered when evaluating our results.
+Our study has several limitations that need to be considered when interpreting our results.
 

### 2023-01-12 RR_manuscript/Draft_RR.Rmd
Fix typo

@@
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
-Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after sighting all analyses strategies.
+Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.
 

### 2023-01-12 scripts/r/04-1_refitted.Rmd
add code to extract divergent transitions from each model

@@
 ```
+
+```{r}
+#| label: get-divergent-transitions
+# Function to add up all DTs from a model
+get_dts <- function(df) {
+  sum(subset(df, Parameter == "divergent__")$Value)
+}
+
+# Load all models, find those with DTs and get min/max, store in tibble
+divergent_transitions <- 
+  dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
+  as_tibble() %>% 
+  transmute(
+    path = value,
+    mod_name = str_remove(path, here("data/analyses/models/")), 
+    mod_name = str_remove(mod_name, ".rds"), 
+    model = map(path, ~ readRDS(file = .))
+  ) %>% 
+  mutate(
+    nuts = map(model, nuts_params), 
+    dts = map(nuts, get_dts)) %>% 
+  unnest(dts) %>% 
+  select(mod_name, dts) %>% 
+  filter(dts != 0) %>% 
+  summarize(min_dt = min(dts), max_dt = max(dts))
+
+```

### 2023-01-13 scripts/r/04-1_refitted.Rmd

--- 2022-11-04 scripts/r/04-1_refitted.Rmd
@@
 ```
+
+```{r}
+#| label: get-divergent-transitions
+# Function to add up all DTs from a model
+get_dts <- function(df) {
+  sum(subset(df, Parameter == "divergent__")$Value)
+}
+
+# Load all models, find those with DTs and get min/max, store in tibble
+divergent_transitions <- 
+  dir_ls(path = here("data/analyses/models"), regexp = ".rds$") %>% 
+  as_tibble() %>% 
+  transmute(
+    path = value,
+    mod_name = str_remove(path, here("data/analyses/models/")), 
+    mod_name = str_remove(mod_name, ".rds"), 
+    model = map(path, ~ readRDS(file = .))
+  ) %>% 
+  mutate(
+    nuts = map(model, nuts_params), 
+    dts = map(nuts, get_dts)) %>% 
+  unnest(dts) %>% 
+  select(mod_name, dts) %>% 
+  filter(dts != 0) %>% 
+  summarize(n = nrow(.), min_dt = min(dts), max_dt = max(dts))
+
+```

### 2023-01-13 RR_manuscript/Draft_RR.Rmd
add info on divergent transitions in RR #288

@@
 Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file  and variable naming conventions and the use of treatment contrasts instead of sum coding.
-All models converged ($\hat{R}$ was approximately 1) and only some had a small number of divergent transitions which were not deemed problematic (range XXX).
+All models converged ($\hat{R}$ was approximately 1).
+Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58% of total number of samples), which the authors deemed not to be problematic.
 

### 2023-01-13 RR_manuscript/Draft_RR.Rmd
add acknowledgements and funding info

@@
 
+# Acknowledgements
+
+We would like to thank the editors David Sbarra and Julia Strand, Matthew Goldrick and two anonymous reviewers for their insightful comments and suggestions.
+
+The initiating authors (SC, JVC, TR) wish to express immense gratitude to all the other authors, without which this project would not have come to be.
+
+All remaining errors are the initiating authors' (SC, JVC, TR)
+
+# Funding
+
+Stefano Coretta was partially supported by the European Research Council Grant No. 742289 Human interaction and the evolution of spoken accent (2017–2022) awarded to Prof. Jonathan Harrington.
+
+Jalal Al-Tamimi was partially supported by the French Investissements d'Avenir - Labex EFL program (ANR-10- LABX-0083), contributing to the IdEx Université Paris Cité - ANR-18-IDEX-0001.
+
+George Moroz, Sita Carraturo: The research leading to these results has received funding from the Basic Research Program at the National Research University Higher School of Economics.
+
+Iñigo	Urrestarazu-Porta: The research leading to these results has received funding from the MADPAB (National Research Agency of the French republic, ANR-20-CE27-0007) and Monumenta Linguae Vasconum 6: avances en la cronología de la historia y la prehistoria de la lengua vasca projects (Ministry of Science and Innovation of the Spanish kingdom, PID2020-118445GB-I00).
+
+Constantijn	Kaland, Martine Grice: German Research Foundation (DFG) - Project-ID 281511265 - SFB 125.
+
+Nina R. Benway: This research was supported in part through computational resources provided by Syracuse University (NSF ACI-1341006; NSF ACI-1541396).
+
 \appendix

### 2023-01-14 scripts/r/04_refit/refit_tr.Rmd
🐛 - fix error for fs package not attached
🐛 - remove obsolete code that was causing errors

@@
 ```
-
-# summary
-
-## Load models
-
-```{r}
-#| label: load-models
-# This code will need to change eventually to pull rds files from OSF... for now it assumes they are stored in a folder called "models"
-
-msa_models <- dir_ls(path = here("data", "analyses", "models"), regexp = ".rds$") %>% 
-  as_tibble() %>% 
-  transmute(path = value, 
-    mod_name = str_remove(path, here("data", "analyses", "models/")), 
-    mod_name = str_remove(mod_name, ".rds"), 
-    model = map(path, ~ readRDS(file = .))) %>% 
-  separate(mod_name, 
-    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
-    sep = "_", remove = F) %>% 
-  unite(group, word1, word2, sep = "_") %>% 
-  dplyr::select(group, mod_name:model) %>% 
-  mutate(sum = map(model, clean_up)) %>% 
-  suppressWarnings() # because it warns every time that some coef have underscores and its annoying
-
-```
-
-## Table
-
-```{r}
-#| label: effect-table
-# Simple pandoc table of the models, estimates, se, etc.
-msa_models %>% 
-  unnest(sum) %>% 
-  select(-model) %>% 
-  knitr::kable(format = "pandoc")
-```
-
-## Plot
-
-```{r} 
-#| label: forest-plot
-# Simple forest plot of the estimates +/- SE
-msa_models %>% 
-  unnest(sum) %>% 
-  mutate(typicality_lab = if_else(typicality == "cat", 
-    "Typicality = categorical", "Typicality = continuous"), 
-    mod_name = fct_reorder(mod_name, estimate)) %>% 
-  ggplot() + 
-  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
-  aes(x = estimate, y = mod_name, color = group) + 
-  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
-    #color = "#cc0033", 
-    alpha = 0.5, size = 3, lineend = "round") + 
-  geom_vline(xintercept = 0, lty = "dashed", color = "grey") +
-  geom_point(pch = 21, stroke = 3, size = 3.1) + 
-  labs(y = "Model", x = "Estimate ± SE") + 
-  clean_theme() + 
-  theme(strip.text.x = element_text(hjust = 0))
-
-```

### 2023-01-14 scripts/r/04_refit/refit_jvc.Rmd
🐛 - fix error due to unzipped folder
🐛 - let code run; remove obsolete code

@@
 
+unzip(here("data", "analyses", "jvc", "anomalocaris_ornata", "MSA.zip"), exdir = here("data", "analyses", "jvc", "anomalocaris_ornata"))
+
 # Analyst team setup
@@
 
-if(F) {
+if(T) {
 msa_raw <- tibble(
@@
 ```
-
-# Results
-
-## Load models
-
-```{r}
-#| label: load-models
-
-msa_models <- dir_ls(path = here("data", "analyses", "models"), 
-  regexp = ".rds$") %>% 
-  as_tibble() %>% 
-  transmute(path = value, 
-    mod_name = str_remove(path, here("data", "analyses", "models/")), 
-    mod_name = str_remove(mod_name, ".rds"), 
-    model = map(path, ~ readRDS(file = .))) %>% 
-  separate(mod_name, 
-    into = c("word1", "word2", "mod_n", "outcome", "typicality"), 
-    sep = "_", remove = F) %>% 
-  unite(group, word1, word2, sep = "_") %>% 
-  dplyr::select(group, mod_name:model) %>% 
-  mutate(sum = map(model, clean_up)) %>% 
-  suppressWarnings() 
-```
-
-## Table
-
-```{r}
-#| label: effect-table
-
-# Simple pandoc table of the models, estimates, se, etc.
-msa_models %>% 
-  unnest(sum) %>% 
-  dplyr::select(-model) %>% 
-  knitr::kable(format = "pandoc")
-
-```
-
-## Plot
-
-```{r}
-#| label: forest-plot
-#| fig.height: 8
-
-# Simple forest plot of the estimates +/- SE
-msa_models %>% 
-  unnest(sum) %>% 
-  mutate(typicality_lab = if_else(typicality == "cat", 
-    "Typicality = categorical", "Typicality = continuous"), 
-    mod_name = fct_reorder(mod_name, estimate)) %>% 
-  ggplot() + 
-  facet_wrap(~ typicality_lab, ncol = 1, scales = "free") + 
-  aes(x = estimate, y = mod_name) + 
-  geom_vline(xintercept = 0, lty = 3) + 
-  geom_segment(aes(x = estimate - se, xend = estimate + se, yend = mod_name), 
-    color = "#cc0033", alpha = 0.5, size = 1.5, lineend = "round") + 
-  geom_point(color = "#cc0033", pch = 21, stroke = 1.5, size = 1.6) + 
-  labs(y = "Model", x = "Estimate ± SE") + 
-  clean_theme() + 
-  theme(strip.text.x = element_text(hjust = 0))
-```

### 2023-01-15 scripts/r/04_refit/refit_jvc.Rmd
🐛 - fix error from unzipped file plus fix path

@@
 #| label: trapezia_cantonensis
+
+unzip(here("data", "analyses", "jvc", "trapezia_cantonensis", "audio_chunks.zip"), exdir = here("data", "analyses", "jvc", "trapezia_cantonensis"))
 
@@
 
-beast_path <- "/Users/casillas/academia/research/in_progress/many_speech_analyses/many_analyses/./data/analyses/jvc/trapezia_cantonensis//audio_chunks/"
+beast_path <- "./data/analyses/jvc/trapezia_cantonensis/audio_chunks/"
 

### 2023-01-15 scripts/r/04_refit/refit_sc.Rmd
🐛 - remove code for model that was excluded

@@
 # since typ:AF = 0 and atyp:ANF = 0
-neosilurus_omanensis_3_f0varrat_cat <- brm(
-  PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
-  data = msa_data,
-  cores = 4,
-  threads = threading(2, grainsize = 100), 
-  backend = "cmdstanr",
-  file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
-  seed = my_seed
-)
+# neosilurus_omanensis_3_f0varrat_cat <- brm(
+#   PitchVariationRatioAtoU ~ effect_cat + Condition + (1|Participant) + (1|Adjective),
+#   data = msa_data,
+#   cores = 4,
+#   threads = threading(2, grainsize = 100), 
+#   backend = "cmdstanr",
+#   file = "data/analyses/models/neosilurus_omanensis_3_f0varrat_cat",
+#   seed = my_seed
+# )
 

### 2023-01-15 scripts/r/04_refit/refit_sc.Rmd
🐛 - fix wrong effect name

@@
   mutate(
-    eff_cont = scale(typ_mean) %>% as.numeric(),
+    effect_con = scale(typ_mean) %>% as.numeric(),
     duration = log(Duration..ms.) %>% scale() %>% as.numeric(),
@@
   duration ~
-    POS * condition * eff_cont +
+    POS * condition * effect_con +
     (POS|speaker) + (POS|AFI),
@@
   intensity ~
-    POS * condition * eff_cont +
+    POS * condition * effect_con +
     (POS|speaker) + (POS|AFI),
@@
   cfo1 ~
-    POS * condition * eff_cont +
+    POS * condition * effect_con +
     (POS|speaker) + (POS|AFI),
@@
   cfo2 ~
-    POS * condition * eff_cont +
+    POS * condition * effect_con +
     (POS|speaker) + (POS|AFI),
@@
   cfo3 ~
-    POS * condition * eff_cont +
+    POS * condition * effect_con +
     (POS|speaker) + (POS|AFI),

### 2023-01-16 scripts/r/04_refit/refit_tr.Rmd
🐛 - fix procambarus_maculosus

@@
 library(lme4)
+library(lmerTest)
 library(here)
@@
 
-data <- read.delim("./data/analyses/tr/selectedData.txt", header = T, sep = "") %>% 
+data <- read.delim("./data/analyses/tr/procambarus_maculosus/selectedData.txt", header = T, sep = "") %>% 
   as_tibble() # %>% 
@@
 
-data = read.csv("./data/analyses/tr/pervagor_meeki/Data/ManySpeech_Praat_merged_data.csv", header=T)
+# data = read.csv("./data/analyses/tr/pervagor_meeki/Data/ManySpeech_Praat_merged_data.csv", header=T)
 
 info <- data %>% 
-  select(sl_rowIdx, bundle, vowel, speaker, sex, typicality, word) %>% 
+  dplyr::select(sl_rowIdx, bundle, vowel, speaker, sex, typicality, word) %>% 
   unique()
@@
 # create a basis for B-splines
-basis <- create.bspline.basis(rangeval = c(0, 1), nbasis = nBasis, norder = nOrder)
+basis <- fda::create.bspline.basis(rangeval = c(0, 1), nbasis = nBasis, norder = nOrder)
 
 # define functional parameter object (will be used to estimate functional parameters later)
-fdParObj <- fdPar(fdobj = basis, Lfdobj = Lfdobj, lambda = lambda)
+fdParObj <- fda::fdPar(fdobj = basis, Lfdobj = Lfdobj, lambda = lambda)
 
@@
   group_by(sl_rowIdx) %>%
-  summarise(coef = c(smooth.basis(argvals = times_norm, y = F0, fdParObj)$fd$coefs),
+  summarise(coef = c(fda::smooth.basis(argvals = times_norm, y = F0, fdParObj)$fd$coefs),
             coefId = seq_len(nBasis)) %>%
@@
   select(-sl_rowIdx) %>% 
-  abind(along = 2) %>%
+  abind::abind(along = 2) %>%
   aperm(c(2,1))
@@
 # create functional data object
-y_fd <- fd(coef = coef, basisobj = basis)
+y_fd <- fda::fd(coef = coef, basisobj = basis)
 
@@
 nPCs <- 3
-y_pcafd <- pca.fd(y_fd, nharm = nPCs, fdParObj)
+y_pcafd <- fda::pca.fd(y_fd, nharm = nPCs, fdParObj)
 # saveRDS(y_pcafd, file = "./pcafd.rds")
@@
                       perturbation = c(-1, 0, 1)
-) %>% setDT
+) %>% data.table::setDT()
 
@@
 curves[, value := (y_pcafd$meanfd$coefs[,1] + perturbation * sd_score[PC] * y_pcafd$harmonics$coefs[,PC]) %>% 
-         fd(., basis) %>%
-         eval.fd(tx, .),
+         fda::fd(., basis) %>%
+         fda::eval.fd(tx, .),
        by = .(PC, perturbation)]
@@
 
-pl <- ggplot(reconstruct) + 
-  aes(x = time, y = value) + 
-  geom_line(size = 1.2) + 
-  facet_grid(k~per, labeller = label_parsed) +
-  xlab("Normalised Time") + ylab("F0 [Hz]") + theme + 
-  guides(linetype = guide_legend(override.aes = list(size = 1)))
-ggsave(filename = "./PCcurves.png", plot = pl, width = 25, height = 20, unit = "cm")
-
-pl <- ggplot(info %>% pivot_longer(cols = s1:s3) %>% 
-               mutate(score = case_when(name == "s1" ~ "s[1]",
-                                        name == "s2" ~ "s[2]",
-                                        name == "s3" ~ "s[3]"))) + 
-  aes(x = 0, y = value, fill = typicality) + 
-  facet_grid(score~., scales = "free_y", labeller = label_parsed, switch = "y") + 
-  geom_boxplot() + ylab("") + xlab("") +
-  theme + theme(strip.background.y = element_rect(fill = "white"), 
-                strip.placement = "outside",
-                legend.margin = margin(t = -15))
-ggsave(filename = "./PCscores.png", plot = pl, width = 18, height = 18, unit = "cm")
+# pl <- ggplot(reconstruct) + 
+#   aes(x = time, y = value) + 
+#   geom_line(size = 1.2) + 
+#   facet_grid(k~per, labeller = label_parsed) +
+#   xlab("Normalised Time") + ylab("F0 [Hz]") + theme + 
+#   guides(linetype = guide_legend(override.aes = list(size = 1)))
+# ggsave(filename = "./PCcurves.png", plot = pl, width = 25, height = 20, unit = "cm")
+# 
+# pl <- ggplot(info %>% pivot_longer(cols = s1:s3) %>% 
+#                mutate(score = case_when(name == "s1" ~ "s[1]",
+#                                         name == "s2" ~ "s[2]",
+#                                         name == "s3" ~ "s[3]"))) + 
+#   aes(x = 0, y = value, fill = typicality) + 
+#   facet_grid(score~., scales = "free_y", labeller = label_parsed, switch = "y") + 
+#   geom_boxplot() + ylab("") + xlab("") +
+#   theme + theme(strip.background.y = element_rect(fill = "white"), 
+#                 strip.placement = "outside",
+#                 legend.margin = margin(t = -15))
+# ggsave(filename = "./PCscores.png", plot = pl, width = 18, height = 18, unit = "cm")
 
@@
                       perturbation = seq(-1, 1, by = .25)
-) %>% setDT
+) %>% data.table::setDT()
 
@@
 
-pl <- ggplot(curves) +
-  aes(x = time, y = value, col = perturbation, group = perturbation) +
-  geom_line(size = 1.2) +
-  scale_color_gradient2(name = "P ", low = "cornflowerblue", mid = "grey", high = "darkgoldenrod1") +
-  facet_grid(~PC, labeller = PC_labeller) +
-  geom_line(data = curves[perturbation == 0], color = "black", size = 1.5) +
-  xlab("Normalised Time") + ylab("F0 [Hz]") +
-  theme + theme(legend.direction = "horizontal", 
-                legend.title = element_text(),
-                legend.text = element_text(size = 12))
-ggsave(filename = "./PCcurves_col.png", plot = pl, width = 20, height = 12, unit = "cm")
+# pl <- ggplot(curves) +
+#   aes(x = time, y = value, col = perturbation, group = perturbation) +
+#   geom_line(size = 1.2) +
+#   scale_color_gradient2(name = "P ", low = "cornflowerblue", mid = "grey", high = "darkgoldenrod1") +
+#   facet_grid(~PC, labeller = PC_labeller) +
+#   geom_line(data = curves[perturbation == 0], color = "black", size = 1.5) +
+#   xlab("Normalised Time") + ylab("F0 [Hz]") +
+#   theme(legend.direction = "horizontal", 
+#                 legend.title = element_text(),
+#                 legend.text = element_text(size = 12))
+# ggsave(filename = "./PCcurves_col.png", plot = pl, width = 20, height = 12, unit = "cm")
+
+```
+
+```{r procambarus_maculosus_models}
+
+s1.lmer <- lmer(s1 ~ typicality * sex + (sex | word) + (typicality | speaker), data = info,
+                control = lmerControl(optimizer = "optimx", optCtrl = list(method = "nlminb"))) %>% 
+  step() %>% get_model()
+
+# they did not interpret the models with typicality in there, so the minimum model we refit will be typicality + sex
+
+s2.lmer <- lmer(s2 ~ typicality * sex + (sex | word) + (typicality | speaker), data = info,
+                control = lmerControl(optimizer = "optimx", optCtrl = list(method = "nlminb"))) %>% 
+  step() %>% get_model()
+# s2 ~ typicality + (typicality | speaker), but failed to converge
+
+s2.lmer <- lmer(s2 ~ typicality + (1 | word) + (1 | speaker), data = info,
+                control = lmerControl(optimizer = "optimx", optCtrl = list(method = "nlminb"))) 
+s2.lmer %>% summary(corr = F)
+
+```
+
+```{r procambarus_maculosus_refitting}
+
+dat <- info %>% 
+  mutate(
+         # scale continuous variables
+         s1_s = (s1 - mean(s1, na.rm = TRUE)) / sd(s1,  na.rm = TRUE),
+         s2_s = (s2 - mean(s2, na.rm = TRUE)) / sd(s2,  na.rm = TRUE),
+         sex_s = as.factor(sex),
+         sex_s = C(sex_s, sum),
+         effect_cat = as.factor(typicality),
+         effect_cat = C(effect_cat, treatment)
+  )
+
+# run brms on standardized models
+procambarus_maculosus_1_pca1_cat <- brm(
+  s1_s ~ 
+         effect_cat + sex_s + 
+    (sex_s | word) + 
+    (effect_cat | speaker),
+  seed = 111,
+  data = dat, 
+  cores = 4,  
+  file = "./data/analyses/models/procambarus_maculosus_1_pca1_cat"
+  )
+
+# run brms on standardized models
+procambarus_maculosus_2_pca2_cat <- brm(
+  s2_s ~ 
+         effect_cat + 
+    (1 | word) +
+    (1 | speaker),
+  seed = 111,
+  data = dat, 
+  cores = 4,  
+  file = "./data/analyses/models/procambarus_maculosus_2_pca2_cat"
+  )
 

### 2023-01-16 scripts/r/04_refit/refit_tr.Rmd
🐛 - include pseudopleuronectes_assasi

@@
 ```
+
+# pseudopleuronectes_assasi
+
+```{r pseudopleuronectes_assasi_setup}
+
+# read csv
+mpa <- read.delim("./data/analyses/tr/pseudopleuronectes_assasi/alldata.txt", header = T, sep = "") %>% 
+  as_tibble()
+
+atypical <- subset(mpa,Typicality=="atypical")
+atypicalAF <- subset(atypical,Condition=="AF")
+atypicalNF <- subset(atypical,Condition=="NF")
+atypicalAF1 <- subset(atypicalAF,Vowel==1)
+atypicalAF2 <- subset(atypicalAF,Vowel==2)
+atypicalNF1 <- subset(atypicalNF,Vowel==1)
+atypicalNF2 <- subset(atypicalNF,Vowel==2)
+atypical1 <- subset(atypical,Vowel==1)
+atypical2 <- subset(atypical,Vowel==2)
+atypicalAFNF1 <- rbind(atypicalAF1,atypicalNF1)
+NF <- subset(mpa,Condition=="NF")
+NFa <- subset(NF,Typicality=="atypical")
+NFm <- subset(NF,Typicality=="medium")
+NFt <- subset(NF,Typicality=="typical")
+NF1 <- subset(NF,Vowel==1)
+NF2 <- subset(NF,Vowel==2)
+```
+
+```{r pseudopleuronectes_assasi_models}
+
+NF1DurTyp <- lmer(Duration~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
+NF1F0Typ <- lmer(MedianST~Sex+Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
+NF1IntTyp <- lmer(MedianInt~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
+NF1DistTyp <- lmer(FormDist~Typicality+(1|Speaker)+(1|TargetColor),data=NF1,REML=FALSE)
+
+```
+
+```{r pseudopleuronectes_assasi_refitting}
+
+# standardize
+NF1 <- NF1 %>% 
+    mutate(
+    Duration_s = (Duration - mean(Duration, na.rm = TRUE)) / sd(Duration,  na.rm = TRUE),
+    MedianST_s = (MedianST - mean(MedianST, na.rm = TRUE)) / sd(MedianST,  na.rm = TRUE),
+    MedianInt_s = (MedianInt - mean(MedianInt, na.rm = TRUE)) / sd(MedianInt,  na.rm = TRUE),
+    FormDist_s = (FormDist - mean(FormDist, na.rm = TRUE)) / sd(FormDist,  na.rm = TRUE),
+    effect_cat = C(as.factor(Typicality), treatment),
+    sex_s = as.factor(Sex),
+    sex_s = C(sex_s, sum)
+  )
+
+pseudopleuronectes_assasi_1_dur_cat <- brm(
+  Duration_s ~ 
+         effect_cat + 
+         (1|Speaker) + 
+         (1|TargetColor),
+  seed = 111,
+  data = NF1, 
+  cores = 4,  
+  file = "./data/analyses/models/pseudopleuronectes_assasi_1_dur_cat"
+  )
+
+pseudopleuronectes_assasi_2_f0_cat <- brm(
+  MedianST ~ 
+         effect_cat + Sex +
+         (1|Speaker) + 
+         (1|TargetColor),
+  seed = 111,
+  data = NF1, 
+  cores = 4,  
+  file = "./data/analyses/models/pseudopleuronectes_assasi_2_f0_cat"
+  )
+
+pseudopleuronectes_assasi_3_int_cat <- brm(
+  FormDist_s ~ 
+         effect_cat + 
+         (1|Speaker) + 
+         (1|TargetColor),
+  seed = 111,
+  data = NF1, 
+  cores = 4,  
+  file = "./data/analyses/models/pseudopleuronectes_assasi_3_int_cat"
+  )
+
+pseudopleuronectes_assasi_4_formants_cat <- brm(
+  MedianInt_s ~ 
+         effect_cat + 
+         (1|Speaker) + 
+         (1|TargetColor),
+  seed = 111,
+  data = NF1, 
+  cores = 4,  
+  file = "./data/analyses/models/pseudopleuronectes_assasi_4_formants_cat"
+  )
+
+```

### 2023-01-16 scripts/r/04_refit/refit_tr.Rmd
🐛 - fix wrong name of predictor in pseudopleuronectes_assasi_2_f0_cat

@@
   MedianST ~ 
-         effect_cat + Sex +
+         effect_cat + sex_s +
          (1|Speaker) + 

### 2023-01-16 RR_manuscript/supplementary_materials.Rmd

@@
 # Read in primary coding sheet
-the_sheet <- "data/analyses/analyses_coding.csv"
+the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"
 
@@
 msa_models_unique <- left_join(
-  read_csv(the_sheet) %>% 
+  read_sheet(the_sheet) %>% 
     filter(added_on_osf == "yes") %>% 

### 2023-01-16 docs/icphs2023/includes/tex/doc_prefix.tex

--- 2022-11-12 docs/icphs2023/main.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  a4paper,
-  11pt,
-  twocolumn]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{48,48,48}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{\textbf{#1}}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.87,0.87,0.75}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.86,0.86,0.80}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.76,0.75,0.62}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.75,0.75,0.82}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.94,0.87,0.69}{#1}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.94,0.94,0.82}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.94,0.94,0.56}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{1.00,0.81,0.69}{\textbf{#1}}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.86,0.64,0.64}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.80,0.80,0.80}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.80,0.58,0.58}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.50,0.62,0.50}{\textbf{#1}}}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-%------------------------------------------------------------------------------%
-% PAPER TEMPLATE FOR ICPHS 2023 Prague                                         %
-%                                                                              %
-% Original template downloaded from:                                           %
-% http://www.icphs2023.org/call-for-papers/                                    %
-%                                                                              %
-% Reformatted to work with Rmarkdown and R by:                                 %
-% Joseph V. Casillas | Rutgers Univesity |11/11/2022                           %
-%                                                                              %
-% Available for download at:                                                   %
-% https://github.com/jvcasillas/icphs2023_rmd_template                         %
-%------------------------------------------------------------------------------%
-
-% Packages
-\usepackage{./includes/tex/icphs2023}
-\usepackage{metalogo} 
-\usepackage{epstopdf}
-\usepackage{tipa}
-
-% Links and urls must be black
-%\hypersetup{urlcolor=black, citecolor=black, linkcolor=black}
-
-% Packages removed from icphs2023.sty because of conflicts
-% They have been added to the .Rmd yaml front matter
-% \usepackage[latin1]{inputenc}
-% \usepackage[T1]{fontenc}
-% \usepackage[leqno,fleqn]{amsmath}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-
-\author{}
-\date{\vspace{-2.5em}}
-
-\begin{document}
-
 \title{Paper template for {ICPhS} 2023 Prague}
@@
 lines).}
-
-\section{Introduction}
-
-The following rules apply to all submitted papers:
-
-\begin{itemize}
-  \item they must be written in English
-  \item they must not contain the name(s) of the author(s) (for
-anonymous review)
-  \item the maximum is four pages for Congress papers, plus up to one additional page of references. Papers for Plenary lectures can be longer
-  \item they must be submitted in PDF format (cf.\ Section~4)
-  \item the paper submission will occur via a web interface
-\end{itemize}
-
-This paper template can be found on the conference website. If there are
-special questions or wishes regarding paper preparation and submission
-for ICPhS 2023, correspondence should be addressed to
-\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}}.
-Information for full paper submission will be available on the web at
-\url{https://www.icphs2023.org/}.
-
-\section{Page layout and style}
-
-The page layout should conform to the following rules. By far the
-easiest way to meet these requirements is to use the supplied templates
-and check details against this example file. If for some reason you
-cannot use the template, please follow these rules as carefully as
-possible, or contact the editors at
-\href{mailto:icphs2023@guarant.cz}{\nolinkurl{icphs2023@guarant.cz}} for
-further instructions.
-
-\subsection{Basic layout features}
-
-\begin{itemize}
-\item The layout is appropriate for A4 format.
-\item Two columns are used
-  except for the title part and possibly for large figures that need a
-  full page width.
-\item Left margin is 20 mm. Right margin will depend on
-  the size of the paper. Column width is 80 mm.
-\item Spacing between
-  columns is 10 mm.
-\item Top margin 25 mm (except first page which has 30
-  mm to the title top). Bottom margin will depend on the size of the
-  paper.
-\item Text height (without headers and footers) is a maximum of
-  235 mm.  Headers and footers should be left empty
-\item Check indentations
-  and spacings by comparing with this example file.
-\end{itemize}
-
-\subsubsection{Headings}
-
-Section headings are centered in boldface with capitalized letters.
-Sub-headings start at the left margin in the column with the first
-letter capitalized and the rest of the heading in lower case.
-Sub-sub-headings appear like sub-headings, except that they are in
-italics and not boldface. See examples in this file. No more than 3
-levels of headings should be used. Empty lines should be left above and
-below each section heading.
-
-\subsection{Text font}
-
-Times or Times New Roman font is used for the main text. Recommended
-font size is 11 points. Other font types may be used if needed for
-special purposes. If using any non-Unicode fonts, these must be embedded
-in the final PDF file.
-
-The \LaTeX{} template can be used either with plain \LaTeX{} or
-\XeLaTeX.
-
-\subsection{Figures}
-
-All figures should be centered on the column (or page, if the figure
-spans both columns). Figure captions should follow each figure and have
-the format given in Fig. \ref{fig:vowels}.
-
-Figures should preferably be line drawings. If they contain grey shades
-or colours, it should be checked that they print well on a high-quality
-noncolour laser printer.
-
-\begin{figure}[!ht]
-\begin{center}
-\includegraphics[width=6cm]{./includes/figures/ipa.eps}
-\caption{The vowel chart used in the International Phonetic
-Alphabet (IPA).}\label{fig:vowels}
-\end{center}
-\end{figure}
-
-\subsection{Tables}
-
-An example of a table is shown as
-Table\textasciitilde{}\ref{tab:decibel}. Somewhat different styles are
-allowed according to the type and purpose of the table. Colour should
-not be used, but grey shading is allowed. There should be a margin of
-6\textasciitilde points (pt) above and below the table.
-
-The caption text may be above or below the table, but this should be
-consistent throughout the submission. Left and right indentation of the
-caption should be 0.5\textasciitilde cm.
-
-\begin{table}[!ht]
-  \begin{center}
-  \begin{tabular}{|c|c|}
-  \hline
-  \rowcolor[gray]{.75}
-  ratio    & Decibels\\
-  \hline
-  $1/1$    & $0$\\
-  $2/1$    & $6$\\
-  $3.16$   & $10$\\
-  $1/10$   & $-20$\\
-  $10/1$   & $20$\\
-  $100/1$  & $40$\\
-  $1000/1$ & $60$\\
-  \hline
-  \end{tabular}
-  \caption{This is an example of a table showing Decibel (dB)
-  ratios.}\label{tab:decibel}
-  \end{center}
-\end{table}
-
-\subsection{Equations}
-
-Equations should be placed on separate lines and numbered. An example of
-an equation is \begin{equation}\label{eq:tzero}
-T_0 = \frac{1}{f_0}.
-\end{equation} Numbers of equations can be on the right or on the left
-margin of the text column.
-
-\subsection{Examples}
-
-Examples from other languages can either be presented in the body text,
-or, if referred to elsewhere or particularly long and complex, can be
-put on a separate, numbered line, as should be done for equations.
-
-\subsection{Phonetic fonts}
-
-We recommend that you use the \textsc{tipa} package for IPA phonetic
-symbols. For information about how to access Unicode fonts in the Word
-template, see \cite{IPA-SIL} or \cite{IPA-KEYBOARD}. The font you use
-must be embedded. Please remember to check this, e.g.~by inspecting the
-``Document Properties --- Fonts'\,' in Acrobat Reader.
-
-\subsection{Page numbering}
-
-Page numbers will be added electronically to the document later.
-\textit{Please do not add page numbers and please do not insert
-any footers or headers!}
-
-\subsection{References}
-
-Please use just the reference number in square brackets. Formulations
-with author names like ``\ldots~as Ladefoged \cite{Ladefoged:2003}
-showed that \ldots'' are acceptable but not ``as shown in {[}Ladefoged,
-3{]}'' or ``as shown in (Ladefoged {[}3{]})''.
-
-References are to be numbered in alphabetical order. Please double-check
-the final version of your paper with regard to the correct
-correspondence of references to their numbers.
-
-\subsection{Hyperlinks}
-
-Links to URLs or email addresses should be formatted as normal text,
-\textit{not} as hyperlinks and not blue or underlined etc. Usually
-hyperlinks to web pages are listed in the references section. If
-required, line breaks can be placed within URLs after slashes or dashes
-(cf.\textasciitilde{}\cite{IPA-SIL,IPA-KEYBOARD}), but doublecheck that
-no hyphens are inserted.
-
-\subsection{Footnotes and endnotes}
-
-If footnotes cannot be avoided they should appear as
-endnotes.\footnote{This footnote appears here as an endnote.}
-
-\section{Multimedia files}
-
-Multimedia data that are part of the paper are to be embedded in the
-submitted PDF; they cannot be submitted as supplementary data. Any
-images are to be included in the paper as Figures (see Section 2.3
-above). It is the authors' responsibility to check image quality ahead
-of submission. Audio examples are to be embedded within the PDF. To do
-this, authors can generate the PDF, and then embed the audio files using
-Adobe Acrobat Professional, or other software that offers the same
-outcome, so that the audio is included in the PDF. The presence of audio
-data should be identified in the text.
-
-We encourage authors to illustrate video data using still photographs
-from the video, and to include them as figures in the PDF. We cannot
-accept embedded video files, but authors are welcome to refer readers to
-a URL on the internet where these can be viewed.
-
-\section{PDF details}
-
-PDF files submitted must comply with the following requirements:
-
-\begin{enumerate}
-\item all special fonts and symbols must be embedded in the PDF
-  file so that correct rendering of the PDF does not depend on the
-  fonts installed on the viewer's computer
-\item there must be no
-  password protection on the PDF file, i.e. PDF files must not be
-  protected by PDF security in any way, i.e. content extraction,
-  document assembly, high resolution printing etc. must not be
-  forbidden
-\item PDF files should not contain any colours, hyperlinks,
-  multimedia or 3D content, and no JavaScript or forms
-\item PDF files
-  should be no larger than 5 MB.
-\end{enumerate}
-
-\section{Anonymity}
-
-In ICPhS 2023 submissions, an anonymous reviewing process will be used.
-This means that for the first submission the name(s) of the author(s)
-and their affiliation(s) \emph{must not} be mentioned. In addition,
-please refrain from using acknowledgements. Please also try to make your
-own previous research as anonymous as possible. As an example: do not
-write ``In our previous study \cite{Stevens:1999} we could show\ldots''
-but ``As shown in \cite{Stevens:1999}\ldots''. Or refer to your own
-published or otherwise widely known work, and to that of the other
-authors, in the ``Julius Caesar style'', i.e.~in the third person (for
-example: his work, her work, their work). Reference as ``anonymous''
-only work that you or the other authors have submitted for publication,
-but which has not yet been published, e.g.~\cite{Anonymous:submitted}.
-
-Please make sure that no author details appear in the Document
-Properties of the PDF file.
-\emph{For the revised paper submission author details are of course needed}.
-Acknowledgements and references to one's own work are possible as usual.
-
-\section{Format of references}
-
-References are formatted using the IEEE standard (available in various
-reference management systems like Zotero or Mendeley). If you do not use
-a reference management system, please use the examples provided for
-monographs \cite{Fant:1960}, contributions to volumes
-\cite{Stevens:1999}, journal articles \cite{Beattie/etal:1982}, articles
-in conference proceedings \cite{Ladefoged:2003}. Abbreviations of
-well-known conferences and journals are possible
-\cite{Peterson/Barney:1952}. Software tools \cite{Boril/Skarnitzl:2016}
-are referenced according to authors' instructions.
-
-\section{R scripts}
-
-You can use knitr code chunks like in any .Rmd document:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\DecValTok{2} \SpecialCharTok{+} \DecValTok{2}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## [1] 4
-\end{verbatim}
-
-This includes inline code: 2 + 2 = 4.
-
-R scripts can be loaded as well:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{source}\NormalTok{(}\StringTok{"./includes/scripts/analysis.R"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-Which means you have access to any objects assigned in the script, like
-Figure \ref{fig:ex_plot}:
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{cars\_plot}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{figure}[!h]
-\caption{This is a figure caption.}\label{fig:ex_plot}
-
-\begin{center}\includegraphics{main_files/figure-latex/ex_plot-1} \end{center}
-
-\end{figure}
-
-\bibliographystyle{./includes/bib/IEEEtran.bst}
-\bibliography{./includes/bib/icphs2023.bib}
-
-\theendnotes
-
-\end{document}

### 2023-01-16 scripts/r/04-1_refitted.Rmd

@@
 ```{r coding}
-the_sheet <- "data/analyses/analyses_coding.csv"
+the_sheet <- "https://docs.google.com/spreadsheets/d/1OOXB-8Uk-fh_urw0Lm4DC0jBueXLIb4Bm-a9--UVXOw/edit?usp=sharing"
 
-coding <- read_csv(the_sheet) %>%
+coding <- read_sheet(the_sheet) %>%
   drop_na(model_n)
@@
 ```{r intake}
-other_sheet <- "data/metadata/team_animal_coord.csv"
+other_sheet <- "https://docs.google.com/spreadsheets/d/1KAZC2vyteTfGE6mlwOiz9b8F9VghDYLGsOzmWaNbmEE/edit?usp=sharing"
 
-team_animal_coord <- read_csv(other_sheet)
+team_animal_coord <- read_sheet(other_sheet)
 

### 2023-01-16 scripts/r/09_credit_taxonomy.Rmd

--- 2022-11-19 scripts/r/09_credit_taxonomy.Rmd
@@
     labs = case_when(
-      country == "Australia" ~ glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
-      country == "Hong Kong SAR, China" ~ glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
-      country == "Nigeria" ~ glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
-      country == "Norway" ~ glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
-      country == "Saudi Arabia" ~ glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
-      country == "Serbia" ~ glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
-      country == "Switzerland" ~ glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
-      country == "Austria" ~ glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
-      country == "Russia" ~ glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
-      country == "Spain" ~ glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
-      country == "Brazil" ~ glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
-      country == "Netherlands" ~ glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
-      country == "New Zealand" ~ glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
-      country == "Canada" ~ glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
-      country == "France" ~ glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
-      country == "Germany" ~ glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
-      country == "United Kingdom" ~ glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
-      country == "United States" ~ glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
+      country == "Australia" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/australia-emoji.png'{close}"), 
+      country == "Hong Kong SAR, China" ~ 
+        glue("{open}'https://emojipedia-us.s3.dualstack.us-west-1.amazonaws.com/thumbs/120/apple/325/flag-hong-kong-sar-china_1f1ed-1f1f0.png'{close}"), 
+      country == "Nigeria" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/nigeria-emoji.png'{close}"), 
+      country == "Norway" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/norway-emoji.png'{close}"), 
+      country == "Saudi Arabia" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/saudi-arabia-emoji.png'{close}"), 
+      country == "Serbia" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/serbia-emoji.png'{close}"), 
+      country == "Switzerland" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/switzerland-emoji.png'{close}"),
+      country == "Austria" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/austria-emoji.png'{close}"),
+      country == "Russia" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/russia-emoji.png'{close}"),
+      country == "Spain" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/spain-emoji.png'{close}"),
+      country == "Brazil" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/brazil-emoji.png'{close}"),
+      country == "Netherlands" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/netherlands-emoji.png'{close}"),
+      country == "New Zealand" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/new-zealand-emoji.png'{close}"),
+      country == "Canada" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/canada-emoji.png'{close}"),
+      country == "France" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/france-emoji.png'{close}"),
+      country == "Germany" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/germany-emoji.png'{close}"),
+      country == "United Kingdom" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/united-kingdom-emoji.png'{close}"),
+      country == "United States" ~ 
+        glue("{open}'https://img.icons8.com/emoji/512/united-states-emoji.png'{close}")
     ), 
-    primary_affiliation_country = fct_reorder(primary_affiliation_country, n, max))
+    country = fct_reorder(country, n, max))
 
@@
   ggplot() + 
-  aes(x = n, y = primary_affiliation_country) + 
-  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
-  geom_point() + 
-  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
-  theme_bw(base_size = 9) + 
+  aes(x = n, y = country) + 
+  geom_segment(aes(x = 0, xend = n, yend = country), size = 2, 
+    color = "grey25", lineend = "round") + 
+  geom_point(size = 6) + 
+  geom_text(aes(label = n), color = "white", size = 3) + 
+  labs(x = "n", y = NULL, 
+    title = "Number of analysts by country", 
+    subtitle = glue("(n = {sum(n_countries$n)})")) + 
+  theme_bw(base_size = 13, base_family = "Times") + 
   scale_y_discrete(name = NULL, labels = n_countries$labs) + 
-  theme(axis.text.y = element_markdown(color = "black"))
+  theme(axis.text.y = element_markdown(color = "black", vjust = 0.65), 
+    panel.grid.major = element_line(colour = 'grey90', size = 0.15),
+    panel.grid.minor = element_line(colour = 'grey90', size = 0.15))
 
+n_countries %>% 
+  arrange(desc(n)) %>% 
+  transmute(Country = glue("{flag} {country}"), n) %>% 
+  knitr::kable(format = "pandoc")
 ```

### 2023-01-17 scripts/r/04_refit/refit_jvc.Rmd
fix path

@@
 
+Currently, the GitHub repo "many_speech" is not available. We have added a zipped version of the GH repo archive (downloaded from OSF) to the OSF component.
+
 ```{r}
 #| label: cromileptes_saxatilis
+
+unzip(here("data", "analyses", "jvc", "cromileptes_saxatilis", "many_speech.zip"), exdir = here("data", "analyses", "jvc", "cromileptes_saxatilis"))
 

### 2023-01-17 RR_manuscript/supplementary_materials.Rmd
include sankey plot in supplementary materials

@@
 ---
-title: "Supplementary materials"
+title: |
+  Multidimensional signals and analytic flexibility:  
+  Estimating degrees of freedom in human speech analyses
+subtitle: "Supplementary materials"
+author: |
+  Initiating authors:  
+  Stefano Coretta, Joseph V. Casillas, and Timo Roettger
 output: pdf_document
@@
 knitr::opts_chunk$set(echo = F, message = F, warning = F)
-knitr::opts_knit$set(root.dir = here::here())
 library("dplyr")
@@
 library("kableExtra")
+```
+
+```{r}
+#| label: sankey-plot
+#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
+#| out.width: "100%"
+knitr::include_graphics(path = here("figs", "flow_outcome.png"))
 ```
@@
     distinct(), 
-  readRDS("./data/peer_review/msa_reviews.rds") %>% 
+  readRDS(here("./data/peer_review/msa_reviews.rds")) %>% 
     select(animal = Q3, phon_rating = Q5_2, stat_rating = Q5_3, 
@@
   left_join(., 
-    read_csv("./data/questionnaires/msa_intake_form_untidy.csv") %>%
+    read_csv(here("./data/questionnaires/msa_intake_form_untidy.csv")) %>%
       filter(added_on_osf == "yes", 

### 2023-01-17 scripts/r/04_refit/refit_jvc.Rmd
Fix path to processed data

@@
 
-cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "processed_data", "NF_durations.csv")) %>% 
+cromileptes_saxatilis_durs <- read_csv(here("data", "analyses", "jvc", "cromileptes_saxatilis", "many_speech", "processed_data", "NF_durations.csv")) %>% 
   filter(typicality != "medium")

### 2023-01-18 RR_manuscript/supplementary_materials.Rmd

--- 2023-01-16 RR_manuscript/supplementary_materials.Rmd
@@
 
-```{r setup}
-#| label: setup
-#| include: false
+```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = F, message = F, warning = F)
@@
 library("kableExtra")
+```
+
+```{r}
+#| label: sankey-plot
+#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
+#| out.width: "100%"
+knitr::include_graphics(path = "./figs/flow_outcome.png")
 ```
@@
 # Create DF of all members with leader names
-team_leaders <- readr::read_csv(
-  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
+team_leaders <- readr::read_csv("./data/questionnaires/msa_intake_form.csv") %>%
   select(ResponseId, Q6) %>% # Questions asking for team leader
@@
 # Vector of teams with submitted analyses (for subsetting)
-submitted_animals <- readRDS(here("./data/analyses/msa_models.rds")) %>% 
+submitted_animals <- readRDS("./data/analyses/msa_models.rds") %>% 
   pull(animal) %>% 

### 2023-01-18 scripts/r/07_team-sds.Rmd

@@
 
-1. Get a list of the subset of teams that need to be downloaded (Max = 30 because the final model only includes 30 teams). 
+1. Get a list of the subset of teams that need to be downloaded (Max = 33 because the final model only includes 33 teams). 
 2. Download the OSF components of the aforementioned subset of teams.
@@
 
-Of the 30 teams included in the meta-analysis, `r length(final_team_names)` included either F0, duration or intensity in the analyses. 
+Of the `r length(teams)` teams included in the meta-analysis, `r length(final_team_names)` included either F0, duration or intensity in the analyses. 
 Next, we download the OSF components of those `r length(final_team_names)` teams.
@@
 
+Note: Downloading from OSF can be buggy due to server limitations. 
+If you have any issues getting all of the components, you can download them manually here: <https://osf.io/n3fyd/>.
+
 # Get means and SDs
@@
 We can pull in specific lines of code with the `source_part` function. 
-If we can't source the lines directly without touching the refit_xx.Rmd files (because *some* people refuse to use `here`), then we will have to copy/paste code to this file and adjusts the paths like heathens.
+If we can't source the lines directly without touching the refit_xx.Rmd files, then we will have to copy/paste code to this file and adjusts the paths.
 
@@
   start = 131, 
-  end = 181
+  end = 183
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 392, 
-  end = 441
+  start = 394, 
+  end = 443
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 1379, 
-  end = 1395
+  start = 1387, 
+  end = 1403
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 478, 
-  end = 489
+  start = 480, 
+  end = 491
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 527, 
-  end = 530
+  start = 533, 
+  end = 536
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 602, 
-  end = 606
+  start = 608, 
+  end = 612
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 644, 
-  end = 662
+  start = 650, 
+  end = 668
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 714, 
-  end = 845
+  start = 720, 
+  end = 859
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 955, 
-  end = 962
+  start = 961, 
+  end = 968
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 1054, 
-  end = 1067
+  start = 1060, 
+  end = 1073
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 1295, 
-  end = 1327
+  start = 1303, 
+  end = 1335
   )
@@
   file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
-  start = 1206, 
-  end = 1214
+  start = 1214, 
+  end = 1222
   )
@@
 
-# Super long because somebody refuses to use `here` and I don't want to modify `refit_sc.Rmd`
 # The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
@@
 final_teams %>% filter(animal == "saron_pictus") %>% pull(outcome) == saron_pictus_df %>% pull(dv)
+```
+
+### sphyrna_ellioti
+
+```{r}
+#| label: sphyrna_ellioti
+#| eval: true
+
+source_part(
+  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
+  start = 537, 
+  end = 558
+  )
+
+# Means and SDs
+sphyrna_ellioti_df <- tribble(
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "sphyrna_ellioti", 1, "duration",  mean(pro_df$Duration..ms.), sd(pro_df$Duration..ms.), 
+  "sphyrna_ellioti", 2, "intensity", mean(pro_df$Intensity),     sd(pro_df$Intensity), 
+  "sphyrna_ellioti", 3, "f0",        mean(pro_df$fo1),          sd(pro_df$fo1), 
+  "sphyrna_ellioti", 4, "f0",        mean(pro_df$fo2),          sd(pro_df$fo2), 
+  "sphyrna_ellioti", 5, "f0",        mean(pro_df$fo3),          sd(pro_df$fo3)
+)
+
+# Check n models == n DVs
+final_teams %>% filter(animal == "sphyrna_ellioti") %>% nrow == nrow(sphyrna_ellioti_df)
+
+# Check DVs are the same as those listen in model excel
+final_teams %>% filter(animal == "sphyrna_ellioti") %>% pull(outcome) == sphyrna_ellioti_df %>% pull(dv)
 ```
@@
   file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
-  start = 1532, 
-  end = 1600
+  start = 1592, 
+  end = 1661
   )
@@
   file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
-  start = 1309, 
-  end = 1420
+  start = 1369, 
+  end = 1480
   )
@@
 
+### procambarus_maculosus
+
+```{r}
+#| label: procambarus_maculosus
+#| eval: true
+source_part(
+  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
+  start = 1153, 
+  end = 1288
+  )
+
+# Means and SDs
+procambarus_maculosus_df <- tribble(
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "procambarus_maculosus", 1,  "f0",  mean(info$s1), sd(info$s1), 
+  "procambarus_maculosus", 2,  "f0",  mean(info$s2), sd(info$s2)
+)
+
+# Check n models == n DVs
+final_teams %>% filter(animal == "procambarus_maculosus") %>% nrow == nrow(procambarus_maculosus_df)
+
+# Check DVs are the same as those listen in model excel
+final_teams %>% filter(animal == "procambarus_maculosus") %>% pull(outcome) == procambarus_maculosus_df %>% pull(dv)
+
+```
+
 ### procambarus_mahogoni
@@
   file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
-  start = 1742, 
-  end = 1745
+  start = 1802, 
+  end = 1812
   )
@@
 
+### pseudopleuronectes_assasi
+
+```{r}
+#| label: pseudopleuronectes_assasi
+#| eval: true
+source_part(
+  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
+  start = 1872, 
+  end = 1892
+  )
+
+# Means and SDs
+pseudopleuronectes_assasi_df <- tribble(
+  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
+  "pseudopleuronectes_assasi", 1,  "duration",  mean(NF1$Duration), sd(NF1$Duration), 
+  "pseudopleuronectes_assasi", 2,  "f0",        mean(NF1$MedianST), sd(NF1$MedianST), 
+  "pseudopleuronectes_assasi", 3,  "intensity", mean(NF1$MedianInt), sd(NF1$MedianInt)
+)
+
+# Check n models == n DVs
+final_teams %>% filter(animal == "pseudopleuronectes_assasi") %>% nrow == nrow(pseudopleuronectes_assasi_df)
+
+# Check DVs are the same as those listen in model excel
+final_teams %>% filter(animal == "pseudopleuronectes_assasi") %>% pull(outcome) == pseudopleuronectes_assasi_df %>% pull(dv)
+```
+
 ### trachyphyllia_lappa
@@
   file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
-  start = 49, 
-  end = 134
+  start = 50, 
+  end = 135
   )
@@
   saron_pictus_df, 
+  sphyrna_ellioti_df, 
   trachurus_riukiuensis_df, 
@@
   pervagor_meeki_df, 
+  procambarus_maculosus_df, 
   procambarus_mahogoni_df, 
+  pseudopleuronectes_assasi_df,
   trachyphyllia_lappa_df

### 2023-01-18 RR_manuscript/supplementary_materials.Rmd
♻️ - render supplementary_materials

@@
 #| out.width: "100%"
-knitr::include_graphics(path = "./figs/flow_outcome.png")
+knitr::include_graphics("../figs/flow_outcome.png", error = FALSE)
 ```

### 2023-01-18 data/analyses/README.Rmd
update all READMEs

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = F)
 ```
+
+The `analyses` directory contains all of the analytic teams' data (downloaded from OSF). 
+The teams' analyses were refit by the initiating authors (sc, jvc, and tr) and the corresponding rds files are stored in the `models` directory. 
+The file `msa_mean_sd_df.csv` contains the unstandardized mean and standard deviations of every submitted model containing pitch, duration or intensity as the outcome measure. 
+Finally, `msa_models.rds` contains the coding sheet completed by the initiating authors of every submitted analysis.
+
+```{r, 'analysis-structure', comment=NA, echo=F}
+fs::dir_tree(recurse = 0)
+```

### 2023-01-19 RR_manuscript/Draft_RR.tex

@@
 Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file and variable naming conventions and the use of treatment contrasts instead of sum coding.
-All models converged (\(\hat{R}\) was approximately 1) and only some had a small number of divergent transitions which were not deemed problematic (range XXX).
+All models converged (\(\hat{R}\) was approximately 1).
+Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58\% of total number of samples), which the authors deemed not to be problematic.
 
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
+Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 32 teams to be eligible to be included in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
-Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after sighting all analyses strategies.
+Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.
 
@@
 
-The included analyses were provided by 30 teams, comprising 109 analysts, with a median of 3.0 individuals per team.
+The included analyses were provided by 32 teams, comprising 117 analysts, with a median of 3.0 individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had a median of 5.8 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
-The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with a median of 70.0.
+Analysts had a median of 5.4 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 46.4 to 92.0 with a median of 70.0.
 We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 119 individual models (including 192 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
-Thirty-six percent of the models used f0 as the outcome variable, 35\% used a measure of duration, 12\% used vowel formants, 14\% intensity, and 3\% other measures.
-
-Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
-Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
+Thirty-seven percent of the models used f0 as the outcome variable, 33\% used a measure of duration, 13\% used vowel formants, 15\% intensity, and 3\% other measures.
+
+Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 45\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 3\% from the whole sentence, and 3\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
 For example, if we consider those analyses that target f0, we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
@@
 The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
-Among the possible operationalizations, 72\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 24\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
+Among the possible operationalizations, 69\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 28\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
 Note that the design of the experiment alongside its description indicated that the experiment was designed to categorically operationalize typicality.
@@
 
-The majority of models were run within a frequentist framework (83\%).
-Seventeen percent were run within a Bayesian framework.
+The majority of models were run within a frequentist framework (84\%).
+Sixteen percent were run within a Bayesian framework.
 While teams almost exclusively used linear models to analyze their data (98\%), teams differed drastically in how they accounted for dependencies within the data.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-Eight percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
+Nine percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+Sixty-two percent specified random intercepts only, and 29\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects included 2.5 random terms in their models.
-Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
-
-When considering both acoustic and statistical analyses, we have found a grand total of 104 different analytic pipelines.
+Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 52 different model specifications.
+
+When considering both acoustic and statistical analyses, we have found a grand total of 119 different analytic pipelines.
 In other words, each individual analysis submitted was unique.
@@
 The question arises whether these unique analysis pipelines led to different conclusions.
-Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 170 critical model coefficients, 37 were claimed to show a statistically reliable effect (21.8\%).
+Thirteen teams out of the thirty-three (39.3939394\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
+Of the 170 critical model coefficients, 45 were claimed to show a statistically reliable effect (23.4\%).
 
@@
 \caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis.
-The data set included analyses from 30 teams and  109 analysts.}
+The data set included analyses from 32 teams and  117 analysts.}
 \centering
@@
  & Team size & 1.0 -- 12.0 & 3.0\\
- & Years after PhD & -3.8 -- 12.4 & 5.8\\
- & Prior belief & 48.5 -- 92.0 & 70.0\\
- & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
- & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
- & Overall peer rating & 39.0 -- 88.7 & 72.2\\
+ & Years after PhD & -3.8 -- 12.4 & 5.4\\
+ & Prior belief & 46.4 -- 92.0 & 70.0\\
+ & Acoustic analysis peer rating & 41.2 -- 88.3 & 73.8\\
+ & Statistical analysis peer rating & 33.0 -- 93.3 & 73.2\\
+ & Overall peer rating & 39.0 -- 88.7 & 70.8\\
  &  &  \vphantom{5} & \\
@@
 \midrule
-\hspace{1em}Outcome & F0 & 37 & 36\\
- & Duration & 36 & 35\\
- & Intensity & 15 & 14\\
- & Formants & 13 & 12\\
+\hspace{1em}Outcome & F0 & 44 & 37\\
+ & Duration & 39 & 33\\
+ & Intensity & 18 & 15\\
+ & Formants & 15 & 13\\
  & Other & 3 & 3\\
  &  &  \vphantom{4} & \\
-\hspace{1em}Temporal window & Segment & 47 & 46\\
- & Word & 45 & 44\\
- & Sentence & 4 & 4\\
+\hspace{1em}Temporal window & Segment & 54 & 46\\
+ & Word & 53 & 45\\
+ & Sentence & 4 & 3\\
  & Phrase & 3 & 3\\
- & Other & 4 & 4\\
+ & Other & 4 & 3\\
  &  &  \vphantom{3} & \\
-\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
- & Continuous (mean) & 25 & 24\\
+\hspace{1em}Typicality operationalization & Categorical & 82 & 69\\
+ & Continuous (mean) & 33 & 28\\
  & Continuous (median) & 3 & 3\\
@@
 \midrule
-\hspace{1em}Framework & Frequentist & 86 & 83\\
- & Bayesian & 18 & 17\\
+\hspace{1em}Framework & Frequentist & 100 & 84\\
+ & Bayesian & 19 & 16\\
  &  &  \vphantom{1} & \\
-\hspace{1em}Model & Linear model & 102 & 98\\
+\hspace{1em}Model & Linear model & 117 & 98\\
  & GAM & 1 & 1\\
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9).
-The mean rating of the statistical analysis is 69.5 (SD = 16.5).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.5).
+The mean rating of the statistical analysis is 69.4 (SD = 15.9).
 For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
-In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.14\) (0.07 * 1.96) with 95\% credibility.''
+In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) with 95\% credibility.''
 
@@
 
-The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
-The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.04 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
+The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.14 standard units (\(\beta\) = 0.132, SD = 0.01).
 For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
@@
 After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
-The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.026 and 0.016 standard units (95\% CrI, mean = -0.005).
 In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
@@
 \textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
-In this non-preregistered model, the meta-analytic intercept estimate is between -0.013 and 0.04 standard units (95\% CrI, \(\beta\) = 0.014).
+In this non-preregistered model, the meta-analytic intercept estimate is between -0.016 and 0.03 standard units (95\% CrI, \(\beta\) = 0.008).
 This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
@@
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed.
-Estimates ranged from -0.65 to 0.99 standard units.
-
-While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 16\%).
+Estimates ranged from -0.7 to 1.01 standard units.
+
+While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 14\%).
 
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to affect model estimates.
-Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
-Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
+Neither analysts' prior beliefs in the phenomenon (\(\beta\) = -0.01, 95\% CrI = {[}-0.04, 0.01{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.04{]}) seem to affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.02, 95\% CrI = {[}-0.01, 0.05{]}).
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.04, 95\% CrI = {[}0.02, 0.07{]}).
 
@@
 This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytic decisions.
-The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing the statistical model.
-By multiplying the numbers of acoustic and model specifications, there are in principle 2444 possible unique combinations.
+The submitted analyses exhibited at least 52 unique ways of operationalizing the acoustic signal alongside 55 unique ways of constructing the statistical model.
+By multiplying the numbers of acoustic and model specifications, there are in principle 2860 possible unique combinations.
 Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results \citep{breznau2021observing}.
 
-Different analysis paths led to different categorical conclusions with 30\% of teams reported to have found at least one statistically reliable effect.
+Different analysis paths led to different categorical conclusions with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
 To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
@@
 These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between -0.65 and 0.99 standard units, which corresponds to duration values ranging from -21.86 to 50.81 ms.
+The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to duration values ranging from -23.34 to 52.07 ms.
 A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 ms at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
@@
 \midrule
-Duration & Segment & 7.4-11.4 & 10-15.4 & ms\\
-Duration & Word & 7.2-26.5 & 9.8-35.8 & ms\\
-f0 & Segment & 8.9-9.8 & 12-13.3 & hz\\
-f0 & Word & 0.9-10.4 & 1.2-14.1 & hz\\
-Intensity & Segment & 0.7-1.6 & 1-2.1 & dB\\
-Intensity & Word & 0.8-0.9 & 1-1.2 & dB\\
+Duration & Segment & 7-10.8 & 9.3-14.4 & ms\\
+Duration & Word & 6.9-25.3 & 9.1-33.4 & ms\\
+f0 & Segment & 0.9-9.4 & 1.2-12.4 & hz\\
+f0 & Word & 0.8-9.9 & 1.1-13.2 & hz\\
+Intensity & Segment & 0.7-1.5 & 0.9-2 & dB\\
+Intensity & Word & 0.7-0.9 & 1-1.2 & dB\\
 \bottomrule
@@
 Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
-However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 30\% of teams reported to have found at least one statistically reliable effect.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
 This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -29\%, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.3939394\%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
@@
 
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+We would like to thank the editors David Sbarra and Julia Strand, Matthew Goldrick and two anonymous reviewers for their insightful comments and suggestions.
+
+The initiating authors (SC, JVC, TR) wish to express immense gratitude to all the other authors, without which this project would not have come to be.
+
+All remaining errors are the initiating authors' (SC, JVC, TR)
+
+\hypertarget{funding}{%
+\section{Funding}\label{funding}}
+
+Stefano Coretta was partially supported by the European Research Council Grant No.~742289 Human interaction and the evolution of spoken accent (2017--2022) awarded to Prof.~Jonathan Harrington.
+
+Jalal Al-Tamimi was partially supported by the French Investissements d'Avenir - Labex EFL program (ANR-10- LABX-0083), contributing to the IdEx Université Paris Cité - ANR-18-IDEX-0001.
+
+George Moroz, Sita Carraturo: The research leading to these results has received funding from the Basic Research Program at the National Research University Higher School of Economics.
+
+Iñigo Urrestarazu-Porta: The research leading to these results has received funding from the MADPAB (National Research Agency of the French republic, ANR-20-CE27-0007) and Monumenta Linguae Vasconum 6: avances en la cronología de la historia y la prehistoria de la lengua vasca projects (Ministry of Science and Innovation of the Spanish kingdom, PID2020-118445GB-I00).
+
+Constantijn Kaland, Martine Grice: German Research Foundation (DFG) - Project-ID 281511265 - SFB 125.
+
+Nina R. Benway: This research was supported in part through computational resources provided by Syracuse University (NSF ACI-1341006; NSF ACI-1541396).
+
 \appendix

### 2023-01-19 RR_manuscript/Draft_RR.Rmd
♻️ - add note about model counting
🐛 - change hard-coded values to code, fix rounding

@@
 # model
+# multivariate are counted as individual models
 model_n <- msa_models_unique %>% 
@@
 The mean of the number of different predictors included in teams' models was `r round(predictor_n$mean_predictor,1)` (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)- round(predictor_n$max_predictor,1)`).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = `r round(predictor_n$min_predictor,1)` - `r round(predictor_n$max_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 Note that the design of the experiment alongside its description indicated that the experiment was designed to categorically operationalize typicality.
-This possibly explains analysts' strong preference.
+This possibly explains the analysts' strong preference.
 
@@
 
-<!-- TR: I am still confused, so if we were to ignore different random effect specifications that the number is x?
-Can we find a clearer way to express this, e.g.
-"When considering choices related to only statistical framework, type of model, distribution family and fixed terms, there were..." -->
-
 <!-- Moved 'found-effect' code to beginning of results section -->
@@
 The question arises whether these unique analysis pipelines led to different conclusions. 
-`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r perc_atleast_1`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 170 critical model coefficients, `r n_effects` were claimed to show a statistically reliable effect (`r round(perc_effects,1)`%).
+`r n_atleast_1 %>% xfun::numbers_to_words() %>% str_to_sentence()` teams out of the `r length(unique(msa_models$animal)) %>% xfun::numbers_to_words()` (`r round( perc_atleast_1, 1)`%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
+Of the `r nrow(msa_models)` critical model coefficients, `r n_effects` were claimed to show a statistically reliable effect (`r round(perc_effects,1)`%).
 

### 2023-01-19 RR_manuscript/Draft_RR.tex
🐛 - change hard-coded values to code, fix rounding

@@
 The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = -4).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1 - 5).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 The question arises whether these unique analysis pipelines led to different conclusions.
-Thirteen teams out of the thirty-three (39.3939394\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 170 critical model coefficients, 45 were claimed to show a statistically reliable effect (23.4\%).
+Thirteen teams out of the thirty-three (39.4\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
+Of the 192 critical model coefficients, 45 were claimed to show a statistically reliable effect (23.4\%).
 

### 2023-01-19 RR_manuscript/Draft_RR.Rmd
🐛 - fix between team var section hard coded values

@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between `r round(meta_bm_prereg_tidy$conf.low[["sd_animal__Intercept"]], 2)` and `r round(meta_bm_prereg_tidy$conf.high[["sd_animal__Intercept"]], 2)` standard units at 95% credibility.
-In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.high[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) with 95% credibility.”
+In other words, the estimated range of variation across teams lies somewhere between `r pm(round((meta_bm_prereg_tidy$conf.low[['sd_animal__Intercept']] * 1.96), 2))` (0.03 * 1.96) and `r pm(round((meta_bm_prereg_tidy$conf.high[['sd_animal__Intercept']] * 1.96), 2))` (0.07 * 1.96) standard units with 95% credibility.
 
@@
 The posterior 95% CrI for between-analysis variability (nested within teams) is `r round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)` to `r round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)` standard units ($\beta$ = 0.132, SD = 0.01).
-For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.
+For the sake of illustration, these would correspond to an estimate of between-model variability in segment and word durations that ranges between 7 to 14 ms for segments and between 7 and 33 ms for words at 95% credibility.
 We interpret these values in more details in the Discussion section.

### 2023-01-19 RR_manuscript/Draft_RR.tex
🐛 - fix between team var section hard coded values

@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
-In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) with 95\% credibility.''
+In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) standard units with 95\% credibility.
 
@@
 The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.14 standard units (\(\beta\) = 0.132, SD = 0.01).
-For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
+For the sake of illustration, these would correspond to an estimate of between-model variability in segment and word durations that ranges between 7 to 14 ms for segments and between 7 and 33 ms for words at 95\% credibility.
 We interpret these values in more details in the Discussion section.

### 2023-01-19 RR_manuscript/Draft_RR.Rmd

@@
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.^[Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
+This analysis was not preregistered and should thus be interpreted with caution.^[Note that before fitting this model, we fitted a separate one in which model ID was the only (non-nested) group-level effect.
 The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.]
@@
 In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.
-by duration, f0, etc,) or, if they do, they do so by a maximum of `r pm(x = 0.02)` standard units.
+by duration, f0, etc,) or, if they do, they do so by a maximum of `r pm(x = 0.03)` standard units.
 
@@
 In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, $\beta$ = `r round(meta_intercept_nest[1],3)`).
-This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
-Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
+This suggests that the acoustic measures of typical word combinations are `r -round(meta_intercept_nest[3],2)` standard units lower to `r round(meta_intercept_nest[4],2)` standard units higher than the measures of atypical word combinations, at 95% confidence.
+This result is qualitatively similar to the results obtained in the preregistered model.
 
@@
 While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.
-are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in blue, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
+are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in orange, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
 
@@
 ## Summary
-
-We gave `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` analyst teams the same speech data set to answer the same research question: *Do 
-speakers acoustically modify utterances to signal atypical word combinations?*
-In order to answer this question, teams had to interpret the research question by
-operationalizing constructs within multidimensional signals, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
-This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytic decisions.
-The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing the statistical model.
-By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
-Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.
-acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results [@breznau2021observing].
-
-Different analysis paths led to different categorical conclusions with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
-To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
-We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
-These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
-We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]
-
-For example, for those analyses that investigated the duration of vowels (e.g.
-the duration of the stressed vowel in *Banane*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)` ms.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, times 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms.]
-
-While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
-for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
-This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against] and has been replicated several times in both production and perception.
-Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction phenomena [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
-Thus, variation between different analyst teams of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 ```
+
+We gave `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` analyst teams the same speech data set to answer the same research question: *Do 
+speakers acoustically modify utterances to signal atypical word combinations?*
+In order to answer this question, teams had to interpret the research question by
+operationalizing constructs within multidimensional signals, operationalizing and choosing appropriate model predictors, and constructing appropriate statistical models.
+This complex process has led to a vast "garden of forking paths", i.e. to a wide range of combinations of possible analytic decisions.
+The submitted analyses exhibited at least `r nrow(unique_model_specs)` unique ways of operationalizing the acoustic signal alongside `r nrow(unique_acou_oper)` unique ways of constructing the statistical model.
+By multiplying the numbers of acoustic and model specifications, there are in principle `r nrow(unique_model_specs) * nrow(unique_acou_oper)` possible unique combinations. 
+Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.
+acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results [@breznau2021observing].
+
+Different analysis paths led to different categorical conclusions with `r round(perc_atleast_1, 1)`% of teams reported to have found at least one statistically reliable effect.
+To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
+We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
+These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
+We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]
+
+```{r ms}
+meta_low <- round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)
+meta_high <- round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)
+
+ms_low <- round(min(msa_models$estimate) * round(msa_sd$sd_min[1], 1), 2)
+ms_high <- round(max(msa_models$estimate) * round(msa_sd$sd_min[1], 1), 2)
+
+ms_sd_min <- round(msa_sd$sd_min[1], 1)
+ms_sd_max <- round(msa_sd$sd_max[1], 1)
+
+ms_meta_low <- round(ms_sd_min * meta_low * 1.96, 1)
+ms_meta_high <- round(ms_sd_max * meta_high * 1.96, 1)
+```
+
+For example, for those analyses that investigated the duration of vowels (e.g.
+the duration of the stressed vowel in *Banáne*), the reported duration measures exhibit standard deviations that range from `r ms_sd_min` to `r ms_sd_max` ms.
+These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
+The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from `r ms_low` to `r ms_high` ms.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r ms_meta_low` and `r ms_meta_high` ms at 95% credibility.
+The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: `r ms_sd_min` * `r meta_low` * 1.96 = `r ms_meta_low` ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, times 1.96: `r ms_sd_max` * `r meta_high` * 1.96 = `r ms_meta_high` ms.
+
+While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
+for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
+This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against] and has been replicated several times in both production and perception.
+Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction phenomena [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect].
+Thus, variation between different analyst teams of `r ms_meta_low` to `r ms_meta_high` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
-As shown by Breznau et al.[-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+As shown by Breznau et al. [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
 
@@
 there is no evidence for a relationship.
-However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with `r round(perc_atleast_1, 1)`% of teams reported to have found at least one statistically reliable effect.
 This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`%, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r round(1-perc_atleast_1, 1)`%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).

### 2023-01-19 RR_manuscript/Draft_RR.tex

@@
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
+This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fitted a separate one in which model ID was the only (non-nested) group-level effect.
   The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.}
@@
 The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.026 and 0.016 standard units (95\% CrI, mean = -0.005).
-In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.03\) standard units.
 
@@
 In this non-preregistered model, the meta-analytic intercept estimate is between -0.016 and 0.03 standard units (95\% CrI, \(\beta\) = 0.008).
-This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
-Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
+This suggests that the acoustic measures of typical word combinations are 0.02 standard units lower to 0.03 standard units higher than the measures of atypical word combinations, at 95\% confidence.
+This result is qualitatively similar to the results obtained in the preregistered model.
 
@@
 
-While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 14\%).
+While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in orange, 14\%).
 
@@
 
-Different analysis paths led to different categorical conclusions with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
+Different analysis paths led to different categorical conclusions with 39.4\% of teams reported to have found at least one statistically reliable effect.
 To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
@@
 
-For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banane}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
-The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to duration values ranging from -23.34 to 52.07 ms.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 ms at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
+For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banáne}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
+The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from -23.34 to 33.84 ms.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.2 and 14.1 ms at 95\% credibility.
+The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: 33.4 * 0.11 * 1.96 = 7.2 ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: 51.4 * 0.14 * 1.96 = 14.1 ms.
 
@@
 Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts \citep{coretta2019}, reduction phenomena \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
-Thus, variation between different analyst teams of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+Thus, variation between different analyst teams of 7.2 to 14.1 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
-As shown by Breznau et al.\citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
 
@@
 Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
-However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.4\% of teams reported to have found at least one statistically reliable effect.
 This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.3939394\%, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.4\%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).

### 2023-01-19 RR_manuscript/Draft_RR.tex

@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 32 teams to be eligible to be included in the meta-analytic model.
+Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 33 teams to be eligible to be included in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
@@
 
-The included analyses were provided by 32 teams, comprising 117 analysts, with a median of 3.0 individuals per team.
+The included analyses were provided by 33 teams, comprising 120 analysts, with a median of 3.0 individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
@@
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 119 individual models (including 192 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 115 individual models (including 192 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 \caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis.
-The data set included analyses from 32 teams and  117 analysts.}
+The data set included analyses from 33 teams and  120 analysts.}
 \centering

### 2023-01-19 RR_manuscript/supplementary_materials.Rmd

@@
   team_leaders %>% 
+    left_join(select(teams, animal, leader = coordinator), by = "leader") %>% 
     filter(leader %in% teams_used_in_analysis) %>% 
-    group_by(leader) %>% 
+    group_by(animal) %>% 
     mutate(member_num = seq_along(ResponseId)) %>% 
-    group_by(leader) %>% 
+    group_by(animal) %>% 
     mutate(n_members = max(member_num)) %>% 
-    distinct(leader, n_members) %>% 
+    distinct(animal, n_members) %>% 
     ungroup() %>% 

### 2023-01-20 RR_manuscript/Draft_RR.tex
♻️ - render manuscript

@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 33 teams to be eligible to be included in the meta-analytic model.
+Of the analyses submitted by the 46 teams, the initiating authors identified analyses from 33 teams to be eligible to be included in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

### 2023-01-20 RR_manuscript/RR.Rmd
🚚 - rename Draft_RR to RR

--- 2023-01-19 RR_manuscript/Draft_RR.Rmd
@@
 
-no_analyses <- msa_models_unique %>%
+no_analyses <- msa_models %>% 
+  select(team, animal, model_n) %>% 
+  distinct() %>% 
   nrow()
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis. 
-Of the analysis submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
+Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

### 2023-01-20 RR_manuscript/RR_stage_2.tex
✨ - run RR diff

--- 2023-01-20 RR_manuscript/Draft_RR.tex
@@
 Details about the refitting procedure can be found at \url{https://many-speech-analyses.github.io/many_analyses/scripts/r/04_refit_workflow}.
-Relative to the registered protocol, we made minor changes to the refitting procedure, specifically file and variable naming conventions and the use of treatment contrasts instead of sum coding.
-All models converged (\(\hat{R}\) was approximately 1).
-Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58\% of total number of samples), which the authors deemed not to be problematic.
 
@@
 When fitting the model, we realized that the measure of conservativeness is related to the standard error of the estimates (i.e.~more group-level effects = higher standard error).
-Moreover, there was no team that declared to have made post-hoc changes to the analyses, thus we decided against including these two preregistered predictors in the model.
+Moreover, there was no team that declared to have made post-hoc changes to the analyses, this we decided against including these two preregistered predictors in the model.
 
@@
 We also archived copies of our survey instruments from analysts and peer-reviewers.
-Further documents concerning the collaborative editing of the Registered Report can be found at \url{https://drive.google.com/drive/folders/1-DOcj1qtEkvWfzu_FrsxkIGfPS0DyLXB?usp=sharing}.
 
@@
 We also excluded any individual analysis that does not produce an outcome that could be interpreted as an answer to our primary question.
-We also did no include analyses for which we could not extract standardized effect sizes. For a list of exclusion criteria, see Section Descriptive statistics below.
+For a list of exlcusion criteria, see Section Descriptive statistics below.
 
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analyses submitted by the 46 teams, the initiating authors identified analyses from 33 teams to be eligible to be included in the meta-analytic model.
+Of the analysis submitted by the 46 teams, the initiating authors identified analyses from 30 teams to be eligible to be included in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
-Note that due to the unforeseen variability across teams, the latter exclusion criteria were not preregistered and were applied after having seen all analytic strategies.
 
@@
 
-The included analyses were provided by 33 teams, comprising 120 analysts, with a median of 3.0 individuals per team.
+The included analyses were provided by 30 teams, comprising 109 analysts, with a median of 3.0 individuals per team.
 Upon sign-up, we collected background information from each analyst through the intake form, which was administered during Phase 1, prior to the data being released to the teams.
-Analysts had a median of 5.4 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
-The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 46.4 to 92.0 with a median of 70.0.
+Analysts had a median of 5.8 years of experience after completing their PhD, ranging from -3.8 years, i.e.~PhD students (or less experienced) to 12.4 years, suggesting that, on average, analysts were experienced researchers.
+The analysts' prior belief in the effect under investigation, on a scale from 0 to 100, ranged from 48.5 to 92.0 with a median of 70.0.
 We take this to suggest that, overall, analysts had a rather high positive prior belief in the investigated relationship between acoustics and word combination typicality.
 
-At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 115 individual models (including 192 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
+At the end of Phase 2 (primary data analysis), the teams had submitted a grand total of 104 individual models (including 170 critical model coefficients, given that some models returned more than one critical coefficient) to answer the research question, with a median of 3 models per team.
 Table \ref{tab:descriptives-table} provides a summary of the contributing teams and their analyses.
@@
 The analytic teams differed in their approach to the acoustic analysis of the speech signal, including choices related to specific acoustic measures, the temporal window used, and how the measures were transformed.
-Thirty-seven percent of the models used f0 as the outcome variable, 33\% used a measure of duration, 13\% used vowel formants, 15\% intensity, and 3\% other measures.
-
-Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 45\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 3\% from the whole sentence, and 3\% used a different time window.
-Based on a coarse coding of how acoustic measures were operationalized, we find a total of 55 different measurement specifications.
+Thirty-six percent of the models used f0 as the outcome variable, 35\% used a measure of duration, 12\% used vowel formants, 14\% intensity, and 3\% other measures.
+
+Forty-five percent of models used acoustic measures taken at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 43\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 3\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 4\% from the whole sentence, and 4\% used a different time window.
+Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
 For example, if we consider those analyses that target f0, we find that it is operationalized in many different ways including the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
@@
 The mean of the number of different predictors included in teams' models was 2 (defined as variables or columns in the data table).
-This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1 - 5).
+This means that, in addition to the critical predictor (typicality of the adjective noun combinations), models had on average one additional predictor (range = 1-\texttt{r}round(predictor\_n\$max\_predictor,1)`).
 Possible information that was used as predictors included the information structure of the sentence, trial number, semantic dimensions of the referent, part of speech, and speaker gender.
@@
 The data given to the teams allowed them to operationalize the predictor of interest, word typicality, in different ways.
-Among the possible operationalizations, 69\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 28\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
+Among the possible operationalizations, 72\% of models contained typicality as a categorical variable (e.g.~atypical vs.~typical), 24\% used a continuous typicality scale from 0-100 by calculating the mean typicality for each word combination as obtained from the norming study, while 3\% of the models used the median typicality rating.
 Note that the design of the experiment alongside its description indicated that the experiment was designed to categorically operationalize typicality.
-This possibly explains the analysts' strong preference.
-
-The majority of models were run within a frequentist framework (84\%).
-Sixteen percent were run within a Bayesian framework.
+This possibly explains analysts' strong preference.
+
+The majority of models were run within a frequentist framework (83\%).
+Seventeen percent were run within a Bayesian framework.
 While teams almost exclusively used linear models to analyze their data (98\%), teams differed drastically in how they accounted for dependencies within the data.
@@
 An appropriate way to account for this non-independence is by using models that include so-called random or group level effects \citep[e.g.,][]{gelman2006data, schielzeth2009conclusions}, variably known as mixed-effects, hierarchical, multi-level, or nested models (among other names).
-Nine percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
-Sixty-two percent specified random intercepts only, and 29\% specified both random intercepts and random slopes to account for the non-independence.
+Eight percent of the linear models specified no random effects at all (without pooling their data), effectively ignoring these non-independences \citep{hurlbert1984pseudoreplication}.
+Sixty-five percent specified random intercepts only, and 27\% specified both random intercepts and random slopes to account for the non-independence.
 On average, teams that specified random effects included 2.5 random terms in their models.
-Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 52 different model specifications.
-
-When considering both acoustic and statistical analyses, we have found a grand total of 119 different analytic pipelines.
+Based on statistical framework, type of model, distribution family, fixed terms, and not including random effects, there were a total of 47 different model specifications.
+
+When considering both acoustic and statistical analyses, we have found a grand total of 104 different analytic pipelines.
 In other words, each individual analysis submitted was unique.
@@
 The question arises whether these unique analysis pipelines led to different conclusions.
-Thirteen teams out of the thirty-three (39.4\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
-Of the 192 critical model coefficients, 45 were claimed to show a statistically reliable effect (23.4\%).
+Nine teams out of the thirty (30\%) reported to have found at least one statistically reliable effect (based on the inferential criteria they specified).
+Of the 104 submitted models, 37 were reported to show a statistically reliable effect (21.8\%).
 
@@
 \caption{\label{tab:descriptives-table}Descriptive statistics of teams, acoustic analyses, and statistical analyses included in the meta-analysis.
-The data set included analyses from 33 teams and  120 analysts.}
+The data set included analyses from 30 teams and  109 analysts.}
 \centering
@@
  & Team size & 1.0 -- 12.0 & 3.0\\
- & Years after PhD & -3.8 -- 12.4 & 5.4\\
- & Prior belief & 46.4 -- 92.0 & 70.0\\
- & Acoustic analysis peer rating & 41.2 -- 88.3 & 73.8\\
- & Statistical analysis peer rating & 33.0 -- 93.3 & 73.2\\
- & Overall peer rating & 39.0 -- 88.7 & 70.8\\
+ & Years after PhD & -3.8 -- 12.4 & 5.8\\
+ & Prior belief & 48.5 -- 92.0 & 70.0\\
+ & Acoustic analysis peer rating & 41.2 -- 88.3 & 75.2\\
+ & Statistical analysis peer rating & 33.0 -- 93.3 & 74.1\\
+ & Overall peer rating & 39.0 -- 88.7 & 72.2\\
  &  &  \vphantom{5} & \\
@@
 \midrule
-\hspace{1em}Outcome & F0 & 44 & 37\\
- & Duration & 39 & 33\\
- & Intensity & 18 & 15\\
- & Formants & 15 & 13\\
+\hspace{1em}Outcome & F0 & 37 & 36\\
+ & Duration & 36 & 35\\
+ & Intensity & 15 & 14\\
+ & Formants & 13 & 12\\
  & Other & 3 & 3\\
  &  &  \vphantom{4} & \\
-\hspace{1em}Temporal window & Segment & 54 & 46\\
- & Word & 53 & 45\\
- & Sentence & 4 & 3\\
+\hspace{1em}Temporal window & Segment & 47 & 46\\
+ & Word & 45 & 44\\
+ & Sentence & 4 & 4\\
  & Phrase & 3 & 3\\
- & Other & 4 & 3\\
+ & Other & 4 & 4\\
  &  &  \vphantom{3} & \\
-\hspace{1em}Typicality operationalization & Categorical & 82 & 69\\
- & Continuous (mean) & 33 & 28\\
+\hspace{1em}Typicality operationalization & Categorical & 75 & 73\\
+ & Continuous (mean) & 25 & 24\\
  & Continuous (median) & 3 & 3\\
@@
 \midrule
-\hspace{1em}Framework & Frequentist & 100 & 84\\
- & Bayesian & 19 & 16\\
+\hspace{1em}Framework & Frequentist & 86 & 83\\
+ & Bayesian & 18 & 17\\
  &  &  \vphantom{1} & \\
-\hspace{1em}Model & Linear model & 117 & 98\\
+\hspace{1em}Model & Linear model & 102 & 98\\
  & GAM & 1 & 1\\
@@
 Teams reviewed each others' acoustic and statistical analyses.
-The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.5).
-The mean rating of the statistical analysis is 69.4 (SD = 15.9).
+The mean rating of the acoustic analyses, on a scale from 0 to 100, is 71.5 (SD = 13.9).
+The mean rating of the statistical analysis is 69.5 (SD = 16.5).
 For reference, as mentioned in the Methods section, a score of 75 was defined as ``an imperfect analysis but the needed changes are unlikely to dramatically alter the final interpretation'', indicating that on average reviewers judged the provided analyses to be appropriate, although ``imperfect''.
@@
 According to the preregistered meta-analytic model, the group-level standard deviation for teams is between 0.03 and 0.07 standard units at 95\% credibility.
-In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.13\) (0.07 * 1.96) standard units with 95\% credibility.
+In other words, the estimated range of variation across teams lies somewhere between \(\pm 0.06\) (0.03 * 1.96) and \(\pm 0.14\) (0.07 * 1.96) with 95\% credibility.''
 
@@
 To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
-This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fitted a separate one in which model ID was the only (non-nested) group-level effect.
+This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
   The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.}
 
-The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.04 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
-The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.14 standard units (\(\beta\) = 0.132, SD = 0.01).
-For the sake of illustration, these would correspond to an estimate of between-model variability in segment and word durations that ranges between 7 to 14 ms for segments and between 7 and 33 ms for words at 95\% credibility.
+The nested model yields a posterior 95\% CrI for between-team variability of 0 to 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of about \(\pm 0\) to \(\pm 0.1\) standard units and 95\% probability.
+The posterior 95\% CrI for between-analysis variability (nested within teams) is 0.11 to 0.15 standard units (\(\beta\) = 0.132, SD = 0.01).
+For the sake of illustration, these would correspond to an estimate of between-model variability in milliseconds (if looking for example at segment duration) that ranges between 7.4 and 15.1 ms at 95\% credibility.
 We interpret these values in more details in the Discussion section.
@@
 After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
-The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.026 and 0.016 standard units (95\% CrI, mean = -0.005).
-In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.03\) standard units.
+The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.024 and 0.021 standard units (95\% CrI, mean = -0.001).
+In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.
 
 \textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
-In this non-preregistered model, the meta-analytic intercept estimate is between -0.016 and 0.03 standard units (95\% CrI, \(\beta\) = 0.008).
-This suggests that the acoustic measures of typical word combinations are 0.02 standard units lower to 0.03 standard units higher than the measures of atypical word combinations, at 95\% confidence.
-This result is qualitatively similar to the results obtained in the preregistered model.
+In this non-preregistered model, the meta-analytic intercept estimate is between -0.013 and 0.04 standard units (95\% CrI, \(\beta\) = 0.014).
+This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
+Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).
 
@@
 When looking at the raw estimates and their variance (grey triangles and lines), it is striking how much estimates differed.
-Estimates ranged from -0.7 to 1.01 standard units.
-
-While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in orange, 14\%).
+Estimates ranged from -0.65 to 0.99 standard units.
+
+While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 16\%).
 
@@
 The model suggests that most team-specific predictors yield very small deviations from the meta-analytic estimate and their 95\% credible intervals include zero, leaving us highly uncertain about their direction.
-Neither analysts' prior beliefs in the phenomenon (\(\beta\) = -0.01, 95\% CrI = {[}-0.04, 0.01{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.04{]}) seem to affect model estimates.
-Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.02, 95\% CrI = {[}-0.01, 0.05{]}).
-Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.04, 95\% CrI = {[}0.02, 0.07{]}).
+Neither analysts' prior beliefs in the phenomenon (\(\beta\) = 0.00, 95\% CrI = {[}-0.03, 0.03{]}), nor their seniority in terms of years after completing their PhD (\(\beta\) = 0.01, 95\% CrI = {[}-0.03, 0.04{]}) seem to affect model estimates.
+Similarly, the evaluation of the quality of the analysis from their peers yielded a rather small effect magnitude, again characterized by large uncertainty (\(\beta\) = 0.01, 95\% CrI = {[}-0.02, 0.05{]}).
+Interestingly, the model uniqueness, i.e.~how unique the choice and combination of predictors are, affects the analysts' estimate, with more unique models producing higher positive estimates (\(\beta\) = 0.05, 95\% CrI = {[}0.02, 0.07{]}).
 
@@
 (A) Posterior samples for the four most frequent outcome variables; (B) Posterior samples for the four most frequent temporal windows: Black points indicate medians; shaded areas represents 50/80/95\% highest density intervals.
-(C) Mean posterior samples (white circles) and 80/95\% credible intervals for all predictors grouped into predictors related to (1) temporal window, (2) outcome variable, and (3) team/analysis.}\label{fig:plot-meta2}
+(C) Mean posterior samples (white circles) and 80/95\% credible intervals for all predictors.}\label{fig:plot-meta2}
 \end{figure}
@@
 This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytic decisions.
-The submitted analyses exhibited at least 52 unique ways of operationalizing the acoustic signal alongside 55 unique ways of constructing the statistical model.
-By multiplying the numbers of acoustic and model specifications, there are in principle 2860 possible unique combinations.
+The submitted analyses exhibited at least 47 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing the statistical model.
+By multiplying the numbers of acoustic and model specifications, there are in principle 2444 possible unique combinations.
 Note that this is a conservative estimate of the number of possible analytic choices for our research question, ignoring many other degrees of freedom like e.g.~acoustic parameter extraction, outlier treatment, and transformations, all of which might have an impact on the final results \citep{breznau2021observing}.
 
-Different analysis paths led to different categorical conclusions with 39.4\% of teams reported to have found at least one statistically reliable effect.
+Different analysis paths led to different categorical conclusions with 30\% of teams reported to have found at least one statistically reliable effect.
 To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
@@
 
-For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banáne}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
-The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from -23.34 to 33.84 ms.
-A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.2 and 14.1 ms at 95\% credibility.
-The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: 33.4 * 0.11 * 1.96 = 7.2 ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: 51.4 * 0.14 * 1.96 = 14.1 ms.
+For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banane}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
+These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
+The reported effect estimates from teams varied between -0.65 and 0.99 standard units, which corresponds to duration values ranging from -21.86 to 50.81 ms.
+A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 ms at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}
 
@@
 Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts \citep{coretta2019}, reduction phenomena \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
-Thus, variation between different analyst teams of 7.2 to 14.1 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
+Thus, variation between different analyst teams of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.
 
@@
 \midrule
-Duration & Segment & 7-10.8 & 9.3-14.4 & ms\\
-Duration & Word & 6.9-25.3 & 9.1-33.4 & ms\\
-f0 & Segment & 0.9-9.4 & 1.2-12.4 & hz\\
-f0 & Word & 0.8-9.9 & 1.1-13.2 & hz\\
-Intensity & Segment & 0.7-1.5 & 0.9-2 & dB\\
-Intensity & Word & 0.7-0.9 & 1-1.2 & dB\\
+Duration & Segment & 7.4-11.4 & 10-15.4 & ms\\
+Duration & Word & 7.2-26.5 & 9.8-35.8 & ms\\
+f0 & Segment & 8.9-9.8 & 12-13.3 & hz\\
+f0 & Word & 0.9-10.4 & 1.2-14.1 & hz\\
+Intensity & Segment & 0.7-1.6 & 1-2.1 & dB\\
+Intensity & Word & 0.8-0.9 & 1-1.2 & dB\\
 \bottomrule
@@
 While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
-As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
+As shown by Breznau et al.\citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
 
@@
 Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
-However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.4\% of teams reported to have found at least one statistically reliable effect.
+However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 30\% of teams reported to have found at least one statistically reliable effect.
 This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.4\%, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -29\%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
@@
 There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
-Thus beyond a mere replication crisis, quantitative disciplines are going through an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
+Beyond a replication crisis, quantitative disciplines are going through what has been called an ``inference crisis'' \citep{rotello2015more, starns2019assessing}.
 As shown by the peer-ratings of the analyses reported in this study, well-trained and experienced speech researchers not only applied completely different approaches to the same research question, but also considered most of these alternative approaches acceptable.
@@
 Some of the analysis teams explicitly recognized and acknowledged the need to formulate a more precise version of the research question by preregistering their planned data analysis pipeline.
-Preregistration, i.e.~a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
-However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims:
-
+
+In light of the observed analytic flexibility, there are a few things that researchers can do to appropriately calibrate confidence in their claims.
 First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
@@
 
-Second, making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
+Second, making analytic pathways completely re-traceable does not change the fact that analysts apply different analytic approaches.
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
@@
 Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of certain functions are expressed in the acoustic signal.
-Possible tools to strengthen theoretical development relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
-Although conceptually promising, in their current state, such formalized models typically work in spaces that are much lower in dimensionality than the complex systems in which we measure.
-Thus, future research should spend resources on attempting to quantitatively relate the abstract theoretical space to the complex measurement space.
+Possible tools to strengthen theoretical development are relate to mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.
 
@@
 
-Our study has several limitations that need to be considered when interpreting our results.
+Our study has several limitations that need to be considered when evaluating our results.
 
@@
 
-See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy-all.png}.
+See \url{https://github.com/many-speech-analyses/many_analyses/blob/main/figs/credit-taxonomy.png}.
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-We would like to thank the editors David Sbarra and Julia Strand, Matthew Goldrick and two anonymous reviewers for their insightful comments and suggestions.
-
-The initiating authors (SC, JVC, TR) wish to express immense gratitude to all the other authors, without which this project would not have come to be.
-
-All remaining errors are the initiating authors' (SC, JVC, TR)
-
-\hypertarget{funding}{%
-\section{Funding}\label{funding}}
-
-Stefano Coretta was partially supported by the European Research Council Grant No.~742289 Human interaction and the evolution of spoken accent (2017--2022) awarded to Prof.~Jonathan Harrington.
-
-Jalal Al-Tamimi was partially supported by the French Investissements d'Avenir - Labex EFL program (ANR-10- LABX-0083), contributing to the IdEx Université Paris Cité - ANR-18-IDEX-0001.
-
-George Moroz, Sita Carraturo: The research leading to these results has received funding from the Basic Research Program at the National Research University Higher School of Economics.
-
-Iñigo Urrestarazu-Porta: The research leading to these results has received funding from the MADPAB (National Research Agency of the French republic, ANR-20-CE27-0007) and Monumenta Linguae Vasconum 6: avances en la cronología de la historia y la prehistoria de la lengua vasca projects (Ministry of Science and Innovation of the Spanish kingdom, PID2020-118445GB-I00).
-
-Constantijn Kaland, Martine Grice: German Research Foundation (DFG) - Project-ID 281511265 - SFB 125.
-
-Nina R. Benway: This research was supported in part through computational resources provided by Syracuse University (NSF ACI-1341006; NSF ACI-1541396).
-
 \appendix

### 2023-01-23 RR_manuscript/RR.Rmd
♻️ - edit per suggestion in #307

@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified analyses from `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams to be eligible to be included in the meta-analytic model.
+Of the analyses submitted by the `r pull_from_tib(team_desc_df, stage, "Submitted", n_teams)` teams, the initiating authors identified `r pull_from_tib(team_desc_df, stage, "Final", n_teams)` teams with submissions meeting the criteria for inclusion in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.

### 2023-01-23 RR_manuscript/RR.Rmd
♻️ - edit per suggestion in #307

@@
 a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
-However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims:
-
-First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
+However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims.
+
+Through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others [@munafo2017manifesto; @vazire2017quality].
 Sharing further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility [@lebel2018unified]. 
@@
 
-Second, making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
+Making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
@@
 
-Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+If we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
 Such an analysis can provide insight into how much the conclusions change due to analytic choices as well as which choices have neglible or large impact on the result. 

### 2023-01-23 RR_manuscript/RR.Rmd
♻️ - edit per suggestion in #307

@@
 
-Making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
+Making analytic pathways completely re-traceable and preregistering them in advance does not change the fact that different analysts might apply different analytic approaches (preregistered or not).
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.

### 2023-01-24 RR_manuscript/RR.Rmd
edits 24th Jan

@@
 When considering both acoustic and statistical analyses, we have found a grand total of `r nrow(unique_acou_stat)` different analytic pipelines.
-In other words, each individual analysis submitted was unique.
+In other words, each individual analysis submitted was unique.^[A sankey diagram illustrating the relationship between choices related to outcome, temporal window and operationalization can be found in the supplementary materials at <https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf>.]
 
@@
 the duration of the stressed vowel in *Banáne*), the reported duration measures exhibit standard deviations that range from `r ms_sd_min` to `r ms_sd_max` ms.
-These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
+These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimated standard units.
 The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from `r ms_low` to `r ms_high` ms.
@@
 Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
-For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
+For example, five teams measured f0 in the noun and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.35 to 0.19 standard deviations. 
 While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.
-mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.
-the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
+mean, minimum, maximum, point or range) and how their statistical model was constructed (i.e.
+the number of predictors ranged from 1-2 and the number of random effect terms ranged from 1-10).
 As shown by Breznau et al. [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.
@@
 Preregistration, i.e.
-a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
+a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
 However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims.

### 2023-01-26 RR_manuscript/RR.Rmd
♻️ - edit and render RR

--- 2023-01-23 RR_manuscript/RR.Rmd
@@
 the duration of the stressed vowel in *Banáne*), the reported duration measures exhibit standard deviations that range from `r ms_sd_min` to `r ms_sd_max` ms.
-These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
+These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the the standard unit values of the meta-analytic estimates.
 The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from `r ms_low` to `r ms_high` ms.

### 2023-01-26 RR_manuscript/RR.tex
♻️ - edit and render RR

--- 2023-01-20 RR_manuscript/Draft_RR.tex
@@
 Only analyses from which it was possible to extract an effect size were included in the meta-analysis.
-Of the analyses submitted by the 46 teams, the initiating authors identified analyses from 33 teams to be eligible to be included in the meta-analytic model.
+Of the analyses submitted by the 46 teams, the initiating authors identified 33 teams with submissions meeting the criteria for inclusion in the meta-analytic model.
 Reasons for exclusion were: use of Generalized Additive Models (4 teams) which do not lend themselves easily to the meta-analytic methods employed in this study, use of machine learning techniques (3 teams), use of typicality as the outcome variable/response (3 teams), or use of other methods that returned statistics that could not be included in the meta-analytic model.
@@
 For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banáne}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
-These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
+These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the the standard unit values of the meta-analytic estimates.
 The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from -23.34 to 33.84 ms.
@@
 Preregistration, i.e.~a time-stamped document in which researchers specify how they plan to collect their data and/or how they plan to conduct their confirmatory analysis, is can be a useful tool to safeguard researchers against the urge to explore many different analytical paths before choosing the one that, in hindsight, seems most justified.
-However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims:
-
-First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
+However, as long as the theoretical landscape does not allow for more precise hypotheses, the value of preregistration is limited and we need to find ways to appropriately calibrate the confidence in our claims.
+
+Through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
 Sharing further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
@@
 
-Second, making analytic pathways completely re-traceable and preregistering them in advance do not change the fact that different analysts might apply different analytic approaches (preregistered or not).
+Making analytic pathways completely re-traceable and preregistering them in advance does not change the fact that different analysts might apply different analytic approaches (preregistered or not).
 Crowd-sourced projects such as the current one can shed light on the range of degrees of freedom during analysis and could possibly help produce a consensual estimated effect if the research hypothesis is specific enough.
@@
 
-Third, if we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
+If we develop a good understanding of relevant analytic degrees of freedom, we could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
 Such an analysis can provide insight into how much the conclusions change due to analytic choices as well as which choices have neglible or large impact on the result.

### 2023-01-26 scripts/r/04-1_refitted.Rmd
♻️ - add note about needing refitted models rds files

@@
 
-```{r}
-#| label: get-divergent-transitions
+For the following to run, it is necessary to have the individual refitted models in `data/analyses/models`.
+
+```{r get-divergent-transitions}
 # Function to add up all DTs from a model

### 2023-01-26 scripts/r/04-1_refitted.Rmd

@@
 library("broom.mixed")
+library("brms")
 

### 2023-01-26 scripts/r/04-1_refitted.Rmd
filter out GAMM from divergent transition calculation

@@
   ) %>% 
+  filter(mod_name != "petauroides_fistulator_1_f0_cat") %>% 
   mutate(

### 2023-01-26 RR_manuscript/RR.Rmd
edit upper bound of divergent transitions

@@
 All models converged ($\hat{R}$ was approximately 1).
-Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58% of total number of samples), which the authors deemed not to be problematic.
+Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 156 (143 represents 3.9% of total number of samples), which the authors deemed not to be problematic.
 

### 2023-01-26 scripts/r/04-1_refitted.Rmd
♻️ - add note about manual up/download to/from OFS

@@
 
-Here's the code that does that for you.
+~~Here's the code that does that for you.~~ The code has repeatedly failed to upload ALL models. Please upload manually.
 
 ```{r upload-refitted, eval=FALSE}
-cache <- osf_retrieve_node("wds2m")
-refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
-  filter(name == "refitted")
-models <- list.files(
-  "./data/analyses/models",
-  full.names = TRUE
-)
-
-osf_upload(
-  refitted,
-  path = models,
-  recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
-)
+# cache <- osf_retrieve_node("wds2m")
+# refitted <- osf_ls_files(osf_ls_files(cache, type = "folder")) %>%
+#   filter(name == "refitted")
+# models <- list.files(
+#   "./data/analyses/models",
+#   full.names = TRUE
+# )
+# 
+# osf_upload(
+#   refitted,
+#   path = models,
+#   recurse = TRUE, conflicts = "skip", progress = TRUE, verbose = TRUE
+# )
 ```
@@
 
+The code has repeatedly failed to download ALL models. Please download manually.
+
 ```{r download-refitted, eval=FALSE}
-cache <- osf_retrieve_node("wds2m")
-refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)
-
-osf_download(
-  refitted_rds,
-  path = "./data/analyses/models/",
-  conflicts = "skip", progress = TRUE, verbose = TRUE
-)
+# cache <- osf_retrieve_node("wds2m")
+# refitted_rds <- osf_ls_files(cache, "models/refitted", n_max = Inf)
+# 
+# osf_download(
+#   refitted_rds,
+#   path = "./data/analyses/models/",
+#   conflicts = "skip", progress = TRUE, verbose = TRUE
+# )
 ```

### 2023-01-27 RR_manuscript/RR.tex
♻️ - render RR

@@
 All models converged (\(\hat{R}\) was approximately 1).
-Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 143 (143 represents 3.58\% of total number of samples), which the authors deemed not to be problematic.
+Of the models with divergent transitions (n = 10), the number of divergences ranged from 1 to 156 (143 represents 3.9\% of total number of samples), which the authors deemed not to be problematic.
 

### 2023-01-27 RR_manuscript/RR.Rmd

@@
 The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at <https://osf.io/3bmcp/>, in the `scripts/r/` folder.
+An interactive web application that allows the interested reader to explore the data set is available at <https://many-speech-analyses.github.io/shiny>.
 
@@
 Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation: 
-Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.
+Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole data set; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.
 whether specific speech production instances were excluded or not) and quantitative grounds (i.e.

### 2023-01-27 RR_manuscript/RR.tex
♻️ - render RR and RR diff

@@
 The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at \url{https://osf.io/3bmcp/}, in the \texttt{scripts/r/} folder.
+An interactive web application that allows the interested reader to explore the data set is available at \url{https://many-speech-analyses.github.io/shiny}.
 
@@
 Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation:
-Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.~whether specific speech production instances were excluded or not) and quantitative grounds (i.e.~whether data were trimmed or not).
+Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole data set; and they differed whether and if so how measurements were excluded based on both qualitative (i.e.~whether specific speech production instances were excluded or not) and quantitative grounds (i.e.~whether data were trimmed or not).
 

### 2023-01-28 RR_manuscript/RR.Rmd
removed reference to "orange" in fig 3

@@
 
-While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.
-are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in orange, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
+While the majority of model estimates and their uncertainty after shrinkage yields inconclusive results (i.e.
+are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (`r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).
 
@@
 Raw estimates are displayed in grey.
-Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.
+Estimates after shrinkage as provided by the meta-analytic model are displayed in black.
 

### 2023-01-30 RR_manuscript/RR.tex
♻️ - render RR and RR diff

@@
 
-While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in orange, 14\%).
+While the majority of model estimates and their uncertainty after shrinkage yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (14\%).
 
@@
 Raw estimates are displayed in grey.
-Estimates after shrinkage as provided by the meta-analytic model are displayed in black/orange.}\label{fig:plot-meta1}
+Estimates after shrinkage as provided by the meta-analytic model are displayed in black.}\label{fig:plot-meta1}
 \end{figure}

### 2023-02-06 RR_manuscript/RR.Rmd
🐛 - re-apply changes from bd13382ce5927a554babf2561c739db5a915c13a (fixes #319)

@@
 In other words, each individual analysis submitted was unique.
+A sankey diagram illustrating the relationship between choices related to outcome, temporal window and operationalization can be found in the supplementary materials at <https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf>.
 

### 2023-02-06 RR_manuscript/RR.tex
🐛 - re-apply changes from bd13382ce5927a554babf2561c739db5a915c13a (fixes #319)

@@
 In other words, each individual analysis submitted was unique.
+A sankey diagram illustrating the relationship between choices related to outcome, temporal window and operationalization can be found in the supplementary materials at \url{https://many-speech-analyses.github.io/many_analyses/RR_manuscript/supplementary_materials.pdf}.
 
@@
 Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
-For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
-While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
+For example, five teams measured f0 in the noun and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.35 to 0.19 standard deviations.
+While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, minimum, maximum, point or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-2 and the number of random effect terms ranged from 1-10).
 As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

### 2023-06-11 RR_manuscript/RR.Rmd
update funding
fix typo

@@
 This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
-If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r round(1-perc_atleast_1, 1)`%, with the majority of teams not detecting the effect.
+If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r round(100 - perc_atleast_1, 1)`%, with the majority of teams not detecting the effect.
 If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
@@
 
-Constantijn	Kaland, Martine Grice: German Research Foundation (DFG) - Project-ID 281511265 - SFB 125.
+Constantijn	Kaland, Martine Grice, Francesco Cangemi, Maria Lialiou, Malin Spaniol, Simon Wehrle: German Research Foundation (DFG) - Project-ID 281511265 - SFB 1252.
 
